### 2005-11-29 TTau_Halpha/kurosawa.tex
new paper
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@603 25464f21-6099-402c-b30a-640f1d40d38b

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
%\usepackage[T1]{fontenc}
%\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amssymb}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Bold symbol macro for standard LaTeX users
\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{times}

\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{\apj}
\newcommand{\pasp}{PASP}
\newcommand{\aj}{AJ}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\aapr}{A\&AR}
\newcommand{\pasj}{PASJ}

\newcommand{\kmps}{\mathrm{km~s^{-1}}}
\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
\newcommand{\Kelvin}{\mathrm{K}}

\usepackage{babel}
\makeatother
\begin{document}
\title[On H-$\alpha$ formation of T Tauri stars]{On formation of H-$\alpha$ from classical T Tauri stars: the disc, wind, and magnetospheric-accretion hybrid model}

\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries and Neil H. Symington\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}

\date{Dates to be inserted}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2005}

\maketitle

\label{firstpage}

\begin{abstract}

We present disc--wind--magnetosphere hybrid radiative transfer models
for classical T~Tauri stars, and investigate the formation of H$\alpha$
to understand their complex circumstellar environment, and to understand
the wide variety of emission line profiles seen in observations. To
overcome the limited applicability of the radiative transfer models
with only magnetospherical accretion to fitting observed H$\alpha$
profiles, and to any other lines affected by the stellar wind) presented,
two types of kinematic wind models are introduced: (1)~the bipolar
wind model in which the wind is originated from the star itself, and
(2)~the disc-wind model in which the wind originates from the inner
part of the accretion disc. We perform systematic investigations of
the model parameters for the wind and the magnetosphere to search
for possible geometrical and physical conditions which lead to the
types of the profiles seen in observations. We find both wind models
can reproduce the wide range profile types seen is observations. We
also find the inclination dependency of the line equivalent width
predicted by the bipolar wind model agree with trends seen in the
observation, but the disc-wind model does not. Using the model results,
we examine the H$\alpha$ spectroscopic classification used by Reipurth
et.~al , and discuss the basic physical conditions required to reproduce
the profiles in each classified type. Using the hybrid model, we fit
the observed H$\alpha$ from the optical component of T~Tau triple
system (T~Tau~N), and find its ratio of the mass-loss to mass-accretion
rate to be $\sim0.18$ with the cold ($T_{\mathrm{wind}}\approx8000\,\mathrm{K}$)
bipolar wind model .

\end{abstract}

\begin{keywords}
stars: formation -- circumstellar matter -- radiative transfer -- stars: pre-main-sequence
\end{keywords}

\section{Introduction }

\label{sec:Introduction}

T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
H$\alpha$ emission, and typically have spectral types of F--K. Some
of the most active CTTS show emission in higher Balmer lines and metal
lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit an excess
amount of continuum flux in the ultraviolet (UV) and infrared (IR).
Their spectral energy distribution and polarisation data suggest the
presence of a circumstellar disc, and it plays an important role in
regulating dynamics of gas flows around CTTS.

Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
\citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
of CTTS line profiles show evidences for both outward wind flows and
inward accretion flows, as seen in the blue-shifted absorption features
in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC) profiles
respectively. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
\citealt{edwards:1987}; \citealt{hartigan:1995}), and the mass-accretion
rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
(e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
show the direct evidence for the presence of bipolar and monopolar
outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
and HV~Tau~C) by \citet{appenzeller:2005} show the extended H$\alpha$
emission in the direction perpendicular to the obscuring circumstellar
disc, and in both above and below the disc --- suggesting the presence
of the bipolar outflows. In slightly larger scale, \emph{HST} observation
of HH30 \citet{burrows:1996} shows the jet traced to within $\lesssim30$~AU
from the star. The jet has a cone shape with an opening angle of $3^{\circ}$
between 70 and 700 AU \citep{koenigl:2000}. \citet{alencar:2000}
found about 80 per cent of their samples (30 CTTS) show blue-shifted
absorption components in at least one of Balmer lines and Ca~K (most
commonly in H$\alpha$).

In a currently favoured model of accretion flows around CTTS, the
accretion discs are disrupted by the magnetosphere of stars which
channels the gas from the disc onto the surface of the stars (e.g.,
\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993};
\citealt{shu:1994}). This picture of the accretion flows is supported
by the evidences that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$)
magnetic field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
and by the radiative transfer models which reproduce the observed
profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
accretion model naturally explains the blue-ward asymmetric emission
lines (seen in some of CTTS) caused by the partial occultation of
the flow by the disc, and the redshifted absorption component at the
typical free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$)
seen in some of CTTS. Despite the success of the magnetospherical
accretion model in explaining the line profiles in some CTTS, the
overwhelming observational evidences for the outflow (mentioned above)
in the CTTS profiles suggests that this model is only a part of a
whole picture. Clearly, the modification to include the out-flowing
wind/jet flow is necessary if one requires to predict the mass-accretion
rate and the mass-loss rate of CTTS by modelling their emission profiles
(e.g. H$\alpha$).

Priory to the magnetospherical models, many alternative models had
been considered to explain the observed spectroscopic features mentioned
earlier. For example, (1)~the Alfv\'{e}n wave-driven wind model
(e.g.~\citealt{decampli:1981}; \citealt{hartmann:1982}), (2)~turbulent
boundary layer (between the accretion disc and stellar surface) model
(e.g.~\citealt{bertout:1988}; \citealt{basri:1989}), (3)~chromospheric
model (e.g.~\citealt{calvet:1984}), and (4)~disc wind model (e.g.
\citealt{calvet:1992b}; \citealt{kwan:1995}). Considering the success
of the magnetospherical accretion flow model in some cases and the
observational evidences for the outflows, it is likely that an improved
spectroscopic model requires both inflow and outflow components. The
combination of the magnetospheric accretion flow model with model
1 or 4 would be a reasonable starting point. Although time consuming
to explore a larger parameter space, more realistic density, velocity
and temperature structure from magnetohydrodynamic wind+accretion
models should be considered as inputs for an radiative transfer model
in the future. Recent work by \citet{alencar:2005} showed the observed
H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better produced
by the radiative transfer model which include the collimated disc-wind
arising from near the inner edge of the accretion disc. \citet{malbet:2005}
considered the combination of a spherical wind and the accretion disc
in their radiative transfer model to reproduce Br$\gamma$ from the
early-type Herbig Be star MWC~297.

The magneto-centrifugal wind model, first proposed by \citet{blandford:1982},
has been often used to reproduce the large-scale wind structure of
T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
by \citealt{burrows:1996}; \citealt{ray:1996}). The launching of
the wind from a Keplerian disc is typically done by treating the equatorial
plane of the disc as a mass-injecting boundary condition (e.g., \citealt{shu:1994};
\citealt{ustyugova:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
Depending on the location of the open magnetic fields anchored to
the disc, two different types of winds are produced. If the field
is constrained to be near the co-rotation radius of stellar magnetosphere,
an {}``X-wind'' \citep{shu:1994} is produces. If the open field
lines are located in a wider area of the disc, a {}``disc-wind''
similar to \citet{koenigl:2000} is produced \citet{krasnopolsky:2003}.
Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
and \citet{pudritz:2005}. Interestingly, \citet{matt:2005} showed
the possibility that the stellar wind along the open magnetic field
originating from the star can cause significant spin-down torque on
the star, provided that mass-loss rate is high enough.

The main aim of this paper is to find a simple kinematic model which
can reproduce the wide variety of the observed profiles, and to perform
the empirical studies of the line formation. More specifically, we
present disc--wind--magnetosphere hybrid models for CTTS, and perform
parametric studies of the H$\alpha$ formation. This study should
provide preliminary physical conditions which lead to the wide variety
of emission line profiles seen in the observation, and would help
to construct more comprehensive circumstellar models (e.g. via MHD
simulations) of T~Tauri stars. the Using the model results, we examine
the H$\alpha$ spectroscopic classification used by \citet{reipurth:1996},
and compare models with observations. We will also discuss whether
our model is consistent with some predictions made by the recent MHD
studies i.e.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
(e.g.~\citealt{koenigl:2000}).

In section~\ref{sec:model-configuration}, the model assumptions,
and the basic model configurations are presented. We discuss the radiative
transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
and the results of model calculations are given in section~\ref{sec:Results}.
The closer examination and discussion of the results are presented
in section~\ref{sec:Discussion}. Finally, the summary of this work
and the conclusion are in section~\ref{sec:Conclusions}.

\section{Model configuration}

\label{sec:model-configuration}

To understand how the different part of the CTTS circumstellar environment
contributes to the formation of H$\alpha$, the model spaced is divided
into four different regions: 1.~Central continuum source, 2.~magnetosphere
accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:config_dipolar}
depicts the relative location in the model space. In all regions,
the density is symmetric around the z-axis. The innermost radius of
the magnetosphere at the equatorial plane coincides with the the inner
radius of the accretion disc. From the inner most part of the accretion
disc, the gas freely fall, moving along the magnetic filed onto the
surface of the star. For the purpose of computational simplicity,
the collimated bipolar wind are defined only in the outside of the
largest radius of the magnetosphere (to avoid overlapping of the wind
with the magnetosphere). In the following subsections, the details
of model components will be described. In our models, two different
types of the wind configurations are considered: (1)~the bipolar
wind resembling the density structure of the MHD simulation by \citealt{krasnopolsky:2003}
in large scale ($\sim100$~AU) in section~\ref{sub:wind_jet}, and
(2) that in small scale ($\sim10$~AU) in section~\ref{sub:Alternative-model-disc-wind}.

\begin{figure*}

\begin{center}

\includegraphics[%
  scale=0.5]{figures/overview3.eps}

\end{center}

\caption{Basic Model Configuration. The system consist of four components: (1)~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, (2)~magnetospherical accretion flow, (3)~bipolar wind outflow, and (4)~accretion disc. The density distribution is symmetric around the z-axis. The innermost raius of the magnetsphere (at the equotrial plane) coincides with the the inner radius of the accretion disc. From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star. For a computational simplicity, the bipolar wind starts from just outside of the largest radius ($R_{\mathrm{mo}}$) of the magnesophere (dotted line). }

\label{fig:config_dipolar}

\end{figure*}

\subsection{Continuum Source}

\label{sub:Continuum-Source}

Unless specified otherwise, we adopt stellar parameters of a typical
classical T~Tauri star for the central continuum source, i.e. radius
($R_{*}$), mass ($M_{*}$), and effective temperature the photosphere
($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$, and $4000\,\mathrm{K}$
respectively. The model atmosphere of \citet{kurucz:1979} equivalently
\citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$ and
$\log g_{*}=3.5$ (cgs) is used to find the photospheric continuum
at H$\alpha$ wavelength. The parameters are summarised in Table~\ref{tab:std_parameters}.

For a model which includes magnetospherical accretion, an additional
source of the continuum source is considered. As the in-falling gas
becomes closer to the stellar surface, it is decelerates in a strong
shock, and heated to $\sim10^{6}\,\mathrm{K}$ (with typical parameters).
The X-ray radiation produced in the shock will be absorbed by the
gas located near, and re-emitted in optical and UV radiation (\citealt{koenigl:1991};
\citealt{hartmann:1994}). This will create hot rings near the stellar
surface where the magnetic field intersects with the surface. For
simplicity, the free-falling kinetic energy is assumed to be thermalized
in the radiating layer, and re-emits as blackbody radiation (with
a single temperature). With the parameters of the magnetosphere and
the star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
of the surface is covered by the hot rings, and its temperature is
about $6400\,\mathrm{K}$. If the mass-accretion rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$,
the ratio of this accretion luminosity to the photospheric luminosity
is about $0.5$. The continuum emission from the hot rings is taken
into account when computing the line profiles.

\begin{table*}

\begin{center}

\begin{tabular}{lccccccccccc}
\hline 
Parameters&
$R_{*}$&
$M_{*}$&
$T_{\mathrm{ph}}$&
$R_{\mathrm{mi}}$&
$R_{\mathrm{mo}}$&
$\dot{M}_{\mathrm{acc}}$&
$\dot{M}_{\mathrm{wind}}$&
$v_{\infty}$&
$b$&
$R_{\mathrm{di}}$&
$R_{\mathrm{do}}$\tabularnewline
&
$\left[R_{\sun}\right]$&
$\left[M_{\sun}\right]$&
$\left[\mathrm{K}\right]$&
$\left[R_{*}\right]$&
$\left[R_{*}\right]$&
$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
$[\mathrm{km\, s^{-1}}]$&
$[-]$&
$\left[R_{*}\right]$&
$\left[\mathrm{AU}\right]$\tabularnewline
\hline
Standard&
$2.0$&
$0.5$&
$4000$&
$2.2$&
$3.0$&
$10^{-7}$&
$10^{-8}$&
$210$&
$4.0$&
$2.2$&
$100$\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary of the standard classical T~Tauri star model parameters.}

\label{tab:std_parameters}

\end{table*}

\subsection{Magnetosphere}

\label{sub:Magnetosphere}

We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
as done so by \citet{muzerolle:2001} and by \citet{symington:2005},
in which the gas accretion on to the stellar surface from the innermost
part of the accretion disc occurs through a dipolar stellar magnetic
field. The magnetic field is assumed to be so strong that the gas
flow does not affect the underlying magnetic field itself. As shown
in Fig.~\ref{fig:config_dipolar}, the innermost radius ($R_{\mathrm{mi}}$)
of the magnetosphere at the equatorial plane ($z=0$) is assigned
to be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
the equatorial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
respectively. The former value corresponds to the co-rotation radius
of the accretion disc, and the geometry of the magnetic field/stream
lines is kept constant throughout this paper. The geometry of the
magnetosphere is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.

The magnetic field and the gas stream lines are assumed to have the
following simple form: \begin{equation}
r=R_{\mathrm{m}}\sin^{2}\theta\label{eq:dipole}\end{equation}
 \citep[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
of the field point ($p$) in Fig.~\ref{fig:config_dipolar} in spherical
coordinates, and $R_{\mathrm{m}}$is the radial distance to the field
line at the equatorial plane ($\theta=\pi/2$). The range of $R_{\mathrm{m}}$is
restricted between $R_{\mathrm{mi}}$ and $R_{\mathrm{mo}}$. Using
the field geometry above and the conservation of energy, the velocity
and the density of the accreting gas along the steam line are found
as in \citet{hartmann:1994}.

The temperature structure of the magnetospheric used by \citet{hartmann:1994}
is simply adopted here. They computed the temperature assuming a volumetric
heating rate which is proportional to $r^{-3}$, and using the energy
balance of the radiative cooling rate of \citet{hartmann:1982} and
the heating rate \citep{hartmann:1994}. Although the temperature
structure of the accretion steam could significantly affect the line
source function, for the purpose of the exploring the general characteristics
of the H$\alpha$ formation, this simple form is a reasonable assumption.
\citet{martin:1996} presented the self-consistent determination of
the thermal structure of the in-flowing gas along the dipole magnetic
field (equation~\ref{eq:dipole}) by solving the heat equation couple
to rate equations for hydrogen. He found that main heat source is
adiabatic compression due to the converging nature of the flow, and
the major contributors of the cooling process are bremsstrahlung radiation
and line emission from Ca~II and Mg~II ions. The results of \citet{martin:1996}
qualitatively agrees with that of \citet{hartmann:1994}.

\subsection{Bipolar Wind}

\label{sub:wind_jet}

As mentioned earlier, the wind model presented here is to simulate
the collimated MHD disc-wind model of \citet{krasnopolsky:2003} in
large scale ($\sim100$~AU) , and the alternative wind model which
resembles the model of \citet{krasnopolsky:2003} in small scale ($\sim10$~AU)
will be presented later (section~\ref{sub:Alternative-model-disc-wind}).

Similar to the simple wind model of \citet{appenzeller:2005}, the
following parametrisation of collimated bipolar wind (region 3 in
Fig.~\ref{fig:config_dipolar}) is adopted. The wind velocity field,
$\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$, is consist of
radial and azimuthal components which depend on the spherical coordinates
$r$ and $\theta$. The radial component $v_{r}\left(r\right)$ is
assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
and the azimuthal component $v_{\phi}$ is assumed to be a constant
fraction ($\gamma$) of the Keplerian velocity for a given distance
($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:

\begin{eqnarray}
\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}\label{eq:wind_velocity_def}\end{eqnarray}
where \begin{equation}
v_{r}\left(r\right)=v_{r0}+\left(v_{\infty}-v_{r0}\right)\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
\begin{equation}
v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This
is chosen so mainly for computational simplicity i.e. to avoid the
overlap between the wind and the magnetosphere; however, see \citet{matt:2005}
for the possibility that wind originates from the stellar surface
(restricted near the polar caps). The range of the polar angle for
the wind is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
where $\theta_{\mathrm{disc}}$ is the opening angle of the accretion
disc, to avoid the overlap. $v_{r0}$is the small radial velocity
at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
which is approximately equal to the thermal velocity of hydrogen with
$T=7500\,\mathrm{K}$. Following \citet{appenzeller:2005}, $\gamma=0.05$
is adopted. The dependency of $v_{r}$ in polar direction ($\theta=0$)
on the values of wind acceleration parameter $\beta$ is shown in
Figure~\ref{fig:wind_vr_rho}. All other parameters describing the
wind are fixed as the standard values given in Table~\ref{tab:std_parameters}.

Further, the density of the wind is assumed to be axi-symmetric and
separable in $r$ and $\theta$ for computational simplicity, i.e.,

\begin{equation}
\rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)\label{eq:wind_density_def}\end{equation}
 with \begin{equation}
F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
 where $b$ is normally positive even number (for the density symmetric
about the equatorial plane), and $n$ is the angular normalisation
constant. For $b=0$, the wind is spherically symmetric except for
the parts disrupted by the accretion disc. The larger the value of
$b$, the higher the degree of the collimation. By integrating equation~\ref{eq:wind_density_theta}
over angles and normalising the integral to $4\pi$, one finds \begin{equation}
n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
 Assuming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
and the mass-flux conserves in time, the radial part of the density
function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
\rho\left(r,\theta\right)=\frac{n\,\dot{M}_{\mathrm{wind}}\,\cos^{b}\theta}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
 For a given mass-accretion rate, the wind mass-loss rate in our typical
model is assigned from the ratio of mass-loss to mass-accretion rate
($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
by both observations and MHD calculations (e.g. \citealt{koenigl:2000}).
Figure~\ref{fig:wind_vr_rho} shows the density along a streamline
in the polar direction ($\theta=0$), for different values of $\beta$
with all other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
The density is relatively sensitive to the value of $\beta$ for $r<10\, R_{\mathrm{mo}}$,
but a little difference is seen beyond $r<100\, R_{\mathrm{mo}}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{cc}
\includegraphics[%
  clip,
  scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
\includegraphics[%
  clip,
  scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{The dependency of the bipolar wind velocity and density structures on the wind accerelation parameter $\beta$. The radial component of the wind  velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left. The wind density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is shown on right. For all $\beta$ values, the density is normalized to the desnity at the base of the wind in polar direction, i.e. $\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.  The smaller the value of $\beta$, the faster the accerelation of the wind. For the raidus ($r/R_{\mathrm{mo}} < 10$, both velocity and density are sensitive to the value of $\beta$. For all $\beta$ values, the radial velocity of the wind reaches the terminal velocity ($\sim 210\,\kmps$ by  $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity $V_{0}=10\,\kmps$, which approximately corresponds to the thermal velocity of a hydrogen atom at 7500~K,  is used for all $v_{r}$ plots. Beyound $r/R_{\mathrm{mo}}= 100$, little difference is seen in the polar density with diffrent $\beta$ values.}

\label{fig:wind_vr_rho}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Accretion disc}

\label{sub:Accretion-disc}

Although it is possible, in our model, to compute the dust-sublimation
radius and the vertical hydrostatic structure of the accretion disc
self-consistently (assuming the radial dependency of the mid-plane
density) by using the iterative Monte Carlo radiative transfer technique
(c.f.~\citet{walker:2004}), we find it to be too time consuming
for the purpose of this paper -- understanding the general characteristic
of H$\alpha$ profile shapes hence exploring a large parameter space.
For this reason, we adopt a simple analytical disc model, the steady
$\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
with the inner radius fixed at the inner radius of the magnetosphere
at equatorial plane. This corresponds to Region 4 in Fig.~\ref{fig:config_dipolar}.

\subsubsection{Density and velocity}

The disc density distribution is given by

\begin{equation}
\rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
 where $w$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
axis, the scale height, the distance from the disc plane, and the
surface density at the mid-plane, respectively. The mid-plane surface
density and the scale height are given as: \begin{equation}
\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
 where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
and the disc mass respectively.\begin{equation}
h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.\label{eq:scale-height}\end{equation}
 With these parameters, the disc is slightly flared. The inner radius
of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
radius of the magnetosphere at the equatorial plane), which is approximately
same as the co-rotating radius of the system with the parameters in
Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
of an object is assumed to be 1/100 of the central mass ($M_{*}$),
and the disc radius ($R_{\mathrm{di}}$) to be 100~au. The velocity
of the gas/dust in the disc is assumed to be Keplerian.

\subsubsection{Dust model}

To calculate the dust scattering and absorption cross section as a
function of wavelength, the optical constants of \citet{draine:1984}
for amorphous carbon grains and \citet{hanner:1988} for silicate
grains are used. The model uses the {}``large grain'' dust model
of \citet{wood:2002} in which the dust grain size distribution is
described by the following function:\begin{equation}
n\left(a\right)da=\left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\, a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da\label{eq:grain-dist-function}\end{equation}
 where $a$ is the grain size restricted between $a_{\mathrm{min}}$
and $a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$
are the terms set by requiring the grains to completely deplete a
solar abundance carbon and silicon. The parameters adopted in our
model are: $C_{\mathrm{C}}=1.32\times10^{-17}$, $C_{\mathrm{Si}}=1.05\times10^{-17}$,
$p=3.0$, $q=0.6$, $a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
$a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds
to Model~1 of the dust model used by \citet{wood:2002}. See also
their Fig.~3 The relative number of each grain is assumed to be that
of solar abundance, C/H$\sim3.5\times10^{-4}$ \citep{anders:1989}
and Si/H$\sim3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.

\subsection{Alternative model: disc-wind model of \citet{knigge:1995}}

\label{sub:Alternative-model-disc-wind}

\begin{figure}

\begin{center}

\includegraphics[%
  scale=0.32]{figures/discwind.eps}

\end{center}

\caption{Basic Model Configuration of the disc-wind, magnetosphere hybrid model. The system consist of four components: (1)~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, (2)~magnetospherical accretion flow, (3)~colliminated wind/jet outflow, and (4)~geometrically thin (but opaque) accretion disc. The disc wind originates from the disc surface between $w_{i}=R_{wi}$ and $w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream lines diverges, are placed at distance $d$ above and below the star. By changing the value of $d$,  the degree of the wind collimation is controlled. The density distribution is symmetric around the z-axis. }

\label{fig:config_discwind}

\end{figure}

The wind model presented here is to simulate the collimated MHD disc-wind
calculations of \citealt{krasnopolsky:2003} in small scale ($\sim10$~AU).
\citet{knigge:1995} introduced the {}``split-monopole'' kinematic
disc-wind model in their studies of the UV resonance lines formed
in the winds of cataclysmic variable stars. In this model, the outflow
arises from the surface of the rotating accretion disc, and has a
biconical geometry. The specific angular momentum is assumed to be
conserved along a stream line, and the poloidal velocity component
is assumed to be simply a radial from vertically displaced {}``sources''
from the central star. We adopt their disc-wind model here, and consider
the combined effect of the disc-wind and the magnetospherical accretion
flow model described earlier. In the following, we briefly described
their disc-wind model. For details of the models, readers are referred
to \citet{knigge:1995} and \citet{long:2002}.

Four basic parameters for the models are: 1. mass-loss rate, 2.~the
degree of the wind collimation, 3.~velocity gradients, and 4.~the
wind temperature. The basic configuration of the disc-wind model is
shown in Figure~\ref{fig:config_discwind}. The disc wind originates
from the disc surface, but the {}``source'' point ($S$), from which
the stream lines diverges, are placed at distance $d$ above and below
the centre of the star. By changing the value of $d$, the degree
of the wind collimation is controlled. The larger the value of $d$,
the wind becomes more parallel to the rotation axis, i.e. the wind
becomes more collimated. The mass-loss launching is restricted between
$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ where the former is set
to be equal to the outer radius of the magnetosphere ($R_{\mathrm{mo}}$)
for simplicity and the latter is set to $1$~AU as in \citealt{krasnopolsky:2003}.

The local mass-loss rate per unit area ($\dot{m}$) is assumed to
be proportional to the mid-plane temperature of the disc, and is a
function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
, i.e. \begin{equation}
\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
 Further, the mid-plane temperature of the disc is assumed to be expressed
as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
relation above, one finds \begin{equation}
\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
where $p=\alpha\times q$. The index of the mid-plane temperature
power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
who found the inner most part of the accretion disc has $q=-1.15$.
To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
of proportionality in equation~\ref{eq:discwind-massloss-w} is found
by integrating $\dot{m}$ from $R_{\mathrm{wi}}$to $R_{\mathrm{wo}}$,
and the normalising the total mass-loss rate to $\dot{M}_{\mathrm{dw}}$.

The azimuthal/rotational component of the wind velocity $v_{\phi}\left(w,z\right)$
is computed from the Keplerian rotational velocity at the emerging
point of the stream line i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
where $w_{i}$ is the distance from the rotational axis ($z$) to
the emerging point on the disc, and by assuming the conservation of
the specific angular momentum along a stream line: \begin{equation}
v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt{castor:1975}),
the poloidal component of the wind velocity ($v_{p}$) parameterised
as:

\begin{equation}
v_{p}\left(w_{i},l\right)=c_{\mathrm{s}}\left(w_{i}\right)+\left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}\label{eq:discwind-poloidal-velocity}\end{equation}
where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the
wind launching point on the disc, the constant scale factor of the
asymptotic terminal velocity to the local escape velocity (from the
wind emerging point on the disc), and the distance from the disc surface
along stream lines respectively. $R_{s}$ is the wind scale length,
and $R_{s}=10\, R_{\mathrm{mi}}$ is adopted as similarly done by
\citet{long:2002}.

Assuming the mass-flux conservation and using the velocity field defined
above, the disc wind density as a function of $w$ and $l$ can be
written as

\begin{equation}
\rho\left(w_{i},l\right)=\frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}\label{eq:discwind-density}\end{equation}
where $Q$ and $\delta$ are the distance from the source point ($S$)
to a point along the stream line and the angle between the stream
line and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
shows the density and the velocity components along the mid stream
line (passing through $w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$
on the disc plane ($z=0$) for different values of the wind acceleration
parameter $\beta$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{cc}
\includegraphics[%
  clip,
  scale=0.45]{plots/dw_vp_vphi.eps}~~~~~~&
\includegraphics[%
  clip,
  scale=0.45]{plots/dw_rho.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{Depdendency of the disc wind density and the velocity on the wind accelreation parameter $\beta$. The wind density $\rho$ (left panel) and the poloidal velocity component $V_{p}$ (right panel) along the stream line starting from the mid point of the wind lanching zone, i.e. $\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$  where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}} \right ) / 2$,  are shown as a function of the distance ($l$) from the wind lanching point (c.f.~ equations~\ref{eq:discwind-poloidal-velocity} and \ref{eq:discwind-density}). The azimuthal velocity component ($V_{\theta}$), which is independent of  $\beta$ (c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in the right panel for a comparison. The density is normalized to the density $\rho_{0}$ at the wind lanching point for $\beta = 1.0$ case.  The $v_{p}$ reaches the terminal velocity by 100~AU for all $beta$. In the fur field ($l>10$~AU), the density is approximately proportional to $\sim l^2$. Up to $l~\sim10$~AU, the density is smaller and the poloidal speed is larger for the wind with a larger $\beta$ value. }

\label{fig:discwind_vr_rho}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Radiative transfer model}

\label{sec:radiative-transfer-model}

We have extended the TORUS radiative transfer code (\citealt{harries:2000};
\citealt{kurosawa:2004a}; \citealt{symington:2005}) to compute the
H$\alpha$ profiles from pre-main-sequence stars which are surrounded
by one or more of the followings: the magnetospherical accretion flow,
the out-flowing collimated wind, and the accretion disc. Previously
in \citet{symington:2005}, the model used in the three-dimensional
(3-D) adaptive mesh refinement (AMR) to investigate the line variability
mainly associated with rotational motion of complex geometrical configurations
of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
modified the code to handle the two-dimensional (2-D) density distribution,
and restricted our models to be axi-symmetric. It was done so in order
to enable us to explore rather large number of parameter spaces (c.f.~section~\ref{sec:model-configuration}).
Note that the velocity field is still in 3-D -- the third component
can be calculated by using the symmetry for a given value of azimuthal
angle. The examples of how the AMR grid for the purpose of the radiative
transfer is constructed are presented in e.g. \citet{wolf:1999},
\citet{kurosawa:2001a} and \citet{steinacker:2003} .

The computation of the H$\alpha$ is divided in two parts: (1)~the
source function calculation ($S_{\nu}$) and (2)~the observed flux/profile
calculation. In the first process, we have utilised the method by
\citet{klein:1978} (see also \citealt{rybicki:1978}; \citet{hartmann:1994})
in which the Sobolev approximation method is applied. The population
of the bound states of hydrogen are assumed to be in statistical equilibrium,
and the gas to be in radiative equilibrium. Our hydrogen atom model
consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
for details.

To compute the observed line profile, the Monte Carlo radiative transfer
method (e.g. \citealt{hillier:1991}) using the Sobolev escape-probability
can be used when (1)~a large velocity gradient is present in the
gas flow, and (2)~the intrinsic line width is negligible compared
to the Doppler broadening of the line. In our earlier models (\citealt{harries:2000};
\citealt{symington:2005}), this method was used to compute the line
profiles since the condition (1) and (2) are reasonably satisfied.
However, as noted and demonstrated by \citet{muzerolle:2001}, even
with a moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
Stark broadening becomes important in the optically thick H$\alpha$
line. \citet{muzerolle:2001} also pointed out that the observed H$\alpha$
profiles from CTTS typically have the wings extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
\citet{reipurth:1996}) which cannot be explained by the infall velocity
of the gas along the magnetosphere alone.

To implement the broadening mechanism, two modifications to our previous
model (\citealt{symington:2005}) are necessary as similarly done
by \citet{muzerolle:2001}. First, the emission and absorption profiles
must be replaced by a Voigt profile which is defined as: \begin{equation}
H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
 where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$, $y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$,
and $y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$ (c.f. \citealt{mihalas:1978}).
$\nu_{0}$ is the line centre frequency, and $\Delta\nu_{\mathrm{D}}$
is the Doppler line width of hydrogen atom (due to its thermal motion)
which is given by $\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
where $m_{\mathrm{H}}$ is the mass of a hydrogen atom. The damping
constant $\Gamma$, which depends on the physical condition of the
gas, is parameterised by \citet*{vernazza:1973} as follows:

\begin{eqnarray}
\Gamma & = & C_{\mathrm{rad}}+C_{\mathrm{vdW}}\left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)\left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
 &  & +\, C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}\label{eq:dampimg_constant_def}\end{eqnarray}
 where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
neutral hydrogens and that of free electrons. Also, $C_{\mathrm{rad}}$,
$C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are natural broadening,
van der Waals broadening, and linear Stark broadening constants respectively.
We simply adopt this parameterisation along with the values of broadening
constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and $C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.
In terms of level populations and the Voigt profile, the line opacity
for the transition $i\rightarrow j$ can be written as: \begin{equation}
\chi_{l}=\frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}\left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)\label{eq:line_opacity}\end{equation}
 where $f_{ij}$, $n_{i}$, $n_{j}$, $g_{i}$and $g_{j}$ are the
oscillator strength, the population of $i$-th level, the population
of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
of the $j$-th level respectively. $m_{e}$ and $e$ are the electron
mass and charge (c.f. \citealt{mihalas:1978}).

The second modification in our model is the replacement of the method
of solving the formal solution from the Monte Carlo radiative transfer
method with Sobolev approximation to the direct integration method
(c.f. \citealt{muzerolle:2001}). We specify the cylindrical coordinates
$\left(p,\, q,\, t\right)$ which is the original stellar coordinate
system $\left(\rho,\,\phi,\, z\right)$ rotated (around $y$ axis)
by the inclination of the line of sight, i.e. the $t$-axis coincides
with the line of sight. The observed flux ($F_{\nu}$) is given by:
\begin{equation}
F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
where $d$, $p_{\mathrm{max}}$, and $I_{\nu}$ are the distance to
an observer, the maximum extent to the model space in the projected
(rotated) plane, and the specific intensity ($I_{\nu}$) in the direction
on observer at the outer boundary. For a given ray along $t$, the
specific intensity is given by:\begin{equation}
I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{t_{0}}^{t_{\infty}}S_{\nu}\left(t\right)\, e^{-\tau}\mathrm{d}\tau\label{eq:formal_sol_integral}\end{equation}
 where $I_{0}$ and $S_{\nu}$ are the intensity at the boundary on
the opposite to the observer and the source function ($\eta_{\nu}/\chi_{\nu}$)
of the stellar atmosphere/wind at a frequency $\nu$. For a ray which
intersects with the stellar core, $I_{0}$ is computed from the stellar
atmosphere mode of \citet{kurucz:1979} as described in section~\ref{sub:Continuum-Source},
and $I_{0}=0$ otherwise. The initial position of each ray is assigned
to be at the centre of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
The code execution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
where $n_{p}$ and $n_{q}$ are the number of cylindrical radial and
angular points for the flux integration, and $n_{\nu}$is the number
of frequency points. In the models presented in the next (section~\ref{sec:Results}),
$n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
otherwise. The linearly spaced radial grid is used for the area where
the ray intersects with magnetosphere, and the logarithmically spaced
grid is used for the wind and the accretion disc regions.

The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
is defined as: \[
\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
 where $\chi_{\nu}$ is the opacity of media the ray passes through.
$\tau_{\infty}$ is the total optical depth measured from the initial
ray point to the observer (or to the outer boundary closer to the
observer). Initially, the optical depth segments $\mathrm{d\tau}$
are computed at the intersections of a ray with the original AMR grid
in which the opacity and emissivity information are stored. For high
optical depth models, additional points are inserted between the original
points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$ values are
interpolated to those points to ensure $\mathrm{d}\tau<0.05$ for
the all ray segments.

For a point in the magnetosphere and the wind flows, the emissivity
and the opacity of the media are given as:\begin{equation}
\left\{ \begin{array}{rcl}
\eta_{\nu} & = & \eta_{\mathrm{c}}^{\mathrm{H}}+\eta_{l}^{\mathrm{H}}\\
\chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}+\sigma_{\mathrm{es}}\end{array}\right.\label{eq:emiss_opa_gas}\end{equation}
where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$
are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the continuum,
line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
electron scattering opacity. Similarly, for a point in the accretion
disc,

\begin{equation}
\left\{ \begin{array}{rcl}
\eta_{\nu} & = & 0\\
\chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}+\kappa_{\mathrm{sca}}^{\mathrm{dust}}\end{array}\right.\label{eq:emiss_opa_dust}\end{equation}
 where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and $\kappa_{\mathrm{sca}}^{\mathrm{dust}}$
are the dust absorption, and scattering opacity which are calculated
using the dust property described in section~\ref{eq:grain-dist-function}.
For computational simplicity, we assumed that the dust emissivity
is zero. Since the disc mass of CTTS are rather small ($\sim0.1\,\mathrm{M_{\sun}}$)
and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
contribution at H$\alpha$ wavelength is expected to be negligible
(e.g.~\citealt{chiang:1997}).

\section{Results}

\label{sec:Results}

\subsection{Magnetosphere}

\label{sub:model-acc}

Using the standard parameters (Table~\ref{tab:std_parameters}) for
the central star and the magnetosphere, we examine the dependency
of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
is computed from the available kinetic energy of the free-falling
gas as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
of their models. The accretion luminosity ($L_{\mathrm{acc}}$) of
models with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
is about a half of the total luminosity (without the hot ring) of
the star, and $L_{\mathrm{acc}}$is proportional to $\dot{M}_{\mathrm{acc}}$.
The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are
similar to that of \citet{muzerolle:2001}. In general, the line strength
becomes weaker as the accretion rate and the temperature become smaller.
The red-shifted absorption becomes less visible for higher accretion
rate and temperature models in which the flux in the damping wings
become important. Figure~\ref{fig:broadening} shows an example of
the effect of the broadening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
due to the damping constants as described in section~\ref{sec:radiative-transfer-model}.
Although the maximum flux of the model with the broadening is almost
identical to that of the model with no damping constant ($\Gamma=0$),
a significant increase of the line flux in both red and blue wings
of seen in the model with broadening. A weak red-shifted absorption
component (which is a signature of the magnetospherical accretion)
is weakened or eliminated by the flux in broadened wing.

Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown
in Figure~\ref{fig:atlas_acc_models}. About a half of the models
shown the figure agree with the observed EW values of H$\alpha$ from
30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
ranges from $\sim3$~\AA\, to $\sim160$~\AA, and the mean to
be $\sim55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
and for some models the EWs are negative. Since the target selection
criteria of \citet{alencar:2000} is not stated in their paper, we
can not conclude that these low $\dot{M}_{\mathrm{acc}}$models disagree
with the observation. \citet{reipurth:1996}, who measured the EW
of 43 TTS and found similar distribution of EW values, mentioned that
their EW measurements are under-representing real samples since the
selection of the targets are based on the strong H$\alpha$ emission
in H$\alpha$ surveys.

The dependency of the profile on the inclination angle ($i$) is demonstrated
in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
parameters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
The figure show that the peak (normalised) flux decrease as the inclination
angle increases. Similarly, the equivalent width also decreases as
the inclination increases. Because of the geometry of the magnetospherical
accretion (c.f. Figure~\ref{fig:config_dipolar}) and of the presence
of the gas with the highest velocity close to the stellar surface,
the highest red-shifted line-of-sight velocity is visible only at
the high inclination angles. This explains the wider appearance of
the profile with $i=80^{\circ}$compared to the relatively narrow
line appearance of the profile with $i=10^{\circ}$. Although not
show here, a similar dependency on the inclination angle is found
for the models with different temperatures ($T_{\mathrm{max}}=6500$,
$8500$, $9500\,\mathrm{K}$).

As seen in the models of \citet{hartmann:1994} and \citet{muzerolle:2001},
our models also show the blue-shifted peak and the blue-ward asymmetry
caused by the occultation of the accretion flow by the equatorial
disc and the stellar disc. On the hand, \citealt{alencar:2000} (see
their Fig.~9) found a substantial fraction of the observed H$\alpha$
profiles also shows the {}``red-shifted'' peak, and the P~Cygni
profiles which can not be explained by the magnetospherical accretion
model alone. In addition, a recent study by \citet{appenzeller:2005}
showed that the equivalent width of H$\alpha$ from CTTS increases
as the inclination angle increases. Our model with the magnetospherical
accretion flow clearly disagrees with their finding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}

\end{center}

\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M}_\mathrm{acc}$) and temperature ($T_{\mathrm{max}}$). The profiles are computed using only magnetospherical accretion flow (i.e. no wind/jet).  All the profiles are computed using the parameters of the 'standard' model (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the mass accretion rate (indicated by the values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from left to right. The profiles are similar to those of \citet{muzerolle:2001}, available on-line (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html). }

\label{fig:atlas_acc_models}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}

\begin{center}

\begin{tabular}{cccc}
\hline 
$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
&
$\dot{M}_{\mathrm{acc}}$ ~$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
\tabularnewline
&
$10^{-7}$&
$10^{-8}$&
$10^{-9}$\tabularnewline
\hline 
$6500$&
$17.9$&
$0.1$&
$0.0$\tabularnewline
$7500$&
$25.2$&
$-0.9$&
$-0.5$\tabularnewline
$8500$&
$68.3$&
$6.5$&
$-0.7$\tabularnewline
$9500$&
$98.6$&
$52.4$&
$1.3$\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary of H$\alpha$ equivalent widths from the magnetospherical accretion flow models show in Figure~\ref{fig:atlas_acc_models}.}

\label{tab:ha_ew_acc_models}

\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/broadening.eps}

\end{center}

\caption{Effect of the line broadening for H$\alpha$. The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the model with no damping, $\Gamma=0$ (dashed).  Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}. The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant. The broaded wings extend to $\sim \pm 800 \kmps$.  The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.  }

\label{fig:broadening}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/acc_inc_effect.eps}

\end{center}

\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).  The profiles are computed with the magneospherical accretion flow using the standard parameters given in Table~\ref{tab:std_parameters} and $T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$ respectively. As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.  Similar dependency is seen in the models with the wide ranges of $T_{\mathrm{max}}$ and $\beta$ (not shown here). }

\label{fig:acc_inclination_effect}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Bipolar Wind}

\label{sub:model-wind}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=0.9]{figures/atlas_ha_i55_wind_only_final.eps}

\end{center}

\caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$). The profiles are computed with only wind (no magnetospherical accretion flow or accretion disc). The 'standard' model (Table~\ref{tab:std_parameters}) are applied here. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively. The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the wind accerelation rate increases from left to right. The P~Cygni profile are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow accerelation) models.  The postion of the absorption the component moves toward the line centre as $\beta$ increases. The effect of line broadening becomes more prominant for higher $T_\mathrm{wind}$ and higher $\beta$ models.}

\label{fig:atlas_wind_model}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As mentioned in earlier, the magnetospherical accretion flow model
alone cannot explain some of the features seen in observations. As
an alternative model, we now examine formation of H$\alpha$ in a
simple bipolar wind as described in section \ref{sub:wind_jet}. The
basic wind model parameters introduced earlier are $\gamma$, $\beta$,
$v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
and $\dot{M}_{\mathrm{wind}}$. To minimise the number of parameters
to be explored, we initially adopt $\gamma=0.05$, $v_{\infty}=200\,\kmps$
\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
Further, the angular extent of the wind (the opening angle of the
wind) is assumed to be $\theta_{\mathrm{wind}}=80^{\circ}$. The degree
of collimation is initially chosen to be $b=4$, i.e. the ratio of
the density in polar direction to the density at the edge of the wind
closest to the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
for given radii. For simplicity, the wind temperature $T_{\mathrm{wind}}$
is assumed to be isothermal\@. Although the line is potentially sensitive
to the temperature structure of the wind, determination of a self-consistent
wind temperature is beyond the scope of this paper. Readers are refereed
to \citet{hartmann:1982} in which the wind temperature structure
is determined by balancing the radiative cooling rate (assuming optically
thin) with the MHD wave heating rate. With these parameters kept constant,
we examine the characteristics of H$\alpha$ profiles, as a function
of the wind acceleration parameter $\beta$ and the isothermal wind
temperature $T_{\mathrm{wind}}$. Dependency on the other parameters
will be discussed later in this section.

Figure~\ref{fig:atlas_wind_model} shows the profile computed at
a mid inclination angle $i=55^{\circ}$ for the range of the wind
temperature between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and
for the range of $\beta$ between $0.2$ and $2.0$. The P~Cygni
profile are prominent in the models with lower values of $T_{\mathrm{wind}}$
and $\beta$ (colder and faster acceleration wind). As the value of
$\beta$ increases, the position of the blue-shifted absorption component
moves toward the line centre. which can be seen clearly in the $T_{\mathrm{wind}}=7000\,\mathrm{K}$
models. While the velocity position of absorption component for the
fastest acceleration ($\beta=0.2$) is almost at the terminal velocity
($v_{\infty}\sim200\,\kmps$), that for the slowest wind acceleration
model ($\beta=4.0$) is located close the line centre ($\sim50\,\kmps$).
As one can see in Figure~\ref{fig:wind_vr_rho}, the column density
of the gas moving at $v_{\infty}$ increases as the wind acceleration
becomes larger since the gas moving at $v_{\infty}$ becomes closer
to the photosphere. At the location where the absorption occurs, the
gas is moving faster for the models with the faster wind acceleration
models; hence, the location of the absorption component is bluer as
$\beta$ becomes smaller (as the wind acceleration faster). The figure
also shows that the intensity of the emission component increases
as $\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
because the density near the photosphere increases (more material
near the photosphere) as the value of $\beta$ increases (Figure~\ref{fig:wind_vr_rho});
hence, the emissivity of increases. Unlike the magnetospherical accretion
only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
profiles are not seen here, nor the blue-ward asymmetry. Because of
the absorption component in P~Cygni profile, most of the profiles
show red-ward asymmetry except for the low temperature wind models
with high inclinations (not shown here).

The dependency of the profile on the wind anisotropy parameter $b$
is demonstrated in Figure~\ref{fig:effect_wind_b_param}. Three models
presented in the figure have the same mass-loss ($10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$),
and are computer at inclination angle $i=55^{\circ}$. The P~Cygni
profile feature becomes more prominent, and the line flux becomes
smaller as the wind becomes more isotropic (smaller $b$ value). For
a fixed mass-loss rate, the column density of along the line of a
sight to the observer at a medium inclination angle (e.g.~$i=55^{\circ}$)
increases as $b$ decreases (c.f.~equation~\ref{eq:wind_density_final});
hence, causing more absorption. Further more, the value of the highest
density in the wind becomes smaller for a smaller $b$ model. As the
wind becomes more isotropic, the high gas concentrated more in the
polar direction has to be spread in the wider angular angles. This
results in a smaller highest density region in the wind; hence the
smaller line emissivity. For the same reason, the emission in the
wings is weaker for the model smaller $b$ value. We also note that
the asymmetry around the line centre decreases as the wind becomes
more isotropic.

The effect of varying the wind mass-loss rate is shown in Figure~\ref{fig:effect_wind_mdot}.
The line is very sensitive to the mass-loss rate. With all other parameters
fixed constant, $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor
of the wind density (equation~\ref{eq:wind_density_final}). For
the formation of H$\alpha$, the recombination process and the subsequent
downward transition to $n=3$ level. Assuming the ionisation fraction
remains constant, the recombination rate is proportional to the square
of wind density. We have found the line flux of the models in the
figure is approximately proportional to the square of the mass-loss
rate. This very sensitive nature of H$\alpha$ would make the line
a good candidate for a mass-loss rate indicator; however, without
solving the ambiguity of the emission component from the magnetospherical
accretion flow and the wind, and without knowing the detailed temperature
structure of the wind, it could provide us a misleading a mass-loss
rate estimate of a T Tauri star.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/windonly_B_effect2.eps}

\end{center}

\caption{The effect of wind collimation. The line profiles computed with with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$ for  the wind anisotropy parameter $b=0, 2, 4$ are shown in dashed, dotted, and solid respectively.  All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.  The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind. The blue-ward asymmetry is still present even in the isotropic wind case ($b=0$).}

\label{fig:effect_wind_b_param}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/windonly_mdot_effect.eps}

\end{center}

\caption{The effect of the wind mass-loss rate.  The profiles computed with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$, and  $\dot{M}_{\mathrm{wind}} = 1.0 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (solid),  $0.5 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dotted), and $0.25 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed) are shown above. The models are computed with only the wind component (no magnetospherical accretion flow or  accretion disc). With all other parameter fixed constant, the mass-loss rate behaves as a scaling factor for the wind density (equation~\ref{eq:wind_density_final}.)}

\label{fig:effect_wind_mdot}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Disc $+$bipolar wind}

\label{sub:model-disc-wind}

Next, we examine the effect of the size of the inner radius of the
disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_alpha_disc}
shows the wind emission profiles computed with and without the accretion
disc at $i=55^{\circ}$. The H$\alpha$ images (projected on to the
plane perpendicular to the observer at the location of the star) are
also shown in the same figure. Both models use the same parameters
as in Figure~\ref{fig:atlas_wind_model}, but with $\beta=0.5$ and
$T_{\mathrm{wind}}=9000\,\mathrm{K}$). The model without the disc
can be also considered as a model with a large inner radius of the
accretion disc, in which none of the wind emission region is blocked
by the disc --- provided the inclination angle is not so high and
the disc is not or slightly flared.

The bipolar nature of the wind is clearly seen in the images. In this
example, the most of the wind emission occurs within a few to a several
(depending mainly on the value of $\beta$) stellar radii from the
star. The figure also shows that the accretion disc blocking the wind
emission from the bottom half of the wind which is moving away from
the observer. This results in the reduction of the wind emission in
the red wing. The image (mid panel) also shows that the accretion
disc is not occulting the stellar disc at this inclination; therefore,
the ratio of the wind emission flux to the photospherical continuum
flux becomes slightly smaller for the model with the disc. This results
in the reduction in the peak flux and the flux in the wings in the
normalised profile shape. If the disc becomes more flared (if the
opening angle exceeds $45^{\circ}$at the outer edge of the accretion
disc), the occultation of the stellar disc by the accretion could
be seen at this inclination angle. Although it is not shown here,
the continuum level of the two models are identical. For the models
with $i<30^{\circ}$, the presence of the disc has little/no effect
on the profile shapes. In the figures, the extent of the H$\alpha$
emission is smaller ($\sim0.2\,\mathrm{AU}$ or $\sim20\, R_{*}$)
compared to the spectro-astrometric observations of \citet{takami:2003}
for RU~Lup and CS Cha which show 1--5~AU scale outflows%
\footnote{\citet{takami:2003} their observation also show that some objects
(e.g~Z CMa and AS~353A) displaying the outflows of larger scale
($>50\,\mathrm{AU}$); however, this could be formed by shocks rather
than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
(e.g.~\citealt{shang:2002}). %
}; however, if a slower wind acceleration rate ( $\beta=4$) is the
emission region become slightly larger ($\sim0.4$~AU).

Although not shown here, we have computed the H$\alpha$ profiles
with the collimated wind and the accretion disc for the same range
of $\beta$ and $T_{\mathrm{max}}$values as in Figure~\ref{fig:atlas_wind_model}.
The inner and the outer radii of the accretion disc are $R_{\mathrm{di}}=R_{\mathrm{mi}}=2.2R_{*}$
and $100\,\mathrm{AU}$ respectively, and the disc is slightly flared
(see section~\ref{sub:Accretion-disc}). Similar to the case in Figure~\ref{fig:effect_alpha_disc},
the line flux of the models with accretion disc decreases to less
than the half of that without the accretion disc similar to the models
shown in Figure~\ref{fig:effect_alpha_disc}. The overall behaviour
of the line profile shapes as functions of $\beta$ and $T_{\mathrm{wind}}$
are very similar to that for the models without the accretion disc.
A significant reduction of the flux in the red wing is seen in the
wind model with the accretion disc when compared with the wind only
model. The wings appear to be weaker in these models compared to the
wind only models because of the lower wind emission flux to the continuum
flux as briefly mentioned earlier.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{ccc}
\includegraphics[%
  clip,
  scale=0.3]{figures/disc_nodisc_compare.eps}&
\includegraphics[%
  scale=0.3,
  angle=270,
  origin=lt]{figures/wind_thindisc.eps}&
\includegraphics[%
  scale=0.3,
  angle=270,
  origin=lt]{figures/wind_nodisc.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{Comparison of of the wind model with and without the optically-thick and geometrically-thin disc.  The latter can be also equivalent to a model with a large inner radius of the accretion disc in which none of the wind emission region is not blocked provided the inclination is moderate. The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used). The flux in the red wing of the line profile from the model with the disc (solid) is greatly reduce by the presence of the accretion disc compared  to that from the model without the disc (dashed).  The peak flux and the flux in the wings are also reduced in the model with the disc because the disc does block the wind emission region, but none of the stellar disc, i.e. the continuumm flux level is unchanged.  The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown. The image flux is computed by integrating the specific flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$. The flux is in an arbitrary units and in logarithmic (base $10$) scale. }

\label{fig:effect_alpha_disc}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Magnetosphere $+$ disc $+$bipolar wind}

\label{sub:model-acc-disc-wind}

We examine the characteristics of the line profiles arising from the
combination of the magnetospherical accretion flow, the wind, and
the accretion disc. For simplicity, the parameters for the magnetosphere
($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
are fixed as in Figure~\ref{fig:atlas_acc_models}), and the wind
mass-loss rate, the isothermal wind temperature and the wind anisotropy
parameter to $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$), $T_{\mathrm{wind}}$
and $b=4$ respectively. The profile computed for $i=55^{\circ}$
is given in Figure~\ref{fig:summary_beta05_t8000}, along with the
profile computed with the magnetosphere only and that with the wind
plus accretion disc configurations for a comparison. As one can see
from the figure, the profile computed for the disc--wind--magnetosphere
hybrid model can be understood as a simple flux sum of the magnetospherical
component and the wind component. In this example, the wind causes
the absorption of the blue side of the profile, and it adds extra
flux around the line centre. As seen before, the presence of the disc
causes the reduction in the red side of the profile since the emission
from the receding gas is block by the disc. The resulting profile
appears to be narrower than that of the magnetosphere model.

The effect of changing the ratio of the wind mass-loss rate to mass-accretion
rate ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With the fixed value
of mass-accretion rate ($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
, the mass-loss rate by the wind is varied. The figure shows that
as $\mu$ increases the P-Cygni absorption deepens, and the position
of minimum flux in the absorption trough appears to move blue-ward.
On the other hand, the emission component becomes stronger as $\mu$
increases. With this combination of the parameters for the magnetosphere
and the wind, the absorption component tends to be too strong for
the models $\mu>0.025$ (with this model configuration), at all inclinations
(not shown here), compared with the observed H$\alpha$ profiles (e.g.\citealt{reipurth:1996};
\citet{alencar:2000}). As we will see later (section~\ref{fig:ttau_model}),
$\mu$ can be as large as $\sim0.3$ with different parameters of
the magnetosphere; hence, this condition $\mu>0.025$ is always valid.

Again, the H$\alpha$ profiles with the same ranges of the wind temperature
($T_{\mathrm{wind}}$) and the wind acceleration parameter ($\beta$)
used in Figure~\ref{fig:atlas_discwind_only} are computed with $\mu=0.01$.
The parameters of the magnetosphere fixed as in Figure~\ref{fig:acc_inclination_effect},
are shown in Figure~\ref{fig:atlas_disc_wind_acc_model} along with
the model with only the magnetosphere, for a comparison. A relatively
small value of $\mu$ is chosen to avoid absorption component of the
P-Cyg profile becoming too strong, as seen in Figure~\ref{fig:effect_mdot_disc_wind_acc}.
In general, even with small values of the anisotropy parameter ($b=0$
and $2$), the absorption component is found to be too strong when
$\mu=0.1$ is used with this combination of the magnetosphere and
the wind. The figure shows that the position of the wind absorption
component moves toward the line centre as $\beta$ becomes larger.
Although little wind emission is seen in this temperature range, it
becomes more important in a model with a higher temperature and a
wind mass-loss rate. In fact, the model with $\beta=2.0$ and $T_{\mathrm{dw}}=9000\,\mathrm{K}$
displays a small amount of the wind emission at $V\sim50\,\mathrm{km\, s^{-1}}$.

As seen in Figure~\ref{fig:summary_beta05_t8000}, the profiles shown
here can be understood as the combination of the emission from the
magnetosphere and the absorption of the flux by the wind component.
In general, the emission from the accretion disc is negligible at
H$\alpha$ wavelength, but the absorption of the continuum flux from
the photosphere by the disc is important for predicting correct line
strengths.

Although the profiles shown in Figure~\ref{fig:atlas_disc_wind_acc_model}
are those at a single inclination angle ($i=55^{\circ}$), they are
very similar to the Type II-B and III-B of the observed CTTS H$\alpha$
profiles (\citealt{reipurth:1996}), which are impossible to be explained
by the magnetospherical accretion flow models (e.g.~\citealt{muzerolle:2001}).
Comparison of the model profiles with different types of the observed
H$\alpha$ profiles will be given in section~\ref{sub:Classification-scheme-proposed}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/summary.eps}

\end{center}

\caption{Comparison of the profiles computed with the magnetosphere, the wind, the disc, and their combinations. The model configureations used above are: (1)~magnetosphere only (dashed), (2)~wind and disc (dash), and (3)~disc, wind and magnetosphere (solid).  The parameters used here are $T_{\mathrm{max}}=7500\,\Kelvin$, $\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$, $\dot{M}_{\mathrm{wind}}=10^-8\,\mathrm{M_{\sun}\,yr^{-1}}$, $T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$. The profile for the case 3 is can be understood as a simple flux sum of the profiles from case 1 and 2.}

\label{fig:summary_beta05_t8000}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/disc_wind_acc_mdot_effect.eps}

\end{center}

\caption{Effect of the mass-loss rate to mass-accretion rate ratio  ($\mu=\dot{M}_{\mathrm{w}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$ profile computed with only the magnetopsherical accretion (thick solid) -- $T_{\mathrm{max}}=7500\,\Kelvin$, $\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$ -- is compared with the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash). All the models are computed with the inclination angle $i=55^{\circ}$. As $\mu$ increases the P-Cygni absorption deepens and the emission component becomes stronger. In genaral, the absorption is too strong for the models $\mu>0.025$ compared with the observations (e.g., \citealt{reipurth:1996}).}

\label{fig:effect_mdot_disc_wind_acc}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=0.9]{figures/atlas_ha_i55_wind_acc_alpha_final2.eps}

\end{center}

\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$), the accretion disc. The mass-loss rate of the wind used here is $\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$. A relatively small mass-loss rate is chosen to avoid unrealistically strong P-cyg absorption component (see text in section~\ref{sub:model-acc-disc-wind} and  Figure~\ref{fig:effect_mdot_disc_wind_acc}).  For a comparison, the profile computed with only the magensopherical accretion flow (dotted) is overlayed. All the profiles are computed at the inclination angle $i=55^{\circ}$. As $\beta$ becomes larger, the postion of the wind absorption component moves toward the line centre. Although little wind emission is seen in this temperature range, it becomes more important in a model with a higher temperature and a wind mass-loss rate. The profiles resembles the observed H$\alpha$ emission profiles affected by the wind.}

\label{fig:atlas_disc_wind_acc_model}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Disc-wind model of \citet{knigge:1995}}

\label{sub:result-discwind-knigge}

As an alternative model for the bipolar wind models (with the combination
of the magnetosphere and the accretion disc) shown in Figures~\ref{fig:atlas_wind_model}
and \ref{fig:atlas_disc_wind_acc_model}, we have also considered
the disc-wind model \citet{knigge:1995} as briefly described in section~\ref{sub:model-disc-wind}.
The former resembles the density structure of \citealt{krasnopolsky:2003}
in large scale ($\sim100$~AU) which described in section~\ref{sub:wind_jet},
and the latter in small scale ($\sim10$~AU) of the same model. The
main difference between the two models are in their density structure.
For a given radius, the density increases toward the polar direction
in the former model, but the density increases toward the equatorial
plane for the models presented here.

First, the disc wind models without the magnetosphere are considered.
Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
computed using only the disc-wind component (c.f. Figure~\ref{fig:config_discwind})
for the same isothermal disc-wind temperature ($T_{\mathrm{dw}}$)
and the wind acceleration parameter ($\beta$) ranges used for the
bipolar wind models. The parameters used for the central star are
as in section~\ref{sub:Continuum-Source}, and the other disc-wind
parameters are summarised in Table~\ref{tab:std_discwind_parameters}.
The figure shows that the wind emission increases $\beta$ and $T_{\mathrm{dw}}$
increase. Similar to the bipolar wind models, the location of the
P-Cyg absorption component moves toward the line centre as $\beta$
increases. The morphology of the profile exhibited by the model changes
from FU-Ori type (IV-B) for the models with small $\beta$ to III-B
and II-B types (\citealt{reipurth:1996}) as the value of $\beta$
increases. Although not shown here, we find that the profile shapes
are relatively insensitive to the value of the wind collimation parameter
$d$. The dependency on the disc wind mass-loss rate of the profile
shape is similar to that of the collimated wind models (Figure~\ref{fig:effect_mdot_disc_wind_acc})
.

We now consider the models computed with the combination of the disc-wind
and the magnetospherical accretion components. The parameters used
for the magnetosphere are set to be same as in the case for Figure~\ref{fig:acc_inclination_effect},
and are kept constant for simplicity. The mass-loss rate of the disc
wind is set to $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$) Figure~\ref{fig:atlas_discwind_acc_model}
shows the models profiles computed using the same ranges of the disc-wind
temperature and the wind acceleration parameter as in the previous
cases.

As in the disc wind only models (Figure~\ref{fig:atlas_discwind_only}),
the location of the absorption component moves toward the line centre
as the value of $\beta$ increases (as the wind acceleration slower).
The figure shows that in the models with smaller $\beta$ and $T_{\mathrm{dw}}$,
the line emission from the magnetosphere dominates. On the other hand,
in the models with larger $\beta$ and $T_{\mathrm{dw}}$, the emission
from the disc wind dominates. Compared to the observation of \citet{reipurth:1996}
and \citet{alencar:2000}, the lines are too strong for $\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
and $\left(9000\,\mathrm{K},\,1.0\right)$ models. The wide varieties
of profile shapes are see in this set of models which resembles II-B,
III-B, IV-B, II-R and III-R%
\footnote{Not shown here, but seen in the models with different combinations
of $i$, $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$.%
} types of the observed H$\alpha$ profiles (\citealt{reipurth:1996}).
The shape of the primary and secondary peaks in the profiles are slightly
{}``rounder'' compared to those of the accretion, collimated wind,
disc hybrid model shown in Figure~\ref{fig:atlas_disc_wind_acc_model}.
The rounder peaks are caused by the rotation of the wind. The profiles
from the disc wind models are affected more by the rotational motion
of the wind since the gas is more concentrated toward the equator,
but in the models with the collimated wind the gas is concentrated
more in the polar directions.

We note the ambiguity seen between some of the disc-wind only models
and the disc-wind, magnetosphere hybrid models. For example, the disc-wind
only model with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
in Figure~\ref{fig:atlas_discwind_only} and the disc-wind model
with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
in Figure~\ref{fig:atlas_discwind_acc_model} give very similar profiles.
Given such an observed profile, it is difficult to distinguish if
the emission is dominated by the accretion or the wind unless some
other lines, not affected associated with wind or magnetosphere, are
used simultaneously.

General characteristics of the profiles from the disc-wind, magnetosphere
hybrid model (Figure~\ref{fig:atlas_discwind_acc_model}) are very
similar to those of the disc, collimated wind, magnetosphere hybrid
model (Figure~\ref{fig:atlas_disc_wind_acc_model}). The main difference
between these two sets of models is the mass-loss rate to the mass
accretion rate $\mu$. While the models presented in this section
use $\mu=0.1$ which is consistent with the MHD jet models (e.g.~\citealt{koenigl:2000}),
the models in Figure~\ref{fig:atlas_disc_wind_acc_model} use much
smaller value ($\mu=0.01$).

\begin{table}

\begin{center}

\begin{tabular}{ccccccc}
\hline 
$d$&
$R_{\mathrm{wi}}$&
$R_{\mathrm{wo}}$&
$\dot{M}_{\mathrm{dw}}$&
$p$&
$f$&
$R_{\mathrm{s}}$\tabularnewline
$\left[R_{*}\right]$&
$\left[R_{*}\right]$&
$\left[\mathrm{AU}\right]$&
$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
$[-]$&
$[-]$&
$\left[R_{*}\right]$\tabularnewline
\hline
$21.4$&
$3.0$&
$1.0$&
$10^{-8}$&
$-3/2$&
$2.0$&
$30$\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary of the standard disc-wind model parameters used in section~\ref{sub:result-discwind-knigge}. See also section~\ref{sub:Alternative-model-disc-wind}.}

\label{tab:std_discwind_parameters}

\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}

\end{center}

\caption{The H$\alpha$ profiles computed with the disc-wind only models. For the wind mass-loss rate fixed at $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line profiles are computed with different combinations of the wind accelreation rate ($\beta$) and the isothermal disc wind temperature ($T_{\mathrm{dw}}$). The wind emission increases as the values of $\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes accelerates slower and as the wind comes warmer.  Similar to the bipolar wind models (Figure~\ref{fig:atlas_wind_mode}), the position of the wind absorption moves toward the line centre as $beta$ becomes larger. The morphology of the profiles are smilar to that of observations. }

\label{fig:atlas_discwind_only}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}

\end{center}

\caption{The disc-wind, magnetoshere hybrid model. Same as Figure~\ref{fig:atlas_discwind_only}, but these models (soild) also include the magnetosphere accretion flow ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$). While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{dw}}$  (the slower accerelation and the hotter models). For a comparison, the profile computed with only the magensopherical accretion flow (dotted) is overlayed. The model profiles are very similar to the observed profiles influenced by the wind outflow.}

\label{fig:atlas_discwind_acc_model}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

\label{sec:Discussion}

\subsection{Classification scheme proposed by Reipurth et. al (1996)}

\label{sub:Classification-scheme-proposed}

\citet{reipurth:1996} proposed the two-dimensional classification
of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
stars. Their classification scheme contains four classes (I, II, III
and IV) differentiated by the ratio of the secondary-to-primary emission
components in the profiles. Each classes are divided into two sub-classes
(B and R) which depends whether the absorption component is on the
blue or red side. Readers are refereed to Fig.~4 of their paper.
Figure~\ref{fig:atlas_reipurth} shows the sample model profiles
which are classified according to the definition of \citet{reipurth:1996}.
The combination of the disc wind, magnetospherical accretion, and
accretion disc can reasonably reproduce all the classes of the profiles
seen in observations. Similar profiles can be reproduced if the bipolar
wind is used instead of the disc wind, but the wind absorption at
a given velocity location occurs at a different inclination angles
when the wind type is switched from the bipolar wind to the disc wind.
The corresponding model parameters used to reproduce the profiles
in the figure are given in Table~\ref{tab:classification} along
with brief comments on possible physical conditions which leads to
the profiles in each class.

Using the samples of H$\alpha$ from 43 CTTS, \citet{reipurth:1996}
found the most common (33~per~cent) type of the profile is Type
III-B. Interestingly, the most common profile type seen in the profiles
from both the bipolar wind, disc and magnetosphere hybrid model (Figure~\ref{fig:atlas_disc_wind_acc_model})
and the disc-wind and the magnetosphere hybrid model (Figure~\ref{fig:atlas_discwind_acc_model})
are Type III-B profiles. In this type of profiles, the main emission
comes from the magnetosphere, and the profile shape is altered a slightly
blue-asymmetric one to a slightly red-asymmetric one via the wind
absorption in the blue wing. The second most common profile (26~per~cent)

Type I (symmetric around line centres) is mainly produced in the magnetosphere.
Although not shown here, this type of profile can be reproduced with
the disc-wind, magnetosphere hybrid mode with pole on configuration.
Since there is not material in the polar region in the disc wind model,
the observer can look the magnetosphere almost directory for high
inclination cases, provided that wind temperature is low enough so
that the wind emission is negligible. Type II-R and Type II-B can
be produced in a similar physical conditions (e.g. in a slow accretion
and low temperature wind plus a magnetosphere). Main difference is
between the two is in their inclination angles. The former is more
likely seen with high inclination.

Type III-R is the least common type of the observed profile (2~per~cent)
according to \citet{reipurth:1996}. Incidentally, we also had a hard
time to reproduce this type of profile since this can be achieve only
at narrow range of parameter space (very high inclination angle with
disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and $\dot{M}_{\mathrm{acc}}~10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).

Similarly the Type IV-R is the second least common type of observed
profile (5~per~cent) which shows the inverse P-Cyg profile shape.
This can be understood since the magnetospherical accretion model
of \citet{hartmann:1994} predicts that the redshifted absorption
can occur at a limited range of inclination angle with which the hot
continuum flux from the footprint of the magnetosphere is seen through
relatively fast moving gas in the accretion stream. Finally Type III-R
profile is very similar to Type II-R, but the wind in this type of
profile may be accretion faster than that in Type II-R.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.65]{figures/atlas_reipurth_like_discwind.eps}

\end{center}

\caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}. The combination of magnetospherical accretion flow, the accretion disc, and the disc wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations. Similar results can be obtained if the disc wind is replaced by the disc wind. The model parameters and short comments are summarised in Table~\ref{tab:classification}. The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.}

\label{fig:atlas_reipurth}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%astro.ex.ac.uk/people/rk/

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table*}

\begin{center}

\begin{tabular}{llllllll}
\hline 
&
$i$&
$\dot{M}_{\mathrm{acc}}$&
$T_{\mathrm{max}}$&
$\dot{M}_{\mathrm{dw}}$&
$T_{\mathrm{dw}}$&
$\beta$&
Comment\tabularnewline
Class&
&
&
&
&
&
&
\tabularnewline
\hline 
I&
$55$&
$10^{-7}$&
$7.5$&
$-$&
$-$&
$-$&
Accretion dominated possibly without the wind. Mid inclination.\tabularnewline
II-B&
$55$&
$10^{-7}$&
$7.5$&
$10^{-9}$&
$8.0$&
$1.0$&
Wind, disc and magnetosphere. Wide range of wind acceleration rate.
Mid--high inclination\tabularnewline
III-B&
$55$&
$10^{-7}$&
$7.5$&
$10^{-9}$&
$9.0$&
$0.5$&
Wind, disc and magnetosphere. Fast--mid wind acceleration rate. Mid
inclination\tabularnewline
IV-B&
$55$&
$10^{-7}$&
$7.5$&
$10^{-8}$&
$9.0$&
$0.5$&
Wind, disc and magnetosphere. Fast wind acceleration rate. Mid inclination\tabularnewline
II-R&
$80$&
$10^{-7}$&
$7.5$&
$10^{-9}$&
$7.0$&
$2.0$&
Wind, disc and magnetosphere. Slow wind acceleration rate. High inclination\tabularnewline
III-R&
$85$&
$10^{-8}$&
$8.2$&
$10^{-9}$&
$6.0$&
$1.0$&
Wind, disc and magnetosphere. Mid wind acceleration rate. Very high
inclination \tabularnewline
IV-R&
$55$&
$10^{-9}$&
$9.5$&
$-$&
$-$&
$-$&
Accretion dominated. Low mass-accretion rate. Mid inclination.\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments. The temepratures are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and $\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}

\label{tab:classification}

\end{table*}

\subsection{An example model fit of T~Tau}

\label{sub:ttau-model}

As a demonstrative purpose, we present a model fit of H$\alpha$ observation
of a classical T Tauri star (T~Tau) obtained by \citet{vink:2005}.
T~Tau is known to be a triple system (e.g.~\citealt{koresko:2000}).
One of the star in the system T~Tau~N (a prototype for T~Tauri
stars) is dominating in optical (e.g.~\citealt{calvet:1994}). The
rotational velocity and the rotational period of the star found by
\citet{herbst:1987} are $v\,\sin i=19.5\pm2.5\,\mathrm{km\, s^{-1}}$
and $2.80\,\mathrm{d}$ respectively. The inclination of the disc
is known to be relatively small (e.g.~$i=29^{\circ}$, \citealt{akeson:2002}).
There is a rather large scatter in the previously estimated the accretion
rates e.g.~$3\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ \citep{johns-krull:2000}
and $\left(3.1-5.7\right)\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
\citep{calvet:2004}.

For the photospheric model, the following parameters from \citet{calvet:2004}
are adopted: $T_{\mathrm{eff}}=5500\,\mathrm{K}$, $M_{*}=1.9\,\mathrm{M_{\sun}}$
and $R_{*}=2.9\, R_{*}$. The standard geometry for the magnetosphere
($R_{\mathrm{mi}}=2.2\, R_{*}$ and $R_{\mathrm{mo}}=3.0\, R_{*}$)
and the bipolar wind configuration (Table~\ref{tab:std_parameters})
are used for simplicity. Again, our purpose here is not to obtain
the best fit parameters, but rather it is to examine if the model
is capable of reasonably reproducing the data from a real object,
in this case, T~Tau~N. The main parameters here (1)~the temperature
of the magnetospherical accretion flow ($T_{\mathrm{max}}$), (2)~the
mass-accretion rate ($\dot{M}_{\mathrm{acc}}$), (3)~the temperature
of the wind ($T_{\mathrm{wind}}$), and (4)~the wind mass-loss rate
($\dot{M_{\mathrm{wind}}}$). The inclination angle is simplify adopted
from \citealt{akeson:2002} i.e.~$i=29^{\circ}$.

Figure~\ref{fig:ttau_model} shows the result of a model fit. The
amount of veiling near H$\alpha$ is very small ($<0.01$) for T~Tau,
according to \citet{basri:1990}; hence, the observation is not corrected
for veiling. The model consists of the magnetosphere, the bipolar
wind, and the accretion disc (with a large hole i.e.$\sim5$\, AU
. The parameters used for the model fit are: $T_{\mathrm{max}}=22000\,\mathrm{K}$,
$T_{\mathrm{wind}}=8000\,\mathrm{K}$, $\dot{M}_{\mathrm{acc}}=1.1\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$,
and $\dot{M}_{\mathrm{wind}}=2.0\times10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$.
The temperature of the magentosphere is relatively high compared to
the standard cases (e.g.~Figure~\ref{fig:atlas_acc_models}; also
\citealt{muzerolle:2001}). Note that the estimated value of $T_{\mathrm{max}}$depends
on the adopted values of $L_{*}$ (or $M_{*}$ and $T_{\mathrm{eff}}$)
for the photospheric continuum model. If a lower value of $L_{*}$
is adopted, $T_{\mathrm{max}}$value would become smaller in order
to match the line strength which is mainly determined by the emission
from the magnetosphere, in this case. For example, if the photospheric
continuum is 3 times smaller than the one used here, one finds $T_{\mathrm{max}}\sim9600\,\mathrm{K}$
which is more similar to that of the standard cases. The figure shows
that the agreement between the model and the observation is quite
reasonable although the line wings are slightly stronger in the models.
In this example, the main profile feature is defined by the emission
from the magnetosphere, but the blue side of the profile is affected
by the absorption by the wind. The mass-loss to mass-accretion rate
$\mu=0.18$ which is similar to the value predicted by observations
and MHD simulations i.e.~$\sim0.1$ \citep{koenigl:2000}. Compared
our mass-accretion rate estimate is much less than that of \citep{johns-krull:2000},
and slightly smaller than that of \citep{calvet:2004} (see above).

Although not shown here for clarity, the peak flux near the line centre
is also affected by the wind absorption (causing about 10 per cent
reduction) compared to the profile computer with magnetosphere only
model (similar effect also seen in Figure~\ref{fig:atlas_disc_wind_acc_model}).
If the fit was performed by ignoring the wind, the temperature and
the mass-accretion rate of the magnetospherical accretion flow will
be underestimated. A better approach to a model fit is a simultaneous
fitting of multiple lines. For example, the near-infrared lines such
as Pa$\beta$ and Br$\gamma$ should be used to determined the mass-loss
rate since these lines are much less affected by the wind. Using the
mass-loss rate from these lines, H$\alpha$ can be used to determine
the wind mass-loss rate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/ttau_compare.eps}

\end{center}

\caption{Comparison of the observed H$\alpha$ profile of T~Tau and the profile computed with the hybrid model, which consist of the magnetosphere, the colliminated wind, and the accretion disc (with a large hole i.e. $\sim 5$~AU). The inclination angle $29^\circ$ is used.  The maximum temperature of the magnetosphere ($T_{\mathrm{max}}$) and the isothermal wind temperature used here are 22000~K and 8000~K respetively. The mass-accretion rate ($\dot{M}_{\mathrm{acc}}$) and the mass-loss rate ($\dot{M}_{\mathrm{wind}}$) are $1.1 \times 10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and $2.0 \times 10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ resplectively ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.18$)}

\label{fig:ttau_model}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Which wind model?}

\label{sub:Which-wind-model}

In the previous sections, two possible geometrical configurations
for the wind from CTTS were considered: 1. the bipolar wind, and 2.~the
disc wind. While the material more concentrated toward the polar regions
for a given radius in the first case, the material is more concentrated
toward the equatorial plane in the second case. As mentioned earlier,
the bipolar wind morel resembles the density distribution of the jet
MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
($>10$~AU), and the disc wind model resembles that in smaller scale
($<10$~AU).

The distinct difference in the density dependency on the polar angles
in two models should be apparent in the inclination angle dependency
on the shapes of the line profiles. Figure~\ref{fig:effect_inclination_compare}
shows the H$\alpha$ profiles computed for 1.~the disc, bipolar-wind,
accretion hybrid model (section\ref{sub:model-acc-disc-wind}) and
2.~the disc-wind, magnetosphere hybrid model (section~\ref{sub:result-discwind-knigge})
at inclination angles $i=10^{\circ},\,55^{\circ},\,80^{\circ}$. Both
models include the magnetospherical accretion component with the same
parameters used as in sections~\ref{sub:model-acc-disc-wind} and
\ref{sub:result-discwind-knigge} i.e. $T_{\mathrm{max}}=7500\,\mathrm{K}$
and $\dot{M}_{\mathrm{acc}}=1\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$.

Mainly because of the geometrical configuration, the P-Cyg absorption
feature weakens as the inclination increases for the model with the
bipolar wind. The optical depth to an observer is higher (from the
wind emission region) for with a lower inclination angle with this
geometry. Although not shown here, this tendency of the inclination
dependency holds for the models with bipolar wind models for wide
ranges of $\beta$ and $T_{\mathrm{wind}}$. For the model with the
disc wind, the absorption becomes stronger as the inclination becomes
larger . The optical depth to an observer becomes larger as the inclination
increases in this geometry.

Similarly, the line equivalent width increases as the inclination
angle increases for the model with the bipolar wind, it decreases
as the inclination angle increases for the model with the disc wind.
With the models with only magnetosphere (section~\ref{sub:model-acc}),
we have also found that the line equivalent width decreases as the
inclination increases in those models (see Figure~\ref{fig:acc_inclination_effect}).
Interestingly, the observational study of \citet{appenzeller:2005}
showed that the H$\alpha$ line equivalent width of CTTS increases
as the inclination angle increases. Only the models with the bipolar
wind agree with the trend seen in their observation. Although the
uncertainty in the inclination angles of the observed object might
be large, a larger sample in addition to that of \citet{appenzeller:2005}
for further investigation of the inclination dependency on the line
profile will be extremely useful for finding a possible wind configuration
of CTTS.

Despite the inclination angle dependency of the observed H$\alpha$
favouring the models with bipolar wind, there are two main aspects
of this model are not quite consistent with the magneto-centrifugal
launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
First, in section~\ref{sub:model-acc-disc-wind}, we found that the
ratio of the mass-loss to mass-accretion rates needed to be rather
small ($\mu<\sim0.025$), in order not to have an unrealistically
strong P-Cyg absorption component, compared to the MHD simulations
suggested \citep{koenigl:2000} i.e. $\mu\approx0.1$. In the model
fit of T~Tau observation (section~\ref{sub:ttau-model}), we found
much larger value of the ratio $\mu=0.18$. Considering large uncertainty
in MHD theories and observational measurements ($\dot{M}_{\mathrm{acc}}$,
$\dot{M}_{\mathrm{wind}}$ and $B$, ), the wide range of the mass-loss
to mass-accretion ratio (e.g.~$0.025<\mu<0.18$) may be still reasonable.
On the other hand, the models with the disc wind (section~\ref{sub:result-discwind-knigge})
using $\mu=0.1$ reproduces the profiles (Figure~\ref{fig:atlas_discwind_acc_model})
similar to that seen in observations. Second, the MHD models predict
that the wind/jet becomes collimated well above the disc plane ($>10$~AU),
but our bipolar wind model are collimated (density enhanced toward
in the polar direction) from right outside of the magnetosphere. Unless
the origin of the wind is from the central star itself, the density
distribution used for the bipolar wind is not quite consistent with
the near field of the MHD jet models, considering that the most of
the H$\alpha$ emission occurs within a few to a several radii of
the magnetosphere (Figure.~\ref{fig:effect_alpha_disc}). The density
structure used for the disc wind model, however, is very similar to
that of MHD simulations in the near field where the most of the H$\alpha$
wind emission occurs. Interestingly, however, the recent study of
\citet{matt:2005} showed the possibility that the stellar wind along
the open magnetic field originating from the star can cause significant
spin-down torque on the star, provided that mass-loss rate is high
enough. Considering the issues mentioned above, it is not possible
to favour the bipolar wind model to the disc wind model without further
observational constraints. In reality, two types of the winds (bipolar
wind and disc wind) may co-exits similar to that seen in e.g. \citet{drew:1998}
and \citet{matt:2005}. In these models, the fast stellar wind is
present in the polar directions, and at the same time the slower disc
wind is present near the equatorial plane.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{cc}
\includegraphics[%
  clip,
  scale=0.45]{figures/disc_wind_acc_inc_effect_m9_b2_t7000.eps}&
\includegraphics[%
  clip,
  scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{Dependency on the inclination angle of the H$\alpha$ model profiles. The profile computed at $i=10^{\circ}$(solid), $55^{\circ}$ (dot) and $80^{\circ}$ using 1.~the disc, bipolar-wind, accretion hybrid model (left panel; c.f. section~\ref{sub:model-acc-disc-wind}) and 2.~using the disc-wind, magentosphere hybrid model (right; c.f. section~\ref{sub:result-discwind-kingge}) are shown for a comparison.  The parameters used for the magnetoshere are same for the both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and  $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The isotherma wind temperature and the wind accrelation parameter used both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.  All the other parameters are same as in sections~\ref{sub:model-acc-disc-wind} and  \ref{sub:result-discwind-knigge}. While the line equivalent width increases as the inclination angle increases for the former model configuration, it decreases as the incination angle increases for the latter. Only the former agrees with the tendency seen in the observational study of \citet{appenzeller:2005} who showed that the H$\alpha$ line equivalent width of CTTS increases as the inclination angle increases. }

\label{fig:effect_inclination_compare}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

\label{sec:Conclusions}

We have presented the disc--wind--magnetosphere hybrid radiative transfer
models for classical T~Tauri stars, and detailed studies of the H$\alpha$
formation from their complex to circumstellar environment and to understand
the wide variety emission line profiles seen in observations. The
two types of wind models considered are (1)~the bipolar wind model
in the wind is originated from the star itself (section~\ref{sub:wind_jet};
Figure~\ref{fig:config_dipolar}), and (2)~the disc-wind model in
which the wind originates from the inner part of the accretion disc
(section~\ref{sub:Alternative-model-disc-wind}; Figure~\ref{fig:config_discwind}).
We found that both wind models combined with the magnetospherical
accretion flow reproduces the wide variety of H$\alpha$ profiles
(Figures~\ref{fig:atlas_disc_wind_acc_model} and \ref{fig:atlas_discwind_acc_model})
seen in the observations.

The inclination dependency of the line equivalent width predicted
by the bipolar wind model agree with trends seen in the observation,
but the disc-wind model does not. With the standard magnetospherical
configuration (Table~\ref{tab:std_parameters}), the ratio of the
mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind
was set to be 4--10 times smaller than that predicated by magneto-hydrodynamical
(MHD) calculations (c.f.~$\mu\sim0.1;$ \citealt{koenigl:2000})
to avoid the blue-shifted absorption component becoming unrealistically
too strong; however $\mu$ used in the disc-wind models are consistent
with MHD calculations.

Using the model results, we examined the H$\alpha$ spectroscopic
classification proposed by \citet{reipurth:1996}, and discuss the
basic physical conditions that reproduce the profiles in each classified
type. Using the hybrid model, we also fit the observed H$\alpha$
from the optical component of T~Tau triple system (T~Tau~N). The
agreement between the model and the observation is excellent; however,
we could not confirm the uniqueness of the fit. The ratio of the mass-loss
to mass-accretion rate was found to be $\sim0.18$.

Although not attempted in this paper, a better approach for determining
the mass-loss and mass-accretion rate consistently is to model multiples
lines simultaneously. For example, the mass-accretion rate of an object
can be determined more easily by modelling Pa$\beta$ and Br$\gamma$
since there is no/little wind effect seen in these lines. The mass-accretion
rate then can be used to model H$\alpha$ to find the wind mass-loss
rate.

Similar model configurations used here may be also applicable to Herbig
Ae/Be and brown dwarfs since their H$\alpha$ observations also exhibit
evidences of the outflow and inflow (e.g.~\citet{finkenzeller:1984};
\citealt{muzerolle:2005}), but no model has been developed to explain
the phenomenon. Further investigation on the possibility of applying
our model to these objects are needed.

Future works should include the followings: (1)~Improving the wind
models. The parametrisation of the wind density structure should be
changed to follow more closely that of MHD simulations. The wind temperature
structure should be calculated self-consistently (c.f.~\citealt{hartmann:1994};
\citealt{martin:1996}). (2)~Computing the line profiles using the
density structure from MHDs directly. Check the consistency, and give
feedback to the MHD models which are needed to be tested against observational
data. (3)~Spectropolarimetric study to explore the geometry and the
rotation of the disc (e.g.~\citealt{vink:2005}). (4)~Modelling
of the extended H$\alpha$ and spectro-astrometric observations (c.f.~\citealt{takami:2003};
\citealt{appenzeller:2005}). (5)~Line variability study using a
3D radiative transfer model (e.g.~\citealt{symington:2005}; \citealt{kurosawa:2005a})
to probe the geometrical structure.

\section*{Acknowledgements}

Authors thank Jorick Vink for providing us the H$\alpha$ data of
T~Tau. This work is supported by PPARC standard grand PPA/G/S/2001/00081.

%

%

%

%----------------------------------------------------

% Bibliography follows here.

%-----------------------------------------------------

%

%

%

\bibliographystyle{mn}

\bibliography{mnras}

%

\label{lastpage}
\end{document}

### 2005-11-29 TTau_Halpha/tmp.tex
new paper
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@603 25464f21-6099-402c-b30a-640f1d40d38b

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amssymb}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Bold symbol macro for standard LaTeX users
\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{lscape}
\usepackage{times}

\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{\apj}
\newcommand{\pasp}{PASP}
\newcommand{\aj}{AJ}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\aapr}{A\&AR}
\newcommand{\pasj}{PASJ}

\newcommand{\kmps}{\mathrm{km~s^{-1}}}
\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
\newcommand{\Kelvin}{\mathrm{K}}

\usepackage{babel}
\makeatother
\begin{document}
\title[On H-$\alpha$ formation of T Tauri stars]{On formation of H-$\alpha$ from classical T Tauri stars: the disc, wind, and magnetospheric-accretion hybrid model}

\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries and Neil H. Symington\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}

\date{Dates to be inserted}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2005}

\maketitle

\label{firstpage}

\begin{abstract}

We investigate the formation of H$\alpha$ from classical T~Tauri
stars with a complex circumstellar geometry -- the combination of
mangnetisherical accretion, collimated steller wind, and accretion
disc. AND MORE

\end{abstract}

\begin{keywords}
stars:formation -- stars: individual: SU Aur -- circumstellar matter -- infrared: stars -- stars: pre-main-sequence
\end{keywords}

\section{Introduction }

\label{sec:Introduction}

T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
H$\alpha$ emission, and typically have spectral types of F--K. Some
of the most active CTTS show emission in higher Balmer lines and metal
lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit an excess
amount of continuum flux in the ultraviolet (UV) and infrared (IR).
Their spectral energy distribution and polarization data suggest the
presence of a circumstellar disc, and it plays an important role in
regulating dynamics of gas flows around CTTS.

Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
\citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
of CTTS line profles show that the evidence for both outward wind
flows and inward accretion flows, as seen in the blueshifted absorption
features in H$\alpha$ profiles and the redshifted inverse P~Cygni
(IPC) profiles. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
\citealt{edwards:1987}; \citealt{hartigan:1995}), and the mass-accretion
rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
(e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).

Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
show the direct evidence for the presence of bipolar and monopolar
outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
and HV~Tau~C) by \citet{appenzeller:2005} show the extended (SCALE?)
H$\alpha$ emission in the direction perpendicular to the obscuring
circumstellar disc, and in both above and below the disc --- suggesting
the presence of the bipolar outflows. In silightly larger scale, \emph{HST}
observation of HH30 (Burrorws et al 1996) shows the jet traced to
within $\lesssim30$~AU from the star. The jet has a cone shape with
an opening angle of $3^{\circ}$ between 70 and 700 AU. (Originally
from Konig and Pudritz 2000 review in PP IV). \citealt{alencar:2000}
found about 80 per cent of their samples (30 CTTS) show blueshifted
absorption componets in at least one of Balmer lines and Ca~K (most
commonly in H$\alpha$).

In a currently favoured model of accretion flows around CTTS, the
accretion discs are disrupted by the magnetosphere of stars which
channels the gas from the disc onto the surface of the stars (e.g.,
\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993}\citealt{shu:1994}).
This picture of the accretion flows is supported by the evidences
that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$) magnetic
field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
and by the radiative transfer models which reproduce the observed
profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
accretion model naturally explains the blueward asymmetic emission
lines (seen in some of CTTS) caused by the partial occulation of the
flow by the disc, and the redshifted absorption componet at the typical
free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$) seen
in some of CTTS.

Dispite the success of the magnetosherical accretion model in explaining
the line profiles in some CTTS, the overwhelming observational evidences
for the outflow (mentoned above) in the CTTS profiles suggests that
this model is only a part of a whole picture. Clearly, the modefification
to include the outflowing wind/jet flow is neccessary if one requires
to predict the mass-accretion rate and the mass-loss rate of CTTS
by modelling their emission profiles (e.g. H$\alpha$).

Priory to the magnetospherical models, many alternative models had
been considered to explain the observed spectroscopic features mentioned
earlier. For example, 1.~the Alfv\'{e}n wave-driven wind model (e.g.~\citealt{decampli:1981};
\citealt{hartmann:1982}), 2.~turbulant boundary layer (between the
accretion disc and stellar surface) model (e.g.~\citealt{bertout:1988};
\citealt{basri:1989}), 3.~chromospheric model (e.g.~\citealt{calvet:1984}),
and 4.~disc wind model (e.g. \citealt{calvet:1992b}; \citealt{kwan:1995}).
Considering the sucess of the magnetospherical accretion flow model
in some cases and the observational eividences for the outflows, it
is likely that an improved spectroscopic model requires both inflow
and outflow components. The combination of the magnetospheric accretion
flow model with model 1 or 4 would be a reasonable starting point
for an improved spectroscopic model. Although time consuming to explore
a larger parameter space, more realistic density, velocity and temperature
structure from magnetohydrodynamic wind+accretion models should be
considered as inputs for an radiative transfer model in the future.

The magnetocentrifugal wind model, first proposed by \citet{blandford:1982},
has been often used to reproduce the large-scale wind structure of
T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
by \citealt{burrows:1996}; \citealt{ray:1996}). The lanching of
the wind from a Keplerian disc is typically done by treating the equaotorial
plane of the disc as a mass-injecting boundary condition (e.g., \citealt{ustyugova:1995};
\citet{shu:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
Depending on the location of the open magnetic fields anchored to
the disc, two different types of winds are preoduced. If the field
is constrained to be near the co-rotation radius of stellar magnetosphere,
an {}``X-wind'' \citep{shu:1994} is produces. If the open field
lines are located in a wider area of the disc, a {}``disc-wind''
similar to \citet{koenigl:2000} is produced \citet{krasnopolsky:2003}.
Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
and \citet{pudritz:2005}.

In this paper, we present a semi-emperical wind -- accretion disc
-- magnetospherical accretion hybrid model for CTTS, and perform parametric
studies of the H$\alpha$ formation. This study should provide preliminary
physical conditions which lead to the wide varaiety of emission line
profiles seen in the observation, and would help to construct more
comprehensive circumstellar models (e.g. via MHD simulations) of T~Tauri
stars. the Using the model results, we examine the H$\alpha$ spectroscopic
classification used by \citet{reipurth:1996}, and compare models
with observations. We will also discuss whether our model is consistent
with some predictions made by the recentt MHD studies (e.g.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$).

In section~\ref{sec:model-configuration}, the model assumptions,
and the basic model configurations are presented. We discuss the radiaive
transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
and the results of model calculations are given in section~\ref{sec:Results}.
The closer examination and discussion of the results are presented
in section~\ref{sec:Discussion}. Finally, the summary of this work
and the conclusion are in section~\ref{sec:Conclusions}.

\section{Model configuration}

\label{sec:model-configuration}

To understand how the different part of the CTTS circumsterllar enviroment
contributes to the fomation of H$\alpha$, the model spaced is devided
into four different regions: 1.~Central contiuum source, 2.~magnetosphere
accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:overview}
depicts the relative location in the model space. In all regions,
the density is symmetric around the z-axis. The innermost raius of
the magnetsphere at the equotrial plane coincides with the the inner
radius of the accretion disc. From the inner most part of the accretion
disc, the gas freely fall, moving along the magneic filed onto the
surface of the star. For the purpose of computational simplicity,
the colliminated wind are defined only in the outside of the largest
radius of the magnesophere. In the following subsections, the details
of model components will be described.

\begin{figure*}

\begin{center}

\includegraphics[%
  scale=0.6]{figures/overview2.eps}

\end{center}

\caption{Basic Model Configuration. The system consist of four components: 1.~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, 2.~magnetospherical accretion flow, 3.~colliminated wind/jet outflow, and 4.~accretion disc. The density distribution is symmetric around the z-axis. The innermost raius of the magnetsphere (at the equotrial plane) coincides with the the inner radius of the accretion disc. From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star. For simplicit, the colliminated wind/jet exists outside of the largest radius of the magnesophere (dotted line). }

\label{fig:overview}

\end{figure*}

\subsection{Contiuum Source}

\label{sub:Contiuum-Source}

Unless specified otherwise, we adopt stellar parameters of a typical
classical T~Tauri star (REF) for the central conitnuum source, i.e.
radius ($R_{*}$), mass ($M_{*}$), and effective temperature the
photosphere ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$,
and $4000\,\mathrm{K}$ respectively. The model atomsphere of \citet{kurucz:1979}
equivallently \citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$
and $\log g_{*}=3.5$ (cgs) is used to continuum flux at H$\alpha$wavelength.
The parameters are summarised in Table~\ref{tab:std_parameters}.

The limb-darkening law used for the continuum source is $I\left(\mu\right)=I_{0}\left(1+b\mu\right)$
where $\mu=\cos\theta$ and $\theta$ is the polar angle. $b$ is
a parameter. For no limb-darkening case, $b=0$, and for the Eddington
approximation case $b=3/2$. The former is used in all the calulcations
presented here. (Is this an ok assumption for T Tauri's? You need
to check this.)

\begin{table*}

\begin{center}

\begin{tabular}{lcccccccccccc}
\hline 
Parameters&
$R_{*}$&
$M_{*}$&
$T_{\mathrm{ph}}$&
$R_{\mathrm{mi}}$&
$R_{\mathrm{mo}}$&
$\dot{M}_{\mathrm{acc}}$&
$\dot{M}_{\mathrm{wind}}$&
$\beta$&
$v_{\infty}$&
$m$&
$R_{\mathrm{di}}$&
$R_{\mathrm{do}}$\tabularnewline
&
$\left[R_{\sun}\right]$&
$\left[M_{\sun}\right]$&
$\left[\mathrm{K}\right]$&
$\left[R_{*}\right]$&
$\left[R_{*}\right]$&
$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
$[-]$&
$[\mathrm{km\, s^{-1}}]$&
$[-]$&
$\left[R_{\sun}\right]$&
$\left[\mathrm{AU}\right]$\tabularnewline
\hline
Standard&
$2.0$&
$0.5$&
$4000$&
$2.2$&
$3.0$&
$10^{-7}$&
$10^{-8}$&
$0.2$&
$200$&
$2.0$&
$2.0$&
$100$\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary of the standard classical T~Tauri star model parameters.}

\label{tab:std_parameters}

\end{table*}

\subsection{Magnetosphere}

\label{sub:Magnetosphere}

We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
as done so by \citet{muzerolle:2001} and by \citet{symington:2005},
in which the gas accretion on to the stellar surface from the innermost
part of the accretion disc occurs through a dipolar stellar magnetic
field. The magnetic field is assumed to be so strong that the gas
flow does not affect the underlying magnetic field itself. As shown
in Fig.~\ref{fig:overview}, the innermost radius ($R_{\mathrm{mi}}$)
of the magnetophere at the equatorial plane ($z=0$) is assigned to
be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
the equaotrial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
respectively. The former value corresponds to the corotation radius
of the accretion disc, and the geometry of the magnetic field/stream
lines is kept constant throghout this paper. The geometry of the magnetosphere
is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.

The magnetic field and the gas stream lines are assumed to have the
following simple form: $r=R_{\mathrm{m}}\sin^{2}\theta$ \citep[see][]{ghosh:1977}
where $r$, and $\theta$ are coordinates of the field point ($p$)
in Fig.~\ref{fig:overview} in spheical coodinates, and $R_{\mathrm{m}}$is
the radial distance to the field line at the equotorial plane ($\theta=\pi/2$).
The range of $R_{\mathrm{m}}$is restricted between $R_{\mathrm{mi}}$
and $R_{\mathrm{mo}}$ as mentioned above. Using the field geometry
above, the conservation of energy, and igoring the rotation of magnetosphere,
the velocity and the density of the accreting gas along the steam
line can be found. See \citet{hartmann:1994} for details.

In all of our models, the temperature structure of the magnetospheric
used by \citet{hartmann:1994} is also adoped here. The temperature
structure was computed assuming a volumetric heating rate which is
proportional to $r^{-3}$, and using the energy balance of the radiative
cooling rate of \citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
Although the temperature structure of the accretion steam could significantly
affect the line source function, for the purpose of the expolaring
the general characteristics of the H$\alpha$ formation, this simple
form is a reasonable assumption.\citet{martin:1996} presented the
self-consistent determination of the thermal structure of the inflowing
gas along the dipole magnetic field, same as the one used here, by
solving the heat equation couple to trate equations for hydrogen.
He found that main heat source is adiabatic compression due to the
convering nature of the flow, and the major contirbutors of the cooling
process are bremsstrahling radiation and line emission from Ca~II
and Mg~II ions. The temerature sturcture of \citet{martin:1996}
qualitaively agrees with that of \citep{hartmann:1994}. The sensitivty
tests of H$\alpha$ on the temperature structure will be presented
later (SPECIFY THE SECTION LATER).

As the infalling gas becomes closer to the stellar surface, it is
decelerates in a strong shock, and heated to $\sim10^{6}\,\mathrm{K}$
(with typical parameters). The X-ray radiation produced in the shock
will be absorbed by the gas located near, and reemitted in optical
and UV radiation (\citealt{koenigl:1991}; \citealt{hartmann:1994}).
This will create hot rings near the stellar surface where the magnetic
field intersects with the surface. For simplicity, the free-falling
kinetic energy is assumed to be thermalized in the radiating layer,
and reemits as blackbody radiation (with a single temerature). With
the parameters of the magnetosphere and the star given above (Table~\ref{tab:std_parameters}),
about $8$~per~cent of the surface is covered by the hot rings,
and its temperature is about $6400\,\mathrm{K}$. If the mass-accretion
rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this
accretion luminosity to the photospheric luminosity is about $0.5$.
The contiuum emission from the hot rings is taken into account when
computing the line profiles.

\subsection{Wind}

\label{sub:wind_jet}

\subsubsection{Colliminated wind model}

JUSTTIFICATION OF USING THIS FORMULATION. BREIFLY MENTIONED THE WORK
DONE BY OTHERS.

Based on the simple model of \citet{appenzeller:2005}, the following
parametrisation of colliminated wind/jet (region 3 in Fig.~\ref{fig:overview})
is adopeted. The wind velocity field, $\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$,
is consist of radial and polar components which depend only on $r$
and $\theta$ respectively. The radial componet $v_{r}\left(r\right)$
is assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
and the azimuthal component $v_{\phi}$ is asuumed to be a constant
fraction ($\gamma$) of the Keplerian velocity for a given distance
($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:

\begin{eqnarray}
\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}+v_{\theta}\hat{\btheta}\label{eq:wind_velocity_def}\end{eqnarray}
where \begin{equation}
v_{r}\left(r\right)=v_{r0}+v_{\infty}\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
\begin{equation}
v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
and \begin{equation}
v_{\theta}\left(r,\theta\right)=v_{\theta0}\,\left(\frac{R_{\mathrm{mo}}}{r}\right)^{\alpha}\frac{\tan\theta}{\left|\tan\theta\right|}\,.\label{eq:wind_velocity_polar_part}\end{equation}
Note that the base of the wind starts at $r=R_{\mathrm{mo}}$, and
the range of the polar angle is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
where $\theta_{\mathrm{disc}}$ is the openning angle of the accretion
disc, to avoid the overlap. $v_{r0}$is the small radial velocity
at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$,
approximately the thermal velocity of hydrogen with $T=7500\,\mathrm{K}$
and $\gamma=0.05$ (\citealt{appenzeller:2005}) are used. The dependency
of $v_{r}$ in polar direction ($\theta=0$) on the values of wind
accerelation parameter $\beta$ is shown in Figure~\ref{fig:wind_vr_rho}.
All other parameters describing the wind are fixed as the standard
values given in Table~\ref{tab:std_parameters}.

Further, the density of the wind is assumed to be axi-symmetric and
separable in $r$ and $\theta$ for computationaly simpliciy, i.e.,

\begin{equation}
\rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)\label{eq:wind_density_def}\end{equation}
 with \begin{equation}
F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
 where $b$ is normally positive even number (for the density symmetric
about the equtotrial plane), and $n$ is the angular normalisation
constant. For $b=0$, the wind is sherically symmetic exept for the
parts dirupted by the accretion disc. The larger the value of $b$,
the higher the degree of the collimination. By integrating equation~\ref{eq:wind_density_theta}
over angles and normalising the integral to $4\pi$, one finds \begin{equation}
n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
 Asumming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
and the mass-flux conserves in time, the radial part of the density
function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
\rho\left(r,\theta\right)=\frac{n\,\cos^{b}\theta\,\dot{M}_{\mathrm{wind}}}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
 For a given mass-accretion rate, the wind mass-loss rate in our typical
model is assined from the ratio of mass-loss to mass-accretion rate
($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
by both observations and magnetohydrodynamical calculations (see e.g.
\citealt{koenigl:2000}).

Figure~\ref{fig:wind_vr_rho} shows the values of $\rho$ in polar
direction ($\theta=0$) for different values of $\beta$ with all
other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{cc}
\includegraphics[%
  clip,
  scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
\includegraphics[%
  clip,
  scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{The dependency of the wind/jet velocity and density structures on the wind accerelation parameter $\beta$. The radial component of the wind/jet velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left. The wind/jet density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is right. The smaller the value of $\beta$, the faster the accerelation of the wind. For the raidus ($r/R_{\mathrm{mo}} < 10$, both velocity and density are sensitive to the value of $\beta$. For all $\beta$ values, the radial velocity of the wind reaches the terminal velocity ($\sim 210\,\kmps$ by  $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity $V_{0}=10\,\kmps$, which approximately corresponds to the thermal velocity of a hydrogen atom at 7500~K,  is used for all $v_{r}$ plots. Beyound $r/R_{\mathrm{mo}}= 100$, little difference is seen in the polar density with diffrent $\beta$ values.}

\label{fig:wind_vr_rho}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Disc-wind model}

GIVE MORE CONVINCING MOTIVIATION FOR USING THIS MODEL. THIS SECTION
MAY BE DELETED.

Alternative to the colliminated wind model, the kinematic disc-wind
mode of \citet{knigge:1995} in which a wind originating from the
surface of the accretion disc with a biconical outflow geometry (Fig.~XXX)
will be presented next. The model was originally developed for describing
the formation of the UV resonance lines in the winds of cataclystic
variable (CV) stars.

\subsection{Accretion disc}

\label{sub:Accretion-disc}

Region 4 in Fig.~\ref{fig:overview}

\subsubsection{Density and velocity}

Although it is possible, in our model, to compute the dust-sublimination
radius and the vertical hydrostatic structure of the accretion disc
self-consistently (assuming the radial dependecy of the mid-plane
density) by using the interative Monte Calro radative transfer technique
(c.f.~\citet{walker:2004}), we find it to be too time consuming
for the purpose of this paper -- understanding the general characteristic
of H$\alpha$ profile shapes hence exploring a large parameter space.
For this reason, we adopt a simple analytical disc model, the steady
$\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
with the inner radius fixed at the inner radius of the magnetosphere
(at equatorial plane). The disc density disribution is given by

\begin{equation}
\rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
 where $w$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
axis, the scale height, the distance from the disc plane, and the
surface density at the mid-plane, respectively. The mid-plane surface
density and the scale height are given as: \begin{equation}
\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{d}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
 where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
and the disc mass respectively.\begin{equation}
h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.\label{eq:scale-height}\end{equation}
 With these parameters, the disc is slightly flared. The inner radius
of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
radius of the magnetosphere at the equaotrial plane), which is approximatly
same as the co-rotating radius of the system with the paramters in
Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
of an object is assumed to be 1/100 of the central mass ($M_{*}$),
and the disc radius ($R_{\mathrm{di}}$) to be 100~au. The velocity
of the gas/dust in the disc is assumed to be Keplerian.

\subsubsection{Dust model}

To calculate the dust scattering and absorption cross section as a
function of wavelength, the optical constants of \citet{draine:1984}
for amorphous carbon grains and \citet{hanner:1988} for silicate
grains are used. The model uses the {}``large grain'' dust model
of \citet{wood:2002} in which the dust grain size distribution is
described by the following function:\begin{equation}
n\left(a\right)da=\left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\, a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da\label{eq:grain-dist-function}\end{equation}
 where $a$ is the grain size restricted between $a_{\mathrm{min}}$
and $a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$
are the terms set by requiring the grains to completely deplete a
solar abundance carbon and silicon. The parameters adopted in our
model are: $C_{\mathrm{C}}=1.32\times10^{-17}$, $C_{\mathrm{Si}}=1.05\times10^{-17}$,
$p=3.0$, $q=0.6$, $a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
$a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds
to Model~1 of the dust model used by \citet{wood:2002}. See also
their Fig.~3 The relative number of each grain is assumed to be that
of solar abundance, C/H$\sim3.5\times10^{-4}$ \citep{anders:1989}
and Si/H$\sim3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.

\section{Radiative transfer model}

\label{sec:radiative-transfer-model}

We have extended the TORUS radiative transfer code (\citealt{harries:2000};
\citealt{kurosawa:2004a}; \citealt{symington:2005}) to compute the
H$\alpha$ profiles from pre-main-sequence stars which are surrounded
by one or more of the followings: the magnetospherical accretion flow,
the out-flowing colliminated wind, and the accreation disc. Previously
in \citet{symington:2005}, the model used in the three-dimentional
(3-D) adaptive mesh refinement (AMR) to inverstigate the line variability
mainly associated with roational motion of complex geometrical configurations
of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
modefied the code to handle the two-dimentional (2-D) density distribution,
and restricted our models to be axi-symmetric. It was done so in order
to enable us to explore rather large number of parameter spaces (c.f.~section~\ref{sec:model-configuration}).
Note that the velocity field is still in 3-D -- the third component
can be calculated by using the symmetry for a given value of azimutal
angle. The examples of how the AMR grid for the purpose of the radiative
transfer is constructed are presented in e.g. \citet{wolf:1999},
\citet{kurosawa:2001a} and \citet{steinacker:2003} .

The computation of the H$\alpha$ is devided in two parts: 1.~the
source function calculation and 2.~the observed flux/profile calulcation.
In the first process, we have utilized the method by \citet{klein:1978}
(see also \citealt{rybicki:1978}; \citet{hartmann:1994}) in which
the Sobolev approximation method is applied. The population of the
bound states of hydrogen are assumed to be in statistical equilibrium,
and the gas to be in radiative equilibrium. Our hydrogen atom model
consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
for details. (AND MORE..)

To compute the observed line profile, the Monte Calro radiative transfer
method (e.g. \citealt{hillier:1991}) using the Soblev escape-probabiliy
can be used when I.~a large velocity gradiant is present in the gas
flow, and II.~the intrinsic line width is negleible compared to the
Doppler broadeing of the line. In our earlier models (\citealt{harries:2000};
\citealt{symington:2005}), this method was used to compute the line
profiles since the condition I and II are resonably satisfied. However,
as noted and demonstrated by \citet{muzerolle:2001}, even with a
moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
Stark broadening becomes important in the optically thick H$\alpha$
line. \citet{muzerolle:2001} (MORE REF HERE) also pointed out that
the observed H$\alpha$profiles from CTTS typically have the wings
extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
\citet{reipurth:1996}) which cannot be explained by the infall velocity
of the gas along the magneosphere.

To implement the broadening meachanism, two modedifications to our
previous model (\citealt{symington:2005}) are necessary. First, the
emission and absorption profiles must be replaced by a Voigt profle
which is defined as: \begin{equation}
H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
 where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$, $y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$,
and $y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$ (c.f. \citealt{mihalas:1978}).
$\nu_{0}$ is the line centre frequency, and $\Delta\nu_{\mathrm{D}}$
is the Doppler line width of hydrogen atom (due to its thermal motion)
which is given by $\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
where $m_{\mathrm{H}}$ is the mass of a hydrogen atom. The damping
constant $\Gamma$, which depends on the physical condition of the
gas, is parameterised by \citet*{vernazza:1973} as follows:

\begin{eqnarray}
\Gamma & = & C_{\mathrm{rad}}+C_{\mathrm{vdW}}\left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)\left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
 &  & +\, C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}\label{eq:dampimg_constant_def}\end{eqnarray}
 where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
neutral hydrogens and that of free electrons. Also, $C_{\mathrm{rad}}$,
$C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are natural broadening,
van der Waals broadening, and linear Stark broadening constants respectively.
We simply adopt this parameterization along with the values of broadening
constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and $C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.
In terms of level populations and the Voigt profile, the line opacity
for the transition $i\rightarrow j$ can be written as: \begin{equation}
\chi_{l}=\frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}\left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)\label{eq:line_opacity}\end{equation}
 where $f_{ij}$, $n_{i}$, $n_{j}$, $g_{i}$and $g_{j}$ are the
oscillator strength, the population of $i$-th level, the population
of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
of the $j$-th level respectively. $m_{e}$and $e$ are the electron
mass and charge (c.f. \citealt{mihalas:1978}).

The second modefication in our model is the replacement of the method
of solving the formal solution from the Monte Calro radiative transfer
method with Sobolev approximation to the direct integration method.
Similarly to the notation used by \citet{muzerolle:2001}, we specify
the cylindical coordinates $\left(p,\, q,\, t\right)$ which is the
original stellar coordinate system $\left(\rho,\,\phi,\, z\right)$
rotated (around $y$ axis) by the inclination of the line of sight,
i.e. the $t$-axis coinsides with the line of sight. The observed
flux ($F_{\nu}$) is given by: \begin{equation}
F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
where $d$, $p_{\mathrm{max}}$, and $I_{\nu}$ are the distance to
an observer, the maximum extent to the model space in the projected
(rotated) plane, and the specific intensity ($I_{\nu}$) in the direction
on observer at the outer boundary. For a given ray along $t$, the
specific intensity is given by:\begin{equation}
I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{-\infty}^{t_{0}}\eta_{\nu}\left(t\right)\, e^{-\tau\left(t\right)}\mathrm{d}t\label{eq:formal_sol_integral}\end{equation}
 where $I_{0}$ and $\eta_{\nu}$ are the intensity at the boundary
on the opposite to the observer and the emissivity of the stellar
atmosphere/wind at a frequency $\nu$. For a ray which intersects
with the stellar core, $I_{0}$ is computed from the stellar stompshere
mode of \citet{kurucz:1979} as descibed in section~\ref{sub:Contiuum-Source},
and $I_{0}=0$ otherwise. The initial position of each ray is assigned
to be at the center of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
The code excution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
where $n_{p}$ and $n_{q}$ are the number of cylindical radial and
angluar points for the flux integration, and $n_{\nu}$is the number
of frequency points. In the models presented in the next (section~\ref{sec:Results}),
$n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
otherwise. The linearliy spaced radial grid is used for the area where
the ray intersects with magnetpshere, and the logarithmically spaced
grid is used for the wind and the accretion disc regions.

The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
is defined as: \[
\tau\left(t\right)\equiv\int_{-\infty}^{t}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
 where $\chi_{\nu}$ is the opacity of media the ray passes through.
$\tau_{\infty}$ is the total optical depth measured from the initial
ray point to the observer (or to the outer boundary closer to the
observer). Initially, the optical depth segments $\mathrm{d\tau}$
are computed at the intersections of a ray with the original AMR grid
in which the opacity and emissivity infomation are stored. For high
opticale depth models, additional points are inserted between the
original points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$
values are interpolated to those points to ensure $\mathrm{d}\tau<0.05$
for the all ray segments.

For a point in the magnetosphere and the wind flows, the emissivity
and the opacity of the media are given as:\begin{equation}
\left\{ \begin{array}{rcl}
\eta_{\nu} & = & \eta_{\mathrm{c}}^{\mathrm{H}}+\eta_{l}^{\mathrm{H}}\\
\chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}+\sigma_{\mathrm{es}}\end{array}\right.\label{eq:emiss_opa_gas}\end{equation}
where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$
are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the contiuum,
line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
electron scattering opacity. Similarly, for a point in the accretion
disc,

\begin{equation}
\left\{ \begin{array}{rcl}
\eta_{\nu} & = & 0\\
\chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}+\kappa_{\mathrm{sca}}^{\mathrm{dust}}\end{array}\right.\label{eq:emiss_opa_dust}\end{equation}
 where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and $\kappa_{\mathrm{sca}}^{\mathrm{dust}}$
are the dust absorption, and scattering opacity which are calculated
using the dust property described in section~\ref{eq:grain-dist-function}.
For computational simplicity, we assumed that the dust emissivity
is zero. Since the disc mass of CTTS are rather small ($\sim0.1\,\mathrm{M_{\sun}}$)
and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
contribution at H$\alpha$ wavelength is expected to be neglegible
(e.g.~\citealt{chiang:1997}). The scattering flux by the accretion
may become important for H$\alpha$ for the edge-on ($i\sim90^{\circ}$)
cases in which the disc obscures the stellar surface -- the main source
of contiuum flux. We examine this effect later in section~\ref{sub:model-acc-disc-wind}.

\section{Results}

\label{sec:Results}

\subsection{Magnetosphere}

\label{sub:model-acc}

Using the standard parameters (Table~\ref{tab:std_parameters}) for
the central star and the magentosphere, we examine the dependency
of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
is computed from the avilable kinetic energy of the free-falling gas
as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
of their models. The accretion luminosity ($L_{\mathrm{acc}}$) of
models with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
is about a half of the total luminosity (without the hot ring) of
the star, and $L_{\mathrm{acc}}$is proportional to $\dot{M}_{\mathrm{acc}}$.
The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are
similar to that of \citet{muzerolle:2001}. In general, the line strength
becomes weaker as the accretion rate and the temperature become smaller.
The red-shifted absorption becomes less visible for higher accretion
rate and temperature models in which the flux in the damping wings
become important. Figure~\ref{fig:broadening} shows an example of
the effect of the boradening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
due to the damping constants as described in section~\ref{sec:radiative-transfer-model}.
Although the maximum flux of the model with the broadening is almost
identical to that of the model with no damping constant ($\Gamma=0$),
a significant increase of the line flux in both red and blue wings
of seen in the model with broadening. A weak red-shifted absorption
component (which is a signiture of the magnetospherical accretion)
is weakened or eliminated by the flux in broadened wing.

Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown
in Figure~\ref{fig:atlas_acc_models}. About a half of the models
shown the figure agree with the observed EW values of H$\alpha$ from
30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
ranges from $\sim3$~\AA\, to $\sim160$~\AA, and the mean to
be $\sim55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
and for some models the EWs are negative. Since the target selection
criteria of \citet{alencar:2000} is not stated in their paper, we
can not conclude that these low $\dot{M}_{\mathrm{acc}}$models disagree
with the observation. \citet{reipurth:1996}, who measured the EW
of 43 TTS and found similar distribution of EW values, mentioned that
their EW measurements are underrepresenting real samples since the
selection of the targerts are based on the strong H$\alpha$ emission
in H$\alpha$ surveys.

The dependency of the profile on the inclination angle ($i$) is demonstrated
in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
paramters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
The figure show that the peak (normalized) flux decrease as the inclination
angle increases. Similarly, the equivalent width also decreases as
the inclination increases. Because of the geometry of the magnsepsherical
accretion (c.f. Figure~\ref{fig:overview}) and of the presence of
the gas with the highest velocity close to the stellar surface, the
highest red-shifted line-of-sight velocity is visible only at the
high incination angles. This explains the wider appearence of the
profile with $i=80^{\circ}$compared to the relatively narrow line
appearence of the profile with $i=10^{\circ}$. Although not show
here, a similar depdency on the inclination angle is found for the
models with different temperatures ($T_{\mathrm{max}}=6500$, $8500$,
$9500\,\mathrm{K}$).

As seen in the models of \citet{hartmann:1994} and \citet{muzerolle:2001},
our models also show the blue-shifted peak and the blue-ward asymmetry
caused by the occultation of the accretion flow by the equotrial disc
and the stellar disc. On the hand, \citealt{alencar:2000} (see their
Fig.~9) found a substential fraction of the observed H$\alpha$ profiles
also shows the {}``red-shifted'' peak, and the P~Cygni profiles
which can not be explained by the magnetospherical accretion model
alone. In addition, a recent study by \citet{appenzeller:2005} showed
that the equivalent width of H$\alpha$ increases as the inclination
angle increases. Our model with the magnetospherical accreation flow
clearly disagrees with their finding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/atlas_ha_i55_acc_model_new3.eps}

\end{center}

\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M_\mathrm{acc}}$) and temperature ($T_{\mathrm{max}}$). The profiles are computed using only magnetospherical accretion flow (i.e. no wind/jet).  All the profiles are computed using the parameters of the 'standard' model (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the mass accretion rate (indicated by the values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from left to right. The profiles are similar to those of \citet{muzerolle:2001}, available on-line (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html). }

\label{fig:atlas_acc_models}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}

\begin{center}

\begin{tabular}{cccc}
\hline 
$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
&
$\dot{M}_{\mathrm{acc}}$ ~$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
\tabularnewline
&
$10^{-7}$&
$10^{-8}$&
$10^{-9}$\tabularnewline
\hline 
$6500$&
$17.9$&
$0.1$&
$0.0$\tabularnewline
$7500$&
$25.2$&
$-0.9$&
$-0.5$\tabularnewline
$8500$&
$68.3$&
$6.5$&
$-0.7$\tabularnewline
$9500$&
$98.6$&
$52.4$&
$1.3$\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary of H$\alpha$ equivalent widths from the magnetospherical accretion flow models show in Figure~\ref{fig:atlas_acc_models}.}

\label{tab:ha_ew_acc_models}

\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/broadening.eps}

\end{center}

\caption{Effect of the line broadening for H$\alpha$. The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the one with no damping constant, $\Gamma=0$ (dashed).  Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}. The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant. The broaded wings extend to $\sim \pm 900 \kmps$.  The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.  }

\label{fig:broadening}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.45]{figures/acc_inc_effect.eps}

\end{center}

\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).  The profiles are computed with the magneospherical accretion flow using the standard parameters given in Table~\ref{tab:std_parameters} and $T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$ respectively. As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.  Similar dependency is seen in the models with $T_{\mathrm{max}}=6500, 8500, 9500$~K (not shown here). }

\label{fig:acc_inclination_effect}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Collimated Wind}

\label{sub:model-wind}

As mentioned in earlier, the magnetopsherical accretion flow model
alone cannot explain some of the feartures seen in observations. As
an alternative model, we now examine formation of H$\alpha$ in a
simple collimated wind as described in section \ref{sub:wind_jet}.
The basic wind model parameters introduced earlier are $\gamma$,
$\beta$, $v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
and $\dot{M}_{\mathrm{wind}}$. To minimize the number of parameters
to be explored, we initially adopte $\gamma=0.05$, $v_{\infty}=200\,\kmps$
\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
Futher, the angular extent of the wind is assumed to be close to the
edge of the accretion disc, i.e. $\theta_{\mathrm{wind}}=80^{\circ}$;
however, in this section, a simple optically-thick and geometrically-thin
(i.e. opaque and zero-thickness) disc instead of the standard $\alpha$-disc
(section~\ref{sub:Accretion-disc}) is used in all models for speed.
The effect of replacing the geometrically thin disc with the $\alpha$-disc
will be discussed later in this section. The degree of collimination
is initially chosen to be $b=4$, i.e. the ratio of the density in
polar direction to the density at the edge of the wind closest to
the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
for given radii. With these parameters kept constant, we examine the
characterstics of H$\alpha$ profiles, as a function of the wind accereation
paramter $\beta$ and the isothermal wind temperature $T_{\mathrm{wind}}$.
Dependency on the other parameters will be discussed later in this
section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=0.9]{figures/atlas_ha_i55_wind_model.eps}

\end{center}

\caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$). The profiles are computed with only wind/jet (no magnetospherical accretion flow). The parameters of the 'standard' model (Table~\ref{tab:std_parameters}) are used. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively. The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the wind accerelation rate increases from left to right. The P~Cygni profile are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow accerelation) models.  The postion of the absorption the component moves toward the line centre as $\beta$ increases. The effect of line broadening becomes more prominant for higher $T_\mathrm{wind}$ and higher $\beta$ models.}

\label{fig:atlas_wind_model}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results are shown in Figure~\ref{fig:atlas_wind_model}. The
P~Cygni profile are seen only in the models with lower $T_{\mathrm{wind}}$
and $\beta$ (colder and faster accerelation wind). As the value of
$\beta$ increases, the postion of the blue-shifted absorption component
moves toward the line centre. For the slowest wind accerelation models
($\beta=4.0$), the absorption components appear to be located at
the line centre, giving the appearence of the double-peak emission
profile. The line strength is very senstive to the temperature of
the wind. Although the line should be also sensitive to the temperature
structure of the wind itself, determination of a self-consistent wind
temperature is beyound the scope of this paper. Readers are refered
to \citet{hartmann:1982} in which the wind temperature structure
is determined by balancing the radiative cooling rate (assuming optically
thin) with the MHD wave heating rate.

The effect of line broadening becomes more prominant for higher $T_{\mathrm{wind}}$
and higher $\beta$ models. Unlike the magnetospherical accretion
only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
profiles are not seen here. Interestingly, in some models (e.g. $T_{\mathrm{wind}}=9000\,\mathrm{K}$
and $\beta=1.0$ model), the absorption componet is present at slightly
red-ward of the line centre, causing the blue-ward asymmetry seen
in the magnetospherical accretion models. The blue-ward asymetry are
caused by: 1. the accretion disc placed at the equotorial plane and
the finited-size steller disc blocking a part of the line emission
region moving away from an observer, 2.~the much larger optical depth
for the line emitted from the opposite side of the observer where
the gas is moving away from the observer. Because of the broad wings
of the Voigt profile, the line photon intereacts with the gas with
much wider range of the projected velocity space.

The dependency of the profile on the wind anisotoropy parameter $b$
is demonstrated in Figure~\ref{fig:effect_wind_b_param}. The line
peak closer to the line centre and the profile becomes slightly more
symmetric around the line centre for the isotropic ($b=0$) compared
to the cases with the colliminated wind ($b=4$). The P~Cygni profile
feature become prominant for the spherical wind models (especially
in $\beta=0.5$ model) because the collumn density of along the line
of a sight of the observer at a medium inclination angle ($i=55^{\circ}$)
increases as the wind becomes more spherical for a given value of
the wind mass-loss rate.

Next, we examine the effect of the size of the inner radius of the
disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_thin_disc}
shows the wind emission profile computed with and without the equotorial
accretion disc. The latter can be also considered as a model with
a large inner radius of the accretion disc in which none of the wind
emission region is not blocked provided the inclination is moderate.
The profile shapes of the models are very similar to each other, but
the one without the accretion disc is slightly more symmetric than
the other. As one expects, the line equivalent width of the model
without the disc is about twice of the model with the disc. Interestingly,
the blueward asymmetry is present also in the profile computed without
the disc. This is mainly caused by the occultaion of a part of emission
region by the steller disc and the fact that the wind (density distribution)
is asymmetric. The H$\alpha$ image (project in the plane of the observer
at the location of the star) for the model with the disc (middle panel)
and that for the model without (right plane) are also shown in the
same figure. The images weere computed with a fast wind accereation
rate ($\beta=0.5$). The extent of the line emission is smaller ($\sim0.2\,\mathrm{AU}$
or $\sim20\, R_{*}$) compared to the spectro-astrometric observations
of \citet{takami:2003} for RU~Lup and CS Cha which have 1--5 AU
scale outflows%
\footnote{\citet{takami:2003} also showed that some objects (e.g~Z CMa and
AS~353A) show the outflows of larger scale ($>50\,\mathrm{AU}$)
which could be formed by shocks rather than MHD-wave heating (e.g.
\citealt{hartmann:1982}) or X-ray heating (e.g.~\citealt{shang:2002}). %
}; however, if a slower wind acceration rate ( $\beta=4$) is the emission
region become larger slightly ($\sim0.4$~AU).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{cc}
\includegraphics[%
  clip,
  scale=0.45]{figures/wind_b_effect.eps}&
\includegraphics[%
  clip,
  scale=0.45]{figures/windonly_B_effect.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{The effect of wind collimation. The dependecy of the line profiles on the wind anisotropy parameter $b$ for the models with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$  is shown on left, and that with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 1.0\right)$ on right. All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.  The degree of the blue-ward asymmetry of the profiles is slightly lower for the spherical (isotroptic) wind model ($b=0$, dashed) compared to the collimated wind (anisotoropic) wind models ($b=4$, solid).  The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind. }

\label{fig:effect_wind_b_param}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\begin{tabular}{ccc}
\includegraphics[%
  clip,
  scale=0.3]{figures/disc_nodisc_compare.eps}&
\includegraphics[%
  scale=0.3,
  angle=270,
  origin=lt]{figures/wind_thindisc.eps}&
\includegraphics[%
  scale=0.3,
  angle=270,
  origin=lt]{figures/wind_nodisc.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{Comparison of of the wind model with and without the optically-thick and geometrically-thin disc.  The latter can be also equivalent to a model with a large inner radius of the accretion disc in which none of the wind emission region is not blocked provided the inclination is moderate. The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used). The line profile of the model with the disc (solid) is similar to the model without the disc (dashed), but the latter is slightly more symmetric than the former. The line equivalent width of the model without the disc is about 2 times that of the model with the disc. The blueward asymmetry is present also in the profile computed without the disc. The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown. The image flux is computed by integrating the specific flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$. The flux is in an arbitrary units and in logarithmic (base $10$) scale. }

\label{fig:effect_thin_disc}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Magnetosphere $+$ wind}

\label{sub:model-acc-wind}

Next, we examine the characteristics of the line profiles arising
from the combination of the magnetospherical accretion flow and the
wind. For simplicity, we fix the parameters for the magnetosphere
($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
as in Figure~\ref{fig:atlas_acc_models}), and use the constant wind
mass-loss rate $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$). Figure~\ref{fig:atlas_wind_acc_model}
shows the results for $i=55^{\circ}$ and the same combinations of
$T_{\mathrm{wind}}$ and $\beta$ used in section~\ref{sub:model-acc-wind}
(Figure~\ref{fig:atlas_wind_model}).

While the emission from the magnetosphere dominates for the models
with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation
and the colder wind models), the emission from the wind dominates
for the models with larger $\beta$ and $T_{\mathrm{wind}}$ (the
slower accerelation and the hotter models). The P~Cygni profile feature
becomes less prominant in some of the models because the additional
emission from the magnetosphere extending in the wings. In most of
the cases, the profiles are understood as a simple sum of the magnetospherilcal
component and the wind component.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=0.9]{figures/atlas_ha_i55_wind_acc_model.eps}

\end{center}

\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ as in Figure~\ref{fig:atlas_acc_models}). While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{wind}}$  (the slower accerelation and the hotter models). The P~Cygni profile feature becomes less prominant in some of the models because of the extra emission from the magnetosphere extends in the wings.}

\label{fig:atlas_wind_acc_model}

\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Magentosphere $+$ disc $+$ wind}

\label{sub:model-acc-disc-wind}

\begin{itemize}
\item Flux contribution by scattering of photon by disc?
\end{itemize}

\subsection{Summary}

\section{Discussion}

\label{sec:Discussion}

\subsection{Classification scheme proposed by Reipurth et. al (1996)}

\citet{reipurth:1996}proposed the two-dimentional classification
of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
stars. Their classification scheme contains four classes (I, II, III
and IV) differenciated by the ratio of the secondary-to-primary emission
components in the profiles. Each classes are devided into two sub-classes
(B and R) which depends whether the absorption componet is on the
blue or red side. Readers are refered to Fig.~4 of their paper. Figure~\ref{fig:atlas_reipurth}
shows the sample profiles which are classified according to the definition
of \citet{reipurth:1996}. The corresponding model parameters are
given in Table~\ref{tab:classification}. As we can see from this
figure, the combinatioin of the wind, magnetospherical accretion,
and accretion disc can reasonably reproduce all the classes of the
profiles seen in observations.

Within the parameter space covered, we find it is difficult to produce
Type I type profile, which is very symmetric around the line centre
and without any absorption feature, if the wind component is added
in the model. Type II-B are

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}

\begin{center}

\includegraphics[%
  clip,
  scale=0.65]{figures/atlas_reipurth_like.eps}

\end{center}

\caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}. The combination of magnetospherical accretion flow, the accretion disc, and the colliminated wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.  The model parameters and short comments are summarised in Table~\ref{tab:classification}. The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.  }

\label{fig:atlas_reipurth}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table*}

\begin{center}

\begin{tabular}{llllllll}
\hline 
&
$i$&
$\dot{M}_{\mathrm{acc}}$&
$T_{\mathrm{max}}$&
$\dot{M}_{\mathrm{wind}}$&
$T_{\mathrm{wind}}$&
$\beta$&
Comment\tabularnewline
Class&
$\left(\mathrm{deg.}\right)$&
$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
$\left(10^{3}\,\mathrm{K}\right)$&
$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
$\left(10^{3}\,\mathrm{K}\right)$&
$\left(-\right)$&
\tabularnewline
\hline 
I&
$55$&
$10^{-7}$&
$7.5$&
$-$&
$-$&
$-$&
Accretion dominated possibly without the wind at a mid inclination.\tabularnewline
II-B&
$10$&
$10^{-7}$&
$7.5$&
$10^{-8}$&
$9.0$&
$1.0$&
Accretion and wind, mid wind accerelation rate, low inclination\tabularnewline
III-B&
$10$&
$10^{-7}$&
$7.5$&
$10^{-8}$&
$8.0$&
$2.0$&
Accretion and wind, with slow wind accerelation rate, low inclination\tabularnewline
IV-B&
$55$&
$-$&
$-$&
$10^{-8}$&
$8.0$&
$0.5$&
Accretion dominated (low accretion rate), mid inclination \tabularnewline
II-R&
$55$&
$10^{-7}$&
$7.5$&
$10^{-8}$&
$9.0$&
$2.0$&
Wind dominated, with fast wind accerelation rate, mid inclination\tabularnewline
III-R&
$80$&
$10^{-7}$&
$7.5$&
$10^{-8}$&
$9.0$&
$1.0$&
Wind dominated, slow wind acceralation rate, high inclination \tabularnewline
IV-R&
$55$&
$10^{-9}$&
$9.5$&
$-$&
$-$&
$-$&
Accreetion dominated possibly without the wind at a mid inclination.\tabularnewline
\hline
\end{tabular}

\end{center}

\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.}

\label{tab:classification}

\end{table*}

\subsection{Comparisons with observations}

For a demonstrative purpose, we performed preliminary model fit of
H$\alpha$ observarions

\begin{itemize}
\item other possible model? Better wind model?
\item Any other bussiness?
\end{itemize}

\section{Conclusions}

\label{sec:Conclusions}

We presented the detailed study of the H$\alpha$ formation from the
circumstealler material of classical T~Tauri stars. AND MORE.

Future studies include:

\begin{enumerate}
\item Improvement of the wind model. Temperature structure estimate by Hartmann()
Alancar's paper. Disc-wind model of Branford and ...
\item Try it with MHD model.
\item Include the scattering flux term although this requires $N_{\phi}\times N_{\theta}$
more times to compute a profile. 
\item Polarization study to explore the geometry and the rotation of the
disc. 
\item Gas in the accretion disc (inner most part and the outer layer of
the disc).
\item Variability study using a 3D model.
\end{enumerate}
\section*{Acknowledgements}

RK is supported by PPARC standard grand PPA/G/S/2001/00081.

%

%

%

%----------------------------------------------------

% Bibliography follows here.

%-----------------------------------------------------

%

%

%

\bibliographystyle{mn}

\bibliography{mnras}

%

\label{lastpage}
\end{document}

### 2005-11-29 TTau_Halpha/plots/example.c

@@ -1,0 +1,73 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <unistd.h>
+#include <grace_np.h>
+
+#ifndef EXIT_SUCCESS
+#  define EXIT_SUCCESS 0
+#endif
+
+#ifndef EXIT_FAILURE
+#  define EXIT_FAILURE -1
+#endif
+
+void my_error_function(const char *msg)
+{
+  fprintf(stderr, "library message: \"%s\"\n", msg);
+}
+
+int
+main(int argc, char* argv[])
+{
+  int i;
+
+  GraceRegisterErrorFunction(my_error_function);
+
+  /* Start Grace with a buffer size of 2048 and open the pipe */
+  if (GraceOpen(2048) == -1) {
+    fprintf(stderr, "Can't run Grace. \n");
+    exit(EXIT_FAILURE);
+  }
+    
+  /* Send some initialization commands to Grace */
+  GracePrintf("world xmax 100");
+  GracePrintf("world ymax 10000");
+  GracePrintf("xaxis tick major 20");
+  GracePrintf("xaxis tick minor 10");
+  GracePrintf("yaxis tick major 2000");
+  GracePrintf("yaxis tick minor 1000");
+  GracePrintf("s0 on");
+  GracePrintf("s0 symbol 1");
+  GracePrintf("s0 symbol size 0.3");
+  GracePrintf("s0 symbol fill pattern 1");
+  GracePrintf("s1 on");
+  GracePrintf("s1 symbol 1");
+  GracePrintf("s1 symbol size 0.3");
+  GracePrintf("s1 symbol fill pattern 1");
+
+  /* Display sample data */
+  for (i = 1; i <= 100 && GraceIsOpen(); i++) {
+    GracePrintf("g0.s0 point %d, %d", i, i);
+    GracePrintf("g0.s1 point %d, %d", i, i * i);
+    /* Update the Grace display after every ten steps */
+    if (i % 10 == 0) {
+      GracePrintf("redraw");
+      /* Wait a second, just to simulate some time needed for
+	 calculations. Your real application shouldn't wait. */
+      sleep(1);
+    }
+  }
+
+  if (GraceIsOpen()) {
+    /* Tell Grace to save the data */
+    GracePrintf("saveall \"sample.agr\"");
+
+    /* Flush the output buffer and close Grace */
+    GraceClose();
+
+    /* We are done */
+    exit(EXIT_SUCCESS);
+  } else {
+    exit(EXIT_FAILURE);
+  }
+}

### 2005-11-29 TTau_Halpha/plots/plot_discwind.f90

@@ -1,0 +1,95 @@
+program plot_discwind
+
+  use subs
+
+  implicit none
+
+  real*8, parameter :: pi =3.141592654d0
+  ! Parameters 
+  real*8 :: Rmin, Rmax, Tmax, alpha, gamma, d, Mstar
+
+  real*8 :: R_min, R_max
+  integer, parameter :: nl = 200
+  integer, parameter :: nbeta = 4
+  real*8 :: beta(nbeta), rho0(nbeta)
+  real*8 :: l(nl), lmin, lmax, log10_lmin, log10_lmax, log10_dl
+  real*8 :: density(nl,nbeta)
+  integer :: i, j
+  real*8 :: wi, f, AU
+
+  ! setting up the parameters====================
+  Rmin = 43.0d0  ! [10^10 cm]
+  Rmax = 1500d0  ! [10^10 cm]
+  Tmax = 1600d0  ! [K]
+  alpha = 0.33   ! [-]
+  gamma = -1.15  ! [-]
+  Mstar = 2.0d0  ! [Msun]
+  d = 300.d0     ! [10^10cm]
+  f = 2.0d0
+  AU = 1.5e3     ! [10^10 cm]  1 AU
+  !==============================================
+
+  ! set up L values
+  lmin = 1.0d-3           ! [10^10 cm]
+!  lmax = 36.0d0*1000.d0  ! [10^10 cm]
+  lmax = 150000.d0  ! [10^10 cm]
+  log10_lmin = LOG10(lmin); log10_lmax = LOG10(lmax)
+  log10_dl = (log10_lmax-log10_lmin)/dble(nl-1)
+
+  do i = 1, nl
+     l(i) = log10_lmin + log10_dl*dble(i-1)
+     l(i) = 10.0d0**l(i)
+  end do
+
+  ! set up the values of beta
+  beta(1) = 0.2
+  beta(2) = 0.5
+  beta(3) = 1.0
+  beta(4) = 2.0
+
+
+  ! now compute the density
+  wi = (Rmin + Rmax)/2.0d0  ! mid point on the disc
+  
+  do j = 1, nbeta
+     do i = 1, nl
+        density(i,j) = discwind_density(l(i), wi, f, Rmin, Rmax, Tmax, alpha, gamma, d, beta(j), Mstar)
+     end do
+  end do
+
+
+  ! normalizing density
+  do j = 1, nbeta     
[…]

### 2005-11-29 TTau_Halpha/plots/plot_rho.f90

@@ -1,0 +1,146 @@
+program plot_rho
+
+  implicit none
+
+  real*8, parameter :: pi =3.141592654d0
+  ! Parameters 
+  real*8 :: m, theta_wind, Mdot_wind, V0, Vinf, R_mo, beta, r_star
+
+  real*8 :: R_min, R_max
+  integer, parameter :: nr = 200
+  integer, parameter :: nt = 3 
+  real*8 :: r(nr), rmin, rmax, log10_rmin, log10_rmax, log10_dr
+  real*8 :: theta(nt)
+  real*8 :: density(nr,nt), rho0, r_cm, gamma
+  integer :: i, j
+!  real*8, parameter :: G = 6.67259d-8 ! in cgs
+!  real*8 :: M_star
+
+  ! setup parameters
+  R_star = 2.0d0  ! [R_sun]
+  m = 2.0d0                           ! [-]
+  theta_wind = 80.0d0 * (pi/180.0d0)  ! [rad]
+  Mdot_wind  = 1.0d-8 * 1.98892d33 / 31536000.0d0  ! [grams/s]
+!  V0 = 20.0       * 1.0d5   ! [cm/s]
+!  V0 = 2.0       * 1.0d5   ! [cm/s]
+  V0 = 10.0       * 1.0d5   ! [cm/s]
+  Vinf = 200.0d0  * 1.0d5   ! [cm/s]
+  R_mo = 3.0d0*R_star * 6.960d10  ! [cm]
+  beta = 2.0d0
+!  gamma = 0.05
+!  M_star = 2.0 * 1.9891d33  !  [g]
+
+  ! setting up r and theta
+  rmin = R_mo
+  rmax = 1000.0d0*R_mo
+  log10_rmin = log10(rmin); log10_rmax = log10(rmax)
+  log10_dr = (log10_rmax-log10_rmin)/dble(nr-1)
+  do i = 1, nr 
+     r(i) = log10_rmin + log10_dr*(i-1)
+     r(i) = 10.0d0 ** r(i)
+  end do
+
+  theta(1) = 0.0d0
+  theta(2) = pi/3.0
+  theta(3) = theta_wind - theta_wind/100.0d0  
+
+  do j = 1, nt
+     do i = 1, nr
+        density(i,j) = rho(r(i), theta(j), m, theta_wind, Mdot_wind, &
+             V0, Vinf, R_mo, beta) ! [g/cm^2]
+     end do
+  end do
+
[…]

### 2005-11-29 TTau_Halpha/plots/subs.f90

@@ -1,0 +1,237 @@
+module subs
+  ! used for plot_discwind
+
+  public:: &
+       mdot_on_disc, &
+       temperature_disc, &
+       speed_of_sound, &
+       escape_velocity, &
+       Vp, &
+       Vphi, &
+       discwind_density
+  
+
+
+contains
+  
+  !
+  !
+  ! Mass loss rate per unit are on the disc surface [g/s/cm^2]
+  function mdot_on_disc(w, Rmin, Rmax, alpha, gamma) RESULT(out)
+    implicit none
+    real*8 :: out
+    !
+    real*8, intent(in) :: w      ! [10^10cm]  cylindical diatance from the center
+    real*8, intent(in) :: Rmin   ! [10^10 cm]
+    real*8, intent(in) :: Rmax   ! [10^10 cm]
+    real*8, intent(in) :: alpha  ! power law index
+    real*8, intent(in) :: gamma  ! power law index
+    !
+    real*8 :: Mdot, R_max, R_min, R, delta, fac, p
+    real*8, parameter ::  pi = 3.1415927d0
+    
+    delta =4.0d0*alpha*gamma
+    p = delta + 2.0d0
+    ! converting everthing in cgs
+    R = w*1.d10  !  [cm]
+    R_min = Rmin * 1.0d10 ! converting from [10^10cm] to [cm]
+    R_max = Rmax * 1.0d10 ! converting from [10^10cm] to [cm]
+    Mdot = Mdot*1.989d33/3.1536d07   ! Converting from [Msun/yr] to [g/s]
+
+    fac = p / ( R_max**p - R_min**p )
+
+    ! just checking
+    if (fac < 0.0d0) then
+       write(*,*) "Error:: fac <0.0 in [discwind_class::mdot_on_disc]."
+       stop
+    end if
+
+    out = Mdot*(R**delta)*fac/(4.0d0*pi)   ! [g/s/cm^2]
+
+  end function mdot_on_disc
+
+
+  !
+  ! disc temperature (at z=0) power law  [K]
+  ! Temperature : T(R)= Tmax*(R/Rmin)^gamma where R is the distance from the center
+  ! (private)
+  function temperature_disc(R, Rmin, Tmax, gamma) RESULT(out)
+    implicit none
+    real*8 :: out
+    real*8, intent(in) :: R      ! [10^10cm] of distance from z-axis
+    real*8, intent(in) :: Rmin   ! [10^10cm] the inner radius of the disc
[…]

### 2006-01-03 TTau_Halpha/kurosawa.tex
Fixed typos and grammatical errors.  (Ryuichi)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@609 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \documentclass[oneside,english,useAMS, usenatbib]{mn2e}
-%\usepackage[T1]{fontenc}
-%\usepackage[latin1]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[latin1]{inputenc}
 \setcounter{tocdepth}{3}
@@
 \begin{document}
-\title[On H-$\alpha$ formation of T Tauri stars]{On formation of H-$\alpha$ from classical T Tauri stars: the disc, wind, and magnetospheric-accretion hybrid model}
-
-\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries and Neil H. Symington\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}
+\title[On the formation of H$\alpha$ around classical T Tauri stars]{On the formation of H$\alpha$ around classical T Tauri stars}
+
+\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa$^1$\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries$^1$ and Neil H. Symington$^2$\\
+$^1$School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL. \\
+$^2$School of Physics and Astronomy, University of St. Andrews, North Haugh, St. Andrews, Fife, KY16 9SS.}
 
@@
 
-We present disc--wind--magnetosphere hybrid radiative transfer models
-for classical T~Tauri stars, and investigate the formation of H$\alpha$
-to understand their complex circumstellar environment, and to understand
+We present  radiative transfer models of classical T~Tauri stars, and investigate the formation of H$\alpha$
+in order to understand their complex circumstellar environment, and to explain
 the wide variety of emission line profiles seen in observations. To
 overcome the limited applicability of the radiative transfer models
-with only magnetospherical accretion to fitting observed H$\alpha$
+with magnetospherical accretion alone to fitting observed H$\alpha$
 profiles, and to any other lines affected by the stellar wind) presented,
@@
 for possible geometrical and physical conditions which lead to the
-types of the profiles seen in observations. We find both wind models
-can reproduce the wide range profile types seen is observations. We
-also find the inclination dependency of the line equivalent width
+types of profiles seen in observations. We find both wind models
+can reproduce the wide range profile types seen is observations, 
+although the inclination dependence of the line equivalent width
 predicted by the bipolar wind model agree with trends seen in the
@@
 
-T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
-\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
+T~Tauri stars (TTS) are young ($<\sim 3\times10^{6}\,\mathrm{yrs}$,
+\citealt{appenzeller:1989}) low-mass stars, and are the progenitors
 of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
@@
 Their spectral energy distribution and polarisation data suggest the
-presence of a circumstellar disc, and it plays an important role in
+presence of a circumstellar disc, which plays an important role in
 regulating dynamics of gas flows around CTTS.
@@
 \citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profiles show evidences for both outward wind flows and
+of CTTS line profiles show evidence for both outward wind flows and
 inward accretion flows, as seen in the blue-shifted absorption features
@@
 show the direct evidence for the presence of bipolar and monopolar
-outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
-two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
+outflows down to $\sim 1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
+Similarly, ESO VLT observation of high-resolution ($R=50\,000$)
+two-dimensional spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
 and HV~Tau~C) by \citet{appenzeller:2005} show the extended H$\alpha$
@@
 disc, and in both above and below the disc --- suggesting the presence
-of the bipolar outflows. In slightly larger scale, \emph{HST} observation
-of HH30 \citet{burrows:1996} shows the jet traced to within $\lesssim30$~AU
+of the bipolar outflows. On a larger scale, \emph{HST} observation
+of HH30 \citep{burrows:1996} shows the jet traced to within $\lesssim30$~AU
 from the star. The jet has a cone shape with an opening angle of $3^{\circ}$
@@
 
-In a currently favoured model of accretion flows around CTTS, the
+In the currently favoured model of accretion flows around CTTS, the
 accretion discs are disrupted by the magnetosphere of stars which
@@
 \citealt{shu:1994}). This picture of the accretion flows is supported
-by the evidences that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$)
+by the evidences that CTTS have relatively strong ($\sim 10^{3}\mathrm{G}$)
 magnetic field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
@@
 in the CTTS profiles suggests that this model is only a part of a
-whole picture. Clearly, the modification to include the out-flowing
+complete picture. Clearly, the modification to include the out-flowing
 wind/jet flow is necessary if one requires to predict the mass-accretion
@@
 to construct more comprehensive circumstellar models (e.g. via MHD
-simulations) of T~Tauri stars. the Using the model results, we examine
+simulations) of T~Tauri stars. Using the model results, we examine
 the H$\alpha$ spectroscopic classification used by \citet{reipurth:1996},
@@
 To understand how the different part of the CTTS circumstellar environment
-contributes to the formation of H$\alpha$, the model spaced is divided
-into four different regions: 1.~Central continuum source, 2.~magnetosphere
-accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:config_dipolar}
+contributes to the formation of H$\alpha$, the model space is divided
+into four different regions: (1)~a central continuum source, (2)~magnetosphere
+accretion flow, (3)~wind outflow, and (4)~accretion disc. Fig.~\ref{fig:config_dipolar}
 depicts the relative location in the model space. In all regions,
@@
 wind resembling the density structure of the MHD simulation by \citealt{krasnopolsky:2003}
-in large scale ($\sim100$~AU) in section~\ref{sub:wind_jet}, and
-(2) that in small scale ($\sim10$~AU) in section~\ref{sub:Alternative-model-disc-wind}.
+in large scale ($\sim 100$~AU) in section~\ref{sub:wind_jet}, and
+(2) that in small scale ($\sim 10$~AU) in section~\ref{sub:Alternative-model-disc-wind}.
 
@@
 
-\caption{Basic Model Configuration.
-The system consist of four components: (1)~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, (2)~magnetospherical accretion flow, (3)~bipolar wind outflow, and (4)~accretion disc.
-The density distribution is symmetric around the z-axis.
-The innermost raius of the magnetsphere (at the equotrial plane) coincides with the the inner radius of the accretion disc.
-From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star.
-For a computational simplicity, the bipolar wind starts from just outside of the largest radius ($R_{\mathrm{mo}}$) of the magnesophere (dotted line).
-}
+\caption{Basic Model Configuration. The system consist of four
+components: (1)~the continuum source located at the origin $\left( o
+\right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
+y-axis are into the paper, (2)~magnetospherical accretion flow,
+(3)~bipolar wind outflow, and (4)~accretion disc. The density
+distribution is symmetric around the z-axis. The innermost radius of
+the magnetosphere (at the equatorial plane) coincides with the the
+inner radius of the accretion disc. From the inner most part of the
+accretion disc, the gas freely fall, moving along the magnetic filed
+onto the surface of the star. For a computational simplicity, the
+bipolar wind starts from just outside of the largest radius
+($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
 
@@
 becomes closer to the stellar surface, it is decelerates in a strong
-shock, and heated to $\sim10^{6}\,\mathrm{K}$ (with typical parameters).
+shock, and heated to $\sim 10^{6}\,\mathrm{K}$ (with typical parameters).
 The X-ray radiation produced in the shock will be absorbed by the
@@
 the star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
-of the surface is covered by the hot rings, and its temperature is
-about $6400\,\mathrm{K}$. If the mass-accretion rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$,
+of the surface is covered by the hot rings. If the mass-accretion rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$,
 the ratio of this accretion luminosity to the photospheric luminosity
-is about $0.5$. The continuum emission from the hot rings is taken
+is about $0.5$, and the corresponding temperature of the hot rings is
+about $6400\,\mathrm{K}$.  The continuum emission from the hot rings is taken
 into account when computing the line profiles.
@@
 coordinates, and $R_{\mathrm{m}}$is the radial distance to the field
-line at the equatorial plane ($\theta=\pi/2$). The range of $R_{\mathrm{m}}$is
+line at the equatorial plane ($\theta=\pi/2$). The range of
+$R_{\mathrm{m}}$ is
 restricted between $R_{\mathrm{mi}}$ and $R_{\mathrm{mo}}$. Using
@@
 the collimated MHD disc-wind model of \citet{krasnopolsky:2003} in
-large scale ($\sim100$~AU) , and the alternative wind model which
-resembles the model of \citet{krasnopolsky:2003} in small scale ($\sim10$~AU)
+large scale ($\sim 100$~AU) , and the alternative wind model which
+resembles the model of \citet{krasnopolsky:2003} in small scale ($\sim
+10$~AU)
 will be presented later (section~\ref{sub:Alternative-model-disc-wind}).
@@
 Fig.~\ref{fig:config_dipolar}) is adopted. The wind velocity field,
-$\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$, is consist of
+$\boldsymbol{v}_{\mathrm{wind}}$, is consist of
 radial and azimuthal components which depend on the spherical coordinates
@@
 \begin{eqnarray}
-\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}\label{eq:wind_velocity_def}\end{eqnarray}
+\boldsymbol{v}_{\mathrm{wind}} & = & v_{r}\hat{\boldsymbol{r}}+v_{\phi}\hat{\boldsymbol{\bphi}}\label{eq:wind_velocity_def}\end{eqnarray}
 where \begin{equation}
@@
 where $\theta_{\mathrm{disc}}$ is the opening angle of the accretion
-disc, to avoid the overlap. $v_{r0}$is the small radial velocity
+disc, to avoid the overlap. $v_{r0}$ is the small radial velocity
 at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
@@
 
-\caption{The dependency of the bipolar wind velocity and density structures on the wind accerelation parameter $\beta$.
-The radial component of the wind  velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left.
-The wind density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is shown on right.
-For all $\beta$ values, the density is normalized to the desnity at the base of the wind in polar direction, i.e.
-$\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.
-The smaller the value of $\beta$, the faster the accerelation of the wind.
-For the raidus ($r/R_{\mathrm{mo}} < 10$, both velocity and density are sensitive to the value of $\beta$.
-For all $\beta$ values, the radial velocity of the wind reaches the terminal velocity ($\sim 210\,\kmps$ by  $r/R_{\mathrm{mo}} \sim 1000$.
-The initial velocity $V_{0}=10\,\kmps$, which approximately corresponds to the thermal velocity of a hydrogen atom at 7500~K,  is used for all $v_{r}$ plots.
-Beyound $r/R_{\mathrm{mo}}= 100$, little difference is seen in the polar density with diffrent $\beta$ values.}
+\caption{The dependency of the bipolar wind velocity and density
+structures on the wind acceleration parameter $\beta$. The radial
+component of the wind velocity
+(equation~\ref{eq:wind_velocity_radial_part}) in polar direction,
+$\theta = 0$ as a function of radius is shown on left. The wind
+density (equation~\ref{eq:wind_density_final} along polar direction as
+a function of radius is shown on right. For all $\beta$ values, the
+density is normalised to the density at the base of the wind in polar
+direction, i.e. $\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.  The
+smaller the value of $\beta$, the faster the acceleration of the
+wind. For the radius ($r/R_{\mathrm{mo}} < 10$, both velocity and
+density are sensitive to the value of $\beta$. For all $\beta$ values,
+the radial velocity of the wind reaches the terminal velocity ($\sim
+210\,\kmps$ by $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity
+$V_{0}=10\,\kmps$, which approximately corresponds to the thermal
+velocity of a hydrogen atom at 7500~K, is used for all $v_{r}$
+plots. Beyond $r/R_{\mathrm{mo}}= 100$, little difference is seen in
+the polar density with different $\beta$ values.}
 
@@
 their Fig.~3 The relative number of each grain is assumed to be that
-of solar abundance, C/H$\sim3.5\times10^{-4}$ \citep{anders:1989}
-and Si/H$\sim3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
+of solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989}
+and Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
 to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
@@
 
-\caption{Basic Model Configuration of the disc-wind, magnetosphere hybrid model.
-The system consist of four components: (1)~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, (2)~magnetospherical accretion flow, (3)~colliminated wind/jet outflow, and (4)~geometrically thin (but opaque) accretion disc.
-The disc wind originates from the disc surface between $w_{i}=R_{wi}$ and $w_{i}=R_{wo}$.
-The wind source points ($S$), from which the stream lines diverges, are placed at distance $d$ above and below the star.
-By changing the value of $d$,  the degree of the wind collimation is controlled.
-The density distribution is symmetric around the z-axis.
-}
+\caption{Basic Model Configuration of the disc-wind, magnetosphere
+hybrid model. The system consist of four components: (1)~the continuum
+source located at the origin $\left( o \right)$ of the cartesian
+coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper,
+(2)~magnetospherical accretion flow, (3)~collimated wind/jet
+outflow, and (4)~geometrically thin (but opaque) accretion disc. The
+disc wind originates from the disc surface between $w_{i}=R_{wi}$ and
+$w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
+lines diverges, are placed at distance $d$ above and below the
+star. By changing the value of $d$, the degree of the wind collimation
+is controlled. The density distribution is symmetric around the
+z-axis. }
 
@@
 The wind model presented here is to simulate the collimated MHD disc-wind
-calculations of \citealt{krasnopolsky:2003} in small scale ($\sim10$~AU).
+calculations of \citealt{krasnopolsky:2003} in small scale ($\sim 10$~AU).
 \citet{knigge:1995} introduced the {}``split-monopole'' kinematic
@@
 of proportionality in equation~\ref{eq:discwind-massloss-w} is found
-by integrating $\dot{m}$ from $R_{\mathrm{wi}}$to $R_{\mathrm{wo}}$,
-and the normalising the total mass-loss rate to $\dot{M}_{\mathrm{dw}}$.
+by integrating $\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$,
+and the normalising the value to the total mass-loss rate $\dot{M}_{\mathrm{dw}}$.
 
@@
 
-\caption{Depdendency of the disc wind density and the velocity on the wind accelreation parameter $\beta$.
-The wind density $\rho$ (left panel) and the poloidal velocity component $V_{p}$ (right panel) along the stream line starting from the mid point of the wind lanching zone, i.e.
-$\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$  where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}} \right ) / 2$,  are shown as a function of the distance ($l$) from the wind lanching point (c.f.~ equations~\ref{eq:discwind-poloidal-velocity} and \ref{eq:discwind-density}).
-The azimuthal velocity component ($V_{\theta}$), which is independent of  $\beta$ (c.f.
-equation~\ref{eq:discwind-toroidal-velocity}), is also shown in the right panel for a comparison.
-The density is normalized to the density $\rho_{0}$ at the wind lanching point for $\beta = 1.0$ case.
-The $v_{p}$ reaches the terminal velocity by 100~AU for all $beta$.
-In the fur field ($l>10$~AU), the density is approximately proportional to $\sim l^2$.
-Up to $l~\sim10$~AU, the density is smaller and the poloidal speed is larger for the wind with a larger $\beta$ value.
-}
+\caption{Dependency of the disc-wind density and velocity on the wind
+acceleration parameter $\beta$. The wind density $\rho$ (left panel)
+and the poloidal velocity component $V_{p}$ (right panel) along the
+stream line starting from the mid point of the wind launching zone,
+i.e. $\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$
+where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}}
+\right ) / 2$, are shown as a function of the distance ($l$) from the
+wind launching point (c.f.~
+equations~\ref{eq:discwind-poloidal-velocity} and
+\ref{eq:discwind-density}). The azimuthal velocity component
+($V_{\theta}$), which is independent of $\beta$
+(c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in
+the right panel for a comparison. The density is normalised to the
+density $\rho_{0}$ at the wind launching point for $\beta = 1.0$ case.
+The $v_{p}$ reaches the terminal velocity by 100~AU for all
+$\beta$. In the far field ($l>10$~AU), the density is approximately
+proportional to $\sim l^2$. Up to $l~\sim 10$~AU, the density is
+smaller and the poloidal speed is larger for the wind with a larger
+$\beta$ value. }
 
@@
 calculation. In the first process, we have utilised the method by
-\citet{klein:1978} (see also \citealt{rybicki:1978}; \citet{hartmann:1994})
+\citet{klein:1978} (see also \citealt{rybicki:1978}; \citealt{hartmann:1994})
 in which the Sobolev approximation method is applied. The population
@@
 line. \citet{muzerolle:2001} also pointed out that the observed H$\alpha$
-profiles from CTTS typically have the wings extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
-\citet{reipurth:1996}) which cannot be explained by the infall velocity
+profiles from CTTS typically have the wings extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\citealt{edwards:1994};
+\citealt{reipurth:1996}) which cannot be explained by the infall velocity
 of the gas along the magnetosphere alone.
 
-To implement the broadening mechanism, two modifications to our previous
-model (\citealt{symington:2005}) are necessary as similarly done
+To implement the broadening mechanism into our previous
+model (\citealt{symington:2005}), we follow the formalism adopted 
 by \citet{muzerolle:2001}. First, the emission and absorption profiles
-must be replaced by a Voigt profile which is defined as: \begin{equation}
+are replaced from the Doppler to the Voigt profile,  which is defined as: 
+\begin{equation}
 H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
@@
 intersects with the stellar core, $I_{0}$ is computed from the stellar
-atmosphere mode of \citet{kurucz:1979} as described in section~\ref{sub:Continuum-Source},
+atmosphere model of \citet{kurucz:1979} as described in section~\ref{sub:Continuum-Source},
 and $I_{0}=0$ otherwise. The initial position of each ray is assigned
@@
 where $n_{p}$ and $n_{q}$ are the number of cylindrical radial and
-angular points for the flux integration, and $n_{\nu}$is the number
-of frequency points. In the models presented in the next (section~\ref{sec:Results}),
-$n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
+angular points for the flux integration, and $n_{\nu}$ is the number
+of frequency points. In the models presented in the following
+section. $n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
 otherwise. The linearly spaced radial grid is used for the area where
@@
 For computational simplicity, we assumed that the dust emissivity
-is zero. Since the disc mass of CTTS are rather small ($\sim0.1\,\mathrm{M_{\sun}}$)
-and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
+is zero. Since the disc mass of CTTS are rather small ($\sim 0.1\,\mathrm{M_{\sun}}$)
+and low temperature ($<\sim 1600\,\mathrm{K}$), the continuum flux
 contribution at H$\alpha$ wavelength is expected to be negligible
@@
 is about a half of the total luminosity (without the hot ring) of
-the star, and $L_{\mathrm{acc}}$is proportional to $\dot{M}_{\mathrm{acc}}$.
+the star, and $L_{\mathrm{acc}}$ is proportional to $\dot{M}_{\mathrm{acc}}$.
 The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
@@
 30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
-ranges from $\sim3$~\AA\, to $\sim160$~\AA, and the mean to
-be $\sim55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
+ranges from $\sim 3$~\AA\, to $\sim 160$~\AA, and the mean to
+be $\sim 55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
 the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
@@
 criteria of \citet{alencar:2000} is not stated in their paper, we
-can not conclude that these low $\dot{M}_{\mathrm{acc}}$models disagree
+can not conclude that these low $\dot{M}_{\mathrm{acc}}$ models disagree
 with the observation. \citet{reipurth:1996}, who measured the EW
@@
 
-\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M}_\mathrm{acc}$) and temperature ($T_{\mathrm{max}}$).
-The profiles are computed using only magnetospherical accretion flow (i.e.
-no wind/jet).
-All the profiles are computed using the parameters of the 'standard' model (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the mass accretion rate (indicated by the values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from left to right.
-The profiles are similar to those of \citet{muzerolle:2001}, available on-line (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html).
-}
+\caption{H$\alpha$ model profiles for wide ranges of mass accretion
+rate ($\dot{M}_\mathrm{acc}$) and temperature
+($T_{\mathrm{max}}$). The profiles are computed using only
+magnetospherical accretion flow (i.e. no wind/jet).  All the profiles
+are computed using the parameters of the 'standard' model
+(Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The
+temperature (indicated along the vertical axis) of the model increase
+from top to bottom, and the mass accretion rate (indicated by the
+values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from
+left to right. The profiles are similar to those of
+\citet{muzerolle:2001}, available on-line
+(http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html). }
 
@@
 
-\caption{The summary of H$\alpha$ equivalent widths from the magnetospherical accretion flow models show in Figure~\ref{fig:atlas_acc_models}.}
+\caption{The summary of H$\alpha$ equivalent widths from the
+magnetospherical accretion flow models show in
+Figure~\ref{fig:atlas_acc_models}.}
 
@@
 
-\caption{Effect of the line broadening for H$\alpha$.
-The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the model with no damping, $\Gamma=0$ (dashed).
-Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}.
-The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant.
-The broaded wings extend to $\sim \pm 800 \kmps$.
-The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.
-}
+\caption{Effect of the line broadening for H$\alpha$. The model
+computed with the damping constant ($\Gamma$), described in
+section~\ref{sec:radiative-transfer-model} (solid), is compared with
+the model with no damping, $\Gamma=0$ (dashed).  Both models are
+computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
+standard parameters given in Table~\ref{tab:std_parameters}. The two
+models have similar peak flux levels (around $V \sim 0~\kmps$), but
+the total flux and the EW of the line increased drastically for the
+model with the damping constant. The broad wings extend to $\sim \pm
+800 \kmps$.  The redshifted absorption feature (very weakly) seen in
+the $\Gamma=0$ model are not seen in the model with the broadening.  }
 
@@
 
-\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).
-The profiles are computed with the magneospherical accretion flow using the standard parameters given in Table~\ref{tab:std_parameters} and $T_{\mathrm{max}}=7500~\Kelvin$.
-The solid, dotted, and dashed lines are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$ respectively.
-As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.
-Similar dependency is seen in the models with the wide ranges of $T_{\mathrm{max}}$ and $\beta$ (not shown here).
-}
+\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).  The
+profiles are computed with the magneospherical accretion flow using
+the standard parameters given in Table~\ref{tab:std_parameters} and
+$T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
+are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$
+respectively. As the inclination becomes larger, the peak flux and the
+equivalent width of the line becomes smaller.  Similar dependency is
+seen in the models with the wide ranges of $T_{\mathrm{max}}$ and
+$\beta$ (not shown here). }
 
@@
 
-\caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$).
-The profiles are computed with only wind (no magnetospherical accretion flow or accretion disc).
-The 'standard' model (Table~\ref{tab:std_parameters}) are applied here.
-The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the wind accerelation rate increases from left to right.
-The P~Cygni profile are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow accerelation) models.
-The postion of the absorption the component moves toward the line centre as $\beta$ increases.
-The effect of line broadening becomes more prominant for higher $T_\mathrm{wind}$ and higher $\beta$ models.}
+\caption{H$\alpha$ model profiles computed with wide ranges of the
+  isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind
+  accerelation rate ($\beta$). The profiles are computed with the wind
+  component only (no magnetospherical accretion flow or accretion
+  disc). The 'standard' model parameters (Table~\ref{tab:std_parameters}) are
+  applied. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$),
+  the inclination ($i$) and the degree of collimination ($b$) are
+  fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$, $55^{\circ}$ and
+  $4.0$\, respectively. The temperature (indicated along the vertical
+  axis) of the model increase from top to bottom, and the wind
+  accerelation rate increases from left to right. The P~Cygni profile
+  are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow
+  accerelation) models.  The postion of the absorption the component
+  moves toward the line centre as $\beta$ increases. The effect of
+  line broadening becomes more prominant for higher $T_\mathrm{wind}$
+  and higher $\beta$ models.}
 
@@
 and $\dot{M}_{\mathrm{wind}}$. To minimise the number of parameters
-to be explored, we initially adopt $\gamma=0.05$, $v_{\infty}=200\,\kmps$
+to be explored, we initially adopt $\gamma=0.05$, $v_{\infty}=210\,\kmps$
 \citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
@@
 fastest acceleration ($\beta=0.2$) is almost at the terminal velocity
-($v_{\infty}\sim200\,\kmps$), that for the slowest wind acceleration
-model ($\beta=4.0$) is located close the line centre ($\sim50\,\kmps$).
+($v_{\infty}\sim 210\,\kmps$), that for the slowest wind acceleration
+model ($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).
 As one can see in Figure~\ref{fig:wind_vr_rho}, the column density
@@
 is demonstrated in Figure~\ref{fig:effect_wind_b_param}. Three models
-presented in the figure have the same mass-loss ($10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$),
-and are computer at inclination angle $i=55^{\circ}$. The P~Cygni
+presented in the figure have the same mass-loss rate ($10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$),
+and are computed at inclination angle $i=55^{\circ}$. The P~Cygni
 profile feature becomes more prominent, and the line flux becomes
@@
 fixed constant, $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor
-of the wind density (equation~\ref{eq:wind_density_final}). For
-the formation of H$\alpha$, the recombination process and the subsequent
-downward transition to $n=3$ level. Assuming the ionisation fraction
-remains constant, the recombination rate is proportional to the square
+of the wind density (equation~\ref{eq:wind_density_final}). The
+important processes in forming H$\alpha$ emission are the
+recombination process and the subsequent downward transition to $n=3$
+level. Assuming the ionisation fraction remains constant, the
+recombination rate is proportional to the square 
 of wind density. We have found the line flux of the models in the
@@
 
-\caption{The effect of wind collimation.
-The line profiles computed with with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$ for  the wind anisotropy parameter $b=0, 2, 4$ are shown in dashed, dotted, and solid respectively.
-All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.
-The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind.
-The blue-ward asymmetry is still present even in the isotropic wind case ($b=0$).}
+\caption{The effect of wind collimation. The line profiles computed
+with with $\left(T_{\mathrm{wind}},~\beta \right) = \left(
+9000\Kelvin, 0.5\right)$ for the wind anisotropy parameter $b=0, 2, 4$
+are shown in dashed, dotted, and solid respectively.  All the other
+parameters are same as in Figure~\ref{fig:atlas_wind_model}.  The
+P~Cygni profile feature becomes prominant for the spherical wind model
+since the collumn density of along the line of a sight of the observer
+at a mid inclination angle ($i=55^{\circ}$) increases for lower $b$
+values for a fixed mass-loss rate of the wind. The blue-ward asymmetry
+is still present even in the isotropic wind case ($b=0$).}
 
@@
 
-\caption{The effect of the wind mass-loss rate.
-The profiles computed with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$, and  $\dot{M}_{\mathrm{wind}} = 1.0 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (solid),  $0.5 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dotted), and $0.25 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed) are shown above.
-The models are computed with only the wind component (no magnetospherical accretion flow or  accretion disc).
-With all other parameter fixed constant, the mass-loss rate behaves as a scaling factor for the wind density (equation~\ref{eq:wind_density_final}.)}
+\caption{The effect of the wind mass-loss rate.  The profiles computed
+with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin,
+0.5\right)$, and $\dot{M}_{\mathrm{wind}} = 1.0 \times
+10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (solid), $0.5 \times
+10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dotted), and $0.25 \times
+10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed) are shown above. The
+models are computed with only the wind component (no magnetospherical
+accretion flow or accretion disc). With all other parameter fixed
+constant, the mass-loss rate behaves as a scaling factor for the wind
+density (equation~\ref{eq:wind_density_final}).}
 
@@
 on the profile shapes. In the figures, the extent of the H$\alpha$
-emission is smaller ($\sim0.2\,\mathrm{AU}$ or $\sim20\, R_{*}$)
+emission is smaller ($\sim 0.2\,\mathrm{AU}$ or $\sim 20\, R_{*}$)
 compared to the spectro-astrometric observations of \citet{takami:2003}
@@
 with the collimated wind and the accretion disc for the same range
-of $\beta$ and $T_{\mathrm{max}}$values as in Figure~\ref{fig:atlas_wind_model}.
-The inner and the outer radii of the accretion disc are $R_{\mathrm{di}}=R_{\mathrm{mi}}=2.2R_{*}$
+of $\beta$ and $T_{\mathrm{max}}$ values as in Figure~\ref{fig:atlas_wind_model}.
+The inner and the outer radii of the accretion disc are $2.2R_{*}$
 and $100\,\mathrm{AU}$ respectively, and the disc is slightly flared
@@
 
-\caption{Comparison of of the wind model with and without the optically-thick and geometrically-thin disc.
-The latter can be also equivalent to a model with a large inner radius of the accretion disc in which none of the wind emission region is not blocked provided the inclination is moderate.
-The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used).
-The flux in the red wing of the line profile from the model with the disc (solid) is greatly reduce by the presence of the accretion disc compared  to that from the model without the disc (dashed).
-The peak flux and the flux in the wings are also reduced in the model with the disc because the disc does block the wind emission region, but none of the stellar disc, i.e.
-the continuumm flux level is unchanged.
-The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown.
-The image flux is computed by integrating the specific flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$.
-The flux is in an arbitrary units and in logarithmic (base $10$) scale.
-}
+\caption{Comparison of the wind models with and without the
+optically-thick and geometrically-thin disc.  The latter can be also
+equivalent to a model with a large inner radius of the accretion disc
+in which none of the wind emission region is not blocked provided the
+inclination is moderate. The left panel shows the profile computed
+with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} =
+9000~\mathrm{K}$ (see text for other parameters used). The flux in the
+red wing of the line profile from the model with the disc (solid) is
+greatly reduce by the presence of the accretion disc compared to that
+from the model without the disc (dashed).  The peak flux and the flux
+in the wings are also reduced in the model with the disc because the
+disc does block the wind emission region, but none of the stellar
+disc, i.e. the continuumm flux level is unchanged.  The H$\alpha$
+image (project in the plane of the observer) for the model with the
+disc (middle panel) and that for the model without (right plane) are
+also shown. The image flux is computed by integrating the specific
+flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$. The
+flux is in an arbitrary units and in logarithmic (base $10$) scale. }
 
@@
 $\mu$ can be as large as $\sim0.3$ with different parameters of
-the magnetosphere; hence, this condition $\mu>0.025$ is always valid.
+the magnetosphere.
 
@@
 becomes more important in a model with a higher temperature and a
-wind mass-loss rate. In fact, the model with $\beta=2.0$ and $T_{\mathrm{dw}}=9000\,\mathrm{K}$
-displays a small amount of the wind emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
+larger wind mass-loss rate. In fact, the model with $\beta=2.0$ and
+$T_{\mathrm{dw}}=9000\,\mathrm{K}$ displays a small amount of the wind
+emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
 
@@
 the photosphere by the disc is important for predicting correct line
-strengths.
+strengths, especially at a high inclination.
 
@@
 
-\caption{Comparison of the profiles computed with the magnetosphere, the wind, the disc, and their combinations.
-The model configureations used above are: (1)~magnetosphere only (dashed), (2)~wind and disc (dash), and (3)~disc, wind and magnetosphere (solid).
-The parameters used here are $T_{\mathrm{max}}=7500\,\Kelvin$, $\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$, $\dot{M}_{\mathrm{wind}}=10^-8\,\mathrm{M_{\sun}\,yr^{-1}}$, $T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$.
-The profile for the case 3 is can be understood as a simple flux sum of the profiles from case 1 and 2.}
+\caption{Comparison of the profiles computed with the magnetosphere,
+the wind, the disc, and their combinations. The model configureations
+used above are: (1)~magnetosphere only (dash), (2)~wind and disc
+(dot), and (3)~disc, wind and magnetosphere (solid).  The parameters
+used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
+$\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$,
+$\dot{M}_{\mathrm{wind}}=10^-8\,\mathrm{M_{\sun}\,yr^{-1}}$,
+$T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$. The profile for
+the case 3 is can be understood as a simple flux sum of the profiles
+from case 1 and 2.}
 
@@
 
-\caption{Effect of the mass-loss rate to mass-accretion rate ratio  ($\mu=\dot{M}_{\mathrm{w}}/\dot{M}_{\mathrm{acc}}$).
-The H$\alpha$ profile computed with only the magnetopsherical accretion (thick solid) -- $T_{\mathrm{max}}=7500\,\Kelvin$, $\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$ -- is compared with the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash).
-All the models are computed with the inclination angle $i=55^{\circ}$.
-As $\mu$ increases the P-Cygni absorption deepens and the emission component becomes stronger.
-In genaral, the absorption is too strong for the models $\mu>0.025$ compared with the observations (e.g., \citealt{reipurth:1996}).}
+\caption{Effect of the mass-loss rate to mass-accretion rate ratio
+($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
+profile computed with only the magnetopsherical accretion (thick
+solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
+$\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ --- is compared with
+the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01
+(solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash). All the models
+are computed with the inclination angle $i=55^{\circ}$. As $\mu$
+increases the P-Cygni absorption deepens and the emission component
+becomes stronger. In genaral, the absorption is too strong for the
+models with $\mu>0.025$ compared to the observations (e.g.,
+\citealt{reipurth:1996}).}
 
@@
 
-\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$), the accretion disc.
-The mass-loss rate of the wind used here is $\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$.
-A relatively small mass-loss rate is chosen to avoid unrealistically strong P-cyg absorption component (see text in section~\ref{sub:model-acc-disc-wind} and  Figure~\ref{fig:effect_mdot_disc_wind_acc}).
-For a comparison, the profile computed with only the magensopherical accretion flow (dotted) is overlayed.
-All the profiles are computed at the inclination angle $i=55^{\circ}$.
-As $\beta$ becomes larger, the postion of the wind absorption component moves toward the line centre.
-Although little wind emission is seen in this temperature range, it becomes more important in a model with a higher temperature and a wind mass-loss rate.
-The profiles resembles the observed H$\alpha$ emission profiles affected by the wind.}
+\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models
+include the magnetospherical accretion flow (with
+$T_{\mathrm{\max}}=7500~\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$),  and the
+accretion disc. The mass-loss rate of the wind is
+$\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$. A
+relatively small mass-loss rate is chosen to avoid unrealistically
+strong P-cyg absorption component (see text in
+section~\ref{sub:model-acc-disc-wind} and
+Figure~\ref{fig:effect_mdot_disc_wind_acc}).  For a comparison, the
+profile computed with only the magensopherical accretion flow (dotted)
+is overlayed. All the profiles are computed at the inclination angle
+$i=55^{\circ}$. As $\beta$ becomes larger, the postion of the wind
+absorption component moves toward the line centre. Although little
+wind emission is seen in this temperature range, it becomes more
+important in a model with a higher temperature and a larger wind
+mass-loss rate. The profiles resembles the observed H$\alpha$ emission
+profiles affected by the wind.}
 
@@
 and \ref{fig:atlas_disc_wind_acc_model}, we have also considered
-the disc-wind model \citet{knigge:1995} as briefly described in section~\ref{sub:model-disc-wind}.
+the disc-wind model of \citet{knigge:1995} as briefly described in section~\ref{sub:model-disc-wind}.
 The former resembles the density structure of \citealt{krasnopolsky:2003}
@@
 main difference between the two models are in their density structure.
-For a given radius, the density increases toward the polar direction
+At a given radius, the density increases toward the polar direction
 in the former model, but the density increases toward the equatorial
@@
 from FU-Ori type (IV-B) for the models with small $\beta$ to III-B
-and II-B types (\citealt{reipurth:1996}) as the value of $\beta$
+and II-B types (see \citealt{reipurth:1996}) as the value of $\beta$
 increases. Although not shown here, we find that the profile shapes
@@
 wind is set to $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$) Figure~\ref{fig:atlas_discwind_acc_model}
+(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$).  Figure~\ref{fig:atlas_discwind_acc_model}
 shows the models profiles computed using the same ranges of the disc-wind
@@
 model (Figure~\ref{fig:atlas_disc_wind_acc_model}). The main difference
-between these two sets of models is the mass-loss rate to the mass
-accretion rate $\mu$. While the models presented in this section
+between these two sets of models is in the ration of the mass-loss rate to the mass
+accretion rate, $\mu$. While the models presented in this section
 use $\mu=0.1$ which is consistent with the MHD jet models (e.g.~\citealt{koenigl:2000}),
 the models in Figure~\ref{fig:atlas_disc_wind_acc_model} use much
-smaller value ($\mu=0.01$).
+smaller value ($\mu=0.01$).   The dependency of the model profiles on
+the inclination angle for the two different wind models will be discussed
+in the next section.
 
@@
 
-\caption{The summary of the standard disc-wind model parameters used in section~\ref{sub:result-discwind-knigge}. See also section~\ref{sub:Alternative-model-disc-wind}.}
+\caption{The summary of the standard disc-wind model parameters used
+in section~\ref{sub:result-discwind-knigge}. See also
+section~\ref{sub:Alternative-model-disc-wind}.}
 
@@
 
-\caption{The H$\alpha$ profiles computed with the disc-wind only models.
-For the wind mass-loss rate fixed at $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line profiles are computed with different combinations of the wind accelreation rate ($\beta$) and the isothermal disc wind temperature ($T_{\mathrm{dw}}$).
-The wind emission increases as the values of $\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes accelerates slower and as the wind comes warmer.
-Similar to the bipolar wind models (Figure~\ref{fig:atlas_wind_mode}), the position of the wind absorption moves toward the line centre as $beta$ becomes larger.
-The morphology of the profiles are smilar to that of observations.
-}
+\caption{The H$\alpha$ profiles computed with the disc-wind only
+models. For the wind mass-loss rate fixed at
+$\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line
+profiles are computed with different combinations of the wind
+accelreation rate ($\beta$) and the isothermal disc wind temperature
+($T_{\mathrm{dw}}$). The wind emission increases as the values of
+$\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes
+accelerates slower and as the wind comes warmer.  Similar to the
+bipolar wind models (Figure~\ref{fig:atlas_wind_mode}), the position
+of the wind absorption moves toward the line centre as $beta$ becomes
+larger. The morphology of the profiles are smilar to that of
+observations. }
 
@@
 
-\caption{The disc-wind, magnetoshere hybrid model.
-Same as Figure~\ref{fig:atlas_discwind_only}, but these models (soild) also include the magnetosphere accretion flow ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$).
-While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{dw}}$  (the slower accerelation and the hotter models).
-For a comparison, the profile computed with only the magensopherical accretion flow (dotted) is overlayed.
-The model profiles are very similar to the observed profiles influenced by the wind outflow.}
+\caption{The disc-wind, magnetoshere hybrid model. Same as
+Figure~\ref{fig:atlas_discwind_only}, but these models (soild) also
+include the magnetosphere accretion flow
+($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
+the emission from the magnetosphere dominates for the models with
+smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the
+colder wind models), the emission from the wind domnates for the
+models with models with larger $\beta$ and $T_{\mathrm{dw}}$ (the
+slower accerelation and the hotter models). For a comparison, the
+profile computed with only the magensopherical accretion flow (dotted)
+is overlayed. The model profiles are very similar to the observed
+profiles influenced by the wind outflow.}
 
@@
 are Type III-B profiles. In this type of profiles, the main emission
-comes from the magnetosphere, and the profile shape is altered a slightly
+comes from the magnetosphere, and the profile shape is altered from a slightly
 blue-asymmetric one to a slightly red-asymmetric one via the wind
-absorption in the blue wing. The second most common profile (26~per~cent)
-
-Type I (symmetric around line centres) is mainly produced in the magnetosphere.
+absorption in the blue wing. The second most common profile (26~per~cent), 
+Type I (symmetric around line centres), is mainly produced in the magnetosphere.
 Although not shown here, this type of profile can be reproduced with
@@
 between the two is in their inclination angles. The former is more
-likely seen with high inclination.
+likely to be seen at high inclination angles.
 
@@
 continuum flux from the footprint of the magnetosphere is seen through
-relatively fast moving gas in the accretion stream. Finally Type III-R
-profile is very similar to Type II-R, but the wind in this type of
-profile may be accretion faster than that in Type II-R.
+relatively fast moving gas in the accretion stream. Finally Type III-B
+profile is very similar to Type II-B, but the wind in this type of
+profile may be accretion faster than that in Type II-B.
 
@@
 
-\caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}.
-The combination of magnetospherical accretion flow, the accretion disc, and the disc wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.
-Similar results can be obtained if the disc wind is replaced by the disc wind.
-The model parameters and short comments are summarised in Table~\ref{tab:classification}.
-The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.}
+\caption{Sample H$\alpha$ model profiles which charactersize the
+classfication by \citet{reipurth:1996}. The combination of
+magnetospherical accretion flow, the accretion disc, and the disc wind
+model can reasonably reproduce wide ranges of H$\alpha$ profiles seen
+in observations. Similar results can be obtained if the bipolar wind is
+replaced by the disc wind. The model parameters and short comments are
+summarised in Table~\ref{tab:classification}. The horizontal axises
+are velocities in $\kmps$, and the vertical axises are nomalized
+fluxes.}
 
@@
 
-\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.
-The temepratures are in $10^{3}\,\Kelvin$.
-$\dot{M}_{\mathrm{acc}}$ and $\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
+\caption{The summary model parameters for the profiles in
+Figure~\ref{fig:atlas_reipurth} and brief comments. The temepratures
+are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
+$\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
 
@@
 is capable of reasonably reproducing the data from a real object,
-in this case, T~Tau~N. The main parameters here (1)~the temperature
+in this case, T~Tau~N. The main model parameters here are (1)~the temperature
 of the magnetospherical accretion flow ($T_{\mathrm{max}}$), (2)~the
@@
 of the wind ($T_{\mathrm{wind}}$), and (4)~the wind mass-loss rate
-($\dot{M_{\mathrm{wind}}}$). The inclination angle is simplify adopted
-from \citealt{akeson:2002} i.e.~$i=29^{\circ}$.
+($\dot{M}_{\mathrm{wind}}$). The inclination angle is simplify adopted
+from \citet{akeson:2002}, i.e.~$i=29^{\circ}$.
 
@@
 for veiling. The model consists of the magnetosphere, the bipolar
-wind, and the accretion disc (with a large hole i.e.$\sim5$\, AU
-. The parameters used for the model fit are: $T_{\mathrm{max}}=22000\,\mathrm{K}$,
-$T_{\mathrm{wind}}=8000\,\mathrm{K}$, $\dot{M}_{\mathrm{acc}}=1.1\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$,
-and $\dot{M}_{\mathrm{wind}}=2.0\times10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-The temperature of the magentosphere is relatively high compared to
-the standard cases (e.g.~Figure~\ref{fig:atlas_acc_models}; also
-\citealt{muzerolle:2001}). Note that the estimated value of $T_{\mathrm{max}}$depends
-on the adopted values of $L_{*}$ (or $M_{*}$ and $T_{\mathrm{eff}}$)
-for the photospheric continuum model. If a lower value of $L_{*}$
-is adopted, $T_{\mathrm{max}}$value would become smaller in order
-to match the line strength which is mainly determined by the emission
-from the magnetosphere, in this case. For example, if the photospheric
-continuum is 3 times smaller than the one used here, one finds $T_{\mathrm{max}}\sim9600\,\mathrm{K}$
-which is more similar to that of the standard cases. The figure shows
-that the agreement between the model and the observation is quite
-reasonable although the line wings are slightly stronger in the models.
-In this example, the main profile feature is defined by the emission
-from the magnetosphere, but the blue side of the profile is affected
-by the absorption by the wind. The mass-loss to mass-accretion rate
-$\mu=0.18$ which is similar to the value predicted by observations
-and MHD simulations i.e.~$\sim0.1$ \citep{koenigl:2000}. Compared
-our mass-accretion rate estimate is much less than that of \citep{johns-krull:2000},
-and slightly smaller than that of \citep{calvet:2004} (see above).
+wind, and the accretion disc (with a large hole i.e. $\sim5$\, AU. The
+parameters used for the model fit are:
+$T_{\mathrm{max}}=22000\,\mathrm{K}$,
+$T_{\mathrm{wind}}=8000\,\mathrm{K}$,
+$\dot{M}_{\mathrm{acc}}=1.1\times10^{-8}\,\mathrm{M_{\sun}\,
+yr^{-1}}$, and
+$\dot{M}_{\mathrm{wind}}=2.0\times10^{-9}\,\mathrm{M_{\sun}\,
+yr^{-1}}$.  The temperature of the magentosphere is relatively high
+compared to the standard cases
+(e.g.~Figure~\ref{fig:atlas_acc_models}; also
+\citealt{muzerolle:2001}). Note that the estimated value of
+$T_{\mathrm{max}}$ depends on the adopted values of $L_{*}$ (or
+$M_{*}$ and $T_{\mathrm{eff}}$) for the photospheric continuum
+model. If a lower value of $L_{*}$ is adopted, $T_{\mathrm{max}}$ value
+would become smaller in order to match the line strength which is
+mainly determined by the emission from the magnetosphere, in this
+case. For example, if the photospheric continuum is 3 times smaller
+than the one used here, one finds
+$T_{\mathrm{max}}\sim9600\,\mathrm{K}$ which is more similar to that
+of the standard cases. The figure shows that the agreement between the
+model and the observation is quite reasonable although the line wings
+are slightly stronger in the models.  In this example, the main
+profile feature is defined by the emission from the magnetosphere, but
+the blue side of the profile is affected by the absorption by the
+wind. The mass-loss to mass-accretion rate $\mu=0.18$ which is similar
+to the value predicted by observations and MHD simulations
+i.e.~$\sim0.1$ \citep{koenigl:2000}. Compared our mass-accretion rate
+estimate is much less than that of \citep{johns-krull:2000}, and
+slightly smaller than that of \citep{calvet:2004} (see above).
 
@@
 
-\caption{Comparison of the observed H$\alpha$ profile of T~Tau and the profile computed with the hybrid model, which consist of the magnetosphere, the colliminated wind, and the accretion disc (with a large hole i.e.
-$\sim 5$~AU).
-The inclination angle $29^\circ$ is used.
-The maximum temperature of the magnetosphere ($T_{\mathrm{max}}$) and the isothermal wind temperature used here are 22000~K and 8000~K respetively.
-The mass-accretion rate ($\dot{M}_{\mathrm{acc}}$) and the mass-loss rate ($\dot{M}_{\mathrm{wind}}$) are $1.1 \times 10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and $2.0 \times 10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ resplectively ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.18$)}
+\caption{Comparison of the observed H$\alpha$ profile of T~Tau and the
+profile computed with the hybrid model, which consist of the
+magnetosphere, the colliminated wind, and the accretion disc (with a
+large hole i.e. $\sim 5$~AU). The inclination angle $29^\circ$ is
+used.  The maximum temperature of the magnetosphere
+($T_{\mathrm{max}}$) and the isothermal wind temperature are
+22000~K and 8000~K respetively. The mass-accretion rate
+($\dot{M}_{\mathrm{acc}}$) and the mass-loss rate
+($\dot{M}_{\mathrm{wind}}$) are $1.1 \times
+10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and $2.0 \times
+10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ resplectively
+($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.18$)}
 
@@
 In the previous sections, two possible geometrical configurations
-for the wind from CTTS were considered: 1. the bipolar wind, and 2.~the
+for the wind from CTTS were considered: (1)~the bipolar wind, and (2)~the
 disc wind. While the material more concentrated toward the polar regions
@@
 toward the equatorial plane in the second case. As mentioned earlier,
-the bipolar wind morel resembles the density distribution of the jet
+the bipolar wind model resembles the density distribution of the jet
 MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
@@
 disc wind, the absorption becomes stronger as the inclination becomes
-larger . The optical depth to an observer becomes larger as the inclination
+larger. The optical depth to an observer becomes larger as the inclination
 increases in this geometry.
@@
 as the inclination angle increases for the model with the disc wind.
-With the models with only magnetosphere (section~\ref{sub:model-acc}),
-we have also found that the line equivalent width decreases as the
+For the models with only magnetosphere (section~\ref{sub:model-acc}),
+we find that the line equivalent width decreases as the
 inclination increases in those models (see Figure~\ref{fig:acc_inclination_effect}).
@@
 
-\caption{Dependency on the inclination angle of the H$\alpha$ model profiles.
-The profile computed at $i=10^{\circ}$(solid), $55^{\circ}$ (dot) and $80^{\circ}$ using 1.~the disc, bipolar-wind, accretion hybrid model (left panel; c.f.
-section~\ref{sub:model-acc-disc-wind}) and 2.~using the disc-wind, magentosphere hybrid model (right; c.f.
-section~\ref{sub:result-discwind-kingge}) are shown for a comparison.
-The parameters used for the magnetoshere are same for the both models, i.e.
-$T_{\mathrm{max}}=7500~\mathrm{K}$ and  $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.
-The isotherma wind temperature and the wind accrelation parameter used both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.
-All the other parameters are same as in sections~\ref{sub:model-acc-disc-wind} and  \ref{sub:result-discwind-knigge}.
-While the line equivalent width increases as the inclination angle increases for the former model configuration, it decreases as the incination angle increases for the latter.
-Only the former agrees with the tendency seen in the observational study of \citet{appenzeller:2005} who showed that the H$\alpha$ line equivalent width of CTTS increases as the inclination angle increases.
-}
+\caption{Dependency of the H$\alpha$ model profiles on the inclination
+angle. The profile computed at $i=10^{\circ}$(solid), $55^{\circ}$
+(dot) and $80^{\circ}$ using 1.~the disc, bipolar-wind, accretion
+hybrid model (left panel; c.f. section~\ref{sub:model-acc-disc-wind})
+and 2.~using the disc-wind, magentosphere hybrid model (right;
+c.f. section~\ref{sub:result-discwind-knigge}) are shown for a
+comparison.  The parameters used for the magnetoshere are same for the
+both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The
+isothermal wind temperature and the wind accrelation parameter used
+both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.  All
+the other parameters are same as in
+sections~\ref{sub:model-acc-disc-wind} and
+\ref{sub:result-discwind-knigge}. While the line equivalent width
+increases as the inclination angle increases for the former model
+configuration, it decreases as the incination angle increases for the
+latter. Only the former agrees with the tendency seen in the
+observational study of \citet{appenzeller:2005} who showed that the
+H$\alpha$ line equivalent width of CTTS increases as the inclination
+angle increases. }
 
@@
 models for classical T~Tauri stars, and detailed studies of the H$\alpha$
-formation from their complex to circumstellar environment and to understand
-the wide variety emission line profiles seen in observations. The
+formation from their complex to circumstellar environment to understand
+the wide variety of H$\alpha$ profiles seen in observations. The
 two types of wind models considered are (1)~the bipolar wind model
-in the wind is originated from the star itself (section~\ref{sub:wind_jet};
+in which the wind originates from the star itself (section~\ref{sub:wind_jet};
 Figure~\ref{fig:config_dipolar}), and (2)~the disc-wind model in
@@
 mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind
-was set to be 4--10 times smaller than that predicated by magneto-hydrodynamical
+was set to be 4 --10 times smaller than that predicated by magneto-hydrodynamical
 (MHD) calculations (c.f.~$\mu\sim0.1;$ \citealt{koenigl:2000})
@@
 Using the model results, we examined the H$\alpha$ spectroscopic
-classification proposed by \citet{reipurth:1996}, and discuss the
+classification proposed by \citet{reipurth:1996}, and discussed the
 basic physical conditions that reproduce the profiles in each classified
@@
 we could not confirm the uniqueness of the fit. The ratio of the mass-loss
-to mass-accretion rate was found to be $\sim0.18$.
+to mass-accretion rate was found to be $\sim0.18$, which is consistent
+with \citet{koenigl:2000}.
 
@@
 \end{document}
+
+% LocalWords:  LyX QL SS al Ryuichi Harries magnetospherical Reipurth Balmer RU
+% LocalWords:  appenzeller progenitors herbig edwards kenyon reipurth alencar
+% LocalWords:  kuhi hartigan bertout gullbring spectro astrometric takami Cha
+% LocalWords:  monopolar Lup ESO VLT koenigl uchida cameron shu jonhs krull kim
+% LocalWords:  guenther muzerolle decampli hartmann basri calvet kwan malbet
+% LocalWords:  blandford ustyugova ouyed krasnopolsky pudritz kurucz ghosh
+% LocalWords:  shakura draine hanner grevesse mathis cotera knigge whitney
+% LocalWords:  harries kurosawa steinacker klein rybicki Sobolev mihalas chiang
+% LocalWords:  vernazza luttermoser

### 2006-01-11 TTau_Halpha/kurosawa.tex
Corrections made after Tim's comments. The subsection on the fits of T Tau is eliminated from kurosawa.tex.  The subsection was saved in a separate tex file: ttau_model_subsec.tex.  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@616 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \usepackage[latin1]{inputenc}
-\setcounter{tocdepth}{3}
+\usepackage{times}
 \usepackage{graphicx}
@@
 
+\setcounter{tocdepth}{3}
 \makeatletter
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{times}
 
@@
 \begin{document}
-\title[On the formation of H$\alpha$ around classical T Tauri stars]{On the formation of H$\alpha$ around classical T Tauri stars}
-
-\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa$^1$\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries$^1$ and Neil H. Symington$^2$\\
-$^1$School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL. \\
-$^2$School of Physics and Astronomy, University of St. Andrews, North Haugh, St. Andrews, Fife, KY16 9SS.}
+\title[On the formation of H$\alpha$ around classical T Tauri
+  stars]{On the formation of H$\alpha$ line emission around classical T Tauri stars}
+
+\author[R. Kurosawa et\,al.]{Ryuichi
+  Kurosawa$^1$\thanks{E-mail:rk@astro.ex.ac.uk}, Tim J. Harries$^1$
+  and Neil H.
+Symington$^2$\\ $^1$School of Physics, University of Exeter, Stocker Road, Exeter EX4~4QL.
+\\ $^2$School of Physics and Astronomy, University of St.
+Andrews, North Haugh, St.
+Andrews, Fife, KY16 9SS.}
 
@@
 
-We present  radiative transfer models of classical T~Tauri stars, and investigate the formation of H$\alpha$
-in order to understand their complex circumstellar environment, and to explain
-the wide variety of emission line profiles seen in observations. To
+We present  radiative transfer models of classical T~Tauri stars, and
+investigate the formation of H$\alpha$ line emission 
+in order to understand their complex circumstellar environments, and to explain
+the wide variety of line profiles seen in observations. To
 overcome the limited applicability of the radiative transfer models
@@
 we examine the H$\alpha$ spectroscopic classification used by Reipurth
-et.~al , and discuss the basic physical conditions required to reproduce
-the profiles in each classified type. Using the hybrid model, we fit
-the observed H$\alpha$ from the optical component of T~Tau triple
-system (T~Tau~N), and find its ratio of the mass-loss to mass-accretion
-rate to be $\sim0.18$ with the cold ($T_{\mathrm{wind}}\approx8000\,\mathrm{K}$)
-bipolar wind model .
+et.~al, and discuss the basic physical conditions required to reproduce
+the profiles in each classified type.
 
@@
 T~Tauri stars (TTS) are young ($<\sim 3\times10^{6}\,\mathrm{yrs}$,
-\citealt{appenzeller:1989}) low-mass stars, and are the progenitors
+\citealt{appenzeller:1989}) low-mass objects, and are the progenitors
 of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
@@
 of the most active CTTS show emission in higher Balmer lines and metal
-lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit an excess
-amount of continuum flux in the ultraviolet (UV) and infrared (IR).
+lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit excess
+ continuum flux in the ultraviolet (UV) and infrared (IR).
 Their spectral energy distribution and polarisation data suggest the
-presence of a circumstellar disc, which plays an important role in
-regulating dynamics of gas flows around CTTS.
+presence of circumstellar discs, which plays an important role in
+regulating dynamics of gas flows around CTTS (e.g. \citealt{camenzind:1990}).
 
 Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
-\citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
+\citealt{kenyon:1994}; \citealt*{reipurth:1996}; \citealt{alencar:2000})
 of CTTS line profiles show evidence for both outward wind flows and
@@
 to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
-\citealt{edwards:1987}; \citealt{hartigan:1995}), and the mass-accretion
+\citealt{edwards:1987}; \citealt*{hartigan:1995}), and the mass-accretion
 rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
 (e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
-Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
-show the direct evidence for the presence of bipolar and monopolar
+Recent H$\alpha$ spectro-astrometric observations by \citet*{takami:2003}
+show direct evidence for the presence of bipolar and monopolar
 outflows down to $\sim 1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observation of high-resolution ($R=50\,000$)
+Similarly, ESO VLT observations using high-resolution ($R=50\,000$)
 two-dimensional spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
@@
 emission in the direction perpendicular to the obscuring circumstellar
-disc, and in both above and below the disc --- suggesting the presence
-of the bipolar outflows. On a larger scale, \emph{HST} observation
-of HH30 \citep{burrows:1996} shows the jet traced to within $\lesssim30$~AU
+disc both above and below the disc, suggesting the presence
+of the bipolar outflows. On a larger scale, \emph{HST} observations
+of HH30 \citep{burrows:1996} show the jet traced to within $\lesssim30$~AU
 from the star. The jet has a cone shape with an opening angle of $3^{\circ}$
 between 70 and 700 AU \citep{koenigl:2000}. \citet{alencar:2000}
-found about 80 per cent of their samples (30 CTTS) show blue-shifted
-absorption components in at least one of Balmer lines and Ca~K (most
+found about 80 per cent of their sample (30 CTTS) show blue-shifted
+absorption components in at least one of the Balmer lines and Ca~K (most
 commonly in H$\alpha$).
 
-In the currently favoured model of accretion flows around CTTS, the
-accretion discs are disrupted by the magnetosphere of stars which
-channels the gas from the disc onto the surface of the stars (e.g.,
+In the currently favoured model of accretion in CTTS, the
+accretion disc is disrupted by the magnetosphere of stars which
+channels the gas from the disc onto the stellar surface (e.g.,
 \citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993};
-\citealt{shu:1994}). This picture of the accretion flows is supported
-by the evidences that CTTS have relatively strong ($\sim 10^{3}\mathrm{G}$)
-magnetic field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
-and by the radiative transfer models which reproduce the observed
-profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
+\citealt{shu:1994}). This picture is supported
+by the evidence that CTTS have relatively strong ($\sim 10^{3}\mathrm{G}$)
+magnetic field (e.g., \citealt{johns-krull:1999};
+\citealt{guenther:1996};  \citealt{symington:2005b})
+and by radiative transfer models which reproduce the observed
+profiles for some TTS (\citealt*{muzerolle:2001}). The magnetospherical
 accretion model naturally explains the blue-ward asymmetric emission
 lines (seen in some of CTTS) caused by the partial occultation of
-the flow by the disc, and the redshifted absorption component at the
+the flow by the stellar disc, and the redshifted absorption component at the
 typical free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$)
@@
 accretion model in explaining the line profiles in some CTTS, the
-overwhelming observational evidences for the outflow (mentioned above)
-in the CTTS profiles suggests that this model is only a part of a
-complete picture. Clearly, the modification to include the out-flowing
-wind/jet flow is necessary if one requires to predict the mass-accretion
+overwhelming observational evidence for outflow (mentioned above)
+in the CTTS profiles suggests that this model is only a part of the
+complete picture. Clearly, a modification to include an out-flowing
+wind/jet flow is necessary if one wishes to predict the mass-accretion
 rate and the mass-loss rate of CTTS by modelling their emission profiles
@@
 
-Priory to the magnetospherical models, many alternative models had
+Prior to the magnetospherical paradigm, many alternative models had
 been considered to explain the observed spectroscopic features mentioned
 earlier. For example, (1)~the Alfv\'{e}n wave-driven wind model
-(e.g.~\citealt{decampli:1981}; \citealt{hartmann:1982}), (2)~turbulent
+(e.g.~\citealt{decampli:1981}; \citealt*{hartmann:1982}), (2)~turbulent
 boundary layer (between the accretion disc and stellar surface) model
 (e.g.~\citealt{bertout:1988}; \citealt{basri:1989}), (3)~chromospheric
-model (e.g.~\citealt{calvet:1984}), and (4)~disc wind model (e.g.
-\citealt{calvet:1992b}; \citealt{kwan:1995}). Considering the success
-of the magnetospherical accretion flow model in some cases and the
-observational evidences for the outflows, it is likely that an improved
-spectroscopic model requires both inflow and outflow components. The
-combination of the magnetospheric accretion flow model with model
-1 or 4 would be a reasonable starting point. Although time consuming
-to explore a larger parameter space, more realistic density, velocity
-and temperature structure from magnetohydrodynamic wind+accretion
-models should be considered as inputs for an radiative transfer model
-in the future. Recent work by \citet{alencar:2005} showed the observed
-H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better produced
-by the radiative transfer model which include the collimated disc-wind
+model (e.g.~\citealt*{calvet:1984}), and (4)~disc wind model (e.g.
+\citealt*{calvet:1992b}; \citealt{kwan:1995}).  Recent work by
+\citet{alencar:2005} showed the observed 
+H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better be produced
+by the radiative transfer model which includes a collimated disc-wind
 arising from near the inner edge of the accretion disc. \citet{malbet:2005}
-considered the combination of a spherical wind and the accretion disc
+considered a combination of a spherical wind and an accretion disc
 in their radiative transfer model to reproduce Br$\gamma$ from the
@@
 the possibility that the stellar wind along the open magnetic field
-originating from the star can cause significant spin-down torque on
+originated from the star can cause significant spin-down torque on
 the star, provided that mass-loss rate is high enough.
@@
 provide preliminary physical conditions which lead to the wide variety
-of emission line profiles seen in the observation, and would help
+of emission line profiles seen in the observation, and will help
 to construct more comprehensive circumstellar models (e.g. via MHD
@@
 contributes to the formation of H$\alpha$, the model space is divided
-into four different regions: (1)~a central continuum source, (2)~magnetosphere
-accretion flow, (3)~wind outflow, and (4)~accretion disc. Fig.~\ref{fig:config_dipolar}
-depicts the relative location in the model space. In all regions,
-the density is symmetric around the z-axis. The innermost radius of
+into four different regions: (1)~a central continuum source, (2)~the magnetospherical
+accretion flow, (3)~the wind outflow, and (4)~the accretion
+disc. Fig.~\ref{fig:config_dipolar} 
+depicts the relative location of the regions in the model space. In
+all regions, the density is symmetric around the z-axis. The innermost radius of
 the magnetosphere at the equatorial plane coincides with the the inner
 radius of the accretion disc. From the inner most part of the accretion
-disc, the gas freely fall, moving along the magnetic filed onto the
-surface of the star. For the purpose of computational simplicity,
-the collimated bipolar wind are defined only in the outside of the
+disc, the gas falls freely, moving along the magnetic field onto the
+surface of the star. For simplicity,
+the collimated bipolar wind is defined only in the outside of the
 largest radius of the magnetosphere (to avoid overlapping of the wind
@@
 types of the wind configurations are considered: (1)~the bipolar
-wind resembling the density structure of the MHD simulation by \citealt{krasnopolsky:2003}
+wind resembling the density structure of the MHD simulation by \citet{krasnopolsky:2003}
 in large scale ($\sim 100$~AU) in section~\ref{sub:wind_jet}, and
@@
 
-\caption{Basic Model Configuration. The system consist of four
+\caption{The basic model configuration. The system consists of four
 components: (1)~the continuum source located at the origin $\left( o
 \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-y-axis are into the paper, (2)~magnetospherical accretion flow,
-(3)~bipolar wind outflow, and (4)~accretion disc. The density
+y-axis are into the paper, (2)~the magnetospherical accretion flow,
+(3)~the bipolar wind outflow, and (4)~the accretion disc. The density
 distribution is symmetric around the z-axis. The innermost radius of
@@
 inner radius of the accretion disc. From the inner most part of the
-accretion disc, the gas freely fall, moving along the magnetic filed
-onto the surface of the star. For a computational simplicity, the
-bipolar wind starts from just outside of the largest radius
+accretion disc, the gas falls freely, moving along the magnetic field
+onto the surface of the star. The bipolar wind starts from just
+outside of the largest radius 
 ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
@@
 ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$, and $4000\,\mathrm{K}$
-respectively. The model atmosphere of \citet{kurucz:1979} equivalently
-\citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$ and
-$\log g_{*}=3.5$ (cgs) is used to find the photospheric continuum
-at H$\alpha$ wavelength. The parameters are summarised in Table~\ref{tab:std_parameters}.
+respectively. The model atmosphere of \citet{kurucz:1993} with
+$T_{\mathrm{ph}}=4000\,\mathrm{K}$ and $\log g_{*}=3.5$ (cgs) is used
+to find the photospheric continuum at the H$\alpha$ wavelength. The
+parameters are summarised in Table~\ref{tab:std_parameters}.
 
 For a model which includes magnetospherical accretion, an additional
-source of the continuum source is considered. As the in-falling gas
-becomes closer to the stellar surface, it is decelerates in a strong
-shock, and heated to $\sim 10^{6}\,\mathrm{K}$ (with typical parameters).
+continuum source is considered. As the in-falling gas 
+becomes close to the stellar surface, it is decelerates in a strong
+shock, and is heated to $\sim 10^{6}\,\mathrm{K}$.
 The X-ray radiation produced in the shock will be absorbed by the
-gas located near, and re-emitted in optical and UV radiation (\citealt{koenigl:1991};
-\citealt{hartmann:1994}). This will create hot rings near the stellar
+gas locally, and re-emitted in optical and UV radiation (\citealt{koenigl:1991};
+\citealt*{hartmann:1994}). This will create hot rings near the stellar
 surface where the magnetic field intersects with the surface. For
@@
 \begin{table*}
+
+\caption{Summary of the standard classical T~Tauri star model parameters.}
+\label{tab:std_parameters}
 
@@
 
-\caption{The summary of the standard classical T~Tauri star model parameters.}
-
-\label{tab:std_parameters}
-
 \end{table*}
@@
 We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
-as done so by \citet{muzerolle:2001} and by \citet{symington:2005},
+as done  by \citet{muzerolle:2001} and by \citet*{symington:2005},
 in which the gas accretion on to the stellar surface from the innermost
@@
 r=R_{\mathrm{m}}\sin^{2}\theta\label{eq:dipole}\end{equation}
- \citep[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
+ \citep*[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
 of the field point ($p$) in Fig.~\ref{fig:config_dipolar} in spherical
-coordinates, and $R_{\mathrm{m}}$is the radial distance to the field
+coordinates, and $R_{\mathrm{m}}$ is the radial distance to the field
 line at the equatorial plane ($\theta=\pi/2$). The range of
@@
 adiabatic compression due to the converging nature of the flow, and
-the major contributors of the cooling process are bremsstrahlung radiation
+the major contributors to the cooling process are bremsstrahlung radiation
 and line emission from Ca~II and Mg~II ions. The results of \citet{martin:1996}
-qualitatively agrees with that of \citet{hartmann:1994}.
+qualitatively agree with that of \citet{hartmann:1994}.
 
@@
 As mentioned earlier, the wind model presented here is to simulate
-the collimated MHD disc-wind model of \citet{krasnopolsky:2003} in
-large scale ($\sim 100$~AU) , and the alternative wind model which
+the collimated MHD disc-wind model of \citet{krasnopolsky:2003} on a 
+large scale ($\sim 100$~AU) , and an alternative wind model which
 resembles the model of \citet{krasnopolsky:2003} in small scale ($\sim
@@
 Fig.~\ref{fig:config_dipolar}) is adopted. The wind velocity field,
-$\boldsymbol{v}_{\mathrm{wind}}$, is consist of
+$\boldsymbol{v}_{\mathrm{wind}}$, consists of
 radial and azimuthal components which depend on the spherical coordinates
@@
 Further, the density of the wind is assumed to be axi-symmetric and
-separable in $r$ and $\theta$ for computational simplicity, i.e.,
+separable in $r$ and $\theta$,
 
@@
 \caption{The dependency of the bipolar wind velocity and density
-structures on the wind acceleration parameter $\beta$. The radial
+structure on the wind acceleration parameter $\beta$. The radial
 component of the wind velocity
 (equation~\ref{eq:wind_velocity_radial_part}) in polar direction,
-$\theta = 0$ as a function of radius is shown on left. The wind
+$\theta = 0$ as a function of radius is shown on the left. The wind
 density (equation~\ref{eq:wind_density_final} along polar direction as
-a function of radius is shown on right. For all $\beta$ values, the
+a function of radius is shown on the right. For all $\beta$ values, the
 density is normalised to the density at the base of the wind in polar
@@
 self-consistently (assuming the radial dependency of the mid-plane
-density) by using the iterative Monte Carlo radiative transfer technique
-(c.f.~\citet{walker:2004}), we find it to be too time consuming
+density) by using an iterative Monte Carlo radiative transfer technique
+(c.f.~\citealt{walker:2004}), we find it to be too time consuming
 for the purpose of this paper -- understanding the general characteristic
@@
 \rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
- where $w$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
+ where $w=\sqrt{x^{2}+y^{2}}$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
 axis, the scale height, the distance from the disc plane, and the
@@
 and Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
-to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
+to values found in the ISM model of \citet*{mathis:1977} and \citet*{kim:1994}.
 Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.
 
-\subsection{Alternative model: disc-wind model of \citet{knigge:1995}}
+\subsection{Alternative model: the disc-wind model}
 
@@
 
-\caption{Basic Model Configuration of the disc-wind, magnetosphere
+\caption{Basic model configuration of the disc-wind, magnetosphere
 hybrid model. The system consist of four components: (1)~the continuum
@@
 coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper,
-(2)~magnetospherical accretion flow, (3)~collimated wind/jet
-outflow, and (4)~geometrically thin (but opaque) accretion disc. The
+(2)~the magnetospherical accretion flow, (3)~the collimated wind/jet
+outflow, and (4)~the geometrically thin (but opaque) accretion disc. The
 disc wind originates from the disc surface between $w_{i}=R_{wi}$ and
@@
 
-The wind model presented here is to simulate the collimated MHD disc-wind
-calculations of \citealt{krasnopolsky:2003} in small scale ($\sim 10$~AU).
-\citet{knigge:1995} introduced the {}``split-monopole'' kinematic
+The wind model presented here is intended to mimic the collimated MHD disc-wind
+calculations of \citet{krasnopolsky:2003} in small scale ($\sim 10$~AU).
+\citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
 disc-wind model in their studies of the UV resonance lines formed
@@
 
-Four basic parameters for the models are: 1. mass-loss rate, 2.~the
-degree of the wind collimation, 3.~velocity gradients, and 4.~the
+Four basic parameters for the models are: (1) mass-loss rate, (2)~the
+degree of the wind collimation, (3)~the velocity gradients, and (4)~the
 wind temperature. The basic configuration of the disc-wind model is
@@
 v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
-Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt{castor:1975}),
+Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt*{castor:1975}),
 the poloidal component of the wind velocity ($v_{p}$) parameterised
@@
 H$\alpha$ profiles from pre-main-sequence stars which are surrounded
-by one or more of the followings: the magnetospherical accretion flow,
+by one or more of the following: the magnetospherical accretion flow,
 the out-flowing collimated wind, and the accretion disc. Previously
@@
 modified the code to handle the two-dimensional (2-D) density distribution,
-and restricted our models to be axi-symmetric. It was done so in order
-to enable us to explore rather large number of parameter spaces (c.f.~section~\ref{sec:model-configuration}).
+and restricted our models to be axi-symmetric. It was done in order
+to enable us to explore rather large number of parameters (c.f.~section~\ref{sec:model-configuration}).
 Note that the velocity field is still in 3-D -- the third component
 can be calculated by using the symmetry for a given value of azimuthal
-angle. The examples of how the AMR grid for the purpose of the radiative
-transfer is constructed are presented in e.g. \citet{wolf:1999},
-\citet{kurosawa:2001a} and \citet{steinacker:2003} .
-
-The computation of the H$\alpha$ is divided in two parts: (1)~the
+angle. An examples of how the AMR grid for the purpose of the radiative
+transfer is constructed are presented in e.g. \citet*{wolf:1999},
+\citet{kurosawa:2001a}, \citet{steinacker:2003} and \citet{kurosawa:2004a}.
+
+The computation of  H$\alpha$ is divided in two parts: (1)~the
 source function calculation ($S_{\nu}$) and (2)~the observed flux/profile
@@
 and the gas to be in radiative equilibrium. Our hydrogen atom model
-consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
+consist of 14 bound state and continuum. Readers are refer to \citet{harries:2000}
 for details.
@@
 section. $n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
-otherwise. The linearly spaced radial grid is used for the area where
-the ray intersects with magnetosphere, and the logarithmically spaced
+otherwise. A linearly spaced radial grid is used for the area where
+the ray intersects with magnetosphere, and a logarithmically spaced
 grid is used for the wind and the accretion disc regions.
@@
 For computational simplicity, we assumed that the dust emissivity
-is zero. Since the disc mass of CTTS are rather small ($\sim 0.1\,\mathrm{M_{\sun}}$)
+is zero. Since the disc mass of CTTS are rather small ($\sim 0.01\,\mathrm{M_{\sun}}$)
 and low temperature ($<\sim 1600\,\mathrm{K}$), the continuum flux
@@
 a significant increase of the line flux in both red and blue wings
-of seen in the model with broadening. A weak red-shifted absorption
+of seen in the model with broadening. The weak red-shifted absorption
 component (which is a signature of the magnetospherical accretion)
@@
 their EW measurements are under-representing real samples since the
-selection of the targets are based on the strong H$\alpha$ emission
+selection of the targets are based on the strong emission
 in H$\alpha$ surveys.
@@
 and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
-The figure show that the peak (normalised) flux decrease as the inclination
+The figure shows that the peak (normalised) flux decreases as the inclination
 angle increases. Similarly, the equivalent width also decreases as
@@
 line appearance of the profile with $i=10^{\circ}$. Although not
-show here, a similar dependency on the inclination angle is found
+shown here, a similar dependency on the inclination angle is found
 for the models with different temperatures ($T_{\mathrm{max}}=6500$,
@@
 caused by the occultation of the accretion flow by the equatorial
-disc and the stellar disc. On the hand, \citealt{alencar:2000} (see
+disc and the stellar disc. However, \citealt{alencar:2000} (see
 their Fig.~9) found a substantial fraction of the observed H$\alpha$
@@
 magnetospherical accretion flow (i.e. no wind/jet).  All the profiles
-are computed using the parameters of the 'standard' model
+are computed using the parameters of the `standard' model
 (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/broadening.eps}
+
+\end{center}
+
+\caption{The effect of line broadening for H$\alpha$. The model
+computed with a damping constant ($\Gamma$), described in
+section~\ref{sec:radiative-transfer-model} (solid), is compared with
+the model with no damping, $\Gamma=0$ (dashed).  Both models are
+computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
+standard parameters given in Table~\ref{tab:std_parameters}. The two
+models have similar peak flux levels (around $V \sim 0~\kmps$), but
+the total flux and the EW of the line increased drastically for the
+model with the damping constant. The broad wings extend to $\sim \pm
+800 \kmps$.  The redshifted absorption feature (very weakly) seen in
+the $\Gamma=0$ model is not seen in the model with the broadening.  }
+
+\label{fig:broadening}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/acc_inc_effect.eps}
+
+\end{center}
+
+\caption{Dependency of H$\alpha$ profiles on inclination ($i$).  The
+profiles are computed with the magneospherical accretion flow using
+the standard parameters given in Table~\ref{tab:std_parameters} and
+$T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
+are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$
+respectively. As the inclination becomes larger, the peak flux and the
+equivalent width of the line becomes smaller.  Similar dependency is
+seen in the models with the wide ranges of $T_{\mathrm{max}}$ and
+$\beta$. }
+
+\label{fig:acc_inclination_effect}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{table}
+
+\caption{Summary of H$\alpha$ equivalent widths from the
+magnetospherical accretion flow models shown in
+Figure~\ref{fig:atlas_acc_models}.}
+
+\label{tab:ha_ew_acc_models}
 
@@
 
-\caption{The summary of H$\alpha$ equivalent widths from the
-magnetospherical accretion flow models show in
-Figure~\ref{fig:atlas_acc_models}.}
-
-\label{tab:ha_ew_acc_models}
-
 \end{table}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/broadening.eps}
-
-\end{center}
-
-\caption{Effect of the line broadening for H$\alpha$. The model
-computed with the damping constant ($\Gamma$), described in
-section~\ref{sec:radiative-transfer-model} (solid), is compared with
-the model with no damping, $\Gamma=0$ (dashed).  Both models are
-computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
-standard parameters given in Table~\ref{tab:std_parameters}. The two
-models have similar peak flux levels (around $V \sim 0~\kmps$), but
-the total flux and the EW of the line increased drastically for the
-model with the damping constant. The broad wings extend to $\sim \pm
-800 \kmps$.  The redshifted absorption feature (very weakly) seen in
-the $\Gamma=0$ model are not seen in the model with the broadening.  }
-
-\label{fig:broadening}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/acc_inc_effect.eps}
-
-\end{center}
-
-\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).  The
-profiles are computed with the magneospherical accretion flow using
-the standard parameters given in Table~\ref{tab:std_parameters} and
-$T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
-are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$
-respectively. As the inclination becomes larger, the peak flux and the
-equivalent width of the line becomes smaller.  Similar dependency is
-seen in the models with the wide ranges of $T_{\mathrm{max}}$ and
-$\beta$ (not shown here). }
-
-\label{fig:acc_inclination_effect}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Bipolar Wind}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_only_final.eps}
-
-\end{center}
-
-\caption{H$\alpha$ model profiles computed with wide ranges of the
-  isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind
-  accerelation rate ($\beta$). The profiles are computed with the wind
-  component only (no magnetospherical accretion flow or accretion
-  disc). The 'standard' model parameters (Table~\ref{tab:std_parameters}) are
-  applied. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$),
-  the inclination ($i$) and the degree of collimination ($b$) are
-  fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$, $55^{\circ}$ and
-  $4.0$\, respectively. The temperature (indicated along the vertical
-  axis) of the model increase from top to bottom, and the wind
-  accerelation rate increases from left to right. The P~Cygni profile
-  are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow
-  accerelation) models.  The postion of the absorption the component
-  moves toward the line centre as $\beta$ increases. The effect of
-  line broadening becomes more prominant for higher $T_\mathrm{wind}$
-  and higher $\beta$ models.}
-
-\label{fig:atlas_wind_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-As mentioned in earlier, the magnetospherical accretion flow model
-alone cannot explain some of the features seen in observations. As
-an alternative model, we now examine formation of H$\alpha$ in a
-simple bipolar wind as described in section \ref{sub:wind_jet}. The
-basic wind model parameters introduced earlier are $\gamma$, $\beta$,
-$v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
-and $\dot{M}_{\mathrm{wind}}$. To minimise the number of parameters
-to be explored, we initially adopt $\gamma=0.05$, $v_{\infty}=210\,\kmps$
-\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
+As mentioned earlier, the magnetospherical accretion flow model alone
+cannot explain some of the features seen in observations. As an
+alternative model, we now examine formation of H$\alpha$ in a simple
+bipolar wind as described in section \ref{sub:wind_jet}. The basic
+wind model parameters introduced earlier are $\gamma$, $\beta$,
+$v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$ and
+$\dot{M}_{\mathrm{wind}}$. To minimise the number of free parameters,
+we initially adopt $\gamma=0.05$, $v_{\infty}=210\,\kmps$
+\citep{appenzeller:2005} and
+$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
 Further, the angular extent of the wind (the opening angle of the
 wind) is assumed to be $\theta_{\mathrm{wind}}=80^{\circ}$. The degree
-of collimation is initially chosen to be $b=4$, i.e. the ratio of
-the density in polar direction to the density at the edge of the wind
-closest to the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
-for given radii. For simplicity, the wind temperature $T_{\mathrm{wind}}$
-is assumed to be isothermal\@. Although the line is potentially sensitive
-to the temperature structure of the wind, determination of a self-consistent
-wind temperature is beyond the scope of this paper. Readers are refereed
-to \citet{hartmann:1982} in which the wind temperature structure
-is determined by balancing the radiative cooling rate (assuming optically
-thin) with the MHD wave heating rate. With these parameters kept constant,
-we examine the characteristics of H$\alpha$ profiles, as a function
-of the wind acceleration parameter $\beta$ and the isothermal wind
-temperature $T_{\mathrm{wind}}$. Dependency on the other parameters
-will be discussed later in this section.
+of collimation is initially chosen to be $b=4$, i.e. the ratio of the
+density in polar direction to the density at the edge of the wind
+closest to the accretion disc is about
+$\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$, for
+given radii. For simplicity, the wind temperature $T_{\mathrm{wind}}$
+is assumed to be isothermal\@. Although the line is potentially
+sensitive to the temperature structure of the wind, determination of a
+self-consistent wind temperature is beyond the scope of this
+paper. Readers are refereed to \citet{hartmann:1982} in which the wind
+temperature structure is determined by balancing the radiative cooling
+rate (assuming optically thin) with the MHD wave heating rate. With
+these parameters kept constant, we examine the characteristics of
+H$\alpha$ profiles, as a function of the wind acceleration parameter
+$\beta$ and the isothermal wind temperature
+$T_{\mathrm{wind}}$. Dependency on the other parameters will be
+discussed later in this section.
 
@@
 for the range of $\beta$ between $0.2$ and $2.0$. The P~Cygni
-profile are prominent in the models with lower values of $T_{\mathrm{wind}}$
+profiles are prominent in the models with lower values of $T_{\mathrm{wind}}$
 and $\beta$ (colder and faster acceleration wind). As the value of
@@
 as $\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
-because the density near the photosphere increases (more material
-near the photosphere) as the value of $\beta$ increases (Figure~\ref{fig:wind_vr_rho});
+because the density near the photosphere increases as the value of
+$\beta$ increases (Figure~\ref{fig:wind_vr_rho}); 
 hence, the emissivity of increases. Unlike the magnetospherical accretion
@@
 with high inclinations (not shown here).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.9]{figures/atlas_ha_i55_wind_only_final.eps}
+
+\end{center}
+
+\caption{H$\alpha$ model profiles computed with wide ranges of the
+  isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind
+  accerelation rate ($\beta$). The profiles are computed with the wind
+  component only (no magnetospherical accretion flow or accretion
+  disc). The `standard' model parameters (Table~\ref{tab:std_parameters}) are
+  applied. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$),
+  the inclination ($i$) and the degree of collimination ($b$) are
+  fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$, $55^{\circ}$ and
+  $4.0$\, respectively. The temperature (indicated along the vertical
+  axis) of the model increases from top to bottom, and the wind
+  accerelation rate increases from left to right. The P~Cygni profile
+  are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow
+  accerelation) models.  The postion of the absorption the component
+  moves toward the line centre as $\beta$ increases. The effect of
+  line broadening becomes more prominant for higher $T_\mathrm{wind}$
+  and higher $\beta$ models.}
+
+\label{fig:atlas_wind_model}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 density in the wind becomes smaller for a smaller $b$ model. As the
-wind becomes more isotropic, the high gas concentrated more in the
+wind becomes more isotropic, the material in the
 polar direction has to be spread in the wider angular angles. This
@@
 P~Cygni profile feature becomes prominant for the spherical wind model
-since the collumn density of along the line of a sight of the observer
+since the column density of along the line of a sight of the observer
 at a mid inclination angle ($i=55^{\circ}$) increases for lower $b$
@@
 accretion disc, in which none of the wind emission region is blocked
-by the disc --- provided the inclination angle is not so high and
+by the disc --- provided the inclination angle is not high and
 the disc is not or slightly flared.
@@
 (e.g.~\citealt{shang:2002}). %
-}; however, if a slower wind acceleration rate ( $\beta=4$) is the
-emission region become slightly larger ($\sim0.4$~AU).
-
-Although not shown here, we have computed the H$\alpha$ profiles
-with the collimated wind and the accretion disc for the same range
-of $\beta$ and $T_{\mathrm{max}}$ values as in Figure~\ref{fig:atlas_wind_model}.
-The inner and the outer radii of the accretion disc are $2.2R_{*}$
-and $100\,\mathrm{AU}$ respectively, and the disc is slightly flared
-(see section~\ref{sub:Accretion-disc}). Similar to the case in Figure~\ref{fig:effect_alpha_disc},
-the line flux of the models with accretion disc decreases to less
-than the half of that without the accretion disc similar to the models
-shown in Figure~\ref{fig:effect_alpha_disc}. The overall behaviour
-of the line profile shapes as functions of $\beta$ and $T_{\mathrm{wind}}$
+}; however, the extent of the line emission region becomes slightly
+larger ($\sim0.4$~AU) if a slower wind acceleration rate ( $\beta=4$)
+is used.
+
+Although not shown here, we have also computed the H$\alpha$ profiles
+from the combination of the collimated wind and the accretion disc
+($R_{\mathrm{di}}=2.2R_{*}$ and $R_{\mathrm{do}}=100\,\mathrm{AU}$) for 
+the same range of $\beta$ and $T_{\mathrm{max}}$ values used in 
+Figure~\ref{fig:atlas_wind_model}.  As expected
+(c.f.~Figure~\ref{fig:effect_alpha_disc}), the models show the 
+decrease in the flux in the blue wing when compared to the flux of the
+same model computed without the accretion disc.
+The overall behaviour of the line profile shapes as functions of $\beta$ and $T_{\mathrm{wind}}$
 are very similar to that for the models without the accretion disc.
@@
 model. The wings appear to be weaker in these models compared to the
-wind only models because of the lower wind emission flux to the continuum
-flux as briefly mentioned earlier.
+wind only models because the ratio of the wind emission flux
+to the continuum flux is lower.
 
@@
 
-\caption{Comparison of the wind models with and without the
+\caption{A comparison of the wind models with and without the
 optically-thick and geometrically-thin disc.  The latter can be also
@@
 red wing of the line profile from the model with the disc (solid) is
-greatly reduce by the presence of the accretion disc compared to that
+greatly reduced by the presence of the accretion disc compared to that
 from the model without the disc (dashed).  The peak flux and the flux
@@
 flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$. The
-flux is in an arbitrary units and in logarithmic (base $10$) scale. }
+flux is in an arbitrary units and on a logarithmic (base $10$) scale. }
 
@@
 \end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/summary.eps}
+
+\end{center}
+
+\caption{A comparison of the profiles computed with the magnetosphere,
+the wind, the disc, and their combinations. The model configurations 
+used above are: (1)~magnetosphere only (dash), (2)~wind and disc
+(dot), and (3)~disc, wind and magnetosphere (solid).  The parameters
+used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
+$\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$,
+$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$,
+$T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$. The profile for
+the case 3 is can be understood as a simple flux sum of the profiles
+from case 1 and 2.}
+
+\label{fig:summary_beta05_t8000}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/disc_wind_acc_mdot_effect.eps}
+
+\end{center}
+
+\caption{The effect of the mass-loss rate to mass-accretion rate ratio
+($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
+profile computed with only the magnetopsherical accretion (thick
+solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
+$\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ --- is compared with
+the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01
+(solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash). All the models
+are computed with the inclination angle $i=55^{\circ}$. As $\mu$
+increases the P-Cygni absorption deepens and the emission component
+becomes stronger. In general, the absorption is too strong for the
+models with $\mu>0.025$ compared to the observations (e.g.,
+\citealt{reipurth:1996}).}
+
+\label{fig:effect_mdot_disc_wind_acc}
+
+\end{figure}
 
@@
 flux around the line centre. As seen before, the presence of the disc
-causes the reduction in the red side of the profile since the emission
-from the receding gas is block by the disc. The resulting profile
+causes a reduction in the red side of the profile since the emission
+from the receding gas is blocked by the disc. The resulting profile
 appears to be narrower than that of the magnetosphere model.
-
-The effect of changing the ratio of the wind mass-loss rate to mass-accretion
-rate ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
-in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With the fixed value
-of mass-accretion rate ($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
-, the mass-loss rate by the wind is varied. The figure shows that
-as $\mu$ increases the P-Cygni absorption deepens, and the position
-of minimum flux in the absorption trough appears to move blue-ward.
-On the other hand, the emission component becomes stronger as $\mu$
-increases. With this combination of the parameters for the magnetosphere
-and the wind, the absorption component tends to be too strong for
-the models $\mu>0.025$ (with this model configuration), at all inclinations
-(not shown here), compared with the observed H$\alpha$ profiles (e.g.\citealt{reipurth:1996};
-\citet{alencar:2000}). As we will see later (section~\ref{fig:ttau_model}),
-$\mu$ can be as large as $\sim0.3$ with different parameters of
-the magnetosphere.
-
-Again, the H$\alpha$ profiles with the same ranges of the wind temperature
-($T_{\mathrm{wind}}$) and the wind acceleration parameter ($\beta$)
-used in Figure~\ref{fig:atlas_discwind_only} are computed with $\mu=0.01$.
-The parameters of the magnetosphere fixed as in Figure~\ref{fig:acc_inclination_effect},
-are shown in Figure~\ref{fig:atlas_disc_wind_acc_model} along with
-the model with only the magnetosphere, for a comparison. A relatively
-small value of $\mu$ is chosen to avoid absorption component of the
-P-Cyg profile becoming too strong, as seen in Figure~\ref{fig:effect_mdot_disc_wind_acc}.
-In general, even with small values of the anisotropy parameter ($b=0$
-and $2$), the absorption component is found to be too strong when
-$\mu=0.1$ is used with this combination of the magnetosphere and
-the wind. The figure shows that the position of the wind absorption
-component moves toward the line centre as $\beta$ becomes larger.
-Although little wind emission is seen in this temperature range, it
-becomes more important in a model with a higher temperature and a
-larger wind mass-loss rate. In fact, the model with $\beta=2.0$ and
-$T_{\mathrm{dw}}=9000\,\mathrm{K}$ displays a small amount of the wind
-emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
-
-As seen in Figure~\ref{fig:summary_beta05_t8000}, the profiles shown
-here can be understood as the combination of the emission from the
-magnetosphere and the absorption of the flux by the wind component.
-In general, the emission from the accretion disc is negligible at
-H$\alpha$ wavelength, but the absorption of the continuum flux from
-the photosphere by the disc is important for predicting correct line
-strengths, especially at a high inclination.
-
-Although the profiles shown in Figure~\ref{fig:atlas_disc_wind_acc_model}
-are those at a single inclination angle ($i=55^{\circ}$), they are
-very similar to the Type II-B and III-B of the observed CTTS H$\alpha$
-profiles (\citealt{reipurth:1996}), which are impossible to be explained
-by the magnetospherical accretion flow models (e.g.~\citealt{muzerolle:2001}).
-Comparison of the model profiles with different types of the observed
-H$\alpha$ profiles will be given in section~\ref{sub:Classification-scheme-proposed}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/summary.eps}
-
-\end{center}
-
-\caption{Comparison of the profiles computed with the magnetosphere,
-the wind, the disc, and their combinations. The model configureations
-used above are: (1)~magnetosphere only (dash), (2)~wind and disc
-(dot), and (3)~disc, wind and magnetosphere (solid).  The parameters
-used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
-$\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$,
-$\dot{M}_{\mathrm{wind}}=10^-8\,\mathrm{M_{\sun}\,yr^{-1}}$,
-$T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$. The profile for
-the case 3 is can be understood as a simple flux sum of the profiles
-from case 1 and 2.}
-
-\label{fig:summary_beta05_t8000}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/disc_wind_acc_mdot_effect.eps}
-
-\end{center}
-
-\caption{Effect of the mass-loss rate to mass-accretion rate ratio
-($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
-profile computed with only the magnetopsherical accretion (thick
-solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
-$\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ --- is compared with
-the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01
-(solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash). All the models
-are computed with the inclination angle $i=55^{\circ}$. As $\mu$
-increases the P-Cygni absorption deepens and the emission component
-becomes stronger. In genaral, the absorption is too strong for the
-models with $\mu>0.025$ compared to the observations (e.g.,
-\citealt{reipurth:1996}).}
-
-\label{fig:effect_mdot_disc_wind_acc}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+The effect of changing the ratio of the wind mass-loss rate to mass-accretion
+rate ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
+in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With a fixed value
+of mass-accretion rate
+($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
+mass-loss rate is varied. The figure shows that 
+as $\mu$ increases the P-Cygni absorption deepens, and the position
+of minimum flux in the absorption trough appears to move blue-ward.
+On the other hand, the emission component becomes stronger as $\mu$
+increases. With this combination of the parameters for the magnetosphere
+and the wind, the absorption component tends to be too strong for
+the models $\mu>0.025$ (with this model configuration), at all inclinations
+(not shown here), compared with the observed H$\alpha$ profiles (e.g.\citealt{reipurth:1996};
+\citealt{alencar:2000}). 
+%As we will see later (section~\ref{fig:ttau_model}),
+%$\mu$ can be as large as $\sim0.3$ with different parameters of
+%the magnetosphere.
+
+Again, the H$\alpha$ profiles with the same range of the wind temperature
+($T_{\mathrm{wind}}$) and the wind acceleration parameter ($\beta$)
+used in Figure~\ref{fig:atlas_wind_model} are computed, but this time with $\mu=0.01$.
+The parameters of the magnetosphere are fixed as in
+Figure~\ref{fig:acc_inclination_effect}. The results are shown in
+Figure~\ref{fig:atlas_disc_wind_acc_model} along with 
+the model with only the magnetosphere for a comparison. A relatively
+small value of $\mu$ is chosen to avoid absorption component of the
+P-Cyg profile becoming too strong, as seen in Figure~\ref{fig:effect_mdot_disc_wind_acc}.
+In general, even with small values of the anisotropy parameter ($b=0$
+and $2$), the absorption component is found to be too strong when
+$\mu=0.1$ is used with this combination of the magnetosphere and
+the wind. The figure shows that the position of the wind absorption
+component moves toward the line centre as $\beta$ becomes larger.
+Although little wind emission is seen in this temperature range, it
+becomes more important in a model with a higher temperature and a
+larger wind mass-loss rate. In fact, the model with $\beta=2.0$ and
+$T_{\mathrm{dw}}=9000\,\mathrm{K}$ displays a small amount of the wind
+emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
+
+As seen in Figure~\ref{fig:summary_beta05_t8000}, the profiles shown
+here can be understood as the combination of the emission from the
+magnetosphere and the absorption of the flux by the wind component.
+In general, the emission from the accretion disc is negligible at
+H$\alpha$ wavelength, but the absorption of the continuum flux from
+the photosphere by the disc is important for predicting correct line
+strengths, especially at a high inclination.
+
+Although the profiles shown in Figure~\ref{fig:atlas_disc_wind_acc_model}
+are those at a single inclination angle ($i=55^{\circ}$), they are
+very similar to the Type II-B and III-B of the observed CTTS H$\alpha$
+profiles (\citealt{reipurth:1996}), which cannot be explained
+by the magnetospherical accretion flow models (e.g.~\citealt{muzerolle:2001}).
+Comparison of the model profiles with different types of the observed
+H$\alpha$ profiles will be given in section~\ref{sub:Classification-scheme-proposed}.
+
 \subsection{Disc-wind model of \citet{knigge:1995}}
@@
 and \ref{fig:atlas_disc_wind_acc_model}, we have also considered
-the disc-wind model of \citet{knigge:1995} as briefly described in section~\ref{sub:model-disc-wind}.
+the disc-wind model of \citet{knigge:1995} as described in section~\ref{sub:model-disc-wind}.
 The former resembles the density structure of \citealt{krasnopolsky:2003}
@@
 plane for the models presented here.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}
+
+\end{center}
+
+\caption{The H$\alpha$ profiles computed with the disc-wind only
+models. With the wind mass-loss rate fixed at
+$\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line
+profiles are computed with different combinations of the wind
+accelreation rate ($\beta$) and the isothermal disc wind temperature
+($T_{\mathrm{dw}}$). The wind emission increases as the values of
+$\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes
+accelerates slower and as the wind comes warmer.  As in the
+bipolar wind models (Figure~\ref{fig:atlas_wind_model}), the position
+of the wind absorption moves toward the line centre as $\beta$ becomes
+larger. The morphology of the profiles are smilar to that of
+observations. }
+
+\label{fig:atlas_discwind_only}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
+
+\end{center}
+
+\caption{The disc-wind, magnetoshere hybrid model. The same as
+Figure~\ref{fig:atlas_discwind_only}, but these models (solid) also
+include the magnetosphere accretion flow
+($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
+the emission from the magnetosphere dominates for the models with
+smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the
+colder wind models), the emission from the wind dominates the
+profiles for models with larger $\beta$ and $T_{\mathrm{dw}}$ (the
+slower accerelation and the hotter models). For a comparison, the
+profile computed with only the magensopherical accretion flow (dotted)
+is overlayed.}
+
+\label{fig:atlas_discwind_acc_model}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 parameters are summarised in Table~\ref{tab:std_discwind_parameters}.
-The figure shows that the wind emission increases $\beta$ and $T_{\mathrm{dw}}$
+The figure shows that the wind emission increases as $\beta$ and $T_{\mathrm{dw}}$
 increase. Similar to the bipolar wind models, the location of the
@@
 $d$. The dependency on the disc wind mass-loss rate of the profile
-shape is similar to that of the collimated wind models (Figure~\ref{fig:effect_mdot_disc_wind_acc})
-.
+shape is similar to that of the collimated wind models
+(Figure~\ref{fig:effect_mdot_disc_wind_acc}).
 
@@
 the location of the absorption component moves toward the line centre
-as the value of $\beta$ increases (as the wind acceleration slower).
+as the value of $\beta$ increases (the wind acceleration is slower).
 The figure shows that in the models with smaller $\beta$ and $T_{\mathrm{dw}}$,
@@
 of $i$, $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$.%
-} types of the observed H$\alpha$ profiles (\citealt{reipurth:1996}).
+} types of  H$\alpha$ profiles (\citealt{reipurth:1996}).
 The shape of the primary and secondary peaks in the profiles are slightly
@@
 \begin{table}
+
+\caption{A summary of the standard disc-wind model parameters used
+in section~\ref{sub:result-discwind-knigge}. See also
+section~\ref{sub:Alternative-model-disc-wind}.}
+
+\label{tab:std_discwind_parameters}
 
@@
 
-\caption{The summary of the standard disc-wind model parameters used
-in section~\ref{sub:result-discwind-knigge}. See also
-section~\ref{sub:Alternative-model-disc-wind}.}
-
-\label{tab:std_discwind_parameters}
-
 \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}
-
-\end{center}
-
-\caption{The H$\alpha$ profiles computed with the disc-wind only
-models. For the wind mass-loss rate fixed at
-$\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line
-profiles are computed with different combinations of the wind
-accelreation rate ($\beta$) and the isothermal disc wind temperature
-($T_{\mathrm{dw}}$). The wind emission increases as the values of
-$\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes
-accelerates slower and as the wind comes warmer.  Similar to the
-bipolar wind models (Figure~\ref{fig:atlas_wind_mode}), the position
-of the wind absorption moves toward the line centre as $beta$ becomes
-larger. The morphology of the profiles are smilar to that of
-observations. }
-
-\label{fig:atlas_discwind_only}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
-
-\end{center}
-
-\caption{The disc-wind, magnetoshere hybrid model. Same as
-Figure~\ref{fig:atlas_discwind_only}, but these models (soild) also
-include the magnetosphere accretion flow
-($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
-$\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
-the emission from the magnetosphere dominates for the models with
-smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the
-colder wind models), the emission from the wind domnates for the
-models with models with larger $\beta$ and $T_{\mathrm{dw}}$ (the
-slower accerelation and the hotter models). For a comparison, the
-profile computed with only the magensopherical accretion flow (dotted)
-is overlayed. The model profiles are very similar to the observed
-profiles influenced by the wind outflow.}
-
-\label{fig:atlas_discwind_acc_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Although not shown here, this type of profile can be reproduced with
-the disc-wind, magnetosphere hybrid mode with pole on configuration.
-Since there is not material in the polar region in the disc wind model,
+the disc-wind, magnetosphere hybrid model with a pole-on configuration.
+Since there is no material in the polar region in the disc wind model,
 the observer can look the magnetosphere almost directory for high
@@
 that the wind emission is negligible. Type II-R and Type II-B can
-be produced in a similar physical conditions (e.g. in a slow accretion
-and low temperature wind plus a magnetosphere). Main difference is
+be produced in similar physical conditions (e.g. in a slow accretion
+and low temperature wind plus a magnetosphere). The main difference is
 between the two is in their inclination angles. The former is more
@@
 Type III-R is the least common type of the observed profile (2~per~cent)
-according to \citet{reipurth:1996}. Incidentally, we also had a hard
-time to reproduce this type of profile since this can be achieve only
+according to \citet{reipurth:1996}. Incidentally, we also found it
+difficult to reproduce this type of profile since this can be achieve only
 at narrow range of parameter space (very high inclination angle with
-disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and $\dot{M}_{\mathrm{acc}}~10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+a disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
+$\dot{M}_{\mathrm{acc}}~10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{figure}
@@
 replaced by the disc wind. The model parameters and short comments are
-summarised in Table~\ref{tab:classification}. The horizontal axises
-are velocities in $\kmps$, and the vertical axises are nomalized
-fluxes.}
+summarised in Table~\ref{tab:classification}. The horizontal axes
+are velocities in $\kmps$, and the vertical axes are nomalized
+flux.}
 
@@
 \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%astro.ex.ac.uk/people/rk/
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{table*}
+
+\caption{The summary model parameters for the profiles in
+Figure~\ref{fig:atlas_reipurth} and brief comments. The temepratures
+are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
+$\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
+
+\label{tab:classification}
 
@@
 $7.5$&
-$10^{-9}$&
+$10^{-8}$&
 $8.0$&
@@
 $7.5$&
-$10^{-9}$&
+$10^{-8}$&
 $9.0$&
@@
 $9.0$&
-$0.5$&
+$0.2$&
 Wind, disc and magnetosphere. Fast wind acceleration rate. Mid inclination\tabularnewline
@@
 $7.5$&
-$10^{-9}$&
+$10^{-8}$&
 $7.0$&
@@
 
-\caption{The summary model parameters for the profiles in
-Figure~\ref{fig:atlas_reipurth} and brief comments. The temepratures
-are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
-$\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
-
-\label{tab:classification}
-
 \end{table*}
 
-\subsection{An example model fit of T~Tau}
-
-\label{sub:ttau-model}
-
-As a demonstrative purpose, we present a model fit of H$\alpha$ observation
-of a classical T Tauri star (T~Tau) obtained by \citet{vink:2005}.
-T~Tau is known to be a triple system (e.g.~\citealt{koresko:2000}).
-One of the star in the system T~Tau~N (a prototype for T~Tauri
-stars) is dominating in optical (e.g.~\citealt{calvet:1994}). The
-rotational velocity and the rotational period of the star found by
-\citet{herbst:1987} are $v\,\sin i=19.5\pm2.5\,\mathrm{km\, s^{-1}}$
-and $2.80\,\mathrm{d}$ respectively. The inclination of the disc
-is known to be relatively small (e.g.~$i=29^{\circ}$, \citealt{akeson:2002}).
-There is a rather large scatter in the previously estimated the accretion
-rates e.g.~$3\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ \citep{johns-krull:2000}
-and $\left(3.1-5.7\right)\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-\citep{calvet:2004}.
-
-For the photospheric model, the following parameters from \citet{calvet:2004}
-are adopted: $T_{\mathrm{eff}}=5500\,\mathrm{K}$, $M_{*}=1.9\,\mathrm{M_{\sun}}$
-and $R_{*}=2.9\, R_{*}$. The standard geometry for the magnetosphere
-($R_{\mathrm{mi}}=2.2\, R_{*}$ and $R_{\mathrm{mo}}=3.0\, R_{*}$)
-and the bipolar wind configuration (Table~\ref{tab:std_parameters})
-are used for simplicity. Again, our purpose here is not to obtain
-the best fit parameters, but rather it is to examine if the model
-is capable of reasonably reproducing the data from a real object,
-in this case, T~Tau~N. The main model parameters here are (1)~the temperature
-of the magnetospherical accretion flow ($T_{\mathrm{max}}$), (2)~the
-mass-accretion rate ($\dot{M}_{\mathrm{acc}}$), (3)~the temperature
-of the wind ($T_{\mathrm{wind}}$), and (4)~the wind mass-loss rate
-($\dot{M}_{\mathrm{wind}}$). The inclination angle is simplify adopted
-from \citet{akeson:2002}, i.e.~$i=29^{\circ}$.
-
-Figure~\ref{fig:ttau_model} shows the result of a model fit. The
-amount of veiling near H$\alpha$ is very small ($<0.01$) for T~Tau,
-according to \citet{basri:1990}; hence, the observation is not corrected
-for veiling. The model consists of the magnetosphere, the bipolar
-wind, and the accretion disc (with a large hole i.e. $\sim5$\, AU. The
-parameters used for the model fit are:
-$T_{\mathrm{max}}=22000\,\mathrm{K}$,
-$T_{\mathrm{wind}}=8000\,\mathrm{K}$,
-$\dot{M}_{\mathrm{acc}}=1.1\times10^{-8}\,\mathrm{M_{\sun}\,
-yr^{-1}}$, and
-$\dot{M}_{\mathrm{wind}}=2.0\times10^{-9}\,\mathrm{M_{\sun}\,
-yr^{-1}}$.  The temperature of the magentosphere is relatively high
-compared to the standard cases
-(e.g.~Figure~\ref{fig:atlas_acc_models}; also
-\citealt{muzerolle:2001}). Note that the estimated value of
-$T_{\mathrm{max}}$ depends on the adopted values of $L_{*}$ (or
-$M_{*}$ and $T_{\mathrm{eff}}$) for the photospheric continuum
-model. If a lower value of $L_{*}$ is adopted, $T_{\mathrm{max}}$ value
-would become smaller in order to match the line strength which is
-mainly determined by the emission from the magnetosphere, in this
-case. For example, if the photospheric continuum is 3 times smaller
-than the one used here, one finds
-$T_{\mathrm{max}}\sim9600\,\mathrm{K}$ which is more similar to that
-of the standard cases. The figure shows that the agreement between the
-model and the observation is quite reasonable although the line wings
-are slightly stronger in the models.  In this example, the main
-profile feature is defined by the emission from the magnetosphere, but
-the blue side of the profile is affected by the absorption by the
-wind. The mass-loss to mass-accretion rate $\mu=0.18$ which is similar
-to the value predicted by observations and MHD simulations
-i.e.~$\sim0.1$ \citep{koenigl:2000}. Compared our mass-accretion rate
-estimate is much less than that of \citep{johns-krull:2000}, and
-slightly smaller than that of \citep{calvet:2004} (see above).
-
-Although not shown here for clarity, the peak flux near the line centre
-is also affected by the wind absorption (causing about 10 per cent
-reduction) compared to the profile computer with magnetosphere only
-model (similar effect also seen in Figure~\ref{fig:atlas_disc_wind_acc_model}).
-If the fit was performed by ignoring the wind, the temperature and
-the mass-accretion rate of the magnetospherical accretion flow will
-be underestimated. A better approach to a model fit is a simultaneous
-fitting of multiple lines. For example, the near-infrared lines such
-as Pa$\beta$ and Br$\gamma$ should be used to determined the mass-loss
-rate since these lines are much less affected by the wind. Using the
-mass-loss rate from these lines, H$\alpha$ can be used to determine
-the wind mass-loss rate.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/ttau_compare.eps}
-
-\end{center}
-
-\caption{Comparison of the observed H$\alpha$ profile of T~Tau and the
-profile computed with the hybrid model, which consist of the
-magnetosphere, the colliminated wind, and the accretion disc (with a
-large hole i.e. $\sim 5$~AU). The inclination angle $29^\circ$ is
-used.  The maximum temperature of the magnetosphere
-($T_{\mathrm{max}}$) and the isothermal wind temperature are
-22000~K and 8000~K respetively. The mass-accretion rate
-($\dot{M}_{\mathrm{acc}}$) and the mass-loss rate
-($\dot{M}_{\mathrm{wind}}$) are $1.1 \times
-10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and $2.0 \times
-10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ resplectively
-($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.18$)}
-
-\label{fig:ttau_model}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{ttau_model_subsec.tex}
 
@@
 In the previous sections, two possible geometrical configurations
-for the wind from CTTS were considered: (1)~the bipolar wind, and (2)~the
-disc wind. While the material more concentrated toward the polar regions
-for a given radius in the first case, the material is more concentrated
-toward the equatorial plane in the second case. As mentioned earlier,
-the bipolar wind model resembles the density distribution of the jet
-MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
-($>10$~AU), and the disc wind model resembles that in smaller scale
-($<10$~AU).
+for the wind from CTTS were considered: (1)~a bipolar wind, and (2)~a
+disc wind. While the material is more concentrated toward the polar
+regions for a given radius in the first case, the material is more concentrated
+toward the equatorial plane in the second case. 
+%As mentioned earlier,
+%the bipolar wind model resembles the density distribution of the jet
+%MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
+%($>10$~AU), and the disc wind model resembles that in smaller scale
+%($<10$~AU).
 
@@
 shows the H$\alpha$ profiles computed for 1.~the disc, bipolar-wind,
-accretion hybrid model (section\ref{sub:model-acc-disc-wind}) and
+accretion hybrid model (section~\ref{sub:model-acc-disc-wind}) and
 2.~the disc-wind, magnetosphere hybrid model (section~\ref{sub:result-discwind-knigge})
@@
 for further investigation of the inclination dependency on the line
-profile will be extremely useful for finding a possible wind configuration
+profile will be extremely useful for determining the wind configuration
 of CTTS.
 
-Despite the inclination angle dependency of the observed H$\alpha$
-favouring the models with bipolar wind, there are two main aspects
-of this model are not quite consistent with the magneto-centrifugal
-launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
-First, in section~\ref{sub:model-acc-disc-wind}, we found that the
-ratio of the mass-loss to mass-accretion rates needed to be rather
-small ($\mu<\sim0.025$), in order not to have an unrealistically
-strong P-Cyg absorption component, compared to the MHD simulations
-suggested \citep{koenigl:2000} i.e. $\mu\approx0.1$. In the model
-fit of T~Tau observation (section~\ref{sub:ttau-model}), we found
-much larger value of the ratio $\mu=0.18$. Considering large uncertainty
-in MHD theories and observational measurements ($\dot{M}_{\mathrm{acc}}$,
-$\dot{M}_{\mathrm{wind}}$ and $B$, ), the wide range of the mass-loss
-to mass-accretion ratio (e.g.~$0.025<\mu<0.18$) may be still reasonable.
-On the other hand, the models with the disc wind (section~\ref{sub:result-discwind-knigge})
-using $\mu=0.1$ reproduces the profiles (Figure~\ref{fig:atlas_discwind_acc_model})
-similar to that seen in observations. Second, the MHD models predict
-that the wind/jet becomes collimated well above the disc plane ($>10$~AU),
-but our bipolar wind model are collimated (density enhanced toward
-in the polar direction) from right outside of the magnetosphere. Unless
-the origin of the wind is from the central star itself, the density
-distribution used for the bipolar wind is not quite consistent with
-the near field of the MHD jet models, considering that the most of
-the H$\alpha$ emission occurs within a few to a several radii of
-the magnetosphere (Figure.~\ref{fig:effect_alpha_disc}). The density
-structure used for the disc wind model, however, is very similar to
-that of MHD simulations in the near field where the most of the H$\alpha$
-wind emission occurs. Interestingly, however, the recent study of
-\citet{matt:2005} showed the possibility that the stellar wind along
-the open magnetic field originating from the star can cause significant
-spin-down torque on the star, provided that mass-loss rate is high
-enough. Considering the issues mentioned above, it is not possible
-to favour the bipolar wind model to the disc wind model without further
-observational constraints. In reality, two types of the winds (bipolar
-wind and disc wind) may co-exits similar to that seen in e.g. \citet{drew:1998}
-and \citet{matt:2005}. In these models, the fast stellar wind is
-present in the polar directions, and at the same time the slower disc
-wind is present near the equatorial plane.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
 \label{fig:effect_inclination_compare}
-
 \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Despite the inclination angle dependency of the observed H$\alpha$
+favouring the models with bipolar wind, there are two main aspects
+of this model are not quite consistent with the magneto-centrifugal
+launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
+First, in section~\ref{sub:model-acc-disc-wind}, we found that the
+ratio of the mass-loss to mass-accretion rates needed to be rather
+small ($\mu<\sim0.025$), in order not to have an unrealistically
+strong P-Cyg absorption component, compared to the MHD simulations
+suggested \citep{koenigl:2000} i.e. $\mu\approx0.1$. 
+%In the model
+%fit of T~Tau observation (section~\ref{sub:ttau-model}), we found
+%much larger value of the ratio $\mu=0.18$. 
+Considering large uncertainty in MHD theories and observational
+measurements (e.g.~$\dot{M}_{\mathrm{acc}}$, 
+$\dot{M}_{\mathrm{wind}}$ and $B$), the wide range of the mass-loss
+to mass-accretion ratio 
+%(e.g.~$0.025<\mu<0.18$) 
+may be still reasonable. On the other hand, the models with the disc
+wind (section~\ref{sub:result-discwind-knigge}) 
+using $\mu=0.1$ reproduces the profiles (Figure~\ref{fig:atlas_discwind_acc_model})
+similar to that seen in observations. Second, the MHD models predict
+that the wind/jet becomes collimated well above the disc plane ($>10$~AU),
+but our bipolar wind model are collimated (density enhanced toward
+in the polar direction) from right outside of the magnetosphere. Unless
+the origin of the wind is from the central star itself, the density
+distribution used for the bipolar wind is not quite consistent with
+the near field of the MHD jet models, considering that the most of
+the H$\alpha$ emission occurs within a few to a several radii of
+the magnetosphere (Figure.~\ref{fig:effect_alpha_disc}). The density
+structure used for the disc wind model, however, is very similar to
+that of MHD simulations in the near field where the most of the H$\alpha$
+wind emission occurs. Interestingly, however, the recent study of
+\citet{matt:2005} demonstrated the possibility that the stellar wind along
+the open magnetic field originating from the star can cause significant
+spin-down torque on the star, provided that mass-loss rate is high
+enough. Considering the issues mentioned above, it is not possible
+to favour the bipolar wind model to the disc wind model without further
+observational constraints. In reality, two types of the winds (bipolar
+wind and disc wind) may co-exits similar to that seen in e.g. \citet*{drew:1998}
+and \citet{matt:2005}. In these models, the fast stellar wind is
+present in the polar directions, and at the same time the slower disc
+wind is present near the equatorial plane.
 
@@
 basic physical conditions that reproduce the profiles in each classified
-type. Using the hybrid model, we also fit the observed H$\alpha$
-from the optical component of T~Tau triple system (T~Tau~N). The
-agreement between the model and the observation is excellent; however,
-we could not confirm the uniqueness of the fit. The ratio of the mass-loss
-to mass-accretion rate was found to be $\sim0.18$, which is consistent
-with \citet{koenigl:2000}.
-
-Although not attempted in this paper, a better approach for determining
-the mass-loss and mass-accretion rate consistently is to model multiples
-lines simultaneously. For example, the mass-accretion rate of an object
-can be determined more easily by modelling Pa$\beta$ and Br$\gamma$
-since there is no/little wind effect seen in these lines. The mass-accretion
-rate then can be used to model H$\alpha$ to find the wind mass-loss
-rate.
+type. Using the diffrent combinations of the inclination ($i$), the
+mass-loss to mass-accretion rate ratio ($\mu$) and the wind
+acceralation rate ($\beta$), our radiativel transfer model was able to
+produce all 7 types of the profiles in  \citet{reipurth:1996}. 
+%Using the hybrid model, we also fit the observed H$\alpha$
+%from the optical component of T~Tau triple system (T~Tau~N). The
+%agreement between the model and the observation is excellent; however,
+%we could not confirm the uniqueness of the fit. The ratio of the mass-loss
+%to mass-accretion rate was found to be $\sim0.18$, which is consistent
+%with \citet{koenigl:2000}.
+%
+%Although not attempted in this paper, a better approach for determining
+%the mass-loss and mass-accretion rate consistently is to model multiples
+%lines simultaneously. For example, the mass-accretion rate of an object
+%can be determined more easily by modelling Pa$\beta$ and Br$\gamma$
+%since there is no/little wind effect seen in these lines. The mass-accretion
+%rate then can be used to model H$\alpha$ to find the wind mass-loss
+%rate.
 
@@
 Ae/Be and brown dwarfs since their H$\alpha$ observations also exhibit
-evidences of the outflow and inflow (e.g.~\citet{finkenzeller:1984};
+evidence of the outflow and inflow (e.g.~\citet{finkenzeller:1984};
 \citealt{muzerolle:2005}), but no model has been developed to explain
@@
 
-Future works should include the followings: (1)~Improving the wind
+Future work should include the followings: (1)~Improving the wind
 models. The parametrisation of the wind density structure should be
@@
 \citealt{martin:1996}). (2)~Computing the line profiles using the
-density structure from MHDs directly. Check the consistency, and give
+density structure from MHD directly. Check the consistency, and give
 feedback to the MHD models which are needed to be tested against observational

### 2006-01-11 TTau_Halpha/tmp.tex
Corrections made after Tim's comments. The subsection on the fits of T Tau is eliminated from kurosawa.tex.  The subsection was saved in a separate tex file: ttau_model_subsec.tex.  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@616 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \documentclass[oneside,english,useAMS, usenatbib]{mn2e}
-\usepackage[T1]{fontenc}
-\usepackage[latin1]{inputenc}
+%\usepackage[T1]{fontenc}
+%\usepackage[latin1]{inputenc}
 \setcounter{tocdepth}{3}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{lscape}
 \usepackage{times}
@@
 
-We investigate the formation of H$\alpha$ from classical T~Tauri
-stars with a complex circumstellar geometry -- the combination of
-mangnetisherical accretion, collimated steller wind, and accretion
-disc. AND MORE
+We present  radiative transfer models of classical T~Tauri stars, and investigate the formation of H$\alpha$
+in order to understand their complex circumstellar environment, and to explain
+the wide variety of emission line profiles seen in observations. To
+overcome the limited applicability of the radiative transfer models
+with only magnetospherical accretion to fitting observed H$\alpha$
+profiles, and to any other lines affected by the stellar wind) presented,
+two types of kinematic wind models are introduced: (1)~the bipolar
+wind model in which the wind is originated from the star itself, and
+(2)~the disc-wind model in which the wind originates from the inner
+part of the accretion disc. We perform systematic investigations of
+the model parameters for the wind and the magnetosphere to search
+for possible geometrical and physical conditions which lead to the
+types of profiles seen in observations. We find both wind models
+can reproduce the wide range profile types seen is observations, 
+although the inclination dependence of the line equivalent width
+predicted by the bipolar wind model agree with trends seen in the
+observation, but the disc-wind model does not. Using the model results,
+we examine the H$\alpha$ spectroscopic classification used by Reipurth
+et.~al , and discuss the basic physical conditions required to reproduce
+the profiles in each classified type. Using the hybrid model, we fit
+the observed H$\alpha$ from the optical component of T~Tau triple
+system (T~Tau~N), and find its ratio of the mass-loss to mass-accretion
+rate to be $\sim0.18$ with the cold ($T_{\mathrm{wind}}\approx8000\,\mathrm{K}$)
+bipolar wind model .
 
@@
 \begin{keywords}
-stars:formation -- stars: individual: SU Aur -- circumstellar matter -- infrared: stars -- stars: pre-main-sequence
+stars: formation -- circumstellar matter -- radiative transfer -- stars: pre-main-sequence
 \end{keywords}
@@
 T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
-\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
+\citealt{appenzeller:1989}) low-mass stars, and are the progenitors
 of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
@@
 amount of continuum flux in the ultraviolet (UV) and infrared (IR).
-Their spectral energy distribution and polarization data suggest the
-presence of a circumstellar disc, and it plays an important role in
+Their spectral energy distribution and polarisation data suggest the
+presence of a circumstellar disc, which plays an important role in
 regulating dynamics of gas flows around CTTS.
@@
 \citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profles show that the evidence for both outward wind
-flows and inward accretion flows, as seen in the blueshifted absorption
-features in H$\alpha$ profiles and the redshifted inverse P~Cygni
-(IPC) profiles. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
+of CTTS line profiles show evidence for both outward wind flows and
+inward accretion flows, as seen in the blue-shifted absorption features
+in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC) profiles
+respectively. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
 to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
@@
 (e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
-
 Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
@@
 outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
-two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
-and HV~Tau~C) by \citet{appenzeller:2005} show the extended (SCALE?)
-H$\alpha$ emission in the direction perpendicular to the obscuring
-circumstellar disc, and in both above and below the disc --- suggesting
-the presence of the bipolar outflows. In silightly larger scale, \emph{HST}
-observation of HH30 (Burrorws et al 1996) shows the jet traced to
-within $\lesssim30$~AU from the star. The jet has a cone shape with
-an opening angle of $3^{\circ}$ between 70 and 700 AU. (Originally
-from Konig and Pudritz 2000 review in PP IV). \citealt{alencar:2000}
-found about 80 per cent of their samples (30 CTTS) show blueshifted
-absorption componets in at least one of Balmer lines and Ca~K (most
+Similarly, ESO VLT observation of high-resolution ($R=50\,000$)
+two-dimensional spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
+and HV~Tau~C) by \citet{appenzeller:2005} show the extended H$\alpha$
+emission in the direction perpendicular to the obscuring circumstellar
+disc, and in both above and below the disc --- suggesting the presence
+of the bipolar outflows. On a larger scale, \emph{HST} observation
+of HH30 \citet{burrows:1996} shows the jet traced to within $\lesssim30$~AU
+from the star. The jet has a cone shape with an opening angle of $3^{\circ}$
+between 70 and 700 AU \citep{koenigl:2000}. \citet{alencar:2000}
+found about 80 per cent of their samples (30 CTTS) show blue-shifted
+absorption components in at least one of Balmer lines and Ca~K (most
 commonly in H$\alpha$).
 
-In a currently favoured model of accretion flows around CTTS, the
+In the currently favoured model of accretion flows around CTTS, the
 accretion discs are disrupted by the magnetosphere of stars which
 channels the gas from the disc onto the surface of the stars (e.g.,
-\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993}\citealt{shu:1994}).
-This picture of the accretion flows is supported by the evidences
-that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$) magnetic
-field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
+\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993};
+\citealt{shu:1994}). This picture of the accretion flows is supported
+by the evidences that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$)
+magnetic field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
 and by the radiative transfer models which reproduce the observed
 profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
-accretion model naturally explains the blueward asymmetic emission
-lines (seen in some of CTTS) caused by the partial occulation of the
-flow by the disc, and the redshifted absorption componet at the typical
-free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$) seen
-in some of CTTS.
-
-Dispite the success of the magnetosherical accretion model in explaining
-the line profiles in some CTTS, the overwhelming observational evidences
-for the outflow (mentoned above) in the CTTS profiles suggests that
-this model is only a part of a whole picture. Clearly, the modefification
-to include the outflowing wind/jet flow is neccessary if one requires
-to predict the mass-accretion rate and the mass-loss rate of CTTS
-by modelling their emission profiles (e.g. H$\alpha$).
+accretion model naturally explains the blue-ward asymmetric emission
+lines (seen in some of CTTS) caused by the partial occultation of
+the flow by the disc, and the redshifted absorption component at the
+typical free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$)
+seen in some of CTTS. Despite the success of the magnetospherical
+accretion model in explaining the line profiles in some CTTS, the
+overwhelming observational evidences for the outflow (mentioned above)
+in the CTTS profiles suggests that this model is only a part of a
+whole picture. Clearly, the modification to include the out-flowing
+wind/jet flow is necessary if one requires to predict the mass-accretion
+rate and the mass-loss rate of CTTS by modelling their emission profiles
+(e.g. H$\alpha$).
 
@@
 been considered to explain the observed spectroscopic features mentioned
-earlier. For example, 1.~the Alfv\'{e}n wave-driven wind model (e.g.~\citealt{decampli:1981};
-\citealt{hartmann:1982}), 2.~turbulant boundary layer (between the
-accretion disc and stellar surface) model (e.g.~\citealt{bertout:1988};
-\citealt{basri:1989}), 3.~chromospheric model (e.g.~\citealt{calvet:1984}),
-and 4.~disc wind model (e.g. \citealt{calvet:1992b}; \citealt{kwan:1995}).
-Considering the sucess of the magnetospherical accretion flow model
-in some cases and the observational eividences for the outflows, it
-is likely that an improved spectroscopic model requires both inflow
-and outflow components. The combination of the magnetospheric accretion
-flow model with model 1 or 4 would be a reasonable starting point
-for an improved spectroscopic model. Although time consuming to explore
-a larger parameter space, more realistic density, velocity and temperature
-structure from magnetohydrodynamic wind+accretion models should be
-considered as inputs for an radiative transfer model in the future.
-
-The magnetocentrifugal wind model, first proposed by \citet{blandford:1982},
+earlier. For example, (1)~the Alfv\'{e}n wave-driven wind model
+(e.g.~\citealt{decampli:1981}; \citealt{hartmann:1982}), (2)~turbulent
+boundary layer (between the accretion disc and stellar surface) model
+(e.g.~\citealt{bertout:1988}; \citealt{basri:1989}), (3)~chromospheric
+model (e.g.~\citealt{calvet:1984}), and (4)~disc wind model (e.g.
+\citealt{calvet:1992b}; \citealt{kwan:1995}). Considering the success
+of the magnetospherical accretion flow model in some cases and the
+observational evidences for the outflows, it is likely that an improved
+spectroscopic model requires both inflow and outflow components. The
+combination of the magnetospheric accretion flow model with model
+1 or 4 would be a reasonable starting point. Although time consuming
+to explore a larger parameter space, more realistic density, velocity
+and temperature structure from magnetohydrodynamic wind+accretion
+models should be considered as inputs for an radiative transfer model
+in the future. Recent work by \citet{alencar:2005} showed the observed
+H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better produced
+by the radiative transfer model which include the collimated disc-wind
+arising from near the inner edge of the accretion disc. \citet{malbet:2005}
+considered the combination of a spherical wind and the accretion disc
+in their radiative transfer model to reproduce Br$\gamma$ from the
+early-type Herbig Be star MWC~297.
+
+The magneto-centrifugal wind model, first proposed by \citet{blandford:1982},
 has been often used to reproduce the large-scale wind structure of
 T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
-by \citealt{burrows:1996}; \citealt{ray:1996}). The lanching of
-the wind from a Keplerian disc is typically done by treating the equaotorial
-plane of the disc as a mass-injecting boundary condition (e.g., \citealt{ustyugova:1995};
-\citet{shu:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
+by \citealt{burrows:1996}; \citealt{ray:1996}). The launching of
+the wind from a Keplerian disc is typically done by treating the equatorial
+plane of the disc as a mass-injecting boundary condition (e.g., \citealt{shu:1994};
+\citealt{ustyugova:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
 Depending on the location of the open magnetic fields anchored to
-the disc, two different types of winds are preoduced. If the field
+the disc, two different types of winds are produced. If the field
 is constrained to be near the co-rotation radius of stellar magnetosphere,
@@
 Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
-and \citet{pudritz:2005}.
-
-In this paper, we present a semi-emperical wind -- accretion disc
--- magnetospherical accretion hybrid model for CTTS, and perform parametric
-studies of the H$\alpha$ formation. This study should provide preliminary
-physical conditions which lead to the wide varaiety of emission line
-profiles seen in the observation, and would help to construct more
-comprehensive circumstellar models (e.g. via MHD simulations) of T~Tauri
-stars. the Using the model results, we examine the H$\alpha$ spectroscopic
-classification used by \citet{reipurth:1996}, and compare models
-with observations. We will also discuss whether our model is consistent
-with some predictions made by the recentt MHD studies (e.g.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$).
+and \citet{pudritz:2005}. Interestingly, \citet{matt:2005} showed
+the possibility that the stellar wind along the open magnetic field
+originating from the star can cause significant spin-down torque on
+the star, provided that mass-loss rate is high enough.
+
+The main aim of this paper is to find a simple kinematic model which
+can reproduce the wide variety of the observed profiles, and to perform
+the empirical studies of the line formation. More specifically, we
+present disc--wind--magnetosphere hybrid models for CTTS, and perform
+parametric studies of the H$\alpha$ formation. This study should
+provide preliminary physical conditions which lead to the wide variety
+of emission line profiles seen in the observation, and would help
+to construct more comprehensive circumstellar models (e.g. via MHD
+simulations) of T~Tauri stars. the Using the model results, we examine
+the H$\alpha$ spectroscopic classification used by \citet{reipurth:1996},
+and compare models with observations. We will also discuss whether
+our model is consistent with some predictions made by the recent MHD
+studies i.e.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
+(e.g.~\citealt{koenigl:2000}).
 
 In section~\ref{sec:model-configuration}, the model assumptions,
-and the basic model configurations are presented. We discuss the radiaive
+and the basic model configurations are presented. We discuss the radiative
 transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
@@
 
-To understand how the different part of the CTTS circumsterllar enviroment
-contributes to the fomation of H$\alpha$, the model spaced is devided
-into four different regions: 1.~Central contiuum source, 2.~magnetosphere
-accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:overview}
+To understand how the different part of the CTTS circumstellar environment
+contributes to the formation of H$\alpha$, the model spaced is divided
+into four different regions: 1.~Central continuum source, 2.~magnetosphere
+accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:config_dipolar}
 depicts the relative location in the model space. In all regions,
-the density is symmetric around the z-axis. The innermost raius of
-the magnetsphere at the equotrial plane coincides with the the inner
+the density is symmetric around the z-axis. The innermost radius of
+the magnetosphere at the equatorial plane coincides with the the inner
 radius of the accretion disc. From the inner most part of the accretion
-disc, the gas freely fall, moving along the magneic filed onto the
+disc, the gas freely fall, moving along the magnetic filed onto the
 surface of the star. For the purpose of computational simplicity,
-the colliminated wind are defined only in the outside of the largest
-radius of the magnesophere. In the following subsections, the details
-of model components will be described.
+the collimated bipolar wind are defined only in the outside of the
+largest radius of the magnetosphere (to avoid overlapping of the wind
+with the magnetosphere). In the following subsections, the details
+of model components will be described. In our models, two different
+types of the wind configurations are considered: (1)~the bipolar
+wind resembling the density structure of the MHD simulation by \citealt{krasnopolsky:2003}
+in large scale ($\sim100$~AU) in section~\ref{sub:wind_jet}, and
+(2) that in small scale ($\sim10$~AU) in section~\ref{sub:Alternative-model-disc-wind}.
 
@@
 \includegraphics[%
-  scale=0.6]{figures/overview2.eps}
+  scale=0.5]{figures/overview3.eps}
 
@@
 \caption{Basic Model Configuration.
-The system consist of four components: 1.~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, 2.~magnetospherical accretion flow, 3.~colliminated wind/jet outflow, and 4.~accretion disc.
+The system consist of four components: (1)~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, (2)~magnetospherical accretion flow, (3)~bipolar wind outflow, and (4)~accretion disc.
 The density distribution is symmetric around the z-axis.
@@
 From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star.
-For simplicit, the colliminated wind/jet exists outside of the largest radius of the magnesophere (dotted line).
+For a computational simplicity, the bipolar wind starts from just outside of the largest radius ($R_{\mathrm{mo}}$) of the magnesophere (dotted line).
 }
 
-\label{fig:overview}
+\label{fig:config_dipolar}
 
@@
 
-\subsection{Contiuum Source}
-
-\label{sub:Contiuum-Source}
+\subsection{Continuum Source}
+
+\label{sub:Continuum-Source}
 
 Unless specified otherwise, we adopt stellar parameters of a typical
-classical T~Tauri star (REF) for the central conitnuum source, i.e.
-radius ($R_{*}$), mass ($M_{*}$), and effective temperature the
-photosphere ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$,
-and $4000\,\mathrm{K}$ respectively. The model atomsphere of \citet{kurucz:1979}
-equivallently \citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$
-and $\log g_{*}=3.5$ (cgs) is used to continuum flux at H$\alpha$wavelength.
-The parameters are summarised in Table~\ref{tab:std_parameters}.
-
-The limb-darkening law used for the continuum source is $I\left(\mu\right)=I_{0}\left(1+b\mu\right)$
-where $\mu=\cos\theta$ and $\theta$ is the polar angle. $b$ is
-a parameter. For no limb-darkening case, $b=0$, and for the Eddington
-approximation case $b=3/2$. The former is used in all the calulcations
-presented here. (Is this an ok assumption for T Tauri's? You need
-to check this.)
+classical T~Tauri star for the central continuum source, i.e. radius
+($R_{*}$), mass ($M_{*}$), and effective temperature the photosphere
+($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$, and $4000\,\mathrm{K}$
+respectively. The model atmosphere of \citet{kurucz:1979} equivalently
+\citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$ and
+$\log g_{*}=3.5$ (cgs) is used to find the photospheric continuum
+at H$\alpha$ wavelength. The parameters are summarised in Table~\ref{tab:std_parameters}.
+
+For a model which includes magnetospherical accretion, an additional
+source of the continuum source is considered. As the in-falling gas
+becomes closer to the stellar surface, it is decelerates in a strong
+shock, and heated to $\sim10^{6}\,\mathrm{K}$ (with typical parameters).
+The X-ray radiation produced in the shock will be absorbed by the
+gas located near, and re-emitted in optical and UV radiation (\citealt{koenigl:1991};
+\citealt{hartmann:1994}). This will create hot rings near the stellar
+surface where the magnetic field intersects with the surface. For
+simplicity, the free-falling kinetic energy is assumed to be thermalized
+in the radiating layer, and re-emits as blackbody radiation (with
+a single temperature). With the parameters of the magnetosphere and
+the star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
+of the surface is covered by the hot rings, and its temperature is
+about $6400\,\mathrm{K}$. If the mass-accretion rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$,
+the ratio of this accretion luminosity to the photospheric luminosity
+is about $0.5$. The continuum emission from the hot rings is taken
+into account when computing the line profiles.
 
@@
 
-\begin{tabular}{lcccccccccccc}
+\begin{tabular}{lccccccccccc}
 \hline 
@@
 $\dot{M}_{\mathrm{wind}}$&
-$\beta$&
 $v_{\infty}$&
-$m$&
+$b$&
 $R_{\mathrm{di}}$&
@@
 $\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$[-]$&
 $[\mathrm{km\, s^{-1}}]$&
 $[-]$&
-$\left[R_{\sun}\right]$&
+$\left[R_{*}\right]$&
 $\left[\mathrm{AU}\right]$\tabularnewline
@@
 $10^{-8}$&
-$0.2$&
-$200$&
-$2.0$&
-$2.0$&
+$210$&
+$4.0$&
+$2.2$&
 $100$\tabularnewline
@@
 flow does not affect the underlying magnetic field itself. As shown
-in Fig.~\ref{fig:overview}, the innermost radius ($R_{\mathrm{mi}}$)
-of the magnetophere at the equatorial plane ($z=0$) is assigned to
-be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
+in Fig.~\ref{fig:config_dipolar}, the innermost radius ($R_{\mathrm{mi}}$)
+of the magnetosphere at the equatorial plane ($z=0$) is assigned
+to be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
 disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
 and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
-the equaotrial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
-respectively. The former value corresponds to the corotation radius
+the equatorial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
+respectively. The former value corresponds to the co-rotation radius
 of the accretion disc, and the geometry of the magnetic field/stream
-lines is kept constant throghout this paper. The geometry of the magnetosphere
-is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
+lines is kept constant throughout this paper. The geometry of the
+magnetosphere is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
 
 The magnetic field and the gas stream lines are assumed to have the
-following simple form: $r=R_{\mathrm{m}}\sin^{2}\theta$ \citep[see][]{ghosh:1977}
-where $r$, and $\theta$ are coordinates of the field point ($p$)
-in Fig.~\ref{fig:overview} in spheical coodinates, and $R_{\mathrm{m}}$is
-the radial distance to the field line at the equotorial plane ($\theta=\pi/2$).
-The range of $R_{\mathrm{m}}$is restricted between $R_{\mathrm{mi}}$
-and $R_{\mathrm{mo}}$ as mentioned above. Using the field geometry
-above, the conservation of energy, and igoring the rotation of magnetosphere,
-the velocity and the density of the accreting gas along the steam
-line can be found. See \citet{hartmann:1994} for details.
-
-In all of our models, the temperature structure of the magnetospheric
-used by \citet{hartmann:1994} is also adoped here. The temperature
-structure was computed assuming a volumetric heating rate which is
-proportional to $r^{-3}$, and using the energy balance of the radiative
-cooling rate of \citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
-Although the temperature structure of the accretion steam could significantly
-affect the line source function, for the purpose of the expolaring
-the general characteristics of the H$\alpha$ formation, this simple
-form is a reasonable assumption.\citet{martin:1996} presented the
-self-consistent determination of the thermal structure of the inflowing
-gas along the dipole magnetic field, same as the one used here, by
-solving the heat equation couple to trate equations for hydrogen.
-He found that main heat source is adiabatic compression due to the
-convering nature of the flow, and the major contirbutors of the cooling
-process are bremsstrahling radiation and line emission from Ca~II
-and Mg~II ions. The temerature sturcture of \citet{martin:1996}
-qualitaively agrees with that of \citep{hartmann:1994}. The sensitivty
-tests of H$\alpha$ on the temperature structure will be presented
-later (SPECIFY THE SECTION LATER).
-
-As the infalling gas becomes closer to the stellar surface, it is
-decelerates in a strong shock, and heated to $\sim10^{6}\,\mathrm{K}$
-(with typical parameters). The X-ray radiation produced in the shock
-will be absorbed by the gas located near, and reemitted in optical
-and UV radiation (\citealt{koenigl:1991}; \citealt{hartmann:1994}).
-This will create hot rings near the stellar surface where the magnetic
-field intersects with the surface. For simplicity, the free-falling
-kinetic energy is assumed to be thermalized in the radiating layer,
-and reemits as blackbody radiation (with a single temerature). With
-the parameters of the magnetosphere and the star given above (Table~\ref{tab:std_parameters}),
-about $8$~per~cent of the surface is covered by the hot rings,
-and its temperature is about $6400\,\mathrm{K}$. If the mass-accretion
-rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this
-accretion luminosity to the photospheric luminosity is about $0.5$.
-The contiuum emission from the hot rings is taken into account when
-computing the line profiles.
-
-\subsection{Wind}
+following simple form: \begin{equation}
+r=R_{\mathrm{m}}\sin^{2}\theta\label{eq:dipole}\end{equation}
+ \citep[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
+of the field point ($p$) in Fig.~\ref{fig:config_dipolar} in spherical
+coordinates, and $R_{\mathrm{m}}$is the radial distance to the field
+line at the equatorial plane ($\theta=\pi/2$). The range of $R_{\mathrm{m}}$is
+restricted between $R_{\mathrm{mi}}$ and $R_{\mathrm{mo}}$. Using
+the field geometry above and the conservation of energy, the velocity
+and the density of the accreting gas along the steam line are found
+as in \citet{hartmann:1994}.
+
+The temperature structure of the magnetospheric used by \citet{hartmann:1994}
+is simply adopted here. They computed the temperature assuming a volumetric
+heating rate which is proportional to $r^{-3}$, and using the energy
+balance of the radiative cooling rate of \citet{hartmann:1982} and
+the heating rate \citep{hartmann:1994}. Although the temperature
+structure of the accretion steam could significantly affect the line
+source function, for the purpose of the exploring the general characteristics
+of the H$\alpha$ formation, this simple form is a reasonable assumption.
+\citet{martin:1996} presented the self-consistent determination of
+the thermal structure of the in-flowing gas along the dipole magnetic
+field (equation~\ref{eq:dipole}) by solving the heat equation couple
+to rate equations for hydrogen. He found that main heat source is
+adiabatic compression due to the converging nature of the flow, and
+the major contributors of the cooling process are bremsstrahlung radiation
+and line emission from Ca~II and Mg~II ions. The results of \citet{martin:1996}
+qualitatively agrees with that of \citet{hartmann:1994}.
+
+\subsection{Bipolar Wind}
 
@@
 
-\subsubsection{Colliminated wind model}
-
-JUSTTIFICATION OF USING THIS FORMULATION. BREIFLY MENTIONED THE WORK
-DONE BY OTHERS.
-
-Based on the simple model of \citet{appenzeller:2005}, the following
-parametrisation of colliminated wind/jet (region 3 in Fig.~\ref{fig:overview})
-is adopeted. The wind velocity field, $\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$,
-is consist of radial and polar components which depend only on $r$
-and $\theta$ respectively. The radial componet $v_{r}\left(r\right)$
-is assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
-and the azimuthal component $v_{\phi}$ is asuumed to be a constant
+As mentioned earlier, the wind model presented here is to simulate
+the collimated MHD disc-wind model of \citet{krasnopolsky:2003} in
+large scale ($\sim100$~AU) , and the alternative wind model which
+resembles the model of \citet{krasnopolsky:2003} in small scale ($\sim10$~AU)
+will be presented later (section~\ref{sub:Alternative-model-disc-wind}).
+
+Similar to the simple wind model of \citet{appenzeller:2005}, the
+following parametrisation of collimated bipolar wind (region 3 in
+Fig.~\ref{fig:config_dipolar}) is adopted. The wind velocity field,
+$\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$, is consist of
+radial and azimuthal components which depend on the spherical coordinates
+$r$ and $\theta$. The radial component $v_{r}\left(r\right)$ is
+assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
+and the azimuthal component $v_{\phi}$ is assumed to be a constant
 fraction ($\gamma$) of the Keplerian velocity for a given distance
@@
 \begin{eqnarray}
-\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}+v_{\theta}\hat{\btheta}\label{eq:wind_velocity_def}\end{eqnarray}
+\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}\label{eq:wind_velocity_def}\end{eqnarray}
 where \begin{equation}
-v_{r}\left(r\right)=v_{r0}+v_{\infty}\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
+v_{r}\left(r\right)=v_{r0}+\left(v_{\infty}-v_{r0}\right)\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
 \begin{equation}
 v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
-and \begin{equation}
-v_{\theta}\left(r,\theta\right)=v_{\theta0}\,\left(\frac{R_{\mathrm{mo}}}{r}\right)^{\alpha}\frac{\tan\theta}{\left|\tan\theta\right|}\,.\label{eq:wind_velocity_polar_part}\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$, and
-the range of the polar angle is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
-where $\theta_{\mathrm{disc}}$ is the openning angle of the accretion
+Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This
+is chosen so mainly for computational simplicity i.e. to avoid the
+overlap between the wind and the magnetosphere; however, see \citet{matt:2005}
+for the possibility that wind originates from the stellar surface
+(restricted near the polar caps). The range of the polar angle for
+the wind is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
+where $\theta_{\mathrm{disc}}$ is the opening angle of the accretion
 disc, to avoid the overlap. $v_{r0}$is the small radial velocity
-at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$,
-approximately the thermal velocity of hydrogen with $T=7500\,\mathrm{K}$
-and $\gamma=0.05$ (\citealt{appenzeller:2005}) are used. The dependency
-of $v_{r}$ in polar direction ($\theta=0$) on the values of wind
-accerelation parameter $\beta$ is shown in Figure~\ref{fig:wind_vr_rho}.
-All other parameters describing the wind are fixed as the standard
-values given in Table~\ref{tab:std_parameters}.
+at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
+which is approximately equal to the thermal velocity of hydrogen with
+$T=7500\,\mathrm{K}$. Following \citet{appenzeller:2005}, $\gamma=0.05$
+is adopted. The dependency of $v_{r}$ in polar direction ($\theta=0$)
+on the values of wind acceleration parameter $\beta$ is shown in
+Figure~\ref{fig:wind_vr_rho}. All other parameters describing the
+wind are fixed as the standard values given in Table~\ref{tab:std_parameters}.
 
 Further, the density of the wind is assumed to be axi-symmetric and
-separable in $r$ and $\theta$ for computationaly simpliciy, i.e.,
+separable in $r$ and $\theta$ for computational simplicity, i.e.,
 
@@
  where $b$ is normally positive even number (for the density symmetric
-about the equtotrial plane), and $n$ is the angular normalisation
-constant. For $b=0$, the wind is sherically symmetic exept for the
-parts dirupted by the accretion disc. The larger the value of $b$,
-the higher the degree of the collimination. By integrating equation~\ref{eq:wind_density_theta}
+about the equatorial plane), and $n$ is the angular normalisation
+constant. For $b=0$, the wind is spherically symmetric except for
+the parts disrupted by the accretion disc. The larger the value of
+$b$, the higher the degree of the collimation. By integrating equation~\ref{eq:wind_density_theta}
 over angles and normalising the integral to $4\pi$, one finds \begin{equation}
 n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
- Asumming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
+ Assuming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
 and the mass-flux conserves in time, the radial part of the density
@@
 hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
-\rho\left(r,\theta\right)=\frac{n\,\cos^{b}\theta\,\dot{M}_{\mathrm{wind}}}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
+\rho\left(r,\theta\right)=\frac{n\,\dot{M}_{\mathrm{wind}}\,\cos^{b}\theta}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
  For a given mass-accretion rate, the wind mass-loss rate in our typical
-model is assined from the ratio of mass-loss to mass-accretion rate
+model is assigned from the ratio of mass-loss to mass-accretion rate
 ($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
-by both observations and magnetohydrodynamical calculations (see e.g.
-\citealt{koenigl:2000}).
-
-Figure~\ref{fig:wind_vr_rho} shows the values of $\rho$ in polar
-direction ($\theta=0$) for different values of $\beta$ with all
-other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
+by both observations and MHD calculations (e.g. \citealt{koenigl:2000}).
+Figure~\ref{fig:wind_vr_rho} shows the density along a streamline
+in the polar direction ($\theta=0$), for different values of $\beta$
+with all other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
+The density is relatively sensitive to the value of $\beta$ for $r<10\, R_{\mathrm{mo}}$,
+but a little difference is seen beyond $r<100\, R_{\mathrm{mo}}$.
 
@@
 
-\caption{The dependency of the wind/jet velocity and density structures on the wind accerelation parameter $\beta$.
-The radial component of the wind/jet velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left.
-The wind/jet density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is right.
+\caption{The dependency of the bipolar wind velocity and density structures on the wind accerelation parameter $\beta$.
+The radial component of the wind  velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left.
+The wind density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is shown on right.
+For all $\beta$ values, the density is normalized to the desnity at the base of the wind in polar direction, i.e.
+$\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.
 The smaller the value of $\beta$, the faster the accerelation of the wind.
@@
 
-\subsubsection{Disc-wind model}
-
-GIVE MORE CONVINCING MOTIVIATION FOR USING THIS MODEL. THIS SECTION
-MAY BE DELETED.
-
-Alternative to the colliminated wind model, the kinematic disc-wind
-mode of \citet{knigge:1995} in which a wind originating from the
-surface of the accretion disc with a biconical outflow geometry (Fig.~XXX)
-will be presented next. The model was originally developed for describing
-the formation of the UV resonance lines in the winds of cataclystic
-variable (CV) stars.
-
 \subsection{Accretion disc}
@@
 
-Region 4 in Fig.~\ref{fig:overview}
-
-\subsubsection{Density and velocity}
-
-Although it is possible, in our model, to compute the dust-sublimination
+Although it is possible, in our model, to compute the dust-sublimation
 radius and the vertical hydrostatic structure of the accretion disc
-self-consistently (assuming the radial dependecy of the mid-plane
-density) by using the interative Monte Calro radative transfer technique
+self-consistently (assuming the radial dependency of the mid-plane
+density) by using the iterative Monte Carlo radiative transfer technique
 (c.f.~\citet{walker:2004}), we find it to be too time consuming
@@
 with the inner radius fixed at the inner radius of the magnetosphere
-(at equatorial plane). The disc density disribution is given by
+at equatorial plane. This corresponds to Region 4 in Fig.~\ref{fig:config_dipolar}.
+
+\subsubsection{Density and velocity}
+
+The disc density distribution is given by
 
@@
 density and the scale height are given as: \begin{equation}
-\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{d}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
+\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
  where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
@@
 of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
-radius of the magnetosphere at the equaotrial plane), which is approximatly
-same as the co-rotating radius of the system with the paramters in
+radius of the magnetosphere at the equatorial plane), which is approximately
+same as the co-rotating radius of the system with the parameters in
 Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
@@
 
+\subsection{Alternative model: disc-wind model of \citet{knigge:1995}}
+
+\label{sub:Alternative-model-disc-wind}
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  scale=0.32]{figures/discwind.eps}
+
+\end{center}
+
+\caption{Basic Model Configuration of the disc-wind, magnetosphere hybrid model.
+The system consist of four components: (1)~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, (2)~magnetospherical accretion flow, (3)~colliminated wind/jet outflow, and (4)~geometrically thin (but opaque) accretion disc.
+The disc wind originates from the disc surface between $w_{i}=R_{wi}$ and $w_{i}=R_{wo}$.
+The wind source points ($S$), from which the stream lines diverges, are placed at distance $d$ above and below the star.
+By changing the value of $d$,  the degree of the wind collimation is controlled.
+The density distribution is symmetric around the z-axis.
+}
+
+\label{fig:config_discwind}
+
+\end{figure}
+
+The wind model presented here is to simulate the collimated MHD disc-wind
+calculations of \citealt{krasnopolsky:2003} in small scale ($\sim10$~AU).
+\citet{knigge:1995} introduced the {}``split-monopole'' kinematic
+disc-wind model in their studies of the UV resonance lines formed
+in the winds of cataclysmic variable stars. In this model, the outflow
+arises from the surface of the rotating accretion disc, and has a
+biconical geometry. The specific angular momentum is assumed to be
+conserved along a stream line, and the poloidal velocity component
+is assumed to be simply a radial from vertically displaced {}``sources''
+from the central star. We adopt their disc-wind model here, and consider
+the combined effect of the disc-wind and the magnetospherical accretion
+flow model described earlier. In the following, we briefly described
+their disc-wind model. For details of the models, readers are referred
+to \citet{knigge:1995} and \citet{long:2002}.
+
+Four basic parameters for the models are: 1. mass-loss rate, 2.~the
+degree of the wind collimation, 3.~velocity gradients, and 4.~the
+wind temperature. The basic configuration of the disc-wind model is
+shown in Figure~\ref{fig:config_discwind}. The disc wind originates
+from the disc surface, but the {}``source'' point ($S$), from which
+the stream lines diverges, are placed at distance $d$ above and below
+the centre of the star. By changing the value of $d$, the degree
+of the wind collimation is controlled. The larger the value of $d$,
+the wind becomes more parallel to the rotation axis, i.e. the wind
+becomes more collimated. The mass-loss launching is restricted between
+$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ where the former is set
+to be equal to the outer radius of the magnetosphere ($R_{\mathrm{mo}}$)
+for simplicity and the latter is set to $1$~AU as in \citealt{krasnopolsky:2003}.
+
+The local mass-loss rate per unit area ($\dot{m}$) is assumed to
+be proportional to the mid-plane temperature of the disc, and is a
+function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
+, i.e. \begin{equation}
+\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
+ Further, the mid-plane temperature of the disc is assumed to be expressed
+as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
+relation above, one finds \begin{equation}
+\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
+where $p=\alpha\times q$. The index of the mid-plane temperature
+power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
+who found the inner most part of the accretion disc has $q=-1.15$.
+To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
+who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
+of proportionality in equation~\ref{eq:discwind-massloss-w} is found
+by integrating $\dot{m}$ from $R_{\mathrm{wi}}$to $R_{\mathrm{wo}}$,
+and the normalising the total mass-loss rate to $\dot{M}_{\mathrm{dw}}$.
+
+The azimuthal/rotational component of the wind velocity $v_{\phi}\left(w,z\right)$
+is computed from the Keplerian rotational velocity at the emerging
+point of the stream line i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
+where $w_{i}$ is the distance from the rotational axis ($z$) to
+the emerging point on the disc, and by assuming the conservation of
+the specific angular momentum along a stream line: \begin{equation}
+v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
+Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt{castor:1975}),
+the poloidal component of the wind velocity ($v_{p}$) parameterised
+as:
+
+\begin{equation}
+v_{p}\left(w_{i},l\right)=c_{\mathrm{s}}\left(w_{i}\right)+\left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}\label{eq:discwind-poloidal-velocity}\end{equation}
+where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the
+wind launching point on the disc, the constant scale factor of the
+asymptotic terminal velocity to the local escape velocity (from the
+wind emerging point on the disc), and the distance from the disc surface
+along stream lines respectively. $R_{s}$ is the wind scale length,
+and $R_{s}=10\, R_{\mathrm{mi}}$ is adopted as similarly done by
+\citet{long:2002}.
+
+Assuming the mass-flux conservation and using the velocity field defined
+above, the disc wind density as a function of $w$ and $l$ can be
+written as
+
+\begin{equation}
+\rho\left(w_{i},l\right)=\frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}\label{eq:discwind-density}\end{equation}
+where $Q$ and $\delta$ are the distance from the source point ($S$)
+to a point along the stream line and the angle between the stream
+line and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
+shows the density and the velocity components along the mid stream
+line (passing through $w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$
+on the disc plane ($z=0$) for different values of the wind acceleration
+parameter $\beta$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+
+\begin{center}
+
+\begin{tabular}{cc}
+\includegraphics[%
+  clip,
+  scale=0.45]{plots/dw_vp_vphi.eps}~~~~~~&
+\includegraphics[%
+  clip,
+  scale=0.45]{plots/dw_rho.eps}\tabularnewline
+\end{tabular}
+
+\end{center}
+
+\caption{Depdendency of the disc wind density and the velocity on the wind accelreation parameter $\beta$.
+The wind density $\rho$ (left panel) and the poloidal velocity component $V_{p}$ (right panel) along the stream line starting from the mid point of the wind lanching zone, i.e.
+$\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$  where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}} \right ) / 2$,  are shown as a function of the distance ($l$) from the wind lanching point (c.f.~ equations~\ref{eq:discwind-poloidal-velocity} and \ref{eq:discwind-density}).
+The azimuthal velocity component ($V_{\theta}$), which is independent of  $\beta$ (c.f.
+equation~\ref{eq:discwind-toroidal-velocity}), is also shown in the right panel for a comparison.
+The density is normalized to the density $\rho_{0}$ at the wind lanching point for $\beta = 1.0$ case.
+The $v_{p}$ reaches the terminal velocity by 100~AU for all $beta$.
+In the fur field ($l>10$~AU), the density is approximately proportional to $\sim l^2$.
+Up to $l~\sim10$~AU, the density is smaller and the poloidal speed is larger for the wind with a larger $\beta$ value.
+}
+
+\label{fig:discwind_vr_rho}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Radiative transfer model}
@@
 by one or more of the followings: the magnetospherical accretion flow,
-the out-flowing colliminated wind, and the accreation disc. Previously
-in \citet{symington:2005}, the model used in the three-dimentional
-(3-D) adaptive mesh refinement (AMR) to inverstigate the line variability
-mainly associated with roational motion of complex geometrical configurations
+the out-flowing collimated wind, and the accretion disc. Previously
+in \citet{symington:2005}, the model used in the three-dimensional
+(3-D) adaptive mesh refinement (AMR) to investigate the line variability
+mainly associated with rotational motion of complex geometrical configurations
 of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
-modefied the code to handle the two-dimentional (2-D) density distribution,
+modified the code to handle the two-dimensional (2-D) density distribution,
 and restricted our models to be axi-symmetric. It was done so in order
@@
 Note that the velocity field is still in 3-D -- the third component
-can be calculated by using the symmetry for a given value of azimutal
+can be calculated by using the symmetry for a given value of azimuthal
 angle. The examples of how the AMR grid for the purpose of the radiative
@@
 
-The computation of the H$\alpha$ is devided in two parts: 1.~the
-source function calculation and 2.~the observed flux/profile calulcation.
-In the first process, we have utilized the method by \citet{klein:1978}
-(see also \citealt{rybicki:1978}; \citet{hartmann:1994}) in which
-the Sobolev approximation method is applied. The population of the
-bound states of hydrogen are assumed to be in statistical equilibrium,
+The computation of the H$\alpha$ is divided in two parts: (1)~the
+source function calculation ($S_{\nu}$) and (2)~the observed flux/profile
+calculation. In the first process, we have utilised the method by
+\citet{klein:1978} (see also \citealt{rybicki:1978}; \citet{hartmann:1994})
+in which the Sobolev approximation method is applied. The population
+of the bound states of hydrogen are assumed to be in statistical equilibrium,
 and the gas to be in radiative equilibrium. Our hydrogen atom model
 consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
-for details. (AND MORE..)
-
-To compute the observed line profile, the Monte Calro radiative transfer
-method (e.g. \citealt{hillier:1991}) using the Soblev escape-probabiliy
-can be used when I.~a large velocity gradiant is present in the gas
-flow, and II.~the intrinsic line width is negleible compared to the
-Doppler broadeing of the line. In our earlier models (\citealt{harries:2000};
+for details.
+
+To compute the observed line profile, the Monte Carlo radiative transfer
+method (e.g. \citealt{hillier:1991}) using the Sobolev escape-probability
+can be used when (1)~a large velocity gradient is present in the
+gas flow, and (2)~the intrinsic line width is negligible compared
+to the Doppler broadening of the line. In our earlier models (\citealt{harries:2000};
 \citealt{symington:2005}), this method was used to compute the line
-profiles since the condition I and II are resonably satisfied. However,
-as noted and demonstrated by \citet{muzerolle:2001}, even with a
-moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
+profiles since the condition (1) and (2) are reasonably satisfied.
+However, as noted and demonstrated by \citet{muzerolle:2001}, even
+with a moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
 Stark broadening becomes important in the optically thick H$\alpha$
-line. \citet{muzerolle:2001} (MORE REF HERE) also pointed out that
-the observed H$\alpha$profiles from CTTS typically have the wings
-extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
+line. \citet{muzerolle:2001} also pointed out that the observed H$\alpha$
+profiles from CTTS typically have the wings extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
 \citet{reipurth:1996}) which cannot be explained by the infall velocity
-of the gas along the magneosphere.
-
-To implement the broadening meachanism, two modedifications to our
-previous model (\citealt{symington:2005}) are necessary. First, the
-emission and absorption profiles must be replaced by a Voigt profle
-which is defined as: \begin{equation}
+of the gas along the magnetosphere alone.
+
+To implement the broadening mechanism, two modifications to our previous
+model (\citealt{symington:2005}) are necessary as similarly done
+by \citet{muzerolle:2001}. First, the emission and absorption profiles
+must be replaced by a Voigt profile which is defined as: \begin{equation}
 H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
@@
 van der Waals broadening, and linear Stark broadening constants respectively.
-We simply adopt this parameterization along with the values of broadening
+We simply adopt this parameterisation along with the values of broadening
 constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
@@
 of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
-of the $j$-th level respectively. $m_{e}$and $e$ are the electron
+of the $j$-th level respectively. $m_{e}$ and $e$ are the electron
 mass and charge (c.f. \citealt{mihalas:1978}).
 
-The second modefication in our model is the replacement of the method
-of solving the formal solution from the Monte Calro radiative transfer
-method with Sobolev approximation to the direct integration method.
-Similarly to the notation used by \citet{muzerolle:2001}, we specify
-the cylindical coordinates $\left(p,\, q,\, t\right)$ which is the
-original stellar coordinate system $\left(\rho,\,\phi,\, z\right)$
-rotated (around $y$ axis) by the inclination of the line of sight,
-i.e. the $t$-axis coinsides with the line of sight. The observed
-flux ($F_{\nu}$) is given by: \begin{equation}
+The second modification in our model is the replacement of the method
+of solving the formal solution from the Monte Carlo radiative transfer
+method with Sobolev approximation to the direct integration method
+(c.f. \citealt{muzerolle:2001}). We specify the cylindrical coordinates
+$\left(p,\, q,\, t\right)$ which is the original stellar coordinate
+system $\left(\rho,\,\phi,\, z\right)$ rotated (around $y$ axis)
+by the inclination of the line of sight, i.e. the $t$-axis coincides
+with the line of sight. The observed flux ($F_{\nu}$) is given by:
+\begin{equation}
 F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
@@
 specific intensity is given by:\begin{equation}
-I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{-\infty}^{t_{0}}\eta_{\nu}\left(t\right)\, e^{-\tau\left(t\right)}\mathrm{d}t\label{eq:formal_sol_integral}\end{equation}
- where $I_{0}$ and $\eta_{\nu}$ are the intensity at the boundary
-on the opposite to the observer and the emissivity of the stellar
-atmosphere/wind at a frequency $\nu$. For a ray which intersects
-with the stellar core, $I_{0}$ is computed from the stellar stompshere
-mode of \citet{kurucz:1979} as descibed in section~\ref{sub:Contiuum-Source},
+I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{t_{0}}^{t_{\infty}}S_{\nu}\left(t\right)\, e^{-\tau}\mathrm{d}\tau\label{eq:formal_sol_integral}\end{equation}
+ where $I_{0}$ and $S_{\nu}$ are the intensity at the boundary on
+the opposite to the observer and the source function ($\eta_{\nu}/\chi_{\nu}$)
+of the stellar atmosphere/wind at a frequency $\nu$. For a ray which
+intersects with the stellar core, $I_{0}$ is computed from the stellar
+atmosphere mode of \citet{kurucz:1979} as described in section~\ref{sub:Continuum-Source},
 and $I_{0}=0$ otherwise. The initial position of each ray is assigned
-to be at the center of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
-The code excution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
-where $n_{p}$ and $n_{q}$ are the number of cylindical radial and
-angluar points for the flux integration, and $n_{\nu}$is the number
+to be at the centre of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
+The code execution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
+where $n_{p}$ and $n_{q}$ are the number of cylindrical radial and
+angular points for the flux integration, and $n_{\nu}$is the number
 of frequency points. In the models presented in the next (section~\ref{sec:Results}),
 $n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
-otherwise. The linearliy spaced radial grid is used for the area where
-the ray intersects with magnetpshere, and the logarithmically spaced
+otherwise. The linearly spaced radial grid is used for the area where
+the ray intersects with magnetosphere, and the logarithmically spaced
 grid is used for the wind and the accretion disc regions.
@@
 is defined as: \[
-\tau\left(t\right)\equiv\int_{-\infty}^{t}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
+\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
  where $\chi_{\nu}$ is the opacity of media the ray passes through.
@@
 are computed at the intersections of a ray with the original AMR grid
-in which the opacity and emissivity infomation are stored. For high
-opticale depth models, additional points are inserted between the
-original points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$
-values are interpolated to those points to ensure $\mathrm{d}\tau<0.05$
-for the all ray segments.
+in which the opacity and emissivity information are stored. For high
+optical depth models, additional points are inserted between the original
+points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$ values are
+interpolated to those points to ensure $\mathrm{d}\tau<0.05$ for
+the all ray segments.
 
@@
 are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
-$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the contiuum,
+$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the continuum,
 line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
@@
 and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
-contribution at H$\alpha$ wavelength is expected to be neglegible
-(e.g.~\citealt{chiang:1997}). The scattering flux by the accretion
-may become important for H$\alpha$ for the edge-on ($i\sim90^{\circ}$)
-cases in which the disc obscures the stellar surface -- the main source
-of contiuum flux. We examine this effect later in section~\ref{sub:model-acc-disc-wind}.
+contribution at H$\alpha$ wavelength is expected to be negligible
+(e.g.~\citealt{chiang:1997}).
 
@@
 Using the standard parameters (Table~\ref{tab:std_parameters}) for
-the central star and the magentosphere, we examine the dependency
+the central star and the magnetosphere, we examine the dependency
 of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
@@
 done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
-is computed from the avilable kinetic energy of the free-falling gas
-as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
+is computed from the available kinetic energy of the free-falling
+gas as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
 used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
@@
 become important. Figure~\ref{fig:broadening} shows an example of
-the effect of the boradening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
+the effect of the broadening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
 and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
@@
 of seen in the model with broadening. A weak red-shifted absorption
-component (which is a signiture of the magnetospherical accretion)
+component (which is a signature of the magnetospherical accretion)
 is weakened or eliminated by the flux in broadened wing.
@@
 of 43 TTS and found similar distribution of EW values, mentioned that
-their EW measurements are underrepresenting real samples since the
-selection of the targerts are based on the strong H$\alpha$ emission
+their EW measurements are under-representing real samples since the
+selection of the targets are based on the strong H$\alpha$ emission
 in H$\alpha$ surveys.
@@
 in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
-paramters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
+parameters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
 and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
-The figure show that the peak (normalized) flux decrease as the inclination
+The figure show that the peak (normalised) flux decrease as the inclination
 angle increases. Similarly, the equivalent width also decreases as
-the inclination increases. Because of the geometry of the magnsepsherical
-accretion (c.f. Figure~\ref{fig:overview}) and of the presence of
-the gas with the highest velocity close to the stellar surface, the
-highest red-shifted line-of-sight velocity is visible only at the
-high incination angles. This explains the wider appearence of the
-profile with $i=80^{\circ}$compared to the relatively narrow line
-appearence of the profile with $i=10^{\circ}$. Although not show
-here, a similar depdency on the inclination angle is found for the
-models with different temperatures ($T_{\mathrm{max}}=6500$, $8500$,
-$9500\,\mathrm{K}$).
+the inclination increases. Because of the geometry of the magnetospherical
+accretion (c.f. Figure~\ref{fig:config_dipolar}) and of the presence
+of the gas with the highest velocity close to the stellar surface,
+the highest red-shifted line-of-sight velocity is visible only at
+the high inclination angles. This explains the wider appearance of
+the profile with $i=80^{\circ}$compared to the relatively narrow
+line appearance of the profile with $i=10^{\circ}$. Although not
+show here, a similar dependency on the inclination angle is found
+for the models with different temperatures ($T_{\mathrm{max}}=6500$,
+$8500$, $9500\,\mathrm{K}$).
 
@@
 our models also show the blue-shifted peak and the blue-ward asymmetry
-caused by the occultation of the accretion flow by the equotrial disc
-and the stellar disc. On the hand, \citealt{alencar:2000} (see their
-Fig.~9) found a substential fraction of the observed H$\alpha$ profiles
-also shows the {}``red-shifted'' peak, and the P~Cygni profiles
-which can not be explained by the magnetospherical accretion model
-alone. In addition, a recent study by \citet{appenzeller:2005} showed
-that the equivalent width of H$\alpha$ increases as the inclination
-angle increases. Our model with the magnetospherical accreation flow
-clearly disagrees with their finding.
+caused by the occultation of the accretion flow by the equatorial
+disc and the stellar disc. On the hand, \citealt{alencar:2000} (see
+their Fig.~9) found a substantial fraction of the observed H$\alpha$
+profiles also shows the {}``red-shifted'' peak, and the P~Cygni
+profiles which can not be explained by the magnetospherical accretion
+model alone. In addition, a recent study by \citet{appenzeller:2005}
+showed that the equivalent width of H$\alpha$ from CTTS increases
+as the inclination angle increases. Our model with the magnetospherical
+accretion flow clearly disagrees with their finding.
 
@@
   clip,
-  scale=0.45]{figures/atlas_ha_i55_acc_model_new3.eps}
-
-\end{center}
-
-\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M_\mathrm{acc}}$) and temperature ($T_{\mathrm{max}}$).
+  scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}
+
+\end{center}
+
+\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M}_\mathrm{acc}$) and temperature ($T_{\mathrm{max}}$).
 The profiles are computed using only magnetospherical accretion flow (i.e.
@@
 \caption{Effect of the line broadening for H$\alpha$.
-The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the one with no damping constant, $\Gamma=0$ (dashed).
+The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the model with no damping, $\Gamma=0$ (dashed).
 Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}.
 The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant.
-The broaded wings extend to $\sim \pm 900 \kmps$.
+The broaded wings extend to $\sim \pm 800 \kmps$.
 The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.
@@
 As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.
-Similar dependency is seen in the models with $T_{\mathrm{max}}=6500, 8500, 9500$~K (not shown here).
+Similar dependency is seen in the models with the wide ranges of $T_{\mathrm{max}}$ and $\beta$ (not shown here).
 }
@@
 
-\subsection{Collimated Wind}
+\subsection{Bipolar Wind}
 
@@
 
-As mentioned in earlier, the magnetopsherical accretion flow model
-alone cannot explain some of the feartures seen in observations. As
-an alternative model, we now examine formation of H$\alpha$ in a
-simple collimated wind as described in section \ref{sub:wind_jet}.
-The basic wind model parameters introduced earlier are $\gamma$,
-$\beta$, $v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
-and $\dot{M}_{\mathrm{wind}}$. To minimize the number of parameters
-to be explored, we initially adopte $\gamma=0.05$, $v_{\infty}=200\,\kmps$
-\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-Futher, the angular extent of the wind is assumed to be close to the
-edge of the accretion disc, i.e. $\theta_{\mathrm{wind}}=80^{\circ}$;
-however, in this section, a simple optically-thick and geometrically-thin
-(i.e. opaque and zero-thickness) disc instead of the standard $\alpha$-disc
-(section~\ref{sub:Accretion-disc}) is used in all models for speed.
-The effect of replacing the geometrically thin disc with the $\alpha$-disc
-will be discussed later in this section. The degree of collimination
-is initially chosen to be $b=4$, i.e. the ratio of the density in
-polar direction to the density at the edge of the wind closest to
-the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
-for given radii. With these parameters kept constant, we examine the
-characterstics of H$\alpha$ profiles, as a function of the wind accereation
-paramter $\beta$ and the isothermal wind temperature $T_{\mathrm{wind}}$.
-Dependency on the other parameters will be discussed later in this
-section.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_model.eps}
+  scale=0.9]{figures/atlas_ha_i55_wind_only_final.eps}
 
@@
 \caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$).
-The profiles are computed with only wind/jet (no magnetospherical accretion flow).
-The parameters of the 'standard' model (Table~\ref{tab:std_parameters}) are used.
+The profiles are computed with only wind (no magnetospherical accretion flow or accretion disc).
+The 'standard' model (Table~\ref{tab:std_parameters}) are applied here.
 The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively.
@@
 
-The results are shown in Figure~\ref{fig:atlas_wind_model}. The
-P~Cygni profile are seen only in the models with lower $T_{\mathrm{wind}}$
-and $\beta$ (colder and faster accerelation wind). As the value of
-$\beta$ increases, the postion of the blue-shifted absorption component
-moves toward the line centre. For the slowest wind accerelation models
-($\beta=4.0$), the absorption components appear to be located at
-the line centre, giving the appearence of the double-peak emission
-profile. The line strength is very senstive to the temperature of
-the wind. Although the line should be also sensitive to the temperature
-structure of the wind itself, determination of a self-consistent wind
-temperature is beyound the scope of this paper. Readers are refered
+As mentioned in earlier, the magnetospherical accretion flow model
+alone cannot explain some of the features seen in observations. As
+an alternative model, we now examine formation of H$\alpha$ in a
+simple bipolar wind as described in section \ref{sub:wind_jet}. The
+basic wind model parameters introduced earlier are $\gamma$, $\beta$,
+$v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
+and $\dot{M}_{\mathrm{wind}}$. To minimise the number of parameters
+to be explored, we initially adopt $\gamma=0.05$, $v_{\infty}=200\,\kmps$
+\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
+Further, the angular extent of the wind (the opening angle of the
+wind) is assumed to be $\theta_{\mathrm{wind}}=80^{\circ}$. The degree
+of collimation is initially chosen to be $b=4$, i.e. the ratio of
+the density in polar direction to the density at the edge of the wind
+closest to the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
+for given radii. For simplicity, the wind temperature $T_{\mathrm{wind}}$
+is assumed to be isothermal\@. Although the line is potentially sensitive
+to the temperature structure of the wind, determination of a self-consistent
+wind temperature is beyond the scope of this paper. Readers are refereed
 to \citet{hartmann:1982} in which the wind temperature structure
 is determined by balancing the radiative cooling rate (assuming optically
-thin) with the MHD wave heating rate.
-
-The effect of line broadening becomes more prominant for higher $T_{\mathrm{wind}}$
-and higher $\beta$ models. Unlike the magnetospherical accretion
+thin) with the MHD wave heating rate. With these parameters kept constant,
+we examine the characteristics of H$\alpha$ profiles, as a function
+of the wind acceleration parameter $\beta$ and the isothermal wind
+temperature $T_{\mathrm{wind}}$. Dependency on the other parameters
+will be discussed later in this section.
+
+Figure~\ref{fig:atlas_wind_model} shows the profile computed at
+a mid inclination angle $i=55^{\circ}$ for the range of the wind
+temperature between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and
+for the range of $\beta$ between $0.2$ and $2.0$. The P~Cygni
+profile are prominent in the models with lower values of $T_{\mathrm{wind}}$
+and $\beta$ (colder and faster acceleration wind). As the value of
+$\beta$ increases, the position of the blue-shifted absorption component
+moves toward the line centre. which can be seen clearly in the $T_{\mathrm{wind}}=7000\,\mathrm{K}$
+models. While the velocity position of absorption component for the
+fastest acceleration ($\beta=0.2$) is almost at the terminal velocity
+($v_{\infty}\sim200\,\kmps$), that for the slowest wind acceleration
+model ($\beta=4.0$) is located close the line centre ($\sim50\,\kmps$).
+As one can see in Figure~\ref{fig:wind_vr_rho}, the column density
+of the gas moving at $v_{\infty}$ increases as the wind acceleration
+becomes larger since the gas moving at $v_{\infty}$ becomes closer
+to the photosphere. At the location where the absorption occurs, the
+gas is moving faster for the models with the faster wind acceleration
+models; hence, the location of the absorption component is bluer as
+$\beta$ becomes smaller (as the wind acceleration faster). The figure
+also shows that the intensity of the emission component increases
+as $\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
+because the density near the photosphere increases (more material
+near the photosphere) as the value of $\beta$ increases (Figure~\ref{fig:wind_vr_rho});
+hence, the emissivity of increases. Unlike the magnetospherical accretion
 only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
-profiles are not seen here. Interestingly, in some models (e.g. $T_{\mathrm{wind}}=9000\,\mathrm{K}$
-and $\beta=1.0$ model), the absorption componet is present at slightly
-red-ward of the line centre, causing the blue-ward asymmetry seen
-in the magnetospherical accretion models. The blue-ward asymetry are
-caused by: 1. the accretion disc placed at the equotorial plane and
-the finited-size steller disc blocking a part of the line emission
-region moving away from an observer, 2.~the much larger optical depth
-for the line emitted from the opposite side of the observer where
-the gas is moving away from the observer. Because of the broad wings
-of the Voigt profile, the line photon intereacts with the gas with
-much wider range of the projected velocity space.
-
-The dependency of the profile on the wind anisotoropy parameter $b$
-is demonstrated in Figure~\ref{fig:effect_wind_b_param}. The line
-peak closer to the line centre and the profile becomes slightly more
-symmetric around the line centre for the isotropic ($b=0$) compared
-to the cases with the colliminated wind ($b=4$). The P~Cygni profile
-feature become prominant for the spherical wind models (especially
-in $\beta=0.5$ model) because the collumn density of along the line
-of a sight of the observer at a medium inclination angle ($i=55^{\circ}$)
-increases as the wind becomes more spherical for a given value of
-the wind mass-loss rate.
+profiles are not seen here, nor the blue-ward asymmetry. Because of
+the absorption component in P~Cygni profile, most of the profiles
+show red-ward asymmetry except for the low temperature wind models
+with high inclinations (not shown here).
+
+The dependency of the profile on the wind anisotropy parameter $b$
+is demonstrated in Figure~\ref{fig:effect_wind_b_param}. Three models
+presented in the figure have the same mass-loss ($10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$),
+and are computer at inclination angle $i=55^{\circ}$. The P~Cygni
+profile feature becomes more prominent, and the line flux becomes
+smaller as the wind becomes more isotropic (smaller $b$ value). For
+a fixed mass-loss rate, the column density of along the line of a
+sight to the observer at a medium inclination angle (e.g.~$i=55^{\circ}$)
+increases as $b$ decreases (c.f.~equation~\ref{eq:wind_density_final});
+hence, causing more absorption. Further more, the value of the highest
+density in the wind becomes smaller for a smaller $b$ model. As the
+wind becomes more isotropic, the high gas concentrated more in the
+polar direction has to be spread in the wider angular angles. This
+results in a smaller highest density region in the wind; hence the
+smaller line emissivity. For the same reason, the emission in the
+wings is weaker for the model smaller $b$ value. We also note that
+the asymmetry around the line centre decreases as the wind becomes
+more isotropic.
+
+The effect of varying the wind mass-loss rate is shown in Figure~\ref{fig:effect_wind_mdot}.
+The line is very sensitive to the mass-loss rate. With all other parameters
+fixed constant, $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor
+of the wind density (equation~\ref{eq:wind_density_final}). For
+the formation of H$\alpha$, the recombination process and the subsequent
+downward transition to $n=3$ level. Assuming the ionisation fraction
+remains constant, the recombination rate is proportional to the square
+of wind density. We have found the line flux of the models in the
+figure is approximately proportional to the square of the mass-loss
+rate. This very sensitive nature of H$\alpha$ would make the line
+a good candidate for a mass-loss rate indicator; however, without
+solving the ambiguity of the emission component from the magnetospherical
+accretion flow and the wind, and without knowing the detailed temperature
+structure of the wind, it could provide us a misleading a mass-loss
+rate estimate of a T Tauri star.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/windonly_B_effect2.eps}
+
+\end{center}
+
+\caption{The effect of wind collimation.
+The line profiles computed with with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$ for  the wind anisotropy parameter $b=0, 2, 4$ are shown in dashed, dotted, and solid respectively.
+All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.
+The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind.
+The blue-ward asymmetry is still present even in the isotropic wind case ($b=0$).}
+
+\label{fig:effect_wind_b_param}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/windonly_mdot_effect.eps}
+
+\end{center}
+
+\caption{The effect of the wind mass-loss rate.
+The profiles computed with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$, and  $\dot{M}_{\mathrm{wind}} = 1.0 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (solid),  $0.5 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dotted), and $0.25 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed) are shown above.
+The models are computed with only the wind component (no magnetospherical accretion flow or  accretion disc).
+With all other parameter fixed constant, the mass-loss rate behaves as a scaling factor for the wind density (equation~\ref{eq:wind_density_final}.)}
+
+\label{fig:effect_wind_mdot}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Disc $+$bipolar wind}
+
+\label{sub:model-disc-wind}
 
 Next, we examine the effect of the size of the inner radius of the
-disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_thin_disc}
-shows the wind emission profile computed with and without the equotorial
-accretion disc. The latter can be also considered as a model with
-a large inner radius of the accretion disc in which none of the wind
-emission region is not blocked provided the inclination is moderate.
-The profile shapes of the models are very similar to each other, but
-the one without the accretion disc is slightly more symmetric than
-the other. As one expects, the line equivalent width of the model
-without the disc is about twice of the model with the disc. Interestingly,
-the blueward asymmetry is present also in the profile computed without
-the disc. This is mainly caused by the occultaion of a part of emission
-region by the steller disc and the fact that the wind (density distribution)
-is asymmetric. The H$\alpha$ image (project in the plane of the observer
-at the location of the star) for the model with the disc (middle panel)
-and that for the model without (right plane) are also shown in the
-same figure. The images weere computed with a fast wind accereation
-rate ($\beta=0.5$). The extent of the line emission is smaller ($\sim0.2\,\mathrm{AU}$
-or $\sim20\, R_{*}$) compared to the spectro-astrometric observations
-of \citet{takami:2003} for RU~Lup and CS Cha which have 1--5 AU
-scale outflows%
-\footnote{\citet{takami:2003} also showed that some objects (e.g~Z CMa and
-AS~353A) show the outflows of larger scale ($>50\,\mathrm{AU}$)
-which could be formed by shocks rather than MHD-wave heating (e.g.
-\citealt{hartmann:1982}) or X-ray heating (e.g.~\citealt{shang:2002}). %
-}; however, if a slower wind acceration rate ( $\beta=4$) is the emission
-region become larger slightly ($\sim0.4$~AU).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{cc}
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/wind_b_effect.eps}&
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/windonly_B_effect.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{The effect of wind collimation.
-The dependecy of the line profiles on the wind anisotropy parameter $b$ for the models with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$  is shown on left, and that with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 1.0\right)$ on right.
-All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.
-The degree of the blue-ward asymmetry of the profiles is slightly lower for the spherical (isotroptic) wind model ($b=0$, dashed) compared to the collimated wind (anisotoropic) wind models ($b=4$, solid).
-The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind.
-}
-
-\label{fig:effect_wind_b_param}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_alpha_disc}
+shows the wind emission profiles computed with and without the accretion
+disc at $i=55^{\circ}$. The H$\alpha$ images (projected on to the
+plane perpendicular to the observer at the location of the star) are
+also shown in the same figure. Both models use the same parameters
+as in Figure~\ref{fig:atlas_wind_model}, but with $\beta=0.5$ and
+$T_{\mathrm{wind}}=9000\,\mathrm{K}$). The model without the disc
+can be also considered as a model with a large inner radius of the
+accretion disc, in which none of the wind emission region is blocked
+by the disc --- provided the inclination angle is not so high and
+the disc is not or slightly flared.
+
+The bipolar nature of the wind is clearly seen in the images. In this
+example, the most of the wind emission occurs within a few to a several
+(depending mainly on the value of $\beta$) stellar radii from the
+star. The figure also shows that the accretion disc blocking the wind
+emission from the bottom half of the wind which is moving away from
+the observer. This results in the reduction of the wind emission in
+the red wing. The image (mid panel) also shows that the accretion
+disc is not occulting the stellar disc at this inclination; therefore,
+the ratio of the wind emission flux to the photospherical continuum
+flux becomes slightly smaller for the model with the disc. This results
+in the reduction in the peak flux and the flux in the wings in the
+normalised profile shape. If the disc becomes more flared (if the
+opening angle exceeds $45^{\circ}$at the outer edge of the accretion
+disc), the occultation of the stellar disc by the accretion could
+be seen at this inclination angle. Although it is not shown here,
+the continuum level of the two models are identical. For the models
+with $i<30^{\circ}$, the presence of the disc has little/no effect
+on the profile shapes. In the figures, the extent of the H$\alpha$
+emission is smaller ($\sim0.2\,\mathrm{AU}$ or $\sim20\, R_{*}$)
+compared to the spectro-astrometric observations of \citet{takami:2003}
+for RU~Lup and CS Cha which show 1--5~AU scale outflows%
+\footnote{\citet{takami:2003} their observation also show that some objects
+(e.g~Z CMa and AS~353A) displaying the outflows of larger scale
+($>50\,\mathrm{AU}$); however, this could be formed by shocks rather
+than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
+(e.g.~\citealt{shang:2002}). %
+}; however, if a slower wind acceleration rate ( $\beta=4$) is the
+emission region become slightly larger ($\sim0.4$~AU).
+
+Although not shown here, we have computed the H$\alpha$ profiles
+with the collimated wind and the accretion disc for the same range
+of $\beta$ and $T_{\mathrm{max}}$values as in Figure~\ref{fig:atlas_wind_model}.
+The inner and the outer radii of the accretion disc are $R_{\mathrm{di}}=R_{\mathrm{mi}}=2.2R_{*}$
+and $100\,\mathrm{AU}$ respectively, and the disc is slightly flared
+(see section~\ref{sub:Accretion-disc}). Similar to the case in Figure~\ref{fig:effect_alpha_disc},
+the line flux of the models with accretion disc decreases to less
+than the half of that without the accretion disc similar to the models
+shown in Figure~\ref{fig:effect_alpha_disc}. The overall behaviour
+of the line profile shapes as functions of $\beta$ and $T_{\mathrm{wind}}$
+are very similar to that for the models without the accretion disc.
+A significant reduction of the flux in the red wing is seen in the
+wind model with the accretion disc when compared with the wind only
+model. The wings appear to be weaker in these models compared to the
+wind only models because of the lower wind emission flux to the continuum
+flux as briefly mentioned earlier.
 
@@
 The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used).
-The line profile of the model with the disc (solid) is similar to the model without the disc (dashed), but the latter is slightly more symmetric than the former.
-The line equivalent width of the model without the disc is about 2 times that of the model with the disc.
-The blueward asymmetry is present also in the profile computed without the disc.
+The flux in the red wing of the line profile from the model with the disc (solid) is greatly reduce by the presence of the accretion disc compared  to that from the model without the disc (dashed).
+The peak flux and the flux in the wings are also reduced in the model with the disc because the disc does block the wind emission region, but none of the stellar disc, i.e.
+the continuumm flux level is unchanged.
 The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown.
@@
 
-\label{fig:effect_thin_disc}
+\label{fig:effect_alpha_disc}
 
@@
 
-\subsection{Magnetosphere $+$ wind}
-
-\label{sub:model-acc-wind}
-
-Next, we examine the characteristics of the line profiles arising
-from the combination of the magnetospherical accretion flow and the
-wind. For simplicity, we fix the parameters for the magnetosphere
+\subsection{Magnetosphere $+$ disc $+$bipolar wind}
+
+\label{sub:model-acc-disc-wind}
+
+We examine the characteristics of the line profiles arising from the
+combination of the magnetospherical accretion flow, the wind, and
+the accretion disc. For simplicity, the parameters for the magnetosphere
 ($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-as in Figure~\ref{fig:atlas_acc_models}), and use the constant wind
-mass-loss rate $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$). Figure~\ref{fig:atlas_wind_acc_model}
-shows the results for $i=55^{\circ}$ and the same combinations of
-$T_{\mathrm{wind}}$ and $\beta$ used in section~\ref{sub:model-acc-wind}
-(Figure~\ref{fig:atlas_wind_model}).
-
-While the emission from the magnetosphere dominates for the models
-with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation
-and the colder wind models), the emission from the wind dominates
-for the models with larger $\beta$ and $T_{\mathrm{wind}}$ (the
-slower accerelation and the hotter models). The P~Cygni profile feature
-becomes less prominant in some of the models because the additional
-emission from the magnetosphere extending in the wings. In most of
-the cases, the profiles are understood as a simple sum of the magnetospherilcal
-component and the wind component.
+are fixed as in Figure~\ref{fig:atlas_acc_models}), and the wind
+mass-loss rate, the isothermal wind temperature and the wind anisotropy
+parameter to $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$), $T_{\mathrm{wind}}$
+and $b=4$ respectively. The profile computed for $i=55^{\circ}$
+is given in Figure~\ref{fig:summary_beta05_t8000}, along with the
+profile computed with the magnetosphere only and that with the wind
+plus accretion disc configurations for a comparison. As one can see
+from the figure, the profile computed for the disc--wind--magnetosphere
+hybrid model can be understood as a simple flux sum of the magnetospherical
+component and the wind component. In this example, the wind causes
+the absorption of the blue side of the profile, and it adds extra
+flux around the line centre. As seen before, the presence of the disc
+causes the reduction in the red side of the profile since the emission
+from the receding gas is block by the disc. The resulting profile
+appears to be narrower than that of the magnetosphere model.
+
+The effect of changing the ratio of the wind mass-loss rate to mass-accretion
+rate ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
+in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With the fixed value
+of mass-accretion rate ($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
+, the mass-loss rate by the wind is varied. The figure shows that
+as $\mu$ increases the P-Cygni absorption deepens, and the position
+of minimum flux in the absorption trough appears to move blue-ward.
+On the other hand, the emission component becomes stronger as $\mu$
+increases. With this combination of the parameters for the magnetosphere
+and the wind, the absorption component tends to be too strong for
+the models $\mu>0.025$ (with this model configuration), at all inclinations
+(not shown here), compared with the observed H$\alpha$ profiles (e.g.\citealt{reipurth:1996};
+\citet{alencar:2000}). As we will see later (section~\ref{fig:ttau_model}),
+$\mu$ can be as large as $\sim0.3$ with different parameters of
+the magnetosphere; hence, this condition $\mu>0.025$ is always valid.
+
+Again, the H$\alpha$ profiles with the same ranges of the wind temperature
+($T_{\mathrm{wind}}$) and the wind acceleration parameter ($\beta$)
+used in Figure~\ref{fig:atlas_discwind_only} are computed with $\mu=0.01$.
+The parameters of the magnetosphere fixed as in Figure~\ref{fig:acc_inclination_effect},
+are shown in Figure~\ref{fig:atlas_disc_wind_acc_model} along with
+the model with only the magnetosphere, for a comparison. A relatively
+small value of $\mu$ is chosen to avoid absorption component of the
+P-Cyg profile becoming too strong, as seen in Figure~\ref{fig:effect_mdot_disc_wind_acc}.
+In general, even with small values of the anisotropy parameter ($b=0$
+and $2$), the absorption component is found to be too strong when
+$\mu=0.1$ is used with this combination of the magnetosphere and
+the wind. The figure shows that the position of the wind absorption
+component moves toward the line centre as $\beta$ becomes larger.
+Although little wind emission is seen in this temperature range, it
+becomes more important in a model with a higher temperature and a
+wind mass-loss rate. In fact, the model with $\beta=2.0$ and $T_{\mathrm{dw}}=9000\,\mathrm{K}$
+displays a small amount of the wind emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
+
+As seen in Figure~\ref{fig:summary_beta05_t8000}, the profiles shown
+here can be understood as the combination of the emission from the
+magnetosphere and the absorption of the flux by the wind component.
+In general, the emission from the accretion disc is negligible at
+H$\alpha$ wavelength, but the absorption of the continuum flux from
+the photosphere by the disc is important for predicting correct line
+strengths.
+
+Although the profiles shown in Figure~\ref{fig:atlas_disc_wind_acc_model}
+are those at a single inclination angle ($i=55^{\circ}$), they are
+very similar to the Type II-B and III-B of the observed CTTS H$\alpha$
+profiles (\citealt{reipurth:1996}), which are impossible to be explained
+by the magnetospherical accretion flow models (e.g.~\citealt{muzerolle:2001}).
+Comparison of the model profiles with different types of the observed
+H$\alpha$ profiles will be given in section~\ref{sub:Classification-scheme-proposed}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/summary.eps}
+
+\end{center}
+
+\caption{Comparison of the profiles computed with the magnetosphere, the wind, the disc, and their combinations.
+The model configureations used above are: (1)~magnetosphere only (dashed), (2)~wind and disc (dash), and (3)~disc, wind and magnetosphere (solid).
+The parameters used here are $T_{\mathrm{max}}=7500\,\Kelvin$, $\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$, $\dot{M}_{\mathrm{wind}}=10^-8\,\mathrm{M_{\sun}\,yr^{-1}}$, $T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$.
+The profile for the case 3 is can be understood as a simple flux sum of the profiles from case 1 and 2.}
+
+\label{fig:summary_beta05_t8000}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/disc_wind_acc_mdot_effect.eps}
+
+\end{center}
+
+\caption{Effect of the mass-loss rate to mass-accretion rate ratio  ($\mu=\dot{M}_{\mathrm{w}}/\dot{M}_{\mathrm{acc}}$).
+The H$\alpha$ profile computed with only the magnetopsherical accretion (thick solid) -- $T_{\mathrm{max}}=7500\,\Kelvin$, $\dot{M}_{acc}=10^-7\,\mathrm{M_{\sun}\,yr^{-1}}$ -- is compared with the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash).
+All the models are computed with the inclination angle $i=55^{\circ}$.
+As $\mu$ increases the P-Cygni absorption deepens and the emission component becomes stronger.
+In genaral, the absorption is too strong for the models $\mu>0.025$ compared with the observations (e.g., \citealt{reipurth:1996}).}
+
+\label{fig:effect_mdot_disc_wind_acc}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_acc_model.eps}
-
-\end{center}
-
-\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ as in Figure~\ref{fig:atlas_acc_models}).
-While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{wind}}$  (the slower accerelation and the hotter models).
-The P~Cygni profile feature becomes less prominant in some of the models because of the extra emission from the magnetosphere extends in the wings.}
-
-\label{fig:atlas_wind_acc_model}
+  scale=0.9]{figures/atlas_ha_i55_wind_acc_alpha_final2.eps}
+
+\end{center}
+
+\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$), the accretion disc.
+The mass-loss rate of the wind used here is $\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$.
+A relatively small mass-loss rate is chosen to avoid unrealistically strong P-cyg absorption component (see text in section~\ref{sub:model-acc-disc-wind} and  Figure~\ref{fig:effect_mdot_disc_wind_acc}).
+For a comparison, the profile computed with only the magensopherical accretion flow (dotted) is overlayed.
+All the profiles are computed at the inclination angle $i=55^{\circ}$.
+As $\beta$ becomes larger, the postion of the wind absorption component moves toward the line centre.
+Although little wind emission is seen in this temperature range, it becomes more important in a model with a higher temperature and a wind mass-loss rate.
+The profiles resembles the observed H$\alpha$ emission profiles affected by the wind.}
+
+\label{fig:atlas_disc_wind_acc_model}
 
@@
 
-\subsection{Magentosphere $+$ disc $+$ wind}
-
-\label{sub:model-acc-disc-wind}
-
-\begin{itemize}
-\item Flux contribution by scattering of photon by disc?
-\end{itemize}
-
-\subsection{Summary}
+\subsection{Disc-wind model of \citet{knigge:1995}}
+
+\label{sub:result-discwind-knigge}
+
+As an alternative model for the bipolar wind models (with the combination
+of the magnetosphere and the accretion disc) shown in Figures~\ref{fig:atlas_wind_model}
+and \ref{fig:atlas_disc_wind_acc_model}, we have also considered
+the disc-wind model \citet{knigge:1995} as briefly described in section~\ref{sub:model-disc-wind}.
+The former resembles the density structure of \citealt{krasnopolsky:2003}
+in large scale ($\sim100$~AU) which described in section~\ref{sub:wind_jet},
+and the latter in small scale ($\sim10$~AU) of the same model. The
+main difference between the two models are in their density structure.
+For a given radius, the density increases toward the polar direction
+in the former model, but the density increases toward the equatorial
+plane for the models presented here.
+
+First, the disc wind models without the magnetosphere are considered.
+Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
+computed using only the disc-wind component (c.f. Figure~\ref{fig:config_discwind})
+for the same isothermal disc-wind temperature ($T_{\mathrm{dw}}$)
+and the wind acceleration parameter ($\beta$) ranges used for the
+bipolar wind models. The parameters used for the central star are
+as in section~\ref{sub:Continuum-Source}, and the other disc-wind
+parameters are summarised in Table~\ref{tab:std_discwind_parameters}.
+The figure shows that the wind emission increases $\beta$ and $T_{\mathrm{dw}}$
+increase. Similar to the bipolar wind models, the location of the
+P-Cyg absorption component moves toward the line centre as $\beta$
+increases. The morphology of the profile exhibited by the model changes
+from FU-Ori type (IV-B) for the models with small $\beta$ to III-B
+and II-B types (\citealt{reipurth:1996}) as the value of $\beta$
+increases. Although not shown here, we find that the profile shapes
+are relatively insensitive to the value of the wind collimation parameter
+$d$. The dependency on the disc wind mass-loss rate of the profile
+shape is similar to that of the collimated wind models (Figure~\ref{fig:effect_mdot_disc_wind_acc})
+.
+
+We now consider the models computed with the combination of the disc-wind
+and the magnetospherical accretion components. The parameters used
+for the magnetosphere are set to be same as in the case for Figure~\ref{fig:acc_inclination_effect},
+and are kept constant for simplicity. The mass-loss rate of the disc
+wind is set to $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$) Figure~\ref{fig:atlas_discwind_acc_model}
+shows the models profiles computed using the same ranges of the disc-wind
+temperature and the wind acceleration parameter as in the previous
+cases.
+
+As in the disc wind only models (Figure~\ref{fig:atlas_discwind_only}),
+the location of the absorption component moves toward the line centre
+as the value of $\beta$ increases (as the wind acceleration slower).
+The figure shows that in the models with smaller $\beta$ and $T_{\mathrm{dw}}$,
+the line emission from the magnetosphere dominates. On the other hand,
+in the models with larger $\beta$ and $T_{\mathrm{dw}}$, the emission
+from the disc wind dominates. Compared to the observation of \citet{reipurth:1996}
+and \citet{alencar:2000}, the lines are too strong for $\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
+and $\left(9000\,\mathrm{K},\,1.0\right)$ models. The wide varieties
+of profile shapes are see in this set of models which resembles II-B,
+III-B, IV-B, II-R and III-R%
+\footnote{Not shown here, but seen in the models with different combinations
+of $i$, $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$.%
+} types of the observed H$\alpha$ profiles (\citealt{reipurth:1996}).
+The shape of the primary and secondary peaks in the profiles are slightly
+{}``rounder'' compared to those of the accretion, collimated wind,
+disc hybrid model shown in Figure~\ref{fig:atlas_disc_wind_acc_model}.
+The rounder peaks are caused by the rotation of the wind. The profiles
+from the disc wind models are affected more by the rotational motion
+of the wind since the gas is more concentrated toward the equator,
+but in the models with the collimated wind the gas is concentrated
+more in the polar directions.
+
+We note the ambiguity seen between some of the disc-wind only models
+and the disc-wind, magnetosphere hybrid models. For example, the disc-wind
+only model with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
+in Figure~\ref{fig:atlas_discwind_only} and the disc-wind model
+with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
+in Figure~\ref{fig:atlas_discwind_acc_model} give very similar profiles.
+Given such an observed profile, it is difficult to distinguish if
+the emission is dominated by the accretion or the wind unless some
+other lines, not affected associated with wind or magnetosphere, are
+used simultaneously.
+
+General characteristics of the profiles from the disc-wind, magnetosphere
+hybrid model (Figure~\ref{fig:atlas_discwind_acc_model}) are very
+similar to those of the disc, collimated wind, magnetosphere hybrid
+model (Figure~\ref{fig:atlas_disc_wind_acc_model}). The main difference
+between these two sets of models is the mass-loss rate to the mass
+accretion rate $\mu$. While the models presented in this section
+use $\mu=0.1$ which is consistent with the MHD jet models (e.g.~\citealt{koenigl:2000}),
+the models in Figure~\ref{fig:atlas_disc_wind_acc_model} use much
+smaller value ($\mu=0.01$).
+
+\begin{table}
+
+\begin{center}
+
+\begin{tabular}{ccccccc}
+\hline 
+$d$&
+$R_{\mathrm{wi}}$&
+$R_{\mathrm{wo}}$&
+$\dot{M}_{\mathrm{dw}}$&
+$p$&
+$f$&
+$R_{\mathrm{s}}$\tabularnewline
+$\left[R_{*}\right]$&
+$\left[R_{*}\right]$&
+$\left[\mathrm{AU}\right]$&
+$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
+$[-]$&
+$[-]$&
+$\left[R_{*}\right]$\tabularnewline
+\hline
+$21.4$&
+$3.0$&
+$1.0$&
+$10^{-8}$&
+$-3/2$&
+$2.0$&
+$30$\tabularnewline
+\hline
+\end{tabular}
+
+\end{center}
+
+\caption{The summary of the standard disc-wind model parameters used in section~\ref{sub:result-discwind-knigge}. See also section~\ref{sub:Alternative-model-disc-wind}.}
+
+\label{tab:std_discwind_parameters}
+
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}
+
+\end{center}
+
+\caption{The H$\alpha$ profiles computed with the disc-wind only models.
+For the wind mass-loss rate fixed at $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line profiles are computed with different combinations of the wind accelreation rate ($\beta$) and the isothermal disc wind temperature ($T_{\mathrm{dw}}$).
+The wind emission increases as the values of $\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes accelerates slower and as the wind comes warmer.
+Similar to the bipolar wind models (Figure~\ref{fig:atlas_wind_mode}), the position of the wind absorption moves toward the line centre as $beta$ becomes larger.
+The morphology of the profiles are smilar to that of observations.
+}
+
+\label{fig:atlas_discwind_only}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
+
+\end{center}
+
+\caption{The disc-wind, magnetoshere hybrid model.
+Same as Figure~\ref{fig:atlas_discwind_only}, but these models (soild) also include the magnetosphere accretion flow ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$).
+While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{dw}}$  (the slower accerelation and the hotter models).
+For a comparison, the profile computed with only the magensopherical accretion flow (dotted) is overlayed.
+The model profiles are very similar to the observed profiles influenced by the wind outflow.}
+
+\label{fig:atlas_discwind_acc_model}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\citet{reipurth:1996}proposed the two-dimentional classification
+\label{sub:Classification-scheme-proposed}
+
+\citet{reipurth:1996} proposed the two-dimensional classification
 of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
 stars. Their classification scheme contains four classes (I, II, III
-and IV) differenciated by the ratio of the secondary-to-primary emission
-components in the profiles. Each classes are devided into two sub-classes
-(B and R) which depends whether the absorption componet is on the
-blue or red side. Readers are refered to Fig.~4 of their paper. Figure~\ref{fig:atlas_reipurth}
-shows the sample profiles which are classified according to the definition
-of \citet{reipurth:1996}. The corresponding model parameters are
-given in Table~\ref{tab:classification}. As we can see from this
-figure, the combinatioin of the wind, magnetospherical accretion,
-and accretion disc can reasonably reproduce all the classes of the
-profiles seen in observations.
-
-Within the parameter space covered, we find it is difficult to produce
-Type I type profile, which is very symmetric around the line centre
-and without any absorption feature, if the wind component is added
-in the model. Type II-B are
+and IV) differentiated by the ratio of the secondary-to-primary emission
+components in the profiles. Each classes are divided into two sub-classes
+(B and R) which depends whether the absorption component is on the
+blue or red side. Readers are refereed to Fig.~4 of their paper.
+Figure~\ref{fig:atlas_reipurth} shows the sample model profiles
+which are classified according to the definition of \citet{reipurth:1996}.
+The combination of the disc wind, magnetospherical accretion, and
+accretion disc can reasonably reproduce all the classes of the profiles
+seen in observations. Similar profiles can be reproduced if the bipolar
+wind is used instead of the disc wind, but the wind absorption at
+a given velocity location occurs at a different inclination angles
+when the wind type is switched from the bipolar wind to the disc wind.
+The corresponding model parameters used to reproduce the profiles
+in the figure are given in Table~\ref{tab:classification} along
+with brief comments on possible physical conditions which leads to
+the profiles in each class.
+
+Using the samples of H$\alpha$ from 43 CTTS, \citet{reipurth:1996}
+found the most common (33~per~cent) type of the profile is Type
+III-B. Interestingly, the most common profile type seen in the profiles
+from both the bipolar wind, disc and magnetosphere hybrid model (Figure~\ref{fig:atlas_disc_wind_acc_model})
+and the disc-wind and the magnetosphere hybrid model (Figure~\ref{fig:atlas_discwind_acc_model})
+are Type III-B profiles. In this type of profiles, the main emission
+comes from the magnetosphere, and the profile shape is altered a slightly
+blue-asymmetric one to a slightly red-asymmetric one via the wind
+absorption in the blue wing. The second most common profile (26~per~cent)
+
+Type I (symmetric around line centres) is mainly produced in the magnetosphere.
+Although not shown here, this type of profile can be reproduced with
+the disc-wind, magnetosphere hybrid mode with pole on configuration.
+Since there is not material in the polar region in the disc wind model,
+the observer can look the magnetosphere almost directory for high
+inclination cases, provided that wind temperature is low enough so
+that the wind emission is negligible. Type II-R and Type II-B can
+be produced in a similar physical conditions (e.g. in a slow accretion
+and low temperature wind plus a magnetosphere). Main difference is
+between the two is in their inclination angles. The former is more
+likely seen with high inclination.
+
+Type III-R is the least common type of the observed profile (2~per~cent)
+according to \citet{reipurth:1996}. Incidentally, we also had a hard
+time to reproduce this type of profile since this can be achieve only
+at narrow range of parameter space (very high inclination angle with
+disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and $\dot{M}_{\mathrm{acc}}~10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+
+Similarly the Type IV-R is the second least common type of observed
+profile (5~per~cent) which shows the inverse P-Cyg profile shape.
+This can be understood since the magnetospherical accretion model
+of \citet{hartmann:1994} predicts that the redshifted absorption
+can occur at a limited range of inclination angle with which the hot
+continuum flux from the footprint of the magnetosphere is seen through
+relatively fast moving gas in the accretion stream. Finally Type III-R
+profile is very similar to Type II-R, but the wind in this type of
+profile may be accretion faster than that in Type II-R.
 
@@
   clip,
-  scale=0.65]{figures/atlas_reipurth_like.eps}
+  scale=0.65]{figures/atlas_reipurth_like_discwind.eps}
 
@@
 \caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}.
-The combination of magnetospherical accretion flow, the accretion disc, and the colliminated wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.
+The combination of magnetospherical accretion flow, the accretion disc, and the disc wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.
+Similar results can be obtained if the disc wind is replaced by the disc wind.
 The model parameters and short comments are summarised in Table~\ref{tab:classification}.
-The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.
-}
+The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%astro.ex.ac.uk/people/rk/
 
@@
 $T_{\mathrm{max}}$&
-$\dot{M}_{\mathrm{wind}}$&
-$T_{\mathrm{wind}}$&
+$\dot{M}_{\mathrm{dw}}$&
+$T_{\mathrm{dw}}$&
 $\beta$&
@@
 Class&
-$\left(\mathrm{deg.}\right)$&
-$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-$\left(10^{3}\,\mathrm{K}\right)$&
-$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-$\left(10^{3}\,\mathrm{K}\right)$&
-$\left(-\right)$&
+&
+&
+&
+&
+&
+&
 \tabularnewline
@@
 $-$&
-Accretion dominated possibly without the wind at a mid inclination.\tabularnewline
+Accretion dominated possibly without the wind. Mid inclination.\tabularnewline
 II-B&
-$10$&
+$55$&
 $10^{-7}$&
 $7.5$&
-$10^{-8}$&
-$9.0$&
+$10^{-9}$&
+$8.0$&
 $1.0$&
-Accretion and wind, mid wind accerelation rate, low inclination\tabularnewline
+Wind, disc and magnetosphere. Wide range of wind acceleration rate.
+Mid--high inclination\tabularnewline
 III-B&
-$10$&
+$55$&
 $10^{-7}$&
 $7.5$&
-$10^{-8}$&
-$8.0$&
-$2.0$&
-Accretion and wind, with slow wind accerelation rate, low inclination\tabularnewline
+$10^{-9}$&
+$9.0$&
+$0.5$&
+Wind, disc and magnetosphere. Fast--mid wind acceleration rate. Mid
+inclination\tabularnewline
 IV-B&
-$55$&
-$-$&
-$-$&
-$10^{-8}$&
-$8.0$&
-$0.5$&
-Accretion dominated (low accretion rate), mid inclination \tabularnewline
-II-R&
 $55$&
@@
 $9.0$&
-$2.0$&
-Wind dominated, with fast wind accerelation rate, mid inclination\tabularnewline
-III-R&
+$0.5$&
+Wind, disc and magnetosphere. Fast wind acceleration rate. Mid inclination\tabularnewline
+II-R&
 $80$&
@@
 $7.5$&
+$10^{-9}$&
+$7.0$&
+$2.0$&
+Wind, disc and magnetosphere. Slow wind acceleration rate. High inclination\tabularnewline
+III-R&
+$85$&
 $10^{-8}$&
-$9.0$&
+$8.2$&
+$10^{-9}$&
+$6.0$&
 $1.0$&
-Wind dominated, slow wind acceralation rate, high inclination \tabularnewline
+Wind, disc and magnetosphere. Mid wind acceleration rate. Very high
+inclination \tabularnewline
 IV-R&
@@
 $-$&
-Accreetion dominated possibly without the wind at a mid inclination.\tabularnewline
+Accretion dominated. Low mass-accretion rate. Mid inclination.\tabularnewline
 \hline
@@
 
-\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.}
+\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.
+The temepratures are in $10^{3}\,\Kelvin$.
+$\dot{M}_{\mathrm{acc}}$ and $\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
 
@@
 
-\subsection{Comparisons with observations}
-
-For a demonstrative purpose, we performed preliminary model fit of
-H$\alpha$ observarions
-
-\begin{itemize}
-\item other possible model? Better wind model?
-\item Any other bussiness?
-\end{itemize}
+\subsection{An example model fit of T~Tau}
+
+\label{sub:ttau-model}
+
+As a demonstrative purpose, we present a model fit of H$\alpha$ observation
+of a classical T Tauri star (T~Tau) obtained by \citet{vink:2005}.
+T~Tau is known to be a triple system (e.g.~\citealt{koresko:2000}).
+One of the star in the system T~Tau~N (a prototype for T~Tauri
+stars) is dominating in optical (e.g.~\citealt{calvet:1994}). The
+rotational velocity and the rotational period of the star found by
+\citet{herbst:1987} are $v\,\sin i=19.5\pm2.5\,\mathrm{km\, s^{-1}}$
+and $2.80\,\mathrm{d}$ respectively. The inclination of the disc
+is known to be relatively small (e.g.~$i=29^{\circ}$, \citealt{akeson:2002}).
+There is a rather large scatter in the previously estimated the accretion
+rates e.g.~$3\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ \citep{johns-krull:2000}
+and $\left(3.1-5.7\right)\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+\citep{calvet:2004}.
+
+For the photospheric model, the following parameters from \citet{calvet:2004}
+are adopted: $T_{\mathrm{eff}}=5500\,\mathrm{K}$, $M_{*}=1.9\,\mathrm{M_{\sun}}$
+and $R_{*}=2.9\, R_{*}$. The standard geometry for the magnetosphere
+($R_{\mathrm{mi}}=2.2\, R_{*}$ and $R_{\mathrm{mo}}=3.0\, R_{*}$)
+and the bipolar wind configuration (Table~\ref{tab:std_parameters})
+are used for simplicity. Again, our purpose here is not to obtain
+the best fit parameters, but rather it is to examine if the model
+is capable of reasonably reproducing the data from a real object,
+in this case, T~Tau~N. The main parameters here (1)~the temperature
+of the magnetospherical accretion flow ($T_{\mathrm{max}}$), (2)~the
+mass-accretion rate ($\dot{M}_{\mathrm{acc}}$), (3)~the temperature
+of the wind ($T_{\mathrm{wind}}$), and (4)~the wind mass-loss rate
+($\dot{M_{\mathrm{wind}}}$). The inclination angle is simplify adopted
+from \citealt{akeson:2002} i.e.~$i=29^{\circ}$.
+
+Figure~\ref{fig:ttau_model} shows the result of a model fit. The
+amount of veiling near H$\alpha$ is very small ($<0.01$) for T~Tau,
+according to \citet{basri:1990}; hence, the observation is not corrected
+for veiling. The model consists of the magnetosphere, the bipolar
+wind, and the accretion disc (with a large hole i.e.$\sim5$\, AU
+. The parameters used for the model fit are: $T_{\mathrm{max}}=22000\,\mathrm{K}$,
+$T_{\mathrm{wind}}=8000\,\mathrm{K}$, $\dot{M}_{\mathrm{acc}}=1.1\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$,
+and $\dot{M}_{\mathrm{wind}}=2.0\times10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$.
+The temperature of the magentosphere is relatively high compared to
+the standard cases (e.g.~Figure~\ref{fig:atlas_acc_models}; also
+\citealt{muzerolle:2001}). Note that the estimated value of $T_{\mathrm{max}}$depends
+on the adopted values of $L_{*}$ (or $M_{*}$ and $T_{\mathrm{eff}}$)
+for the photospheric continuum model. If a lower value of $L_{*}$
+is adopted, $T_{\mathrm{max}}$value would become smaller in order
+to match the line strength which is mainly determined by the emission
+from the magnetosphere, in this case. For example, if the photospheric
+continuum is 3 times smaller than the one used here, one finds $T_{\mathrm{max}}\sim9600\,\mathrm{K}$
+which is more similar to that of the standard cases. The figure shows
+that the agreement between the model and the observation is quite
+reasonable although the line wings are slightly stronger in the models.
+In this example, the main profile feature is defined by the emission
+from the magnetosphere, but the blue side of the profile is affected
+by the absorption by the wind. The mass-loss to mass-accretion rate
+$\mu=0.18$ which is similar to the value predicted by observations
+and MHD simulations i.e.~$\sim0.1$ \citep{koenigl:2000}. Compared
+our mass-accretion rate estimate is much less than that of \citep{johns-krull:2000},
+and slightly smaller than that of \citep{calvet:2004} (see above).
+
+Although not shown here for clarity, the peak flux near the line centre
+is also affected by the wind absorption (causing about 10 per cent
+reduction) compared to the profile computer with magnetosphere only
+model (similar effect also seen in Figure~\ref{fig:atlas_disc_wind_acc_model}).
+If the fit was performed by ignoring the wind, the temperature and
+the mass-accretion rate of the magnetospherical accretion flow will
+be underestimated. A better approach to a model fit is a simultaneous
+fitting of multiple lines. For example, the near-infrared lines such
+as Pa$\beta$ and Br$\gamma$ should be used to determined the mass-loss
+rate since these lines are much less affected by the wind. Using the
+mass-loss rate from these lines, H$\alpha$ can be used to determine
+the wind mass-loss rate.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/ttau_compare.eps}
+
+\end{center}
+
+\caption{Comparison of the observed H$\alpha$ profile of T~Tau and the profile computed with the hybrid model, which consist of the magnetosphere, the colliminated wind, and the accretion disc (with a large hole i.e.
+$\sim 5$~AU).
+The inclination angle $29^\circ$ is used.
+The maximum temperature of the magnetosphere ($T_{\mathrm{max}}$) and the isothermal wind temperature used here are 22000~K and 8000~K respetively.
+The mass-accretion rate ($\dot{M}_{\mathrm{acc}}$) and the mass-loss rate ($\dot{M}_{\mathrm{wind}}$) are $1.1 \times 10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and $2.0 \times 10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ resplectively ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.18$)}
+
+\label{fig:ttau_model}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Which wind model?}
+
+\label{sub:Which-wind-model}
+
+In the previous sections, two possible geometrical configurations
+for the wind from CTTS were considered: 1. the bipolar wind, and 2.~the
+disc wind. While the material more concentrated toward the polar regions
+for a given radius in the first case, the material is more concentrated
+toward the equatorial plane in the second case. As mentioned earlier,
+the bipolar wind morel resembles the density distribution of the jet
+MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
+($>10$~AU), and the disc wind model resembles that in smaller scale
+($<10$~AU).
+
+The distinct difference in the density dependency on the polar angles
+in two models should be apparent in the inclination angle dependency
+on the shapes of the line profiles. Figure~\ref{fig:effect_inclination_compare}
+shows the H$\alpha$ profiles computed for 1.~the disc, bipolar-wind,
+accretion hybrid model (section\ref{sub:model-acc-disc-wind}) and
+2.~the disc-wind, magnetosphere hybrid model (section~\ref{sub:result-discwind-knigge})
+at inclination angles $i=10^{\circ},\,55^{\circ},\,80^{\circ}$. Both
+models include the magnetospherical accretion component with the same
+parameters used as in sections~\ref{sub:model-acc-disc-wind} and
+\ref{sub:result-discwind-knigge} i.e. $T_{\mathrm{max}}=7500\,\mathrm{K}$
+and $\dot{M}_{\mathrm{acc}}=1\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$.
+
+Mainly because of the geometrical configuration, the P-Cyg absorption
+feature weakens as the inclination increases for the model with the
+bipolar wind. The optical depth to an observer is higher (from the
+wind emission region) for with a lower inclination angle with this
+geometry. Although not shown here, this tendency of the inclination
+dependency holds for the models with bipolar wind models for wide
+ranges of $\beta$ and $T_{\mathrm{wind}}$. For the model with the
+disc wind, the absorption becomes stronger as the inclination becomes
+larger . The optical depth to an observer becomes larger as the inclination
+increases in this geometry.
+
+Similarly, the line equivalent width increases as the inclination
+angle increases for the model with the bipolar wind, it decreases
+as the inclination angle increases for the model with the disc wind.
+With the models with only magnetosphere (section~\ref{sub:model-acc}),
+we have also found that the line equivalent width decreases as the
+inclination increases in those models (see Figure~\ref{fig:acc_inclination_effect}).
+Interestingly, the observational study of \citet{appenzeller:2005}
+showed that the H$\alpha$ line equivalent width of CTTS increases
+as the inclination angle increases. Only the models with the bipolar
+wind agree with the trend seen in their observation. Although the
+uncertainty in the inclination angles of the observed object might
+be large, a larger sample in addition to that of \citet{appenzeller:2005}
+for further investigation of the inclination dependency on the line
+profile will be extremely useful for finding a possible wind configuration
+of CTTS.
+
+Despite the inclination angle dependency of the observed H$\alpha$
+favouring the models with bipolar wind, there are two main aspects
+of this model are not quite consistent with the magneto-centrifugal
+launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
+First, in section~\ref{sub:model-acc-disc-wind}, we found that the
+ratio of the mass-loss to mass-accretion rates needed to be rather
+small ($\mu<\sim0.025$), in order not to have an unrealistically
+strong P-Cyg absorption component, compared to the MHD simulations
+suggested \citep{koenigl:2000} i.e. $\mu\approx0.1$. In the model
+fit of T~Tau observation (section~\ref{sub:ttau-model}), we found
+much larger value of the ratio $\mu=0.18$. Considering large uncertainty
+in MHD theories and observational measurements ($\dot{M}_{\mathrm{acc}}$,
+$\dot{M}_{\mathrm{wind}}$ and $B$, ), the wide range of the mass-loss
+to mass-accretion ratio (e.g.~$0.025<\mu<0.18$) may be still reasonable.
+On the other hand, the models with the disc wind (section~\ref{sub:result-discwind-knigge})
+using $\mu=0.1$ reproduces the profiles (Figure~\ref{fig:atlas_discwind_acc_model})
+similar to that seen in observations. Second, the MHD models predict
+that the wind/jet becomes collimated well above the disc plane ($>10$~AU),
+but our bipolar wind model are collimated (density enhanced toward
+in the polar direction) from right outside of the magnetosphere. Unless
+the origin of the wind is from the central star itself, the density
+distribution used for the bipolar wind is not quite consistent with
+the near field of the MHD jet models, considering that the most of
+the H$\alpha$ emission occurs within a few to a several radii of
+the magnetosphere (Figure.~\ref{fig:effect_alpha_disc}). The density
+structure used for the disc wind model, however, is very similar to
+that of MHD simulations in the near field where the most of the H$\alpha$
+wind emission occurs. Interestingly, however, the recent study of
+\citet{matt:2005} showed the possibility that the stellar wind along
+the open magnetic field originating from the star can cause significant
+spin-down torque on the star, provided that mass-loss rate is high
+enough. Considering the issues mentioned above, it is not possible
+to favour the bipolar wind model to the disc wind model without further
+observational constraints. In reality, two types of the winds (bipolar
+wind and disc wind) may co-exits similar to that seen in e.g. \citet{drew:1998}
+and \citet{matt:2005}. In these models, the fast stellar wind is
+present in the polar directions, and at the same time the slower disc
+wind is present near the equatorial plane.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+
+\begin{center}
+
+\begin{tabular}{cc}
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/disc_wind_acc_inc_effect_m9_b2_t7000.eps}&
+\includegraphics[%
+  clip,
+  scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}\tabularnewline
+\end{tabular}
+
+\end{center}
+
+\caption{Dependency on the inclination angle of the H$\alpha$ model profiles.
+The profile computed at $i=10^{\circ}$(solid), $55^{\circ}$ (dot) and $80^{\circ}$ using 1.~the disc, bipolar-wind, accretion hybrid model (left panel; c.f.
+section~\ref{sub:model-acc-disc-wind}) and 2.~using the disc-wind, magentosphere hybrid model (right; c.f.
+section~\ref{sub:result-discwind-kingge}) are shown for a comparison.
+The parameters used for the magnetoshere are same for the both models, i.e.
+$T_{\mathrm{max}}=7500~\mathrm{K}$ and  $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.
+The isotherma wind temperature and the wind accrelation parameter used both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.
+All the other parameters are same as in sections~\ref{sub:model-acc-disc-wind} and  \ref{sub:result-discwind-knigge}.
+While the line equivalent width increases as the inclination angle increases for the former model configuration, it decreases as the incination angle increases for the latter.
+Only the former agrees with the tendency seen in the observational study of \citet{appenzeller:2005} who showed that the H$\alpha$ line equivalent width of CTTS increases as the inclination angle increases.
+}
+
+\label{fig:effect_inclination_compare}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We presented the detailed study of the H$\alpha$ formation from the
-circumstealler material of classical T~Tauri stars. AND MORE.
-
-Future studies include:
-
-\begin{enumerate}
-\item Improvement of the wind model. Temperature structure estimate by Hartmann()
-Alancar's paper. Disc-wind model of Branford and ...
-\item Try it with MHD model.
-\item Include the scattering flux term although this requires $N_{\phi}\times N_{\theta}$
-more times to compute a profile. 
-\item Polarization study to explore the geometry and the rotation of the
-disc. 
-\item Gas in the accretion disc (inner most part and the outer layer of
-the disc).
-\item Variability study using a 3D model.
-\end{enumerate}
+We have presented the disc--wind--magnetosphere hybrid radiative transfer
+models for classical T~Tauri stars, and detailed studies of the H$\alpha$
+formation from their complex to circumstellar environment and to understand
+the wide variety emission line profiles seen in observations. The
+two types of wind models considered are (1)~the bipolar wind model
+in the wind is originated from the star itself (section~\ref{sub:wind_jet};
+Figure~\ref{fig:config_dipolar}), and (2)~the disc-wind model in
+which the wind originates from the inner part of the accretion disc
+(section~\ref{sub:Alternative-model-disc-wind}; Figure~\ref{fig:config_discwind}).
+We found that both wind models combined with the magnetospherical
+accretion flow reproduces the wide variety of H$\alpha$ profiles
+(Figures~\ref{fig:atlas_disc_wind_acc_model} and \ref{fig:atlas_discwind_acc_model})
+seen in the observations.
+
+The inclination dependency of the line equivalent width predicted
+by the bipolar wind model agree with trends seen in the observation,
+but the disc-wind model does not. With the standard magnetospherical
+configuration (Table~\ref{tab:std_parameters}), the ratio of the
+mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind
+was set to be 4--10 times smaller than that predicated by magneto-hydrodynamical
+(MHD) calculations (c.f.~$\mu\sim0.1;$ \citealt{koenigl:2000})
+to avoid the blue-shifted absorption component becoming unrealistically
+too strong; however $\mu$ used in the disc-wind models are consistent
+with MHD calculations.
+
+Using the model results, we examined the H$\alpha$ spectroscopic
+classification proposed by \citet{reipurth:1996}, and discuss the
+basic physical conditions that reproduce the profiles in each classified
+type. Using the hybrid model, we also fit the observed H$\alpha$
+from the optical component of T~Tau triple system (T~Tau~N). The
+agreement between the model and the observation is excellent; however,
+we could not confirm the uniqueness of the fit. The ratio of the mass-loss
+to mass-accretion rate was found to be $\sim0.18$.
+
+Although not attempted in this paper, a better approach for determining
+the mass-loss and mass-accretion rate consistently is to model multiples
+lines simultaneously. For example, the mass-accretion rate of an object
+can be determined more easily by modelling Pa$\beta$ and Br$\gamma$
+since there is no/little wind effect seen in these lines. The mass-accretion
+rate then can be used to model H$\alpha$ to find the wind mass-loss
+rate.
+
+Similar model configurations used here may be also applicable to Herbig
+Ae/Be and brown dwarfs since their H$\alpha$ observations also exhibit
+evidences of the outflow and inflow (e.g.~\citet{finkenzeller:1984};
+\citealt{muzerolle:2005}), but no model has been developed to explain
+the phenomenon. Further investigation on the possibility of applying
+our model to these objects are needed.
+
+Future works should include the followings: (1)~Improving the wind
+models. The parametrisation of the wind density structure should be
+changed to follow more closely that of MHD simulations. The wind temperature
+structure should be calculated self-consistently (c.f.~\citealt{hartmann:1994};
+\citealt{martin:1996}). (2)~Computing the line profiles using the
+density structure from MHDs directly. Check the consistency, and give
+feedback to the MHD models which are needed to be tested against observational
+data. (3)~Spectropolarimetric study to explore the geometry and the
+rotation of the disc (e.g.~\citealt{vink:2005}). (4)~Modelling
+of the extended H$\alpha$ and spectro-astrometric observations (c.f.~\citealt{takami:2003};
+\citealt{appenzeller:2005}). (5)~Line variability study using a
+3D radiative transfer model (e.g.~\citealt{symington:2005}; \citealt{kurosawa:2005a})
+to probe the geometrical structure.
+
 \section*{Acknowledgements}
 
-RK is supported by PPARC standard grand PPA/G/S/2001/00081.
+Authors thank Jorick Vink for providing us the H$\alpha$ data of
+T~Tau. This work is supported by PPARC standard grand PPA/G/S/2001/00081.
 

### 2006-01-11 TTau_Halpha/ttau_model_subsec.tex
Corrections made after Tim's comments. The subsection on the fits of T Tau is eliminated from kurosawa.tex.  The subsection was saved in a separate tex file: ttau_model_subsec.tex.  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@616 25464f21-6099-402c-b30a-640f1d40d38b

--- 2005-11-29 TTau_Halpha/tmp.tex
@@
-%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
-\usepackage[T1]{fontenc}
-\usepackage[latin1]{inputenc}
-\setcounter{tocdepth}{3}
-\usepackage{graphicx}
-\usepackage{amssymb}
+\subsection{An example model fit of T~Tau}
 
-\makeatletter
+\label{sub:ttau-model}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Bold symbol macro for standard LaTeX users
-\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}
+As a demonstrative purpose, we present a model fit of H$\alpha$ observation
+of a classical T Tauri star (T~Tau) obtained by \citet{vink:2005}.
+T~Tau is known to be a triple system (e.g.~\citealt{koresko:2000}).
+One of the star in the system T~Tau~N (a prototype for T~Tauri
+stars) is dominating in optical (e.g.~\citealt{calvet:1994}). The
+rotational velocity and the rotational period of the star found by
+\citet{herbst:1987} are $v\,\sin i=19.5\pm2.5\,\mathrm{km\, s^{-1}}$
+and $2.80\,\mathrm{d}$ respectively. The inclination of the disc
+is known to be relatively small (e.g.~$i=29^{\circ}$, \citealt{akeson:2002}).
+There is a rather large scatter in the previously estimated the accretion
+rates e.g.~$3\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ \citep{johns-krull:2000}
+and $\left(3.1-5.7\right)\times10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+\citep{calvet:2004}.
 
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
+For the photospheric model, the following parameters from \citet{calvet:2004}
+are adopted: $T_{\mathrm{eff}}=5500\,\mathrm{K}$, $M_{*}=1.9\,\mathrm{M_{\sun}}$
+and $R_{*}=2.9\, R_{*}$. The standard geometry for the magnetosphere
+($R_{\mathrm{mi}}=2.2\, R_{*}$ and $R_{\mathrm{mo}}=3.0\, R_{*}$)
+and the bipolar wind configuration (Table~\ref{tab:std_parameters})
+are used for simplicity. Again, our purpose here is not to obtain
+the best fit parameters, but rather it is to examine if the model
+is capable of reasonably reproducing the data from a real object,
+in this case, T~Tau~N. The main model parameters here are (1)~the temperature
+of the magnetospherical accretion flow ($T_{\mathrm{max}}$), (2)~the
+mass-accretion rate ($\dot{M}_{\mathrm{acc}}$), (3)~the temperature
+of the wind ($T_{\mathrm{wind}}$), and (4)~the wind mass-loss rate
+($\dot{M}_{\mathrm{wind}}$). The inclination angle is simplify adopted
+from \citet{akeson:2002}, i.e.~$i=29^{\circ}$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{lscape}
-\usepackage{times}
+Figure~\ref{fig:ttau_model} shows the result of a model fit. The
+amount of veiling near H$\alpha$ is very small ($<0.01$) for T~Tau,
+according to \citet{basri:1990}; hence, the observation is not corrected
+for veiling. The model consists of the magnetosphere, the bipolar
+wind, and the accretion disc (with a large hole i.e. $\sim5$\, AU. The
+parameters used for the model fit are:
+$T_{\mathrm{max}}=22000\,\mathrm{K}$,
+$T_{\mathrm{wind}}=8000\,\mathrm{K}$,
+$\dot{M}_{\mathrm{acc}}=1.1\times10^{-8}\,\mathrm{M_{\sun}\,
+yr^{-1}}$, and
+$\dot{M}_{\mathrm{wind}}=2.0\times10^{-9}\,\mathrm{M_{\sun}\,
+yr^{-1}}$.  The temperature of the magentosphere is relatively high
+compared to the standard cases
+(e.g.~Figure~\ref{fig:atlas_acc_models}; also
+\citealt{muzerolle:2001}). Note that the estimated value of
+$T_{\mathrm{max}}$ depends on the adopted values of $L_{*}$ (or
+$M_{*}$ and $T_{\mathrm{eff}}$) for the photospheric continuum
+model. If a lower value of $L_{*}$ is adopted, $T_{\mathrm{max}}$ value
+would become smaller in order to match the line strength which is
+mainly determined by the emission from the magnetosphere, in this
+case. For example, if the photospheric continuum is 3 times smaller
+than the one used here, one finds
+$T_{\mathrm{max}}\sim9600\,\mathrm{K}$ which is more similar to that
+of the standard cases. The figure shows that the agreement between the
+model and the observation is quite reasonable although the line wings
+are slightly stronger in the models.  In this example, the main
+profile feature is defined by the emission from the magnetosphere, but
+the blue side of the profile is affected by the absorption by the
+wind. The mass-loss to mass-accretion rate $\mu=0.18$ which is similar
+to the value predicted by observations and MHD simulations
+i.e.~$\sim0.1$ \citep{koenigl:2000}. Compared our mass-accretion rate
+estimate is much less than that of \citep{johns-krull:2000}, and
+slightly smaller than that of \citep{calvet:2004} (see above).
 
-\newcommand{\aap}{A\&A}
-\newcommand{\aaps}{A\&AS}
-\newcommand{\apj}{ApJ}
-\newcommand{\apjl}{\apj}
-\newcommand{\pasp}{PASP}
-\newcommand{\aj}{AJ}
-\newcommand{\mnras}{MNRAS}
-\newcommand{\apjs}{ApJS}
-\newcommand{\aapr}{A\&AR}
-\newcommand{\pasj}{PASJ}
-
-\newcommand{\kmps}{\mathrm{km~s^{-1}}}
-\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
-\newcommand{\Kelvin}{\mathrm{K}}
-
-\usepackage{babel}
-\makeatother
-\begin{document}
-\title[On H-$\alpha$ formation of T Tauri stars]{On formation of H-$\alpha$ from classical T Tauri stars: the disc, wind, and magnetospheric-accretion hybrid model}
-
-\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries and Neil H. Symington\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}
-
-\date{Dates to be inserted}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2005}
-
-\maketitle
-
-\label{firstpage}
-
-\begin{abstract}
-
-We investigate the formation of H$\alpha$ from classical T~Tauri
-stars with a complex circumstellar geometry -- the combination of
-mangnetisherical accretion, collimated steller wind, and accretion
-disc. AND MORE
-
-\end{abstract}
-
-\begin{keywords}
-stars:formation -- stars: individual: SU Aur -- circumstellar matter -- infrared: stars -- stars: pre-main-sequence
-\end{keywords}
-
-\section{Introduction }
-
-\label{sec:Introduction}
-
-T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
-\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
-of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
-H$\alpha$ emission, and typically have spectral types of F--K. Some
-of the most active CTTS show emission in higher Balmer lines and metal
-lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit an excess
-amount of continuum flux in the ultraviolet (UV) and infrared (IR).
-Their spectral energy distribution and polarization data suggest the
-presence of a circumstellar disc, and it plays an important role in
-regulating dynamics of gas flows around CTTS.
-
-Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
-\citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profles show that the evidence for both outward wind
-flows and inward accretion flows, as seen in the blueshifted absorption
-features in H$\alpha$ profiles and the redshifted inverse P~Cygni
-(IPC) profiles. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
-to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
-\citealt{edwards:1987}; \citealt{hartigan:1995}), and the mass-accretion
-rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
-
-Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
-show the direct evidence for the presence of bipolar and monopolar
-outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
-two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
-and HV~Tau~C) by \citet{appenzeller:2005} show the extended (SCALE?)
-H$\alpha$ emission in the direction perpendicular to the obscuring
-circumstellar disc, and in both above and below the disc --- suggesting
-the presence of the bipolar outflows. In silightly larger scale, \emph{HST}
-observation of HH30 (Burrorws et al 1996) shows the jet traced to
-within $\lesssim30$~AU from the star. The jet has a cone shape with
-an opening angle of $3^{\circ}$ between 70 and 700 AU. (Originally
-from Konig and Pudritz 2000 review in PP IV). \citealt{alencar:2000}
-found about 80 per cent of their samples (30 CTTS) show blueshifted
-absorption componets in at least one of Balmer lines and Ca~K (most
-commonly in H$\alpha$).
-
-In a currently favoured model of accretion flows around CTTS, the
-accretion discs are disrupted by the magnetosphere of stars which
-channels the gas from the disc onto the surface of the stars (e.g.,
-\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993}\citealt{shu:1994}).
-This picture of the accretion flows is supported by the evidences
-that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$) magnetic
-field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
-and by the radiative transfer models which reproduce the observed
-profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
-accretion model naturally explains the blueward asymmetic emission
-lines (seen in some of CTTS) caused by the partial occulation of the
-flow by the disc, and the redshifted absorption componet at the typical
-free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$) seen
-in some of CTTS.
-
-Dispite the success of the magnetosherical accretion model in explaining
-the line profiles in some CTTS, the overwhelming observational evidences
-for the outflow (mentoned above) in the CTTS profiles suggests that
-this model is only a part of a whole picture. Clearly, the modefification
-to include the outflowing wind/jet flow is neccessary if one requires
-to predict the mass-accretion rate and the mass-loss rate of CTTS
-by modelling their emission profiles (e.g. H$\alpha$).
-
-Priory to the magnetospherical models, many alternative models had
-been considered to explain the observed spectroscopic features mentioned
-earlier. For example, 1.~the Alfv\'{e}n wave-driven wind model (e.g.~\citealt{decampli:1981};
-\citealt{hartmann:1982}), 2.~turbulant boundary layer (between the
-accretion disc and stellar surface) model (e.g.~\citealt{bertout:1988};
-\citealt{basri:1989}), 3.~chromospheric model (e.g.~\citealt{calvet:1984}),
-and 4.~disc wind model (e.g. \citealt{calvet:1992b}; \citealt{kwan:1995}).
-Considering the sucess of the magnetospherical accretion flow model
-in some cases and the observational eividences for the outflows, it
-is likely that an improved spectroscopic model requires both inflow
-and outflow components. The combination of the magnetospheric accretion
-flow model with model 1 or 4 would be a reasonable starting point
-for an improved spectroscopic model. Although time consuming to explore
-a larger parameter space, more realistic density, velocity and temperature
-structure from magnetohydrodynamic wind+accretion models should be
-considered as inputs for an radiative transfer model in the future.
-
-The magnetocentrifugal wind model, first proposed by \citet{blandford:1982},
-has been often used to reproduce the large-scale wind structure of
-T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
-by \citealt{burrows:1996}; \citealt{ray:1996}). The lanching of
-the wind from a Keplerian disc is typically done by treating the equaotorial
-plane of the disc as a mass-injecting boundary condition (e.g., \citealt{ustyugova:1995};
-\citet{shu:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
-Depending on the location of the open magnetic fields anchored to
-the disc, two different types of winds are preoduced. If the field
-is constrained to be near the co-rotation radius of stellar magnetosphere,
-an {}``X-wind'' \citep{shu:1994} is produces. If the open field
-lines are located in a wider area of the disc, a {}``disc-wind''
-similar to \citet{koenigl:2000} is produced \citet{krasnopolsky:2003}.
-Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
-and \citet{pudritz:2005}.
-
-In this paper, we present a semi-emperical wind -- accretion disc
--- magnetospherical accretion hybrid model for CTTS, and perform parametric
-studies of the H$\alpha$ formation. This study should provide preliminary
-physical conditions which lead to the wide varaiety of emission line
-profiles seen in the observation, and would help to construct more
-comprehensive circumstellar models (e.g. via MHD simulations) of T~Tauri
-stars. the Using the model results, we examine the H$\alpha$ spectroscopic
-classification used by \citet{reipurth:1996}, and compare models
-with observations. We will also discuss whether our model is consistent
-with some predictions made by the recentt MHD studies (e.g.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$).
-
-In section~\ref{sec:model-configuration}, the model assumptions,
-and the basic model configurations are presented. We discuss the radiaive
-transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
-and the results of model calculations are given in section~\ref{sec:Results}.
-The closer examination and discussion of the results are presented
-in section~\ref{sec:Discussion}. Finally, the summary of this work
-and the conclusion are in section~\ref{sec:Conclusions}.
-
-\section{Model configuration}
-
-\label{sec:model-configuration}
-
-To understand how the different part of the CTTS circumsterllar enviroment
-contributes to the fomation of H$\alpha$, the model spaced is devided
-into four different regions: 1.~Central contiuum source, 2.~magnetosphere
-accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:overview}
-depicts the relative location in the model space. In all regions,
-the density is symmetric around the z-axis. The innermost raius of
-the magnetsphere at the equotrial plane coincides with the the inner
-radius of the accretion disc. From the inner most part of the accretion
-disc, the gas freely fall, moving along the magneic filed onto the
-surface of the star. For the purpose of computational simplicity,
-the colliminated wind are defined only in the outside of the largest
-radius of the magnesophere. In the following subsections, the details
-of model components will be described.
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  scale=0.6]{figures/overview2.eps}
-
-\end{center}
-
-\caption{Basic Model Configuration.
-The system consist of four components: 1.~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, 2.~magnetospherical accretion flow, 3.~colliminated wind/jet outflow, and 4.~accretion disc.
-The density distribution is symmetric around the z-axis.
-The innermost raius of the magnetsphere (at the equotrial plane) coincides with the the inner radius of the accretion disc.
-From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star.
-For simplicit, the colliminated wind/jet exists outside of the largest radius of the magnesophere (dotted line).
-}
-
-\label{fig:overview}
-
-\end{figure*}
-
-\subsection{Contiuum Source}
-
-\label{sub:Contiuum-Source}
-
-Unless specified otherwise, we adopt stellar parameters of a typical
-classical T~Tauri star (REF) for the central conitnuum source, i.e.
-radius ($R_{*}$), mass ($M_{*}$), and effective temperature the
-photosphere ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$,
-and $4000\,\mathrm{K}$ respectively. The model atomsphere of \citet{kurucz:1979}
-equivallently \citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$
-and $\log g_{*}=3.5$ (cgs) is used to continuum flux at H$\alpha$wavelength.
-The parameters are summarised in Table~\ref{tab:std_parameters}.
-
-The limb-darkening law used for the continuum source is $I\left(\mu\right)=I_{0}\left(1+b\mu\right)$
-where $\mu=\cos\theta$ and $\theta$ is the polar angle. $b$ is
-a parameter. For no limb-darkening case, $b=0$, and for the Eddington
-approximation case $b=3/2$. The former is used in all the calulcations
-presented here. (Is this an ok assumption for T Tauri's? You need
-to check this.)
-
-\begin{table*}
-
-\begin{center}
-
-\begin{tabular}{lcccccccccccc}
-\hline 
-Parameters&
-$R_{*}$&
-$M_{*}$&
-$T_{\mathrm{ph}}$&
-$R_{\mathrm{mi}}$&
-$R_{\mathrm{mo}}$&
-$\dot{M}_{\mathrm{acc}}$&
-$\dot{M}_{\mathrm{wind}}$&
-$\beta$&
-$v_{\infty}$&
-$m$&
-$R_{\mathrm{di}}$&
-$R_{\mathrm{do}}$\tabularnewline
-&
-$\left[R_{\sun}\right]$&
-$\left[M_{\sun}\right]$&
-$\left[\mathrm{K}\right]$&
-$\left[R_{*}\right]$&
-$\left[R_{*}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$[-]$&
-$[\mathrm{km\, s^{-1}}]$&
-$[-]$&
-$\left[R_{\sun}\right]$&
-$\left[\mathrm{AU}\right]$\tabularnewline
-\hline
-Standard&
-$2.0$&
-$0.5$&
-$4000$&
-$2.2$&
-$3.0$&
-$10^{-7}$&
-$10^{-8}$&
-$0.2$&
-$200$&
-$2.0$&
-$2.0$&
-$100$\tabularnewline
-\hline
-\end{tabular}
-
-\end{center}
-
-\caption{The summary of the standard classical T~Tauri star model parameters.}
-
-\label{tab:std_parameters}
-
-\end{table*}
-
-\subsection{Magnetosphere}
-
-\label{sub:Magnetosphere}
-
-We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
-as done so by \citet{muzerolle:2001} and by \citet{symington:2005},
-in which the gas accretion on to the stellar surface from the innermost
-part of the accretion disc occurs through a dipolar stellar magnetic
-field. The magnetic field is assumed to be so strong that the gas
-flow does not affect the underlying magnetic field itself. As shown
-in Fig.~\ref{fig:overview}, the innermost radius ($R_{\mathrm{mi}}$)
-of the magnetophere at the equatorial plane ($z=0$) is assigned to
-be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
-disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
-and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
-the equaotrial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
-respectively. The former value corresponds to the corotation radius
-of the accretion disc, and the geometry of the magnetic field/stream
-lines is kept constant throghout this paper. The geometry of the magnetosphere
-is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
-
-The magnetic field and the gas stream lines are assumed to have the
-following simple form: $r=R_{\mathrm{m}}\sin^{2}\theta$ \citep[see][]{ghosh:1977}
-where $r$, and $\theta$ are coordinates of the field point ($p$)
-in Fig.~\ref{fig:overview} in spheical coodinates, and $R_{\mathrm{m}}$is
-the radial distance to the field line at the equotorial plane ($\theta=\pi/2$).
-The range of $R_{\mathrm{m}}$is restricted between $R_{\mathrm{mi}}$
-and $R_{\mathrm{mo}}$ as mentioned above. Using the field geometry
-above, the conservation of energy, and igoring the rotation of magnetosphere,
-the velocity and the density of the accreting gas along the steam
-line can be found. See \citet{hartmann:1994} for details.
-
-In all of our models, the temperature structure of the magnetospheric
-used by \citet{hartmann:1994} is also adoped here. The temperature
-structure was computed assuming a volumetric heating rate which is
-proportional to $r^{-3}$, and using the energy balance of the radiative
-cooling rate of \citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
-Although the temperature structure of the accretion steam could significantly
-affect the line source function, for the purpose of the expolaring
-the general characteristics of the H$\alpha$ formation, this simple
-form is a reasonable assumption.\citet{martin:1996} presented the
-self-consistent determination of the thermal structure of the inflowing
-gas along the dipole magnetic field, same as the one used here, by
-solving the heat equation couple to trate equations for hydrogen.
-He found that main heat source is adiabatic compression due to the
-convering nature of the flow, and the major contirbutors of the cooling
-process are bremsstrahling radiation and line emission from Ca~II
-and Mg~II ions. The temerature sturcture of \citet{martin:1996}
-qualitaively agrees with that of \citep{hartmann:1994}. The sensitivty
-tests of H$\alpha$ on the temperature structure will be presented
-later (SPECIFY THE SECTION LATER).
-
-As the infalling gas becomes closer to the stellar surface, it is
-decelerates in a strong shock, and heated to $\sim10^{6}\,\mathrm{K}$
-(with typical parameters). The X-ray radiation produced in the shock
-will be absorbed by the gas located near, and reemitted in optical
-and UV radiation (\citealt{koenigl:1991}; \citealt{hartmann:1994}).
-This will create hot rings near the stellar surface where the magnetic
-field intersects with the surface. For simplicity, the free-falling
-kinetic energy is assumed to be thermalized in the radiating layer,
-and reemits as blackbody radiation (with a single temerature). With
-the parameters of the magnetosphere and the star given above (Table~\ref{tab:std_parameters}),
-about $8$~per~cent of the surface is covered by the hot rings,
-and its temperature is about $6400\,\mathrm{K}$. If the mass-accretion
-rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this
-accretion luminosity to the photospheric luminosity is about $0.5$.
-The contiuum emission from the hot rings is taken into account when
-computing the line profiles.
-
-\subsection{Wind}
-
-\label{sub:wind_jet}
-
-\subsubsection{Colliminated wind model}
-
-JUSTTIFICATION OF USING THIS FORMULATION. BREIFLY MENTIONED THE WORK
-DONE BY OTHERS.
-
-Based on the simple model of \citet{appenzeller:2005}, the following
-parametrisation of colliminated wind/jet (region 3 in Fig.~\ref{fig:overview})
-is adopeted. The wind velocity field, $\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$,
-is consist of radial and polar components which depend only on $r$
-and $\theta$ respectively. The radial componet $v_{r}\left(r\right)$
-is assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
-and the azimuthal component $v_{\phi}$ is asuumed to be a constant
-fraction ($\gamma$) of the Keplerian velocity for a given distance
-($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:
-
-\begin{eqnarray}
-\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}+v_{\theta}\hat{\btheta}\label{eq:wind_velocity_def}\end{eqnarray}
-where \begin{equation}
-v_{r}\left(r\right)=v_{r0}+v_{\infty}\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
-\begin{equation}
-v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
-and \begin{equation}
-v_{\theta}\left(r,\theta\right)=v_{\theta0}\,\left(\frac{R_{\mathrm{mo}}}{r}\right)^{\alpha}\frac{\tan\theta}{\left|\tan\theta\right|}\,.\label{eq:wind_velocity_polar_part}\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$, and
-the range of the polar angle is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
-where $\theta_{\mathrm{disc}}$ is the openning angle of the accretion
-disc, to avoid the overlap. $v_{r0}$is the small radial velocity
-at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$,
-approximately the thermal velocity of hydrogen with $T=7500\,\mathrm{K}$
-and $\gamma=0.05$ (\citealt{appenzeller:2005}) are used. The dependency
-of $v_{r}$ in polar direction ($\theta=0$) on the values of wind
-accerelation parameter $\beta$ is shown in Figure~\ref{fig:wind_vr_rho}.
-All other parameters describing the wind are fixed as the standard
-values given in Table~\ref{tab:std_parameters}.
-
-Further, the density of the wind is assumed to be axi-symmetric and
-separable in $r$ and $\theta$ for computationaly simpliciy, i.e.,
-
-\begin{equation}
-\rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)\label{eq:wind_density_def}\end{equation}
- with \begin{equation}
-F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
- where $b$ is normally positive even number (for the density symmetric
-about the equtotrial plane), and $n$ is the angular normalisation
-constant. For $b=0$, the wind is sherically symmetic exept for the
-parts dirupted by the accretion disc. The larger the value of $b$,
-the higher the degree of the collimination. By integrating equation~\ref{eq:wind_density_theta}
-over angles and normalising the integral to $4\pi$, one finds \begin{equation}
-n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
- Asumming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
-and the mass-flux conserves in time, the radial part of the density
-function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
-hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
-\rho\left(r,\theta\right)=\frac{n\,\cos^{b}\theta\,\dot{M}_{\mathrm{wind}}}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
- For a given mass-accretion rate, the wind mass-loss rate in our typical
-model is assined from the ratio of mass-loss to mass-accretion rate
-($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
-by both observations and magnetohydrodynamical calculations (see e.g.
-\citealt{koenigl:2000}).
-
-Figure~\ref{fig:wind_vr_rho} shows the values of $\rho$ in polar
-direction ($\theta=0$) for different values of $\beta$ with all
-other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{cc}
-\includegraphics[%
-  clip,
-  scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
-\includegraphics[%
-  clip,
-  scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{The dependency of the wind/jet velocity and density structures on the wind accerelation parameter $\beta$.
-The radial component of the wind/jet velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left.
-The wind/jet density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is right.
-The smaller the value of $\beta$, the faster the accerelation of the wind.
-For the raidus ($r/R_{\mathrm{mo}} < 10$, both velocity and density are sensitive to the value of $\beta$.
-For all $\beta$ values, the radial velocity of the wind reaches the terminal velocity ($\sim 210\,\kmps$ by  $r/R_{\mathrm{mo}} \sim 1000$.
-The initial velocity $V_{0}=10\,\kmps$, which approximately corresponds to the thermal velocity of a hydrogen atom at 7500~K,  is used for all $v_{r}$ plots.
-Beyound $r/R_{\mathrm{mo}}= 100$, little difference is seen in the polar density with diffrent $\beta$ values.}
-
-\label{fig:wind_vr_rho}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Disc-wind model}
-
-GIVE MORE CONVINCING MOTIVIATION FOR USING THIS MODEL. THIS SECTION
-MAY BE DELETED.
-
-Alternative to the colliminated wind model, the kinematic disc-wind
-mode of \citet{knigge:1995} in which a wind originating from the
-surface of the accretion disc with a biconical outflow geometry (Fig.~XXX)
-will be presented next. The model was originally developed for describing
-the formation of the UV resonance lines in the winds of cataclystic
-variable (CV) stars.
-
-\subsection{Accretion disc}
-
-\label{sub:Accretion-disc}
-
-Region 4 in Fig.~\ref{fig:overview}
-
-\subsubsection{Density and velocity}
-
-Although it is possible, in our model, to compute the dust-sublimination
-radius and the vertical hydrostatic structure of the accretion disc
-self-consistently (assuming the radial dependecy of the mid-plane
-density) by using the interative Monte Calro radative transfer technique
-(c.f.~\citet{walker:2004}), we find it to be too time consuming
-for the purpose of this paper -- understanding the general characteristic
-of H$\alpha$ profile shapes hence exploring a large parameter space.
-For this reason, we adopt a simple analytical disc model, the steady
-$\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
-with the inner radius fixed at the inner radius of the magnetosphere
-(at equatorial plane). The disc density disribution is given by
-
-\begin{equation}
-\rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
- where $w$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
-axis, the scale height, the distance from the disc plane, and the
-surface density at the mid-plane, respectively. The mid-plane surface
-density and the scale height are given as: \begin{equation}
-\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{d}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
- where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
-and the disc mass respectively.\begin{equation}
-h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.\label{eq:scale-height}\end{equation}
- With these parameters, the disc is slightly flared. The inner radius
-of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
-radius of the magnetosphere at the equaotrial plane), which is approximatly
-same as the co-rotating radius of the system with the paramters in
-Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
-of an object is assumed to be 1/100 of the central mass ($M_{*}$),
-and the disc radius ($R_{\mathrm{di}}$) to be 100~au. The velocity
-of the gas/dust in the disc is assumed to be Keplerian.
-
-\subsubsection{Dust model}
-
-To calculate the dust scattering and absorption cross section as a
-function of wavelength, the optical constants of \citet{draine:1984}
-for amorphous carbon grains and \citet{hanner:1988} for silicate
-grains are used. The model uses the {}``large grain'' dust model
-of \citet{wood:2002} in which the dust grain size distribution is
-described by the following function:\begin{equation}
-n\left(a\right)da=\left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\, a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da\label{eq:grain-dist-function}\end{equation}
- where $a$ is the grain size restricted between $a_{\mathrm{min}}$
-and $a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$
-are the terms set by requiring the grains to completely deplete a
-solar abundance carbon and silicon. The parameters adopted in our
-model are: $C_{\mathrm{C}}=1.32\times10^{-17}$, $C_{\mathrm{Si}}=1.05\times10^{-17}$,
-$p=3.0$, $q=0.6$, $a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
-$a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
-and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds
-to Model~1 of the dust model used by \citet{wood:2002}. See also
-their Fig.~3 The relative number of each grain is assumed to be that
-of solar abundance, C/H$\sim3.5\times10^{-4}$ \citep{anders:1989}
-and Si/H$\sim3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
-to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
-Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.
-
-\section{Radiative transfer model}
-
-\label{sec:radiative-transfer-model}
-
-We have extended the TORUS radiative transfer code (\citealt{harries:2000};
-\citealt{kurosawa:2004a}; \citealt{symington:2005}) to compute the
-H$\alpha$ profiles from pre-main-sequence stars which are surrounded
-by one or more of the followings: the magnetospherical accretion flow,
-the out-flowing colliminated wind, and the accreation disc. Previously
-in \citet{symington:2005}, the model used in the three-dimentional
-(3-D) adaptive mesh refinement (AMR) to inverstigate the line variability
-mainly associated with roational motion of complex geometrical configurations
-of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
-modefied the code to handle the two-dimentional (2-D) density distribution,
-and restricted our models to be axi-symmetric. It was done so in order
-to enable us to explore rather large number of parameter spaces (c.f.~section~\ref{sec:model-configuration}).
-Note that the velocity field is still in 3-D -- the third component
-can be calculated by using the symmetry for a given value of azimutal
-angle. The examples of how the AMR grid for the purpose of the radiative
-transfer is constructed are presented in e.g. \citet{wolf:1999},
-\citet{kurosawa:2001a} and \citet{steinacker:2003} .
-
-The computation of the H$\alpha$ is devided in two parts: 1.~the
-source function calculation and 2.~the observed flux/profile calulcation.
-In the first process, we have utilized the method by \citet{klein:1978}
-(see also \citealt{rybicki:1978}; \citet{hartmann:1994}) in which
-the Sobolev approximation method is applied. The population of the
-bound states of hydrogen are assumed to be in statistical equilibrium,
-and the gas to be in radiative equilibrium. Our hydrogen atom model
-consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
-for details. (AND MORE..)
-
-To compute the observed line profile, the Monte Calro radiative transfer
-method (e.g. \citealt{hillier:1991}) using the Soblev escape-probabiliy
-can be used when I.~a large velocity gradiant is present in the gas
-flow, and II.~the intrinsic line width is negleible compared to the
-Doppler broadeing of the line. In our earlier models (\citealt{harries:2000};
-\citealt{symington:2005}), this method was used to compute the line
-profiles since the condition I and II are resonably satisfied. However,
-as noted and demonstrated by \citet{muzerolle:2001}, even with a
-moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
-Stark broadening becomes important in the optically thick H$\alpha$
-line. \citet{muzerolle:2001} (MORE REF HERE) also pointed out that
-the observed H$\alpha$profiles from CTTS typically have the wings
-extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
-\citet{reipurth:1996}) which cannot be explained by the infall velocity
-of the gas along the magneosphere.
-
-To implement the broadening meachanism, two modedifications to our
-previous model (\citealt{symington:2005}) are necessary. First, the
-emission and absorption profiles must be replaced by a Voigt profle
-which is defined as: \begin{equation}
-H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
- where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$, $y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$,
-and $y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$ (c.f. \citealt{mihalas:1978}).
-$\nu_{0}$ is the line centre frequency, and $\Delta\nu_{\mathrm{D}}$
-is the Doppler line width of hydrogen atom (due to its thermal motion)
-which is given by $\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
-where $m_{\mathrm{H}}$ is the mass of a hydrogen atom. The damping
-constant $\Gamma$, which depends on the physical condition of the
-gas, is parameterised by \citet*{vernazza:1973} as follows:
-
-\begin{eqnarray}
-\Gamma & = & C_{\mathrm{rad}}+C_{\mathrm{vdW}}\left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)\left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
- &  & +\, C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}\label{eq:dampimg_constant_def}\end{eqnarray}
- where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
-neutral hydrogens and that of free electrons. Also, $C_{\mathrm{rad}}$,
-$C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are natural broadening,
-van der Waals broadening, and linear Stark broadening constants respectively.
-We simply adopt this parameterization along with the values of broadening
-constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
-$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and $C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.
-In terms of level populations and the Voigt profile, the line opacity
-for the transition $i\rightarrow j$ can be written as: \begin{equation}
-\chi_{l}=\frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}\left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)\label{eq:line_opacity}\end{equation}
- where $f_{ij}$, $n_{i}$, $n_{j}$, $g_{i}$and $g_{j}$ are the
-oscillator strength, the population of $i$-th level, the population
-of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
-of the $j$-th level respectively. $m_{e}$and $e$ are the electron
-mass and charge (c.f. \citealt{mihalas:1978}).
-
-The second modefication in our model is the replacement of the method
-of solving the formal solution from the Monte Calro radiative transfer
-method with Sobolev approximation to the direct integration method.
-Similarly to the notation used by \citet{muzerolle:2001}, we specify
-the cylindical coordinates $\left(p,\, q,\, t\right)$ which is the
-original stellar coordinate system $\left(\rho,\,\phi,\, z\right)$
-rotated (around $y$ axis) by the inclination of the line of sight,
-i.e. the $t$-axis coinsides with the line of sight. The observed
-flux ($F_{\nu}$) is given by: \begin{equation}
-F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
-where $d$, $p_{\mathrm{max}}$, and $I_{\nu}$ are the distance to
-an observer, the maximum extent to the model space in the projected
-(rotated) plane, and the specific intensity ($I_{\nu}$) in the direction
-on observer at the outer boundary. For a given ray along $t$, the
-specific intensity is given by:\begin{equation}
-I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{-\infty}^{t_{0}}\eta_{\nu}\left(t\right)\, e^{-\tau\left(t\right)}\mathrm{d}t\label{eq:formal_sol_integral}\end{equation}
- where $I_{0}$ and $\eta_{\nu}$ are the intensity at the boundary
-on the opposite to the observer and the emissivity of the stellar
-atmosphere/wind at a frequency $\nu$. For a ray which intersects
-with the stellar core, $I_{0}$ is computed from the stellar stompshere
-mode of \citet{kurucz:1979} as descibed in section~\ref{sub:Contiuum-Source},
-and $I_{0}=0$ otherwise. The initial position of each ray is assigned
-to be at the center of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
-The code excution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
-where $n_{p}$ and $n_{q}$ are the number of cylindical radial and
-angluar points for the flux integration, and $n_{\nu}$is the number
-of frequency points. In the models presented in the next (section~\ref{sec:Results}),
-$n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
-otherwise. The linearliy spaced radial grid is used for the area where
-the ray intersects with magnetpshere, and the logarithmically spaced
-grid is used for the wind and the accretion disc regions.
-
-The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
-is defined as: \[
-\tau\left(t\right)\equiv\int_{-\infty}^{t}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
- where $\chi_{\nu}$ is the opacity of media the ray passes through.
-$\tau_{\infty}$ is the total optical depth measured from the initial
-ray point to the observer (or to the outer boundary closer to the
-observer). Initially, the optical depth segments $\mathrm{d\tau}$
-are computed at the intersections of a ray with the original AMR grid
-in which the opacity and emissivity infomation are stored. For high
-opticale depth models, additional points are inserted between the
-original points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$
-values are interpolated to those points to ensure $\mathrm{d}\tau<0.05$
-for the all ray segments.
-
-For a point in the magnetosphere and the wind flows, the emissivity
-and the opacity of the media are given as:\begin{equation}
-\left\{ \begin{array}{rcl}
-\eta_{\nu} & = & \eta_{\mathrm{c}}^{\mathrm{H}}+\eta_{l}^{\mathrm{H}}\\
-\chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}+\sigma_{\mathrm{es}}\end{array}\right.\label{eq:emiss_opa_gas}\end{equation}
-where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$
-are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
-$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the contiuum,
-line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
-electron scattering opacity. Similarly, for a point in the accretion
-disc,
-
-\begin{equation}
-\left\{ \begin{array}{rcl}
-\eta_{\nu} & = & 0\\
-\chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}+\kappa_{\mathrm{sca}}^{\mathrm{dust}}\end{array}\right.\label{eq:emiss_opa_dust}\end{equation}
- where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and $\kappa_{\mathrm{sca}}^{\mathrm{dust}}$
-are the dust absorption, and scattering opacity which are calculated
-using the dust property described in section~\ref{eq:grain-dist-function}.
-For computational simplicity, we assumed that the dust emissivity
-is zero. Since the disc mass of CTTS are rather small ($\sim0.1\,\mathrm{M_{\sun}}$)
-and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
-contribution at H$\alpha$ wavelength is expected to be neglegible
-(e.g.~\citealt{chiang:1997}). The scattering flux by the accretion
-may become important for H$\alpha$ for the edge-on ($i\sim90^{\circ}$)
-cases in which the disc obscures the stellar surface -- the main source
-of contiuum flux. We examine this effect later in section~\ref{sub:model-acc-disc-wind}.
-
-\section{Results}
-
-\label{sec:Results}
-
-\subsection{Magnetosphere}
-
-\label{sub:model-acc}
-
-Using the standard parameters (Table~\ref{tab:std_parameters}) for
-the central star and the magentosphere, we examine the dependency
-of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
-flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
-done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
-is computed from the avilable kinetic energy of the free-falling gas
-as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
-used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
-of their models. The accretion luminosity ($L_{\mathrm{acc}}$) of
-models with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-is about a half of the total luminosity (without the hot ring) of
-the star, and $L_{\mathrm{acc}}$is proportional to $\dot{M}_{\mathrm{acc}}$.
-The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
-dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are
-similar to that of \citet{muzerolle:2001}. In general, the line strength
-becomes weaker as the accretion rate and the temperature become smaller.
-The red-shifted absorption becomes less visible for higher accretion
-rate and temperature models in which the flux in the damping wings
-become important. Figure~\ref{fig:broadening} shows an example of
-the effect of the boradening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
-due to the damping constants as described in section~\ref{sec:radiative-transfer-model}.
-Although the maximum flux of the model with the broadening is almost
-identical to that of the model with no damping constant ($\Gamma=0$),
-a significant increase of the line flux in both red and blue wings
-of seen in the model with broadening. A weak red-shifted absorption
-component (which is a signiture of the magnetospherical accretion)
-is weakened or eliminated by the flux in broadened wing.
-
-Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown
-in Figure~\ref{fig:atlas_acc_models}. About a half of the models
-shown the figure agree with the observed EW values of H$\alpha$ from
-30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
-ranges from $\sim3$~\AA\, to $\sim160$~\AA, and the mean to
-be $\sim55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
-the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
-and for some models the EWs are negative. Since the target selection
-criteria of \citet{alencar:2000} is not stated in their paper, we
-can not conclude that these low $\dot{M}_{\mathrm{acc}}$models disagree
-with the observation. \citet{reipurth:1996}, who measured the EW
-of 43 TTS and found similar distribution of EW values, mentioned that
-their EW measurements are underrepresenting real samples since the
-selection of the targerts are based on the strong H$\alpha$ emission
-in H$\alpha$ surveys.
-
-The dependency of the profile on the inclination angle ($i$) is demonstrated
-in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
-paramters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
-The figure show that the peak (normalized) flux decrease as the inclination
-angle increases. Similarly, the equivalent width also decreases as
-the inclination increases. Because of the geometry of the magnsepsherical
-accretion (c.f. Figure~\ref{fig:overview}) and of the presence of
-the gas with the highest velocity close to the stellar surface, the
-highest red-shifted line-of-sight velocity is visible only at the
-high incination angles. This explains the wider appearence of the
-profile with $i=80^{\circ}$compared to the relatively narrow line
-appearence of the profile with $i=10^{\circ}$. Although not show
-here, a similar depdency on the inclination angle is found for the
-models with different temperatures ($T_{\mathrm{max}}=6500$, $8500$,
-$9500\,\mathrm{K}$).
-
-As seen in the models of \citet{hartmann:1994} and \citet{muzerolle:2001},
-our models also show the blue-shifted peak and the blue-ward asymmetry
-caused by the occultation of the accretion flow by the equotrial disc
-and the stellar disc. On the hand, \citealt{alencar:2000} (see their
-Fig.~9) found a substential fraction of the observed H$\alpha$ profiles
-also shows the {}``red-shifted'' peak, and the P~Cygni profiles
-which can not be explained by the magnetospherical accretion model
-alone. In addition, a recent study by \citet{appenzeller:2005} showed
-that the equivalent width of H$\alpha$ increases as the inclination
-angle increases. Our model with the magnetospherical accreation flow
-clearly disagrees with their finding.
+Although not shown here for clarity, the peak flux near the line centre
+is also affected by the wind absorption (causing about 10 per cent
+reduction) compared to the profile computer with magnetosphere only
+model (similar effect also seen in Figure~\ref{fig:atlas_disc_wind_acc_model}).
+If the fit was performed by ignoring the wind, the temperature and
+the mass-accretion rate of the magnetospherical accretion flow will
+be underestimated. A better approach to a model fit is a simultaneous
+fitting of multiple lines. For example, the near-infrared lines such
+as Pa$\beta$ and Br$\gamma$ should be used to determined the mass-loss
+rate since these lines are much less affected by the wind. Using the
+mass-loss rate from these lines, H$\alpha$ can be used to determine
+the wind mass-loss rate.
 
@@
   clip,
-  scale=0.45]{figures/atlas_ha_i55_acc_model_new3.eps}
+  scale=0.45]{figures/ttau_compare.eps}
 
@@
 
-\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M_\mathrm{acc}}$) and temperature ($T_{\mathrm{max}}$).
-The profiles are computed using only magnetospherical accretion flow (i.e.
-no wind/jet).
-All the profiles are computed using the parameters of the 'standard' model (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the mass accretion rate (indicated by the values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from left to right.
-The profiles are similar to those of \citet{muzerolle:2001}, available on-line (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html).
-}
+\caption{Comparison of the observed H$\alpha$ profile of T~Tau and the
+profile computed with the hybrid model, which consist of the
+magnetosphere, the colliminated wind, and the accretion disc (with a
+large hole i.e. $\sim 5$~AU). The inclination angle $29^\circ$ is
+used.  The maximum temperature of the magnetosphere
+($T_{\mathrm{max}}$) and the isothermal wind temperature are
+22000~K and 8000~K respetively. The mass-accretion rate
+($\dot{M}_{\mathrm{acc}}$) and the mass-loss rate
+($\dot{M}_{\mathrm{wind}}$) are $1.1 \times
+10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and $2.0 \times
+10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ resplectively
+($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.18$)}
 
-\label{fig:atlas_acc_models}
+\label{fig:ttau_model}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table}
-
-\begin{center}
-
-\begin{tabular}{cccc}
-\hline 
-$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
-&
-$\dot{M}_{\mathrm{acc}}$ ~$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-\tabularnewline
-&
-$10^{-7}$&
-$10^{-8}$&
-$10^{-9}$\tabularnewline
-\hline 
-$6500$&
-$17.9$&
-$0.1$&
-$0.0$\tabularnewline
-$7500$&
-$25.2$&
-$-0.9$&
-$-0.5$\tabularnewline
-$8500$&
-$68.3$&
-$6.5$&
-$-0.7$\tabularnewline
-$9500$&
-$98.6$&
-$52.4$&
-$1.3$\tabularnewline
-\hline
-\end{tabular}
-
-\end{center}
-
-\caption{The summary of H$\alpha$ equivalent widths from the magnetospherical accretion flow models show in Figure~\ref{fig:atlas_acc_models}.}
-
-\label{tab:ha_ew_acc_models}
-
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/broadening.eps}
-
-\end{center}
-
-\caption{Effect of the line broadening for H$\alpha$.
-The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the one with no damping constant, $\Gamma=0$ (dashed).
-Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}.
-The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant.
-The broaded wings extend to $\sim \pm 900 \kmps$.
-The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.
-}
-
-\label{fig:broadening}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/acc_inc_effect.eps}
-
-\end{center}
-
-\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).
-The profiles are computed with the magneospherical accretion flow using the standard parameters given in Table~\ref{tab:std_parameters} and $T_{\mathrm{max}}=7500~\Kelvin$.
-The solid, dotted, and dashed lines are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$ respectively.
-As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.
-Similar dependency is seen in the models with $T_{\mathrm{max}}=6500, 8500, 9500$~K (not shown here).
-}
-
-\label{fig:acc_inclination_effect}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Collimated Wind}
-
-\label{sub:model-wind}
-
-As mentioned in earlier, the magnetopsherical accretion flow model
-alone cannot explain some of the feartures seen in observations. As
-an alternative model, we now examine formation of H$\alpha$ in a
-simple collimated wind as described in section \ref{sub:wind_jet}.
-The basic wind model parameters introduced earlier are $\gamma$,
-$\beta$, $v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
-and $\dot{M}_{\mathrm{wind}}$. To minimize the number of parameters
-to be explored, we initially adopte $\gamma=0.05$, $v_{\infty}=200\,\kmps$
-\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-Futher, the angular extent of the wind is assumed to be close to the
-edge of the accretion disc, i.e. $\theta_{\mathrm{wind}}=80^{\circ}$;
-however, in this section, a simple optically-thick and geometrically-thin
-(i.e. opaque and zero-thickness) disc instead of the standard $\alpha$-disc
-(section~\ref{sub:Accretion-disc}) is used in all models for speed.
-The effect of replacing the geometrically thin disc with the $\alpha$-disc
-will be discussed later in this section. The degree of collimination
-is initially chosen to be $b=4$, i.e. the ratio of the density in
-polar direction to the density at the edge of the wind closest to
-the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
-for given radii. With these parameters kept constant, we examine the
-characterstics of H$\alpha$ profiles, as a function of the wind accereation
-paramter $\beta$ and the isothermal wind temperature $T_{\mathrm{wind}}$.
-Dependency on the other parameters will be discussed later in this
-section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_model.eps}
-
-\end{center}
-
-\caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$).
-The profiles are computed with only wind/jet (no magnetospherical accretion flow).
-The parameters of the 'standard' model (Table~\ref{tab:std_parameters}) are used.
-The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the wind accerelation rate increases from left to right.
-The P~Cygni profile are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow accerelation) models.
-The postion of the absorption the component moves toward the line centre as $\beta$ increases.
-The effect of line broadening becomes more prominant for higher $T_\mathrm{wind}$ and higher $\beta$ models.}
-
-\label{fig:atlas_wind_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The results are shown in Figure~\ref{fig:atlas_wind_model}. The
-P~Cygni profile are seen only in the models with lower $T_{\mathrm{wind}}$
-and $\beta$ (colder and faster accerelation wind). As the value of
-$\beta$ increases, the postion of the blue-shifted absorption component
-moves toward the line centre. For the slowest wind accerelation models
-($\beta=4.0$), the absorption components appear to be located at
-the line centre, giving the appearence of the double-peak emission
-profile. The line strength is very senstive to the temperature of
-the wind. Although the line should be also sensitive to the temperature
-structure of the wind itself, determination of a self-consistent wind
-temperature is beyound the scope of this paper. Readers are refered
-to \citet{hartmann:1982} in which the wind temperature structure
-is determined by balancing the radiative cooling rate (assuming optically
-thin) with the MHD wave heating rate.
-
-The effect of line broadening becomes more prominant for higher $T_{\mathrm{wind}}$
-and higher $\beta$ models. Unlike the magnetospherical accretion
-only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
-profiles are not seen here. Interestingly, in some models (e.g. $T_{\mathrm{wind}}=9000\,\mathrm{K}$
-and $\beta=1.0$ model), the absorption componet is present at slightly
-red-ward of the line centre, causing the blue-ward asymmetry seen
-in the magnetospherical accretion models. The blue-ward asymetry are
-caused by: 1. the accretion disc placed at the equotorial plane and
-the finited-size steller disc blocking a part of the line emission
-region moving away from an observer, 2.~the much larger optical depth
-for the line emitted from the opposite side of the observer where
-the gas is moving away from the observer. Because of the broad wings
-of the Voigt profile, the line photon intereacts with the gas with
-much wider range of the projected velocity space.
-
-The dependency of the profile on the wind anisotoropy parameter $b$
-is demonstrated in Figure~\ref{fig:effect_wind_b_param}. The line
-peak closer to the line centre and the profile becomes slightly more
-symmetric around the line centre for the isotropic ($b=0$) compared
-to the cases with the colliminated wind ($b=4$). The P~Cygni profile
-feature become prominant for the spherical wind models (especially
-in $\beta=0.5$ model) because the collumn density of along the line
-of a sight of the observer at a medium inclination angle ($i=55^{\circ}$)
-increases as the wind becomes more spherical for a given value of
-the wind mass-loss rate.
-
-Next, we examine the effect of the size of the inner radius of the
-disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_thin_disc}
-shows the wind emission profile computed with and without the equotorial
-accretion disc. The latter can be also considered as a model with
-a large inner radius of the accretion disc in which none of the wind
-emission region is not blocked provided the inclination is moderate.
-The profile shapes of the models are very similar to each other, but
-the one without the accretion disc is slightly more symmetric than
-the other. As one expects, the line equivalent width of the model
-without the disc is about twice of the model with the disc. Interestingly,
-the blueward asymmetry is present also in the profile computed without
-the disc. This is mainly caused by the occultaion of a part of emission
-region by the steller disc and the fact that the wind (density distribution)
-is asymmetric. The H$\alpha$ image (project in the plane of the observer
-at the location of the star) for the model with the disc (middle panel)
-and that for the model without (right plane) are also shown in the
-same figure. The images weere computed with a fast wind accereation
-rate ($\beta=0.5$). The extent of the line emission is smaller ($\sim0.2\,\mathrm{AU}$
-or $\sim20\, R_{*}$) compared to the spectro-astrometric observations
-of \citet{takami:2003} for RU~Lup and CS Cha which have 1--5 AU
-scale outflows%
-\footnote{\citet{takami:2003} also showed that some objects (e.g~Z CMa and
-AS~353A) show the outflows of larger scale ($>50\,\mathrm{AU}$)
-which could be formed by shocks rather than MHD-wave heating (e.g.
-\citealt{hartmann:1982}) or X-ray heating (e.g.~\citealt{shang:2002}). %
-}; however, if a slower wind acceration rate ( $\beta=4$) is the emission
-region become larger slightly ($\sim0.4$~AU).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{cc}
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/wind_b_effect.eps}&
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/windonly_B_effect.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{The effect of wind collimation.
-The dependecy of the line profiles on the wind anisotropy parameter $b$ for the models with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$  is shown on left, and that with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 1.0\right)$ on right.
-All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.
-The degree of the blue-ward asymmetry of the profiles is slightly lower for the spherical (isotroptic) wind model ($b=0$, dashed) compared to the collimated wind (anisotoropic) wind models ($b=4$, solid).
-The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind.
-}
-
-\label{fig:effect_wind_b_param}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{ccc}
-\includegraphics[%
-  clip,
-  scale=0.3]{figures/disc_nodisc_compare.eps}&
-\includegraphics[%
-  scale=0.3,
-  angle=270,
-  origin=lt]{figures/wind_thindisc.eps}&
-\includegraphics[%
-  scale=0.3,
-  angle=270,
-  origin=lt]{figures/wind_nodisc.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{Comparison of of the wind model with and without the optically-thick and geometrically-thin disc.
-The latter can be also equivalent to a model with a large inner radius of the accretion disc in which none of the wind emission region is not blocked provided the inclination is moderate.
-The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used).
-The line profile of the model with the disc (solid) is similar to the model without the disc (dashed), but the latter is slightly more symmetric than the former.
-The line equivalent width of the model without the disc is about 2 times that of the model with the disc.
-The blueward asymmetry is present also in the profile computed without the disc.
-The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown.
-The image flux is computed by integrating the specific flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$.
-The flux is in an arbitrary units and in logarithmic (base $10$) scale.
-}
-
-\label{fig:effect_thin_disc}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magnetosphere $+$ wind}
-
-\label{sub:model-acc-wind}
-
-Next, we examine the characteristics of the line profiles arising
-from the combination of the magnetospherical accretion flow and the
-wind. For simplicity, we fix the parameters for the magnetosphere
-($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-as in Figure~\ref{fig:atlas_acc_models}), and use the constant wind
-mass-loss rate $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$). Figure~\ref{fig:atlas_wind_acc_model}
-shows the results for $i=55^{\circ}$ and the same combinations of
-$T_{\mathrm{wind}}$ and $\beta$ used in section~\ref{sub:model-acc-wind}
-(Figure~\ref{fig:atlas_wind_model}).
-
-While the emission from the magnetosphere dominates for the models
-with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation
-and the colder wind models), the emission from the wind dominates
-for the models with larger $\beta$ and $T_{\mathrm{wind}}$ (the
-slower accerelation and the hotter models). The P~Cygni profile feature
-becomes less prominant in some of the models because the additional
-emission from the magnetosphere extending in the wings. In most of
-the cases, the profiles are understood as a simple sum of the magnetospherilcal
-component and the wind component.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_acc_model.eps}
-
-\end{center}
-
-\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ as in Figure~\ref{fig:atlas_acc_models}).
-While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{wind}}$  (the slower accerelation and the hotter models).
-The P~Cygni profile feature becomes less prominant in some of the models because of the extra emission from the magnetosphere extends in the wings.}
-
-\label{fig:atlas_wind_acc_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magentosphere $+$ disc $+$ wind}
-
-\label{sub:model-acc-disc-wind}
-
-\begin{itemize}
-\item Flux contribution by scattering of photon by disc?
-\end{itemize}
-
-\subsection{Summary}
-
-\section{Discussion}
-
-\label{sec:Discussion}
-
-\subsection{Classification scheme proposed by Reipurth et. al (1996)}
-
-\citet{reipurth:1996}proposed the two-dimentional classification
-of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
-stars. Their classification scheme contains four classes (I, II, III
-and IV) differenciated by the ratio of the secondary-to-primary emission
-components in the profiles. Each classes are devided into two sub-classes
-(B and R) which depends whether the absorption componet is on the
-blue or red side. Readers are refered to Fig.~4 of their paper. Figure~\ref{fig:atlas_reipurth}
-shows the sample profiles which are classified according to the definition
-of \citet{reipurth:1996}. The corresponding model parameters are
-given in Table~\ref{tab:classification}. As we can see from this
-figure, the combinatioin of the wind, magnetospherical accretion,
-and accretion disc can reasonably reproduce all the classes of the
-profiles seen in observations.
-
-Within the parameter space covered, we find it is difficult to produce
-Type I type profile, which is very symmetric around the line centre
-and without any absorption feature, if the wind component is added
-in the model. Type II-B are
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.65]{figures/atlas_reipurth_like.eps}
-
-\end{center}
-
-\caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}.
-The combination of magnetospherical accretion flow, the accretion disc, and the colliminated wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.
-The model parameters and short comments are summarised in Table~\ref{tab:classification}.
-The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.
-}
-
-\label{fig:atlas_reipurth}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table*}
-
-\begin{center}
-
-\begin{tabular}{llllllll}
-\hline 
-&
-$i$&
-$\dot{M}_{\mathrm{acc}}$&
-$T_{\mathrm{max}}$&
-$\dot{M}_{\mathrm{wind}}$&
-$T_{\mathrm{wind}}$&
-$\beta$&
-Comment\tabularnewline
-Class&
-$\left(\mathrm{deg.}\right)$&
-$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-$\left(10^{3}\,\mathrm{K}\right)$&
-$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-$\left(10^{3}\,\mathrm{K}\right)$&
-$\left(-\right)$&
-\tabularnewline
-\hline 
-I&
-$55$&
-$10^{-7}$&
-$7.5$&
-$-$&
-$-$&
-$-$&
-Accretion dominated possibly without the wind at a mid inclination.\tabularnewline
-II-B&
-$10$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$1.0$&
-Accretion and wind, mid wind accerelation rate, low inclination\tabularnewline
-III-B&
-$10$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$8.0$&
-$2.0$&
-Accretion and wind, with slow wind accerelation rate, low inclination\tabularnewline
-IV-B&
-$55$&
-$-$&
-$-$&
-$10^{-8}$&
-$8.0$&
-$0.5$&
-Accretion dominated (low accretion rate), mid inclination \tabularnewline
-II-R&
-$55$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$2.0$&
-Wind dominated, with fast wind accerelation rate, mid inclination\tabularnewline
-III-R&
-$80$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$1.0$&
-Wind dominated, slow wind acceralation rate, high inclination \tabularnewline
-IV-R&
-$55$&
-$10^{-9}$&
-$9.5$&
-$-$&
-$-$&
-$-$&
-Accreetion dominated possibly without the wind at a mid inclination.\tabularnewline
-\hline
-\end{tabular}
-
-\end{center}
-
-\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.}
-
-\label{tab:classification}
-
-\end{table*}
-
-\subsection{Comparisons with observations}
-
-For a demonstrative purpose, we performed preliminary model fit of
-H$\alpha$ observarions
-
-\begin{itemize}
-\item other possible model? Better wind model?
-\item Any other bussiness?
-\end{itemize}
-
-\section{Conclusions}
-
-\label{sec:Conclusions}
-
-We presented the detailed study of the H$\alpha$ formation from the
-circumstealler material of classical T~Tauri stars. AND MORE.
-
-Future studies include:
-
-\begin{enumerate}
-\item Improvement of the wind model. Temperature structure estimate by Hartmann()
-Alancar's paper. Disc-wind model of Branford and ...
-\item Try it with MHD model.
-\item Include the scattering flux term although this requires $N_{\phi}\times N_{\theta}$
-more times to compute a profile. 
-\item Polarization study to explore the geometry and the rotation of the
-disc. 
-\item Gas in the accretion disc (inner most part and the outer layer of
-the disc).
-\item Variability study using a 3D model.
-\end{enumerate}
-\section*{Acknowledgements}
-
-RK is supported by PPARC standard grand PPA/G/S/2001/00081.
-
-%
-
-%
-
-%
-
-%----------------------------------------------------
-
-% Bibliography follows here.
-
-%-----------------------------------------------------
-
-%
-
-%
-
-%
-
-\bibliographystyle{mn}
-
-\bibliography{mnras}
-
-%
-
-\label{lastpage}
-\end{document}

### 2006-01-15 TTau_Halpha/kurosawa.tex
Change made in Discussion sections. The rearranges made in the order of presentation in Model section.  Plus many minor changes.  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@617 25464f21-6099-402c-b30a-640f1d40d38b

@@
 with magnetospherical accretion alone to fitting observed H$\alpha$
-profiles, and to any other lines affected by the stellar wind) presented,
+profiles, and to any other lines affected by the stellar wind,
 two types of kinematic wind models are introduced: (1)~the bipolar
@@
 show direct evidence for the presence of bipolar and monopolar
-outflows down to $\sim 1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
+outflows down to $\sim 1\,\mathrm{au}$ scale (e.g.\,CS~Cha and RU~Lup).
 Similarly, ESO VLT observations using high-resolution ($R=50\,000$)
@@
 of the bipolar outflows. On a larger scale, \emph{HST} observations
-of HH30 \citep{burrows:1996} show the jet traced to within $\lesssim30$~AU
+of HH30 \citep{burrows:1996} show the jet traced to within $\lesssim30$~au
 from the star. The jet has a cone shape with an opening angle of $3^{\circ}$
-between 70 and 700 AU \citep{koenigl:2000}. \citet{alencar:2000}
+between 70 and 700 au \citep{koenigl:2000}. \citet{alencar:2000}
 found about 80 per cent of their sample (30 CTTS) show blue-shifted
@@
 surface of the star. For simplicity,
-the collimated bipolar wind is defined only in the outside of the
+the out-flowing wind component is defined only in the outside of the
 largest radius of the magnetosphere (to avoid overlapping of the wind
 with the magnetosphere). In the following subsections, the details
-of model components will be described. In our models, two different
-types of the wind configurations are considered: (1)~the bipolar
-wind resembling the density structure of the MHD simulation by \citet{krasnopolsky:2003}
-in large scale ($\sim 100$~AU) in section~\ref{sub:wind_jet}, and
-(2) that in small scale ($\sim 10$~AU) in section~\ref{sub:Alternative-model-disc-wind}.
-
+of model components will be described.
 \begin{figure*}
@@
 $\left[R_{*}\right]$&
-$\left[\mathrm{AU}\right]$\tabularnewline
+$\left[\mathrm{au}\right]$\tabularnewline
 \hline
@@
 
-\subsection{Bipolar Wind}
+\subsection{Outflow geometries}
+Two different types of the wind configurations are considered: (1)~the
+bipolar wind model which resembles the density structure of the MHD
+simulation by \citet{krasnopolsky:2003} in \em large scale \em ($\sim
+100$~au), and (2)~the disc-wind model which resembles the density of
+the same MHD simulation in \em small scale \em ($\sim 10$~au).  While
+the wind density is more concentrated toward the polar directions in
+(1), it is more concentrated toward the equatorial direction in
+(2). The following describes each model in details.
+
+\subsubsection{Bipolar Wind}
 
 \label{sub:wind_jet}
-
-As mentioned earlier, the wind model presented here is to simulate
-the collimated MHD disc-wind model of \citet{krasnopolsky:2003} on a 
-large scale ($\sim 100$~AU) , and an alternative wind model which
-resembles the model of \citet{krasnopolsky:2003} in small scale ($\sim
-10$~AU)
-will be presented later (section~\ref{sub:Alternative-model-disc-wind}).
 
@@
 
+\subsubsection{Disc wind}
+
+\label{sub:Alternative-model-disc-wind}
+
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  scale=0.32]{figures/discwind.eps}
+
+\end{center}
+
+\caption{Basic model configuration of the disc-wind, magnetosphere
+hybrid model. The system consist of four components: (1)~the continuum
+source located at the origin $\left( o \right)$ of the cartesian
+coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper,
+(2)~the magnetospherical accretion flow, (3)~the collimated wind/jet
+outflow, and (4)~the geometrically thin (but opaque) accretion disc. The
+disc wind originates from the disc surface between $w_{i}=R_{wi}$ and
+$w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
+lines diverges, are placed at distance $d$ above and below the
+star. By changing the value of $d$, the degree of the wind collimation
+is controlled. The density distribution is symmetric around the
+z-axis. }
+
+\label{fig:config_discwind}
+
+\end{figure}
+
+The wind model presented here is intended to mimic the collimated MHD disc-wind
+calculations of \citet{krasnopolsky:2003} in small scale ($\sim 10$~au).
+\citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
+disc-wind model in their studies of the UV resonance lines formed
+in the winds of cataclysmic variable stars. In this model, the outflow
+arises from the surface of the rotating accretion disc, and has a
+biconical geometry. The specific angular momentum is assumed to be
+conserved along a stream line, and the poloidal velocity component
+is assumed to be simply a radial from vertically displaced {}``sources''
+from the central star. We adopt their disc-wind model here, and consider
+the combined effect of the disc-wind and the magnetospherical accretion
+flow model described earlier. In the following, we briefly described
+their disc-wind model. For details of the models, readers are referred
+to \citet{knigge:1995} and \citet{long:2002}.
+
+Four basic parameters for the models are: (1) mass-loss rate, (2)~the
+degree of the wind collimation, (3)~the velocity gradients, and (4)~the
+wind temperature. The basic configuration of the disc-wind model is
+shown in Figure~\ref{fig:config_discwind}. The disc wind originates
+from the disc surface, but the {}``source'' point ($S$), from which
+the stream lines diverges, are placed at distance $d$ above and below
+the centre of the star. By changing the value of $d$, the degree
+of the wind collimation is controlled. The larger the value of $d$,
+the wind becomes more parallel to the rotation axis, i.e. the wind
+becomes more collimated. The mass-loss launching is restricted between
+$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ where the former is set
+to be equal to the outer radius of the magnetosphere ($R_{\mathrm{mo}}$)
+for simplicity and the latter is set to $1$~au as in \citealt{krasnopolsky:2003}.
+
+The local mass-loss rate per unit area ($\dot{m}$) is assumed to
+be proportional to the mid-plane temperature of the disc, and is a
+function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
+, i.e. \begin{equation}
+\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
+ Further, the mid-plane temperature of the disc is assumed to be expressed
+as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
+relation above, one finds \begin{equation}
+\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
+where $p=\alpha\times q$. The index of the mid-plane temperature
+power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
+who found the inner most part of the accretion disc has $q=-1.15$.
+To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
+who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
+of proportionality in equation~\ref{eq:discwind-massloss-w} is found
+by integrating $\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$,
+and the normalising the value to the total mass-loss rate $\dot{M}_{\mathrm{dw}}$.
+
+The azimuthal/rotational component of the wind velocity $v_{\phi}\left(w,z\right)$
+is computed from the Keplerian rotational velocity at the emerging
+point of the stream line i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
+where $w_{i}$ is the distance from the rotational axis ($z$) to
+the emerging point on the disc, and by assuming the conservation of
+the specific angular momentum along a stream line: \begin{equation}
+v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
+Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt*{castor:1975}),
+the poloidal component of the wind velocity ($v_{p}$) parameterised
+as:
+
+\begin{equation}
+v_{p}\left(w_{i},l\right)=c_{\mathrm{s}}\left(w_{i}\right)+\left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}\label{eq:discwind-poloidal-velocity}\end{equation}
+where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the
+wind launching point on the disc, the constant scale factor of the
+asymptotic terminal velocity to the local escape velocity (from the
+wind emerging point on the disc), and the distance from the disc surface
+along stream lines respectively. $R_{s}$ is the wind scale length,
+and $R_{s}=10\, R_{\mathrm{mi}}$ is adopted as similarly done by
+\citet{long:2002}.
+
+Assuming the mass-flux conservation and using the velocity field defined
+above, the disc wind density as a function of $w$ and $l$ can be
+written as
+
+\begin{equation}
+\rho\left(w_{i},l\right)=\frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}\label{eq:discwind-density}\end{equation}
+where $Q$ and $\delta$ are the distance from the source point ($S$)
+to a point along the stream line and the angle between the stream
+line and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
+shows the density and the velocity components along the mid stream
+line (passing through $w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$
+on the disc plane ($z=0$) for different values of the wind acceleration
+parameter $\beta$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+
+\begin{center}
+
+\begin{tabular}{cc}
+\includegraphics[%
+  clip,
+  scale=0.45]{plots/dw_vp_vphi.eps}~~~~~~&
+\includegraphics[%
+  clip,
+  scale=0.45]{plots/dw_rho.eps}\tabularnewline
+\end{tabular}
+
+\end{center}
+
+\caption{Dependency of the disc-wind density and velocity on the wind
+acceleration parameter $\beta$. The wind density $\rho$ (left panel)
+and the poloidal velocity component $V_{p}$ (right panel) along the
+stream line starting from the mid point of the wind launching zone,
+i.e. $\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$
+where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}}
+\right ) / 2$, are shown as a function of the distance ($l$) from the
+wind launching point (c.f.~
+equations~\ref{eq:discwind-poloidal-velocity} and
+\ref{eq:discwind-density}). The azimuthal velocity component
+($V_{\theta}$), which is independent of $\beta$
+(c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in
+the right panel for a comparison. The density is normalised to the
+density $\rho_{0}$ at the wind launching point for $\beta = 1.0$ case.
+The $v_{p}$ reaches the terminal velocity by 100~au for all
+$\beta$. In the far field ($l>10$~au), the density is approximately
+proportional to $\sim l^2$. Up to $l~\sim 10$~au, the density is
+smaller and the poloidal speed is larger for the wind with a larger
+$\beta$ value. }
+
+\label{fig:discwind_vr_rho}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Accretion disc}
@@
 Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.
-
-\subsection{Alternative model: the disc-wind model}
-
-\label{sub:Alternative-model-disc-wind}
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  scale=0.32]{figures/discwind.eps}
-
-\end{center}
-
-\caption{Basic model configuration of the disc-wind, magnetosphere
-hybrid model. The system consist of four components: (1)~the continuum
-source located at the origin $\left( o \right)$ of the cartesian
-coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper,
-(2)~the magnetospherical accretion flow, (3)~the collimated wind/jet
-outflow, and (4)~the geometrically thin (but opaque) accretion disc. The
-disc wind originates from the disc surface between $w_{i}=R_{wi}$ and
-$w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
-lines diverges, are placed at distance $d$ above and below the
-star. By changing the value of $d$, the degree of the wind collimation
-is controlled. The density distribution is symmetric around the
-z-axis. }
-
-\label{fig:config_discwind}
-
-\end{figure}
-
-The wind model presented here is intended to mimic the collimated MHD disc-wind
-calculations of \citet{krasnopolsky:2003} in small scale ($\sim 10$~AU).
-\citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
-disc-wind model in their studies of the UV resonance lines formed
-in the winds of cataclysmic variable stars. In this model, the outflow
-arises from the surface of the rotating accretion disc, and has a
-biconical geometry. The specific angular momentum is assumed to be
-conserved along a stream line, and the poloidal velocity component
-is assumed to be simply a radial from vertically displaced {}``sources''
-from the central star. We adopt their disc-wind model here, and consider
-the combined effect of the disc-wind and the magnetospherical accretion
-flow model described earlier. In the following, we briefly described
-their disc-wind model. For details of the models, readers are referred
-to \citet{knigge:1995} and \citet{long:2002}.
-
-Four basic parameters for the models are: (1) mass-loss rate, (2)~the
-degree of the wind collimation, (3)~the velocity gradients, and (4)~the
-wind temperature. The basic configuration of the disc-wind model is
-shown in Figure~\ref{fig:config_discwind}. The disc wind originates
-from the disc surface, but the {}``source'' point ($S$), from which
-the stream lines diverges, are placed at distance $d$ above and below
-the centre of the star. By changing the value of $d$, the degree
-of the wind collimation is controlled. The larger the value of $d$,
-the wind becomes more parallel to the rotation axis, i.e. the wind
-becomes more collimated. The mass-loss launching is restricted between
-$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ where the former is set
-to be equal to the outer radius of the magnetosphere ($R_{\mathrm{mo}}$)
-for simplicity and the latter is set to $1$~AU as in \citealt{krasnopolsky:2003}.
-
-The local mass-loss rate per unit area ($\dot{m}$) is assumed to
-be proportional to the mid-plane temperature of the disc, and is a
-function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
-, i.e. \begin{equation}
-\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
- Further, the mid-plane temperature of the disc is assumed to be expressed
-as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
-relation above, one finds \begin{equation}
-\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
-where $p=\alpha\times q$. The index of the mid-plane temperature
-power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
-who found the inner most part of the accretion disc has $q=-1.15$.
-To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
-who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
-of proportionality in equation~\ref{eq:discwind-massloss-w} is found
-by integrating $\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$,
-and the normalising the value to the total mass-loss rate $\dot{M}_{\mathrm{dw}}$.
-
-The azimuthal/rotational component of the wind velocity $v_{\phi}\left(w,z\right)$
-is computed from the Keplerian rotational velocity at the emerging
-point of the stream line i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
-where $w_{i}$ is the distance from the rotational axis ($z$) to
-the emerging point on the disc, and by assuming the conservation of
-the specific angular momentum along a stream line: \begin{equation}
-v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
-Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt*{castor:1975}),
-the poloidal component of the wind velocity ($v_{p}$) parameterised
-as:
-
-\begin{equation}
-v_{p}\left(w_{i},l\right)=c_{\mathrm{s}}\left(w_{i}\right)+\left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}\label{eq:discwind-poloidal-velocity}\end{equation}
-where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the
-wind launching point on the disc, the constant scale factor of the
-asymptotic terminal velocity to the local escape velocity (from the
-wind emerging point on the disc), and the distance from the disc surface
-along stream lines respectively. $R_{s}$ is the wind scale length,
-and $R_{s}=10\, R_{\mathrm{mi}}$ is adopted as similarly done by
-\citet{long:2002}.
-
-Assuming the mass-flux conservation and using the velocity field defined
-above, the disc wind density as a function of $w$ and $l$ can be
-written as
-
-\begin{equation}
-\rho\left(w_{i},l\right)=\frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}\label{eq:discwind-density}\end{equation}
-where $Q$ and $\delta$ are the distance from the source point ($S$)
-to a point along the stream line and the angle between the stream
-line and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
-shows the density and the velocity components along the mid stream
-line (passing through $w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$
-on the disc plane ($z=0$) for different values of the wind acceleration
-parameter $\beta$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{cc}
-\includegraphics[%
-  clip,
-  scale=0.45]{plots/dw_vp_vphi.eps}~~~~~~&
-\includegraphics[%
-  clip,
-  scale=0.45]{plots/dw_rho.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{Dependency of the disc-wind density and velocity on the wind
-acceleration parameter $\beta$. The wind density $\rho$ (left panel)
-and the poloidal velocity component $V_{p}$ (right panel) along the
-stream line starting from the mid point of the wind launching zone,
-i.e. $\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$
-where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}}
-\right ) / 2$, are shown as a function of the distance ($l$) from the
-wind launching point (c.f.~
-equations~\ref{eq:discwind-poloidal-velocity} and
-\ref{eq:discwind-density}). The azimuthal velocity component
-($V_{\theta}$), which is independent of $\beta$
-(c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in
-the right panel for a comparison. The density is normalised to the
-density $\rho_{0}$ at the wind launching point for $\beta = 1.0$ case.
-The $v_{p}$ reaches the terminal velocity by 100~AU for all
-$\beta$. In the far field ($l>10$~AU), the density is approximately
-proportional to $\sim l^2$. Up to $l~\sim 10$~AU, the density is
-smaller and the poloidal speed is larger for the wind with a larger
-$\beta$ value. }
-
-\label{fig:discwind_vr_rho}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \caption{Dependency of H$\alpha$ profiles on inclination ($i$).  The
-profiles are computed with the magneospherical accretion flow using
+profiles are computed with the magnetospherical accretion flow using
 the standard parameters given in Table~\ref{tab:std_parameters} and
@@
   isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind
-  accerelation rate ($\beta$). The profiles are computed with the wind
+  acceleration rate ($\beta$). The profiles are computed with the wind
   component only (no magnetospherical accretion flow or accretion
@@
   applied. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$),
-  the inclination ($i$) and the degree of collimination ($b$) are
+  the inclination ($i$) and the degree of columniation ($b$) are
   fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$, $55^{\circ}$ and
@@
   axis) of the model increases from top to bottom, and the wind
-  accerelation rate increases from left to right. The P~Cygni profile
+  acceleration rate increases from left to right. The P~Cygni profile
   are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow
-  accerelation) models.  The postion of the absorption the component
+  acceleration) models.  The position of the absorption the component
   moves toward the line centre as $\beta$ increases. The effect of
-  line broadening becomes more prominant for higher $T_\mathrm{wind}$
+  line broadening becomes more prominent for higher $T_\mathrm{wind}$
   and higher $\beta$ models.}
@@
   clip,
-  scale=0.45]{figures/windonly_B_effect2.eps}
+  scale=0.62]{figures/windonly_B_effect2.eps}
 
@@
 parameters are same as in Figure~\ref{fig:atlas_wind_model}.  The
-P~Cygni profile feature becomes prominant for the spherical wind model
+P~Cygni profile feature becomes prominent for the spherical wind model
 since the column density of along the line of a sight of the observer
@@
 on the profile shapes. In the figures, the extent of the H$\alpha$
-emission is smaller ($\sim 0.2\,\mathrm{AU}$ or $\sim 20\, R_{*}$)
+emission is smaller ($\sim 0.2\,\mathrm{au}$ or $\sim 20\, R_{*}$)
 compared to the spectro-astrometric observations of \citet{takami:2003}
-for RU~Lup and CS Cha which show 1--5~AU scale outflows%
+for RU~Lup and CS Cha which show 1--5~au scale outflows%
 \footnote{\citet{takami:2003} their observation also show that some objects
 (e.g~Z CMa and AS~353A) displaying the outflows of larger scale
-($>50\,\mathrm{AU}$); however, this could be formed by shocks rather
+($>50\,\mathrm{au}$); however, this could be formed by shocks rather
 than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
@@
 }; however, the extent of the line emission region becomes slightly
-larger ($\sim0.4$~AU) if a slower wind acceleration rate ( $\beta=4$)
+larger ($\sim0.4$~au) if a slower wind acceleration rate ( $\beta=4$)
 is used.
@@
 from the combination of the collimated wind and the accretion disc
-($R_{\mathrm{di}}=2.2R_{*}$ and $R_{\mathrm{do}}=100\,\mathrm{AU}$) for 
+($R_{\mathrm{di}}=2.2R_{*}$ and $R_{\mathrm{do}}=100\,\mathrm{au}$) for 
 the same range of $\beta$ and $T_{\mathrm{max}}$ values used in 
@@
 disc does block the wind emission region, but none of the stellar
-disc, i.e. the continuumm flux level is unchanged.  The H$\alpha$
+disc, i.e. the continuum flux level is unchanged.  The H$\alpha$
 image (project in the plane of the observer) for the model with the
@@
 ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
-profile computed with only the magnetopsherical accretion (thick
+profile computed with only the magnetospherical accretion (thick
 solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
@@
 relatively small mass-loss rate is chosen to avoid unrealistically
-strong P-cyg absorption component (see text in
+strong P-Cyg absorption component (see text in
 section~\ref{sub:model-acc-disc-wind} and
 Figure~\ref{fig:effect_mdot_disc_wind_acc}).  For a comparison, the
-profile computed with only the magensopherical accretion flow (dotted)
+profile computed with only the magnetospherical accretion flow (dotted)
 is overlayed. All the profiles are computed at the inclination angle
-$i=55^{\circ}$. As $\beta$ becomes larger, the postion of the wind
+$i=55^{\circ}$. As $\beta$ becomes larger, the position of the wind
 absorption component moves toward the line centre. Although little
@@
 larger wind mass-loss rate. In fact, the model with $\beta=2.0$ and
-$T_{\mathrm{dw}}=9000\,\mathrm{K}$ displays a small amount of the wind
+$T_{\mathrm{wind}}=9000\,\mathrm{K}$ displays a small amount of the wind
 emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
@@
 
-Although the profiles shown in Figure~\ref{fig:atlas_disc_wind_acc_model}
-are those at a single inclination angle ($i=55^{\circ}$), they are
-very similar to the Type II-B and III-B of the observed CTTS H$\alpha$
-profiles (\citealt{reipurth:1996}), which cannot be explained
-by the magnetospherical accretion flow models (e.g.~\citealt{muzerolle:2001}).
-Comparison of the model profiles with different types of the observed
-H$\alpha$ profiles will be given in section~\ref{sub:Classification-scheme-proposed}.
+Although the profiles shown in
+Figure~\ref{fig:atlas_disc_wind_acc_model} are those at a single
+inclination angle ($i=55^{\circ}$), they are very similar to the most
+common types of H$\alpha$ profiles seen in the observations
+(e.g.~\citealt{reipurth:1996}). Apparently, this type of profile
+(affected by the blue-shifted absorption feature) cannot be explained
+by the magnetospherical accretion flow alone
+(e.g.~\citealt{muzerolle:2001}).  Comparison of the model profiles
+with different types of the observed H$\alpha$ profiles will be given
+in section~\ref{sub:Classification-scheme-proposed}.
 
@@
 The former resembles the density structure of \citealt{krasnopolsky:2003}
-in large scale ($\sim100$~AU) which described in section~\ref{sub:wind_jet},
-and the latter in small scale ($\sim10$~AU) of the same model. The
+in large scale ($\sim100$~au) which described in section~\ref{sub:wind_jet},
+and the latter in small scale ($\sim10$~au) of the same model. The
 main difference between the two models are in their density structure.
@@
 profiles are computed with different combinations of the wind
-accelreation rate ($\beta$) and the isothermal disc wind temperature
+acceleration rate ($\beta$) and the isothermal disc-wind temperature
 ($T_{\mathrm{dw}}$). The wind emission increases as the values of
@@
 of the wind absorption moves toward the line centre as $\beta$ becomes
-larger. The morphology of the profiles are smilar to that of
+larger. The morphology of the profiles are similar to that of
 observations. }
@@
 
-\caption{The disc-wind, magnetoshere hybrid model. The same as
+\caption{The disc-wind, magnetosphere hybrid model. The same as
 Figure~\ref{fig:atlas_discwind_only}, but these models (solid) also
@@
 the emission from the magnetosphere dominates for the models with
-smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster accerelation and the
+smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster acceleration and the
 colder wind models), the emission from the wind dominates the
@@
 slower accerelation and the hotter models). For a comparison, the
-profile computed with only the magensopherical accretion flow (dotted)
+profile computed with only the magnetospherical accretion flow (dotted)
 is overlayed.}
@@
 
-First, the disc wind models without the magnetosphere are considered.
+First, the disc-wind models without the magnetosphere are considered.
 Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
@@
 increases. The morphology of the profile exhibited by the model changes
-from FU-Ori type (IV-B) for the models with small $\beta$ to III-B
-and II-B types (see \citealt{reipurth:1996}) as the value of $\beta$
+from FU-Ori type for the models with small $\beta$ to the stronger
+emission types which are more commonly seen in the observed H$\alpha$
+(c.f.~\citealt{reipurth:1996}) as the value of $\beta$
 increases.  Although not shown here, we find that the profile shapes
@@
 
-We now consider the models computed with the combination of the disc-wind
-and the magnetospherical accretion components. The parameters used
-for the magnetosphere are set to be same as in the case for Figure~\ref{fig:acc_inclination_effect},
-and are kept constant for simplicity. The mass-loss rate of the disc
-wind is set to $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$).  Figure~\ref{fig:atlas_discwind_acc_model}
-shows the models profiles computed using the same ranges of the disc-wind
-temperature and the wind acceleration parameter as in the previous
-cases.
-
-As in the disc wind only models (Figure~\ref{fig:atlas_discwind_only}),
-the location of the absorption component moves toward the line centre
-as the value of $\beta$ increases (the wind acceleration is slower).
-The figure shows that in the models with smaller $\beta$ and $T_{\mathrm{dw}}$,
-the line emission from the magnetosphere dominates. On the other hand,
-in the models with larger $\beta$ and $T_{\mathrm{dw}}$, the emission
-from the disc wind dominates. Compared to the observation of \citet{reipurth:1996}
-and \citet{alencar:2000}, the lines are too strong for $\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
-and $\left(9000\,\mathrm{K},\,1.0\right)$ models. The wide varieties
-of profile shapes are see in this set of models which resembles II-B,
-III-B, IV-B, II-R and III-R%
-\footnote{Not shown here, but seen in the models with different combinations
-of $i$, $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$.%
-} types of  H$\alpha$ profiles (\citealt{reipurth:1996}).
-The shape of the primary and secondary peaks in the profiles are slightly
-{}``rounder'' compared to those of the accretion, collimated wind,
-disc hybrid model shown in Figure~\ref{fig:atlas_disc_wind_acc_model}.
-The rounder peaks are caused by the rotation of the wind. The profiles
-from the disc wind models are affected more by the rotational motion
-of the wind since the gas is more concentrated toward the equator,
-but in the models with the collimated wind the gas is concentrated
-more in the polar directions.
+We now consider the models computed with the combination of the
+disc-wind and the magnetospherical accretion components. The
+parameters used for the magnetosphere are set to be same as in the
+case for Figure~\ref{fig:acc_inclination_effect}, and are kept
+constant for simplicity. The mass-loss rate of the disc wind is set to
+$\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$).
+Figure~\ref{fig:atlas_discwind_acc_model} shows the models profiles
+computed using the same ranges of the disc-wind temperature and the
+wind acceleration parameter as in the previous cases.
+
+As in the disc wind only models
+(Figure~\ref{fig:atlas_discwind_only}), the location of the absorption
+component moves toward the line centre as the value of $\beta$
+increases (the wind acceleration is slower).  The figure shows that in
+the models with smaller $\beta$ and $T_{\mathrm{dw}}$, the line
+emission from the magnetosphere dominates. On the other hand, in the
+models with larger $\beta$ and $T_{\mathrm{dw}}$, the emission from
+the disc wind dominates. Compared to the observation of
+\citet{reipurth:1996} and \citet{alencar:2000}, the lines are too
+strong for
+$\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
+and $\left(9000\,\mathrm{K},\,1.0\right)$ models.
+
+Although the models in Figure~\ref{fig:atlas_discwind_acc_model} are
+computed with limited ranges of  $T_{\mathrm{dw}}$ and $\beta$, the
+resulting profiles exhibit the wide varieties of line shapes which are
+very similar to the types of H$\alpha$ profiles seen in the
+observations (c.f.~\citealt{reipurth:1996}).  The shape of the
+primary and secondary peaks in the profiles are slightly {}``rounder''
+compared to those of the accretion, collimated wind, disc hybrid model
+shown in Figure~\ref{fig:atlas_disc_wind_acc_model}.  The rounder
+peaks are caused by the rotation of the wind. The profiles from the
+disc-wind models are affected more by the rotational motion of the
+wind since the gas is more concentrated toward the equator, but in the
+models with the collimated wind the gas is concentrated more in the
+polar directions.
 
@@
 $\left[R_{*}\right]$&
-$\left[\mathrm{AU}\right]$&
+$\left[\mathrm{au}\right]$&
 $\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
@@
 when the wind type is switched from the bipolar wind to the disc wind.
-The corresponding model parameters used to reproduce the profiles
+The corresponding parameters (of the disc-wind, magnetosphere,
+hybrid model) used to reproduce the profiles
 in the figure are given in Table~\ref{tab:classification} along
 with brief comments on possible physical conditions which leads to
-the profiles in each class.
-
+the profiles in each class. In the following, we will discuss each 
+classification type of \citet{reipurth:1996} based on our model
+results.
+
+\textbf{Type~I}: 
 Using the samples of H$\alpha$ from 43 CTTS, \citet{reipurth:1996}
-found the most common (33~per~cent) type of the profile is Type
-III-B. Interestingly, the most common profile type seen in the profiles
-from both the bipolar wind, disc and magnetosphere hybrid model (Figure~\ref{fig:atlas_disc_wind_acc_model})
-and the disc-wind and the magnetosphere hybrid model (Figure~\ref{fig:atlas_discwind_acc_model})
-are Type III-B profiles. In this type of profiles, the main emission
-comes from the magnetosphere, and the profile shape is altered from a slightly
-blue-asymmetric one to a slightly red-asymmetric one via the wind
-absorption in the blue wing. The second most common profile (26~per~cent), 
-Type I (symmetric around line centres), is mainly produced in the magnetosphere.
-Although not shown here, this type of profile can be reproduced with
-the disc-wind, magnetosphere hybrid model with a pole-on configuration.
-Since there is no material in the polar region in the disc wind model,
-the observer can look the magnetosphere almost directory for high
-inclination cases, provided that wind temperature is low enough so
-that the wind emission is negligible. Type II-R and Type II-B can
-be produced in similar physical conditions (e.g. in a slow accretion
-and low temperature wind plus a magnetosphere). The main difference is
-between the two is in their inclination angles. The former is more
-likely to be seen at high inclination angles.
-
-Type III-R is the least common type of the observed profile (2~per~cent)
+found this type to be the second most common (26~per~cent) among
+them. Type~I (symmetric around line centres), is mainly
+produced in the magnetosphere.  Although not shown here, this type of
+profile can be reproduced with the disc-wind, magnetosphere hybrid
+model with low inclination angles ($<\sim10^\circ$).  Since there is
+no material in the polar region in the disc wind model, the observer
+can look the magnetosphere almost directory for high inclination
+cases, provided that wind temperature is low enough so that the wind
+emission is negligible. The bipolar wind, magnetosphere and accretion
+hybrid model with high inclination ($70^\circ$ -- $80^\circ$) can also 
+give this type of profile since the influence of the bipolar wind is
+minimum in the equatorial directions. The wind acceleration parameter
+for the bipolar wind must be relatively small  ($\beta < \sim 0.5$).
+
+\textbf{Type~II-B}:  
+This type can be produced by the disc-wind magnetosphere hybrid models
+at moderate to high inclination angles with wide ranges of the wind
+acceleration rate ($\sim 0.2 < \beta < \sim 2.0$) and the wind
+temperature ($\sim 7000\,\mathrm{K}< T < \sim 9000 \mathrm{K}$). If
+the inclination is high ($i \sim 80^\circ$), the disc-wind
+acceleration parameter should be relatively small ($\beta < \sim
+0.5$). If the inclination is moderate ($i \sim 60^\circ$), the wind
+acceleration parameter should be relatively high ($\beta > \sim 2.0$).
+This type can be also produced in the bipolar wind, magnetosphere disc
+hybrid model with similar ranges of inclinations ($\sim 60^\circ < i <
+\sim 80^\circ$) and temperatures ($\sim 7000\,\mathrm{K}< T < \sim
+9000 \mathrm{K}$), but the wind acceleration should be always high
+($\beta > \sim 1.0$).
+
+\textbf{Type~II-R}:  
+The physical conditions which result in this type
+is very similar to those of Type~II-B according to the disc-wind
+magnetosphere hybrid models. The main difference is between 
+the two is in their inclination angles. This type is more likely
+seen at higher inclination angles ($i \sim 80^\circ$) compared to Type
+II-B.  
+With the bipolar wind model, the wind acceleration parameter must be
+very large ($\beta \sim 6.0$) to produce this type, and the
+inclination must be moderate to low ($i < \sim 60^\circ$).  This type
+is rarely seen in the bipolar wind models with the nominal parameter
+ranges i.e. $\sim 0.2 < \beta < \sim 2.0$ and $\sim 7000\,\mathrm{K}<
+T < \sim 9000 \mathrm{K}$.  More common in the models with the disc wind.
+
+\textbf{Type~III-B}:
+This type is the most commonly seen profiles in the CTTS H$\alpha$
+samples in \citet{reipurth:1996}. Interestingly, the most common
+profile type seen in both the bipolar wind, disc, magnetosphere hybrid
+models and the disc-wind, magnetosphere hybrid model are Type~III-B
+profiles (c.f.~Figures~\ref{fig:atlas_disc_wind_acc_model} and
+\ref{fig:atlas_discwind_acc_model}). In this type of profiles, the
+main emission comes from the magnetosphere, and the profile shape is
+altered from a slightly blue-asymmetric one to a slightly
+red-asymmetric one via the wind absorption in the blue wing.  In the
+models with the disc-wind, the acceleration parameter should be
+relatively small ($\beta<0.5$). The profile type changes from Type
+III-R to Type~II-R if the value of $\beta$ increases. The
+inclination angles must be moderate to high ($\sim 60^\circ <i <
+\sim 80^\circ$).  On the other hand, the inclination must be low to
+moderate ($i < \sim 60^\circ$) in the models with the
+bipolar wind.  The difference in the inclination dependency occurs
+since the density distribution of the two types of the winds are
+different.
+
+\textbf{Type~III-R}: 
+This is the least common type of the observed profile (2~per~cent)
 according to \citet{reipurth:1996}. Incidentally, we also found it
-difficult to reproduce this type of profile since this can be achieve only
-at narrow range of parameter space (very high inclination angle with
-a disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
-$\dot{M}_{\mathrm{acc}}~10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
-
-Similarly the Type IV-R is the second least common type of observed
-profile (5~per~cent) which shows the inverse P-Cyg profile shape.
-This can be understood since the magnetospherical accretion model
-of \citet{hartmann:1994} predicts that the redshifted absorption
-can occur at a limited range of inclination angle with which the hot
-continuum flux from the footprint of the magnetosphere is seen through
-relatively fast moving gas in the accretion stream. Finally Type III-B
-profile is very similar to Type II-B, but the wind in this type of
-profile may be accretion faster than that in Type II-B.
+difficult to reproduce this type of profile since this can be achieve
+only at narrow range of parameter space (very high inclination angle
+with a disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
+$\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+Similarly, in the models with the bipolar wind, the inclination angle
+must be very high (close to edge on) to produce this type of profile.
+Since the inclination angles must be high for both wind models, this
+indicates that the accretion disc plays an important role in producing
+this type of the profile, but not the wind.  The rareness of this type in
+the observation can be understood by the required high inclination
+angle (almost edge-on) in our models.
+
+\textbf{Type~IV-B}: 
+This type of the profiles is very similar to Type III-B, but the wind
+in this type of profile may be accelerating faster (a smaller $\beta$
+value) than that in Type~III-B.  In the models with the disc-wind,
+this type is seen at moderate to high inclinations ($\sim 60^\circ <i
+\sim 80^\circ$) with relatively small value of the acceleration
+parameters ($\beta < \sim 0.5$).  In the models with the bipolar wind,
+this type is commonly seen at moderate to low inclinations (($i \sim <
+60^\circ$).  The difference in the inclination dependency occurs
+because of the density distribution of the two types of the winds are
+different.
+
+\textbf{Type~IV-R}: 
+This is the second least common type of observed profile (5~per~cent)
+which shows the inverse P-Cyg profile shape.  This can be understood
+since the magnetospherical accretion model of \citet{hartmann:1994}
+predicts that the redshifted absorption can occur at a limited range
+of inclination angle ($i= \sim 50^\circ$, but depends on the geometry of
+the magnetosphere) with which the hot continuum flux from the
+footprint of the magnetosphere is seen through relatively fast moving
+gas in the accretion stream.  The wind component must be very
+weak. The mass-accretion rate should be much lower
+($\dot{M}_{\mathrm{acc}} \sim 10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$)
+than that of the models which produce Type~I profiles since the flux
+in the broadening wings can not be too high to produce the inverse
+P-Cyg profile.
 
@@
 
-\caption{Sample H$\alpha$ model profiles which charactersize the
-classfication by \citet{reipurth:1996}. The combination of
+\caption{Sample H$\alpha$ model profiles which characterise the
+classification by \citet{reipurth:1996}. The combination of
 magnetospherical accretion flow, the accretion disc, and the disc wind
@@
 summarised in Table~\ref{tab:classification}. The horizontal axes
-are velocities in $\kmps$, and the vertical axes are nomalized
+are velocities in $\kmps$, and the vertical axes are normalised
 flux.}
@@
 \caption{The summary model parameters for the profiles in
-Figure~\ref{fig:atlas_reipurth} and brief comments. The temepratures
+Figure~\ref{fig:atlas_reipurth} and brief comments. The temperatures
 are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
@@
 $0.5$&
-Wind, disc and magnetosphere. Fast--mid wind acceleration rate. Mid
+Wind, disc and magnetosphere. Fast--mid wind acceleration rate. Mid--high
 inclination\tabularnewline
@@
 $0.2$&
-Wind, disc and magnetosphere. Fast wind acceleration rate. Mid inclination\tabularnewline
+Wind, disc and magnetosphere. Fast wind acceleration rate. Mid--high inclination\tabularnewline
 II-R&
@@
 %MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
-%($>10$~AU), and the disc wind model resembles that in smaller scale
-%($<10$~AU).
+%($>10$~au), and the disc wind model resembles that in smaller scale
+%($<10$~au).
 
@@
 2.~the disc-wind, magnetosphere hybrid model (section~\ref{sub:result-discwind-knigge})
-at inclination angles $i=10^{\circ},\,55^{\circ},\,80^{\circ}$. Both
+at inclination angles $i=10^{\circ}$, $55^{\circ}$ and $80^{\circ}$. Both
 models include the magnetospherical accretion component with the same
@@
 \caption{Dependency of the H$\alpha$ model profiles on the inclination
-angle. The profile computed at $i=10^{\circ}$(solid), $55^{\circ}$
-(dot) and $80^{\circ}$ using 1.~the disc, bipolar-wind, accretion
-hybrid model (left panel; c.f. section~\ref{sub:model-acc-disc-wind})
-and 2.~using the disc-wind, magentosphere hybrid model (right;
+angle. The profiles computed at $i=10^{\circ}$(solid), $55^{\circ}$
+(dot) and $80^{\circ}$ (dash) using 1.~the disc, bipolar-wind,
+accretion hybrid model (left panel;
+c.f. section~\ref{sub:model-acc-disc-wind}) and 2.~using the
+disc-wind, magnetosphere hybrid model (right;
 c.f. section~\ref{sub:result-discwind-knigge}) are shown for a
-comparison.  The parameters used for the magnetoshere are same for the
-both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
+comparison.  The parameters used for the magnetosphere are same for
+the both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
 $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The
-isothermal wind temperature and the wind accrelation parameter used
-both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.  All
-the other parameters are same as in
+isothermal wind temperature and the wind acceleration parameter used
+in both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.
+All the other parameters are same as in
 sections~\ref{sub:model-acc-disc-wind} and
@@
 increases as the inclination angle increases for the former model
-configuration, it decreases as the incination angle increases for the
+configuration, it decreases as the inclination angle increases for the
 latter. Only the former agrees with the tendency seen in the
@@
 Despite the inclination angle dependency of the observed H$\alpha$
-favouring the models with bipolar wind, there are two main aspects
-of this model are not quite consistent with the magneto-centrifugal
+favouring the models with bipolar wind, there are two main aspects of
+this model which are not quite consistent with the magneto-centrifugal
 launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
@@
 similar to that seen in observations. Second, the MHD models predict
-that the wind/jet becomes collimated well above the disc plane ($>10$~AU),
+that the wind/jet becomes collimated well above the disc plane ($>10$~au),
 but our bipolar wind model are collimated (density enhanced toward
@@
 \citet{matt:2005} demonstrated the possibility that the stellar wind along
-the open magnetic field originating from the star can cause significant
+the open magnetic field originated from the star can cause significant
 spin-down torque on the star, provided that mass-loss rate is high
@@
 wind is present near the equatorial plane.
+
+One possible way to distinguish the two different wind models is to
+examine the profile shape of a CTTS which is known to be viewed at
+pole-on. If the profile contains a prominent blue-shifted absorption
+component (e.g. Type IV-B), the system is more likely to be associated
+with the bipolar wind type of outflow (but not with the disc-wind type
+of outflow).
 
@@
 basic physical conditions that reproduce the profiles in each classified
-type. Using the diffrent combinations of the inclination ($i$), the
+type. Using the different combinations of the inclination ($i$), the
 mass-loss to mass-accretion rate ratio ($\mu$) and the wind
-acceralation rate ($\beta$), our radiativel transfer model was able to
+acceleration rate ($\beta$), our radiative transfer model was able to
 produce all 7 types of the profiles in  \citet{reipurth:1996}. 

### 2006-01-16 TTau_Halpha/kurosawa.tex
A minor change made. (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@618 25464f21-6099-402c-b30a-640f1d40d38b

@@
 produced in the magnetosphere.  Although not shown here, this type of
-profile can be reproduced with the disc-wind, magnetosphere hybrid
+profile can be also reproduced with the disc-wind, magnetosphere hybrid
 model with low inclination angles ($<\sim10^\circ$).  Since there is

### 2006-01-16 TTau_Halpha/kurosawa.tex
Minor chnages. Replaced the phrase "inner most" to "innermost".  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@619 25464f21-6099-402c-b30a-640f1d40d38b

@@
 the magnetosphere at the equatorial plane coincides with the the inner
-radius of the accretion disc. From the inner most part of the accretion
+radius of the accretion disc. From the innermost part of the accretion
 disc, the gas falls freely, moving along the magnetic field onto the
@@
 the magnetosphere (at the equatorial plane) coincides with the the
-inner radius of the accretion disc. From the inner most part of the
+inner radius of the accretion disc. From the innermost part of the
 accretion disc, the gas falls freely, moving along the magnetic field
@@
 power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
-who found the inner most part of the accretion disc has $q=-1.15$.
+who found the innermost part of the accretion disc has $q=-1.15$.
 To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}

### 2006-01-18 TTau_Halpha/kurosawa.tex
end of wednesday  -th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@620 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-We present  radiative transfer models of classical T~Tauri stars, and
-investigate the formation of H$\alpha$ line emission 
-in order to understand their complex circumstellar environments, and to explain
-the wide variety of line profiles seen in observations. To
-overcome the limited applicability of the radiative transfer models
-with magnetospherical accretion alone to fitting observed H$\alpha$
-profiles, and to any other lines affected by the stellar wind,
-two types of kinematic wind models are introduced: (1)~the bipolar
-wind model in which the wind is originated from the star itself, and
-(2)~the disc-wind model in which the wind originates from the inner
-part of the accretion disc. We perform systematic investigations of
+We present  radiative transfer models of the circumstellar environment of 
+classical T~Tauri stars, concentrating on the formation of the H$\alpha$ 
+emission. The wide variety of line profiles seen in observations are
+indicative of both inflow and outflow, and we therefore employ
+a circumstellar structure that includes both magnetospheric accretion
+and a wind. We adopt two kinematic models for the outflow, a generic
+bipolar wind and a disc wind. We perform systematic investigations of
 the model parameters for the wind and the magnetosphere to search
 for possible geometrical and physical conditions which lead to the
-types of profiles seen in observations. We find both wind models
+types of profiles seen in observations. We find that both wind models
 can reproduce the wide range profile types seen is observations, 
-although the inclination dependence of the line equivalent width
+and that the most common profile types observed occupy a large
+volume of parameter space. Conversely, the most infrequently observed
+profile morphologies require a very specific set of models parameters.
+Although a particular outflow model (bipolar or disc-wind) is not
+well-constrained by a single line profile observations, we find that
+the inclination dependence of the line equivalent width
 predicted by the bipolar wind model agree with trends seen in the
@@
 we examine the H$\alpha$ spectroscopic classification used by Reipurth
-et.~al, and discuss the basic physical conditions required to reproduce
+et.~al, and discuss the basic physical conditions that are required to reproduce
 the profiles in each classified type.
@@
 \citealt{kenyon:1994}; \citealt*{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profiles show evidence for both outward wind flows and
-inward accretion flows, as seen in the blue-shifted absorption features
+of CTTS line profiles have revealed evidence for both outward wind flows and
+inward accretion flows, characterized by the blue-shifted absorption features
 in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC) profiles
@@
 Recent H$\alpha$ spectro-astrometric observations by \citet*{takami:2003}
-show direct evidence for the presence of bipolar and monopolar
+provide indirect evidence for the presence of bipolar and monopolar
 outflows down to $\sim 1\,\mathrm{au}$ scale (e.g.\,CS~Cha and RU~Lup).
@@
 two-dimensional spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
-and HV~Tau~C) by \citet{appenzeller:2005} show the extended H$\alpha$
+and HV~Tau~C) by \citet{appenzeller:2005} show extended H$\alpha$
 emission in the direction perpendicular to the obscuring circumstellar
-disc both above and below the disc, suggesting the presence
-of the bipolar outflows. On a larger scale, \emph{HST} observations
-of HH30 \citep{burrows:1996} show the jet traced to within $\lesssim30$~au
-from the star. The jet has a cone shape with an opening angle of $3^{\circ}$
+disc,  suggesting the presence
+of the bipolar outflows. On an even  larger scale, \emph{HST} observations
+of HH30 \citep{burrows:1996} trace the jet to within $\lesssim30$~au of  the star. The jet has a cone shape with an opening angle of $3^{\circ}$
 between 70 and 700 au \citep{koenigl:2000}. \citet{alencar:2000}
 found about 80 per cent of their sample (30 CTTS) show blue-shifted
-absorption components in at least one of the Balmer lines and Ca~K (most
-commonly in H$\alpha$).
+absorption components in at least one of the Balmer lines and Ca~K.
 
 In the currently favoured model of accretion in CTTS, the
-accretion disc is disrupted by the magnetosphere of stars which
+accretion disc is disrupted by the magnetosphere, which
 channels the gas from the disc onto the stellar surface (e.g.,
@@
 \citealt{shu:1994}). This picture is supported
-by the evidence that CTTS have relatively strong ($\sim 10^{3}\mathrm{G}$)
-magnetic field (e.g., \citealt{johns-krull:1999};
-\citealt{guenther:1996};  \citealt{symington:2005b})
-and by radiative transfer models which reproduce the observed
-profiles for some TTS (\citealt*{muzerolle:2001}). The magnetospherical
-accretion model naturally explains the blue-ward asymmetric emission
-lines (seen in some of CTTS) caused by the partial occultation of
-the flow by the stellar disc, and the redshifted absorption component at the
-typical free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$)
-seen in some of CTTS. Despite the success of the magnetospherical
-accretion model in explaining the line profiles in some CTTS, the
-overwhelming observational evidence for outflow (mentioned above)
-in the CTTS profiles suggests that this model is only a part of the
-complete picture. Clearly, a modification to include an out-flowing
-wind/jet flow is necessary if one wishes to predict the mass-accretion
-rate and the mass-loss rate of CTTS by modelling their emission profiles
-(e.g. H$\alpha$).
-
-Prior to the magnetospherical paradigm, many alternative models had
-been considered to explain the observed spectroscopic features mentioned
-earlier. For example, (1)~the Alfv\'{e}n wave-driven wind model
-(e.g.~\citealt{decampli:1981}; \citealt*{hartmann:1982}), (2)~turbulent
-boundary layer (between the accretion disc and stellar surface) model
-(e.g.~\citealt{bertout:1988}; \citealt{basri:1989}), (3)~chromospheric
-model (e.g.~\citealt*{calvet:1984}), and (4)~disc wind model (e.g.
-\citealt*{calvet:1992b}; \citealt{kwan:1995}).  Recent work by
-\citet{alencar:2005} showed the observed 
-H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better be produced
-by the radiative transfer model which includes a collimated disc-wind
-arising from near the inner edge of the accretion disc. \citet{malbet:2005}
-considered a combination of a spherical wind and an accretion disc
-in their radiative transfer model to reproduce Br$\gamma$ from the
-early-type Herbig Be star MWC~297.
-
-The magneto-centrifugal wind model, first proposed by \citet{blandford:1982},
-has been often used to reproduce the large-scale wind structure of
-T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
-by \citealt{burrows:1996}; \citealt{ray:1996}). The launching of
-the wind from a Keplerian disc is typically done by treating the equatorial
-plane of the disc as a mass-injecting boundary condition (e.g., \citealt{shu:1994};
-\citealt{ustyugova:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
-Depending on the location of the open magnetic fields anchored to
-the disc, two different types of winds are produced. If the field
-is constrained to be near the co-rotation radius of stellar magnetosphere,
-an {}``X-wind'' \citep{shu:1994} is produces. If the open field
-lines are located in a wider area of the disc, a {}``disc-wind''
-similar to \citet{koenigl:2000} is produced \citet{krasnopolsky:2003}.
-Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
-and \citet{pudritz:2005}. Interestingly, \citet{matt:2005} showed
-the possibility that the stellar wind along the open magnetic field
-originated from the star can cause significant spin-down torque on
-the star, provided that mass-loss rate is high enough.
+by recent measurements of strong ($\sim 10^{3}\mathrm{G}$)
+magnetic fields in CTTS  (e.g., \citealt{johns-krull:1999};
+\citealt{guenther:1996}xxxx;  \citealt{symington:2005b})
+and by radiative transfer models which reproduce the gross characteristics of observed
+profiles for some TTS (\citealt*{muzerolle:2001}). In particular the magnetospheric accretion (MA) model
+explains blue-ward asymmetric emission line profiles as resulting from the partial occultation of
+the flow by the  stellar photosphere, while inverse P~Cygni profiles in the MA model result from
+inflowing material  at near free-fall velocities seen projected against hotspots on the stellar surface.
+
+Despite these successes,  the overwhelming observational evidence for outflow
+in the CTTS  suggests that the MA  model is only one component of a complex
+circumstellar environment. Clearly, one must include the contribution of any
+wind/jet flow if one wishes to both accurately predict the mass-accretion
+rate and also determined the mass-loss rate of CTTS via emission profile
+modelling. The first attempt in this direction was made by \citet{alencar:2005} who demonstrated that
+ the observed  H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better reproduced
+by the radiative transfer model which included a collimated disc-wind
+arising from near the inner edge of the accretion disc.
+
+%Prior to the MA paradigm, many alternative models had
+%been considered to explain the observed spectroscopic features mentioned
+%above. For example, (1)~an Alfv\'{e}n wave-driven wind model
+%(e.g.~\citealt{decampli:1981}; \citealt*{hartmann:1982}), (2)~a turbulent
+%boundary layer (between the accretion disc and stellar surface) model
+%(e.g.~\citealt{bertout:1988}; \citealt{basri:1989}), (3)~a chromospheric
+%model (e.g.~\citealt*{calvet:1984}), and (4)~a disc wind model (e.g.
+%\citealt*{calvet:1992b}; \citealt{kwan:1995}).
 
@@
 can reproduce the wide variety of the observed profiles, and to perform
-the empirical studies of the line formation. More specifically, we
-present disc--wind--magnetosphere hybrid models for CTTS, and perform
-parametric studies of the H$\alpha$ formation. This study should
-provide preliminary physical conditions which lead to the wide variety
-of emission line profiles seen in the observation, and will help
-to construct more comprehensive circumstellar models (e.g. via MHD
-simulations) of T~Tauri stars. Using the model results, we examine
-the H$\alpha$ spectroscopic classification used by \citet{reipurth:1996},
-and compare models with observations. We will also discuss whether
-our model is consistent with some predictions made by the recent MHD
+empirical studies of line formation in an attempt to place morphological
+classification schemes on a firmer physical footing. We will also discuss whether
+our model is consistent with some predictions made by recent MHD
 studies i.e.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
@@
 and the results of model calculations are given in section~\ref{sec:Results}.
-The closer examination and discussion of the results are presented
-in section~\ref{sec:Discussion}. Finally, the summary of this work
-and the conclusion are in section~\ref{sec:Conclusions}.
+We discuss our results in the context of Reipurth's classification scheme in section~\ref{sec:Discussion}, and our summary and conclusions are presented in section~\ref{sec:Conclusions}.
 
@@
 
-To understand how the different part of the CTTS circumstellar environment
-contributes to the formation of H$\alpha$, the model space is divided
-into four different regions: (1)~a central continuum source, (2)~the magnetospherical
+In order to understand how the different parts of the CTTS circumstellar environment
+contribute to the formation of H$\alpha$, the model space is divided
+into four different regions: (1)~a central continuum source, (2)~the magnetospheric
 accretion flow, (3)~the wind outflow, and (4)~the accretion
 disc. Fig.~\ref{fig:config_dipolar} 
-depicts the relative location of the regions in the model space. In
-all regions, the density is symmetric around the z-axis. The innermost radius of
+depicts the relative location of the regions in the model space.
+The density is assumed to be rotationally symmetric around the $z$-axis. The innermost radius of
 the magnetosphere at the equatorial plane coincides with the the inner
@@
 disc, the gas falls freely, moving along the magnetic field onto the
-surface of the star. For simplicity,
-the out-flowing wind component is defined only in the outside of the
-largest radius of the magnetosphere (to avoid overlapping of the wind
-with the magnetosphere). In the following subsections, the details
-of model components will be described.
+surface of the star.  In the following subsections we describe the details
+of model components.
 \begin{figure*}
@@
 \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-y-axis are into the paper, (2)~the magnetospherical accretion flow,
+$y$-axis is into the paper, (2)~the magnetospherical accretion flow,
 (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
-distribution is symmetric around the z-axis. The innermost radius of
+distribution is symmetric around the $z$-axis. The innermost radius of
 the magnetosphere (at the equatorial plane) coincides with the the
@@
 onto the surface of the star. The bipolar wind starts from just
-outside of the largest radius 
+outside the largest radius 
 ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
@@
 
-\subsection{Continuum Source}
+\subsection{The continuum source}
 
@@
 
-Unless specified otherwise, we adopt stellar parameters of a typical
+We adopt stellar parameters of a typical
 classical T~Tauri star for the central continuum source, i.e. radius
@@
 respectively. The model atmosphere of \citet{kurucz:1993} with
-$T_{\mathrm{ph}}=4000\,\mathrm{K}$ and $\log g_{*}=3.5$ (cgs) is used
-to find the photospheric continuum at the H$\alpha$ wavelength. The
+$T_{\mathrm{ph}}=4000\,\mathrm{K}$ and $\log g_{*}=3.5$ (cgs) defines
+the photospheric contribution to the continuum flux. The
 parameters are summarised in Table~\ref{tab:std_parameters}.
 
-For a model which includes magnetospherical accretion, an additional
-continuum source is considered. As the in-falling gas 
-becomes close to the stellar surface, it is decelerates in a strong
+An additional continuum source is considered for models which includes 
+magnetospheric accretion: as the infalling gas 
+approaches the stellar surface, it decelerates in a strong
 shock, and is heated to $\sim 10^{6}\,\mathrm{K}$.
@@
 gas locally, and re-emitted in optical and UV radiation (\citealt{koenigl:1991};
-\citealt*{hartmann:1994}). This will create hot rings near the stellar
-surface where the magnetic field intersects with the surface. For
-simplicity, the free-falling kinetic energy is assumed to be thermalized
-in the radiating layer, and re-emits as blackbody radiation (with
-a single temperature). With the parameters of the magnetosphere and
+\citealt*{hartmann:1994}). This will create hot rings  where the magnetic field
+intersects with the surface. We assume that the free-falling kinetic energy is thermalized
+in the radiating layer, and is re-emitted  as blackbody radiation with
+a single temperature. With the parameters of the magnetosphere and
 the star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
@@
 
-\subsection{Magnetosphere}
+\subsection{The magnetosphere}
 
@@
 
-We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
+We adopt the MA flow model of \citet{hartmann:1994},
 as done  by \citet{muzerolle:2001} and by \citet*{symington:2005},
@@
 the equatorial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
-respectively. The former value corresponds to the co-rotation radius
+respectively. The former value is  the co-rotation radius
 of the accretion disc, and the geometry of the magnetic field/stream
-lines is kept constant throughout this paper. The geometry of the
-magnetosphere is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
+lines is fixed for all calculations. We note that this magnetospheric geometry
+is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
 
@@
 restricted between $R_{\mathrm{mi}}$ and $R_{\mathrm{mo}}$. Using
-the field geometry above and the conservation of energy, the velocity
+the field geometry above and conservation of energy, the velocity
 and the density of the accreting gas along the steam line are found
@@
 The temperature structure of the magnetospheric used by \citet{hartmann:1994}
-is simply adopted here. They computed the temperature assuming a volumetric
-heating rate which is proportional to $r^{-3}$, and using the energy
+is adopted here. They computed the temperature, assuming a volumetric
+heating rate which is proportional to $r^{-3}$, by solving the energy
 balance of the radiative cooling rate of \citet{hartmann:1982} and
-the heating rate \citep{hartmann:1994}. Although the temperature
-structure of the accretion steam could significantly affect the line
-source function, for the purpose of the exploring the general characteristics
-of the H$\alpha$ formation, this simple form is a reasonable assumption.
-\citet{martin:1996} presented the self-consistent determination of
-the thermal structure of the in-flowing gas along the dipole magnetic
-field (equation~\ref{eq:dipole}) by solving the heat equation couple
-to rate equations for hydrogen. He found that main heat source is
+the heating rate \citep{hartmann:1994}. 
+\citet{martin:1996} presented a self-consistent determination of
+the thermal structure of the inflowing gas along the dipole magnetic
+field (equation~\ref{eq:dipole}) by solving the heat equation coupled
+to the rate equations for hydrogen. He found that main heat source is
 adiabatic compression due to the converging nature of the flow, and
@@
 \subsection{Outflow geometries}
-Two different types of the wind configurations are considered: (1)~the
-bipolar wind model which resembles the density structure of the MHD
-simulation by \citet{krasnopolsky:2003} in \em large scale \em ($\sim
-100$~au), and (2)~the disc-wind model which resembles the density of
-the same MHD simulation in \em small scale \em ($\sim 10$~au).  While
-the wind density is more concentrated toward the polar directions in
-(1), it is more concentrated toward the equatorial direction in
-(2). The following describes each model in details.
-
-\subsubsection{Bipolar Wind}
+
+The magneto-centrifugal wind paradigm, first proposed by \citet{blandford:1982},
+has been often used to model the large-scale wind structure of
+T Tauri stars, or the observed optical jets (e.g.~HH~30 jet
+by \citealt{burrows:1996}; \citealt{ray:1996}). The launching of
+the wind from a Keplerian disc is typically done by treating the equatorial
+plane of the disc as a mass-injecting boundary condition (e.g., \citealt{shu:1994};
+\citealt{ustyugova:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
+Depending on the location of the open magnetic fields anchored to
+the disc, two different types of winds are produced. If the field
+is constrained to be near the co-rotation radius of stellar magnetosphere,
+an {}``X-wind'' \citep{shu:1994} is produces. If the open field
+lines are located in a wider area of the disc, a {}``disc-wind''
+similar to that of \citet{koenigl:2000} is produced \citep{krasnopolsky:2003}.
+Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
+and \citet{pudritz:2005}.
+
+Clearly there are several alternative outflow scenarios. Here we adopt
+two simple kinematical models which broadly represent the results of
+MHD simulations. The first is a bipolar wind model, in which the outflow is collimated
+along the rotational axes (a model similar to that of \citet{krasnopolsky:2003}). The
+second model is based on the disc-wind paradigm, in which the density of the outflow
+increases towards the equatorial plane. The  difference in latitudinal density
+structure between the two outflow models should provide an indication as to whether
+line profiles alone can be used to constrain the outflow geometry. In the following
+sections we present details of the two outflow structures.
+
+\subsubsection{The bipolar wind}
 
@@
 
-Similar to the simple wind model of \citet{appenzeller:2005}, the
+In a similar fashion to the simple model of  \citet{appenzeller:2005}, the
 following parametrisation of collimated bipolar wind (region 3 in
@@
 $r$ and $\theta$. The radial component $v_{r}\left(r\right)$ is
-assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
+assumed to follow the classical beta-velocity law \citep[c.f.][]{castor:1979},
 and the azimuthal component $v_{\phi}$ is assumed to be a constant
@@
 v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This
-is chosen so mainly for computational simplicity i.e. to avoid the
-overlap between the wind and the magnetosphere; however, see \citet{matt:2005}
-for the possibility that wind originates from the stellar surface
-(restricted near the polar caps). The range of the polar angle for
+Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This naturally leads
+to a density discontinuity, but allows a simple parameterization of the wind whereas
+a self-consistent interface between the magnetosphere and wind would require
+a full MHD calculation that is beyond the scope of this paper. The range of polar angle for
 the wind is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
 where $\theta_{\mathrm{disc}}$ is the opening angle of the accretion
-disc, to avoid the overlap. $v_{r0}$ is the small radial velocity
+disc. $v_{r0}$ is the small radial velocity
 at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
@@
 
-Further, the density of the wind is assumed to be axi-symmetric and
+The density of the wind is assumed to be axi-symmetric and
 separable in $r$ and $\theta$,
@@
 F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
- where $b$ is normally positive even number (for the density symmetric
+ where $b$ is normally a positive even number (for density symmetric
 about the equatorial plane), and $n$ is the angular normalisation
@@
 n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
- Assuming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
-and the mass-flux conserves in time, the radial part of the density
+ Assuming the total mass-loss rate via the wind is $\dot{M}_{\mathrm{wind}}$
+and the mass-flux is constant, the radial part of the density
 function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
-hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
+hence, equation~\ref{eq:wind_density_def} becomes \begin{equation}
 \rho\left(r,\theta\right)=\frac{n\,\dot{M}_{\mathrm{wind}}\,\cos^{b}\theta}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
@@
 model is assigned from the ratio of mass-loss to mass-accretion rate
-($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
+$\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$, a value indicated
 by both observations and MHD calculations (e.g. \citealt{koenigl:2000}).
@@
 in the polar direction ($\theta=0$), for different values of $\beta$
-with all other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
-The density is relatively sensitive to the value of $\beta$ for $r<10\, R_{\mathrm{mo}}$,
-but a little difference is seen beyond $r<100\, R_{\mathrm{mo}}$.
+with all other parameters fixed at the standard values (Table~\ref{tab:std_parameters}).
+The density is relatively sensitive to the value of $\beta$ for $r<10\, R_{\mathrm{mo}}$.
 
@@
 smaller the value of $\beta$, the faster the acceleration of the
-wind. For the radius ($r/R_{\mathrm{mo}} < 10$, both velocity and
+wind. For the radii $r/R_{\mathrm{mo}} < 10$, both velocity and
 density are sensitive to the value of $\beta$. For all $\beta$ values,
 the radial velocity of the wind reaches the terminal velocity ($\sim
-210\,\kmps$ by $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity
+210\,\kmps$) by $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity
 $V_{0}=10\,\kmps$, which approximately corresponds to the thermal
 velocity of a hydrogen atom at 7500~K, is used for all $v_{r}$
-plots. Beyond $r/R_{\mathrm{mo}}= 100$, little difference is seen in
-the polar density with different $\beta$ values.}
+plots.}
 
@@
 
-\subsubsection{Disc wind}
+\subsubsection{The disc wind}
 
@@
 source located at the origin $\left( o \right)$ of the cartesian
-coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper,
-(2)~the magnetospherical accretion flow, (3)~the collimated wind/jet
-outflow, and (4)~the geometrically thin (but opaque) accretion disc. The
+coordinates $\left(x,y,z\right)$ -- the $y$-axis is into the paper,
+(2)~the magnetospherical accretion flow, (3)~the disc wind, and
+(4)~the geometrically thin (but opaque) accretion disc. The
 disc wind originates from the disc surface between $w_{i}=R_{wi}$ and
@@
 lines diverges, are placed at distance $d$ above and below the
-star. By changing the value of $d$, the degree of the wind collimation
-is controlled. The density distribution is symmetric around the
-z-axis. }
+star. The degree of wind collimation is controlled by changing the value of $d$. }
 
@@
 
-The wind model presented here is intended to mimic the collimated MHD disc-wind
-calculations of \citet{krasnopolsky:2003} in small scale ($\sim 10$~au).
 \citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
 disc-wind model in their studies of the UV resonance lines formed
-in the winds of cataclysmic variable stars. In this model, the outflow
+in the winds of cataclysmic variable stars. His formalism provides
+a simple parameterization of a disc wind that has similar properties 
+to those found by  MHD modelling. In this model, the outflow
 arises from the surface of the rotating accretion disc, and has a
@@
 is assumed to be simply a radial from vertically displaced {}``sources''
-from the central star. We adopt their disc-wind model here, and consider
-the combined effect of the disc-wind and the magnetospherical accretion
-flow model described earlier. In the following, we briefly described
-their disc-wind model. For details of the models, readers are referred
-to \citet{knigge:1995} and \citet{long:2002}.
-
-Four basic parameters for the models are: (1) mass-loss rate, (2)~the
-degree of the wind collimation, (3)~the velocity gradients, and (4)~the
+from the central star.  Here we briefly describe the disc-wind model, and
+readers are referred to \citet{knigge:1995} and \citet{long:2002} for
+details.
+
+The four basic parameters of the model are: (1) the mass-loss rate, (2)~the
+degree of the wind collimation, (3)~the velocity gradient, and (4)~the
 wind temperature. The basic configuration of the disc-wind model is
@@
 the stream lines diverges, are placed at distance $d$ above and below
-the centre of the star. By changing the value of $d$, the degree
-of the wind collimation is controlled. The larger the value of $d$,
-the wind becomes more parallel to the rotation axis, i.e. the wind
-becomes more collimated. The mass-loss launching is restricted between
+the centre of the star. The degree
+of the wind collimation is controlled by changing the value of $d$. (xxxx rephrase). 
+The mass-loss launching occurs between
 $R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ where the former is set
 to be equal to the outer radius of the magnetosphere ($R_{\mathrm{mo}}$)
-for simplicity and the latter is set to $1$~au as in \citealt{krasnopolsky:2003}.
+and the latter is set to $1$~au as in \citealt{krasnopolsky:2003}.
 
@@
 \dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
- Further, the mid-plane temperature of the disc is assumed to be expressed
+ The mid-plane temperature of the disc is assumed to be expressed
 as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
@@
 who found the innermost part of the accretion disc has $q=-1.15$.
-To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
+In order to be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
 who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
@@
 v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
-Based on the classic $\beta$ velocity law of hot stellar winds (c.f.~\citealt*{castor:1975}),
+Based on the canonical $\beta$ velocity law of hot stellar winds (c.f.~\citealt*{castor:1975}),
 the poloidal component of the wind velocity ($v_{p}$) parameterised
@@
 wind emerging point on the disc), and the distance from the disc surface
-along stream lines respectively. $R_{s}$ is the wind scale length,
-and $R_{s}=10\, R_{\mathrm{mi}}$ is adopted as similarly done by
-\citet{long:2002}.
-
-Assuming the mass-flux conservation and using the velocity field defined
+along stream lines respectively. $R_{s}$ is the wind scale length (=10\, R_{\mathrm{mi}}$, \citealt{long:2002}).
+
+Assuming mass-flux conservation and using the velocity field defined
 above, the disc wind density as a function of $w$ and $l$ can be
@@
 
-\caption{Dependency of the disc-wind density and velocity on the wind
+\caption{The dependency of the disc-wind density and velocity on the wind
 acceleration parameter $\beta$. The wind density $\rho$ (left panel)
-and the poloidal velocity component $V_{p}$ (right panel) along the
+and the poloidal velocity component $v_{p}$ (right panel) along the
 stream line starting from the mid point of the wind launching zone,
@@
 \ref{eq:discwind-density}). The azimuthal velocity component
-($V_{\theta}$), which is independent of $\beta$
+($v_{\phi}$), which is independent of $\beta$
 (c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in
-the right panel for a comparison. The density is normalised to the
-density $\rho_{0}$ at the wind launching point for $\beta = 1.0$ case.
+the right panel for comparison. The density is normalised to the
+density $\rho_{0}$ at the wind launching point for the $\beta = 1.0$ case.
 The $v_{p}$ reaches the terminal velocity by 100~au for all
 $\beta$. In the far field ($l>10$~au), the density is approximately
-proportional to $\sim l^2$. Up to $l~\sim 10$~au, the density is
-smaller and the poloidal speed is larger for the wind with a larger
-$\beta$ value. }
+proportional to $\sim l^2$. }
 
@@
 
-\subsection{Accretion disc}
+\subsection{The accretion disc}
 
@@
 
-Although it is possible, in our model, to compute the dust-sublimation
-radius and the vertical hydrostatic structure of the accretion disc
-self-consistently (assuming the radial dependency of the mid-plane
-density) by using an iterative Monte Carlo radiative transfer technique
-(c.f.~\citealt{walker:2004}), we find it to be too time consuming
-for the purpose of this paper -- understanding the general characteristic
-of H$\alpha$ profile shapes hence exploring a large parameter space.
-For this reason, we adopt a simple analytical disc model, the steady
+We adopt a simple analytical accretion disc model, the
 $\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
@@
  With these parameters, the disc is slightly flared. The inner radius
-of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
-radius of the magnetosphere at the equatorial plane), which is approximately
-same as the co-rotating radius of the system with the parameters in
-Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
-of an object is assumed to be 1/100 of the central mass ($M_{*}$),
-and the disc radius ($R_{\mathrm{di}}$) to be 100~au. The velocity
+of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ . The disc mass, $M_{\mathrm{d}}$,
+is assumed to be 1/100 of the stellar mass ($M_{*}$),
+and the outer disc radius ($R_{\mathrm{di}}$) is 100~au. The velocity
 of the gas/dust in the disc is assumed to be Keplerian.
@@
 
-To calculate the dust scattering and absorption cross section as a
+In order to calculate the dust scattering and absorption cross section as a
 function of wavelength, the optical constants of \citet{draine:1984}
@@
 to Model~1 of the dust model used by \citet{wood:2002}. See also
-their Fig.~3 The relative number of each grain is assumed to be that
+their Fig.~3 The relative numbers of each grain is assumed to be that
 of solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989}
@@
 to values found in the ISM model of \citet*{mathis:1977} and \citet*{kim:1994}.
-Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.
-
-\section{Radiative transfer model}
+
+\section{The radiative transfer model}
 
@@
 
-We have extended the TORUS radiative transfer code (\citealt{harries:2000};
-\citealt{kurosawa:2004a}; \citealt{symington:2005}) to compute the
-H$\alpha$ profiles from pre-main-sequence stars which are surrounded
-by one or more of the following: the magnetospherical accretion flow,
-the out-flowing collimated wind, and the accretion disc. Previously
-in \citet{symington:2005}, the model used in the three-dimensional
-(3-D) adaptive mesh refinement (AMR) to investigate the line variability
-mainly associated with rotational motion of complex geometrical configurations
-of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
-modified the code to handle the two-dimensional (2-D) density distribution,
-and restricted our models to be axi-symmetric. It was done in order
-to enable us to explore rather large number of parameters (c.f.~section~\ref{sec:model-configuration}).
+We have extended the {\sc TORUS} radiative transfer code (\citealt{harries:2000};
+\citealt{kurosawa:2004a}; \citealt{symington:2005}) to include the multiple circumstellar components
+described above. In previous calculations
+\citep{symington:2005},  the model was used with a  three-dimensional
+(3-D) adaptive mesh refinement (AMR) grid to investigate the line variability
+associated with rotational modulation of complex geometrical configurations
+of magnetospheric inflow (see also \citealt*{kurosawa:2005a}). We
+modified the code to handle the a two-dimensional (2-D) density distribution,
+and restricted our models to be axi-symmetric. 
 Note that the velocity field is still in 3-D -- the third component
-can be calculated by using the symmetry for a given value of azimuthal
-angle. An examples of how the AMR grid for the purpose of the radiative
-transfer is constructed are presented in e.g. \citet*{wolf:1999},
-\citet{kurosawa:2001a}, \citet{steinacker:2003} and \citet{kurosawa:2004a}.
+can be calculated by using symmetry for a given value of azimuthal
+angle.
 
@@
 source function calculation ($S_{\nu}$) and (2)~the observed flux/profile
-calculation. In the first process, we have utilised the method by
+calculation. In the first process, we have used the method of
 \citet{klein:1978} (see also \citealt{rybicki:1978}; \citealt{hartmann:1994})
@@
 and the gas to be in radiative equilibrium. Our hydrogen atom model
-consist of 14 bound state and continuum. Readers are refer to \citet{harries:2000}
+consist of 14 bound states and a continuum. Readers are refer to \citet{harries:2000}
 for details.
 
-To compute the observed line profile, the Monte Carlo radiative transfer
-method (e.g. \citealt{hillier:1991}) using the Sobolev escape-probability
+Monte Carlo radiative transfer (e.g. \citealt{hillier:1991}), under the Sobolev approximation,
 can be used when (1)~a large velocity gradient is present in the
@@
 to the Doppler broadening of the line. In our earlier models (\citealt{harries:2000};
-\citealt{symington:2005}), this method was used to compute the line
-profiles since the condition (1) and (2) are reasonably satisfied.
+\citealt{symington:2005}), this method was adopted since these conditions are satisfied.
 However, as noted and demonstrated by \citet{muzerolle:2001}, even
-with a moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
+with a moderate mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
 Stark broadening becomes important in the optically thick H$\alpha$
@@
 profiles from CTTS typically have the wings extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\citealt{edwards:1994};
-\citealt{reipurth:1996}) which cannot be explained by the infall velocity
-of the gas along the magnetosphere alone.
-
-To implement the broadening mechanism into our previous
-model (\citealt{symington:2005}), we follow the formalism adopted 
+\citealt{reipurth:1996}) which cannot be explained by the infall velocity alone.
+
+We have implemented the broadening mechanism following the formalism described 
 by \citet{muzerolle:2001}. First, the emission and absorption profiles
@@
 
-The second modification in our model is the replacement of the method
-of solving the formal solution from the Monte Carlo radiative transfer
-method with Sobolev approximation to the direct integration method
-(c.f. \citealt{muzerolle:2001}). We specify the cylindrical coordinates
+xxxx - explain coordinate rotation
+
+We further modified  {\sc torus} by replacing the Monte Carlo line transfer
+algorithm with a direct integration method (c.f. \citealt{muzerolle:2001}xxxx cite mihalas). 
+We specify the cylindrical coordinates
 $\left(p,\, q,\, t\right)$ which is the original stellar coordinate
-system $\left(\rho,\,\phi,\, z\right)$ rotated (around $y$ axis)
+system $\left(\rho,\,\phi,\, z\right)$ rotated (around the $y$ axis)
 by the inclination of the line of sight, i.e. the $t$-axis coincides
@@
 intersects with the stellar core, $I_{0}$ is computed from the stellar
-atmosphere model of \citet{kurucz:1979} as described in section~\ref{sub:Continuum-Source},
-and $I_{0}=0$ otherwise. The initial position of each ray is assigned
+atmosphere model of \citet{kurucz:1979} (xxxx hot spot) as described in section~\ref{sub:Continuum-Source}, and $I_{0}=0$ otherwise. The initial position of each ray is assigned
 to be at the centre of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
@@
 using the dust property described in section~\ref{eq:grain-dist-function}.
-For computational simplicity, we assumed that the dust emissivity
-is zero. Since the disc mass of CTTS are rather small ($\sim 0.01\,\mathrm{M_{\sun}}$)
-and low temperature ($<\sim 1600\,\mathrm{K}$), the continuum flux
+We neglect the emissivity from the disc: since the disc mass of CTTS are rather small ($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($<\sim 1600\,\mathrm{K}$), the continuum flux
 contribution at H$\alpha$ wavelength is expected to be negligible
 (e.g.~\citealt{chiang:1997}).
+
+xxxx finished here xxxxx
 

### 2006-01-18 TTau_Halpha/kurosawa.tex
Revisions done after discussions with Tim.   (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@621 25464f21-6099-402c-b30a-640f1d40d38b

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
+\documentclass[english,useAMS, usenatbib]{mn2e}
 \usepackage[T1]{fontenc}
@@
 
-We present  radiative transfer models of the circumstellar environment of 
-classical T~Tauri stars, concentrating on the formation of the H$\alpha$ 
-emission. The wide variety of line profiles seen in observations are
-indicative of both inflow and outflow, and we therefore employ
-a circumstellar structure that includes both magnetospheric accretion
-and a wind. We adopt two kinematic models for the outflow, a generic
-bipolar wind and a disc wind. We perform systematic investigations of
-the model parameters for the wind and the magnetosphere to search
-for possible geometrical and physical conditions which lead to the
-types of profiles seen in observations. We find that both wind models
-can reproduce the wide range profile types seen is observations, 
-and that the most common profile types observed occupy a large
-volume of parameter space. Conversely, the most infrequently observed
-profile morphologies require a very specific set of models parameters.
-Although a particular outflow model (bipolar or disc-wind) is not
+We present radiative transfer models of the circumstellar environment
+of classical T~Tauri stars, concentrating on the formation of the
+H$\alpha$ emission. The wide variety of line profiles seen in
+observations are indicative of both inflow and outflow, and we
+therefore employ a circumstellar structure that includes both
+magnetospheric accretion and a wind. We adopt two kinematic models for
+the outflow, a generic bipolar wind and a disc wind. We perform
+systematic investigations of the model parameters for the wind and the
+magnetosphere to search for possible geometrical and physical
+conditions which lead to the types of profiles seen in
+observations. We find that both wind models can reproduce the wide
+range profile types seen is observations, and that the most common
+profile types observed occupy a large volume of parameter
+space. Conversely, the most infrequently observed profile morphologies
+require a very specific set of models parameters.  Although a
+particular outflow model (bipolar or disc-wind) is not
 well-constrained by a single line profile observations, we find that
-the inclination dependence of the line equivalent width
-predicted by the bipolar wind model agree with trends seen in the
-observation, but the disc-wind model does not. Using the model results,
-we examine the H$\alpha$ spectroscopic classification used by Reipurth
-et.~al, and discuss the basic physical conditions that are required to reproduce
+the inclination dependence of the line equivalent width predicted by
+the bipolar wind model agree with trends seen in the observation, but
+the disc-wind model does not. Using the model results, we examine the
+H$\alpha$ spectroscopic classification used by Reipurth et.~al, and
+discuss the basic physical conditions that are required to reproduce
 the profiles in each classified type.
@@
 
-T~Tauri stars (TTS) are young ($<\sim 3\times10^{6}\,\mathrm{yrs}$,
+T~Tauri stars (TTS) are young ($\gtrsim 3\times10^{6}\,\mathrm{yrs}$,
 \citealt{appenzeller:1989}) low-mass objects, and are the progenitors
 of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
-H$\alpha$ emission, and typically have spectral types of F--K. Some
-of the most active CTTS show emission in higher Balmer lines and metal
-lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit excess
- continuum flux in the ultraviolet (UV) and infrared (IR).
-Their spectral energy distribution and polarisation data suggest the
-presence of circumstellar discs, which plays an important role in
-regulating dynamics of gas flows around CTTS (e.g. \citealt{camenzind:1990}).
-
-Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
-\citealt{kenyon:1994}; \citealt*{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profiles have revealed evidence for both outward wind flows and
-inward accretion flows, characterized by the blue-shifted absorption features
-in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC) profiles
-respectively. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
-to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
-\citealt{edwards:1987}; \citealt*{hartigan:1995}), and the mass-accretion
-rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
-Recent H$\alpha$ spectro-astrometric observations by \citet*{takami:2003}
-provide indirect evidence for the presence of bipolar and monopolar
-outflows down to $\sim 1\,\mathrm{au}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observations using high-resolution ($R=50\,000$)
-two-dimensional spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
-and HV~Tau~C) by \citet{appenzeller:2005} show extended H$\alpha$
-emission in the direction perpendicular to the obscuring circumstellar
-disc,  suggesting the presence
-of the bipolar outflows. On an even  larger scale, \emph{HST} observations
-of HH30 \citep{burrows:1996} trace the jet to within $\lesssim30$~au of  the star. The jet has a cone shape with an opening angle of $3^{\circ}$
-between 70 and 700 au \citep{koenigl:2000}. \citet{alencar:2000}
-found about 80 per cent of their sample (30 CTTS) show blue-shifted
-absorption components in at least one of the Balmer lines and Ca~K.
-
-In the currently favoured model of accretion in CTTS, the
-accretion disc is disrupted by the magnetosphere, which
-channels the gas from the disc onto the stellar surface (e.g.,
-\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993};
-\citealt{shu:1994}). This picture is supported
-by recent measurements of strong ($\sim 10^{3}\mathrm{G}$)
-magnetic fields in CTTS  (e.g., \citealt{johns-krull:1999};
-\citealt{guenther:1996}xxxx;  \citealt{symington:2005b})
-and by radiative transfer models which reproduce the gross characteristics of observed
-profiles for some TTS (\citealt*{muzerolle:2001}). In particular the magnetospheric accretion (MA) model
-explains blue-ward asymmetric emission line profiles as resulting from the partial occultation of
-the flow by the  stellar photosphere, while inverse P~Cygni profiles in the MA model result from
-inflowing material  at near free-fall velocities seen projected against hotspots on the stellar surface.
-
-Despite these successes,  the overwhelming observational evidence for outflow
-in the CTTS  suggests that the MA  model is only one component of a complex
-circumstellar environment. Clearly, one must include the contribution of any
-wind/jet flow if one wishes to both accurately predict the mass-accretion
-rate and also determined the mass-loss rate of CTTS via emission profile
-modelling. The first attempt in this direction was made by \citet{alencar:2005} who demonstrated that
- the observed  H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better reproduced
-by the radiative transfer model which included a collimated disc-wind
-arising from near the inner edge of the accretion disc.
+H$\alpha$ emission, and typically have spectral types of F--K. Some of
+the most active CTTS show emission in higher Balmer lines and metal
+lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit excess continuum
+flux in the ultraviolet (UV) and infrared (IR).  Their spectral energy
+distribution and polarisation data suggest the presence of
+circumstellar discs, which plays an important role in regulating
+dynamics of gas flows around CTTS (e.g. \citealt{camenzind:1990}).
+
+Many observational studies (e.g., \citealt{herbig:1962};
+\citealt{edwards:1994}; \citealt{kenyon:1994};
+\citealt*{reipurth:1996}; \citealt{alencar:2000}) of CTTS line
+profiles have revealed evidence for both outward wind flows and inward
+accretion flows, characterised by the blue-shifted absorption features
+in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC)
+profiles respectively. Typical mass-loss rates of CTTS are about
+$10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\,
+yr^{-1}}$ (e.g., \citealt{kuhi:1964}; \citealt{edwards:1987};
+\citealt*{hartigan:1995}), and the mass-accretion rates are also about
+$10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\,
+yr^{-1}}$ (e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988};
+\citealt{gullbring:1998}).  Recent H$\alpha$ spectro-astrometric
+observations by \citet*{takami:2003} provide indirect evidence for the
+presence of bipolar and monopolar outflows down to $\sim
+1\,\mathrm{au}$ scale (e.g.\,CS~Cha and RU~Lup).  Similarly, ESO VLT
+observations using high-resolution ($R=50\,000$) two-dimensional
+spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B, and HV~Tau~C) by
+\citet{appenzeller:2005} show extended H$\alpha$ emission in the
+direction perpendicular to the obscuring circumstellar disc,
+suggesting the presence of the bipolar outflows. On an even larger
+scale, \emph{HST} observations of HH30 \citep{burrows:1996} trace the
+jet to within $\lesssim30$~au of the star. The jet has a cone shape
+with an opening angle of $3^{\circ}$ between 70 and 700 au
+\citep{koenigl:2000}. \citet{alencar:2000} found about 80 per cent of
+their sample (30 CTTS) show blue-shifted absorption components in at
+least one of the Balmer lines and Ca~K.
+
+In the currently favoured model of accretion in CTTS, the accretion
+disc is disrupted by the magnetosphere, which channels the gas from
+the disc onto the stellar surface (e.g., \citealt{uchida:1985};
+\citealt{koenigl:1991}; \citealt{cameron:1993};
+\citealt{shu:1994}). This picture is supported by recent measurements
+of strong ($\sim 10^{3}\mathrm{G}$) magnetic fields in CTTS (e.g.,
+\citealt{johns-krull:1999}; \citealt{symington:2005b}) and by
+radiative transfer models which reproduce the gross characteristics of
+observed profiles for some TTS (\citealt*{muzerolle:2001}). In
+particular the magnetospheric accretion (MA) model explains blue-ward
+asymmetric emission line profiles as resulting from the partial
+occultation of the flow by the stellar photosphere, while inverse
+P~Cygni profiles in the MA model result from inflowing material at
+near free-fall velocities seen projected against hotspots on the
+stellar surface.
+
+Despite these successes, the overwhelming observational evidence for
+outflow in the CTTS suggests that the MA model is only one component
+of a complex circumstellar environment. Clearly, one must include the
+contribution of any wind/jet flow if one wishes to both accurately
+predict the mass-accretion rate and also determined the mass-loss rate
+of CTTS via emission profile modelling. The first attempt in this
+direction was made by \citet{alencar:2005} who demonstrated that the
+observed H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better
+reproduced by the radiative transfer model which included a collimated
+disc-wind arising from near the inner edge of the accretion disc.
 
@@
 The main aim of this paper is to find a simple kinematic model which
-can reproduce the wide variety of the observed profiles, and to perform
-empirical studies of line formation in an attempt to place morphological
-classification schemes on a firmer physical footing. We will also discuss whether
-our model is consistent with some predictions made by recent MHD
-studies i.e.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
+can reproduce the wide variety of the observed profiles, and to
+perform empirical studies of line formation in an attempt to place
+morphological classification schemes on a firmer physical footing. We
+will also discuss whether our model is consistent with some
+predictions made by recent MHD studies i.e.~
+$\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
 (e.g.~\citealt{koenigl:2000}).
 
-In section~\ref{sec:model-configuration}, the model assumptions,
-and the basic model configurations are presented. We discuss the radiative
-transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
-and the results of model calculations are given in section~\ref{sec:Results}.
-We discuss our results in the context of Reipurth's classification scheme in section~\ref{sec:Discussion}, and our summary and conclusions are presented in section~\ref{sec:Conclusions}.
+In section~\ref{sec:model-configuration}, the model assumptions, and
+the basic model configurations are presented. We discuss the radiative
+transfer model used to compute the profiles in
+section~\ref{sec:radiative-transfer-model}, and the results of model
+calculations are given in section~\ref{sec:Results}.  We discuss our
+results in the context of Reipurth's classification scheme in
+section~\ref{sec:Discussion}, and our summary and conclusions are
+presented in section~\ref{sec:Conclusions}.
 
@@
 
-In order to understand how the different parts of the CTTS circumstellar environment
-contribute to the formation of H$\alpha$, the model space is divided
-into four different regions: (1)~a central continuum source, (2)~the magnetospheric
-accretion flow, (3)~the wind outflow, and (4)~the accretion
-disc. Fig.~\ref{fig:config_dipolar} 
-depicts the relative location of the regions in the model space.
-The density is assumed to be rotationally symmetric around the $z$-axis. The innermost radius of
-the magnetosphere at the equatorial plane coincides with the the inner
-radius of the accretion disc. From the innermost part of the accretion
-disc, the gas falls freely, moving along the magnetic field onto the
-surface of the star.  In the following subsections we describe the details
-of model components.
+In order to understand how the different parts of the CTTS
+circumstellar environment contribute to the formation of H$\alpha$,
+the model space is divided into four different regions: (1)~a central
+continuum source, (2)~the magnetospheric accretion flow, (3)~the wind
+outflow, and (4)~the accretion disc. Fig.~\ref{fig:config_dipolar}
+depicts the relative location of the regions in the model space.  The
+density is assumed to be rotationally symmetric around the
+$z$-axis. The innermost radius of the magnetosphere at the equatorial
+plane coincides with the the inner radius of the accretion disc. From
+the innermost part of the accretion disc, the gas falls freely, moving
+along the magnetic field onto the surface of the star.  In the
+following subsections we describe the details of model components.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
     \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-$y$-axis is into the paper, (2)~the magnetospherical accretion flow,
+    $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
     (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
@@
 \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$, and $4000\,\mathrm{K}$
-respectively. The model atmosphere of \citet{kurucz:1993} with
+respectively. The model atmosphere of \citet{kurucz:1979} with
 $T_{\mathrm{ph}}=4000\,\mathrm{K}$ and $\log g_{*}=3.5$ (cgs) defines
@@
 An additional continuum source is considered for models which includes
-magnetospheric accretion: as the infalling gas 
-approaches the stellar surface, it decelerates in a strong
-shock, and is heated to $\sim 10^{6}\,\mathrm{K}$.
-The X-ray radiation produced in the shock will be absorbed by the
-gas locally, and re-emitted in optical and UV radiation (\citealt{koenigl:1991};
-\citealt*{hartmann:1994}). This will create hot rings  where the magnetic field
-intersects with the surface. We assume that the free-falling kinetic energy is thermalized
+magnetospheric accretion: as the infalling gas approaches the stellar
+surface, it decelerates in a strong shock, and is heated to $\sim
+10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
+be absorbed by the gas locally, and re-emitted in optical and UV
+radiation (\citealt{koenigl:1991}; \citealt*{hartmann:1994}). This
+will create hot rings where the magnetic field intersects with the
+surface. We assume that the free-falling kinetic energy is thermalized
 in the radiating layer, and is re-emitted as blackbody radiation with
-a single temperature. With the parameters of the magnetosphere and
-the star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
-of the surface is covered by the hot rings. If the mass-accretion rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$,
-the ratio of this accretion luminosity to the photospheric luminosity
-is about $0.5$, and the corresponding temperature of the hot rings is
-about $6400\,\mathrm{K}$.  The continuum emission from the hot rings is taken
-into account when computing the line profiles.
+a single temperature. With the parameters of the magnetosphere and the
+star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
+of the surface is covered by the hot rings. If the mass-accretion rate
+is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this accretion
+luminosity to the photospheric luminosity is about $0.5$, and the
+corresponding temperature of the hot rings is about
+$6400\,\mathrm{K}$.  The continuum emission from the hot rings is
+taken into account when computing the line profiles.
 
@@
 the equatorial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
-respectively. The former value is  the co-rotation radius
-of the accretion disc, and the geometry of the magnetic field/stream
+respectively. The geometry of the magnetic field/stream
 lines is fixed for all calculations. We note that this magnetospheric geometry
@@
 The magnetic field and the gas stream lines are assumed to have the
-following simple form: \begin{equation}
-r=R_{\mathrm{m}}\sin^{2}\theta\label{eq:dipole}\end{equation}
+following simple form:
+\begin{equation}
+      r=R_{\mathrm{m}}\sin^{2}\theta
+  \label{eq:dipole}
+\end{equation}
 \citep*[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
@@
 line at the equatorial plane ($\theta=\pi/2$). The range of
-$R_{\mathrm{m}}$ is
-restricted between $R_{\mathrm{mi}}$ and $R_{\mathrm{mo}}$. Using
-the field geometry above and conservation of energy, the velocity
-and the density of the accreting gas along the steam line are found
-as in \citet{hartmann:1994}.
-
-The temperature structure of the magnetospheric used by \citet{hartmann:1994}
-is adopted here. They computed the temperature, assuming a volumetric
-heating rate which is proportional to $r^{-3}$, by solving the energy
-balance of the radiative cooling rate of \citet{hartmann:1982} and
-the heating rate \citep{hartmann:1994}. 
-\citet{martin:1996} presented a self-consistent determination of
-the thermal structure of the inflowing gas along the dipole magnetic
-field (equation~\ref{eq:dipole}) by solving the heat equation coupled
-to the rate equations for hydrogen. He found that main heat source is
+$R_{\mathrm{m}}$ is restricted between $R_{\mathrm{mi}}$ and
+$R_{\mathrm{mo}}$. Using the field geometry above and conservation of
+energy, the velocity and the density of the accreting gas along the
+steam line are found as in \citet{hartmann:1994}.
+
+The temperature structure of the magnetospheric used by
+\citet{hartmann:1994} is adopted here. They computed the temperature,
+assuming a volumetric heating rate which is proportional to $r^{-3}$,
+by solving the energy balance of the radiative cooling rate of
+\citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
+\citet{martin:1996} presented a self-consistent determination of the
+thermal structure of the inflowing gas along the dipole magnetic field
+(equation~\ref{eq:dipole}) by solving the heat equation coupled to the
+rate equations for hydrogen. He found that main heat source is
 adiabatic compression due to the converging nature of the flow, and
-the major contributors to the cooling process are bremsstrahlung radiation
-and line emission from Ca~II and Mg~II ions. The results of \citet{martin:1996}
-qualitatively agree with that of \citet{hartmann:1994}.
+the major contributors to the cooling process are bremsstrahlung
+radiation and line emission from Ca~II and Mg~II ions. The results of
+\citet{martin:1996} qualitatively agree with that of
+\citet{hartmann:1994}.
 
@@
 
-The magneto-centrifugal wind paradigm, first proposed by \citet{blandford:1982},
-has been often used to model the large-scale wind structure of
-T Tauri stars, or the observed optical jets (e.g.~HH~30 jet
-by \citealt{burrows:1996}; \citealt{ray:1996}). The launching of
-the wind from a Keplerian disc is typically done by treating the equatorial
-plane of the disc as a mass-injecting boundary condition (e.g., \citealt{shu:1994};
-\citealt{ustyugova:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
-Depending on the location of the open magnetic fields anchored to
-the disc, two different types of winds are produced. If the field
-is constrained to be near the co-rotation radius of stellar magnetosphere,
-an {}``X-wind'' \citep{shu:1994} is produces. If the open field
-lines are located in a wider area of the disc, a {}``disc-wind''
-similar to that of \citet{koenigl:2000} is produced \citep{krasnopolsky:2003}.
-Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
-and \citet{pudritz:2005}.
+The magneto-centrifugal wind paradigm, first proposed by
+\citet{blandford:1982}, has been often used to model the large-scale
+wind structure of T Tauri stars, or the observed optical jets
+(e.g.~HH~30 jet by \citealt{burrows:1996}; \citealt{ray:1996}). The
+launching of the wind from a Keplerian disc is typically done by
+treating the equatorial plane of the disc as a mass-injecting boundary
+condition (e.g., \citealt{shu:1994}; \citealt{ustyugova:1995};
+\citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).  Depending on the
+location of the open magnetic fields anchored to the disc, two
+different types of winds are produced. If the field is constrained to
+be near the co-rotation radius of stellar magnetosphere, an
+{}``X-wind'' \citep{shu:1994} is produces. If the open field lines are
+located in a wider area of the disc, a {}``disc-wind'' similar to that
+of \citet{koenigl:2000} is produced \citep{krasnopolsky:2003}.  Recent
+reviews on the jet/wind-disc connection can be found in
+\citet{koenigl:2000} and \citet{pudritz:2005}.
 
@@
 two simple kinematical models which broadly represent the results of
-MHD simulations. The first is a bipolar wind model, in which the outflow is collimated
-along the rotational axes (a model similar to that of \citet{krasnopolsky:2003}). The
-second model is based on the disc-wind paradigm, in which the density of the outflow
-increases towards the equatorial plane. The  difference in latitudinal density
-structure between the two outflow models should provide an indication as to whether
-line profiles alone can be used to constrain the outflow geometry. In the following
-sections we present details of the two outflow structures.
+MHD simulations. The first is a bipolar wind model, in which the
+outflow is collimated along the rotational axes (a model similar to
+that of \citet{krasnopolsky:2003}). The second model is based on the
+disc-wind paradigm, in which the density of the outflow increases
+towards the equatorial plane. The difference in latitudinal density
+structure between the two outflow models should provide an indication
+as to whether line profiles alone can be used to constrain the outflow
+geometry. In the following sections we present details of the two
+outflow structures.
 
@@
 
-In a similar fashion to the simple model of  \citet{appenzeller:2005}, the
-following parametrisation of collimated bipolar wind (region 3 in
+In a similar fashion to the simple model of \citet{appenzeller:2005},
+the following parametrisation of collimated bipolar wind (region 3 in
 Fig.~\ref{fig:config_dipolar}) is adopted. The wind velocity field,
-$\boldsymbol{v}_{\mathrm{wind}}$, consists of
-radial and azimuthal components which depend on the spherical coordinates
-$r$ and $\theta$. The radial component $v_{r}\left(r\right)$ is
-assumed to follow the classical beta-velocity law \citep[c.f.][]{castor:1979},
+$\boldsymbol{v}_{\mathrm{wind}}$, consists of radial and azimuthal
+components which depend on the spherical coordinates $r$ and
+$\theta$. The radial component $v_{r}\left(r\right)$ is assumed to
+follow the classical beta-velocity law \citep[c.f.][]{castor:1979},
 and the azimuthal component $v_{\phi}$ is assumed to be a constant
@@
 ($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:
-
-\begin{eqnarray}
-\boldsymbol{v}_{\mathrm{wind}} & = & v_{r}\hat{\boldsymbol{r}}+v_{\phi}\hat{\boldsymbol{\bphi}}\label{eq:wind_velocity_def}\end{eqnarray}
-where \begin{equation}
-v_{r}\left(r\right)=v_{r0}+\left(v_{\infty}-v_{r0}\right)\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
 \begin{equation}
-v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This naturally leads
-to a density discontinuity, but allows a simple parameterization of the wind whereas
-a self-consistent interface between the magnetosphere and wind would require
-a full MHD calculation that is beyond the scope of this paper. The range of polar angle for
-the wind is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
-where $\theta_{\mathrm{disc}}$ is the opening angle of the accretion
-disc. $v_{r0}$ is the small radial velocity
-at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
+     \boldsymbol{v}_{\mathrm{wind}}  = 
+     v_{r}\hat{\boldsymbol{r}}+v_{\phi}\hat{\boldsymbol{\bphi}}
+  \label{eq:wind_velocity_def}
+\end{equation}
+where 
+\begin{equation}
+   v_{r}\left(r\right) =
+   v_{r0}+\left(v_{\infty}-v_{r0}\right)\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,
+   \label{eq:wind_velocity_radial_part}
+\end{equation}
+and
+\begin{equation}
+      v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,.
+   \label{eq:wind_velocity_azimuth_part}
+\end{equation}
+Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This
+naturally leads to a density discontinuity, but allows a simple
+parameterisation of the wind whereas a self-consistent interface
+between the magnetosphere and wind would require a full MHD
+calculation that is beyond the scope of this paper. The range of polar
+angle for the wind is restricted to
+$\theta>\left|\theta_{\mathrm{disc}}\right|$ where
+$\theta_{\mathrm{disc}}$ is the opening angle of the accretion
+disc. $v_{r0}$ is the small radial velocity at the base of the wind
+($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
 which is approximately equal to the thermal velocity of hydrogen with
-$T=7500\,\mathrm{K}$. Following \citet{appenzeller:2005}, $\gamma=0.05$
-is adopted. The dependency of $v_{r}$ in polar direction ($\theta=0$)
-on the values of wind acceleration parameter $\beta$ is shown in
-Figure~\ref{fig:wind_vr_rho}. All other parameters describing the
-wind are fixed as the standard values given in Table~\ref{tab:std_parameters}.
+$T=7500\,\mathrm{K}$. Following \citet{appenzeller:2005},
+$\gamma=0.05$ is adopted. The dependency of $v_{r}$ in polar direction
+($\theta=0$) on the values of wind acceleration parameter $\beta$ is
+shown in Figure~\ref{fig:wind_vr_rho}. All other parameters describing
+the wind are fixed as the standard values given in
+Table~\ref{tab:std_parameters}.
 
@@
 separable in $r$ and $\theta$, 
-
 \begin{equation}
-\rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)\label{eq:wind_density_def}\end{equation}
- with \begin{equation}
-F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
+    \rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)
+    \label{eq:wind_density_def}
+\end{equation}
+with 
+\begin{equation}
+    F\left(\theta\right)=n\,\cos^{b}\theta
+    \label{eq:wind_density_theta}
+\end{equation}
 where $b$ is normally a positive even number (for density symmetric
@@
 $b$, the higher the degree of the collimation. By integrating equation~\ref{eq:wind_density_theta}
-over angles and normalising the integral to $4\pi$, one finds \begin{equation}
-n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
- Assuming the total mass-loss rate via the wind is $\dot{M}_{\mathrm{wind}}$
-and the mass-flux is constant, the radial part of the density
-function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
-hence, equation~\ref{eq:wind_density_def} becomes \begin{equation}
-\rho\left(r,\theta\right)=\frac{n\,\dot{M}_{\mathrm{wind}}\,\cos^{b}\theta}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
- For a given mass-accretion rate, the wind mass-loss rate in our typical
-model is assigned from the ratio of mass-loss to mass-accretion rate
-$\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$, a value indicated
-by both observations and MHD calculations (e.g. \citealt{koenigl:2000}).
-Figure~\ref{fig:wind_vr_rho} shows the density along a streamline
-in the polar direction ($\theta=0$), for different values of $\beta$
-with all other parameters fixed at the standard values (Table~\ref{tab:std_parameters}).
-The density is relatively sensitive to the value of $\beta$ for $r<10\, R_{\mathrm{mo}}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+over angles and normalising the integral to $4\pi$, one finds 
+\begin{equation}
+  n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.
+  \label{eq:wind_density_theta_norm}
+\end{equation}
+Assuming the total mass-loss rate via the wind is
+$\dot{M}_{\mathrm{wind}}$ and the mass-flux is constant, the radial
+part of the density function is reduced to
+$P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi
+r^{2}v_{r}\left(r\right)\right]^{-1}$;
+hence, equation~\ref{eq:wind_density_def} becomes 
+\begin{equation}
+  \rho\left(r,\theta\right) = 
+  \frac{n\,\dot{M}_{\mathrm{wind}}\,\cos^{b}\theta}{4\pi r^{2}\,
+    v_{r}\left(r\right)}\,.
+  \label{eq:wind_density_final}
+\end{equation}
+For a given mass-accretion rate, the wind mass-loss rate in our
+typical model is assigned from the ratio of mass-loss to
+mass-accretion rate
+$\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$, a value
+indicated by both observations and MHD calculations
+(e.g. \citealt{koenigl:2000}).  Figure~\ref{fig:wind_vr_rho} shows the
+density along a streamline in the polar direction ($\theta=0$), for
+different values of $\beta$ with all other parameters fixed at the
+standard values (Table~\ref{tab:std_parameters}).  The density is
+relatively sensitive to the value of $\beta$ for $r<10\,
+R_{\mathrm{mo}}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
   \end{center}
-
   \caption{The dependency of the bipolar wind velocity and density
@@
 \end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
     coordinates $\left(x,y,z\right)$ -- the $y$-axis is into the paper,
-(2)~the magnetospherical accretion flow, (3)~the disc wind, and
-(4)~the geometrically thin (but opaque) accretion disc. The
-disc wind originates from the disc surface between $w_{i}=R_{wi}$ and
+    (2)~the magnetospheric accretion flow, (3)~the disc wind, and
+    (4)~the geometrically thin (but opaque) accretion disc. The disc wind
+    originates from the disc surface between $w_{i}=R_{wi}$ and
     $w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
     lines diverges, are placed at distance $d$ above and below the
-star. The degree of wind collimation is controlled by changing the value of $d$. }
+    star. The degree of wind collimation is controlled by changing the
+    value of $d$. }
 
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 in the winds of cataclysmic variable stars. His formalism provides
-a simple parameterization of a disc wind that has similar properties 
+a simple parameterisation of a disc wind that has similar properties 
 to those found by  MHD modelling. In this model, the outflow
@@
 
-The four basic parameters of the model are: (1) the mass-loss rate, (2)~the
-degree of the wind collimation, (3)~the velocity gradient, and (4)~the
-wind temperature. The basic configuration of the disc-wind model is
-shown in Figure~\ref{fig:config_discwind}. The disc wind originates
-from the disc surface, but the {}``source'' point ($S$), from which
-the stream lines diverges, are placed at distance $d$ above and below
-the centre of the star. The degree
-of the wind collimation is controlled by changing the value of $d$. (xxxx rephrase). 
-The mass-loss launching occurs between
-$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ where the former is set
-to be equal to the outer radius of the magnetosphere ($R_{\mathrm{mo}}$)
-and the latter is set to $1$~au as in \citealt{krasnopolsky:2003}.
+The four basic parameters of the model are: (1)~the mass-loss rate,
+(2)~the degree of the wind collimation, (3)~the velocity gradient, and
+(4)~the wind temperature. The basic configuration of the disc-wind
+model is shown in Figure~\ref{fig:config_discwind}. The disc wind
+originates from the disc surface, but the {}``source'' point ($S$),
+from which the stream lines diverges, are placed at distance $d$ above
+and below the centre of the star.  The angle of the mass-loss
+launching from the disc is controlled by changing the value of
+$d$. The mass-loss launching occurs between $R_{\mathrm{wi}}$ and
+$R_{\mathrm{wo}}$ where the former is set to be equal to the outer
+radius of the magnetosphere ($R_{\mathrm{mo}}$) and the latter is set
+to $1$~au as in \citealt{krasnopolsky:2003}.
 
@@
 be proportional to the mid-plane temperature of the disc, and is a
-function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
-, i.e. \begin{equation}
-\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
+function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$, i.e.
+\begin{equation}
+  \dot{m}\left(w\right) \propto
+       T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}
+\end{equation}
 The mid-plane temperature of the disc is assumed to be expressed
 as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
-relation above, one finds \begin{equation}
-\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
-where $p=\alpha\times q$. The index of the mid-plane temperature
-power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
-who found the innermost part of the accretion disc has $q=-1.15$.
-In order to be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
-who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
-of proportionality in equation~\ref{eq:discwind-massloss-w} is found
-by integrating $\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$,
-and the normalising the value to the total mass-loss rate $\dot{M}_{\mathrm{dw}}$.
-
-The azimuthal/rotational component of the wind velocity $v_{\phi}\left(w,z\right)$
-is computed from the Keplerian rotational velocity at the emerging
-point of the stream line i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
-where $w_{i}$ is the distance from the rotational axis ($z$) to
-the emerging point on the disc, and by assuming the conservation of
-the specific angular momentum along a stream line: \begin{equation}
-v_{\phi}\left(w,z\right)\,=v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.\label{eq:discwind-toroidal-velocity}\end{equation}
-Based on the canonical $\beta$ velocity law of hot stellar winds (c.f.~\citealt*{castor:1975}),
-the poloidal component of the wind velocity ($v_{p}$) parameterised
-as:
-
+relation above, one finds 
 \begin{equation}
-v_{p}\left(w_{i},l\right)=c_{\mathrm{s}}\left(w_{i}\right)+\left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}\label{eq:discwind-poloidal-velocity}\end{equation}
-where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the
-wind launching point on the disc, the constant scale factor of the
+  \dot{m}\left(w\right)\propto w^{p}
+  \label{eq:discwind-massloss-w}
+\end{equation}
+where $p=\alpha\times q$. The index of the mid-plane temperature power
+law is adopted from the dust radiative transfer model of
+\citet{whitney:2003a} who found the innermost part of the accretion
+disc has $q=-1.15$.  In order to be consistent with the collimated
+disc-wind model of \citet{krasnopolsky:2003} who used $p=-3/2$, the
+value of $\alpha$ is set to 1.3. The constant of proportionality in
+equation~\ref{eq:discwind-massloss-w} is found by integrating
+$\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$, and the
+normalising the value to the total mass-loss rate
+$\dot{M}_{\mathrm{dw}}$.
+
+The azimuthal/rotational component of the wind velocity
+$v_{\phi}\left(w,z\right)$ is computed from the Keplerian rotational
+velocity at the emerging point of the stream line
+i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
+where $w_{i}$ is the distance from the rotational axis ($z$) to the
+emerging point on the disc, and by assuming the conservation of the
+specific angular momentum along a stream line:
+\begin{equation}
+  v_{\phi}\left(w,z\right)\, = 
+  v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.
+  \label{eq:discwind-toroidal-velocity}
+\end{equation}
+Based on the canonical $\beta$ velocity law of hot stellar winds
+(c.f.~\citealt*{castor:1975}), the poloidal component of the wind
+velocity ($v_{p}$) parameterised as:
+\begin{equation}
+  v_{p}\left(w_{i},l\right) = c_{\mathrm{s}}\left(w_{i}\right) +
+  \left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}
+  \label{eq:discwind-poloidal-velocity}
+\end{equation}  
+where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the wind
+launching point on the disc, the constant scale factor of the
 asymptotic terminal velocity to the local escape velocity (from the
-wind emerging point on the disc), and the distance from the disc surface
-along stream lines respectively. $R_{s}$ is the wind scale length (=10\, R_{\mathrm{mi}}$, \citealt{long:2002}).
+wind emerging point on the disc), and the distance from the disc
+surface along stream lines respectively. $R_{s}$ is the wind scale
+length (=10\, $R_{\mathrm{mi}}$, \citealt{long:2002}).
 
@@
 written as
-
 \begin{equation}
-\rho\left(w_{i},l\right)=\frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}\label{eq:discwind-density}\end{equation}
-where $Q$ and $\delta$ are the distance from the source point ($S$)
-to a point along the stream line and the angle between the stream
-line and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
+  \rho\left(w_{i},l\right) =
+  \frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ 
+  \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}
+  \label{eq:discwind-density}
+\end{equation} 
+where $Q$ and $\delta$ are the distance from the source point ($S$) to
+a point along the stream line and the angle between the stream line
+and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
 shows the density and the velocity components along the mid stream
-line (passing through $w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$
-on the disc plane ($z=0$) for different values of the wind acceleration
-parameter $\beta$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+line (passing through
+$w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$ on the disc
+plane ($z=0$) for different values of the wind acceleration parameter
+$\beta$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
 	clip,
-  scale=0.45]{plots/dw_vp_vphi.eps}~~~~~~&
+	scale=0.59]{plots/dw_vp_vphi.eps}~~~~~~&
       \includegraphics[%
 	clip,
-  scale=0.45]{plots/dw_rho.eps}\tabularnewline
+	scale=0.59]{plots/dw_rho.eps}\tabularnewline
     \end{tabular}
@@
 
-We adopt a simple analytical accretion disc model, the
-$\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
-with the inner radius fixed at the inner radius of the magnetosphere
-at equatorial plane. This corresponds to Region 4 in Fig.~\ref{fig:config_dipolar}.
+We adopt a simple analytical accretion disc model, the $\alpha$-disc
+`standard model' (\citealt{shakura:1973}; \citealt*{frank:2002}) with
+the inner radius fixed at the inner radius of the magnetosphere at
+equatorial plane. This corresponds to Region 4 in
+Fig.~\ref{fig:config_dipolar}.
 
@@
 The disc density distribution is given by 
-
 \begin{equation}
-\rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
- where $w=\sqrt{x^{2}+y^{2}}$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
-axis, the scale height, the distance from the disc plane, and the
-surface density at the mid-plane, respectively. The mid-plane surface
-density and the scale height are given as: \begin{equation}
-\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
+  \rho_{\mathrm{d}}\left(w,z\right) = 
+  \Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}
+  \label{eq:disc-density-function}
+\end{equation}
+where $w=\sqrt{x^{2}+y^{2}}$, $h$, $z$ and $\Sigma$ are the distance
+from the symmetry axis, the scale height, the distance from the disc
+plane, and the surface density at the mid-plane, respectively. The
+mid-plane surface density and the scale height are given as:
+\begin{equation}
+  \Sigma\left(w\right) = 
+  \frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}
+  \label{eq:density-midplane}
+\end{equation} 
 where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
-and the disc mass respectively.\begin{equation}
-h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.\label{eq:scale-height}\end{equation}
+and the disc mass respectively.
+\begin{equation}
+  h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.
+  \label{eq:scale-height}
+\end{equation}
 With these parameters, the disc is slightly flared. The inner radius
-of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ . The disc mass, $M_{\mathrm{d}}$,
-is assumed to be 1/100 of the stellar mass ($M_{*}$),
-and the outer disc radius ($R_{\mathrm{di}}$) is 100~au. The velocity
-of the gas/dust in the disc is assumed to be Keplerian.
+of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ . The disc
+mass, $M_{\mathrm{d}}$, is assumed to be 1/100 of the stellar mass
+($M_{*}$), and the outer disc radius ($R_{\mathrm{di}}$) is
+100~au. The velocity of the gas/dust in the disc is assumed to be
+Keplerian.
 
@@
 
-In order to calculate the dust scattering and absorption cross section as a
-function of wavelength, the optical constants of \citet{draine:1984}
-for amorphous carbon grains and \citet{hanner:1988} for silicate
-grains are used. The model uses the {}``large grain'' dust model
-of \citet{wood:2002} in which the dust grain size distribution is
-described by the following function:\begin{equation}
-n\left(a\right)da=\left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\, a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da\label{eq:grain-dist-function}\end{equation}
- where $a$ is the grain size restricted between $a_{\mathrm{min}}$
-and $a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$
-are the terms set by requiring the grains to completely deplete a
-solar abundance carbon and silicon. The parameters adopted in our
-model are: $C_{\mathrm{C}}=1.32\times10^{-17}$, $C_{\mathrm{Si}}=1.05\times10^{-17}$,
-$p=3.0$, $q=0.6$, $a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
+In order to calculate the dust scattering and absorption cross section
+as a function of wavelength, the optical constants of
+\citet{draine:1984} for amorphous carbon grains and
+\citet{hanner:1988} for silicate grains are used. The model uses the
+{}``large grain'' dust model of \citet{wood:2002} in which the dust
+grain size distribution is described by the following function:
+\begin{equation}
+  n\left(a\right)da = \left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\,
+  a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da
+  \label{eq:grain-dist-function}
+\end{equation}
+where $a$ is the grain size restricted between $a_{\mathrm{min}}$ and
+$a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$ are the
+terms set by requiring the grains to completely deplete a solar
+abundance carbon and silicon. The parameters adopted in our model are:
+$C_{\mathrm{C}}=1.32\times10^{-17}$,
+$C_{\mathrm{Si}}=1.05\times10^{-17}$, $p=3.0$, $q=0.6$,
+$a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
 $a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
-and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds
-to Model~1 of the dust model used by \citet{wood:2002}. See also
-their Fig.~3 The relative numbers of each grain is assumed to be that
-of solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989}
-and Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
-to values found in the ISM model of \citet*{mathis:1977} and \citet*{kim:1994}.
+and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds to
+Model~1 of the dust model used by \citet{wood:2002}. See also their
+Fig.~3 The relative numbers of each grain is assumed to be that of
+solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989} and
+Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar to
+values found in the ISM model of \citet*{mathis:1977} and
+\citet*{kim:1994}.
 
@@
 
-We have extended the {\sc TORUS} radiative transfer code (\citealt{harries:2000};
-\citealt{kurosawa:2004a}; \citealt{symington:2005}) to include the multiple circumstellar components
-described above. In previous calculations
+We have extended the {\sc TORUS} radiative transfer code
+(\citealt{harries:2000}; \citealt{kurosawa:2004a};
+\citealt{symington:2005}) to include the multiple circumstellar
+components described above. In previous calculations
 \citep{symington:2005}, the model was used with a three-dimensional
-(3-D) adaptive mesh refinement (AMR) grid to investigate the line variability
-associated with rotational modulation of complex geometrical configurations
-of magnetospheric inflow (see also \citealt*{kurosawa:2005a}). We
-modified the code to handle the a two-dimensional (2-D) density distribution,
-and restricted our models to be axi-symmetric. 
-Note that the velocity field is still in 3-D -- the third component
-can be calculated by using symmetry for a given value of azimuthal
-angle.
-
-The computation of  H$\alpha$ is divided in two parts: (1)~the
-source function calculation ($S_{\nu}$) and (2)~the observed flux/profile
+(3-D) adaptive mesh refinement (AMR) grid to investigate the line
+variability associated with rotational modulation of complex
+geometrical configurations of magnetospheric inflow (see also
+\citealt*{kurosawa:2005a}). We modified the code to handle the a
+two-dimensional (2-D) density distribution, and restricted our models
+to be axi-symmetric.  Note that the velocity field is still in 3-D --
+the third component can be calculated by using symmetry for a given
+value of azimuthal angle.
+
+The computation of H$\alpha$ is divided in two parts: (1)~the source
+function calculation ($S_{\nu}$) and (2)~the observed flux/profile
 calculation. In the first process, we have used the method of
-\citet{klein:1978} (see also \citealt{rybicki:1978}; \citealt{hartmann:1994})
-in which the Sobolev approximation method is applied. The population
-of the bound states of hydrogen are assumed to be in statistical equilibrium,
-and the gas to be in radiative equilibrium. Our hydrogen atom model
-consist of 14 bound states and a continuum. Readers are refer to \citet{harries:2000}
-for details.
-
-Monte Carlo radiative transfer (e.g. \citealt{hillier:1991}), under the Sobolev approximation,
-can be used when (1)~a large velocity gradient is present in the
-gas flow, and (2)~the intrinsic line width is negligible compared
-to the Doppler broadening of the line. In our earlier models (\citealt{harries:2000};
-\citealt{symington:2005}), this method was adopted since these conditions are satisfied.
+\citet{klein:1978} (see also \citealt{rybicki:1978};
+\citealt{hartmann:1994}) in which the Sobolev approximation method is
+applied. The population of the bound states of hydrogen are assumed to
+be in statistical equilibrium, and the gas to be in radiative
+equilibrium. Our hydrogen atom model consist of 14 bound states and a
+continuum. Readers are refer to \citet{harries:2000} for details.
+
+Monte Carlo radiative transfer (e.g. \citealt{hillier:1991}), under
+the Sobolev approximation, can be used when (1)~a large velocity
+gradient is present in the gas flow, and (2)~the intrinsic line width
+is negligible compared to the Doppler broadening of the line. In our
+earlier models (\citealt{harries:2000}; \citealt{symington:2005}),
+this method was adopted since these conditions are satisfied.
 However, as noted and demonstrated by \citet{muzerolle:2001}, even
-with a moderate mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
-Stark broadening becomes important in the optically thick H$\alpha$
-line. \citet{muzerolle:2001} also pointed out that the observed H$\alpha$
-profiles from CTTS typically have the wings extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\citealt{edwards:1994};
-\citealt{reipurth:1996}) which cannot be explained by the infall velocity alone.
-
-We have implemented the broadening mechanism following the formalism described 
-by \citet{muzerolle:2001}. First, the emission and absorption profiles
-are replaced from the Doppler to the Voigt profile,  which is defined as: 
+with a moderate mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\,
+yr^{-1}}$), Stark broadening becomes important in the optically thick
+H$\alpha$ line. \citet{muzerolle:2001} also pointed out that the
+observed H$\alpha$ profiles from CTTS typically have the wings
+extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\citealt{edwards:1994};
+\citealt{reipurth:1996}) which cannot be explained by the infall
+velocity alone.
+
+We have implemented the broadening mechanism following the formalism
+described by \citet{muzerolle:2001}. First, the emission and
+absorption profiles are replaced from the Doppler to the Voigt
+profile, which is defined as:
 \begin{equation}
-H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
- where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$, $y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$,
-and $y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$ (c.f. \citealt{mihalas:1978}).
-$\nu_{0}$ is the line centre frequency, and $\Delta\nu_{\mathrm{D}}$
-is the Doppler line width of hydrogen atom (due to its thermal motion)
-which is given by $\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
+  H\left(a,y\right) \equiv
+  \frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'  
+  \label{eq:voigt_profile_def}
+\end{equation}
+where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$,
+$y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$, and
+$y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$
+(c.f. \citealt{mihalas:1978}).  $\nu_{0}$ is the line centre
+frequency, and $\Delta\nu_{\mathrm{D}}$ is the Doppler line width of
+hydrogen atom (due to its thermal motion) which is given by
+$\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
 where $m_{\mathrm{H}}$ is the mass of a hydrogen atom. The damping
-constant $\Gamma$, which depends on the physical condition of the
-gas, is parameterised by \citet*{vernazza:1973} as follows:
-
+constant $\Gamma$, which depends on the physical condition of the gas,
+is parameterised by \citet*{vernazza:1973} as follows:
 \begin{eqnarray}
-\Gamma & = & C_{\mathrm{rad}}+C_{\mathrm{vdW}}\left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)\left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
- &  & +\, C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}\label{eq:dampimg_constant_def}\end{eqnarray}
+  \Gamma & = & C_{\mathrm{rad}} + C_{\mathrm{vdW}}
+  \left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)
+  \left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
+  &  & + \,
+  C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}
+  \label{eq:dampimg_constant_def}
+\end{eqnarray}
 where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
-neutral hydrogens and that of free electrons. Also, $C_{\mathrm{rad}}$,
-$C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are natural broadening,
-van der Waals broadening, and linear Stark broadening constants respectively.
-We simply adopt this parameterisation along with the values of broadening
-constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
-$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and $C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.
-In terms of level populations and the Voigt profile, the line opacity
-for the transition $i\rightarrow j$ can be written as: \begin{equation}
-\chi_{l}=\frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}\left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)\label{eq:line_opacity}\end{equation}
+neutral hydrogens and that of free electrons. Also,
+$C_{\mathrm{rad}}$, $C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are
+natural broadening, van der Waals broadening, and linear Stark
+broadening constants respectively.  We simply adopt this
+parameterisation along with the values of broadening constants for
+H$\alpha$ from \citet{luttermoser:1992},
+i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
+$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and
+$C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.  In terms of level
+populations and the Voigt profile, the line opacity for the transition
+$i\rightarrow j$ can be written as: 
+\begin{equation}
+  \chi_{l} = \frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}
+  \left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)
+  \label{eq:line_opacity}
+\end{equation}
 where $f_{ij}$, $n_{i}$, $n_{j}$, $g_{i}$and $g_{j}$ are the
-oscillator strength, the population of $i$-th level, the population
-of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
+oscillator strength, the population of $i$-th level, the population of
+$j$-th level, the degeneracy of the $i$-th level, and the degeneracy
 of the $j$-th level respectively. $m_{e}$ and $e$ are the electron
@@
 
-xxxx - explain coordinate rotation
-
-We further modified  {\sc torus} by replacing the Monte Carlo line transfer
-algorithm with a direct integration method (c.f. \citealt{muzerolle:2001}xxxx cite mihalas). 
-We specify the cylindrical coordinates
-$\left(p,\, q,\, t\right)$ which is the original stellar coordinate
-system $\left(\rho,\,\phi,\, z\right)$ rotated (around the $y$ axis)
-by the inclination of the line of sight, i.e. the $t$-axis coincides
-with the line of sight. The observed flux ($F_{\nu}$) is given by:
+We further modified {\sc torus} by replacing the Monte Carlo line
+transfer algorithm with a direct integration method
+(c.f. \citealt{mihalas:1978}) for computing the observed flux as a
+function of frequence.  The integration of the flux is performed in
+the cylindrical coordinate system $\left(p,\, q,\, t\right)$ which is
+obtained by rotating the original stellar coordinate system
+$\left(\rho,\,\phi,\, z\right)$ around the $y$ axis by the inclination
+of the line of sight.  Note that the $t$-axis coincides with the line
+of sight with this rotation. The observed flux ($F_{\nu}$) is given
+by:
 \begin{equation}
-F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
+  F_{\nu}=\frac{1}{4\pi d^{2}}
+  \int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\,
+  I_{\nu}\mathrm{\, d}q\,\mathrm{d}p
+  \label{eq:flux_integral}
+\end{equation}
 where $d$, $p_{\mathrm{max}}$, and $I_{\nu}$ are the distance to
@@
 on observer at the outer boundary. For a given ray along $t$, the
-specific intensity is given by:\begin{equation}
-I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{t_{0}}^{t_{\infty}}S_{\nu}\left(t\right)\, e^{-\tau}\mathrm{d}\tau\label{eq:formal_sol_integral}\end{equation}
- where $I_{0}$ and $S_{\nu}$ are the intensity at the boundary on
-the opposite to the observer and the source function ($\eta_{\nu}/\chi_{\nu}$)
-of the stellar atmosphere/wind at a frequency $\nu$. For a ray which
-intersects with the stellar core, $I_{0}$ is computed from the stellar
-atmosphere model of \citet{kurucz:1979} (xxxx hot spot) as described in section~\ref{sub:Continuum-Source}, and $I_{0}=0$ otherwise. The initial position of each ray is assigned
-to be at the centre of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
-The code execution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
-where $n_{p}$ and $n_{q}$ are the number of cylindrical radial and
-angular points for the flux integration, and $n_{\nu}$ is the number
-of frequency points. In the models presented in the following
-section. $n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
-otherwise. A linearly spaced radial grid is used for the area where
-the ray intersects with magnetosphere, and a logarithmically spaced
-grid is used for the wind and the accretion disc regions.
+specific intensity is given by:
+\begin{equation}
+       I_{\nu} = I_{0}e^{-\tau_{\infty}} + 
+           \int_{t_{0}}^{t_{\infty}}S_{\nu}\left(t\right)\,
+                e^{-\tau}\mathrm{d}\tau
+ \label{eq:formal_sol_integral}
+\end{equation}
+where $I_{0}$ and $S_{\nu}$ are the intensity at the boundary on the
+opposite to the observer and the source function
+($\eta_{\nu}/\chi_{\nu}$) of the stellar atmosphere/wind at a
+frequency $\nu$. For a ray which intersects with the stellar core,
+$I_{0}$ is computed from the stellar atmosphere model of
+\citet{kurucz:1979} as described in
+section~\ref{sub:Continuum-Source}, and $I_{0}=0$ otherwise. If the
+the ray intersects with the hot ring on the stellar surface created by
+the accretion stream, we set
+$I_{0}=B_{\nu}\left(T_{\mathrm{ring}}\right)$ where $B_{\nu}$ is the
+Planck function and $T_{\mathrm{ring}}$ is the temperature of the hot
+ring.  The initial position of each ray is assigned to be at the
+centre of the surface element ($\mathrm{d}A=p\,\sin
+q\,\mathrm{d}q\,\mathrm{dp}$).  The code execution time is
+proportional to $n_{p}\, n_{q}\, n_{\nu}$ where $n_{p}$ and $n_{q}$
+are the number of cylindrical radial and angular points for the flux
+integration, and $n_{\nu}$ is the number of frequency points. In the
+models presented in the following section. $n_{p}=180$, $n_{q}=100$,
+and $n_{\nu}=101$ are used unless specified otherwise. A linearly
+spaced radial grid is used for the area where the ray intersects with
+magnetosphere, and a logarithmically spaced grid is used for the wind
+and the accretion disc regions.
 
 The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
-is defined as: \[
-\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
+is defined as: 
+\[
+\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'
+\]
 where $\chi_{\nu}$ is the opacity of media the ray passes through.
@@
 For a point in the magnetosphere and the wind flows, the emissivity
-and the opacity of the media are given as:\begin{equation}
-\left\{ \begin{array}{rcl}
+and the opacity of the media are given as:
+\begin{equation}
+  \left\{ 
+  \begin{array}{rcl}
     \eta_{\nu} & = & \eta_{\mathrm{c}}^{\mathrm{H}}+\eta_{l}^{\mathrm{H}}\\
-\chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}+\sigma_{\mathrm{es}}\end{array}\right.\label{eq:emiss_opa_gas}\end{equation}
-where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$
-are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
-$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the continuum,
-line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
-electron scattering opacity. Similarly, for a point in the accretion
-disc,
-
+    \chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}
+    +\sigma_{\mathrm{es}}
+  \end{array}
+  \right.
+  \label{eq:emiss_opa_gas}
+\end{equation}
+where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$ are
+the continuum and line emissivity of
+hydrogen. $\chi_{c}^{\mathrm{H}}$, $\chi_{l}^{\mathrm{H}}$, and
+$\sigma_{\mathrm{es}}$ are the continuum, line opacity
+(equation~\ref{eq:line_opacity}) of hydrogen, and the electron
+scattering opacity. Similarly, for a point in the accretion disc,
 \begin{equation}
-\left\{ \begin{array}{rcl}
+  \left\{ 
+  \begin{array}{rcl}
     \eta_{\nu} & = & 0\\
-\chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}+\kappa_{\mathrm{sca}}^{\mathrm{dust}}\end{array}\right.\label{eq:emiss_opa_dust}\end{equation}
- where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and $\kappa_{\mathrm{sca}}^{\mathrm{dust}}$
-are the dust absorption, and scattering opacity which are calculated
-using the dust property described in section~\ref{eq:grain-dist-function}.
-We neglect the emissivity from the disc: since the disc mass of CTTS are rather small ($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($<\sim 1600\,\mathrm{K}$), the continuum flux
-contribution at H$\alpha$ wavelength is expected to be negligible
-(e.g.~\citealt{chiang:1997}).
+    \chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}
+    +\kappa_{\mathrm{sca}}^{\mathrm{dust}}
+  \end{array}
+  \right.
+  \label{eq:emiss_opa_dust}
+\end{equation}
+where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and
+$\kappa_{\mathrm{sca}}^{\mathrm{dust}}$ are the dust absorption, and
+scattering opacity which are calculated using the dust property
+described in section~\ref{eq:grain-dist-function}.  We neglect the
+emissivity from the disc: since the disc mass of CTTS are rather small
+($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($<\sim
+1600\,\mathrm{K}$), the continuum flux contribution at H$\alpha$
+wavelength is expected to be negligible (e.g.~\citealt{chiang:1997}).
 
@@
 
-Using the standard parameters (Table~\ref{tab:std_parameters}) for
-the central star and the magnetosphere, we examine the dependency
-of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
-flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
+Using the standard parameters (Table~\ref{tab:std_parameters}) for the
+central star and the magnetosphere, we examine the dependency of
+H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion flow
+and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
 done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
-is computed from the available kinetic energy of the free-falling
-gas as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
-used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
-of their models. The accretion luminosity ($L_{\mathrm{acc}}$) of
-models with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-is about a half of the total luminosity (without the hot ring) of
-the star, and $L_{\mathrm{acc}}$ is proportional to $\dot{M}_{\mathrm{acc}}$.
-The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
-dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are
-similar to that of \citet{muzerolle:2001}. In general, the line strength
-becomes weaker as the accretion rate and the temperature become smaller.
-The red-shifted absorption becomes less visible for higher accretion
-rate and temperature models in which the flux in the damping wings
-become important. Figure~\ref{fig:broadening} shows an example of
-the effect of the broadening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
-due to the damping constants as described in section~\ref{sec:radiative-transfer-model}.
-Although the maximum flux of the model with the broadening is almost
-identical to that of the model with no damping constant ($\Gamma=0$),
-a significant increase of the line flux in both red and blue wings
-of seen in the model with broadening. The weak red-shifted absorption
-component (which is a signature of the magnetospherical accretion)
-is weakened or eliminated by the flux in broadened wing.
-
-Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown
-in Figure~\ref{fig:atlas_acc_models}. About a half of the models
-shown the figure agree with the observed EW values of H$\alpha$ from
-30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
-ranges from $\sim 3$~\AA\, to $\sim 160$~\AA, and the mean to
-be $\sim 55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
-the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
-and for some models the EWs are negative. Since the target selection
-criteria of \citet{alencar:2000} is not stated in their paper, we
-can not conclude that these low $\dot{M}_{\mathrm{acc}}$ models disagree
-with the observation. \citet{reipurth:1996}, who measured the EW
-of 43 TTS and found similar distribution of EW values, mentioned that
-their EW measurements are under-representing real samples since the
-selection of the targets are based on the strong emission
-in H$\alpha$ surveys.
-
-The dependency of the profile on the inclination angle ($i$) is demonstrated
-in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
-parameters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
-The figure shows that the peak (normalised) flux decreases as the inclination
-angle increases. Similarly, the equivalent width also decreases as
-the inclination increases. Because of the geometry of the magnetospherical
-accretion (c.f. Figure~\ref{fig:config_dipolar}) and of the presence
-of the gas with the highest velocity close to the stellar surface,
-the highest red-shifted line-of-sight velocity is visible only at
-the high inclination angles. This explains the wider appearance of
-the profile with $i=80^{\circ}$compared to the relatively narrow
-line appearance of the profile with $i=10^{\circ}$. Although not
-shown here, a similar dependency on the inclination angle is found
-for the models with different temperatures ($T_{\mathrm{max}}=6500$,
-$8500$, $9500\,\mathrm{K}$).
-
-As seen in the models of \citet{hartmann:1994} and \citet{muzerolle:2001},
-our models also show the blue-shifted peak and the blue-ward asymmetry
-caused by the occultation of the accretion flow by the equatorial
-disc and the stellar disc. However, \citealt{alencar:2000} (see
-their Fig.~9) found a substantial fraction of the observed H$\alpha$
-profiles also shows the {}``red-shifted'' peak, and the P~Cygni
-profiles which can not be explained by the magnetospherical accretion
-model alone. In addition, a recent study by \citet{appenzeller:2005}
-showed that the equivalent width of H$\alpha$ from CTTS increases
-as the inclination angle increases. Our model with the magnetospherical
-accretion flow clearly disagrees with their finding.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+is computed from the available kinetic energy of the free-falling gas
+as describe by \citet{hartmann:1994} while \citet{muzerolle:2001} used
+the constant hot ring temperature ($8000\,\mathrm{K}$) for most of
+their models. The accretion luminosity ($L_{\mathrm{acc}}$) of models
+with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ is
+about a half of the total luminosity (without the hot ring) of the
+star, and $L_{\mathrm{acc}}$ is proportional to
+$\dot{M}_{\mathrm{acc}}$.  The results are placed in
+Figure~\ref{fig:atlas_acc_models}. Overall dependency on
+$T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are similar to that of
+\citet{muzerolle:2001}. In general, the line strength becomes weaker
+as the accretion rate and the temperature become smaller.  The
+red-shifted absorption becomes less visible for higher accretion rate
+and temperature models in which the flux in the damping wings become
+important. Figure~\ref{fig:broadening} shows an example of the effect
+of the broadening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
+and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$) due
+to the damping constants as described in
+section~\ref{sec:radiative-transfer-model}.  Although the maximum flux
+of the model with the broadening is almost identical to that of the
+model with no damping constant ($\Gamma=0$), a significant increase of
+the line flux in both red and blue wings of seen in the model with
+broadening. The weak red-shifted absorption component (which is a
+signature of the magnetospheric accretion) is weakened or eliminated
+by the flux in broadened wing.
+
+Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown in
+Figure~\ref{fig:atlas_acc_models}. About a half of the models shown
+the figure agree with the observed EW values of H$\alpha$ from 30 TTS
+presented by \citet{alencar:2000} who found the EW of H$\alpha$ ranges
+from $\sim 3$~\AA\, to $\sim 160$~\AA, and the mean to be $\sim
+55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models, the EW values
+are smaller than the minimum EW observed by \citet{alencar:2000}, and
+for some models the EWs are negative. Since the target selection
+criteria of \citet{alencar:2000} is not stated in their paper, we can
+not conclude that these low $\dot{M}_{\mathrm{acc}}$ models disagree
+with the observation. \citet{reipurth:1996}, who measured the EW of 43
+TTS and found similar distribution of EW values, mentioned that their
+EW measurements are under-representing real samples since the
+selection of the targets are based on the strong emission in H$\alpha$
+surveys.
+
+The dependency of the profile on the inclination angle ($i$) is
+demonstrated in Figure~\ref{fig:acc_inclination_effect}. The model
+uses the same parameters as in Figure~\ref{fig:broadening} (with
+broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).  The
+figure shows that the peak (normalised) flux decreases as the
+inclination angle increases. Similarly, the equivalent width also
+decreases as the inclination increases. Because of the geometry of the
+magnetospheric accretion (c.f. Figure~\ref{fig:config_dipolar}) and of
+the presence of the gas with the highest velocity close to the stellar
+surface, the highest red-shifted line-of-sight velocity is visible
+only at the high inclination angles. This explains the wider
+appearance of the profile with $i=80^{\circ}$compared to the
+relatively narrow line appearance of the profile with
+$i=10^{\circ}$. Although not shown here, a similar dependency on the
+inclination angle is found for the models with different temperatures
+($T_{\mathrm{max}}=6500$, $8500$, $9500\,\mathrm{K}$).
+
+As seen in the models of \citet{hartmann:1994} and
+\citet{muzerolle:2001}, our models also show the blue-shifted peak and
+the blue-ward asymmetry caused by the occultation of the accretion
+flow by the equatorial disc and the stellar disc. However,
+\citealt{alencar:2000} (see their Fig.~9) found a substantial fraction
+of the observed H$\alpha$ profiles also shows the {}``red-shifted''
+peak, and the P~Cygni profiles which can not be explained by the
+magnetospheric accretion model alone. In addition, a recent study by
+\citet{appenzeller:2005} showed that the equivalent width of H$\alpha$
+from CTTS increases as the inclination angle increases. Our model with
+the magnetospheric accretion flow clearly disagrees with their
+finding.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
     ($T_{\mathrm{max}}$). The profiles are computed using only
-magnetospherical accretion flow (i.e. no wind/jet).  All the profiles
+    magnetospheric accretion flow (i.e. no wind/jet).  All the profiles
     are computed using the parameters of the `standard' model
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
   \caption{Dependency of H$\alpha$ profiles on inclination ($i$).  The
-profiles are computed with the magnetospherical accretion flow using
+    profiles are computed with the magnetospheric accretion flow using
     the standard parameters given in Table~\ref{tab:std_parameters} and
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}
@@
 \caption{Summary of H$\alpha$ equivalent widths from the
-magnetospherical accretion flow models shown in
+magnetospheric accretion flow models shown in
 Figure~\ref{fig:atlas_acc_models}.}
@@
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-As mentioned earlier, the magnetospherical accretion flow model alone
+As mentioned earlier, the magnetospheric accretion flow model alone
 cannot explain some of the features seen in observations. As an
@@
 
-Figure~\ref{fig:atlas_wind_model} shows the profile computed at
-a mid inclination angle $i=55^{\circ}$ for the range of the wind
-temperature between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and
-for the range of $\beta$ between $0.2$ and $2.0$. The P~Cygni
-profiles are prominent in the models with lower values of $T_{\mathrm{wind}}$
-and $\beta$ (colder and faster acceleration wind). As the value of
-$\beta$ increases, the position of the blue-shifted absorption component
-moves toward the line centre. which can be seen clearly in the $T_{\mathrm{wind}}=7000\,\mathrm{K}$
-models. While the velocity position of absorption component for the
-fastest acceleration ($\beta=0.2$) is almost at the terminal velocity
-($v_{\infty}\sim 210\,\kmps$), that for the slowest wind acceleration
-model ($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).
-As one can see in Figure~\ref{fig:wind_vr_rho}, the column density
-of the gas moving at $v_{\infty}$ increases as the wind acceleration
-becomes larger since the gas moving at $v_{\infty}$ becomes closer
-to the photosphere. At the location where the absorption occurs, the
-gas is moving faster for the models with the faster wind acceleration
-models; hence, the location of the absorption component is bluer as
-$\beta$ becomes smaller (as the wind acceleration faster). The figure
-also shows that the intensity of the emission component increases
-as $\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
+Figure~\ref{fig:atlas_wind_model} shows the profile computed at a mid
+inclination angle $i=55^{\circ}$ for the range of the wind temperature
+between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and for the range
+of $\beta$ between $0.2$ and $2.0$. The P~Cygni profiles are prominent
+in the models with lower values of $T_{\mathrm{wind}}$ and $\beta$
+(colder and faster acceleration wind). As the value of $\beta$
+increases, the position of the blue-shifted absorption component moves
+toward the line centre. which can be seen clearly in the
+$T_{\mathrm{wind}}=7000\,\mathrm{K}$ models. While the velocity
+position of absorption component for the fastest acceleration
+($\beta=0.2$) is almost at the terminal velocity ($v_{\infty}\sim
+210\,\kmps$), that for the slowest wind acceleration model
+($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).  As
+one can see in Figure~\ref{fig:wind_vr_rho}, the column density of the
+gas moving at $v_{\infty}$ increases as the wind acceleration becomes
+larger since the gas moving at $v_{\infty}$ becomes closer to the
+photosphere. At the location where the absorption occurs, the gas is
+moving faster for the models with the faster wind acceleration models;
+hence, the location of the absorption component is bluer as $\beta$
+becomes smaller (as the wind acceleration faster). The figure also
+shows that the intensity of the emission component increases as
+$\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
 because the density near the photosphere increases as the value of
-$\beta$ increases (Figure~\ref{fig:wind_vr_rho}); 
-hence, the emissivity of increases. Unlike the magnetospherical accretion
-only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
+$\beta$ increases (Figure~\ref{fig:wind_vr_rho}); hence, the
+emissivity of increases. Unlike the magnetospheric accretion only
+models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
 profiles are not seen here, nor the blue-ward asymmetry. Because of
-the absorption component in P~Cygni profile, most of the profiles
-show red-ward asymmetry except for the low temperature wind models
-with high inclinations (not shown here).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+the absorption component in P~Cygni profile, most of the profiles show
+red-ward asymmetry except for the low temperature wind models with
+high inclinations (not shown here).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
     acceleration rate ($\beta$). The profiles are computed with the wind
-  component only (no magnetospherical accretion flow or accretion
+    component only (no magnetospheric accretion flow or accretion
     disc). The `standard' model parameters (Table~\ref{tab:std_parameters}) are
@@
 a good candidate for a mass-loss rate indicator; however, without
-solving the ambiguity of the emission component from the magnetospherical
+solving the ambiguity of the emission component from the magnetospheric
 accretion flow and the wind, and without knowing the detailed temperature
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
     10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed) are shown above. The
-models are computed with only the wind component (no magnetospherical
+    models are computed with only the wind component (no magnetospheric
     accretion flow or accretion disc). With all other parameter fixed
@@
 from the combination of the collimated wind and the accretion disc
-($R_{\mathrm{di}}=2.2R_{*}$ and $R_{\mathrm{do}}=100\,\mathrm{au}$) for 
-the same range of $\beta$ and $T_{\mathrm{max}}$ values used in 
+($R_{\mathrm{di}}=2.2R_{*}$ and $R_{\mathrm{do}}=100\,\mathrm{au}$)
+for the same range of $\beta$ and $T_{\mathrm{max}}$ values used in
 Figure~\ref{fig:atlas_wind_model}.  As expected
@@
 decrease in the flux in the blue wing when compared to the flux of the
-same model computed without the accretion disc.
-The overall behaviour of the line profile shapes as functions of $\beta$ and $T_{\mathrm{wind}}$
-are very similar to that for the models without the accretion disc.
-A significant reduction of the flux in the red wing is seen in the
-wind model with the accretion disc when compared with the wind only
-model. The wings appear to be weaker in these models compared to the
-wind only models because the ratio of the wind emission flux
-to the continuum flux is lower.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+same model computed without the accretion disc.  The overall behaviour
+of the line profile shapes as functions of $\beta$ and
+$T_{\mathrm{wind}}$ are very similar to that for the models without
+the accretion disc.  A significant reduction of the flux in the red
+wing is seen in the wind model with the accretion disc when compared
+with the wind only model. The wings appear to be weaker in these
+models compared to the wind only models because the ratio of the wind
+emission flux to the continuum flux is lower.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
 \end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
     ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
-profile computed with only the magnetospherical accretion (thick
+    profile computed with only the magnetospheric accretion (thick
     solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
@@
 \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We examine the characteristics of the line profiles arising from the
-combination of the magnetospherical accretion flow, the wind, and
-the accretion disc. For simplicity, the parameters for the magnetosphere
-($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-are fixed as in Figure~\ref{fig:atlas_acc_models}), and the wind
-mass-loss rate, the isothermal wind temperature and the wind anisotropy
-parameter to $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$), $T_{\mathrm{wind}}$
-and $b=4$ respectively. The profile computed for $i=55^{\circ}$
-is given in Figure~\ref{fig:summary_beta05_t8000}, along with the
-profile computed with the magnetosphere only and that with the wind
-plus accretion disc configurations for a comparison. As one can see
-from the figure, the profile computed for the disc--wind--magnetosphere
-hybrid model can be understood as a simple flux sum of the magnetospherical
-component and the wind component. In this example, the wind causes
-the absorption of the blue side of the profile, and it adds extra
-flux around the line centre. As seen before, the presence of the disc
-causes a reduction in the red side of the profile since the emission
-from the receding gas is blocked by the disc. The resulting profile
-appears to be narrower than that of the magnetosphere model.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+combination of the magnetospheric accretion flow, the wind, and the
+accretion disc. For simplicity, the parameters for the magnetosphere
+($T_{\mathrm{max}}=7500\,\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ are
+fixed as in Figure~\ref{fig:atlas_acc_models}), and the wind mass-loss
+rate, the isothermal wind temperature and the wind anisotropy
+parameter to $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,
+yr^{-1}}$
+(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$),
+$T_{\mathrm{wind}}$ and $b=4$ respectively. The profile computed for
+$i=55^{\circ}$ is given in Figure~\ref{fig:summary_beta05_t8000},
+along with the profile computed with the magnetosphere only and that
+with the wind plus accretion disc configurations for a comparison. As
+one can see from the figure, the profile computed for the
+disc--wind--magnetosphere hybrid model can be understood as a simple
+flux sum of the magnetospheric component and the wind component. In
+this example, the wind causes the absorption of the blue side of the
+profile, and it adds extra flux around the line centre. As seen
+before, the presence of the disc causes a reduction in the red side of
+the profile since the emission from the receding gas is blocked by the
+disc. The resulting profile appears to be narrower than that of the
+magnetosphere model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
   \caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models
-include the magnetospherical accretion flow (with
+    include the magnetospheric accretion flow (with
     $T_{\mathrm{\max}}=7500~\mathrm{K}$ and
@@
     Figure~\ref{fig:effect_mdot_disc_wind_acc}).  For a comparison, the
-profile computed with only the magnetospherical accretion flow (dotted)
+    profile computed with only the magnetospheric accretion flow (dotted)
     is overlayed. All the profiles are computed at the inclination angle
@@
 \end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The effect of changing the ratio of the wind mass-loss rate to mass-accretion
-rate ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
-in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With a fixed value
-of mass-accretion rate
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The effect of changing the ratio of the wind mass-loss rate to
+mass-accretion rate
+($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
+in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With a fixed value of
+mass-accretion rate
 ($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
-mass-loss rate is varied. The figure shows that 
-as $\mu$ increases the P-Cygni absorption deepens, and the position
-of minimum flux in the absorption trough appears to move blue-ward.
-On the other hand, the emission component becomes stronger as $\mu$
-increases. With this combination of the parameters for the magnetosphere
-and the wind, the absorption component tends to be too strong for
-the models $\mu>0.025$ (with this model configuration), at all inclinations
-(not shown here), compared with the observed H$\alpha$ profiles (e.g.\citealt{reipurth:1996};
-\citealt{alencar:2000}). 
+mass-loss rate is varied. The figure shows that as $\mu$ increases the
+P-Cygni absorption deepens, and the position of minimum flux in the
+absorption trough appears to move blue-ward.  On the other hand, the
+emission component becomes stronger as $\mu$ increases. With this
+combination of the parameters for the magnetosphere and the wind, the
+absorption component tends to be too strong for the models $\mu>0.025$
+(with this model configuration), at all inclinations (not shown here),
+compared with the observed H$\alpha$ profiles
+(e.g.\citealt{reipurth:1996}; \citealt{alencar:2000}).
 %As we will see later (section~\ref{fig:ttau_model}),
@@
 
-Again, the H$\alpha$ profiles with the same range of the wind temperature
-($T_{\mathrm{wind}}$) and the wind acceleration parameter ($\beta$)
-used in Figure~\ref{fig:atlas_wind_model} are computed, but this time with $\mu=0.01$.
-The parameters of the magnetosphere are fixed as in
-Figure~\ref{fig:acc_inclination_effect}. The results are shown in
-Figure~\ref{fig:atlas_disc_wind_acc_model} along with 
-the model with only the magnetosphere for a comparison. A relatively
-small value of $\mu$ is chosen to avoid absorption component of the
-P-Cyg profile becoming too strong, as seen in Figure~\ref{fig:effect_mdot_disc_wind_acc}.
-In general, even with small values of the anisotropy parameter ($b=0$
-and $2$), the absorption component is found to be too strong when
-$\mu=0.1$ is used with this combination of the magnetosphere and
-the wind. The figure shows that the position of the wind absorption
-component moves toward the line centre as $\beta$ becomes larger.
-Although little wind emission is seen in this temperature range, it
-becomes more important in a model with a higher temperature and a
-larger wind mass-loss rate. In fact, the model with $\beta=2.0$ and
-$T_{\mathrm{wind}}=9000\,\mathrm{K}$ displays a small amount of the wind
-emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
+Again, the H$\alpha$ profiles with the same range of the wind
+temperature ($T_{\mathrm{wind}}$) and the wind acceleration parameter
+($\beta$) used in Figure~\ref{fig:atlas_wind_model} are computed, but
+this time with $\mu=0.01$.  The parameters of the magnetosphere are
+fixed as in Figure~\ref{fig:acc_inclination_effect}. The results are
+shown in Figure~\ref{fig:atlas_disc_wind_acc_model} along with the
+model with only the magnetosphere for a comparison. A relatively small
+value of $\mu$ is chosen to avoid absorption component of the P-Cyg
+profile becoming too strong, as seen in
+Figure~\ref{fig:effect_mdot_disc_wind_acc}.  In general, even with
+small values of the anisotropy parameter ($b=0$ and $2$), the
+absorption component is found to be too strong when $\mu=0.1$ is used
+with this combination of the magnetosphere and the wind. The figure
+shows that the position of the wind absorption component moves toward
+the line centre as $\beta$ becomes larger.  Although little wind
+emission is seen in this temperature range, it becomes more important
+in a model with a higher temperature and a larger wind mass-loss
+rate. In fact, the model with $\beta=2.0$ and
+$T_{\mathrm{wind}}=9000\,\mathrm{K}$ displays a small amount of the
+wind emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
 
@@
 (affected by the blue-shifted absorption feature) cannot be explained
-by the magnetospherical accretion flow alone
+by the magnetospheric accretion flow alone
 (e.g.~\citealt{muzerolle:2001}).  Comparison of the model profiles
@@
 
-As an alternative model for the bipolar wind models (with the combination
-of the magnetosphere and the accretion disc) shown in Figures~\ref{fig:atlas_wind_model}
-and \ref{fig:atlas_disc_wind_acc_model}, we have also considered
-the disc-wind model of \citet{knigge:1995} as described in section~\ref{sub:model-disc-wind}.
-The former resembles the density structure of \citealt{krasnopolsky:2003}
-in large scale ($\sim100$~au) which described in section~\ref{sub:wind_jet},
-and the latter in small scale ($\sim10$~au) of the same model. The
-main difference between the two models are in their density structure.
-At a given radius, the density increases toward the polar direction
-in the former model, but the density increases toward the equatorial
-plane for the models presented here.
+As an alternative model for the bipolar wind models (with the
+combination of the magnetosphere and the accretion disc) shown in
+Figures~\ref{fig:atlas_wind_model} and
+\ref{fig:atlas_disc_wind_acc_model}, we have also considered the
+disc-wind model of \citet{knigge:1995} as described in
+section~\ref{sub:model-disc-wind}.  The former resembles the density
+structure of \citealt{krasnopolsky:2003} in large scale ($\sim100$~au)
+which described in section~\ref{sub:wind_jet}, and the latter in small
+scale ($\sim10$~au) of the same model. The main difference between the
+two models are in their density structure.  At a given radius, the
+density increases toward the polar direction in the former model, but
+the density increases toward the equatorial plane for the models
+presented here.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     profiles for models with larger $\beta$ and $T_{\mathrm{dw}}$ (the
-slower accerelation and the hotter models). For a comparison, the
-profile computed with only the magnetospherical accretion flow (dotted)
+    slower acceleration and the hotter models). For a comparison, the
+    profile computed with only the magnetospheric accretion flow (dotted)
     is overlayed.}
@@
 We now consider the models computed with the combination of the
-disc-wind and the magnetospherical accretion components. The
+disc-wind and the magnetospheric accretion components. The
 parameters used for the magnetosphere are set to be same as in the
@@
 which are classified according to the definition of \citet{reipurth:1996}.
-The combination of the disc wind, magnetospherical accretion, and
+The combination of the disc wind, magnetospheric accretion, and
 accretion disc can reasonably reproduce all the classes of the profiles
@@
 which shows the inverse P-Cyg profile shape.  This can be understood
-since the magnetospherical accretion model of \citet{hartmann:1994}
+since the magnetospheric accretion model of \citet{hartmann:1994}
 predicts that the redshifted absorption can occur at a limited range
@@
     classification by \citet{reipurth:1996}. The combination of
-magnetospherical accretion flow, the accretion disc, and the disc wind
+    magnetospheric accretion flow, the accretion disc, and the disc wind
     model can reasonably reproduce wide ranges of H$\alpha$ profiles seen
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%astro.ex.ac.uk/people/rk/
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+% Uncomment the following if you want to include TTau model section
+%
 %\input{ttau_model_subsec.tex}
+%
+%
 
@@
 at inclination angles $i=10^{\circ}$, $55^{\circ}$ and $80^{\circ}$. Both
-models include the magnetospherical accretion component with the same
+models include the magnetospheric accretion component with the same
 parameters used as in sections~\ref{sub:model-acc-disc-wind} and
@@
 
-We have presented the disc--wind--magnetosphere hybrid radiative transfer
-models for classical T~Tauri stars, and detailed studies of the H$\alpha$
-formation from their complex to circumstellar environment to understand
-the wide variety of H$\alpha$ profiles seen in observations. The
-two types of wind models considered are (1)~the bipolar wind model
-in which the wind originates from the star itself (section~\ref{sub:wind_jet};
-Figure~\ref{fig:config_dipolar}), and (2)~the disc-wind model in
-which the wind originates from the inner part of the accretion disc
-(section~\ref{sub:Alternative-model-disc-wind}; Figure~\ref{fig:config_discwind}).
-We found that both wind models combined with the magnetospherical
-accretion flow reproduces the wide variety of H$\alpha$ profiles
-(Figures~\ref{fig:atlas_disc_wind_acc_model} and \ref{fig:atlas_discwind_acc_model})
-seen in the observations.
-
-The inclination dependency of the line equivalent width predicted
-by the bipolar wind model agree with trends seen in the observation,
-but the disc-wind model does not. With the standard magnetospherical
+We have presented the disc--wind--magnetosphere hybrid radiative
+transfer models for classical T~Tauri stars, and detailed studies of
+the H$\alpha$ formation from their complex to circumstellar
+environment to understand the wide variety of H$\alpha$ profiles seen
+in observations. The two types of wind models considered are (1)~the
+bipolar wind model in which the wind originates from the star itself
+(section~\ref{sub:wind_jet}; Figure~\ref{fig:config_dipolar}), and
+(2)~the disc-wind model in which the wind originates from the inner
+part of the accretion disc
+(section~\ref{sub:Alternative-model-disc-wind};
+Figure~\ref{fig:config_discwind}).  We found that both wind models
+combined with the magnetospheric accretion flow reproduces the wide
+variety of H$\alpha$ profiles
+(Figures~\ref{fig:atlas_disc_wind_acc_model} and
+\ref{fig:atlas_discwind_acc_model}) seen in the observations.
+
+The inclination dependency of the line equivalent width predicted by
+the bipolar wind model agree with trends seen in the observation, but
+the disc-wind model does not. With the standard magnetospheric
 configuration (Table~\ref{tab:std_parameters}), the ratio of the
-mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind
-was set to be 4 --10 times smaller than that predicated by magneto-hydrodynamical
-(MHD) calculations (c.f.~$\mu\sim0.1;$ \citealt{koenigl:2000})
-to avoid the blue-shifted absorption component becoming unrealistically
-too strong; however $\mu$ used in the disc-wind models are consistent
-with MHD calculations.
+mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind was
+set to be 4 --10 times smaller than that predicated by
+magneto-hydrodynamical (MHD) calculations (c.f.~$\mu\sim0.1;$
+\citealt{koenigl:2000}) to avoid the blue-shifted absorption component
+becoming unrealistically too strong; however $\mu$ used in the
+disc-wind models are consistent with MHD calculations.
 
@@
 classification proposed by \citet{reipurth:1996}, and discussed the
-basic physical conditions that reproduce the profiles in each classified
-type. Using the different combinations of the inclination ($i$), the
-mass-loss to mass-accretion rate ratio ($\mu$) and the wind
+basic physical conditions that reproduce the profiles in each
+classified type. Using the different combinations of the inclination
+($i$), the mass-loss to mass-accretion rate ratio ($\mu$) and the wind
 acceleration rate ($\beta$), our radiative transfer model was able to
@@
 models. The parametrisation of the wind density structure should be
-changed to follow more closely that of MHD simulations. The wind temperature
-structure should be calculated self-consistently (c.f.~\citealt{hartmann:1994};
-\citealt{martin:1996}). (2)~Computing the line profiles using the
-density structure from MHD directly. Check the consistency, and give
-feedback to the MHD models which are needed to be tested against observational
-data. (3)~Spectropolarimetric study to explore the geometry and the
-rotation of the disc (e.g.~\citealt{vink:2005}). (4)~Modelling
-of the extended H$\alpha$ and spectro-astrometric observations (c.f.~\citealt{takami:2003};
-\citealt{appenzeller:2005}). (5)~Line variability study using a
-3D radiative transfer model (e.g.~\citealt{symington:2005}; \citealt{kurosawa:2005a})
-to probe the geometrical structure.
+changed to follow more closely that of MHD simulations. The wind
+temperature structure should be calculated self-consistently
+(c.f.~\citealt{hartmann:1994}; \citealt{martin:1996}). (2)~Computing
+the line profiles using the density structure from MHD directly. Check
+the consistency, and give feedback to the MHD models which are needed
+to be tested against observational data. (3)~Spectropolarimetric study
+to explore the geometry and the rotation of the disc
+(e.g.~\citealt{vink:2005}). (4)~Modelling of the extended H$\alpha$
+and spectro-astrometric observations (c.f.~\citealt{takami:2003};
+\citealt{appenzeller:2005}). (5)~Line variability study using a 3D
+radiative transfer model (e.g.~\citealt{symington:2005};
+\citealt{kurosawa:2005a}) to probe the geometrical structure.
 
@@
 %
-
+%----------------------------------------------------
+% Bibliography follows here.
+%-----------------------------------------------------
 %
+\bibliographystyle{mn}
+\bibliography{mnras}
 
 %
-
-%----------------------------------------------------
-
-% Bibliography follows here.
-
-%-----------------------------------------------------
-
-%
-
-%
-
-%
-
-\bibliographystyle{mn}
-
-\bibliography{mnras}
-
 %

### 2006-01-19 TTau_Halpha/kurosawa.tex
th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@622 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-\caption{Summary of the standard classical T~Tauri star model parameters.}
+\caption{Summary of the reference classical T~Tauri star model parameters.}
 \label{tab:std_parameters}
@@
 
-xxxx finished here xxxxx
-
 \section{Results}
@@
 
-\subsection{Magnetosphere}
+\subsection{Magnetosphere only models}
 
@@
 
-Using the standard parameters (Table~\ref{tab:std_parameters}) for the
+Using the reference model parameters (Table~\ref{tab:std_parameters}) for the
 central star and the magnetosphere, we examine the dependency of
 H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion flow
-and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
-done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
-is computed from the available kinetic energy of the free-falling gas
-as describe by \citet{hartmann:1994} while \citet{muzerolle:2001} used
-the constant hot ring temperature ($8000\,\mathrm{K}$) for most of
-their models. The accretion luminosity ($L_{\mathrm{acc}}$) of models
+and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as
+done by \citet{muzerolle:2001} for H$\beta$. We note that here we have
+ computed the hot ring temperature self-consistently, whereas \citet{muzerolle:2001} used
+a constant hot ring temperature ($8000\,\mathrm{K}$) for most of
+their models.  The accretion luminosity ($L_{\mathrm{acc}}$) for models
 with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ is
-about a half of the total luminosity (without the hot ring) of the
-star, and $L_{\mathrm{acc}}$ is proportional to
-$\dot{M}_{\mathrm{acc}}$.  The results are placed in
-Figure~\ref{fig:atlas_acc_models}. Overall dependency on
-$T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are similar to that of
-\citet{muzerolle:2001}. In general, the line strength becomes weaker
-as the accretion rate and the temperature become smaller.  The
-red-shifted absorption becomes less visible for higher accretion rate
-and temperature models in which the flux in the damping wings become
-important. Figure~\ref{fig:broadening} shows an example of the effect
-of the broadening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$) due
-to the damping constants as described in
-section~\ref{sec:radiative-transfer-model}.  Although the maximum flux
-of the model with the broadening is almost identical to that of the
+about a half of the photospheric luminosity.
+
+H$\alpha$ line profiles for a range of $T_{\mathrm{max}}$ and
+$\dot{M}_{\mathrm{acc}}$ are presented in  Figure~\ref{fig:atlas_acc_models}. 
+The  overall dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ is similar to that of
+\citet{muzerolle:2001}. In general, the line strength weakens
+as the accretion rate and the temperature drop.  The
+red-shifted absorption becomes less visible for the higher accretion rate
+and higher temperature models as it becomes filled-in by the stronger Stark-broadened
+line-wing emission.
+
+We demonstrate this effect in Figure~\ref{fig:broadening}, which shows an example 
+for an H$\alpha$  model with $T_{\mathrm{max}}=7500\,\mathrm{K}$
+and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, both with and without
+damping.  Although the maximum flux of the model with broadening is almost identical to that of the
 model with no damping constant ($\Gamma=0$), a significant increase of
-the line flux in both red and blue wings of seen in the model with
-broadening. The weak red-shifted absorption component (which is a
-signature of the magnetospheric accretion) is weakened or eliminated
-by the flux in broadened wing.
-
-Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown in
-Figure~\ref{fig:atlas_acc_models}. About a half of the models shown
-the figure agree with the observed EW values of H$\alpha$ from 30 TTS
-presented by \citet{alencar:2000} who found the EW of H$\alpha$ ranges
-from $\sim 3$~\AA\, to $\sim 160$~\AA, and the mean to be $\sim
-55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models, the EW values
-are smaller than the minimum EW observed by \citet{alencar:2000}, and
-for some models the EWs are negative. Since the target selection
-criteria of \citet{alencar:2000} is not stated in their paper, we can
-not conclude that these low $\dot{M}_{\mathrm{acc}}$ models disagree
-with the observation. \citet{reipurth:1996}, who measured the EW of 43
-TTS and found similar distribution of EW values, mentioned that their
-EW measurements are under-representing real samples since the
-selection of the targets are based on the strong emission in H$\alpha$
-surveys.
-
-The dependency of the profile on the inclination angle ($i$) is
+the line flux in both red and blue wings of seen. The weak red-shifted
+absorption component (which is a signature of the magnetospheric accretion)
+is weakened or eliminated by the flux in broadened wing.
+
+Table~\ref{tab:ha_ew_acc_models} shows the EW for the models in
+Figure~\ref{fig:atlas_acc_models}.  The EWs for half the models
+fall within the range of EWs ($\sim 3$~\AA\, to $\sim 160$~\AA)
+measured by \citet{alencar:2000}. The equivalent widths of models 
+with the lowest mass accretion rates fall below the minimum EW
+observed by  \citet{alencar:2000}, while several models would
+be designated as weak-lined T~Tauri stars using the traditional
+10\,\AA\ cut-off.
+
+xxxx might want to talk about line widths as an accretion 
+indicator here as well (white and basri).
+
+The dependency of the line profile on inclination angle ($i$) is
 demonstrated in Figure~\ref{fig:acc_inclination_effect}. The model
-uses the same parameters as in Figure~\ref{fig:broadening} (with
-broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
+has  $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
 $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).  The
 figure shows that the peak (normalised) flux decreases as the
-inclination angle increases. Similarly, the equivalent width also
-decreases as the inclination increases. Because of the geometry of the
+inclination angle increases, as does the EW.
+
+xxxx check reasons for inclination dependence xxxx
+
+Because of the geometry of the
 magnetospheric accretion (c.f. Figure~\ref{fig:config_dipolar}) and of
@@
 relatively narrow line appearance of the profile with
-$i=10^{\circ}$. Although not shown here, a similar dependency on the
-inclination angle is found for the models with different temperatures
-($T_{\mathrm{max}}=6500$, $8500$, $9500\,\mathrm{K}$).
-
-As seen in the models of \citet{hartmann:1994} and
-\citet{muzerolle:2001}, our models also show the blue-shifted peak and
-the blue-ward asymmetry caused by the occultation of the accretion
-flow by the equatorial disc and the stellar disc. However,
-\citealt{alencar:2000} (see their Fig.~9) found a substantial fraction
-of the observed H$\alpha$ profiles also shows the {}``red-shifted''
-peak, and the P~Cygni profiles which can not be explained by the
-magnetospheric accretion model alone. In addition, a recent study by
-\citet{appenzeller:2005} showed that the equivalent width of H$\alpha$
-from CTTS increases as the inclination angle increases. Our model with
-the magnetospheric accretion flow clearly disagrees with their
-finding.
+$i=10^{\circ}$.
+
+A similar EW dependence on
+inclination angle is found for the models with different 
+magnetospheric temperatures ($T_{\mathrm{max}}=6500$,
+$8500$, $9500\,\mathrm{K}$).
+
+Our models show a blue-shifted line peak and
+a blueward asymmetry caused by occultation of the accretion
+flow by the stellar photosphere (see also \citet{hartmann:1994} and
+\citet{muzerolle:2001}). However, \citealt{alencar:2000} (see their Fig.~9)
+found a substantial fraction
+of the observed H$\alpha$ profiles show a red-shifted
+peak. Furthermore, a recent study by
+\citet{appenzeller:2005} demonstrated  that the equivalent width of H$\alpha$
+from CTTS {\em increases} as the inclination angle increases. 
+Clearly a magnetospheric accretion only model cannot explain the
+full properties of the H$\alpha$ profiles in CTTS.
 
@@
     rate ($\dot{M}_\mathrm{acc}$) and temperature
-    ($T_{\mathrm{max}}$). The profiles are computed using only
-    magnetospheric accretion flow (i.e. no wind/jet).  All the profiles
-    are computed using the parameters of the `standard' model
+    ($T_{\mathrm{max}}$). The profiles are computed using only the
+    magnetospheric accretion flow (i.e. no outflow).  All the profiles
+    are computed using the parameters of the reference model
     (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The
-    temperature (indicated along the vertical axis) of the model increase
+    temperature (indicated along the vertical axis) of the model increases
     from top to bottom, and the mass accretion rate (indicated by the
-    values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from
-    left to right. The profiles are similar to those of
-    \citet{muzerolle:2001}, available on-line
-    (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html). }
+    values in $\mathrm{M_{\odot}\,yr^{-1}}$ along the top) increases from
+    left to right. }
 
@@
 
-  \caption{The effect of line broadening for H$\alpha$. The model
+  \caption{The effect of line broadening on H$\alpha$. A model
     computed with a damping constant ($\Gamma$), described in
     section~\ref{sec:radiative-transfer-model} (solid), is compared with
-    the model with no damping, $\Gamma=0$ (dashed).  Both models are
+    a model with no damping, $\Gamma=0$ (dashed).  Both models are
     computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
-    standard parameters given in Table~\ref{tab:std_parameters}. The two
+    reference parameters given in Table~\ref{tab:std_parameters}. The two
     models have similar peak flux levels (around $V \sim 0~\kmps$), but
@@
 
-  \caption{Dependency of H$\alpha$ profiles on inclination ($i$).  The
-    profiles are computed with the magnetospheric accretion flow using
-    the standard parameters given in Table~\ref{tab:std_parameters} and
+  \caption{The dependency of the H$\alpha$ profile on inclination ($i$).  The
+    profiles are computed with a magnetospheric accretion flow only using
+    the reference parameters given in Table~\ref{tab:std_parameters} and
     $T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
@@
     respectively. As the inclination becomes larger, the peak flux and the
-    equivalent width of the line becomes smaller.  Similar dependency is
-    seen in the models with the wide ranges of $T_{\mathrm{max}}$ and
-    $\beta$. }
+    equivalent width of the line becomes smaller.  }
 
@@
 
-\subsection{Bipolar Wind}
+\subsection{Bipolar wind only models}
 
@@
 
-As mentioned earlier, the magnetospheric accretion flow model alone
-cannot explain some of the features seen in observations. As an
+As mentioned above, the MA model alone
+cannot explain the observations. As an
 alternative model, we now examine formation of H$\alpha$ in a simple
@@
 $v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$ and
-$\dot{M}_{\mathrm{wind}}$. To minimise the number of free parameters,
-we initially adopt $\gamma=0.05$, $v_{\infty}=210\,\kmps$
+$\dot{M}_{\mathrm{wind}}$. We fix several of these parameters
+at plausible values:  $\gamma=0.05$, $v_{\infty}=210\,\kmps$
 \citep{appenzeller:2005} and
@@
 closest to the accretion disc is about
-$\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$, for
-given radii. For simplicity, the wind temperature $T_{\mathrm{wind}}$
-is assumed to be isothermal\@. Although the line is potentially
+$\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$
+Although the line is potentially
 sensitive to the temperature structure of the wind, determination of a
@@
 temperature structure is determined by balancing the radiative cooling
-rate (assuming optically thin) with the MHD wave heating rate. With
-these parameters kept constant, we examine the characteristics of
-H$\alpha$ profiles, as a function of the wind acceleration parameter
+rate (assuming optically thin) with the MHD wave heating rate.
+We pragmatically assume that the wind is isothermal at $T_{\mathrm{wind}}$.
+
+Initially we examine the characteristics of the
+H$\alpha$ profile  as a function of the wind acceleration parameter
 $\beta$ and the isothermal wind temperature
-$T_{\mathrm{wind}}$. Dependency on the other parameters will be
-discussed later in this section.
-
-Figure~\ref{fig:atlas_wind_model} shows the profile computed at a mid
-inclination angle $i=55^{\circ}$ for the range of the wind temperature
-between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and for the range
-of $\beta$ between $0.2$ and $2.0$. The P~Cygni profiles are prominent
+$T_{\mathrm{wind}}$.  Figure~\ref{fig:atlas_wind_model} shows profiles computed at  $i=55^{\circ}$
+ for a range of wind temperatures
+between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and  $\beta$ between $0.2$ and $2.0$.
+
+Classical P~Cygni profiles are prominent
 in the models with lower values of $T_{\mathrm{wind}}$ and $\beta$
-(colder and faster acceleration wind). As the value of $\beta$
+(a colder and faster accelerating wind). As the value of $\beta$
 increases, the position of the blue-shifted absorption component moves
-toward the line centre. which can be seen clearly in the
-$T_{\mathrm{wind}}=7000\,\mathrm{K}$ models. While the velocity
-position of absorption component for the fastest acceleration
+toward the line centre -- this can be seen clearly in the
+$T_{\mathrm{wind}}=7000\,\mathrm{K}$ models. The velocity position
+ of the absorption component of the fastest accelerating wind
 ($\beta=0.2$) is almost at the terminal velocity ($v_{\infty}\sim
 210\,\kmps$), that for the slowest wind acceleration model
-($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).  As
+($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).
+
+ As
 one can see in Figure~\ref{fig:wind_vr_rho}, the column density of the
@@
 
-\subsection{Disc-wind model of \citet{knigge:1995}}
+\subsection{The disc-wind model}
 
@@
 
-As an alternative model for the bipolar wind models (with the
-combination of the magnetosphere and the accretion disc) shown in
-Figures~\ref{fig:atlas_wind_model} and
-\ref{fig:atlas_disc_wind_acc_model}, we have also considered the
-disc-wind model of \citet{knigge:1995} as described in
-section~\ref{sub:model-disc-wind}.  The former resembles the density
-structure of \citealt{krasnopolsky:2003} in large scale ($\sim100$~au)
-which described in section~\ref{sub:wind_jet}, and the latter in small
-scale ($\sim10$~au) of the same model. The main difference between the
-two models are in their density structure.  At a given radius, the
-density increases toward the polar direction in the former model, but
-the density increases toward the equatorial plane for the models
-presented here.
+In this section we examine profiles produced using our alternative
+kinematic model of the outflow: the disc wind. This type of outflow
+has been predicted by several MHD calculations (e.g. \citet{koenigl:2000};
+ \citealt{krasnopolsky:2003}), and broadly consists of a wind with
+a latitudinal density-dependence with density increasing towards
+the equator (see~\ref{sub:model-disc-wind}), in contrast with the 
+bipolar stellar wind.
 
@@
 
-  \caption{The H$\alpha$ profiles computed with the disc-wind only
-    models. With the wind mass-loss rate fixed at
-    $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, the line
+  \caption{H$\alpha$ profiles computed with the disc-wind only.
+     The wind mass-loss rate is fixed at
+    $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, and the line
     profiles are computed with different combinations of the wind
-    acceleration rate ($\beta$) and the isothermal disc-wind temperature
-    ($T_{\mathrm{dw}}$). The wind emission increases as the values of
-    $\beta$ and $T_{\mathrm{wind}}$ increase ( as the wind becomes
-    accelerates slower and as the wind comes warmer.  As in the
+    acceleration rate ($\beta$) and isothermal disc-wind temperature
+    ($T_{\mathrm{dw}}$). The wind emission grows as the values of
+    $\beta$ and $T_{\mathrm{wind}}$ increase.   As in the
     bipolar wind models (Figure~\ref{fig:atlas_wind_model}), the position
     of the wind absorption moves toward the line centre as $\beta$ becomes
-    larger. The morphology of the profiles are similar to that of
-    observations. }
+    larger.     }
 
@@
 
-  \caption{The disc-wind, magnetosphere hybrid model. The same as
-    Figure~\ref{fig:atlas_discwind_only}, but these models (solid) also
-    include the magnetosphere accretion flow
+  \caption{The disc-wind, magnetosphere hybrid model. These models
+  (solid lines) have the  same parameters as
+    Figure~\ref{fig:atlas_discwind_only}, but  also
+    include the magnetospheric accretion flow
     ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
@@
     the emission from the magnetosphere dominates for the models with
-    smaller $\beta$ and $T_{\mathrm{dw}}$ (the faster acceleration and the
-    colder wind models), the emission from the wind dominates the
-    profiles for models with larger $\beta$ and $T_{\mathrm{dw}}$ (the
-    slower acceleration and the hotter models). For a comparison, the
-    profile computed with only the magnetospheric accretion flow (dotted)
-    is overlayed.}
+    smaller $\beta$ and $T_{\mathrm{dw}}$, the emission from the wind dominates the
+    profiles for models with larger $\beta$ and $T_{\mathrm{dw}}$.  The contribution
+    of the magnetosphere can be judged from the profiles computed with
+    the magnetosphere only (dotted lines).}
 
@@
 
-First, the disc-wind models without the magnetosphere are considered.
+Firstly, we consider the disc-wind models without the magnetosphere.
 Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
@@
 and the wind acceleration parameter ($\beta$) ranges used for the
-bipolar wind models. The parameters used for the central star are
-as in section~\ref{sub:Continuum-Source}, and the other disc-wind
+bipolar wind models (c.f. xxxx cite bipolar figure here). The parameters used for the central star are
+as in section~\ref{sub:Continuum-Source}, and the disc-wind
 parameters are summarised in Table~\ref{tab:std_discwind_parameters}.
 The figure shows that the wind emission increases as $\beta$ and $T_{\mathrm{dw}}$
-increase. Similar to the bipolar wind models, the location of the
+increase. The $\beta$ dependence arises simply because for large $\beta$
+there is a greater mass of wind material close to the star.
+As with  the bipolar wind models, the location of the
 P-Cyg absorption component moves toward the line centre as $\beta$
-increases. The morphology of the profile exhibited by the model changes
+increases.
+
+The morphology of the profile exhibited by the model changes
 from FU-Ori type for the models with small $\beta$ to the stronger
@@
 (c.f.~\citealt{reipurth:1996}) as the value of $\beta$
-increases.  Although not shown here, we find that the profile shapes
+increases.  We find that the profile shapes
 are relatively insensitive to the value of the wind collimation parameter
 $d$. The dependency on the disc wind mass-loss rate of the profile
-shape is similar to that of the collimated wind models
+shape is similar to that of the bipolar wind models
 (Figure~\ref{fig:effect_mdot_disc_wind_acc}).
 
-We now consider the models computed with the combination of the
+We now consider the models computed with a combination of the
 disc-wind and the magnetospheric accretion components. The
 parameters used for the magnetosphere are set to be same as in the
-case for Figure~\ref{fig:acc_inclination_effect}, and are kept
-constant for simplicity. The mass-loss rate of the disc wind is set to
+case for Figure~\ref{fig:acc_inclination_effect}.  
+The mass-loss rate of the disc wind is set to
 $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
@@
 
-As in the disc wind only models
+As in the disc-wind only models
 (Figure~\ref{fig:atlas_discwind_only}), the location of the absorption
 component moves toward the line centre as the value of $\beta$
-increases (the wind acceleration is slower).  The figure shows that in
+increases.  The figure shows that in
 the models with smaller $\beta$ and $T_{\mathrm{dw}}$, the line
-emission from the magnetosphere dominates. On the other hand, in the
-models with larger $\beta$ and $T_{\mathrm{dw}}$, the emission from
-the disc wind dominates. Compared to the observation of
-\citet{reipurth:1996} and \citet{alencar:2000}, the lines are too
-strong for
+emission from the magnetosphere dominates, while this situation reverses for the
+models with larger $\beta$ and $T_{\mathrm{dw}}$. The model with
 $\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
-and $\left(9000\,\mathrm{K},\,1.0\right)$ models.
+results in an H$\alpha$ profile that is far too strong to be compatible
+ with observations (\citet{reipurth:1996} and \citet{alencar:2000}).
 
@@
 computed with limited ranges of  $T_{\mathrm{dw}}$ and $\beta$, the
-resulting profiles exhibit the wide varieties of line shapes which are
-very similar to the types of H$\alpha$ profiles seen in the
+resulting profiles exhibit a wide variety of line profile shapes,
+many of  which are similar to the types of H$\alpha$ profiles seen in the
 observations (c.f.~\citealt{reipurth:1996}).   The shape of the
 primary and secondary peaks in the profiles are slightly {}``rounder''
-compared to those of the accretion, collimated wind, disc hybrid model
+in comparison to those of the accretion, bipolar wind, disc hybrid model
 shown in Figure~\ref{fig:atlas_disc_wind_acc_model}.  The rounder
-peaks are caused by the rotation of the wind. The profiles from the
-disc-wind models are affected more by the rotational motion of the
-wind since the gas is more concentrated toward the equator, but in the
-models with the collimated wind the gas is concentrated more in the
-polar directions.
-
-We note the ambiguity seen between some of the disc-wind only models
-and the disc-wind, magnetosphere hybrid models. For example, the disc-wind
+peaks are the result of wind rotation.
+
+xxxx think of a way of talking about rotation in comparison between
+the disc wind model and the bipolar wind model xxxx
+
+An examination of the profiles in Figures~\ref{fig:atlas_discwind_only} and
+Figure~\ref{fig:atlas_discwind_acc_model} reveals some of problems
+with uniqueness that must inevitably occur when trying to assign
+an individual profile as wind or accretion dominated i.e. very similar profiles may arise
+from very different circumstellar geometries. For example, the disc-wind
 only model with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
-in Figure~\ref{fig:atlas_discwind_only} and the disc-wind model
-with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
-in Figure~\ref{fig:atlas_discwind_acc_model} give very similar profiles.
-Given such an observed profile, it is difficult to distinguish if
-the emission is dominated by the accretion or the wind unless some
-other lines, not affected associated with wind or magnetosphere, are
-used simultaneously.
-
-General characteristics of the profiles from the disc-wind, magnetosphere
+(Figures~\ref{fig:atlas_discwind_only}) and the  accretion dominated model with
+ $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
+in (Figure~\ref{fig:atlas_discwind_acc_model}) give very similar profiles.
+
+xxxx paragraph below may need changing after new models are added xxxx
+
+The general characteristics of the profiles from the disc-wind, magnetosphere
 hybrid model (Figure~\ref{fig:atlas_discwind_acc_model}) are very
-similar to those of the disc, collimated wind, magnetosphere hybrid
+similar to those of the disc, bipolar wind, magnetosphere hybrid
 model (Figure~\ref{fig:atlas_disc_wind_acc_model}). The main difference
-between these two sets of models is in the ration of the mass-loss rate to the mass
+between these two sets of models is in the ratio of the mass-loss rate to the mass
 accretion rate, $\mu$. While the models presented in this section

### 2006-01-19 TTau_Halpha/plots/plot_rho.f90
new plots for stellar wind velocity and density added. RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@624 25464f21-6099-402c-b30a-640f1d40d38b

@@ -4,7 +4,7 @@ program plot_rho
 
   real*8, parameter :: pi =3.141592654d0
   ! Parameters 
-  real*8 :: m, theta_wind, Mdot_wind, V0, Vinf, R_mo, beta, r_star
+  real*8 :: m, theta_wind, Mdot_wind, V0, Vinf, R_mo, beta, r_star, R_star_cm
 
   real*8 :: R_min, R_max
   integer, parameter :: nr = 200
@@ -18,21 +18,23 @@ program plot_rho
 
   ! setup parameters
   R_star = 2.0d0  ! [R_sun]
-  m = 2.0d0                           ! [-]
-  theta_wind = 80.0d0 * (pi/180.0d0)  ! [rad]
+  R_star_cm = R_star*6.960d10  ! [R_sun]
+  m = 0.0
+  theta_wind = 30.0d0 * (pi/180.0d0)  ! [rad]
   Mdot_wind  = 1.0d-8 * 1.98892d33 / 31536000.0d0  ! [grams/s]
 !  V0 = 20.0       * 1.0d5   ! [cm/s]
 !  V0 = 2.0       * 1.0d5   ! [cm/s]
   V0 = 10.0       * 1.0d5   ! [cm/s]
   Vinf = 200.0d0  * 1.0d5   ! [cm/s]
-  R_mo = 3.0d0*R_star * 6.960d10  ! [cm]
+  R_mo = 3.0d0*R_star_cm    ! [cm]
   beta = 2.0d0
+
 !  gamma = 0.05
 !  M_star = 2.0 * 1.9891d33  !  [g]
 
   ! setting up r and theta
-  rmin = R_mo
-  rmax = 1000.0d0*R_mo
+  rmin = 1.000001*R_star_cm
+  rmax = 1000.0d0*R_star_cm
   log10_rmin = log10(rmin); log10_rmax = log10(rmax)
   log10_dr = (log10_rmax-log10_rmin)/dble(nr-1)
   do i = 1, nr 
@@ -47,20 +49,18 @@ program plot_rho
   do j = 1, nt
      do i = 1, nr
         density(i,j) = rho(r(i), theta(j), m, theta_wind, Mdot_wind, &
-             V0, Vinf, R_mo, beta) ! [g/cm^2]
+             V0, Vinf, R_star_cm, beta) ! [g/cm^2]
      end do
   end do
 
-  ! normalize the density at r=R_mo and theta = 0
[…]

### 2006-01-20 TTau_Halpha/kurosawa.tex
Minor changes in the figure captions.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@625 25464f21-6099-402c-b30a-640f1d40d38b

@@
     used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
-    $\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$,
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$,
     $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$,
-    $T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$. The profile for
+    $T_{\mathrm{wind}}=9000\,\Kelvin$, and $\beta=0.5$. The profile for
     the case 3 is can be understood as a simple flux sum of the profiles
@@
 
-  \caption{The effect of the mass-loss rate to mass-accretion rate ratio
-    ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
-    profile computed with only the magnetospheric accretion (thick
-    solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
-    $\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ --- is compared with
-    the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01
-    (solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash). All the models
-    are computed with the inclination angle $i=55^{\circ}$. As $\mu$
-    increases the P-Cygni absorption deepens and the emission component
-    becomes stronger. In general, the absorption is too strong for the
-    models with $\mu>0.025$ compared to the observations (e.g.,
-    \citealt{reipurth:1996}).}
+  \caption{The effect of the mass-loss rate to mass-accretion rate
+    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
+    H$\alpha$ profile computed with only the magnetospheric accretion
+    (thick solid) is compared with the magnetosphere--wind--disc
+    hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1
+    (dot) and 0.2 (dash). The magnetosphere used here has
+    $T_{\mathrm{max}}=7500\,\Kelvin$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
+    temperature and the acceleration parameter of the bipolar wind are
+    $T_{\mathrm{wind}}=7000\,\Kelvin$ and $\beta=2.0$ respectively.
+    All the models are computed with the inclination angle
+    $i=55^{\circ}$. As $\mu$ increases the P-Cygni absorption deepens
+    and the emission component becomes stronger. In general, the
+    absorption is too strong for the models with $\mu>0.025$ compared
+    to the observations (e.g., \citealt{reipurth:1996}).}
 

### 2006-01-23 TTau_Halpha/kurosawa.tex
Minor change. (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@627 25464f21-6099-402c-b30a-640f1d40d38b

@@
 will also discuss whether our model is consistent with some
-predictions made by recent MHD studies i.e.~
+predictions made by recent (magneto-hydrodynamics) MHD studies i.e.~
 $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+%% \begin{figure*}
+
+%%   \begin{center}
+
+%%     \includegraphics[%
+%%       scale=0.5]{figures/overview3.eps}
+
+%%   \end{center}
+
+%%   \caption{The basic model configuration. The system consists of four
+%%     components: (1)~the continuum source located at the origin $\left( o
+%%     \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
+%%     $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
+%%     (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
+%%     distribution is symmetric around the $z$-axis. The innermost radius of
+%%     the magnetosphere (at the equatorial plane) coincides with the the
+%%     inner radius of the accretion disc. From the innermost part of the
+%%     accretion disc, the gas falls freely, moving along the magnetic field
+%%     onto the surface of the star. The bipolar wind starts from just
+%%     outside the largest radius 
+%%     ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
+
+%%   \label{fig:config_dipolar}
+
+%% \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
 
@@
     \includegraphics[%
-      scale=0.5]{figures/overview3.eps}
+      scale=0.3]{figures/overview3_alt.eps}
 
@@
     accretion disc, the gas falls freely, moving along the magnetic field
-    onto the surface of the star. The bipolar wind starts from just
-    outside the largest radius 
-    ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
+    onto the surface of the star. The wind density is enhaced toward
+    the polar directions to mimic the collimated wind structure of the
+    magneto-hydrodynamical simulations (e.g.~\citealt{krasnopolsky:2003}). }
 
@@
 
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hline
-Standard&
+&
 $2.0$&
@@
 be near the co-rotation radius of stellar magnetosphere, an
-{}``X-wind'' \citep{shu:1994} is produces. If the open field lines are
+{}``X-wind'' \citep{shu:1994} is produced. If the open field lines are
 located in a wider area of the disc, a {}``disc-wind'' similar to that
@@
 outflow is collimated along the rotational axes (a model similar to
-that of \citet{krasnopolsky:2003}). The second model is based on the
-disc-wind paradigm, in which the density of the outflow increases
-towards the equatorial plane. The difference in latitudinal density
-structure between the two outflow models should provide an indication
-as to whether line profiles alone can be used to constrain the outflow
-geometry. In the following sections we present details of the two
-outflow structures.
+that of \citealt{krasnopolsky:2003} in large scale, $>10$~au). The
+second model is based on the disc-wind paradigm, in which the density
+of the outflow increases towards the equatorial plane. The difference
+in latitudinal density structure between the two outflow models should
+provide an indication as to whether line profiles alone can be used to
+constrain the outflow geometry. In the following sections we present
+details of the two outflow structures.
 
@@
 shown in Figure~\ref{fig:wind_vr_rho}. All other parameters describing
-the wind are fixed as the standard values given in
+the wind are fixed as the reference values given in
 Table~\ref{tab:std_parameters}.
@@
 different values of $\beta$ with all other parameters fixed at the
-standard values (Table~\ref{tab:std_parameters}).  The density is
+reference values (Table~\ref{tab:std_parameters}).  The density is
 relatively sensitive to the value of $\beta$ for $r<10\,
@@
 
-Table~\ref{tab:ha_ew_acc_models} shows the EW for the models in
-Figure~\ref{fig:atlas_acc_models}.  The EWs for half the models
-fall within the range of EWs ($\sim 3$~\AA\, to $\sim 160$~\AA)
-measured by \citet{alencar:2000}. The equivalent widths of models 
+Table~\ref{tab:ha_ew_acc_models} shows the equivalent width (EW) for
+the models in Figure~\ref{fig:atlas_acc_models}.  The EWs for half the
+models fall within the range of EWs ($\sim 3$~\AA\, to $\sim 160$~\AA)
+measured by \citet{alencar:2000}. The EWs of models 
 with the lowest mass accretion rates fall below the minimum EW
 observed by  \citet{alencar:2000}, while several models would
-be designated as weak-lined T~Tauri stars using the traditional
-10\,\AA\ cut-off.
-
-xxxx might want to talk about line widths as an accretion 
-indicator here as well (white and basri).
+be designated as weak-lined T~Tauri stars (WTTS) using the traditional
+10\,\AA\ cut-off \citep[e.g.][]{herbig:1988}.
+
+xxxx Changed xxxxx
+
+\citet{white:2003} empirically showed that the full width of H$\alpha$ at 10
+per~cent of its peak flux (10 per~cent width) is a better
+indicator for an accretion than the EW criteria. They proposed that a
+T~Tauri star shows the 10 per~cent width greater than
+$270\,\mathrm{km\,s^{-1}}$, the star should be a CTTS. The 10 per~cent
+widths of the model H$\alpha$ profiles
+(Figure~\ref{fig:atlas_acc_models}) are summarised in
+Table~\ref{tab:ha_ten_percent_acc_models}.  Using the criteria of
+\citet{white:2003}, the half of the models shown in the figure can be
+classified as CTTS, and the other half as WTTS.
 
@@
 figure shows that the peak (normalised) flux decreases as the
-inclination angle increases, as does the EW.
-
-xxxx check reasons for inclination dependence xxxx
+inclination angle increases, as does the EW.  The line flux and the
+EWs decreases since the fraction of the accretion stream blocked by
+the photosphere increases as the inclination increase.
+
+xxxx Changed xxxxx
 
@@
 relatively narrow line appearance of the profile with
-$i=10^{\circ}$.
-
-A similar EW dependence on
+$i=10^{\circ}$.  A similar EW dependence on
 inclination angle is found for the models with different 
-magnetospheric temperatures ($T_{\mathrm{max}}=6500$,
-$8500$, $9500\,\mathrm{K}$).
+magnetospheric temperatures and the mass-accretion rates.
 
@@
       clip,
-      scale=0.45]{figures/broadening.eps}
+      scale=0.59]{figures/broadening.eps}
 
@@
       clip,
-      scale=0.45]{figures/acc_inc_effect.eps}
+      scale=0.59]{figures/acc_inc_effect.eps}
 
@@
 
-\caption{Summary of H$\alpha$ equivalent widths from the
+\caption{Summary of H$\alpha$ equivalent widths (\AA) from the
 magnetospheric accretion flow models shown in
-Figure~\ref{fig:atlas_acc_models}.}
+Figure~\ref{fig:atlas_acc_models}. Note that the equivalent widths are
+positive when the lines are in emission.}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+
+\caption{Summary of 10 per~cent widths ($\mathrm{km\,s^{-1}}$) from the
+magnetospheric accretion flow models shown in
+Figure~\ref{fig:atlas_acc_models}.}
+
+\label{tab:ha_ten_percent_acc_models}
+
+\begin{center}
+
+\begin{tabular}{cccc}
+\hline 
+$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
+&
+$\dot{M}_{\mathrm{acc}}$ ~$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
+\tabularnewline
+&
+$10^{-7}$&
+$10^{-8}$&
+$10^{-9}$\tabularnewline
+\hline 
+$6500$&
+$300$&
+$120$&
+$100$\tabularnewline
+$7500$&
+$360$&
+$145$&
+$120$\tabularnewline
+$8500$&
+$790$&
+$330$&
+$130$\tabularnewline
+$9500$&
+$1530$&
+$520$&
+$200$\tabularnewline
+\hline
+\end{tabular}
+
+\end{center}
+
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Bipolar wind only models}
@@
     component only (no magnetospheric accretion flow or accretion
-    disc). The `standard' model parameters (Table~\ref{tab:std_parameters}) are
+    disc). The `reference' model parameters (Table~\ref{tab:std_parameters}) are
     applied. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$),
@@
 Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
-computed using only the disc-wind component (c.f. Figure~\ref{fig:config_discwind})
-for the same isothermal disc-wind temperature ($T_{\mathrm{dw}}$)
-and the wind acceleration parameter ($\beta$) ranges used for the
-bipolar wind models (c.f. xxxx cite bipolar figure here). The parameters used for the central star are
-as in section~\ref{sub:Continuum-Source}, and the disc-wind
-parameters are summarised in Table~\ref{tab:std_discwind_parameters}.
-The figure shows that the wind emission increases as $\beta$ and $T_{\mathrm{dw}}$
-increase. The $\beta$ dependence arises simply because for large $\beta$
-there is a greater mass of wind material close to the star.
-As with  the bipolar wind models, the location of the
-P-Cyg absorption component moves toward the line centre as $\beta$
-increases.
-
-The morphology of the profile exhibited by the model changes
-from FU-Ori type for the models with small $\beta$ to the stronger
-emission types which are more commonly seen in the observed H$\alpha$
-(c.f.~\citealt{reipurth:1996}) as the value of $\beta$
-increases.  We find that the profile shapes
-are relatively insensitive to the value of the wind collimation parameter
-$d$. The dependency on the disc wind mass-loss rate of the profile
-shape is similar to that of the bipolar wind models
+computed using only the disc-wind component
+(c.f. Figure~\ref{fig:config_discwind}) for the same isothermal
+disc-wind temperature ($T_{\mathrm{dw}}$) and the wind acceleration
+parameter ($\beta$) ranges used for the bipolar wind models
+(c.f. Figures~\ref{fig:atlas_wind_model} and
+\ref{fig:atlas_disc_wind_acc_model}).  The parameters used for the
+central star are as in section~\ref{sub:Continuum-Source}, and the
+disc-wind parameters are summarised in
+Table~\ref{tab:std_discwind_parameters}.  The figure shows that the
+wind emission increases as $\beta$ and $T_{\mathrm{dw}}$ increase. The
+$\beta$ dependence arises simply because for large $\beta$ there is a
+greater mass of wind material close to the star.  As with the bipolar
+wind models, the location of the P-Cyg absorption component moves
+toward the line centre as $\beta$ increases.
+
+The morphology of the profile exhibited by the model changes from
+FU-Ori type (c.f.~\citealt{reipurth:1996}) for the models with small
+$\beta$ to the stronger emission types which are more commonly seen in
+the observed H$\alpha$ (c.f.~\citealt{reipurth:1996}) as the value of
+$\beta$ increases.  We find that the profile shapes are relatively
+insensitive to the value of the wind collimation parameter $d$. The
+dependency on the disc wind mass-loss rate of the profile shape is
+similar to that of the bipolar wind models
 (Figure~\ref{fig:effect_mdot_disc_wind_acc}).
@@
 results in an H$\alpha$ profile that is far too strong to be compatible
- with observations (\citet{reipurth:1996} and \citet{alencar:2000}).
-
+ with observations (\citet{reipurth:1996} and \citet{alencar:2000});
+ however, the lower mass-loss rate models (while keeping $\mu$ constant)
+ produce the profiles with the line strengths comparable to observations.
 Although the models in Figure~\ref{fig:atlas_discwind_acc_model} are
@@
 many of  which are similar to the types of H$\alpha$ profiles seen in the
-observations (c.f.~\citealt{reipurth:1996}).   The shape of the
-primary and secondary peaks in the profiles are slightly {}``rounder''
-in comparison to those of the accretion, bipolar wind, disc hybrid model
-shown in Figure~\ref{fig:atlas_disc_wind_acc_model}.  The rounder
-peaks are the result of wind rotation.
-
-xxxx think of a way of talking about rotation in comparison between
-the disc wind model and the bipolar wind model xxxx
+observations (c.f.~\citealt{reipurth:1996}).
 
@@
 only model with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
-(Figures~\ref{fig:atlas_discwind_only}) and the  accretion dominated model with
+ (in Figures~\ref{fig:atlas_discwind_only}) and the  accretion dominated model with
  $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
-in (Figure~\ref{fig:atlas_discwind_acc_model}) give very similar profiles.
+(in Figure~\ref{fig:atlas_discwind_acc_model}) give very similar profiles.
 
@@
 
-\caption{A summary of the standard disc-wind model parameters used
+\caption{A summary of the reference disc-wind model parameters used
 in section~\ref{sub:result-discwind-knigge}. See also
@@
 the bipolar wind model agree with trends seen in the observation, but
-the disc-wind model does not. With the standard magnetospheric
+the disc-wind model does not. With the reference magnetospheric
 configuration (Table~\ref{tab:std_parameters}), the ratio of the

### 2006-01-24 TTau_Halpha/kurosawa.tex
Minor change. (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@628 25464f21-6099-402c-b30a-640f1d40d38b
a minor update.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@629 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% \begin{figure*}
+
+%%   \begin{center}
+
+%%     \includegraphics[%
+%%       scale=0.5]{figures/overview3.eps}
+
+%%   \end{center}
+
+%%   \caption{The basic model configuration. The system consists of four
+%%     components: (1)~the continuum source located at the origin $\left( o
+%%     \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
+%%     $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
+%%     (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
+%%     distribution is symmetric around the $z$-axis. The innermost radius of
+%%     the magnetosphere (at the equatorial plane) coincides with the the
+%%     inner radius of the accretion disc. From the innermost part of the
+%%     accretion disc, the gas falls freely, moving along the magnetic field
+%%     onto the surface of the star. The bipolar wind starts from just
+%%     outside the largest radius 
+%%     ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
+
+%%   \label{fig:config_dipolar}
+
+%% \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      scale=0.3]{figures/overview3_alt.eps}
+
+  \end{center}
+
+  \caption{The basic model configuration. The system consists of four
+    components: (1)~the continuum source located at the origin $\left( o
+    \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
+    $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
+    (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
+    distribution is symmetric around the $z$-axis. The innermost radius of
+    the magnetosphere (at the equatorial plane) coincides with the the
+    inner radius of the accretion disc. From the innermost part of the
+    accretion disc, the gas falls freely, moving along the magnetic field
+    onto the surface of the star. The wind density is enhaced toward
+    the polar directions to mimic the collimated wind structure of the
+    magneto-hydrodynamical simulations (e.g.~\citealt{krasnopolsky:2003}). }
+
+  \label{fig:config_dipolar}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Model configuration}
@@
 following subsections we describe the details of model components.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \begin{figure*}
-
-%%   \begin{center}
-
-%%     \includegraphics[%
-%%       scale=0.5]{figures/overview3.eps}
-
-%%   \end{center}
-
-%%   \caption{The basic model configuration. The system consists of four
-%%     components: (1)~the continuum source located at the origin $\left( o
-%%     \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-%%     $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
-%%     (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
-%%     distribution is symmetric around the $z$-axis. The innermost radius of
-%%     the magnetosphere (at the equatorial plane) coincides with the the
-%%     inner radius of the accretion disc. From the innermost part of the
-%%     accretion disc, the gas falls freely, moving along the magnetic field
-%%     onto the surface of the star. The bipolar wind starts from just
-%%     outside the largest radius 
-%%     ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
-
-%%   \label{fig:config_dipolar}
-
-%% \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      scale=0.3]{figures/overview3_alt.eps}
-
-  \end{center}
-
-  \caption{The basic model configuration. The system consists of four
-    components: (1)~the continuum source located at the origin $\left( o
-    \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-    $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
-    (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
-    distribution is symmetric around the $z$-axis. The innermost radius of
-    the magnetosphere (at the equatorial plane) coincides with the the
-    inner radius of the accretion disc. From the innermost part of the
-    accretion disc, the gas falls freely, moving along the magnetic field
-    onto the surface of the star. The wind density is enhaced toward
-    the polar directions to mimic the collimated wind structure of the
-    magneto-hydrodynamical simulations (e.g.~\citealt{krasnopolsky:2003}). }
-
-  \label{fig:config_dipolar}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 outflow is collimated along the rotational axes (a model similar to
-that of \citealt{krasnopolsky:2003} in large scale, $>10$~au). The
+that of \citet{krasnopolsky:2003} in large scale, $>10$~au). The
 second model is based on the disc-wind paradigm, in which the density
@@
 \label{sub:wind_jet}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+  \begin{center}
+
+    \begin{tabular}{cc}
+      \includegraphics[%
+	clip,
+	scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
+      \includegraphics[%
+	clip,
+	scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
+    \end{tabular}
+
+  \end{center}
+  \caption{The dependency of the bipolar wind velocity and density
+    structure on the wind acceleration parameter $\beta$. The radial
+    component of the wind velocity
+    (equation~\ref{eq:wind_velocity_radial_part}) in polar direction,
+    $\theta = 0$ as a function of radius is shown on the left. The wind
+    density (equation~\ref{eq:wind_density_final} along polar direction as
+    a function of radius is shown on the right. For all $\beta$ values, the
+    density is normalised to the density at the base of the wind in polar
+    direction, i.e. $\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.  The
+    smaller the value of $\beta$, the faster the acceleration of the
+    wind. For the radii $r/R_{\mathrm{mo}} < 10$, both velocity and
+    density are sensitive to the value of $\beta$. For all $\beta$ values,
+    the radial velocity of the wind reaches the terminal velocity ($\sim
+    210\,\kmps$) by $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity
+    $V_{0}=10\,\kmps$, which approximately corresponds to the thermal
+    velocity of a hydrogen atom at 7500~K, is used for all $v_{r}$
+    plots.}
+
+  \label{fig:wind_vr_rho}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-
-  \begin{center}
-
-    \begin{tabular}{cc}
-      \includegraphics[%
-	clip,
-	scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
-      \includegraphics[%
-	clip,
-	scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
-    \end{tabular}
-
-  \end{center}
-  \caption{The dependency of the bipolar wind velocity and density
-    structure on the wind acceleration parameter $\beta$. The radial
-    component of the wind velocity
-    (equation~\ref{eq:wind_velocity_radial_part}) in polar direction,
-    $\theta = 0$ as a function of radius is shown on the left. The wind
-    density (equation~\ref{eq:wind_density_final} along polar direction as
-    a function of radius is shown on the right. For all $\beta$ values, the
-    density is normalised to the density at the base of the wind in polar
-    direction, i.e. $\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.  The
-    smaller the value of $\beta$, the faster the acceleration of the
-    wind. For the radii $r/R_{\mathrm{mo}} < 10$, both velocity and
-    density are sensitive to the value of $\beta$. For all $\beta$ values,
-    the radial velocity of the wind reaches the terminal velocity ($\sim
-    210\,\kmps$) by $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity
-    $V_{0}=10\,\kmps$, which approximately corresponds to the thermal
-    velocity of a hydrogen atom at 7500~K, is used for all $v_{r}$
-    plots.}
-
-  \label{fig:wind_vr_rho}
-
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsubsection{The disc wind}
@@
 \label{sub:Alternative-model-disc-wind}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      scale=0.32]{figures/discwind.eps}
-
-  \end{center}
-
-  \caption{Basic model configuration of the disc-wind, magnetosphere
-    hybrid model. The system consist of four components: (1)~the continuum
-    source located at the origin $\left( o \right)$ of the cartesian
-    coordinates $\left(x,y,z\right)$ -- the $y$-axis is into the paper,
-    (2)~the magnetospheric accretion flow, (3)~the disc wind, and
-    (4)~the geometrically thin (but opaque) accretion disc. The disc wind
-    originates from the disc surface between $w_{i}=R_{wi}$ and
-    $w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
-    lines diverges, are placed at distance $d$ above and below the
-    star. The degree of wind collimation is controlled by changing the
-    value of $d$. }
-
-  \label{fig:config_discwind}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 to $1$~au as in \citealt{krasnopolsky:2003}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      scale=0.32]{figures/discwind.eps}
+
+  \end{center}
+
+  \caption{Basic model configuration of the disc-wind, magnetosphere
+    hybrid model. The system consist of four components: (1)~the continuum
+    source located at the origin $\left( o \right)$ of the cartesian
+    coordinates $\left(x,y,z\right)$ -- the $y$-axis is into the paper,
+    (2)~the magnetospheric accretion flow, (3)~the disc wind, and
+    (4)~the geometrically thin (but opaque) accretion disc. The disc wind
+    originates from the disc surface between $w_{i}=R_{wi}$ and
+    $w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
+    lines diverges, are placed at distance $d$ above and below the
+    star. The degree of wind collimation is controlled by changing the
+    value of $d$. }
+
+  \label{fig:config_discwind}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2006-01-24 TTau_Halpha/kurosawa.tex
cut out bipolar stuff - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@630 25464f21-6099-402c-b30a-640f1d40d38b

@@
 therefore employ a circumstellar structure that includes both
-magnetospheric accretion and a wind. We adopt two kinematic models for
-the outflow, a generic bipolar wind and a disc wind. We perform
+magnetospheric accretion and a disc wind.  We perform
 systematic investigations of the model parameters for the wind and the
@@
 conditions which lead to the types of profiles seen in
-observations. We find that both wind models can reproduce the wide
+observations. We find that the hybrid models can reproduce the wide
 range profile types seen is observations, and that the most common
@@
 space. Conversely, the most infrequently observed profile morphologies
-require a very specific set of models parameters.  Although a
-particular outflow model (bipolar or disc-wind) is not
-well-constrained by a single line profile observations, we find that
-the inclination dependence of the line equivalent width predicted by
-the bipolar wind model agree with trends seen in the observation, but
-the disc-wind model does not. Using the model results, we examine the
+require a very specific set of models parameters.  We investigate the
+wind contribution to the line profile as a function of model parameters, and
+examine the reliability of H$\alpha$ as a mass accretion diagnostic.
+Finally, we examine the
 H$\alpha$ spectroscopic classification used by Reipurth et.~al, and
@@
 
-%Prior to the MA paradigm, many alternative models had
-%been considered to explain the observed spectroscopic features mentioned
-%above. For example, (1)~an Alfv\'{e}n wave-driven wind model
-%(e.g.~\citealt{decampli:1981}; \citealt*{hartmann:1982}), (2)~a turbulent
-%boundary layer (between the accretion disc and stellar surface) model
-%(e.g.~\citealt{bertout:1988}; \citealt{basri:1989}), (3)~a chromospheric
-%model (e.g.~\citealt*{calvet:1984}), and (4)~a disc wind model (e.g.
-%\citealt*{calvet:1992b}; \citealt{kwan:1995}).
-
 The main aim of this paper is to find a simple kinematic model which
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \begin{figure*}
-
-%%   \begin{center}
-
-%%     \includegraphics[%
-%%       scale=0.5]{figures/overview3.eps}
-
-%%   \end{center}
-
-%%   \caption{The basic model configuration. The system consists of four
-%%     components: (1)~the continuum source located at the origin $\left( o
-%%     \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-%%     $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
-%%     (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
-%%     distribution is symmetric around the $z$-axis. The innermost radius of
-%%     the magnetosphere (at the equatorial plane) coincides with the the
-%%     inner radius of the accretion disc. From the innermost part of the
-%%     accretion disc, the gas falls freely, moving along the magnetic field
-%%     onto the surface of the star. The bipolar wind starts from just
-%%     outside the largest radius 
-%%     ($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }
-
-%%   \label{fig:config_dipolar}
-
-%% \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      scale=0.3]{figures/overview3_alt.eps}
-
-  \end{center}
-
-  \caption{The basic model configuration. The system consists of four
-    components: (1)~the continuum source located at the origin $\left( o
-    \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
-    $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
-    (3)~the bipolar wind outflow, and (4)~the accretion disc. The density
-    distribution is symmetric around the $z$-axis. The innermost radius of
-    the magnetosphere (at the equatorial plane) coincides with the the
-    inner radius of the accretion disc. From the innermost part of the
-    accretion disc, the gas falls freely, moving along the magnetic field
-    onto the surface of the star. The wind density is enhaced toward
-    the polar directions to mimic the collimated wind structure of the
-    magneto-hydrodynamical simulations (e.g.~\citealt{krasnopolsky:2003}). }
-
-  \label{fig:config_dipolar}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%
 
@@
 continuum source, (2)~the magnetospheric accretion flow, (3)~the wind
-outflow, and (4)~the accretion disc. Fig.~\ref{fig:config_dipolar}
+outflow, and (4)~the accretion disc. Fig.~\ref{fig:config_discwind}
 depicts the relative location of the regions in the model space.  The
@@
 
-\subsection{Outflow geometries}
+\subsection{The disc-wind outflow geometru}
+\label{sub:wind_jet}
 
@@
 reviews on the jet/wind-disc connection can be found in
-\citet{koenigl:2000} and \citet{pudritz:2005}.
-
-Clearly there are several alternative outflow scenarios. Here we adopt
-two simple kinematical models which broadly represent the results of
-MHD simulations. The first is a bipolar wind model, in which the
-outflow is collimated along the rotational axes (a model similar to
-that of \citet{krasnopolsky:2003} in large scale, $>10$~au). The
-second model is based on the disc-wind paradigm, in which the density
-of the outflow increases towards the equatorial plane. The difference
-in latitudinal density structure between the two outflow models should
-provide an indication as to whether line profiles alone can be used to
-constrain the outflow geometry. In the following sections we present
-details of the two outflow structures.
-
-\subsubsection{The bipolar wind}
-
-\label{sub:wind_jet}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-
-  \begin{center}
-
-    \begin{tabular}{cc}
-      \includegraphics[%
-	clip,
-	scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
-      \includegraphics[%
-	clip,
-	scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
-    \end{tabular}
-
-  \end{center}
-  \caption{The dependency of the bipolar wind velocity and density
-    structure on the wind acceleration parameter $\beta$. The radial
-    component of the wind velocity
-    (equation~\ref{eq:wind_velocity_radial_part}) in polar direction,
-    $\theta = 0$ as a function of radius is shown on the left. The wind
-    density (equation~\ref{eq:wind_density_final} along polar direction as
-    a function of radius is shown on the right. For all $\beta$ values, the
-    density is normalised to the density at the base of the wind in polar
-    direction, i.e. $\rho_0 = \rho\left(R_\mathrm{mo},0\right)$.  The
-    smaller the value of $\beta$, the faster the acceleration of the
-    wind. For the radii $r/R_{\mathrm{mo}} < 10$, both velocity and
-    density are sensitive to the value of $\beta$. For all $\beta$ values,
-    the radial velocity of the wind reaches the terminal velocity ($\sim
-    210\,\kmps$) by $r/R_{\mathrm{mo}} \sim 1000$. The initial velocity
-    $V_{0}=10\,\kmps$, which approximately corresponds to the thermal
-    velocity of a hydrogen atom at 7500~K, is used for all $v_{r}$
-    plots.}
-
-  \label{fig:wind_vr_rho}
-
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In a similar fashion to the simple model of \citet{appenzeller:2005},
-the following parametrisation of collimated bipolar wind (region 3 in
-Fig.~\ref{fig:config_dipolar}) is adopted. The wind velocity field,
-$\boldsymbol{v}_{\mathrm{wind}}$, consists of radial and azimuthal
-components which depend on the spherical coordinates $r$ and
-$\theta$. The radial component $v_{r}\left(r\right)$ is assumed to
-follow the classical beta-velocity law \citep[c.f.][]{castor:1979},
-and the azimuthal component $v_{\phi}$ is assumed to be a constant
-fraction ($\gamma$) of the Keplerian velocity for a given distance
-($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:
-\begin{equation}
-     \boldsymbol{v}_{\mathrm{wind}}  = 
-     v_{r}\hat{\boldsymbol{r}}+v_{\phi}\hat{\boldsymbol{\bphi}}
-  \label{eq:wind_velocity_def}
-\end{equation}
-where 
-\begin{equation}
-   v_{r}\left(r\right) =
-   v_{r0}+\left(v_{\infty}-v_{r0}\right)\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,
-   \label{eq:wind_velocity_radial_part}
-\end{equation}
-and
-\begin{equation}
-      v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,.
-   \label{eq:wind_velocity_azimuth_part}
-\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$. This
-naturally leads to a density discontinuity, but allows a simple
-parameterisation of the wind whereas a self-consistent interface
-between the magnetosphere and wind would require a full MHD
-calculation that is beyond the scope of this paper. The range of polar
-angle for the wind is restricted to
-$\theta>\left|\theta_{\mathrm{disc}}\right|$ where
-$\theta_{\mathrm{disc}}$ is the opening angle of the accretion
-disc. $v_{r0}$ is the small radial velocity at the base of the wind
-($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$
-which is approximately equal to the thermal velocity of hydrogen with
-$T=7500\,\mathrm{K}$. Following \citet{appenzeller:2005},
-$\gamma=0.05$ is adopted. The dependency of $v_{r}$ in polar direction
-($\theta=0$) on the values of wind acceleration parameter $\beta$ is
-shown in Figure~\ref{fig:wind_vr_rho}. All other parameters describing
-the wind are fixed as the reference values given in
-Table~\ref{tab:std_parameters}.
-
-The density of the wind is assumed to be axi-symmetric and
-separable in $r$ and $\theta$, 
-\begin{equation}
-    \rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)
-    \label{eq:wind_density_def}
-\end{equation}
-with 
-\begin{equation}
-    F\left(\theta\right)=n\,\cos^{b}\theta
-    \label{eq:wind_density_theta}
-\end{equation}
-where $b$ is normally a positive even number (for density symmetric
-about the equatorial plane), and $n$ is the angular normalisation
-constant. For $b=0$, the wind is spherically symmetric except for
-the parts disrupted by the accretion disc. The larger the value of
-$b$, the higher the degree of the collimation. By integrating equation~\ref{eq:wind_density_theta}
-over angles and normalising the integral to $4\pi$, one finds 
-\begin{equation}
-  n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.
-  \label{eq:wind_density_theta_norm}
-\end{equation}
-Assuming the total mass-loss rate via the wind is
-$\dot{M}_{\mathrm{wind}}$ and the mass-flux is constant, the radial
-part of the density function is reduced to
-$P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi
-r^{2}v_{r}\left(r\right)\right]^{-1}$;
-hence, equation~\ref{eq:wind_density_def} becomes 
-\begin{equation}
-  \rho\left(r,\theta\right) = 
-  \frac{n\,\dot{M}_{\mathrm{wind}}\,\cos^{b}\theta}{4\pi r^{2}\,
-    v_{r}\left(r\right)}\,.
-  \label{eq:wind_density_final}
-\end{equation}
-For a given mass-accretion rate, the wind mass-loss rate in our
-typical model is assigned from the ratio of mass-loss to
-mass-accretion rate
-$\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$, a value
-indicated by both observations and MHD calculations
-(e.g. \citealt{koenigl:2000}).  Figure~\ref{fig:wind_vr_rho} shows the
-density along a streamline in the polar direction ($\theta=0$), for
-different values of $\beta$ with all other parameters fixed at the
-reference values (Table~\ref{tab:std_parameters}).  The density is
-relatively sensitive to the value of $\beta$ for $r<10\,
-R_{\mathrm{mo}}$.
-
-\subsubsection{The disc wind}
-
-\label{sub:Alternative-model-disc-wind}
+\citet{koenigl:2000} and \citet{pudritz:2005}. Clearly there are several alternative outflow scenarios. Here we adopt
+a simple kinematical model, based on the disc-wind paradigm, which broadly represents the results of
+MHD simulations,
 
@@
 
-\subsection{Bipolar wind only models}
-
-\label{sub:model-wind}
-
-As mentioned above, the MA model alone
-cannot explain the observations. As an
-alternative model, we now examine formation of H$\alpha$ in a simple
-bipolar wind as described in section \ref{sub:wind_jet}. The basic
-wind model parameters introduced earlier are $\gamma$, $\beta$,
-$v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$ and
-$\dot{M}_{\mathrm{wind}}$. We fix several of these parameters
-at plausible values:  $\gamma=0.05$, $v_{\infty}=210\,\kmps$
-\citep{appenzeller:2005} and
-$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-Further, the angular extent of the wind (the opening angle of the
-wind) is assumed to be $\theta_{\mathrm{wind}}=80^{\circ}$. The degree
-of collimation is initially chosen to be $b=4$, i.e. the ratio of the
-density in polar direction to the density at the edge of the wind
-closest to the accretion disc is about
-$\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$
-Although the line is potentially
-sensitive to the temperature structure of the wind, determination of a
-self-consistent wind temperature is beyond the scope of this
-paper. Readers are refereed to \citet{hartmann:1982} in which the wind
-temperature structure is determined by balancing the radiative cooling
-rate (assuming optically thin) with the MHD wave heating rate.
-We pragmatically assume that the wind is isothermal at $T_{\mathrm{wind}}$.
-
-Initially we examine the characteristics of the
-H$\alpha$ profile  as a function of the wind acceleration parameter
-$\beta$ and the isothermal wind temperature
-$T_{\mathrm{wind}}$.  Figure~\ref{fig:atlas_wind_model} shows profiles computed at  $i=55^{\circ}$
- for a range of wind temperatures
-between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and  $\beta$ between $0.2$ and $2.0$.
-
-Classical P~Cygni profiles are prominent
-in the models with lower values of $T_{\mathrm{wind}}$ and $\beta$
-(a colder and faster accelerating wind). As the value of $\beta$
-increases, the position of the blue-shifted absorption component moves
-toward the line centre -- this can be seen clearly in the
-$T_{\mathrm{wind}}=7000\,\mathrm{K}$ models. The velocity position
- of the absorption component of the fastest accelerating wind
-($\beta=0.2$) is almost at the terminal velocity ($v_{\infty}\sim
-210\,\kmps$), that for the slowest wind acceleration model
-($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).
-
- As
-one can see in Figure~\ref{fig:wind_vr_rho}, the column density of the
-gas moving at $v_{\infty}$ increases as the wind acceleration becomes
-larger since the gas moving at $v_{\infty}$ becomes closer to the
-photosphere. At the location where the absorption occurs, the gas is
-moving faster for the models with the faster wind acceleration models;
-hence, the location of the absorption component is bluer as $\beta$
-becomes smaller (as the wind acceleration faster). The figure also
-shows that the intensity of the emission component increases as
-$\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
-because the density near the photosphere increases as the value of
-$\beta$ increases (Figure~\ref{fig:wind_vr_rho}); hence, the
-emissivity of increases. Unlike the magnetospheric accretion only
-models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
-profiles are not seen here, nor the blue-ward asymmetry. Because of
-the absorption component in P~Cygni profile, most of the profiles show
-red-ward asymmetry except for the low temperature wind models with
-high inclinations (not shown here).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.9]{figures/atlas_ha_i55_wind_only_final.eps}
-
-  \end{center}
-
-  \caption{H$\alpha$ model profiles computed with wide ranges of the
-    isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind
-    acceleration rate ($\beta$). The profiles are computed with the wind
-    component only (no magnetospheric accretion flow or accretion
-    disc). The `reference' model parameters (Table~\ref{tab:std_parameters}) are
-    applied. The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$),
-    the inclination ($i$) and the degree of columniation ($b$) are
-    fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$, $55^{\circ}$ and
-    $4.0$\, respectively. The temperature (indicated along the vertical
-    axis) of the model increases from top to bottom, and the wind
-    acceleration rate increases from left to right. The P~Cygni profile
-    are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow
-    acceleration) models.  The position of the absorption the component
-    moves toward the line centre as $\beta$ increases. The effect of
-    line broadening becomes more prominent for higher $T_\mathrm{wind}$
-    and higher $\beta$ models.}
-
-  \label{fig:atlas_wind_model}
-
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The dependency of the profile on the wind anisotropy parameter $b$
-is demonstrated in Figure~\ref{fig:effect_wind_b_param}. Three models
-presented in the figure have the same mass-loss rate ($10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$),
-and are computed at inclination angle $i=55^{\circ}$. The P~Cygni
-profile feature becomes more prominent, and the line flux becomes
-smaller as the wind becomes more isotropic (smaller $b$ value). For
-a fixed mass-loss rate, the column density of along the line of a
-sight to the observer at a medium inclination angle (e.g.~$i=55^{\circ}$)
-increases as $b$ decreases (c.f.~equation~\ref{eq:wind_density_final});
-hence, causing more absorption. Further more, the value of the highest
-density in the wind becomes smaller for a smaller $b$ model. As the
-wind becomes more isotropic, the material in the
-polar direction has to be spread in the wider angular angles. This
-results in a smaller highest density region in the wind; hence the
-smaller line emissivity. For the same reason, the emission in the
-wings is weaker for the model smaller $b$ value. We also note that
-the asymmetry around the line centre decreases as the wind becomes
-more isotropic.
-
-The effect of varying the wind mass-loss rate is shown in Figure~\ref{fig:effect_wind_mdot}.
-The line is very sensitive to the mass-loss rate. With all other parameters
-fixed constant, $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor
-of the wind density (equation~\ref{eq:wind_density_final}). The
-important processes in forming H$\alpha$ emission are the
-recombination process and the subsequent downward transition to $n=3$
-level. Assuming the ionisation fraction remains constant, the
-recombination rate is proportional to the square 
-of wind density. We have found the line flux of the models in the
-figure is approximately proportional to the square of the mass-loss
-rate. This very sensitive nature of H$\alpha$ would make the line
-a good candidate for a mass-loss rate indicator; however, without
-solving the ambiguity of the emission component from the magnetospheric
-accretion flow and the wind, and without knowing the detailed temperature
-structure of the wind, it could provide us a misleading a mass-loss
-rate estimate of a T Tauri star.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.62]{figures/windonly_B_effect2.eps}
-
-  \end{center}
-
-  \caption{The effect of wind collimation. The line profiles computed
-    with with $\left(T_{\mathrm{wind}},~\beta \right) = \left(
-    9000\Kelvin, 0.5\right)$ for the wind anisotropy parameter $b=0, 2, 4$
-    are shown in dashed, dotted, and solid respectively.  All the other
-    parameters are same as in Figure~\ref{fig:atlas_wind_model}.  The
-    P~Cygni profile feature becomes prominent for the spherical wind model
-    since the column density of along the line of a sight of the observer
-    at a mid inclination angle ($i=55^{\circ}$) increases for lower $b$
-    values for a fixed mass-loss rate of the wind. The blue-ward asymmetry
-    is still present even in the isotropic wind case ($b=0$).}
-
-  \label{fig:effect_wind_b_param}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.45]{figures/windonly_mdot_effect.eps}
-
-  \end{center}
-
-  \caption{The effect of the wind mass-loss rate.  The profiles computed
-    with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin,
-    0.5\right)$, and $\dot{M}_{\mathrm{wind}} = 1.0 \times
-    10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (solid), $0.5 \times
-    10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dotted), and $0.25 \times
-    10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed) are shown above. The
-    models are computed with only the wind component (no magnetospheric
-    accretion flow or accretion disc). With all other parameter fixed
-    constant, the mass-loss rate behaves as a scaling factor for the wind
-    density (equation~\ref{eq:wind_density_final}).}
-
-  \label{fig:effect_wind_mdot}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Disc $+$bipolar wind}
-
-\label{sub:model-disc-wind}
-
-Next, we examine the effect of the size of the inner radius of the
-disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_alpha_disc}
-shows the wind emission profiles computed with and without the accretion
-disc at $i=55^{\circ}$. The H$\alpha$ images (projected on to the
-plane perpendicular to the observer at the location of the star) are
-also shown in the same figure. Both models use the same parameters
-as in Figure~\ref{fig:atlas_wind_model}, but with $\beta=0.5$ and
-$T_{\mathrm{wind}}=9000\,\mathrm{K}$). The model without the disc
-can be also considered as a model with a large inner radius of the
-accretion disc, in which none of the wind emission region is blocked
-by the disc --- provided the inclination angle is not high and
-the disc is not or slightly flared.
-
-The bipolar nature of the wind is clearly seen in the images. In this
-example, the most of the wind emission occurs within a few to a several
-(depending mainly on the value of $\beta$) stellar radii from the
-star. The figure also shows that the accretion disc blocking the wind
-emission from the bottom half of the wind which is moving away from
-the observer. This results in the reduction of the wind emission in
-the red wing. The image (mid panel) also shows that the accretion
-disc is not occulting the stellar disc at this inclination; therefore,
-the ratio of the wind emission flux to the photospherical continuum
-flux becomes slightly smaller for the model with the disc. This results
-in the reduction in the peak flux and the flux in the wings in the
-normalised profile shape. If the disc becomes more flared (if the
-opening angle exceeds $45^{\circ}$at the outer edge of the accretion
-disc), the occultation of the stellar disc by the accretion could
-be seen at this inclination angle. Although it is not shown here,
-the continuum level of the two models are identical. For the models
-with $i<30^{\circ}$, the presence of the disc has little/no effect
-on the profile shapes. In the figures, the extent of the H$\alpha$
-emission is smaller ($\sim 0.2\,\mathrm{au}$ or $\sim 20\, R_{*}$)
-compared to the spectro-astrometric observations of \citet{takami:2003}
-for RU~Lup and CS Cha which show 1--5~au scale outflows%
-\footnote{\citet{takami:2003} their observation also show that some objects
-(e.g~Z CMa and AS~353A) displaying the outflows of larger scale
-($>50\,\mathrm{au}$); however, this could be formed by shocks rather
-than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
-(e.g.~\citealt{shang:2002}). %
-}; however, the extent of the line emission region becomes slightly
-larger ($\sim0.4$~au) if a slower wind acceleration rate ( $\beta=4$)
-is used.
-
-Although not shown here, we have also computed the H$\alpha$ profiles
-from the combination of the collimated wind and the accretion disc
-($R_{\mathrm{di}}=2.2R_{*}$ and $R_{\mathrm{do}}=100\,\mathrm{au}$)
-for the same range of $\beta$ and $T_{\mathrm{max}}$ values used in
-Figure~\ref{fig:atlas_wind_model}.  As expected
-(c.f.~Figure~\ref{fig:effect_alpha_disc}), the models show the
-decrease in the flux in the blue wing when compared to the flux of the
-same model computed without the accretion disc.  The overall behaviour
-of the line profile shapes as functions of $\beta$ and
-$T_{\mathrm{wind}}$ are very similar to that for the models without
-the accretion disc.  A significant reduction of the flux in the red
-wing is seen in the wind model with the accretion disc when compared
-with the wind only model. The wings appear to be weaker in these
-models compared to the wind only models because the ratio of the wind
-emission flux to the continuum flux is lower.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-
-  \begin{center}
-
-    \begin{tabular}{ccc}
-      \includegraphics[%
-	clip,
-	scale=0.3]{figures/disc_nodisc_compare.eps}&
-      \includegraphics[%
-	scale=0.3,
-	angle=270,
-	origin=lt]{figures/wind_thindisc.eps}&
-      \includegraphics[%
-	scale=0.3,
-	angle=270,
-	origin=lt]{figures/wind_nodisc.eps}\tabularnewline
-    \end{tabular}
-
-  \end{center}
-
-  \caption{A comparison of the wind models with and without the
-    optically-thick and geometrically-thin disc.  The latter can be also
-    equivalent to a model with a large inner radius of the accretion disc
-    in which none of the wind emission region is not blocked provided the
-    inclination is moderate. The left panel shows the profile computed
-    with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} =
-    9000~\mathrm{K}$ (see text for other parameters used). The flux in the
-    red wing of the line profile from the model with the disc (solid) is
-    greatly reduced by the presence of the accretion disc compared to that
-    from the model without the disc (dashed).  The peak flux and the flux
-    in the wings are also reduced in the model with the disc because the
-    disc does block the wind emission region, but none of the stellar
-    disc, i.e. the continuum flux level is unchanged.  The H$\alpha$
-    image (project in the plane of the observer) for the model with the
-    disc (middle panel) and that for the model without (right plane) are
-    also shown. The image flux is computed by integrating the specific
-    flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$. The
-    flux is in an arbitrary units and on a logarithmic (base $10$) scale. }
-
-  \label{fig:effect_alpha_disc}
-
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.45]{figures/summary.eps}
-
-  \end{center}
-
-  \caption{A comparison of the profiles computed with the magnetosphere,
-    the wind, the disc, and their combinations. The model configurations 
-    used above are: (1)~magnetosphere only (dash), (2)~wind and disc
-    (dot), and (3)~disc, wind and magnetosphere (solid).  The parameters
-    used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
-    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$,
-    $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$,
-    $T_{\mathrm{wind}}=9000\,\Kelvin$, and $\beta=0.5$. The profile for
-    the case 3 is can be understood as a simple flux sum of the profiles
-    from case 1 and 2.}
-
-  \label{fig:summary_beta05_t8000}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magnetosphere $+$ disc $+$bipolar wind}
-
-\label{sub:model-acc-disc-wind}
-
-We examine the characteristics of the line profiles arising from the
-combination of the magnetospheric accretion flow, the wind, and the
-accretion disc. For simplicity, the parameters for the magnetosphere
-($T_{\mathrm{max}}=7500\,\mathrm{K}$ and
-$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ are
-fixed as in Figure~\ref{fig:atlas_acc_models}), and the wind mass-loss
-rate, the isothermal wind temperature and the wind anisotropy
-parameter to $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,
-yr^{-1}}$
-(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$),
-$T_{\mathrm{wind}}$ and $b=4$ respectively. The profile computed for
-$i=55^{\circ}$ is given in Figure~\ref{fig:summary_beta05_t8000},
-along with the profile computed with the magnetosphere only and that
-with the wind plus accretion disc configurations for a comparison. As
-one can see from the figure, the profile computed for the
-disc--wind--magnetosphere hybrid model can be understood as a simple
-flux sum of the magnetospheric component and the wind component. In
-this example, the wind causes the absorption of the blue side of the
-profile, and it adds extra flux around the line centre. As seen
-before, the presence of the disc causes a reduction in the red side of
-the profile since the emission from the receding gas is blocked by the
-disc. The resulting profile appears to be narrower than that of the
-magnetosphere model.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.9]{figures/atlas_ha_i55_wind_acc_alpha_final2.eps}
-
-  \end{center}
-
-  \caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models
-    include the magnetospheric accretion flow (with
-    $T_{\mathrm{\max}}=7500~\mathrm{K}$ and
-    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$),  and the
-    accretion disc. The mass-loss rate of the wind is
-    $\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$. A
-    relatively small mass-loss rate is chosen to avoid unrealistically
-    strong P-Cyg absorption component (see text in
-    section~\ref{sub:model-acc-disc-wind} and
-    Figure~\ref{fig:effect_mdot_disc_wind_acc}).  For a comparison, the
-    profile computed with only the magnetospheric accretion flow (dotted)
-    is overlayed. All the profiles are computed at the inclination angle
-    $i=55^{\circ}$. As $\beta$ becomes larger, the position of the wind
-    absorption component moves toward the line centre. Although little
-    wind emission is seen in this temperature range, it becomes more
-    important in a model with a higher temperature and a larger wind
-    mass-loss rate. The profiles resembles the observed H$\alpha$ emission
-    profiles affected by the wind.}
-
-  \label{fig:atlas_disc_wind_acc_model}
-
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The effect of changing the ratio of the wind mass-loss rate to
-mass-accretion rate
-($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
-in Figure~\ref{fig:effect_mdot_disc_wind_acc}. With a fixed value of
-mass-accretion rate
-($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
-mass-loss rate is varied. The figure shows that as $\mu$ increases the
-P-Cygni absorption deepens, and the position of minimum flux in the
-absorption trough appears to move blue-ward.  On the other hand, the
-emission component becomes stronger as $\mu$ increases. With this
-combination of the parameters for the magnetosphere and the wind, the
-absorption component tends to be too strong for the models $\mu>0.025$
-(with this model configuration), at all inclinations (not shown here),
-compared with the observed H$\alpha$ profiles
-(e.g.\citealt{reipurth:1996}; \citealt{alencar:2000}).
-%As we will see later (section~\ref{fig:ttau_model}),
-%$\mu$ can be as large as $\sim0.3$ with different parameters of
-%the magnetosphere.
-
-Again, the H$\alpha$ profiles with the same range of the wind
-temperature ($T_{\mathrm{wind}}$) and the wind acceleration parameter
-($\beta$) used in Figure~\ref{fig:atlas_wind_model} are computed, but
-this time with $\mu=0.01$.  The parameters of the magnetosphere are
-fixed as in Figure~\ref{fig:acc_inclination_effect}. The results are
-shown in Figure~\ref{fig:atlas_disc_wind_acc_model} along with the
-model with only the magnetosphere for a comparison. A relatively small
-value of $\mu$ is chosen to avoid absorption component of the P-Cyg
-profile becoming too strong, as seen in
-Figure~\ref{fig:effect_mdot_disc_wind_acc}.  In general, even with
-small values of the anisotropy parameter ($b=0$ and $2$), the
-absorption component is found to be too strong when $\mu=0.1$ is used
-with this combination of the magnetosphere and the wind. The figure
-shows that the position of the wind absorption component moves toward
-the line centre as $\beta$ becomes larger.  Although little wind
-emission is seen in this temperature range, it becomes more important
-in a model with a higher temperature and a larger wind mass-loss
-rate. In fact, the model with $\beta=2.0$ and
-$T_{\mathrm{wind}}=9000\,\mathrm{K}$ displays a small amount of the
-wind emission at $V\sim50\,\mathrm{km\, s^{-1}}$.
-
-As seen in Figure~\ref{fig:summary_beta05_t8000}, the profiles shown
-here can be understood as the combination of the emission from the
-magnetosphere and the absorption of the flux by the wind component.
-In general, the emission from the accretion disc is negligible at
-H$\alpha$ wavelength, but the absorption of the continuum flux from
-the photosphere by the disc is important for predicting correct line
-strengths, especially at a high inclination.
-
-Although the profiles shown in
-Figure~\ref{fig:atlas_disc_wind_acc_model} are those at a single
-inclination angle ($i=55^{\circ}$), they are very similar to the most
-common types of H$\alpha$ profiles seen in the observations
-(e.g.~\citealt{reipurth:1996}). Apparently, this type of profile
-(affected by the blue-shifted absorption feature) cannot be explained
-by the magnetospheric accretion flow alone
-(e.g.~\citealt{muzerolle:2001}).  Comparison of the model profiles
-with different types of the observed H$\alpha$ profiles will be given
-in section~\ref{sub:Classification-scheme-proposed}.
 
@@
 
-\subsection{Which wind model?}
-
-\label{sub:Which-wind-model}
+\subsection{H$\alpha$ as a mass accretion diagnostic}
+
+\label{sub:ha-mass-accretion-diagnostic}
 

### 2006-01-25 TTau_Halpha/kurosawa.tex
Major change. Bipolar wind section removed. Additional material on the disc wind models to be inserted. Still not complete. (RK)
Cvs: ----------------------------------------------------------------------


git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@631 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+  \begin{center}
+
+    \includegraphics[%
+      scale=0.6]{figures/discwind.eps}
+
+  \end{center}
+
+  \caption{Basic model configuration of the disc-wind, magnetosphere
+    hybrid model. The system consist of four components: (1)~the
+    continuum source located at the origin $\left( o \right)$ of the
+    cartesian coordinates $\left(x,y,z\right)$ -- the $y$-axis is into
+    the paper, (2)~the magnetospheric accretion flow, (3)~the disc
+    wind, and (4)~the accretion disc. The disc wind originates from
+    the disc surface between $w_{i}=R_{\mathrm{wi}}$ and
+    $w_{i}=R_{\mathrm{wo}}$ where $w_{i}$ is the distance from the $z$
+    axis on the equatorial plane.  The wind source
+    points ($S$), from which the stream lines diverges, are placed at
+    distance $d$ above and below the star. The degree of wind
+    collimation is controlled by changing the value of $d$.}
+
+  \label{fig:config_discwind}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{The continuum source}
@@
 
-\begin{tabular}{lccccccccccc}
+\begin{tabular}{lccccccccc}
 \hline 
@@
 $\dot{M}_{\mathrm{wind}}$&
-$v_{\infty}$&
-$b$&
 $R_{\mathrm{di}}$&
@@
 $\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$[\mathrm{km\, s^{-1}}]$&
-$[-]$&
 $\left[R_{*}\right]$&
@@
 $10^{-8}$&
-$210$&
-$4.0$&
 $2.2$&
@@
 flow does not affect the underlying magnetic field itself. As shown
-in Fig.~\ref{fig:config_dipolar}, the innermost radius ($R_{\mathrm{mi}}$)
+in Fig.~\ref{ig:config_discwind} (region~2), the innermost radius ($R_{\mathrm{mi}}$)
 of the magnetosphere at the equatorial plane ($z=0$) is assigned
@@
 \end{equation}
-\citep*[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
-of the field point ($p$) in Fig.~\ref{fig:config_dipolar} in spherical
-coordinates, and $R_{\mathrm{m}}$ is the radial distance to the field
-line at the equatorial plane ($\theta=\pi/2$). The range of
-$R_{\mathrm{m}}$ is restricted between $R_{\mathrm{mi}}$ and
-$R_{\mathrm{mo}}$. Using the field geometry above and conservation of
+\citep*[see][]{ghosh:1977} where $r$, and $\theta$ are the radial and
+the polar component of a field point position vector in the accretion
+stream.  $R_{\mathrm{m}}$ is the radial distance to the field
+line at the equatorial plane ($\theta=\pi/2$), and its value is
+restricted between $R_{\mathrm{mi}}$ and 
+$R_{\mathrm{mo}}$ (Figure~\ref{fig:config_discwind}). 
+Using the field geometry above and conservation of
 energy, the velocity and the density of the accreting gas along the
@@
 
-\subsection{The disc-wind outflow geometru}
-\label{sub:wind_jet}
+\subsection{The disc wind}
+\label{sub:model-disc-wind}
 
@@
 radius of the magnetosphere ($R_{\mathrm{mo}}$) and the latter is set
-to $1$~au as in \citealt{krasnopolsky:2003}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      scale=0.32]{figures/discwind.eps}
-
-  \end{center}
-
-  \caption{Basic model configuration of the disc-wind, magnetosphere
-    hybrid model. The system consist of four components: (1)~the continuum
-    source located at the origin $\left( o \right)$ of the cartesian
-    coordinates $\left(x,y,z\right)$ -- the $y$-axis is into the paper,
-    (2)~the magnetospheric accretion flow, (3)~the disc wind, and
-    (4)~the geometrically thin (but opaque) accretion disc. The disc wind
-    originates from the disc surface between $w_{i}=R_{wi}$ and
-    $w_{i}=R_{wo}$.  The wind source points ($S$), from which the stream
-    lines diverges, are placed at distance $d$ above and below the
-    star. The degree of wind collimation is controlled by changing the
-    value of $d$. }
-
-  \label{fig:config_discwind}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+to $1$~au as in \citet{krasnopolsky:2003}.
 
@@
 normalising the value to the total mass-loss rate
-$\dot{M}_{\mathrm{dw}}$.
+$\dot{M}_{\mathrm{wind}}$.
 
@@
 surface along stream lines respectively. $R_{s}$ is the wind scale
-length (=10\, $R_{\mathrm{mi}}$, \citealt{long:2002}).
+length, and its value is set to 10~$R_{\mathrm{mi}}$ by following
+\citet{long:2002}).
 
@@
   \frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ 
-  \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}
+  \frac{d}{D\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}
   \label{eq:discwind-density}
 \end{equation} 
-where $Q$ and $\delta$ are the distance from the source point ($S$) to
+where $D$ and $\delta$ are the distance from the source point ($S$) to
 a point along the stream line and the angle between the stream line
-and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
+and the disc normal, respectively. Figure~\ref{fig:discwind_vr_rho}
 shows the density and the velocity components along the mid stream
@@
 equatorial plane. This corresponds to Region 4 in
-Fig.~\ref{fig:config_dipolar}.
+Fig.~\ref{fig:config_discwind}.
 
@@
 Keplerian.
+
+Because of the geometrical constraints imposed by the magnetosphere
+and the disc wind, the finite height of the $\alpha$ disc causes an
+undesirable interface problem at the boundary; hence, the inner part
+($R_{\mathrm{di}} < w < R_{\mathrm{wo}}$) of the disc is replaced by
+the geometrically thin (but opaque) disc. Since the emissivity of the
+disc at the optical wavelength is negligible and the disc scale height
+is relatively small in the inner part of disc, this replacement is
+reasonable.  On the other hand, the finite height of the disc at the
+outer part is important for determining the shape of the H$\alpha$
+profiles observed at high inclinations, as we will see in section~XXX.
 
@@
 10\,\AA\ cut-off \citep[e.g.][]{herbig:1988}.
-
-xxxx Changed xxxxx
-
 \citet{white:2003} empirically showed that the full width of H$\alpha$ at 10
@@
 inclination angle increases, as does the EW.  The line flux and the
-EWs decreases since the fraction of the accretion stream blocked by
-the photosphere increases as the inclination increase.
-
-xxxx Changed xxxxx
+EWs decrease mainly because the fraction of the accretion stream
+blocked by the photosphere increases as the inclination increases.
+The line EW in Figure~\ref{fig:acc_inclination_effect} changes from
+32\,\AA\, to 21\,\AA\, as the inclination changes from $10^\circ$ to
+$80^\circ$, i.e. the fractional change of 0.65.  On the other hand,
+the 10~per~cent width of the line changes from 290~$\kmps$ to
+470~$\kmps$; hence,
+the fractional change is 1.6.  The both values are relatively
+sensitive to the inclination angle.
 
 Because of the geometry of the
-magnetospheric accretion (c.f. Figure~\ref{fig:config_dipolar}) and of
+magnetospheric accretion (c.f. Figure~\ref{fig:config_discwind}) and of
 the presence of the gas with the highest velocity close to the stellar
@@
 only at the high inclination angles. This explains the wider
-appearance of the profile with $i=80^{\circ}$compared to the
+appearance of the profile with $i=80^{\circ}$ compared to the
 relatively narrow line appearance of the profile with
@@
 a blueward asymmetry caused by occultation of the accretion
-flow by the stellar photosphere (see also \citet{hartmann:1994} and
-\citet{muzerolle:2001}). However, \citealt{alencar:2000} (see their Fig.~9)
+flow by the stellar photosphere (see also \citealt{hartmann:1994};
+\citealt{muzerolle:2001}). However, \citealt{alencar:2000} (see their Fig.~9)
 found a substantial fraction
@@
 
-\subsection{The disc-wind model}
+\subsection{Disc-wind only models}
 
 \label{sub:result-discwind-knigge}
-
-In this section we examine profiles produced using our alternative
-kinematic model of the outflow: the disc wind. This type of outflow
-has been predicted by several MHD calculations (e.g. \citet{koenigl:2000};
- \citealt{krasnopolsky:2003}), and broadly consists of a wind with
-a latitudinal density-dependence with density increasing towards
-the equator (see~\ref{sub:model-disc-wind}), in contrast with the 
-bipolar stellar wind.
 
@@
      The wind mass-loss rate is fixed at
-    $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, and the line
+    $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, and the line
     profiles are computed with different combinations of the wind
     acceleration rate ($\beta$) and isothermal disc-wind temperature
-    ($T_{\mathrm{dw}}$). The wind emission grows as the values of
+    ($T_{\mathrm{wind}}$). The wind emission grows as the values of
     $\beta$ and $T_{\mathrm{wind}}$ increase.   As in the
@@
     ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
-    $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
     the emission from the magnetosphere dominates for the models with
-    smaller $\beta$ and $T_{\mathrm{dw}}$, the emission from the wind dominates the
-    profiles for models with larger $\beta$ and $T_{\mathrm{dw}}$.  The contribution
+    smaller $\beta$ and $T_{\mathrm{wind}}$, the emission from the wind dominates the
+    profiles for models with larger $\beta$ and $T_{\mathrm{wind}}$.  The contribution
     of the magnetosphere can be judged from the profiles computed with
@@
 
-Firstly, we consider the disc-wind models without the magnetosphere.
+In this section, we examine profiles produced using the 
+the disc wind outflow model described in
+section~\ref{sub:model-disc-wind}. This type of outflow 
+has been predicted by several MHD calculations (e.g. \citet{koenigl:2000};
+ \citealt{krasnopolsky:2003}), and broadly consists of a wind with
+its density increasing toward the equatorial plane.
+
+GEOMETRY? REFERENCE MODEL?
+
+The parameters used for the
+central star are as in section~\ref{sub:Continuum-Source}, and the
+disc-wind parameters are summarised in
+Table~\ref{tab:std_discwind_parameters}.
+
+Although the line is potentially
+sensitive to the temperature structure of the wind, determination of a
+self-consistent wind temperature is beyond the scope of this
+paper. Readers are refereed to \citet{hartmann:1982} in which the wind
+temperature structure is determined by balancing the radiative cooling
+rate (assuming optically thin) with the MHD wave heating rate.
+We pragmatically assume that the wind is isothermal at $T_{\mathrm{wind}}$.
+
+Initially we examine the characteristics of the
+H$\alpha$ profile  as a function of the wind acceleration parameter
+$\beta$ and the isothermal wind temperature
+$T_{\mathrm{wind}}$.  Figure~\ref{fig:atlas_discwind_only} shows profiles computed at  $i=55^{\circ}$
+ for a range of wind temperatures
+between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and  $\beta$ between $0.2$ and $2.0$.
+
+Classical P~Cygni profiles are prominent
+in the models with lower values of $T_{\mathrm{wind}}$ and $\beta$
+(a colder and faster accelerating wind). As the value of $\beta$
+increases, the position of the blue-shifted absorption component moves
+toward the line centre -- this can be seen clearly in the
+$T_{\mathrm{wind}}=7000\,\mathrm{K}$ models. The velocity position
+ of the absorption component of the fastest accelerating wind
+($\beta=0.2$) is almost at the terminal velocity ($v_{\infty}\sim
+210\,\kmps$), that for the slowest wind acceleration model
+($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).
+
+ As
+one can see in Figure~\ref{fig:wind_vr_rho}, the column density of the
+gas moving at $v_{\infty}$ increases as the wind acceleration becomes
+larger since the gas moving at $v_{\infty}$ becomes closer to the
+photosphere. At the location where the absorption occurs, the gas is
+moving faster for the models with the faster wind acceleration models;
+hence, the location of the absorption component is bluer as $\beta$
+becomes smaller (as the wind acceleration faster). The figure also
+shows that the intensity of the emission component increases as
+$\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
+because the density near the photosphere increases as the value of
+$\beta$ increases (Figure~\ref{fig:wind_vr_rho}); hence, the
+emissivity of increases. Unlike the magnetospheric accretion only
+models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
+profiles are not seen here, nor the blue-ward asymmetry. Because of
+the absorption component in P~Cygni profile, most of the profiles show
+red-ward asymmetry except for the low temperature wind models with
+high inclinations (not shown here).
+
+The effect of varying the wind mass-loss rate is shown in Figure~\ref{fig:effect_wind_mdot}.
+The line is very sensitive to the mass-loss rate. With all other parameters
+fixed constant, $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor
+of the wind density (equation~\ref{eq:wind_density_final}). The
+important processes in forming H$\alpha$ emission are the
+recombination process and the subsequent downward transition to $n=3$
+level. Assuming the ionisation fraction remains constant, the
+recombination rate is proportional to the square 
+of wind density. We have found the line flux of the models in the
+figure is approximately proportional to the square of the mass-loss
+rate. This very sensitive nature of H$\alpha$ would make the line
+a good candidate for a mass-loss rate indicator; however, without
+solving the ambiguity of the emission component from the magnetospheric
+accretion flow and the wind, and without knowing the detailed temperature
+structure of the wind, it could provide us a misleading a mass-loss
+rate estimate of a T Tauri star.
+
 Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
@@
 (c.f. Figure~\ref{fig:config_discwind}) for the same isothermal
-disc-wind temperature ($T_{\mathrm{dw}}$) and the wind acceleration
+disc-wind temperature ($T_{\mathrm{wind}}$) and the wind acceleration
 parameter ($\beta$) ranges used for the bipolar wind models
 (c.f. Figures~\ref{fig:atlas_wind_model} and
-\ref{fig:atlas_disc_wind_acc_model}).  The parameters used for the
-central star are as in section~\ref{sub:Continuum-Source}, and the
-disc-wind parameters are summarised in
-Table~\ref{tab:std_discwind_parameters}.  The figure shows that the
-wind emission increases as $\beta$ and $T_{\mathrm{dw}}$ increase. The
+\ref{fig:atlas_disc_wind_acc_model}).
+
+  The figure shows that the
+wind emission increases as $\beta$ and $T_{\mathrm{wind}}$ increase. The
 $\beta$ dependence arises simply because for large $\beta$ there is a
@@
 
+\subsection{Disc--wind--magnetosphere  hybrid models}
+
+\label{sub:result-discwind-hybrid}
+
 We now consider the models computed with a combination of the
@@
 The mass-loss rate of the disc wind is set to
-$\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$).
+$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+(i.e.~$\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.1$).
 Figure~\ref{fig:atlas_discwind_acc_model} shows the models profiles
@@
 increases.  The figure shows that in
-the models with smaller $\beta$ and $T_{\mathrm{dw}}$, the line
+the models with smaller $\beta$ and $T_{\mathrm{wind}}$, the line
 emission from the magnetosphere dominates, while this situation reverses for the
-models with larger $\beta$ and $T_{\mathrm{dw}}$. The model with
-$\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
+models with larger $\beta$ and $T_{\mathrm{wind}}$. The model with
+$\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
 results in an H$\alpha$ profile that is far too strong to be compatible
@@
 Although the models in Figure~\ref{fig:atlas_discwind_acc_model} are
-computed with limited ranges of  $T_{\mathrm{dw}}$ and $\beta$, the
+computed with limited ranges of  $T_{\mathrm{wind}}$ and $\beta$, the
 resulting profiles exhibit a wide variety of line profile shapes,
@@
 (in Figure~\ref{fig:atlas_discwind_acc_model}) give very similar profiles.
-
-xxxx paragraph below may need changing after new models are added xxxx
 
@@
 $R_{\mathrm{wo}}$&
-$\dot{M}_{\mathrm{dw}}$&
+$\dot{M}_{\mathrm{wind}}$&
 $p$&
@@
 are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
-$\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
+$\dot{M}_{\mathrm{wind}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
 
@@
 $T_{\mathrm{max}}$&
-$\dot{M}_{\mathrm{dw}}$&
-$T_{\mathrm{dw}}$&
+$\dot{M}_{\mathrm{wind}}$&
+$T_{\mathrm{wind}}$&
 $\beta$&
@@
 bipolar wind model in which the wind originates from the star itself
-(section~\ref{sub:wind_jet}; Figure~\ref{fig:config_dipolar}), and
+(section~\ref{sub:model-disc-wind}; Figure~\ref{fig:config_dipolar}), and
 (2)~the disc-wind model in which the wind originates from the inner

### 2006-01-25 TTau_Halpha/tmp.tex
Major change. Bipolar wind section removed. Additional material on the disc wind models to be inserted. Still not complete. (RK)
Cvs: ----------------------------------------------------------------------


git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@631 25464f21-6099-402c-b30a-640f1d40d38b

--- 2005-11-29 TTau_Halpha/tmp.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
+\documentclass[english,useAMS, usenatbib]{mn2e}
 \usepackage[T1]{fontenc}
 \usepackage[latin1]{inputenc}
-\setcounter{tocdepth}{3}
+\usepackage{times}
 \usepackage{graphicx}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{lscape}
-\usepackage{times}
 
@@
 \begin{document}
-\title[On H-$\alpha$ formation of T Tauri stars]{On formation of H-$\alpha$ from classical T Tauri stars: the disc, wind, and magnetospheric-accretion hybrid model}
-
-\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries and Neil H. Symington\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}
+\title[On the formation of H$\alpha$ around classical T Tauri
+  stars]{On the formation of H$\alpha$ line emission around classical T Tauri stars}
+
+\author[R. Kurosawa et\,al.]{Ryuichi
+  Kurosawa$^1$\thanks{E-mail:rk@astro.ex.ac.uk}, Tim J. Harries$^1$
+  and Neil H.
+Symington$^2$\\ $^1$School of Physics, University of Exeter, Stocker Road, Exeter EX4~4QL.
+\\ $^2$School of Physics and Astronomy, University of St.
+Andrews, North Haugh, St.
+Andrews, Fife, KY16 9SS.}
 
@@
 
-We investigate the formation of H$\alpha$ from classical T~Tauri
-stars with a complex circumstellar geometry -- the combination of
-mangnetisherical accretion, collimated steller wind, and accretion
-disc. AND MORE
+We present radiative transfer models of the circumstellar environment
+of classical T~Tauri stars, concentrating on the formation of the
+H$\alpha$ emission. The wide variety of line profiles seen in
+observations are indicative of both inflow and outflow, and we
+therefore employ a circumstellar structure that includes both
+magnetospheric accretion and a disc wind.  We perform
+systematic investigations of the model parameters for the wind and the
+magnetosphere to search for possible geometrical and physical
+conditions which lead to the types of profiles seen in
+observations. We find that the hybrid models can reproduce the wide
+range profile types seen is observations, and that the most common
+profile types observed occupy a large volume of parameter
+space. Conversely, the most infrequently observed profile morphologies
+require a very specific set of models parameters.  We investigate the
+wind contribution to the line profile as a function of model parameters, and
+examine the reliability of H$\alpha$ as a mass accretion diagnostic.
+Finally, we examine the
+H$\alpha$ spectroscopic classification used by Reipurth et.~al, and
+discuss the basic physical conditions that are required to reproduce
+the profiles in each classified type.
 
@@
 
-T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
-\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
+T~Tauri stars (TTS) are young ($\gtrsim 3\times10^{6}\,\mathrm{yrs}$,
+\citealt{appenzeller:1989}) low-mass objects, and are the progenitors
 of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
-H$\alpha$ emission, and typically have spectral types of F--K. Some
-of the most active CTTS show emission in higher Balmer lines and metal
-lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit an excess
-amount of continuum flux in the ultraviolet (UV) and infrared (IR).
-Their spectral energy distribution and polarization data suggest the
-presence of a circumstellar disc, and it plays an important role in
-regulating dynamics of gas flows around CTTS.
-
-Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
-\citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profles show that the evidence for both outward wind
-flows and inward accretion flows, as seen in the blueshifted absorption
-features in H$\alpha$ profiles and the redshifted inverse P~Cygni
-(IPC) profiles. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
-to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
-\citealt{edwards:1987}; \citealt{hartigan:1995}), and the mass-accretion
-rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
-
-Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
-show the direct evidence for the presence of bipolar and monopolar
-outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
-two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
-and HV~Tau~C) by \citet{appenzeller:2005} show the extended (SCALE?)
-H$\alpha$ emission in the direction perpendicular to the obscuring
-circumstellar disc, and in both above and below the disc --- suggesting
-the presence of the bipolar outflows. In silightly larger scale, \emph{HST}
-observation of HH30 (Burrorws et al 1996) shows the jet traced to
-within $\lesssim30$~AU from the star. The jet has a cone shape with
-an opening angle of $3^{\circ}$ between 70 and 700 AU. (Originally
-from Konig and Pudritz 2000 review in PP IV). \citealt{alencar:2000}
-found about 80 per cent of their samples (30 CTTS) show blueshifted
-absorption componets in at least one of Balmer lines and Ca~K (most
-commonly in H$\alpha$).
-
-In a currently favoured model of accretion flows around CTTS, the
-accretion discs are disrupted by the magnetosphere of stars which
-channels the gas from the disc onto the surface of the stars (e.g.,
-\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993}\citealt{shu:1994}).
-This picture of the accretion flows is supported by the evidences
-that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$) magnetic
-field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
-and by the radiative transfer models which reproduce the observed
-profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
-accretion model naturally explains the blueward asymmetic emission
-lines (seen in some of CTTS) caused by the partial occulation of the
-flow by the disc, and the redshifted absorption componet at the typical
-free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$) seen
-in some of CTTS.
-
-Dispite the success of the magnetosherical accretion model in explaining
-the line profiles in some CTTS, the overwhelming observational evidences
-for the outflow (mentoned above) in the CTTS profiles suggests that
-this model is only a part of a whole picture. Clearly, the modefification
-to include the outflowing wind/jet flow is neccessary if one requires
-to predict the mass-accretion rate and the mass-loss rate of CTTS
-by modelling their emission profiles (e.g. H$\alpha$).
-
-Priory to the magnetospherical models, many alternative models had
-been considered to explain the observed spectroscopic features mentioned
-earlier. For example, 1.~the Alfv\'{e}n wave-driven wind model (e.g.~\citealt{decampli:1981};
-\citealt{hartmann:1982}), 2.~turbulant boundary layer (between the
-accretion disc and stellar surface) model (e.g.~\citealt{bertout:1988};
-\citealt{basri:1989}), 3.~chromospheric model (e.g.~\citealt{calvet:1984}),
-and 4.~disc wind model (e.g. \citealt{calvet:1992b}; \citealt{kwan:1995}).
-Considering the sucess of the magnetospherical accretion flow model
-in some cases and the observational eividences for the outflows, it
-is likely that an improved spectroscopic model requires both inflow
-and outflow components. The combination of the magnetospheric accretion
-flow model with model 1 or 4 would be a reasonable starting point
-for an improved spectroscopic model. Although time consuming to explore
-a larger parameter space, more realistic density, velocity and temperature
-structure from magnetohydrodynamic wind+accretion models should be
-considered as inputs for an radiative transfer model in the future.
-
-The magnetocentrifugal wind model, first proposed by \citet{blandford:1982},
-has been often used to reproduce the large-scale wind structure of
-T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
-by \citealt{burrows:1996}; \citealt{ray:1996}). The lanching of
-the wind from a Keplerian disc is typically done by treating the equaotorial
-plane of the disc as a mass-injecting boundary condition (e.g., \citealt{ustyugova:1995};
-\citet{shu:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
-Depending on the location of the open magnetic fields anchored to
-the disc, two different types of winds are preoduced. If the field
-is constrained to be near the co-rotation radius of stellar magnetosphere,
-an {}``X-wind'' \citep{shu:1994} is produces. If the open field
-lines are located in a wider area of the disc, a {}``disc-wind''
-similar to \citet{koenigl:2000} is produced \citet{krasnopolsky:2003}.
-Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
-and \citet{pudritz:2005}.
-
-In this paper, we present a semi-emperical wind -- accretion disc
--- magnetospherical accretion hybrid model for CTTS, and perform parametric
-studies of the H$\alpha$ formation. This study should provide preliminary
-physical conditions which lead to the wide varaiety of emission line
-profiles seen in the observation, and would help to construct more
-comprehensive circumstellar models (e.g. via MHD simulations) of T~Tauri
-stars. the Using the model results, we examine the H$\alpha$ spectroscopic
-classification used by \citet{reipurth:1996}, and compare models
-with observations. We will also discuss whether our model is consistent
-with some predictions made by the recentt MHD studies (e.g.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$).
-
-In section~\ref{sec:model-configuration}, the model assumptions,
-and the basic model configurations are presented. We discuss the radiaive
-transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
-and the results of model calculations are given in section~\ref{sec:Results}.
-The closer examination and discussion of the results are presented
-in section~\ref{sec:Discussion}. Finally, the summary of this work
-and the conclusion are in section~\ref{sec:Conclusions}.
+H$\alpha$ emission, and typically have spectral types of F--K. Some of
+the most active CTTS show emission in higher Balmer lines and metal
+lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit excess continuum
+flux in the ultraviolet (UV) and infrared (IR).  Their spectral energy
+distribution and polarisation data suggest the presence of
+circumstellar discs, which plays an important role in regulating
+dynamics of gas flows around CTTS (e.g. \citealt{camenzind:1990}).
+
+Many observational studies (e.g., \citealt{herbig:1962};
+\citealt{edwards:1994}; \citealt{kenyon:1994};
+\citealt*{reipurth:1996}; \citealt{alencar:2000}) of CTTS line
+profiles have revealed evidence for both outward wind flows and inward
+accretion flows, characterised by the blue-shifted absorption features
+in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC)
+profiles respectively. Typical mass-loss rates of CTTS are about
+$10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\,
+yr^{-1}}$ (e.g., \citealt{kuhi:1964}; \citealt{edwards:1987};
+\citealt*{hartigan:1995}), and the mass-accretion rates are also about
+$10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\,
+yr^{-1}}$ (e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988};
+\citealt{gullbring:1998}).  Recent H$\alpha$ spectro-astrometric
+observations by \citet*{takami:2003} provide indirect evidence for the
+presence of bipolar and monopolar outflows down to $\sim
+1\,\mathrm{au}$ scale (e.g.\,CS~Cha and RU~Lup).  Similarly, ESO VLT
+observations using high-resolution ($R=50\,000$) two-dimensional
+spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B, and HV~Tau~C) by
+\citet{appenzeller:2005} show extended H$\alpha$ emission in the
+direction perpendicular to the obscuring circumstellar disc,
+suggesting the presence of the bipolar outflows. On an even larger
+scale, \emph{HST} observations of HH30 \citep{burrows:1996} trace the
+jet to within $\lesssim30$~au of the star. The jet has a cone shape
+with an opening angle of $3^{\circ}$ between 70 and 700 au
+\citep{koenigl:2000}. \citet{alencar:2000} found about 80 per cent of
+their sample (30 CTTS) show blue-shifted absorption components in at
+least one of the Balmer lines and Ca~K.
+
+In the currently favoured model of accretion in CTTS, the accretion
+disc is disrupted by the magnetosphere, which channels the gas from
+the disc onto the stellar surface (e.g., \citealt{uchida:1985};
+\citealt{koenigl:1991}; \citealt{cameron:1993};
+\citealt{shu:1994}). This picture is supported by recent measurements
+of strong ($\sim 10^{3}\mathrm{G}$) magnetic fields in CTTS (e.g.,
+\citealt{johns-krull:1999}; \citealt{symington:2005b}) and by
+radiative transfer models which reproduce the gross characteristics of
+observed profiles for some TTS (\citealt*{muzerolle:2001}). In
+particular the magnetospheric accretion (MA) model explains blue-ward
+asymmetric emission line profiles as resulting from the partial
+occultation of the flow by the stellar photosphere, while inverse
+P~Cygni profiles in the MA model result from inflowing material at
+near free-fall velocities seen projected against hotspots on the
+stellar surface.
+
+Despite these successes, the overwhelming observational evidence for
+outflow in the CTTS suggests that the MA model is only one component
+of a complex circumstellar environment. Clearly, one must include the
+contribution of any wind/jet flow if one wishes to both accurately
+predict the mass-accretion rate and also determined the mass-loss rate
+of CTTS via emission profile modelling. The first attempt in this
+direction was made by \citet{alencar:2005} who demonstrated that the
+observed H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better
+reproduced by the radiative transfer model which included a collimated
+disc-wind arising from near the inner edge of the accretion disc.
+
+The main aim of this paper is to find a simple kinematic model which
+can reproduce the wide variety of the observed profiles, and to
+perform empirical studies of line formation in an attempt to place
+morphological classification schemes on a firmer physical footing. We
+will also discuss whether our model is consistent with some
+predictions made by recent (magneto-hydrodynamics) MHD studies i.e.~
+$\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$
+(e.g.~\citealt{koenigl:2000}).
+
+In section~\ref{sec:model-configuration}, the model assumptions, and
+the basic model configurations are presented. We discuss the radiative
+transfer model used to compute the profiles in
+section~\ref{sec:radiative-transfer-model}, and the results of model
+calculations are given in section~\ref{sec:Results}.  We discuss our
+results in the context of Reipurth's classification scheme in
+section~\ref{sec:Discussion}, and our summary and conclusions are
+presented in section~\ref{sec:Conclusions}.
+
+%%%%%%%%%%%%%%
 
@@
 
-To understand how the different part of the CTTS circumsterllar enviroment
-contributes to the fomation of H$\alpha$, the model spaced is devided
-into four different regions: 1.~Central contiuum source, 2.~magnetosphere
-accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:overview}
-depicts the relative location in the model space. In all regions,
-the density is symmetric around the z-axis. The innermost raius of
-the magnetsphere at the equotrial plane coincides with the the inner
-radius of the accretion disc. From the inner most part of the accretion
-disc, the gas freely fall, moving along the magneic filed onto the
-surface of the star. For the purpose of computational simplicity,
-the colliminated wind are defined only in the outside of the largest
-radius of the magnesophere. In the following subsections, the details
-of model components will be described.
-
-\begin{figure*}
+In order to understand how the different parts of the CTTS
+circumstellar environment contribute to the formation of H$\alpha$,
+the model space is divided into four different regions: (1)~a central
+continuum source, (2)~the magnetospheric accretion flow, (3)~the wind
+outflow, and (4)~the accretion disc. Fig.~\ref{fig:config_discwind}
+depicts the relative location of the regions in the model space.  The
+density is assumed to be rotationally symmetric around the
+$z$-axis. The innermost radius of the magnetosphere at the equatorial
+plane coincides with the the inner radius of the accretion disc. From
+the innermost part of the accretion disc, the gas falls freely, moving
+along the magnetic field onto the surface of the star.  In the
+following subsections we describe the details of model components.
+
+\subsection{The continuum source}
+
+\label{sub:Continuum-Source}
+
+We adopt stellar parameters of a typical
+classical T~Tauri star for the central continuum source, i.e. radius
+($R_{*}$), mass ($M_{*}$), and effective temperature the photosphere
+($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$, and $4000\,\mathrm{K}$
+respectively. The model atmosphere of \citet{kurucz:1979} with
+$T_{\mathrm{ph}}=4000\,\mathrm{K}$ and $\log g_{*}=3.5$ (cgs) defines
+the photospheric contribution to the continuum flux. The
+parameters are summarised in Table~\ref{tab:std_parameters}.
+
+An additional continuum source is considered for models which includes
+magnetospheric accretion: as the infalling gas approaches the stellar
+surface, it decelerates in a strong shock, and is heated to $\sim
+10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
+be absorbed by the gas locally, and re-emitted in optical and UV
+radiation (\citealt{koenigl:1991}; \citealt*{hartmann:1994}). This
+will create hot rings where the magnetic field intersects with the
+surface. We assume that the free-falling kinetic energy is thermalized
+in the radiating layer, and is re-emitted as blackbody radiation with
+a single temperature. With the parameters of the magnetosphere and the
+star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
+of the surface is covered by the hot rings. If the mass-accretion rate
+is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this accretion
+luminosity to the photospheric luminosity is about $0.5$, and the
+corresponding temperature of the hot rings is about
+$6400\,\mathrm{K}$.  The continuum emission from the hot rings is
+taken into account when computing the line profiles.
+
+\begin{table*}
+
+\caption{Summary of the reference classical T~Tauri star model parameters.}
+\label{tab:std_parameters}
 
@@
 
-\includegraphics[%
-  scale=0.6]{figures/overview2.eps}
-
-\end{center}
-
-\caption{Basic Model Configuration.
-The system consist of four components: 1.~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, 2.~magnetospherical accretion flow, 3.~colliminated wind/jet outflow, and 4.~accretion disc.
-The density distribution is symmetric around the z-axis.
-The innermost raius of the magnetsphere (at the equotrial plane) coincides with the the inner radius of the accretion disc.
-From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star.
-For simplicit, the colliminated wind/jet exists outside of the largest radius of the magnesophere (dotted line).
-}
-
-\label{fig:overview}
-
-\end{figure*}
-
-\subsection{Contiuum Source}
-
-\label{sub:Contiuum-Source}
-
-Unless specified otherwise, we adopt stellar parameters of a typical
-classical T~Tauri star (REF) for the central conitnuum source, i.e.
-radius ($R_{*}$), mass ($M_{*}$), and effective temperature the
-photosphere ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$,
-and $4000\,\mathrm{K}$ respectively. The model atomsphere of \citet{kurucz:1979}
-equivallently \citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$
-and $\log g_{*}=3.5$ (cgs) is used to continuum flux at H$\alpha$wavelength.
-The parameters are summarised in Table~\ref{tab:std_parameters}.
-
-The limb-darkening law used for the continuum source is $I\left(\mu\right)=I_{0}\left(1+b\mu\right)$
-where $\mu=\cos\theta$ and $\theta$ is the polar angle. $b$ is
-a parameter. For no limb-darkening case, $b=0$, and for the Eddington
-approximation case $b=3/2$. The former is used in all the calulcations
-presented here. (Is this an ok assumption for T Tauri's? You need
-to check this.)
-
-\begin{table*}
-
-\begin{center}
-
-\begin{tabular}{lcccccccccccc}
+\begin{tabular}{lccccccccccc}
 \hline 
@@
 $\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$[-]$&
 $[\mathrm{km\, s^{-1}}]$&
 $[-]$&
-$\left[R_{\sun}\right]$&
-$\left[\mathrm{AU}\right]$\tabularnewline
+$\left[R_{*}\right]$&
+$\left[\mathrm{au}\right]$\tabularnewline
 \hline
-Standard&
+&
 $2.0$&
@@
 
-\caption{The summary of the standard classical T~Tauri star model parameters.}
-
-\label{tab:std_parameters}
-
 \end{table*}
 
-\subsection{Magnetosphere}
+\subsection{The magnetosphere}
 
@@
 
-We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
-as done so by \citet{muzerolle:2001} and by \citet{symington:2005},
+We adopt the MA flow model of \citet{hartmann:1994},
+as done  by \citet{muzerolle:2001} and by \citet*{symington:2005},
 in which the gas accretion on to the stellar surface from the innermost
@@
 flow does not affect the underlying magnetic field itself. As shown
-in Fig.~\ref{fig:overview}, the innermost radius ($R_{\mathrm{mi}}$)
-of the magnetophere at the equatorial plane ($z=0$) is assigned to
-be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
+in Fig.~\ref{fig:config_dipolar}, the innermost radius ($R_{\mathrm{mi}}$)
+of the magnetosphere at the equatorial plane ($z=0$) is assigned
+to be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
 disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
 and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
-the equaotrial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
-respectively. The former value corresponds to the corotation radius
-of the accretion disc, and the geometry of the magnetic field/stream
-lines is kept constant throghout this paper. The geometry of the magnetosphere
+the equatorial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
+respectively. The geometry of the magnetic field/stream
+lines is fixed for all calculations. We note that this magnetospheric geometry
 is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
@@
 The magnetic field and the gas stream lines are assumed to have the
-following simple form: $r=R_{\mathrm{m}}\sin^{2}\theta$ \citep[see][]{ghosh:1977}
-where $r$, and $\theta$ are coordinates of the field point ($p$)
-in Fig.~\ref{fig:overview} in spheical coodinates, and $R_{\mathrm{m}}$is
-the radial distance to the field line at the equotorial plane ($\theta=\pi/2$).
-The range of $R_{\mathrm{m}}$is restricted between $R_{\mathrm{mi}}$
-and $R_{\mathrm{mo}}$ as mentioned above. Using the field geometry
-above, the conservation of energy, and igoring the rotation of magnetosphere,
-the velocity and the density of the accreting gas along the steam
-line can be found. See \citet{hartmann:1994} for details.
-
-In all of our models, the temperature structure of the magnetospheric
-used by \citet{hartmann:1994} is also adoped here. The temperature
-structure was computed assuming a volumetric heating rate which is
-proportional to $r^{-3}$, and using the energy balance of the radiative
-cooling rate of \citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
-Although the temperature structure of the accretion steam could significantly
-affect the line source function, for the purpose of the expolaring
-the general characteristics of the H$\alpha$ formation, this simple
-form is a reasonable assumption.\citet{martin:1996} presented the
-self-consistent determination of the thermal structure of the inflowing
-gas along the dipole magnetic field, same as the one used here, by
-solving the heat equation couple to trate equations for hydrogen.
-He found that main heat source is adiabatic compression due to the
-convering nature of the flow, and the major contirbutors of the cooling
-process are bremsstrahling radiation and line emission from Ca~II
-and Mg~II ions. The temerature sturcture of \citet{martin:1996}
-qualitaively agrees with that of \citep{hartmann:1994}. The sensitivty
-tests of H$\alpha$ on the temperature structure will be presented
-later (SPECIFY THE SECTION LATER).
-
-As the infalling gas becomes closer to the stellar surface, it is
-decelerates in a strong shock, and heated to $\sim10^{6}\,\mathrm{K}$
-(with typical parameters). The X-ray radiation produced in the shock
-will be absorbed by the gas located near, and reemitted in optical
-and UV radiation (\citealt{koenigl:1991}; \citealt{hartmann:1994}).
-This will create hot rings near the stellar surface where the magnetic
-field intersects with the surface. For simplicity, the free-falling
-kinetic energy is assumed to be thermalized in the radiating layer,
-and reemits as blackbody radiation (with a single temerature). With
-the parameters of the magnetosphere and the star given above (Table~\ref{tab:std_parameters}),
-about $8$~per~cent of the surface is covered by the hot rings,
-and its temperature is about $6400\,\mathrm{K}$. If the mass-accretion
-rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this
-accretion luminosity to the photospheric luminosity is about $0.5$.
-The contiuum emission from the hot rings is taken into account when
-computing the line profiles.
-
-\subsection{Wind}
-
+following simple form:
+\begin{equation}
+      r=R_{\mathrm{m}}\sin^{2}\theta
+  \label{eq:dipole}
+\end{equation}
+\citep*[see][]{ghosh:1977} where $r$, and $\theta$ are coordinates
+of the field point ($p$) in Fig.~\ref{fig:config_dipolar} in spherical
+coordinates, and $R_{\mathrm{m}}$ is the radial distance to the field
+line at the equatorial plane ($\theta=\pi/2$). The range of
+$R_{\mathrm{m}}$ is restricted between $R_{\mathrm{mi}}$ and
+$R_{\mathrm{mo}}$. Using the field geometry above and conservation of
+energy, the velocity and the density of the accreting gas along the
+steam line are found as in \citet{hartmann:1994}.
+
+The temperature structure of the magnetospheric used by
+\citet{hartmann:1994} is adopted here. They computed the temperature,
+assuming a volumetric heating rate which is proportional to $r^{-3}$,
+by solving the energy balance of the radiative cooling rate of
+\citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
+\citet{martin:1996} presented a self-consistent determination of the
+thermal structure of the inflowing gas along the dipole magnetic field
+(equation~\ref{eq:dipole}) by solving the heat equation coupled to the
+rate equations for hydrogen. He found that main heat source is
+adiabatic compression due to the converging nature of the flow, and
+the major contributors to the cooling process are bremsstrahlung
+radiation and line emission from Ca~II and Mg~II ions. The results of
+\citet{martin:1996} qualitatively agree with that of
+\citet{hartmann:1994}.
+
+\subsection{The disc-wind outflow geometru}
 \label{sub:wind_jet}
 
-\subsubsection{Colliminated wind model}
-
-JUSTTIFICATION OF USING THIS FORMULATION. BREIFLY MENTIONED THE WORK
-DONE BY OTHERS.
-
-Based on the simple model of \citet{appenzeller:2005}, the following
-parametrisation of colliminated wind/jet (region 3 in Fig.~\ref{fig:overview})
-is adopeted. The wind velocity field, $\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$,
-is consist of radial and polar components which depend only on $r$
-and $\theta$ respectively. The radial componet $v_{r}\left(r\right)$
-is assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
-and the azimuthal component $v_{\phi}$ is asuumed to be a constant
-fraction ($\gamma$) of the Keplerian velocity for a given distance
-($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:
-
-\begin{eqnarray}
-\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}+v_{\theta}\hat{\btheta}\label{eq:wind_velocity_def}\end{eqnarray}
-where \begin{equation}
-v_{r}\left(r\right)=v_{r0}+v_{\infty}\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
+The magneto-centrifugal wind paradigm, first proposed by
+\citet{blandford:1982}, has been often used to model the large-scale
+wind structure of T Tauri stars, or the observed optical jets
+(e.g.~HH~30 jet by \citealt{burrows:1996}; \citealt{ray:1996}). The
+launching of the wind from a Keplerian disc is typically done by
+treating the equatorial plane of the disc as a mass-injecting boundary
+condition (e.g., \citealt{shu:1994}; \citealt{ustyugova:1995};
+\citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).  Depending on the
+location of the open magnetic fields anchored to the disc, two
+different types of winds are produced. If the field is constrained to
+be near the co-rotation radius of stellar magnetosphere, an
+{}``X-wind'' \citep{shu:1994} is produced. If the open field lines are
+located in a wider area of the disc, a {}``disc-wind'' similar to that
+of \citet{koenigl:2000} is produced \citep{krasnopolsky:2003}.  Recent
+reviews on the jet/wind-disc connection can be found in
+\citet{koenigl:2000} and \citet{pudritz:2005}. Clearly there are several alternative outflow scenarios. Here we adopt
+a simple kinematical model, based on the disc-wind paradigm, which broadly represents the results of
+MHD simulations,
+
+\citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
+disc-wind model in their studies of the UV resonance lines formed
+in the winds of cataclysmic variable stars. His formalism provides
+a simple parameterisation of a disc wind that has similar properties 
+to those found by  MHD modelling. In this model, the outflow
+arises from the surface of the rotating accretion disc, and has a
+biconical geometry. The specific angular momentum is assumed to be
+conserved along a stream line, and the poloidal velocity component
+is assumed to be simply a radial from vertically displaced {}``sources''
+from the central star.  Here we briefly describe the disc-wind model, and
+readers are referred to \citet{knigge:1995} and \citet{long:2002} for
+details.
+
+The four basic parameters of the model are: (1)~the mass-loss rate,
+(2)~the degree of the wind collimation, (3)~the velocity gradient, and
+(4)~the wind temperature. The basic configuration of the disc-wind
+model is shown in Figure~\ref{fig:config_discwind}. The disc wind
+originates from the disc surface, but the {}``source'' point ($S$),
+from which the stream lines diverges, are placed at distance $d$ above
+and below the centre of the star.  The angle of the mass-loss
+launching from the disc is controlled by changing the value of
+$d$. The mass-loss launching occurs between $R_{\mathrm{wi}}$ and
+$R_{\mathrm{wo}}$ where the former is set to be equal to the outer
+radius of the magnetosphere ($R_{\mathrm{mo}}$) and the latter is set
+to $1$~au as in \citealt{krasnopolsky:2003}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+  \begin{center}
+
+    \includegraphics[%
+      scale=0.6]{figures/discwind.eps}
+
+  \end{center}
+
+  \caption{Basic model configuration of the disc-wind, magnetosphere
+    hybrid model. The system consist of four components: (1)~the
+    continuum source located at the origin $\left( o \right)$ of the
+    cartesian coordinates $\left(x,y,z\right)$ -- the $y$-axis is into
+    the paper, (2)~the magnetospheric accretion flow, (3)~the disc
+    wind, and (4)~the accretion disc. The disc wind originates from
+    the disc surface between $w_{i}=R_{\mathrm{wi}}$ and
+    $w_{i}=R_{\mathrm{wo}}$ where $w_{i}$ is the distance from the $z$
+    axis on the equatorial plane.  The wind source
+    points ($S$), from which the stream lines diverges, are placed at
+    distance $d$ above and below the star. The degree of wind
+    collimation is controlled by changing the value of $d$.}
+
+  \label{fig:config_discwind}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The local mass-loss rate per unit area ($\dot{m}$) is assumed to
+be proportional to the mid-plane temperature of the disc, and is a
+function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$, i.e.
 \begin{equation}
-v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
-and \begin{equation}
-v_{\theta}\left(r,\theta\right)=v_{\theta0}\,\left(\frac{R_{\mathrm{mo}}}{r}\right)^{\alpha}\frac{\tan\theta}{\left|\tan\theta\right|}\,.\label{eq:wind_velocity_polar_part}\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$, and
-the range of the polar angle is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
-where $\theta_{\mathrm{disc}}$ is the openning angle of the accretion
-disc, to avoid the overlap. $v_{r0}$is the small radial velocity
-at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$,
-approximately the thermal velocity of hydrogen with $T=7500\,\mathrm{K}$
-and $\gamma=0.05$ (\citealt{appenzeller:2005}) are used. The dependency
-of $v_{r}$ in polar direction ($\theta=0$) on the values of wind
-accerelation parameter $\beta$ is shown in Figure~\ref{fig:wind_vr_rho}.
-All other parameters describing the wind are fixed as the standard
-values given in Table~\ref{tab:std_parameters}.
-
-Further, the density of the wind is assumed to be axi-symmetric and
-separable in $r$ and $\theta$ for computationaly simpliciy, i.e.,
-
+  \dot{m}\left(w\right) \propto
+       T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}
+\end{equation}
+The mid-plane temperature of the disc is assumed to be expressed
+as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
+relation above, one finds 
 \begin{equation}
-\rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)\label{eq:wind_density_def}\end{equation}
- with \begin{equation}
-F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
- where $b$ is normally positive even number (for the density symmetric
-about the equtotrial plane), and $n$ is the angular normalisation
-constant. For $b=0$, the wind is sherically symmetic exept for the
-parts dirupted by the accretion disc. The larger the value of $b$,
-the higher the degree of the collimination. By integrating equation~\ref{eq:wind_density_theta}
-over angles and normalising the integral to $4\pi$, one finds \begin{equation}
-n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
- Asumming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
-and the mass-flux conserves in time, the radial part of the density
-function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
-hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
-\rho\left(r,\theta\right)=\frac{n\,\cos^{b}\theta\,\dot{M}_{\mathrm{wind}}}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
- For a given mass-accretion rate, the wind mass-loss rate in our typical
-model is assined from the ratio of mass-loss to mass-accretion rate
-($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
-by both observations and magnetohydrodynamical calculations (see e.g.
-\citealt{koenigl:2000}).
-
-Figure~\ref{fig:wind_vr_rho} shows the values of $\rho$ in polar
-direction ($\theta=0$) for different values of $\beta$ with all
-other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+  \dot{m}\left(w\right)\propto w^{p}
+  \label{eq:discwind-massloss-w}
+\end{equation}
+where $p=\alpha\times q$. The index of the mid-plane temperature power
+law is adopted from the dust radiative transfer model of
+\citet{whitney:2003a} who found the innermost part of the accretion
+disc has $q=-1.15$.  In order to be consistent with the collimated
+disc-wind model of \citet{krasnopolsky:2003} who used $p=-3/2$, the
+value of $\alpha$ is set to 1.3. The constant of proportionality in
+equation~\ref{eq:discwind-massloss-w} is found by integrating
+$\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$, and the
+normalising the value to the total mass-loss rate
+$\dot{M}_{\mathrm{dw}}$.
+
+The azimuthal/rotational component of the wind velocity
+$v_{\phi}\left(w,z\right)$ is computed from the Keplerian rotational
+velocity at the emerging point of the stream line
+i.e. $v_{\phi}\left(w_{i},0\right)=\left(GM_{*}/w_{i}\right)^{1/2}$
+where $w_{i}$ is the distance from the rotational axis ($z$) to the
+emerging point on the disc, and by assuming the conservation of the
+specific angular momentum along a stream line:
+\begin{equation}
+  v_{\phi}\left(w,z\right)\, = 
+  v_{\phi}\left(w_{i},0\right)\,\left(\frac{w_{i}}{w}\right)\,\,.
+  \label{eq:discwind-toroidal-velocity}
+\end{equation}
+Based on the canonical $\beta$ velocity law of hot stellar winds
+(c.f.~\citealt*{castor:1975}), the poloidal component of the wind
+velocity ($v_{p}$) parameterised as:
+\begin{equation}
+  v_{p}\left(w_{i},l\right) = c_{\mathrm{s}}\left(w_{i}\right) +
+  \left[f\, v_{\mathrm{esc}}-c_{\mathrm{s}}\left(w_{i}\right)\right]\left(1-\frac{R_{s}}{l+R_{s}}\right)^{\beta}
+  \label{eq:discwind-poloidal-velocity}
+\end{equation}  
+where $c_{\mathrm{s}}$, $f$, and $l$ are the sound speed at the wind
+launching point on the disc, the constant scale factor of the
+asymptotic terminal velocity to the local escape velocity (from the
+wind emerging point on the disc), and the distance from the disc
+surface along stream lines respectively. $R_{s}$ is the wind scale
+length (=10\, $R_{\mathrm{mi}}$, \citealt{long:2002}).
+
+Assuming mass-flux conservation and using the velocity field defined
+above, the disc wind density as a function of $w$ and $l$ can be
+written as
+\begin{equation}
+  \rho\left(w_{i},l\right) =
+  \frac{\dot{m}\left(w_{i}\right)}{v_{p}\left(w_{i},l\right)\,\left|\cos\delta\right|}\,\left\{ 
+  \frac{d}{Q\left(w_{i},l\right)\,\cos\delta}\right\} ^{2}
+  \label{eq:discwind-density}
+\end{equation} 
+where $Q$ and $\delta$ are the distance from the source point ($S$) to
+a point along the stream line and the angle between the stream line
+and the disc normal respectively. Figure~\ref{fig:discwind_vr_rho}
+shows the density and the velocity components along the mid stream
+line (passing through
+$w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$ on the disc
+plane ($z=0$) for different values of the wind acceleration parameter
+$\beta$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
 	clip,
-  scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
+	scale=0.59]{plots/dw_vp_vphi.eps}~~~~~~&
       \includegraphics[%
 	clip,
-  scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
+	scale=0.59]{plots/dw_rho.eps}\tabularnewline
     \end{tabular}
@@
 
-\caption{The dependency of the wind/jet velocity and density structures on the wind accerelation parameter $\beta$.
-The radial component of the wind/jet velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left.
-The wind/jet density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is right.
-The smaller the value of $\beta$, the faster the accerelation of the wind.
-For the raidus ($r/R_{\mathrm{mo}} < 10$, both velocity and density are sensitive to the value of $\beta$.
-For all $\beta$ values, the radial velocity of the wind reaches the terminal velocity ($\sim 210\,\kmps$ by  $r/R_{\mathrm{mo}} \sim 1000$.
-The initial velocity $V_{0}=10\,\kmps$, which approximately corresponds to the thermal velocity of a hydrogen atom at 7500~K,  is used for all $v_{r}$ plots.
-Beyound $r/R_{\mathrm{mo}}= 100$, little difference is seen in the polar density with diffrent $\beta$ values.}
-
-\label{fig:wind_vr_rho}
+  \caption{The dependency of the disc-wind density and velocity on the wind
+    acceleration parameter $\beta$. The wind density $\rho$ (left panel)
+    and the poloidal velocity component $v_{p}$ (right panel) along the
+    stream line starting from the mid point of the wind launching zone,
+    i.e. $\left ( w,z \right ) = \left ( w_{\mathrm{mid}}, 0 \right )$
+    where $w_{\mathrm{mid}} = \left( R_{\mathrm{wi}}+R_{\mathrm{wo}}
+    \right ) / 2$, are shown as a function of the distance ($l$) from the
+    wind launching point (c.f.~
+    equations~\ref{eq:discwind-poloidal-velocity} and
+    \ref{eq:discwind-density}). The azimuthal velocity component
+    ($v_{\phi}$), which is independent of $\beta$
+    (c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in
+    the right panel for comparison. The density is normalised to the
+    density $\rho_{0}$ at the wind launching point for the $\beta = 1.0$ case.
+    The $v_{p}$ reaches the terminal velocity by 100~au for all
+    $\beta$. In the far field ($l>10$~au), the density is approximately
+    proportional to $\sim l^2$. }
+
+  \label{fig:discwind_vr_rho}
 
 \end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Disc-wind model}
-
-GIVE MORE CONVINCING MOTIVIATION FOR USING THIS MODEL. THIS SECTION
-MAY BE DELETED.
-
-Alternative to the colliminated wind model, the kinematic disc-wind
-mode of \citet{knigge:1995} in which a wind originating from the
-surface of the accretion disc with a biconical outflow geometry (Fig.~XXX)
-will be presented next. The model was originally developed for describing
-the formation of the UV resonance lines in the winds of cataclystic
-variable (CV) stars.
-
-\subsection{Accretion disc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{The accretion disc}
 
@@
 
-Region 4 in Fig.~\ref{fig:overview}
+We adopt a simple analytical accretion disc model, the $\alpha$-disc
+`standard model' (\citealt{shakura:1973}; \citealt*{frank:2002}) with
+the inner radius fixed at the inner radius of the magnetosphere at
+equatorial plane. This corresponds to Region 4 in
+Fig.~\ref{fig:config_dipolar}.
 
@@
 
-Although it is possible, in our model, to compute the dust-sublimination
-radius and the vertical hydrostatic structure of the accretion disc
-self-consistently (assuming the radial dependecy of the mid-plane
-density) by using the interative Monte Calro radative transfer technique
-(c.f.~\citet{walker:2004}), we find it to be too time consuming
-for the purpose of this paper -- understanding the general characteristic
-of H$\alpha$ profile shapes hence exploring a large parameter space.
-For this reason, we adopt a simple analytical disc model, the steady
-$\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
-with the inner radius fixed at the inner radius of the magnetosphere
-(at equatorial plane). The disc density disribution is given by
-
+The disc density distribution is given by 
 \begin{equation}
-\rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
- where $w$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
-axis, the scale height, the distance from the disc plane, and the
-surface density at the mid-plane, respectively. The mid-plane surface
-density and the scale height are given as: \begin{equation}
-\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{d}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
+  \rho_{\mathrm{d}}\left(w,z\right) = 
+  \Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}
+  \label{eq:disc-density-function}
+\end{equation}
+where $w=\sqrt{x^{2}+y^{2}}$, $h$, $z$ and $\Sigma$ are the distance
+from the symmetry axis, the scale height, the distance from the disc
+plane, and the surface density at the mid-plane, respectively. The
+mid-plane surface density and the scale height are given as:
+\begin{equation}
+  \Sigma\left(w\right) = 
+  \frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}
+  \label{eq:density-midplane}
+\end{equation} 
 where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
-and the disc mass respectively.\begin{equation}
-h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.\label{eq:scale-height}\end{equation}
+and the disc mass respectively.
+\begin{equation}
+  h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.
+  \label{eq:scale-height}
+\end{equation}
 With these parameters, the disc is slightly flared. The inner radius
-of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
-radius of the magnetosphere at the equaotrial plane), which is approximatly
-same as the co-rotating radius of the system with the paramters in
-Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
-of an object is assumed to be 1/100 of the central mass ($M_{*}$),
-and the disc radius ($R_{\mathrm{di}}$) to be 100~au. The velocity
-of the gas/dust in the disc is assumed to be Keplerian.
+of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ . The disc
+mass, $M_{\mathrm{d}}$, is assumed to be 1/100 of the stellar mass
+($M_{*}$), and the outer disc radius ($R_{\mathrm{di}}$) is
+100~au. The velocity of the gas/dust in the disc is assumed to be
+Keplerian.
 
@@
 
-To calculate the dust scattering and absorption cross section as a
-function of wavelength, the optical constants of \citet{draine:1984}
-for amorphous carbon grains and \citet{hanner:1988} for silicate
-grains are used. The model uses the {}``large grain'' dust model
-of \citet{wood:2002} in which the dust grain size distribution is
-described by the following function:\begin{equation}
-n\left(a\right)da=\left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\, a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da\label{eq:grain-dist-function}\end{equation}
- where $a$ is the grain size restricted between $a_{\mathrm{min}}$
-and $a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$
-are the terms set by requiring the grains to completely deplete a
-solar abundance carbon and silicon. The parameters adopted in our
-model are: $C_{\mathrm{C}}=1.32\times10^{-17}$, $C_{\mathrm{Si}}=1.05\times10^{-17}$,
-$p=3.0$, $q=0.6$, $a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
+In order to calculate the dust scattering and absorption cross section
+as a function of wavelength, the optical constants of
+\citet{draine:1984} for amorphous carbon grains and
+\citet{hanner:1988} for silicate grains are used. The model uses the
+{}``large grain'' dust model of \citet{wood:2002} in which the dust
+grain size distribution is described by the following function:
+\begin{equation}
+  n\left(a\right)da = \left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\,
+  a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da
+  \label{eq:grain-dist-function}
+\end{equation}
+where $a$ is the grain size restricted between $a_{\mathrm{min}}$ and
+$a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$ are the
+terms set by requiring the grains to completely deplete a solar
+abundance carbon and silicon. The parameters adopted in our model are:
+$C_{\mathrm{C}}=1.32\times10^{-17}$,
+$C_{\mathrm{Si}}=1.05\times10^{-17}$, $p=3.0$, $q=0.6$,
+$a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
 $a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
-and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds
-to Model~1 of the dust model used by \citet{wood:2002}. See also
-their Fig.~3 The relative number of each grain is assumed to be that
-of solar abundance, C/H$\sim3.5\times10^{-4}$ \citep{anders:1989}
-and Si/H$\sim3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
-to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
-Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.
-
-\section{Radiative transfer model}
+and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds to
+Model~1 of the dust model used by \citet{wood:2002}. See also their
+Fig.~3 The relative numbers of each grain is assumed to be that of
+solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989} and
+Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar to
+values found in the ISM model of \citet*{mathis:1977} and
+\citet*{kim:1994}.
+
+\section{The radiative transfer model}
 
@@
 
-We have extended the TORUS radiative transfer code (\citealt{harries:2000};
-\citealt{kurosawa:2004a}; \citealt{symington:2005}) to compute the
-H$\alpha$ profiles from pre-main-sequence stars which are surrounded
-by one or more of the followings: the magnetospherical accretion flow,
-the out-flowing colliminated wind, and the accreation disc. Previously
-in \citet{symington:2005}, the model used in the three-dimentional
-(3-D) adaptive mesh refinement (AMR) to inverstigate the line variability
-mainly associated with roational motion of complex geometrical configurations
-of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
-modefied the code to handle the two-dimentional (2-D) density distribution,
-and restricted our models to be axi-symmetric. It was done so in order
-to enable us to explore rather large number of parameter spaces (c.f.~section~\ref{sec:model-configuration}).
-Note that the velocity field is still in 3-D -- the third component
-can be calculated by using the symmetry for a given value of azimutal
-angle. The examples of how the AMR grid for the purpose of the radiative
-transfer is constructed are presented in e.g. \citet{wolf:1999},
-\citet{kurosawa:2001a} and \citet{steinacker:2003} .
-
-The computation of the H$\alpha$ is devided in two parts: 1.~the
-source function calculation and 2.~the observed flux/profile calulcation.
-In the first process, we have utilized the method by \citet{klein:1978}
-(see also \citealt{rybicki:1978}; \citet{hartmann:1994}) in which
-the Sobolev approximation method is applied. The population of the
-bound states of hydrogen are assumed to be in statistical equilibrium,
-and the gas to be in radiative equilibrium. Our hydrogen atom model
-consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
-for details. (AND MORE..)
-
-To compute the observed line profile, the Monte Calro radiative transfer
-method (e.g. \citealt{hillier:1991}) using the Soblev escape-probabiliy
-can be used when I.~a large velocity gradiant is present in the gas
-flow, and II.~the intrinsic line width is negleible compared to the
-Doppler broadeing of the line. In our earlier models (\citealt{harries:2000};
-\citealt{symington:2005}), this method was used to compute the line
-profiles since the condition I and II are resonably satisfied. However,
-as noted and demonstrated by \citet{muzerolle:2001}, even with a
-moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
-Stark broadening becomes important in the optically thick H$\alpha$
-line. \citet{muzerolle:2001} (MORE REF HERE) also pointed out that
-the observed H$\alpha$profiles from CTTS typically have the wings
-extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
-\citet{reipurth:1996}) which cannot be explained by the infall velocity
-of the gas along the magneosphere.
-
-To implement the broadening meachanism, two modedifications to our
-previous model (\citealt{symington:2005}) are necessary. First, the
-emission and absorption profiles must be replaced by a Voigt profle
-which is defined as: \begin{equation}
-H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
- where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$, $y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$,
-and $y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$ (c.f. \citealt{mihalas:1978}).
-$\nu_{0}$ is the line centre frequency, and $\Delta\nu_{\mathrm{D}}$
-is the Doppler line width of hydrogen atom (due to its thermal motion)
-which is given by $\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
+We have extended the {\sc TORUS} radiative transfer code
+(\citealt{harries:2000}; \citealt{kurosawa:2004a};
+\citealt{symington:2005}) to include the multiple circumstellar
+components described above. In previous calculations
+\citep{symington:2005}, the model was used with a three-dimensional
+(3-D) adaptive mesh refinement (AMR) grid to investigate the line
+variability associated with rotational modulation of complex
+geometrical configurations of magnetospheric inflow (see also
+\citealt*{kurosawa:2005a}). We modified the code to handle the a
+two-dimensional (2-D) density distribution, and restricted our models
+to be axi-symmetric.  Note that the velocity field is still in 3-D --
+the third component can be calculated by using symmetry for a given
+value of azimuthal angle.
+
+The computation of H$\alpha$ is divided in two parts: (1)~the source
+function calculation ($S_{\nu}$) and (2)~the observed flux/profile
+calculation. In the first process, we have used the method of
+\citet{klein:1978} (see also \citealt{rybicki:1978};
+\citealt{hartmann:1994}) in which the Sobolev approximation method is
+applied. The population of the bound states of hydrogen are assumed to
+be in statistical equilibrium, and the gas to be in radiative
+equilibrium. Our hydrogen atom model consist of 14 bound states and a
+continuum. Readers are refer to \citet{harries:2000} for details.
+
+Monte Carlo radiative transfer (e.g. \citealt{hillier:1991}), under
+the Sobolev approximation, can be used when (1)~a large velocity
+gradient is present in the gas flow, and (2)~the intrinsic line width
+is negligible compared to the Doppler broadening of the line. In our
+earlier models (\citealt{harries:2000}; \citealt{symington:2005}),
+this method was adopted since these conditions are satisfied.
+However, as noted and demonstrated by \citet{muzerolle:2001}, even
+with a moderate mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\,
+yr^{-1}}$), Stark broadening becomes important in the optically thick
+H$\alpha$ line. \citet{muzerolle:2001} also pointed out that the
+observed H$\alpha$ profiles from CTTS typically have the wings
+extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\citealt{edwards:1994};
+\citealt{reipurth:1996}) which cannot be explained by the infall
+velocity alone.
+
+We have implemented the broadening mechanism following the formalism
+described by \citet{muzerolle:2001}. First, the emission and
+absorption profiles are replaced from the Doppler to the Voigt
+profile, which is defined as:
+\begin{equation}
+  H\left(a,y\right) \equiv
+  \frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'  
+  \label{eq:voigt_profile_def}
+\end{equation}
+where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$,
+$y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$, and
+$y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$
+(c.f. \citealt{mihalas:1978}).  $\nu_{0}$ is the line centre
+frequency, and $\Delta\nu_{\mathrm{D}}$ is the Doppler line width of
+hydrogen atom (due to its thermal motion) which is given by
+$\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
 where $m_{\mathrm{H}}$ is the mass of a hydrogen atom. The damping
-constant $\Gamma$, which depends on the physical condition of the
-gas, is parameterised by \citet*{vernazza:1973} as follows:
-
+constant $\Gamma$, which depends on the physical condition of the gas,
+is parameterised by \citet*{vernazza:1973} as follows:
 \begin{eqnarray}
-\Gamma & = & C_{\mathrm{rad}}+C_{\mathrm{vdW}}\left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)\left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
- &  & +\, C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}\label{eq:dampimg_constant_def}\end{eqnarray}
+  \Gamma & = & C_{\mathrm{rad}} + C_{\mathrm{vdW}}
+  \left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)
+  \left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
+  &  & + \,
+  C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}
+  \label{eq:dampimg_constant_def}
+\end{eqnarray}
 where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
-neutral hydrogens and that of free electrons. Also, $C_{\mathrm{rad}}$,
-$C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are natural broadening,
-van der Waals broadening, and linear Stark broadening constants respectively.
-We simply adopt this parameterization along with the values of broadening
-constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
-$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and $C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.
-In terms of level populations and the Voigt profile, the line opacity
-for the transition $i\rightarrow j$ can be written as: \begin{equation}
-\chi_{l}=\frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}\left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)\label{eq:line_opacity}\end{equation}
+neutral hydrogens and that of free electrons. Also,
+$C_{\mathrm{rad}}$, $C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are
+natural broadening, van der Waals broadening, and linear Stark
+broadening constants respectively.  We simply adopt this
+parameterisation along with the values of broadening constants for
+H$\alpha$ from \citet{luttermoser:1992},
+i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
+$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and
+$C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.  In terms of level
+populations and the Voigt profile, the line opacity for the transition
+$i\rightarrow j$ can be written as: 
+\begin{equation}
+  \chi_{l} = \frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}
+  \left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)
+  \label{eq:line_opacity}
+\end{equation}
 where $f_{ij}$, $n_{i}$, $n_{j}$, $g_{i}$and $g_{j}$ are the
-oscillator strength, the population of $i$-th level, the population
-of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
-of the $j$-th level respectively. $m_{e}$and $e$ are the electron
+oscillator strength, the population of $i$-th level, the population of
+$j$-th level, the degeneracy of the $i$-th level, and the degeneracy
+of the $j$-th level respectively. $m_{e}$ and $e$ are the electron
 mass and charge (c.f. \citealt{mihalas:1978}).
 
-The second modefication in our model is the replacement of the method
-of solving the formal solution from the Monte Calro radiative transfer
-method with Sobolev approximation to the direct integration method.
-Similarly to the notation used by \citet{muzerolle:2001}, we specify
-the cylindical coordinates $\left(p,\, q,\, t\right)$ which is the
-original stellar coordinate system $\left(\rho,\,\phi,\, z\right)$
-rotated (around $y$ axis) by the inclination of the line of sight,
-i.e. the $t$-axis coinsides with the line of sight. The observed
-flux ($F_{\nu}$) is given by: \begin{equation}
-F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
+We further modified {\sc torus} by replacing the Monte Carlo line
+transfer algorithm with a direct integration method
+(c.f. \citealt{mihalas:1978}) for computing the observed flux as a
+function of frequence.  The integration of the flux is performed in
+the cylindrical coordinate system $\left(p,\, q,\, t\right)$ which is
+obtained by rotating the original stellar coordinate system
+$\left(\rho,\,\phi,\, z\right)$ around the $y$ axis by the inclination
+of the line of sight.  Note that the $t$-axis coincides with the line
+of sight with this rotation. The observed flux ($F_{\nu}$) is given
+by:
+\begin{equation}
+  F_{\nu}=\frac{1}{4\pi d^{2}}
+  \int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\,
+  I_{\nu}\mathrm{\, d}q\,\mathrm{d}p
+  \label{eq:flux_integral}
+\end{equation}
 where $d$, $p_{\mathrm{max}}$, and $I_{\nu}$ are the distance to
@@
 on observer at the outer boundary. For a given ray along $t$, the
-specific intensity is given by:\begin{equation}
-I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{-\infty}^{t_{0}}\eta_{\nu}\left(t\right)\, e^{-\tau\left(t\right)}\mathrm{d}t\label{eq:formal_sol_integral}\end{equation}
- where $I_{0}$ and $\eta_{\nu}$ are the intensity at the boundary
-on the opposite to the observer and the emissivity of the stellar
-atmosphere/wind at a frequency $\nu$. For a ray which intersects
-with the stellar core, $I_{0}$ is computed from the stellar stompshere
-mode of \citet{kurucz:1979} as descibed in section~\ref{sub:Contiuum-Source},
-and $I_{0}=0$ otherwise. The initial position of each ray is assigned
-to be at the center of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
-The code excution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
-where $n_{p}$ and $n_{q}$ are the number of cylindical radial and
-angluar points for the flux integration, and $n_{\nu}$is the number
-of frequency points. In the models presented in the next (section~\ref{sec:Results}),
-$n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
-otherwise. The linearliy spaced radial grid is used for the area where
-the ray intersects with magnetpshere, and the logarithmically spaced
-grid is used for the wind and the accretion disc regions.
+specific intensity is given by:
+\begin{equation}
+       I_{\nu} = I_{0}e^{-\tau_{\infty}} + 
+           \int_{t_{0}}^{t_{\infty}}S_{\nu}\left(t\right)\,
+                e^{-\tau}\mathrm{d}\tau
+ \label{eq:formal_sol_integral}
+\end{equation}
+where $I_{0}$ and $S_{\nu}$ are the intensity at the boundary on the
+opposite to the observer and the source function
+($\eta_{\nu}/\chi_{\nu}$) of the stellar atmosphere/wind at a
+frequency $\nu$. For a ray which intersects with the stellar core,
+$I_{0}$ is computed from the stellar atmosphere model of
+\citet{kurucz:1979} as described in
+section~\ref{sub:Continuum-Source}, and $I_{0}=0$ otherwise. If the
+the ray intersects with the hot ring on the stellar surface created by
+the accretion stream, we set
+$I_{0}=B_{\nu}\left(T_{\mathrm{ring}}\right)$ where $B_{\nu}$ is the
+Planck function and $T_{\mathrm{ring}}$ is the temperature of the hot
+ring.  The initial position of each ray is assigned to be at the
+centre of the surface element ($\mathrm{d}A=p\,\sin
+q\,\mathrm{d}q\,\mathrm{dp}$).  The code execution time is
+proportional to $n_{p}\, n_{q}\, n_{\nu}$ where $n_{p}$ and $n_{q}$
+are the number of cylindrical radial and angular points for the flux
+integration, and $n_{\nu}$ is the number of frequency points. In the
+models presented in the following section. $n_{p}=180$, $n_{q}=100$,
+and $n_{\nu}=101$ are used unless specified otherwise. A linearly
+spaced radial grid is used for the area where the ray intersects with
+magnetosphere, and a logarithmically spaced grid is used for the wind
+and the accretion disc regions.
 
 The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
-is defined as: \[
-\tau\left(t\right)\equiv\int_{-\infty}^{t}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
+is defined as: 
+\[
+\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'
+\]
 where $\chi_{\nu}$ is the opacity of media the ray passes through.
@@
 are computed at the intersections of a ray with the original AMR grid
-in which the opacity and emissivity infomation are stored. For high
-opticale depth models, additional points are inserted between the
-original points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$
-values are interpolated to those points to ensure $\mathrm{d}\tau<0.05$
-for the all ray segments.
+in which the opacity and emissivity information are stored. For high
+optical depth models, additional points are inserted between the original
+points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$ values are
+interpolated to those points to ensure $\mathrm{d}\tau<0.05$ for
+the all ray segments.
 
 For a point in the magnetosphere and the wind flows, the emissivity
-and the opacity of the media are given as:\begin{equation}
-\left\{ \begin{array}{rcl}
+and the opacity of the media are given as:
+\begin{equation}
+  \left\{ 
+  \begin{array}{rcl}
     \eta_{\nu} & = & \eta_{\mathrm{c}}^{\mathrm{H}}+\eta_{l}^{\mathrm{H}}\\
-\chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}+\sigma_{\mathrm{es}}\end{array}\right.\label{eq:emiss_opa_gas}\end{equation}
-where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$
-are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
-$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the contiuum,
-line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
-electron scattering opacity. Similarly, for a point in the accretion
-disc,
-
+    \chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}
+    +\sigma_{\mathrm{es}}
+  \end{array}
+  \right.
+  \label{eq:emiss_opa_gas}
+\end{equation}
+where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$ are
+the continuum and line emissivity of
+hydrogen. $\chi_{c}^{\mathrm{H}}$, $\chi_{l}^{\mathrm{H}}$, and
+$\sigma_{\mathrm{es}}$ are the continuum, line opacity
+(equation~\ref{eq:line_opacity}) of hydrogen, and the electron
+scattering opacity. Similarly, for a point in the accretion disc,
 \begin{equation}
-\left\{ \begin{array}{rcl}
+  \left\{ 
+  \begin{array}{rcl}
     \eta_{\nu} & = & 0\\
-\chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}+\kappa_{\mathrm{sca}}^{\mathrm{dust}}\end{array}\right.\label{eq:emiss_opa_dust}\end{equation}
- where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and $\kappa_{\mathrm{sca}}^{\mathrm{dust}}$
-are the dust absorption, and scattering opacity which are calculated
-using the dust property described in section~\ref{eq:grain-dist-function}.
-For computational simplicity, we assumed that the dust emissivity
-is zero. Since the disc mass of CTTS are rather small ($\sim0.1\,\mathrm{M_{\sun}}$)
-and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
-contribution at H$\alpha$ wavelength is expected to be neglegible
-(e.g.~\citealt{chiang:1997}). The scattering flux by the accretion
-may become important for H$\alpha$ for the edge-on ($i\sim90^{\circ}$)
-cases in which the disc obscures the stellar surface -- the main source
-of contiuum flux. We examine this effect later in section~\ref{sub:model-acc-disc-wind}.
+    \chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}
+    +\kappa_{\mathrm{sca}}^{\mathrm{dust}}
+  \end{array}
+  \right.
+  \label{eq:emiss_opa_dust}
+\end{equation}
+where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and
+$\kappa_{\mathrm{sca}}^{\mathrm{dust}}$ are the dust absorption, and
+scattering opacity which are calculated using the dust property
+described in section~\ref{eq:grain-dist-function}.  We neglect the
+emissivity from the disc: since the disc mass of CTTS are rather small
+($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($<\sim
+1600\,\mathrm{K}$), the continuum flux contribution at H$\alpha$
+wavelength is expected to be negligible (e.g.~\citealt{chiang:1997}).
 
@@
 
-Using the standard parameters (Table~\ref{tab:std_parameters}) for
-the central star and the magentosphere, we examine the dependency
-of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
-flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
-done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
-is computed from the avilable kinetic energy of the free-falling gas
-as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
-used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
-of their models. The accretion luminosity ($L_{\mathrm{acc}}$) of
-models with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-is about a half of the total luminosity (without the hot ring) of
-the star, and $L_{\mathrm{acc}}$is proportional to $\dot{M}_{\mathrm{acc}}$.
-The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
-dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are
-similar to that of \citet{muzerolle:2001}. In general, the line strength
-becomes weaker as the accretion rate and the temperature become smaller.
-The red-shifted absorption becomes less visible for higher accretion
-rate and temperature models in which the flux in the damping wings
-become important. Figure~\ref{fig:broadening} shows an example of
-the effect of the boradening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
-due to the damping constants as described in section~\ref{sec:radiative-transfer-model}.
-Although the maximum flux of the model with the broadening is almost
-identical to that of the model with no damping constant ($\Gamma=0$),
-a significant increase of the line flux in both red and blue wings
-of seen in the model with broadening. A weak red-shifted absorption
-component (which is a signiture of the magnetospherical accretion)
+Using the reference model parameters (Table~\ref{tab:std_parameters}) for the
+central star and the magnetosphere, we examine the dependency of
+H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion flow
+and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as
+done by \citet{muzerolle:2001} for H$\beta$. We note that here we have
+ computed the hot ring temperature self-consistently, whereas \citet{muzerolle:2001} used
+a constant hot ring temperature ($8000\,\mathrm{K}$) for most of
+their models.  The accretion luminosity ($L_{\mathrm{acc}}$) for models
+with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ is
+about a half of the photospheric luminosity.
+
+H$\alpha$ line profiles for a range of $T_{\mathrm{max}}$ and
+$\dot{M}_{\mathrm{acc}}$ are presented in  Figure~\ref{fig:atlas_acc_models}. 
+The  overall dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ is similar to that of
+\citet{muzerolle:2001}. In general, the line strength weakens
+as the accretion rate and the temperature drop.  The
+red-shifted absorption becomes less visible for the higher accretion rate
+and higher temperature models as it becomes filled-in by the stronger Stark-broadened
+line-wing emission.
+
+We demonstrate this effect in Figure~\ref{fig:broadening}, which shows an example 
+for an H$\alpha$  model with $T_{\mathrm{max}}=7500\,\mathrm{K}$
+and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, both with and without
+damping.  Although the maximum flux of the model with broadening is almost identical to that of the
+model with no damping constant ($\Gamma=0$), a significant increase of
+the line flux in both red and blue wings of seen. The weak red-shifted
+absorption component (which is a signature of the magnetospheric accretion)
 is weakened or eliminated by the flux in broadened wing.
 
-Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown
-in Figure~\ref{fig:atlas_acc_models}. About a half of the models
-shown the figure agree with the observed EW values of H$\alpha$ from
-30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
-ranges from $\sim3$~\AA\, to $\sim160$~\AA, and the mean to
-be $\sim55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
-the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
-and for some models the EWs are negative. Since the target selection
-criteria of \citet{alencar:2000} is not stated in their paper, we
-can not conclude that these low $\dot{M}_{\mathrm{acc}}$models disagree
-with the observation. \citet{reipurth:1996}, who measured the EW
-of 43 TTS and found similar distribution of EW values, mentioned that
-their EW measurements are underrepresenting real samples since the
-selection of the targerts are based on the strong H$\alpha$ emission
-in H$\alpha$ surveys.
-
-The dependency of the profile on the inclination angle ($i$) is demonstrated
-in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
-paramters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
-The figure show that the peak (normalized) flux decrease as the inclination
-angle increases. Similarly, the equivalent width also decreases as
-the inclination increases. Because of the geometry of the magnsepsherical
-accretion (c.f. Figure~\ref{fig:overview}) and of the presence of
-the gas with the highest velocity close to the stellar surface, the
-highest red-shifted line-of-sight velocity is visible only at the
-high incination angles. This explains the wider appearence of the
-profile with $i=80^{\circ}$compared to the relatively narrow line
-appearence of the profile with $i=10^{\circ}$. Although not show
-here, a similar depdency on the inclination angle is found for the
-models with different temperatures ($T_{\mathrm{max}}=6500$, $8500$,
-$9500\,\mathrm{K}$).
-
-As seen in the models of \citet{hartmann:1994} and \citet{muzerolle:2001},
-our models also show the blue-shifted peak and the blue-ward asymmetry
-caused by the occultation of the accretion flow by the equotrial disc
-and the stellar disc. On the hand, \citealt{alencar:2000} (see their
-Fig.~9) found a substential fraction of the observed H$\alpha$ profiles
-also shows the {}``red-shifted'' peak, and the P~Cygni profiles
-which can not be explained by the magnetospherical accretion model
-alone. In addition, a recent study by \citet{appenzeller:2005} showed
-that the equivalent width of H$\alpha$ increases as the inclination
-angle increases. Our model with the magnetospherical accreation flow
-clearly disagrees with their finding.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+Table~\ref{tab:ha_ew_acc_models} shows the equivalent width (EW) for
+the models in Figure~\ref{fig:atlas_acc_models}.  The EWs for half the
+models fall within the range of EWs ($\sim 3$~\AA\, to $\sim 160$~\AA)
+measured by \citet{alencar:2000}. The EWs of models 
+with the lowest mass accretion rates fall below the minimum EW
+observed by  \citet{alencar:2000}, while several models would
+be designated as weak-lined T~Tauri stars (WTTS) using the traditional
+10\,\AA\ cut-off \citep[e.g.][]{herbig:1988}.
+
+xxxx Changed xxxxx
+
+\citet{white:2003} empirically showed that the full width of H$\alpha$ at 10
+per~cent of its peak flux (10 per~cent width) is a better
+indicator for an accretion than the EW criteria. They proposed that a
+T~Tauri star shows the 10 per~cent width greater than
+$270\,\mathrm{km\,s^{-1}}$, the star should be a CTTS. The 10 per~cent
+widths of the model H$\alpha$ profiles
+(Figure~\ref{fig:atlas_acc_models}) are summarised in
+Table~\ref{tab:ha_ten_percent_acc_models}.  Using the criteria of
+\citet{white:2003}, the half of the models shown in the figure can be
+classified as CTTS, and the other half as WTTS.
+
+The dependency of the line profile on inclination angle ($i$) is
+demonstrated in Figure~\ref{fig:acc_inclination_effect}. The model
+has  $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
+$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).  The
+figure shows that the peak (normalised) flux decreases as the
+inclination angle increases, as does the EW.  The line flux and the
+EWs decreases since the fraction of the accretion stream blocked by
+the photosphere increases as the inclination increase.
+
+xxxx Changed xxxxx
+
+Because of the geometry of the
+magnetospheric accretion (c.f. Figure~\ref{fig:config_dipolar}) and of
+the presence of the gas with the highest velocity close to the stellar
+surface, the highest red-shifted line-of-sight velocity is visible
+only at the high inclination angles. This explains the wider
+appearance of the profile with $i=80^{\circ}$compared to the
+relatively narrow line appearance of the profile with
+$i=10^{\circ}$.  A similar EW dependence on
+inclination angle is found for the models with different 
+magnetospheric temperatures and the mass-accretion rates.
+
+Our models show a blue-shifted line peak and
+a blueward asymmetry caused by occultation of the accretion
+flow by the stellar photosphere (see also \citet{hartmann:1994} and
+\citet{muzerolle:2001}). However, \citealt{alencar:2000} (see their Fig.~9)
+found a substantial fraction
+of the observed H$\alpha$ profiles show a red-shifted
+peak. Furthermore, a recent study by
+\citet{appenzeller:2005} demonstrated  that the equivalent width of H$\alpha$
+from CTTS {\em increases} as the inclination angle increases. 
+Clearly a magnetospheric accretion only model cannot explain the
+full properties of the H$\alpha$ profiles in CTTS.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
       clip,
-  scale=0.45]{figures/atlas_ha_i55_acc_model_new3.eps}
+      scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}
 
@@
 
-\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M_\mathrm{acc}}$) and temperature ($T_{\mathrm{max}}$).
-The profiles are computed using only magnetospherical accretion flow (i.e.
-no wind/jet).
-All the profiles are computed using the parameters of the 'standard' model (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the mass accretion rate (indicated by the values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from left to right.
-The profiles are similar to those of \citet{muzerolle:2001}, available on-line (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html).
-}
+  \caption{H$\alpha$ model profiles for wide ranges of mass accretion
+    rate ($\dot{M}_\mathrm{acc}$) and temperature
+    ($T_{\mathrm{max}}$). The profiles are computed using only the
+    magnetospheric accretion flow (i.e. no outflow).  All the profiles
+    are computed using the parameters of the reference model
+    (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The
+    temperature (indicated along the vertical axis) of the model increases
+    from top to bottom, and the mass accretion rate (indicated by the
+    values in $\mathrm{M_{\odot}\,yr^{-1}}$ along the top) increases from
+    left to right. }
 
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.59]{figures/broadening.eps}
+
+  \end{center}
+
+  \caption{The effect of line broadening on H$\alpha$. A model
+    computed with a damping constant ($\Gamma$), described in
+    section~\ref{sec:radiative-transfer-model} (solid), is compared with
+    a model with no damping, $\Gamma=0$ (dashed).  Both models are
+    computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
+    reference parameters given in Table~\ref{tab:std_parameters}. The two
+    models have similar peak flux levels (around $V \sim 0~\kmps$), but
+    the total flux and the EW of the line increased drastically for the
+    model with the damping constant. The broad wings extend to $\sim \pm
+    800 \kmps$.  The redshifted absorption feature (very weakly) seen in
+    the $\Gamma=0$ model is not seen in the model with the broadening.  }
+
+  \label{fig:broadening}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.59]{figures/acc_inc_effect.eps}
+
+  \end{center}
+
+  \caption{The dependency of the H$\alpha$ profile on inclination ($i$).  The
+    profiles are computed with a magnetospheric accretion flow only using
+    the reference parameters given in Table~\ref{tab:std_parameters} and
+    $T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
+    are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$
+    respectively. As the inclination becomes larger, the peak flux and the
+    equivalent width of the line becomes smaller.  }
+
+  \label{fig:acc_inclination_effect}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}
+
+\caption{Summary of H$\alpha$ equivalent widths (\AA) from the
+magnetospheric accretion flow models shown in
+Figure~\ref{fig:atlas_acc_models}. Note that the equivalent widths are
+positive when the lines are in emission.}
+
+\label{tab:ha_ew_acc_models}
 
@@
 
-\caption{The summary of H$\alpha$ equivalent widths from the magnetospherical accretion flow models show in Figure~\ref{fig:atlas_acc_models}.}
-
-\label{tab:ha_ew_acc_models}
-
 \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+
+\caption{Summary of 10 per~cent widths ($\mathrm{km\,s^{-1}}$) from the
+magnetospheric accretion flow models shown in
+Figure~\ref{fig:atlas_acc_models}.}
+
+\label{tab:ha_ten_percent_acc_models}
+
+\begin{center}
+
+\begin{tabular}{cccc}
+\hline 
+$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
+&
+$\dot{M}_{\mathrm{acc}}$ ~$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
+\tabularnewline
+&
+$10^{-7}$&
+$10^{-8}$&
+$10^{-9}$\tabularnewline
+\hline 
+$6500$&
+$300$&
+$120$&
+$100$\tabularnewline
+$7500$&
+$360$&
+$145$&
+$120$\tabularnewline
+$8500$&
+$790$&
+$330$&
+$130$\tabularnewline
+$9500$&
+$1530$&
+$520$&
+$200$\tabularnewline
+\hline
+\end{tabular}
+
+\end{center}
+
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
       clip,
-  scale=0.45]{figures/broadening.eps}
+      scale=0.45]{figures/disc_wind_acc_mdot_effect.eps}
 
@@
 
-\caption{Effect of the line broadening for H$\alpha$.
-The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the one with no damping constant, $\Gamma=0$ (dashed).
-Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}.
-The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant.
-The broaded wings extend to $\sim \pm 900 \kmps$.
-The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.
-}
-
-\label{fig:broadening}
+  \caption{The effect of the mass-loss rate to mass-accretion rate
+    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
+    H$\alpha$ profile computed with only the magnetospheric accretion
+    (thick solid) is compared with the magnetosphere--wind--disc
+    hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1
+    (dot) and 0.2 (dash). The magnetosphere used here has
+    $T_{\mathrm{max}}=7500\,\Kelvin$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
+    temperature and the acceleration parameter of the bipolar wind are
+    $T_{\mathrm{wind}}=7000\,\Kelvin$ and $\beta=2.0$ respectively.
+    All the models are computed with the inclination angle
+    $i=55^{\circ}$. As $\mu$ increases the P-Cygni absorption deepens
+    and the emission component becomes stronger. In general, the
+    absorption is too strong for the models with $\mu>0.025$ compared
+    to the observations (e.g., \citealt{reipurth:1996}).}
+
+  \label{fig:effect_mdot_disc_wind_acc}
 
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{The disc-wind model}
+
+\label{sub:result-discwind-knigge}
+
+In this section we examine profiles produced using our alternative
+kinematic model of the outflow: the disc wind. This type of outflow
+has been predicted by several MHD calculations (e.g. \citet{koenigl:2000};
+ \citealt{krasnopolsky:2003}), and broadly consists of a wind with
+a latitudinal density-dependence with density increasing towards
+the equator (see~\ref{sub:model-disc-wind}), in contrast with the 
+bipolar stellar wind.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
 
@@
       clip,
-  scale=0.45]{figures/acc_inc_effect.eps}
+      scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}
 
@@
 
-\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).
-The profiles are computed with the magneospherical accretion flow using the standard parameters given in Table~\ref{tab:std_parameters} and $T_{\mathrm{max}}=7500~\Kelvin$.
-The solid, dotted, and dashed lines are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$ respectively.
-As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.
-Similar dependency is seen in the models with $T_{\mathrm{max}}=6500, 8500, 9500$~K (not shown here).
-}
-
-\label{fig:acc_inclination_effect}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Collimated Wind}
-
-\label{sub:model-wind}
-
-As mentioned in earlier, the magnetopsherical accretion flow model
-alone cannot explain some of the feartures seen in observations. As
-an alternative model, we now examine formation of H$\alpha$ in a
-simple collimated wind as described in section \ref{sub:wind_jet}.
-The basic wind model parameters introduced earlier are $\gamma$,
-$\beta$, $v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
-and $\dot{M}_{\mathrm{wind}}$. To minimize the number of parameters
-to be explored, we initially adopte $\gamma=0.05$, $v_{\infty}=200\,\kmps$
-\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-Futher, the angular extent of the wind is assumed to be close to the
-edge of the accretion disc, i.e. $\theta_{\mathrm{wind}}=80^{\circ}$;
-however, in this section, a simple optically-thick and geometrically-thin
-(i.e. opaque and zero-thickness) disc instead of the standard $\alpha$-disc
-(section~\ref{sub:Accretion-disc}) is used in all models for speed.
-The effect of replacing the geometrically thin disc with the $\alpha$-disc
-will be discussed later in this section. The degree of collimination
-is initially chosen to be $b=4$, i.e. the ratio of the density in
-polar direction to the density at the edge of the wind closest to
-the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
-for given radii. With these parameters kept constant, we examine the
-characterstics of H$\alpha$ profiles, as a function of the wind accereation
-paramter $\beta$ and the isothermal wind temperature $T_{\mathrm{wind}}$.
-Dependency on the other parameters will be discussed later in this
-section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+  \caption{H$\alpha$ profiles computed with the disc-wind only.
+     The wind mass-loss rate is fixed at
+    $\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, and the line
+    profiles are computed with different combinations of the wind
+    acceleration rate ($\beta$) and isothermal disc-wind temperature
+    ($T_{\mathrm{dw}}$). The wind emission grows as the values of
+    $\beta$ and $T_{\mathrm{wind}}$ increase.   As in the
+    bipolar wind models (Figure~\ref{fig:atlas_wind_model}), the position
+    of the wind absorption moves toward the line centre as $\beta$ becomes
+    larger.     }
+
+  \label{fig:atlas_discwind_only}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
       clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_model.eps}
+      scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
 
@@
 
-\caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$).
-The profiles are computed with only wind/jet (no magnetospherical accretion flow).
-The parameters of the 'standard' model (Table~\ref{tab:std_parameters}) are used.
-The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the wind accerelation rate increases from left to right.
-The P~Cygni profile are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow accerelation) models.
-The postion of the absorption the component moves toward the line centre as $\beta$ increases.
-The effect of line broadening becomes more prominant for higher $T_\mathrm{wind}$ and higher $\beta$ models.}
-
-\label{fig:atlas_wind_model}
+  \caption{The disc-wind, magnetosphere hybrid model. These models
+  (solid lines) have the  same parameters as
+    Figure~\ref{fig:atlas_discwind_only}, but  also
+    include the magnetospheric accretion flow
+    ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
+    the emission from the magnetosphere dominates for the models with
+    smaller $\beta$ and $T_{\mathrm{dw}}$, the emission from the wind dominates the
+    profiles for models with larger $\beta$ and $T_{\mathrm{dw}}$.  The contribution
+    of the magnetosphere can be judged from the profiles computed with
+    the magnetosphere only (dotted lines).}
+
+  \label{fig:atlas_discwind_acc_model}
 
 \end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The results are shown in Figure~\ref{fig:atlas_wind_model}. The
-P~Cygni profile are seen only in the models with lower $T_{\mathrm{wind}}$
-and $\beta$ (colder and faster accerelation wind). As the value of
-$\beta$ increases, the postion of the blue-shifted absorption component
-moves toward the line centre. For the slowest wind accerelation models
-($\beta=4.0$), the absorption components appear to be located at
-the line centre, giving the appearence of the double-peak emission
-profile. The line strength is very senstive to the temperature of
-the wind. Although the line should be also sensitive to the temperature
-structure of the wind itself, determination of a self-consistent wind
-temperature is beyound the scope of this paper. Readers are refered
-to \citet{hartmann:1982} in which the wind temperature structure
-is determined by balancing the radiative cooling rate (assuming optically
-thin) with the MHD wave heating rate.
-
-The effect of line broadening becomes more prominant for higher $T_{\mathrm{wind}}$
-and higher $\beta$ models. Unlike the magnetospherical accretion
-only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
-profiles are not seen here. Interestingly, in some models (e.g. $T_{\mathrm{wind}}=9000\,\mathrm{K}$
-and $\beta=1.0$ model), the absorption componet is present at slightly
-red-ward of the line centre, causing the blue-ward asymmetry seen
-in the magnetospherical accretion models. The blue-ward asymetry are
-caused by: 1. the accretion disc placed at the equotorial plane and
-the finited-size steller disc blocking a part of the line emission
-region moving away from an observer, 2.~the much larger optical depth
-for the line emitted from the opposite side of the observer where
-the gas is moving away from the observer. Because of the broad wings
-of the Voigt profile, the line photon intereacts with the gas with
-much wider range of the projected velocity space.
-
-The dependency of the profile on the wind anisotoropy parameter $b$
-is demonstrated in Figure~\ref{fig:effect_wind_b_param}. The line
-peak closer to the line centre and the profile becomes slightly more
-symmetric around the line centre for the isotropic ($b=0$) compared
-to the cases with the colliminated wind ($b=4$). The P~Cygni profile
-feature become prominant for the spherical wind models (especially
-in $\beta=0.5$ model) because the collumn density of along the line
-of a sight of the observer at a medium inclination angle ($i=55^{\circ}$)
-increases as the wind becomes more spherical for a given value of
-the wind mass-loss rate.
-
-Next, we examine the effect of the size of the inner radius of the
-disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_thin_disc}
-shows the wind emission profile computed with and without the equotorial
-accretion disc. The latter can be also considered as a model with
-a large inner radius of the accretion disc in which none of the wind
-emission region is not blocked provided the inclination is moderate.
-The profile shapes of the models are very similar to each other, but
-the one without the accretion disc is slightly more symmetric than
-the other. As one expects, the line equivalent width of the model
-without the disc is about twice of the model with the disc. Interestingly,
-the blueward asymmetry is present also in the profile computed without
-the disc. This is mainly caused by the occultaion of a part of emission
-region by the steller disc and the fact that the wind (density distribution)
-is asymmetric. The H$\alpha$ image (project in the plane of the observer
-at the location of the star) for the model with the disc (middle panel)
-and that for the model without (right plane) are also shown in the
-same figure. The images weere computed with a fast wind accereation
-rate ($\beta=0.5$). The extent of the line emission is smaller ($\sim0.2\,\mathrm{AU}$
-or $\sim20\, R_{*}$) compared to the spectro-astrometric observations
-of \citet{takami:2003} for RU~Lup and CS Cha which have 1--5 AU
-scale outflows%
-\footnote{\citet{takami:2003} also showed that some objects (e.g~Z CMa and
-AS~353A) show the outflows of larger scale ($>50\,\mathrm{AU}$)
-which could be formed by shocks rather than MHD-wave heating (e.g.
-\citealt{hartmann:1982}) or X-ray heating (e.g.~\citealt{shang:2002}). %
-}; however, if a slower wind acceration rate ( $\beta=4$) is the emission
-region become larger slightly ($\sim0.4$~AU).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Firstly, we consider the disc-wind models without the magnetosphere.
+Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
+computed using only the disc-wind component
+(c.f. Figure~\ref{fig:config_discwind}) for the same isothermal
+disc-wind temperature ($T_{\mathrm{dw}}$) and the wind acceleration
+parameter ($\beta$) ranges used for the bipolar wind models
+(c.f. Figures~\ref{fig:atlas_wind_model} and
+\ref{fig:atlas_disc_wind_acc_model}).  The parameters used for the
+central star are as in section~\ref{sub:Continuum-Source}, and the
+disc-wind parameters are summarised in
+Table~\ref{tab:std_discwind_parameters}.  The figure shows that the
+wind emission increases as $\beta$ and $T_{\mathrm{dw}}$ increase. The
+$\beta$ dependence arises simply because for large $\beta$ there is a
+greater mass of wind material close to the star.  As with the bipolar
+wind models, the location of the P-Cyg absorption component moves
+toward the line centre as $\beta$ increases.
+
+The morphology of the profile exhibited by the model changes from
+FU-Ori type (c.f.~\citealt{reipurth:1996}) for the models with small
+$\beta$ to the stronger emission types which are more commonly seen in
+the observed H$\alpha$ (c.f.~\citealt{reipurth:1996}) as the value of
+$\beta$ increases.  We find that the profile shapes are relatively
+insensitive to the value of the wind collimation parameter $d$. The
+dependency on the disc wind mass-loss rate of the profile shape is
+similar to that of the bipolar wind models
+(Figure~\ref{fig:effect_mdot_disc_wind_acc}).
+
+We now consider the models computed with a combination of the
+disc-wind and the magnetospheric accretion components. The
+parameters used for the magnetosphere are set to be same as in the
+case for Figure~\ref{fig:acc_inclination_effect}.  
+The mass-loss rate of the disc wind is set to
+$\dot{M}_{\mathrm{dw}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+(i.e.~$\mu=\dot{M}_{\mathrm{dw}}/\dot{M}_{\mathrm{acc}}=0.1$).
+Figure~\ref{fig:atlas_discwind_acc_model} shows the models profiles
+computed using the same ranges of the disc-wind temperature and the
+wind acceleration parameter as in the previous cases.
+
+As in the disc-wind only models
+(Figure~\ref{fig:atlas_discwind_only}), the location of the absorption
+component moves toward the line centre as the value of $\beta$
+increases.  The figure shows that in
+the models with smaller $\beta$ and $T_{\mathrm{dw}}$, the line
+emission from the magnetosphere dominates, while this situation reverses for the
+models with larger $\beta$ and $T_{\mathrm{dw}}$. The model with
+$\left(T_{\mathrm{dw}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
+results in an H$\alpha$ profile that is far too strong to be compatible
+ with observations (\citet{reipurth:1996} and \citet{alencar:2000});
+ however, the lower mass-loss rate models (while keeping $\mu$ constant)
+ produce the profiles with the line strengths comparable to observations.
+Although the models in Figure~\ref{fig:atlas_discwind_acc_model} are
+computed with limited ranges of  $T_{\mathrm{dw}}$ and $\beta$, the
+resulting profiles exhibit a wide variety of line profile shapes,
+many of  which are similar to the types of H$\alpha$ profiles seen in the
+observations (c.f.~\citealt{reipurth:1996}).
+
+An examination of the profiles in Figures~\ref{fig:atlas_discwind_only} and
+Figure~\ref{fig:atlas_discwind_acc_model} reveals some of problems
+with uniqueness that must inevitably occur when trying to assign
+an individual profile as wind or accretion dominated i.e. very similar profiles may arise
+from very different circumstellar geometries. For example, the disc-wind
+only model with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
+ (in Figures~\ref{fig:atlas_discwind_only}) and the  accretion dominated model with
+ $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
+(in Figure~\ref{fig:atlas_discwind_acc_model}) give very similar profiles.
+
+xxxx paragraph below may need changing after new models are added xxxx
+
+The general characteristics of the profiles from the disc-wind, magnetosphere
+hybrid model (Figure~\ref{fig:atlas_discwind_acc_model}) are very
+similar to those of the disc, bipolar wind, magnetosphere hybrid
+model (Figure~\ref{fig:atlas_disc_wind_acc_model}). The main difference
+between these two sets of models is in the ratio of the mass-loss rate to the mass
+accretion rate, $\mu$. While the models presented in this section
+use $\mu=0.1$ which is consistent with the MHD jet models (e.g.~\citealt{koenigl:2000}),
+the models in Figure~\ref{fig:atlas_disc_wind_acc_model} use much
+smaller value ($\mu=0.01$).   The dependency of the model profiles on
+the inclination angle for the two different wind models will be discussed
+in the next section.
+
+\begin{table}
+
+\caption{A summary of the reference disc-wind model parameters used
+in section~\ref{sub:result-discwind-knigge}. See also
+section~\ref{sub:Alternative-model-disc-wind}.}
+
+\label{tab:std_discwind_parameters}
 
@@
 
-\begin{tabular}{cc}
+\begin{tabular}{ccccccc}
+\hline 
+$d$&
+$R_{\mathrm{wi}}$&
+$R_{\mathrm{wo}}$&
+$\dot{M}_{\mathrm{dw}}$&
+$p$&
+$f$&
+$R_{\mathrm{s}}$\tabularnewline
+$\left[R_{*}\right]$&
+$\left[R_{*}\right]$&
+$\left[\mathrm{au}\right]$&
+$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
+$[-]$&
+$[-]$&
+$\left[R_{*}\right]$\tabularnewline
+\hline
+$21.4$&
+$3.0$&
+$1.0$&
+$10^{-8}$&
+$-3/2$&
+$2.0$&
+$30$\tabularnewline
+\hline
+\end{tabular}
+
+\end{center}
+
+\end{table}
+
+\section{Discussion}
+
+\label{sec:Discussion}
+
+\subsection{Classification scheme proposed by Reipurth et. al (1996)}
+
+\label{sub:Classification-scheme-proposed}
+
+\citet{reipurth:1996} proposed the two-dimensional classification
+of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
+stars. Their classification scheme contains four classes (I, II, III
+and IV) differentiated by the ratio of the secondary-to-primary emission
+components in the profiles. Each classes are divided into two sub-classes
+(B and R) which depends whether the absorption component is on the
+blue or red side. Readers are refereed to Fig.~4 of their paper.
+Figure~\ref{fig:atlas_reipurth} shows the sample model profiles
+which are classified according to the definition of \citet{reipurth:1996}.
+The combination of the disc wind, magnetospheric accretion, and
+accretion disc can reasonably reproduce all the classes of the profiles
+seen in observations. Similar profiles can be reproduced if the bipolar
+wind is used instead of the disc wind, but the wind absorption at
+a given velocity location occurs at a different inclination angles
+when the wind type is switched from the bipolar wind to the disc wind.
+The corresponding parameters (of the disc-wind, magnetosphere,
+hybrid model) used to reproduce the profiles
+in the figure are given in Table~\ref{tab:classification} along
+with brief comments on possible physical conditions which leads to
+the profiles in each class. In the following, we will discuss each 
+classification type of \citet{reipurth:1996} based on our model
+results.
+
+\textbf{Type~I}: 
+Using the samples of H$\alpha$ from 43 CTTS, \citet{reipurth:1996}
+found this type to be the second most common (26~per~cent) among
+them. Type~I (symmetric around line centres), is mainly
+produced in the magnetosphere.  Although not shown here, this type of
+profile can be also reproduced with the disc-wind, magnetosphere hybrid
+model with low inclination angles ($<\sim10^\circ$).  Since there is
+no material in the polar region in the disc wind model, the observer
+can look the magnetosphere almost directory for high inclination
+cases, provided that wind temperature is low enough so that the wind
+emission is negligible. The bipolar wind, magnetosphere and accretion
+hybrid model with high inclination ($70^\circ$ -- $80^\circ$) can also 
+give this type of profile since the influence of the bipolar wind is
+minimum in the equatorial directions. The wind acceleration parameter
+for the bipolar wind must be relatively small  ($\beta < \sim 0.5$).
+
+\textbf{Type~II-B}:  
+This type can be produced by the disc-wind magnetosphere hybrid models
+at moderate to high inclination angles with wide ranges of the wind
+acceleration rate ($\sim 0.2 < \beta < \sim 2.0$) and the wind
+temperature ($\sim 7000\,\mathrm{K}< T < \sim 9000 \mathrm{K}$). If
+the inclination is high ($i \sim 80^\circ$), the disc-wind
+acceleration parameter should be relatively small ($\beta < \sim
+0.5$). If the inclination is moderate ($i \sim 60^\circ$), the wind
+acceleration parameter should be relatively high ($\beta > \sim 2.0$).
+This type can be also produced in the bipolar wind, magnetosphere disc
+hybrid model with similar ranges of inclinations ($\sim 60^\circ < i <
+\sim 80^\circ$) and temperatures ($\sim 7000\,\mathrm{K}< T < \sim
+9000 \mathrm{K}$), but the wind acceleration should be always high
+($\beta > \sim 1.0$).
+
+\textbf{Type~II-R}:  
+The physical conditions which result in this type
+is very similar to those of Type~II-B according to the disc-wind
+magnetosphere hybrid models. The main difference is between 
+the two is in their inclination angles. This type is more likely
+seen at higher inclination angles ($i \sim 80^\circ$) compared to Type
+II-B.  
+With the bipolar wind model, the wind acceleration parameter must be
+very large ($\beta \sim 6.0$) to produce this type, and the
+inclination must be moderate to low ($i < \sim 60^\circ$).  This type
+is rarely seen in the bipolar wind models with the nominal parameter
+ranges i.e. $\sim 0.2 < \beta < \sim 2.0$ and $\sim 7000\,\mathrm{K}<
+T < \sim 9000 \mathrm{K}$.  More common in the models with the disc wind.
+
+\textbf{Type~III-B}:
+This type is the most commonly seen profiles in the CTTS H$\alpha$
+samples in \citet{reipurth:1996}. Interestingly, the most common
+profile type seen in both the bipolar wind, disc, magnetosphere hybrid
+models and the disc-wind, magnetosphere hybrid model are Type~III-B
+profiles (c.f.~Figures~\ref{fig:atlas_disc_wind_acc_model} and
+\ref{fig:atlas_discwind_acc_model}). In this type of profiles, the
+main emission comes from the magnetosphere, and the profile shape is
+altered from a slightly blue-asymmetric one to a slightly
+red-asymmetric one via the wind absorption in the blue wing.  In the
+models with the disc-wind, the acceleration parameter should be
+relatively small ($\beta<0.5$). The profile type changes from Type
+III-R to Type~II-R if the value of $\beta$ increases. The
+inclination angles must be moderate to high ($\sim 60^\circ <i <
+\sim 80^\circ$).  On the other hand, the inclination must be low to
+moderate ($i < \sim 60^\circ$) in the models with the
+bipolar wind.  The difference in the inclination dependency occurs
+since the density distribution of the two types of the winds are
+different.
+
+\textbf{Type~III-R}: 
+This is the least common type of the observed profile (2~per~cent)
+according to \citet{reipurth:1996}. Incidentally, we also found it
+difficult to reproduce this type of profile since this can be achieve
+only at narrow range of parameter space (very high inclination angle
+with a disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
+$\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+Similarly, in the models with the bipolar wind, the inclination angle
+must be very high (close to edge on) to produce this type of profile.
+Since the inclination angles must be high for both wind models, this
+indicates that the accretion disc plays an important role in producing
+this type of the profile, but not the wind.  The rareness of this type in
+the observation can be understood by the required high inclination
+angle (almost edge-on) in our models.
+
+\textbf{Type~IV-B}: 
+This type of the profiles is very similar to Type III-B, but the wind
+in this type of profile may be accelerating faster (a smaller $\beta$
+value) than that in Type~III-B.  In the models with the disc-wind,
+this type is seen at moderate to high inclinations ($\sim 60^\circ <i
+\sim 80^\circ$) with relatively small value of the acceleration
+parameters ($\beta < \sim 0.5$).  In the models with the bipolar wind,
+this type is commonly seen at moderate to low inclinations (($i \sim <
+60^\circ$).  The difference in the inclination dependency occurs
+because of the density distribution of the two types of the winds are
+different.
+
+\textbf{Type~IV-R}: 
+This is the second least common type of observed profile (5~per~cent)
+which shows the inverse P-Cyg profile shape.  This can be understood
+since the magnetospheric accretion model of \citet{hartmann:1994}
+predicts that the redshifted absorption can occur at a limited range
+of inclination angle ($i= \sim 50^\circ$, but depends on the geometry of
+the magnetosphere) with which the hot continuum flux from the
+footprint of the magnetosphere is seen through relatively fast moving
+gas in the accretion stream.  The wind component must be very
+weak. The mass-accretion rate should be much lower
+($\dot{M}_{\mathrm{acc}} \sim 10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$)
+than that of the models which produce Type~I profiles since the flux
+in the broadening wings can not be too high to produce the inverse
+P-Cyg profile.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
     \includegraphics[%
       clip,
-  scale=0.45]{figures/wind_b_effect.eps}&
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/windonly_B_effect.eps}\tabularnewline
-\end{tabular}
+      scale=0.65]{figures/atlas_reipurth_like_discwind.eps}
 
@@
 
-\caption{The effect of wind collimation.
-The dependecy of the line profiles on the wind anisotropy parameter $b$ for the models with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$  is shown on left, and that with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 1.0\right)$ on right.
-All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.
-The degree of the blue-ward asymmetry of the profiles is slightly lower for the spherical (isotroptic) wind model ($b=0$, dashed) compared to the collimated wind (anisotoropic) wind models ($b=4$, solid).
-The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind.
-}
-
-\label{fig:effect_wind_b_param}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{ccc}
-\includegraphics[%
-  clip,
-  scale=0.3]{figures/disc_nodisc_compare.eps}&
-\includegraphics[%
-  scale=0.3,
-  angle=270,
-  origin=lt]{figures/wind_thindisc.eps}&
-\includegraphics[%
-  scale=0.3,
-  angle=270,
-  origin=lt]{figures/wind_nodisc.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{Comparison of of the wind model with and without the optically-thick and geometrically-thin disc.
-The latter can be also equivalent to a model with a large inner radius of the accretion disc in which none of the wind emission region is not blocked provided the inclination is moderate.
-The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used).
-The line profile of the model with the disc (solid) is similar to the model without the disc (dashed), but the latter is slightly more symmetric than the former.
-The line equivalent width of the model without the disc is about 2 times that of the model with the disc.
-The blueward asymmetry is present also in the profile computed without the disc.
-The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown.
-The image flux is computed by integrating the specific flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$.
-The flux is in an arbitrary units and in logarithmic (base $10$) scale.
-}
-
-\label{fig:effect_thin_disc}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magnetosphere $+$ wind}
-
-\label{sub:model-acc-wind}
-
-Next, we examine the characteristics of the line profiles arising
-from the combination of the magnetospherical accretion flow and the
-wind. For simplicity, we fix the parameters for the magnetosphere
-($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-as in Figure~\ref{fig:atlas_acc_models}), and use the constant wind
-mass-loss rate $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$). Figure~\ref{fig:atlas_wind_acc_model}
-shows the results for $i=55^{\circ}$ and the same combinations of
-$T_{\mathrm{wind}}$ and $\beta$ used in section~\ref{sub:model-acc-wind}
-(Figure~\ref{fig:atlas_wind_model}).
-
-While the emission from the magnetosphere dominates for the models
-with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation
-and the colder wind models), the emission from the wind dominates
-for the models with larger $\beta$ and $T_{\mathrm{wind}}$ (the
-slower accerelation and the hotter models). The P~Cygni profile feature
-becomes less prominant in some of the models because the additional
-emission from the magnetosphere extending in the wings. In most of
-the cases, the profiles are understood as a simple sum of the magnetospherilcal
-component and the wind component.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_acc_model.eps}
-
-\end{center}
-
-\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ as in Figure~\ref{fig:atlas_acc_models}).
-While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{wind}}$  (the slower accerelation and the hotter models).
-The P~Cygni profile feature becomes less prominant in some of the models because of the extra emission from the magnetosphere extends in the wings.}
-
-\label{fig:atlas_wind_acc_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magentosphere $+$ disc $+$ wind}
-
-\label{sub:model-acc-disc-wind}
-
-\begin{itemize}
-\item Flux contribution by scattering of photon by disc?
-\end{itemize}
-
-\subsection{Summary}
-
-\section{Discussion}
-
-\label{sec:Discussion}
-
-\subsection{Classification scheme proposed by Reipurth et. al (1996)}
-
-\citet{reipurth:1996}proposed the two-dimentional classification
-of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
-stars. Their classification scheme contains four classes (I, II, III
-and IV) differenciated by the ratio of the secondary-to-primary emission
-components in the profiles. Each classes are devided into two sub-classes
-(B and R) which depends whether the absorption componet is on the
-blue or red side. Readers are refered to Fig.~4 of their paper. Figure~\ref{fig:atlas_reipurth}
-shows the sample profiles which are classified according to the definition
-of \citet{reipurth:1996}. The corresponding model parameters are
-given in Table~\ref{tab:classification}. As we can see from this
-figure, the combinatioin of the wind, magnetospherical accretion,
-and accretion disc can reasonably reproduce all the classes of the
-profiles seen in observations.
-
-Within the parameter space covered, we find it is difficult to produce
-Type I type profile, which is very symmetric around the line centre
-and without any absorption feature, if the wind component is added
-in the model. Type II-B are
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.65]{figures/atlas_reipurth_like.eps}
-
-\end{center}
-
-\caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}.
-The combination of magnetospherical accretion flow, the accretion disc, and the colliminated wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.
-The model parameters and short comments are summarised in Table~\ref{tab:classification}.
-The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.
-}
+  \caption{Sample H$\alpha$ model profiles which characterise the
+    classification by \citet{reipurth:1996}. The combination of
+    magnetospheric accretion flow, the accretion disc, and the disc wind
+    model can reasonably reproduce wide ranges of H$\alpha$ profiles seen
+    in observations. Similar results can be obtained if the bipolar wind is
+    replaced by the disc wind. The model parameters and short comments are
+    summarised in Table~\ref{tab:classification}. The horizontal axes
+    are velocities in $\kmps$, and the vertical axes are normalised
+    flux.}
 
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table*}
+
+\caption{The summary model parameters for the profiles in
+Figure~\ref{fig:atlas_reipurth} and brief comments. The temperatures
+are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
+$\dot{M}_{\mathrm{dw}}$ are in $\mathrm{M_{\sun}\,yr^{-1}}$.}
+
+\label{tab:classification}
 
@@
 $-$&
-Accretion dominated possibly without the wind at a mid inclination.\tabularnewline
+Accretion dominated possibly without the wind. Mid inclination.\tabularnewline
 II-B&
-$10$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$1.0$&
-Accretion and wind, mid wind accerelation rate, low inclination\tabularnewline
-III-B&
-$10$&
+$55$&
 $10^{-7}$&
@@
 $8.0$&
-$2.0$&
-Accretion and wind, with slow wind accerelation rate, low inclination\tabularnewline
-IV-B&
-$55$&
-$-$&
-$-$&
-$10^{-8}$&
-$8.0$&
-$0.5$&
-Accretion dominated (low accretion rate), mid inclination \tabularnewline
-II-R&
+$1.0$&
+Wind, disc and magnetosphere. Wide range of wind acceleration rate.
+Mid--high inclination\tabularnewline
+III-B&
 $55$&
@@
 $9.0$&
-$2.0$&
-Wind dominated, with fast wind accerelation rate, mid inclination\tabularnewline
-III-R&
+$0.5$&
+Wind, disc and magnetosphere. Fast--mid wind acceleration rate. Mid--high
+inclination\tabularnewline
+IV-B&
+$55$&
+$10^{-7}$&
+$7.5$&
+$10^{-8}$&
+$9.0$&
+$0.2$&
+Wind, disc and magnetosphere. Fast wind acceleration rate. Mid--high inclination\tabularnewline
+II-R&
 $80$&
@@
 $10^{-8}$&
-$9.0$&
+$7.0$&
+$2.0$&
+Wind, disc and magnetosphere. Slow wind acceleration rate. High inclination\tabularnewline
+III-R&
+$85$&
+$10^{-8}$&
+$8.2$&
+$10^{-9}$&
+$6.0$&
 $1.0$&
-Wind dominated, slow wind acceralation rate, high inclination \tabularnewline
+Wind, disc and magnetosphere. Mid wind acceleration rate. Very high
+inclination \tabularnewline
 IV-R&
@@
 
-\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.}
-
-\label{tab:classification}
-
 \end{table*}
 
-\subsection{Comparisons with observations}
-
-For a demonstrative purpose, we performed preliminary model fit of
-H$\alpha$ observarions
-
-\begin{itemize}
-\item other possible model? Better wind model?
-\item Any other bussiness?
-\end{itemize}
+% Uncomment the following if you want to include TTau model section
+%
+%\input{ttau_model_subsec.tex}
+%
+%
+
+\subsection{H$\alpha$ as a mass accretion diagnostic}
+
+\label{sub:ha-mass-accretion-diagnostic}
+
+In the previous sections, two possible geometrical configurations
+for the wind from CTTS were considered: (1)~a bipolar wind, and (2)~a
+disc wind. While the material is more concentrated toward the polar
+regions for a given radius in the first case, the material is more concentrated
+toward the equatorial plane in the second case. 
+%As mentioned earlier,
+%the bipolar wind model resembles the density distribution of the jet
+%MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
+%($>10$~au), and the disc wind model resembles that in smaller scale
+%($<10$~au).
+
+The distinct difference in the density dependency on the polar angles
+in two models should be apparent in the inclination angle dependency
+on the shapes of the line profiles. Figure~\ref{fig:effect_inclination_compare}
+shows the H$\alpha$ profiles computed for 1.~the disc, bipolar-wind,
+accretion hybrid model (section~\ref{sub:model-acc-disc-wind}) and
+2.~the disc-wind, magnetosphere hybrid model (section~\ref{sub:result-discwind-knigge})
+at inclination angles $i=10^{\circ}$, $55^{\circ}$ and $80^{\circ}$. Both
+models include the magnetospheric accretion component with the same
+parameters used as in sections~\ref{sub:model-acc-disc-wind} and
+\ref{sub:result-discwind-knigge} i.e. $T_{\mathrm{max}}=7500\,\mathrm{K}$
+and $\dot{M}_{\mathrm{acc}}=1\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$.
+
+Mainly because of the geometrical configuration, the P-Cyg absorption
+feature weakens as the inclination increases for the model with the
+bipolar wind. The optical depth to an observer is higher (from the
+wind emission region) for with a lower inclination angle with this
+geometry. Although not shown here, this tendency of the inclination
+dependency holds for the models with bipolar wind models for wide
+ranges of $\beta$ and $T_{\mathrm{wind}}$. For the model with the
+disc wind, the absorption becomes stronger as the inclination becomes
+larger. The optical depth to an observer becomes larger as the inclination
+increases in this geometry.
+
+Similarly, the line equivalent width increases as the inclination
+angle increases for the model with the bipolar wind, it decreases
+as the inclination angle increases for the model with the disc wind.
+For the models with only magnetosphere (section~\ref{sub:model-acc}),
+we find that the line equivalent width decreases as the
+inclination increases in those models (see Figure~\ref{fig:acc_inclination_effect}).
+Interestingly, the observational study of \citet{appenzeller:2005}
+showed that the H$\alpha$ line equivalent width of CTTS increases
+as the inclination angle increases. Only the models with the bipolar
+wind agree with the trend seen in their observation. Although the
+uncertainty in the inclination angles of the observed object might
+be large, a larger sample in addition to that of \citet{appenzeller:2005}
+for further investigation of the inclination dependency on the line
+profile will be extremely useful for determining the wind configuration
+of CTTS.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+  \begin{center}
+
+    \begin{tabular}{cc}
+      \includegraphics[%
+	clip,
+	scale=0.45]{figures/disc_wind_acc_inc_effect_m9_b2_t7000.eps}&
+      \includegraphics[%
+	clip,
+	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}\tabularnewline
+    \end{tabular}
+
+  \end{center}
+
+  \caption{Dependency of the H$\alpha$ model profiles on the inclination
+    angle. The profiles computed at $i=10^{\circ}$(solid), $55^{\circ}$
+    (dot) and $80^{\circ}$ (dash) using 1.~the disc, bipolar-wind,
+    accretion hybrid model (left panel;
+    c.f. section~\ref{sub:model-acc-disc-wind}) and 2.~using the
+    disc-wind, magnetosphere hybrid model (right;
+    c.f. section~\ref{sub:result-discwind-knigge}) are shown for a
+    comparison.  The parameters used for the magnetosphere are same for
+    the both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The
+    isothermal wind temperature and the wind acceleration parameter used
+    in both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.
+    All the other parameters are same as in
+    sections~\ref{sub:model-acc-disc-wind} and
+    \ref{sub:result-discwind-knigge}. While the line equivalent width
+    increases as the inclination angle increases for the former model
+    configuration, it decreases as the inclination angle increases for the
+    latter. Only the former agrees with the tendency seen in the
+    observational study of \citet{appenzeller:2005} who showed that the
+    H$\alpha$ line equivalent width of CTTS increases as the inclination
+    angle increases. }
+
+  \label{fig:effect_inclination_compare}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Despite the inclination angle dependency of the observed H$\alpha$
+favouring the models with bipolar wind, there are two main aspects of
+this model which are not quite consistent with the magneto-centrifugal
+launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
+First, in section~\ref{sub:model-acc-disc-wind}, we found that the
+ratio of the mass-loss to mass-accretion rates needed to be rather
+small ($\mu<\sim0.025$), in order not to have an unrealistically
+strong P-Cyg absorption component, compared to the MHD simulations
+suggested \citep{koenigl:2000} i.e. $\mu\approx0.1$.
+%In the model
+%fit of T~Tau observation (section~\ref{sub:ttau-model}), we found
+%much larger value of the ratio $\mu=0.18$. 
+Considering large uncertainty in MHD theories and observational
+measurements (e.g.~$\dot{M}_{\mathrm{acc}}$, 
+$\dot{M}_{\mathrm{wind}}$ and $B$), the wide range of the mass-loss
+to mass-accretion ratio 
+%(e.g.~$0.025<\mu<0.18$) 
+may be still reasonable. On the other hand, the models with the disc
+wind (section~\ref{sub:result-discwind-knigge}) 
+using $\mu=0.1$ reproduces the profiles (Figure~\ref{fig:atlas_discwind_acc_model})
+similar to that seen in observations. Second, the MHD models predict
+that the wind/jet becomes collimated well above the disc plane ($>10$~au),
+but our bipolar wind model are collimated (density enhanced toward
+in the polar direction) from right outside of the magnetosphere. Unless
+the origin of the wind is from the central star itself, the density
+distribution used for the bipolar wind is not quite consistent with
+the near field of the MHD jet models, considering that the most of
+the H$\alpha$ emission occurs within a few to a several radii of
+the magnetosphere (Figure.~\ref{fig:effect_alpha_disc}). The density
+structure used for the disc wind model, however, is very similar to
+that of MHD simulations in the near field where the most of the H$\alpha$
+wind emission occurs. Interestingly, however, the recent study of
+\citet{matt:2005} demonstrated the possibility that the stellar wind along
+the open magnetic field originated from the star can cause significant
+spin-down torque on the star, provided that mass-loss rate is high
+enough. Considering the issues mentioned above, it is not possible
+to favour the bipolar wind model to the disc wind model without further
+observational constraints. In reality, two types of the winds (bipolar
+wind and disc wind) may co-exits similar to that seen in e.g. \citet*{drew:1998}
+and \citet{matt:2005}. In these models, the fast stellar wind is
+present in the polar directions, and at the same time the slower disc
+wind is present near the equatorial plane.
+
+One possible way to distinguish the two different wind models is to
+examine the profile shape of a CTTS which is known to be viewed at
+pole-on. If the profile contains a prominent blue-shifted absorption
+component (e.g. Type IV-B), the system is more likely to be associated
+with the bipolar wind type of outflow (but not with the disc-wind type
+of outflow).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We presented the detailed study of the H$\alpha$ formation from the
-circumstealler material of classical T~Tauri stars. AND MORE.
-
-Future studies include:
-
-\begin{enumerate}
-\item Improvement of the wind model. Temperature structure estimate by Hartmann()
-Alancar's paper. Disc-wind model of Branford and ...
-\item Try it with MHD model.
-\item Include the scattering flux term although this requires $N_{\phi}\times N_{\theta}$
-more times to compute a profile. 
-\item Polarization study to explore the geometry and the rotation of the
-disc. 
-\item Gas in the accretion disc (inner most part and the outer layer of
-the disc).
-\item Variability study using a 3D model.
-\end{enumerate}
+We have presented the disc--wind--magnetosphere hybrid radiative
+transfer models for classical T~Tauri stars, and detailed studies of
+the H$\alpha$ formation from their complex to circumstellar
+environment to understand the wide variety of H$\alpha$ profiles seen
+in observations. The two types of wind models considered are (1)~the
+bipolar wind model in which the wind originates from the star itself
+(section~\ref{sub:wind_jet}; Figure~\ref{fig:config_dipolar}), and
+(2)~the disc-wind model in which the wind originates from the inner
+part of the accretion disc
+(section~\ref{sub:Alternative-model-disc-wind};
+Figure~\ref{fig:config_discwind}).  We found that both wind models
+combined with the magnetospheric accretion flow reproduces the wide
+variety of H$\alpha$ profiles
+(Figures~\ref{fig:atlas_disc_wind_acc_model} and
+\ref{fig:atlas_discwind_acc_model}) seen in the observations.
+
+The inclination dependency of the line equivalent width predicted by
+the bipolar wind model agree with trends seen in the observation, but
+the disc-wind model does not. With the reference magnetospheric
+configuration (Table~\ref{tab:std_parameters}), the ratio of the
+mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind was
+set to be 4 --10 times smaller than that predicated by
+magneto-hydrodynamical (MHD) calculations (c.f.~$\mu\sim0.1;$
+\citealt{koenigl:2000}) to avoid the blue-shifted absorption component
+becoming unrealistically too strong; however $\mu$ used in the
+disc-wind models are consistent with MHD calculations.
+
+Using the model results, we examined the H$\alpha$ spectroscopic
+classification proposed by \citet{reipurth:1996}, and discussed the
+basic physical conditions that reproduce the profiles in each
+classified type. Using the different combinations of the inclination
+($i$), the mass-loss to mass-accretion rate ratio ($\mu$) and the wind
+acceleration rate ($\beta$), our radiative transfer model was able to
+produce all 7 types of the profiles in \citet{reipurth:1996}.
+%Using the hybrid model, we also fit the observed H$\alpha$
+%from the optical component of T~Tau triple system (T~Tau~N). The
+%agreement between the model and the observation is excellent; however,
+%we could not confirm the uniqueness of the fit. The ratio of the mass-loss
+%to mass-accretion rate was found to be $\sim0.18$, which is consistent
+%with \citet{koenigl:2000}.
+%
+%Although not attempted in this paper, a better approach for determining
+%the mass-loss and mass-accretion rate consistently is to model multiples
+%lines simultaneously. For example, the mass-accretion rate of an object
+%can be determined more easily by modelling Pa$\beta$ and Br$\gamma$
+%since there is no/little wind effect seen in these lines. The mass-accretion
+%rate then can be used to model H$\alpha$ to find the wind mass-loss
+%rate.
+
+Similar model configurations used here may be also applicable to Herbig
+Ae/Be and brown dwarfs since their H$\alpha$ observations also exhibit
+evidence of the outflow and inflow (e.g.~\citet{finkenzeller:1984};
+\citealt{muzerolle:2005}), but no model has been developed to explain
+the phenomenon. Further investigation on the possibility of applying
+our model to these objects are needed.
+
+Future work should include the followings: (1)~Improving the wind
+models. The parametrisation of the wind density structure should be
+changed to follow more closely that of MHD simulations. The wind
+temperature structure should be calculated self-consistently
+(c.f.~\citealt{hartmann:1994}; \citealt{martin:1996}). (2)~Computing
+the line profiles using the density structure from MHD directly. Check
+the consistency, and give feedback to the MHD models which are needed
+to be tested against observational data. (3)~Spectropolarimetric study
+to explore the geometry and the rotation of the disc
+(e.g.~\citealt{vink:2005}). (4)~Modelling of the extended H$\alpha$
+and spectro-astrometric observations (c.f.~\citealt{takami:2003};
+\citealt{appenzeller:2005}). (5)~Line variability study using a 3D
+radiative transfer model (e.g.~\citealt{symington:2005};
+\citealt{kurosawa:2005a}) to probe the geometrical structure.
+
 \section*{Acknowledgements}
 
-RK is supported by PPARC standard grand PPA/G/S/2001/00081.
+Authors thank Jorick Vink for providing us the H$\alpha$ data of
+T~Tau. This work is supported by PPARC standard grand PPA/G/S/2001/00081.
 
 %
-
+%----------------------------------------------------
+% Bibliography follows here.
+%-----------------------------------------------------
 %
+\bibliographystyle{mn}
+\bibliography{mnras}
 
 %
-
-%----------------------------------------------------
-
-% Bibliography follows here.
-
-%-----------------------------------------------------
-
-%
-
-%
-
-%
-
-\bibliographystyle{mn}
-
-\bibliography{mnras}
-
 %

### 2006-01-26 TTau_Halpha/kurosawa.tex
Major structual change. Now more or less complte. The discussion sections may need  revisions. Some plots need to be replaced after the model curretly running finishes.  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@632 25464f21-6099-402c-b30a-640f1d40d38b

@@
-%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
 \documentclass[english,useAMS, usenatbib]{mn2e}
@@
 
-  \caption{Basic model configuration of the disc-wind, magnetosphere
+  \caption{Basic model configuration of the disc-wind-magnetosphere
     hybrid model. The system consist of four components: (1)~the
@@
 flow does not affect the underlying magnetic field itself. As shown
-in Fig.~\ref{ig:config_discwind} (region~2), the innermost radius ($R_{\mathrm{mi}}$)
+in Fig.~\ref{fig:config_discwind} (region~2), the innermost radius ($R_{\mathrm{mi}}$)
 of the magnetosphere at the equatorial plane ($z=0$) is assigned
@@
 emissivity from the disc: since the disc mass of CTTS are rather small
-($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($<\sim
+($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($\lesssim 
 1600\,\mathrm{K}$), the continuum flux contribution at H$\alpha$
@@
 \section{Results}
-
 \label{sec:Results}
@@
 \subsection{Magnetosphere only models}
-
 \label{sub:model-acc}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}
+
+  \end{center}
+
+  \caption{H$\alpha$ model profiles for wide ranges of mass accretion
+    rate ($\dot{M}_\mathrm{acc}$) and temperature
+    ($T_{\mathrm{max}}$). The profiles are computed using only the
+    magnetospheric accretion flow (i.e. no outflow).  All the profiles
+    are computed using the parameters of the reference model
+    (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The
+    temperature (indicated along the vertical axis) of the model increases
+    from top to bottom, and the mass accretion rate (indicated by the
+    values in $\mathrm{M_{\odot}\,yr^{-1}}$ along the top) increases from
+    left to right. }
+
+  \label{fig:atlas_acc_models}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.59]{figures/broadening.eps}
+
+  \end{center}
+
+  \caption{The effect of line broadening on H$\alpha$. A model
+    computed with a damping constant ($\Gamma$), described in
+    section~\ref{sec:radiative-transfer-model} (solid), is compared with
+    a model with no damping, $\Gamma=0$ (dashed).  Both models are
+    computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
+    reference parameters given in Table~\ref{tab:std_parameters}. The two
+    models have similar peak flux levels (around $V \sim 0~\kmps$), but
+    the total flux and the EW of the line increased drastically for the
+    model with the damping constant. The broad wings extend to $\sim \pm
+    800 \kmps$.  The redshifted absorption feature (very weakly) seen in
+    the $\Gamma=0$ model is not seen in the model with the broadening.  }
+
+  \label{fig:broadening}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.59]{figures/acc_inc_effect.eps}
+
+  \end{center}
+
+  \caption{The dependency of the H$\alpha$ profile on inclination ($i$).  The
+    profiles are computed with a magnetospheric accretion flow only using
+    the reference parameters given in Table~\ref{tab:std_parameters} and
+    $T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
+    are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$
+    respectively. As the inclination becomes larger, the peak flux and the
+    equivalent width of the line becomes smaller.  }
+
+  \label{fig:acc_inclination_effect}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 full properties of the H$\alpha$ profiles in CTTS.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}
-
-  \end{center}
-
-  \caption{H$\alpha$ model profiles for wide ranges of mass accretion
-    rate ($\dot{M}_\mathrm{acc}$) and temperature
-    ($T_{\mathrm{max}}$). The profiles are computed using only the
-    magnetospheric accretion flow (i.e. no outflow).  All the profiles
-    are computed using the parameters of the reference model
-    (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$. The
-    temperature (indicated along the vertical axis) of the model increases
-    from top to bottom, and the mass accretion rate (indicated by the
-    values in $\mathrm{M_{\odot}\,yr^{-1}}$ along the top) increases from
-    left to right. }
-
-  \label{fig:atlas_acc_models}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.59]{figures/broadening.eps}
-
-  \end{center}
-
-  \caption{The effect of line broadening on H$\alpha$. A model
-    computed with a damping constant ($\Gamma$), described in
-    section~\ref{sec:radiative-transfer-model} (solid), is compared with
-    a model with no damping, $\Gamma=0$ (dashed).  Both models are
-    computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
-    reference parameters given in Table~\ref{tab:std_parameters}. The two
-    models have similar peak flux levels (around $V \sim 0~\kmps$), but
-    the total flux and the EW of the line increased drastically for the
-    model with the damping constant. The broad wings extend to $\sim \pm
-    800 \kmps$.  The redshifted absorption feature (very weakly) seen in
-    the $\Gamma=0$ model is not seen in the model with the broadening.  }
-
-  \label{fig:broadening}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.59]{figures/acc_inc_effect.eps}
-
-  \end{center}
-
-  \caption{The dependency of the H$\alpha$ profile on inclination ($i$).  The
-    profiles are computed with a magnetospheric accretion flow only using
-    the reference parameters given in Table~\ref{tab:std_parameters} and
-    $T_{\mathrm{max}}=7500~\Kelvin$. The solid, dotted, and dashed lines
-    are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$
-    respectively. As the inclination becomes larger, the peak flux and the
-    equivalent width of the line becomes smaller.  }
-
-  \label{fig:acc_inclination_effect}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.45]{figures/disc_wind_acc_mdot_effect.eps}
-
-  \end{center}
-
-  \caption{The effect of the mass-loss rate to mass-accretion rate
-    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
-    H$\alpha$ profile computed with only the magnetospheric accretion
-    (thick solid) is compared with the magnetosphere--wind--disc
-    hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1
-    (dot) and 0.2 (dash). The magnetosphere used here has
-    $T_{\mathrm{max}}=7500\,\Kelvin$ and
-    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
-    temperature and the acceleration parameter of the bipolar wind are
-    $T_{\mathrm{wind}}=7000\,\Kelvin$ and $\beta=2.0$ respectively.
-    All the models are computed with the inclination angle
-    $i=55^{\circ}$. As $\mu$ increases the P-Cygni absorption deepens
-    and the emission component becomes stronger. In general, the
-    absorption is too strong for the models with $\mu>0.025$ compared
-    to the observations (e.g., \citealt{reipurth:1996}).}
-
-  \label{fig:effect_mdot_disc_wind_acc}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Disc-wind only models}
-
 \label{sub:result-discwind-knigge}
@@
     ($T_{\mathrm{wind}}$). The wind emission grows as the values of
-    $\beta$ and $T_{\mathrm{wind}}$ increase.   As in the
-    bipolar wind models (Figure~\ref{fig:atlas_wind_model}), the position
+    $\beta$ and $T_{\mathrm{wind}}$ increase.   The position
     of the wind absorption moves toward the line centre as $\beta$ becomes
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
-
-  \end{center}
-
-  \caption{The disc-wind, magnetosphere hybrid model. These models
-  (solid lines) have the  same parameters as
-    Figure~\ref{fig:atlas_discwind_only}, but  also
-    include the magnetospheric accretion flow
-    ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
-    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
-    the emission from the magnetosphere dominates for the models with
-    smaller $\beta$ and $T_{\mathrm{wind}}$, the emission from the wind dominates the
-    profiles for models with larger $\beta$ and $T_{\mathrm{wind}}$.  The contribution
-    of the magnetosphere can be judged from the profiles computed with
-    the magnetosphere only (dotted lines).}
-
-  \label{fig:atlas_discwind_acc_model}
-
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In this section, we examine profiles produced using the 
 the disc wind outflow model described in
-section~\ref{sub:model-disc-wind}. This type of outflow 
-has been predicted by several MHD calculations (e.g. \citet{koenigl:2000};
- \citealt{krasnopolsky:2003}), and broadly consists of a wind with
-its density increasing toward the equatorial plane.
-
-GEOMETRY? REFERENCE MODEL?
-
+section~\ref{sub:model-disc-wind}. 
 The parameters used for the
@@
 disc-wind parameters are summarised in
-Table~\ref{tab:std_discwind_parameters}.
-
-Although the line is potentially
+Table~\ref{tab:std_discwind_parameters}. Although the line is potentially
 sensitive to the temperature structure of the wind, determination of a
@@
 
-Initially we examine the characteristics of the
-H$\alpha$ profile  as a function of the wind acceleration parameter
-$\beta$ and the isothermal wind temperature
-$T_{\mathrm{wind}}$.  Figure~\ref{fig:atlas_discwind_only} shows profiles computed at  $i=55^{\circ}$
- for a range of wind temperatures
-between $7000\,\mathrm{K}$ and $9000\,\mathrm{K}$, and  $\beta$ between $0.2$ and $2.0$.
-
+Initially we examine the characteristics of the H$\alpha$ profile as a
+function of the wind acceleration parameter $\beta$ and the isothermal
+wind temperature $T_{\mathrm{wind}}$.  The mass-loss rate is kept
+constant at
+$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$.
+Figure~\ref{fig:atlas_discwind_only} shows the model profiles computed
+for the wind temperatures between $7000\,\mathrm{K}$ and
+$9000\,\mathrm{K}$, and those with $\beta$ between $0.2$ and $2.0$,
+computed at inclination $i=55^{\circ}$.
+The morphology of the profile exhibited by the model changes from
+FU-Ori type (c.f.~\citealt{reipurth:1996}) for the models with small
+$\beta$ to the stronger emission types which are more commonly seen in
+the observed H$\alpha$ (c.f.~\citealt{reipurth:1996}) as the value of
+$\beta$ increases.  
 Classical P~Cygni profiles are prominent
@@
 increases, the position of the blue-shifted absorption component moves
-toward the line centre -- this can be seen clearly in the
-$T_{\mathrm{wind}}=7000\,\mathrm{K}$ models. The velocity position
- of the absorption component of the fastest accelerating wind
-($\beta=0.2$) is almost at the terminal velocity ($v_{\infty}\sim
-210\,\kmps$), that for the slowest wind acceleration model
-($\beta=4.0$) is located close the line centre ($\sim 50\,\kmps$).
-
- As
-one can see in Figure~\ref{fig:wind_vr_rho}, the column density of the
+toward the line centre. The blue edge of the absorption component in
+the fastest accelerating wind 
+($\beta=0.2$) model is almost at the terminal velocity ($v_{\infty}\sim
+160\,\kmps$) of the disc wind (c.f.~Figure~\ref{fig:discwind_vr_rho}), that
+for the slowest wind acceleration model 
+($\beta=4.0$) is located close the line centre ($\sim 20\,\kmps$).
+
+ As one can see in Figure~\ref{fig:discwind_vr_rho}, the column density of the
 gas moving at $v_{\infty}$ increases as the wind acceleration becomes
@@
 because the density near the photosphere increases as the value of
-$\beta$ increases (Figure~\ref{fig:wind_vr_rho}); hence, the
+$\beta$ increases (Figure~\ref{fig:discwind_vr_rho}); hence, the
 emissivity of increases. Unlike the magnetospheric accretion only
@@
 the absorption component in P~Cygni profile, most of the profiles show
-red-ward asymmetry except for the low temperature wind models with
-high inclinations (not shown here).
-
-The effect of varying the wind mass-loss rate is shown in Figure~\ref{fig:effect_wind_mdot}.
-The line is very sensitive to the mass-loss rate. With all other parameters
-fixed constant, $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor
-of the wind density (equation~\ref{eq:wind_density_final}). The
-important processes in forming H$\alpha$ emission are the
-recombination process and the subsequent downward transition to $n=3$
-level. Assuming the ionisation fraction remains constant, the
-recombination rate is proportional to the square 
-of wind density. We have found the line flux of the models in the
-figure is approximately proportional to the square of the mass-loss
-rate. This very sensitive nature of H$\alpha$ would make the line
-a good candidate for a mass-loss rate indicator; however, without
-solving the ambiguity of the emission component from the magnetospheric
-accretion flow and the wind, and without knowing the detailed temperature
-structure of the wind, it could provide us a misleading a mass-loss
-rate estimate of a T Tauri star.
-
-Figure~\ref{fig:atlas_discwind_only} shows the H$\alpha$ profiles
-computed using only the disc-wind component
-(c.f. Figure~\ref{fig:config_discwind}) for the same isothermal
-disc-wind temperature ($T_{\mathrm{wind}}$) and the wind acceleration
-parameter ($\beta$) ranges used for the bipolar wind models
-(c.f. Figures~\ref{fig:atlas_wind_model} and
-\ref{fig:atlas_disc_wind_acc_model}).
-
-  The figure shows that the
-wind emission increases as $\beta$ and $T_{\mathrm{wind}}$ increase. The
-$\beta$ dependence arises simply because for large $\beta$ there is a
-greater mass of wind material close to the star.  As with the bipolar
-wind models, the location of the P-Cyg absorption component moves
-toward the line centre as $\beta$ increases.
-
-The morphology of the profile exhibited by the model changes from
-FU-Ori type (c.f.~\citealt{reipurth:1996}) for the models with small
-$\beta$ to the stronger emission types which are more commonly seen in
-the observed H$\alpha$ (c.f.~\citealt{reipurth:1996}) as the value of
-$\beta$ increases.  We find that the profile shapes are relatively
-insensitive to the value of the wind collimation parameter $d$. The
-dependency on the disc wind mass-loss rate of the profile shape is
-similar to that of the bipolar wind models
-(Figure~\ref{fig:effect_mdot_disc_wind_acc}).
-
-\subsection{Disc--wind--magnetosphere  hybrid models}
-
-\label{sub:result-discwind-hybrid}
-
-We now consider the models computed with a combination of the
-disc-wind and the magnetospheric accretion components. The
-parameters used for the magnetosphere are set to be same as in the
-case for Figure~\ref{fig:acc_inclination_effect}.  
-The mass-loss rate of the disc wind is set to
-$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.1$).
-Figure~\ref{fig:atlas_discwind_acc_model} shows the models profiles
-computed using the same ranges of the disc-wind temperature and the
-wind acceleration parameter as in the previous cases.
-
-As in the disc-wind only models
-(Figure~\ref{fig:atlas_discwind_only}), the location of the absorption
-component moves toward the line centre as the value of $\beta$
-increases.  The figure shows that in
-the models with smaller $\beta$ and $T_{\mathrm{wind}}$, the line
-emission from the magnetosphere dominates, while this situation reverses for the
-models with larger $\beta$ and $T_{\mathrm{wind}}$. The model with
-$\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
-results in an H$\alpha$ profile that is far too strong to be compatible
- with observations (\citet{reipurth:1996} and \citet{alencar:2000});
- however, the lower mass-loss rate models (while keeping $\mu$ constant)
- produce the profiles with the line strengths comparable to observations.
-Although the models in Figure~\ref{fig:atlas_discwind_acc_model} are
-computed with limited ranges of  $T_{\mathrm{wind}}$ and $\beta$, the
-resulting profiles exhibit a wide variety of line profile shapes,
-many of  which are similar to the types of H$\alpha$ profiles seen in the
-observations (c.f.~\citealt{reipurth:1996}).
-
-An examination of the profiles in Figures~\ref{fig:atlas_discwind_only} and
-Figure~\ref{fig:atlas_discwind_acc_model} reveals some of problems
-with uniqueness that must inevitably occur when trying to assign
-an individual profile as wind or accretion dominated i.e. very similar profiles may arise
-from very different circumstellar geometries. For example, the disc-wind
-only model with $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
- (in Figures~\ref{fig:atlas_discwind_only}) and the  accretion dominated model with
- $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
-(in Figure~\ref{fig:atlas_discwind_acc_model}) give very similar profiles.
-
-The general characteristics of the profiles from the disc-wind, magnetosphere
-hybrid model (Figure~\ref{fig:atlas_discwind_acc_model}) are very
-similar to those of the disc, bipolar wind, magnetosphere hybrid
-model (Figure~\ref{fig:atlas_disc_wind_acc_model}). The main difference
-between these two sets of models is in the ratio of the mass-loss rate to the mass
-accretion rate, $\mu$. While the models presented in this section
-use $\mu=0.1$ which is consistent with the MHD jet models (e.g.~\citealt{koenigl:2000}),
-the models in Figure~\ref{fig:atlas_disc_wind_acc_model} use much
-smaller value ($\mu=0.01$).   The dependency of the model profiles on
-the inclination angle for the two different wind models will be discussed
-in the next section.
-
+red-ward asymmetry except for the fast wind acceleration models
+($\beta=0.2$ and $0.5$)with low inclinations (not shown here).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.45]{figures/discwind_d_effect.eps}
+
+  \end{center}
+
+  \caption{The dependency of the H$\alpha$ profile on the source
+    displacement parameter $d$. The line profiles are computed with 
+    the wind parameter $T_{\mathrm{wind}} = 9000\Kelvin$ and $\beta  =
+    0.5$ for $i=55^{\circ}$.  The profiles in the figure uses $d = 
+    11~R_{*}$ (dashed),   $18~R_{*}$ (dash-dot) and $22~R_{*}$
+    (dash-dot). All the other parameters are same as in
+    Figure~\ref{fig:atlas_discwind_only}.  As the wind becomes more
+    collimated (larger $d$), the wind launching angle becomes smaller
+    and the wind density is enhanced towards the symmetry axis
+    ($z$); hence, the wind emission increases.  The absorption
+    component is relatively insensitive to $d$ since the change in the
+    column density toward the observer is relatively small.  No
+    magnetospherical component is included. 
+  }
+
+  \label{fig:discwind_d_effect}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.45]{figures/discwind_mdot_effect.eps}
+
+  \end{center}
+
+  \caption{The effect of the wind mass-loss rate.  The profiles computed
+    with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin,
+    0.5\right)$, and $\dot{M}_{\mathrm{wind}} = 
+    2.0 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dashed), 
+   $1.0 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (solid), and 
+   $0.5 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dash-dot) 
+    are shown above. The
+    models are computed with only the disc-wind component (no magnetospheric
+    accretion). With all other parameter fixed
+    constant, the mass-loss rate behaves as a scaling factor for the wind
+    density (c.f.~equation~\ref{eq:discwind-density}).}
+
+  \label{fig:discwind_mdot_effect}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The effect of varying the wind mass-loss rate is shown in
+Figure~\ref{fig:discwind_mdot_effect}.  The line is very sensitive to the
+mass-loss rate. With all other parameters fixed constant,
+$\dot{M}_{\mathrm{wind}}$ acts as an scaling factor of the wind
+density (equation~\ref{eq:discwind-density}). The important processes
+in forming H$\alpha$ emission are the recombination process and the
+subsequent downward transition to $n=3$ level. Assuming the ionisation
+fraction remains constant, the recombination rate is proportional to
+the square of wind density; hence the line is very sensitive to the
+change in $\dot{M}_{\mathrm{wind}}$.  We have found the line flux of
+the models in the figure is approximately proportional to the square
+of the mass-loss rate. This very sensitive nature of H$\alpha$ would
+make the line a good candidate for a mass-loss rate indicator;
+however, without solving the ambiguity of the emission component from
+the magnetospheric accretion flow and the wind, and without knowing
+the detailed temperature structure of the wind, it could provide us a
+misleading a mass-loss rate estimate of a T Tauri star.
+
+By inspecting the model H$\alpha$ images computed (no shown here), we have
+ found that the extent of the H$\alpha$ emission region is relatively
+ small i.e.~$h\lesssim 0.2\,\mathrm{au}$ or $20\, R_{*}$ where h is the
+ vertical distance from the disc when compared to the
+ spectro-astrometric observations of \citet{takami:2003} 
+for RU~Lup and CS Cha which show 1--5~au scale outflows%
+\footnote{Their observations also show some objects
+(e.g~Z CMa and AS~353A) displaying the outflows in larger scale
+($>50\,\mathrm{au}$); however, this could be formed in shocks rather
+than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
+(e.g.~\citealt{shang:2002}). %
+}. The extent of the line emission region becomes slightly
+larger ($\sim0.4$~au) if a slower wind acceleration rate (e,g,~$\beta=4$)
+is used.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}
@@
 in section~\ref{sub:result-discwind-knigge}. See also
-section~\ref{sub:Alternative-model-disc-wind}.}
+section~\ref{sub:model-disc-wind}.}
 
@@
 \hline
-$21.4$&
+$22$&
 $3.0$&
@@
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Disc-wind-magnetosphere hybrid models}
+\label{sub:result-discwind-hybrid}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
+
+  \end{center}
+
+  \caption{The disc-wind-magnetosphere hybrid model. These models
+  (solid lines) have the  same parameters as
+    Figure~\ref{fig:atlas_discwind_only}, but  also
+    include the magnetospheric accretion flow
+    ($T_{\mathrm{\max}}=7500~\mathrm{K}$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$). While
+    the emission from the magnetosphere dominates for the models with
+    smaller $\beta$ and $T_{\mathrm{wind}}$, the emission from the wind dominates the
+    profiles for models with larger $\beta$ and $T_{\mathrm{wind}}$.  The contribution
+    of the magnetosphere can be judged from the profiles computed with
+    the magnetosphere only (dotted lines).}
+
+  \label{fig:atlas_hybrid}
+
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We now consider the models computed with a combination of the
+disc-wind and the magnetospheric accretion components. The parameters
+used for the magnetosphere are  same as in 
+Figure~\ref{fig:acc_inclination_effect}, and  the mass-loss rate of
+the disc wind is 
+$\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+(i.e.~$\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.1$).
+Figure~\ref{fig:atlas_hybrid} shows the models profiles
+computed using the same ranges of the disc-wind temperature and the
+wind acceleration parameter as in the previous cases.
+
+As in the disc-wind only models
+(Figure~\ref{fig:atlas_discwind_only}), the location of the absorption
+component moves toward the line centre as the value of $\beta$
+increases.  The figure shows that in the models with smaller $\beta$
+and $T_{\mathrm{wind}}$, the line emission from the magnetosphere
+dominates, while this situation reverses for the models with larger
+$\beta$ and $T_{\mathrm{wind}}$. The model with
+$\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
+results in an H$\alpha$ profile that is far too strong to be
+compatible with observations (\citealt{reipurth:1996} and
+\citealt{alencar:2000}); however, the lower mass-loss rate models
+(while keeping $\mu$ constant) produce the profiles with the line
+strengths comparable to observations.  Although the models in
+Figure~\ref{fig:atlas_hybrid} are computed with limited
+ranges of $T_{\mathrm{wind}}$, $\beta$ and a fixed $i$, the resulting
+profiles exhibit a wide variety of line profile shapes, many of which
+are similar to the types of H$\alpha$ profiles seen in the observations
+(c.f.~\citealt{reipurth:1996}).
+
+An examination of the profiles in
+Figures~\ref{fig:atlas_discwind_only} and
+Figure~\ref{fig:atlas_hybrid} reveals some of problems
+with uniqueness that must inevitably occur when trying to assign an
+individual profile as wind or accretion dominated i.e. very similar
+profiles may arise from very different circumstellar geometries. For
+example, the disc-wind only model with
+$\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
+in Figures~\ref{fig:atlas_discwind_only} and the accretion dominated
+model with
+$\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
+in Figure~\ref{fig:atlas_hybrid} give very similar
+profiles.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.45]{figures/discwind_mu_effect.eps}
+
+  \end{center}
+
+  \caption{The effect of the mass-loss rate to mass-accretion rate
+    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
+    H$\alpha$ profile computed with only the magnetospheric accretion
+    (thick solid) is compared with the disc-wind-magnetosphere
+    hybrid models for $\mu =$ 0.025 (dash-dot), 0.1
+    (solid) and 0.2 (dash). The magnetosphere used here has
+    $T_{\mathrm{max}}=7500\,\Kelvin$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
+    temperature and the acceleration parameter of the disc wind are
+    $T_{\mathrm{wind}}=9000\,\Kelvin$ and $\beta=0.5$ respectively.
+    All the models are computed with the inclination angle
+    $i=55^{\circ}$. As $\mu$ increases the emission component becomes
+    stronger and the wings becomes broader, as expected. The
+    absorption component is relatively insensitive to the value of
+    $\mu$ in this example. The wide range of $\mu$ reasonably
+    reproduces the profiles similar to ones seen in observations
+    (e.g.~\citealt{reipurth:1996}).}
+
+  \label{fig:discwind_mu_effect}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The effect of changing the ratio of the wind mass-loss rate to
+mass-accretion rate
+($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
+in Figure~\ref{fig:discwind_mu_effect}. With a fixed value of
+mass-accretion rate
+($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
+mass-loss rate is varied. The figure shows that as $\mu$ increases the
+P-Cygni absorption deepens only slightly., and the position of minimum flux in the
+absorption trough appears to move blue-ward.  On the other hand, the
+flux peak increase and the line wings become stronger as $\mu$
+increases.  Although MHD models suggests (e.g.~\citealt{koenigl:2000})
+that $\mu \sim 0.1$, the figure suggest that models a relatively wide range
+of $\mu$  (e.g.~between 0.025 and 0.2 in this case)  reproduce the
+profiles similar to observations.
+
+Apparently, the type of profiles  
+(affected by the blue-shifted absorption feature) seen in this section
+cannot be explained by the magnetospheric accretion flow alone
+(e.g.~\citealt{muzerolle:2001}).  Comparison of the model profiles
+with different types of the observed H$\alpha$ profiles will be given
+in section~\ref{sub:Classification-scheme-proposed}.
 
@@
 \label{sub:Classification-scheme-proposed}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.65]{figures/atlas_reipurth_like_discwind.eps}
+
+  \end{center}
+
+  \caption{Sample H$\alpha$ model profiles which characterise the
+    classification by \citet{reipurth:1996}. The combination of
+    magnetospheric accretion flow, the accretion disc, and the disc wind
+    model can reasonably reproduce wide ranges of H$\alpha$ profiles seen
+    in observations.  The model parameters used for each profile and
+    short comments are summarised in
+    Table~\ref{tab:classification}. The horizontal axes 
+    are velocities in $\kmps$, and the vertical axes are normalised
+    flux.}
+
+  \label{fig:atlas_reipurth}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 accretion disc can reasonably reproduce all the classes of the profiles
-seen in observations. Similar profiles can be reproduced if the bipolar
-wind is used instead of the disc wind, but the wind absorption at
-a given velocity location occurs at a different inclination angles
-when the wind type is switched from the bipolar wind to the disc wind.
-The corresponding parameters (of the disc-wind, magnetosphere,
-hybrid model) used to reproduce the profiles
-in the figure are given in Table~\ref{tab:classification} along
+seen in observations. The corresponding parameters of the
+disc-wind-magnetosphere hybrid model used to reproduce the profiles
+in the figure are summarised in Table~\ref{tab:classification} along
 with brief comments on possible physical conditions which leads to
@@
 produced in the magnetosphere.  Although not shown here, this type of
-profile can be also reproduced with the disc-wind, magnetosphere hybrid
-model with low inclination angles ($<\sim10^\circ$).  Since there is
+profile can be also reproduced with the disc-wind-magnetosphere hybrid
+model with low inclination angles ($\lesssim 10^\circ$).  Since there is
 no material in the polar region in the disc wind model, the observer
@@
 cases, provided that wind temperature is low enough so that the wind
-emission is negligible. The bipolar wind, magnetosphere and accretion
-hybrid model with high inclination ($70^\circ$ -- $80^\circ$) can also 
-give this type of profile since the influence of the bipolar wind is
-minimum in the equatorial directions. The wind acceleration parameter
-for the bipolar wind must be relatively small  ($\beta < \sim 0.5$).
+emission is negligible.
 
 \textbf{Type~II-B}:  
-This type can be produced by the disc-wind magnetosphere hybrid models
+This type can be produced by the disc-wind-magnetosphere hybrid models
 at moderate to high inclination angles with wide ranges of the wind
-acceleration rate ($\sim 0.2 < \beta < \sim 2.0$) and the wind
-temperature ($\sim 7000\,\mathrm{K}< T < \sim 9000 \mathrm{K}$). If
+acceleration rate ($0.2 \lesssim \beta  \lesssim 2.0$) and the wind
+temperature ($7000\,\mathrm{K} \lesssim T \lesssim 9000 \mathrm{K}$). If
 the inclination is high ($i \sim 80^\circ$), the disc-wind
-acceleration parameter should be relatively small ($\beta < \sim
+acceleration parameter should be relatively small ($\beta \lesssim
 0.5$). If the inclination is moderate ($i \sim 60^\circ$), the wind
-acceleration parameter should be relatively high ($\beta > \sim 2.0$).
-This type can be also produced in the bipolar wind, magnetosphere disc
-hybrid model with similar ranges of inclinations ($\sim 60^\circ < i <
-\sim 80^\circ$) and temperatures ($\sim 7000\,\mathrm{K}< T < \sim
-9000 \mathrm{K}$), but the wind acceleration should be always high
-($\beta > \sim 1.0$).
+acceleration parameter should be relatively high ($\beta \gtrsim 2.0$).
 
@@
 The physical conditions which result in this type
-is very similar to those of Type~II-B according to the disc-wind
-magnetosphere hybrid models. The main difference is between 
+is very similar to those of Type~II-B according to the
+disc-wind-magnetosphere hybrid models. The main difference is between  
 the two is in their inclination angles. This type is more likely
 seen at higher inclination angles ($i \sim 80^\circ$) compared to Type
-II-B.  
-With the bipolar wind model, the wind acceleration parameter must be
-very large ($\beta \sim 6.0$) to produce this type, and the
-inclination must be moderate to low ($i < \sim 60^\circ$).  This type
-is rarely seen in the bipolar wind models with the nominal parameter
-ranges i.e. $\sim 0.2 < \beta < \sim 2.0$ and $\sim 7000\,\mathrm{K}<
-T < \sim 9000 \mathrm{K}$.  More common in the models with the disc wind.
+II-B.  Commonly seen in the models with the disc wind only model.
 
@@
 samples in \citet{reipurth:1996}. Interestingly, the most common
-profile type seen in both the bipolar wind, disc, magnetosphere hybrid
-models and the disc-wind, magnetosphere hybrid model are Type~III-B
-profiles (c.f.~Figures~\ref{fig:atlas_disc_wind_acc_model} and
-\ref{fig:atlas_discwind_acc_model}). In this type of profiles, the
+profile type seen in the disc-wind-magnetosphere hybrid model are
+Type~III-B profiles (c.f.~Figures~\ref{fig:atlas_hybrid} and
+\ref{fig:atlas_hybrid}). In this type of profiles, the
 main emission comes from the magnetosphere, and the profile shape is
@@
 III-R to Type~II-R if the value of $\beta$ increases. The
-inclination angles must be moderate to high ($\sim 60^\circ <i <
-\sim 80^\circ$).  On the other hand, the inclination must be low to
-moderate ($i < \sim 60^\circ$) in the models with the
-bipolar wind.  The difference in the inclination dependency occurs
-since the density distribution of the two types of the winds are
-different.
+inclination angles must be moderate to high ($ 60^\circ \lesssim i \lesssim
+ 80^\circ$).
 
@@
 $\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
-Similarly, in the models with the bipolar wind, the inclination angle
-must be very high (close to edge on) to produce this type of profile.
-Since the inclination angles must be high for both wind models, this
+Since the inclination angles must be high, this
 indicates that the accretion disc plays an important role in producing
@@
 value) than that in Type~III-B.  In the models with the disc-wind,
-this type is seen at moderate to high inclinations ($\sim 60^\circ <i
-\sim 80^\circ$) with relatively small value of the acceleration
-parameters ($\beta < \sim 0.5$).  In the models with the bipolar wind,
-this type is commonly seen at moderate to low inclinations (($i \sim <
-60^\circ$).  The difference in the inclination dependency occurs
-because of the density distribution of the two types of the winds are
-different.
+this type is seen at moderate to high inclinations ($60^\circ \lesssim
+ i \lesssim  80^\circ$) with relatively small value of the acceleration
+parameters ($\beta \lesssim 0.5$).
 
 \textbf{Type~IV-R}: 
-This is the second least common type of observed profile (5~per~cent)
+This is the second least common type of the observed profiles (5~per~cent)
 which shows the inverse P-Cyg profile shape.  This can be understood
@@
 predicts that the redshifted absorption can occur at a limited range
-of inclination angle ($i= \sim 50^\circ$, but depends on the geometry of
+of inclination angle ($i\simeq 50^\circ$, but depends on the geometry of
 the magnetosphere) with which the hot continuum flux from the
@@
 P-Cyg profile.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.65]{figures/atlas_reipurth_like_discwind.eps}
-
-  \end{center}
-
-  \caption{Sample H$\alpha$ model profiles which characterise the
-    classification by \citet{reipurth:1996}. The combination of
-    magnetospheric accretion flow, the accretion disc, and the disc wind
-    model can reasonably reproduce wide ranges of H$\alpha$ profiles seen
-    in observations. Similar results can be obtained if the bipolar wind is
-    replaced by the disc wind. The model parameters and short comments are
-    summarised in Table~\ref{tab:classification}. The horizontal axes
-    are velocities in $\kmps$, and the vertical axes are normalised
-    flux.}
-
-  \label{fig:atlas_reipurth}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection{H$\alpha$ as a mass accretion diagnostic}
+\subsection{Inclination dependency of H$\alpha$ profiles}
 
 \label{sub:ha-mass-accretion-diagnostic}
-
-In the previous sections, two possible geometrical configurations
-for the wind from CTTS were considered: (1)~a bipolar wind, and (2)~a
-disc wind. While the material is more concentrated toward the polar
-regions for a given radius in the first case, the material is more concentrated
-toward the equatorial plane in the second case. 
-%As mentioned earlier,
-%the bipolar wind model resembles the density distribution of the jet
-%MHD simulation of e.g.~\citet{krasnopolsky:2003} in large scale
-%($>10$~au), and the disc wind model resembles that in smaller scale
-%($<10$~au).
-
-The distinct difference in the density dependency on the polar angles
-in two models should be apparent in the inclination angle dependency
-on the shapes of the line profiles. Figure~\ref{fig:effect_inclination_compare}
-shows the H$\alpha$ profiles computed for 1.~the disc, bipolar-wind,
-accretion hybrid model (section~\ref{sub:model-acc-disc-wind}) and
-2.~the disc-wind, magnetosphere hybrid model (section~\ref{sub:result-discwind-knigge})
-at inclination angles $i=10^{\circ}$, $55^{\circ}$ and $80^{\circ}$. Both
-models include the magnetospheric accretion component with the same
-parameters used as in sections~\ref{sub:model-acc-disc-wind} and
-\ref{sub:result-discwind-knigge} i.e. $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=1\times10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-
-Mainly because of the geometrical configuration, the P-Cyg absorption
-feature weakens as the inclination increases for the model with the
-bipolar wind. The optical depth to an observer is higher (from the
-wind emission region) for with a lower inclination angle with this
-geometry. Although not shown here, this tendency of the inclination
-dependency holds for the models with bipolar wind models for wide
-ranges of $\beta$ and $T_{\mathrm{wind}}$. For the model with the
-disc wind, the absorption becomes stronger as the inclination becomes
-larger. The optical depth to an observer becomes larger as the inclination
-increases in this geometry.
-
-Similarly, the line equivalent width increases as the inclination
-angle increases for the model with the bipolar wind, it decreases
-as the inclination angle increases for the model with the disc wind.
-For the models with only magnetosphere (section~\ref{sub:model-acc}),
-we find that the line equivalent width decreases as the
-inclination increases in those models (see Figure~\ref{fig:acc_inclination_effect}).
-Interestingly, the observational study of \citet{appenzeller:2005}
-showed that the H$\alpha$ line equivalent width of CTTS increases
-as the inclination angle increases. Only the models with the bipolar
-wind agree with the trend seen in their observation. Although the
-uncertainty in the inclination angles of the observed object might
-be large, a larger sample in addition to that of \citet{appenzeller:2005}
-for further investigation of the inclination dependency on the line
-profile will be extremely useful for determining the wind configuration
-of CTTS.
 
@@
 	clip,
-	scale=0.45]{figures/disc_wind_acc_inc_effect_m9_b2_t7000.eps}&
+	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}&
       \includegraphics[%
 	clip,
-	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}\tabularnewline
+	scale=0.45]{figures/disc_wind_acc_inc_effect_m9_b2_t7000.eps}\tabularnewline
     \end{tabular}
@@
     angle. The profiles computed at $i=10^{\circ}$(solid), $55^{\circ}$
-    (dot) and $80^{\circ}$ (dash) using 1.~the disc, bipolar-wind,
-    accretion hybrid model (left panel;
-    c.f. section~\ref{sub:model-acc-disc-wind}) and 2.~using the
-    disc-wind, magnetosphere hybrid model (right;
-    c.f. section~\ref{sub:result-discwind-knigge}) are shown for a
+    (dot) and $80^{\circ}$ (dash) using (1)~the
+    disc-wind-magnetosphere hybrid model (left;
+    c.f. section~\ref{sub:result-discwind-knigge}) and (2)~the disc, stellar wind,
+    magnetosphere hybrid model (right panel;
+    c.f. Figure~\ref{fig:config_stellarwind}) are shown for a
     comparison.  The parameters used for the magnetosphere are same for
@@
     isothermal wind temperature and the wind acceleration parameter used
-    in both models are $T=7000~\mathrm{K}$ and $\beta=1.0$ respectively.
+    in (1) are $T_{\mathrm{wind}}=7000~\mathrm{K}$ and $\beta=1.0$,
+    and those in (2)
+    are $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=0.5$ respectively.
     All the other parameters are same as in
-    sections~\ref{sub:model-acc-disc-wind} and
+    sections~\ref{sub:result-discwind-hybrid} and
     \ref{sub:result-discwind-knigge}. While the line equivalent width
-    increases as the inclination angle increases for the former model
-    configuration, it decreases as the inclination angle increases for the
-    latter. Only the former agrees with the tendency seen in the
+    decreases as the inclination angle increases for the disc-wind
+    model, it increases as the inclination angle increases for the
+    stellar wind model. Only the latter agrees with the tendency seen in the
     observational study of \citet{appenzeller:2005} who showed that the
@@
 
-Despite the inclination angle dependency of the observed H$\alpha$
-favouring the models with bipolar wind, there are two main aspects of
-this model which are not quite consistent with the magneto-centrifugal
-launched jet numerical models (e.g \citealt{krasnopolsky:2003}).
-First, in section~\ref{sub:model-acc-disc-wind}, we found that the
-ratio of the mass-loss to mass-accretion rates needed to be rather
-small ($\mu<\sim0.025$), in order not to have an unrealistically
-strong P-Cyg absorption component, compared to the MHD simulations
-suggested \citep{koenigl:2000} i.e. $\mu\approx0.1$.
-%In the model
-%fit of T~Tau observation (section~\ref{sub:ttau-model}), we found
-%much larger value of the ratio $\mu=0.18$. 
-Considering large uncertainty in MHD theories and observational
-measurements (e.g.~$\dot{M}_{\mathrm{acc}}$, 
-$\dot{M}_{\mathrm{wind}}$ and $B$), the wide range of the mass-loss
-to mass-accretion ratio 
-%(e.g.~$0.025<\mu<0.18$) 
-may be still reasonable. On the other hand, the models with the disc
-wind (section~\ref{sub:result-discwind-knigge}) 
-using $\mu=0.1$ reproduces the profiles (Figure~\ref{fig:atlas_discwind_acc_model})
-similar to that seen in observations. Second, the MHD models predict
-that the wind/jet becomes collimated well above the disc plane ($>10$~au),
-but our bipolar wind model are collimated (density enhanced toward
-in the polar direction) from right outside of the magnetosphere. Unless
-the origin of the wind is from the central star itself, the density
-distribution used for the bipolar wind is not quite consistent with
-the near field of the MHD jet models, considering that the most of
-the H$\alpha$ emission occurs within a few to a several radii of
-the magnetosphere (Figure.~\ref{fig:effect_alpha_disc}). The density
-structure used for the disc wind model, however, is very similar to
-that of MHD simulations in the near field where the most of the H$\alpha$
-wind emission occurs. Interestingly, however, the recent study of
-\citet{matt:2005} demonstrated the possibility that the stellar wind along
-the open magnetic field originated from the star can cause significant
-spin-down torque on the star, provided that mass-loss rate is high
-enough. Considering the issues mentioned above, it is not possible
-to favour the bipolar wind model to the disc wind model without further
-observational constraints. In reality, two types of the winds (bipolar
-wind and disc wind) may co-exits similar to that seen in e.g. \citet*{drew:1998}
-and \citet{matt:2005}. In these models, the fast stellar wind is
-present in the polar directions, and at the same time the slower disc
-wind is present near the equatorial plane.
-
-One possible way to distinguish the two different wind models is to
+In the previous sections, we have considered the H$\alpha$ line
+formations in the disc wind which mimic the density distribution of the
+magneto-centrifugal launched jet numerical models
+(e.g.~\citealt{krasnopolsky:2003}). The density in this model is more
+concentrated toward the equatorial plane in near field. 
+In this section, we investigate the consistency of the line formation
+in the disc-wind model with the recent the recent observation of
+\citet{appenzeller:2005} by concentrating on the inclination
+dependency of the EW of H$\alpha$.  Their study showed that 
+that the line equivalent width of CTTS increases
+as the inclination angle increases.
+
+The right panel in Figure~\ref{fig:effect_inclination_compare} shows
+the profiles computed with the disc-wind, magnetosphere hybrid model
+(section~\ref{sub:result-discwind-knigge}) 
+at inclination angles $i=10^{\circ}$, $55^{\circ}$ and
+$80^{\circ}$. The magnetospheric accretion component uses the  
+parameters used as the reference model (Table~\ref{tab:std_parameters}).  
+The figure shows that the absorption
+feature becomes stronger as the inclination increases, mainly because
+of the geometrical configuration.  The optical depth to becomes larger
+as the inclination angle increases since there is more material
+towards the equatorial plane.  Although not shown here, this tendency
+of the inclination dependency holds for the models with the wide
+ranges of $\beta$ and $T_{\mathrm{wind}}$ values.  
+As a result, the EW becomes smaller as the inclination
+angle increases. Clearly, this is not consist with the trend seen in
+the observation of \citet{appenzeller:2005}. Recall that a similar
+inclination dependency was found for the models with only
+magnetosphere (Figure~\ref{fig:acc_inclination_effect}).
+
+We have also considered an alternative wind model which would produce
+the inclination dependency of the H$\alpha$ EW  seen in the
+observation. In this model, the disc-wind is replaced by the stellar
+wind moving only in radial direction with the classical beta-velocity
+law \citep[c.f.][]{castor:1979}
+i.e.
+$v_{r}\left(\ r  \right) = v_{\infty} \left( 1 - R_{*}/r
+  \right)^{\beta}$  where  $v_{\infty}$ and  $R_{*}$ are the 
+  wind terminal velocity and the stellar radius respectively. $\beta$
+  is the wind acceleration parameter similar to the one seen in the
+  disc-wind model (c.f.~equation~\ref{eq:discwind-poloidal-velocity}).
+The wind emerges from the stellar surface, but restricted to be within
+$\sim30^{\circ}$ from the symmetry axis hence forming the cone-shaped 
+regions both above and below the poles. The density is computed from
+assuming the constant mass-loss rate per unit area over the stellar
+surface, the mass-flux conservation, and using the beta velocity low
+above.  The schematic of the model configuration is shown in
+Figure~\ref{fig:config_stellarwind}. Again, we assume the wind
+temperature ($T_{\mathrm{wind}}$) is isothermal for simplicity.  
+This model configuration is motivated by the recent study by
+\citet{matt:2005} who demonstrated the possibility that the stellar
+wind along the open magnetic field originated from the star can cause
+significant spin-down torque on the star, provided that mass-loss rate
+is high enough.
+
+The right panel in Figure~\ref{fig:effect_inclination_compare} shows
+the H$\alpha$ profiles computed using the alternative hybrid model at
+the same inclination angles used for the disc-wind-magnetosphere
+hybrid model. The wind acceleration parameter ($\beta$) and the wind
+temperature ($T_{\mathrm{wind}}$)used here are $0.5$ and
+$9000\,\Kelvin$ respectively. All the other parameters are same as in
+the disc-wind magnetosphere model.  With this set of $\beta$ and
+$T_{\mathrm{wind}}$, the wind emission is comparable or a slightly
+greater than the emission from the magnetosphere. Because of the
+geometry of the wind, the P-Cyg absorption feature weakens as the
+inclination increases. The optical depth of the wind is much higher in
+the polar direction compared to that at higher inclination. For the
+same reason, the EW of the line increases as the inclination increase
+as clearly seen in the figure.  Although not shown here, this tendency
+of the inclination dependency holds for the models with this wind
+models for wide ranges of $\beta$ and $T_{\mathrm{wind}}$ as long as
+the emission from the wind is comparable to that of the magnetosphere.
+
+The distinct difference in the density dependency on the polar angles
+in two different wind models should be apparent in the inclination
+angle dependency on the observed line profiles. For example, one
+possible way to distinguish the two different wind models is to 
 examine the profile shape of a CTTS which is known to be viewed at
@@
 component (e.g. Type IV-B), the system is more likely to be associated
-with the bipolar wind type of outflow (but not with the disc-wind type
-of outflow).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+with the `bipolar' stellar wind type of outflow (but not with the disc-wind type
+of outflow).  In reality, two types of the winds (bipolar stellar wind and
+disc wind) may co-exits similar to that seen in
+e.g. \citet*{drew:1998} and \citet{matt:2005}. In these models, the
+fast stellar wind is present in the polar directions, and at the same
+time the slower disc wind is present near the equatorial plane.
+
+The extensive parameter studies of the simple stellar wind model
+presented in this section have not been performed. The models
+presented here are for a demonstrative purpose, and the further
+investigation is necessary before the models are applied to a real
+system, perhaps, by combining our radiative transfer model with the
+results from MHD 'stellar' wind calculations.
+
+In this analysis, we found only the models with the bipolar stellar
+wind agree with the trend seen in their observation. Although the
+uncertainty in the inclination angles of the observed object might be
+large, a larger sample in addition to that of \citet{appenzeller:2005}
+for further investigation of the inclination dependency on the line
+profile will be extremely useful for determining the wind
+configuration of CTTS.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      scale=0.3]{figures/overview4.eps}
+
+  \end{center}
+
+  \caption{The alternative hybrid model. The model replaces the
+    disc-wind in the previous hybrid model with the stellar wind. The
+    wind launching from the stellar surface is limited within the
+    cones with the opening angle $\sim30^\circ$ to avoid the wind from
+    overlapping with the magnetosphere.  The system consists of four
+    components: (1)~the continuum source located at the origin $\left( o
+    \right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
+    $y$-axis is into the paper, (2)~the magnetospheric accretion flow,
+    (3)~the stellar wind outflow, and (4)~the accretion disc. The density
+    distribution is symmetric around the $z$-axis. }
+
+  \label{fig:config_stellarwind}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We have presented the disc--wind--magnetosphere hybrid radiative
+We have presented the disc-wind-magnetosphere hybrid radiative
 transfer models for classical T~Tauri stars, and detailed studies of
 the H$\alpha$ formation from their complex to circumstellar
-environment to understand the wide variety of H$\alpha$ profiles seen
-in observations. The two types of wind models considered are (1)~the
-bipolar wind model in which the wind originates from the star itself
-(section~\ref{sub:model-disc-wind}; Figure~\ref{fig:config_dipolar}), and
-(2)~the disc-wind model in which the wind originates from the inner
-part of the accretion disc
-(section~\ref{sub:Alternative-model-disc-wind};
-Figure~\ref{fig:config_discwind}).  We found that both wind models
-combined with the magnetospheric accretion flow reproduces the wide
-variety of H$\alpha$ profiles
-(Figures~\ref{fig:atlas_disc_wind_acc_model} and
-\ref{fig:atlas_discwind_acc_model}) seen in the observations.
-
-The inclination dependency of the line equivalent width predicted by
-the bipolar wind model agree with trends seen in the observation, but
-the disc-wind model does not. With the reference magnetospheric
-configuration (Table~\ref{tab:std_parameters}), the ratio of the
-mass-loss to mass-accretion rates ($\mu$) used in the bipolar wind was
-set to be 4 --10 times smaller than that predicated by
-magneto-hydrodynamical (MHD) calculations (c.f.~$\mu\sim0.1;$
-\citealt{koenigl:2000}) to avoid the blue-shifted absorption component
-becoming unrealistically too strong; however $\mu$ used in the
-disc-wind models are consistent with MHD calculations.
+environment.  We found that hybrid model can reproduce the wide
+variety of profile seen in observations
+(Figures~\ref{fig:atlas_acc_models}, \ref{fig:atlas_discwind_only},
+\ref{fig:atlas_hybrid} and \ref{fig:atlas_reipurth}). 
+Especially, the blue-shifted
+wind absorption feature very commonly seen in the H$\alpha$ profile of
+CTTS were well understood by this model.  This was not possible in the
+magnetospherical accretion only model presented in earlier works
+(e.g.~\citealt{muzerolle:2001}).
 
@@
 basic physical conditions that reproduce the profiles in each
-classified type. Using the different combinations of the inclination
+classified type
+(section~\ref{sub:Classification-scheme-proposed}). Using the different
+combinations of the inclination 
 ($i$), the mass-loss to mass-accretion rate ratio ($\mu$) and the wind
 acceleration rate ($\beta$), our radiative transfer model was able to
-produce all 7 types of the profiles in \citet{reipurth:1996}.
-%Using the hybrid model, we also fit the observed H$\alpha$
-%from the optical component of T~Tau triple system (T~Tau~N). The
-%agreement between the model and the observation is excellent; however,
-%we could not confirm the uniqueness of the fit. The ratio of the mass-loss
-%to mass-accretion rate was found to be $\sim0.18$, which is consistent
-%with \citet{koenigl:2000}.
-%
-%Although not attempted in this paper, a better approach for determining
-%the mass-loss and mass-accretion rate consistently is to model multiples
-%lines simultaneously. For example, the mass-accretion rate of an object
-%can be determined more easily by modelling Pa$\beta$ and Br$\gamma$
-%since there is no/little wind effect seen in these lines. The mass-accretion
-%rate then can be used to model H$\alpha$ to find the wind mass-loss
-%rate.
+produce all 7 classes of profiles defined in \citet{reipurth:1996}.
+
+The value of $\mu$, 0.1,  suggested by both MHD calculations and observations
+(c.f.~\citep{koenigl:2000}) is consistent with the 
+disc-wind-magnetosphere models presented here. We found that the
+hybrid models with $0.025<\mu<0.2$ are also consistent with the type
+of the profiles seen in the observations (e.g~\citealt{reipurth:1996}).
+
+Unfortunately, the dependency of the line equivalent width on
+the inclination angle predicted by  
+the disc-wind-magnetosphere hybrid model does not agree with the trend
+seen the observation of \citet{appenzeller:2005}; however, their
+results are based on a small number of objects (12). We have also
+considered an alternative hybrid model in which the disc-wind is
+replace by the narrow cone-shaped stellar wind, and found that the
+alternative wind hybrid model can reasonably reproduces the 
+line equivalent width dependency on the inclination seen in the
+observation (Figure~\ref{fig:effect_inclination_compare}).
 

### 2006-01-26 TTau_Halpha/kurosawa.tex
Close to final version.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@633 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
+To quantify the relative amount of the wind emission compared to the
+that of the magnetosphere, we have computed the ratio the EW of the
+hybrid model in Figure~\ref{fig:atlas_hybrid} with the EW of the
+magnetosphere only model.   The EW ratio sometimes becomes below 1.0
+when the wind only contributes to the absorption, but not to the
+emission component of the resulting profile. 
+In some models (e.g.~with $T_{\mathrm{wind}}=8000\,\Kelvin$ and
+$\beta=2.0$), the contribution of the wind to the EW is much larger
+than that from the magnetosphere (EW ratio is 3.2). This clearly
+demonstrates that the difficulty of using the EW of H$\alpha$ as
+accretion indicator since it might as the indicator for the
+mass-loss.  We have also seen in Figure~\ref{fig:atlas_discwind_only}
+that the disc wind models without the magnetosphere can produce the
+H$\alpha$ line with significantly large EW. 
+If the line fit was applied to an observed H$\alpha$ line by ignoring
+the wind, the temperature and  
+the mass-accretion rate of the magnetospherical accretion flow could 
+be overestimated. A better approach to a model fit is a simultaneous
+fitting of multiple lines. For example, the near-infrared lines such
+as Pa$\beta$ and Br$\gamma$ should be used to determined the mass-loss
+rate since these lines are much less affected by the wind. Using the
+mass-loss rate from these lines, H$\alpha$ can be used to determine
+the wind mass-loss rate.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.45]{figures/discwind_mu_effect.eps}
+
+  \end{center}
+
+  \caption{The effect of the mass-loss rate to mass-accretion rate
+    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
+    H$\alpha$ profile computed with only the magnetospheric accretion
+    (thick solid) is compared with the disc-wind-magnetosphere
+    hybrid models for $\mu =$ 0.05 (dash-dot), 0.1
+    (solid) and 0.2 (dash). The magnetosphere used here has
+    $T_{\mathrm{max}}=7500\,\Kelvin$ and
+    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
+    temperature and the acceleration parameter of the disc wind are
+    $T_{\mathrm{wind}}=9000\,\Kelvin$ and $\beta=0.5$ respectively.
+    All the models are computed with the inclination angle
+    $i=55^{\circ}$. As $\mu$ increases the emission component becomes
+    stronger and the wings becomes broader, as expected. The
+    absorption component is relatively insensitive to the value of
+    $\mu$ in this example. The wide range of $\mu$ reasonably
+    reproduces the profiles similar to ones seen in observations
+    (e.g.~\citealt{reipurth:1996}).}
+
+  \label{fig:discwind_mu_effect}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 An examination of the profiles in
@@
 profiles.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-
-  \begin{center}
-
-    \includegraphics[%
-      clip,
-      scale=0.45]{figures/discwind_mu_effect.eps}
-
-  \end{center}
-
-  \caption{The effect of the mass-loss rate to mass-accretion rate
-    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
-    H$\alpha$ profile computed with only the magnetospheric accretion
-    (thick solid) is compared with the disc-wind-magnetosphere
-    hybrid models for $\mu =$ 0.025 (dash-dot), 0.1
-    (solid) and 0.2 (dash). The magnetosphere used here has
-    $T_{\mathrm{max}}=7500\,\Kelvin$ and
-    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
-    temperature and the acceleration parameter of the disc wind are
-    $T_{\mathrm{wind}}=9000\,\Kelvin$ and $\beta=0.5$ respectively.
-    All the models are computed with the inclination angle
-    $i=55^{\circ}$. As $\mu$ increases the emission component becomes
-    stronger and the wings becomes broader, as expected. The
-    absorption component is relatively insensitive to the value of
-    $\mu$ in this example. The wide range of $\mu$ reasonably
-    reproduces the profiles similar to ones seen in observations
-    (e.g.~\citealt{reipurth:1996}).}
-
-  \label{fig:discwind_mu_effect}
-
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 in section~\ref{sub:Classification-scheme-proposed}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+
+  \caption{The ratio of the line equivalent width (EW) of the
+    disc-wind magnetosphere hybrid models in
+    Figure~\ref{fig:atlas_hybrid} to the EW of the magnetosphere only model. }
+
+\label{tab:ew_ratio}
+
+\begin{center}
+
+\begin{tabular}{lccccc}
+\hline 
+$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
+&
+$\beta$&
+&
+&
+\tabularnewline
+&
+&
+$0.2$&
+$0.5$&
+$1.0$&
+$2.0$\tabularnewline
+\hline 
+$7000$&
+&
+$1.1$&
+$.94$&
+$.89$&
+$.96$\tabularnewline
+$8000$&
+&
+$1.1$&
+$.92$&
+$1.2$&
+$3.2$\tabularnewline
+$9000$&
+&
+$1.0$&
+$1.1$&
+$7.5$&
+$36.$\tabularnewline
+\hline
+\end{tabular}
+
+\end{center}
+
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	clip,
-	scale=0.45]{figures/disc_wind_acc_inc_effect_m9_b2_t7000.eps}\tabularnewline
+	scale=0.45]{figures/stellarwind_inc_effect.eps}\tabularnewline
     \end{tabular}
@@
 $T_{\mathrm{wind}}$, the wind emission is comparable or a slightly
-greater than the emission from the magnetosphere. Because of the
-geometry of the wind, the P-Cyg absorption feature weakens as the
-inclination increases. The optical depth of the wind is much higher in
+greater than the emission from the magnetosphere. The profiles show
+rather complex absorption features because of the interaction of
+photons created in the wind with the magnetosphere. 
+While the blue-shifted absorption features are formed in the wind, the
+absorption features near the line centre and in the red wing (only for
+$i=10^\circ$) are caused by the wind emission by the magnetosphere
+which has a rather complex flow geometry. 
+Because of the geometry of the wind, the P-Cyg absorption feature
+weakens as the inclination increases. The optical depth of the wind is
+much higher in 
 the polar direction compared to that at higher inclination. For the
@@
 
+The profiles computed with the hybrid model showed that the wind
+emission contribution becomes significantly larger than that from the
+magnetosphere (Figure~\ref{atlas_hybrid} and
+Table~\ref{tab:ew_ratio}).  Henceforth, a large H$\alpha$ equivalent
+width does not necessary indicate a large mass-accretion rate, but it
+could be caused by the mass-loss by the wind outflow.
+
 Using the model results, we examined the H$\alpha$ spectroscopic
@@
 disc-wind-magnetosphere models presented here. We found that the
-hybrid models with $0.025<\mu<0.2$ are also consistent with the type
+hybrid models with $0.05<\mu<0.2$ are also consistent with the type
 of the profiles seen in the observations (e.g~\citealt{reipurth:1996}).

### 2006-01-26 TTau_Halpha/kurosawa.tex
Minor update.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@634 25464f21-6099-402c-b30a-640f1d40d38b

@@
 outer part is important for determining the shape of the H$\alpha$
-profiles observed at high inclinations, as we will see in section~XXX.
+profiles observed at high inclinations.
 

### 2006-01-26 TTau_Halpha/kurosawa.tex
test
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@635 25464f21-6099-402c-b30a-640f1d40d38b

@@
 the geometrically thin (but opaque) disc. Since the emissivity of the
-disc at the optical wavelength is negligible and the disc scale height
-is relatively small in the inner part of disc, this replacement is
-reasonable.  On the other hand, the finite height of the disc at the
-outer part is important for determining the shape of the H$\alpha$
-profiles observed at high inclinations.
+disc at optical wavelengths is negligible, and the disc scale height
+is relatively small in the inner part of disc, this simplification is
+reasonable:  the most important factor in determining the shape of the 
+H$\alpha$ profiles is the finite height of the disc at large radii for large
+inclinations.
 
@@
 \citet{white:2003}, the half of the models shown in the figure can be
-classified as CTTS, and the other half as WTTS.
+classified as CTTS, and the other half as WTTS. However, the profiles corresponding
+to the WTTS designations have an inverse P-Cygni morphology that is rarely
+seen in observations (\citealt{reipurth:1996} and
+section~\ref{sub:Classification-scheme-proposed}).
 
@@
 FU-Ori type (c.f.~\citealt{reipurth:1996}) for the models with small
-$\beta$ to the stronger emission types which are more commonly seen in
-the observed H$\alpha$ (c.f.~\citealt{reipurth:1996}) as the value of
+$\beta$ to the stronger emission types, which are more commonly seen in
+the observed H$\alpha$ (c.f.~\citealt{reipurth:1996}), as the value of
 $\beta$ increases.  
@@
 
- As one can see in Figure~\ref{fig:discwind_vr_rho}, the column density of the
-gas moving at $v_{\infty}$ increases as the wind acceleration becomes
-larger since the gas moving at $v_{\infty}$ becomes closer to the
-photosphere. At the location where the absorption occurs, the gas is
-moving faster for the models with the faster wind acceleration models;
-hence, the location of the absorption component is bluer as $\beta$
-becomes smaller (as the wind acceleration faster). The figure also
-shows that the intensity of the emission component increases as
-$\beta$ increases for a given $T_{\mathrm{wind}}$. This is mainly
+The intensity of the emission component increases as
+$\beta$ increases for a fixed $T_{\mathrm{wind}}$. This is mainly
 because the density near the photosphere increases as the value of
 $\beta$ increases (Figure~\ref{fig:discwind_vr_rho}); hence, the
-emissivity of increases. Unlike the magnetospheric accretion only
-models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
-profiles are not seen here, nor the blue-ward asymmetry. Because of
-the absorption component in P~Cygni profile, most of the profiles show
-red-ward asymmetry except for the fast wind acceleration models
-($\beta=0.2$ and $0.5$)with low inclinations (not shown here).
+emissivity of increases. Most of the profiles show a red-ward asymmetry, mainly
+due to the presence of the classical P-Cygni absorption. However we find
+that the disc-wind models with the fastest acceleration ($\beta=0.2$ and $0.5$)
+and viewed at low inclinations, show a strong blue asymmetry due to
+occultation of the receding half of the outflow by the optically thick disc.
 
@@
     the wind parameter $T_{\mathrm{wind}} = 9000\Kelvin$ and $\beta  =
-    0.5$ for $i=55^{\circ}$.  The profiles in the figure uses $d = 
+    0.5$ for $i=55^{\circ}$.  The profiles in the figure use $d = 
     11~R_{*}$ (dashed),   $18~R_{*}$ (dash-dot) and $22~R_{*}$
@@
     component is relatively insensitive to $d$ since the change in the
-    column density toward the observer is relatively small.  No
-    magnetospherical component is included. 
-  }
+    column density toward the observer is relatively small. }
 
@@
    $0.5 \times 10^{-8}~\mathrm{M_{\sun}\,yr^{-1}}$\, (dash-dot) 
-    are shown above. The
-    models are computed with only the disc-wind component (no magnetospheric
-    accretion). With all other parameter fixed
-    constant, the mass-loss rate behaves as a scaling factor for the wind
+    are shown above. With all other parameter fixed, 
+    the mass-loss rate behaves as a scaling factor for the wind
     density (c.f.~equation~\ref{eq:discwind-density}).}
@@
 The effect of varying the wind mass-loss rate is shown in
-Figure~\ref{fig:discwind_mdot_effect}.  The line is very sensitive to the
-mass-loss rate. With all other parameters fixed constant,
-$\dot{M}_{\mathrm{wind}}$ acts as an scaling factor of the wind
-density (equation~\ref{eq:discwind-density}). The important processes
-in forming H$\alpha$ emission are the recombination process and the
-subsequent downward transition to $n=3$ level. Assuming the ionisation
-fraction remains constant, the recombination rate is proportional to
-the square of wind density; hence the line is very sensitive to the
-change in $\dot{M}_{\mathrm{wind}}$.  We have found the line flux of
-the models in the figure is approximately proportional to the square
-of the mass-loss rate. This very sensitive nature of H$\alpha$ would
-make the line a good candidate for a mass-loss rate indicator;
-however, without solving the ambiguity of the emission component from
-the magnetospheric accretion flow and the wind, and without knowing
-the detailed temperature structure of the wind, it could provide us a
-misleading a mass-loss rate estimate of a T Tauri star.
-
-By inspecting the model H$\alpha$ images computed (no shown here), we have
- found that the extent of the H$\alpha$ emission region is relatively
- small i.e.~$h\lesssim 0.2\,\mathrm{au}$ or $20\, R_{*}$ where h is the
- vertical distance from the disc when compared to the
- spectro-astrometric observations of \citet{takami:2003} 
-for RU~Lup and CS Cha which show 1--5~au scale outflows%
-\footnote{Their observations also show some objects
-(e.g~Z CMa and AS~353A) displaying the outflows in larger scale
-($>50\,\mathrm{au}$); however, this could be formed in shocks rather
-than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
-(e.g.~\citealt{shang:2002}). %
-}. The extent of the line emission region becomes slightly
-larger ($\sim0.4$~au) if a slower wind acceleration rate (e,g,~$\beta=4$)
-is used.
+Figure~\ref{fig:discwind_mdot_effect}. With all other parameters fixed,
+$\dot{M}_{\mathrm{wind}}$ acts as an scaling factor for the wind
+density (equation~\ref{eq:discwind-density}). The important process
+that populates the $n=3$ level is recombination, and therefore the
+line emissivity varies as the square of the density (assuming that the
+ionisation fraction remains constant); hence the line is very sensitive to 
+changes in $\dot{M}_{\mathrm{wind}}$.  We indeed find that  the line flux of
+the models is approximately proportional to the square
+of the mass-loss rate.
 
@@
 
-We now consider the models computed with a combination of the
-disc-wind and the magnetospheric accretion components. The parameters
+We now consider models computed with a combination of the
+disc-wind and magnetospheric accretion components. The parameters
 used for the magnetosphere are  same as in 
@@
 Figure~\ref{fig:atlas_hybrid} shows the models profiles
-computed using the same ranges of the disc-wind temperature and the
+computed using the same ranges of the disc-wind temperature and
 wind acceleration parameter as in the previous cases.
@@
 \citealt{alencar:2000}); however, the lower mass-loss rate models
-(while keeping $\mu$ constant) produce the profiles with the line
+(while keeping $\mu$ constant) produce profiles with the line
 strengths comparable to observations.  Although the models in
@@
 
-To quantify the relative amount of the wind emission compared to the
-that of the magnetosphere, we have computed the ratio the EW of the
-hybrid model in Figure~\ref{fig:atlas_hybrid} with the EW of the
-magnetosphere only model.   The EW ratio sometimes becomes below 1.0
-when the wind only contributes to the absorption, but not to the
-emission component of the resulting profile. 
+In order to quantify the relative contributions of the wind emission and
+ the magnetosphere, we have computed the ratio the EW of the
+hybrid model in Figure~\ref{fig:atlas_hybrid} to the EW of the
+magnetosphere only model (Table~\ref{tab:ew_ratio}).
+This  ratio falls below 1.0 when the wind only contributes
+to the line absorption, but not to the emission. 
 In some models (e.g.~with $T_{\mathrm{wind}}=8000\,\Kelvin$ and
 $\beta=2.0$), the contribution of the wind to the EW is much larger
-than that from the magnetosphere (EW ratio is 3.2). This clearly
-demonstrates that the difficulty of using the EW of H$\alpha$ as
-accretion indicator since it might as the indicator for the
-mass-loss.  We have also seen in Figure~\ref{fig:atlas_discwind_only}
-that the disc wind models without the magnetosphere can produce the
+than that of the magnetosphere (EW ratio is 3.2). This clearly
+demonstrates that the difficulty of using the EW of H$\alpha$ alone as
+an accretion measure.   We have also seen in Figure~\ref{fig:atlas_discwind_only}
+that disc wind models {\em without}  a magnetosphere can produce an
 H$\alpha$ line with significantly large EW.
-If the line fit was applied to an observed H$\alpha$ line by ignoring
-the wind, the temperature and  
-the mass-accretion rate of the magnetospherical accretion flow could 
-be overestimated. A better approach to a model fit is a simultaneous
-fitting of multiple lines. For example, the near-infrared lines such
-as Pa$\beta$ and Br$\gamma$ should be used to determined the mass-loss
-rate since these lines are much less affected by the wind. Using the
-mass-loss rate from these lines, H$\alpha$ can be used to determine
-the wind mass-loss rate.
 
@@
     H$\alpha$ profile computed with only the magnetospheric accretion
-    (thick solid) is compared with the disc-wind-magnetosphere
+    (thick solid) is compared to the disc-wind-magnetosphere
     hybrid models for $\mu =$ 0.05 (dash-dot), 0.1
@@
 in section~\ref{sub:Classification-scheme-proposed}.
+
+xxx add a sample halpha image from poster xxxx
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+
+  \begin{center}
+
+    \includegraphics[%
+      clip,
+      scale=0.45]{figures/discwind_hybrid_ha_image.eps}
+
+  \end{center}
+
+  \caption{An H$\alpha$ image of the disc-wind hybrid model viewed at an inclination
+  of 80$^\circ$. The false-colour scale shows logarithmic surface brightness (arbitrary
+  units) and the axes are linear dimensions in au.}
+
+  \label{fig:discwind_hybrid_ha_image}
+
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+xxxx alter text for consistency with above image xxxx
+
+By inspecting the model H$\alpha$ images computed (no shown here), we have
+found that the extent of the H$\alpha$ emission region is relatively
+small i.e.~$h\lesssim 0.2\,\mathrm{au}$ or $20\, R_{*}$ where h is the
+vertical distance from the disc when compared to the
+spectro-astrometric observations of \citet{takami:2003} 
+for RU~Lup and CS Cha which show 1--5~au scale outflows%
+\footnote{Their observations also show some objects
+(e.g~Z CMa and AS~353A) displaying the outflows in larger scale
+($>50\,\mathrm{au}$); however, this could be formed in shocks rather
+than MHD-wave heating (e.g. \citealt{hartmann:1982}) or X-ray heating
+(e.g.~\citealt{shang:2002}). %
+}. The extent of the line emission region becomes slightly
+larger ($\sim0.4$~au) if a slower wind acceleration rate (e,g,~$\beta=4$)
+is used.
 

### 2006-01-26 TTau_Halpha/kurosawa.tex
end of thursday - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@637 25464f21-6099-402c-b30a-640f1d40d38b

@@
       clip,
-      scale=0.45]{figures/discwind_hybrid_ha_image.eps}
+      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
 
@@
 
-\subsection{Classification scheme proposed by Reipurth et. al (1996)}
+\subsection{The morphological classification
+ scheme proposed by Reipurth et. al (1996)}
 
@@
   \caption{Sample H$\alpha$ model profiles which characterise the
-    classification by \citet{reipurth:1996}. The combination of
-    magnetospheric accretion flow, the accretion disc, and the disc wind
-    model can reasonably reproduce wide ranges of H$\alpha$ profiles seen
-    in observations.  The model parameters used for each profile and
-    short comments are summarised in
+    classification scheme of \citet{reipurth:1996}. The combination of
+    magnetospheric accretion flow, the accretion disc, and the disc-wind
+    can reproduce the wide range of H$\alpha$ profiles seen
+    in observations.  The model parameters used for each profile along with
+    short comments are given in
     Table~\ref{tab:classification}. The horizontal axes 
@@
 
-\citet{reipurth:1996} proposed the two-dimensional classification
+\citet{reipurth:1996} proposed a two-dimensional classification
 of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
@@
 and IV) differentiated by the ratio of the secondary-to-primary emission
-components in the profiles. Each classes are divided into two sub-classes
-(B and R) which depends whether the absorption component is on the
-blue or red side. Readers are refereed to Fig.~4 of their paper.
-Figure~\ref{fig:atlas_reipurth} shows the sample model profiles
+components in the profiles. Each class is divided into two sub-classes
+(B and R) which depends whether the secondary peak is on the
+blue or red side of the primary peak. Readers are refereed to Fig.~4 of their paper.
+Figure~\ref{fig:atlas_reipurth} shows  sample model profiles
 which are classified according to the definition of \citet{reipurth:1996}.
-The combination of the disc wind, magnetospheric accretion, and
-accretion disc can reasonably reproduce all the classes of the profiles
+The combination of the disc wind, magnetospheric accretion flow, and
+the accretion disc can reproduce all the classes of the profiles
 seen in observations. The corresponding parameters of the
@@
 in the figure are summarised in Table~\ref{tab:classification} along
-with brief comments on possible physical conditions which leads to
-the profiles in each class. In the following, we will discuss each 
-classification type of \citet{reipurth:1996} based on our model
-results.
+with brief comments on possible physical conditions which lead to
+the profiles in each class. Below we discuss the Reipurth scheme in the
+context of our models parameters.
 
 \textbf{Type~I}:
-Using the samples of H$\alpha$ from 43 CTTS, \citet{reipurth:1996}
-found this type to be the second most common (26~per~cent) among
-them. Type~I (symmetric around line centres), is mainly
-produced in the magnetosphere.  Although not shown here, this type of
-profile can be also reproduced with the disc-wind-magnetosphere hybrid
-model with low inclination angles ($\lesssim 10^\circ$).  Since there is
-no material in the polar region in the disc wind model, the observer
-can look the magnetosphere almost directory for high inclination
-cases, provided that wind temperature is low enough so that the wind
-emission is negligible.
+
+\citet{reipurth:1996} found that Type I profiles (symmetric around line centres) constituted 26~per~cent
+of the 43 CTTS H$\alpha$ profiles in their sample, making it the second most common
+morphological type. We find that Type~I  profiles are dominated by magnetospheric
+emission at rates in excess of $\appox 10^{-8}\, \dot{M_\odot}\,{\rm yr}^{-1}$. Type~I profiles
+appear at a wide range of inclinations (Figure~\ref{magnetosphere only inc dependence figure}).
+An object that displays a Type~I profile may have relatively weak disc wind, but in this
+case it must be viewed from the pole (in order that no wind material is seen projected
+against the stellar photosphere).
 
 \textbf{Type~II-B}:
+
+These profiles have a secondary blue peak that is in excess of half the strength of the 
+primary peak, and comprised 16~per~cent of the Reipurth sample.
+
 This type can be produced by the disc-wind-magnetosphere hybrid models
@@
 \textbf{Type~II-R}:
+
+These
+
 The physical conditions which result in this type
@@
 \textbf{Type~III-B}:
+
+xxx describe this type xxxx
+
 This type is the most commonly seen profiles in the CTTS H$\alpha$
@@
 \textbf{Type~III-R}:
+
+xxx describe this type xxxx
+
 This is the least common type of the observed profile (2~per~cent)
@@
 \textbf{Type~IV-B}:
+
+xxx describe this type xxxx
+
 This type of the profiles is very similar to Type III-B, but the wind
@@
 \textbf{Type~IV-R}:
+
+xxx describe this type xxxx
+
 This is the second least common type of the observed profiles (5~per~cent)

### 2006-01-27 TTau_Halpha/kurosawa.tex
Minior update
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@640 25464f21-6099-402c-b30a-640f1d40d38b

@@
       clip,
-      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
+      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image2.eps}
 
@@
 
-\citet{reipurth:1996} found that Type I profiles (symmetric around line centres) constituted 26~per~cent
-of the 43 CTTS H$\alpha$ profiles in their sample, making it the second most common
-morphological type. We find that Type~I  profiles are dominated by magnetospheric
-emission at rates in excess of $\appox 10^{-8}\, \dot{M_\odot}\,{\rm yr}^{-1}$. Type~I profiles
-appear at a wide range of inclinations (Figure~\ref{magnetosphere only inc dependence figure}).
-An object that displays a Type~I profile may have relatively weak disc wind, but in this
-case it must be viewed from the pole (in order that no wind material is seen projected
-against the stellar photosphere).
+\citet{reipurth:1996} found that Type I profiles (symmetric around
+line centres) constituted 26~per~cent of the 43 CTTS H$\alpha$
+profiles in their sample, making it the second most common
+morphological type. We find that Type~I profiles are dominated by
+magnetospheric emission at rates in excess of $\approx 10^{-8}\,
+\dot{M_\odot}\,\mathrm{yr^{-1}}$. Type~I profiles appear at a wide range
+of inclinations (Figure~\ref{fig:acc_inclination_effect}).  An object
+that displays a Type~I profile may have 
+relatively weak disc wind, but in this case it must be viewed from the
+pole (in order that no wind material is seen projected against the
+stellar photosphere).
 
@@
 as the inclination angle increases since there is more material
-towards the equatorial plane.  Although not shown here, this tendency
+towards the equatorial plane.  This tendency
 of the inclination dependency holds for the models with the wide
@@
 As a result, the EW becomes smaller as the inclination
-angle increases. Clearly, this is not consist with the trend seen in
+angle increases: 41\AA, 27\AA, and 19\AA\, for $i=10^\circ$, $55^\circ$, and
+$80^\circ$ respectively. 
+Clearly, this is not consist with the trend seen in
 the observation of \citet{appenzeller:2005}. Recall that a similar
@@
 same reason, the EW of the line increases as the inclination increase
-as clearly seen in the figure.  Although not shown here, this tendency
+as clearly seen in the figure. Specifically their values are 
+49\AA, 60\AA, and 84\AA\, for $i=10^\circ$, $55^\circ$, and
+$80^\circ$ respectively.  This tendency
 of the inclination dependency holds for the models with this wind
@@
 emission contribution becomes significantly larger than that from the
-magnetosphere (Figure~\ref{atlas_hybrid} and
+magnetosphere (Figure~\ref{fig:atlas_hybrid} and
 Table~\ref{tab:ew_ratio}).  Henceforth, a large H$\alpha$ equivalent
@@
 The value of $\mu$, 0.1,  suggested by both MHD calculations and observations
-(c.f.~\citep{koenigl:2000}) is consistent with the 
+(c.f.~\citealt{koenigl:2000}) is consistent with the 
 disc-wind-magnetosphere models presented here. We found that the
@@
 
+%
+% Appendix starts here
+%
+%\newpage
+%\onecolumn
+\appendix
+
+\section{H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model}
+
+Here we present xxxxxxxxxxxxxxx.
+
+%\twocolumn
+%======================================================================
+\begin{figure}
+
+  \begin{center}
+      \includegraphics[%
+	clip,
+	scale=0.6]{figures/discwind_hybrid_mdot7_inc10.eps}\tabularnewline
+      \vspace{0.5 cm}
+
+      \includegraphics[%
+	clip,
+      scale=0.6]{figures/discwind_hybrid_mdot7_inc55.eps}\tabularnewline
+
+      \vspace{0.5 cm}
+
+      \includegraphics[%
+	clip, scale=0.6]{figures/discwind_hybrid_mdot7_inc80.eps}\tabularnewline
+  \end{center}
+
+  \caption{The H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
+  $\dot{M_{\mathrm{acc}}} =10^{-7}\,M_{\sun}\,\mathrm{yr{-1}}$ and
+  $\dot{M_{\mathrm{wind}}}=10^{-6}\,M_{\sun}\,\mathrm{yr{-1}}$. }
+
+  \label{fig:atlas01}
+
+\end{figure}
+%======================================================================
+
+%======================================================================
+\begin{figure}
+
+  \begin{center}
+      \includegraphics[%
+	clip,
+	scale=0.6]{figures/discwind_hybrid_mdot8_inc10.eps}\tabularnewline
+      \vspace{0.5 cm}
+
+      \includegraphics[%
+	clip,
+      scale=0.6]{figures/discwind_hybrid_mdot8_inc55.eps}\tabularnewline
+
+      \vspace{0.5 cm}
+
+      \includegraphics[%
+	clip, scale=0.6]{figures/discwind_hybrid_mdot8_inc80.eps}\tabularnewline
+  \end{center}
+
+  \caption{The H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
+  $\dot{M_{\mathrm{acc}}} =10^{-8}\,M_{\sun}\,\mathrm{yr{-1}}$ and
+  $\dot{M_{\mathrm{wind}}}=10^{-7}\,M_{\sun}\,\mathrm{yr{-1}}$. }
+
+  \label{fig:atlas02}
+
+\end{figure}
+%======================================================================
+
+%======================================================================
+\begin{figure}
+
+  \begin{center}
+      \includegraphics[%
+	clip,
+	scale=0.6]{figures/discwind_hybrid_mdot9_inc10.eps}\tabularnewline
+      \vspace{0.5 cm}
+
+      \includegraphics[%
+	clip,
+      scale=0.6]{figures/discwind_hybrid_mdot9_inc55.eps}\tabularnewline
+
+      \vspace{0.5 cm}
+
+      \includegraphics[%
+	clip, scale=0.6]{figures/discwind_hybrid_mdot9_inc80.eps}\tabularnewline
+  \end{center}
+
+  \caption{The H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
+  $\dot{M_{\mathrm{acc}}} =10^{-9}\,M_{\sun}\,\mathrm{yr{-1}}$ and
+  $\dot{M_{\mathrm{wind}}}=10^{-10}\,M_{\sun}\,\mathrm{yr{-1}}$. }
+
+  \label{fig:atlas03}
+
+\end{figure}
+%======================================================================
+
 \label{lastpage}

### 2006-01-27 TTau_Halpha/kurosawa.tex
Change in appendix.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@641 25464f21-6099-402c-b30a-640f1d40d38b

@@
       clip,
-      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image2.eps}
+      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
 
@@
 	clip,
-	scale=0.45]{figures/stellarwind_inc_effect.eps}\tabularnewline
+	scale=0.61]{figures/stellarwind_inc_effect.eps}\tabularnewline
     \end{tabular}
@@
 
-Here we present xxxxxxxxxxxxxxx.
+Additional H$\alpha$ model line profiles 
+computed using disc-wind-magnetosphere hybrid model
+(section~\ref{sub:result-discwind-hybrid}) are presented here.  All
+the models use the reference parameters for the 
+magnetospherical geometry and the photosphere as given in
+Table~\ref{tab:std_paramters} in the main text. The ratio ($\mu$) of the
+mass-loss rate to mass-accretion rate is fixed to 0.1 for the all 
+models. Three sets of model profiles, each with a different
+mass-accretion rate, are presented here: 
+(1) $\dot{M}_{\mathrm{acc}}=10^{-7}\,M_{\sun}\,\mathrm{yr^{-1}}$ (Figure~\ref{fig:atlas01}), 
+(2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,M_{\sun}\,\mathrm{yr^{-1}}$ (Figure~\ref{fig:atlas01}), and
+(3) $\dot{M}_{\mathrm{acc}}=10^{-7}\,M_{\sun}\,\mathrm{yr^{-1}}$
+(Figure~\ref{fig:atlas01}).   The temperature of the magnetosphere
+used for (1), (2) and (3) are $7500\Kelvin$, $8500\Kelvin$ and
+$9500\Kelvin$ respectively.  The corresponding wind mass-loss rates
+are used for $\mu=0.1$. In each set the profiles are presented for the
+inclination angle of $10^\circ$, $55^\circ$, and $80^\circ$. 
+The disc-wind geometry used to compute these profiles are same as in
+section~\ref{sub:result-discwind-hybrid}.
 

### 2006-01-27 TTau_Halpha/kurosawa.tex
nearly final draft
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@642 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-This type can be produced by the disc-wind-magnetosphere hybrid models
-at moderate to high inclination angles with wide ranges of the wind
-acceleration rate ($0.2 \lesssim \beta  \lesssim 2.0$) and the wind
-temperature ($7000\,\mathrm{K} \lesssim T \lesssim 9000 \mathrm{K}$). If
-the inclination is high ($i \sim 80^\circ$), the disc-wind
-acceleration parameter should be relatively small ($\beta \lesssim
-0.5$). If the inclination is moderate ($i \sim 60^\circ$), the wind
-acceleration parameter should be relatively high ($\beta \gtrsim 2.0$).
+We find that Type~II-B profiles only occur at medium to high inclinations, and for systems
+with mass accretion rates of $\approx 10^{-7}\,
+\dot{M_\odot}\,\mathrm{yr^{-1}}$. If the system is viewed at high inclination, a Type~II-B profile implies
+a fast wind acceleration, and conversely a moderate inclination angle suggests
+a more modest wind acceleration.
 
@@
 
-These
-
-The physical conditions which result in this type
-is very similar to those of Type~II-B according to the
-disc-wind-magnetosphere hybrid models. The main difference is between  
-the two is in their inclination angles. This type is more likely
-seen at higher inclination angles ($i \sim 80^\circ$) compared to Type
-II-B.  Commonly seen in the models with the disc wind only model.
+These profiles are characterised by a secondary red peak that is in excess of half the strength
+of the primary peak. They are approximately as common as the Type~II-B lines.
+
+For the  $\dot{M_{\rm acc}} = 10^{-7}\,
+\dot{M_\odot}\,\mathrm{yr^{-1}}$ a switch from Type~II-B profiles to Type~II-R occurs
+when the inclination angle changes from $55^\circ$ to $80^\circ$. This profile type is 
+also seen at lower mass-accretion rates, but typically only in the models with the
+slowest accelerating winds. It is perhaps unsurprising that the Type~II-B and Type~II-R profiles
+are equally common, since (in general) the split between the profile types
+results from a geometrical (viewing angle) effect rather than a marked difference in physical
+parameters (mass accretion rate, wind acceleration etc).
 
@@
 
-xxx describe this type xxxx
-
-This type is the most commonly seen profiles in the CTTS H$\alpha$
-samples in \citet{reipurth:1996}. Interestingly, the most common
-profile type seen in the disc-wind-magnetosphere hybrid model are
-Type~III-B profiles (c.f.~Figures~\ref{fig:atlas_hybrid} and
-\ref{fig:atlas_hybrid}). In this type of profiles, the
-main emission comes from the magnetosphere, and the profile shape is
-altered from a slightly blue-asymmetric one to a slightly
-red-asymmetric one via the wind absorption in the blue wing.  In the
-models with the disc-wind, the acceleration parameter should be
-relatively small ($\beta<0.5$). The profile type changes from Type
-III-R to Type~II-R if the value of $\beta$ increases. The
-inclination angles must be moderate to high ($ 60^\circ \lesssim i \lesssim
- 80^\circ$).
+Profiles with a blue secondary peak that is less than half the strength of the 
+primary peak are classified as Type~III-B. This type of profile is the most common
+in the Reipurth sample, comprising 14 out of 43 (33 per cent) CTTS.
+
+We find Type~III-B profiles only in our  $\dot{M_{\rm acc}} = 10^{-7}\,
+\dot{M_\odot}\,\mathrm{yr^{-1}}$ models. A fast wind acceleration and a moderate 
+inclination are necessary, or a slower accelerating wind viewed pole-on. 
+We do not see this profile type in our high inclination models.
 
@@
 
-xxx describe this type xxxx
-
-This is the least common type of the observed profile (2~per~cent)
-according to \citet{reipurth:1996}. Incidentally, we also found it
-difficult to reproduce this type of profile since this can be achieve
-only at narrow range of parameter space (very high inclination angle
-with a disc wind model, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
-$\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
-Since the inclination angles must be high, this
-indicates that the accretion disc plays an important role in producing
-this type of the profile, but not the wind.  The rareness of this type in
-the observation can be understood by the required high inclination
-angle (almost edge-on) in our models.
+This profile type has a red secondary peak that is less than half the strength
+of the primary peak, and only one object with this type of profile was observed in the 
+Reipurth sample (SZ Cha).
+
+We are able to reproduce this profile type, but only using a very narrow range of
+parameter space. In fact there are no Type~III-R profiles in our model grid, but
+by 'tweaking' the magnetospheric temperature, and using an inclination ($85^\circ$) sufficient
+that the disc starts to obscure the central H$\alpha$ emission. For completeness, the final
+model parameters we used to achieve the profiles are:  (very high inclination, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and $\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+
+It is interesting that the most infrequently observed profile type was in fact the most difficult
+for us to reproduce. It appears that this profile morphology requires some obscuration effects
+by the dust disc, and therefore a high inclination; this naturally explains the rarity of the profile
+in the observations.
 
@@
 
-xxx describe this type xxxx
-
-This type of the profiles is very similar to Type III-B, but the wind
-in this type of profile may be accelerating faster (a smaller $\beta$
-value) than that in Type~III-B.  In the models with the disc-wind,
-this type is seen at moderate to high inclinations ($60^\circ \lesssim
- i \lesssim  80^\circ$) with relatively small value of the acceleration
-parameters ($\beta \lesssim 0.5$).
+This  profile classification is the classical P-Cygni, in which the blue-shifted absorption component
+has a sufficient velocity to be present beyond the emission line wing. It occurs infrequently
+in observations (7 per cent of the Reipurth sample).
+
+No Type~IV-B profiles were produced in our model grid, since the blue wing of the magnetosphere
+has generally such a large extent that it always exceeds the projected wind terminal velocity, and
+thus the bluemost extent of the absorption component. Only by running a model with 
+a larger terminal velocity, were we able to achieve a classical P-Cygni shape. We suspect
+that the disc-wind geometry is not the best kinematic model for producing this morphology. A more
+straightfoward explanation lies with a bipolar flow, viewed along its axis, or even a simple spherical wind.
 
@@
 
-xxx describe this type xxxx
-
-This is the second least common type of the observed profiles (5~per~cent)
-which shows the inverse P-Cyg profile shape.  This can be understood
-since the magnetospheric accretion model of \citet{hartmann:1994}
-predicts that the redshifted absorption can occur at a limited range
-of inclination angle ($i\simeq 50^\circ$, but depends on the geometry of
-the magnetosphere) with which the hot continuum flux from the
-footprint of the magnetosphere is seen through relatively fast moving
-gas in the accretion stream.  The wind component must be very
-weak. The mass-accretion rate should be much lower
-($\dot{M}_{\mathrm{acc}} \sim 10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$)
-than that of the models which produce Type~I profiles since the flux
-in the broadening wings can not be too high to produce the inverse
-P-Cyg profile.
+This is the inverse P-Cygni profile type, and only occurs in about 5~per~cent of 
+H$\alpha$ profiles.
+
+Type~IV-R profiles occur very infrequently in our hybrid model grid, with only
+the lowest mass-accretion rate models viewed at high inclination showing the 
+characteristic shape (although using the EW criterion these models would not
+be classified as CTTS). The inverse P-Cygni profile requires that the observer
+view the hot accretion footprints through the fast moving magnetospheric 
+accretion flow, and this means that the inclination angle is restricted to 
+small range.
+
+We can reproduce Type-IV-R profiles more readily if we adopt a cooler magnetospheric
+temperature than indicated by the accretion-rate/temperature relationship presented
+by Muzerolle (xxxx).
 
@@
 
-\subsection{Inclination dependency of H$\alpha$ profiles}
+\subsection{The inclination dependence of H$\alpha$ profiles}
 
@@
 
-  \caption{Dependency of the H$\alpha$ model profiles on the inclination
-    angle. The profiles computed at $i=10^{\circ}$(solid), $55^{\circ}$
-    (dot) and $80^{\circ}$ (dash) using (1)~the
+  \caption{The dependence of the H$\alpha$ model profiles on the inclination
+    angle. The profiles computed at $i=10^{\circ}$(solid line), $55^{\circ}$
+    (dotted line) and $80^{\circ}$ (dashed line ) using (1)~the
     disc-wind-magnetosphere hybrid model (left;
@@
     magnetosphere hybrid model (right panel;
-    c.f. Figure~\ref{fig:config_stellarwind}) are shown for a
-    comparison.  The parameters used for the magnetosphere are same for
+    c.f. Figure~\ref{fig:config_stellarwind}).  The parameters used for the magnetosphere are same for
     the both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
@@
     sections~\ref{sub:result-discwind-hybrid} and
-    \ref{sub:result-discwind-knigge}. While the line equivalent width
-    decreases as the inclination angle increases for the disc-wind
-    model, it increases as the inclination angle increases for the
-    stellar wind model. Only the latter agrees with the tendency seen in the
-    observational study of \citet{appenzeller:2005} who showed that the
-    H$\alpha$ line equivalent width of CTTS increases as the inclination
-    angle increases. }
+    \ref{sub:result-discwind-knigge}.  }
 
@@
 
-In the previous sections, we have considered the H$\alpha$ line
-formations in the disc wind which mimic the density distribution of the
-magneto-centrifugal launched jet numerical models
-(e.g.~\citealt{krasnopolsky:2003}). The density in this model is more
-concentrated toward the equatorial plane in near field. 
-In this section, we investigate the consistency of the line formation
-in the disc-wind model with the recent the recent observation of
-\citet{appenzeller:2005} by concentrating on the inclination
-dependency of the EW of H$\alpha$.  Their study showed that 
-that the line equivalent width of CTTS increases
-as the inclination angle increases.
-
-The right panel in Figure~\ref{fig:effect_inclination_compare} shows
+Recently, \citet{appenzeller:2005} have shown that the EW of H$\alpha$ is inclination
+dependent, with the EW increasing as the inclination angle increases. Is our hybrid 
+model consistent with this observation?
+
+The left-hand panel in Figure~\ref{fig:effect_inclination_compare} shows
 the profiles computed with the disc-wind, magnetosphere hybrid model
@@
 feature becomes stronger as the inclination increases, mainly because
-of the geometrical configuration.  The optical depth to becomes larger
-as the inclination angle increases since there is more material
-towards the equatorial plane.  This tendency
-of the inclination dependency holds for the models with the wide
-ranges of $\beta$ and $T_{\mathrm{wind}}$ values.  
-As a result, the EW becomes smaller as the inclination
+of the geometrical configuration.  The optical depth to the observer becomes larger
+as the inclination angle increases, since the density of the disc wind increases towards
+the equatorial plane--as a result, the EW becomes smaller as the inclination
 angle increases: 41\AA, 27\AA, and 19\AA\, for $i=10^\circ$, $55^\circ$, and
-$80^\circ$ respectively. 
-Clearly, this is not consist with the trend seen in
-the observation of \citet{appenzeller:2005}. Recall that a similar
-inclination dependency was found for the models with only
-magnetosphere (Figure~\ref{fig:acc_inclination_effect}).
-
-We have also considered an alternative wind model which would produce
-the inclination dependency of the H$\alpha$ EW  seen in the
-observation. In this model, the disc-wind is replaced by the stellar
-wind moving only in radial direction with the classical beta-velocity
-law \citep[c.f.][]{castor:1979}
+$80^\circ$ respectively.  This is a robust result, and is insensitive to the adopted wind 
+parameters. Recall that this is the same EW/inclination dependency as the magnetosphere
+only models (Figure~\ref{fig:acc_inclination_effect}).
+
+Clearly the inclination dependency of the line strength is in contradiction with
+the  \citet{appenzeller:2005} result, and thus merits further investigation. 
+In the previous sections, we have considered H$\alpha$ line
+formation in a disc wind, which mimics the density distribution of the
+magneto-centrifugal launched jet  models
+(e.g.~\citealt{krasnopolsky:2003}). The density in this model is more
+concentrated toward the equatorial plane in the region where the line emissivity is highest, although further out the material becomes collimated into a bipolar jet this would not 
+contribute significantly to the line emission in our models.
+
+As an alternative, we consider a wind model in which the outflow density
+increases towards the pole, rather than the  equator. In this model, 
+the disc-wind is replaced by a stellar wind, propagating only in the radial
+direction, accelerating under the  classical beta-velocity law \citep[c.f.][]{castor:1979}
 i.e.
@@
 This model configuration is motivated by the recent study by
-\citet{matt:2005} who demonstrated the possibility that the stellar
-wind along the open magnetic field originated from the star can cause
-significant spin-down torque on the star, provided that mass-loss rate
-is high enough.
-
-The right panel in Figure~\ref{fig:effect_inclination_compare} shows
-the H$\alpha$ profiles computed using the alternative hybrid model at
+\citet{matt:2005} who demonstrated that the stellar
+wind along  open magnetic field lines originating from the star may cause
+significant spin-down torque.
+
+The right-hand panel in Figure~\ref{fig:effect_inclination_compare} shows
+H$\alpha$ profiles computed using the alternative model at
 the same inclination angles used for the disc-wind-magnetosphere
@@
 photons created in the wind with the magnetosphere.
-While the blue-shifted absorption features are formed in the wind, the
+
+xxx check this out and rephrase xxx
+
+The blue-shifted absorption features are formed in the wind, the
 absorption features near the line centre and in the red wing (only for
-$i=10^\circ$) are caused by the wind emission by the magnetosphere
-which has a rather complex flow geometry. 
-Because of the geometry of the wind, the P-Cyg absorption feature
-weakens as the inclination increases. The optical depth of the wind is
+$i=10^\circ$) are caused by the wind absorbing emission from the  magnetosphere.
+
+Because of the geometry of the wind, the P-Cygni absorption feature
+weakens as the inclination increases: the optical depth of the wind is
 much higher in 
-the polar direction compared to that at higher inclination. For the
-same reason, the EW of the line increases as the inclination increase
-as clearly seen in the figure. Specifically their values are 
+the polar direction. For the
+same reason, the EW of the line increases as the inclination increases
+as clearly seen in the figure. Specifically the values are 
 49\AA, 60\AA, and 84\AA\, for $i=10^\circ$, $55^\circ$, and
@@
 of the inclination dependency holds for the models with this wind
-models for wide ranges of $\beta$ and $T_{\mathrm{wind}}$ as long as
+models for wide ranges of $\beta$ and $T_{\mathrm{wind}}$ providing that
 the emission from the wind is comparable to that of the magnetosphere.
 
-The distinct difference in the density dependency on the polar angles
-in two different wind models should be apparent in the inclination
-angle dependency on the observed line profiles. For example, one
+The \citet{appenzeller:2005} study used just xxx objects, and a significantly
+greater sample should be investigated before firm  conclusions are
+drawn. However our models indicate a significant difference in the 
+inclination dependence of the line morphology which may be simply
+tested against observation.  For example, one
 possible way to distinguish the two different wind models is to 
-examine the profile shape of a CTTS which is known to be viewed at
-pole-on. If the profile contains a prominent blue-shifted absorption
+examine the profile shape of a CTTS which is known to be viewed close
+to pole-on (e.g. a CTTS with a very low $v \sin i$). 
+If the profile contains a prominent blue-shifted absorption
 component (e.g. Type IV-B), the system is more likely to be associated
-with the `bipolar' stellar wind type of outflow (but not with the disc-wind type
-of outflow).  In reality, two types of the winds (bipolar stellar wind and
-disc wind) may co-exits similar to that seen in
-e.g. \citet*{drew:1998} and \citet{matt:2005}. In these models, the
-fast stellar wind is present in the polar directions, and at the same
-time the slower disc wind is present near the equatorial plane.
-
-The extensive parameter studies of the simple stellar wind model
-presented in this section have not been performed. The models
-presented here are for a demonstrative purpose, and the further
-investigation is necessary before the models are applied to a real
-system, perhaps, by combining our radiative transfer model with the
-results from MHD 'stellar' wind calculations.
-
-In this analysis, we found only the models with the bipolar stellar
-wind agree with the trend seen in their observation. Although the
-uncertainty in the inclination angles of the observed object might be
-large, a larger sample in addition to that of \citet{appenzeller:2005}
-for further investigation of the inclination dependency on the line
-profile will be extremely useful for determining the wind
-configuration of CTTS.
+with the bipolar stellar wind type of outflow, and not with the disc-wind.
+In reality, however, the two types of winds may be present in the same 
+object, in a similar fashion to that seen in the models of 
+\citet*{drew:1998} and \citet{matt:2005}. In these models, the
+fast stellar wind is present in the polar directions, while at the same
+time a slower, denser disc-wind is present near the equatorial plane.
 
@@
 
-  \caption{The alternative hybrid model. The model replaces the
-    disc-wind in the previous hybrid model with the stellar wind. The
-    wind launching from the stellar surface is limited within the
-    cones with the opening angle $\sim30^\circ$ to avoid the wind from
-    overlapping with the magnetosphere.  The system consists of four
+  \caption{The alternative outflow model. This model replaces the
+    disc-wind with a stellar wind. The
+    wind is launched from the stellar surface, and is limited to 
+    cones with opening angles of $\sim30^\circ$.  The system consists of four
     components: (1)~the continuum source located at the origin $\left( o
@@
 
-We have presented the disc-wind-magnetosphere hybrid radiative
+We have presented disc-wind-magnetosphere hybrid radiative
 transfer models for classical T~Tauri stars, and detailed studies of
 the H$\alpha$ formation from their complex to circumstellar
-environment.  We found that hybrid model can reproduce the wide
+environment.  We found that the hybrid model can reproduce the wide
 variety of profile seen in observations
@@
 \ref{fig:atlas_hybrid} and \ref{fig:atlas_reipurth}).
-Especially, the blue-shifted
-wind absorption feature very commonly seen in the H$\alpha$ profile of
-CTTS were well understood by this model.  This was not possible in the
-magnetospherical accretion only model presented in earlier works
-(e.g.~\citealt{muzerolle:2001}).
-
-The profiles computed with the hybrid model showed that the wind
-emission contribution becomes significantly larger than that from the
-magnetosphere (Figure~\ref{fig:atlas_hybrid} and
-Table~\ref{tab:ew_ratio}).  Henceforth, a large H$\alpha$ equivalent
-width does not necessary indicate a large mass-accretion rate, but it
-could be caused by the mass-loss by the wind outflow.
 
@@
 
-The value of $\mu$, 0.1,  suggested by both MHD calculations and observations
-(c.f.~\citealt{koenigl:2000}) is consistent with the 
-disc-wind-magnetosphere models presented here. We found that the
-hybrid models with $0.05<\mu<0.2$ are also consistent with the type
-of the profiles seen in the observations (e.g~\citealt{reipurth:1996}).
+One potential free parameter of our models is the ratio of mass-loss rate to mass-accretion rate
+($\mu$). Most MHD simulations predict a value of  $\mu = 0.1$ (c.f.~\citealt{koenigl:2000}), 
+and we have adopted this figure for most of our models. The success of our
+profile in matching observations is therefore encouraging,  and provides support
+for this canonical value of $\mu$. We have computed sample models with other
+values of $\mu$, (cite figure xxxx) and find that models with $0.05 <\mu<0.2$ are still
+be consistent with observations. Wind-only or magnetosphere-only models may be
+representative of individual line profiles, but neither can explain the complete
+Reipurth classification scheme--even magnetosphere dominated profiles (Type~I)
+can be readily explained by the hybrid model with $\mu=0.1$.
 
@@
 the disc-wind-magnetosphere hybrid model does not agree with the trend
-seen the observation of \citet{appenzeller:2005}; however, their
-results are based on a small number of objects (12). We have also
-considered an alternative hybrid model in which the disc-wind is
-replace by the narrow cone-shaped stellar wind, and found that the
-alternative wind hybrid model can reasonably reproduces the 
-line equivalent width dependency on the inclination seen in the
-observation (Figure~\ref{fig:effect_inclination_compare}).
-
-Similar model configurations used here may be also applicable to Herbig
-Ae/Be and brown dwarfs since their H$\alpha$ observations also exhibit
-evidence of the outflow and inflow (e.g.~\citet{finkenzeller:1984};
-\citealt{muzerolle:2005}), but no model has been developed to explain
-the phenomenon. Further investigation on the possibility of applying
-our model to these objects are needed.
-
-Future work should include the followings: (1)~Improving the wind
-models. The parametrisation of the wind density structure should be
-changed to follow more closely that of MHD simulations. The wind
-temperature structure should be calculated self-consistently
-(c.f.~\citealt{hartmann:1994}; \citealt{martin:1996}). (2)~Computing
-the line profiles using the density structure from MHD directly. Check
-the consistency, and give feedback to the MHD models which are needed
-to be tested against observational data. (3)~Spectropolarimetric study
-to explore the geometry and the rotation of the disc
-(e.g.~\citealt{vink:2005}). (4)~Modelling of the extended H$\alpha$
-and spectro-astrometric observations (c.f.~\citealt{takami:2003};
-\citealt{appenzeller:2005}). (5)~Line variability study using a 3D
-radiative transfer model (e.g.~\citealt{symington:2005};
-\citealt{kurosawa:2005a}) to probe the geometrical structure.
+seen the observations of \citet{appenzeller:2005}. We may appeal
+to the small sample size of their study (12 objects) to question
+the validity of the EW effect, but we have have also
+considered an alternative  model in which the disc-wind is
+replaced by a biconical stellar wind, and have found that this
+alternative wind model can reproduce the 
+line equivalent width dependency on the inclination 
+(Figure~\ref{fig:effect_inclination_compare}).  However, MHD simulations
+predict that bipolar or jet-like flows in CTTS are always accompanied by
+a disc-wind originating near the star: the real situation therefore is likely
+to be a combination of the two flows.
+
+Although we have concentrated on CTTS here, the hybrid model is equally
+applicable to pre-main-sequence stars across the mass spectrum. Herbig
+Ae/Be star profiles are equally diverse, and whilst many of the profiles
+are indicative of a wind (\citet{finkenzeller:1984}) some lines may be explained
+by magnetospheric accretion alone (e.g. \citealt{muzerolle:2005}). One possible
+advantage in applying the hybrid model to the Herbig Ae/Be systems is the growing
+observational data probing the line formation region and inner disc using techniques
+such as spectro-astrometry (Baines xxxx), spectropolarimetry (Vink xxxx) and
+interferometry (Monnier etc). These high-resolution techniques may aid model
+fitting of individual objects by constraining some of the model parameters, in
+particular the inclination.
+
+Velocity broadened, asymmetric H$\alpha$ profiles in BDs are used as an
+indicator of ongoing magnetospheric accretion, and the same models that
+are used for CTTS are applied to these systems in order to determine mass-accretion
+rates (muzerolle, lawson, jayawardhana xxxx). The line profiles however display
+the same wide variety of morphologies as the CTTS and Herbig Ae/Be stars (although
+we note as yet no BD profile has been observed with red-shifted absorption).
+It is natural to assume that the same physics applies in these low mass objects, 
+and that a hybrid model may be more successful in fitting these profiles, and will
+give greater insight into the circumstellar kinematics.
+
+There are several avenues of future work to consider. Here we have adopted
+a simple analytical form for the accretion and outflow velocity and density structure.
+A more self-consistent approach would be to use the results of MHD simulations
+as an input to the radiative-transfer modelling. The thermodynamics of the 
+circumstellar gas needs to be examined (c.f.~\citealt{hartmann:1994}; \citealt{martin:1996})
+and also computed self-consistently with the radiation field used in the radiative-transfer,
+a process that would decrease the free parameters of the model.
+We intend to calculate other observables from the model that may be compared with observation 
+and should provide further constraints. The line polarization signature, which
+arises from scattering of line and continuum photons in the circumstellar dust, encodes both dynamical and geometric information, such as the size of the inner disk radius  (Vink obs paper, Vink theory paper xxxx).
+Spectro-astrometry may provide information on the system's inclination, and the geometry
+of the outflow on large scales (Takami paper; Baines paper xxxx). Interferometry also provides information on inner disc radii and inclinations, although currently only for the Herbig Ae/Be stars.
+
+We have concentrated on the formation of the H$\alpha$ line, since it is the best studied CTTS
+emission line. However it is clear that simultaneous fitting of several emission line profile should
+provide much stronger constrains. In particular it appears that the near-IR hydrogen lines (Pa$\beta$ and Br$\gamma$) are less-effected by outflows than H$\alpha$. One could therefore use these
+lines to constrain the mass-accretion rate, and H$\alpha$ the mass-loss rate. A potential pitfall 
+is the significant temporal variability that all CTTS show in their emission lines; the observational
+data on a particular object must be co-temporaneous.
 
@@
 
-Authors thank Jorick Vink for providing us the H$\alpha$ data of
-T~Tau. This work is supported by PPARC standard grand PPA/G/S/2001/00081.
+This work is supported by PPARC standard grand PPA/G/S/2001/00081
+and PPARC rolling grant xxxxx.
 
@@
 
-Additional H$\alpha$ model line profiles 
+Here we present our H$\alpha$ model line profile grid 
 computed using disc-wind-magnetosphere hybrid model
-(section~\ref{sub:result-discwind-hybrid}) are presented here.  All
+(section~\ref{sub:result-discwind-hybrid}).  All
 the models use the reference parameters for the 
-magnetospherical geometry and the photosphere as given in
+magnetospheric geometry and the photosphere as given in
 Table~\ref{tab:std_paramters} in the main text. The ratio ($\mu$) of the
@@
 used for (1), (2) and (3) are $7500\Kelvin$, $8500\Kelvin$ and
-$9500\Kelvin$ respectively.  The corresponding wind mass-loss rates
-are used for $\mu=0.1$. In each set the profiles are presented for the
-inclination angle of $10^\circ$, $55^\circ$, and $80^\circ$. 
+$9500\Kelvin$ respectively. The profiles are presented for the
+inclination angles of $10^\circ$, $55^\circ$, and $80^\circ$. 
 The disc-wind geometry used to compute these profiles are same as in
@@
 
-  \caption{The H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
+  \caption{An H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
   $\dot{M_{\mathrm{acc}}} =10^{-7}\,M_{\sun}\,\mathrm{yr{-1}}$ and
-  $\dot{M_{\mathrm{wind}}}=10^{-6}\,M_{\sun}\,\mathrm{yr{-1}}$. }
+  $\dot{M_{\mathrm{wind}}}=10^{-6}\,M_{\sun}\,\mathrm{yr{-1}}$. 
+  Profiles are presented
+  for inclinations of $10^\circ$ (top figure), $55^\circ$ (middle figure), and $80^\circ$ (bottom figure).
+  For each inclination, 12 profiles are given, for three different values of the wind temperature, and four
+  different values of the wind acceleration parameter $\beta$.}
 
@@
 
-  \caption{The H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
+  \caption{As for Figure~\ref{fig:atlas01} except
   $\dot{M_{\mathrm{acc}}} =10^{-8}\,M_{\sun}\,\mathrm{yr{-1}}$ and
@@
 
-  \caption{The H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
+  \caption{As for Figure~\ref{fig:atlas01} except
     $\dot{M_{\mathrm{acc}}} =10^{-9}\,M_{\sun}\,\mathrm{yr{-1}}$ and

### 2006-01-29 TTau_Halpha/kurosawa.tex
Fixed the plots (Type IV-B). Now close to final version.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@643 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \title[On the formation of H$\alpha$ around classical T Tauri
-  stars]{On the formation of H$\alpha$ line emission around classical T Tauri stars}
+  stars]{On the formation of H$\alpha$ line emission around classical
+  T Tauri star: the disc-wind-magnetosphere hybrid models}
 
@@
 ($R_{*}$), mass ($M_{*}$), and effective temperature the photosphere
-($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$, and $4000\,\mathrm{K}$
+($T_{\mathrm{ph}}$) are $2\, \mathrm{R_{\sun}}$, $0.5\,
+\mathrm{M_{\sun}}$, and $4000\,\mathrm{K}$ 
 respectively. The model atmosphere of \citet{kurucz:1979} with
@@
 &
-$\left[R_{\sun}\right]$&
-$\left[M_{\sun}\right]$&
+$\left[\mathrm{R_{\sun}}\right]$&
+$\left[\mathrm{M_{\sun}}\right]$&
 $\left[\mathrm{K}\right]$&
@@
 $\left[R_{*}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
+$\left[\mathrm{M_{\sun}}\,\mathrm{yr^{-1}}\right]$&
+$\left[\mathrm{M_{\sun}}\,\mathrm{yr^{-1}}\right]$&
 $\left[R_{*}\right]$&
@@
 and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
-the equatorial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
+the equatorial plane) are set to be $2.2\, \mathrm{R_{\sun}}$ and $3.0\, \mathrm{R_{\sun}}$
 respectively. The geometry of the magnetic field/stream
@@
 restricted between $R_{\mathrm{mi}}$ and 
-$R_{\mathrm{mo}}$ (Figure~\ref{fig:config_discwind}). 
+$R_{\mathrm{mo}}$ (Fig.~\ref{fig:config_discwind}). 
 Using the field geometry above and conservation of
@@
 (4)~the wind temperature. The basic configuration of the disc-wind
-model is shown in Figure~\ref{fig:config_discwind}. The disc wind
+model is shown in Fig.~\ref{fig:config_discwind}. The disc wind
 originates from the disc surface, but the {}``source'' point ($S$),
@@
   \dot{m}\left(w\right) \propto
-       T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}
+       \left[ T\left(w\right) \right]  ^{\alpha}\,\,.\label{eq:discwind-massloss-temp}
 \end{equation}
@@
 a point along the stream line and the angle between the stream line
-and the disc normal, respectively. Figure~\ref{fig:discwind_vr_rho}
+and the disc normal, respectively. Fig.~\ref{fig:discwind_vr_rho}
 shows the density and the velocity components along the mid stream
@@
     from top to bottom, and the mass accretion rate (indicated by the
-    values in $\mathrm{M_{\odot}\,yr^{-1}}$ along the top) increases from
+    values in $\mathrm{M_{\sun}\,yr^{-1}}$ along the top) increases from
     left to right. }
@@
 H$\alpha$ line profiles for a range of $T_{\mathrm{max}}$ and
-$\dot{M}_{\mathrm{acc}}$ are presented in  Figure~\ref{fig:atlas_acc_models}. 
+$\dot{M}_{\mathrm{acc}}$ are presented in  Fig.~\ref{fig:atlas_acc_models}. 
 The  overall dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ is similar to that of
@@
 
-We demonstrate this effect in Figure~\ref{fig:broadening}, which shows an example 
+We demonstrate this effect in Fig.~\ref{fig:broadening}, which shows an example 
 for an H$\alpha$  model with $T_{\mathrm{max}}=7500\,\mathrm{K}$
@@
 Table~\ref{tab:ha_ew_acc_models} shows the equivalent width (EW) for
-the models in Figure~\ref{fig:atlas_acc_models}.  The EWs for half the
+the models in Fig.~\ref{fig:atlas_acc_models}.  The EWs for half the
 models fall within the range of EWs ($\sim 3$~\AA\, to $\sim 160$~\AA)
@@
 widths of the model H$\alpha$ profiles
-(Figure~\ref{fig:atlas_acc_models}) are summarised in
+(Fig.~\ref{fig:atlas_acc_models}) are summarised in
 Table~\ref{tab:ha_ten_percent_acc_models}.  Using the criteria of
@@
 The dependency of the line profile on inclination angle ($i$) is
-demonstrated in Figure~\ref{fig:acc_inclination_effect}. The model
+demonstrated in Fig.~\ref{fig:acc_inclination_effect}. The model
 has  $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
@@
 blocked by the photosphere increases as the inclination increases.
-The line EW in Figure~\ref{fig:acc_inclination_effect} changes from
+The line EW in Fig.~\ref{fig:acc_inclination_effect} changes from
 32\,\AA\, to 21\,\AA\, as the inclination changes from $10^\circ$ to
@@
 Because of the geometry of the
-magnetospheric accretion (c.f. Figure~\ref{fig:config_discwind}) and of
+magnetospheric accretion (c.f. Fig.~\ref{fig:config_discwind}) and of
 the presence of the gas with the highest velocity close to the stellar
@@
 flow by the stellar photosphere (see also \citealt{hartmann:1994};
-\citealt{muzerolle:2001}). However, \citealt{alencar:2000} (see their Fig.~9)
+\citealt{muzerolle:2001}). However, \citealt{alencar:2000} (see their fig.~9)
 found a substantial fraction
@@
 magnetospheric accretion flow models shown in
-Figure~\ref{fig:atlas_acc_models}. Note that the equivalent widths are
+Fig.~\ref{fig:atlas_acc_models}. Note that the equivalent widths are
 positive when the lines are in emission.}
@@
 magnetospheric accretion flow models shown in
-Figure~\ref{fig:atlas_acc_models}.}
+Fig.~\ref{fig:atlas_acc_models}.}
 
@@
 $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$.
-Figure~\ref{fig:atlas_discwind_only} shows the model profiles computed
+Fig.~\ref{fig:atlas_discwind_only} shows the model profiles computed
 for the wind temperatures between $7000\,\mathrm{K}$ and
@@
 ($\beta=0.2$) model is almost at the terminal velocity ($v_{\infty}\sim
-160\,\kmps$) of the disc wind (c.f.~Figure~\ref{fig:discwind_vr_rho}), that
+160\,\kmps$) of the disc wind (c.f.~Fig.~\ref{fig:discwind_vr_rho}), that
 for the slowest wind acceleration model 
@@
 because the density near the photosphere increases as the value of
-$\beta$ increases (Figure~\ref{fig:discwind_vr_rho}); hence, the
+$\beta$ increases (Fig.~\ref{fig:discwind_vr_rho}); hence, the
 emissivity of increases. Most of the profiles show a red-ward asymmetry, mainly
@@
     0.5$ for $i=55^{\circ}$.  The profiles in the figure use $d = 
-    11~R_{*}$ (dashed),   $18~R_{*}$ (dash-dot) and $22~R_{*}$
+   2~R_{*}$ (dashed),   $7~R_{*}$ (dash-dot) and $88~R_{*}$
     (dash-dot). All the other parameters are same as in
-    Figure~\ref{fig:atlas_discwind_only}.  As the wind becomes more
-    collimated (larger $d$), the wind launching angle becomes smaller
-    and the wind density is enhanced towards the symmetry axis
-    ($z$); hence, the wind emission increases.  The absorption
-    component is relatively insensitive to $d$ since the change in the
-    column density toward the observer is relatively small. }
+    Fig.~\ref{fig:atlas_discwind_only}.  As the wind becomes more
+    collimated (larger $d$), the wind emission becomes stronger.  
+    The P-Cygni absorption disappears for the model with a small
+    collimation (e.g.~$d = 2~R_{*}$ case) since the opening angel of
+    the disc wind is larger than the inclination angle. }
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We now examine the sensitivity of the model profiles on the wind
+collimation or the source displacement parameter $d$. As we can see
+from Fig.~\ref{fig:config_discwind}, the disc wind
+geometry/collimation is determined by $d$ and the wind launching radii
+($R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$). Here, we fix the values of
+$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ as in
+Table~\ref{tab:std_discwind_parameters}, and inspect the model
+dependency on $d$ alone.  The minimum wind opening angle (measured
+from the symmetry axis) is given by
+$\theta_{\mathrm{open}}=\arctan\left( d/R_{\mathrm{wi}} \right)$.
+Fig.~\ref{fig:discwind_d_effect} shows the profiles computed for $d
+= 2~R_{*}$, $7~R_{*}$ and $88~R_{*}$ for the inclination angle
+$i=55^{\circ}$.  As the wind becomes more collimated (larger $d$), the
+wind launching angle becomes smaller and the wind density is enhanced
+towards the symmetry axis ($z$); hence, the wind emission increases.
+When the collimation of the wind is small (as in the $d = 2~R_{*}$
+case), the P-Cygni absorption is absent from the profile because the
+opening angel of the disc wind is greater than the inclination angle.
+For the disc wind models presented in this paper, we use $d=44~R_{*}$
+to have a moderate amount of wind absorption at a moderate inclination
+angle ($i\sim60^\circ$).
 
@@
 The effect of varying the wind mass-loss rate is shown in
-Figure~\ref{fig:discwind_mdot_effect}. With all other parameters fixed,
+Fig.~\ref{fig:discwind_mdot_effect}. With all other parameters fixed,
 $\dot{M}_{\mathrm{wind}}$ acts as an scaling factor for the wind
@@
   (solid lines) have the  same parameters as
-    Figure~\ref{fig:atlas_discwind_only}, but  also
+    Fig.~\ref{fig:atlas_discwind_only}, but  also
     include the magnetospheric accretion flow
@@
 used for the magnetosphere are  same as in 
-Figure~\ref{fig:acc_inclination_effect}, and  the mass-loss rate of
+Fig.~\ref{fig:acc_inclination_effect}, and  the mass-loss rate of
 the disc wind is 
@@
 (i.e.~$\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}=0.1$).
-Figure~\ref{fig:atlas_hybrid} shows the models profiles
+Fig.~\ref{fig:atlas_hybrid} shows the models profiles
 computed using the same ranges of the disc-wind temperature and
@@
 As in the disc-wind only models
-(Figure~\ref{fig:atlas_discwind_only}), the location of the absorption
+(Fig.~\ref{fig:atlas_discwind_only}), the location of the absorption
 component moves toward the line centre as the value of $\beta$
@@
 strengths comparable to observations.  Although the models in
-Figure~\ref{fig:atlas_hybrid} are computed with limited
+Fig.~\ref{fig:atlas_hybrid} are computed with limited
 ranges of $T_{\mathrm{wind}}$, $\beta$ and a fixed $i$, the resulting
@@
  the magnetosphere, we have computed the ratio the EW of the
-hybrid model in Figure~\ref{fig:atlas_hybrid} to the EW of the
+hybrid model in Fig.~\ref{fig:atlas_hybrid} to the EW of the
 magnetosphere only model (Table~\ref{tab:ew_ratio}).
@@
 demonstrates that the difficulty of using the EW of H$\alpha$ alone as
-an accretion measure.   We have also seen in Figure~\ref{fig:atlas_discwind_only}
+an accretion measure.   We have also seen in Fig.~\ref{fig:atlas_discwind_only}
 that disc wind models {\em without}  a magnetosphere can produce an
@@
 Figures~\ref{fig:atlas_discwind_only} and
-Figure~\ref{fig:atlas_hybrid} reveals some of problems
+Fig.~\ref{fig:atlas_hybrid} reveals some of problems
 with uniqueness that must inevitably occur when trying to assign an
@@
 $\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,0.5\right)$
-in Figure~\ref{fig:atlas_hybrid} give very similar
+in Fig.~\ref{fig:atlas_hybrid} give very similar
 profiles.
@@
 ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
-in Figure~\ref{fig:discwind_mu_effect}. With a fixed value of
+in Fig.~\ref{fig:discwind_mu_effect}. With a fixed value of
 mass-accretion rate
@@
 
-xxx add a sample halpha image from poster xxxx
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{An H$\alpha$ image of the disc-wind hybrid model viewed at an inclination
-  of 80$^\circ$. The false-colour scale shows logarithmic surface brightness (arbitrary
-  units) and the axes are linear dimensions in au.}
+  of 80$^\circ$. The false-colour scale shows logarithmic (base 10)
+  surface brightness (arbitrary units) and the axes are linear
+  dimensions in au. The parameter used for the magnetosphere are as
+  the reference model in Table~\ref{tab:std_parameters}. The wind
+  temperature of $T_{\mathrm{max}}=7000~\Kelvin$ and the wind
+  acceleration parameter $\beta=1.0$ are adopted here.  }
 
@@
 
-xxxx alter text for consistency with above image xxxx
-
-By inspecting the model H$\alpha$ images computed (no shown here), we have
+By inspecting the model H$\alpha$ images computed
+(Fig.~\ref{fig:discwind_hybrid_ha_image}), we have 
 found that the extent of the H$\alpha$ emission region is relatively
-small i.e.~$h\lesssim 0.2\,\mathrm{au}$ or $20\, R_{*}$ where h is the
+small i.e.~$h\sim 0.1\,\mathrm{au}$ or $10\, R_{*}$ where h is the
 vertical distance from the disc when compared to the
@@
     disc-wind magnetosphere hybrid models in
-    Figure~\ref{fig:atlas_hybrid} to the EW of the magnetosphere only model. }
+    Fig.~\ref{fig:atlas_hybrid} to the EW of the magnetosphere only model. }
 
@@
 blue or red side of the primary peak. Readers are refereed to Fig.~4 of their paper.
-Figure~\ref{fig:atlas_reipurth} shows  sample model profiles
+Fig.~\ref{fig:atlas_reipurth} shows  sample model profiles
 which are classified according to the definition of \citet{reipurth:1996}.
@@
 the profiles in each class. Below we discuss the Reipurth scheme in the
-context of our models parameters.
+context of our models parameters. Readers are referred to
+appendix~\ref{sec:appendix} for the complete model profiles used in 
+this discussion.
 
 \textbf{Type~I}: 
-
 \citet{reipurth:1996} found that Type I profiles (symmetric around
@@
 magnetospheric emission at rates in excess of $\approx 10^{-8}\,
-\dot{M_\odot}\,\mathrm{yr^{-1}}$. Type~I profiles appear at a wide range
-of inclinations (Figure~\ref{fig:acc_inclination_effect}).  An object
+\mathrm{M_{\sun}\, yr^{-1}}$. Type~I profiles appear at a wide range
+of inclinations (Fig.~\ref{fig:acc_inclination_effect}).  An object
 that displays a Type~I profile may have 
@@
 \textbf{Type~II-B}:  
-
-These profiles have a secondary blue peak that is in excess of half the strength of the 
-primary peak, and comprised 16~per~cent of the Reipurth sample.
-
-We find that Type~II-B profiles only occur at medium to high inclinations, and for systems
-with mass accretion rates of $\approx 10^{-7}\,
-\dot{M_\odot}\,\mathrm{yr^{-1}}$. If the system is viewed at high inclination, a Type~II-B profile implies
-a fast wind acceleration, and conversely a moderate inclination angle suggests
-a more modest wind acceleration.
+These profiles have a secondary blue peak that is in excess of half
+the strength of the primary peak, and comprised 16~per~cent of the
+Reipurth sample.
+We find that Type~II-B profiles only occur at medium to high
+inclinations, and for systems with mass accretion rates of $\approx
+10^{-7}\, \mathrm{M_{\sun}\, yr^{-1}}$. If the system is viewed at
+high inclination, a Type~II-B profile implies a fast wind
+acceleration, and conversely a moderate inclination angle suggests a
+more modest wind acceleration.
 
 \textbf{Type~II-R}:  
-
-These profiles are characterised by a secondary red peak that is in excess of half the strength
-of the primary peak. They are approximately as common as the Type~II-B lines.
-
-For the  $\dot{M_{\rm acc}} = 10^{-7}\,
-\dot{M_\odot}\,\mathrm{yr^{-1}}$ a switch from Type~II-B profiles to Type~II-R occurs
-when the inclination angle changes from $55^\circ$ to $80^\circ$. This profile type is 
-also seen at lower mass-accretion rates, but typically only in the models with the
-slowest accelerating winds. It is perhaps unsurprising that the Type~II-B and Type~II-R profiles
-are equally common, since (in general) the split between the profile types
-results from a geometrical (viewing angle) effect rather than a marked difference in physical
-parameters (mass accretion rate, wind acceleration etc).
+These profiles are characterised by a secondary red peak that is in
+excess of half the strength of the primary peak. They are
+approximately as common as the Type~II-B lines.
+For the $\dot{M}_{{\rm acc}} = 10^{-7}\,
+\mathrm{M_{\sun}\,yr^{-1}}$ a switch from Type~II-B profiles to
+Type~II-R occurs when the inclination angle changes from $55^\circ$ to
+$80^\circ$. This profile type is also seen at lower mass-accretion
+rates, but typically only in the models with the slowest accelerating
+winds. It is perhaps unsurprising that the Type~II-B and Type~II-R
+profiles are equally common, since (in general) the split between the
+profile types results from a geometrical (viewing angle) effect rather
+than a marked difference in physical parameters (mass accretion rate,
+wind acceleration etc).
 
 \textbf{Type~III-B}:
-
-Profiles with a blue secondary peak that is less than half the strength of the 
-primary peak are classified as Type~III-B. This type of profile is the most common
-in the Reipurth sample, comprising 14 out of 43 (33 per cent) CTTS.
-
-We find Type~III-B profiles only in our  $\dot{M_{\rm acc}} = 10^{-7}\,
-\dot{M_\odot}\,\mathrm{yr^{-1}}$ models. A fast wind acceleration and a moderate 
-inclination are necessary, or a slower accelerating wind viewed pole-on. 
-We do not see this profile type in our high inclination models.
+Profiles with a blue secondary peak that is less than half the
+strength of the primary peak are classified as Type~III-B. This type
+of profile is the most common in the Reipurth sample, comprising 14
+out of 43 (33 per cent) CTTS.
+We find Type~III-B profiles only in our $\dot{M}_{{\rm acc}} = 10^{-7}\,
+\mathrm{M_{\sun}\,yr^{-1}}$ models. A fast wind acceleration and
+a moderate inclination are necessary, or a slower accelerating wind
+viewed pole-on.  We do not see this profile type in our high
+inclination models.
 
 \textbf{Type~III-R}: 
-
-This profile type has a red secondary peak that is less than half the strength
-of the primary peak, and only one object with this type of profile was observed in the 
-Reipurth sample (SZ Cha).
-
-We are able to reproduce this profile type, but only using a very narrow range of
-parameter space. In fact there are no Type~III-R profiles in our model grid, but
-by 'tweaking' the magnetospheric temperature, and using an inclination ($85^\circ$) sufficient
-that the disc starts to obscure the central H$\alpha$ emission. For completeness, the final
-model parameters we used to achieve the profiles are:  (very high inclination, $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and $\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
-
-It is interesting that the most infrequently observed profile type was in fact the most difficult
-for us to reproduce. It appears that this profile morphology requires some obscuration effects
-by the dust disc, and therefore a high inclination; this naturally explains the rarity of the profile
-in the observations.
+This profile type has a red secondary peak that is less than half the
+strength of the primary peak, and only one object with this type of
+profile was observed in the Reipurth sample (SZ Cha).
+We are able to reproduce this profile type, but only using a very
+narrow range of parameter space. In fact there are no Type~III-R
+profiles in our model grid, but by 'tweaking' the magnetospheric
+temperature, and using an inclination ($85^\circ$) sufficient that the
+disc starts to obscure the central H$\alpha$ emission. For
+completeness, the final model parameters we used to achieve the
+profiles are: (very high inclination,
+$T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
+$\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+It is interesting that the most infrequently observed profile type was
+in fact the most difficult for us to reproduce. It appears that this
+profile morphology requires some obscuration effects by the dust disc,
+and therefore a high inclination; this naturally explains the rarity
+of the profile in the observations.
 
 \textbf{Type~IV-B}: 
-
-This  profile classification is the classical P-Cygni, in which the blue-shifted absorption component
-has a sufficient velocity to be present beyond the emission line wing. It occurs infrequently
-in observations (7 per cent of the Reipurth sample).
-
-No Type~IV-B profiles were produced in our model grid, since the blue wing of the magnetosphere
-has generally such a large extent that it always exceeds the projected wind terminal velocity, and
-thus the bluemost extent of the absorption component. Only by running a model with 
-a larger terminal velocity, were we able to achieve a classical P-Cygni shape. We suspect
-that the disc-wind geometry is not the best kinematic model for producing this morphology. A more
-straightfoward explanation lies with a bipolar flow, viewed along its axis, or even a simple spherical wind.
+This profile classification is the classical P-Cygni, in which the
+blue-shifted absorption component has a sufficient velocity to be
+present beyond the emission line wing. It occurs infrequently in
+observations (7 per cent of the Reipurth sample).
+No Type~IV-B profiles were produced in our model grid, since the blue
+wing of the magnetosphere has generally such a large extent that it
+always exceeds the projected wind terminal velocity, and thus the
+bluemost extent of the absorption component. Only by running a model
+with a larger terminal velocity or with a smaller magnetospheric
+temperature, were we able to achieve a classical
+P-Cygni shape. We suspect that the disc-wind geometry is not the best
+kinematic model for producing this morphology. A more straightforward
+explanation lies with a bipolar flow, viewed along its axis, or even a
+simple spherical wind.
 
 \textbf{Type~IV-R}: 
-
-This is the inverse P-Cygni profile type, and only occurs in about 5~per~cent of 
-H$\alpha$ profiles.
-
-Type~IV-R profiles occur very infrequently in our hybrid model grid, with only
-the lowest mass-accretion rate models viewed at high inclination showing the 
-characteristic shape (although using the EW criterion these models would not
-be classified as CTTS). The inverse P-Cygni profile requires that the observer
-view the hot accretion footprints through the fast moving magnetospheric 
-accretion flow, and this means that the inclination angle is restricted to 
-small range.
-
-We can reproduce Type-IV-R profiles more readily if we adopt a cooler magnetospheric
-temperature than indicated by the accretion-rate/temperature relationship presented
-by Muzerolle (xxxx).
+This is the inverse P-Cygni profile type, and only occurs in about
+5~per~cent of H$\alpha$ profiles.
+Type~IV-R profiles occur very infrequently in our hybrid model grid,
+with only the lowest mass-accretion rate models viewed at high
+inclination showing the characteristic shape (although using the EW
+criterion these models would not be classified as CTTS). The inverse
+P-Cygni profile requires that the observer view the hot accretion
+footprints through the fast moving magnetospheric accretion flow, and
+this means that the inclination angle is restricted to small range.
+We can reproduce Type~IV-R profiles more readily if we adopt a cooler
+magnetospheric temperature than indicated by the
+accretion-rate/temperature relationship presented by
+\citet{muzerolle:2001}.
 
@@
 \caption{The summary model parameters for the profiles in
-Figure~\ref{fig:atlas_reipurth} and brief comments. The temperatures
+Fig.~\ref{fig:atlas_reipurth} and brief comments. The temperatures
 are in $10^{3}\,\Kelvin$. $\dot{M}_{\mathrm{acc}}$ and
@@
 $-$&
-Accretion dominated possibly without the wind. Mid inclination.\tabularnewline
+Accretion dominated. Wide range of inclination.\tabularnewline
 II-B&
@@
 $1.0$&
-Wind, disc and magnetosphere. Wide range of wind acceleration rate.
+Wide range of wind acceleration rate.
 Mid--high inclination\tabularnewline
+II-R&
+$80$&
+$10^{-7}$&
+$7.5$&
+$10^{-8}$&
+$7.0$&
+$2.0$&
+Slow wind acceleration rate. High inclination\tabularnewline
 III-B&
@@
 $0.5$&
-Wind, disc and magnetosphere. Fast--mid wind acceleration rate. Mid--high
-inclination\tabularnewline
-IV-B&
-$55$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$0.2$&
-Wind, disc and magnetosphere. Fast wind acceleration rate. Mid--high inclination\tabularnewline
-II-R&
-$80$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$7.0$&
-$2.0$&
-Wind, disc and magnetosphere. Slow wind acceleration rate. High inclination\tabularnewline
+Fast wind acceleration rate. Mid inclination\tabularnewline
 III-R&
@@
 $1.0$&
-Wind, disc and magnetosphere. Mid wind acceleration rate. Very high
+Mid wind acceleration rate. Very high
 inclination \tabularnewline
+IV-B&
+$30$&
+$10^{-7}$&
+$5.5$&
+$10^{-8}$&
+$6.0$&
+$0.2$&
+Fast wind acceleration rate. Mid--high inclination\tabularnewline
 IV-R&
@@
 
-  \caption{The dependence of the H$\alpha$ model profiles on the inclination
-    angle. The profiles computed at $i=10^{\circ}$(solid line), $55^{\circ}$
-    (dotted line) and $80^{\circ}$ (dashed line ) using (1)~the
-    disc-wind-magnetosphere hybrid model (left;
-    c.f. section~\ref{sub:result-discwind-knigge}) and (2)~the disc, stellar wind,
-    magnetosphere hybrid model (right panel;
-    c.f. Figure~\ref{fig:config_stellarwind}).  The parameters used for the magnetosphere are same for
-    the both models, i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
+  \caption{The dependence of the H$\alpha$ model profiles on the
+    inclination angle. The profiles computed at $i=10^{\circ}$(solid
+    line), $55^{\circ}$ (dotted line) and $80^{\circ}$ (dashed line )
+    using (1)~the disc-wind-magnetosphere hybrid model (left;
+    c.f. section~\ref{sub:result-discwind-knigge}) and (2)~the disc,
+    stellar wind, magnetosphere hybrid model (right panel;
+    c.f. Fig.~\ref{fig:config_stellarwind}).  The parameters used for
+    the magnetosphere are same for the both models,
+    i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
     $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The
-    isothermal wind temperature and the wind acceleration parameter used
-    in (1) are $T_{\mathrm{wind}}=7000~\mathrm{K}$ and $\beta=1.0$,
-    and those in (2)
-    are $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=0.5$ respectively.
+    isothermal wind temperature and the wind acceleration parameter
+    used in (1) are $T_{\mathrm{wind}}=7000~\mathrm{K}$ and
+    $\beta=1.0$, and those in (2) are
+    $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=1.0$ respectively.
     All the other parameters are same as in
@@
 
-Recently, \citet{appenzeller:2005} have shown that the EW of H$\alpha$ is inclination
-dependent, with the EW increasing as the inclination angle increases. Is our hybrid 
-model consistent with this observation?
-
-The left-hand panel in Figure~\ref{fig:effect_inclination_compare} shows
-the profiles computed with the disc-wind, magnetosphere hybrid model
-(section~\ref{sub:result-discwind-knigge}) 
-at inclination angles $i=10^{\circ}$, $55^{\circ}$ and
-$80^{\circ}$. The magnetospheric accretion component uses the  
-parameters used as the reference model (Table~\ref{tab:std_parameters}).  
-The figure shows that the absorption
-feature becomes stronger as the inclination increases, mainly because
-of the geometrical configuration.  The optical depth to the observer becomes larger
-as the inclination angle increases, since the density of the disc wind increases towards
-the equatorial plane--as a result, the EW becomes smaller as the inclination
-angle increases: 41\AA, 27\AA, and 19\AA\, for $i=10^\circ$, $55^\circ$, and
-$80^\circ$ respectively.  This is a robust result, and is insensitive to the adopted wind 
-parameters. Recall that this is the same EW/inclination dependency as the magnetosphere
-only models (Figure~\ref{fig:acc_inclination_effect}).
-
-Clearly the inclination dependency of the line strength is in contradiction with
-the  \citet{appenzeller:2005} result, and thus merits further investigation. 
-In the previous sections, we have considered H$\alpha$ line
-formation in a disc wind, which mimics the density distribution of the
-magneto-centrifugal launched jet  models
+Recently, \citet{appenzeller:2005} have shown that the EW of the
+observed H$\alpha$ from CTTS is inclination dependent, with the EW
+increasing as the inclination angle increases. Next, we will examine
+whether the hybrid model is consistent with the inclination dependency
+found in the observation.
+The left-hand panel in Fig.~\ref{fig:effect_inclination_compare}
+shows the profiles computed with the disc-wind, magnetosphere hybrid
+model (section~\ref{sub:result-discwind-knigge}) at inclination angles
+$i=10^{\circ}$, $55^{\circ}$ and $80^{\circ}$. The magnetospheric
+accretion component uses the parameters used as the reference model
+(Table~\ref{tab:std_parameters}).  The figure shows that the
+absorption feature becomes stronger as the inclination increases,
+mainly because of the geometrical configuration.  The optical depth to
+the observer becomes larger as the inclination angle increases, since
+the density of the disc wind increases towards the equatorial
+plane--as a result, the EW becomes smaller as the inclination angle
+increases: 41\,\AA, 27\,\AA, and 19\,\AA\, for $i=10^\circ$,
+$55^\circ$, and $80^\circ$ respectively.  This is a robust result, and
+is insensitive to the adopted wind parameters. Recall that this is the
+same EW/inclination dependency as the magnetosphere only models
+(Fig.~\ref{fig:acc_inclination_effect}).
+
+Clearly the inclination dependency of the line strength is in
+contradiction with the \citet{appenzeller:2005} result, and thus
+merits further investigation.  In the previous sections, we have
+considered H$\alpha$ line formation in a disc wind, which mimics the
+density distribution of the magneto-centrifugal launched jet models
 (e.g.~\citealt{krasnopolsky:2003}). The density in this model is more
-concentrated toward the equatorial plane in the region where the line emissivity is highest, although further out the material becomes collimated into a bipolar jet this would not 
-contribute significantly to the line emission in our models.
-
-As an alternative, we consider a wind model in which the outflow density
-increases towards the pole, rather than the  equator. In this model, 
-the disc-wind is replaced by a stellar wind, propagating only in the radial
-direction, accelerating under the  classical beta-velocity law \citep[c.f.][]{castor:1979}
-i.e.
+concentrated toward the equatorial plane in the region where the line
+emissivity is highest, although further out the material becomes
+collimated into a bipolar jet this would not contribute significantly
+to the line emission in our models.
+
+As an alternative, we consider a wind model in which the outflow
+density increases towards the pole, rather than the equator. In this
+model, the disc-wind is replaced by a stellar wind, propagating only
+in the radial direction, accelerating under the classical
+beta-velocity law \citep[c.f.][]{castor:1979} i.e.
 $v_{r}\left(\ r  \right) = v_{\infty} \left( 1 - R_{*}/r
@@
 above.  The schematic of the model configuration is shown in
-Figure~\ref{fig:config_stellarwind}. Again, we assume the wind
+Fig.~\ref{fig:config_stellarwind}. Again, we assume the wind
 temperature ($T_{\mathrm{wind}}$) is isothermal for simplicity.  
@@
 
-The right-hand panel in Figure~\ref{fig:effect_inclination_compare} shows
-H$\alpha$ profiles computed using the alternative model at
-the same inclination angles used for the disc-wind-magnetosphere
-hybrid model. The wind acceleration parameter ($\beta$) and the wind
-temperature ($T_{\mathrm{wind}}$)used here are $0.5$ and
+The right-hand panel in Fig.~\ref{fig:effect_inclination_compare}
+shows H$\alpha$ profiles computed using the alternative model at the
+same inclination angles used for the disc-wind-magnetosphere hybrid
+model. The wind acceleration parameter ($\beta$) and the wind
+temperature ($T_{\mathrm{wind}}$)used here are $1.0$ and
 $9000\,\Kelvin$ respectively. All the other parameters are same as in
 the disc-wind magnetosphere model.  With this set of $\beta$ and
-$T_{\mathrm{wind}}$, the wind emission is comparable or a slightly
-greater than the emission from the magnetosphere. The profiles show
-rather complex absorption features because of the interaction of
-photons created in the wind with the magnetosphere.
-
-xxx check this out and rephrase xxx
-
-The blue-shifted absorption features are formed in the wind, the
-absorption features near the line centre and in the red wing (only for
-$i=10^\circ$) are caused by the wind absorbing emission from the  magnetosphere.
-
-Because of the geometry of the wind, the P-Cygni absorption feature
-weakens as the inclination increases: the optical depth of the wind is
-much higher in 
-the polar direction. For the
-same reason, the EW of the line increases as the inclination increases
-as clearly seen in the figure. Specifically the values are 
-49\AA, 60\AA, and 84\AA\, for $i=10^\circ$, $55^\circ$, and
-$80^\circ$ respectively.  This tendency
-of the inclination dependency holds for the models with this wind
-models for wide ranges of $\beta$ and $T_{\mathrm{wind}}$ providing that
-the emission from the wind is comparable to that of the magnetosphere.
-
-The \citet{appenzeller:2005} study used just xxx objects, and a significantly
+$T_{\mathrm{wind}}$, the wind emission is significantly larger than
+the emission from the magnetosphere.  Because of the geometry of the
+wind, the P-Cygni absorption feature weakens as the inclination
+increases: the optical depth of the wind is much higher in the polar
+direction. For the same reason, the EW of the line increases as the
+inclination increases as clearly seen in the figure. Specifically the
+values are 54\,\AA, 69\,\AA, and 98\,\AA\, for $i=10^\circ$,
+$55^\circ$, and $80^\circ$ respectively.  This tendency of the
+inclination dependency holds for the models with this wind models for
+wide ranges of $\beta$ and $T_{\mathrm{wind}}$ providing that the
+emission from the wind is greater than that of the magnetosphere.
+
+The \citet{appenzeller:2005} study used just 12 objects, and a significantly
 greater sample should be investigated before firm  conclusions are
@@
 
-One potential free parameter of our models is the ratio of mass-loss rate to mass-accretion rate
-($\mu$). Most MHD simulations predict a value of  $\mu = 0.1$ (c.f.~\citealt{koenigl:2000}), 
-and we have adopted this figure for most of our models. The success of our
-profile in matching observations is therefore encouraging,  and provides support
-for this canonical value of $\mu$. We have computed sample models with other
-values of $\mu$, (cite figure xxxx) and find that models with $0.05 <\mu<0.2$ are still
-be consistent with observations. Wind-only or magnetosphere-only models may be
-representative of individual line profiles, but neither can explain the complete
-Reipurth classification scheme--even magnetosphere dominated profiles (Type~I)
-can be readily explained by the hybrid model with $\mu=0.1$.
+One potential free parameter of our models is the ratio of mass-loss
+rate to mass-accretion rate ($\mu$). Most MHD simulations predict a
+value of $\mu = 0.1$ (c.f.~\citealt{koenigl:2000}), and we have
+adopted this figure for most of our models. The success of our profile
+in matching observations is therefore encouraging, and provides
+support for this canonical value of $\mu$. We have computed sample
+models with other values of $\mu$,
+(Fig.~\ref{fig:discwind_mu_effect}) and find that models with $0.05
+<\mu<0.2$ are still be consistent with observations. Wind-only or
+magnetosphere-only models may be representative of individual line
+profiles, but neither can explain the complete Reipurth classification
+scheme--even magnetosphere dominated profiles (Type~I) can be readily
+explained by the hybrid model with $\mu=0.1$.
 
@@
 line equivalent width dependency on the inclination 
-(Figure~\ref{fig:effect_inclination_compare}).  However, MHD simulations
+(Fig.~\ref{fig:effect_inclination_compare}).  However, MHD simulations
 predict that bipolar or jet-like flows in CTTS are always accompanied by
@@
 
-Although we have concentrated on CTTS here, the hybrid model is equally
-applicable to pre-main-sequence stars across the mass spectrum. Herbig
-Ae/Be star profiles are equally diverse, and whilst many of the profiles
-are indicative of a wind (\citet{finkenzeller:1984}) some lines may be explained
-by magnetospheric accretion alone (e.g. \citealt{muzerolle:2005}). One possible
-advantage in applying the hybrid model to the Herbig Ae/Be systems is the growing
-observational data probing the line formation region and inner disc using techniques
-such as spectro-astrometry (Baines xxxx), spectropolarimetry (Vink xxxx) and
-interferometry (Monnier etc). These high-resolution techniques may aid model
-fitting of individual objects by constraining some of the model parameters, in
-particular the inclination.
-
-Velocity broadened, asymmetric H$\alpha$ profiles in BDs are used as an
-indicator of ongoing magnetospheric accretion, and the same models that
-are used for CTTS are applied to these systems in order to determine mass-accretion
-rates (muzerolle, lawson, jayawardhana xxxx). The line profiles however display
-the same wide variety of morphologies as the CTTS and Herbig Ae/Be stars (although
-we note as yet no BD profile has been observed with red-shifted absorption).
-It is natural to assume that the same physics applies in these low mass objects, 
-and that a hybrid model may be more successful in fitting these profiles, and will
-give greater insight into the circumstellar kinematics.
-
-There are several avenues of future work to consider. Here we have adopted
-a simple analytical form for the accretion and outflow velocity and density structure.
-A more self-consistent approach would be to use the results of MHD simulations
-as an input to the radiative-transfer modelling. The thermodynamics of the 
-circumstellar gas needs to be examined (c.f.~\citealt{hartmann:1994}; \citealt{martin:1996})
-and also computed self-consistently with the radiation field used in the radiative-transfer,
-a process that would decrease the free parameters of the model.
-We intend to calculate other observables from the model that may be compared with observation 
-and should provide further constraints. The line polarization signature, which
-arises from scattering of line and continuum photons in the circumstellar dust, encodes both dynamical and geometric information, such as the size of the inner disk radius  (Vink obs paper, Vink theory paper xxxx).
-Spectro-astrometry may provide information on the system's inclination, and the geometry
-of the outflow on large scales (Takami paper; Baines paper xxxx). Interferometry also provides information on inner disc radii and inclinations, although currently only for the Herbig Ae/Be stars.
-
-We have concentrated on the formation of the H$\alpha$ line, since it is the best studied CTTS
-emission line. However it is clear that simultaneous fitting of several emission line profile should
-provide much stronger constrains. In particular it appears that the near-IR hydrogen lines (Pa$\beta$ and Br$\gamma$) are less-effected by outflows than H$\alpha$. One could therefore use these
-lines to constrain the mass-accretion rate, and H$\alpha$ the mass-loss rate. A potential pitfall 
-is the significant temporal variability that all CTTS show in their emission lines; the observational
-data on a particular object must be co-temporaneous.
+Although we have concentrated on CTTS here, the hybrid model is
+equally applicable to pre-main-sequence stars across the mass
+spectrum. Herbig Ae/Be star profiles are equally diverse, and whilst
+many of the profiles are indicative of a wind
+(\citet{finkenzeller:1984}) some lines may be explained by
+magnetospheric accretion alone (e.g. \citealt{muzerolle:2005}). One
+possible advantage in applying the hybrid model to the Herbig Ae/Be
+systems is the growing observational data probing the line formation
+region and inner disc using techniques such as spectro-astrometry
+\citep[e.g.][]{baines:2006}, spectropolarimetry
+\citep[e.g.][]{vink:2005} and interferometry
+\citep[e.g.][]{monnier:2005}. These high-resolution techniques may aid
+model fitting of individual objects by constraining some of the model
+parameters, in particular the inclination.
+
+Velocity broadened, asymmetric H$\alpha$ profiles in BDs are used as
+an indicator of ongoing magnetospheric accretion, and the same models
+that are used for CTTS are applied to these systems in order to
+determine mass-accretion rates (e.g.~\citealt{mohanty:2005}; 
+\citealt{muzerolle:2005}). The line profiles however display the same
+wide variety of morphologies as the CTTS and Herbig Ae/Be stars
+(although we note as yet no BD profile has been observed with
+red-shifted absorption).  It is natural to assume that the same
+physics applies in these low mass objects, and that a hybrid model may
+be more successful in fitting these profiles, and will give greater
+insight into the circumstellar kinematics.
+
+There are several avenues of future work to consider. Here we have
+adopted a simple analytical form for the accretion and outflow
+velocity and density structure.  A more self-consistent approach would
+be to use the results of MHD simulations as an input to the
+radiative-transfer modelling. The thermodynamics of the circumstellar
+gas needs to be examined (c.f.~\citealt{hartmann:1994};
+\citealt{martin:1996}) and also computed self-consistently with the
+radiation field used in the radiative-transfer, a process that would
+decrease the free parameters of the model.  We intend to calculate
+other observables from the model that may be compared with observation
+and should provide further constraints. The line polarisation
+signature, which arises from scattering of line and continuum photons
+in the circumstellar dust, encodes both dynamical and geometric
+information, such as the size of the inner disk radius
+(e.g.~\citealt{vink:2005a}: \citealt{vink:2005}). Spectro-astrometry
+may provide information on the system's inclination, and the geometry
+of the outflow on large scales (e.g.~\citealt{takami:2003}:
+\citealt{baines:2006}). Interferometry also provides information on
+inner disc radii and inclinations, although currently only for the
+Herbig Ae/Be stars.
+
+We have concentrated on the formation of the H$\alpha$ line, since it
+is the best studied CTTS emission line. However it is clear that
+simultaneous fitting of several emission line profile should provide
+much stronger constrains. In particular it appears that the near-IR
+hydrogen lines (Pa$\beta$ and Br$\gamma$) are less-effected by
+outflows than H$\alpha$. One could therefore use these lines to
+constrain the mass-accretion rate, and H$\alpha$ the mass-loss rate. A
+potential pitfall is the significant temporal variability that all
+CTTS show in their emission lines; the observational data on a
+particular object must be co-temporaneous.
 
@@
 \section{H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model}
+\label{sec:appendix}
 
@@
 magnetospheric geometry and the photosphere as given in
-Table~\ref{tab:std_paramters} in the main text. The ratio ($\mu$) of the
+Table~\ref{tab:std_parameters} in the main text. The ratio ($\mu$) of the
 mass-loss rate to mass-accretion rate is fixed to 0.1 for the all 
@@
 mass-accretion rate, are presented here: 
-(1) $\dot{M}_{\mathrm{acc}}=10^{-7}\,M_{\sun}\,\mathrm{yr^{-1}}$ (Figure~\ref{fig:atlas01}), 
-(2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,M_{\sun}\,\mathrm{yr^{-1}}$ (Figure~\ref{fig:atlas01}), and
-(3) $\dot{M}_{\mathrm{acc}}=10^{-7}\,M_{\sun}\,\mathrm{yr^{-1}}$
-(Figure~\ref{fig:atlas01}).   The temperature of the magnetosphere
+(1) $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas01}), 
+(2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas02}), and
+(3) $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$
+(Fig.~\ref{fig:atlas02}).   The temperature of the magnetosphere
 used for (1), (2) and (3) are $7500\Kelvin$, $8500\Kelvin$ and
@@
   \caption{An H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
-  $\dot{M_{\mathrm{acc}}} =10^{-7}\,M_{\sun}\,\mathrm{yr{-1}}$ and
-  $\dot{M_{\mathrm{wind}}}=10^{-6}\,M_{\sun}\,\mathrm{yr{-1}}$. 
+  $\dot{M}_{\mathrm{acc}} =10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$ and
+  $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr{-1}}$. 
   Profiles are presented
@@
 
-  \caption{As for Figure~\ref{fig:atlas01} except
-  $\dot{M_{\mathrm{acc}}} =10^{-8}\,M_{\sun}\,\mathrm{yr{-1}}$ and
-  $\dot{M_{\mathrm{wind}}}=10^{-7}\,M_{\sun}\,\mathrm{yr{-1}}$. }
+  \caption{As for Fig.~\ref{fig:atlas01} except
+  $\dot{M}_{\mathrm{acc}} =10^{-8}\,\mathrm{M_{\sun}\,yr{-1}}$ and
+  $\dot{M}_{\mathrm{wind}}=10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$. }
 
@@
 
-  \caption{As for Figure~\ref{fig:atlas01} except
-    $\dot{M_{\mathrm{acc}}} =10^{-9}\,M_{\sun}\,\mathrm{yr{-1}}$ and
-  $\dot{M_{\mathrm{wind}}}=10^{-10}\,M_{\sun}\,\mathrm{yr{-1}}$. }
+  \caption{As for Fig.~\ref{fig:atlas01} except
+    $\dot{M_{\mathrm{acc}}} =10^{-9}\,\mathrm{M_{\sun}\,yr{-1}}$ and
+  $\dot{M_{\mathrm{wind}}}=10^{-10}\,\mathrm{M_{\sun}\,yr{-1}}$. }
 

### 2006-01-29 TTau_Halpha/plots/plot_discwind.f90

@@ -30,7 +30,8 @@ program plot_discwind
   !==============================================
 
   ! set up L values
-  lmin = 1.0d-3           ! [10^10 cm]
+!  lmin = 1.0d-3           ! [10^10 cm]
+  lmin = 1.0d-6           ! [10^10 cm]
 !  lmax = 36.0d0*1000.d0  ! [10^10 cm]
   lmax = 150000.d0  ! [10^10 cm]
   log10_lmin = LOG10(lmin); log10_lmax = LOG10(lmax)

### 2006-01-29 TTau_Halpha/kurosawa.tex
minor change in the caption in the apendix.  (rk)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@644 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-  \caption{An H$\alpha$ atlas of the disc-wind-magnetosphere hybrid model with
-  $\dot{M}_{\mathrm{acc}} =10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$ and
+  \caption{An H$\alpha$ atlas of the disc-wind-magnetosphere hybrid
+  model with $\dot{M}_{\mathrm{acc}}
+  =10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$ and
   $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr{-1}}$.
-  Profiles are presented
-  for inclinations of $10^\circ$ (top figure), $55^\circ$ (middle figure), and $80^\circ$ (bottom figure).
-  For each inclination, 12 profiles are given, for three different values of the wind temperature, and four
-  different values of the wind acceleration parameter $\beta$.}
+  Profiles are presented for inclinations of $10^\circ$ (top figure),
+  $55^\circ$ (middle figure), and $80^\circ$ (bottom figure).  For
+  each inclination, 12 profiles are given, for three different values
+  of the wind temperature, and four different values of the wind
+  acceleration parameter $\beta$. The contribution of the
+  magnetosphere can be judged from the profiles computed with the
+  magnetosphere only (dotted lines).}
 

### 2006-01-30 TTau_Halpha/kurosawa.tex
Minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@645 25464f21-6099-402c-b30a-640f1d40d38b

@@
   stars]{On the formation of H$\alpha$ line emission around classical
-  T Tauri star: the disc-wind-magnetosphere hybrid models}
+  T Tauri star: the disc-wind-magnetosphere hybrid model}
 

### 2006-01-30 TTau_Halpha/kurosawa.tex
replaced the greyscale image for a better contrast one.  RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@646 25464f21-6099-402c-b30a-640f1d40d38b
Typo fixed.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@647 25464f21-6099-402c-b30a-640f1d40d38b

@@
 case), the P-Cygni absorption is absent from the profile because the
-opening angel of the disc wind is greater than the inclination angle.
+opening angle of the disc wind is greater than the inclination angle.
 For the disc wind models presented in this paper, we use $d=44~R_{*}$
-to have a moderate amount of wind absorption at a moderate inclination
-angle ($i\sim60^\circ$).
+in order to have a moderate amount of wind absorption at a moderate
+inclination angle ($i\sim60^\circ$).
 
@@
 
+%    \includegraphics[%
+%      clip,
+%      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
     \includegraphics[%
 	clip,
-      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
+     scale=0.45, angle=270]{figures/discwind_hybrid_ha_image_grey.eps}
 

### 2006-01-30 TTau_Halpha/kurosawa.tex
Typo corrections done. The reference are now inserted in the main text!!! (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@648 25464f21-6099-402c-b30a-640f1d40d38b

@@
   stars]{On the formation of H$\alpha$ line emission around classical
-  T Tauri star: the disc-wind-magnetosphere hybrid model}
+  T Tauri stars: the disc-wind-magnetosphere hybrid model}
 
@@
     hybrid model. The system consist of four components: (1)~the
-    continuum source located at the origin $\left( o \right)$ of the
+    continuum source located at the origin of the
     cartesian coordinates $\left(x,y,z\right)$ -- the $y$-axis is into
@@
 disc-wind model in their studies of the UV resonance lines formed
-in the winds of cataclysmic variable stars. His formalism provides
+in the winds of cataclysmic variable stars. Their formalism provides
 a simple parameterisation of a disc wind that has similar properties 
@@
 Model~1 of the dust model used by \citet{wood:2002}. See also their
-Fig.~3 The relative numbers of each grain is assumed to be that of
+Fig.~3.  The relative numbers of each grain is assumed to be that of
 solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989} and
@@
 \[
-\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'
+\tau\left(t\right)\equiv\int_{t}^{\tau_{\infty}}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'
 \]
@@
     model with the damping constant. The broad wings extend to $\sim \pm
-    800 \kmps$.  The redshifted absorption feature (very weakly) seen in
+    800\,\kmps$.  The redshifted absorption feature (very weakly) seen in
     the $\Gamma=0$ model is not seen in the model with the broadening.  }
@@
 (while keeping $\mu$ constant) produce profiles with the line
-strengths comparable to observations.  Although the models in
-Fig.~\ref{fig:atlas_hybrid} are computed with limited
-ranges of $T_{\mathrm{wind}}$, $\beta$ and a fixed $i$, the resulting
-profiles exhibit a wide variety of line profile shapes, many of which
-are similar to the types of H$\alpha$ profiles seen in the observations
-(c.f.~\citealt{reipurth:1996}).
+strengths comparable to observations (c.f.~appendix~\ref{sec:appendix}).
+Although the models in Fig.~\ref{fig:atlas_hybrid} are computed with
+limited ranges of $T_{\mathrm{wind}}$, $\beta$ and a fixed $i$, the
+resulting profiles exhibit a wide variety of line profile shapes, many
+of which are similar to the types of H$\alpha$ profiles seen in the
+observations (c.f.~\citealt{reipurth:1996}).
 
@@
 mass-loss rate is varied. The figure shows that as $\mu$ increases the
-P-Cygni absorption deepens only slightly., and the position of minimum flux in the
-absorption trough appears to move blue-ward.  On the other hand, the
-flux peak increase and the line wings become stronger as $\mu$
-increases.  Although MHD models suggests (e.g.~\citealt{koenigl:2000})
-that $\mu \sim 0.1$, the figure suggest that models a relatively wide range
-of $\mu$  (e.g.~between 0.025 and 0.2 in this case)  reproduce the
-profiles similar to observations.
+P-Cygni absorption deepens only slightly, and the position of minimum
+flux in the absorption trough appears to move blue-ward.  On the other
+hand, the flux peak increase and the line wings become stronger as
+$\mu$ increases.  Although MHD models suggests
+(e.g.~\citealt{koenigl:2000}) that $\mu \sim 0.1$, the figure suggest
+that models a relatively wide range of $\mu$ (e.g.~between 0.025 and
+0.2 in this case) reproduce the profiles similar to observations.
 
@@
 many of the profiles are indicative of a wind
-(\citet{finkenzeller:1984}) some lines may be explained by
+(\citealt{finkenzeller:1984}) some lines may be explained by
 magnetospheric accretion alone (e.g. \citealt{muzerolle:2005}). One
@@
 %
-\bibliographystyle{mn}
-\bibliography{mnras}
+
+%\bibliographystyle{mn}
+%\bibliography{mnras}
+
+\begin{thebibliography}{73}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Alencar} \& {Basri}(2000)}]{alencar:2000}
+{Alencar} S.~H.~P., {Basri} G., 2000, \aj, 119, 1881
+
+\bibitem[{{Alencar} {et~al.}(2005){Alencar}, {Basri}, {Hartmann}, \&
+  {Calvet}}]{alencar:2005}
+{Alencar} S.~H.~P., {Basri} G., {Hartmann} L., {Calvet} N., 2005, \aap, 440,
+  595
+
+\bibitem[{{Anders} \& {Grevesse}(1989)}]{anders:1989}
+{Anders} E., {Grevesse} N., 1989, geochim. cosmochim. acta, 53, 197
+
+\bibitem[{{Appenzeller} {et~al.}(2005){Appenzeller}, {Bertout}, \&
+  {Stahl}}]{appenzeller:2005}
+{Appenzeller} I., {Bertout} C., {Stahl} O., 2005, \aap, 434, 1005
+
+\bibitem[{{Appenzeller} \& {Mundt}(1989)}]{appenzeller:1989}
+{Appenzeller} I., {Mundt} R., 1989, \aapr, 1, 291
+
+\bibitem[{{Baines} {et~al.}(2005){Baines}, {Oudmaijer}, {Porter}, \&
+  {Pozzo}}]{baines:2006}
+{Baines} D., {Oudmaijer} R., {Porter} J., {Pozzo} M., 2005, preprint
+  (astro-ph/0512534)
+
+\bibitem[{{Bertout} {et~al.}(1988){Bertout}, {Basri}, \&
+  {Bouvier}}]{bertout:1988}
+{Bertout} C., {Basri} G., {Bouvier} J., 1988, \apj, 330, 350
+
+\bibitem[{{Blandford} \& {Payne}(1982)}]{blandford:1982}
+{Blandford} R.~D., {Payne} D.~G., 1982, \mnras, 199, 883
+
+\bibitem[{{Burrows} {et~al.}(1996){Burrows}, {Stapelfeldt}, {Watson}, {Krist},
+  {Ballester}, {Clarke}, {Crisp}, {Gallagher}, {Griffiths}, {Hester},
+  {Hoessel}, {Holtzman}, {Mould}, {Scowen}, {Trauger}, \&
+  {Westphal}}]{burrows:1996}
+{Burrows} C.~J. et al., 1996, \apj, 473, 437
+
+\bibitem[{{Camenzind}(1990)}]{camenzind:1990}
+{Camenzind} M., 1990, Reviews of Modern Astronomy, 3, 234
+
+\bibitem[{{Castor} {et~al.}(1975){Castor}, {Abbott}, \& {Klein}}]{castor:1975}
+{Castor} J.~I., {Abbott} D.~C., {Klein} R.~I., 1975, \apj, 195, 157
+
+\bibitem[{{Castor} \& {Lamers}(1979)}]{castor:1979}
+{Castor} J.~I., {Lamers} H.~J.~G.~L.~M., 1979, \apjs, 39, 481
+
+\bibitem[{{Chiang} \& {Goldreich}(1997)}]{chiang:1997}
+{Chiang} E.~I., {Goldreich} P., 1997, \apj, 490, 368
+
+\bibitem[{{Collier Cameron} \& {Campbell}(1993)}]{cameron:1993}
+{Collier Cameron} A., {Campbell} C.~G., 1993, \aap, 274, 309
+
+\bibitem[{{Draine} \& {Lee}(1984)}]{draine:1984}
+{Draine} B.~T., {Lee} H.~M., 1984, \apj, 285, 89
+
+\bibitem[{{Drew} {et~al.}(1998){Drew}, {Proga}, \& {Stone}}]{drew:1998}
+{Drew} J.~E., {Proga} D., {Stone} J.~M., 1998, \mnras, 296, L6
+
+\bibitem[{{Edwards} {et~al.}(1987){Edwards}, {Cabrit}, {Strom}, {Heyer},
+  {Strom}, \& {Anderson}}]{edwards:1987}
+{Edwards} S., {Cabrit} S., {Strom} S.~E., {Heyer} I., {Strom} K.~M., {Anderson}
+  E., 1987, \apj, 321, 473
+
+\bibitem[{{Edwards} {et~al.}(1994){Edwards}, {Hartigan}, {Ghandour}, \&
+  {Andrulis}}]{edwards:1994}
+{Edwards} S., {Hartigan} P., {Ghandour} L., {Andrulis} C., 1994, \aj, 108, 1056
+
+\bibitem[{{Finkenzeller} \& {Mundt}(1984)}]{finkenzeller:1984}
+{Finkenzeller} U., {Mundt} R., 1984, \aaps, 55, 109
+
+\bibitem[{{Frank} {et~al.}(2002){Frank}, {King}, \& {Raine}}]{frank:2002}
+{Frank} J., {King} A., {Raine} D.~J., 2002, {Accretion Power in Astrophysics,
+  3rd edn.} Cambridge Univ.\, Press, Cambridge, p. 398
+
+\bibitem[{{Ghosh} {et~al.}(1977){Ghosh}, {Pethick}, \& {Lamb}}]{ghosh:1977}
+{Ghosh} P., {Pethick} C.~J., {Lamb} F.~K., 1977, \apj, 217, 578
+
+\bibitem[{Grevesse \& Noels(1993)}]{grevesse:1993}
+Grevesse N., Noels A., 1993, in Origin and Evolution of the Elements, N.\ P.,
+  E.\ V.-F., M.\ C., eds., Cambridge Univ.\, Press, Cambridge, p.~15
+
+\bibitem[{{Gullbring} {et~al.}(1998){Gullbring}, {Hartmann}, {Briceno}, \&
+  {Calvet}}]{gullbring:1998}
+{Gullbring} E., {Hartmann} L., {Briceno} C., {Calvet} N., 1998, \apj, 492, 323
+
+\bibitem[{{Hanner}(1988)}]{hanner:1988}
+{Hanner} M., 1988, in NASA Conf. Pub. 3004, 22, Vol. 3004, p.~22
+
+\bibitem[{{Harries}(2000)}]{harries:2000}
+{Harries} T.~J., 2000, MNRAS, 315, 722
+
+\bibitem[{{Hartigan} {et~al.}(1995){Hartigan}, {Edwards}, \&
+  {Ghandour}}]{hartigan:1995}
+{Hartigan} P., {Edwards} S., {Ghandour} L., 1995, \apj, 452, 736
+
+\bibitem[{{Hartmann} {et~al.}(1982){Hartmann}, {Avrett}, \&
+  {Edwards}}]{hartmann:1982}
+{Hartmann} L., {Avrett} E., {Edwards} S., 1982, \apj, 261, 279
+
+\bibitem[{{Hartmann} {et~al.}(1994){Hartmann}, {Hewett}, \&
+  {Calvet}}]{hartmann:1994}
+{Hartmann} L., {Hewett} R., {Calvet} N., 1994, \apj, 426, 669
+
+\bibitem[{{Herbig}(1962)}]{herbig:1962}
+{Herbig} G.~H., 1962, Advances in Astronomy and Astrophysics, 1, 47
+
+\bibitem[{{Herbig} \& {Bell}(1988)}]{herbig:1988}
+{Herbig} G.~H., {Bell} K.~R., 1988, {Catalog of emission line stars of the
+  orion population}, Vol.~3. Lick Observatory Bulletin, Santa Cruz: Lick
+  Observatory
+
+\bibitem[{Hillier(1991)}]{hillier:1991}
+Hillier D.~J., 1991, \aap, 247, 455
+
+\bibitem[{{Johns-Krull} {et~al.}(1999){Johns-Krull}, {Valenti}, {Hatzes}, \&
+  {Kanaan}}]{johns-krull:1999}
+{Johns-Krull} C.~M., {Valenti} J.~A., {Hatzes} A.~P., {Kanaan} A., 1999, \apjl,
+  510, L41
+
+\bibitem[{{Kenyon} \& {Hartmann}(1987)}]{kenyon:1987}
+{Kenyon} S.~J., {Hartmann} L., 1987, \apj, 323, 714
+
+\bibitem[{{Kenyon} {et~al.}(1994){Kenyon}, {Hartmann}, {Hewett},
+  {Carrasco}~{Cruz-Gonzalez}, {Recillas}, {Salas}, {Serrano}, {Strom}, {Strom},
+  \& {Newton}}]{kenyon:1994}
+{Kenyon} S.~J., {Hartmann} L., {Hewett} R., {Carrasco}~{Cruz-Gonzalez} I.,
+  {Recillas} E., {Salas} L., {Serrano} A., {Strom} K.~M., {Strom} S.~E.,
+  {Newton} G., 1994, \aj, 107, 2153
+
+\bibitem[{{Kim} {et~al.}(1994){Kim}, {Martin}, \& {Hendry}}]{kim:1994}
+{Kim} S., {Martin} P.~G., {Hendry} P.~D., 1994, \apj, 422, 164
+
+\bibitem[{{Klein} \& {Castor}(1978)}]{klein:1978}
+{Klein} R.~I., {Castor} J.~I., 1978, \apj, 220, 902
+
+\bibitem[{{Knigge} {et~al.}(1995){Knigge}, {Woods}, \& {Drew}}]{knigge:1995}
+{Knigge} C., {Woods} J.~A., {Drew} E., 1995, \mnras, 273, 225
+
+\bibitem[{{K\"{o}nigl}(1991)}]{koenigl:1991}
+{K\"{o}nigl} A., 1991, \apj, 370, L39
+
+\bibitem[{{K\"{o}nigl} \& {Pudritz}(2000)}]{koenigl:2000}
+{K\"{o}nigl} A., {Pudritz} R.~E., 2000, Protostars and Planets IV, 759
+
+\bibitem[{{Krasnopolsky} {et~al.}(2003){Krasnopolsky}, {Li}, \&
+  {Blandford}}]{krasnopolsky:2003}
+{Krasnopolsky} R., {Li} Z.-Y., {Blandford} R.~D., 2003, \apj, 595, 631
+
+\bibitem[{{Kuhi}(1964)}]{kuhi:1964}
+{Kuhi} L.~V., 1964, \apj, 140, 1409
+
+\bibitem[{{Kurosawa} {et~al.}(2004){Kurosawa}, {Harries}, {Bate}, \&
+  {Symington}}]{kurosawa:2004a}
+{Kurosawa} R., {Harries} T.~J., {Bate} M.~R., {Symington} N.~H., 2004, \mnras,
+  351, 1134
+
+\bibitem[{{Kurosawa} {et~al.}(2005){Kurosawa}, {Harries}, \&
+  {Symington}}]{kurosawa:2005a}
+{Kurosawa} R., {Harries} T.~J., {Symington} N.~H., 2005, \mnras, 358, 671
+
+\bibitem[{{Kurucz}(1979)}]{kurucz:1979}
+{Kurucz} R.~L., 1979, \apjs, 40, 1
+
+\bibitem[{{Long} \& {Knigge}(2002)}]{long:2002}
+{Long} K.~S., {Knigge} C., 2002, \apj, 579, 725
+
+\bibitem[{{Luttermoser} \& {Johnson}(1992)}]{luttermoser:1992}
+{Luttermoser} D.~G., {Johnson} H.~R., 1992, \apj, 388, 579
+
+\bibitem[{{Martin}(1996)}]{martin:1996}
+{Martin} S.~C., 1996, \apj, 470, 537
+
+\bibitem[{{Mathis} {et~al.}(1977){Mathis}, {Rumpl}, \&
+  {Nordsieck}}]{mathis:1977}
+{Mathis} J.~S., {Rumpl} W., {Nordsieck} K.~H., 1977, \apj, 217, 425
+
+\bibitem[{{Matt} \& {Pudritz}(2005)}]{matt:2005}
+{Matt} S., {Pudritz} R.~E., 2005, \apjl, 632, L135
+
+\bibitem[{{Mihalas}(1978)}]{mihalas:1978}
+{Mihalas} D., 1978, {Stellar atmospheres, 2nd edn}. W.\ H.\ Freeman and Co.,
+  San Francisco
+
+\bibitem[{{Mohanty} {et~al.}(2005){Mohanty}, {Jayawardhana}, \&
+  {Basri}}]{mohanty:2005}
+{Mohanty} S., {Jayawardhana} R., {Basri} G., 2005, Memorie della Societa
+  Astronomica Italiana, 76, 303
+
+\bibitem[{{Monnier} {et~al.}(2005){Monnier}, {Millan-Gabet}, {Billmeier},
+  {Akeson}, {Wallace}, {Berger}, {Calvet}, {D'Alessio}, {Danchi}, {Hartmann},
+  {Hillenbrand}, {Kuchner}, {Rajagopal}, {Traub}, {Tuthill}, {Boden}, {Booth},
+  {Colavita}, {Gathright}, {Hrynevych}, {Le Mignant}, {Ligon}, {Neyman},
+  {Swain}, {Thompson}, {Vasisht}, {Wizinowich}, {Beichman}, {Beletic},
+  {Creech-Eakman}, {Koresko}, {Sargent}, {Shao}, \& {van Belle}}]{monnier:2005}
+{Monnier} J.~D. et al., 2005, \apj, 624, 832
+
+\bibitem[{{Muzerolle} {et~al.}(2001){Muzerolle}, {Calvet}, \&
+  {Hartmann}}]{muzerolle:2001}
+{Muzerolle} J., {Calvet} N., {Hartmann} L., 2001, \apj, 550, 944
+
+\bibitem[{{Muzerolle} {et~al.}(2005){Muzerolle}, {Luhman}, {Brice{\~n}o},
+  {Hartmann}, \& {Calvet}}]{muzerolle:2005}
+{Muzerolle} J., {Luhman} K.~L., {Brice{\~n}o} C., {Hartmann} L., {Calvet} N.,
+  2005, \apj, 625, 906
+
+\bibitem[{{Ouyed} \& {Pudritz}(1997)}]{ouyed:1997}
+{Ouyed} R., {Pudritz} R.~E., 1997, \apj, 482, 712
+
+\bibitem[{{Pudritz} \& {Banerjee}(2005)}]{pudritz:2005}
+{Pudritz} R.~E., {Banerjee} R., 2005, in Cesaroni, R., Felli, M.,
+Churchwell, E., Walmsley, M., eds, Proc.~IAU Symp. 225, Massive star
+birth: A crossroads of Astrophysics, Cambridge University Press,
+Cambridge,  p.~163
+
+\bibitem[{{Ray} {et~al.}(1996){Ray}, {Mundt}, {Dyson}, {Falle}, \&
+  {Raga}}]{ray:1996}
+{Ray} T.~P., {Mundt} R., {Dyson} J.~E., {Falle} S.~A.~E.~G., {Raga} A.~C.,
+  1996, \apjl, 468, L103
+
+\bibitem[{{Reipurth} {et~al.}(1996){Reipurth}, {Pedrosa}, \&
+  {Lago}}]{reipurth:1996}
+{Reipurth} B., {Pedrosa} A., {Lago} M.~T.~V.~T., 1996, \aaps, 120, 229
+
+\bibitem[{{Rybicki} \& {Hummer}(1978)}]{rybicki:1978}
+{Rybicki} G.~B., {Hummer} D.~G., 1978, \apj, 219, 654
+
+\bibitem[{{Shakura} \& {Sunyaev}(1973)}]{shakura:1973}
+{Shakura} N.~I., {Sunyaev} R.~A., 1973, \aap, 24, 337
+
+\bibitem[{{Shang} {et~al.}(2002){Shang}, {Glassgold}, {Shu}, \&
+  {Lizano}}]{shang:2002}
+{Shang} H., {Glassgold} A.~E., {Shu} F.~H., {Lizano} S., 2002, \apj, 564, 853
+
+\bibitem[{{Shu} {et~al.}(1994){Shu}, {Najita}, {Ostriker}, {Wilkin}, {Ruden},
+  \& {Lizano}}]{shu:1994}
+{Shu} F.~H., {Najita} J., {Ostriker} E., {Wilkin} F., {Ruden} S., {Lizano} S.,
+  1994, \apj, 429, 781
+
+\bibitem[{{Symington} {et~al.}(2005{\natexlab{a}}){Symington}, {Harries}, \&
+  {Kurosawa}}]{symington:2005}
+{Symington} N.~H., {Harries} T.~J., {Kurosawa} R., 2005{\natexlab{a}}, \mnras,
+  356, 1489
+
+\bibitem[{{Symington} {et~al.}(2005{\natexlab{b}}){Symington}, {Harries},
+  {Kurosawa}, \& {Naylor}}]{symington:2005b}
+{Symington} N.~H., {Harries} T.~J., {Kurosawa} R., {Naylor} T.,
+  2005{\natexlab{b}}, \mnras, 358, 977
+
+\bibitem[{{Takami} {et~al.}(2003){Takami}, {Bailey}, \&
+  {Chrysostomou}}]{takami:2003}
+{Takami} M., {Bailey} J., {Chrysostomou} A., 2003, \aap, 397, 675
+
+\bibitem[{{Uchida} \& {Shibata}(1985)}]{uchida:1985}
+{Uchida} Y., {Shibata} K., 1985, \pasj, 37, 515
+
+\bibitem[{{Ustyugova} {et~al.}(1995){Ustyugova}, {Koldoba}, {Romanova},
+  {Chechetkin}, \& {Lovelace}}]{ustyugova:1995}
+{Ustyugova} G.~V., {Koldoba} A.~V., {Romanova} M.~M., {Chechetkin} V.~M.,
+  {Lovelace} R.~V.~E., 1995, \apjl, 439, L39
+
+\bibitem[{{Vernazza} {et~al.}(1973){Vernazza}, {Avrett}, \&
+  {Loeser}}]{vernazza:1973}
+{Vernazza} J.~E., {Avrett} E.~H., {Loeser} R., 1973, \apj, 184, 605
+
+\bibitem[{{Vink} {et~al.}(2005{\natexlab{a}}){Vink}, {Drew}, {Harries},
+  {Oudmaijer}, \& {Unruh}}]{vink:2005}
+{Vink} J.~S., {Drew} J.~E., {Harries} T.~J., {Oudmaijer} R.~D., {Unruh} Y.,
+  2005{\natexlab{a}}, \mnras, 359, 1049
+
+\bibitem[{{Vink} {et~al.}(2005{\natexlab{b}}){Vink}, {Harries}, \&
+  {Drew}}]{vink:2005a}
+{Vink} J.~S., {Harries} T.~J., {Drew} J.~E., 2005{\natexlab{b}}, \aap, 430, 213
+
+\bibitem[{{White} \& {Basri}(2003)}]{white:2003}
+{White} R.~J., {Basri} G., 2003, \apj, 582, 1109
+
+\bibitem[{{Whitney} {et~al.}(2003){Whitney}, {Wood}, {Bjorkman}, \&
+  {Wolff}}]{whitney:2003a}
+{Whitney} B.~A., {Wood} K., {Bjorkman} J.~E., {Wolff} M.~J., 2003, \apj, 591,
+  1049
+
+\bibitem[{{Wood} {et~al.}(2002){Wood}, {Wolff}, {Bjorkman}, \&
+  {Whitney}}]{wood:2002}
+{Wood} K., {Wolff} M.~J., {Bjorkman} J.~E., {Whitney} B., 2002, \apj, 564, 887
+
+\end{thebibliography}
 

### 2006-01-31 TTau_Halpha/submit/kurosawa.tex
Added "sumbit" directory containing the copy of kurosawa.tex and eps figures which renamed to fig01.eps, fig02.eps and etc.  RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@651 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-01-30 TTau_Halpha/kurosawa.tex
@@
     \includegraphics[%
-      scale=0.6]{figures/discwind.eps}
+      scale=0.6]{fig01.eps}
 
@@
   \dot{m}\left(w\right) \propto
-       \left[ T\left(w\right) \right]  ^{\alpha}\,\,.\label{eq:discwind-massloss-temp}
+       \left[ T\left(w\right) \right]  ^{4\alpha}\,\,.\label{eq:discwind-massloss-temp}
 \end{equation}
@@
 \end{equation}
-where $p=\alpha\times q$. The index of the mid-plane temperature power
+where $p=4\alpha\times q$. The index of the mid-plane temperature power
 law is adopted from the dust radiative transfer model of
@@
 disc has $q=-1.15$.  In order to be consistent with the collimated
-disc-wind model of \citet{krasnopolsky:2003} who used $p=-3/2$, the
-value of $\alpha$ is set to 1.3. The constant of proportionality in
+disc-wind model of \citet{krasnopolsky:2003} who used $p=-5/2$, the
+value of $\alpha$ is set to 0.76. The constant of proportionality in
 equation~\ref{eq:discwind-massloss-w} is found by integrating
@@
 	clip,
-	scale=0.59]{plots/dw_vp_vphi.eps}~~~~~~&
+	scale=0.59]{fig02a.eps}~~~~~~&
       \includegraphics[%
 	clip,
-	scale=0.59]{plots/dw_rho.eps}\tabularnewline
+	scale=0.59]{fig02b.eps}\tabularnewline
     \end{tabular}
@@
       clip,
-      scale=0.45]{figures/atlas_ha_i55_acc_model_final.eps}
+      scale=0.45]{fig03.eps}
 
@@
       clip,
-      scale=0.59]{figures/broadening.eps}
+      scale=0.59]{fig04.eps}
 
@@
       clip,
-      scale=0.59]{figures/acc_inc_effect.eps}
+      scale=0.59]{fig05.eps}
 
@@
       clip,
-      scale=0.9]{figures/atlas_ha_i55_discwind_only_final.eps}
+      scale=0.9]{fig06.eps}
 
@@
       clip,
-      scale=0.45]{figures/discwind_d_effect.eps}
+      scale=0.45]{fig07.eps}
 
@@
       clip,
-      scale=0.45]{figures/discwind_mdot_effect.eps}
+      scale=0.45]{fig08.eps}
 
@@
       clip,
-      scale=0.9]{figures/atlas_ha_i55_acc_discwind_final.eps}
+      scale=0.9]{fig09.eps}
 
@@
       clip,
-      scale=0.45]{figures/discwind_mu_effect.eps}
+      scale=0.45]{fig10.eps}
 
@@
 
+    \includegraphics[%
+      clip,
+      scale=0.45,angle=270]{fig11.eps}
 %    \includegraphics[%
 %	clip,
-%      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
-    \includegraphics[%
-	clip,
-     scale=0.45, angle=270]{figures/discwind_hybrid_ha_image_grey.eps}
+%     scale=0.45, angle=270]{fig11_grey.eps}
 
@@
       clip,
-      scale=0.65]{figures/atlas_reipurth_like_discwind.eps}
+      scale=0.65]{fig12.eps}
 
@@
 	clip,
-	scale=0.45]{figures/discwind_acc_inc_effect_m9_b1_t7000.eps}&
+	scale=0.45]{fig13a.eps}&
       \includegraphics[%
 	clip,
-	scale=0.61]{figures/stellarwind_inc_effect.eps}\tabularnewline
+	scale=0.61]{fig13b.eps}\tabularnewline
     \end{tabular}
@@
     \includegraphics[%
-      scale=0.3]{figures/overview4.eps}
+      scale=0.3]{fig14.eps}
 
@@
 	clip,
-	scale=0.6]{figures/discwind_hybrid_mdot7_inc10.eps}\tabularnewline
+	scale=0.6]{fig_a1_01.eps}\tabularnewline
       \vspace{0.5 cm}
@@
 	clip,
-      scale=0.6]{figures/discwind_hybrid_mdot7_inc55.eps}\tabularnewline
+      scale=0.6]{fig_a1_02.eps}\tabularnewline
 
@@
       \includegraphics[%
-	clip, scale=0.6]{figures/discwind_hybrid_mdot7_inc80.eps}\tabularnewline
+	clip, scale=0.6]{fig_a1_03.eps}\tabularnewline
   \end{center}
@@
 	clip,
-	scale=0.6]{figures/discwind_hybrid_mdot8_inc10.eps}\tabularnewline
+	scale=0.6]{fig_a2_01.eps}\tabularnewline
       \vspace{0.5 cm}
@@
 	clip,
-      scale=0.6]{figures/discwind_hybrid_mdot8_inc55.eps}\tabularnewline
+      scale=0.6]{fig_a2_02.eps}\tabularnewline
 
@@
       \includegraphics[%
-	clip, scale=0.6]{figures/discwind_hybrid_mdot8_inc80.eps}\tabularnewline
+	clip, scale=0.6]{fig_a2_03.eps}\tabularnewline
   \end{center}
@@
 	clip,
-	scale=0.6]{figures/discwind_hybrid_mdot9_inc10.eps}\tabularnewline
+	scale=0.6]{fig_a3_01.eps}\tabularnewline
       \vspace{0.5 cm}
@@
 	clip,
-      scale=0.6]{figures/discwind_hybrid_mdot9_inc55.eps}\tabularnewline
+      scale=0.6]{fig_a3_02.eps}\tabularnewline
 
@@
       \includegraphics[%
-	clip, scale=0.6]{figures/discwind_hybrid_mdot9_inc80.eps}\tabularnewline
+	clip, scale=0.6]{fig_a3_03.eps}\tabularnewline
   \end{center}

### 2006-02-01 TTau_Halpha/submit/kurosawa.tex
Many typos fixed. (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@652 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \usepackage{amssymb}
+\usepackage{babel}
 
@@
 %% Bold symbol macro for standard LaTeX users
+
+%% Because html converters don't know tabularnewline
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\IfFileExists{url.sty}{\usepackage{url}}
+                      {\newcommand{\url}{\texttt}}
+\providecommand{\tabularnewline}{\\}
+
 \newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}
-
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 
@@
 
-\usepackage{babel}
 \makeatother
@@
   stars]{On the formation of H$\alpha$ line emission around classical
-  T Tauri stars: the disc-wind-magnetosphere hybrid model}
+  T Tauri stars}
 
@@
 observations. We find that the hybrid models can reproduce the wide
-range profile types seen is observations, and that the most common
+range of profile types seen in observations, and that the most common
 profile types observed occupy a large volume of parameter
 space. Conversely, the most infrequently observed profile morphologies
-require a very specific set of models parameters.  We investigate the
+require a very specific set of models parameters.  We find our model
+profiles are consistent with the canonical value of the 
+mass-loss rate to mass-accretion rate ratio ($\mu=0.1$) found in
+earlier magneto-hydrodynamic calculations and observations, but the
+models with $0.05<\mu<0.2$ are still in accord with observed
+H$\alpha$ profiles.  We investigate the
 wind contribution to the line profile as a function of model parameters, and
@@
 distribution and polarisation data suggest the presence of
-circumstellar discs, which plays an important role in regulating
+circumstellar discs, which play an important role in regulating
 dynamics of gas flows around CTTS (e.g. \citealt{camenzind:1990}).
@@
 profiles respectively. Typical mass-loss rates of CTTS are about
-$10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\,
+$10^{-9}$ to $10^{-7}\,\mathrm{M_{\sun}\,
 yr^{-1}}$ (e.g., \citealt{kuhi:1964}; \citealt{edwards:1987};
 \citealt*{hartigan:1995}), and the mass-accretion rates are also about
-$10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\,
+$10^{-9}$ to $10^{-7}\,\mathrm{M_{\sun}\,
 yr^{-1}}$ (e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988};
@@
 observations using high-resolution ($R=50\,000$) two-dimensional
-spectra of edge-on CTTS (HH30$^{*}$, HK~Tau~B, and HV~Tau~C) by
+spectra of edge-on CTTS (HH~30, HK~Tau~B, and HV~Tau~C) by
 \citet{appenzeller:2005} show extended H$\alpha$ emission in the
@@
 their sample (30 CTTS) show blue-shifted absorption components in at
-least one of the Balmer lines and Ca~K.
+least one of the Balmer lines and Na~D.
 
@@
 radiative transfer models which reproduce the gross characteristics of
-observed profiles for some TTS (\citealt*{muzerolle:2001}). In
+observed profiles for some CTTS (\citealt*{muzerolle:2001}). In
 particular the magnetospheric accretion (MA) model explains blue-ward
@@
 Despite these successes, the overwhelming observational evidence for
-outflow in the CTTS suggests that the MA model is only one component
+outflows in CTTS suggests that the MA model is only one component
 of a complex circumstellar environment. Clearly, one must include the
 contribution of any wind/jet flow if one wishes to both accurately
-predict the mass-accretion rate and also determined the mass-loss rate
-of CTTS via emission profile modelling. The first attempt in this
+predict the mass-accretion rate and also determine the mass-loss rate
+of a CTTS via emission profile modelling. The first attempt in this
 direction was made by \citet{alencar:2005} who demonstrated that the
@@
 
-In section~\ref{sec:model-configuration}, the model assumptions, and
+In Section~\ref{sec:model-configuration}, the model assumptions and
 the basic model configurations are presented. We discuss the radiative
 transfer model used to compute the profiles in
-section~\ref{sec:radiative-transfer-model}, and the results of model
-calculations are given in section~\ref{sec:Results}.  We discuss our
+Section~\ref{sec:radiative-transfer-model}, and the results of model
+calculations are given in Section~\ref{sec:Results}.  We discuss our
 results in the context of Reipurth's classification scheme in
-section~\ref{sec:Discussion}, and our summary and conclusions are
-presented in section~\ref{sec:Conclusions}.
+Section~\ref{sec:Discussion}, and our summary and conclusions are
+presented in Section~\ref{sec:Conclusions}.
 
@@
 along the magnetic field onto the surface of the star.  In the
-following subsections we describe the details of model components.
+following subsections we describe the details of the model components.
 
@@
     axis on the equatorial plane.  The wind source
-    points ($S$), from which the stream lines diverges, are placed at
+    points ($S$), from which the stream lines diverge, are placed at
     distance $d$ above and below the star. The degree of wind
@@
 classical T~Tauri star for the central continuum source, i.e. radius
-($R_{*}$), mass ($M_{*}$), and effective temperature the photosphere
+($R_{*}$), mass ($M_{*}$), and effective temperature of the photosphere
 ($T_{\mathrm{ph}}$) are $2\, \mathrm{R_{\sun}}$, $0.5\,
@@
 
-An additional continuum source is considered for models which includes
+An additional continuum source is considered for models which include 
 magnetospheric accretion: as the infalling gas approaches the stellar
@@
 10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
-be absorbed by the gas locally, and re-emitted in optical and UV
+be absorbed by the gas locally, and re-emitted  optical and UV
 radiation (\citealt{koenigl:1991}; \citealt*{hartmann:1994}). This
@@
 The magnetic field and the gas stream lines are assumed to have the
-following simple form:
+following simple form 
 \begin{equation}
@@
 radiation and line emission from Ca~II and Mg~II ions. The results of
-\citet{martin:1996} qualitatively agree with that of
+\citet{martin:1996} qualitatively agree with those of
 \citet{hartmann:1994}.
@@
 different types of winds are produced. If the field is constrained to
-be near the co-rotation radius of stellar magnetosphere, an
+be near the co-rotation radius of the stellar magnetosphere, an
 {}``X-wind'' \citep{shu:1994} is produced. If the open field lines are
 located in a wider area of the disc, a {}``disc-wind'' similar to that
-of \citet{koenigl:2000} is produced \citep{krasnopolsky:2003}.  Recent
-reviews on the jet/wind-disc connection can be found in
-\citet{koenigl:2000} and \citet{pudritz:2005}. Clearly there are several alternative outflow scenarios. Here we adopt
-a simple kinematical model, based on the disc-wind paradigm, which broadly represents the results of
-MHD simulations,
+of \citet{koenigl:2000} is produced (see also
+\citealt{krasnopolsky:2003}).  Recent reviews on the jet/wind-disc
+connection can be found in \citet{koenigl:2000} and
+\citet{pudritz:2005}. Clearly there are several alternative outflow
+scenarios. Here we adopt a simple kinematical model, based on the
+disc-wind paradigm, which broadly represents the results of MHD
+simulations,
 
@@
 conserved along a stream line, and the poloidal velocity component
-is assumed to be simply a radial from vertically displaced {}``sources''
+is assumed to be simply a radial from {}``sources'' vertically displaced 
 from the central star.  Here we briefly describe the disc-wind model, and
@@
 originates from the disc surface, but the {}``source'' point ($S$),
-from which the stream lines diverges, are placed at distance $d$ above
+from which the stream lines diverge, are placed at distance $d$ above
 and below the centre of the star.  The angle of the mass-loss
@@
 radius of the magnetosphere ($R_{\mathrm{mo}}$) and the latter is set
-to $1$~au as in \citet{krasnopolsky:2003}.
+to $1$~au,  as in \citet{krasnopolsky:2003}.
 
@@
 equation~\ref{eq:discwind-massloss-w} is found by integrating
-$\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$, and the
+$\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$, and 
 normalising the value to the total mass-loss rate
@@
 length, and its value is set to 10~$R_{\mathrm{mi}}$ by following
-\citet{long:2002}).
+\citet{long:2002}.
 
@@
   \caption{The dependency of the disc-wind density and velocity on the wind
-    acceleration parameter $\beta$. The wind density $\rho$ (left panel)
-    and the poloidal velocity component $v_{p}$ (right panel) along the
+    acceleration parameter $\beta$. The wind density $\rho$ (right panel)
+    and the poloidal velocity component $v_{p}$ (left panel) along the
     stream line starting from the mid point of the wind launching zone,
@@
 terms set by requiring the grains to completely deplete a solar
-abundance carbon and silicon. The parameters adopted in our model are:
+abundance of carbon and silicon. The parameters adopted in our model are:
 $C_{\mathrm{C}}=1.32\times10^{-17}$,
@@
 geometrical configurations of magnetospheric inflow (see also
-\citealt*{kurosawa:2005a}). We modified the code to handle the a
+\citealt*{kurosawa:2005a}). We modified the code to handle a
 two-dimensional (2-D) density distribution, and restricted our models
@@
 where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
-neutral hydrogens and that of free electrons. Also,
+neutral hydrogen atoms and that of free electrons. Also,
 $C_{\mathrm{rad}}$, $C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are
 natural broadening, van der Waals broadening, and linear Stark
-broadening constants respectively.  We simply adopt this
+broadening constants respectively.  We adopt this
 parameterisation along with the values of broadening constants for
@@
 \citet{kurucz:1979} as described in
-section~\ref{sub:Continuum-Source}, and $I_{0}=0$ otherwise. If the
+Section~\ref{sub:Continuum-Source}, and $I_{0}=0$ otherwise. If the
 the ray intersects with the hot ring on the stellar surface created by
@@
 integration, and $n_{\nu}$ is the number of frequency points. In the
-models presented in the following section. $n_{p}=180$, $n_{q}=100$,
+models presented in the following section, $n_{p}=180$, $n_{q}=100$,
 and $n_{\nu}=101$ are used unless specified otherwise. A linearly
@@
 
-The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
+The optical depth $\tau$ in equation~\ref{eq:formal_sol_integral}
 is defined as: 
@@
 scattering opacity which are calculated using the dust property
-described in section~\ref{eq:grain-dist-function}.  We neglect the
-emissivity from the disc: since the disc mass of CTTS are rather small
+described in Section~\ref{eq:grain-dist-function}.  We neglect the
+emissivity from the disc: since the disc masses of CTTS are rather small
 ($\sim 0.01\,\mathrm{M_{\sun}}$) and low temperature ($\lesssim 
@@
     from top to bottom, and the mass accretion rate (indicated by the
-    values in $\mathrm{M_{\sun}\,yr^{-1}}$ along the top) increases from
+    values in $\mathrm{M_{\sun}\,yr^{-1}}$ along the top) decreases from
     left to right. }
@@
     computed with a damping constant ($\Gamma$), described in
-    section~\ref{sec:radiative-transfer-model} (solid), is compared with
+    Section~\ref{sec:radiative-transfer-model} (solid), is compared with
     a model with no damping, $\Gamma=0$ (dashed).  Both models are
@@
 central star and the magnetosphere, we examine the dependency of
-H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion flow
+H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of the accretion flow
 and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as
@@
 model with no damping constant ($\Gamma=0$), a significant increase of
-the line flux in both red and blue wings of seen. The weak red-shifted
+the line flux in both red and blue wings is seen. The weak red-shifted
 absorption component (which is a signature of the magnetospheric accretion)
@@
 per~cent of its peak flux (10 per~cent width) is a better
-indicator for an accretion than the EW criteria. They proposed that a
-T~Tauri star shows the 10 per~cent width greater than
+indicator for an accretion than the EW criteria. They proposed that if
+a T~Tauri star shows a 10 per~cent width greater than
 $270\,\mathrm{km\,s^{-1}}$, the star should be a CTTS. The 10 per~cent
@@
 Table~\ref{tab:ha_ten_percent_acc_models}.  Using the criteria of
-\citet{white:2003}, the half of the models shown in the figure can be
+\citet{white:2003}, half of the models shown in the figure can be
 classified as CTTS, and the other half as WTTS. However, the profiles corresponding
@@
 seen in observations (\citealt{reipurth:1996} and
-section~\ref{sub:Classification-scheme-proposed}).
+Section~\ref{sub:Classification-scheme-proposed}).
 
@@
 The line EW in Fig.~\ref{fig:acc_inclination_effect} changes from
-32\,\AA\, to 21\,\AA\, as the inclination changes from $10^\circ$ to
-$80^\circ$, i.e. the fractional change of 0.65.  On the other hand,
+32 to 21\,\AA\, as the inclination changes from $10^\circ$ to
+$80^\circ$, i.e. a fractional change of 0.65.  On the other hand,
 the 10~per~cent width of the line changes from 290~$\kmps$ to
-470~$\kmps$; hence,
-the fractional change is 1.6.  The both values are relatively
-sensitive to the inclination angle.
+470~$\kmps$; hence, the fractional change is 1.6.
 
@@
 
-In this section, we examine profiles produced using the 
+In this section, we examine profiles produced using 
 the disc wind outflow model described in
-section~\ref{sub:model-disc-wind}. 
+Section~\ref{sub:model-disc-wind}. 
 The parameters used for the
-central star are as in section~\ref{sub:Continuum-Source}, and the
+central star are as in Section~\ref{sub:Continuum-Source}, and the
 disc-wind parameters are summarised in
@@
 
-We now examine the sensitivity of the model profiles on the wind
+We now examine the sensitivity of the model profiles to the wind
 collimation or the source displacement parameter $d$. As we can see
@@
 Fig.~\ref{fig:discwind_mdot_effect}. With all other parameters fixed,
-$\dot{M}_{\mathrm{wind}}$ acts as an scaling factor for the wind
-density (equation~\ref{eq:discwind-density}). The important process
+$\dot{M}_{\mathrm{wind}}$ acts as a scaling factor for the wind
+density (equation~\ref{eq:discwind-density}). The most important process
 that populates the $n=3$ level is recombination, and therefore the
@@
 \caption{A summary of the reference disc-wind model parameters used
-in section~\ref{sub:result-discwind-knigge}. See also
-section~\ref{sub:model-disc-wind}.}
+in Section~\ref{sub:result-discwind-knigge}. See also
+Section~\ref{sub:model-disc-wind}.}
 
@@
 In order to quantify the relative contributions of the wind emission and
- the magnetosphere, we have computed the ratio the EW of the
+ the magnetosphere, we have computed the ratio of the EW of the
 hybrid model in Fig.~\ref{fig:atlas_hybrid} to the EW of the
@@
 Figures~\ref{fig:atlas_discwind_only} and
-Fig.~\ref{fig:atlas_hybrid} reveals some of problems
+Fig.~\ref{fig:atlas_hybrid} reveals some problems
 with uniqueness that must inevitably occur when trying to assign an
@@
 hand, the flux peak increase and the line wings become stronger as
-$\mu$ increases.  Although MHD models suggests
+$\mu$ increases.  Although MHD models suggest
 (e.g.~\citealt{koenigl:2000}) that $\mu \sim 0.1$, the figure suggest
-that models a relatively wide range of $\mu$ (e.g.~between 0.025 and
-0.2 in this case) reproduce the profiles similar to observations.
-
-Apparently, the type of profiles  
-(affected by the blue-shifted absorption feature) seen in this section
-cannot be explained by the magnetospheric accretion flow alone
-(e.g.~\citealt{muzerolle:2001}).  Comparison of the model profiles
-with different types of the observed H$\alpha$ profiles will be given
-in section~\ref{sub:Classification-scheme-proposed}.
+that models with a relatively wide range of $\mu$ (e.g.~between 0.05 and
+0.2 in this case) produce profiles similar to observations.
 
@@
 found that the extent of the H$\alpha$ emission region is relatively
-small i.e.~$h\sim 0.1\,\mathrm{au}$ or $10\, R_{*}$ where h is the
-vertical distance from the disc when compared to the
+small (i.e.~$h\sim 0.1\,\mathrm{au}$ or $10\, R_{*}$ where $h$ is the
+vertical distance from the disc) when compared to the
 spectro-astrometric observations of \citet{takami:2003} 
@@
 (e.g.~\citealt{shang:2002}). %
-}. The extent of the line emission region becomes slightly
-larger ($\sim0.4$~au) if a slower wind acceleration rate (e,g,~$\beta=4$)
-is used.
+}.  In our model, the wind emission flux drops by $\sim10^{4}$ by
+the time the wind reaches $h \approx 0.1\,\mathrm{au}$. The extent of the line
+emission region becomes slightly larger ($\sim0.4$~au) if a slower
+wind acceleration rate (e,g,~$\beta=4$) is used. The discrepancy with
+the observations is perhaps caused by the lack of the material
+connecting the \emph{disc wind} to a collimated \emph{jet} in our
+model, which may be excited by alternative heating mechanism
+(e.g.~shocks) thus producing observable H$\alpha$ emission at large
+distances from the central object.
 
@@
 (B and R) which depends whether the secondary peak is on the
-blue or red side of the primary peak. Readers are refereed to Fig.~4 of their paper.
+blue or red side of the primary peak. Readers are referred to Fig.~4 of their paper.
 Fig.~\ref{fig:atlas_reipurth} shows  sample model profiles
@@
 narrow range of parameter space. In fact there are no Type~III-R
-profiles in our model grid, but by 'tweaking' the magnetospheric
+profiles in our model grid, but we obtain one by `tweaking' the magnetospheric
 temperature, and using an inclination ($85^\circ$) sufficient that the
@@
 completeness, the final model parameters we used to achieve the
-profiles are: (very high inclination,
+profiles are: very high inclination,
 $T_{\mathrm{max}}\sim8300\,\mathrm{K}$, and
-$\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$).
+$\dot{M}_{\mathrm{acc}}\sim10^{-8}\,\mathrm{M_{\sun}yr^{-1}}$.
 It is interesting that the most infrequently observed profile type was
@@
 
-\caption{The summary model parameters for the profiles in
+\caption{The summary of model parameters for the profiles in
 Fig.~\ref{fig:atlas_reipurth} and brief comments. The temperatures
@@
 $1.0$&
-Wide range of wind acceleration rate.
+Wide range of wind acceleration rates.
 Mid--high inclination\tabularnewline
@@
   \caption{The dependence of the H$\alpha$ model profiles on the
-    inclination angle. The profiles computed at $i=10^{\circ}$(solid
-    line), $55^{\circ}$ (dotted line) and $80^{\circ}$ (dashed line )
+    inclination angle. The profiles computed at $i=10^{\circ}$ (solid
+    line), $55^{\circ}$ (dotted line) and $80^{\circ}$ (dashed line)
     using (1)~the disc-wind-magnetosphere hybrid model (left;
-    c.f. section~\ref{sub:result-discwind-knigge}) and (2)~the disc,
+    c.f. Section~\ref{sub:result-discwind-knigge}) and (2)~the disc,
     stellar wind, magnetosphere hybrid model (right panel;
@@
     All the other parameters are same as in
-    sections~\ref{sub:result-discwind-hybrid} and
+    Sections~\ref{sub:result-discwind-hybrid} and
     \ref{sub:result-discwind-knigge}.  }
@@
 shows the profiles computed with the disc-wind, magnetosphere hybrid
-model (section~\ref{sub:result-discwind-knigge}) at inclination angles
+model (Section~\ref{sub:result-discwind-knigge}) at inclination angles
 $i=10^{\circ}$, $55^{\circ}$ and $80^{\circ}$. The magnetospheric
@@
 the density of the disc wind increases towards the equatorial
-plane--as a result, the EW becomes smaller as the inclination angle
-increases: 41\,\AA, 27\,\AA, and 19\,\AA\, for $i=10^\circ$,
+plane -- as a result, the EW becomes smaller as the inclination angle
+increases: 41, 27, and 19\,\AA\, for $i=10^\circ$,
 $55^\circ$, and $80^\circ$ respectively.  This is a robust result, and
@@
 emissivity is highest, although further out the material becomes
-collimated into a bipolar jet this would not contribute significantly
+collimated into a bipolar jet, this would not contribute significantly
 to the line emission in our models.
@@
 assuming the constant mass-loss rate per unit area over the stellar
-surface, the mass-flux conservation, and using the beta velocity low
+surface, the mass-flux conservation, and using the beta velocity law
 above.  The schematic of the model configuration is shown in
@@
 model. The wind acceleration parameter ($\beta$) and the wind
-temperature ($T_{\mathrm{wind}}$)used here are $1.0$ and
+temperature ($T_{\mathrm{wind}}$) used here are $1.0$ and
 $9000\,\Kelvin$ respectively. All the other parameters are same as in
@@
 inclination increases as clearly seen in the figure. Specifically the
-values are 54\,\AA, 69\,\AA, and 98\,\AA\, for $i=10^\circ$,
+values are 54, 69, and 98\,\AA\, for $i=10^\circ$,
 $55^\circ$, and $80^\circ$ respectively.  This tendency of the
@@
 transfer models for classical T~Tauri stars, and detailed studies of
-the H$\alpha$ formation from their complex to circumstellar
+the H$\alpha$ formation from their complex circumstellar
 environment.  We found that the hybrid model can reproduce the wide
@@
 classified type
-(section~\ref{sub:Classification-scheme-proposed}). Using the different
+(Section~\ref{sub:Classification-scheme-proposed}). Using the different
 combinations of the inclination 
@@
 (Fig.~\ref{fig:discwind_mu_effect}) and find that models with $0.05
-<\mu<0.2$ are still be consistent with observations. Wind-only or
+<\mu<0.2$ are still consistent with observations. Wind-only or
 magnetosphere-only models may be representative of individual line
@@
 to the small sample size of their study (12 objects) to question
-the validity of the EW effect, but we have have also
+the validity of the EW effect, but we have also
 considered an alternative  model in which the disc-wind is
@@
 predict that bipolar or jet-like flows in CTTS are always accompanied by
-a disc-wind originating near the star: the real situation therefore is likely
+a disc-wind originating near the star: the actual situation therefore is likely
 to be a combination of the two flows.
@@
 
-Velocity broadened, asymmetric H$\alpha$ profiles in BDs are used as
-an indicator of ongoing magnetospheric accretion, and the same models
-that are used for CTTS are applied to these systems in order to
-determine mass-accretion rates (e.g.~\citealt{mohanty:2005}; 
-\citealt{muzerolle:2005}). The line profiles however display the same
-wide variety of morphologies as the CTTS and Herbig Ae/Be stars
-(although we note as yet no BD profile has been observed with
-red-shifted absorption).  It is natural to assume that the same
-physics applies in these low mass objects, and that a hybrid model may
-be more successful in fitting these profiles, and will give greater
-insight into the circumstellar kinematics.
+Velocity broadened, asymmetric H$\alpha$ profiles in brown dwarfs
+(BDs) are used as an indicator of ongoing magnetospheric accretion,
+and the same models that are used for CTTS are applied to these
+systems in order to determine mass-accretion rates
+(e.g.~\citealt*{lawson:2004}; \citealt{muzerolle:2005}). The line
+profiles however display the same wide variety of morphologies as the
+CTTS and Herbig Ae/Be stars (although we note as yet no BD profile has
+been observed with red-shifted absorption).  It is natural to assume
+that the same physics applies in these low mass objects, and that a
+hybrid model may be more successful in fitting these profiles, and
+will give greater insight into the circumstellar kinematics.
 
@@
 much stronger constrains. In particular it appears that the near-IR
-hydrogen lines (Pa$\beta$ and Br$\gamma$) are less-effected by
+hydrogen lines (Pa$\beta$ and Br$\gamma$) are less effected by
 outflows than H$\alpha$. One could therefore use these lines to
@@
 
-This work is supported by PPARC standard grand PPA/G/S/2001/00081
-and PPARC rolling grant xxxxx.
+This work is supported by PPARC standard grant PPA/G/S/2001/00081
+and PPARC rolling grant PP/C501609/1.
 
@@
 
-\bibitem[{{Alencar} {et~al.}(2005){Alencar}, {Basri}, {Hartmann}, \&
+\bibitem[{{Alencar} {et~al.}(2005){Alencar}, {Basri}, {Hartmann} \&
   {Calvet}}]{alencar:2005}
@@
 \bibitem[{{Anders} \& {Grevesse}(1989)}]{anders:1989}
-{Anders} E., {Grevesse} N., 1989, geochim. cosmochim. acta, 53, 197
-
-\bibitem[{{Appenzeller} {et~al.}(2005){Appenzeller}, {Bertout}, \&
+{Anders} E., {Grevesse} N., 1989, Geochim. cosmochim. Acta, 53, 197
+
+\bibitem[{{Appenzeller} {et~al.}(2005){Appenzeller}, {Bertout} \&
   {Stahl}}]{appenzeller:2005}
@@
 
-\bibitem[{{Baines} {et~al.}(2005){Baines}, {Oudmaijer}, {Porter}, \&
+\bibitem[{{Baines} {et~al.}(2005){Baines}, {Oudmaijer}, {Porter} \&
   {Pozzo}}]{baines:2006}
@@
 
-\bibitem[{{Bertout} {et~al.}(1988){Bertout}, {Basri}, \&
+\bibitem[{{Bertout} {et~al.}(1988){Bertout}, {Basri} \&
   {Bouvier}}]{bertout:1988}
@@
   {Ballester}, {Clarke}, {Crisp}, {Gallagher}, {Griffiths}, {Hester},
-  {Hoessel}, {Holtzman}, {Mould}, {Scowen}, {Trauger}, \&
+  {Hoessel}, {Holtzman}, {Mould}, {Scowen}, {Trauger} \&
   {Westphal}}]{burrows:1996}
@@
 
-\bibitem[{{Castor} {et~al.}(1975){Castor}, {Abbott}, \& {Klein}}]{castor:1975}
+\bibitem[{{Castor} {et~al.}(1975){Castor}, {Abbott} \& {Klein}}]{castor:1975}
 {Castor} J.~I., {Abbott} D.~C., {Klein} R.~I., 1975, \apj, 195, 157
@@
 
-\bibitem[{{Drew} {et~al.}(1998){Drew}, {Proga}, \& {Stone}}]{drew:1998}
+\bibitem[{{Drew} {et~al.}(1998){Drew}, {Proga} \& {Stone}}]{drew:1998}
 {Drew} J.~E., {Proga} D., {Stone} J.~M., 1998, \mnras, 296, L6
@@
 \bibitem[{{Edwards} {et~al.}(1987){Edwards}, {Cabrit}, {Strom}, {Heyer},
-  {Strom}, \& {Anderson}}]{edwards:1987}
+  {Strom} \& {Anderson}}]{edwards:1987}
 {Edwards} S., {Cabrit} S., {Strom} S.~E., {Heyer} I., {Strom} K.~M., {Anderson}
@@
 
-\bibitem[{{Edwards} {et~al.}(1994){Edwards}, {Hartigan}, {Ghandour}, \&
+\bibitem[{{Edwards} {et~al.}(1994){Edwards}, {Hartigan}, {Ghandour} \&
   {Andrulis}}]{edwards:1994}
@@
 
-\bibitem[{{Frank} {et~al.}(2002){Frank}, {King}, \& {Raine}}]{frank:2002}
+\bibitem[{{Frank} {et~al.}(2002){Frank}, {King} \& {Raine}}]{frank:2002}
 {Frank} J., {King} A., {Raine} D.~J., 2002, {Accretion Power in Astrophysics,
@@
 
-\bibitem[{{Ghosh} {et~al.}(1977){Ghosh}, {Pethick}, \& {Lamb}}]{ghosh:1977}
+\bibitem[{{Ghosh} {et~al.}(1977){Ghosh}, {Pethick} \& {Lamb}}]{ghosh:1977}
 {Ghosh} P., {Pethick} C.~J., {Lamb} F.~K., 1977, \apj, 217, 578
@@
 
-\bibitem[{{Gullbring} {et~al.}(1998){Gullbring}, {Hartmann}, {Briceno}, \&
+\bibitem[{{Gullbring} {et~al.}(1998){Gullbring}, {Hartmann}, {Briceno} \&
   {Calvet}}]{gullbring:1998}
@@
 
-\bibitem[{{Hartigan} {et~al.}(1995){Hartigan}, {Edwards}, \&
+\bibitem[{{Hartigan} {et~al.}(1995){Hartigan}, {Edwards} \&
   {Ghandour}}]{hartigan:1995}
@@
 
-\bibitem[{{Hartmann} {et~al.}(1982){Hartmann}, {Avrett}, \&
+\bibitem[{{Hartmann} {et~al.}(1982){Hartmann}, {Avrett} \&
   {Edwards}}]{hartmann:1982}
@@
 
-\bibitem[{{Hartmann} {et~al.}(1994){Hartmann}, {Hewett}, \&
+\bibitem[{{Hartmann} {et~al.}(1994){Hartmann}, {Hewett} \&
   {Calvet}}]{hartmann:1994}
@@
 {Herbig} G.~H., {Bell} K.~R., 1988, {Catalog of emission line stars of the
-  orion population}, Vol.~3. Lick Observatory Bulletin, Santa Cruz: Lick
+  Orion population}, Vol.~3. Lick Observatory Bulletin, Santa Cruz: Lick
   Observatory
@@
 
-\bibitem[{{Johns-Krull} {et~al.}(1999){Johns-Krull}, {Valenti}, {Hatzes}, \&
+\bibitem[{{Johns-Krull} {et~al.}(1999){Johns-Krull}, {Valenti}, {Hatzes} \&
   {Kanaan}}]{johns-krull:1999}
@@
 
-\bibitem[{{Kim} {et~al.}(1994){Kim}, {Martin}, \& {Hendry}}]{kim:1994}
+\bibitem[{{Kim} {et~al.}(1994){Kim}, {Martin} \& {Hendry}}]{kim:1994}
 {Kim} S., {Martin} P.~G., {Hendry} P.~D., 1994, \apj, 422, 164
@@
 
-\bibitem[{{Knigge} {et~al.}(1995){Knigge}, {Woods}, \& {Drew}}]{knigge:1995}
+\bibitem[{{Knigge} {et~al.}(1995){Knigge}, {Woods} \& {Drew}}]{knigge:1995}
 {Knigge} C., {Woods} J.~A., {Drew} E., 1995, \mnras, 273, 225
@@
 
-\bibitem[{{Krasnopolsky} {et~al.}(2003){Krasnopolsky}, {Li}, \&
+\bibitem[{{Krasnopolsky} {et~al.}(2003){Krasnopolsky}, {Li} \&
   {Blandford}}]{krasnopolsky:2003}
@@
 
-\bibitem[{{Kurosawa} {et~al.}(2004){Kurosawa}, {Harries}, {Bate}, \&
+\bibitem[{{Kurosawa} {et~al.}(2004){Kurosawa}, {Harries}, {Bate} \&
   {Symington}}]{kurosawa:2004a}
@@
 
-\bibitem[{{Kurosawa} {et~al.}(2005){Kurosawa}, {Harries}, \&
+\bibitem[{{Kurosawa} {et~al.}(2005){Kurosawa}, {Harries} \&
   {Symington}}]{kurosawa:2005a}
@@
 
+\bibitem[{{Lawson} {et~al.}(2004){Lawson}, {Lyo} \& {Muzerolle}}]{lawson:2004}
+{Lawson} W.~A., {Lyo} A.-R., {Muzerolle} J., 2004, \mnras, 351, L39
+
 \bibitem[{{Long} \& {Knigge}(2002)}]{long:2002}
@@
 
-\bibitem[{{Mathis} {et~al.}(1977){Mathis}, {Rumpl}, \&
+\bibitem[{{Mathis} {et~al.}(1977){Mathis}, {Rumpl} \&
   {Nordsieck}}]{mathis:1977}
@@
   San Francisco
-
-\bibitem[{{Mohanty} {et~al.}(2005){Mohanty}, {Jayawardhana}, \&
-  {Basri}}]{mohanty:2005}
-{Mohanty} S., {Jayawardhana} R., {Basri} G., 2005, Memorie della Societa
-  Astronomica Italiana, 76, 303
 
@@
   {Swain}, {Thompson}, {Vasisht}, {Wizinowich}, {Beichman}, {Beletic},
-  {Creech-Eakman}, {Koresko}, {Sargent}, {Shao}, \& {van Belle}}]{monnier:2005}
+  {Creech-Eakman}, {Koresko}, {Sargent}, {Shao} \& {van Belle}}]{monnier:2005}
 {Monnier} J.~D. et al., 2005, \apj, 624, 832
 
-\bibitem[{{Muzerolle} {et~al.}(2001){Muzerolle}, {Calvet}, \&
+\bibitem[{{Muzerolle} {et~al.}(2001){Muzerolle}, {Calvet} \&
   {Hartmann}}]{muzerolle:2001}
@@
 \bibitem[{{Muzerolle} {et~al.}(2005){Muzerolle}, {Luhman}, {Brice{\~n}o},
-  {Hartmann}, \& {Calvet}}]{muzerolle:2005}
+  {Hartmann} \& {Calvet}}]{muzerolle:2005}
 {Muzerolle} J., {Luhman} K.~L., {Brice{\~n}o} C., {Hartmann} L., {Calvet} N.,
@@
 
-\bibitem[{{Ray} {et~al.}(1996){Ray}, {Mundt}, {Dyson}, {Falle}, \&
+\bibitem[{{Ray} {et~al.}(1996){Ray}, {Mundt}, {Dyson}, {Falle} \&
   {Raga}}]{ray:1996}
@@
 
-\bibitem[{{Reipurth} {et~al.}(1996){Reipurth}, {Pedrosa}, \&
+\bibitem[{{Reipurth} {et~al.}(1996){Reipurth}, {Pedrosa} \&
   {Lago}}]{reipurth:1996}
@@
 
-\bibitem[{{Shang} {et~al.}(2002){Shang}, {Glassgold}, {Shu}, \&
+\bibitem[{{Shang} {et~al.}(2002){Shang}, {Glassgold}, {Shu} \&
   {Lizano}}]{shang:2002}
@@
 
-\bibitem[{{Symington} {et~al.}(2005{\natexlab{a}}){Symington}, {Harries}, \&
+\bibitem[{{Symington} {et~al.}(2005{\natexlab{a}}){Symington}, {Harries} \&
   {Kurosawa}}]{symington:2005}
@@
 \bibitem[{{Symington} {et~al.}(2005{\natexlab{b}}){Symington}, {Harries},
-  {Kurosawa}, \& {Naylor}}]{symington:2005b}
+  {Kurosawa} \& {Naylor}}]{symington:2005b}
 {Symington} N.~H., {Harries} T.~J., {Kurosawa} R., {Naylor} T.,
@@
 
-\bibitem[{{Takami} {et~al.}(2003){Takami}, {Bailey}, \&
+\bibitem[{{Takami} {et~al.}(2003){Takami}, {Bailey} \&
   {Chrysostomou}}]{takami:2003}
@@
 \bibitem[{{Ustyugova} {et~al.}(1995){Ustyugova}, {Koldoba}, {Romanova},
-  {Chechetkin}, \& {Lovelace}}]{ustyugova:1995}
+  {Chechetkin} \& {Lovelace}}]{ustyugova:1995}
 {Ustyugova} G.~V., {Koldoba} A.~V., {Romanova} M.~M., {Chechetkin} V.~M.,
@@
 
-\bibitem[{{Vernazza} {et~al.}(1973){Vernazza}, {Avrett}, \&
+\bibitem[{{Vernazza} {et~al.}(1973){Vernazza}, {Avrett} \&
   {Loeser}}]{vernazza:1973}
@@
 \bibitem[{{Vink} {et~al.}(2005{\natexlab{a}}){Vink}, {Drew}, {Harries},
-  {Oudmaijer}, \& {Unruh}}]{vink:2005}
+  {Oudmaijer} \& {Unruh}}]{vink:2005}
 {Vink} J.~S., {Drew} J.~E., {Harries} T.~J., {Oudmaijer} R.~D., {Unruh} Y.,
@@
 
-\bibitem[{{Vink} {et~al.}(2005{\natexlab{b}}){Vink}, {Harries}, \&
+\bibitem[{{Vink} {et~al.}(2005{\natexlab{b}}){Vink}, {Harries} \&
   {Drew}}]{vink:2005a}
@@
 
-\bibitem[{{Whitney} {et~al.}(2003){Whitney}, {Wood}, {Bjorkman}, \&
+\bibitem[{{Whitney} {et~al.}(2003){Whitney}, {Wood}, {Bjorkman} \&
   {Wolff}}]{whitney:2003a}
@@
 
-\bibitem[{{Wood} {et~al.}(2002){Wood}, {Wolff}, {Bjorkman}, \&
+\bibitem[{{Wood} {et~al.}(2002){Wood}, {Wolff}, {Bjorkman} \&
   {Whitney}}]{wood:2002}
@@
 Here we present our H$\alpha$ model line profile grid 
-computed using disc-wind-magnetosphere hybrid model
-(section~\ref{sub:result-discwind-hybrid}).  All
+computed using the disc-wind-magnetosphere hybrid model
+ in Section~\ref{sub:result-discwind-hybrid}.  All
 the models use the reference parameters for the 
@@
 Table~\ref{tab:std_parameters} in the main text. The ratio ($\mu$) of the
-mass-loss rate to mass-accretion rate is fixed to 0.1 for the all 
+mass-loss rate to mass-accretion rate is fixed to 0.1 for  all the 
 models. Three sets of model profiles, each with a different
@@
 (2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas02}), and
-(3) $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$
+(3) $\dot{M}_{\mathrm{acc}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$
 (Fig.~\ref{fig:atlas02}).   The temperature of the magnetosphere
-used for (1), (2) and (3) are $7500\Kelvin$, $8500\Kelvin$ and
-$9500\Kelvin$ respectively. The profiles are presented for the
+used for (1), (2) and (3) are $7500\,\Kelvin$, $8500\,\Kelvin$ and
+$9500\,\Kelvin$ respectively. The profiles are presented for the
 inclination angles of $10^\circ$, $55^\circ$, and $80^\circ$. 
 The disc-wind geometry used to compute these profiles are same as in
-section~\ref{sub:result-discwind-hybrid}.
+Section~\ref{sub:result-discwind-hybrid}. These profiles are available
+electrically at \url{http://www.astro.ex.ac.uk/people/rk/profiles}.
 
@@
   \caption{As for Fig.~\ref{fig:atlas01} except
-    $\dot{M_{\mathrm{acc}}} =10^{-9}\,\mathrm{M_{\sun}\,yr{-1}}$ and
-  $\dot{M_{\mathrm{wind}}}=10^{-10}\,\mathrm{M_{\sun}\,yr{-1}}$. }
+    $\dot{M}_{\mathrm{acc}} =10^{-9}\,\mathrm{M_{\sun}\,yr{-1}}$ and
+  $\dot{M}_{\mathrm{wind}}=10^{-10}\,\mathrm{M_{\sun}\,yr{-1}}$. }
 

### 2006-02-02 TTau_Halpha/submit/kurosawa.tex
Right after the submission.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@653 25464f21-6099-402c-b30a-640f1d40d38b

@@
 direction was made by \citet{alencar:2005} who demonstrated that the
-observed H$\alpha$, H$\beta$ and Na~D lines of RW Aur are better
+observed H$\alpha$, H$\beta$ and Na~D lines of RW~Aur are better
 reproduced by the radiative transfer model which included a collimated
@@
 Assuming mass-flux conservation and using the velocity field defined
-above, the disc wind density as a function of $w$ and $l$ can be
+above, the disc wind density as a function of $w_{i}$ and $l$ can be
 written as
@@
     respectively. As the inclination becomes larger, the peak flux and the
-    equivalent width of the line becomes smaller.  }
+    equivalent width of the line become smaller.  }
 
@@
 $\beta$ increases (Fig.~\ref{fig:discwind_vr_rho}); hence, the
-emissivity of increases. Most of the profiles show a red-ward asymmetry, mainly
+emissivity increases. Most of the profiles show a red-ward asymmetry, mainly
 due to the presence of the classical P-Cygni absorption. However we find
@@
 results in an H$\alpha$ profile that is far too strong to be
-compatible with observations (\citealt{reipurth:1996} and
+compatible with observations (\citealt{reipurth:1996}; 
 \citealt{alencar:2000}); however, the lower mass-loss rate models
 (while keeping $\mu$ constant) produce profiles with the line
-strengths comparable to observations (c.f.~appendix~\ref{sec:appendix}).
+strengths comparable to observations (c.f.~Appendix~\ref{sec:appendix}).
 Although the models in Fig.~\ref{fig:atlas_hybrid} are computed with
@@
 emission region becomes slightly larger ($\sim0.4$~au) if a slower
-wind acceleration rate (e,g,~$\beta=4$) is used. The discrepancy with
-the observations is perhaps caused by the lack of the material
-connecting the \emph{disc wind} to a collimated \emph{jet} in our
-model, which may be excited by alternative heating mechanism
-(e.g.~shocks) thus producing observable H$\alpha$ emission at large
-distances from the central object.
+wind acceleration rate (e,g,~$\beta=4$) is used. The discrepancy
+between the observations and the model is perhaps caused by the lack
+of the material connecting the \emph{disc wind} to a collimated
+\emph{jet} in our model, which may be excited by alternative heating
+mechanism (e.g.~shocks) thus producing observable H$\alpha$ emission
+at large distances from the central object.
 
@@
 context of our models parameters. Readers are referred to
-appendix~\ref{sec:appendix} for the complete model profiles used in 
+Appendix~\ref{sec:appendix} for the complete model profiles used in 
 this discussion.
@@
   model with $\dot{M}_{\mathrm{acc}}
-  =10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$ and
-  $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr{-1}}$.
+  =10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ and
+  $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr^{-1}}$.
   Profiles are presented for inclinations of $10^\circ$ (top figure),
@@
   \caption{As for Fig.~\ref{fig:atlas01} except
-  $\dot{M}_{\mathrm{acc}} =10^{-8}\,\mathrm{M_{\sun}\,yr{-1}}$ and
-  $\dot{M}_{\mathrm{wind}}=10^{-7}\,\mathrm{M_{\sun}\,yr{-1}}$. }
+  $\dot{M}_{\mathrm{acc}} =10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and
+  $\dot{M}_{\mathrm{wind}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$. }
 
@@
   \caption{As for Fig.~\ref{fig:atlas01} except
-    $\dot{M}_{\mathrm{acc}} =10^{-9}\,\mathrm{M_{\sun}\,yr{-1}}$ and
-  $\dot{M}_{\mathrm{wind}}=10^{-10}\,\mathrm{M_{\sun}\,yr{-1}}$. }
+    $\dot{M}_{\mathrm{acc}} =10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$ and
+  $\dot{M}_{\mathrm{wind}}=10^{-10}\,\mathrm{M_{\sun}\,yr^{-1}}$. }
 

### 2006-04-05 TTau_Halpha/revision01/response_to_ref.txt
Revised version after the refree's report
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@693 25464f21-6099-402c-b30a-640f1d40d38b

Dear Referee,

Thank you very much for reviewing our paper, and for doing so in
timely mannar.  We have reviewed our paper by considering your
comments and suggestions very carefully.  
The answers to your questions follows "*" marks before 
the indented texts below.

Kind regards,

Ryuichi Kurosawa, Tim Harries and Neil Symington

===================================================================
General comments

Introduction, 3rd paragraph: The blue-ward asymmetric emission is
generated in magnetospheric accretion models not only by the
occultation of the flow by the stellar photosphere, which occults
mostly high velocity blue-shifted material, but also by the
occultation of part of the receding flow by the inner disk, which
occults mostly low velocity redshifted emission. Both effects (lack of
low velocity red-shifted emission and lack of high velocity
blue-shifted emission) contribute to generate the blue-ward asymmetry.

   * Thank you for point that out. I replaced the sentence 
     from 
	  "... blue-ward asymmetric emission line 
	    profiles as resulting from the partial occultation 
	    of the flow by the stellar photosphere, .... 
     to

	  "... blue-ward asymmetric emission line 
	    profiles as resulting from the partial occultation 
	    of the flow by the inner part of the accretion disc and by
	    the stellar photosphere, .... "

Section 2.1, 1st paragraph: The adopted parameters of a typical
classical T Tauri star are listed in Table 1. I think that a mass
accretion rate of 10^-8 Msun/yr is much more representative of a
typical CTTS than 10^-7 Msun/yr. The values you adopted as typical for
both Macc and Mwind rates are actually quite high compared to what is
usually measured (see for ex. Gullbring et al. 1998). It is true that
some CTTSs present such high Macc and Mwind rate values, but these are
only a few. This is just a comment and does not invalidate your
results since you ended up calculating profiles for Macc = 10^-7,
10^-8 and 10^-9 Msun/yr, which clearly encompasses the whole range of
measured Macc rates in CTTSs.

    * I agree. A typical value of mass-accretion rate is ~3x10^-8
      Msun/yr according to Gullbring et al. (1998) and  Calvet et al. (2004).
      A slightly higher mass-accretion was used so that the line 
      broadening can be seen more clearly, and because 
      10^-7 is a nice round number. I clarify this point in caption of
      Table 1.

Section 2.1, 2nd paragraph: A better reference to the accretion schock
characteristics would be Calvet & Gullbring (1998) ApJ 509, 802 and
Gullbring et al. (2000) ApJ 544, 927, instead of Konigl (1991) and
Hartmann et al. (1994).

     * I replaced the references as you suggested.

In this paragraph you obtain about 8% of the stellar surface covered
by hot rings. This is quite a large value compared with the values
obtained by Gullbring & Calvet in the papers cited above, which range
rather from 0.1% to 1% for several CTTSs. But this could be due to the
fact that you are using a large Macc rate (10^-7 Msun/yr) for a
CTTS. Does this affect your results ? Was the hot ring surface
coverage recalculated consistently when you computed models with 10^-8
Msun/yr and 10^-9 Msun/yr ? In that case, what values were used ?

   * The surface "area" covered by the hot rings depends only on 
     the geometry of the magnetosphere (Rmi and Rmo); however, 
     the total accretion luminosity (L_acc) depends on the
     mass-accretion rate (Macc).
     The surface intensity of the hot rings is computed according to 
     this total luminosity due to accretion and by assuming they
     radiates as a blackbody.

     If a smaller hot ring surface was adopted, the ring temperature
     will increase in order to have a fixed L_acc for a given amount
     of mass-accretion rate.  So, yes, we calculate the amount of
     total "flux" according to a mass-accretion rate, but the surface
     coverage does not change.

     In our model, the hot ring simply acts
     as a source of additional continuum source, but the total amount
     of the additional continuum flux from the hot ring does not
     change.  This means that the level population does not change;
     hence, the H-alpha line strength is not affected by the change in
     the area coverage of the rings provided that the change is not so
     big. If the area coverage is much bigger (e.g. 30%), then the
     geometry of the magnetosphere itself changes significantly.  This
     would result in the line strength slightly for a fixed
     inclination angle, but overall shape of the profile would not
     change so much. For example, we used Rmi=2.2R* and Rmo = 3.0R*
     (Small and Wide (SW) model of Muzerolle et al 2001) which results
     in 8% hot ring coverage. If we were to use Rmi=2.2R* and Rmi =
     2.8R* and Rmo=3.0* (Small and narrow (SN) model of Muzerolle et
     al 2001), then the coverage would be 1% of the total surface,
     which is more similar to the fraction estimated in Gullring et al
     (2000).  If we look at the model comparison of Muzerolle et al
     (2001) (see their Fig. 5), the line strength changes, but the
     line profiles shape do not change much (except for the 10^3 K
     model). We confirmed, by running additional models, the line
     shapes do not change significantly for H-alpha by changing from
     SW to SN model.

     To make it clear about this point, I have inserted the following
     texts near the end of the 2nd paragraph in  Section 2.1:

        "In our model, the fraction of hot-ring coverage area is
        determined only by the geometry of the magnetosphere (Section
        2.2). Gullring et al (2000) estimated the fractions of the
        hot-ring coverage area for three intermediate CTTS by using
        the observed UV and optical spectra. They found the range of
        fraction to be 0.3--3.0~per~cent.  This is smaller than the
        value adopted here; however, even if we use 1~per~cent
        hot-ring area coverage model (by changing the width of the
        magnetosphere), we find the line shapes of H$\alpha$ do not
        change significantly. "

     Also I added the following sentence, just before the last
     sentence in Section 2.1:

        "The luminosity ratio and the temperature depend on a adopted
         mass-accretion rate."

Sect. 2.2, 3rd paragraph: You say that the results of Martin (1996)
qualitatively agree with those of Hartmann et al (1994). There is a
comment about that in the Muzerolle et al (1998) (ApJ 492, 743) paper
on page 751, where they also use the Hartmann et al (1994) law. They
say that the Martin (1996) temperature distribution is inadequate to
obtain line emission consistent with the observations, even at Halpha,
while their temperature distribution generates profiles that look like
the observed ones. So I think that you should not say that both
temperatures agree, even qualitatively.  It gives the idea that they
generate the same types of profiles, which is not true. The fact that
they do not agree is actually a big problem, since the Hartmann et
al. (1994) temperature structure, which is somewhat arbitrary,
reproduces the observed profiles, while the Martin (1996) temperature
structure, which was calculated consistently, does not. We are missing
some physics in there.

   * Thank you for reminding me this point. 
     I removed the sentence, "The results of Martin(1996)
     qualitatively agree with those of Hartmann et al. (1994)" from the
     text, and added the following at end of the paragraph to reflect
     your comments.

        "Although the model of Martin (1996) seems to be more
         comprehensive than that of Hartmann et al. (1994), Muzerolle
         et al (1998) found that the line profile models computed
         according to the temperature structure of the former do not
         agree with observations while they do have much better
         agreement when the temperature of the latter model was used. 
	 The temperature structure of the magnetosphere is still a big
         uncertainty in the accretion model; however, for a
         heuristic reason, we adopted the model of Hartmann et
         al. (1994). "

Sect. 2.3, 4th paragraph: I could not follow you in the end of the
paragraph. You have p=4*alpha*q and q = -1.15 from Whitney et
al. (2003). You say that in order to be consistent with Krasnopolsky
et al. (2003) who used p = -5/2, the value of alpha was set to
0.76. Well, alpha=p/(4*q)=-2.5/(4*(-1.15))=0.54 and not 0.76.

   * You are absolutely correct. This is my mistake.
     It should be p=-7/2 which is the value used in the models.  
     With p=-7/2,  
         alpha=p/(4*q)=-3.5/(4*(-1.15)) = 0.76.

	 ==> Corrected.

Sect. 4.1, 1st paragraph Tmax is not defined. I know it is the maximum
temperature of the accretion flow, but you must define it.

   * I added the following sentences after the first sentence of the
     same paragraph:
       "The temperature structure of Hartmann et al. (1994, ApJ, 426,
	669) is  adopted here, and the parameter Tmax sets
	the maximum temperature of the accretion streams. "

Sect. 4.1, 5th paragraph You say the EWs decrease as the inclination
increases mainly because the fraction of the accretion stream blocked
by the photosphere increases. I agree that the fraction of the
accretion stream blocked by the photosphere increases a lot as the
inclination increases (in Fig. 1, lower left funnel portion or z<0 and
x<0 for an observer looking from the upper right corner), but the
fraction blocked by the inner disk (at z<0 and x>0 in Fig. 1) also
increases a lot and contributes to the decrease in the EWs. The
photosphere mostly blocks blue-shifted material, while the inner disk
mostly blocks redshifted material.

   * You are absolutely right. I changed the sentence as you pointed
     out.

     ORIGINAL 
       "The line flux and the EWs decrease mainly because the fraction
        of the accretion stream blocked by the photosphere increases
        as the inclination increases."

     REVISED
       "The line flux and the EWs decrease mainly because (1) the
        fraction of the accretion stream blocked by the photosphere
        increases as the inclination increases (c.f. Fig. 1,
        lower-left part of the accretion stream i.e.  z<0 and x<0),
        and (2) the fraction of the accretion stream blocked by the
        inner part of the accretion disc increases as the inclination
        increases (c.f. Fig. 1, lower-right part of accretion stream
        i.e. z<0 and x>0). While the photosphere mostly blocks the
        blue-shifted part of the stream, the inner disc blocks the
        red-shifted part."

Sect. 4.1, 6th paragraph I don't understand why the highest
red-shifted line-of-sight velocity is visible only at the high
inclination angles. Looking at Figure 1, at low inclinations (even at
i=0) we actually see all the highest red-shifted material of the upper
right funnel portion (z>0, x>0, for an observer looking from the upper
right corner). Actually, looking at the profiles in Fig. 5, I don't
see much of a change in the redshifted wing width (for example at v >
120 km/s) with the increase in inclination. The blue-shifted wing
changes more.

   * Sorry. I meant to say "the blue-shifted" line-of-sight velocity
     instead of the red-shifted ...  As you mentioned the difference
     in the red wing is very small, but the difference in the blue
     wing is small but visible. By reflecting these points, I have
     made the correction as follows:

       ORIGINAL
       "..., the highest red-shifted line-of-sight velocity is visible
        only at the high inclination angles. This explains the wider
        appearance of the profile with i=80 deg. compared to the
        relatively narrow line appearance of the profile with
        i=10 deg."

       REVISED 
       "..., the highest blue-shifted line-of-sight velocity is seen
        only at the high inclination angles. For example, the
        accretion stream close to the photosphere (~1 R*) above the
        photosphere)on the upper-left quadrant in Fig.1 (x<0 and z>0)
        will be more aligned with the line-of-sight of an observer in
        the upper-right quadrant in the same figure (x>0 and z>0) as
        the inclination increases.  This results in a slight increase
        in the blue wing flux for a higher inclination model as seen
        in Fig. 5."

   * In addition to this correction, the last sentence in this
     paragraph (Sect. 4.1, 6th paragraph),

     "A similar EW dependence on
      inclination angle is found for the models with different 
      magnetospheric temperatures and the mass-accretion rates."

      was moved to the end of the previous paragraph (Sect. 4.1, 6th
      paragraph) because it was out of place.

Sect. 4.2, end of 2nd paragraph: You comment that the blue edge of the
absorption component in the slowest wind acceleration model (beta=4.0)
is located close to line centre (~20 km/s). But you don't show
beta=4.0 models. Was that a mistake and you intended to say beta=2.0 ?
I think you should cite the blue edge absorption component velocity of
the fastest model shown in Fig.6, which is beta=2.0. It is easier for
the reader to be able to check in the figure what you are explaining
in the text, and you make your point in the same way.

   * You are right again. I meant to say beta=2.0 instead of
     beta=4.0.  ==> Corrected.

Sect. 4.2, Table 4: Were does the value of p= -3/2 come from ? In
Section 2.3 you said you would be consistent with the model of
Krasnopolsky (2003) who used p= -5/2.

   * It should be p= -7/2.  
     A similar correction was made in Section 2.3 as you also pointed out.
     Sorry for the careless mistakes.
     ==> Corrected.

Sect. 4.2, 4th paragraph: The opening angle is measured from the
symmetry axis (z), then it should be given by theta_open=arctan(Rwi/d)
instead of theta_open=arctan(d/Rwi). High values of d correspond to
more collimated winds and therefore to smaller opening angles.

   * My mistake again. It should have written as
     theta_open=arctan(Rwi/d). 
     ==> Corrected.

Sect. 4.2, end of 4th paragraph: You say that you used d=44 Rstar for
the disc wind models presented in the paper but Table 4 has d= 22
Rstar listed. Which one is correct ? If Table 4 is a summary of the
reference disc wind models used in Section 4.2, maybe you should not
list d=22 Rstar, since you actually varied d in that section. Either
you put the range of values used (from 2 Rstar to 88 Rstar, as in
Fig. 7) or you don't put any value for d in Table 4.

   * This is my mistake again. I got confused between R* and Rsun.
     The largest displacement (d) model is "d=22R*." 
     d=44R* and d=88R*
     should be replaced with d = 22R*. "d=22R*" is the value used in 
     the models shown in Figure 6.
     ==> The values are corrected in the text and in the caption of
     Figure 7.

   * Deleted the entry for d from Table 4 as suggested.

Sect. 4.2: A general comment on the wind models presented in this
section. Blandford & Payne (1982) showed that in order to launch a
wind magneto centrifugally, the poloidal component of the magnetic
field must make an angle of less than 60 degrees with the disk
surface. In order for that to be achieved in your model, you must have
(supposing a flat disc, which should be reasonable for the inner disk
regions):

d < Rw*tg(theta), where theta = 90 - theta_open = 60 degrees is the
angle between the field line and the disk surface (x axis).

This means that for Rw = Rwi = 3 Rstar, you must have d < 5.2 Rstar
and that for Rw = 1 au ~ 100 Rstar, you must have d < 173 Rstar

The last condition is clearly satisfied in all your models, since d is
always less than 173 Rstar. But the inner field lines, passing close
to Rwi, do not satisfy the Blandford & Payne (1982) condition, since
for that you would need to have d < 5.2 Rstar in all cases.

In other words, if you fixed d = 44 Rstar in the disc wind models
presented in the paper, as you say you did in the 4th paragraph of
Sect. 4.2, for the wind to be launched centrifugally according to
Blandford & Payne, the field lines must present Rw > d/tan(60), which
is Rw > 25.4 Rstar. This means that field lines from Rwi = 3 Rstar to
Rw = 25 Rstar will not be able to launch a wind magneto-centrifugally
with d=44 Rstar.

How do you launch the wind in the inner field line region ? If you
cannot launch a wind in that region, how does it affect your results ?

   * I noticed the launching angle (measured from disc plane)
     condition of Blandford & Payne (1982) is not satisfied in the
     inner region of our simple disc wind model.  This is was done so
     that wind has a moderate amount of collimation. Since the stream
     line is straight, the wind will never bend toward the symmetry
     axis (z-axis) as the distance from the disc increases unlike the
     model of Blandford & Payne (1982). We therefore used a larger
     launching angle to simulate the stream lines in the far field (at
     a larger distance from the disc plane) in their model.  This is
     an intrinsic problem with approximating the stream lines with
     straight lines. A better model is perhaps to compute the field
     lines using Blandford & Payne (1982) model as done in
     e.g. Alencar et al (2005, A&A, 440, 595).  Also, in our mode, if
     the launching angle is too small (<60 deg.), the wind absorption
     feature would not been seen for profiles computed with i<60
     deg. since the wind stream line is straight and little material
     is present in the line-of-sight to an observer in this case.
     Since more than 50% of observed H-alpha profiles (e.g. Reipurth
     1996, A&AS, 120, 229 and Alencar & Basri 2000, ApJ 119, 1881) are
     affected by wind absorption, it was necessary for our model to
     used the launching angle (at the inner most part) greater than 60
     degrees to be more consistent with observation.

     If the launching angle (measured from the disc plane) is 60 deg. at
     the inner most part of the  wind, and the inclination angle
     (measured from the symmetry  axis, z-axis) is less than 60 deg., little
     absorption is expected, as demonstrated in Fig. 7.
     The situation will however change if the
     field/stream line is not straight and bending towards the
     symmetry axis as the wind travel higher above the disc.

     In summary, this was necessary compromise in order (1) to be more
     consistent with observation, and (2) to simulate more
     "colliminated" wind (toward the symmetry axis).

     To answer your question how it would effect our results, I run
     additional models with d=5Rstar which satisfies the wind
     launching condition of Blandford & Payne (1982) in all disc wind
     zone in our model.  These models showed that the wind absorption
     and emission features weakens,  but overall morphology dependence
     of the profiles on the wind temperature and the wind acceleration rate
     is very similar to what we found in the models shown in Figs. 6
     and 9.  Hence, the major conclusions obtained by using the wind
     models with a larger launching angle (at the very inner part of
     the disc) presented in this paper would not differ from the
     conclusions obtained from the disc wind models with d=5Rstar.

     To clarify the points you raised above, I have inserted the
     following in text (mostly the same as mentioned above).

     After the 4th paragraph in Section 4.3, the following new
     paragraphs are inserted:

       "Blandford & Payne (1982) showed that in order to launch a wind
        from a disc plane magneto-centrifugally, the launching angle
        (theta_L, measured from the equatorial disc plane) must be
        less than 60 degrees. In our models, the wind launching zone
        is restricted in between Rwi < wi < Rwo (see Fig. 1 and Table
        1) with Rwi = 3 Rstar and Rwo=1 au.  This sets the upper limit
        of the source displacement distance (d) to be around 5.2 Rstar
        if we want to satisfy the launching angle condition of
        Blandford & Payne (1982) for all the stream lines in our disc
        wind model.  In the models presented in Fig. 6 (and later in
        Fig. 9 in next section), we have adopted d =22 Rstar
        instead. This means that some part of the disc wind (3Rstar <
        wi < 25.4 Rstar) may not be able to be launched from the disc
        plane according to the model of Blandford & Payne (1982).

	We have used a larger launching angle or a larger source
	displacement distance for the following two reasons: (1) to
	simulate more 'colliminated' wind (toward the symmetry axis,
	and (2) to be more consistent with the fraction of H-alpha
	profiles affected by wind absorptions in observations.

      	Since the stream lines in our simple disc wind are represented
	by straight lines, the wind never bends toward the symmetry
	axis (z-axis) as the distance from the disc increases unlike
	the model of Blandford & Payne (1982). We therefore used a
	larger launching angle to simulate the stream lines in the far
	field (at a larger distance from the disc plane) in their
	model.  This is an intrinsic problem with approximating the
	stream lines with straight lines. A better model is perhaps to
	compute the field lines using Blandford & Payne (1982) model
	as done so in Alencar et al (2005, A&A, 440, 595).  Also, in
	our mode, if the launching angle is too small (<60 deg.), the
	wind absorption feature would be not been seen or would be
	very small for profiles computed with i<60 deg.  If the
	launching angle is 60 deg. at the inner most part of the wind,
	and the inclination angle (measured from the symmetry axis,
	z-axis) is less than 60 deg., little (wind) absorption is
	expected, as demonstrated in Figure 7.  The situation will
	however changes if the field/stream line is not straight and
	bending towards the symmetry axis as the wind travel higher
	above the disc.  Since more than 50 per cent of observed
	H-alpha profiles (e.g. Reipurth 1996, A&AS, 120, 229 and
	Alencar & Basri 2000, ApJ 119, 1881) are affected by wind
	absorption, it was necessary for our model to used the
	launching angle (at the inner most part) greater than 60
	degrees to be more consistent with observations; although this
	would mean that the launching angle condition of Blandford and
	Payne (1982) is violated for wind from a very inner part of
	the disc.

	 In addition to the models given in Figs. 6 and 9, we have
	 computed the models with d=5Rstar (not shown here) which
	 satisfies the wind launching condition of Blandford & Payne
	 (1982) in all parts of the disc wind zone in our model.
	 These models showed that the wind absorption and emission
	 features weaken, but overall morphology dependence of the
	 profiles on the wind temperature rate and the wind
	 acceleration rate is similar to what we found in the models
	 shown in Figs. 6 and 9.  The minimum inclination angle at
	 which the wind absorption becomes important is larger than
	 that of the models with a larger source displacement (d = 22
	 Rstar) as expected."

Sect. 4.3, 1st paragraph: You say the parameters used for the
magnetosphere are the same as in Fig.5, but in that figure you have
models with 3 different inclinations. Did you calculate models for the
three inclinations or just for i=55 degrees ? Please specify this in
the text.

   * All the models in Section 4 are computed at i=55 deg. The
     profiles computed at 10 and 80 deg. are given in Appendix A. 
     I see that is confusing. 
     I corrected the sentence as follows:

     ORIGINAL
        "The parameters used for the magnetosphere are  same as in 
         Fig. 5, ...."

     REVISED
        "The parameters used for the magnetosphere are same as in 
         Fig. 5 (with i=55 deg.), ...."

   * Also the last sentence is the same paragraph changed to reflect
     your comment:

     ORIGINAL
       "Fig. 9 shows the models profiles computed 
        using the same ranges of the disc-wind temperature and wind
        acceleration parameter as in the previous cases."

     REVISED
       "Fig. 9 shows the models profiles computed (at $i=55^\circ$)
        using the same ranges of the disc-wind temperature and wind
        acceleration parameter as in the previous cases."

Sect. 4.3, 5th paragraph: It is hard to see in Fig. 10 that the
position of minimum flux in the absorption moves blue-ward. I actually
don not see any difference between the models with mu=0.1 and 0.2.

   * You are correct. I don't know why I said that.
     I rephrase the sentence as follows

     ORIGINAL 
     "The figure shows that as $\mu$ increases the
     P-Cygni absorption deepens only slightly, and the position of minimum
     flux in the absorption trough appears to move blue-ward."

     REVISED
     "The figure shows that as $\mu$ increases the
     P-Cygni absorption deepens only slightly." and the position of minimum
     flux in the absorption trough appears to remain at same locations."

Sect. 5.1, Type III-B: This is the most common profile type in the
Reipurth et al. (1996) sample but you only find it in you Macc = 10^-7
Msun/yr models, which is not a common or average value for Macc rate
in CTTSs. As said in some previous comment, CTTSs tend to have Macc =
10^-8 Msun/yr and only a few present Macc = 10^-7 Msun/yr. To what do
you attribute that discrepancy between the data and the models ?

   * I have run additional models with a typical mass accretion rate
     (3x10^-8 Msun/yr, Gullbring et al. 1998; Calvet et al. 2004) for
     CTTSs.  Please see
     http://www.astro.ex.ac.uk/people/rk/profiles/extra

     for the profile computed at i=10,55,80 and for beta=0.2, 0.5,
     1.0, 2.0 Twind=7000, 8000, 9000, 10000K

      According to these models which use a more typical
      mass-accretion rate, Type III-B can be seen for at least in
      three models with fast accelerating and high wind temperature
      i.e. (beta, Twind) = (0.2, 10000K), (0.5, 9000K) and (0.5,
      10000K).

      A possible reason for not being able to find Type III profiles
      in lower mass-accretion rate models (e.g. in Mdot_acc =
      1.0x10^-8 Msun/yr models) is perhaps due to a wrong radial
      dependence (p in Equation 3) of the mass-loss rate per unit area
      used in our models.  This dependence shall be examined in more
      carefully in future.

      I added a following comments based on these additional runs.

      "In addition to the models shown in Appendix A, we have run a
      set of hybrid models (not shown here) with a typical
      mass-accretion rate for CTTS i.e. 3x10^-8 Msun/yr (Gullbring et
      al. 1998; Calvet et al. 2004) using i=10,55,80 with combinations
      of beta=0.2, 0.5, 1.0, 2.0 and Twind=7000, 8000, 9000,
      10000K. Based on these models, we found that Type III-B profiles
      can be seen for at least in three models with fast accelerating
      and high wind temperature at moderate inclination angle i.e. i =
      55 degrees with (beta, Twind) = (0.2, 10000K), (0.5, 9000K) and
      (0.5, 10000K).  A possible reason for not being able to find
      Type III profiles in lower mass-accretion rate models (e.g. in
      Mdot_acc = 1.0x10^-8 Msun/yr models) is perhaps due to a wrong
      radial dependence (p in Equation 3) of the mass-loss rate per
      unit area used in our models.  This dependence shall be examined
      more carefully in future."

Sect. 5.1, Type IV-R: In axisymmetric models (rotation and magnetic
axis aligned) the inverse P Cygni profile really restricts the
inclination angle to a small range. But there are observational
evidences (SU Aur: Johns & Basri 1995, AA Tau: Bouvier et al. 2003,
for example) for inclined magnetospheres and in that case you could
see the accretion shock through the fast moving accretion flow at
basically any inclination. It would only depend on a combination of
the rotation axis and magnetic axis inclinations. In Halpha, in
particular, it might still be difficult to see inverse P Cygni
profiles because of the wide emission wings due to broadening effects
(such as the Stark effect).

   * Yes, you are quite right. I am aware of the effect of the
     inclined magneto-axis CTTS models. In fact, I wrote a paper on SU
     Aur Pa-beta line variability. H-alpha variability of of SU Aur
     indeed shows a very complex line profile morphology dramatically
     changing with its rotational phase (e.g.  Johns & Basri 1995, see
     also their movie
     http://sprg.ssl.berkeley.edu/~cmj/html/suaur.mpg).  Although it
     does not look it has a clear IV-R type profile at any given
     rotational phase for H-alpha, I am aware that Pa-beta line does
     show IV-R type profile, and the strength of inverse P-Cyg or the
     absorption features in the redwing changes as the rotational
     phase changes (e.g. Kuorsawa et al, 2005, MNRAS, 358, 671).

     I wanted to restrict the cases for purely axi-symmetric
     geometries in this paper for clarity of discussion.  In reality,
     a situation may not be as simple as this classification, as we
     know the lines are sometimes highly variable. This problem will
     be tackled in near future. For a starter, I am currently
     computing line profiles based on the MHD model of Romanova et al
     (2003, ApJ, 595, 1009) who considered the disc accretion problem
     with an inclined dipole magnetic field, and investigate if the
     overall line variability features seen in the observation can be
     explained by this model. I am working on the case with and
     without the additional outflow (discwind or/and stellar wind).

     I will clarify this point by adding the following near the end of
     the first paragraph in Section 5.1 :

       "Although in general H-alpha in the spectra of CTTS shows a
        significant amount of variablity, which is in some cases
        induced by the rotational motion of an inclined magnetosphere
        (e.g. Johns &  Basri 1995; Bouvier et al. 2003), we restrict
        our discussion in this section for the cases of axi-symmetric
        geometries."

    Also a short comment is added at the end of Type IV-R section,

       "The restriction in the inclination angle mentioned above would
        be relaxed if the axis of the magnetosphere is tilted with
        respect to the rotational axis since the line-of-sight to an
        observer from the accretion hot rings will pass through a
        different part of the magnetosphere as a rotational phase
        changes (as it precesses around the rotational axis)."

Sect. 5.2, 3rd paragraph: What is the mass loss rate used in the
stellar wind models ? This value should be added to the text. Matt &
Pudritz (2005) suggest 10^-9 Msun/yr to solve the angular momentum
problem.

   * Thank you for pointing this out.  I should have quoted the
     mass-loss rate used in the models.    
     In both models in Fig.13, Mdot_wind = 10^-8 Msun/yr is used so 
     that mu=Mdot_wind/Mdot_acc = 0.1, and to be consistent with 
     the mass-accretion rate (Mdot_acc=10^-7 Msun/yr) used for the
     models in earlier in the paper. It seems that the ratio mu is an
     important factor in Matt & Pudritz (2005) in balancing the
     torques on a central star (their equation 3).
     I tried the models with Mdot_wind = 10^-9 Msun/yr  (keeping
     mu=0.1), and found the same inclination dependency for these
     models, so the main conclusion of this section 
     does not change when Mdot_wind is changed from 10^-9 Msun/yr to
     10^-9 Msun/yr.

     To reflect your points, I added the following in the text 
     (Sect. 5.2, 4th paragraph).

     After the first sentence of the paragraph, I inserted:

        "The mass-loss rate of the stellar wind in this model is 10^-8
	Msun/yr, which is same as the mass-loss rate used in the
	disc-wind magnetosphere hybrid model in the same figure.  In
	both models, the mass-accretion rate of 10^-7 Msun/yr is
	used."

     At the end of the paragraph, I inserted: 
        "A similar inclination dependency of EW is found for lower
        wind mass-loss rate models (e.g. Mdot_wind = 10^-9 Msun/yr)
        while keeping mu=0.1."

     Also in the figure caption of Figure 13  just before the last
	sentence,  I added:
	"The wind mass-loss rates used in both models are Mdot_wind =
	10^-8 Msun/yr."

***** Spells and other minor comments

Sect. 2.1, 2nd paragraph: ... and re-emitted optical and UV radiation.
Maybe rephrase as: ... and re-emitted as optical and UV radiation.

   * Corrected.

Sect. 2.2, 1st paragraph: Rmi and Rmo --> 2.2 Rsun and 3.0 Rsun should
be 2.2 Rstar and 3.0 Rstar

   * Corrected.

Sect. 2.3, 5th paragraph: The Rs value is set to 10 Rmi. Shouldn't it
be 10 Rwi, as in Table 4 ?

   * Yes. Thank you for noticing. Changed it to Rwi,

Sect. 2.3, caption of Figure 2: ...the density is approximately
proportional to ~ l^2 It looks like ~ l^-2

   * Yes, you are correct. My mistake again. It should be l^-2.
     ==> corrected.

Sect. 3, last paragraph: ...the dust property described in Section 10. 
¨Section 10¨ should be ¨Section 2.4.2¨

   * Corrected.

Sect. 4.2, caption of Figure 7: The 88 Rstar model is represented by a
solid line and not by a dash-dotted line as written.

   * Corrected.

In the same caption, "opening angel" should be "opening angle"

   * Corrected.

Sect. 4.3, 4th paragraph: "Figures 6" should be "Fig. 6"

   * Corrected.

Sect. 4.3, 5th paragraph: ...the flux peak increase and ...  ¨increase¨ 
should be ¨increases¨

   * Corrected.

Sect. 4.3, caption of Figure 11: The parameter used for the
magnetosphere are....  ¨parameter¨ should be ¨parameters¨

   * Corrected.

Sect. 5.2, 4th paragraph: The sentece below must be rewritten: ...This
tendency (...) holds for the models with this wind models for wide
ranges of beta...

   * Changed the sentence 
     From 
     "This tendency of the inclination dependency holds for the models
      with this wind models for wide ranges of beta and
      T_wind providing that the emission from the wind is
      greater than that of the magnetosphere."

     To
     "This inclination dependency of EW is seen in the models with
      wide ranges of beta and T_wind, provided that the wind emission
      of the model is dominating the emission from magnetosphere."

In addition to the referee's suggestions, we noticed the following 
minor mistakes in the original manuscript, and corrected.

1. The mass-loss rate in figure a1 and figure a2 were miss-labeled in
   the captions.  ==>  corrected.

2. In Figure 13, the velocity ranges out the two plots should be
   same for a better comparison. We changed the range of the 
   right plot to -800km/s <V < 800 km/s.

### 2006-04-05 TTau_Halpha/figures/appedix.tex
Revised version after the refree's report
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@693 25464f21-6099-402c-b30a-640f1d40d38b

--- 2005-11-29 TTau_Halpha/tmp.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
+\documentclass[english]{article}
 \usepackage[T1]{fontenc}
 \usepackage[latin1]{inputenc}
-\setcounter{tocdepth}{3}
 \usepackage{graphicx}
-\usepackage{amssymb}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% Bold symbol macro for standard LaTeX users
-\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}
-
 %% Because html converters don't know tabularnewline
 \providecommand{\tabularnewline}{\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\usepackage{lscape}
-\usepackage{times}
-
-\newcommand{\aap}{A\&A}
-\newcommand{\aaps}{A\&AS}
-\newcommand{\apj}{ApJ}
-\newcommand{\apjl}{\apj}
-\newcommand{\pasp}{PASP}
-\newcommand{\aj}{AJ}
-\newcommand{\mnras}{MNRAS}
-\newcommand{\apjs}{ApJS}
-\newcommand{\aapr}{A\&AR}
-\newcommand{\pasj}{PASJ}
-
-\newcommand{\kmps}{\mathrm{km~s^{-1}}}
-\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
-\newcommand{\Kelvin}{\mathrm{K}}
 
@@
 \begin{document}
-\title[On H-$\alpha$ formation of T Tauri stars]{On formation of H-$\alpha$ from classical T Tauri stars: the disc, wind, and magnetospheric-accretion hybrid model}
-
-\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk}, Tim J. Harries and Neil H. Symington\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}
-
-\date{Dates to be inserted}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2005}
-
-\maketitle
-
-\label{firstpage}
-
-\begin{abstract}
-
-We investigate the formation of H$\alpha$ from classical T~Tauri
-stars with a complex circumstellar geometry -- the combination of
-mangnetisherical accretion, collimated steller wind, and accretion
-disc. AND MORE
-
-\end{abstract}
-
-\begin{keywords}
-stars:formation -- stars: individual: SU Aur -- circumstellar matter -- infrared: stars -- stars: pre-main-sequence
-\end{keywords}
-
-\section{Introduction }
-
-\label{sec:Introduction}
-
-T~Tauri stars (TTS) are young ($<\sim3\times10^{6}\,\mathrm{yrs}$,
-\citealt{appenzeller:1989}) low-mass stars, and known as progenitors
-of solar-type stars. Classical T~Tauri stars (CTTS) exhibit strong
-H$\alpha$ emission, and typically have spectral types of F--K. Some
-of the most active CTTS show emission in higher Balmer lines and metal
-lines (e.g., \ion{Ca}{ii}~H and K). They also exhibit an excess
-amount of continuum flux in the ultraviolet (UV) and infrared (IR).
-Their spectral energy distribution and polarization data suggest the
-presence of a circumstellar disc, and it plays an important role in
-regulating dynamics of gas flows around CTTS.
-
-Many observational studies (e.g., \citealt{herbig:1962}; \citealt{edwards:1994};
-\citealt{kenyon:1994}; \citealt{reipurth:1996}; \citealt{alencar:2000})
-of CTTS line profles show that the evidence for both outward wind
-flows and inward accretion flows, as seen in the blueshifted absorption
-features in H$\alpha$ profiles and the redshifted inverse P~Cygni
-(IPC) profiles. Typical mass-loss rates of CTTS are about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$
-to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ (e.g., \citealt{kuhi:1964};
-\citealt{edwards:1987}; \citealt{hartigan:1995}), and the mass-accretion
-rates are also about $10^{-9}\,\mathrm{M_{\sun}\, yr^{-1}}$ to $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(e.g., \citealt{kenyon:1987}; \citealt*{bertout:1988}; \citealt{gullbring:1998}).
-
-Recent H$\alpha$ spectro-astrometric observations by \citet{takami:2003}
-show the direct evidence for the presence of bipolar and monopolar
-outflows down to $\sim1\,\mathrm{AU}$ scale (e.g.\,CS~Cha and RU~Lup).
-Similarly, ESO VLT observation of high-resolution ($\mathrm{R=50\,000}$)
-two-dimensional spectral of edge-on CTTS (HH30$^{*}$, HK~Tau~B,
-and HV~Tau~C) by \citet{appenzeller:2005} show the extended (SCALE?)
-H$\alpha$ emission in the direction perpendicular to the obscuring
-circumstellar disc, and in both above and below the disc --- suggesting
-the presence of the bipolar outflows. In silightly larger scale, \emph{HST}
-observation of HH30 (Burrorws et al 1996) shows the jet traced to
-within $\lesssim30$~AU from the star. The jet has a cone shape with
-an opening angle of $3^{\circ}$ between 70 and 700 AU. (Originally
-from Konig and Pudritz 2000 review in PP IV). \citealt{alencar:2000}
-found about 80 per cent of their samples (30 CTTS) show blueshifted
-absorption componets in at least one of Balmer lines and Ca~K (most
-commonly in H$\alpha$).
-
-In a currently favoured model of accretion flows around CTTS, the
-accretion discs are disrupted by the magnetosphere of stars which
-channels the gas from the disc onto the surface of the stars (e.g.,
-\citealt{uchida:1985}; \citealt{koenigl:1991}; \citealt{cameron:1993}\citealt{shu:1994}).
-This picture of the accretion flows is supported by the evidences
-that CTTS have relatively strong ($\sim10^{3}\mathrm{G}$) magnetic
-field (e.g., \citealt*{jonhs-krull:1999}; \citealt{guenther:1996})
-and by the radiative transfer models which reproduce the observed
-profiles for some TTS (\citealt{muzerolle:2001}). The magnetospherical
-accretion model naturally explains the blueward asymmetic emission
-lines (seen in some of CTTS) caused by the partial occulation of the
-flow by the disc, and the redshifted absorption componet at the typical
-free-fall velocities (a few hundred $\mathrm{km\, s^{-1}}$) seen
-in some of CTTS.
-
-Dispite the success of the magnetosherical accretion model in explaining
-the line profiles in some CTTS, the overwhelming observational evidences
-for the outflow (mentoned above) in the CTTS profiles suggests that
-this model is only a part of a whole picture. Clearly, the modefification
-to include the outflowing wind/jet flow is neccessary if one requires
-to predict the mass-accretion rate and the mass-loss rate of CTTS
-by modelling their emission profiles (e.g. H$\alpha$).
-
-Priory to the magnetospherical models, many alternative models had
-been considered to explain the observed spectroscopic features mentioned
-earlier. For example, 1.~the Alfv\'{e}n wave-driven wind model (e.g.~\citealt{decampli:1981};
-\citealt{hartmann:1982}), 2.~turbulant boundary layer (between the
-accretion disc and stellar surface) model (e.g.~\citealt{bertout:1988};
-\citealt{basri:1989}), 3.~chromospheric model (e.g.~\citealt{calvet:1984}),
-and 4.~disc wind model (e.g. \citealt{calvet:1992b}; \citealt{kwan:1995}).
-Considering the sucess of the magnetospherical accretion flow model
-in some cases and the observational eividences for the outflows, it
-is likely that an improved spectroscopic model requires both inflow
-and outflow components. The combination of the magnetospheric accretion
-flow model with model 1 or 4 would be a reasonable starting point
-for an improved spectroscopic model. Although time consuming to explore
-a larger parameter space, more realistic density, velocity and temperature
-structure from magnetohydrodynamic wind+accretion models should be
-considered as inputs for an radiative transfer model in the future.
-
-The magnetocentrifugal wind model, first proposed by \citet{blandford:1982},
-has been often used to reproduce the large-scale wind structure of
-T Tauri stars, or to model observed optical jets (e.g.~HH~30 jet
-by \citealt{burrows:1996}; \citealt{ray:1996}). The lanching of
-the wind from a Keplerian disc is typically done by treating the equaotorial
-plane of the disc as a mass-injecting boundary condition (e.g., \citealt{ustyugova:1995};
-\citet{shu:1995}; \citealt{ouyed:1997}; \citealt{krasnopolsky:2003}).
-Depending on the location of the open magnetic fields anchored to
-the disc, two different types of winds are preoduced. If the field
-is constrained to be near the co-rotation radius of stellar magnetosphere,
-an {}``X-wind'' \citep{shu:1994} is produces. If the open field
-lines are located in a wider area of the disc, a {}``disc-wind''
-similar to \citet{koenigl:2000} is produced \citet{krasnopolsky:2003}.
-Recent reviews on the jet/wind-disc connection can be found in \citet{koenigl:2000}
-and \citet{pudritz:2005}.
-
-In this paper, we present a semi-emperical wind -- accretion disc
--- magnetospherical accretion hybrid model for CTTS, and perform parametric
-studies of the H$\alpha$ formation. This study should provide preliminary
-physical conditions which lead to the wide varaiety of emission line
-profiles seen in the observation, and would help to construct more
-comprehensive circumstellar models (e.g. via MHD simulations) of T~Tauri
-stars. the Using the model results, we examine the H$\alpha$ spectroscopic
-classification used by \citet{reipurth:1996}, and compare models
-with observations. We will also discuss whether our model is consistent
-with some predictions made by the recentt MHD studies (e.g.~ $\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$).
-
-In section~\ref{sec:model-configuration}, the model assumptions,
-and the basic model configurations are presented. We discuss the radiaive
-transfer model used to compute the profiles in section~\ref{sec:radiative-transfer-model},
-and the results of model calculations are given in section~\ref{sec:Results}.
-The closer examination and discussion of the results are presented
-in section~\ref{sec:Discussion}. Finally, the summary of this work
-and the conclusion are in section~\ref{sec:Conclusions}.
-
-\section{Model configuration}
-
-\label{sec:model-configuration}
-
-To understand how the different part of the CTTS circumsterllar enviroment
-contributes to the fomation of H$\alpha$, the model spaced is devided
-into four different regions: 1.~Central contiuum source, 2.~magnetosphere
-accretion flow, 3.~wind outflow, and 4.~accretion disc. Fig.~\ref{fig:overview}
-depicts the relative location in the model space. In all regions,
-the density is symmetric around the z-axis. The innermost raius of
-the magnetsphere at the equotrial plane coincides with the the inner
-radius of the accretion disc. From the inner most part of the accretion
-disc, the gas freely fall, moving along the magneic filed onto the
-surface of the star. For the purpose of computational simplicity,
-the colliminated wind are defined only in the outside of the largest
-radius of the magnesophere. In the following subsections, the details
-of model components will be described.
-
-\begin{figure*}
-
-\begin{center}
-
+\begin{tabular}{c}
 \includegraphics[%
-  scale=0.6]{figures/overview2.eps}
-
-\end{center}
-
-\caption{Basic Model Configuration.
-The system consist of four components: 1.~the continuum source located at the origin $\left( o \right)$ of the cartisian coordinates $\left(x,y,z\right)$ -- the y-axis are into the paper, 2.~magnetospherical accretion flow, 3.~colliminated wind/jet outflow, and 4.~accretion disc.
-The density distribution is symmetric around the z-axis.
-The innermost raius of the magnetsphere (at the equotrial plane) coincides with the the inner radius of the accretion disc.
-From the inner most part of the accretion disc, the gas freely fall, moving along the magneic filed onto the surface of the star.
-For simplicit, the colliminated wind/jet exists outside of the largest radius of the magnesophere (dotted line).
-}
-
-\label{fig:overview}
-
-\end{figure*}
-
-\subsection{Contiuum Source}
-
-\label{sub:Contiuum-Source}
-
-Unless specified otherwise, we adopt stellar parameters of a typical
-classical T~Tauri star (REF) for the central conitnuum source, i.e.
-radius ($R_{*}$), mass ($M_{*}$), and effective temperature the
-photosphere ($T_{\mathrm{ph}}$) are $2\, R_{\sun}$, $0.5\, M_{\sun}$,
-and $4000\,\mathrm{K}$ respectively. The model atomsphere of \citet{kurucz:1979}
-equivallently \citet{kurucz:1993}  with $T_{\mathrm{ph}}=4000\,\mathrm{K}$
-and $\log g_{*}=3.5$ (cgs) is used to continuum flux at H$\alpha$wavelength.
-The parameters are summarised in Table~\ref{tab:std_parameters}.
-
-The limb-darkening law used for the continuum source is $I\left(\mu\right)=I_{0}\left(1+b\mu\right)$
-where $\mu=\cos\theta$ and $\theta$ is the polar angle. $b$ is
-a parameter. For no limb-darkening case, $b=0$, and for the Eddington
-approximation case $b=3/2$. The former is used in all the calulcations
-presented here. (Is this an ok assumption for T Tauri's? You need
-to check this.)
-
-\begin{table*}
-
-\begin{center}
-
-\begin{tabular}{lcccccccccccc}
-\hline 
-Parameters&
-$R_{*}$&
-$M_{*}$&
-$T_{\mathrm{ph}}$&
-$R_{\mathrm{mi}}$&
-$R_{\mathrm{mo}}$&
-$\dot{M}_{\mathrm{acc}}$&
-$\dot{M}_{\mathrm{wind}}$&
-$\beta$&
-$v_{\infty}$&
-$m$&
-$R_{\mathrm{di}}$&
-$R_{\mathrm{do}}$\tabularnewline
-&
-$\left[R_{\sun}\right]$&
-$\left[M_{\sun}\right]$&
-$\left[\mathrm{K}\right]$&
-$\left[R_{*}\right]$&
-$\left[R_{*}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
-$[-]$&
-$[\mathrm{km\, s^{-1}}]$&
-$[-]$&
-$\left[R_{\sun}\right]$&
-$\left[\mathrm{AU}\right]$\tabularnewline
-\hline
-Standard&
-$2.0$&
-$0.5$&
-$4000$&
-$2.2$&
-$3.0$&
-$10^{-7}$&
-$10^{-8}$&
-$0.2$&
-$200$&
-$2.0$&
-$2.0$&
-$100$\tabularnewline
-\hline
+  scale=0.45]{/usr/local/home/rk/paper/TTau_Halpha/figures/discwind_hybrid_mdot7_inc10.eps}\tabularnewline
+\includegraphics[%
+  scale=0.45]{/usr/local/home/rk/paper/TTau_Halpha/figures/discwind_hybrid_mdot7_inc55.eps}\tabularnewline
+\includegraphics[%
+  scale=0.45]{/usr/local/home/rk/paper/TTau_Halpha/figures/discwind_hybrid_mdot7_inc80.eps}\tabularnewline
 \end{tabular}
-
-\end{center}
-
-\caption{The summary of the standard classical T~Tauri star model parameters.}
-
-\label{tab:std_parameters}
-
-\end{table*}
-
-\subsection{Magnetosphere}
-
-\label{sub:Magnetosphere}
-
-We adopt the magnetospherical accretion flow model of \citet{hartmann:1994},
-as done so by \citet{muzerolle:2001} and by \citet{symington:2005},
-in which the gas accretion on to the stellar surface from the innermost
-part of the accretion disc occurs through a dipolar stellar magnetic
-field. The magnetic field is assumed to be so strong that the gas
-flow does not affect the underlying magnetic field itself. As shown
-in Fig.~\ref{fig:overview}, the innermost radius ($R_{\mathrm{mi}}$)
-of the magnetophere at the equatorial plane ($z=0$) is assigned to
-be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
-disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
-and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
-the equaotrial plane) are set to be $2.2\, R_{\sun}$ and $3.0\, R_{\sun}$
-respectively. The former value corresponds to the corotation radius
-of the accretion disc, and the geometry of the magnetic field/stream
-lines is kept constant throghout this paper. The geometry of the magnetosphere
-is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.
-
-The magnetic field and the gas stream lines are assumed to have the
-following simple form: $r=R_{\mathrm{m}}\sin^{2}\theta$ \citep[see][]{ghosh:1977}
-where $r$, and $\theta$ are coordinates of the field point ($p$)
-in Fig.~\ref{fig:overview} in spheical coodinates, and $R_{\mathrm{m}}$is
-the radial distance to the field line at the equotorial plane ($\theta=\pi/2$).
-The range of $R_{\mathrm{m}}$is restricted between $R_{\mathrm{mi}}$
-and $R_{\mathrm{mo}}$ as mentioned above. Using the field geometry
-above, the conservation of energy, and igoring the rotation of magnetosphere,
-the velocity and the density of the accreting gas along the steam
-line can be found. See \citet{hartmann:1994} for details.
-
-In all of our models, the temperature structure of the magnetospheric
-used by \citet{hartmann:1994} is also adoped here. The temperature
-structure was computed assuming a volumetric heating rate which is
-proportional to $r^{-3}$, and using the energy balance of the radiative
-cooling rate of \citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
-Although the temperature structure of the accretion steam could significantly
-affect the line source function, for the purpose of the expolaring
-the general characteristics of the H$\alpha$ formation, this simple
-form is a reasonable assumption.\citet{martin:1996} presented the
-self-consistent determination of the thermal structure of the inflowing
-gas along the dipole magnetic field, same as the one used here, by
-solving the heat equation couple to trate equations for hydrogen.
-He found that main heat source is adiabatic compression due to the
-convering nature of the flow, and the major contirbutors of the cooling
-process are bremsstrahling radiation and line emission from Ca~II
-and Mg~II ions. The temerature sturcture of \citet{martin:1996}
-qualitaively agrees with that of \citep{hartmann:1994}. The sensitivty
-tests of H$\alpha$ on the temperature structure will be presented
-later (SPECIFY THE SECTION LATER).
-
-As the infalling gas becomes closer to the stellar surface, it is
-decelerates in a strong shock, and heated to $\sim10^{6}\,\mathrm{K}$
-(with typical parameters). The X-ray radiation produced in the shock
-will be absorbed by the gas located near, and reemitted in optical
-and UV radiation (\citealt{koenigl:1991}; \citealt{hartmann:1994}).
-This will create hot rings near the stellar surface where the magnetic
-field intersects with the surface. For simplicity, the free-falling
-kinetic energy is assumed to be thermalized in the radiating layer,
-and reemits as blackbody radiation (with a single temerature). With
-the parameters of the magnetosphere and the star given above (Table~\ref{tab:std_parameters}),
-about $8$~per~cent of the surface is covered by the hot rings,
-and its temperature is about $6400\,\mathrm{K}$. If the mass-accretion
-rate is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this
-accretion luminosity to the photospheric luminosity is about $0.5$.
-The contiuum emission from the hot rings is taken into account when
-computing the line profiles.
-
-\subsection{Wind}
-
-\label{sub:wind_jet}
-
-\subsubsection{Colliminated wind model}
-
-JUSTTIFICATION OF USING THIS FORMULATION. BREIFLY MENTIONED THE WORK
-DONE BY OTHERS.
-
-Based on the simple model of \citet{appenzeller:2005}, the following
-parametrisation of colliminated wind/jet (region 3 in Fig.~\ref{fig:overview})
-is adopeted. The wind velocity field, $\mathbf{v}_{\mathrm{wind}}\left(r,\theta\right)$,
-is consist of radial and polar components which depend only on $r$
-and $\theta$ respectively. The radial componet $v_{r}\left(r\right)$
-is assumed to be in the classical beta-velocity law \citep[c.f.][]{castor:1979},
-and the azimuthal component $v_{\phi}$ is asuumed to be a constant
-fraction ($\gamma$) of the Keplerian velocity for a given distance
-($w=\sqrt{x^{2}+y^{2}}$) from the symmetry axis ($z$-axis) , i.e.:
-
-\begin{eqnarray}
-\mathbf{v}_{\mathrm{wind}} & = & v_{r}\hat{\mathbf{r}}+v_{\phi}\hat{\mathbf{\bphi}}+v_{\theta}\hat{\btheta}\label{eq:wind_velocity_def}\end{eqnarray}
-where \begin{equation}
-v_{r}\left(r\right)=v_{r0}+v_{\infty}\left(1-\frac{R_{\mathrm{mo}}}{r}\right)^{\beta}\,,\label{eq:wind_velocity_radial_part}\end{equation}
-\begin{equation}
-v_{\phi}\left(w\right)=\gamma\,\left(\frac{GM_{*}}{w}\right)^{1/2}\,,\label{eq:wind_velocity_azimuth_part}\end{equation}
-and \begin{equation}
-v_{\theta}\left(r,\theta\right)=v_{\theta0}\,\left(\frac{R_{\mathrm{mo}}}{r}\right)^{\alpha}\frac{\tan\theta}{\left|\tan\theta\right|}\,.\label{eq:wind_velocity_polar_part}\end{equation}
-Note that the base of the wind starts at $r=R_{\mathrm{mo}}$, and
-the range of the polar angle is restricted to $\theta>\left|\theta_{\mathrm{disc}}\right|$
-where $\theta_{\mathrm{disc}}$ is the openning angle of the accretion
-disc, to avoid the overlap. $v_{r0}$is the small radial velocity
-at the base of the wind ($r=R_{\mathrm{mo}}$). Normally, $v_{r0}=10\,\mathrm{km\, s^{-1}}$,
-approximately the thermal velocity of hydrogen with $T=7500\,\mathrm{K}$
-and $\gamma=0.05$ (\citealt{appenzeller:2005}) are used. The dependency
-of $v_{r}$ in polar direction ($\theta=0$) on the values of wind
-accerelation parameter $\beta$ is shown in Figure~\ref{fig:wind_vr_rho}.
-All other parameters describing the wind are fixed as the standard
-values given in Table~\ref{tab:std_parameters}.
-
-Further, the density of the wind is assumed to be axi-symmetric and
-separable in $r$ and $\theta$ for computationaly simpliciy, i.e.,
-
-\begin{equation}
-\rho\left(r,\theta\right)=P\left(r\right)\, F\left(\theta\right)\label{eq:wind_density_def}\end{equation}
- with \begin{equation}
-F\left(\theta\right)=n\,\cos^{b}\theta\label{eq:wind_density_theta}\end{equation}
- where $b$ is normally positive even number (for the density symmetric
-about the equtotrial plane), and $n$ is the angular normalisation
-constant. For $b=0$, the wind is sherically symmetic exept for the
-parts dirupted by the accretion disc. The larger the value of $b$,
-the higher the degree of the collimination. By integrating equation~\ref{eq:wind_density_theta}
-over angles and normalising the integral to $4\pi$, one finds \begin{equation}
-n=\frac{1+b}{1-\cos^{1+b}\theta_{\mathrm{wind}}}\,.\label{eq:wind_density_theta_norm}\end{equation}
- Asumming the total mass-loss rate by the wind/jet is $\dot{M}_{\mathrm{wind}}$
-and the mass-flux conserves in time, the radial part of the density
-function is reduced to $P\left(r\right)=\dot{M}_{\mathrm{wind}}\,\left[4\pi r^{2}v_{r}\left(r\right)\right]^{-1}$;
-hence, Equation~\ref{eq:wind_density_def} becomes \begin{equation}
-\rho\left(r,\theta\right)=\frac{n\,\cos^{b}\theta\,\dot{M}_{\mathrm{wind}}}{4\pi r^{2}\, v_{r}\left(r\right)}\,.\label{eq:wind_density_final}\end{equation}
- For a given mass-accretion rate, the wind mass-loss rate in our typical
-model is assined from the ratio of mass-loss to mass-accretion rate
-($\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}\approx0.1$), indicated
-by both observations and magnetohydrodynamical calculations (see e.g.
-\citealt{koenigl:2000}).
-
-Figure~\ref{fig:wind_vr_rho} shows the values of $\rho$ in polar
-direction ($\theta=0$) for different values of $\beta$ with all
-other parameters fixed as the standard values (Table~\ref{tab:std_parameters}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{cc}
-\includegraphics[%
-  clip,
-  scale=0.45]{plots/discwind_vr_pol.eps}~~~~~~&
-\includegraphics[%
-  clip,
-  scale=0.45]{plots/density_wind_pol.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{The dependency of the wind/jet velocity and density structures on the wind accerelation parameter $\beta$.
-The radial component of the wind/jet velocity (equation~\ref{eq:wind_velocity_radial_part}) in polar direction, $\theta = 0$ as a function of radius is shown on left.
-The wind/jet density (equation~\ref{eq:wind_density_final} along polar direction as a function of radius is right.
-The smaller the value of $\beta$, the faster the accerelation of the wind.
-For the raidus ($r/R_{\mathrm{mo}} < 10$, both velocity and density are sensitive to the value of $\beta$.
-For all $\beta$ values, the radial velocity of the wind reaches the terminal velocity ($\sim 210\,\kmps$ by  $r/R_{\mathrm{mo}} \sim 1000$.
-The initial velocity $V_{0}=10\,\kmps$, which approximately corresponds to the thermal velocity of a hydrogen atom at 7500~K,  is used for all $v_{r}$ plots.
-Beyound $r/R_{\mathrm{mo}}= 100$, little difference is seen in the polar density with diffrent $\beta$ values.}
-
-\label{fig:wind_vr_rho}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Disc-wind model}
-
-GIVE MORE CONVINCING MOTIVIATION FOR USING THIS MODEL. THIS SECTION
-MAY BE DELETED.
-
-Alternative to the colliminated wind model, the kinematic disc-wind
-mode of \citet{knigge:1995} in which a wind originating from the
-surface of the accretion disc with a biconical outflow geometry (Fig.~XXX)
-will be presented next. The model was originally developed for describing
-the formation of the UV resonance lines in the winds of cataclystic
-variable (CV) stars.
-
-\subsection{Accretion disc}
-
-\label{sub:Accretion-disc}
-
-Region 4 in Fig.~\ref{fig:overview}
-
-\subsubsection{Density and velocity}
-
-Although it is possible, in our model, to compute the dust-sublimination
-radius and the vertical hydrostatic structure of the accretion disc
-self-consistently (assuming the radial dependecy of the mid-plane
-density) by using the interative Monte Calro radative transfer technique
-(c.f.~\citet{walker:2004}), we find it to be too time consuming
-for the purpose of this paper -- understanding the general characteristic
-of H$\alpha$ profile shapes hence exploring a large parameter space.
-For this reason, we adopt a simple analytical disc model, the steady
-$\alpha$-disc `standard model' (\citealt{shakura:1973}; \citealt*{frank:2002})
-with the inner radius fixed at the inner radius of the magnetosphere
-(at equatorial plane). The disc density disribution is given by
-
-\begin{equation}
-\rho_{\mathrm{d}}\left(w,z\right)=\Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}\label{eq:disc-density-function}\end{equation}
- where $w$, $h$, $z$ and $\Sigma$ are the distance from the symmetry
-axis, the scale height, the distance from the disc plane, and the
-surface density at the mid-plane, respectively. The mid-plane surface
-density and the scale height are given as: \begin{equation}
-\Sigma\left(w\right)=\frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{d}}^{2}}\, w^{-3/4}\label{eq:density-midplane}\end{equation}
- where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
-and the disc mass respectively.\begin{equation}
-h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.\label{eq:scale-height}\end{equation}
- With these parameters, the disc is slightly flared. The inner radius
-of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ (the inner
-radius of the magnetosphere at the equaotrial plane), which is approximatly
-same as the co-rotating radius of the system with the paramters in
-Table~\ref{tab:std_parameters}. The disc mass, $M_{\mathrm{d}}$,
-of an object is assumed to be 1/100 of the central mass ($M_{*}$),
-and the disc radius ($R_{\mathrm{di}}$) to be 100~au. The velocity
-of the gas/dust in the disc is assumed to be Keplerian.
-
-\subsubsection{Dust model}
-
-To calculate the dust scattering and absorption cross section as a
-function of wavelength, the optical constants of \citet{draine:1984}
-for amorphous carbon grains and \citet{hanner:1988} for silicate
-grains are used. The model uses the {}``large grain'' dust model
-of \citet{wood:2002} in which the dust grain size distribution is
-described by the following function:\begin{equation}
-n\left(a\right)da=\left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\, a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da\label{eq:grain-dist-function}\end{equation}
- where $a$ is the grain size restricted between $a_{\mathrm{min}}$
-and $a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$
-are the terms set by requiring the grains to completely deplete a
-solar abundance carbon and silicon. The parameters adopted in our
-model are: $C_{\mathrm{C}}=1.32\times10^{-17}$, $C_{\mathrm{Si}}=1.05\times10^{-17}$,
-$p=3.0$, $q=0.6$, $a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
-$a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
-and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds
-to Model~1 of the dust model used by \citet{wood:2002}. See also
-their Fig.~3 The relative number of each grain is assumed to be that
-of solar abundance, C/H$\sim3.5\times10^{-4}$ \citep{anders:1989}
-and Si/H$\sim3.6\times10^{-5}$ \citep{grevesse:1993} which are similar
-to values found in the ISM model of \citet{mathis:1977} and \citet*{kim:1994}.
-Similar abundances were used in the circumstellar disc models of \citet{cotera:2001}.
-
-\section{Radiative transfer model}
-
-\label{sec:radiative-transfer-model}
-
-We have extended the TORUS radiative transfer code (\citealt{harries:2000};
-\citealt{kurosawa:2004a}; \citealt{symington:2005}) to compute the
-H$\alpha$ profiles from pre-main-sequence stars which are surrounded
-by one or more of the followings: the magnetospherical accretion flow,
-the out-flowing colliminated wind, and the accreation disc. Previously
-in \citet{symington:2005}, the model used in the three-dimentional
-(3-D) adaptive mesh refinement (AMR) to inverstigate the line variability
-mainly associated with roational motion of complex geometrical configurations
-of magnetospherical flow (see also \citealt*{kurosawa:2005a}). We
-modefied the code to handle the two-dimentional (2-D) density distribution,
-and restricted our models to be axi-symmetric. It was done so in order
-to enable us to explore rather large number of parameter spaces (c.f.~section~\ref{sec:model-configuration}).
-Note that the velocity field is still in 3-D -- the third component
-can be calculated by using the symmetry for a given value of azimutal
-angle. The examples of how the AMR grid for the purpose of the radiative
-transfer is constructed are presented in e.g. \citet{wolf:1999},
-\citet{kurosawa:2001a} and \citet{steinacker:2003} .
-
-The computation of the H$\alpha$ is devided in two parts: 1.~the
-source function calculation and 2.~the observed flux/profile calulcation.
-In the first process, we have utilized the method by \citet{klein:1978}
-(see also \citealt{rybicki:1978}; \citet{hartmann:1994}) in which
-the Sobolev approximation method is applied. The population of the
-bound states of hydrogen are assumed to be in statistical equilibrium,
-and the gas to be in radiative equilibrium. Our hydrogen atom model
-consist of 14 bound state and continuum. Readers are refer to \citet{klein:1978}
-for details. (AND MORE..)
-
-To compute the observed line profile, the Monte Calro radiative transfer
-method (e.g. \citealt{hillier:1991}) using the Soblev escape-probabiliy
-can be used when I.~a large velocity gradiant is present in the gas
-flow, and II.~the intrinsic line width is negleible compared to the
-Doppler broadeing of the line. In our earlier models (\citealt{harries:2000};
-\citealt{symington:2005}), this method was used to compute the line
-profiles since the condition I and II are resonably satisfied. However,
-as noted and demonstrated by \citet{muzerolle:2001}, even with a
-moderate amount of mass-accretion rate ($~10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$),
-Stark broadening becomes important in the optically thick H$\alpha$
-line. \citet{muzerolle:2001} (MORE REF HERE) also pointed out that
-the observed H$\alpha$profiles from CTTS typically have the wings
-extending to $500\,\mathrm{km\, s^{-1}}$(e.g.~\cite{edwards:1994};
-\citet{reipurth:1996}) which cannot be explained by the infall velocity
-of the gas along the magneosphere.
-
-To implement the broadening meachanism, two modedifications to our
-previous model (\citealt{symington:2005}) are necessary. First, the
-emission and absorption profiles must be replaced by a Voigt profle
-which is defined as: \begin{equation}
-H\left(a,y\right)\equiv\frac{a}{\pi}\int_{-\infty}^{\infty}\frac{e^{-y'^{2}}}{\left(y-y'\right)^{2}+a^{2}}\, dy'\label{eq:voigt_profile_def}\end{equation}
- where $a=\Gamma/4\pi\Delta\nu_{\mathrm{D}}$, $y=\left(\nu-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$,
-and $y'=\left(\nu'-\nu_{0}\right)/\Delta\nu_{\mathrm{D}}$ (c.f. \citealt{mihalas:1978}).
-$\nu_{0}$ is the line centre frequency, and $\Delta\nu_{\mathrm{D}}$
-is the Doppler line width of hydrogen atom (due to its thermal motion)
-which is given by $\Delta\nu_{\mathrm{D}}=\left(2kT/m_{\mathrm{H}}\right)^{1/2}\times\left(\nu_{0}/c\right)$
-where $m_{\mathrm{H}}$ is the mass of a hydrogen atom. The damping
-constant $\Gamma$, which depends on the physical condition of the
-gas, is parameterised by \citet*{vernazza:1973} as follows:
-
-\begin{eqnarray}
-\Gamma & = & C_{\mathrm{rad}}+C_{\mathrm{vdW}}\left(\frac{n_{\mathrm{HI}}}{10^{16}\,\mathrm{cm^{-3}}}\right)\left(\frac{T}{5000\,\mathrm{K}}\right)^{0.3}\nonumber \\
- &  & +\, C_{\mathrm{Stark}}\left(\frac{n_{e}}{10^{12}\,\mathrm{cm^{-3}}}\right)^{2/3}\label{eq:dampimg_constant_def}\end{eqnarray}
- where $n_{\mathrm{H\, I}}$ and $n_{e}$ are the number density of
-neutral hydrogens and that of free electrons. Also, $C_{\mathrm{rad}}$,
-$C_{\mathrm{vdW}}$ and $C_{\mathrm{Stark}}$ are natural broadening,
-van der Waals broadening, and linear Stark broadening constants respectively.
-We simply adopt this parameterization along with the values of broadening
-constants for H$\alpha$ from \citet{luttermoser:1992}, i.e. $C_{\mathrm{rad}}=6.5\times10^{-4}$~\AA,
-$C_{\mathrm{vdW}}=4.4\times10^{-4}$~\AA~ and $C_{\mathrm{Stark}}=1.17\times10^{-3}$~\AA.
-In terms of level populations and the Voigt profile, the line opacity
-for the transition $i\rightarrow j$ can be written as: \begin{equation}
-\chi_{l}=\frac{\pi^{1/2}e^{2}}{m_{e}c}f_{ij}n_{j}\left(1-\frac{g_{j}n_{i}}{g_{i}n_{j}}\right)H\left(a,y\right)\label{eq:line_opacity}\end{equation}
- where $f_{ij}$, $n_{i}$, $n_{j}$, $g_{i}$and $g_{j}$ are the
-oscillator strength, the population of $i$-th level, the population
-of $j$-th level, the degeneracy of the $i$-th level, and the degeneracy
-of the $j$-th level respectively. $m_{e}$and $e$ are the electron
-mass and charge (c.f. \citealt{mihalas:1978}).
-
-The second modefication in our model is the replacement of the method
-of solving the formal solution from the Monte Calro radiative transfer
-method with Sobolev approximation to the direct integration method.
-Similarly to the notation used by \citet{muzerolle:2001}, we specify
-the cylindical coordinates $\left(p,\, q,\, t\right)$ which is the
-original stellar coordinate system $\left(\rho,\,\phi,\, z\right)$
-rotated (around $y$ axis) by the inclination of the line of sight,
-i.e. the $t$-axis coinsides with the line of sight. The observed
-flux ($F_{\nu}$) is given by: \begin{equation}
-F_{\nu}=\frac{1}{4\pi d^{2}}\int_{0}^{p_{\mathrm{max}}}\int_{0}^{2\pi}p\,\sin q\, I_{\nu}\mathrm{\, d}q\,\mathrm{d}p\label{eq:flux_integral}\end{equation}
-where $d$, $p_{\mathrm{max}}$, and $I_{\nu}$ are the distance to
-an observer, the maximum extent to the model space in the projected
-(rotated) plane, and the specific intensity ($I_{\nu}$) in the direction
-on observer at the outer boundary. For a given ray along $t$, the
-specific intensity is given by:\begin{equation}
-I_{\nu}=I_{0}e^{-\tau_{\infty}}+\int_{-\infty}^{t_{0}}\eta_{\nu}\left(t\right)\, e^{-\tau\left(t\right)}\mathrm{d}t\label{eq:formal_sol_integral}\end{equation}
- where $I_{0}$ and $\eta_{\nu}$ are the intensity at the boundary
-on the opposite to the observer and the emissivity of the stellar
-atmosphere/wind at a frequency $\nu$. For a ray which intersects
-with the stellar core, $I_{0}$ is computed from the stellar stompshere
-mode of \citet{kurucz:1979} as descibed in section~\ref{sub:Contiuum-Source},
-and $I_{0}=0$ otherwise. The initial position of each ray is assigned
-to be at the center of the surface element ($\mathrm{d}A=p\,\sin q\,\mathrm{d}q\,\mathrm{dp}$).
-The code excution time is proportional to $n_{p}\, n_{q}\, n_{\nu}$
-where $n_{p}$ and $n_{q}$ are the number of cylindical radial and
-angluar points for the flux integration, and $n_{\nu}$is the number
-of frequency points. In the models presented in the next (section~\ref{sec:Results}),
-$n_{p}=180$, $n_{q}=100$, and $n_{\nu}=101$ are used unless specified
-otherwise. The linearliy spaced radial grid is used for the area where
-the ray intersects with magnetpshere, and the logarithmically spaced
-grid is used for the wind and the accretion disc regions.
-
-The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
-is defined as: \[
-\tau\left(t\right)\equiv\int_{-\infty}^{t}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'\]
- where $\chi_{\nu}$ is the opacity of media the ray passes through.
-$\tau_{\infty}$ is the total optical depth measured from the initial
-ray point to the observer (or to the outer boundary closer to the
-observer). Initially, the optical depth segments $\mathrm{d\tau}$
-are computed at the intersections of a ray with the original AMR grid
-in which the opacity and emissivity infomation are stored. For high
-opticale depth models, additional points are inserted between the
-original points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$
-values are interpolated to those points to ensure $\mathrm{d}\tau<0.05$
-for the all ray segments.
-
-For a point in the magnetosphere and the wind flows, the emissivity
-and the opacity of the media are given as:\begin{equation}
-\left\{ \begin{array}{rcl}
-\eta_{\nu} & = & \eta_{\mathrm{c}}^{\mathrm{H}}+\eta_{l}^{\mathrm{H}}\\
-\chi_{\nu} & = & \chi_{c}^{\mathrm{H}}+\chi_{l}^{\mathrm{H}}+\sigma_{\mathrm{es}}\end{array}\right.\label{eq:emiss_opa_gas}\end{equation}
-where $\eta_{\mathrm{c}}^{\mathrm{H}}$ and $\eta_{l}^{\mathrm{H}}$
-are the continuum and line emissivity of hydrogen. $\chi_{c}^{\mathrm{H}}$,
-$\chi_{l}^{\mathrm{H}}$, and $\sigma_{\mathrm{es}}$ are the contiuum,
-line opacity (equation~\ref{eq:line_opacity}) of hydrogen, and the
-electron scattering opacity. Similarly, for a point in the accretion
-disc,
-
-\begin{equation}
-\left\{ \begin{array}{rcl}
-\eta_{\nu} & = & 0\\
-\chi_{\nu} & = & \kappa_{\mathrm{abs}}^{\mathrm{dust}}+\kappa_{\mathrm{sca}}^{\mathrm{dust}}\end{array}\right.\label{eq:emiss_opa_dust}\end{equation}
- where $\kappa_{\mathrm{abs}}^{\mathrm{dust}}$ and $\kappa_{\mathrm{sca}}^{\mathrm{dust}}$
-are the dust absorption, and scattering opacity which are calculated
-using the dust property described in section~\ref{eq:grain-dist-function}.
-For computational simplicity, we assumed that the dust emissivity
-is zero. Since the disc mass of CTTS are rather small ($\sim0.1\,\mathrm{M_{\sun}}$)
-and low temperature ($<\sim1600\,\mathrm{K}$), the continuum flux
-contribution at H$\alpha$ wavelength is expected to be neglegible
-(e.g.~\citealt{chiang:1997}). The scattering flux by the accretion
-may become important for H$\alpha$ for the edge-on ($i\sim90^{\circ}$)
-cases in which the disc obscures the stellar surface -- the main source
-of contiuum flux. We examine this effect later in section~\ref{sub:model-acc-disc-wind}.
-
-\section{Results}
-
-\label{sec:Results}
-
-\subsection{Magnetosphere}
-
-\label{sub:model-acc}
-
-Using the standard parameters (Table~\ref{tab:std_parameters}) for
-the central star and the magentosphere, we examine the dependency
-of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of accretion
-flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as similarly
-done by \citet{muzerolle:2001} for H$\beta$. The hot ring temperature
-is computed from the avilable kinetic energy of the free-falling gas
-as describe by \citet{hartmann:1994} while \citet{muzerolle:2001}
-used the constant hot ring temperature ($8000\,\mathrm{K}$) for most
-of their models. The accretion luminosity ($L_{\mathrm{acc}}$) of
-models with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-is about a half of the total luminosity (without the hot ring) of
-the star, and $L_{\mathrm{acc}}$is proportional to $\dot{M}_{\mathrm{acc}}$.
-The results are placed in Figure~\ref{fig:atlas_acc_models}. Overall
-dependency on $T_{\mathrm{max}}$ and $\dot{M}_{\mathrm{acc}}$ are
-similar to that of \citet{muzerolle:2001}. In general, the line strength
-becomes weaker as the accretion rate and the temperature become smaller.
-The red-shifted absorption becomes less visible for higher accretion
-rate and temperature models in which the flux in the damping wings
-become important. Figure~\ref{fig:broadening} shows an example of
-the effect of the boradening of H alpha (with $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$)
-due to the damping constants as described in section~\ref{sec:radiative-transfer-model}.
-Although the maximum flux of the model with the broadening is almost
-identical to that of the model with no damping constant ($\Gamma=0$),
-a significant increase of the line flux in both red and blue wings
-of seen in the model with broadening. A weak red-shifted absorption
-component (which is a signiture of the magnetospherical accretion)
-is weakened or eliminated by the flux in broadened wing.
-
-Table~\ref{tab:ha_ew_acc_models} shows the EW for the models shown
-in Figure~\ref{fig:atlas_acc_models}. About a half of the models
-shown the figure agree with the observed EW values of H$\alpha$ from
-30 TTS presented by \citet{alencar:2000} who found the EW of H$\alpha$
-ranges from $\sim3$~\AA\, to $\sim160$~\AA, and the mean to
-be $\sim55$~\AA. For the lowest $\dot{M}_{\mathrm{acc}}$ models,
-the EW values are smaller than the minimum EW observed by \citet{alencar:2000},
-and for some models the EWs are negative. Since the target selection
-criteria of \citet{alencar:2000} is not stated in their paper, we
-can not conclude that these low $\dot{M}_{\mathrm{acc}}$models disagree
-with the observation. \citet{reipurth:1996}, who measured the EW
-of 43 TTS and found similar distribution of EW values, mentioned that
-their EW measurements are underrepresenting real samples since the
-selection of the targerts are based on the strong H$\alpha$ emission
-in H$\alpha$ surveys.
-
-The dependency of the profile on the inclination angle ($i$) is demonstrated
-in Figure~\ref{fig:acc_inclination_effect}. The model uses the same
-paramters as in Figure~\ref{fig:broadening} (with broadening, $T_{\mathrm{max}}=7500\,\mathrm{K}$
-and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).
-The figure show that the peak (normalized) flux decrease as the inclination
-angle increases. Similarly, the equivalent width also decreases as
-the inclination increases. Because of the geometry of the magnsepsherical
-accretion (c.f. Figure~\ref{fig:overview}) and of the presence of
-the gas with the highest velocity close to the stellar surface, the
-highest red-shifted line-of-sight velocity is visible only at the
-high incination angles. This explains the wider appearence of the
-profile with $i=80^{\circ}$compared to the relatively narrow line
-appearence of the profile with $i=10^{\circ}$. Although not show
-here, a similar depdency on the inclination angle is found for the
-models with different temperatures ($T_{\mathrm{max}}=6500$, $8500$,
-$9500\,\mathrm{K}$).
-
-As seen in the models of \citet{hartmann:1994} and \citet{muzerolle:2001},
-our models also show the blue-shifted peak and the blue-ward asymmetry
-caused by the occultation of the accretion flow by the equotrial disc
-and the stellar disc. On the hand, \citealt{alencar:2000} (see their
-Fig.~9) found a substential fraction of the observed H$\alpha$ profiles
-also shows the {}``red-shifted'' peak, and the P~Cygni profiles
-which can not be explained by the magnetospherical accretion model
-alone. In addition, a recent study by \citet{appenzeller:2005} showed
-that the equivalent width of H$\alpha$ increases as the inclination
-angle increases. Our model with the magnetospherical accreation flow
-clearly disagrees with their finding.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/atlas_ha_i55_acc_model_new3.eps}
-
-\end{center}
-
-\caption{H$\alpha$ model profiles for wide ranges of mass accretion rate ($\dot{M_\mathrm{acc}}$) and temperature ($T_{\mathrm{max}}$).
-The profiles are computed using only magnetospherical accretion flow (i.e.
-no wind/jet).
-All the profiles are computed using the parameters of the 'standard' model (Table~\ref{tab:std_parameters}) and inclination $i=55^{\circ}$.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the mass accretion rate (indicated by the values in $\mathrm{M_{\odot}\,yr^{-1}}$ at the top) increases from left to right.
-The profiles are similar to those of \citet{muzerolle:2001}, available on-line (http://cfa--www.harvard.edu/cfa/youngstars/models/magnetospheric\_models.html).
-}
-
-\label{fig:atlas_acc_models}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table}
-
-\begin{center}
-
-\begin{tabular}{cccc}
-\hline 
-$T_{\mathrm{max}}\,\,\left(\mathrm{K}\right)$&
-&
-$\dot{M}_{\mathrm{acc}}$ ~$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-\tabularnewline
-&
-$10^{-7}$&
-$10^{-8}$&
-$10^{-9}$\tabularnewline
-\hline 
-$6500$&
-$17.9$&
-$0.1$&
-$0.0$\tabularnewline
-$7500$&
-$25.2$&
-$-0.9$&
-$-0.5$\tabularnewline
-$8500$&
-$68.3$&
-$6.5$&
-$-0.7$\tabularnewline
-$9500$&
-$98.6$&
-$52.4$&
-$1.3$\tabularnewline
-\hline
-\end{tabular}
-
-\end{center}
-
-\caption{The summary of H$\alpha$ equivalent widths from the magnetospherical accretion flow models show in Figure~\ref{fig:atlas_acc_models}.}
-
-\label{tab:ha_ew_acc_models}
-
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/broadening.eps}
-
-\end{center}
-
-\caption{Effect of the line broadening for H$\alpha$.
-The model computed with the damping constant ($\Gamma$), described in section~\ref{sec:radiative-transfer-model} (solid),  is compared with the one with no damping constant, $\Gamma=0$ (dashed).
-Both models are computed with  $T_{\mathrm{max}}=7500~\Kelvin$,  $i=55^{\circ}$, and the standard parameters given in Table~\ref{tab:std_parameters}.
-The two models have similar peak flux levels (around $V \sim 0~\kmps$), but the total flux and the EW of the line increased drastically for the model with the damping constant.
-The broaded wings extend to $\sim \pm 900 \kmps$.
-The redshifted absorption feature (very weakly) seen in the  $\Gamma=0$ model are not seen in the model with the broadening.
-}
-
-\label{fig:broadening}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/acc_inc_effect.eps}
-
-\end{center}
-
-\caption{Dependecy of H$\alpha$ profiles on inclination ($i$).
-The profiles are computed with the magneospherical accretion flow using the standard parameters given in Table~\ref{tab:std_parameters} and $T_{\mathrm{max}}=7500~\Kelvin$.
-The solid, dotted, and dashed lines are for $i=10^{\circ}$, $55^{\circ}$, and $80^{\circ}$ respectively.
-As the inclination becomes larger, the peak flux and the equivalent width of the line becomes smaller.
-Similar dependency is seen in the models with $T_{\mathrm{max}}=6500, 8500, 9500$~K (not shown here).
-}
-
-\label{fig:acc_inclination_effect}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Collimated Wind}
-
-\label{sub:model-wind}
-
-As mentioned in earlier, the magnetopsherical accretion flow model
-alone cannot explain some of the feartures seen in observations. As
-an alternative model, we now examine formation of H$\alpha$ in a
-simple collimated wind as described in section \ref{sub:wind_jet}.
-The basic wind model parameters introduced earlier are $\gamma$,
-$\beta$, $v_{\infty}$, $b$, $\theta_{\mathrm{wind}}$, $T_{\mathrm{wind}}$
-and $\dot{M}_{\mathrm{wind}}$. To minimize the number of parameters
-to be explored, we initially adopte $\gamma=0.05$, $v_{\infty}=200\,\kmps$
-\citep{appenzeller:2005} and $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$.
-Futher, the angular extent of the wind is assumed to be close to the
-edge of the accretion disc, i.e. $\theta_{\mathrm{wind}}=80^{\circ}$;
-however, in this section, a simple optically-thick and geometrically-thin
-(i.e. opaque and zero-thickness) disc instead of the standard $\alpha$-disc
-(section~\ref{sub:Accretion-disc}) is used in all models for speed.
-The effect of replacing the geometrically thin disc with the $\alpha$-disc
-will be discussed later in this section. The degree of collimination
-is initially chosen to be $b=4$, i.e. the ratio of the density in
-polar direction to the density at the edge of the wind closest to
-the accretion disc is about $\left(\cos0^{\circ}/\cos80^{\circ}\right)^{4}\approx10^{3}$,
-for given radii. With these parameters kept constant, we examine the
-characterstics of H$\alpha$ profiles, as a function of the wind accereation
-paramter $\beta$ and the isothermal wind temperature $T_{\mathrm{wind}}$.
-Dependency on the other parameters will be discussed later in this
-section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_model.eps}
-
-\end{center}
-
-\caption{H$\alpha$ model profiles computed with wide ranges of the isothermal wind temperature ($T_{\mathrm{wind}}$) and the wind accerelation rate ($\beta$).
-The profiles are computed with only wind/jet (no magnetospherical accretion flow).
-The parameters of the 'standard' model (Table~\ref{tab:std_parameters}) are used.
-The wind mass-loss rate ($\dot{M}_{\mathrm{wind}}$), the inclination ($i$) and the degree of collimination ($b$) are fixed at $10^{-8}~{\mathrm{M_{\sun}~yr^{-1}}}$,  $55^{\circ}$ and $4.0$\, respectively.
-The temperature (indicated along the vertical axis) of the model increase from top to bottom, and the wind accerelation rate increases from left to right.
-The P~Cygni profile are seen for lower $T_{\mathrm{wind}}$ and lower $\beta$ (slow accerelation) models.
-The postion of the absorption the component moves toward the line centre as $\beta$ increases.
-The effect of line broadening becomes more prominant for higher $T_\mathrm{wind}$ and higher $\beta$ models.}
-
-\label{fig:atlas_wind_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The results are shown in Figure~\ref{fig:atlas_wind_model}. The
-P~Cygni profile are seen only in the models with lower $T_{\mathrm{wind}}$
-and $\beta$ (colder and faster accerelation wind). As the value of
-$\beta$ increases, the postion of the blue-shifted absorption component
-moves toward the line centre. For the slowest wind accerelation models
-($\beta=4.0$), the absorption components appear to be located at
-the line centre, giving the appearence of the double-peak emission
-profile. The line strength is very senstive to the temperature of
-the wind. Although the line should be also sensitive to the temperature
-structure of the wind itself, determination of a self-consistent wind
-temperature is beyound the scope of this paper. Readers are refered
-to \citet{hartmann:1982} in which the wind temperature structure
-is determined by balancing the radiative cooling rate (assuming optically
-thin) with the MHD wave heating rate.
-
-The effect of line broadening becomes more prominant for higher $T_{\mathrm{wind}}$
-and higher $\beta$ models. Unlike the magnetospherical accretion
-only models (Figure~\ref{fig:atlas_acc_models}), the inverse P~Cygni
-profiles are not seen here. Interestingly, in some models (e.g. $T_{\mathrm{wind}}=9000\,\mathrm{K}$
-and $\beta=1.0$ model), the absorption componet is present at slightly
-red-ward of the line centre, causing the blue-ward asymmetry seen
-in the magnetospherical accretion models. The blue-ward asymetry are
-caused by: 1. the accretion disc placed at the equotorial plane and
-the finited-size steller disc blocking a part of the line emission
-region moving away from an observer, 2.~the much larger optical depth
-for the line emitted from the opposite side of the observer where
-the gas is moving away from the observer. Because of the broad wings
-of the Voigt profile, the line photon intereacts with the gas with
-much wider range of the projected velocity space.
-
-The dependency of the profile on the wind anisotoropy parameter $b$
-is demonstrated in Figure~\ref{fig:effect_wind_b_param}. The line
-peak closer to the line centre and the profile becomes slightly more
-symmetric around the line centre for the isotropic ($b=0$) compared
-to the cases with the colliminated wind ($b=4$). The P~Cygni profile
-feature become prominant for the spherical wind models (especially
-in $\beta=0.5$ model) because the collumn density of along the line
-of a sight of the observer at a medium inclination angle ($i=55^{\circ}$)
-increases as the wind becomes more spherical for a given value of
-the wind mass-loss rate.
-
-Next, we examine the effect of the size of the inner radius of the
-disc and the distribution of the H$\alpha$ emission region. Figure~\ref{fig:effect_thin_disc}
-shows the wind emission profile computed with and without the equotorial
-accretion disc. The latter can be also considered as a model with
-a large inner radius of the accretion disc in which none of the wind
-emission region is not blocked provided the inclination is moderate.
-The profile shapes of the models are very similar to each other, but
-the one without the accretion disc is slightly more symmetric than
-the other. As one expects, the line equivalent width of the model
-without the disc is about twice of the model with the disc. Interestingly,
-the blueward asymmetry is present also in the profile computed without
-the disc. This is mainly caused by the occultaion of a part of emission
-region by the steller disc and the fact that the wind (density distribution)
-is asymmetric. The H$\alpha$ image (project in the plane of the observer
-at the location of the star) for the model with the disc (middle panel)
-and that for the model without (right plane) are also shown in the
-same figure. The images weere computed with a fast wind accereation
-rate ($\beta=0.5$). The extent of the line emission is smaller ($\sim0.2\,\mathrm{AU}$
-or $\sim20\, R_{*}$) compared to the spectro-astrometric observations
-of \citet{takami:2003} for RU~Lup and CS Cha which have 1--5 AU
-scale outflows%
-\footnote{\citet{takami:2003} also showed that some objects (e.g~Z CMa and
-AS~353A) show the outflows of larger scale ($>50\,\mathrm{AU}$)
-which could be formed by shocks rather than MHD-wave heating (e.g.
-\citealt{hartmann:1982}) or X-ray heating (e.g.~\citealt{shang:2002}). %
-}; however, if a slower wind acceration rate ( $\beta=4$) is the emission
-region become larger slightly ($\sim0.4$~AU).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{cc}
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/wind_b_effect.eps}&
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/windonly_B_effect.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{The effect of wind collimation.
-The dependecy of the line profiles on the wind anisotropy parameter $b$ for the models with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 0.5\right)$  is shown on left, and that with $\left(T_{\mathrm{wind}},~\beta \right) = \left( 9000\Kelvin, 1.0\right)$ on right.
-All the other parameters are same as in Figure~\ref{fig:atlas_wind_model}.
-The degree of the blue-ward asymmetry of the profiles is slightly lower for the spherical (isotroptic) wind model ($b=0$, dashed) compared to the collimated wind (anisotoropic) wind models ($b=4$, solid).
-The P~Cygni profile feature become prominant for the spherical wind models (especially in $\beta=0.5$ model) since the collumn density of along the line of a sight of the observer at a medium inclination angle ($i=55^{\circ}$) increases for lower $b$ values for a fixed mass-loss rate of the wind.
-}
-
-\label{fig:effect_wind_b_param}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\begin{tabular}{ccc}
-\includegraphics[%
-  clip,
-  scale=0.3]{figures/disc_nodisc_compare.eps}&
-\includegraphics[%
-  scale=0.3,
-  angle=270,
-  origin=lt]{figures/wind_thindisc.eps}&
-\includegraphics[%
-  scale=0.3,
-  angle=270,
-  origin=lt]{figures/wind_nodisc.eps}\tabularnewline
-\end{tabular}
-
-\end{center}
-
-\caption{Comparison of of the wind model with and without the optically-thick and geometrically-thin disc.
-The latter can be also equivalent to a model with a large inner radius of the accretion disc in which none of the wind emission region is not blocked provided the inclination is moderate.
-The left panel shows the profile computed with $i=55^{\circ}$, $\beta=0.5$ and $T_{\mathrm{wind}} = 9000~\mathrm{K}$ (see text for other parameters used).
-The line profile of the model with the disc (solid) is similar to the model without the disc (dashed), but the latter is slightly more symmetric than the former.
-The line equivalent width of the model without the disc is about 2 times that of the model with the disc.
-The blueward asymmetry is present also in the profile computed without the disc.
-The H$\alpha$ image (project in the plane of the observer) for the model with the disc (middle panel) and that for the model without (right plane) are also shown.
-The image flux is computed by integrating the specific flux over the wavelength range ($-800\,\kmps < v < 800\,\kmps$.
-The flux is in an arbitrary units and in logarithmic (base $10$) scale.
-}
-
-\label{fig:effect_thin_disc}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magnetosphere $+$ wind}
-
-\label{sub:model-acc-wind}
-
-Next, we examine the characteristics of the line profiles arising
-from the combination of the magnetospherical accretion flow and the
-wind. For simplicity, we fix the parameters for the magnetosphere
-($T_{\mathrm{max}}=7500\,\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$
-as in Figure~\ref{fig:atlas_acc_models}), and use the constant wind
-mass-loss rate $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
-(i.e.~$\dot{M}_{\mathrm{wind}}=0.1\,\dot{M}_{\mathrm{acc}}$). Figure~\ref{fig:atlas_wind_acc_model}
-shows the results for $i=55^{\circ}$ and the same combinations of
-$T_{\mathrm{wind}}$ and $\beta$ used in section~\ref{sub:model-acc-wind}
-(Figure~\ref{fig:atlas_wind_model}).
-
-While the emission from the magnetosphere dominates for the models
-with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation
-and the colder wind models), the emission from the wind dominates
-for the models with larger $\beta$ and $T_{\mathrm{wind}}$ (the
-slower accerelation and the hotter models). The P~Cygni profile feature
-becomes less prominant in some of the models because the additional
-emission from the magnetosphere extending in the wings. In most of
-the cases, the profiles are understood as a simple sum of the magnetospherilcal
-component and the wind component.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.9]{figures/atlas_ha_i55_wind_acc_model.eps}
-
-\end{center}
-
-\caption{Same as Figure~\ref{fig:atlas_wind_model}, but the models include the magnetospherical accretion flow (with $T_{\mathrm{\max}}=7500~\mathrm{K}$ and $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ as in Figure~\ref{fig:atlas_acc_models}).
-While the emission from the magnetosphere dominates for the models with smaller $\beta$ and $T_{\mathrm{wind}}$ (the faster accerelation and the colder wind models), the emission from the wind domnates for the models with models with larger $\beta$ and $T_{\mathrm{wind}}$  (the slower accerelation and the hotter models).
-The P~Cygni profile feature becomes less prominant in some of the models because of the extra emission from the magnetosphere extends in the wings.}
-
-\label{fig:atlas_wind_acc_model}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Magentosphere $+$ disc $+$ wind}
-
-\label{sub:model-acc-disc-wind}
-
-\begin{itemize}
-\item Flux contribution by scattering of photon by disc?
-\end{itemize}
-
-\subsection{Summary}
-
-\section{Discussion}
-
-\label{sec:Discussion}
-
-\subsection{Classification scheme proposed by Reipurth et. al (1996)}
-
-\citet{reipurth:1996}proposed the two-dimentional classification
-of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
-stars. Their classification scheme contains four classes (I, II, III
-and IV) differenciated by the ratio of the secondary-to-primary emission
-components in the profiles. Each classes are devided into two sub-classes
-(B and R) which depends whether the absorption componet is on the
-blue or red side. Readers are refered to Fig.~4 of their paper. Figure~\ref{fig:atlas_reipurth}
-shows the sample profiles which are classified according to the definition
-of \citet{reipurth:1996}. The corresponding model parameters are
-given in Table~\ref{tab:classification}. As we can see from this
-figure, the combinatioin of the wind, magnetospherical accretion,
-and accretion disc can reasonably reproduce all the classes of the
-profiles seen in observations.
-
-Within the parameter space covered, we find it is difficult to produce
-Type I type profile, which is very symmetric around the line centre
-and without any absorption feature, if the wind component is added
-in the model. Type II-B are
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.65]{figures/atlas_reipurth_like.eps}
-
-\end{center}
-
-\caption{Sample H$\alpha$ model profiles which charactersize the classfication by \citet{reipurth:1996}.
-The combination of magnetospherical accretion flow, the accretion disc, and the colliminated wind model can reasonably reproduce wide ranges of H$\alpha$ profiles seen in observations.
-The model parameters and short comments are summarised in Table~\ref{tab:classification}.
-The horizontal axises are velocities in $\kmps$, and the vertical axises are nomalized fluxes.
-}
-
-\label{fig:atlas_reipurth}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table*}
-
-\begin{center}
-
-\begin{tabular}{llllllll}
-\hline 
-&
-$i$&
-$\dot{M}_{\mathrm{acc}}$&
-$T_{\mathrm{max}}$&
-$\dot{M}_{\mathrm{wind}}$&
-$T_{\mathrm{wind}}$&
-$\beta$&
-Comment\tabularnewline
-Class&
-$\left(\mathrm{deg.}\right)$&
-$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-$\left(10^{3}\,\mathrm{K}\right)$&
-$\left(\mathrm{M_{\sun}\, yr^{-1}}\right)$&
-$\left(10^{3}\,\mathrm{K}\right)$&
-$\left(-\right)$&
-\tabularnewline
-\hline 
-I&
-$55$&
-$10^{-7}$&
-$7.5$&
-$-$&
-$-$&
-$-$&
-Accretion dominated possibly without the wind at a mid inclination.\tabularnewline
-II-B&
-$10$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$1.0$&
-Accretion and wind, mid wind accerelation rate, low inclination\tabularnewline
-III-B&
-$10$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$8.0$&
-$2.0$&
-Accretion and wind, with slow wind accerelation rate, low inclination\tabularnewline
-IV-B&
-$55$&
-$-$&
-$-$&
-$10^{-8}$&
-$8.0$&
-$0.5$&
-Accretion dominated (low accretion rate), mid inclination \tabularnewline
-II-R&
-$55$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$2.0$&
-Wind dominated, with fast wind accerelation rate, mid inclination\tabularnewline
-III-R&
-$80$&
-$10^{-7}$&
-$7.5$&
-$10^{-8}$&
-$9.0$&
-$1.0$&
-Wind dominated, slow wind acceralation rate, high inclination \tabularnewline
-IV-R&
-$55$&
-$10^{-9}$&
-$9.5$&
-$-$&
-$-$&
-$-$&
-Accreetion dominated possibly without the wind at a mid inclination.\tabularnewline
-\hline
-\end{tabular}
-
-\end{center}
-
-\caption{The summary model parameters for the profiles in Figure~\ref{fig:atlas_reipurth} and brief comments.}
-
-\label{tab:classification}
-
-\end{table*}
-
-\subsection{Comparisons with observations}
-
-For a demonstrative purpose, we performed preliminary model fit of
-H$\alpha$ observarions
-
-\begin{itemize}
-\item other possible model? Better wind model?
-\item Any other bussiness?
-\end{itemize}
-
-\section{Conclusions}
-
-\label{sec:Conclusions}
-
-We presented the detailed study of the H$\alpha$ formation from the
-circumstealler material of classical T~Tauri stars. AND MORE.
-
-Future studies include:
-
-\begin{enumerate}
-\item Improvement of the wind model. Temperature structure estimate by Hartmann()
-Alancar's paper. Disc-wind model of Branford and ...
-\item Try it with MHD model.
-\item Include the scattering flux term although this requires $N_{\phi}\times N_{\theta}$
-more times to compute a profile. 
-\item Polarization study to explore the geometry and the rotation of the
-disc. 
-\item Gas in the accretion disc (inner most part and the outer layer of
-the disc).
-\item Variability study using a 3D model.
-\end{enumerate}
-\section*{Acknowledgements}
-
-RK is supported by PPARC standard grand PPA/G/S/2001/00081.
-
-%
-
-%
-
-%
-
-%----------------------------------------------------
-
-% Bibliography follows here.
-
-%-----------------------------------------------------
-
-%
-
-%
-
-%
-
-\bibliographystyle{mn}
-
-\bibliography{mnras}
-
-%
-
-\label{lastpage}
 \end{document}

### 2006-04-05 TTau_Halpha/for_ref.tex
Revised version after the refree's report
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@693 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-01-30 TTau_Halpha/kurosawa.tex
@@
 
+Testing the reference here. \citet{calvet:2004}. \citet{calvet:1998}, \citet{gullbring:2000}.
+\citet{muzerolle:1998}, \citet{bouvier:2003}, \citet{johns:1995}.
+
 \section*{Acknowledgements}
@@
 %
+
 \bibliographystyle{mn}

### 2006-04-05 TTau_Halpha/revision01/kurosawa.tex
Revised version after the refree's report
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@693 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-02-02 TTau_Halpha/submit/kurosawa.tex
@@
 asymmetric emission line profiles as resulting from the partial
-occultation of the flow by the stellar photosphere, while inverse
+occultation of the flow  by the inner part of the accretion disc and
+by the stellar photosphere, while inverse 
 P~Cygni profiles in the MA model result from inflowing material at
@@
 10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
-be absorbed by the gas locally, and re-emitted  optical and UV
-radiation (\citealt{koenigl:1991}; \citealt*{hartmann:1994}). This
+be absorbed by the gas locally, and re-emitted as optical and UV
+(\citealt{calvet:1998}; \citealt{gullbring:2000}). This
 will create hot rings where the magnetic field intersects with the
@@
 star given above (Table~\ref{tab:std_parameters}), about $8$~per~cent
-of the surface is covered by the hot rings. If the mass-accretion rate
-is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of this accretion
+of the surface is covered by the hot rings. 
+In our model, the fraction of hot-ring coverage area is
+determined only by the geometry of the magnetosphere
+(Section~\ref{sub:Magnetosphere}). \citet{gullbring:2000} estimated the
+fractions of the hot-ring coverage area for three intermediate CTTS by
+using the observed UV and optical spectra. They found the range of
+fraction to be 0.3--3.0~per~cent.  This is smaller than the value adopted
+here; however, even if we use 1~per~cent hot-ring area
+coverage model (by changing the width of the magnetosphere), we
+find the line shapes of H$\alpha$ do not change significantly.
+
+If the mass-accretion rate
+is $10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$, the ratio of the accretion
 luminosity to the photospheric luminosity is about $0.5$, and the
 corresponding temperature of the hot rings is about
-$6400\,\mathrm{K}$.  The continuum emission from the hot rings is
-taken into account when computing the line profiles.
+$6400\,\mathrm{K}$.  The luminosity ratio and the temperature depend
+on a adopted mass-accretion rate. The continuum emission from the hot
+rings is taken into account when computing the line profiles.
 
@@
 
-\caption{Summary of the reference classical T~Tauri star model parameters.}
+\caption{Summary of the reference classical T~Tauri star model
+  parameters. Note that a typical mass-accretion rate of CTTS is $\sim 3
+  \times 10^{-8}\,\mathrm{M_{\sun}\, yr^{-1}}$
+  (e.g. \citealt{gullbring:1998}; \citealt{calvet:2004}); however, a
+  slightly higher mass-accretion rate is adopted here to demonstrate the 
+  effect of line-broadenings more clearly (c.f. Section~\ref{sub:model-acc}). }
 \label{tab:std_parameters}
@@
 
-We adopt the MA flow model of \citet{hartmann:1994},
+We adopt the MA flow model of \citet*{hartmann:1994},
 as done  by \citet{muzerolle:2001} and by \citet*{symington:2005},
@@
 and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
-the equatorial plane) are set to be $2.2\, \mathrm{R_{\sun}}$ and $3.0\, \mathrm{R_{\sun}}$
+the equatorial plane) are set to be $2.2\, R_{*}$ and $3.0\, R_{*}$
 respectively. The geometry of the magnetic field/stream
@@
 energy, the velocity and the density of the accreting gas along the
-steam line are found as in \citet{hartmann:1994}.
+stream line are found as in \citet{hartmann:1994}.
 
@@
 the major contributors to the cooling process are bremsstrahlung
-radiation and line emission from Ca~II and Mg~II ions. The results of
-\citet{martin:1996} qualitatively agree with those of
-\citet{hartmann:1994}.
+radiation and line emission from Ca~II and Mg~II ions. 
+Although the model of \citet{martin:1996} seems to be more comprehensive
+than that of \citet{hartmann:1994}, \citet*{muzerolle:1998} found that
+the line profile models computed according to the temperature
+structure of the former do not agree with observations while they do
+have much better agreement when the temperature of the latter model was
+used.  The temperature structure of the magnetosphere is still a big
+uncertainty in the accretion model; however, for a heuristic reason,
+we adopted the model of \citet{hartmann:1994}.
 
@@
 disc has $q=-1.15$.  In order to be consistent with the collimated
-disc-wind model of \citet{krasnopolsky:2003} who used $p=-5/2$, the
+disc-wind model of \citet{krasnopolsky:2003} who used $p=-7/2$, the
 value of $\alpha$ is set to 0.76. The constant of proportionality in
@@
 surface along stream lines respectively. $R_{s}$ is the wind scale
-length, and its value is set to 10~$R_{\mathrm{mi}}$ by following
+length, and its value is set to 10~$R_{\mathrm{wi}}$ by following
 \citet{long:2002}.
@@
     $\beta$. In the far field ($l>10$~au), the density is approximately
-    proportional to $\sim l^2$. }
+    proportional to $\sim l^{-2}$. }
 
@@
 \subsubsection{Dust model}
+\label{sub:dust-model}
 
@@
 centre of the surface element ($\mathrm{d}A=p\,\sin
-q\,\mathrm{d}q\,\mathrm{dp}$).  The code execution time is
+q\,\mathrm{d}q\,\mathrm{d}p$).  The code execution time is
 proportional to $n_{p}\, n_{q}\, n_{\nu}$ where $n_{p}$ and $n_{q}$
@@
 scattering opacity which are calculated using the dust property
-described in Section~\ref{eq:grain-dist-function}.  We neglect the
+described in Section~\ref{sub:dust-model}.  We neglect the
 emissivity from the disc: since the disc masses of CTTS are rather small
@@
 
-Using the reference model parameters (Table~\ref{tab:std_parameters}) for the
-central star and the magnetosphere, we examine the dependency of
-H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of the accretion flow
-and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as
-done by \citet{muzerolle:2001} for H$\beta$. We note that here we have
- computed the hot ring temperature self-consistently, whereas \citet{muzerolle:2001} used
-a constant hot ring temperature ($8000\,\mathrm{K}$) for most of
-their models.  The accretion luminosity ($L_{\mathrm{acc}}$) for models
-with $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ is
-about a half of the photospheric luminosity.
+Using the reference model parameters (Table~\ref{tab:std_parameters})
+for the central star and the magnetosphere, we examine the dependency
+of H$\alpha$ on the temperature ($T_{\mathrm{max}}$) of the accretion
+flow and the mass accretion rate ($\dot{M}_{\mathrm{acc}}$), as done
+by \citet{muzerolle:2001} for H$\beta$. 
+The temperature structure of \citet{hartmann:1994} is  adopted here,
+and the parameter $T_{\mathrm{max}}$ sets the maximum temperature of the accretion
+streams. 
+We note that here we have
+computed the hot ring temperature self-consistently, whereas
+\citet{muzerolle:2001} used a constant hot ring temperature
+($8000\,\mathrm{K}$) for most of their models.  The accretion
+luminosity ($L_{\mathrm{acc}}$) for models with
+$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$ is about
+a half of the photospheric luminosity.
 
@@
 figure shows that the peak (normalised) flux decreases as the
-inclination angle increases, as does the EW.  The line flux and the
-EWs decrease mainly because the fraction of the accretion stream
-blocked by the photosphere increases as the inclination increases.
+inclination angle increases, as does the EW.  
+The line flux and the EWs decrease mainly because (1)~the fraction of
+the accretion stream blocked by the photosphere increases as the
+inclination increases (c.f.~Fig.~\ref{fig:config_discwind}, lower-left
+part of the accretion stream i.e.~$z<0$ and $x<0$), and (2)~the
+fraction of the accretion stream blocked by the inner part of the
+accretion disc increases as the inclination increases
+(c.f.~Fig.~\ref{fig:config_discwind}, lower-right part of accretion
+stream i.e.~$z<0$ and $x>0$). While the photosphere mostly blocks the
+blue-shifted part of the stream, the inner disc blocks the red-shifted
+part.
 The line EW in Fig.~\ref{fig:acc_inclination_effect} changes from
 32 to 21\,\AA\, as the inclination changes from $10^\circ$ to
-$80^\circ$, i.e. a fractional change of 0.65.  On the other hand,
+$80^\circ$, i.e.~a fractional change of 0.65.  On the other hand,
 the 10~per~cent width of the line changes from 290~$\kmps$ to
 470~$\kmps$; hence, the fractional change is 1.6.  
+A similar EW dependence on
+inclination angle is found for the models with different 
+magnetospheric temperatures and the mass-accretion rates.
 
@@
 the presence of the gas with the highest velocity close to the stellar
-surface, the highest red-shifted line-of-sight velocity is visible
-only at the high inclination angles. This explains the wider
-appearance of the profile with $i=80^{\circ}$ compared to the
-relatively narrow line appearance of the profile with
-$i=10^{\circ}$.  A similar EW dependence on
-inclination angle is found for the models with different 
-magnetospheric temperatures and the mass-accretion rates.
+surface, the highest blue-shifted line-of-sight velocity is seen 
+only at the high inclination angles. For example, the
+accretion stream close to the photosphere ($\sim 1R_{*}$ above the
+photosphere) on the upper-left
+quadrant in Fig.~\ref{fig:config_discwind} ($x<0$ and $z>0$) will be
+more aligned with the line-of-sight of an observer in the upper-right
+quadrant in the same figure ($x>0$ and $z>0$) as the inclination
+increases. This results in a slight increase in the blue wing flux for
+a higher inclination model as seen in
+Fig.~\ref{fig:acc_inclination_effect}.
 
@@
 for the slowest wind acceleration model 
-($\beta=4.0$) is located close the line centre ($\sim 20\,\kmps$).
+($\beta=2.0$) is located close the line centre ($\sim 20\,\kmps$).
 
@@
     0.5$ for $i=55^{\circ}$.  The profiles in the figure use $d = 
-   2~R_{*}$ (dashed),   $7~R_{*}$ (dash-dot) and $88~R_{*}$
-    (dash-dot). All the other parameters are same as in
+   2~R_{*}$ (dashed),   $7~R_{*}$ (dash-dot) and $22~R_{*}$
+    (solid). All the other parameters are same as in
     Fig.~\ref{fig:atlas_discwind_only}.  As the wind becomes more
@@
     The P-Cygni absorption disappears for the model with a small
-    collimation (e.g.~$d = 2~R_{*}$ case) since the opening angel of
+    collimation (e.g.~$d = 2~R_{*}$ case) since the opening angle of
     the disc wind is larger than the inclination angle. }
@@
 from the symmetry axis) is given by
-$\theta_{\mathrm{open}}=\arctan\left( d/R_{\mathrm{wi}} \right)$.
+$\theta_{\mathrm{open}}=\arctan\left( R_{\mathrm{wi}}/d \right)$.
 Fig.~\ref{fig:discwind_d_effect} shows the profiles computed for $d
-= 2~R_{*}$, $7~R_{*}$ and $88~R_{*}$ for the inclination angle
+= 2~R_{*}$, $7~R_{*}$ and $22~R_{*}$ for the inclination angle
 $i=55^{\circ}$.  As the wind becomes more collimated (larger $d$), the
@@
 opening angle of the disc wind is greater than the inclination angle.
-For the disc wind models presented in this paper, we use $d=44~R_{*}$
+For the disc wind models presented in
+Fig.~\ref{fig:atlas_discwind_only}, we use $d=22~R_{*}$ 
 in order to have a moderate amount of wind absorption at a moderate
 inclination angle ($i\sim60^\circ$).
+
+\citet{blandford:1982} showed that in order to launch a wind from a
+disc plane magneto-centrifugally, the launching angle ($\theta_{L}$,
+measured from the equatorial disc plane) must be less than $60^{\circ}$.
+ In our models, the wind launching zone is restricted in
+between $R_{\mathrm{wi}} < w_{i} < R_{\mathrm{wo}}$ (see
+Fig.~\ref{fig:config_discwind} and Table~\ref{tab:std_parameters}) with
+$R_{\mathrm{wi}} = 3\,R_{*} $ and 
+$R_{\mathrm{wo}}=1$~au.  This sets the upper limit of the source displacement
+distance ($d$) to be around $5.2\,R_{*}$ if we want to satisfy the
+launching angle condition of \citet{blandford:1982} for all the
+stream lines in our disc wind model.  In the models presented in
+Fig.~\ref{fig:atlas_discwind_only} (and later in
+Fig.~\ref{fig:atlas_hybrid} in next section), we have adopted 
+$d =22\, R_{*}$ instead. This means that some part of the disc
+wind ($3\,R_{*} < w_{i} < 25.4\,R_{*}$) may not be able to be launched
+from the disc plane according to the model of \citet{blandford:1982}.
+We have used a larger launching angle or a larger source displacement
+distance for the following two reasons: (1)~to simulate more
+\emph{collimated} wind (toward the symmetry axis, and (2)~to be more
+consistent with the fraction of H$\alpha$ profiles affected by wind
+absorptions in observations.
+
+Since the stream lines in our simple disc wind are represented by
+straight lines, the wind never bends toward the symmetry axis ($z$-axis)
+as the distance from the disc increases unlike the
+model of \citet{blandford:1982}. We therefore used a larger
+launching angle to simulate the stream lines in the far field (at a larger
+distance from the disc plane) in their model.  This is an intrinsic
+problem with approximating the stream lines with straight lines. A
+better model is perhaps to compute the field lines using
+\citet{blandford:1982} model as done so in \citet{alencar:2005}.
+Also, in our mode, if the launching angle is too small
+($<60^{\circ}$), the wind absorption feature would be not been seen
+or would be 
+very small for profiles computed with an inclination angle
+$i<60^{\circ}$.  If the launching angle is $60^{\circ}$ at the inner
+most part of the wind, and the inclination 
+angle (measured from the symmetry axis, $z$-axis) is less than $60^{\circ}$,
+little (wind) absorption is expected, as demonstrated in Fig.~\ref{fig:discwind_d_effect}.
+The situation will however change if the field/stream lines are not
+straight and bending towards the symmetry axis as the wind travel
+higher above the disc.  Since more than 50~per~cent of observed
+H$\alpha$ profiles (e.g. \citealt{reipurth:1996};
+\citealt{alencar:2000}) are affected by wind absorption, it was 
+necessary for our model to used the launching angle (at the inner most
+part) greater than $60^{\circ}$ to be more consistent with observations;
+although this would mean that the launching angle condition of
+\citet{blandford:1982} is violated for wind from a very inner part
+of the disc.
+
+In addition to the models given in Figs.~\ref{fig:atlas_discwind_only}
+and \ref{fig:atlas_hybrid}, we have computed the models with $d = 5\,
+R_{*}$ (not shown here) which satisfies the wind launching condition
+of \citet{blandford:1982} in all parts of the disc wind zone in our model.  These
+models showed that the wind absorption and emission features weaken,
+but overall morphology dependence of the profiles on the wind
+temperature rate and the wind acceleration rate is similar to what we
+found in the models shown in Figs.~\ref{fig:atlas_discwind_only} and
+\ref{fig:atlas_hybrid}.  The minimum inclination angle at which the
+wind absorption becomes important is larger than that of the models
+with a larger source displacement ($d = 22\, R_{*}$) as expected.
 
@@
 
-The effect of varying the wind mass-loss rate is shown in
+Finally, the effect of varying the wind mass-loss rate is shown in
 Fig.~\ref{fig:discwind_mdot_effect}. With all other parameters fixed,
@@
 \caption{A summary of the reference disc-wind model parameters used
-in Section~\ref{sub:result-discwind-knigge}. See also
-Section~\ref{sub:model-disc-wind}.}
+in Sections~\ref{sub:result-discwind-knigge} and \ref{sub:result-discwind-hybrid}.
+See also Section~\ref{sub:model-disc-wind}.}
 
@@
 
-\begin{tabular}{ccccccc}
+\begin{tabular}{cccccc}
 \hline 
-$d$&
 $R_{\mathrm{wi}}$&
@@
 $\left[R_{*}\right]$&
-$\left[R_{*}\right]$&
 $\left[\mathrm{au}\right]$&
-$\left[M_{\sun}\,\mathrm{yr^{-1}}\right]$&
+$\left[\mathrm{M_{\sun}\,yr^{-1}}\right]$&
 $[-]$&
@@
 \hline
-$22$&
 $3.0$&
@@
 $10^{-8}$&
-$-3/2$&
+$-7/2$&
 $2.0$&
@@
 used for the magnetosphere are  same as in 
-Fig.~\ref{fig:acc_inclination_effect}, and  the mass-loss rate of
+Fig.~\ref{fig:acc_inclination_effect} (with $i=55^{\circ}$ ), and  the mass-loss rate of
 the disc wind is 
@@
 Fig.~\ref{fig:atlas_hybrid} shows the models profiles
-computed using the same ranges of the disc-wind temperature and
+computed (at $i=55^\circ$) using the same ranges of the disc-wind temperature and
 wind acceleration parameter as in the previous cases.
@@
 An examination of the profiles in
-Figures~\ref{fig:atlas_discwind_only} and
-Fig.~\ref{fig:atlas_hybrid} reveals some problems
+Figs.~\ref{fig:atlas_discwind_only} and \ref{fig:atlas_hybrid} reveals
+some problems 
 with uniqueness that must inevitably occur when trying to assign an
@@
 P-Cygni absorption deepens only slightly, and the position of minimum
-flux in the absorption trough appears to move blue-ward.  On the other
-hand, the flux peak increase and the line wings become stronger as
+flux in the absorption trough appears to remain at same positions.  On the other
+hand, the flux peak increases and the line wings become stronger as
 $\mu$ increases.  Although MHD models suggest
@@
   surface brightness (arbitrary units) and the axes are linear
-  dimensions in au. The parameter used for the magnetosphere are as
+  dimensions in au. The parameters used for the magnetosphere are as
   the reference model in Table~\ref{tab:std_parameters}. The wind
@@
 this discussion.          
+Although in general H$\alpha$ in the spectra of CTTS shows a
+significant amount of variablity, which is in some cases induced by
+the rotational motion of an inclined magnetosphere
+(e.g.~\citealt{johns:1995}; \citealt{bouvier:2003}), we restrict our
+discussion in this section for the cases of axi-symmetric geometries.
 
@@
 inclination models.
+In addition to the models shown in Appendix~\ref{sec:appendix}, we
+have run a set of hybrid models (not shown here) with a typical
+mass-accretion rate for CTTS i.e. $3\times10^{-8}
+\mathrm{M_{\sun}\,yr^{-1}}$ (\citealt{gullbring:1998};
+\citealt{calvet:2004}) using $i=10^{\circ},55^{\circ},80^{\circ}$ with
+combinations of $\beta = 0.2, 0.5, 1.0, 2.0$ and
+$T_{\mathrm{wind}}=7000, 8000, 9000, 10000$~K. Based on these models,
+we found that Type~III-B profiles can be seen for at least in three
+models with fast accelerating and high wind temperature at moderate
+inclination angle i.e. $i = 55^{\circ}$ with $\left ( \beta,
+T_{\mathrm{wind}} \right ) = \left ( 0.2, 10000\,\Kelvin \right )$,
+$\left ( 0.5, 9000\,\Kelvin \right )$ and $\left ( 0.5, 10000\,\Kelvin
+\right )$.  A possible reason for not being able to find Type~III
+profiles in lower mass-accretion rate models (e.g. in
+$\dot{M}_{\mathrm{acc}} =
+1.0\times10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ models) is perhaps due
+to a wrong radial dependence ($p$ in
+equation~\ref{eq:discwind-massloss-w}) of the mass-loss rate per unit
+area adopted in our models.  This dependence shall be examined more
+carefully in future.
 
@@
 \citet{muzerolle:2001}. 
+The restriction in the inclination angle mentioned above would be
+relaxed if the axis of the magnetosphere is tilted with respect to the
+rotational axis since the line-of-sight to an observer from the
+accretion hot rings will pass through a different part of the
+magnetosphere as a rotational phase changes (as it precesses around
+the rotational axis).
 
@@
     $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=1.0$ respectively.
+    The wind mass-loss rates used in both models are
+    $\dot{M}_{\mathrm{wind}}=10^{-8}~\mathrm{M_{\sun}~yr^{-1}}$ . 
     All the other parameters are same as in
@@
 same inclination angles used for the disc-wind-magnetosphere hybrid
-model. The wind acceleration parameter ($\beta$) and the wind
+model. The mass-loss rate of the stellar wind in this model is
+$10^{-8}\, \mathrm{M_{\sun}\,yr^{-1}}$, which
+is same as the mass-loss rate used in the disc-wind magnetosphere
+hybrid model in the same figure.   In both models, the mass-accretion
+rate of $10^{-7}\, \mathrm{M_{\sun}\,yr^{-1}}$ is used.
+The wind acceleration parameter ($\beta$) and the wind
 temperature ($T_{\mathrm{wind}}$) used here are $1.0$ and
@@
 values are 54, 69, and 98\,\AA\, for $i=10^\circ$,
-$55^\circ$, and $80^\circ$ respectively.  This tendency of the
-inclination dependency holds for the models with this wind models for
-wide ranges of $\beta$ and $T_{\mathrm{wind}}$ providing that the
-emission from the wind is greater than that of the magnetosphere.
+$55^\circ$, and $80^\circ$ respectively.  
+This inclination dependency of EW is seen in the models with wide ranges of 
+$\beta$ and $T_{\mathrm{wind}}$, provided that the wind emission
+of the model is dominating the emission from magnetosphere.
+A similar inclination dependency of EW is found for lower wind
+mass-loss rate models
+(e.g.~$\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$)
+while keeping $\mu=0.1$.
 
@@
 
-This work is supported by PPARC standard grant PPA/G/S/2001/00081
-and PPARC rolling grant PP/C501609/1.
+We thank an anonymous referee who provided us valuable comments and
+suggestions which improved the clarity of the manuscript. This work
+was supported by PPARC standard grant PPA/G/S/2001/00081 and PPARC
+rolling grant PP/C501609/1.
 
@@
 %
+% All 8 or fewer should be listed, otherwise use at al.
 
@@
 {Blandford} R.~D., {Payne} D.~G., 1982, \mnras, 199, 883
+
+\bibitem[{{Bouvier} {et~al.}(2003){Bouvier}, {Grankin}, {Alencar}, {Dougados},
+  {Fern{\'a}ndez}, {Basri}, {Batalha}, {Guenther}, {Ibrahimov}, {Magakian},
+  {Melnikov}, {Petrov}, {Rud}, \& {Zapatero Osorio}}]{bouvier:2003}
+{Bouvier} J.~et al., 2003, \aap, 409, 169
 
@@
 
+\bibitem[{{Calvet} \& {Gullbring}(1998)}]{calvet:1998}
+{Calvet} N., {Gullbring} E., 1998, \apj, 509, 802
+
+\bibitem[{{Calvet} {et~al.}(2004){Calvet}, {Muzerolle}, {Brice{\~n}o},
+  {Hern{\'a}ndez}, {Hartmann}, {Saucedo}, \& {Gordon}}]{calvet:2004}
+{Calvet} N., {Muzerolle} J., {Brice{\~n}o} C., {Hern{\'a}ndez} J.,
+  {Hartmann}
+  L., {Saucedo} J.~L., {Gordon} K.~D., 2004, \aj, 128, 1294
+
 \bibitem[{{Camenzind}(1990)}]{camenzind:1990}
@@
 
+\bibitem[{{Gullbring} {et~al.}(2000){Gullbring}, {Calvet}, {Muzerolle}, \&
+  {Hartmann}}]{gullbring:2000}
+{Gullbring} E., {Calvet} N., {Muzerolle} J., {Hartmann} L., 2000, \apj, 544, 927
+
 \bibitem[{{Hanner}(1988)}]{hanner:1988}
@@
 
+\bibitem[{{Johns} \& {Basri}(1995)}]{johns:1995}
+{Johns} C.~M., {Basri} G., 1995, \apj, 449, 341
+
 \bibitem[{{Johns-Krull} {et~al.}(1999){Johns-Krull}, {Valenti}, {Hatzes} \&
@@
   \& {Newton}}]{kenyon:1994}
-{Kenyon} S.~J., {Hartmann} L., {Hewett} R., {Carrasco}~{Cruz-Gonzalez} I.,
-  {Recillas} E., {Salas} L., {Serrano} A., {Strom} K.~M., {Strom} S.~E.,
-  {Newton} G., 1994, \aj, 107, 2153
+{Kenyon} S.~J. et al., 1994, \aj, 107, 2153
 
@@
 
+\bibitem[{{Muzerolle} {et~al.}(1998){Muzerolle}, {Calvet}, \&
+  {Hartmann}}]{muzerolle:1998}
+{Muzerolle} J., {Calvet} N., {Hartmann} L., 1998, \apj, 492, 743
+
 \bibitem[{{Muzerolle} {et~al.}(2001){Muzerolle}, {Calvet} \&
@@
 \bibitem[{{Pudritz} \& {Banerjee}(2005)}]{pudritz:2005}
-{Pudritz} R.~E., {Banerjee} R., 2005, in Cesaroni, R., Felli, M.,
-Churchwell, E., Walmsley, M., eds, Proc.~IAU Symp. 225, Massive star
-birth: A crossroads of Astrophysics, Cambridge University Press,
-Cambridge,  p.~163
+{Pudritz} R.~E., {Banerjee} R., 2005, in Proc.~IAU Symp. Massive star
+birth: A crossroads of Astrophysics, Cesaroni, R., Felli, M.,
+Churchwell, E., Walmsley, M., eds, Cambridge Univ.\, Press, Cambridge,
+225, p.~163
 
@@
   =10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ and
-  $\dot{M}_{\mathrm{wind}}=10^{-6}\,\mathrm{M_{\sun}\,yr^{-1}}$.
+  $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$.
   Profiles are presented for inclinations of $10^\circ$ (top figure),
@@
   $\dot{M}_{\mathrm{acc}} =10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ and
-  $\dot{M}_{\mathrm{wind}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$. }
+  $\dot{M}_{\mathrm{wind}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$. }
 

### 2006-04-05 TTau_Halpha/revision01/response_to_ref.txt
minor change in the response to refree.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@694 25464f21-6099-402c-b30a-640f1d40d38b
tims changes
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@695 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-     In our model, the hot ring simply acts
-     as a source of additional continuum source, but the total amount
-     of the additional continuum flux from the hot ring does not
-     change.  This means that the level population does not change;
+     The level populations are relatively insensitive to the actual 
+     distribution of the hot spots on the stellar surface and
      hence, the H-alpha line strength is not affected by the change in
-     the area coverage of the rings provided that the change is not so
-     big. If the area coverage is much bigger (e.g. 30%), then the
-     geometry of the magnetosphere itself changes significantly.  This
+     the area coverage of the rings provided that the change is not too
+     greate. If the area coverage is much bigger (e.g. 30%), then the
+     geometry of the magnetosphere itself must change significantly.  This
      would result in the line strength slightly for a fixed
@@
      al 2001), then the coverage would be 1% of the total surface,
-     which is more similar to the fraction estimated in Gullring et al
+     which is more similar to the fraction estimated in Gullbring et al
      (2000).  If we look at the model comparison of Muzerolle et al
@@
         determined only by the geometry of the magnetosphere (Section
-        2.2). Gullring et al (2000) estimated the fractions of the
+        2.2). Gullbring et al (2000) estimated the fractions of the
         hot-ring coverage area for three intermediate CTTS by using
@@
         magnetosphere), we find the line shapes of H$\alpha$ do not
-        change significantly. "
+        change significantly (see also figure~5 of Muzerolle et al. 2001). "
 
@@
 
-   * Thank you for reminding me this point. 
-     I removed the sentence, "The results of Martin(1996)
-     qualitatively agree with those of Hartmann et al. (1994)" from the
-     text, and added the following at end of the paragraph to reflect
-     your comments.
+   * The two temperature structures _do_ agree in a qualitative sense,
+     in that their behaviour as a function of distance along a
+     streamline follows a similar dependence. Nonetheless, you are
+     right that Muzerolle could not reconcile the Martin T structure
+     with observations. We have made the following change:
 
-        "Although the model of Martin (1996) seems to be more
-         comprehensive than that of Hartmann et al. (1994), Muzerolle
-         et al (1998) found that the line profile models computed
-         according to the temperature structure of the former do not
-         agree with observations while they do have much better
-         agreement when the temperature of the latter model was used. 
-	 The temperature structure of the magnetosphere is still a big
-         uncertainty in the accretion model; however, for a
-         heuristic reason, we adopted the model of Hartmann et
+        "Muzerolle et al (1998) found that the line profile models computed
+         according to the Martin (1996) temperature structure do not
+         agree with observations, unlike profiles based on the (less self-consistent)
+         Hartmann et al. (1994) temperature distribution.
+	 It is clear that The temperature structure of the magnetosphere is still a large
+         source of uncertainty in the accretion model; here  we adopted the model of Hartmann et
          al. (1994). "
@@
 
-   * You are absolutely correct. This is my mistake.
-     It should be p=-7/2 which is the value used in the models.  
+   * You are absolutely correct. This is a typo, 
+     it should be p=-7/2 which is the value used in the models.  
      With p=-7/2,  
@@
 
-   * You are absolutely right. I changed the sentence as you pointed
+   * I agree. I changed the sentence as you pointed
      out.
@@
         accretion stream close to the photosphere (~1 R*) above the
-        photosphere)on the upper-left quadrant in Fig.1 (x<0 and z>0)
+        photosphere) on the upper-left quadrant in Fig.1 (x<0 and z>0)
         will be more aligned with the line-of-sight of an observer in
@@
 
-   * You are right again. I meant to say beta=2.0 instead of
+   * I meant to say beta=2.0 instead of
      beta=4.0.  ==> Corrected.
@@
      A similar correction was made in Section 2.3 as you also pointed out.
-     Sorry for the careless mistakes.
      ==> Corrected.
@@
 
-   * My mistake again. It should have written as
+   * This was a typo. It should have written as
      theta_open=arctan(Rwi/d). 
@@
      an intrinsic problem with approximating the stream lines with
-     straight lines. A better model is perhaps to compute the field
-     lines using Blandford & Payne (1982) model as done in
-     e.g. Alencar et al (2005, A&A, 440, 595).  Also, in our mode, if
+     straight lines.  Also, in our mode, if
      the launching angle is too small (<60 deg.), the wind absorption
@@
      used the launching angle (at the inner most part) greater than 60
-     degrees to be more consistent with observation.
+     degrees to be more consistent with observations.
 
@@
 
-     To answer your question how it would effect our results, I run
+     To answer your question how it would effect our results, I ran
      additional models with d=5Rstar which satisfies the wind
@@
      conclusions obtained from the disc wind models with d=5Rstar.
+
+     These models (for  Mdot_acc=1x10^-8 Msun/yr & Mdot_wind=1x10^-9
+     Msun/yr cases) with d=5Rstar are posted on the following website.
+
+     http://www.astro.ex.ac.uk/people/rk/profiles/extra2
 
@@
         Fig. 9 in next section), we have adopted d =22 Rstar
-        instead. This means that some part of the disc wind (3Rstar <
-        wi < 25.4 Rstar) may not be able to be launched from the disc
-        plane according to the model of Blandford & Payne (1982).
-
-	We have used a larger launching angle or a larger source
+        instead. We have used this larger source
 	displacement distance for the following two reasons: (1) to
-	simulate more 'colliminated' wind (toward the symmetry axis,
-	and (2) to be more consistent with the fraction of H-alpha
-	profiles affected by wind absorptions in observations.
+	simulate a more 'colliminated' wind (toward the symmetry axis,
+	and (2) for greater consistency with the fraction of H-alpha
+	profiles affected by wind absorption in observations (ref xxxxx).
 
@@
 	model.  This is an intrinsic problem with approximating the
-	stream lines with straight lines. A better model is perhaps to
-	compute the field lines using Blandford & Payne (1982) model
-	as done so in Alencar et al (2005, A&A, 440, 595).  Also, in
+	stream lines with straight lines.  Also, in
 	our mode, if the launching angle is too small (<60 deg.), the
@@
 	 profiles on the wind temperature rate and the wind
-	 acceleration rate is similar to what we found in the models
+	 acceleration rate are similar to the models
 	 shown in Figs. 6 and 9.  The minimum inclination angle at
@@
 
-   * You are correct. I don't know why I said that.
+   * You are correct.
      I rephrase the sentence as follows
@@
      "The figure shows that as $\mu$ increases the
-     P-Cygni absorption deepens only slightly." and the position of minimum
-     flux in the absorption trough appears to remain at same locations."
+     P-Cygni absorption deepens only slightly  and the position of minimum
+     flux in the absorption trough appears to remain at same location."
 
@@
 
-      A possible reason for not being able to find Type III profiles
-      in lower mass-accretion rate models (e.g. in Mdot_acc =
-      1.0x10^-8 Msun/yr models) is perhaps due to a wrong radial
-      dependence (p in Equation 3) of the mass-loss rate per unit area
-      used in our models.  This dependence shall be examined in more
-      carefully in future.
-
       I added a following comments based on these additional runs.
 
-      "In addition to the models shown in Appendix A, we have run a
-      set of hybrid models (not shown here) with a typical
-      mass-accretion rate for CTTS i.e. 3x10^-8 Msun/yr (Gullbring et
-      al. 1998; Calvet et al. 2004) using i=10,55,80 with combinations
-      of beta=0.2, 0.5, 1.0, 2.0 and Twind=7000, 8000, 9000,
-      10000K. Based on these models, we found that Type III-B profiles
-      can be seen for at least in three models with fast accelerating
-      and high wind temperature at moderate inclination angle i.e. i =
-      55 degrees with (beta, Twind) = (0.2, 10000K), (0.5, 9000K) and
-      (0.5, 10000K).  A possible reason for not being able to find
-      Type III profiles in lower mass-accretion rate models (e.g. in
-      Mdot_acc = 1.0x10^-8 Msun/yr models) is perhaps due to a wrong
-      radial dependence (p in Equation 3) of the mass-loss rate per
-      unit area used in our models.  This dependence shall be examined
-      more carefully in future."
+      "Although Type III-B profiles do not occur at macc=10^-8, we
+      have examined the intermediate case of macc=3x10-8, which may
+      represent a typical T Tauri mass accretion rate  (Gullbring et
+      al. 1998; Calvet et al. 2004). We find that the models with fast accelerating,
+      high temperature winds do display  Type III-B profiles. It is
+      clear that our model, as it stands, requires above-average (but
+      perhaps not atypical) mass-accretion rates in order to produce
+      Type III-B profiles. It is less clear whether the 14 Type-IIIB
+      objects found by Reipurth et al. consistute the highest
+      mass-accretors in their sample: the aveage EW for T~Tauri stars
+      with Type III-B profiles is 69\AA, which is in the top quartile
+      of their complete T~Tauri star sample, perhaps indicating that
+      Type-IIIB profiles are associated with high EWs, and therefore
+      strong mass-accretion."
 
@@
        "Although in general H-alpha in the spectra of CTTS shows a
-        significant amount of variablity, which is in some cases
+        significant amount of variablity, which may in some cases
         induced by the rotational motion of an inclined magnetosphere
         (e.g. Johns &  Basri 1995; Bouvier et al. 2003), we restrict
-        our discussion in this section for the cases of axi-symmetric
-        geometries."
+        our discussion in this section to the axisymmetric case only."
 
@@
        "The restriction in the inclination angle mentioned above would
-        be relaxed if the axis of the magnetosphere is tilted with
-        respect to the rotational axis since the line-of-sight to an
-        observer from the accretion hot rings will pass through a
-        different part of the magnetosphere as a rotational phase
-        changes (as it precesses around the rotational axis)."
+        be relaxed if the axis of the magnetosphere was tilted with
+        respect to the rotational axis, since the line-of-sight from an
+        observer to the hot rings will pass through 
+        different parts of the magnetosphere as the rotational phase
+        changes."
 
@@
      models, so the main conclusion of this section 
-     does not change when Mdot_wind is changed from 10^-9 Msun/yr to
+     does not change when Mdot_wind is changed from 10^-8 Msun/yr to
      10^-9 Msun/yr.
@@
         "A similar inclination dependency of EW is found for lower
-        wind mass-loss rate models (e.g. Mdot_wind = 10^-9 Msun/yr)
+        mass-loss rate models (e.g. Mdot_wind = 10^-9 Msun/yr)
         while keeping mu=0.1."
@@
 	sentence,  I added:
-	"The wind mass-loss rates used in both models are Mdot_wind =
+	"The wind mass-loss rates used in both models is Mdot_wind =
 	10^-8 Msun/yr."

### 2006-04-05 TTau_Halpha/revision01/response_to_ref.txt
Corrections discussed with Tim have made to this version.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@696 25464f21-6099-402c-b30a-640f1d40d38b

@@
 comments and suggestions very carefully.  
-The answers to your questions follows "*" marks before 
+The answers to your questions follow "*" marks before 
 the indented texts below.
@@
 	    profiles as resulting from the partial occultation 
-	    of the flow by the inner part of the accretion disc and by
-	    the stellar photosphere, .... "
+	    of the flow by the stellar photosphere and by the inner
+	    part of the accretion disc, .... "
 
@@
      this total luminosity due to accretion and by assuming they
-     radiates as a blackbody.
+     radiate as a blackbody.
 
@@
      The level populations are relatively insensitive to the actual
-     distribution of the hot spots on the stellar surface and
-     hence, the H-alpha line strength is not affected by the change in
-     the area coverage of the rings provided that the change is not too
+     distribution of the hot spots on the stellar surface and hence,
+     the H-alpha line strength is not affected by the change in the
+     area coverage of the rings provided that the change is not too
      greate. If the area coverage is much bigger (e.g. 30%), then the
-     geometry of the magnetosphere itself must change significantly.  This
-     would result in the line strength slightly for a fixed
+     geometry of the magnetosphere itself must change significantly.
+     This would result in the line strength slightly for a fixed
      inclination angle, but overall shape of the profile would not
@@
      (Small and Wide (SW) model of Muzerolle et al 2001) which results
-     in 8% hot ring coverage. If we were to use Rmi=2.2R* and Rmi =
-     2.8R* and Rmo=3.0* (Small and narrow (SN) model of Muzerolle et
-     al 2001), then the coverage would be 1% of the total surface,
-     which is more similar to the fraction estimated in Gullbring et al
-     (2000).  If we look at the model comparison of Muzerolle et al
-     (2001) (see their Fig. 5), the line strength changes, but the
-     line profiles shape do not change much (except for the 10^3 K
-     model). We confirmed, by running additional models, the line
-     shapes do not change significantly for H-alpha by changing from
-     SW to SN model.
+     in 8% hot ring coverage. If we were to use Rmi =2.8R* and
+     Rmo=3.0R* (Small and narrow (SN) model of Muzerolle et al 2001),
+     then the coverage would be 1% of the total surface, which is more
+     similar to the fraction estimated in Gullbring et al (2000).  If
+     we look at the model comparison of Muzerolle et al (2001) (see
+     their Fig. 5), the line strength changes, but the line profiles
+     shape do not change much (except for the 10^3 K model). We
+     confirmed, by running additional models, the line shapes do not
+     change significantly for H-alpha by changing from SW to SN model.
 
@@
 
-        "Muzerolle et al (1998) found that the line profile models computed
-         according to the Martin (1996) temperature structure do not
-         agree with observations, unlike profiles based on the (less self-consistent)
-         Hartmann et al. (1994) temperature distribution.
-	 It is clear that The temperature structure of the magnetosphere is still a large
-         source of uncertainty in the accretion model; here  we adopted the model of Hartmann et
+        "Muzerolle et al (1998) found that the line profile models
+         computed according to the temperature structure of Martin (1996)
+         do not agree with observations, unlike profiles based on the
+         (less self-consistent) Hartmann et al. (1994) temperature
+         distribution.  It is clear that The temperature structure of
+         the magnetosphere is still a large source of uncertainty in
+         the accretion model; here we adopted the model of Hartmann et
          al. (1994). "
@@
         instead. We have used this larger source
-	displacement distance for the following two reasons: (1) to
-	simulate a more 'colliminated' wind (toward the symmetry axis,
-	and (2) for greater consistency with the fraction of H-alpha
-	profiles affected by wind absorption in observations (ref xxxxx).
+	displacement distance for the following two reasons.
 
-      	Since the stream lines in our simple disc wind are represented
-	by straight lines, the wind never bends toward the symmetry
-	axis (z-axis) as the distance from the disc increases unlike
-	the model of Blandford & Payne (1982). We therefore used a
-	larger launching angle to simulate the stream lines in the far
-	field (at a larger distance from the disc plane) in their
-	model.  This is an intrinsic problem with approximating the
-	stream lines with straight lines.  Also, in
-	our mode, if the launching angle is too small (<60 deg.), the
-	wind absorption feature would be not been seen or would be
-	very small for profiles computed with i<60 deg.  If the
-	launching angle is 60 deg. at the inner most part of the wind,
-	and the inclination angle (measured from the symmetry axis,
-	z-axis) is less than 60 deg., little (wind) absorption is
-	expected, as demonstrated in Figure 7.  The situation will
-	however changes if the field/stream line is not straight and
-	bending towards the symmetry axis as the wind travel higher
-	above the disc.  Since more than 50 per cent of observed
-	H-alpha profiles (e.g. Reipurth 1996, A&AS, 120, 229 and
-	Alencar & Basri 2000, ApJ 119, 1881) are affected by wind
-	absorption, it was necessary for our model to used the
-	launching angle (at the inner most part) greater than 60
-	degrees to be more consistent with observations; although this
-	would mean that the launching angle condition of Blandford and
-	Payne (1982) is violated for wind from a very inner part of
-	the disc.
+      	First, we want to simulate a more 'colliminated' wind (toward
+	the symmetry axis).  Since the stream lines in our simple disc
+	wind are represented by straight lines, the wind never bends
+	toward the symmetry axis (z-axis) as the distance from the
+	disc increases unlike the model of Blandford & Payne
+	(1982). We therefore used a larger launching angle to simulate
+	the stream lines in the far field (at a larger distance from
+	the disc plane) in their model.  This is an intrinsic problem
+	with approximating the stream lines with straight lines.
+
+	Second, the larger source displacement model would provide a
+        greater consistency with the fraction of H-alpha profiles
+        affected by wind absorption seen in observations.  According
+        to the observations of Reipurth (1996, A&AS, 120, 229) and
+        Alencar & Basri (2000, ApJ 119, 1881), more than 50 per cent
+        of CTTS show wind absorption features in their H-alpha
+        profiles. In our model, if the launching angle is too small
+        (<60 deg.), the wind absorption feature would not be seen or
+        would be very small for profiles computed with i<60 deg., as
+        demonstrated in Fig. 7.  The situation will however change if
+        the field/stream line is not straight and bending towards the
+        symmetry axis as the wind travel higher above the disc.
 
@@
 	features weaken, but overall morphology dependence of the 
-	 profiles on the wind temperature rate and the wind
-	 acceleration rate are similar to the models
-	 shown in Figs. 6 and 9.  The minimum inclination angle at
-	 which the wind absorption becomes important is larger than
-	 that of the models with a larger source displacement (d = 22
-	 Rstar) as expected."
+	profiles on the wind temperature  and the wind 
+	acceleration rate are similar to the models shown in Figs. 6 
+	and 9.  The minimum inclination angle at which the wind 
+	absorption becomes important is larger than that of the 
+	models with a larger source displacement (d = 22 Rstar) as 
+	expected."
 
@@
       Type III-B profiles. It is less clear whether the 14 Type-IIIB
-      objects found by Reipurth et al. consistute the highest
-      mass-accretors in their sample: the aveage EW for T~Tauri stars
+      objects found by Reipurth et al. constitute the highest
+      mass-accretors in their sample: the average EW for T~Tauri stars
       with Type III-B profiles is 69\AA, which is in the top quartile
@@
 
+**** Additional Corrections *********************************
+
 In addition to the referee's suggestions, we noticed the following 
@@
 
-2. In Figure 13, the velocity ranges out the two plots should be
+2. In Figure 13, the velocity ranges of the two plots should be
    same for a better comparison. We changed the range of the 

### 2006-04-05 TTau_Halpha/revision01/kurosawa.tex
Corrections discussed with Tim have made to this version.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@696 25464f21-6099-402c-b30a-640f1d40d38b

@@
 asymmetric emission line profiles as resulting from the partial
-occultation of the flow  by the inner part of the accretion disc and
-by the stellar photosphere, while inverse 
+occultation of the flow by the stellar photosphere and by the inner
+part of the accretion disc, while inverse 
 P~Cygni profiles in the MA model result from inflowing material at
@@
 coverage model (by changing the width of the magnetosphere), we
-find the line shapes of H$\alpha$ do not change significantly.
+find the line shapes of H$\alpha$ do not change significantly (see
+also Fig.~5 of \citealt{muzerolle:2001}).
 
@@
   slightly higher mass-accretion rate is adopted here to demonstrate the 
-  effect of line-broadenings more clearly (c.f. Section~\ref{sub:model-acc}). }
+  effect of line-broadening more clearly (c.f. Section~\ref{sub:model-acc}). }
 \label{tab:std_parameters}
@@
 radiation and line emission from Ca~II and Mg~II ions. 
-Although the model of \citet{martin:1996} seems to be more comprehensive
-than that of \citet{hartmann:1994}, \citet*{muzerolle:1998} found that
-the line profile models computed according to the temperature
-structure of the former do not agree with observations while they do
-have much better agreement when the temperature of the latter model was
-used.  The temperature structure of the magnetosphere is still a big
-uncertainty in the accretion model; however, for a heuristic reason,
-we adopted the model of \citet{hartmann:1994}.
+\citet*{muzerolle:1998} found that the line profile models computed
+according to the temperature structure of \citet{martin:1996} do not
+agree with observations, unlike profiles based on the (less
+self-consistent) \citet{hartmann:1994} temperature distribution.  It
+is clear that The temperature structure of the magnetosphere is still
+a large source of uncertainty in the accretion model; here we adopted
+the model of \citet{hartmann:1994}.
 
@@
 We have used a larger launching angle or a larger source displacement
-distance for the following two reasons: (1)~to simulate more
-\emph{collimated} wind (toward the symmetry axis, and (2)~to be more
-consistent with the fraction of H$\alpha$ profiles affected by wind
-absorptions in observations.
-
-Since the stream lines in our simple disc wind are represented by
-straight lines, the wind never bends toward the symmetry axis ($z$-axis)
-as the distance from the disc increases unlike the
-model of \citet{blandford:1982}. We therefore used a larger
-launching angle to simulate the stream lines in the far field (at a larger
-distance from the disc plane) in their model.  This is an intrinsic
-problem with approximating the stream lines with straight lines. A
-better model is perhaps to compute the field lines using
-\citet{blandford:1982} model as done so in \citet{alencar:2005}.
-Also, in our mode, if the launching angle is too small
-($<60^{\circ}$), the wind absorption feature would be not been seen
-or would be 
-very small for profiles computed with an inclination angle
-$i<60^{\circ}$.  If the launching angle is $60^{\circ}$ at the inner
-most part of the wind, and the inclination 
-angle (measured from the symmetry axis, $z$-axis) is less than $60^{\circ}$,
-little (wind) absorption is expected, as demonstrated in Fig.~\ref{fig:discwind_d_effect}.
-The situation will however change if the field/stream lines are not
-straight and bending towards the symmetry axis as the wind travel
-higher above the disc.  Since more than 50~per~cent of observed
-H$\alpha$ profiles (e.g. \citealt{reipurth:1996};
-\citealt{alencar:2000}) are affected by wind absorption, it was 
-necessary for our model to used the launching angle (at the inner most
-part) greater than $60^{\circ}$ to be more consistent with observations;
-although this would mean that the launching angle condition of
-\citet{blandford:1982} is violated for wind from a very inner part
-of the disc.
+distance for the following two reasons.
+
+First, we want to simulate a more \emph{colliminated} wind (toward
+the symmetry axis).  Since the stream lines in our simple disc
+wind are represented by straight lines, the wind never bends
+toward the symmetry axis ($z$-axis) as the distance from the
+disc increases unlike the model of \citet{blandford:1982}. We
+therefore used a larger launching angle to simulate 
+the stream lines in the far field (at a larger distance from
+the disc plane) in their model.  This is an intrinsic problem
+with approximating the stream lines with straight lines.
+
+Second, the larger source displacement model would provide a greater
+consistency with the fraction of H$\alpha$ profiles affected by wind
+absorption seen in observations.  According to the observations of
+\citet{reipurth:1996} and \citet{alencar:2000}, more than 50 per cent
+of CTTS show wind absorption features in their H$\alpha$
+profiles. In our model, if the launching angle is too small
+($\theta_{\mathrm{L}}<60^{\circ}$), the wind absorption feature would not be seen or
+would be very small for profiles computed with $i<60^{\circ}$, as
+demonstrated in Fig.~~\ref{fig:discwind_d_effect}.  The situation will
+however change if the field/stream line is not straight and bending
+towards the symmetry axis as the wind travel higher above the disc.
 
@@
 R_{*}$ (not shown here) which satisfies the wind launching condition
-of \citet{blandford:1982} in all parts of the disc wind zone in our model.  These
-models showed that the wind absorption and emission features weaken,
-but overall morphology dependence of the profiles on the wind
-temperature rate and the wind acceleration rate is similar to what we
-found in the models shown in Figs.~\ref{fig:atlas_discwind_only} and
-\ref{fig:atlas_hybrid}.  The minimum inclination angle at which the
-wind absorption becomes important is larger than that of the models
-with a larger source displacement ($d = 22\, R_{*}$) as expected.
+of \citet{blandford:1982} in all parts of the disc wind zone in our
+model.  These models showed that the wind absorption and emission
+features weaken, but overall morphology dependence of the profiles on
+the wind temperature and the wind acceleration rate is similar to
+what we found in the models shown in
+Figs.~\ref{fig:atlas_discwind_only} and \ref{fig:atlas_hybrid}.  The
+minimum inclination angle at which the wind absorption becomes
+important is larger than that of the models with a larger source
+displacement ($d = 22\, R_{*}$) as expected.
 
@@
 P-Cygni absorption deepens only slightly, and the position of minimum
-flux in the absorption trough appears to remain at same positions.  On the other
+flux in the absorption trough appears to remain at same location.  On the other
 hand, the flux peak increases and the line wings become stronger as
@@
 Although in general H$\alpha$ in the spectra of CTTS shows a
-significant amount of variablity, which is in some cases induced by
+significant amount of variablity, which may in some cases induced by
 the rotational motion of an inclined magnetosphere
 (e.g.~\citealt{johns:1995}; \citealt{bouvier:2003}), we restrict our
-discussion in this section for the cases of axi-symmetric geometries.
+discussion in this section to the axi-symmetric case only.
 
@@
 inclination models.
-In addition to the models shown in Appendix~\ref{sec:appendix}, we
-have run a set of hybrid models (not shown here) with a typical
-mass-accretion rate for CTTS i.e. $3\times10^{-8}
-\mathrm{M_{\sun}\,yr^{-1}}$ (\citealt{gullbring:1998};
-\citealt{calvet:2004}) using $i=10^{\circ},55^{\circ},80^{\circ}$ with
-combinations of $\beta = 0.2, 0.5, 1.0, 2.0$ and
-$T_{\mathrm{wind}}=7000, 8000, 9000, 10000$~K. Based on these models,
-we found that Type~III-B profiles can be seen for at least in three
-models with fast accelerating and high wind temperature at moderate
-inclination angle i.e. $i = 55^{\circ}$ with $\left ( \beta,
-T_{\mathrm{wind}} \right ) = \left ( 0.2, 10000\,\Kelvin \right )$,
-$\left ( 0.5, 9000\,\Kelvin \right )$ and $\left ( 0.5, 10000\,\Kelvin
-\right )$.  A possible reason for not being able to find Type~III
-profiles in lower mass-accretion rate models (e.g. in
+Although Type~III-B profiles do not occur at
 $\dot{M}_{\mathrm{acc}} =
-1.0\times10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ models) is perhaps due
-to a wrong radial dependence ($p$ in
-equation~\ref{eq:discwind-massloss-w}) of the mass-loss rate per unit
-area adopted in our models.  This dependence shall be examined more
-carefully in future.
+1.0\times10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, we have examined
+the intermediate case of
+$\dot{M}_{\mathrm{acc}} =3\times10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$, which may
+represent a typical T Tauri mass accretion rate
+(\citealt{gullbring:1998}; \citealt{calvet:2004}). We find that
+the models with fast accelerating, high temperature winds do
+display Type~III-B profiles. It is clear that our model, as it
+stands, requires above-average (but perhaps not atypical)
+mass-accretion rates in order to produce Type~III-B profiles. It
+is less clear whether the 14 Type~III-B objects found by
+\citet{reipurth:1996} constitute the highest mass-accretion rate
+objects in their sample: the average EW for T~Tauri stars with
+Type~III-B profiles is 69\AA, which is in the top quartile of
+their complete T~Tauri star sample, perhaps indicating that
+Type~III-B profiles are associated with high EWs, and therefore
+strong mass-accretion.
 
@@
 The restriction in the inclination angle mentioned above would be
-relaxed if the axis of the magnetosphere is tilted with respect to the
-rotational axis since the line-of-sight to an observer from the
-accretion hot rings will pass through a different part of the
-magnetosphere as a rotational phase changes (as it precesses around
-the rotational axis).
+relaxed if the axis of the magnetosphere was tilted with respect to the
+rotational axis since the line-of-sight from an observer to the hot
+rings will pass through  different parts of the 
+magnetosphere as the rotational phase changes.
 
@@
     $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=1.0$ respectively.
-    The wind mass-loss rates used in both models are
+    The wind mass-loss rates used in both models is
     $\dot{M}_{\mathrm{wind}}=10^{-8}~\mathrm{M_{\sun}~yr^{-1}}$ . 

### 2006-04-05 TTau_Halpha/revision01/kurosawa.tex
Minor typos fixed after proof reading (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@697 25464f21-6099-402c-b30a-640f1d40d38b

@@
 $i=55^{\circ}$.  As the wind becomes more collimated (larger $d$), the
-wind launching angle becomes smaller and the wind density is enhanced
+wind opening angle becomes smaller and the wind density is enhanced
 towards the symmetry axis ($z$); hence, the wind emission increases.
@@
 
-First, we want to simulate a more \emph{colliminated} wind (toward
+First, we want to simulate a more \emph{collimated} wind (toward
 the symmetry axis).  Since the stream lines in our simple disc
@@
 would be very small for profiles computed with $i<60^{\circ}$, as
-demonstrated in Fig.~~\ref{fig:discwind_d_effect}.  The situation will
+demonstrated in Fig.~\ref{fig:discwind_d_effect}.  The situation will
 however change if the field/stream line is not straight and bending
@@
 $\left(T_{\mathrm{wind}},\,\beta\right)=\left(8000\,\mathrm{K},\,1.0\right)$
-in Figures~\ref{fig:atlas_discwind_only} and the accretion dominated
+in Fig.~\ref{fig:atlas_discwind_only} and the accretion dominated
 model with
@@
 objects in their sample: the average EW for T~Tauri stars with
-Type~III-B profiles is 69\AA, which is in the top quartile of
+Type~III-B profiles is 69~\AA, which is in the top quartile of
 their complete T~Tauri star sample, perhaps indicating that
@@
 {Frank} J., {King} A., {Raine} D.~J., 2002, {Accretion Power in Astrophysics,
-  3rd edn.} Cambridge Univ.\, Press, Cambridge, p. 398
+  3rd edn.} Cambridge Univ.\, Press, Cambridge, p.~398
 
@@
 \bibitem[{Grevesse \& Noels(1993)}]{grevesse:1993}
-Grevesse N., Noels A., 1993, in Origin and Evolution of the Elements, N.\ P.,
-  E.\ V.-F., M.\ C., eds., Cambridge Univ.\, Press, Cambridge, p.~15
+Grevesse N., Noels A., 1993, in {Prantzos} N., {Vangioni-Flam} E., {Casse}
+M., eds,  Origin and Evolution of the Elements,  Cambridge Univ.\, Press, Cambridge, p.~15
 
@@
 \bibitem[{{Pudritz} \& {Banerjee}(2005)}]{pudritz:2005}
-{Pudritz} R.~E., {Banerjee} R., 2005, in Proc.~IAU Symp. Massive star
-birth: A crossroads of Astrophysics, Cesaroni, R., Felli, M.,
-Churchwell, E., Walmsley, M., eds, Cambridge Univ.\, Press, Cambridge,
-225, p.~163
+{Pudritz} R.~E., {Banerjee} R., 2005, in {Cesaroni}, R., {Felli}, M.,
+{Churchwell}, E., {Walmsley}, M., eds, Proc.~IAU Symp.~225, Massive star
+birth: A crossroads of Astrophysics,  Cambridge Univ.\, Press,
+Cambridge, p.~163
 

### 2006-04-07 TTau_Halpha/kurosawa_resubmit/response_to_ref.txt
After resubmission.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@699 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-04-05 TTau_Halpha/revision01/response_to_ref.txt
@@
          (less self-consistent) Hartmann et al. (1994) temperature
-         distribution.  It is clear that The temperature structure of
+         distribution.  It is clear that the temperature structure of
          the magnetosphere is still a large source of uncertainty in

### 2006-04-07 TTau_Halpha/kurosawa_resubmit/kurosawa.tex
After resubmission.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@699 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-04-05 TTau_Halpha/revision01/kurosawa.tex
@@
 accretion flows, characterised by the blue-shifted absorption features
-in H$\alpha$ profiles and the redshifted inverse P~Cygni (IPC)
+in H$\alpha$ profiles and redshifted inverse P~Cygni (IPC)
 profiles respectively. Typical mass-loss rates of CTTS are about
@@
 10^{6}\,\mathrm{K}$.  The X-ray radiation produced in the shock will
-be absorbed by the gas locally, and re-emitted as optical and UV
+be absorbed by the gas locally, and re-emitted as optical and UV light 
 (\citealt{calvet:1998}; \citealt{gullbring:2000}). This
@@
 $6400\,\mathrm{K}$.  The luminosity ratio and the temperature depend
-on a adopted mass-accretion rate. The continuum emission from the hot
+on an adopted mass-accretion rate. The continuum emission from the hot
 rings is taken into account when computing the line profiles.
@@
 self-consistent) \citet{hartmann:1994} temperature distribution.  It
-is clear that The temperature structure of the magnetosphere is still
+is clear that the temperature structure of the magnetosphere is still
 a large source of uncertainty in the accretion model; here we adopted
@@
 shows the density and the velocity components along the mid stream
-line (passing through
-$w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$ on the disc
+line, passing through
+$w_{i}=\left(R_{\mathrm{wi}}+R_{\mathrm{wo}}\right)/2$, on the disc
 plane ($z=0$) for different values of the wind acceleration parameter
@@
     (c.f. equation~\ref{eq:discwind-toroidal-velocity}), is also shown in
-    the right panel for comparison. The density is normalised to the
+    the left panel for comparison. The density is normalised to the
     density $\rho_{0}$ at the wind launching point for the $\beta = 1.0$ case.
@@
 (c.f. \citealt{mihalas:1978}) for computing the observed flux as a
-function of frequence.  The integration of the flux is performed in
+function of frequency.  The integration of the flux is performed in
 the cylindrical coordinate system $\left(p,\, q,\, t\right)$ which is
@@
     model with the damping constant. The broad wings extend to $\sim \pm
-    800\,\kmps$.  The redshifted absorption feature (very weakly) seen in
+    800\,\kmps$.  The redshifted absorption feature seen (very weakly) in
     the $\Gamma=0$ model is not seen in the model with the broadening.  }
@@
 the models in Fig.~\ref{fig:atlas_acc_models}.  The EWs for half the
-models fall within the range of EWs ($\sim 3$~\AA\, to $\sim 160$~\AA)
+models fall within the range of EWs ($\sim 3$ to $\sim 160$~\AA)
 measured by \citet{alencar:2000}. The EWs of models 
@@
 $80^\circ$, i.e.~a fractional change of 0.65.  On the other hand,
-the 10~per~cent width of the line changes from 290~$\kmps$ to
+the 10~per~cent width of the line changes from 290 to
 470~$\kmps$; hence, the fractional change is 1.6.  
@@
 objects in their sample: the average EW for T~Tauri stars with
-Type~III-B profiles is 69~\AA, which is in the top quartile of
+Type~III-B profiles is 64~\AA, which is in the top quartile of
 their complete T~Tauri star sample, perhaps indicating that
@@
 \hline 
-&
+Class&
 $i$&
@@
 Comment\tabularnewline
-Class&
-&
-&
-&
-&
-&
-&
-\tabularnewline
 \hline 
 I&
-$55$&
+$55^{\circ}$&
 $10^{-7}$&
@@
 II-B&
-$55$&
+$55^{\circ}$&
 $10^{-7}$&
@@
 Wide range of wind acceleration rates.
-Mid--high inclination\tabularnewline
+Mid--high inclination.\tabularnewline
 II-R&
-$80$&
+$80^{\circ}$&
 $10^{-7}$&
@@
 $2.0$&
-Slow wind acceleration rate. High inclination\tabularnewline
+Slow wind acceleration rate. High inclination.\tabularnewline
 III-B&
-$55$&
+$55^{\circ}$&
 $10^{-7}$&
@@
 $0.5$&
-Fast wind acceleration rate. Mid inclination\tabularnewline
+Fast wind acceleration rate. Mid inclination.\tabularnewline
 III-R&
-$85$&
+$85^{\circ}$&
 $10^{-8}$&
@@
 Mid wind acceleration rate. Very high
-inclination \tabularnewline
+inclination.\tabularnewline
 IV-B&
-$30$&
+$30^{\circ}$&
 $10^{-7}$&
@@
 $0.2$&
-Fast wind acceleration rate. Mid--high inclination\tabularnewline
+Fast wind acceleration rate. Mid--high inclination.\tabularnewline
 IV-R&
-$55$&
+$55^{\circ}$&
 $10^{-9}$&
@@
 regions both above and below the poles. The density is computed from
-assuming the constant mass-loss rate per unit area over the stellar
-surface, the mass-flux conservation, and using the beta velocity law
+assuming a constant mass-loss rate per unit area over the stellar
+surface, requiring mass-flux conservation, and using the beta velocity law
 above.  The schematic of the model configuration is shown in
@@
 This model configuration is motivated by the recent study by
-\citet{matt:2005} who demonstrated that the stellar
+\citet{matt:2005} who demonstrated that a stellar
 wind along  open magnetic field lines originating from the star may cause
@@
 $10^{-8}\, \mathrm{M_{\sun}\,yr^{-1}}$, which
-is same as the mass-loss rate used in the disc-wind magnetosphere
+is the same as the mass-loss rate used in the disc-wind magnetosphere
 hybrid model in the same figure.   In both models, the mass-accretion
@@
 temperature ($T_{\mathrm{wind}}$) used here are $1.0$ and
-$9000\,\Kelvin$ respectively. All the other parameters are same as in
+$9000\,\Kelvin$ respectively. All the other parameters are the same as in
 the disc-wind magnetosphere model.  With this set of $\beta$ and
@@
 direction. For the same reason, the EW of the line increases as the
-inclination increases as clearly seen in the figure. Specifically the
+inclination increases, as clearly seen in the figure. Specifically the
 values are 54, 69, and 98\,\AA\, for $i=10^\circ$,
@@
 profiles, but neither can explain the complete Reipurth classification
-scheme--even magnetosphere dominated profiles (Type~I) can be readily
+scheme -- even magnetosphere dominated profiles (Type~I) can be readily
 explained by the hybrid model with $\mu=0.1$.
@@
 
-We have concentrated on the formation of the H$\alpha$ line, since it
+We have concentrated on the formation of the H$\alpha$ line, because it
 is the best studied CTTS emission line. However it is clear that
-simultaneous fitting of several emission line profile should provide
-much stronger constrains. In particular it appears that the near-IR
-hydrogen lines (Pa$\beta$ and Br$\gamma$) are less effected by
+simultaneous fitting of several emission line profiles should provide
+much stronger constraints. In particular it appears that the near-IR
+hydrogen lines (Pa$\beta$ and Br$\gamma$) are less affected by
 outflows than H$\alpha$. One could therefore use these lines to
-constrain the mass-accretion rate, and H$\alpha$ the mass-loss rate. A
-potential pitfall is the significant temporal variability that all
-CTTS show in their emission lines; the observational data on a
-particular object must be co-temporaneous.
+constrain the mass-accretion rate, and use H$\alpha$ to obtain the
+mass-loss rate. A potential pitfall is the significant temporal
+variability that all CTTS show in their emission lines; the
+observational data on a particular object must be co-temporaneous.
 
@@
 (3) $\dot{M}_{\mathrm{acc}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$
-(Fig.~\ref{fig:atlas02}).   The temperature of the magnetosphere
+(Fig.~\ref{fig:atlas02}).   The temperatures of the magnetospheres
 used for (1), (2) and (3) are $7500\,\Kelvin$, $8500\,\Kelvin$ and
@@
 inclination angles of $10^\circ$, $55^\circ$, and $80^\circ$. 
-The disc-wind geometry used to compute these profiles are same as in
+The disc-wind geometry used to compute these profiles are the same as in
 Section~\ref{sub:result-discwind-hybrid}. These profiles are available

### 2006-04-07 BD_radvel/main.tex
Initial import
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@700 25464f21-6099-402c-b30a-640f1d40d38b

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Bold symbol macro for standard LaTeX users
\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{times}
\usepackage{amssymb}

\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{\apj}
\newcommand{\pasp}{PASP}
\newcommand{\aj}{AJ}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\aapr}{A\&AR}
\newcommand{\pasj}{PASJ}

\newcommand{\kmps}{\mathrm{km~s^{-1}}}
\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
\newcommand{\Kelvin}{\mathrm{K}}

\usepackage{babel}
\makeatother
\begin{document}
\title[Radial and rotational velocities of young brown dwarfs candidates  in the Upper Sco and $\rho$~Oph]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in Upper Scorpius OB association and $\rho$~Ophiuchi cloud core}

\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk} and  Tim J.~Harries\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}

\date{Dates to be inserted}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2006}

\maketitle

\label{firstpage}

\begin{abstract}

We present the results of a radial velocity (RV) survey for 15 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi
dark cloud core. We obtained high-resolution echelle spectra at VLT
using Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
epochs for each object, and measured the shifts in their RVs to identify
candidates for binary/multiple systems in the sample. We found no
spectroscopic binary in our sample, based on the shape of cross-corelation
curves. We found 9 out of 18 (50 per cent) in our sample show a significant
RV change in 4--33~d time scale, and are considered as binary/multiple
`candidates.' The fraction slightly decreases to 43 per cent (6 out
of 14) if we consider the objects only in the UScoOB. These fractions
do not necessary represent that of a real binary population among
young BDs and VLM stars since their true multiplicities are still
to be confirmed by follow-up spectroscopic monitoring. Our RV-shift
tests successfully detected the recently confirmed 3 binaries in UScoOB
via high-resolution imaging technique. We found the RV dispersion
of the objects in UScoOB is very similar to that of the BDs and VLM
stars in Chamaeleon~I (Cha~I) previously studied by others. We also
measured the rotational velocities ($v\,\sin i$) of the samples,
and found good agreements with earlier studies. The distribution of
$v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which
is also similar to that of the Cha~I population.

\end{abstract}

\begin{keywords}
stars: binaries:spectroscopic -- stars: low-mass, brown dwarfs -- stars: formation -- stars:planetary system: formation
\end{keywords}

\section{Introduction }

\label{sec:Introduction}

Most stars are member of binary systems; hence, it is important for
a star formation theory to be able to predict the binary fraction,
period distribution, and mass-ratio distribution of newly born stellar
objects across a wide range mass spectrum. The study of the individual
binary system is the only direct mean to determine the fundamental
stellar properties such as stellar masses and radii.

Recent high resolution imaging studies of young brown dwarfs (BDs)
and very low-mass (VLM) stars have placed strong constraints on binaries
with separations of $\sim1-100\,\mathrm{au}$. For example, Hubble
Space Telescope (\emph{HST}) observations of $\alpha$~Per and the
Pleiades indicates a binary fraction ($f$) of $>10$~per~cent with
a bias towards separations ($a$) of less than $15$~au, and a mass-ratio
($q$) of $>0.7$ \citep{martin:2003} for objects around and below
the hydrogen burning limit (see also \citealt{bouy:2006}). A similar
lack of wide binaries were found in the field T-dwarf study \citep{burgasser:2003},
while $f=15$~per~cent was determined by \citet{close:2003} using
the adaptive optics at Gemini North. They also found an upper limit
to the semi-major axis distribution of $\sim20\,\mathrm{au}$. An
\emph{HST} study of more than 80 field last M and L dwarfs \citep{gizis:2003}
indicated $f=15$~per~cent with separations in the range of 1.6--16~au.
For s small sample (12) of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
$f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
by using similar imaging technique..

Using Monte Carlo simulation techniques, the data from radial velocity
surveys available on literatures, and carefully considering the sensitivity
and sampling biases, \citet{maxted:2005}  found an overall BD/VLM
binary frequency of 32--45 per~cent assuming $f=15$~per~cent for
$a>2.6$~au. A recent photometric study \citep{pinfield:2003} of
low-mass objects in Pleiades and Praesepe suggested, albeit indirectly,
$f$ as large as 50~per~cent. which would only be compatible with
direct imaging studies if 70--80~per~cent of those binaries have
$a<1\,\mathrm{au}$. For a more comprehensive review of the current
status of BD/VLM binary fraction and the separation distribution,
readers are refer to an excellent article on multiplicity studies
by \cite{burgasser:2006}.

The extensive imaging surveys provide excellent observational constraints
on wider BD+BD binaries, but it is now necessary to search for shorter
period BD+BD binaries systematically. Binaries with the separation
of less than 1~au are not resolved by current imaging technique,
but will be detectable as spectroscopic binaries, providing the mass-ratio
is not too extreme, and velocity separation is large enough. The first
BD+BD spectroscopic binary, PPl~15  \citep{basri:1999} showed a
double-peaked cross-correlation function with a maximum velocity separation
of $>70\,\kmps$. The binary was found to have an eccentric orbit
($e=0.4$) with a period of $\sim5.8\,\mathrm{d}$. \citet{basri:1999}
suggested that the formation process of substellar objects is biased
towards smaller separation binaries based on the short period of PPl~15
and the lack of Pleiades BD binaries with separations $>40\,\mathrm{au}$.
Note that the median separation of binaries with solar-type primaries
is 30~au \citet{duquennoy:1991}. The pioneer works on the RV studies
of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
and \citet{joergens:2006} who found a sevral binary candidates among
them; however, the orbital parameters and masses of binaries remains
unknown because the follow-up spectroscopic monitoring is lacking
or still being taking places. In addition to the follow-up observations,
the number of BDs and VLM star binary candidates should be increased
to have a better statistics on the short period binary parameters.

The separation distribution of BD/VLM binaries is critical to understanding
their origin. There are two main models for the formation of BDs and
VLM stars. First, they formed in a similar manner to higher mass stars,
but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002}).
Second, BD/VLM objects have low masses because they are ejected from
the dense core in which they form via dynamical interactions in multiple
system, cutting off their accretion before they have reached stellar
masses (\citealt{reipurth:2001}; \citealt{bate:2002}). Alternatively,
there is a third model in which a free-floating BD or planetary-mass
object can be formed in the process of the photo-evaporation \citep{whitworth:2004}.
The outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
removed by the strong radiation pressure from the nearby massive O
and B stars before the accretion onto the protostar at core centre
occurs. Apparently, this is more relevant to the high-mass star forming
clouds.

Due to the dynamical interaction involved in the second model, BD/VLM
binaries that survive are generally expected to have small separations.
In the first model, wider binaries may be expected to be more common.
\citet{bate:2002} suggested that close binaries ($a<10\,\mathrm{au}$)
do not form directly, but result from hardening of wider systems though
a combination of dynamical interactions, accretion and interactions
with circum-binary discs. If BD/VLM binaries have formed through such
mechanisms, one would expect to find binaries with 1--10~au separations
without also finding many with separation $<1$~au. If the absence/rarity
of binaries with 1~au were found, it would support the idea that
they are ejected quickly from multiple systems before they have undergone
the interactions that shorten the periods.

Our immediate aim is to identify spectroscopic and close BD/VLM binaries
using the high-resolution echelle spectroscopy at two epochs. This
experiment is sensitive to VLM binaries with separations of $<0.1$~au
which corresponds to a period of $\sim10\,\mathrm{d}$. A larger sample
of candidates will enable us to measure the binary fraction of these
short-period/close binaries (once confirmed), and address whether
there is a significant population of 'hidden' VLM companions. The
long term goal of this project to follow up the binary candidates
found in this paper by spectroscopically monitoring them in different
time scales, enabling us to obtain the radial velocity curves and
their minimum masses.

In Section~\ref{sec:observation-reduction}. we describe the observations
and the data reduction. The results of radial velocity and rotational
velocity ($v\,\sin i$) measurements are presented in Sections~\ref{sub:Radial-velocities}
and \ref{sub:Radial-velocities} respectively. We discuss the binary/multiplicity
fraction indicated by our RV survey in Section~\ref{sec:Binary-frequency}.
Finally, conclusions will be given in Section~\ref{sec:Conclusions}.

\section{Observations}

\label{sec:observation-reduction}

Our sample consist of 18 young very low-mass objects previously identified
in the star forming regions: 15 objects in the Upper Scorpius OB association
($\mathrm{d\approx145\, pc}$, \citealt{dezeeuw:1999}) from the list
of \citet{ardila:2000} and 3 objects in the $\rho$~Ophiuchi cloud
core ($\mathrm{d\approx150\, pc}$, \citealt{dezeeuw:1997}) from
 \citet{luhman:1999}. The spectral type of the objects spreads between
M5 and M8.5, and the age $<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999};
\citealt{ardila:2000}; \citealt{muzerolle:2003}; \citealt{kraus:2005}).
The sample is not complete, and the selection is mainly based on the
brightness and the observability. The basic known properties of the
targets based on literatures is summarised in Table~\ref{tab:literatures}.

We obtained high resolution spectra with the Kueyen telescope of VLT
(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
were carried out between April 5, 2004 and May 15, 2005 in the service
mode. For each object, the spectra were obtained at two different
epochs separated by 4--33~d to increase the chance of detectability
for multiplicities. For each object at a given night, two separate
spectra are obtained consecutively. This will allow us to derive more
reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
The data was obtained using the red arm of UVES spectrograph with
two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
were used. Unfortnately, the litheum lines at $\lambda\lambda6707.76$,$6707.93$
just fell shortward of the minimum wavelength. The slit width and
length of 1'' and 12'' are used respectively with a typical seeing
of 0.8''.

The data were reduced by the standard ESO pipeline procedures for
UVES echelle spectra. In summary, the data were corrected for bias,
interorder background, sky background, sky emission lines and cosmic
ray hits. Further, they were flattened, optimally extracted, and finally
the different orders were merged. No binning was performed to achieve
high resolution required for the RV measurements. The wavelength was
calibrated using the Thorium-Argon arc spectra with a typical value
of the standard deviation of the dispersion solution of 5~m\AA\,
which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
However, the autoguiding of the telescope keeps the star at the centre
of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
the upper limit for the systematic error in the RV measurements \citep{bailer-jones:2004}.
The accuracy of the wavelength calibration will be demonstrated in
the RV measurements of a RV standard in the following section. A typical
signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
15, and the heliocentric velocity correction was applied to the final
spectra.

%==========================================

\begin{table*}

\label{tab:literatures}

\caption{Summary of known properties of the targers from literatures: a.~\citet{luhman:1999} (original list for $\rho$~Oph), b.~\citet{ardila:2000} (original list for UScoOB),  c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003}, e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}. }

\begin{center}

\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{yes^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{yes^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{yes^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}

\end{center}

\end{table*}

%==========================================

\section{Results}

\label{sec:Results}

\subsection{Radial velocities}

\label{sub:Radial-velocities}

%==========================================

\begin{table*}

\caption{Summary of the observation, the heliocentric radial velocities ($\mathrm{RV}$) from two-epoch and the average rotational velocities ($v\sin i$). The uncetainties of relative radial velocties ($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049 and the average radial velocties ($\overline{\mathrm{RV}}$) are also given. The last column indicates whether a target is a candidate for multiplicity i.e.~the measured radial velocity changes from two different epoch is larger than $1\,\sigma_{\mathrm{RRV}}$ of each others (c.f.~Fig.~\ref{fig:radvel01}).}

\begin{center}

\begin{tabular}{lcrrrrrc}
\hline 
Object&
Date&
MDJ-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$&
candidate?\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
2004-Apr-25&
20.22051&
$-6.14\pm0.84$&
0.68&
&
&
\tabularnewline
&
2004-May-08&
33.27776&
$-5.96\pm0.60$&
0.34&
$-6.05\pm1.03$&
$16.5\pm0.6$&
no\tabularnewline
GY 141&
2004-May-11&
36.16016&
$-4.39\pm0.60$&
0.34&
&
&
\tabularnewline
&
2004-May-18&
43.15707&
$-2.95\pm0.51$&
0.11&
$-3.67\pm0.79$&
$4.4\pm1.4$&
yes\tabularnewline
GY 310&
2004-Apr-25&
20.32700&
$-4.83\pm0.74$&
0.54&
&
&
\tabularnewline
&
2004-May-10&
35.31139&
$-8.43\pm0.51$&
0.11&
$-6.63\pm0.90$&
$11.1\pm6.0$&
yes\tabularnewline
USco 40&
2004-Apr-06&
01.25900&
$-7.15\pm0.74$&
0.54&
&
&
\tabularnewline
&
2004-May-08&
33.25324&
$-6.80\pm0.51$&
0.11&
$-6.98\pm0.90$&
$34.2\pm0.5$&
no\tabularnewline
USco 53&
2004-Apr-05&
00.39651&
$-7.27\pm0.93$&
1.21&
&
&
\tabularnewline
&
2004-May-03&
28.23079&
$-5.43\pm0.74$&
0.55&
$-6.35\pm1.19$&
$40.0\pm0.6$&
no\tabularnewline
USco 55&
2004-Apr-06&
01.33509&
$-5.39\pm0.50$&
0.02&
&
&
\tabularnewline
&
2004-May-03&
28.30546&
$-6.38\pm0.53$&
0.27&
$-6.38\pm0.73$&
$22.9\pm0.8$&
yes\tabularnewline
USco 66&
2004-Apr-06&
01.29007&
$-5.32\pm0.57$&
0.29&
&
&
\tabularnewline
&
2004-May-03&
28.28683&
$-6.41\pm0.65$&
0.42&
$-5.87\pm0.86$&
$25.9\pm1.2$&
no\tabularnewline
USco 67&
2004-Apr-06&
01.21481&
$-6.01\pm0.74$&
0.55&
&
&
\tabularnewline
&
2004-May-03&
28.21759&
$-6.83\pm0.59$&
0.31&
$-6.42\pm0.90$&
$18.4\pm0.4$&
no\tabularnewline
USco 75&
2004-Apr-05&
00.37453&
$-6.75\pm0.67$&
0.44&
&
&
\tabularnewline
&
2004-May-08&
33.09532&
$-9.88\pm1.94$&
1.88&
$-8.32\pm2.05$&
$55.6\pm3.0$&
yes\tabularnewline
USco 100&
2004-Apr-06&
01.30836&
$-6.76\pm2.74$&
2.69&
&
&
\tabularnewline
&
2004-May-03&
28.26425&
$-10.23\pm1.80$&
1.73&
$-8.47\pm3.28$&
$43.7\pm3.2$&
no\tabularnewline
USco 101&
2004-Apr-05&
00.30191&
$-4.22\pm0.87$&
0.71&
&
&
\tabularnewline
&
2004-May-03&
28.14804&
$-6.07\pm0.69$&
0.48&
$-5.15\pm1.11$&
$19.1\pm0.3$&
yes\tabularnewline
USco 104&
2004-Apr-05&
00.27545&
$-5.83\pm0.50$&
0.02&
&
&
\tabularnewline
&
2004-May-03&
28.12391&
$-7.48\pm0.50$&
0.06&
$-6.66\pm0.06$&
$16.7\pm0.4$&
yes\tabularnewline
USco 109&
2004-Apr-06&
01.23587&
$-4.15\pm0.52$&
0.16&
&
&
\tabularnewline
&
2004-May-08&
33.11929&
$-4.41\pm0.50$&
0.03&
$-5.12\pm0.72$&
$8.6\pm1.2$&
yes\tabularnewline
USco 112&
2004-Apr-05&
00.34486&
$-2.70\pm0.69$&
0.47&
&
&
\tabularnewline
&
2004-May-08&
33.07139&
$-3.46\pm0.51$&
0.11&
$-3.08\pm0.86$&
$5.8\pm1.2$&
yes\tabularnewline
USco 121&
2004-Apr-25&
20.19466&
$-39.47\pm0.51$&
0.11&
&
&
\tabularnewline
&
2004-May-03&
28.18537&
$-42.43\pm0.50$&
0.02&
$-40.95\pm0.71$&
$17.6\pm1.3$&
yes\tabularnewline
USco 128&
2004-May-14&
39.28595&
$-7.41\pm0.85$&
0.69&
&
&
\tabularnewline
&
2004-May-18&
43.09885&
$-6.94\pm1.16$&
1.05&
$-7.18\pm1.44$&
$3.6\pm1.1$&
no\tabularnewline
USco 130&
2004-May-10&
35.26060&
$-4.83\pm0.54$&
0.21&
&
&
\tabularnewline
&
2004-May-14&
39.34201&
$-4.95\pm0.74$&
0.55&
$-4.89\pm0.92$&
$15.2\pm1.1$&
no\tabularnewline
USco 132&
2004-May-12&
37.28394&
$-7.18\pm0.58$&
0.30&
&
&
\tabularnewline
&
2004-Jun-18&
43.12719&
$-7.37\pm1.02$&
0.89&
$-7.28\pm1.17$&
$9.1\pm0.7$&
no\tabularnewline
\hline
\end{tabular}

\end{center}

\label{tab:summary_results}

\end{table*}

%==========================================

%==========================================

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=1.3]{figures/radvel_all01.eps}

\end{center}

\caption{Relative radial velocities (RVs) of objects measured in two different epochs. The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD). The objects are considered to have a non-constant  RV when the error bars of two data points do not overlap each other. The non-constant RV objects are considered as binary/multiple candidates.}

\label{fig:radvel01}

\end{figure*}

%==========================================

\addtocounter{figure}{-1}

%==========================================

\begin{figure*}

\begin{center}

\includegraphics[%
  clip,
  scale=1.3]{figures/radvel_all02.eps}

\end{center}

\caption{continued}

\label{fig:radvel02}

\end{figure*}

%==========================================

The radial velocities of each object are determined by using the cross-correlation
function of object spectra with that of a template star which has
a spectra type similar to those of our objects. By visual inspections,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, the defects and the fringes (in near infrared) of CCDs, The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation function
which is fitted by the combination of two gaussian functions sharing
their centres and a constant term. LHS~49 (Proxima Cen, M5.5) is
chosen as the template for this purpose. The radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for a consistency.

Before applying the cross-correlation technique to out main targets,
we have applied the technique to the radial velocity standard HD~140538
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.8\pm0.6\,\kmps$
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep{udry:1999}.

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainties of RVs with respect to the template star. The
two consecutive measurements of RVs (from same nights) are used to
find the RV of the night, and their uncertainties are obtained from
the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
two epochs are also given in the same table for a reference. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
for the values for USco~66 and USco~75. This difference is not surprising
since the former is a known binary \citep{kraus:2005} and the latter
is a non-constant RV object (a candidate for a multiple) found in
the RV-shift test which will be discussed next.

For each object and for each RV measurement, the deviations ($\Delta\mathrm{RV}$)
from the average RV are computed and summaries in Fig.~\ref{fig:radvel01}
along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
to aid the identifications of multiplicity candidates. Note that in
computing $\Delta\mathrm{RV}$ we do not require the knowledge of
absolute or the heliocentric radial velocities, but only the relative
velecities (with respect to a template). We choose a object as a candidate
when the 1$\sigma_{\mathrm{RRV}}$ error bar from each RV measurement
overlaps one another. Using this simple criteria, the candidate were
selected and indicated in the same table (Table~\ref{tab:summary_results}).
We found 9 out of 18 (50 per cent of) our sample are considered as
candidates. The recent observation of \citet{kraus:2005} (which was
not known to authors at the time of our observation: April--May, 2004)
confirms that USco~65 and USco~66 are multiple systems, and USco~109
is most likely a multiple system. In our RV-shift tests, we found
all the multiples confirmed by \citet{kraus:2005} in our multiple
candidates. Further they found USco~67, 128, 130, 132 as non-multiple,
and similarly we found them as 'non-candidates' for multiplicity.
The discrepancy between their results and ours are only in USco~75
and USco~112. While our results suggests that these are candidates
for multiple systems, \citet{kraus:2005} did not find them as multiple
systems. This difference may be caused by the difference in sensitivity
(on a binary separation) of the two different methods. Another possible
caused of the difference is that the uncertainties in RVs may be underestimated.
The surface activities of the objects may also contribute noise in
the RV measuements; however, the levels of th noise is expeted be
small for BD and VLM stars (c.f.~\citealt{joergens:2006}).

Finally, the histogram of the RVs using only the objects in UScoOB
is given in Figure~\ref{fig:vrad_vrot_histrogram}. The total number
of the objects is 14. Note that USco~121 is excluded from the graph
since it is identified as a non-member of the UScoOB association based
on the RV value (see Table~\ref{tab:summary_results}).  \citet{muzerolle:2003}
also found it to be a likely non-member based on the radial velocity
and the low lithium abundance. The distribution of the RVs in the
figure was fitted by a gaussian function. We found that the standard
deviation and the peak position of the radial velocity distribution
are $1.2\,\kmps$ and $-5.9\,\kmps$ respectively. The former is very
similar to the standard deviation (0.9~$\kmps$) of the radial velocity
distribution of 9 BDs and VLM objects in Cha~I found by \citet{joergens:2006b}.
They also studied the radial velocity distribution of more massive
25 T~Tauri stars in Cha~I, and found the standard deviations ($1.3\,\kmps$)
is not significantly different from that of the brown dwarfs and the
very low-mass objects. Unfortunately, we do not have the radial velocity
measurements of the higher mass counter parts (T~Tauri stars) in
Upper Sco OB association. This is also planned for a near future investigation
as this is important for the study of the mass dependency of the kinematics
in a young stellar cluster.

According to the hydrodynamical calculation of a low-mass star forming
cluster of \cite{bate:2003} which yields a stellar density of $1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$,
the rms dispersion (1-D) of the stars and the BDs is $1.2\,\kmps$.
Similarly for the model with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\, pc^{-3}}$),
the rms dispersion is 2.5~$\kmps$ (\citealt{bate:2005}). The standard
deviation of $\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our
analysis is more comparable the lower stellar density model.

%==========================================

\begin{figure*}

\begin{center}

\begin{tabular}{cc}
\includegraphics[%
  clip,
  scale=0.45]{figures/radvel_hist.eps}&
\includegraphics[%
  clip,
  scale=0.45]{figures/vrot_hist.eps}\tabularnewline
\end{tabular}

\end{center}

\caption{Histogram of the average heliocentric radial velocities (left) and the rotational velocities (right) of 14 UScoOB BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding USco~121, non-member). The gaussian fit (dash) of the radial velociity distribution gives the standard deviation of  $1.2\,\kmps$ and the peak position of $-5.9\,\kmps$.  The log-normal fit (dash-dot) of  the rotational velocity distribution gives  the standard deviation $27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}

\label{fig:vrad_vrot_histrogram}

\end{figure*}

%==========================================

\subsection{Rotational velocities}

\label{sub:Rotational-velocities}

The rotational velocities of the objects are determined by measuring
the widths of the cross correlation curves of the target spectra against
a templates spectra from an object which is known to have a very small
rotational velocity. The line broadening of the targets are assumed
to be dominated by rotational broadening. As in the cases for the
radial velocity measurements, LHS~49 is chosen for the template.
Using its known period ($P\approx83\,\mathrm{d}$, \citealt{benedict:1998})
and radius ($R_{*}\approx0.145\,\mathrm{R_{\odot}}$ from the VLTI
measurement by \citealt{segransan:2003}), the rotational velocity
of LHS~49 is estimated as $v\,\sin i=2\pi R_{*}/P\approx0.1\,\kmps$;
hence, negligibly small.

The width of the cross-correlation curves ($\sigma_{\mathrm{CCF}}$)
are calibrated with the rotational velocities ($v\,\sin i$) by cross
correlating the template spectra against the same template spectra
with added rotation (convolved with a given $v\,\sin i$), as similarly
done by e.g.~\citet{tinney:1998}, \citet{mohanty:2003} and \citet{white:2003}.
The linear limb-darkening law with a solar-like parameter ($\epsilon=0.6$)
was assumed in the formulation of the rotational profile described
by \citet{gray:1992}, his Eq.~17.12. For each object, two measurements
of rotational velocities are computed from two independent spectra
obtained at different epochs. As similary done for the RV measurements,
the mean and the standard deviation of the mean are used as the final
rotational velocity and its uncertainty. The final results are placed
in Table~\ref{tab:summary_results}. In general, our measurements
are in good agreement with the earlier measurements of \citet{muzerolle:2003}
and \citet{mohanty:2005}, given in Table~\ref{tab:literatures}.
For example, \citet{muzerolle:2003} found $v\,\sin i=16.8\pm2.7\,\mathrm{km\, s^{-1}}$
for GY~5 while we found $v\,\sin i=16.5\pm0.6\,\mathrm{km\, s^{-1}}$.

The range of $v\,\sin i$ found among our objects is $3.6$--$55.6\,\kmps$,
and a similar range is also found by \citet{mohanty:2005}. The left
panel of Figure~\ref{fig:vrad_vrot_histrogram} shows the histogram
of $v\,\sin i$ distribution for the UScoOB objects (14 objects excluding
USco 121, non member). The log-normal fit of this distribution gives
the peak position at $16.9\,\kmps$ and the standard deviation $\sigma=27.8\,\kmps$.
Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
bin size used for UScoOB obects and the log-normal fit, we find the
$v\,\sin i$ distribution of the BD and VLM stars (8 objects) in Cha~I
peaks at $15.4\,\kmps$, and has the standard deviation of $8.0\,\kmps$.
The peak of the distribution is similar to that of Upper Sco objects,
but the standard deviation of the distribution is significantly smaller
than that of the Upper Sco objects. The difference maybe due to the
very small number of samples. A similar fit was applied to the $v\,\sin i$
distribution of 14 T~Tauri stars in Cha~I using the data of \citet{joergens:2001},
and we found the peak at $17.0\,\kmps$ and the standard deviation
$25.9\,\kmps$ which are very similar to those of the Upper Sco brown
dwarf candidate objects.

\section{Binary frequency}

\label{sec:Binary-frequency}

According to Table~\ref{tab:summary_results}, 9 out of 18 (50 per
cent of) samples are considered as binary/multiple candidates. The
fraction slightly decreases to 43 per cent (6 out of 14) if we consider
the objects only in the UScoOB. These fractions are significantly
larger than the binary fraction (25~per~cent, 3 out of 12) found
by the recent high-resolution imaging survey of brown dwarfs and very
low-mass objects (M5.5--M7.5 ) in the UScoOB \citep{kraus:2005}.
The imaging surveys are sensitive to wider binaries (separation$\gtrsim4\,\mathrm{au}$)
while our technique is more sensitive to narrower ($\lesssim1\,\mathrm{au}$)
or shorter period ($\sim10\,\mathrm{d}$) binaries. However, our RV-shift
test also detected all the binaries found in the imaging survey of
\citet{kraus:2005}, demonstrating that the method is also effective
in the systems with a separation 5--18~au. In Section~\ref{sub:Radial-velocities},
we have found all the binaries confirmed by \citet{kraus:2005} also
as our binary/multiple candidates. In addition to those samples commonly
found, we have two more candidates (USco~75 and USco~112) which
are in the sample of \citet{kraus:2005}, but not detected as binaries
by them. If we assume these objects are real binary/multiple systems
but not detected by the imaging survey because of possibly very small
separations, their multiplicity fraction would increase to 5 out of
9 (56~per~cent) which is more consistent with the fraction suggested
by our RV survey.

Another possible reason for the different binary fraction suggested
by our data is that the uncertainties in the RV values may be underestimated.
Since the our suggested binary fraction is merely that for the binary
`candidates', the follow-up RV monitoring of the candidates must be
done to confirm the true multiplicity, and to determined firmer constraint
on the binary/multiple faction in the UScoOB. This is planned for
a near future. The binary fraction of slightly more massive pre-main-sequence
stars was studied by \citet{kohler:2000} using the K-band speckle
interferometry of X-ray selected samples. For the UScoOB members with
spectral type M0--M5 (0.7--0.13~$\mathrm{M_{\odot}}$), they found
the binary fraction of $52\left(\pm10\right)$~per~cent (26 out
of 50) with the separation 21--1000~au. On the other hand, \citet{kohler:2000}
found no wide ($>20\,\mathrm{au}$) binary in their survey, and suggested
that there may be a discontinuity in separation distribution around
$M_{*}\sim0.1\,\mathrm{M_{\odot}}$.

A similar imaging survey of the brown dwarf candidates in Cha~I cloud
by \citet{neuhaeuser:2002} and \citet{neuhaeuser:2003} also found
the multiplicity rate $\lesssim10\,\mathrm{per\, cent}$ using 12
objects (Cha~H$\alpha$~1--12 with M6--M8). Using a subset of the
same sample and the same radial velocity technique used in this paper,
\citet{joergens:2006} found only 11~per~cent (1 out of 9) of the
sample showed non-constant RVs in her multi-epoch data, indicating
a much smaller multiplicity fraction. It is unclear at this moment
whether the difference is caused by the physical nature of the two
different star forming regions.

\section{Conclusions}

\label{sec:Conclusions}

We have presented two-epoch RV survey of 18 young BDs and VLM stars
in UScoOB and $\rho$~Oph dark cloud core using the high resolution
UVES echelle spectroscopy at VLT. The amount of the shifts in RVs
in time is used to identify the candidates for multiplicity.

We found 9 out of 18 objects (50~per~cent) are possible candidates
in this analysis. For the objects in UScoOB, we found 6 out of 14
objects (43~per~cent) as candidates. Compared to the average binary
fraction ($\sim20\,\mathrm{per\, cent}$) of magnitude-limited imaging
surveys for BDs and VLM stars (M6 and later) in the field (c.f.~\citealt{burgasser:2006}),
the fraction of the binary `candidates' found by this RV survey is
significantly higher. The possible reasons to for the discrepancy
are: (1) caused by the different sensitivity on the binary separation
in the imaging and RV technique, (2) caused by possibly under estimated
uncertainties in the measured RV values. The true multiplicity of
the candidates must be confirmed by follow-up spectroscopy monitoring
of candidates.

We found a good agreement with the high resolution imaging survey
of the BD and VLM objects in UScoOB of \citet{kraus:2005}. All three
confirmed binaries in UScoOB by \citet{kraus:2005} are found as the
multiplicity candidate this RV survey; however, we found two objects
(USco~75 and USco~112) also as binary candidates while they found
them as singles.

From the distribution of RV values in UScoOB, we confirmed that USco~121
is most likely a non-member of the association, as similarly found
so by  \citet{muzerolle:2003}. We found the RV dispersion of the
objects in UScoOB is very similar to that of the BDs and VLM stars
in Chamaeleon~I (Cha~I) previously studied by others. The rotational
velocities ($v\,\sin i$) of the samples are also measured. The distribution
of $v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$
which is similar to that of the Cha~I population.

The follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates are identified from the earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} pointed out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straight forwardly,
i.e. without correcting for bias.

\section*{Acknowledgements}

This work is supported by PPARC rolling grant PP/C501609/1. We thank
the staff of VLT of the ESO for the observations carried out in the
service mode.

%

%

%

%----------------------------------------------------

% Bibliography follows here.

%-----------------------------------------------------

%

%

%

\bibliographystyle{mn}

\bibliography{local}

%

\label{lastpage}
\end{document}

### 2006-04-07 torus/amr_mod.f90
wr104 working again - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@702 25464f21-6099-402c-b30a-640f1d40d38b

@@ -213,6 +213,7 @@ CONTAINS
        grid%octreeRoot%threeD = .false.
        grid%octreeRoot%maxChildren = 4
     else
+       grid%octreeRoot%cylindrical = .false.
        grid%octreeRoot%twoD = .false.
        grid%octreeRoot%threeD = .true.
        grid%octreeRoot%maxChildren = 8
@@ -435,40 +436,40 @@ CONTAINS
        endif
        parent%child(newChildIndex)%splitAzimuthally = .false.
        parent%child(newChildIndex)%maxChildren = 4
-    endif
 
 
-    if (PRESENT(splitAzimuthally)) then
-       if (splitAzimuthally) then
-          parent%child(newChildIndex)%splitAzimuthally = .true.
-          parent%child(newChildIndex)%maxChildren = 8
-          rVec =  subcellCentre(parent,iChild)
-          parent%child(newChildIndex)%phi = atan2(rvec%y, rVec%x)
-          if (parent%child(newChildIndex)%phi < 0.d0) then
-              parent%child(newChildIndex)%phi = parent%child(newChildIndex)%phi + twoPi 
-          endif
-          if (parent%splitAzimuthally) then
-             parent%child(newChildIndex)%dphi = parent%dphi/2.d0
+       if (PRESENT(splitAzimuthally)) then
+          if (splitAzimuthally) then
+             parent%child(newChildIndex)%splitAzimuthally = .true.
+             parent%child(newChildIndex)%maxChildren = 8
+             rVec =  subcellCentre(parent,iChild)
+             parent%child(newChildIndex)%phi = atan2(rvec%y, rVec%x)
+             if (parent%child(newChildIndex)%phi < 0.d0) then
+                parent%child(newChildIndex)%phi = parent%child(newChildIndex)%phi + twoPi 
+             endif
+             if (parent%splitAzimuthally) then
+                parent%child(newChildIndex)%dphi = parent%dphi/2.d0
+             else
+                parent%child(newChildIndex)%dphi = parent%dphi
+             endif
           else
-             parent%child(newChildIndex)%dphi = parent%dphi
+             if (parent%splitAzimuthally) then
+                rVec =  subcellCentre(parent,iChild)
+                parent%child(newChildIndex)%phi = atan2(rvec%y, rVec%x)
[…]

### 2006-04-07 torus/cluster_class.f90

@@ -403,7 +403,7 @@ contains
        case("wr104")
           call find_n_particle_in_subcell(nparticle, density_ave, sphData, &
                thisOctal, subcell)          
-          thisOctal%rho(subcell) = max(1.d-30,real(nparticle)/ thisOctal%subcellsize**3)
+          thisOctal%rho(subcell) = max(1.d-30,dble(nparticle)/ cellVolume(thisOctal, subcell))
     end select
 
   end subroutine assign_density
@@ -433,37 +433,39 @@ contains
     ! Finding the number of particles in this subcell first
     call find_n_particle_in_subcell(nparticle, density_ave, sphData,&
          thisOctal, subcell)
-    ! Allocate the memory for new particle list of the child
-    ALLOCATE(thisOctal%child(newChildIndex)%gas_particle_list(nparticle))
 
-    ! # of particles in thisOctal
-    np = SIZE(thisOctal%gas_particle_list)
-
-    ! Units of length
-    udist = get_udist(sphData) / 1.0d10  ! [10^10cm]
+    if (nParticle > 0) then
+       ! Allocate the memory for new particle list of the child
+       ALLOCATE(thisOctal%child(newChildIndex)%gas_particle_list(nparticle))
        
-    k=0
-    do i = 1, np
-       ! extract the SPH index of particles in the parent cell.
-       j = thisOctal%gas_particle_list(i)
+       ! # of particles in thisOctal
+       np = SIZE(thisOctal%gas_particle_list)
        
-       ! copy this value if this particle is in this child.
-       ! Using a routine in sph_data_class. 
-       call get_position_gas_particle(sphData, j, x, y, z)
+       ! Units of length
+       udist = get_udist(sphData) / 1.0d10  ! [10^10cm]
        
-       ! convert units
-       x = x*udist; y = y*udist;  z = z*udist  ! [10^10cm]
-       
-       ! quick check to see if this gas particle
-       ! belongs to this child cell.
-       if ( within_subcell(thisOctal, subcell, x, y, z) ) then
-          k = k+1
-          ! add this particle index to this child using
-          ! a routine in linked_list_class.f90
-          thisOctal%child(newChildIndex)%gas_particle_list(k) = j
-       end if
-    end do
-
+       k=0
+       do i = 1, np
+          ! extract the SPH index of particles in the parent cell.
+          j = thisOctal%gas_particle_list(i)
+          
+          ! copy this value if this particle is in this child.
+          ! Using a routine in sph_data_class. 
[…]

### 2006-04-07 torus/dust_mod.f90

@@ -893,6 +893,36 @@ recursive subroutine fillAMRgridMie(thisOctal, sigmaSca, sigmaAbs, nLambda)
 
   end subroutine fillDustUniform
 
+
+  recursive subroutine sublimateDustWR104(thisOctal)
+    use input_variables, only : tThresh
+    type(OCTAL), pointer :: thisOctal, child
+    integer :: subcell, i
+    real(double) :: temperature
+    real(double), parameter :: subRange = 50.d0
+    real(double) :: frac
+    do subcell = 1, thisOctal%maxChildren
+       if (thisOctal%hasChild(subcell)) then
+          ! find the child
+          do i = 1, thisOctal%nChildren, 1
+             if (thisOctal%indexChild(i) == subcell) then
+                child => thisOctal%child(i)
+                call sublimateDustWR104(child)
+                exit
+             end if
+          end do
+       else
+          temperature = thisOctal%temperature(subcell)
+
+          frac = 1.d0
+          if (temperature > tThresh) then
+             frac = exp(-dble((temperature-tThresh)/subRange))
+          endif
+          thisOctal%dustTypeFraction(subcell,1) = frac
+       endif
+    end do
+  end subroutine sublimateDustWR104
+
   recursive subroutine sublimateDust(grid, thisOctal, totFrac, nFrac, tauMax)
 
     use input_variables, only : rInner, rOuter

### 2006-04-07 torus/grid_mod.f90

@@ -6590,7 +6590,6 @@ contains
 !             plot_this_subcell = .false.
 !          end if
 
-
           
           if (plot_this_subcell) then
              select case (name)

### 2006-04-07 torus/inputs_mod.f90

@@ -228,7 +228,7 @@ subroutine inputs()
 
      if (doSmoothGrid) then
        call getReal("smoothfactor", smoothFactor, cLine, nLines, &
-            "Inter-cell maximum ratio before smooth: ","(a,f6.1,1x,a)", 5., ok, .false.)
+            "Inter-cell maximum ratio before smooth: ","(a,f6.1,1x,a)", 5., ok, .true.)
      else
        smoothFactor = 0.0      
      end if

### 2006-04-07 torus/octal_mod.f90

@@ -343,35 +343,67 @@ CONTAINS
     !
     TYPE(octalVector)     :: cellCenter
     real(double) :: x0, y0, z0  ! cell center
-    real(double) :: d, dp, dm
+    real(double) :: d, dp, dm, r, phi, r0, phi0, dphi
     real(double), parameter :: eps = 0.0d0
     
     d = (this%subcellSize)*0.5d0
     dp = d+eps
     dm = d-eps
+
     
     cellCenter = subcellCentre(this,subcell)
     x0=dble(cellCenter%x); y0=dble(cellCenter%y); z0=dble(cellCenter%z)
-
     ! Fortran check the condidtion from
     ! the top, so this should work, and it is faster...
 
     if (this%threeD) then
-       if ( x > (x0+dp) ) then
-          out = .false.
-       else if ( x < (x0-dm)) then
-          out = .false.      
-       elseif ( y > (y0+dp) ) then
-          out = .false.
-       elseif ( y < (y0-dm)) then
-          out = .false.
-       elseif ( z > (z0+dp) ) then
-          out = .false.
-       elseif ( z < (z0-dm)) then
-          out = .false.
+       if (.not.this%cylindrical) then
+          if ( x > (x0+dp) ) then
+             out = .false.
+          else if ( x < (x0-dm)) then
+             out = .false.      
+          elseif ( y > (y0+dp) ) then
+             out = .false.
+          elseif ( y < (y0-dm)) then
+             out = .false.
+          elseif ( z > (z0+dp) ) then
+             out = .false.
+          elseif ( z < (z0-dm)) then
+             out = .false.
+          else
+             out = .true.
+          end if
        else
-          out = .true.
-       end if
+          r = sqrt(x**2+y**2)
+          phi = atan2(y,x)
+          if (phi < 0.d0) phi = phi + twoPi
+          r0 = sqrt(x0**2 + y0**2)
+          phi0 = atan2(y0,x0)
+          
+          if (phi0 < 0.d0) phi0 = phi0 + twoPi
+          if (this%splitAzimuthally) then
+             dphi = this%dphi/4.d0
+          else
+             dphi = this%dphi/2.d0
+          endif
+
+          if ( z > (z0+dp) ) then
+             out = .false.
+          elseif ( z < (z0-dm)) then
+             out = .false.
[…]

### 2006-04-07 torus/spectrum_mod.f90

@@ -75,7 +75,7 @@ module spectrum_mod
     subroutine readSpectrum(spectrum, filename)
       type(SPECTRUMTYPE) :: spectrum
       character(len=*) :: filename
-      real :: fTemp(12000),xTemp(12000)
+      real :: fTemp(120000),xTemp(120000)
       integer :: nLambda, i
 
       open(20,file=filename,form="formatted",status="old")

### 2006-04-10 BD_radvel/kurosawa.tex
committed by th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@703 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-04-07 BD_radvel/main.tex
@@
 \begin{document}
-\title[Radial and rotational velocities of young brown dwarfs candidates  in the Upper Sco and $\rho$~Oph]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in Upper Scorpius OB association and $\rho$~Ophiuchi cloud core}
+\title[Radial and rotational velocities of young BDs and VLM stars]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core}
 
@@
 
-We present the results of a radial velocity (RV) survey for 15 brown
+We present the results of a radial velocity (RV) survey of 15 brown
 dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
@@
 epochs for each object, and measured the shifts in their RVs to identify
-candidates for binary/multiple systems in the sample. We found no
-spectroscopic binary in our sample, based on the shape of cross-corelation
-curves. We found 9 out of 18 (50 per cent) in our sample show a significant
+candidates for binary/multiple systems in the sample.
+We found 9 out of 18 (50 per cent) in our sample show a significant
 RV change in 4--33~d time scale, and are considered as binary/multiple
@@
 young BDs and VLM stars since their true multiplicities are still
-to be confirmed by follow-up spectroscopic monitoring. Our RV-shift
-tests successfully detected the recently confirmed 3 binaries in UScoOB
+to be confirmed by follow-up spectroscopic monitoring. We found no
+double-lined spectroscopic binaries in our sample, based on the shape of cross-corelation
+curves. Our RV-shift tests successfully detected the recently confirmed 3 binaries in UScoOB
 via high-resolution imaging technique. We found the RV dispersion
@@
 stars in Chamaeleon~I (Cha~I) previously studied by others. We also
-measured the rotational velocities ($v\,\sin i$) of the samples,
+measured the rotational velocities ($v\,\sin i$) of the sample,
 and found good agreements with earlier studies. The distribution of
 $v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which
-is also similar to that of the Cha~I population.
+is similar to that of the Cha~I population.
 
@@
 
-Most stars are member of binary systems; hence, it is important for
-a star formation theory to be able to predict the binary fraction,
+Most stars are member of binary systems and it is therefore important that
+a complete star formation theory be able to predict the binary fraction,
 period distribution, and mass-ratio distribution of newly born stellar
-objects across a wide range mass spectrum. The study of the individual
-binary system is the only direct mean to determine the fundamental
+objects across a wide range of masses. Furthermore, the study of the individual
+binary system is the only direct means to determine the fundamental
 stellar properties such as stellar masses and radii.
 
-Recent high resolution imaging studies of young brown dwarfs (BDs)
+Recent high-resolution imaging studies of young brown dwarfs (BDs)
 and very low-mass (VLM) stars have placed strong constraints on binaries
@@
 the hydrogen burning limit (see also \citealt{bouy:2006}). A similar
-lack of wide binaries were found in the field T-dwarf study \citep{burgasser:2003},
+lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
 while $f=15$~per~cent was determined by \citet{close:2003} using
@@
 $f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
-by using similar imaging technique..
-
-Using Monte Carlo simulation techniques, the data from radial velocity
-surveys available on literatures, and carefully considering the sensitivity
+by using a similar imaging technique..
+
+Using a Monte Carlo simulation, the data from radial velocity
+surveys available in the literature, and by carefully considering the sensitivity
 and sampling biases, \citet{maxted:2005}  found an overall BD/VLM
@@
 status of BD/VLM binary fraction and the separation distribution,
-readers are refer to an excellent article on multiplicity studies
+readers are refer to a recent review of multiplicity studies
 by \cite{burgasser:2006}.
@@
 period BD+BD binaries systematically. Binaries with the separation
-of less than 1~au are not resolved by current imaging technique,
+of less than 1~au are not resolved by current imaging techniques,
 but will be detectable as spectroscopic binaries, providing the mass-ratio
@@
 Note that the median separation of binaries with solar-type primaries
-is 30~au \citet{duquennoy:1991}. The pioneer works on the RV studies
+is 30~au \citet{duquennoy:1991}. Pioneering work on the RVs
 of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
-and \citet{joergens:2006} who found a sevral binary candidates among
-them; however, the orbital parameters and masses of binaries remains
+and \citet{joergens:2006} who found a several binary candidates;
+however, the orbital parameters and masses of binaries remains
 unknown because the follow-up spectroscopic monitoring is lacking
-or still being taking places. In addition to the follow-up observations,
-the number of BDs and VLM star binary candidates should be increased
-to have a better statistics on the short period binary parameters.
+or still being undertaken. In addition to the follow-up observations,
+the number of BDs and VLM star binary candidates needs to be increased
+in order to have better statistics on short-period binary parameters.
 
@@
 their origin. There are two main models for the formation of BDs and
-VLM stars. First, they formed in a similar manner to higher mass stars,
-but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002}).
-Second, BD/VLM objects have low masses because they are ejected from
+VLM stars: first, they formed in a similar manner to higher mass stars,
+but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002});
+second, BD/VLM objects have low masses because they are ejected from
 the dense core in which they form via dynamical interactions in multiple
@@
 there is a third model in which a free-floating BD or planetary-mass
-object can be formed in the process of the photo-evaporation \citep{whitworth:2004}.
-The outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
-removed by the strong radiation pressure from the nearby massive O
-and B stars before the accretion onto the protostar at core centre
-occurs. Apparently, this is more relevant to the high-mass star forming
-clouds.
+object can be formed in the process of the photo-evaporation \citep{whitworth:2004} with
+the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
+removed by the strong radiation pressure from the nearby massive OB
+ stars before the accretion onto the protostar at core centre
+occurs.
 
@@
 with circum-binary discs. If BD/VLM binaries have formed through such
-mechanisms, one would expect to find binaries with 1--10~au separations
-without also finding many with separation $<1$~au. If the absence/rarity
+mechanisms, one would not expect to find binaries with 1--10~au separations
+without also finding many with separation $<1$~au. If an absence/rarity
 of binaries with 1~au were found, it would support the idea that
 they are ejected quickly from multiple systems before they have undergone
-the interactions that shorten the periods.
+the interactions that shorten their periods.
 
@@
 long term goal of this project to follow up the binary candidates
-found in this paper by spectroscopically monitoring them in different
+found in this paper by spectroscopically monitoring them over different
 time scales, enabling us to obtain the radial velocity curves and
@@
 and \ref{sub:Radial-velocities} respectively. We discuss the binary/multiplicity
-fraction indicated by our RV survey in Section~\ref{sec:Binary-frequency}.
-Finally, conclusions will be given in Section~\ref{sec:Conclusions}.
+fraction indicated by our RV survey in Section~\ref{sec:Binary-frequency}, and give
+our conclusions in Section~\ref{sec:Conclusions}.
 
@@
 
-Our sample consist of 18 young very low-mass objects previously identified
-in the star forming regions: 15 objects in the Upper Scorpius OB association
-($\mathrm{d\approx145\, pc}$, \citealt{dezeeuw:1999}) from the list
+Our sample consists of 18 young, very low-mass objects: 15 objects in the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$, \citealt{dezeeuw:1999}) from the list
 of \citet{ardila:2000} and 3 objects in the $\rho$~Ophiuchi cloud
 core ($\mathrm{d\approx150\, pc}$, \citealt{dezeeuw:1997}) from
- \citet{luhman:1999}. The spectral type of the objects spreads between
+ \citet{luhman:1999}. The spectral type of the objects range between
 M5 and M8.5, and the age $<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999};
 \citealt{ardila:2000}; \citealt{muzerolle:2003}; \citealt{kraus:2005}).
-The sample is not complete, and the selection is mainly based on the
-brightness and the observability. The basic known properties of the
-targets based on literatures is summarised in Table~\ref{tab:literatures}.
-
-We obtained high resolution spectra with the Kueyen telescope of VLT
+The sample is not complete, and the selection was solely based on 
+brightness and the observability. The basic properties of the
+targets based on the literature is summarised in Table~\ref{tab:literatures}.
+
+We obtained high-resolution spectra with the Kueyen telescope of VLT
 (Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
-were carried out between April 5, 2004 and May 15, 2005 in the service
-mode. For each object, the spectra were obtained at two different
-epochs separated by 4--33~d to increase the chance of detectability
-for multiplicities. For each object at a given night, two separate
-spectra are obtained consecutively. This will allow us to derive more
+were carried out between 2004 April 5 and 2005 (XXX?)  May 15 in  service
+mode. For each object, spectra were obtained at two different
+epochs separated by several (between 4 and 33~d). For each object at a given 
+night, two separate spectra are obtained consecutively. This allows us to derive more
 reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
-The data was obtained using the red arm of UVES spectrograph with
+The data were obtained using the red arm of UVES spectrograph with
 two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
 coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
-were used. Unfortnately, the litheum lines at $\lambda\lambda6707.76$,$6707.93$
-just fell shortward of the minimum wavelength. The slit width and
-length of 1'' and 12'' are used respectively with a typical seeing
+were used. The slit width and length of 1'' and 12'' were used respectively with a typical seeing
 of 0.8''.
 
-The data were reduced by the standard ESO pipeline procedures for
+The data were reduced via the standard ESO pipeline procedures for
 UVES echelle spectra. In summary, the data were corrected for bias,
 interorder background, sky background, sky emission lines and cosmic
-ray hits. Further, they were flattened, optimally extracted, and finally
+ray hits. They were then flattened, optimally extracted, and finally
 the different orders were merged. No binning was performed to achieve
@@
 
-\caption{Summary of known properties of the targers from literatures: a.~\citet{luhman:1999} (original list for $\rho$~Oph), b.~\citet{ardila:2000} (original list for UScoOB),  c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003}, e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}.
+\caption{Summary of known properties of the targets from literature: a.~\citet{luhman:1999} (original list for $\rho$~Oph), b.~\citet{ardila:2000} (original list for UScoOB),  c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003}, e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}.
 }
@@
 
-\caption{Summary of the observation, the heliocentric radial velocities ($\mathrm{RV}$) from two-epoch and the average rotational velocities ($v\sin i$).
+\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$) from two-epoch and the average rotational velocities ($v\sin i$).
 The uncetainties of relative radial velocties ($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049 and the average radial velocties ($\overline{\mathrm{RV}}$) are also given.
@@
 \caption{Relative radial velocities (RVs) of objects measured in two different epochs.
-The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD).
+The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD; XXX do you really mean MJD rather than heliocentric JD????).
 The objects are considered to have a non-constant  RV when the error bars of two data points do not overlap each other.
@@
 
-The radial velocities of each object are determined by using the cross-correlation
-function of object spectra with that of a template star which has
-a spectra type similar to those of our objects. By visual inspections,
+The radial velocities of each object were determined by using the cross-correlation
+function of the object spectrum with that of a template star which has
+a spectra type. By visual inspection,
 the wavelength ranges used for the cross-correlation calculations
 are chosen by avoiding the regions of spectra affected by the telluric
-lines, the defects and the fringes (in near infrared) of CCDs, The
+lines, and defects and fringes (in near infrared) of the CCDs. The
 radial velocities of objects with respect to the template are obtained
@@
 which is fitted by the combination of two gaussian functions sharing
-their centres and a constant term. LHS~49 (Proxima Cen, M5.5) is
+their centres and a constant term (XXXX What does this mean?). LHS~49 (Proxima Cen, M5.5) was
 chosen as the template for this purpose. The radial velocity of the
@@
 measurements of the heliocentric radial velocities, our measurement
-($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for a consistency.
+($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for consistency.
 
@@
 the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
-is the uncertainties of RVs with respect to the template star. The
+is the uncertainty of RV with respect to the template star. The
 two consecutive measurements of RVs (from same nights) are used to
@@
 the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
-The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
-two epochs are also given in the same table for a reference. The $\overline{\mathrm{RV}}$
+(XXX What do you need to include the uncertainty in the template
+star measurement when we are looking for relative changes in the
+bd RVs?) The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
+two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
 values of the objects in UScoOB are consistent with the earlier measurements
 of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
-for the values for USco~66 and USco~75. This difference is not surprising
+for the values for USco~66 and USco~75. This is unsurprising
 since the former is a known binary \citep{kraus:2005} and the latter
@@
 along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
-to aid the identifications of multiplicity candidates. Note that in
+to aid the identification of multiplicity candidates. Note that in
 computing $\Delta\mathrm{RV}$ we do not require the knowledge of
 absolute or the heliocentric radial velocities, but only the relative
-velecities (with respect to a template). We choose a object as a candidate
+velocities (with respect to a template). We identify an object as a candidate
 when the 1$\sigma_{\mathrm{RRV}}$ error bar from each RV measurement
@@
 (on a binary separation) of the two different methods. Another possible
-caused of the difference is that the uncertainties in RVs may be underestimated.
-The surface activities of the objects may also contribute noise in
+caused of the difference is that the uncertainties in RVs may be underestimated, since
+surface activity of the objects may also contribute noise in
 the RV measuements; however, the levels of th noise is expeted be
@@
 
-According to the hydrodynamical calculation of a low-mass star forming
+According to the hydrodynamical simulations of a low-mass star-forming
 cluster of \cite{bate:2003} which yields a stellar density of $1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$,
@@
 
-\caption{Histogram of the average heliocentric radial velocities (left) and the rotational velocities (right) of 14 UScoOB BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding USco~121, non-member).
-The gaussian fit (dash) of the radial velociity distribution gives the standard deviation of  $1.2\,\kmps$ and the peak position of $-5.9\,\kmps$.
-The log-normal fit (dash-dot) of  the rotational velocity distribution gives  the standard deviation $27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
-
+\caption{Histogram of the average heliocentric radial velocities (left) and the rotational velocities (right) of 14 UScoOB BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding USco~121, a non-member).
+The gaussian fit (dashed line) of the radial velociity distribution gives a standard deviation of  $1.2\,\kmps$ and the peak position of $-5.9\,\kmps$.
+The log-normal fit (dash-dot) of  the rotational velocity distribution gives  a standard deviation $27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
 \label{fig:vrad_vrot_histrogram}
@@
 
-The rotational velocities of the objects are determined by measuring
-the widths of the cross correlation curves of the target spectra against
-a templates spectra from an object which is known to have a very small
-rotational velocity. The line broadening of the targets are assumed
+The rotational velocities of the objects were determined by measuring
+the widths of the cross correlation functions of the target spectra against
+a template spectrum from an object which is known to have a very small
+rotational velocity. The line broadening of the targets is assumed
 to be dominated by rotational broadening. As in the cases for the
-radial velocity measurements, LHS~49 is chosen for the template.
-Using its known period ($P\approx83\,\mathrm{d}$, \citealt{benedict:1998})
+radial velocity measurements, LHS~49 is chosen as the template.
+Using its rotational period ($P\approx83\,\mathrm{d}$, \citealt{benedict:1998})
 and radius ($R_{*}\approx0.145\,\mathrm{R_{\odot}}$ from the VLTI
@@
 of LHS~49 is estimated as $v\,\sin i=2\pi R_{*}/P\approx0.1\,\kmps$;
-hence, negligibly small.
+negligibly small.
 
@@
 correlating the template spectra against the same template spectra
-with added rotation (convolved with a given $v\,\sin i$), as similarly
+with added rotation (convolved with a given $v\,\sin i$), as
 done by e.g.~\citet{tinney:1998}, \citet{mohanty:2003} and \citet{white:2003}.
-The linear limb-darkening law with a solar-like parameter ($\epsilon=0.6$)
+A linear limb-darkening law with a solar-like parameter ($\epsilon=0.6$)
 was assumed in the formulation of the rotational profile described
@@
 of rotational velocities are computed from two independent spectra
-obtained at different epochs. As similary done for the RV measurements,
+obtained at different epochs. As for the RV measurements,
 the mean and the standard deviation of the mean are used as the final
-rotational velocity and its uncertainty. The final results are placed
+rotational velocity and its uncertainty. The final results are recorded
 in Table~\ref{tab:summary_results}. In general, our measurements
@@
 USco 121, non member). The log-normal fit of this distribution gives
-the peak position at $16.9\,\kmps$ and the standard deviation $\sigma=27.8\,\kmps$.
+the peak position at $16.9\,\kmps$ with a standard deviation $\sigma=27.8\,\kmps$.
 Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
@@
 than that of the Upper Sco objects. The difference maybe due to the
-very small number of samples. A similar fit was applied to the $v\,\sin i$
+very small sample. A similar fit was applied to the $v\,\sin i$
 distribution of 14 T~Tauri stars in Cha~I using the data of \citet{joergens:2001},
-and we found the peak at $17.0\,\kmps$ and the standard deviation
+and we found a peak at $17.0\,\kmps$ with a  standard deviation
 $25.9\,\kmps$ which are very similar to those of the Upper Sco brown
@@
 According to Table~\ref{tab:summary_results}, 9 out of 18 (50 per
-cent of) samples are considered as binary/multiple candidates. The
+cent of) the sample are considered as binary/multiple candidates. The
 fraction slightly decreases to 43 per cent (6 out of 14) if we consider
@@
 in UScoOB and $\rho$~Oph dark cloud core using the high resolution
-UVES echelle spectroscopy at VLT. The amount of the shifts in RVs
-in time is used to identify the candidates for multiplicity.
-
-We found 9 out of 18 objects (50~per~cent) are possible candidates
+UVES echelle spectroscopy at VLT.  We found 9 out of 18 objects (50~per~cent) are possible candidates
 in this analysis. For the objects in UScoOB, we found 6 out of 14
@@
 This work is supported by PPARC rolling grant PP/C501609/1. We thank
-the staff of VLT of the ESO for the observations carried out in the
+the staff of VLT of the ESO for the observations carried out in
 service mode.

### 2006-04-11 BD_radvel/kurosawa.tex
Dates (MDJ -> HJD) changed. Observed dates were 1 day off (I was listing the dates the data was reduced before instead)...=> fixed. (RK).
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@704 25464f21-6099-402c-b30a-640f1d40d38b

@@
 (Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
-were carried out between 2004 April 5 and 2005 (XXX?)  May 15 in  service
+were carried out between 2004 April 5 and 2004 May 17 in  service
 mode. For each object, spectra were obtained at two different
@@
 Date&
-MDJ-2453100&
+HJD-2453100&
 RV&
@@
 GY 5&
-2004-Apr-25&
-20.22051&
+2004-Apr-24&
+20.7198440&
 $-6.14\pm0.84$&
@@
 &
-2004-May-08&
-33.27776&
+2004-May-07&
+33.7721938&
 $-5.96\pm0.60$&
@@
 GY 141&
-2004-May-11&
-36.16016&
+2004-May-10&
+36.6712108&
 $-4.39\pm0.60$&
@@
 &
-2004-May-18&
-43.15707&
+2004-May-17&
+43.6683007&
 $-2.95\pm0.51$&
@@
 GY 310&
-2004-Apr-25&
-20.32700&
+2004-Apr-24&
+20.8373504&
 $-4.83\pm0.74$&
@@
 &
-2004-May-10&
-35.31139&
+2004-May-09&
+35.8224052&
 $-8.43\pm0.51$&
@@
 USco 40&
-2004-Apr-06&
-01.25900&
+2004-Apr-05&
+1.7661754&
 $-7.15\pm0.74$&
@@
 &
-2004-May-08&
-33.25324&
+2004-May-07&
+33.7620554&
 $-6.80\pm0.51$&
@@
 USco 53&
-2004-Apr-05&
-00.39651&
+2004-Apr-04&
+0.9036653&
 $-7.27\pm0.93$&
@@
 &
-2004-May-03&
-28.23079&
+2004-May-02&
+28.7394676&
 $-5.43\pm0.74$&
@@
 USco 55&
-2004-Apr-06&
-01.33509&
+2004-Apr-05&
+1.8422807&
 $-5.39\pm0.50$&
@@
 &
-2004-May-03&
-28.30546&
+2004-May-02&
+28.8141198&
 $-6.38\pm0.53$&
@@
 USco 66&
-2004-Apr-06&
-01.29007&
+2004-Apr-05&
+1.7972634&
 $-5.32\pm0.57$&
@@
 &
-2004-May-03&
-28.28683&
+2004-May-02&
+28.7956003&
 $-6.41\pm0.65$&
@@
 USco 67&
-2004-Apr-06&
-01.21481&
+2004-Apr-05&
+1.7188620&
 $-6.01\pm0.74$&
@@
 &
-2004-May-03&
-28.21759&
+2004-May-02&
+28.7113799&
 $-6.83\pm0.59$&
@@
 USco 75&
-2004-Apr-05&
-00.37453&
+2004-Apr-04&
+0.8840376&
 $-6.75\pm0.67$&
@@
 &
-2004-May-08&
-33.09532&
+2004-May-07&
+33.6065432&
 $-9.88\pm1.94$&
@@
 2004-Apr-06&
-01.30836&
+1.8179138&
 $-6.76\pm2.74$&
@@
 &
-2004-May-03&
-28.26425&
+2004-May-02&
+28.7752928&
 $-10.23\pm1.80$&
@@
 USco 101&
-2004-Apr-05&
-00.30191&
+2004-Apr-04&
+0.8120734&
 $-4.22\pm0.87$&
@@
 &
-2004-May-03&
-28.14804&
+2004-May-02&
+28.6591660&
 $-6.07\pm0.69$&
@@
 USco 104&
-2004-Apr-05&
-00.27545&
+2004-Apr-04&
+0.7850385&
 $-5.83\pm0.50$&
@@
 &
-2004-May-03&
-28.12391&
+2004-May-02&
+28.6349480&
 $-7.48\pm0.50$&
@@
 USco 109&
-2004-Apr-06&
-01.23587&
+2004-Apr-05&
+1.7453989&
 $-4.15\pm0.52$&
@@
 &
-2004-May-08&
-33.11929&
+2004-May-07&
+33.6304878&
 $-4.41\pm0.50$&
@@
 USco 112&
-2004-Apr-05&
-00.34486&
+2004-Apr-04&
+0.8552168&
 $-2.70\pm0.69$&
@@
 &
-2004-May-08&
-33.07139&
+2004-May-07&
+33.5826368&
 $-3.46\pm0.51$&
@@
 USco 121&
-2004-Apr-25&
-20.19466&
+2004-Apr-24&
+20.7059408&
 $-39.47\pm0.51$&
@@
 &
-2004-May-03&
-28.18537&
+2004-May-02&
+28.6969641&
 $-42.43\pm0.50$&
@@
 USco 128&
-2004-May-14&
-39.28595&
+2004-May-13&
+39.7978276&
 $-7.41\pm0.85$&
@@
 &
-2004-May-18&
-43.09885&
+2004-May-17&
+43.6108024&
 $-6.94\pm1.16$&
@@
 USco 130&
-2004-May-10&
-35.26060&
+2004-May-09&
+35.7724090&
 $-4.83\pm0.54$&
@@
 &
-2004-May-14&
-39.34201&
+2004-May-13&
+39.8538830&
 $-4.95\pm0.74$&
@@
 USco 132&
-2004-May-12&
-37.28394&
+2004-May-13&
+39.8268683&
 $-7.18\pm0.58$&
@@
 &
-2004-Jun-18&
-43.12719&
+2004-May-17&
+43.6391138&
 $-7.37\pm1.02$&
@@
 
-\caption{Relative radial velocities (RVs) of objects measured in two different epochs.
-The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD; XXX do you really mean MJD rather than heliocentric JD????).
-The objects are considered to have a non-constant  RV when the error bars of two data points do not overlap each other.
-The non-constant RV objects are considered as binary/multiple candidates.}
+\caption{Relative radial velocities (RVs) of objects measured in two
+different epochs. The vertical axes indicate the amount of deviation
+($\Delta \mathrm{RV}$) from the `average' radial velocitiy
+($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and
+the horizontal axes indicate the time of the observation in
+heliocentric Julian date (HJD). The objects are considered to have a
+non-constant RV when the error bars of two data points do not overlap
+each other. The non-constant RV objects are considered as
+binary/multiple candidates.}
 
@@
 by measuring the location of the peak in the cross-correlation function
-which is fitted by the combination of two gaussian functions sharing
-their centres and a constant term (XXXX What does this mean?). LHS~49 (Proxima Cen, M5.5) was
+which is fitted by a function which consists of two gaussian functions
+(with a common centre) plus a constant term . LHS~49 (Proxima Cen, M5.5) was
 chosen as the template for this purpose. The radial velocity of the
@@
 two consecutive measurements of RVs (from same nights) are used to
-find the RV of the night, and their uncertainties are obtained from
+find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
 the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
 the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
-(XXX What do you need to include the uncertainty in the template
-star measurement when we are looking for relative changes in the
-bd RVs?) The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
+Note that for finding a shift in the radial velocities from two
+different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
+only requires relative (with respect to a template) RV values.
+The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
 two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
@@
 
-This work is supported by PPARC rolling grant PP/C501609/1. We thank
-the staff of VLT of the ESO for the observations carried out in
-service mode.
+We thank the staff of VLT of the ESO for the observations carried out in
+service mode.  This work is supported by PPARC rolling grant PP/C501609/1.
 

### 2006-04-18 BD_radvel/work/chi_square.f90
New figures added
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@706 25464f21-6099-402c-b30a-640f1d40d38b

@@ -1,0 +1,227 @@
+module chi_square
+
+  ! Collection of functions for computing chi_square and chi-quare 
+  ! probability
+
+  
+  public :: chi_sq_dist, chi_sq_prob, chi_sq
+  private :: gamma, simpson
+
+contains
+  
+
+  !
+  !
+  ! 
+  double precision function chi_sq(y, sigma, yfit, n)
+    implicit none
+    integer         , intent(in) :: n          ! number of data points
+    double precision, intent(in) :: y(n)       ! data points
+    double precision, intent(in) :: sigma(n)
+    ! fitted values model evaluated at the data x values.
+    double precision, intent(in) :: yfit(n) 
+    !
+    double precision :: tmp
+    integer :: i 
+    
+    chi_sq = 0.0d0
+    do i = 1, n
+       tmp = (y(i)-yfit(i))/sigma(i)
+       chi_sq = chi_sq + tmp*tmp
+    end do
+    
+  end function chi_sq
+  
+  !
+  ! The probability distribution function for chi-sq
+  ! with "nfree" degrees of freedom.
+  function chi_sq_dist(chi_sq,nfree) RESULT(out)
+    implicit none
+    double precision :: out 
+    integer, intent(in) ::  nfree
+    double precision, intent(in) ::  chi_sq
+    !
+    double precision :: nu
+    !
+    nu = nfree
+    out  = ( chi_sq**((nu-2.0d0)/2.0d0) )  &
+         /                                        &
+         ( (2.0d0**(nu-2.0d0))*gamma(nu/2.0d0)*dexp(chi_sq/2.0d0) )
+    !
+    return
+  end function chi_sq_dist
+  
+  
+  
+  
+  !====================================================================
+  !  This function calclulats the chi-squre probability.
+  !  (c.f. "Datareduction and Error Analysis for the Physical
+  !  Sciences" by P. Bevington, page 193.
+  !===================================================================
+  ! Created: 18-aug-1998 : Kurosawa  
+  !====================================================================
+  double precision function chi_sq_prob(chi_sq,nfree)
+    implicit none
+    !
+    double precision, intent(in) :: chi_sq
+    integer, intent(in) :: nfree 
+    !
+    double precision ::  z, term, sum,  f1
+    integer :: imax, i
[…]

### 2006-04-18 BD_radvel/work/rv_chisq.f90

@@ -1,0 +1,201 @@
+program rv_chisq
+
+  use chi_square
+
+  implicit none
+  ! Given a set of RV measurements (with their uncertainties)
+  ! from two epochs, this program computes the chisq prob of 
+  ! the RV being constant. 
+
+  integer, parameter :: nobj=18  ! number of objects in the list
+  integer, parameter :: ntime=2  ! number of observations for each object
+  real*8 :: RV(ntime, nobj)      ! radial velocities in km/s
+  real*8 :: err_RV(ntime, nobj)  ! uncertainties in RV in km/s
+  character(LEN=10) :: object_id(nobj)   ! name of the objects in the list.
+  character(LEN=10) :: dum_a     ! 
+  !
+  ! File unti numbers
+  integer, parameter :: LUIN =23
+  integer, parameter :: LUOUT =24
+  integer, parameter :: LUHIST =25
+  integer, parameter :: LUEXP =26
+  integer, parameter :: LUdiv =27
+  !
+  integer :: i, j
+  ! used for chisq
+  real*8  :: RV_data(ntime)  ! RV from data
+  real*8  :: RV_fit(ntime)   ! RV of fitting function
+  real*8  :: error(ntime)    ! uncertainties in RV 
+  real*8  :: RV_ave(nobj)  ! average RV from two epochs.
+  integer :: nu ! number of degree of freedom
+  real*8  :: p(nobj)   ! chi_squre probability
+  real*8  :: xs(nobj)  ! chi_squre
+  ! for histogram
+   integer, parameter :: nbin = 7
+!  integer, parameter :: nbin = 14
+  real*8 :: N(nbin)  ! number of object
+  real*8 :: binsize 
+  real*8 :: mlp, norm
+
+  ! expected distribution chi-sq distibution
+  integer,parameter :: nxs = 100
+  real*8 :: p_exp(nxs)
+  real*8 :: xs_exp(nxs)
+  real*8 :: mlp_exp(nxs)
+  real*8 :: freq(nxs)
+  real*8 :: dlog10_xs, area, xs_min, xs_max, d_xs
+  real*8 :: err_extra
+
+  ! reading the data file.
+  open(unit=LUIN, file="rv.dat", status="old")
[…]

### 2006-05-01 BD_radvel/kurosawa.tex
New figures added
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@706 25464f21-6099-402c-b30a-640f1d40d38b
Major channge made. Close to a final version. RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@710 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-We present the results of a radial velocity (RV) survey of 15 brown
+We present the results of a radial velocity (RV) survey of 14 brown
 dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
-association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi
-dark cloud core. We obtained high-resolution echelle spectra at VLT
-using Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
-epochs for each object, and measured the shifts in their RVs to identify
-candidates for binary/multiple systems in the sample.
-We found 9 out of 18 (50 per cent) in our sample show a significant
-RV change in 4--33~d time scale, and are considered as binary/multiple
-`candidates.' The fraction slightly decreases to 43 per cent (6 out
-of 14) if we consider the objects only in the UScoOB. These fractions
-do not necessary represent that of a real binary population among
-young BDs and VLM stars since their true multiplicities are still
-to be confirmed by follow-up spectroscopic monitoring. We found no
-double-lined spectroscopic binaries in our sample, based on the shape of cross-corelation
-curves. Our RV-shift tests successfully detected the recently confirmed 3 binaries in UScoOB
-via high-resolution imaging technique. We found the RV dispersion
-of the objects in UScoOB is very similar to that of the BDs and VLM
-stars in Chamaeleon~I (Cha~I) previously studied by others. We also
-measured the rotational velocities ($v\,\sin i$) of the sample,
-and found good agreements with earlier studies. The distribution of
-$v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which
-is similar to that of the Cha~I population.
+association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
+cloud core. We obtained high-resolution echelle spectra at VLT using
+Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
+epochs for each object, and measured the shifts in their RVs to
+identify candidates for binary/multiple systems in the sample. The
+average time separation of the RV measurements is 21.6~d, and our
+survey is sensitive to the binaries with separation $<0.12$~au.  We
+found 2 out of 17 objects (or $12^{+13}_{-10}$~per~cent by fraction)
+show a significant RV change in 4--33~d time scale, and are 
+considered as binary/multiple `candidates.'  We found no double-lined
+spectroscopic binaries in our sample, based on the shape of
+cross-corelation curves. The RV dispersion of the objects in UScoOB is
+found to be very similar to that of the BDs and VLM stars in
+Chamaeleon~I (Cha~I) previously studied by others. We also found the
+distribution of the rotational velocities ($v\,\sin i$) of the UScoOB
+objects is good agreement with that of Cha~I from earlier studies.
 
@@
 the adaptive optics at Gemini North. They also found an upper limit
-to the semi-major axis distribution of $\sim20\,\mathrm{au}$. An
-\emph{HST} study of more than 80 field last M and L dwarfs \citep{gizis:2003}
+to the semimajor axis distribution of $\sim20\,\mathrm{au}$. An
+\emph{HST} study of more than 80 field late M and L dwarfs \citep{gizis:2003}
 indicated $f=15$~per~cent with separations in the range of 1.6--16~au.
@@
 $f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
-by using a similar imaging technique..
+by using a similar imaging technique. More recently,
+\citet{basri:2006}, combined with the results of earlier works, found
+the upper limit of the overall binary fraction for VLM stars of
+$26\pm10$~per~cent.
 
@@
 and the data reduction. The results of radial velocity and rotational
-velocity ($v\,\sin i$) measurements are presented in Sections~\ref{sub:Radial-velocities}
-and \ref{sub:Radial-velocities} respectively. We discuss the binary/multiplicity
-fraction indicated by our RV survey in Section~\ref{sec:Binary-frequency}, and give
+velocity ($v\,\sin i$) measurements are presented in
+Section~\ref{sec:Results}. We discuss the binary/multiplicity 
+fraction indicated by our RV survey, and compare our results with
+earlier works in Section~\ref{sec:Binary-fraction}, and give
 our conclusions in Section~\ref{sec:Conclusions}.
@@
 
-Our sample consists of 18 young, very low-mass objects: 15 objects in the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$, \citealt{dezeeuw:1999}) from the list
-of \citet{ardila:2000} and 3 objects in the $\rho$~Ophiuchi cloud
-core ($\mathrm{d\approx150\, pc}$, \citealt{dezeeuw:1997}) from
- \citet{luhman:1999}. The spectral type of the objects range between
-M5 and M8.5, and the age $<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999};
-\citealt{ardila:2000}; \citealt{muzerolle:2003}; \citealt{kraus:2005}).
-The sample is not complete, and the selection was solely based on 
-brightness and the observability. The basic properties of the
-targets based on the literature is summarised in Table~\ref{tab:literatures}.
+Our sample consists of 18 young, very low-mass objects: 15 objects in
+the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$,
+\citealt{dezeeuw:1999}) from the list of \citet{ardila:2000} and 3
+objects in the $\rho$~Ophiuchi cloud core ($\mathrm{d\approx150\,
+pc}$, \citealt{dezeeuw:1997}) from \citet{luhman:1999}. The spectral
+type of the objects range between M5 and M8.5, and the age
+$<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999}; \citealt{ardila:2000};
+\citealt{muzerolle:2003}; \citealt{kraus:2005}).  The sample is not
+complete, and the selection was solely based on brightness and the
+observability. The basic properties of the targets based on the
+literature is summarised in Table~\ref{tab:literatures}.
 
 We obtained high-resolution spectra with the Kueyen telescope of VLT
-(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
-were carried out between 2004 April 5 and 2004 May 17 in  service
-mode. For each object, spectra were obtained at two different
-epochs separated by several (between 4 and 33~d). For each object at a given 
-night, two separate spectra are obtained consecutively. This allows us to derive more
-reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
-The data were obtained using the red arm of UVES spectrograph with
-two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
-coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
-were used. The slit width and length of 1'' and 12'' were used respectively with a typical seeing
-of 0.8''.
+(Cerro Parnal, Chile) using the UVES echelle spectrograph. The
+observations were carried out between 2004 April 5 and 2004 May 17 in
+service mode. For each object, spectra were obtained at two different
+epochs separated by several (between 4 and 33~d). For each object at a
+given night, two separate spectra are obtained consecutively. This
+allows us to derive more reliable uncertainty estimates in the RV
+values of our targets (c.f.~\citealt{joergens:2006}).  The data were
+obtained using the red arm of UVES spectrograph with two mosaic CCDs
+(EEV + MIT/LL with 2k$\times$4k pixels). The wavelength coverage of
+6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$ were
+used. The slit width and length of 1'' and 12'' were used respectively
+with a typical seeing of 0.8''.
 
@@
 
+\caption{Summary of known properties of the targets from literature:
+a.~\citet{luhman:1999} (original list for $\rho$~Oph),
+b.~\citet{ardila:2000} (original list for UScoOB),
+c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003},
+e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}. }
+
 \label{tab:literatures}
-
-\caption{Summary of known properties of the targets from literature: a.~\citet{luhman:1999} (original list for $\rho$~Oph), b.~\citet{ardila:2000} (original list for UScoOB),  c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003}, e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}.
-}
 
@@
 
-\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$) from two-epoch and the average rotational velocities ($v\sin i$).
-The uncetainties of relative radial velocties ($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049 and the average radial velocties ($\overline{\mathrm{RV}}$) are also given.
-The last column indicates whether a target is a candidate for multiplicity i.e.~the measured radial velocity changes from two different epoch is larger than $1\,\sigma_{\mathrm{RRV}}$ of each others (c.f.~Fig.~\ref{fig:radvel01}).}
+\caption{Summary of the observations, the heliocentric radial
+velocities ($\mathrm{RV}$) from two-epoch and the average rotational
+velocities ($v\sin i$). The uncertainties of relative radial velocities
+($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049
+and the average radial velocities ($\overline{\mathrm{RV}}$) are also
+given. }
+
+\label{tab:summary_results}
 
@@
 
-\begin{tabular}{lcrrrrrc}
+\begin{tabular}{lcrrrrr}
 \hline 
@@
 $\overline{\mathrm{RV}}$&
-$v\sin i$&
-candidate?\tabularnewline
+$v\sin i$\tabularnewline
 &
@@
 $\left[\mathrm{km\, s^{-1}}\right]$&
-$\left[\mathrm{km\, s^{-1}}\right]$&
-\tabularnewline
+$\left[\mathrm{km\, s^{-1}}\right]$\tabularnewline
 \hline 
@@
 &
-&
 \tabularnewline
@@
 $-6.05\pm1.03$&
-$16.5\pm0.6$&
-no\tabularnewline
+$16.5\pm0.6$\tabularnewline
 GY 141&
@@
 $-3.67\pm0.79$&
-$4.4\pm1.4$&
-yes\tabularnewline
+$4.4\pm1.4$\tabularnewline
 GY 310&
@@
 $-6.63\pm0.90$&
-$11.1\pm6.0$&
-yes\tabularnewline
+$11.1\pm6.0$\tabularnewline
 USco 40&
@@
 $-6.98\pm0.90$&
-$34.2\pm0.5$&
-no\tabularnewline
+$34.2\pm0.5$\tabularnewline
 USco 53&
@@
 $-6.35\pm1.19$&
-$40.0\pm0.6$&
-no\tabularnewline
+$40.0\pm0.6$\tabularnewline
 USco 55&
@@
 $-6.38\pm0.73$&
-$22.9\pm0.8$&
-yes\tabularnewline
+$22.9\pm0.8$\tabularnewline
 USco 66&
@@
 $-5.87\pm0.86$&
-$25.9\pm1.2$&
-no\tabularnewline
+$25.9\pm1.2$\tabularnewline
 USco 67&
@@
 $-6.42\pm0.90$&
-$18.4\pm0.4$&
-no\tabularnewline
+$18.4\pm0.4$\tabularnewline
 USco 75&
@@
 $-8.32\pm2.05$&
-$55.6\pm3.0$&
-yes\tabularnewline
+$55.6\pm3.0$\tabularnewline
 USco 100&
@@
 $-8.47\pm3.28$&
-$43.7\pm3.2$&
-no\tabularnewline
+$43.7\pm3.2$\tabularnewline
 USco 101&
@@
 $-5.15\pm1.11$&
-$19.1\pm0.3$&
-yes\tabularnewline
+$19.1\pm0.3$\tabularnewline
 USco 104&
@@
 $-6.66\pm0.06$&
-$16.7\pm0.4$&
-yes\tabularnewline
+$16.7\pm0.4$\tabularnewline
 USco 109&
@@
 $-5.12\pm0.72$&
-$8.6\pm1.2$&
-yes\tabularnewline
+$8.6\pm1.2$\tabularnewline
 USco 112&
@@
 $-3.08\pm0.86$&
-$5.8\pm1.2$&
-yes\tabularnewline
+$5.8\pm1.2$\tabularnewline
 USco 121&
@@
 $-40.95\pm0.71$&
-$17.6\pm1.3$&
-yes\tabularnewline
+$17.6\pm1.3$\tabularnewline
 USco 128&
@@
 $-7.18\pm1.44$&
-$3.6\pm1.1$&
-no\tabularnewline
+$3.6\pm1.1$\tabularnewline
 USco 130&
@@
 $-4.89\pm0.92$&
-$15.2\pm1.1$&
-no\tabularnewline
+$15.2\pm1.1$\tabularnewline
 USco 132&
@@
 $-7.28\pm1.17$&
-$9.1\pm0.7$&
-no\tabularnewline
+$9.1\pm0.7$\tabularnewline
 \hline
@@
 \end{center}
-
-\label{tab:summary_results}
 
@@
 different epochs. The vertical axes indicate the amount of deviation
-($\Delta \mathrm{RV}$) from the `average' radial velocitiy
+($\Delta \mathrm{RV}$) from the `average' radial velocity
 ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and
@@
 which is fitted by a function which consists of two gaussian functions
-(with a common centre) plus a constant term . LHS~49 (Proxima Cen, M5.5) was
+(with a common centre) plus a constant term. LHS~49 (Proxima Cen, M5.5) was
 chosen as the template for this purpose. The radial velocity of the
@@
 values of the objects in UScoOB are consistent with the earlier measurements
-of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
-for the values for USco~66 and USco~75. This is unsurprising
-since the former is a known binary \citep{kraus:2005} and the latter
-is a non-constant RV object (a candidate for a multiple) found in
-the RV-shift test which will be discussed next.
+of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.
 
 For each object and for each RV measurement, the deviations ($\Delta\mathrm{RV}$)
-from the average RV are computed and summaries in Fig.~\ref{fig:radvel01}
+from the average RV are computed and summarized in Fig.~\ref{fig:radvel01}
 along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
@@
 absolute or the heliocentric radial velocities, but only the relative
-velocities (with respect to a template). We identify an object as a candidate
-when the 1$\sigma_{\mathrm{RRV}}$ error bar from each RV measurement
-overlaps one another. Using this simple criteria, the candidate were
-selected and indicated in the same table (Table~\ref{tab:summary_results}).
-We found 9 out of 18 (50 per cent of) our sample are considered as
-candidates. The recent observation of \citet{kraus:2005} (which was
-not known to authors at the time of our observation: April--May, 2004)
-confirms that USco~65 and USco~66 are multiple systems, and USco~109
-is most likely a multiple system. In our RV-shift tests, we found
-all the multiples confirmed by \citet{kraus:2005} in our multiple
-candidates. Further they found USco~67, 128, 130, 132 as non-multiple,
-and similarly we found them as 'non-candidates' for multiplicity.
-The discrepancy between their results and ours are only in USco~75
-and USco~112. While our results suggests that these are candidates
-for multiple systems, \citet{kraus:2005} did not find them as multiple
-systems. This difference may be caused by the difference in sensitivity
-(on a binary separation) of the two different methods. Another possible
-caused of the difference is that the uncertainties in RVs may be underestimated, since
-surface activity of the objects may also contribute noise in
-the RV measuements; however, the levels of th noise is expeted be
-small for BD and VLM stars (c.f.~\citealt{joergens:2006}).
-
-Finally, the histogram of the RVs using only the objects in UScoOB
-is given in Figure~\ref{fig:vrad_vrot_histrogram}. The total number
+velocities (with respect to a template).
+
+To identify an object with a RV variation with a statistical
+significance from our sample, we apply the method described by
+\citet{maxted:2005}, which we briefly summarize next, to our data.
+There are three steps in this method: 
+(1)~compute the $\chi^{2}$ by fitting the two-epoch RV data for each 
+object with a constant function (a zero-th order polynomial),
+(2)~compute the corresponding $\chi^{2}$ probability ($p$),
+(3)~designate the object as a non-constant RV object or a binary
+candidate if $p<10^{-3}$ (1~per~cent).  When computing $\chi^{2}$, we
+use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$). 
+The number of degree of freedom in the fitting procedure is obviously
+1.  A similar method was also used in a recent RV survey of VLM stars
+by \citet{basri:2006}.
+
+We have computed $p$ for all the objects, and have plotted the results 
+as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
+(excluding the non-member USco~121). 
+The figure clearly shows two distinctive populations: one on the left
+(with small $-\log{p}$ values) occupied by the RV constant objects,
+and one on in the right-most bin (with the largest $-\log{p}$)
+occupied by the RV variable objects which have $p<10^{-3}$.  The
+expected distribution of $p$ computed consistently with our
+uncertainty measurements is also shown in the same figure. The RV
+constant population on the left side reasonably matches the expected
+curve. This assures that our uncertainties in RV values are
+reasonable, and an additional systematic error may not be necessary in
+this analysis. According
+to the figure, there are four objects which shows significant RV
+variations out of 17 samples. They are GY~141, GY~310, USco~55, and
+USco~104, and considered as our preliminary binary/multiple
+candidates.  We will discuss the effect of the systematics error in detail, and
+list our final binary/multiple candidate later in
+Section~\ref{sec:Binary-fraction}.
+
+%==========================================
+
+\begin{figure}
+
+\begin{center}
+\includegraphics[%
+  clip,
+  scale=0.63]{figures/chisq_hist.eps}
+\end{center}
+
+\caption{The histogram of the $\chi^2$ probability ($p$) for fitting the
+  observed (relative) RV values with a constant (a horizontal
+  line). The constant used in the fit is determined from the weighted mean of
+  the two RV measurements for each object.  The objects with
+  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
+  which appear in the right-most $\log{p}$ bin in the histogram. There
+  are four objects which satisfies this condition. The
+  expected distribution (dashed) for constant objects based on the RV
+  uncertainties in the observations (Table~\ref{tab:summary_results})
+  and based on the $\chi^{2}$ probability function is also shown for a
+  comparison.  The match between the expected distribution and the
+  histogram is reasonable, indicating that our uncertainty estimates
+  in RV values are also reasonable.  }
+
+\label{fig:chisq-test}
+
+\end{figure}
+
+%==========================================
+
+Finally, the histogram of $\overline{\mathrm{RV}}$ for the objects in UScoOB
+is given in Fig.~\ref{fig:vrad_histrogram}. The total number
 of the objects is 14. Note that USco~121 is excluded from the graph
@@
 According to the hydrodynamical simulations of a low-mass star-forming
-cluster of \cite{bate:2003} which yields a stellar density of $1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$,
-the rms dispersion (1-D) of the stars and the BDs is $1.2\,\kmps$.
-Similarly for the model with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\, pc^{-3}}$),
-the rms dispersion is 2.5~$\kmps$ (\citealt{bate:2005}). The standard
-deviation of $\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our
-analysis is more comparable the lower stellar density model.
-
-%==========================================
-
-\begin{figure*}
+cluster of \cite{bate:2003} which yields a stellar density of
+$1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
+of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
+with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\,
+pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
+(\citealt{bate:2005}). The standard deviation of
+$\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our analysis is more
+comparable the lower stellar density model.
+
+%==========================================
+
+\begin{figure}
 
@@
 
-\begin{tabular}{cc}
 \includegraphics[%
   clip,
-  scale=0.45]{figures/radvel_hist.eps}&
-\includegraphics[%
-  clip,
-  scale=0.45]{figures/vrot_hist.eps}\tabularnewline
-\end{tabular}
+  scale=0.63]{figures/radvel_hist.eps}
 
@@
 
-\caption{Histogram of the average heliocentric radial velocities (left) and the rotational velocities (right) of 14 UScoOB BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding USco~121, a non-member).
-The gaussian fit (dashed line) of the radial velociity distribution gives a standard deviation of  $1.2\,\kmps$ and the peak position of $-5.9\,\kmps$.
-The log-normal fit (dash-dot) of  the rotational velocity distribution gives  a standard deviation $27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
-\label{fig:vrad_vrot_histrogram}
-
-\end{figure*}
+\caption{Histogram of the average heliocentric radial velocities of 14 UScoOB BD and VLM
+objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
+a non-member). The gaussian fit (dashed line) of the radial velociity
+distribution gives a standard deviation of $1.2\,\kmps$ and the peak
+position of $-5.9\,\kmps$. }
+\label{fig:vrad_histrogram}
+
+\end{figure}
 
@@
 The range of $v\,\sin i$ found among our objects is $3.6$--$55.6\,\kmps$,
-and a similar range is also found by \citet{mohanty:2005}. The left
-panel of Figure~\ref{fig:vrad_vrot_histrogram} shows the histogram
+and a similar range is also found by \citet{mohanty:2005}. 
+Fig.~\ref{fig:vrot_histrogram} shows the histogram
 of $v\,\sin i$ distribution for the UScoOB objects (14 objects excluding
@@
 
-\section{Binary frequency}
-
-\label{sec:Binary-frequency}
-
-According to Table~\ref{tab:summary_results}, 9 out of 18 (50 per
-cent of) the sample are considered as binary/multiple candidates. The
-fraction slightly decreases to 43 per cent (6 out of 14) if we consider
-the objects only in the UScoOB. These fractions are significantly
-larger than the binary fraction (25~per~cent, 3 out of 12) found
-by the recent high-resolution imaging survey of brown dwarfs and very
-low-mass objects (M5.5--M7.5 ) in the UScoOB \citep{kraus:2005}.
-The imaging surveys are sensitive to wider binaries (separation$\gtrsim4\,\mathrm{au}$)
-while our technique is more sensitive to narrower ($\lesssim1\,\mathrm{au}$)
-or shorter period ($\sim10\,\mathrm{d}$) binaries. However, our RV-shift
-test also detected all the binaries found in the imaging survey of
-\citet{kraus:2005}, demonstrating that the method is also effective
-in the systems with a separation 5--18~au. In Section~\ref{sub:Radial-velocities},
-we have found all the binaries confirmed by \citet{kraus:2005} also
-as our binary/multiple candidates. In addition to those samples commonly
-found, we have two more candidates (USco~75 and USco~112) which
-are in the sample of \citet{kraus:2005}, but not detected as binaries
-by them. If we assume these objects are real binary/multiple systems
-but not detected by the imaging survey because of possibly very small
-separations, their multiplicity fraction would increase to 5 out of
-9 (56~per~cent) which is more consistent with the fraction suggested
-by our RV survey.
-
-Another possible reason for the different binary fraction suggested
-by our data is that the uncertainties in the RV values may be underestimated.
-Since the our suggested binary fraction is merely that for the binary
-`candidates', the follow-up RV monitoring of the candidates must be
-done to confirm the true multiplicity, and to determined firmer constraint
-on the binary/multiple faction in the UScoOB. This is planned for
-a near future. The binary fraction of slightly more massive pre-main-sequence
-stars was studied by \citet{kohler:2000} using the K-band speckle
-interferometry of X-ray selected samples. For the UScoOB members with
-spectral type M0--M5 (0.7--0.13~$\mathrm{M_{\odot}}$), they found
-the binary fraction of $52\left(\pm10\right)$~per~cent (26 out
-of 50) with the separation 21--1000~au. On the other hand, \citet{kohler:2000}
-found no wide ($>20\,\mathrm{au}$) binary in their survey, and suggested
-that there may be a discontinuity in separation distribution around
-$M_{*}\sim0.1\,\mathrm{M_{\odot}}$.
-
-A similar imaging survey of the brown dwarf candidates in Cha~I cloud
-by \citet{neuhaeuser:2002} and \citet{neuhaeuser:2003} also found
-the multiplicity rate $\lesssim10\,\mathrm{per\, cent}$ using 12
-objects (Cha~H$\alpha$~1--12 with M6--M8). Using a subset of the
-same sample and the same radial velocity technique used in this paper,
-\citet{joergens:2006} found only 11~per~cent (1 out of 9) of the
-sample showed non-constant RVs in her multi-epoch data, indicating
-a much smaller multiplicity fraction. It is unclear at this moment
-whether the difference is caused by the physical nature of the two
-different star forming regions.
+%==========================================
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.63]{figures/vrot_hist.eps}
+
+\end{center}
+
+\caption{Histogram of the rotational velocities (right) of 14 UScoOB BD and VLM
+objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
+a non-member).  The log-normal fit (dash-dot) of the
+rotational velocity distribution gives a standard deviation
+$27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
+\label{fig:vrot_histrogram}
+
+\end{figure}
+%==========================================
+
+\section{Binary fraction}
+\label{sec:Binary-fraction}
+
+In Section~\ref{sub:Radial-velocities}, we found 4 out of 17
+(excluding USco~121; non-member) objects show a statistically
+significant RV variation, indicating that they are binary/multiple
+candidates. In order to estimate the uncertainty in the
+binary/multiple fraction from this relatively small sample, we will
+follow the method used by \citet{basri:2006} who considered the binomial
+distribution, $P_{B}\left ( x, n, p \right )$ of $x$ positive event
+out of $n$ trials with the probability $p$ for a positive event in each
+trial. In our case, $n=17$ (the number sample)  and $p=4/17=0.24$
+(the fraction of binary/multiple).  The uncertainties was estimated by
+plotting $P_{B}\left ( x, 17, 0.24 \right )$, and finding the values
+of $x$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
+analysis, we find the final binary/multiple fraction along with the
+uncertainties of our sample to be $f=24^{+16}_{-14}$~per~cent.
+
+Next, we investigate the range of semimajor axes of binaries
+(equivalently the range of binary periods) to which our RV survey is
+sensitive. For this purpose, we will consider the detection
+probability for binaries or the RV variables, given the time
+separations of two-epoch observations and the ranges of estimated
+primary masses (c.f.~Tables~\ref{tab:literatures} and
+\ref{tab:summary_results}).  The probability will be calculated based
+on the simulated RV observations of binaries whose orbit are randomly
+selected from a model. A similar method was used by
+\citet{maxted:2005} and \citet{basri:2006}.  The most important
+factors in determining the detection probability are the size of
+uncertainties in RV measurements (which we use the average
+$\sigma_{\mathrm{RRV}}$ from our observation), and the time
+separations of observations.  The smaller the errors in RV
+measurements, the larger the probability for a given binary orbit and
+a time separation of orbit. The larger the time separation of
+observations, the larger the upper limit of the semimajor axis to
+which an observation is sensitive.  The average time separation of the
+two-epoch RV observations of our targets is $21.6$~d.
+In the following, we will briefly discuss our model assumptions and
+parameters which are essentially the same as those of
+\citet{maxted:2005} but with some simplifications.
+
+There are six basic parameters our Monte Carlo simulation: 
+primary mass ($M_{1}$), mass ratio ($q$), eccentricity
+($e$), orbital phase ($\phi$), orbital inclination ($i$),
+longitude of periastron ($\lambda$). The primary mass $M_{1}$ is
+assigned from the adopted mass of 
+the targets in Table~\ref{tab:literatures}, with a uniform random
+deviation of $\pm0.002\,M_{\sun}$. The mass ratio is assumed to be
+uniformly distributed between $q=0$ and $0.2$. The eccentricity $e$ is
+assumed to be zero (circular orbits).  Both \citet{maxted:2005}
+and \citet{basri:2006} found the detection probability is insensitive
+to the assumed distribution of $q$ and $e$. The orbital phase is
+randomly chosen between 0 and 1.  The inclination $i$ is randomly
+chosen from the cumulative distribution of $\cos{i}$. The longitude of
+periastron $\lambda$ is not necessary since we assumed $e=0$.
+
+In order to compute the detection probability as a function of
+semimajor axis $a$, we take the following procedure: (1)~for each
+object in our targets, we randomly select $10^5$ binaries using the
+assumption stated above for a given value of $a$, and compute the RV
+of the primary ($V_{1}$), (2)~evolve the orbit by the time separation
+of the RV measuremets use in the observations for this object, and
+take another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
+$V_{2}$ and the average uncertainty in RV ($\sigma_{\mathrm{RRV}}$)
+from the observations, we compute the $\chi^{2}$ probability $p$,  and
+flag the trial as a detection if $p<10^{-3}$ as done for the real
+data, (4)~find the fraction of detections out of all random trials,
+(5) repeat 1--4 for a range of $a$ between $10^{-3}$~and 10~au, and
+(6) repeat 5 for the all targets, and find the detection probability
+averaged over all targets as a function of $a$.
+
+The result of the simulation is shown in
+Fig.~\ref{fig:detect_prob}. The detection probability curve shown here
+is very similar that of \citet{basri:2006} for a constant time
+separation (20~d) case (see their Fig.~4). The probability remains
+fairly constant up to  $a \approx 0.1\,\mathrm{au}$, and it rapidly
+decreases beyond $a\approx 0.3\,\mathrm{au}$.  This turning point will
+increase if we used larger time separations in our observation. 
+From this figure, we find that the 80~per~cent detection probability
+up to for binaries with $a<0.12\,\mathrm{au}$, given our time
+separations and the average uncertainty ($~0.5\,\kmps$) in the RV
+measurements.
+
+%==========================================
+\begin{figure}
+
+\begin{center}
+\includegraphics[%
+  clip,
+  scale=0.63]{figures/detect_prob.eps}
+\end{center}
+
+\caption{The binary detection probability (solid) as a function of the semimajor
+  axis ($a$) based on Monte~Carlo simulations of RV measurements is
+  shown.  For each object in our target list, the simulation was performed
+  using the time separation ($\Delta t$) of the two-epoch observation
+  used in the observation (c.f.~Table~\ref{tab:summary_results}) and
+  the estimated primary mass  (c.f.~Table~\ref{tab:literatures}).  The
+  final detection probability is obtained by averaging
+  over the simulated observations of all the objects.  The average
+  time separation in the two-epoch observations  is $\sim
+  21.6\,\mathrm{d}$, and the average uncertainty in RV is
+  $~0.5\,\kmps$. The probability remains fairly
+  constant up to $a \approx 0.1\,\mathrm{au}$, and it rapidly decreases
+  beyond $a\approx 0.3\,\mathrm{au}$.  The 80~per~cent detection
+  probability is achieved for binaries with $a<0.12\,\mathrm{au}$. 
+  The binary separation distribution (dash) similar to that of
+  \citet{maxted:2005} and \citet{basri:2006} are shown also for a
+  comparison. The distribution is a gaussinan in logarithmic
+  space, centred at $\log{a}=10$, and truncated at $a=15$~au. See text
+  for a detail.}
+
+\label{fig:detect_prob}
+
+\end{figure}
+
+%==========================================
+
+The expected binary fraction for our survey can be obtained
+by integrating the product of the detection probability found above
+with an assumed binary separation distribution function over a range
+of $a$. Here, we simply adopt one of the separation distribution
+function used by \citet{maxted:2005}. The binary separation ($a$)
+distribution is assumed to be  gaussian in  log($a$) space with its
+centre $\log{a_{o}}=0.6$ and width $\sigma_{\log{a}}=1.0$, and
+truncated at $\log{a}=1.176$ where $a$ is in au. This form of the
+distribution function is motivated by the distribution of solar-type
+binaries found in \citet{duquennoy:1991}, and the truncation is
+suggested from the lack of wide binaries for $a>15$~au 
+(e.g.~\citealt{burgasser:2003}). The distribution is normalized such
+that the total binary fraction of 26~per~cent as
+suggested by \citet{basri:2006}.  The resulting separation
+distribution function is shown also in Fig.~\ref{fig:detect_prob}. 
+Using this and the detection probability in the same figure, we find
+the expected binary fraction to be $f_{\mathrm{exp}}=3.2$~per~cent
+(for $a<0.12$~au), which is
+much smaller than our observed binary fraction of
+$f_{\mathrm{obs}}=24^{+16}_{-14}$. The two values are not consistent
+with each other. There are two possible reasons for the discrepancy:
+(1)~the assumed binary separation distribution mentioned above is
+unrealistic, and (2)~the uncertainties in our RV measurements are
+underestimated.  The first reason is less likely since both
+\citet{maxted:2005} and \citet{basri:2006} found this form of the $a$
+distribution function is consistent with the observed binary
+fractions estimated from many earlier surveys.  We will investigate
+the possibility for the second reason in the following.
+
+Apparently, the underestimated uncertainties could have been caused by
+neglecting a systematic error. In Section~\ref{sub:Radial-velocities}
+(see Fig.~\ref{fig:chisq-test}), we found the histogram of the
+$\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
+is reasonably matches with the expected distribution.  This lead us to
+conclude that the uncertainty estimates in RV values were
+reasonable. Here, we will inspect the effect of the systematic error
+on the observed binary fraction more closely. There are two possible
+source of errors: (1)~the RV shifts caused by surface/atmospheric
+activity, and (2)~the RV shifts due to the limit of the stability of
+autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
+negligibly small for a young VLM objects with $M_{*}<0.12\,M_{\sun}$.
+The size of RV errors caused by (2) is expected to be $<1\,\kmps$
+\citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
+additional systematic error was not needed to be added to the RV
+uncertainties of \citet{joergens:2006} who used the same instruments
+as ours, and used the same method of estimating the
+uncertainties. Hence, we expect the systematic error to be much
+smaller than $<1\,\kmps$ if one is required.
+
+The observed binary fraction is expected to be very sensitive to the
+assumed size of the systematic error since the RV shifts and the
+systematic errors are in same order of magnitude.  This point is
+demonstrated further in Fig.~\ref{fig:adding_sys_err} which shows the
+the number of observed binaries (non-constant RV objects) plotted
+against the size of the additional systematic error.  The number of
+detections decreases rapidly as $\sigma_{\mathrm{sys}}$ increases.
+The number remains constant at 2 for a relatively wide range of the
+systematic errors i.e.  $0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
+\kmps$.  No binary is detected for $\sigma_{\mathrm{sys}} > \sim
+0.375\, \kmps$.  We have computed the $\chi^2$ probabilities for the
+RV constant as done earlier (Fig~\ref{fig:chisq-test}) along with the
+expected distribution of ($-\log{p}$) with an additional
+$\sigma_{\mathrm{sys}}$ introduced in the analysis. We find that the
+case with $\sigma_{\mathrm{sys}}=0.1\,\kmps$ gives a better agreement
+with the histogram of $-\log{p}$ to the expected
+distribution (not shown here), compared to the case with
+$\sigma_{\mathrm{sys}}=0\,\kmps$. In the following analysis, we will
+adopt $\sigma_{\mathrm{sys}}=0.1\,\kmps$. This means that even if our
+systematic error is slightly underestimated, the number of detection
+remains the same according to Fig.~\ref{fig:adding_sys_err}.
+
+We have re-analysed the number of observed binaries
+(Fig~\ref{fig:chisq-test}), the detection probability
+(Fig.~\ref{fig:detect_prob}), and the expected binary fraction as done
+earlier but this time with the additional systematic error
+$\sigma_{\mathrm{sys}}=0.1\,\kmps$.  The result is summarised in
+Table~\ref{tab:binary_fraction}.  
+Although the small number statistics makes us difficult to withdraw a
+firm conclusion on the binary fraction from our data, we find the case
+with $\sigma_{\mathrm{sys}} = 0.1\, \kmps$ has a better agreement with
+the expected binary fraction (c.f.~Table~\ref{tab:binary_fraction}).
+Our tentative conclusion of the binary fraction found in this analysis
+is $f_{\mathrm{sys}}=12^{+13}_{-10}$~per~cent for $a<0.12$~au.  The
+large uncertainties in this values is due to small number
+statistics. The expected binary fraction
+$f_{\mathrm{exp}}=2.9$~per~cent is still within the uncertainty of our
+binary fraction.  The two objects identified as 
+binary/multiple candidates are GY~310 and USco~104.
+
+%==========================================
+\begin{figure}
+
+\begin{center}
+
+\includegraphics[%
+  clip,
+  scale=0.63]{figures/detect_err_add.eps}
+
+\end{center}
+
+\caption{The number of binaries/multiples (non-constant RV objects)
+  detected as a function of the size of additional systematic error ($\sigma_{\mathrm{sys}}$)
+  in RV measurement. The number of detections decreases rapidly from 4
+  to 2 as $\sigma_{\mathrm{sys}}=0.1\,\kmps$, which may be caused by
+  from the instability of the autoguiding of the telescope, is added to
+  the uncertainties estimated in
+  Table~\ref{tab:summary_results}. The number of the detections
+  remains constant at 2 for a relatively wide range of the additional
+  errors. i.e.~$0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
+  \kmps$. No binary is found for  $\sigma_{\mathrm{sys}} > 0.375\,\kmps$.} 
+\label{fig:adding_sys_err}
+
+\end{figure}
+%==========================================
+
+\begin{table}
+
+\caption{Summary of observed binary fraction ($f_{\mathrm{obs}}$) compared with the
+  expected binary fraction ($f_{\mathrm{exp}}$) with and without a
+  systematic error ($\sigma_{\mathrm{sys}}$). }
+
+\label{tab:binary_fraction}
+
+\begin{center}
+
+\begin{tabular}{ccccl}
+\hline 
+$\sigma_{\mathrm{sys}}$&  
+N. detected&  
+$f_{\mathrm{obs}}$&
+$f_{\mathrm{exp}}$&  
+obj.~ID  \tabularnewline
+($\kmps$)&
+&
+(per~cent)&
+(per~cent)&
+\tabularnewline
+\hline
+$0.0$&
+$4$&
+$24^{+16}_{-14}$&
+$3.2$&
+GY~141\tabularnewline
+&
+&
+&
+&
+GY~310\tabularnewline
+&
+&
+&
+&
+USco~55\tabularnewline
+&
+&
+&
+&
+USco~104\tabularnewline
+$0.1$&
+$2$&
+$12^{+13}_{-10}$&
+$2.9$&
+GY~310\tabularnewline
+&
+&
+&
+&
+USco~104\tabularnewline
+\hline
+\end{tabular}
+
+\end{center}
+
+\end{table}
+%==========================================
 
@@
 We have presented two-epoch RV survey of 18 young BDs and VLM stars
-in UScoOB and $\rho$~Oph dark cloud core using the high resolution
-UVES echelle spectroscopy at VLT.  We found 9 out of 18 objects (50~per~cent) are possible candidates
-in this analysis. For the objects in UScoOB, we found 6 out of 14
-objects (43~per~cent) as candidates. Compared to the average binary
-fraction ($\sim20\,\mathrm{per\, cent}$) of magnitude-limited imaging
-surveys for BDs and VLM stars (M6 and later) in the field (c.f.~\citealt{burgasser:2006}),
-the fraction of the binary `candidates' found by this RV survey is
-significantly higher. The possible reasons to for the discrepancy
-are: (1) caused by the different sensitivity on the binary separation
-in the imaging and RV technique, (2) caused by possibly under estimated
-uncertainties in the measured RV values. The true multiplicity of
-the candidates must be confirmed by follow-up spectroscopy monitoring
-of candidates.
-
-We found a good agreement with the high resolution imaging survey
-of the BD and VLM objects in UScoOB of \citet{kraus:2005}. All three
-confirmed binaries in UScoOB by \citet{kraus:2005} are found as the
-multiplicity candidate this RV survey; however, we found two objects
-(USco~75 and USco~112) also as binary candidates while they found
-them as singles.
-
-From the distribution of RV values in UScoOB, we confirmed that USco~121
-is most likely a non-member of the association, as similarly found
-so by  \citet{muzerolle:2003}. We found the RV dispersion of the
-objects in UScoOB is very similar to that of the BDs and VLM stars
-in Chamaeleon~I (Cha~I) previously studied by others. The rotational
-velocities ($v\,\sin i$) of the samples are also measured. The distribution
-of $v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$
-which is similar to that of the Cha~I population.
+($0.02~M_{\sun} < M_{*} < 0.1~M_{\sun}$) in
+UScoOB and $\rho$~Oph dark cloud core using the high resolution UVES
+echelle spectroscopy at VLT.  The average time separation of RV
+measurements are 21.6~d, and our RV survey is sensitive to binaries
+with separation smaller than 0.12~au.  One of our targets USco~121 is
+most likely a non-member of the UScoOB association based on the
+deviation of the RV from the result of the population in the
+association. A similar conclusion was found by \citet{muzerolle:2003}
+from their RV study and the low lithium abundance.
+
+We found 2 (GY~310 and USco~104) out of 17 objects as our final
+binary/multiple candidates. This corresponds to the binary fraction of
+$12^{+13}_{-10}$~per~cent for the binary separation $a<0.12$~au, which
+is larger than the expected binary fraction of 2.9~per~cent, but it is
+still within the uncertainties of the observed value.  The expected
+binary fraction was computed by using a similar binary separation
+models used by \citet{maxted:2005} and \citet{basri:2006}.  We found
+that the final estimate of the binary fraction is very sensitive to
+the assumed size of systematic error. If the systematic error was
+ignored, we would have found 4 binary/multiple candidates.
+
+The recent high-resolution imaging survey of brown dwarfs and very
+low-mass objects (M5.5--M7.5 ) in the UScoOB by \citet{kraus:2005} (which was
+not known to authors at the time of our observation: April--May, 2004)
+confirms that USco~65 and USco~66 are multiple systems, and USco~109
+is most likely a multiple system.  Their projected separations are
+($a>4.0$~au), and are well above our sensitivity limit of
+0.12~au. Hence, it is not surprising that we did not find any of them
+as a multiple, and it also indicates that any of them is unlikely to
+have a component of a triple system within 0.12~au from their primaries. 
+On the other hand, we found USco~104 as a binary candidate, but this
+was not in their target list.  Further they found USco~67, 75, 112, 128,
+130, 132 as non-multiple, and similarly we found them as
+'non-candidates' for multiplicity.
+
+We found the RV dispersion ($1.2\,\kmps$) of the objects in UScoOB is
+very similar to that of the BDs and VLM stars in Chamaeleon~I (Cha~I)
+previous study by \citet{joergens:2006b}. The rotational velocities
+($v\,\sin i$) of the samples are also measured. The distribution of
+$v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which is
+also similar to that of the Cha~I population found by
+\citet{joergens:2006b}.
 
@@
 \end{document}
+
+% LocalWords:  BDs VLM OB Ophiuchi al Ryuichi Harries QL RV UScoOB BD echelle
+% LocalWords:  VLT UVES RVs Cha bouy burgasser gizis kraus basri maxted PPl EEV
+% LocalWords:  pinfield substellar duquennoy VLMs guenther joergens padoan CCDs
+% LocalWords:  reipurth whitworth dezeeuw ardila luhman muzerolle Kueyen Parnal
+% LocalWords:  LL ESO interorder autoguiding FWHM jones Oph wilking mohanty Sp
+% LocalWords:  GY USco LHS HJD gaussian Cen garcia sanchez HD RRV pc CCF exp
+% LocalWords:  obs

### 2006-05-08 BD_radvel/kurosawa.tex
minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@711 25464f21-6099-402c-b30a-640f1d40d38b

@@
 spectroscopic binaries in our sample, based on the shape of
-cross-corelation curves. The RV dispersion of the objects in UScoOB is
-found to be very similar to that of the BDs and VLM stars in
-Chamaeleon~I (Cha~I) previously studied by others. We also found the
-distribution of the rotational velocities ($v\,\sin i$) of the UScoOB
-objects is good agreement with that of Cha~I from earlier studies.
+cross-corelation curves. The RV dispersion of the objects in UScoOB
+is found to be very similar to that of the BD and VLM stars in
+Chamaeleon~I (Cha~) previously studies by others. We also found the
+distribution of the mean rotational velocities ($v\,\sin i$) of the
+UScoOB objects is similar to that of the Cha~I, but the dispersion of
+$v\,\sin i$ is much larger than that of the Cha~I objects.
 
@@
 observations were carried out between 2004 April 5 and 2004 May 17 in
-service mode. For each object, spectra were obtained at two different
-epochs separated by several (between 4 and 33~d). For each object at a
+the service mode. For each object, spectra were obtained at two different
+epochs separated by 4--33~d. For each object at a
 given night, two separate spectra are obtained consecutively. This
@@
 
-\caption{Summary of known properties of the targets from literature:
+\caption{Summary of known properties of the targets from literatures:
 a.~\citet{luhman:1999} (original list for $\rho$~Oph),
@@
 function of the object spectrum with that of a template star which has
-a spectra type. By visual inspection,
+a similar spectra type. By visual inspection,
 the wavelength ranges used for the cross-correlation calculations
@@
 radial velocities of objects with respect to the template are obtained
-by measuring the location of the peak in the cross-correlation function
-which is fitted by a function which consists of two gaussian functions
+by measuring the location of the peak in the cross-correlation
+function. The location of the peak is determined by fitting the
+cross-correlation function by a function which consists of two gaussians 
 (with a common centre) plus a constant term. LHS~49 (Proxima Cen, M5.5) was
@@
 only requires relative (with respect to a template) RV values.
-The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
+The 'average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
 two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
@@
 as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
-(excluding the non-member USco~121). 
+(excluding the non-member USco~121; see explanation later). 
 The figure clearly shows two distinctive populations: one on the left
@@
 reasonable, and an additional systematic error may not be necessary in
-this analysis. According
-to the figure, there are four objects which shows significant RV
+this analysis (but see Section~\ref{sec:Binary-fraction}). According
+to the figure, there are four objects which show significant RV
 variations out of 17 samples. They are GY~141, GY~310, USco~55, and
@@
 
-\caption{The histogram of the $\chi^2$ probability ($p$) for fitting the
+\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
   observed (relative) RV values with a constant (a horizontal
@@
   $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
-  which appear in the right-most $\log{p}$ bin in the histogram. There
-  are four objects which satisfies this condition. The
-  expected distribution (dashed) for constant objects based on the RV
+  which appear in the right-most bin in the histogram. There
+  are four objects which satisfy this condition. The
+  expected distribution (dashed) for RV constant objects based on the RV
   uncertainties in the observations (Table~\ref{tab:summary_results})
@@
 measurements of the higher mass counter parts (T~Tauri stars) in
-Upper Sco OB association. This is also planned for a near future investigation
+Upper Sco OB association. This is planned for a near future investigation
 as this is important for the study of the mass dependency of the kinematics
@@
 $25.9\,\kmps$ which are very similar to those of the Upper Sco brown
-dwarf candidate objects.
+dwarf candidates and VLM stars.
 
@@
 
-\caption{Histogram of the rotational velocities (right) of 14 UScoOB BD and VLM
+\caption{Histogram of the rotational velocities ($v\,\sin{i}$) of 14 UScoOB BD and VLM
 objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
@@
 of $x$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
-analysis, we find the final binary/multiple fraction along with the
+analysis, we find the binary/multiple fraction along with the
 uncertainties of our sample to be $f=24^{+16}_{-14}$~per~cent.
@@
 data, (4)~find the fraction of detections out of all random trials,
-(5) repeat 1--4 for a range of $a$ between $10^{-3}$~and 10~au, and
+(5) repeat 1--4 for the range of $a$ between $10^{-3}$~and 10~au, and
 (6) repeat 5 for the all targets, and find the detection probability
@@
 decreases beyond $a\approx 0.3\,\mathrm{au}$.  This turning point will
-increase if we used larger time separations in our observation. 
+increase if we had used larger time separations in our observation. 
 From this figure, we find that the 80~per~cent detection probability
 up to for binaries with $a<0.12\,\mathrm{au}$, given our time
-separations and the average uncertainty ($~0.5\,\kmps$) in the RV
+separations and the average uncertainty ($\sim0.5\,\kmps$) in the RV
 measurements.
@@
 \caption{The binary detection probability (solid) as a function of the semimajor
-  axis ($a$) based on Monte~Carlo simulations of RV measurements is
+  axis ($a$), based on Monte~Carlo simulations of RV measurements, is
   shown.  For each object in our target list, the simulation was performed
-  using the time separation ($\Delta t$) of the two-epoch observation
-  used in the observation (c.f.~Table~\ref{tab:summary_results}) and
+  using the time separation ($\Delta t$) actually used in our
+  two-epoch observations (c.f.~Table~\ref{tab:summary_results}) and
   the estimated primary mass  (c.f.~Table~\ref{tab:literatures}).  The
@@
   comparison. The distribution is a gaussinan in logarithmic
-  space, centred at $\log{a}=10$, and truncated at $a=15$~au. See text
+  space, centred at $\log{a}=0.6$, and truncated at $a=15$~au. See text
   for a detail.}
@@
 $\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
-is reasonably matches with the expected distribution.  This lead us to
+reasonably matches the expected distribution.  This lead us to
 conclude that the uncertainty estimates in RV values were
@@
 systematic errors i.e.  $0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
-\kmps$.  No binary is detected for $\sigma_{\mathrm{sys}} > \sim
+\kmps$.  No binary is detected for $\sigma_{\mathrm{sys}} > 
 0.375\, \kmps$.  We have computed the $\chi^2$ probabilities for the
@@
   detected as a function of the size of additional systematic error ($\sigma_{\mathrm{sys}}$)
-  in RV measurement. The number of detections decreases rapidly from 4
+  in RV measurements. The number of detections decreases rapidly from 4
   to 2 as $\sigma_{\mathrm{sys}}=0.1\,\kmps$, which may be caused by
-  from the instability of the autoguiding of the telescope, is added to
+  the instability of the autoguiding of the telescope, is added to
   the uncertainties estimated in
-  Table~\ref{tab:summary_results}. The number of the detections
+  Table~\ref{tab:summary_results}. The number of  detections
   remains constant at 2 for a relatively wide range of the additional
@@
 
-\caption{Summary of observed binary fraction ($f_{\mathrm{obs}}$) compared with the
-  expected binary fraction ($f_{\mathrm{exp}}$) with and without a
+\caption{Summary of the observed binary fractions ($f_{\mathrm{obs}}$) compared with the
+  expected binary fractions ($f_{\mathrm{exp}}$) with and without a
   systematic error ($\sigma_{\mathrm{sys}}$). }
@@
 also similar to that of the Cha~I population found by
-\citet{joergens:2006b}.
+\citet{joergens:2006b}; however, the dispersion of $v\,\sin i$ for the
+UScoOB objects ($27.8\,\kmps$) is found to be much larger than that of
+the Cha~I objects ($8.0\,\kmps$)
 

### 2006-05-08 BD_radvel/kurosawa.tex
minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@712 25464f21-6099-402c-b30a-640f1d40d38b

@@
 survey is sensitive to the binaries with separation $<0.12$~au.  We
-found 2 out of 17 objects (or $12^{+13}_{-10}$~per~cent by fraction)
+found 2 out of 17 objects (or $24^{+16}_{-14}$~per~cent by fraction)
 show a significant RV change in 4--33~d time scale, and are 
@@
 UScoOB objects is similar to that of the Cha~I, but the dispersion of
-$v\,\sin i$ is much larger than that of the Cha~I objects.
+$v\,\sin i$ is significantly larger than that of the Cha~I objects.
 
@@
 is not too extreme, and velocity separation is large enough. The first
-BD+BD spectroscopic binary, PPl~15  \citep{basri:1999} showed a
+BD+BD spectroscopic binary, PPl~15  \citep{basri:1999}, showed a
 double-peaked cross-correlation function with a maximum velocity separation
@@
 
-Before applying the cross-correlation technique to out main targets,
+Before applying the cross-correlation technique to our main targets,
 we have applied the technique to the radial velocity standard HD~140538
@@
 only requires relative (with respect to a template) RV values.
-The 'average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
+The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
 two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
@@
 computing $\Delta\mathrm{RV}$ we do not require the knowledge of
-absolute or the heliocentric radial velocities, but only the relative
+absolute radial velocities, but only the relative
 velocities (with respect to a template).
@@
 constant population on the left side reasonably matches the expected
-curve. This assures that our uncertainties in RV values are
+curve. This reassures that our uncertainties in RV values are
 reasonable, and an additional systematic error may not be necessary in
@@
 candidates.  We will discuss the effect of the systematics error in detail, and
-list our final binary/multiple candidate later in
-Section~\ref{sec:Binary-fraction}.
+list our final binary/multiple candidates in Section~\ref{sec:Binary-fraction}.
 
@@
 but the standard deviation of the distribution is significantly smaller
-than that of the Upper Sco objects. The difference maybe due to the
+than that of our Upper Sco objects. The difference maybe due to the
 very small sample. A similar fit was applied to the $v\,\sin i$

### 2006-05-08 BD_radvel/kurosawa.tex
Revision after Tim's comments.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@713 25464f21-6099-402c-b30a-640f1d40d38b

@@
 survey is sensitive to the binaries with separation $<0.12$~au.  We
-found 2 out of 17 objects (or $24^{+16}_{-14}$~per~cent by fraction)
+found 4 out of 17 objects (or $24^{+16}_{-14}$~per~cent by fraction)
 show a significant RV change in 4--33~d time scale, and are 
@@
   beyond $a\approx 0.3\,\mathrm{au}$.  The 80~per~cent detection
-  probability is achieved for binaries with $a<0.12\,\mathrm{au}$. 
-  The binary separation distribution (dash) similar to that of
-  \citet{maxted:2005} and \citet{basri:2006} are shown also for a
-  comparison. The distribution is a gaussinan in logarithmic
-  space, centred at $\log{a}=0.6$, and truncated at $a=15$~au. See text
-  for a detail.}
+  probability is achieved for binaries with $a<0.12\,\mathrm{au}$. }
 
@@
 
-The expected binary fraction for our survey can be obtained
-by integrating the product of the detection probability found above
-with an assumed binary separation distribution function over a range
-of $a$. Here, we simply adopt one of the separation distribution
-function used by \citet{maxted:2005}. The binary separation ($a$)
-distribution is assumed to be  gaussian in  log($a$) space with its
-centre $\log{a_{o}}=0.6$ and width $\sigma_{\log{a}}=1.0$, and
-truncated at $\log{a}=1.176$ where $a$ is in au. This form of the
-distribution function is motivated by the distribution of solar-type
-binaries found in \citet{duquennoy:1991}, and the truncation is
-suggested from the lack of wide binaries for $a>15$~au 
-(e.g.~\citealt{burgasser:2003}). The distribution is normalized such
-that the total binary fraction of 26~per~cent as
-suggested by \citet{basri:2006}.  The resulting separation
-distribution function is shown also in Fig.~\ref{fig:detect_prob}. 
-Using this and the detection probability in the same figure, we find
-the expected binary fraction to be $f_{\mathrm{exp}}=3.2$~per~cent
-(for $a<0.12$~au), which is
-much smaller than our observed binary fraction of
-$f_{\mathrm{obs}}=24^{+16}_{-14}$. The two values are not consistent
-with each other. There are two possible reasons for the discrepancy:
-(1)~the assumed binary separation distribution mentioned above is
-unrealistic, and (2)~the uncertainties in our RV measurements are
-underestimated.  The first reason is less likely since both
-\citet{maxted:2005} and \citet{basri:2006} found this form of the $a$
-distribution function is consistent with the observed binary
-fractions estimated from many earlier surveys.  We will investigate
-the possibility for the second reason in the following.
-
-Apparently, the underestimated uncertainties could have been caused by
-neglecting a systematic error. In Section~\ref{sub:Radial-velocities}
+%% The expected binary fraction for our survey can be obtained
+%% by integrating the product of the detection probability found above
+%% with an assumed binary separation distribution function over a range
+%% of $a$. Here, we simply adopt one of the separation distribution
+%% function used by \citet{maxted:2005}. The binary separation ($a$)
+%% distribution is assumed to be  gaussian in  log($a$) space with its
+%% centre $\log{a_{o}}=0.6$ and width $\sigma_{\log{a}}=1.0$, and
+%% truncated at $\log{a}=1.176$ where $a$ is in au. This form of the
+%% distribution function is motivated by the distribution of solar-type
+%% binaries found in \citet{duquennoy:1991}, and the truncation is
+%% suggested from the lack of wide binaries for $a>15$~au 
+%% (e.g.~\citealt{burgasser:2003}). The distribution is normalized such
+%% that the total binary fraction of 26~per~cent as
+%% suggested by \citet{basri:2006}.  The resulting separation
+%% distribution function is shown also in Fig.~\ref{fig:detect_prob}. 
+%% Using this and the detection probability in the same figure, we find
+%% the expected binary fraction to be $f_{\mathrm{exp}}=3.2$~per~cent
+%% (for $a<0.12$~au), which is
+%% much smaller than our observed binary fraction of
+%% $f_{\mathrm{obs}}=24^{+16}_{-14}$. The two values are not consistent
+%% with each other. There are two possible reasons for the discrepancy:
+%% (1)~the assumed binary separation distribution mentioned above is
+%% unrealistic, and (2)~the uncertainties in our RV measurements are
+%% underestimated.  The first reason is less likely since both
+%% \citet{maxted:2005} and \citet{basri:2006} found this form of the $a$
+%% distribution function is consistent with the observed binary
+%% fractions estimated from many earlier surveys.  We will investigate
+%% the possibility for the second reason in the following.
+
+In Section~\ref{sub:Radial-velocities}
 (see Fig.~\ref{fig:chisq-test}), we found the histogram of the
@@
 
-The observed binary fraction is expected to be very sensitive to the
-assumed size of the systematic error since the RV shifts and the
-systematic errors are in same order of magnitude.  This point is
-demonstrated further in Fig.~\ref{fig:adding_sys_err} which shows the
-the number of observed binaries (non-constant RV objects) plotted
-against the size of the additional systematic error.  The number of
-detections decreases rapidly as $\sigma_{\mathrm{sys}}$ increases.
-The number remains constant at 2 for a relatively wide range of the
-systematic errors i.e.  $0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
-\kmps$.  No binary is detected for $\sigma_{\mathrm{sys}} > 
-0.375\, \kmps$.  We have computed the $\chi^2$ probabilities for the
-RV constant as done earlier (Fig~\ref{fig:chisq-test}) along with the
-expected distribution of ($-\log{p}$) with an additional
-$\sigma_{\mathrm{sys}}$ introduced in the analysis. We find that the
-case with $\sigma_{\mathrm{sys}}=0.1\,\kmps$ gives a better agreement
-with the histogram of $-\log{p}$ to the expected
-distribution (not shown here), compared to the case with
-$\sigma_{\mathrm{sys}}=0\,\kmps$. In the following analysis, we will
-adopt $\sigma_{\mathrm{sys}}=0.1\,\kmps$. This means that even if our
-systematic error is slightly underestimated, the number of detection
-remains the same according to Fig.~\ref{fig:adding_sys_err}.
-
-We have re-analysed the number of observed binaries
-(Fig~\ref{fig:chisq-test}), the detection probability
-(Fig.~\ref{fig:detect_prob}), and the expected binary fraction as done
-earlier but this time with the additional systematic error
-$\sigma_{\mathrm{sys}}=0.1\,\kmps$.  The result is summarised in
-Table~\ref{tab:binary_fraction}.  
-Although the small number statistics makes us difficult to withdraw a
-firm conclusion on the binary fraction from our data, we find the case
-with $\sigma_{\mathrm{sys}} = 0.1\, \kmps$ has a better agreement with
-the expected binary fraction (c.f.~Table~\ref{tab:binary_fraction}).
-Our tentative conclusion of the binary fraction found in this analysis
-is $f_{\mathrm{sys}}=12^{+13}_{-10}$~per~cent for $a<0.12$~au.  The
-large uncertainties in this values is due to small number
-statistics. The expected binary fraction
-$f_{\mathrm{exp}}=2.9$~per~cent is still within the uncertainty of our
-binary fraction.  The two objects identified as 
-binary/multiple candidates are GY~310 and USco~104.
-
-%==========================================
-\begin{figure}
+The observed binary fraction is expected to be sensitive to the
+assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
+the RV shifts and the systematic errors are in the same order of
+magnitude. The number of binary detections would decrease as
+$\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
+probabilities ($p$) for each object being a RV constant object as done
+earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
+systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
+the uncertainties in the RVs of each object.  The results are
+summarised in Table~\ref{tab:prob_compare} along with the probabilities
+computed without the systematic error (as in
+Section\ref{sub:Radial-velocities}).  The number of objects with
+$p<10^{-3}$ decreases from 4 to 2 as the systematic error is
+introduced. Unfortunately, the probabilities computed with
+$\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
+below $p=10^{-3}$ boundary value; hence, they become RV constant
+objects as $\sigma_{\mathrm{sys}}=0.2\,\kmps$ is introduced. This
+clearly demonstrates the importance of the uncertainty estimates in
+the measured RV values.  We found that the histogram of the $\chi^2$
+probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
+Fig~\ref{fig:chisq-test}), also have a good agreement with the
+expected distribution of $-\log{p}$ (not shown here).  
+The binary fraction estimated with the assumed systematic error is
+$2/17$ or $f=12^{+13}_{-10}$~per~cent for $a<0.12$~au.
+
+%% %==========================================
+%% \begin{figure}
+
+%% \begin{center}
+
+%% \includegraphics[%
+%%   clip,
+%%   scale=0.63]{figures/detect_err_add.eps}
+
+%% \end{center}
+
+%% \caption{The number of binaries/multiples (non-constant RV objects)
+%%   detected as a function of the size of additional systematic error ($\sigma_{\mathrm{sys}}$)
+%%   in RV measurements. The number of detections decreases rapidly from 4
+%%   to 2 as $\sigma_{\mathrm{sys}}=0.1\,\kmps$, which may be caused by
+%%   the instability of the autoguiding of the telescope, is added to
+%%   the uncertainties estimated in
+%%   Table~\ref{tab:summary_results}. The number of  detections
+%%   remains constant at 2 for a relatively wide range of the additional
+%%   errors. i.e.~$0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
+%%   \kmps$. No binary is found for  $\sigma_{\mathrm{sys}} > 0.375\,\kmps$.} 
+%% \label{fig:adding_sys_err}
+
+%% \end{figure}
+%% %==========================================
+
+%==========================================
+\begin{table}
+
+\caption{Comparison of the $\chi^{2}$ probability ($p$), for each object
+  being a RV constant, computed with an addition systematic error
+  $\sigma_{\mathrm{sys}}$ (right), and without (left). The objects are
+  listed in ascending order of $p$. The ellipses represent the
+  boundary ($p=10^{-3}$) between RV constant objects and RV 
+  variable objects. }
+
+\label{tab:prob_compare}
 
 \begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.63]{figures/detect_err_add.eps}
-
-\end{center}
-
-\caption{The number of binaries/multiples (non-constant RV objects)
-  detected as a function of the size of additional systematic error ($\sigma_{\mathrm{sys}}$)
-  in RV measurements. The number of detections decreases rapidly from 4
-  to 2 as $\sigma_{\mathrm{sys}}=0.1\,\kmps$, which may be caused by
-  the instability of the autoguiding of the telescope, is added to
-  the uncertainties estimated in
-  Table~\ref{tab:summary_results}. The number of  detections
-  remains constant at 2 for a relatively wide range of the additional
-  errors. i.e.~$0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
-  \kmps$. No binary is found for  $\sigma_{\mathrm{sys}} > 0.375\,\kmps$.} 
-\label{fig:adding_sys_err}
-
-\end{figure}
-%==========================================
-
-\begin{table}
-
-\caption{Summary of the observed binary fractions ($f_{\mathrm{obs}}$) compared with the
-  expected binary fractions ($f_{\mathrm{exp}}$) with and without a
-  systematic error ($\sigma_{\mathrm{sys}}$). }
-
-\label{tab:binary_fraction}
-
-\begin{center}
-
-\begin{tabular}{ccccl}
+\begin{tabular}{lclc}
 \hline 
-$\sigma_{\mathrm{sys}}$&  
-N. detected&  
-$f_{\mathrm{obs}}$&
-$f_{\mathrm{exp}}$&  
-obj.~ID  \tabularnewline
-($\kmps$)&
-&
-(per~cent)&
-(per~cent)&
-\tabularnewline
+&
+$\sigma_{\mathrm{sys}}=0.0\,\kmps$&
+&
+$\sigma_{\mathrm{sys}}=0.2\,\kmps$\tabularnewline
+obj.~ID&
+$p$&
+obj.~ID&
+$p$\tabularnewline
 \hline
-$0.0$&
-$4$&
-$24^{+16}_{-14}$&
-$3.2$&
-GY~141\tabularnewline
-&
-&
-&
-&
-GY~310\tabularnewline
-&
-&
-&
-&
-USco~55\tabularnewline
-&
-&
-&
-&
-USco~104\tabularnewline
-$0.1$&
-$2$&
-$12^{+13}_{-10}$&
-$2.9$&
-GY~310\tabularnewline
-&
-&
-&
-&
-USco~104\tabularnewline
+USco~104&
+$4.3\times10^{-12}$&
+USco~104&
+$3.5\times10^{-6}$\tabularnewline
+GY~310&
+$1.8\times10^{-10}$&
+GY~310&
+$2.0\times10^{-5}$\tabularnewline
+GY~141&
+$1.6\times10^{-4}$&
+$\cdots$&
+$\cdots$\tabularnewline
+USco~55&
+$7.2\times10^{-4}$&
+GY~141&
+$5.8\times10^{-2}$\tabularnewline
+$\cdots$&
+$\cdots$&
+USco~55&
+$1.6\times10^{-1}$\tabularnewline
+USco~101&
+$8.9\times10^{-2}$&
+USco~130&
+$2.3\times10^{-1}$\tabularnewline
+USco~66&
+$9.2\times10^{-2}$&
+USco~132&
+$2.6\times10^{-1}$\tabularnewline
+USco~75&
+$2.8\times10^{-1}$&
+USco~101 &
+$2.8\times10^{-1}$\tabularnewline
+USco~109&
+$3.0\times10^{-1}$&
+GY~5&
+$2.8\times10^{-1}$\tabularnewline
+USco~112&
+$3.1\times10^{-1}$&
+USco~75&
+$3.9\times10^{-1}$\tabularnewline
+USco~132&
+$3.2\times10^{-1}$&
+USco~66&
+$4.3\times10^{-1}$\tabularnewline
+USco-~30&
+$3.2\times10^{-1}$&
+USco~128&
+$4.6\times10^{-1}$\tabularnewline
+GY~5&
+$3.7\times10^{-1}$&
+USco~53&
+$5.8\times10^{-1}$\tabularnewline
+USco~53 &
+$4.2\times10^{-1}$&
+USco40&
+$6.0\times10^{-1}$\tabularnewline
+USco~67&
+$4.8\times10^{-1}$&
+USco~112&
+$6.5\times10^{-1}$\tabularnewline
+USco~128&
+$5.4\times10^{-1}$&
+USco~100&
+$6.6\times10^{-1}$\tabularnewline
+USco~100&
+$6.2\times10^{-1}$&
+USco~67&
+$7.0\times10^{-1}$\tabularnewline
+USco~40&
+$7.2\times10^{-1}$&
+USco~109&
+$7.1\times10^{-1}$\tabularnewline
 \hline
@@
 \end{table}
+%==========================================
+
+%% %==========================================
+%% \begin{table}
+
+%% \caption{Summary of the observed binary fractions ($f_{\mathrm{obs}}$) compared with the
+%%   expected binary fractions ($f_{\mathrm{exp}}$) with and without a
+%%   systematic error ($\sigma_{\mathrm{sys}}$). }
+
+%% \label{tab:binary_fraction}
+
+%% \begin{center}
+
+%% \begin{tabular}{ccccl}
+%% \hline 
+%% $\sigma_{\mathrm{sys}}$&  
+%% N. detected&  
+%% $f_{\mathrm{obs}}$&
+%% $f_{\mathrm{exp}}$&  
+%% obj.~ID  \tabularnewline
+%% ($\kmps$)&
+%% &
+%% (per~cent)&
+%% (per~cent)&
+%% \tabularnewline
+%% \hline
+%% $0.0$&
+%% $4$&
+%% $24^{+16}_{-14}$&
+%% $3.2$&
+%% GY~141\tabularnewline
+%% &
+%% &
+%% &
+%% &
+%% GY~310\tabularnewline
+%% &
+%% &
+%% &
+%% &
+%% USco~55\tabularnewline
+%% &
+%% &
+%% &
+%% &
+%% USco~104\tabularnewline
+%% $0.1$&
+%% $2$&
+%% $12^{+13}_{-10}$&
+%% $2.9$&
+%% GY~310\tabularnewline
+%% &
+%% &
+%% &
+%% &
+%% USco~104\tabularnewline
+%% \hline
+%% \end{tabular}
+
+%% \end{center}
+
+%% \end{table}
 %==========================================
@@
 
-We found 2 (GY~310 and USco~104) out of 17 objects as our final
+We found 4 (GY~141, GY~310, USco~55 and USco~104) out of 17 objects as our 
 binary/multiple candidates. This corresponds to the binary fraction of
-$12^{+13}_{-10}$~per~cent for the binary separation $a<0.12$~au, which
-is larger than the expected binary fraction of 2.9~per~cent, but it is
-still within the uncertainties of the observed value.  The expected
-binary fraction was computed by using a similar binary separation
-models used by \citet{maxted:2005} and \citet{basri:2006}.  We found
-that the final estimate of the binary fraction is very sensitive to
-the assumed size of systematic error. If the systematic error was
-ignored, we would have found 4 binary/multiple candidates.
+$24^{+16}_{-14}$~per~cent for the binary separation $a<0.12$~au.  We found
+that the estimated binary fraction is very sensitive to
+the assumed size of systematic error. If an additional systematic
+error of $0.2\,\kmps$  was added to the uncertainties in the RV
+measurements, we found only 2 (GY~310 and USco~104) out of 17 objects
+as our binary/multiple candidates, which corresponds to the binary
+fraction of $12^{+13}_{-10}$~per~cent.
 
@@
 not known to authors at the time of our observation: April--May, 2004)
-confirms that USco~65 and USco~66 are multiple systems, and USco~109
+confirms that USco~55 and USco~66 are multiple systems, and USco~109
 is most likely a multiple system.  Their projected separations are
 ($a>4.0$~au), and are well above our sensitivity limit of
-0.12~au. Hence, it is not surprising that we did not find any of them
-as a multiple, and it also indicates that any of them is unlikely to
-have a component of a triple system within 0.12~au from their primaries. 
-On the other hand, we found USco~104 as a binary candidate, but this
+0.12~au. Hence, it is not surprising that we did not find USco~66 and
+USco~109 as multiples. Interestingly, we also found USco~55 as a
+candidate for a multiple system. This may indicate that USco~55 is  
+a triple system with one of object located within 0.12~au from the
+primary.  In addition, we found USco~104 as a binary candidate, but this
 was not in their target list.  Further they found USco~67, 75, 112, 128,

### 2006-05-08 BD_radvel/kurosawa.tex
minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@714 25464f21-6099-402c-b30a-640f1d40d38b

@@
 objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
-a non-member). The gaussian fit (dashed line) of the radial velociity
+a non-member). The gaussian fit (dashed) of the radial velociity
 distribution gives a standard deviation of $1.2\,\kmps$ and the peak
@@
 objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
-a non-member).  The log-normal fit (dash-dot) of the
+a non-member).  The log-normal fit (dashed) of the
 rotational velocity distribution gives a standard deviation

### 2006-05-09 BD_radvel/kurosawa.tex
Change after Tim's revision #2.  RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@715 25464f21-6099-402c-b30a-640f1d40d38b

@@
 spectroscopic binaries in our sample, based on the shape of
-cross-corelation curves. The RV dispersion of the objects in UScoOB
+cross-correlation curves. The RV dispersion of the objects in UScoOB
 is found to be very similar to that of the BD and VLM stars in
@@
 primary masses (c.f.~Tables~\ref{tab:literatures} and
-\ref{tab:summary_results}).  The probability will be calculated based
+\ref{tab:summary_results}).  The probability is calculated based
 on the simulated RV observations of binaries whose orbit are randomly
@@
 $\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
-reasonably matches the expected distribution.  This lead us to
+reasonably matches the expected distribution.  This leads us to
 conclude that the uncertainty estimates in RV values were
@@
 $\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
-below $p=10^{-3}$ boundary value; hence, they become RV constant
-objects as $\sigma_{\mathrm{sys}}=0.2\,\kmps$ is introduced. This
+below the $p=10^{-3}$ boundary value; hence, they become RV constant
+objects as the systematic error is introduced. This
 clearly demonstrates the importance of the uncertainty estimates in
@@
 probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
-Fig~\ref{fig:chisq-test}), also have a good agreement with the
+Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
 expected distribution of $-\log{p}$ (not shown here).  
@@
 measurements are 21.6~d, and our RV survey is sensitive to binaries
-with separation smaller than 0.12~au.  One of our targets USco~121 is
+with separation smaller than 0.12~au.  One of our targets, USco~121, is
 most likely a non-member of the UScoOB association based on the
@@
 the assumed size of systematic error. If an additional systematic
-error of $0.2\,\kmps$  was added to the uncertainties in the RV
-measurements, we found only 2 (GY~310 and USco~104) out of 17 objects
+error of $0.2\,\kmps$  is added to the uncertainties in the RV
+measurements, we find only 2 (GY~310 and USco~104) out of 17 objects
 as our binary/multiple candidates, which corresponds to the binary
@@
 is most likely a multiple system.  Their projected separations are
-($a>4.0$~au), and are well above our sensitivity limit of
-0.12~au. Hence, it is not surprising that we did not find USco~66 and
+$a>4.0$~au which is well above our sensitivity limit of
+0.12~au; therefore, it is not surprising that we did not identify USco~66 and
 USco~109 as multiples. Interestingly, we also found USco~55 as a
@@
 a triple system with one of object located within 0.12~au from the
-primary.  In addition, we found USco~104 as a binary candidate, but this
+primary.  In addition, we identify USco~104 as a binary candidate, but this
 was not in their target list.  Further they found USco~67, 75, 112, 128,
@@
 previous study by \citet{joergens:2006b}. The rotational velocities
-($v\,\sin i$) of the samples are also measured. The distribution of
+($v\,\sin i$) of the samples were also measured. The distribution of
 $v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which is
@@
 
-The follow-up spectroscopic observations of the binary candidates
+Follow-up spectroscopic observations of the binary candidates
 presented here are planned in near future. There are only a few RV
-variable binary candidates are identified from the earlier surveys
+variable binary candidates identified in earlier surveys
 (\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
-As \citet{burgasser:2006} pointed out most of the current RV and
+As \citet{burgasser:2006} points out most of the current RV and
 imaging surveys use samples from magnitude-limited survey, but one
 should attempt to use the samples from volume-limited survey in order
-to find a correct statistics on binary parameters more straight forwardly,
+to find a correct statistics on binary parameters more straightforwardly,
 i.e. without correcting for bias.
@@
 
-We thank the staff of VLT of the ESO for the observations carried out in
-service mode.  This work is supported by PPARC rolling grant PP/C501609/1.
+We thank the staff of VLT of the ESO for carrying out the observations
+in service mode. RK thank Rob Jeffries for helpful suggestions on the
+data analysis presented in this paper. This work was supported by
+PPARC rolling grant PP/C501609/1.
 

### 2006-05-10 TTau_Halpha/astro-ph/kurosawa.tex
After accepeted by MNRAS
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@717 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-04-07 TTau_Halpha/kurosawa_resubmit/kurosawa.tex
@@
 of the magnetosphere at the equatorial plane ($z=0$) is assigned
-to be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
+to be the same as the inner radius ($R_{\mathrm{di}}$) of the accretion
 disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
@@
 
-The temperature structure of the magnetospheric used by
+The temperature structure of the magnetosphere used by
 \citet{hartmann:1994} is adopted here. They computed the temperature,
@@
 where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
-and the disc mass respectively.
+and the disc mass respectively, and
 \begin{equation}
@@
 mass, $M_{\mathrm{d}}$, is assumed to be 1/100 of the stellar mass
-($M_{*}$), and the outer disc radius ($R_{\mathrm{di}}$) is
+($M_{*}$), and the outer disc radius ($R_{\mathrm{do}}$) is
 100~au. The velocity of the gas/dust in the disc is assumed to be
@@
 has  $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
-$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).  The
+$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$.  The
 figure shows that the peak (normalised) flux decreases as the
@@
 $d =22\, R_{*}$ instead. This means that some part of the disc
-wind ($3\,R_{*} < w_{i} < 25.4\,R_{*}$) may not be able to be launched
+wind ($3\,R_{*} < w_{i} < 12.7\,R_{*}$) may not be able to be launched
 from the disc plane according to the model of \citet{blandford:1982}.
@@
 however change if the field/stream line is not straight and bending
-towards the symmetry axis as the wind travel higher above the disc.
+towards the symmetry axis as the wind travels higher above the disc.
 
@@
 and \ref{fig:atlas_hybrid}, we have computed the models with $d = 5\,
-R_{*}$ (not shown here) which satisfies the wind launching condition
+R_{*}$ (not shown here) which satisfy the wind launching condition
 of \citet{blandford:1982} in all parts of the disc wind zone in our
@@
 Although in general H$\alpha$ in the spectra of CTTS shows a
-significant amount of variablity, which may in some cases induced by
+significant amount of variablity, which may in some cases be induced by
 the rotational motion of an inclined magnetosphere
@@
     $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=1.0$ respectively.
-    The wind mass-loss rates used in both models is
+    The wind mass-loss rate used in both models is
     $\dot{M}_{\mathrm{wind}}=10^{-8}~\mathrm{M_{\sun}~yr^{-1}}$ . 
@@
 
-We thank an anonymous referee who provided us valuable comments and
+We thank the referee, Silvia Alencar, who provided us with valuable comments and
 suggestions which improved the clarity of the manuscript. This work
@@
 (3) $\dot{M}_{\mathrm{acc}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$
-(Fig.~\ref{fig:atlas02}).   The temperatures of the magnetospheres
+(Fig.~\ref{fig:atlas03}).   The temperatures of the magnetospheres
 used for (1), (2) and (3) are $7500\,\Kelvin$, $8500\,\Kelvin$ and

### 2006-05-11 BD_radvel/kurosawa.tex
Minor changes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@716 25464f21-6099-402c-b30a-640f1d40d38b
Worked on the Stu's comments (not finshed though). RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@718 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \newcommand{\pasj}{PASJ}
+\newcommand{\nat}{Nat}
 
@@
 association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
-cloud core. We obtained high-resolution echelle spectra at VLT using
+cloud core. We obtained high-resolution echelle spectra at the VLT using
 Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
@@
 average time separation of the RV measurements is 21.6~d, and our
-survey is sensitive to the binaries with separation $<0.12$~au.  We
-found 4 out of 17 objects (or $24^{+16}_{-14}$~per~cent by fraction)
+survey is sensitive to the binaries with separation $<0.1$~au.  We
+found 4 out of 17 objects (or $24^{+16}_{-13}$~per~cent by fraction)
 show a significant RV change in 4--33~d time scale, and are 
@@
 is found to be very similar to that of the BD and VLM stars in
-Chamaeleon~I (Cha~) previously studies by others. We also found the
-distribution of the mean rotational velocities ($v\,\sin i$) of the
+Chamaeleon~I (Cha~). We also found the distribution of the mean
+rotational velocities ($v\,\sin i$) of the 
 UScoOB objects is similar to that of the Cha~I, but the dispersion of
-$v\,\sin i$ is significantly larger than that of the Cha~I objects.
+$v\,\sin i$ is much larger than that of the Cha~I objects.
 
@@
 a complete star formation theory be able to predict the binary fraction,
-period distribution, and mass-ratio distribution of newly born stellar
-objects across a wide range of masses. Furthermore, the study of the individual
-binary system is the only direct means to determine the fundamental
+period distribution, and mass-ratio distribution of  stellar
+objects across a wide range of masses. Furthermore, the study of individual
+binary systems is the only direct means to determine fundamental
 stellar properties such as stellar masses and radii.
 
-Recent high-resolution imaging studies of young brown dwarfs (BDs)
+Recent high-resolution imaging studies of brown dwarfs (BDs)
 and very low-mass (VLM) stars have placed strong constraints on binaries
@@
 lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
-while $f=15$~per~cent was determined by \citet{close:2003} using
-the adaptive optics at Gemini North. They also found an upper limit
-to the semimajor axis distribution of $\sim20\,\mathrm{au}$. An
+while $f\approx15$~per~cent was determined by \citet{close:2003} using
+the adaptive optics at Gemini North. They also found the vast majority
+of systems have a semimajor axis $<20\,\mathrm{au}$ (see also
+\citealt{siegler:2005} but \citealt{luhman:2004}). An
 \emph{HST} study of more than 80 field late M and L dwarfs \citep{gizis:2003}
-indicated $f=15$~per~cent with separations in the range of 1.6--16~au.
-For s small sample (12) of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
+indicated $f\approx15$~per~cent with separations in the range of 1.6--16~au.
+For a small (12) sample of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
 in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
@@
 Note that the median separation of binaries with solar-type primaries
-is 30~au \citet{duquennoy:1991}. Pioneering work on the RVs
+is 30~au \citep{duquennoy:1991}. Pioneering works on the RVs
 of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
@@
 
-The separation distribution of BD/VLM binaries is critical to understanding
-their origin. There are two main models for the formation of BDs and
-VLM stars: first, they formed in a similar manner to higher mass stars,
-but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002});
-second, BD/VLM objects have low masses because they are ejected from
-the dense core in which they form via dynamical interactions in multiple
-system, cutting off their accretion before they have reached stellar
-masses (\citealt{reipurth:2001}; \citealt{bate:2002}). Alternatively,
-there is a third model in which a free-floating BD or planetary-mass
-object can be formed in the process of the photo-evaporation \citep{whitworth:2004} with
+The first BD+BD eclipsing binary (2MASS J0532184--J0546085) was
+discovered by \citet*{stassun:2006} from the $I$-band photometric
+monitoring of the system. Combining their light curves and the results
+from the follow-up radial velocity measurements, they were able to determined
+the precise oribital and physical parameters of the system.  The projected
+semimajor axis and the period of the binary are found as
+$0.0398\pm0.0010$~au and $9.779621\pm0.000042$~d respectively.
+
+The separation distribution of BD/VLM binaries is critical to
+understanding their origin. There are two main models for the
+formation of BDs and VLM stars: first, they have low masses because
+they form in low-mass, dense molecular cloud cores
+(e.g.~\citealt{padoan:2002}); second, BD/VLM objects have low masses
+because they are ejected from the dense core in which they form via
+dynamical interactions in multiple system, cutting off their accretion
+before they have reached stellar masses (\citealt{reipurth:2001};
+\citealt*{bate:2002}). Alternatively, there is a third model in which
+a free-floating BD or planetary-mass object can be formed in the
+process of the photo-evaporation
+(e.g.~\citealt{mccaughrean:2002};~\citealt{whitworth:2004}) with  
 the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
 removed by the strong radiation pressure from the nearby massive OB
- stars before the accretion onto the protostar at core centre
-occurs.
+stars before the accretion onto the protostar at core centre occurs.
 
@@
 In the first model, wider binaries may be expected to be more common.
-\citet{bate:2002} suggested that close binaries ($a<10\,\mathrm{au}$)
+\citet*{bate:2002b} suggested that close binaries ($a<10\,\mathrm{au}$)
 do not form directly, but result from hardening of wider systems though
@@
 without also finding many with separation $<1$~au. If an absence/rarity
-of binaries with 1~au were found, it would support the idea that
+of binaries with 1~au were found, it may support the idea that
 they are ejected quickly from multiple systems before they have undergone
@@
 $12.0^{f}$&
-$\mathrm{yes^{e}}$\tabularnewline
+$\mathrm{visual^{e}}$\tabularnewline
 USco 66&
@@
 $27.5^{f}$&
-$\mathrm{yes^{e}}$\tabularnewline
+$\mathrm{visual^{e}}$\tabularnewline
 USco 67&
@@
 $6.0^{f}$&
-$\mathrm{yes^{e}}$\tabularnewline
+$\mathrm{visual^{e}}$\tabularnewline
 USco 112&
@@
 velocities (with respect to a template). 
+Alternatively, we also computed the cross-correlation functions of
+spectra of a same object (instead of using the spectra of the template
+LHS~49) from two different epochs in order to find
+$\Delta\mathrm{RV}$. The resulting cross-correlation functions were
+found to be too noisy (due to the relatively low S/N in the object
+spectra), and the peak positions of the cross-correlation curves were
+not reliably located.
 
@@
 cluster of \cite{bate:2003} which yields a stellar density of
-$1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
+$\sim10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
 of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
-with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\,
+with a higher stellar density ($\sim10^{4}\,\mathrm{stars\,
 pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
@@
 Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
-bin size used for UScoOB obects and the log-normal fit, we find the
+bin size used for UScoOB obects and a log-normal fit, we find the
 $v\,\sin i$ distribution of the BD and VLM stars (8 objects) in Cha~I
@@
 The peak of the distribution is similar to that of Upper Sco objects,
-but the standard deviation of the distribution is significantly smaller
+but the standard deviation of the distribution is much smaller
 than that of our Upper Sco objects. The difference maybe due to the
 very small sample. A similar fit was applied to the $v\,\sin i$
-distribution of 14 T~Tauri stars in Cha~I using the data of \citet{joergens:2001},
-and we found a peak at $17.0\,\kmps$ with a  standard deviation
-$25.9\,\kmps$ which are very similar to those of the Upper Sco brown
-dwarf candidates and VLM stars.
+distribution of 14 higher mass T~Tauri stars in Cha~I using the data
+of \citet{joergens:2001}, and we found a peak at $17.0\,\kmps$ with a
+standard deviation $25.9\,\kmps$ which are very similar to those of
+the Upper Sco brown dwarf candidates and VLM stars.
 
@@
 out of $n$ trials with the probability $p$ for a positive event in each
-trial. In our case, $n=17$ (the number sample)  and $p=4/17=0.24$
+trial. In our case, $n=17$ (the number of sample)  and $p=4/17=0.24$
 (the fraction of binary/multiple).  The uncertainties was estimated by
@@
 analysis, we find the binary/multiple fraction along with the
-uncertainties of our sample to be $f=24^{+16}_{-14}$~per~cent.
+uncertainties of our sample to be $f=24^{+16}_{-13}$~per~cent.
 
@@
 
-There are six basic parameters our Monte Carlo simulation: 
+There are six basic parameters in our Monte Carlo simulation: 
 primary mass ($M_{1}$), mass ratio ($q$), eccentricity
@@
 of the primary ($V_{1}$), (2)~evolve the orbit by the time separation
-of the RV measuremets use in the observations for this object, and
+of the RV measuremets used in the observations for this object, and
 take another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
@@
 From this figure, we find that the 80~per~cent detection probability
-up to for binaries with $a<0.12\,\mathrm{au}$, given our time
+up to for binaries with $a<0.1\,\mathrm{au}$, given our time
 separations and the average uncertainty ($\sim0.5\,\kmps$) in the RV
@@
   beyond $a\approx 0.3\,\mathrm{au}$.  The 80~per~cent detection
-  probability is achieved for binaries with $a<0.12\,\mathrm{au}$. }
+  probability is achieved for binaries with $a<0.1\,\mathrm{au}$. }
 
@@
 %% the expected binary fraction to be $f_{\mathrm{exp}}=3.2$~per~cent
-%% (for $a<0.12$~au), which is
+%% (for $a<0.1$~au), which is
 %% much smaller than our observed binary fraction of
-%% $f_{\mathrm{obs}}=24^{+16}_{-14}$. The two values are not consistent
+%% $f_{\mathrm{obs}}=24^{+16}_{-13}$. The two values are not consistent
 %% with each other. There are two possible reasons for the discrepancy:
@@
 $\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
-reasonably matches the expected distribution.  This leads us to
-conclude that the uncertainty estimates in RV values were
+reasonably matches the expected distribution.  This leas us to
+conclude that the uncertainty estimates in RV values are 
 reasonable. Here, we will inspect the effect of the systematic error
@@
 autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
-negligibly small for a young VLM objects with $M_{*}<0.12\,M_{\sun}$.
+negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
 The size of RV errors caused by (2) is expected to be $<1\,\kmps$
@@
 uncertainties. Hence, we expect the systematic error to be much
-smaller than $<1\,\kmps$ if one is required.
+smaller than $1\,\kmps$ if one is required.
 
@@
 The binary fraction estimated with the assumed systematic error is
-$2/17$ or $f=12^{+13}_{-10}$~per~cent for $a<0.12$~au.
+$2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
 
@@
 %% $4$&
-%% $24^{+16}_{-14}$&
+%% $24^{+16}_{-13}$&
 %% $3.2$&
@@
 measurements are 21.6~d, and our RV survey is sensitive to binaries
-with separation smaller than 0.12~au.  One of our targets, USco~121, is
+with separation smaller than 0.1~au.  One of our targets, USco~121, is
 most likely a non-member of the UScoOB association based on the
@@
 binary/multiple candidates. This corresponds to the binary fraction of
-$24^{+16}_{-14}$~per~cent for the binary separation $a<0.12$~au.  We found
+$24^{+16}_{-13}$~per~cent for the binary separation $a<0.1$~au.  We found
 that the estimated binary fraction is very sensitive to
@@
 $a>4.0$~au which is well above our sensitivity limit of
-0.12~au; therefore, it is not surprising that we did not identify USco~66 and
+0.1~au; therefore, it is not surprising that we did not identify USco~66 and
 USco~109 as multiples. Interestingly, we also found USco~55 as a
 candidate for a multiple system. This may indicate that USco~55 is  
-a triple system with one of object located within 0.12~au from the
+a triple system with one of object located within 0.1~au from the
 primary.  In addition, we identify USco~104 as a binary candidate, but this
@@
 We thank the staff of VLT of the ESO for carrying out the observations
-in service mode. RK thank Rob Jeffries for helpful suggestions on the
-data analysis presented in this paper. This work was supported by
+in service mode. RK is grateful for Rob Jeffries for helpful suggestions on the
+data analysis presented in this paper. RK also thank Matteww Bate for
+providing us helpful comments on the manuscript. This work was supported by
 PPARC rolling grant PP/C501609/1.

### 2006-05-12 BD_radvel/kurosawa.tex
minor changes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@719 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-\author[R. Kurosawa et\,al.]{Ryuichi Kurosawa\thanks{E-mail: rk@astro.ex.ac.uk} and  Tim J.~Harries\\ School of Physics, University of Exeter, Stocker Road, Exeter EX4 4QL}
+\author[R. Kurosawa et\,al.]{Ryuichi
+  Kurosawa$^1$\thanks{E-mail:rk@astro.ex.ac.uk}, Tim J. Harries$^1$
+  and S.~P.~Littlefair$^2$\\ $^1$School of Physics, University of
+  Exeter, Stocker Road, Exeter EX4~4QL. \\ $^2$Department of Physics
+  and Astronomy, University of Sheffield, Sheffield S3 7RH}
 
@@
 lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
-while $f\approx15$~per~cent was determined by \citet{close:2003} using
+while $f\approx15$~per~cent (for the field objects with
+0.03--0.1~$\mathrm{M_{\sun}}$ and M8.0--L0.5) was  determined by
+\citet{close:2003} using   
 the adaptive optics at Gemini North. They also found the vast majority
@@
 out of $n$ trials with the probability $p$ for a positive event in each
-trial. In our case, $n=17$ (the number of sample)  and $p=4/17=0.24$
-(the fraction of binary/multiple).  The uncertainties was estimated by
-plotting $P_{B}\left ( x, 17, 0.24 \right )$, and finding the values
-of $x$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
+trial. In our case, $n=17$ (the number of sample) and $x=4$.  The peak
+of $P_{B}\left ( 4, 17, p \right )$ curve suggests the binary fraction of
+24~per~cent, as its should be ($4/17=0.24$).  The uncertainties was estimated by
+plotting $P_{B}\left ( 4, 17, p \right )$, and finding the values
+of $p$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
 analysis, we find the binary/multiple fraction along with the

### 2006-06-07 torus/amr_mod.f90
photoionization work -th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@734 25464f21-6099-402c-b30a-640f1d40d38b

@@ -4293,7 +4293,7 @@ IF ( .NOT. gridConverged ) RETURN
          split = .false.
       endif
       if (modulus(subcellCentre(thisoctal,subcell)) < 6.*grid%rinner) then
-         if (thisOctal%nDepth < 7) split = .true.
+         if (thisOctal%nDepth < 6) split = .true.
       endif
       
    case ("testamr","proto","wrshell")

### 2006-06-07 torus/grid_mod.f90

@@ -6604,9 +6604,9 @@ contains
                 value = thisOctal%rho(subcell)
                 if (thisOctal%diffusionApprox(subcell)) value = 1.
              case("ionization")
-                value = thisOctal%ionfrac(subcell,returnIonNumber("H I", grid%ion, grid%nIon))
+                value = thisOctal%ionfrac(subcell,returnIonNumber("C IV", grid%ion, grid%nIon))
              case("photocoeff")
-                value = thisOctal%photoIonCoeff(subcell,1)
+                value = thisOctal%photoIonCoeff(subcell,7)
              case("temperature")
                 value = thisOctal%temperature(subcell)
              case("chiLine")
@@ -6873,9 +6873,9 @@ contains
                 value = thisOctal%rho(subcell)
                 if (value < 1.e-20) update = .false.
              case("ionization")
-                value = thisOctal%ionfrac(subcell,returnIonNumber("H I", grid%ion, grid%nIon))
+                value = thisOctal%ionfrac(subcell,returnIonNumber("C IV", grid%ion, grid%nIon))
              case("photocoeff")
-                value = thisOctal%photoIonCoeff(subcell,1)
+                value = thisOctal%photoIonCoeff(subcell,7)
              case("temperature")
                 value = thisOctal%temperature(subcell)
                 if (value < 3.)  update = .false.

### 2006-06-07 torus/photoion_mod.f90

@@ -27,10 +27,20 @@ end type RECOMBTABLE
 
 
 type GAMMATABLE
-   integer :: ntemp
+   integer :: nGamma
+   integer :: nFreq
+   integer :: nTemp
+   real(double), pointer :: freq(:)
    real(double), pointer :: temp(:)
-   real(double), pointer :: gamma(:)
+   real(double), pointer :: gamma(:,:)
 end type GAMMATABLE
+
+
+
+  real :: heIRecombinationFit(32, 3, 3)
+  real :: heIRecombinationLambda(32)
+  real :: heIRecombinationNe(3)
+  real :: heIIrecombinationLines(3:30, 2:16)
 
 contains
 
@@ -80,24 +90,26 @@ contains
     real(double) :: hiContEmissivity, forbiddenEmissivity
     real(double) :: probNonIonizing, probHydrogen
     real(double) :: freq(1000), spectrum(1000), nuStart, nuEnd
-    integer :: nFreq
+    integer, parameter :: nFreq = 1000
     logical, save :: firsttime = .true.
     nuStart = cSpeed / (10.d4 * 1.d-8)
     nuEnd =  1.d16
 
-    nFreq = 1000
     do i = 1, nFreq
        freq(i) = log10(nuStart) + dble(i-1)/dble(nFreq-1) * (log10(nuEnd)-log10(nuStart))
        freq(i) = 10.d0**freq(i)
     enddo
 
+    call createGammaTable(HIgammaTable, 'gammaHI.dat')
 
     call createSahaMilneTables(hTable, heTable)
 
     call createRecombTable(Hrecombtable, 'e1b.d')
 
-    call createHIGammaTable(HIgammaTable)
 
+    call readHeIRecombinationLinesFit()
+
+    call readHeIIrecombination()
 
     lCore = 0.d0
     do i = 1, nSource
@@ -106,7 +118,7 @@ contains
 
     write(*,'(a,1pe12.5)') "Total souce luminosity (lsol): ",lCore/lSol
 
-    nMonte = 100000
+    nMonte = 200000
 
     nIter = 0
 
@@ -170,18 +182,21 @@ contains
                 else
                    spectrum = 1.d-30
                    call addHydrogenLymanContinuum(nFreq, freq, spectrum, thisOctal, subcell, grid)
-                   call addHigherHydrogenContinuum(nfreq, freq, spectrum, thisOctal, subcell, grid)
[…]

### 2006-06-07 torus/photon_mod.f90

@@ -52,6 +52,8 @@ module photon_mod
      logical :: resonanceLine             ! resonance line photon?
   end type PHOTON
 
+
+
 contains
 
   ! this subroutine rotates the stokes vectors of a photon - this

### 2006-06-07 BD_radvel/kurosawa.tex
minor change in acknowledgement.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@725 25464f21-6099-402c-b30a-640f1d40d38b
A new paragraph on the stellar pulsation added.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@735 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \newcommand{\Kelvin}{\mathrm{K}}
+\newcommand{\Msun}{\mathrm{M_{\odot}}}
 
@@
 up to for binaries with $a<0.1\,\mathrm{au}$, given our time
-separations and the average uncertainty ($\sim0.5\,\kmps$) in the RV
+separations and the average uncertainty ($\sim0.56\,\kmps$) in the RV
 measurements.
@@
   21.6\,\mathrm{d}$, and the average uncertainty in RV is
-  $~0.5\,\kmps$. The probability remains fairly
+  $~0.56\,\kmps$. The probability remains fairly
   constant up to $a \approx 0.1\,\mathrm{au}$, and it rapidly decreases
@@
 $2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
+
+%
+% This may be out of place =======================
+An alternative explanation for the RV variations found in the binary
+candidates above is a type of stellar pulsations found by
+\citet{palla:2005}. They studied the non-adiabatic, linear
+instability of very VLM stars and BD during the deturium burning phase
+in the core, and found unstable fundamental modes in the time-scale
+between $\sim 1$ and $\sim 5$~h for the object mass from $0.02$ and
+$0.1\,\Msun$.  By using their pulsation periods and by assuming that the
+pulsation amplitudes is 5~per~cent of the radius of the objects, we
+find that the expected RV variation can be $>6\,\kmps$.
+As mentioned in Section~\ref{sec:observation-reduction}, for each object at a
+given night, two separate spectra are obtained consecutively (with
+time separations of $\sim 0.5$~h.). Before co-adding the two spectra
+together, we have measured the RV from each spectrum to check if there
+is a large jump in the RV measurements in short
+time-scale. The shifts in the RV values in measured in the two
+consecutive spectra are found to be between $XXX$ and  $XXX\,\kmps$,
+which is much smaller than the expected RV variation based on the
+models of \citet{palla:2005}; hence, found no/little indication of the
+pulsations.
 
@@
 We thank the staff of VLT of the ESO for carrying out the observations
-in service mode. RK is grateful for Rob Jeffries for helpful suggestions on the
-data analysis presented in this paper. RK also thank Matteww Bate for
-providing us helpful comments on the manuscript. This work was supported by
-PPARC rolling grant PP/C501609/1.
+in service mode. RK is grateful for Rob Jeffries for helpful
+suggestions on the data analysis presented in this paper. RK also
+thank Matteww Bate and Tim Naylor for providing us helpful comments on
+the manuscript. This work was supported by PPARC rolling grant
+PP/C501609/1.
 

### 2006-06-07 torus/ion_mod.f90
photoion - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@736 25464f21-6099-402c-b30a-640f1d40d38b

@@ -82,7 +82,7 @@ contains
     call createIon(ionArray(nIon), 1, 1, 1.360e1) ! H I
 
     nIon = nIon + 1
-    call createIon(ionArray(nIon), 1, 0, 999.e9) ! H II
+    call createIon(ionArray(nIon), 1, 0, 1.e-10) ! H II
 
     nIon = nIon + 1
     call createIon(ionArray(nIon), 2, 2, 2.459e1) ! He I 

### 2006-06-07 torus/photoion_mod.f90

@@ -84,7 +84,7 @@ contains
 
     type(SAHAMILNETABLE) :: hTable, heTable
     type(RECOMBTABLE) :: Hrecombtable
-    type(GAMMATABLE) :: HIgammaTable
+    type(GAMMATABLE) :: gammaTableArray(3) ! H, HeI, HeII
 
     real(double) :: hRecombemissivity, hlymanContemissivity, helymanContEmissivity
     real(double) :: hiContEmissivity, forbiddenEmissivity
@@ -93,14 +93,17 @@ contains
     integer, parameter :: nFreq = 1000
     logical, save :: firsttime = .true.
     nuStart = cSpeed / (10.d4 * 1.d-8)
-    nuEnd =  1.d16
+    nuEnd =  2.d0*maxval(grid%ion(1:grid%nIon)%nuThresh)
+    write(*,*) "shortest wavelength",1.d8*cspeed/nuEnd
 
     do i = 1, nFreq
        freq(i) = log10(nuStart) + dble(i-1)/dble(nFreq-1) * (log10(nuEnd)-log10(nuStart))
        freq(i) = 10.d0**freq(i)
     enddo
 
-    call createGammaTable(HIgammaTable, 'gammaHI.dat')
+    call createGammaTable(gammaTableArray(1), 'gammaHI.dat')
+    call createGammaTable(gammaTableArray(2), 'gammaHeI.dat')
+    call createGammaTable(gammaTableArray(3), 'gammaHeII.dat')
 
     call createSahaMilneTables(hTable, heTable)
 
@@ -118,7 +121,7 @@ contains
 
     write(*,'(a,1pe12.5)') "Total souce luminosity (lsol): ",lCore/lSol
 
-    nMonte = 200000
+    nMonte = 100000
 
     nIter = 0
 
@@ -164,16 +167,6 @@ contains
                 call amrGridValues(grid%octreeRoot, octVec, foundOctal=thisOctal, foundsubcell=subcell,iLambda=iLam, &
                      lambda=real(thisLam), kappaSca=kappaScadb, kappaAbs=kappaAbsdb, grid=grid)
 
-!                call calcEmissivities(grid, thisOctal, subcell, hTable, heTable, higammatable, hRecombTable, &
-!                     hRecombemissivity, hlymanContemissivity, helymancontemissivity, hiContEmissivity, forbiddenEmissivity)
-
-!                hiContEmissivity = hiContEmissivity * fourPi
-
[…]

### 2006-06-07 torus/utils_mod.f90

@@ -201,6 +201,7 @@ contains
     REAL(double) ::  LX,LX1,LX2,LY1,LY2,GR
     if ( (x.le.0.0d0).or.(x1.le.0.0d0).or.(x2.le.0.0d0)) then
        write(*,*) 'f.up in logint_dble',x,x1,x2,y1,y2
+       do;enddo
        stop
     endif
     LX=LOG(X)

### 2006-06-12 BD_radvel/tmp.tex
Minor changes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@739 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-06-07 BD_radvel/kurosawa.tex
@@
 function. The location of the peak is determined by fitting the
-cross-correlation function by a function which consists of two gaussians 
-(with a common centre) plus a constant term. LHS~49 (Proxima Cen, M5.5) was
-chosen as the template for this purpose. The radial velocity of the
+section of the cross-correlation function around the peak by a second
+order polynomial. LHS~49 (Proxima Cen, M5.5) was
+chosen as the template for this purpose. The heliocentric radial velocity of the
 template object LHS~49 was obtained by measuring the wavelength shifts
@@
 the cross-correlation technique, but also the validity of the wavelength
-calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.8\pm0.6\,\kmps$
+calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.18\pm0.62\,\kmps$
 which is in good agreement with the Elodie radial velocity measurement
@@
 the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
-is the uncertainty of RV with respect to the template star. The
-two consecutive measurements of RVs (from same nights) are used to
-find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
-the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
-the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
+is the uncertainty of RV with respect to the template star. 
+To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
+procedure: (1)~add random gaussian deviate noise to the object spectra using the
+corresponding variance spectra, (2)~compute the cross-correlation
+curve using the spectra with added noise and the template, (3)~measure
+the RV by location the peak, (4)~repeat 1--3 for 100 times, and computes the standard
+deviation of the 100 RV values. This should provide a good estimate of
+uncertainties in RV cased by the uncertainties in the flux levels.
+%The two consecutive measurements of RVs (from same nights) are used to
+%find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
+%the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
+%the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
 Note that for finding a shift in the radial velocities from two
@@
 time-scale. The shifts in the RV values in measured in the two
-consecutive spectra are found to be between $XXX$ and  $XXX\,\kmps$,
-which is much smaller than the expected RV variation based on the
-models of \citet{palla:2005}; hence, found no/little indication of the
-pulsations.
+consecutive spectra are found to be between $0.02\pm0.10$ (USco~128)
+and  $2.04\pm1.67\,\kmps$ (USco~66), which is much smaller than the
+expected RV variation based on the models of \citet{palla:2005};
+hence, found little indication of the pulsations.
 
@@
 $4.3\times10^{-1}$\tabularnewline
-USco-~30&
+USco~130&
 $3.2\times10^{-1}$&
@@
 $4.2\times10^{-1}$&
-USco40&
+USco~40&
 $6.0\times10^{-1}$\tabularnewline

### 2006-06-12 BD_radvel/kurosawa.tex
New RV measurements. Revisions done.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@740 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-In Section~\ref{sec:observation-reduction}. we describe the observations
-and the data reduction. The results of radial velocity and rotational
-velocity ($v\,\sin i$) measurements are presented in
-Section~\ref{sec:Results}. We discuss the binary/multiplicity 
-fraction indicated by our RV survey, and compare our results with
-earlier works in Section~\ref{sec:Binary-fraction}, and give
-our conclusions in Section~\ref{sec:Conclusions}.
+In Section~\ref{sec:observation-reduction}. we describe the
+observations and the data reduction. The results of radial velocity
+and rotational velocity ($v\,\sin i$) measurements are presented in
+Section~\ref{sec:Results}. We discuss the binary/multiplicity fraction
+indicated by our RV survey in Section~\ref{sec:Binary-fraction}, and
+give our conclusions in Section~\ref{sec:Conclusions}.
 
@@
 
-\caption{Summary of known properties of the targets from literatures:
-a.~\citet{luhman:1999} (original list for $\rho$~Oph),
-b.~\citet{ardila:2000} (original list for UScoOB),
-c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003},
+\caption{Summary of known properties of the targets from literatures: a.~\citet{luhman:1999}
+(original list for $\rho$~Oph), b.~\citet{ardila:2000} (original
+list for UScoOB), c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003},
 e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}. }
@@
 
-\begin{center}
-
-\begin{tabular}{llcccc}
+\begin{center}\begin{tabular}{llcccc}
 \hline 
@@
 \hline
-\end{tabular}
-
-\end{center}
+\end{tabular}\par\end{center}
 
@@
 %==========================================
-
 \begin{table*}
 
-\caption{Summary of the observations, the heliocentric radial
-velocities ($\mathrm{RV}$) from two-epoch and the average rotational
-velocities ($v\sin i$). The uncertainties of relative radial velocities
-($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049
-and the average radial velocities ($\overline{\mathrm{RV}}$) are also
-given. }
+\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$)
+from two-epoch and the average rotational velocities ($v\sin i$).
+The uncertainties of relative radial velocities ($\sigma_{\mathrm{RRV}}$)
+with respect to the template star LHS~049 and the average radial
+velocities ($\overline{\mathrm{RV}}$) are also given. }
 
@@
 
-\begin{center}
-
-\begin{tabular}{lcrrrrr}
+\begin{center}\begin{tabular}{lcrrrrr}
 \hline 
-Object&
+0.81&
 Date&
@@
 20.7198440&
-$-6.14\pm0.84$&
-0.68&
+$-6.77\pm2.02$&
+1.96&
 &
@@
 33.7721938&
-$-5.96\pm0.60$&
-0.34&
-$-6.05\pm1.03$&
+$-6.02\pm0.85$&
+0.68&
+$-6.39\pm2.19$&
 $16.5\pm0.6$\tabularnewline
@@
 36.6712108&
-$-4.39\pm0.60$&
-0.34&
+$-4.15\pm0.63$&
+0.38&
 &
@@
 43.6683007&
-$-2.95\pm0.51$&
-0.11&
-$-3.67\pm0.79$&
+$-3.46\pm0.66$&
+0.43&
+$-3.81\pm0.91$&
 $4.4\pm1.4$\tabularnewline
@@
 20.8373504&
-$-4.83\pm0.74$&
-0.54&
+$-5.27\pm0.92$&
+0.77&
 &
@@
 35.8224052&
-$-8.43\pm0.51$&
-0.11&
-$-6.63\pm0.90$&
+$-8.19\pm0.71$&
+0.51&
+$-6.73\pm1.16$&
 $11.1\pm6.0$\tabularnewline
@@
 1.7661754&
-$-7.15\pm0.74$&
-0.54&
+$-7.34\pm0.52$&
+0.15&
 &
@@
 33.7620554&
-$-6.80\pm0.51$&
-0.11&
-$-6.98\pm0.90$&
+$-6.28\pm0.52$&
+0.15&
+$-6.81\pm0.74$&
 $34.2\pm0.5$\tabularnewline
@@
 0.9036653&
-$-7.27\pm0.93$&
-1.21&
+$-8.27\pm0.70$&
+0.50&
 &
@@
 28.7394676&
-$-5.43\pm0.74$&
-0.55&
-$-6.35\pm1.19$&
+$-7.22\pm0.63$&
+0.39&
+$-7.75\pm0.95$&
 $40.0\pm0.6$\tabularnewline
@@
 1.8422807&
-$-5.39\pm0.50$&
-0.02&
+$-6.21\pm0.50$&
+0.04&
 &
@@
 28.8141198&
-$-6.38\pm0.53$&
-0.27&
-$-6.38\pm0.73$&
+$-6.55\pm0.50$&
+0.06&
+$-6.38\pm0.71$&
 $22.9\pm0.8$\tabularnewline
@@
 1.7972634&
-$-5.32\pm0.57$&
-0.29&
+$-7.24\pm0.95$&
+0.81&
 &
@@
 28.7956003&
-$-6.41\pm0.65$&
-0.42&
-$-5.87\pm0.86$&
+$-8.38\pm1.32$&
+1.22&
+$-7.81\pm1.63$&
 $25.9\pm1.2$\tabularnewline
@@
 1.7188620&
-$-6.01\pm0.74$&
-0.55&
+$-7.07\pm0.67$&
+0.44&
 &
@@
 28.7113799&
-$-6.83\pm0.59$&
-0.31&
-$-6.42\pm0.90$&
+$-5.70\pm0.58$&
+0.30&
+$-6.38\pm0.88$&
 $18.4\pm0.4$\tabularnewline
@@
 0.8840376&
-$-6.75\pm0.67$&
-0.44&
+$-6.80\pm0.70$&
+0.50&
 &
@@
 33.6065432&
-$-9.88\pm1.94$&
-1.88&
-$-8.32\pm2.05$&
+$-6.16\pm0.78$&
+0.60&
+$-6.48\pm1.05$&
 $55.6\pm3.0$\tabularnewline
@@
 1.8179138&
-$-6.76\pm2.74$&
-2.69&
+$-7.37\pm0.67$&
+0.44&
 &
@@
 28.7752928&
-$-10.23\pm1.80$&
-1.73&
-$-8.47\pm3.28$&
+$-7.47\pm0.62$&
+0.36&
+$-7.42\pm0.91$&
 $43.7\pm3.2$\tabularnewline
@@
 0.8120734&
-$-4.22\pm0.87$&
-0.71&
+$-3.25\pm0.66$&
+0.44&
 &
@@
 28.6591660&
-$-6.07\pm0.69$&
-0.48&
-$-5.15\pm1.11$&
+$-5.03\pm0.60$&
+0.32&
+$-4.14\pm0.89$&
 $19.1\pm0.3$\tabularnewline
@@
 0.7850385&
-$-5.83\pm0.50$&
-0.02&
+$-7.05\pm0.61$&
+0.35&
 &
@@
 28.6349480&
-$-7.48\pm0.50$&
-0.06&
-$-6.66\pm0.06$&
+$-7.62\pm0.57$&
+0.27&
+$-7.33\pm0.83$&
 $16.7\pm0.4$\tabularnewline
@@
 1.7453989&
-$-4.15\pm0.52$&
-0.16&
+$-4.72\pm0.50$&
+0.07&
 &
@@
 33.6304878&
-$-4.41\pm0.50$&
-0.03&
-$-5.12\pm0.72$&
+$-4.70\pm0.51$&
+0.09&
+$-4.71\pm0.72$&
 $8.6\pm1.2$\tabularnewline
@@
 0.8552168&
-$-2.70\pm0.69$&
-0.47&
+$-2.95\pm0.50$&
+0.05&
 &
@@
 33.5826368&
-$-3.46\pm0.51$&
-0.11&
-$-3.08\pm0.86$&
+$-3.41\pm0.51$&
+0.07&
+$-3.18\pm0.71$&
 $5.8\pm1.2$\tabularnewline
@@
 20.7059408&
-$-39.47\pm0.51$&
-0.11&
+$-40.76\pm0.90$&
+0.74&
 &
@@
 28.6969641&
-$-42.43\pm0.50$&
-0.02&
-$-40.95\pm0.71$&
+$-42.48\pm0.54$&
+0.20&
+$-41.62\pm1.04$&
 $17.6\pm1.3$\tabularnewline
@@
 39.7978276&
-$-7.41\pm0.85$&
-0.69&
+$-7.03\pm0.51$&
+0.09&
 &
@@
 43.6108024&
-$-6.94\pm1.16$&
-1.05&
-$-7.18\pm1.44$&
+$-6.32\pm0.51$&
+0.10&
+$-6.68\pm0.72$&
 $3.6\pm1.1$\tabularnewline
@@
 35.7724090&
-$-4.83\pm0.54$&
-0.21&
+$-3.92\pm0.94$&
+0.80&
 &
@@
 39.8538830&
-$-4.95\pm0.74$&
-0.55&
-$-4.89\pm0.92$&
+$-3.90\pm0.67$&
+0.45&
+$-3.91\pm1.16$&
 $15.2\pm1.1$\tabularnewline
@@
 39.8268683&
-$-7.18\pm0.58$&
-0.30&
+$-6.68\pm0.53$&
+0.18&
 &
@@
 43.6391138&
-$-7.37\pm1.02$&
-0.89&
-$-7.28\pm1.17$&
+$-6.61\pm0.54$&
+0.20&
+$-6.64\pm0.76$&
 $9.1\pm0.7$\tabularnewline
 \hline
-\end{tabular}
-
-\end{center}
+\end{tabular}\par\end{center}
 
@@
 
+%\includegraphics[%
+%  clip,
+%  scale=1.3]{figures/radvel_all01.eps}
 \includegraphics[%
   clip,
-  scale=1.3]{figures/radvel_all01.eps}
+  scale=0.9]{figures/radvel_all01.eps}
 
@@
 
+%\includegraphics[%
+%  clip,
+%  scale=1.3]{figures/radvel_all02.eps}
 \includegraphics[%
   clip,
-  scale=1.3]{figures/radvel_all02.eps}
+  scale=0.9]{figures/radvel_all02.eps}
 
@@
 the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
-is the uncertainty of RV with respect to the template star. The
-two consecutive measurements of RVs (from same nights) are used to
-find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
-the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
-the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
+is the uncertainty of RV with respect to the template star. 
+To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
+procedure: (1)~add random gaussian deviate noise to the object spectra using the
+corresponding variance spectra, (2)~compute the cross-correlation
+curve using the spectra with added noise and the template, (3)~measure
+the RV by locating the peak, (4)~repeat 1--3 for 100 times, and compute the standard
+deviation of the 100 RV values. This should provide a good estimate of
+uncertainties in RVs cased by the uncertainties in the flux levels.
+We have also used an alternative method of estimating
+$\sigma_{\mathrm{RRV}}$ values as described in
+(c.f.~\citealt{joergens:2006}. The standard deviations of the mean of
+the two independent RV measurements obtained from the two consecutive
+spectra taken in the same night were assigned as the uncertainties
+($\sigma_{\mathrm{RRV}}$). Although not shown here, we found that the
+results from the two methods agree each other quite well. 
 Note that for finding a shift in the radial velocities from two
 different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
-only requires relative (with respect to a template) RV values.
+only requires the relative (with respect to a template) RV values.
 The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
-two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
-values of the objects in UScoOB are consistent with the earlier measurements
-of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.
+two epochs are also given in the same table. 
+%The $\overline{\mathrm{RV}}$
+%values of the objects in UScoOB are consistent with the earlier measurements
+%of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.
 
@@
 
-We have computed $p$ for all the objects, and have plotted the results 
+We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
+and have plotted the results  
 as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
@@
 (with small $-\log{p}$ values) occupied by the RV constant objects,
-and one on in the right-most bin (with the largest $-\log{p}$)
-occupied by the RV variable objects which have $p<10^{-3}$.  The
+and one on the right (with the large $-\log{p}$ values)
+occupied by the RV variable candidates.  The
 expected distribution of $p$ computed consistently with our
@@
 reasonable, and an additional systematic error may not be necessary in
-this analysis (but see Section~\ref{sec:Binary-fraction}). According
-to the figure, there are four objects which show significant RV
-variations out of 17 samples. They are GY~141, GY~310, USco~55, and
-USco~104, and considered as our preliminary binary/multiple
-candidates.  We will discuss the effect of the systematics error in detail, and
-list our final binary/multiple candidates in Section~\ref{sec:Binary-fraction}.
+this analysis. 
+The boundary ($p=10^{-3}$) between the RV variable and the RV
+constants seems somewhat arbitrary, but here we simply adopt the
+definition of \citet{maxted:2005}.  Based on this criteria, there are
+four objects which show significant RV variations (out of 17 samples)
+as one can see from the figure.   They are USco~112, USco~128,
+USco~40, and USco~55, and considered as our preliminary binary/multiple 
+candidates.  We will discuss the binary fraction and the expected binary
+detection probability later in Section~\ref{sec:Binary-fraction}.
 
@@
 \begin{center}
+%\includegraphics[%
+%  clip,
+%  scale=0.63]{figures/chisq_hist.eps}
 \includegraphics[%
   clip,
-  scale=0.63]{figures/chisq_hist.eps}
+  scale=0.46]{figures/chisq_hist.eps}
 \end{center}
@@
 
+%==========================================
+\begin{table}
+
+\caption{The $\chi^{2}$ probabilities ($p$) of each object being a RV constant,
+listed in ascending order of $p$. The ellipses represent the boundary
+($p=10^{-3}$) between RV constant objects and RV variable objects. }
+
+\label{tab:chisq_prob}
+
+\begin{center}\begin{tabular}{cc}
+\hline 
+obj.~ID&
+$p$\tabularnewline
+\hline 
+USco~112&
+$8.9\times10^{-8}$\tabularnewline
+USco~128&
+$1.3\times10^{-7}$\tabularnewline
+USco~40&
+$5.8\times10^{-7}$\tabularnewline
+USco~55&
+$2.4\times10^{-6}$\tabularnewline
+$\cdots$&
+$\cdots$\tabularnewline
+USco~101&
+$1.1\times10^{-3}$\tabularnewline
+GY~310&
+$1.6\times10^{-3}$\tabularnewline
+USco~67&
+$1.0\times10^{-2}$\tabularnewline
+USco~53&
+$9.8\times10^{-2}$\tabularnewline
+USco~104&
+$2.0\times10^{-1}$\tabularnewline
+GY~141&
+$2.3\times10^{-1}$\tabularnewline
+USco~75&
+$4.1\times10^{-1}$\tabularnewline
+USco~66&
+$4.4\times10^{-1}$\tabularnewline
+GY~5&
+$7.2\times10^{-1}$\tabularnewline
+USco~132&
+$7.9\times10^{-1}$\tabularnewline
+USco~100&
+$8.6\times10^{-1}$\tabularnewline
+USco~109&
+$8.6\times10^{-1}$\tabularnewline
+USco~130&
+$9.8\times10^{-1}$\tabularnewline
+\hline
+\end{tabular}\par\end{center}
+
+\end{table} %==========================================
+
 Finally, the histogram of $\overline{\mathrm{RV}}$ for the objects in UScoOB
@@
 deviation and the peak position of the radial velocity distribution
-are $1.2\,\kmps$ and $-5.9\,\kmps$ respectively. The former is very
+are $1.0\,\kmps$ and $-6.3\,\kmps$ respectively. The former is very
 similar to the standard deviation (0.9~$\kmps$) of the radial velocity
@@
 (\citealt{bate:2005}). The standard deviation of
-$\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our analysis is more
+$\overline{\mathrm{RV}}$ ($1.0\,\kmps$) found in our analysis is more
 comparable the lower stellar density model.
@@
 
+%\includegraphics[%
+%  clip,
+%  scale=0.63]{figures/radvel_hist.eps}
 \includegraphics[%
   clip,
-  scale=0.63]{figures/radvel_hist.eps}
+  scale=0.46]{figures/radvel_hist.eps}
 
@@
 a non-member). The gaussian fit (dashed) of the radial velociity
-distribution gives a standard deviation of $1.2\,\kmps$ and the peak
-position of $-5.9\,\kmps$. }
+distribution gives a standard deviation of $1.0\,\kmps$ and the peak
+position of $-6.3\,\kmps$. }
 \label{fig:vrad_histrogram}
@@
 up to for binaries with $a<0.1\,\mathrm{au}$, given our time
-separations and the average uncertainty ($\sim0.56\,\kmps$) in the RV
+separations and the average uncertainty ($\sim0.42\,\kmps$) in the RV
 measurements.
@@
   21.6\,\mathrm{d}$, and the average uncertainty in RV is
-  $~0.56\,\kmps$. The probability remains fairly
+  $~0.42\,\kmps$. The probability remains fairly
   constant up to $a \approx 0.1\,\mathrm{au}$, and it rapidly decreases
@@
 conclude that the uncertainty estimates in RV values are 
-reasonable. Here, we will inspect the effect of the systematic error
-on the observed binary fraction more closely. There are two possible
+reasonable.  There are two possible
 source of errors: (1)~the RV shifts caused by surface/atmospheric
@@
 
-The observed binary fraction is expected to be sensitive to the
-assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
-the RV shifts and the systematic errors are in the same order of
-magnitude. The number of binary detections would decrease as
-$\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
-probabilities ($p$) for each object being a RV constant object as done
-earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
-systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
-the uncertainties in the RVs of each object.  The results are
-summarised in Table~\ref{tab:prob_compare} along with the probabilities
-computed without the systematic error (as in
-Section\ref{sub:Radial-velocities}).  The number of objects with
-$p<10^{-3}$ decreases from 4 to 2 as the systematic error is
-introduced. Unfortunately, the probabilities computed with
-$\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
-below the $p=10^{-3}$ boundary value; hence, they become RV constant
-objects as the systematic error is introduced. This
-clearly demonstrates the importance of the uncertainty estimates in
-the measured RV values.  We found that the histogram of the $\chi^2$
-probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
-Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
-expected distribution of $-\log{p}$ (not shown here).  
-The binary fraction estimated with the assumed systematic error is
-$2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
-
+% The observed binary fraction is expected to be sensitive to the
+% assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
+% the RV shifts and the systematic errors are in the same order of
+% magnitude. The number of binary detections would decrease as
+% $\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
+% probabilities ($p$) for each object being a RV constant object as done
+% earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
+% systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
+% the uncertainties in the RVs of each object.  The results are
+% summarised in Table~\ref{tab:prob_compare} along with the probabilities
+% computed without the systematic error (as in
+% Section\ref{sub:Radial-velocities}).  The number of objects with
+% $p<10^{-3}$ decreases from 4 to 2 as the systematic error is
+% introduced. Unfortunately, the probabilities computed with
+% $\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
+% below the $p=10^{-3}$ boundary value; hence, they become RV constant
+% objects as the systematic error is introduced. This
+% clearly demonstrates the importance of the uncertainty estimates in
+% the measured RV values.  We found that the histogram of the $\chi^2$
+% probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
+% Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
+% expected distribution of $-\log{p}$ (not shown here).  
+% The binary fraction estimated with the assumed systematic error is
+% $2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
 %
+% %
 % This may be out of place =======================
@@
 is a large jump in the RV measurements in short
-time-scale. The shifts in the RV values in measured in the two
-consecutive spectra are found to be between $XXX$ and  $XXX\,\kmps$,
-which is much smaller than the expected RV variation based on the
-models of \citet{palla:2005}; hence, found no/little indication of the
-pulsations.
+time-scale. The size of the shifts in the RV values measured in the two
+consecutive spectra are found in between $0.02\pm0.10$ (USco~128)
+and  $2.04\pm1.67\,\kmps$ (USco~66), and the average size of the
+shifts $0.36\,\kmps$, which is much smaller than the
+expected RV variation based on the models of \citet{palla:2005};
+hence, found little indication of the pulsations in our sample.
 
@@
 
-%==========================================
-\begin{table}
-
-\caption{Comparison of the $\chi^{2}$ probability ($p$), for each object
-  being a RV constant, computed with an addition systematic error
-  $\sigma_{\mathrm{sys}}$ (right), and without (left). The objects are
-  listed in ascending order of $p$. The ellipses represent the
-  boundary ($p=10^{-3}$) between RV constant objects and RV 
-  variable objects. }
-
-\label{tab:prob_compare}
-
-\begin{center}
-\begin{tabular}{lclc}
-\hline 
-&
-$\sigma_{\mathrm{sys}}=0.0\,\kmps$&
-&
-$\sigma_{\mathrm{sys}}=0.2\,\kmps$\tabularnewline
-obj.~ID&
-$p$&
-obj.~ID&
-$p$\tabularnewline
-\hline
-USco~104&
-$4.3\times10^{-12}$&
-USco~104&
-$3.5\times10^{-6}$\tabularnewline
-GY~310&
-$1.8\times10^{-10}$&
-GY~310&
-$2.0\times10^{-5}$\tabularnewline
-GY~141&
-$1.6\times10^{-4}$&
-$\cdots$&
-$\cdots$\tabularnewline
-USco~55&
-$7.2\times10^{-4}$&
-GY~141&
-$5.8\times10^{-2}$\tabularnewline
-$\cdots$&
-$\cdots$&
-USco~55&
-$1.6\times10^{-1}$\tabularnewline
-USco~101&
-$8.9\times10^{-2}$&
-USco~130&
-$2.3\times10^{-1}$\tabularnewline
-USco~66&
-$9.2\times10^{-2}$&
-USco~132&
-$2.6\times10^{-1}$\tabularnewline
-USco~75&
-$2.8\times10^{-1}$&
-USco~101 &
-$2.8\times10^{-1}$\tabularnewline
-USco~109&
-$3.0\times10^{-1}$&
-GY~5&
-$2.8\times10^{-1}$\tabularnewline
-USco~112&
-$3.1\times10^{-1}$&
-USco~75&
-$3.9\times10^{-1}$\tabularnewline
-USco~132&
-$3.2\times10^{-1}$&
-USco~66&
-$4.3\times10^{-1}$\tabularnewline
-USco-~30&
-$3.2\times10^{-1}$&
-USco~128&
-$4.6\times10^{-1}$\tabularnewline
-GY~5&
-$3.7\times10^{-1}$&
-USco~53&
-$5.8\times10^{-1}$\tabularnewline
-USco~53 &
-$4.2\times10^{-1}$&
-USco40&
-$6.0\times10^{-1}$\tabularnewline
-USco~67&
-$4.8\times10^{-1}$&
-USco~112&
-$6.5\times10^{-1}$\tabularnewline
-USco~128&
-$5.4\times10^{-1}$&
-USco~100&
-$6.6\times10^{-1}$\tabularnewline
-USco~100&
-$6.2\times10^{-1}$&
-USco~67&
-$7.0\times10^{-1}$\tabularnewline
-USco~40&
-$7.2\times10^{-1}$&
-USco~109&
-$7.1\times10^{-1}$\tabularnewline
-\hline
-\end{tabular}
-
-\end{center}
-
-\end{table}
-%==========================================
+%% %==========================================
+%% \begin{table}
+%%
+%%
+%% \caption{Comparison of the $\chi^{2}$ probability ($p$), for each object
+%%   being a RV constant, computed with an addition systematic error
+%%   $\sigma_{\mathrm{sys}}$ (right), and without (left). The objects are
+%%   listed in ascending order of $p$. The ellipses represent the
+%%   boundary ($p=10^{-3}$) between RV constant objects and RV 
+%%   variable objects. }
+%%
+%% \label{tab:prob_compare}
+%%
+%% \begin{center}
+%% \begin{tabular}{lclc}
+%% \hline 
+%% &
+%% $\sigma_{\mathrm{sys}}=0.0\,\kmps$&
+%% &
+%% $\sigma_{\mathrm{sys}}=0.2\,\kmps$\tabularnewline
+%% obj.~ID&
+%% $p$&
+%% obj.~ID&
+%% $p$\tabularnewline
+%% \hline
+%% USco~104&
+%% $4.3\times10^{-12}$&
+%% USco~104&
+%% $3.5\times10^{-6}$\tabularnewline
+%% GY~310&
+%% $1.8\times10^{-10}$&
+%% GY~310&
+%% $2.0\times10^{-5}$\tabularnewline
+%% GY~141&
+%% $1.6\times10^{-4}$&
+%% $\cdots$&
+%% $\cdots$\tabularnewline
+%% USco~55&
+%% $7.2\times10^{-4}$&
+%% GY~141&
+%% $5.8\times10^{-2}$\tabularnewline
+%% $\cdots$&
+%% $\cdots$&
+%% USco~55&
+%% $1.6\times10^{-1}$\tabularnewline
+%% USco~101&
+%% $8.9\times10^{-2}$&
+%% USco~130&
+%% $2.3\times10^{-1}$\tabularnewline
+%% USco~66&
+%% $9.2\times10^{-2}$&
+%% USco~132&
+%% $2.6\times10^{-1}$\tabularnewline
+%% USco~75&
+%% $2.8\times10^{-1}$&
+%% USco~101 &
+%% $2.8\times10^{-1}$\tabularnewline
+%% USco~109&
+%% $3.0\times10^{-1}$&
+%% GY~5&
+%% $2.8\times10^{-1}$\tabularnewline
+%% USco~112&
+%% $3.1\times10^{-1}$&
+%% USco~75&
+%% $3.9\times10^{-1}$\tabularnewline
+%% USco~132&
+%% $3.2\times10^{-1}$&
+%% USco~66&
+%% $4.3\times10^{-1}$\tabularnewline
+%% USco~130&
+%% $3.2\times10^{-1}$&
+%% USco~128&
+%% $4.6\times10^{-1}$\tabularnewline
+%% GY~5&
+%% $3.7\times10^{-1}$&
+%% USco~53&
+%% $5.8\times10^{-1}$\tabularnewline
+%% USco~53 &
+%% $4.2\times10^{-1}$&
+%% USco~40&
+%% $6.0\times10^{-1}$\tabularnewline
+%% USco~67&
+%% $4.8\times10^{-1}$&
+%% USco~112&
+%% $6.5\times10^{-1}$\tabularnewline
+%% USco~128&
+%% $5.4\times10^{-1}$&
+%% USco~100&
+%% $6.6\times10^{-1}$\tabularnewline
+%% USco~100&
+%% $6.2\times10^{-1}$&
+%% USco~67&
+%% $7.0\times10^{-1}$\tabularnewline
+%% USco~40&
+%% $7.2\times10^{-1}$&
+%% USco~109&
+%% $7.1\times10^{-1}$\tabularnewline
+%% \hline
+%% \end{tabular} 
+%%
+%%
+%% \end{center}
+%%
+%% \end{table}
+%% %==========================================
 
@@
 
-We found 4 (GY~141, GY~310, USco~55 and USco~104) out of 17 objects as our 
+We found 4 (USco~112, USco~128, USco~40 and USco~55) out of 17 objects as our 
 binary/multiple candidates. This corresponds to the binary fraction of
-$24^{+16}_{-13}$~per~cent for the binary separation $a<0.1$~au.  We found
-that the estimated binary fraction is very sensitive to
-the assumed size of systematic error. If an additional systematic
-error of $0.2\,\kmps$  is added to the uncertainties in the RV
-measurements, we find only 2 (GY~310 and USco~104) out of 17 objects
-as our binary/multiple candidates, which corresponds to the binary
-fraction of $12^{+13}_{-10}$~per~cent.
-
+$24^{+16}_{-13}$~per~cent for the binary separation $a<0.1$~au.  
 The recent high-resolution imaging survey of brown dwarfs and very
@@
 0.1~au; therefore, it is not surprising that we did not identify USco~66 and
-USco~109 as multiples. Interestingly, we also found USco~55 as a
-candidate for a multiple system. This may indicate that USco~55 is  
-a triple system with one of object located within 0.1~au from the
-primary.  In addition, we identify USco~104 as a binary candidate, but this
-was not in their target list.  Further they found USco~67, 75, 112, 128,
-130, 132 as non-multiple, and similarly we found them as
-'non-candidates' for multiplicity.
-
-We found the RV dispersion ($1.2\,\kmps$) of the objects in UScoOB is
+USco~109 as multiples. Interestingly, we also found USco~55 as 
+a candidate for a multiple system. This may indicate that it is  
+a triple system with one of objects located within 0.1~au from the
+primary.  In addition, we identify USco~112 and 128 as binary
+candidates, but they did not find them as multiples. Further they found USco~67, 75,
+130 and 132 as non-multiple, and so did we.
+
+We found the RV dispersion ($1.0\,\kmps$) of the objects in UScoOB is
 very similar to that of the BDs and VLM stars in Chamaeleon~I (Cha~I)
@@
 We thank the staff of VLT of the ESO for carrying out the observations
-in service mode. RK is grateful for Rob Jeffries for helpful
-suggestions on the data analysis presented in this paper. RK also
-thank Matteww Bate and Tim Naylor for providing us helpful comments on
+in service mode. RK is grateful for Rob Jeffries  and Tim Naylor for helpful
+suggestions on the data analysis presented in this paper. We also
+thank Matteww Bate for providing us valuable comments on
 the manuscript. This work was supported by PPARC rolling grant

### 2006-06-12 BD_radvel/tmp.tex
New RV measurements. Revisions done.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@740 25464f21-6099-402c-b30a-640f1d40d38b

@@
-%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 1.4.1 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
-\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
+\documentclass[onecolumn,english,oneside,useAMS, usenatbib]{mn2e}
 \usepackage[T1]{fontenc}
@@
 %% Bold symbol macro for standard LaTeX users
-\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}
+\providecommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
+
+\makeatletter
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Bold symbol macro for standard LaTeX users
+
+%% Because html converters don't know tabularnewline
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
 \usepackage{times}
-\usepackage{amssymb}
 
@@
 \newcommand{\kmps}{\mathrm{km~s^{-1}}}
-\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
+\newcommand{\ion}[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
 \newcommand{\Kelvin}{\mathrm{K}}
 \newcommand{\Msun}{\mathrm{M_{\odot}}}
+
+\makeatother
 
@@
 \begin{document}
-\title[Radial and rotational velocities of young BDs and VLM stars]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core}
-
-\author[R. Kurosawa et\,al.]{Ryuichi
-  Kurosawa$^1$\thanks{E-mail:rk@astro.ex.ac.uk}, Tim J. Harries$^1$
-  and S.~P.~Littlefair$^2$\\ $^1$School of Physics, University of
-  Exeter, Stocker Road, Exeter EX4~4QL. \\ $^2$Department of Physics
-  and Astronomy, University of Sheffield, Sheffield S3 7RH}
+
+\title{{[}}
+
+\maketitle
+Radial and rotational velocities of young BDs and VLM stars]{Radial
+and rotational velocities of young brown dwarfs and very low-mass
+stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi
+cloud core}
+
+\author{{[}}
+
+R. Kurosawa et\,al.]{Ryuichi Kurosawa$^{1}$\thanks{E-mail:rk@astro.ex.ac.uk},
+Tim J. Harries$^{1}$ and S.~P.~Littlefair$^{2}$\\
+ $^{1}$School of Physics, University of Exeter, Stocker Road, Exeter
+EX4~4QL. \\
+ $^{2}$Department of Physics and Astronomy, University of Sheffield,
+Sheffield S3 7RH}
 
@@
 \pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2006}
-
-\maketitle
 
@@
 dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
-association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
-cloud core. We obtained high-resolution echelle spectra at the VLT using
-Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
-epochs for each object, and measured the shifts in their RVs to
-identify candidates for binary/multiple systems in the sample. The
-average time separation of the RV measurements is 21.6~d, and our
-survey is sensitive to the binaries with separation $<0.1$~au.  We
-found 4 out of 17 objects (or $24^{+16}_{-13}$~per~cent by fraction)
-show a significant RV change in 4--33~d time scale, and are 
-considered as binary/multiple `candidates.'  We found no double-lined
-spectroscopic binaries in our sample, based on the shape of
-cross-correlation curves. The RV dispersion of the objects in UScoOB
-is found to be very similar to that of the BD and VLM stars in
-Chamaeleon~I (Cha~). We also found the distribution of the mean
-rotational velocities ($v\,\sin i$) of the 
-UScoOB objects is similar to that of the Cha~I, but the dispersion of
-$v\,\sin i$ is much larger than that of the Cha~I objects.
+association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi
+dark cloud core. We obtained high-resolution echelle spectra at the
+VLT using Ultraviolet and Visual Echelle Spectrograph (UVES) at two
+different epochs for each object, and measured the shifts in their
+RVs to identify candidates for binary/multiple systems in the sample.
+The average time separation of the RV measurements is 21.6~d, and
+our survey is sensitive to the binaries with separation $<0.1$~au.
+We found 4 out of 17 objects (or $24_{-13}^{+16}$~per~cent by fraction)
+show a significant RV change in 4--33~d time scale, and are considered
+as binary/multiple `candidates.' We found no double-lined spectroscopic
+binaries in our sample, based on the shape of cross-correlation curves.
+The RV dispersion of the objects in UScoOB is found to be very similar
+to that of the BD and VLM stars in Chamaeleon~I (Cha~). We also
+found the distribution of the mean rotational velocities ($v\,\sin i$)
+of the UScoOB objects is similar to that of the Cha~I, but the dispersion
+of $v\,\sin i$ is much larger than that of the Cha~I objects.
 
@@
 
-\begin{keywords}
-stars: binaries:spectroscopic -- stars: low-mass, brown dwarfs -- stars: formation -- stars:planetary system: formation
+\begin{keywords} stars: binaries:spectroscopic -- stars: low-mass,
+brown dwarfs -- stars: formation -- stars:planetary system: formation
 \end{keywords}
@@
 
-Most stars are member of binary systems and it is therefore important that
-a complete star formation theory be able to predict the binary fraction,
-period distribution, and mass-ratio distribution of  stellar
+Most stars are member of binary systems and it is therefore important
+that a complete star formation theory be able to predict the binary
+fraction, period distribution, and mass-ratio distribution of stellar
 objects across a wide range of masses. Furthermore, the study of individual
-binary systems is the only direct means to determine fundamental
-stellar properties such as stellar masses and radii.
-
-Recent high-resolution imaging studies of brown dwarfs (BDs)
-and very low-mass (VLM) stars have placed strong constraints on binaries
-with separations of $\sim1-100\,\mathrm{au}$. For example, Hubble
-Space Telescope (\emph{HST}) observations of $\alpha$~Per and the
-Pleiades indicates a binary fraction ($f$) of $>10$~per~cent with
-a bias towards separations ($a$) of less than $15$~au, and a mass-ratio
+binary systems is the only direct means to determine fundamental stellar
+properties such as stellar masses and radii.
+
+Recent high-resolution imaging studies of brown dwarfs (BDs) and very
+low-mass (VLM) stars have placed strong constraints on binaries with
+separations of $\sim1-100\,\mathrm{au}$. For example, Hubble Space
+Telescope (\emph{HST}) observations of $\alpha$~Per and the Pleiades
+indicates a binary fraction ($f$) of $>10$~per~cent with a bias
+towards separations ($a$) of less than $15$~au, and a mass-ratio
 ($q$) of $>0.7$ \citep{martin:2003} for objects around and below
@@
 lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
-while $f\approx15$~per~cent (for the field objects with
-0.03--0.1~$\mathrm{M_{\sun}}$ and M8.0--L0.5) was  determined by
-\citet{close:2003} using   
-the adaptive optics at Gemini North. They also found the vast majority
-of systems have a semimajor axis $<20\,\mathrm{au}$ (see also
-\citealt{siegler:2005} but \citealt{luhman:2004}). An
-\emph{HST} study of more than 80 field late M and L dwarfs \citep{gizis:2003}
-indicated $f\approx15$~per~cent with separations in the range of 1.6--16~au.
-For a small (12) sample of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
-in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
-$f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
-by using a similar imaging technique. More recently,
-\citet{basri:2006}, combined with the results of earlier works, found
-the upper limit of the overall binary fraction for VLM stars of
-$26\pm10$~per~cent.
-
-Using a Monte Carlo simulation, the data from radial velocity
-surveys available in the literature, and by carefully considering the sensitivity
+while $f\approx15$~per~cent (for the field objects with 0.03--0.1~$\mathrm{M_{\sun}}$
+and M8.0--L0.5) was determined by \citet{close:2003} using the adaptive
+optics at Gemini North. They also found the vast majority of systems
+have a semimajor axis $<20\,\mathrm{au}$ (see also \citealt{siegler:2005}
+but \citealt{luhman:2004}). An \emph{HST} study of more than 80 field
+late M and L dwarfs \citep{gizis:2003} indicated $f\approx15$~per~cent
+with separations in the range of 1.6--16~au. For a small (12) sample
+of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$) in Upper Scorpius
+OB association (UScoOB), \citet{kraus:2005} found $f=25_{-8}^{+16}$~per~cent
+for $5\,\mathrm{au}<a<18\,\mathrm{au}$ by using a similar imaging
+technique. More recently, \citet{basri:2006}, combined with the results
+of earlier works, found the upper limit of the overall binary fraction
+for VLM stars of $26\pm10$~per~cent.
+
+Using a Monte Carlo simulation, the data from radial velocity surveys
+available in the literature, and by carefully considering the sensitivity
 and sampling biases, \citet{maxted:2005} found an overall BD/VLM
@@
 status of BD/VLM binary fraction and the separation distribution,
-readers are refer to a recent review of multiplicity studies
-by \cite{burgasser:2006}.
+readers are refer to a recent review of multiplicity studies by \cite{burgasser:2006}.
 
@@
 Note that the median separation of binaries with solar-type primaries
-is 30~au \citep{duquennoy:1991}. Pioneering works on the RVs
-of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
+is 30~au \citep{duquennoy:1991}. Pioneering works on the RVs of
+BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
 and \citet{joergens:2006} who found a several binary candidates;
-however, the orbital parameters and masses of binaries remains
-unknown because the follow-up spectroscopic monitoring is lacking
-or still being undertaken. In addition to the follow-up observations,
-the number of BDs and VLM star binary candidates needs to be increased
-in order to have better statistics on short-period binary parameters.
-
-The first BD+BD eclipsing binary (2MASS J0532184--J0546085) was
-discovered by \citet*{stassun:2006} from the $I$-band photometric
-monitoring of the system. Combining their light curves and the results
-from the follow-up radial velocity measurements, they were able to determined
+however, the orbital parameters and masses of binaries remains unknown
+because the follow-up spectroscopic monitoring is lacking or still
+being undertaken. In addition to the follow-up observations, the number
+of BDs and VLM star binary candidates needs to be increased in order
+to have better statistics on short-period binary parameters.
+
+The first BD+BD eclipsing binary (2MASS J0532184--J0546085) was discovered
+by \citet*{stassun:2006} from the $I$-band photometric monitoring
+of the system. Combining their light curves and the results from the
+follow-up radial velocity measurements, they were able to determined
 the precise oribital and physical parameters of the system. The projected
-semimajor axis and the period of the binary are found as
-$0.0398\pm0.0010$~au and $9.779621\pm0.000042$~d respectively.
-
-The separation distribution of BD/VLM binaries is critical to
-understanding their origin. There are two main models for the
-formation of BDs and VLM stars: first, they have low masses because
-they form in low-mass, dense molecular cloud cores
-(e.g.~\citealt{padoan:2002}); second, BD/VLM objects have low masses
-because they are ejected from the dense core in which they form via
-dynamical interactions in multiple system, cutting off their accretion
-before they have reached stellar masses (\citealt{reipurth:2001};
-\citealt*{bate:2002}). Alternatively, there is a third model in which
-a free-floating BD or planetary-mass object can be formed in the
-process of the photo-evaporation
-(e.g.~\citealt{mccaughrean:2002};~\citealt{whitworth:2004}) with  
-the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
+semimajor axis and the period of the binary are found as $0.0398\pm0.0010$~au
+and $9.779621\pm0.000042$~d respectively.
+
+The separation distribution of BD/VLM binaries is critical to understanding
+their origin. There are two main models for the formation of BDs and
+VLM stars: first, they have low masses because they form in low-mass,
+dense molecular cloud cores (e.g.~\citealt{padoan:2002}); second,
+BD/VLM objects have low masses because they are ejected from the dense
+core in which they form via dynamical interactions in multiple system,
+cutting off their accretion before they have reached stellar masses
+(\citealt{reipurth:2001}; \citealt*{bate:2002}). Alternatively,
+there is a third model in which a free-floating BD or planetary-mass
+object can be formed in the process of the photo-evaporation (e.g.~\citealt{mccaughrean:2002};~\citealt{whitworth:2004})
+with the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
 removed by the strong radiation pressure from the nearby massive OB
@@
 without also finding many with separation $<1$~au. If an absence/rarity
-of binaries with 1~au were found, it may support the idea that
-they are ejected quickly from multiple systems before they have undergone
+of binaries with 1~au were found, it may support the idea that they
+are ejected quickly from multiple systems before they have undergone
 the interactions that shorten their periods.
@@
 and the data reduction. The results of radial velocity and rotational
-velocity ($v\,\sin i$) measurements are presented in
-Section~\ref{sec:Results}. We discuss the binary/multiplicity 
-fraction indicated by our RV survey, and compare our results with
-earlier works in Section~\ref{sec:Binary-fraction}, and give
-our conclusions in Section~\ref{sec:Conclusions}.
+velocity ($v\,\sin i$) measurements are presented in Section~\ref{sec:Results}.
+We discuss the binary/multiplicity fraction indicated by our RV survey,
+and compare our results with earlier works in Section~\ref{sec:Binary-fraction},
+and give our conclusions in Section~\ref{sec:Conclusions}.
 
@@
 
-Our sample consists of 18 young, very low-mass objects: 15 objects in
-the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$,
-\citealt{dezeeuw:1999}) from the list of \citet{ardila:2000} and 3
-objects in the $\rho$~Ophiuchi cloud core ($\mathrm{d\approx150\,
-pc}$, \citealt{dezeeuw:1997}) from \citet{luhman:1999}. The spectral
-type of the objects range between M5 and M8.5, and the age
-$<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999}; \citealt{ardila:2000};
-\citealt{muzerolle:2003}; \citealt{kraus:2005}).  The sample is not
-complete, and the selection was solely based on brightness and the
-observability. The basic properties of the targets based on the
-literature is summarised in Table~\ref{tab:literatures}.
+Our sample consists of 18 young, very low-mass objects: 15 objects
+in the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$,
+\citealt{dezeeuw:1999}) from the list of \citet{ardila:2000} and
+3 objects in the $\rho$~Ophiuchi cloud core ($\mathrm{d\approx150\, pc}$,
+\citealt{dezeeuw:1997}) from \citet{luhman:1999}. The spectral type
+of the objects range between M5 and M8.5, and the age $<\sim10\,\mathrm{Myr}$
+(\citealt{luhman:1999}; \citealt{ardila:2000}; \citealt{muzerolle:2003};
+\citealt{kraus:2005}). The sample is not complete, and the selection
+was solely based on brightness and the observability. The basic properties
+of the targets based on the literature is summarised in Table~\ref{tab:literatures}.
 
 We obtained high-resolution spectra with the Kueyen telescope of VLT
-(Cerro Parnal, Chile) using the UVES echelle spectrograph. The
-observations were carried out between 2004 April 5 and 2004 May 17 in
-the service mode. For each object, spectra were obtained at two different
-epochs separated by 4--33~d. For each object at a
-given night, two separate spectra are obtained consecutively. This
-allows us to derive more reliable uncertainty estimates in the RV
-values of our targets (c.f.~\citealt{joergens:2006}).  The data were
-obtained using the red arm of UVES spectrograph with two mosaic CCDs
-(EEV + MIT/LL with 2k$\times$4k pixels). The wavelength coverage of
-6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$ were
-used. The slit width and length of 1'' and 12'' were used respectively
+(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
+were carried out between 2004 April 5 and 2004 May 17 in the service
+mode. For each object, spectra were obtained at two different epochs
+separated by 4--33~d. For each object at a given night, two separate
+spectra are obtained consecutively. This allows us to derive more
+reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
+The data were obtained using the red arm of UVES spectrograph with
+two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
+coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
+were used. The slit width and length of 1'' and 12'' were used respectively
 with a typical seeing of 0.8''.
@@
 
-\caption{Summary of the observations, the heliocentric radial
-velocities ($\mathrm{RV}$) from two-epoch and the average rotational
-velocities ($v\sin i$). The uncertainties of relative radial velocities
-($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049
-and the average radial velocities ($\overline{\mathrm{RV}}$) are also
-given. }
+\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$)
+from two-epoch and the average rotational velocities ($v\sin i$).
+The uncertainties of relative radial velocities ($\sigma_{\mathrm{RRV}}$)
+with respect to the template star LHS~049 and the average radial
+velocities ($\overline{\mathrm{RV}}$) are also given. }
 
@@
 
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=1.3]{figures/radvel_all01.eps}
-
-\end{center}
-
-\caption{Relative radial velocities (RVs) of objects measured in two
-different epochs. The vertical axes indicate the amount of deviation
-($\Delta \mathrm{RV}$) from the `average' radial velocity
-($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and
-the horizontal axes indicate the time of the observation in
-heliocentric Julian date (HJD). The objects are considered to have a
-non-constant RV when the error bars of two data points do not overlap
-each other. The non-constant RV objects are considered as
-binary/multiple candidates.}
+\begin{center}\includegraphics[clip,scale=1.3]{figures/radvel_all01}\par\end{center}
+
+\caption{Relative radial velocities (RVs) of objects measured in two different
+epochs. The vertical axes indicate the amount of deviation ($\Delta\mathrm{RV}$)
+from the `average' radial velocity ($\overline{\mathrm{RV}}$) in
+Table~\ref{tab:summary_results}), and the horizontal axes indicate
+the time of the observation in heliocentric Julian date (HJD). The
+objects are considered to have a non-constant RV when the error bars
+of two data points do not overlap each other. The non-constant RV
+objects are considered as binary/multiple candidates.}
 
@@
 
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=1.3]{figures/radvel_all02.eps}
-
-\end{center}
+\begin{center}\includegraphics[clip,scale=1.3]{figures/radvel_all02}\par\end{center}
 
@@
 
-The radial velocities of each object were determined by using the cross-correlation
-function of the object spectrum with that of a template star which has
-a similar spectra type. By visual inspection,
-the wavelength ranges used for the cross-correlation calculations
-are chosen by avoiding the regions of spectra affected by the telluric
-lines, and defects and fringes (in near infrared) of the CCDs. The
-radial velocities of objects with respect to the template are obtained
-by measuring the location of the peak in the cross-correlation
-function. The location of the peak is determined by fitting the
-section of the cross-correlation function around the peak by a second
-order polynomial. LHS~49 (Proxima Cen, M5.5) was
-chosen as the template for this purpose. The heliocentric radial velocity of the
-template object LHS~49 was obtained by measuring the wavelength shifts
-of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
-This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
-in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
-who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
-RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
+The radial velocities of each object were determined by using the
+cross-correlation function of the object spectrum with that of a template
+star which has a similar spectra type. By visual inspection, the wavelength
+ranges used for the cross-correlation calculations are chosen by avoiding
+the regions of spectra affected by the telluric lines, and defects
+and fringes (in near infrared) of the CCDs. The radial velocities
+of objects with respect to the template are obtained by measuring
+the location of the peak in the cross-correlation function. The location
+of the peak is determined by fitting the section of the cross-correlation
+function around the peak by a second order polynomial. LHS~49 (Proxima
+Cen, M5.5) was chosen as the template for this purpose. The heliocentric
+radial velocity of the template object LHS~49 was obtained by measuring
+the wavelength shifts of the prominent photospheric absorption features
+\ion{K}{i}~$\lambda\lambda$7664.911,~7698.974. This gives us
+$\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is in good agreement
+with the earlier measurement of \citet{garcia-sanchez:2001} who found
+$\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric RV of
+each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
 with the RV of each object with respect to LHS~49. In the following
@@
 the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
-is the uncertainty of RV with respect to the template star. 
-To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
-procedure: (1)~add random gaussian deviate noise to the object spectra using the
-corresponding variance spectra, (2)~compute the cross-correlation
+is the uncertainty of RV with respect to the template star. To determine
+the $\sigma_{\mathrm{RRV}}$, we have used the following procedure:
+(1)~add random gaussian deviate noise to the object spectra using
+the corresponding variance spectra, (2)~compute the cross-correlation
 curve using the spectra with added noise and the template, (3)~measure
-the RV by location the peak, (4)~repeat 1--3 for 100 times, and computes the standard
-deviation of the 100 RV values. This should provide a good estimate of
-uncertainties in RV cased by the uncertainties in the flux levels.
-%The two consecutive measurements of RVs (from same nights) are used to
+the RV by location the peak, (4)~repeat 1--3 for 100 times, and computes
+the standard deviation of the 100 RV values. This should provide a
+good estimate of uncertainties in RV cased by the uncertainties in
+the flux levels. %The two consecutive measurements of RVs (from same nights) are used to
 %find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
@@
 %the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
-Note that for finding a shift in the radial velocities from two
-different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
-only requires relative (with respect to a template) RV values.
-The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
-two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
+Note that for finding a shift in the radial velocities from two different
+epochs, only $\sigma_{\mathrm{RRV}}$ is important since one only
+requires relative (with respect to a template) RV values. The `average'
+radial velocities $\left(\overline{\mathrm{RV}}\right)$ of the two
+epochs are also given in the same table. The $\overline{\mathrm{RV}}$
 values of the objects in UScoOB are consistent with the earlier measurements
@@
 computing $\Delta\mathrm{RV}$ we do not require the knowledge of
-absolute radial velocities, but only the relative
-velocities (with respect to a template). 
-Alternatively, we also computed the cross-correlation functions of
-spectra of a same object (instead of using the spectra of the template
-LHS~49) from two different epochs in order to find
+absolute radial velocities, but only the relative velocities (with
+respect to a template). Alternatively, we also computed the cross-correlation
+functions of spectra of a same object (instead of using the spectra
+of the template LHS~49) from two different epochs in order to find
 $\Delta\mathrm{RV}$. The resulting cross-correlation functions were
@@
 
-To identify an object with a RV variation with a statistical
-significance from our sample, we apply the method described by
-\citet{maxted:2005}, which we briefly summarize next, to our data.
-There are three steps in this method: 
-(1)~compute the $\chi^{2}$ by fitting the two-epoch RV data for each 
-object with a constant function (a zero-th order polynomial),
-(2)~compute the corresponding $\chi^{2}$ probability ($p$),
-(3)~designate the object as a non-constant RV object or a binary
-candidate if $p<10^{-3}$ (1~per~cent).  When computing $\chi^{2}$, we
-use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$). 
+To identify an object with a RV variation with a statistical significance
+from our sample, we apply the method described by \citet{maxted:2005},
+which we briefly summarize next, to our data. There are three steps
+in this method: (1)~compute the $\chi^{2}$ by fitting the two-epoch
+RV data for each object with a constant function (a zero-th order
+polynomial), (2)~compute the corresponding $\chi^{2}$ probability
+($p$), (3)~designate the object as a non-constant RV object or a
+binary candidate if $p<10^{-3}$ (1~per~cent). When computing $\chi^{2}$,
+we use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$).
 The number of degree of freedom in the fitting procedure is obviously
@@
 as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
-(excluding the non-member USco~121; see explanation later). 
-The figure clearly shows two distinctive populations: one on the left
-(with small $-\log{p}$ values) occupied by the RV constant objects,
-and one on in the right-most bin (with the largest $-\log{p}$)
-occupied by the RV variable objects which have $p<10^{-3}$.  The
-expected distribution of $p$ computed consistently with our
-uncertainty measurements is also shown in the same figure. The RV
-constant population on the left side reasonably matches the expected
-curve. This reassures that our uncertainties in RV values are
-reasonable, and an additional systematic error may not be necessary in
-this analysis (but see Section~\ref{sec:Binary-fraction}). According
-to the figure, there are four objects which show significant RV
-variations out of 17 samples. They are GY~141, GY~310, USco~55, and
-USco~104, and considered as our preliminary binary/multiple
-candidates.  We will discuss the effect of the systematics error in detail, and
+(excluding the non-member USco~121; see explanation later). The figure
+clearly shows two distinctive populations: one on the left (with small
+$-\log{p}$ values) occupied by the RV constant objects, and one on
+in the right-most bin (with the largest $-\log{p}$) occupied by the
+RV variable objects which have $p<10^{-3}$. The expected distribution
+of $p$ computed consistently with our uncertainty measurements is
+also shown in the same figure. The RV constant population on the left
+side reasonably matches the expected curve. This reassures that our
+uncertainties in RV values are reasonable, and an additional systematic
+error may not be necessary in this analysis (but see Section~\ref{sec:Binary-fraction}).
+According to the figure, there are four objects which show significant
+RV variations out of 17 samples. They are GY~141, GY~310, USco~55,
+and USco~104, and considered as our preliminary binary/multiple candidates.
+We will discuss the effect of the systematics error in detail, and
 list our final binary/multiple candidates in Section~\ref{sec:Binary-fraction}.
@@
 
-\begin{center}
-\includegraphics[%
-  clip,
-  scale=0.63]{figures/chisq_hist.eps}
-\end{center}
-
-\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
-  observed (relative) RV values with a constant (a horizontal
-  line). The constant used in the fit is determined from the weighted mean of
-  the two RV measurements for each object.  The objects with
-  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
-  which appear in the right-most bin in the histogram. There
-  are four objects which satisfy this condition. The
-  expected distribution (dashed) for RV constant objects based on the RV
-  uncertainties in the observations (Table~\ref{tab:summary_results})
-  and based on the $\chi^{2}$ probability function is also shown for a
-  comparison.  The match between the expected distribution and the
+\begin{center}\includegraphics[clip,scale=0.63]{figures/chisq_hist} \par\end{center}
+
+\caption{Histogram of the $\chi^{2}$ probability ($p$) for fitting the observed
+(relative) RV values with a constant (a horizontal line). The constant
+used in the fit is determined from the weighted mean of the two RV
+measurements for each object. The objects with $p<10^{-3}$ are identified
+as \emph{non-constant} or \emph{multiple}, which appear in the right-most
+bin in the histogram. There are four objects which satisfy this condition.
+The expected distribution (dashed) for RV constant objects based on
+the RV uncertainties in the observations (Table~\ref{tab:summary_results})
+and based on the $\chi^{2}$ probability function is also shown for
+a comparison. The match between the expected distribution and the
 histogram is reasonable, indicating that our uncertainty estimates
@@
 
-Finally, the histogram of $\overline{\mathrm{RV}}$ for the objects in UScoOB
-is given in Fig.~\ref{fig:vrad_histrogram}. The total number
-of the objects is 14. Note that USco~121 is excluded from the graph
-since it is identified as a non-member of the UScoOB association based
-on the RV value (see Table~\ref{tab:summary_results}).  \citet{muzerolle:2003}
+Finally, the histogram of $\overline{\mathrm{RV}}$ for the objects
+in UScoOB is given in Fig.~\ref{fig:vrad_histrogram}. The total
+number of the objects is 14. Note that USco~121 is excluded from
+the graph since it is identified as a non-member of the UScoOB association
+based on the RV value (see Table~\ref{tab:summary_results}). \citet{muzerolle:2003}
 also found it to be a likely non-member based on the radial velocity
@@
 According to the hydrodynamical simulations of a low-mass star-forming
-cluster of \cite{bate:2003} which yields a stellar density of
-$\sim10^{3}\,\mathrm{stars\, pc^{-3}}$, the rms dispersion (1-D)
-of the stars and the BDs is $1.2\,\kmps$.  Similarly for the model
-with a higher stellar density ($\sim10^{4}\,\mathrm{stars\,
-pc^{-3}}$), the rms dispersion is 2.5~$\kmps$
-(\citealt{bate:2005}). The standard deviation of
-$\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our analysis is more
-comparable the lower stellar density model.
+cluster of \cite{bate:2003} which yields a stellar density of $\sim10^{3}\,\mathrm{stars\, pc^{-3}}$,
+the rms dispersion (1-D) of the stars and the BDs is $1.2\,\kmps$.
+Similarly for the model with a higher stellar density ($\sim10^{4}\,\mathrm{stars\, pc^{-3}}$),
+the rms dispersion is 2.5~$\kmps$ (\citealt{bate:2005}). The standard
+deviation of $\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our
+analysis is more comparable the lower stellar density model.
 
@@
 
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.63]{figures/radvel_hist.eps}
-
-\end{center}
-
-\caption{Histogram of the average heliocentric radial velocities of 14 UScoOB BD and VLM
-objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
-a non-member). The gaussian fit (dashed) of the radial velociity
-distribution gives a standard deviation of $1.2\,\kmps$ and the peak
-position of $-5.9\,\kmps$. }
+\begin{center}\includegraphics[clip,scale=0.63]{figures/radvel_hist}\par\end{center}
+
+\caption{Histogram of the average heliocentric radial velocities of 14 UScoOB
+BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding
+USco~121, a non-member). The gaussian fit (dashed) of the radial
+velociity distribution gives a standard deviation of $1.2\,\kmps$
+and the peak position of $-5.9\,\kmps$. }
+
 \label{fig:vrad_histrogram}
@@
 The rotational velocities of the objects were determined by measuring
-the widths of the cross correlation functions of the target spectra against
-a template spectrum from an object which is known to have a very small
-rotational velocity. The line broadening of the targets is assumed
-to be dominated by rotational broadening. As in the cases for the
-radial velocity measurements, LHS~49 is chosen as the template.
+the widths of the cross correlation functions of the target spectra
+against a template spectrum from an object which is known to have
+a very small rotational velocity. The line broadening of the targets
+is assumed to be dominated by rotational broadening. As in the cases
+for the radial velocity measurements, LHS~49 is chosen as the template.
 Using its rotational period ($P\approx83\,\mathrm{d}$, \citealt{benedict:1998})
@@
 correlating the template spectra against the same template spectra
-with added rotation (convolved with a given $v\,\sin i$), as
-done by e.g.~\citet{tinney:1998}, \citet{mohanty:2003} and \citet{white:2003}.
+with added rotation (convolved with a given $v\,\sin i$), as done
+by e.g.~\citet{tinney:1998}, \citet{mohanty:2003} and \citet{white:2003}.
 A linear limb-darkening law with a solar-like parameter ($\epsilon=0.6$)
@@
 of rotational velocities are computed from two independent spectra
-obtained at different epochs. As for the RV measurements,
-the mean and the standard deviation of the mean are used as the final
-rotational velocity and its uncertainty. The final results are recorded
-in Table~\ref{tab:summary_results}. In general, our measurements
-are in good agreement with the earlier measurements of \citet{muzerolle:2003}
-and \citet{mohanty:2005}, given in Table~\ref{tab:literatures}.
-For example, \citet{muzerolle:2003} found $v\,\sin i=16.8\pm2.7\,\mathrm{km\, s^{-1}}$
-for GY~5 while we found $v\,\sin i=16.5\pm0.6\,\mathrm{km\, s^{-1}}$.
+obtained at different epochs. As for the RV measurements, the mean
+and the standard deviation of the mean are used as the final rotational
+velocity and its uncertainty. The final results are recorded in Table~\ref{tab:summary_results}.
+In general, our measurements are in good agreement with the earlier
+measurements of \citet{muzerolle:2003} and \citet{mohanty:2005},
+given in Table~\ref{tab:literatures}. For example, \citet{muzerolle:2003}
+found $v\,\sin i=16.8\pm2.7\,\mathrm{km\, s^{-1}}$ for GY~5 while
+we found $v\,\sin i=16.5\pm0.6\,\mathrm{km\, s^{-1}}$.
 
 The range of $v\,\sin i$ found among our objects is $3.6$--$55.6\,\kmps$,
-and a similar range is also found by \citet{mohanty:2005}. 
-Fig.~\ref{fig:vrot_histrogram} shows the histogram
-of $v\,\sin i$ distribution for the UScoOB objects (14 objects excluding
-USco 121, non member). The log-normal fit of this distribution gives
-the peak position at $16.9\,\kmps$ with a standard deviation $\sigma=27.8\,\kmps$.
-Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
-bin size used for UScoOB obects and a log-normal fit, we find the
-$v\,\sin i$ distribution of the BD and VLM stars (8 objects) in Cha~I
-peaks at $15.4\,\kmps$, and has the standard deviation of $8.0\,\kmps$.
-The peak of the distribution is similar to that of Upper Sco objects,
-but the standard deviation of the distribution is much smaller
-than that of our Upper Sco objects. The difference maybe due to the
-very small sample. A similar fit was applied to the $v\,\sin i$
-distribution of 14 higher mass T~Tauri stars in Cha~I using the data
-of \citet{joergens:2001}, and we found a peak at $17.0\,\kmps$ with a
-standard deviation $25.9\,\kmps$ which are very similar to those of
-the Upper Sco brown dwarf candidates and VLM stars.
+and a similar range is also found by \citet{mohanty:2005}. Fig.~\ref{fig:vrot_histrogram}
+shows the histogram of $v\,\sin i$ distribution for the UScoOB objects
+(14 objects excluding USco 121, non member). The log-normal fit of
+this distribution gives the peak position at $16.9\,\kmps$ with a
+standard deviation $\sigma=27.8\,\kmps$. Using the $v\,\sin i$ data
+in \citet{joergens:2001}, the same histogram bin size used for UScoOB
+obects and a log-normal fit, we find the $v\,\sin i$ distribution
+of the BD and VLM stars (8 objects) in Cha~I peaks at $15.4\,\kmps$,
+and has the standard deviation of $8.0\,\kmps$. The peak of the distribution
+is similar to that of Upper Sco objects, but the standard deviation
+of the distribution is much smaller than that of our Upper Sco objects.
+The difference maybe due to the very small sample. A similar fit was
+applied to the $v\,\sin i$ distribution of 14 higher mass T~Tauri
+stars in Cha~I using the data of \citet{joergens:2001}, and we found
+a peak at $17.0\,\kmps$ with a standard deviation $25.9\,\kmps$
+which are very similar to those of the Upper Sco brown dwarf candidates
+and VLM stars.
 
@@
 
-\begin{center}
-
-\includegraphics[%
-  clip,
-  scale=0.63]{figures/vrot_hist.eps}
-
-\end{center}
-
-\caption{Histogram of the rotational velocities ($v\,\sin{i}$) of 14 UScoOB BD and VLM
-objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
-a non-member).  The log-normal fit (dashed) of the
-rotational velocity distribution gives a standard deviation
-$27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
+\begin{center}\includegraphics[clip,scale=0.63]{figures/vrot_hist}\par\end{center}
+
+\caption{Histogram of the rotational velocities ($v\,\sin{i}$) of 14 UScoOB
+BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding
+USco~121, a non-member). The log-normal fit (dashed) of the rotational
+velocity distribution gives a standard deviation $27.8\,\kmps$ and
+the peak poistion $16.9\,\kmps$.}
+
 \label{fig:vrot_histrogram}
 
-\end{figure}
-%==========================================
+\end{figure} %==========================================
 
 \section{Binary fraction}
+
 \label{sec:Binary-fraction}
 
-In Section~\ref{sub:Radial-velocities}, we found 4 out of 17
-(excluding USco~121; non-member) objects show a statistically
-significant RV variation, indicating that they are binary/multiple
-candidates. In order to estimate the uncertainty in the
-binary/multiple fraction from this relatively small sample, we will
-follow the method used by \citet{basri:2006} who considered the binomial
-distribution, $P_{B}\left ( x, n, p \right )$ of $x$ positive event
-out of $n$ trials with the probability $p$ for a positive event in each
-trial. In our case, $n=17$ (the number of sample) and $x=4$.  The peak
-of $P_{B}\left ( 4, 17, p \right )$ curve suggests the binary fraction of
-24~per~cent, as its should be ($4/17=0.24$).  The uncertainties was estimated by
-plotting $P_{B}\left ( 4, 17, p \right )$, and finding the values
-of $p$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
-analysis, we find the binary/multiple fraction along with the
-uncertainties of our sample to be $f=24^{+16}_{-13}$~per~cent.
-
-Next, we investigate the range of semimajor axes of binaries
-(equivalently the range of binary periods) to which our RV survey is
-sensitive. For this purpose, we will consider the detection
-probability for binaries or the RV variables, given the time
-separations of two-epoch observations and the ranges of estimated
-primary masses (c.f.~Tables~\ref{tab:literatures} and
-\ref{tab:summary_results}).  The probability is calculated based
+In Section~\ref{sub:Radial-velocities}, we found 4 out of 17 (excluding
+USco~121; non-member) objects show a statistically significant RV
+variation, indicating that they are binary/multiple candidates. In
+order to estimate the uncertainty in the binary/multiple fraction
+from this relatively small sample, we will follow the method used
+by \citet{basri:2006} who considered the binomial distribution, $P_{B}\left(x,n,p\right)$
+of $x$ positive event out of $n$ trials with the probability $p$
+for a positive event in each trial. In our case, $n=17$ (the number
+of sample) and $x=4$. The peak of $P_{B}\left(4,17,p\right)$ curve
+suggests the binary fraction of 24~per~cent, as its should be ($4/17=0.24$).
+The uncertainties was estimated by plotting $P_{B}\left(4,17,p\right)$,
+and finding the values of $p$ at which $P_{B}$ reduced to $e^{-1}$
+of the peak value. In this analysis, we find the binary/multiple fraction
+along with the uncertainties of our sample to be $f=24_{-13}^{+16}$~per~cent.
+
+Next, we investigate the range of semimajor axes of binaries (equivalently
+the range of binary periods) to which our RV survey is sensitive.
+For this purpose, we will consider the detection probability for binaries
+or the RV variables, given the time separations of two-epoch observations
+and the ranges of estimated primary masses (c.f.~Tables~\ref{tab:literatures}
+and \ref{tab:summary_results}). The probability is calculated based
 on the simulated RV observations of binaries whose orbit are randomly
-selected from a model. A similar method was used by
-\citet{maxted:2005} and \citet{basri:2006}.  The most important
-factors in determining the detection probability are the size of
-uncertainties in RV measurements (which we use the average
-$\sigma_{\mathrm{RRV}}$ from our observation), and the time
-separations of observations.  The smaller the errors in RV
-measurements, the larger the probability for a given binary orbit and
-a time separation of orbit. The larger the time separation of
+selected from a model. A similar method was used by \citet{maxted:2005}
+and \citet{basri:2006}. The most important factors in determining
+the detection probability are the size of uncertainties in RV measurements
+(which we use the average $\sigma_{\mathrm{RRV}}$ from our observation),
+and the time separations of observations. The smaller the errors in
+RV measurements, the larger the probability for a given binary orbit
+and a time separation of orbit. The larger the time separation of
 observations, the larger the upper limit of the semimajor axis to
-which an observation is sensitive.  The average time separation of the
-two-epoch RV observations of our targets is $21.6$~d.
-In the following, we will briefly discuss our model assumptions and
-parameters which are essentially the same as those of
-\citet{maxted:2005} but with some simplifications.
-
-There are six basic parameters in our Monte Carlo simulation: 
-primary mass ($M_{1}$), mass ratio ($q$), eccentricity
-($e$), orbital phase ($\phi$), orbital inclination ($i$),
-longitude of periastron ($\lambda$). The primary mass $M_{1}$ is
-assigned from the adopted mass of 
-the targets in Table~\ref{tab:literatures}, with a uniform random
-deviation of $\pm0.002\,M_{\sun}$. The mass ratio is assumed to be
-uniformly distributed between $q=0$ and $0.2$. The eccentricity $e$ is
-assumed to be zero (circular orbits).  Both \citet{maxted:2005}
-and \citet{basri:2006} found the detection probability is insensitive
-to the assumed distribution of $q$ and $e$. The orbital phase is
-randomly chosen between 0 and 1.  The inclination $i$ is randomly
-chosen from the cumulative distribution of $\cos{i}$. The longitude of
-periastron $\lambda$ is not necessary since we assumed $e=0$.
-
-In order to compute the detection probability as a function of
-semimajor axis $a$, we take the following procedure: (1)~for each
-object in our targets, we randomly select $10^5$ binaries using the
-assumption stated above for a given value of $a$, and compute the RV
-of the primary ($V_{1}$), (2)~evolve the orbit by the time separation
-of the RV measuremets used in the observations for this object, and
-take another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
+which an observation is sensitive. The average time separation of
+the two-epoch RV observations of our targets is $21.6$~d. In the
+following, we will briefly discuss our model assumptions and parameters
+which are essentially the same as those of \citet{maxted:2005} but
+with some simplifications.
+
+There are six basic parameters in our Monte Carlo simulation: primary
+mass ($M_{1}$), mass ratio ($q$), eccentricity ($e$), orbital phase
+($\phi$), orbital inclination ($i$), longitude of periastron ($\lambda$).
+The primary mass $M_{1}$ is assigned from the adopted mass of the
+targets in Table~\ref{tab:literatures}, with a uniform random deviation
+of $\pm0.002\, M_{\sun}$. The mass ratio is assumed to be uniformly
+distributed between $q=0$ and $0.2$. The eccentricity $e$ is assumed
+to be zero (circular orbits). Both \citet{maxted:2005} and \citet{basri:2006}
+found the detection probability is insensitive to the assumed distribution
+of $q$ and $e$. The orbital phase is randomly chosen between 0 and
+1. The inclination $i$ is randomly chosen from the cumulative distribution
+of $\cos{i}$. The longitude of periastron $\lambda$ is not necessary
+since we assumed $e=0$.
+
+In order to compute the detection probability as a function of semimajor
+axis $a$, we take the following procedure: (1)~for each object in
+our targets, we randomly select $10^{5}$ binaries using the assumption
+stated above for a given value of $a$, and compute the RV of the
+primary ($V_{1}$), (2)~evolve the orbit by the time separation of
+the RV measuremets used in the observations for this object, and take
+another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
 $V_{2}$ and the average uncertainty in RV ($\sigma_{\mathrm{RRV}}$)
-from the observations, we compute the $\chi^{2}$ probability $p$,  and
-flag the trial as a detection if $p<10^{-3}$ as done for the real
-data, (4)~find the fraction of detections out of all random trials,
-(5) repeat 1--4 for the range of $a$ between $10^{-3}$~and 10~au, and
-(6) repeat 5 for the all targets, and find the detection probability
-averaged over all targets as a function of $a$.
-
-The result of the simulation is shown in
-Fig.~\ref{fig:detect_prob}. The detection probability curve shown here
-is very similar that of \citet{basri:2006} for a constant time
-separation (20~d) case (see their Fig.~4). The probability remains
-fairly constant up to  $a \approx 0.1\,\mathrm{au}$, and it rapidly
-decreases beyond $a\approx 0.3\,\mathrm{au}$.  This turning point will
-increase if we had used larger time separations in our observation. 
-From this figure, we find that the 80~per~cent detection probability
-up to for binaries with $a<0.1\,\mathrm{au}$, given our time
-separations and the average uncertainty ($\sim0.56\,\kmps$) in the RV
-measurements.
+from the observations, we compute the $\chi^{2}$ probability $p$,
+and flag the trial as a detection if $p<10^{-3}$ as done for the
+real data, (4)~find the fraction of detections out of all random
+trials, (5) repeat 1--4 for the range of $a$ between $10^{-3}$~and
+10~au, and (6) repeat 5 for the all targets, and find the detection
+probability averaged over all targets as a function of $a$.
+
+The result of the simulation is shown in Fig.~\ref{fig:detect_prob}.
+The detection probability curve shown here is very similar that of
+\citet{basri:2006} for a constant time separation (20~d) case (see
+their Fig.~4). The probability remains fairly constant up to $a\approx0.1\,\mathrm{au}$,
+and it rapidly decreases beyond $a\approx0.3\,\mathrm{au}$. This
+turning point will increase if we had used larger time separations
+in our observation. From this figure, we find that the 80~per~cent
+detection probability up to for binaries with $a<0.1\,\mathrm{au}$,
+given our time separations and the average uncertainty ($\sim0.56\,\kmps$)
+in the RV measurements.
 
@@
 
-\begin{center}
-\includegraphics[%
-  clip,
-  scale=0.63]{figures/detect_prob.eps}
-\end{center}
+\begin{center}\includegraphics[clip,scale=0.63]{figures/detect_prob} \par\end{center}
 
 \caption{The binary detection probability (solid) as a function of the semimajor
-  axis ($a$), based on Monte~Carlo simulations of RV measurements, is
-  shown.  For each object in our target list, the simulation was performed
-  using the time separation ($\Delta t$) actually used in our
-  two-epoch observations (c.f.~Table~\ref{tab:summary_results}) and
-  the estimated primary mass  (c.f.~Table~\ref{tab:literatures}).  The
-  final detection probability is obtained by averaging
-  over the simulated observations of all the objects.  The average
-  time separation in the two-epoch observations  is $\sim
-  21.6\,\mathrm{d}$, and the average uncertainty in RV is
-  $~0.56\,\kmps$. The probability remains fairly
-  constant up to $a \approx 0.1\,\mathrm{au}$, and it rapidly decreases
-  beyond $a\approx 0.3\,\mathrm{au}$.  The 80~per~cent detection
-  probability is achieved for binaries with $a<0.1\,\mathrm{au}$. }
+axis ($a$), based on Monte~Carlo simulations of RV measurements,
+is shown. For each object in our target list, the simulation was performed
+using the time separation ($\Delta t$) actually used in our two-epoch
+observations (c.f.~Table~\ref{tab:summary_results}) and the estimated
+primary mass (c.f.~Table~\ref{tab:literatures}). The final detection
+probability is obtained by averaging over the simulated observations
+of all the objects. The average time separation in the two-epoch observations
+is $\sim21.6\,\mathrm{d}$, and the average uncertainty in RV is $~0.56\,\kmps$.
+The probability remains fairly constant up to $a\approx0.1\,\mathrm{au}$,
+and it rapidly decreases beyond $a\approx0.3\,\mathrm{au}$. The 80~per~cent
+detection probability is achieved for binaries with $a<0.1\,\mathrm{au}$. }
 
@@
 
-In Section~\ref{sub:Radial-velocities}
-(see Fig.~\ref{fig:chisq-test}), we found the histogram of the
-$\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
-reasonably matches the expected distribution.  This leas us to
-conclude that the uncertainty estimates in RV values are 
-reasonable. Here, we will inspect the effect of the systematic error
-on the observed binary fraction more closely. There are two possible
-source of errors: (1)~the RV shifts caused by surface/atmospheric
-activity, and (2)~the RV shifts due to the limit of the stability of
-autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
-negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
+In Section~\ref{sub:Radial-velocities} (see Fig.~\ref{fig:chisq-test}),
+we found the histogram of the $\chi^{2}$ probability $p$, for the
+RV data fit assuming constant RV, reasonably matches the expected
+distribution. This leas us to conclude that the uncertainty estimates
+in RV values are reasonable. Here, we will inspect the effect of the
+systematic error on the observed binary fraction more closely. There
+are two possible source of errors: (1)~the RV shifts caused by surface/atmospheric
+activity, and (2)~the RV shifts due to the limit of the stability
+of autoguiding of the telescope. \citet{joergens:2006} found that
+(1) is negligibly small for young VLM objects with $M_{*}<0.12\, M_{\sun}$.
 The size of RV errors caused by (2) is expected to be $<1\,\kmps$
 \citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
-additional systematic error was not needed to be added to the RV
-uncertainties of \citet{joergens:2006} who used the same instruments
-as ours, and used the same method of estimating the
-uncertainties. Hence, we expect the systematic error to be much
-smaller than $1\,\kmps$ if one is required.
-
-The observed binary fraction is expected to be sensitive to the
-assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
-the RV shifts and the systematic errors are in the same order of
-magnitude. The number of binary detections would decrease as
-$\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
-probabilities ($p$) for each object being a RV constant object as done
-earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
-systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
-the uncertainties in the RVs of each object.  The results are
-summarised in Table~\ref{tab:prob_compare} along with the probabilities
-computed without the systematic error (as in
-Section\ref{sub:Radial-velocities}).  The number of objects with
-$p<10^{-3}$ decreases from 4 to 2 as the systematic error is
-introduced. Unfortunately, the probabilities computed with
-$\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
-below the $p=10^{-3}$ boundary value; hence, they become RV constant
-objects as the systematic error is introduced. This
-clearly demonstrates the importance of the uncertainty estimates in
-the measured RV values.  We found that the histogram of the $\chi^2$
-probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
-Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
-expected distribution of $-\log{p}$ (not shown here).  
-The binary fraction estimated with the assumed systematic error is
-$2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
-
-%
+additional systematic error was not needed to be added to the RV uncertainties
+of \citet{joergens:2006} who used the same instruments as ours, and
+used the same method of estimating the uncertainties. Hence, we expect
+the systematic error to be much smaller than $1\,\kmps$ if one is
+required.
+
+The observed binary fraction is expected to be sensitive to the assumed
+size of the systematic error ($\sigma_{\mathrm{sys}}$) since the
+RV shifts and the systematic errors are in the same order of magnitude.
+The number of binary detections would decrease as $\sigma_{\mathrm{sys}}$
+increases. We have computed the $\chi^{2}$ probabilities ($p$) for
+each object being a RV constant object as done earlier (Section\ref{sub:Radial-velocities}),
+but with the assumed systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$,
+which was added to the uncertainties in the RVs of each object. The
+results are summarised in Table~\ref{tab:prob_compare} along with
+the probabilities computed without the systematic error (as in Section\ref{sub:Radial-velocities}).
+The number of objects with $p<10^{-3}$ decreases from 4 to 2 as the
+systematic error is introduced. Unfortunately, the probabilities computed
+with $\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55
+are just below the $p=10^{-3}$ boundary value; hence, they become
+RV constant objects as the systematic error is introduced. This clearly
+demonstrates the importance of the uncertainty estimates in the measured
+RV values. We found that the histogram of the $\chi^{2}$ probabilities
+with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in Fig~\ref{fig:chisq-test}),
+is also in reasonable agreement with the expected distribution of
+$-\log{p}$ (not shown here). The binary fraction estimated with the
+assumed systematic error is $2/17$ or $f=12_{-8}^{+13}$~per~cent
+for $a<0.1$~au.
+
 % This may be out of place =======================
 An alternative explanation for the RV variations found in the binary
-candidates above is a type of stellar pulsations found by
-\citet{palla:2005}. They studied the non-adiabatic, linear
-instability of very VLM stars and BD during the deturium burning phase
-in the core, and found unstable fundamental modes in the time-scale
-between $\sim 1$ and $\sim 5$~h for the object mass from $0.02$ and
-$0.1\,\Msun$.  By using their pulsation periods and by assuming that the
-pulsation amplitudes is 5~per~cent of the radius of the objects, we
-find that the expected RV variation can be $>6\,\kmps$.
-As mentioned in Section~\ref{sec:observation-reduction}, for each object at a
-given night, two separate spectra are obtained consecutively (with
-time separations of $\sim 0.5$~h.). Before co-adding the two spectra
-together, we have measured the RV from each spectrum to check if there
-is a large jump in the RV measurements in short
-time-scale. The shifts in the RV values in measured in the two
-consecutive spectra are found to be between $0.02\pm0.10$ (USco~128)
-and  $2.04\pm1.67\,\kmps$ (USco~66), which is much smaller than the
-expected RV variation based on the models of \citet{palla:2005};
-hence, found little indication of the pulsations.
+candidates above is a type of stellar pulsations found by \citet{palla:2005}.
+They studied the non-adiabatic, linear instability of very VLM stars
+and BD during the deturium burning phase in the core, and found unstable
+fundamental modes in the time-scale between $\sim1$ and $\sim5$~h
+for the object mass from $0.02$ and $0.1\,\Msun$. By using their
+pulsation periods and by assuming that the pulsation amplitudes is
+5~per~cent of the radius of the objects, we find that the expected
+RV variation can be $>6\,\kmps$. As mentioned in Section~\ref{sec:observation-reduction},
+for each object at a given night, two separate spectra are obtained
+consecutively (with time separations of $\sim0.5$~h.). Before co-adding
+the two spectra together, we have measured the RV from each spectrum
+to check if there is a large jump in the RV measurements in short
+time-scale. The shifts in the RV values in measured in the two consecutive
+spectra are found to be between $0.02\pm0.10$ (USco~128) and $2.04\pm1.67\,\kmps$
+(USco~66), which is much smaller than the expected RV variation based
+on the models of \citet{palla:2005}; hence, found little indication
+of the pulsations.
 
@@
 
-\caption{Comparison of the $\chi^{2}$ probability ($p$), for each object
-  being a RV constant, computed with an addition systematic error
-  $\sigma_{\mathrm{sys}}$ (right), and without (left). The objects are
-  listed in ascending order of $p$. The ellipses represent the
-  boundary ($p=10^{-3}$) between RV constant objects and RV 
-  variable objects. }
+\caption{The $\chi^{2}$ probability ($p$), for each object being a RV constant,
+listed in ascending order of $p$. The ellipses represent the boundary
+($p=10^{-3}$) between RV constant objects and RV variable objects. }
 
@@
 
-\begin{center}
-\begin{tabular}{lclc}
+\begin{center}\begin{tabular}{lc}
 \hline 
-&
-$\sigma_{\mathrm{sys}}=0.0\,\kmps$&
-&
-$\sigma_{\mathrm{sys}}=0.2\,\kmps$\tabularnewline
-obj.~ID&
-$p$&
 obj.~ID&
@@
 \hline 
-USco~104&
-$4.3\times10^{-12}$&
-USco~104&
-$3.5\times10^{-6}$\tabularnewline
-GY~310&
-$1.8\times10^{-10}$&
-GY~310&
-$2.0\times10^{-5}$\tabularnewline
-GY~141&
-$1.6\times10^{-4}$&
+USco~112&
+$8.9\times10^{-8}$\tabularnewline
+USco~128&
+$1.3\times10^{-7}$\tabularnewline
+USco~40&
+$5.8\times10^{-7}$\tabularnewline
+USco~55&
+$2.4\times10^{-6}$\tabularnewline
 $\cdots$&
 $\cdots$\tabularnewline
-USco~55&
-$7.2\times10^{-4}$&
+USco~101&
+$1.1\times10^{-3}$\tabularnewline
+GY~310&
+$1.6\times10^{-3}$\tabularnewline
+USco~67&
+$1.0\times10^{-2}$\tabularnewline
+USco~53&
+$9.8\times10^{-2}$\tabularnewline
+USco~104&
+$2.0\times10^{-1}$\tabularnewline
 GY~141&
-$5.8\times10^{-2}$\tabularnewline
-$\cdots$&
-$\cdots$&
-USco~55&
-$1.6\times10^{-1}$\tabularnewline
-USco~101&
-$8.9\times10^{-2}$&
+$2.3\times10^{-1}$\tabularnewline
+USco~75&
+$4.1\times10^{-1}$\tabularnewline
+USco~66&
+$4.4\times10^{-1}$\tabularnewline
+GY~5&
+$7.2\times10^{-1}$\tabularnewline
+USco~132&
+$7.9\times10^{-1}$\tabularnewline
+USco~100&
+$8.6\times10^{-1}$\tabularnewline
+USco~109&
+$8.6\times10^{-1}$\tabularnewline
 USco~130&
-$2.3\times10^{-1}$\tabularnewline
-USco~66&
-$9.2\times10^{-2}$&
-USco~132&
-$2.6\times10^{-1}$\tabularnewline
-USco~75&
-$2.8\times10^{-1}$&
-USco~101 &
-$2.8\times10^{-1}$\tabularnewline
-USco~109&
-$3.0\times10^{-1}$&
-GY~5&
-$2.8\times10^{-1}$\tabularnewline
-USco~112&
-$3.1\times10^{-1}$&
-USco~75&
-$3.9\times10^{-1}$\tabularnewline
-USco~132&
-$3.2\times10^{-1}$&
-USco~66&
-$4.3\times10^{-1}$\tabularnewline
-USco~130&
-$3.2\times10^{-1}$&
-USco~128&
-$4.6\times10^{-1}$\tabularnewline
-GY~5&
-$3.7\times10^{-1}$&
-USco~53&
-$5.8\times10^{-1}$\tabularnewline
-USco~53 &
-$4.2\times10^{-1}$&
-USco~40&
-$6.0\times10^{-1}$\tabularnewline
-USco~67&
-$4.8\times10^{-1}$&
-USco~112&
-$6.5\times10^{-1}$\tabularnewline
-USco~128&
-$5.4\times10^{-1}$&
-USco~100&
-$6.6\times10^{-1}$\tabularnewline
-USco~100&
-$6.2\times10^{-1}$&
-USco~67&
-$7.0\times10^{-1}$\tabularnewline
-USco~40&
-$7.2\times10^{-1}$&
-USco~109&
-$7.1\times10^{-1}$\tabularnewline
+$9.8\times10^{-1}$\tabularnewline
 \hline
-\end{tabular}
-
-\end{center}
-
-\end{table}
-%==========================================
+\end{tabular}\par\end{center}
+
+\end{table} %==========================================
 
@@
 We have presented two-epoch RV survey of 18 young BDs and VLM stars
-($0.02~M_{\sun} < M_{*} < 0.1~M_{\sun}$) in
-UScoOB and $\rho$~Oph dark cloud core using the high resolution UVES
-echelle spectroscopy at VLT.  The average time separation of RV
-measurements are 21.6~d, and our RV survey is sensitive to binaries
-with separation smaller than 0.1~au.  One of our targets, USco~121, is
-most likely a non-member of the UScoOB association based on the
-deviation of the RV from the result of the population in the
-association. A similar conclusion was found by \citet{muzerolle:2003}
-from their RV study and the low lithium abundance.
-
-We found 4 (GY~141, GY~310, USco~55 and USco~104) out of 17 objects as our 
-binary/multiple candidates. This corresponds to the binary fraction of
-$24^{+16}_{-13}$~per~cent for the binary separation $a<0.1$~au.  We found
-that the estimated binary fraction is very sensitive to
-the assumed size of systematic error. If an additional systematic
-error of $0.2\,\kmps$  is added to the uncertainties in the RV
-measurements, we find only 2 (GY~310 and USco~104) out of 17 objects
-as our binary/multiple candidates, which corresponds to the binary
-fraction of $12^{+13}_{-10}$~per~cent.
+($0.02~M_{\sun}<M_{*}<0.1~M_{\sun}$) in UScoOB and $\rho$~Oph dark
+cloud core using the high resolution UVES echelle spectroscopy at
+VLT. The average time separation of RV measurements are 21.6~d, and
+our RV survey is sensitive to binaries with separation smaller than
+0.1~au. One of our targets, USco~121, is most likely a non-member
+of the UScoOB association based on the deviation of the RV from the
+result of the population in the association. A similar conclusion
+was found by \citet{muzerolle:2003} from their RV study and the low
+lithium abundance.
+
+We found 4 (GY~141, GY~310, USco~55 and USco~104) out of 17 objects
+as our binary/multiple candidates. This corresponds to the binary
+fraction of $24_{-13}^{+16}$~per~cent for the binary separation
+$a<0.1$~au. We found that the estimated binary fraction is very
+sensitive to the assumed size of systematic error. If an additional
+systematic error of $0.2\,\kmps$ is added to the uncertainties in
+the RV measurements, we find only 2 (GY~310 and USco~104) out of
+17 objects as our binary/multiple candidates, which corresponds to
+the binary fraction of $12_{-10}^{+13}$~per~cent.
 
 The recent high-resolution imaging survey of brown dwarfs and very
-low-mass objects (M5.5--M7.5 ) in the UScoOB by \citet{kraus:2005} (which was
-not known to authors at the time of our observation: April--May, 2004)
-confirms that USco~55 and USco~66 are multiple systems, and USco~109
-is most likely a multiple system.  Their projected separations are
-$a>4.0$~au which is well above our sensitivity limit of
-0.1~au; therefore, it is not surprising that we did not identify USco~66 and
-USco~109 as multiples. Interestingly, we also found USco~55 as a
-candidate for a multiple system. This may indicate that USco~55 is  
-a triple system with one of object located within 0.1~au from the
-primary.  In addition, we identify USco~104 as a binary candidate, but this
-was not in their target list.  Further they found USco~67, 75, 112, 128,
-130, 132 as non-multiple, and similarly we found them as
-'non-candidates' for multiplicity.
-
-We found the RV dispersion ($1.2\,\kmps$) of the objects in UScoOB is
-very similar to that of the BDs and VLM stars in Chamaeleon~I (Cha~I)
-previous study by \citet{joergens:2006b}. The rotational velocities
-($v\,\sin i$) of the samples were also measured. The distribution of
-$v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which is
-also similar to that of the Cha~I population found by
-\citet{joergens:2006b}; however, the dispersion of $v\,\sin i$ for the
-UScoOB objects ($27.8\,\kmps$) is found to be much larger than that of
-the Cha~I objects ($8.0\,\kmps$)
-
-Follow-up spectroscopic observations of the binary candidates
-presented here are planned in near future. There are only a few RV
-variable binary candidates identified in earlier surveys
-(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
-As \citet{burgasser:2006} points out most of the current RV and
-imaging surveys use samples from magnitude-limited survey, but one
-should attempt to use the samples from volume-limited survey in order
-to find a correct statistics on binary parameters more straightforwardly,
-i.e. without correcting for bias.
-
-\section*{Acknowledgements}
+low-mass objects (M5.5--M7.5 ) in the UScoOB by \citet{kraus:2005}
+(which was not known to authors at the time of our observation: April--May,
+2004) confirms that USco~55 and USco~66 are multiple systems, and
+USco~109 is most likely a multiple system. Their projected separations
+are $a>4.0$~au which is well above our sensitivity limit of 0.1~au;
+therefore, it is not surprising that we did not identify USco~66
+and USco~109 as multiples. Interestingly, we also found USco~55
+as a candidate for a multiple system. This may indicate that USco~55
+is a triple system with one of object located within 0.1~au from
+the primary. In addition, we identify USco~104 as a binary candidate,
+but this was not in their target list. Further they found USco~67,
+75, 112, 128, 130, 132 as non-multiple, and similarly we found them
+as 'non-candidates' for multiplicity.
+
+We found the RV dispersion ($1.2\,\kmps$) of the objects in UScoOB
+is very similar to that of the BDs and VLM stars in Chamaeleon~I
+(Cha~I) previous study by \citet{joergens:2006b}. The rotational
+velocities ($v\,\sin i$) of the samples were also measured. The distribution
+of $v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$
+which is also similar to that of the Cha~I population found by \citet{joergens:2006b};
+however, the dispersion of $v\,\sin i$ for the UScoOB objects ($27.8\,\kmps$)
+is found to be much larger than that of the Cha~I objects ($8.0\,\kmps$)
+
+Follow-up spectroscopic observations of the binary candidates presented
+here are planned in near future. There are only a few RV variable
+binary candidates identified in earlier surveys (\citealt{guenther:2003};
+\citealt{kenyon:2005}; \citealt{joergens:2006}). As \citet{burgasser:2006}
+points out most of the current RV and imaging surveys use samples
+from magnitude-limited survey, but one should attempt to use the samples
+from volume-limited survey in order to find a correct statistics on
+binary parameters more straightforwardly, i.e. without correcting
+for bias.
+
+\section{{*}}
+
+{Acknowledgements}
 
 We thank the staff of VLT of the ESO for carrying out the observations
-in service mode. RK is grateful for Rob Jeffries for helpful
-suggestions on the data analysis presented in this paper. RK also
-thank Matteww Bate and Tim Naylor for providing us helpful comments on
-the manuscript. This work was supported by PPARC rolling grant
-PP/C501609/1.
-
-%
-
-%
-
-%
+in service mode. RK is grateful for Rob Jeffries for helpful suggestions
+on the data analysis presented in this paper. RK also thank Matteww
+Bate and Tim Naylor for providing us helpful comments on the manuscript.
+This work was supported by PPARC rolling grant PP/C501609/1.
 
@@
 
-%
-
-%
-
-%
-
 \bibliographystyle{mn}
 
+\bibliographystyle{mn}
 \bibliography{local}
-
-%
 
@@
 \end{document}
-
-% LocalWords:  BDs VLM OB Ophiuchi al Ryuichi Harries QL RV UScoOB BD echelle
-% LocalWords:  VLT UVES RVs Cha bouy burgasser gizis kraus basri maxted PPl EEV
-% LocalWords:  pinfield substellar duquennoy VLMs guenther joergens padoan CCDs
-% LocalWords:  reipurth whitworth dezeeuw ardila luhman muzerolle Kueyen Parnal
-% LocalWords:  LL ESO interorder autoguiding FWHM jones Oph wilking mohanty Sp
-% LocalWords:  GY USco LHS HJD gaussian Cen garcia sanchez HD RRV pc CCF exp
-% LocalWords:  obs

### 2006-06-15 BD_radvel/kurosawa.tex
Fixed minor typo found by Stu.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@743 25464f21-6099-402c-b30a-640f1d40d38b

@@
 and have plotted the results  
-as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
+as a histogram of $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
 (excluding the non-member USco~121; see explanation later). 
@@
 expected RV variation based on the models of \citet{palla:2005};
-hence, found little indication of the pulsations in our sample.
+hence, we found little indication of the pulsations in our sample.
 
@@
 suggestions on the data analysis presented in this paper. We also
-thank Matteww Bate for providing us valuable comments on
+thank Matthew Bate for providing us valuable comments on
 the manuscript. This work was supported by PPARC rolling grant

### 2006-06-15 torus/amr_mod.f90
photoion_mod parallelization
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@744 25464f21-6099-402c-b30a-640f1d40d38b

@@ -6237,7 +6237,7 @@ IF ( .NOT. gridConverged ) RETURN
     TYPE(octalVector) :: rVec
     integer,save :: it
     real :: fac
-    real,save :: radius(200),temp(200)
+    real,save :: radius(400),temp(400)
     integer :: i
     logical,save :: firsttime = .true.
 

### 2006-06-15 torus/dust_mod.f90

@@ -427,6 +427,9 @@ contains
       ! finding the cross sections
       sigmaExt(:) = 0.0; sigmaAbs(:)=0.0; sigmaSca(:)=0.0 ! initializing the values
 
+      if (writeoutput) write(*,*) "Dust law: ",aMin,aMax,qDist
+      if (writeoutput) open(20,file="albedo.dat",form="formatted",status="unknown")
+      if (writeoutput) open(21,file="gfactor.dat",form="formatted",status="unknown")
       do i = 1, grid%nLambda
          do j = 1, ngrain
             call mieDistCrossSection(aMin, aMax, a0, qDist, pDist, grid%lamArray(i), &
@@ -440,18 +443,10 @@ contains
          sigmaAbs(i) =    sigmaAbs(i)/total_abundance 
          sigmaSca(i) =    sigmaSca(i)/total_abundance 
          
-      end do
-         
-
-      if (writeoutput) write(*,*) "Dust law: ",aMin,aMax,qDist
-      if (writeoutput) open(20,file="albedo.dat",form="formatted",status="unknown")
-      if (writeoutput) open(21,file="gfactor.dat",form="formatted",status="unknown")
-      do i = 1, grid%nLambda
-         call mieDistCrossSection(aMin, aMax, a0, qDist, pdist, grid%lamArray(i),  mReal(i), mImg(i), sigmaExt(i), &
-              sigmaSca(i), sigmaAbs(i), gSca)
          if (writeoutput) write(21,*) grid%lamArray(i), gsca
          if (writeoutput) write(20,*) grid%lamArray(i),sigmaExt(i),sigmaAbs(i),sigmaSca(i),sigmaSca(i)/sigmaExt(i)
-      enddo
+      end do
+         
       if (writeoutput) close(20)
       if (writeoutput) close(21)
 

### 2006-06-15 torus/ion_mod.f90

@@ -105,8 +105,8 @@ contains
     nIon = nIon + 1
     call createIon(ionArray(nIon), 6, 3, 6.449e1) ! C IV
 
-    nIon = nIon + 1
-    call createIon(ionArray(nIon), 6, 2, 3.921e2) ! C V
+!    nIon = nIon + 1
+!    call createIon(ionArray(nIon), 6, 2, 3.921e2) ! C V
 
     nIon = nIon + 1
     call createIon(ionArray(nIon), 7, 7, 1.453e1) ! N I
@@ -120,8 +120,8 @@ contains
     nIon = nIon + 1
     call createIon(ionArray(nIon), 7, 4, 7.747e1) ! N IV
 
-    nIon = nIon + 1
-    call createIon(ionArray(nIon), 7, 3, 9.789e1) ! N V
+!    nIon = nIon + 1
+!    call createIon(ionArray(nIon), 7, 3, 9.789e1) ! N V
 
     nIon = nIon + 1
     call createIon(ionArray(nIon), 8, 8, 1.362e1) ! O I
@@ -135,8 +135,8 @@ contains
     nIon = nIon + 1
     call createIon(ionArray(nIon), 8, 5, 7.741e1) ! O IV
 
-    nIon = nIon + 1
-    call createIon(ionArray(nIon), 8, 4, 1.139e2) ! O V
+!    nIon = nIon + 1
+!    call createIon(ionArray(nIon), 8, 4, 1.139e2) ! O V
 
     nIon = nIon + 1
     call createIon(ionArray(nIon), 10, 10, 2.156e1) ! Ne I
@@ -289,6 +289,11 @@ subroutine addLevels(thisIon)
         call addLevel(thisIon, "1D_2", 1.403841d0, 2.)
         call addLevel(thisIon, "1S_0", 3.36753d0, 0.)
 !        call addLevel(thisIon, "5S^0_2", 7.274391d0, 2.)
+
+     case("S IV")
+        call addLevel(thisIon, "2P^0_1/2", 0.d0, 0.5)
+        call addLevel(thisIon, "2P^0_3/2", 0.117962d0, 1.5)
+
     case DEFAULT
   end select
 end subroutine addLevels
@@ -567,6 +572,13 @@ subroutine addTransitions(thisIon)
         gamma = (/  1.42  , 1.88  , 2.02  ,  2.08  /)
[…]

### 2006-06-15 torus/utils_mod.f90

@@ -3092,6 +3092,7 @@ function returnAbundance(z) result(a)
 !        write(*,*) "NO HELIUM!!!!!!!!!!!!!!"
 !        a = 1.e-10
      case(6)
+!        write(*,*) "NO HEAVIES!!!!!!!!!!!!!!"
         a = 22.e-5
      case(7)
         a = 4.e-5

### 2006-06-19 BD_radvel/kurosawa/kurosawa.tex
Preparation for sumbission done (clean up and renaming the files). The clean version is stored in a new directory called kurosawa/.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@746 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-06-15 BD_radvel/kurosawa.tex
@@
-%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
+\documentclass[english,useAMS, usenatbib]{mn2e}
 \usepackage[T1]{fontenc}
@@
 \begin{document}
-\title[Radial and rotational velocities of young BDs and VLM stars]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core}
+\title[Young BDs and VLM stars]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core}
 
@@
 For a small (12) sample of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
-in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
+in Upper Scorpius OB association (UScoOB), \citet*{kraus:2005} found
 $f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
@@
 the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$,
-\citealt{dezeeuw:1999}) from the list of \citet{ardila:2000} and 3
+\citealt{dezeeuw:1999}) from the list of \citet*{ardila:2000} and 3
 objects in the $\rho$~Ophiuchi cloud core ($\mathrm{d\approx150\,
@@
 \caption{Summary of known properties of the targets from literatures: a.~\citet{luhman:1999}
-(original list for $\rho$~Oph), b.~\citet{ardila:2000} (original
-list for UScoOB), c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003},
-e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}. }
+(original list for $\rho$~Oph), b.~\citet*{ardila:2000} (original
+list for UScoOB), c.~\citet*{wilking:1999}, d.~\citet{muzerolle:2003},
+e.~\citet{kraus:2005}, and f.~\citet*{mohanty:2005}. }
 
@@
 \hline 
-0.81&
+Object&
 Date&
@@
   clip,
-  scale=0.9]{figures/radvel_all01.eps}
+  scale=0.9]{fig01a.eps}
 
@@
 ($\Delta \mathrm{RV}$) from the `average' radial velocity
-($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and
+($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}, and
 the horizontal axes indicate the time of the observation in
@@
   clip,
-  scale=0.9]{figures/radvel_all02.eps}
+  scale=0.9]{fig01b.eps}
 
@@
 which is in good agreement with the Elodie radial velocity measurement
-of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep{udry:1999}.
+of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
 
@@
 $\sigma_{\mathrm{RRV}}$ values as described in
-(c.f.~\citealt{joergens:2006}. The standard deviations of the mean of
+(c.f.~\citealt{joergens:2006}). The standard deviations of the mean of
 the two independent RV measurements obtained from the two consecutive
@@
 two epochs are also given in the same table.
-%The $\overline{\mathrm{RV}}$
-%values of the objects in UScoOB are consistent with the earlier measurements
-%of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.
 
@@
   clip,
-  scale=0.46]{figures/chisq_hist.eps}
+  scale=0.46]{fig02.eps}
 \end{center}
@@
   clip,
-  scale=0.46]{figures/radvel_hist.eps}
+  scale=0.46]{fig03.eps}
 
@@
 are in good agreement with the earlier measurements of \citet{muzerolle:2003}
-and \citet{mohanty:2005}, given in Table~\ref{tab:literatures}.
+and \citet*{mohanty:2005}, given in Table~\ref{tab:literatures}.
 For example, \citet{muzerolle:2003} found $v\,\sin i=16.8\pm2.7\,\mathrm{km\, s^{-1}}$
@@
   clip,
-  scale=0.63]{figures/vrot_hist.eps}
+  scale=0.63]{fig04.eps}
 
@@
   clip,
-  scale=0.63]{figures/detect_prob.eps}
+  scale=0.63]{fig05.eps}
 \end{center}
@@
 %==========================================
-
-%% The expected binary fraction for our survey can be obtained
-%% by integrating the product of the detection probability found above
-%% with an assumed binary separation distribution function over a range
-%% of $a$. Here, we simply adopt one of the separation distribution
-%% function used by \citet{maxted:2005}. The binary separation ($a$)
-%% distribution is assumed to be  gaussian in  log($a$) space with its
-%% centre $\log{a_{o}}=0.6$ and width $\sigma_{\log{a}}=1.0$, and
-%% truncated at $\log{a}=1.176$ where $a$ is in au. This form of the
-%% distribution function is motivated by the distribution of solar-type
-%% binaries found in \citet{duquennoy:1991}, and the truncation is
-%% suggested from the lack of wide binaries for $a>15$~au 
-%% (e.g.~\citealt{burgasser:2003}). The distribution is normalized such
-%% that the total binary fraction of 26~per~cent as
-%% suggested by \citet{basri:2006}.  The resulting separation
-%% distribution function is shown also in Fig.~\ref{fig:detect_prob}. 
-%% Using this and the detection probability in the same figure, we find
-%% the expected binary fraction to be $f_{\mathrm{exp}}=3.2$~per~cent
-%% (for $a<0.1$~au), which is
-%% much smaller than our observed binary fraction of
-%% $f_{\mathrm{obs}}=24^{+16}_{-13}$. The two values are not consistent
-%% with each other. There are two possible reasons for the discrepancy:
-%% (1)~the assumed binary separation distribution mentioned above is
-%% unrealistic, and (2)~the uncertainties in our RV measurements are
-%% underestimated.  The first reason is less likely since both
-%% \citet{maxted:2005} and \citet{basri:2006} found this form of the $a$
-%% distribution function is consistent with the observed binary
-%% fractions estimated from many earlier surveys.  We will investigate
-%% the possibility for the second reason in the following.
 
@@
 
-% The observed binary fraction is expected to be sensitive to the
-% assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
-% the RV shifts and the systematic errors are in the same order of
-% magnitude. The number of binary detections would decrease as
-% $\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
-% probabilities ($p$) for each object being a RV constant object as done
-% earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
-% systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
-% the uncertainties in the RVs of each object.  The results are
-% summarised in Table~\ref{tab:prob_compare} along with the probabilities
-% computed without the systematic error (as in
-% Section\ref{sub:Radial-velocities}).  The number of objects with
-% $p<10^{-3}$ decreases from 4 to 2 as the systematic error is
-% introduced. Unfortunately, the probabilities computed with
-% $\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
-% below the $p=10^{-3}$ boundary value; hence, they become RV constant
-% objects as the systematic error is introduced. This
-% clearly demonstrates the importance of the uncertainty estimates in
-% the measured RV values.  We found that the histogram of the $\chi^2$
-% probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
-% Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
-% expected distribution of $-\log{p}$ (not shown here).  
-% The binary fraction estimated with the assumed systematic error is
-% $2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
-%
-% %
-% This may be out of place =======================
 An alternative explanation for the RV variations found in the binary
@@
 
-%% %==========================================
-%% \begin{figure}
-
-%% \begin{center}
-
-%% \includegraphics[%
-%%   clip,
-%%   scale=0.63]{figures/detect_err_add.eps}
-
-%% \end{center}
-
-%% \caption{The number of binaries/multiples (non-constant RV objects)
-%%   detected as a function of the size of additional systematic error ($\sigma_{\mathrm{sys}}$)
-%%   in RV measurements. The number of detections decreases rapidly from 4
-%%   to 2 as $\sigma_{\mathrm{sys}}=0.1\,\kmps$, which may be caused by
-%%   the instability of the autoguiding of the telescope, is added to
-%%   the uncertainties estimated in
-%%   Table~\ref{tab:summary_results}. The number of  detections
-%%   remains constant at 2 for a relatively wide range of the additional
-%%   errors. i.e.~$0.05\,\kmps < \sigma_{\mathrm{sys}} < 0.275\,
-%%   \kmps$. No binary is found for  $\sigma_{\mathrm{sys}} > 0.375\,\kmps$.} 
-%% \label{fig:adding_sys_err}
-
-%% \end{figure}
-%% %==========================================
-
-%% %==========================================
-%% \begin{table}
-%%
-%%
-%% \caption{Comparison of the $\chi^{2}$ probability ($p$), for each object
-%%   being a RV constant, computed with an addition systematic error
-%%   $\sigma_{\mathrm{sys}}$ (right), and without (left). The objects are
-%%   listed in ascending order of $p$. The ellipses represent the
-%%   boundary ($p=10^{-3}$) between RV constant objects and RV 
-%%   variable objects. }
-%%
-%% \label{tab:prob_compare}
-%%
-%% \begin{center}
-%% \begin{tabular}{lclc}
-%% \hline 
-%% &
-%% $\sigma_{\mathrm{sys}}=0.0\,\kmps$&
-%% &
-%% $\sigma_{\mathrm{sys}}=0.2\,\kmps$\tabularnewline
-%% obj.~ID&
-%% $p$&
-%% obj.~ID&
-%% $p$\tabularnewline
-%% \hline
-%% USco~104&
-%% $4.3\times10^{-12}$&
-%% USco~104&
-%% $3.5\times10^{-6}$\tabularnewline
-%% GY~310&
-%% $1.8\times10^{-10}$&
-%% GY~310&
-%% $2.0\times10^{-5}$\tabularnewline
-%% GY~141&
-%% $1.6\times10^{-4}$&
-%% $\cdots$&
-%% $\cdots$\tabularnewline
-%% USco~55&
-%% $7.2\times10^{-4}$&
-%% GY~141&
-%% $5.8\times10^{-2}$\tabularnewline
-%% $\cdots$&
-%% $\cdots$&
-%% USco~55&
-%% $1.6\times10^{-1}$\tabularnewline
-%% USco~101&
-%% $8.9\times10^{-2}$&
-%% USco~130&
-%% $2.3\times10^{-1}$\tabularnewline
-%% USco~66&
-%% $9.2\times10^{-2}$&
-%% USco~132&
-%% $2.6\times10^{-1}$\tabularnewline
-%% USco~75&
-%% $2.8\times10^{-1}$&
-%% USco~101 &
-%% $2.8\times10^{-1}$\tabularnewline
-%% USco~109&
-%% $3.0\times10^{-1}$&
-%% GY~5&
-%% $2.8\times10^{-1}$\tabularnewline
-%% USco~112&
-%% $3.1\times10^{-1}$&
-%% USco~75&
-%% $3.9\times10^{-1}$\tabularnewline
-%% USco~132&
-%% $3.2\times10^{-1}$&
-%% USco~66&
-%% $4.3\times10^{-1}$\tabularnewline
-%% USco~130&
-%% $3.2\times10^{-1}$&
-%% USco~128&
-%% $4.6\times10^{-1}$\tabularnewline
-%% GY~5&
-%% $3.7\times10^{-1}$&
-%% USco~53&
-%% $5.8\times10^{-1}$\tabularnewline
-%% USco~53 &
-%% $4.2\times10^{-1}$&
-%% USco~40&
-%% $6.0\times10^{-1}$\tabularnewline
-%% USco~67&
-%% $4.8\times10^{-1}$&
-%% USco~112&
-%% $6.5\times10^{-1}$\tabularnewline
-%% USco~128&
-%% $5.4\times10^{-1}$&
-%% USco~100&
-%% $6.6\times10^{-1}$\tabularnewline
-%% USco~100&
-%% $6.2\times10^{-1}$&
-%% USco~67&
-%% $7.0\times10^{-1}$\tabularnewline
-%% USco~40&
-%% $7.2\times10^{-1}$&
-%% USco~109&
-%% $7.1\times10^{-1}$\tabularnewline
-%% \hline
-%% \end{tabular} 
-%%
-%%
-%% \end{center}
-%%
-%% \end{table}
-%% %==========================================
-
-%% %==========================================
-%% \begin{table}
-
-%% \caption{Summary of the observed binary fractions ($f_{\mathrm{obs}}$) compared with the
-%%   expected binary fractions ($f_{\mathrm{exp}}$) with and without a
-%%   systematic error ($\sigma_{\mathrm{sys}}$). }
-
-%% \label{tab:binary_fraction}
-
-%% \begin{center}
-
-%% \begin{tabular}{ccccl}
-%% \hline 
-%% $\sigma_{\mathrm{sys}}$&  
-%% N. detected&  
-%% $f_{\mathrm{obs}}$&
-%% $f_{\mathrm{exp}}$&  
-%% obj.~ID  \tabularnewline
-%% ($\kmps$)&
-%% &
-%% (per~cent)&
-%% (per~cent)&
-%% \tabularnewline
-%% \hline
-%% $0.0$&
-%% $4$&
-%% $24^{+16}_{-13}$&
-%% $3.2$&
-%% GY~141\tabularnewline
-%% &
-%% &
-%% &
-%% &
-%% GY~310\tabularnewline
-%% &
-%% &
-%% &
-%% &
-%% USco~55\tabularnewline
-%% &
-%% &
-%% &
-%% &
-%% USco~104\tabularnewline
-%% $0.1$&
-%% $2$&
-%% $12^{+13}_{-10}$&
-%% $2.9$&
-%% GY~310\tabularnewline
-%% &
-%% &
-%% &
-%% &
-%% USco~104\tabularnewline
-%% \hline
-%% \end{tabular}
-
-%% \end{center}
-
-%% \end{table}
-%==========================================
-
 \section{Conclusions}
@@
 %
-
+%----------------------------------------------------
+% Bibliography follows here.
+%-----------------------------------------------------
 %
 
-%
-
-%----------------------------------------------------
-
-% Bibliography follows here.
-
-%-----------------------------------------------------
-
-%
-
-%
-
-%
-
-\bibliographystyle{mn}
-
-\bibliography{local}
-
-%
+%\bibliographystyle{mn}
+%\bibliography{local}
+
+\begin{thebibliography}{46}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Ardila} {et~al.}(2000){Ardila}, {Mart{\'{\i}}n}, \&
+  {Basri}}]{ardila:2000}
+{Ardila} D., {Mart{\'{\i}}n} E., {Basri} G., 2000, \aj, 120, 479
+
+\bibitem[{{Bailer-Jones}(2004)}]{bailer-jones:2004}
+{Bailer-Jones} C.~A.~L., 2004, \aap, 419, 703
+
+\bibitem[{{Baranne} \& et~al.(1996)}]{baranne:1996}
+{Baranne} A., et~al., 1996, \aaps, 119, 373
+
+\bibitem[{{Basri} \& {Mart{\'{\i}}n}(1999)}]{basri:1999}
+{Basri} G., {Mart{\'{\i}}n} E.~L., 1999, \aj, 118, 2460
+
+\bibitem[{{Basri} \& {Reiners}(2006)}]{basri:2006}
+{Basri} G., {Reiners} A., 2006, preprint (astro-ph/0604259)
+
+\bibitem[{{Bate} \& {Bonnell}(2005)}]{bate:2005}
+{Bate} M.~R., {Bonnell} I.~A., 2005, \mnras, 356, 1201
+
+\bibitem[{{Bate} {et~al.}(2002{\natexlab{a}}){Bate}, {Bonnell}, \&
+  {Bromm}}]{bate:2002}
+{Bate} M.~R., {Bonnell} I.~A., {Bromm} V., 2002{\natexlab{a}}, \mnras, 332, L65
+
+\bibitem[{{Bate} {et~al.}(2002{\natexlab{b}}){Bate}, {Bonnell}, \&
+  {Bromm}}]{bate:2002b}
+---, 2002{\natexlab{b}}, \mnras, 336, 705
+
+\bibitem[{{Bate} {et~al.}(2003){Bate}, {Bonnell}, \& {Bromm}}]{bate:2003}
+---, 2003, \mnras, 339, 577
+
+\bibitem[{{Benedict} \& et~al.(1998)}]{benedict:1998}
+{Benedict} G.~F., et~al., 1998, \aj, 116, 429
+
+\bibitem[{{Bouy} {et~al.}(2006){Bouy}, {Moraux}, {Bouvier}, {Brandner},
+  {Mart{\'{\i}}n}, {Allard}, {Baraffe}, \& {Fern{\'a}ndez}}]{bouy:2006}
+{Bouy} H., {Moraux} E., {Bouvier} J., {Brandner} W., {Mart{\'{\i}}n} E.~L.,
+  {Allard} F., {Baraffe} I., {Fern{\'a}ndez} M., 2006, \apj, 637, 1056
+
+\bibitem[{{Burgasser} {et~al.}(2003){Burgasser}, {McElwain}, \&
+  {Kirkpatrick}}]{burgasser:2003}
+{Burgasser} A.~J., {McElwain} M.~W., {Kirkpatrick} J.~D., 2003, \aj, 126, 2487
+
+\bibitem[{{Burgasser} {et~al.}(2006){Burgasser}, {Reid}, {Siegler}, {Close},
+  {Allen}, {Lowrance}, \& {Gizis}}]{burgasser:2006}
+{Burgasser} A.~J., {Reid} I.~N., {Siegler} N., {Close} L., {Allen} P.,
+  {Lowrance} P., {Gizis} J., 2006, preprint (astro-ph/0602122)
+
+\bibitem[{{Close} {et~al.}(2003){Close}, {Siegler}, {Freed}, \&
+  {Biller}}]{close:2003}
+{Close} L.~M., {Siegler} N., {Freed} M., {Biller} B., 2003, \apj, 587, 407
+
+\bibitem[{{de Zeeuw} {et~al.}(1997){de Zeeuw}, {Brown}, {de Bruijne},
+  {Hoogerwerf}, {Lub}, {Le Poole}, \& {Blaauw}}]{dezeeuw:1997}
+{de Zeeuw} P.~T., {Brown} A.~G.~A., {de Bruijne} J.~H.~J., {Hoogerwerf} R.,
+  {Lub} J., {Le Poole} R.~S., {Blaauw} A., 1997, in {Battrick} B.,
+  ed., Proc. ESA Symp.~SP-402, Hipparcos Venice '97,  ESA,
+  Noordwijk, p.~495
+
+\bibitem[{{de Zeeuw} {et~al.}(1999){de Zeeuw}, {Hoogerwerf}, {de Bruijne},
+  {Brown}, \& {Blaauw}}]{dezeeuw:1999}
+{de Zeeuw} P.~T., {Hoogerwerf} R., {de Bruijne} J.~H.~J., {Brown} A.~G.~A.,
+  {Blaauw} A., 1999, \aj, 117, 354
+
+\bibitem[{{Duquennoy} \& {Mayor}(1991)}]{duquennoy:1991}
+{Duquennoy} A., {Mayor} M., 1991, \aap, 248, 485
+
+\bibitem[{{Garc{\'{\i}}a-S{\'a}nchez}
+  {et~al.}(2001){Garc{\'{\i}}a-S{\'a}nchez}, {Weissman}, {Preston}, {Jones},
+  {Lestrade}, {Latham}, {Stefanik}, \& {Paredes}}]{garcia-sanchez:2001}
+{Garc{\'{\i}}a-S{\'a}nchez} J., {Weissman} P.~R., {Preston} R.~A., {Jones}
+  D.~L., {Lestrade} J.-F., {Latham} D.~W., {Stefanik} R.~P., {Paredes} J.~M.,
+  2001, \aap, 379, 634
+
+\bibitem[{{Gizis} {et~al.}(2003){Gizis}, {Reid}, {Knapp}, {Liebert},
+  {Kirkpatrick}, {Koerner}, \& {Burgasser}}]{gizis:2003}
+{Gizis} J.~E., {Reid} I.~N., {Knapp} G.~R., {Liebert} J., {Kirkpatrick} J.~D.,
+  {Koerner} D.~W., {Burgasser} A.~J., 2003, \aj, 125, 3302
+
+\bibitem[{{Gray}(1992)}]{gray:1992}
+{Gray} D.~F., 1992, {The Observation and Analysis of Stellar Photospheres}.
+  Cambridge Univ.\, Press, Cambridge, UK
+
+\bibitem[{{Guenther} \& {Wuchterl}(2003)}]{guenther:2003}
+{Guenther} E.~W., {Wuchterl} G., 2003, \aap, 401, 677
+
+\bibitem[{{Joergens}(2006{\natexlab{a}})}]{joergens:2006b}
+{Joergens} V., 2006{\natexlab{a}}, \aap, 448, 655
+
+\bibitem[{{Joergens}(2006{\natexlab{b}})}]{joergens:2006}
+---, 2006{\natexlab{b}}, \aap, 446, 1165
+
+\bibitem[{{Joergens} \& {Guenther}(2001)}]{joergens:2001}
+{Joergens} V., {Guenther} E., 2001, \aap, 379, L9
+
+\bibitem[{{Kenyon} {et~al.}(2005){Kenyon}, {Jeffries}, {Naylor}, {Oliveira}, \&
+  {Maxted}}]{kenyon:2005}
+{Kenyon} M.~J., {Jeffries} R.~D., {Naylor} T., {Oliveira} J.~M., {Maxted}
+  P.~F.~L., 2005, \mnras, 356, 89
+
+\bibitem[{{Kraus} {et~al.}(2005){Kraus}, {White}, \&
+  {Hillenbrand}}]{kraus:2005}
+{Kraus} A.~L., {White} R.~J., {Hillenbrand} L.~A., 2005, \apj, 633, 452
+
+\bibitem[{{Luhman}(2004)}]{luhman:2004}
+{Luhman} K.~L., 2004, \apj, 614, 398
+
+\bibitem[{{Luhman} \& {Rieke}(1999)}]{luhman:1999}
+{Luhman} K.~L., {Rieke} G.~H., 1999, \apj, 525, 440
+
+\bibitem[{{Mart{\'{\i}}n} {et~al.}(2003){Mart{\'{\i}}n}, {Barrado y
+  Navascu{\'e}s}, {Baraffe}, {Bouy}, \& {Dahm}}]{martin:2003}
+{Mart{\'{\i}}n} E.~L., {Barrado y Navascu{\'e}s} D., {Baraffe} I., {Bouy} H.,
+  {Dahm} S., 2003, \apj, 594, 525
+
+\bibitem[{{Maxted} \& {Jeffries}(2005)}]{maxted:2005}
+{Maxted} P.~F.~L., {Jeffries} R.~D., 2005, \mnras, 362, L45
+
+\bibitem[{{McCaughrean} \& {Andersen}(2002)}]{mccaughrean:2002}
+{McCaughrean} M.~J., {Andersen} M., 2002, \aap, 389, 513
+
+\bibitem[{{Mohanty} \& {Basri}(2003)}]{mohanty:2003}
+{Mohanty} S., {Basri} G., 2003, in  {Brown} A., {Harper} G.~M., and
+{Ayres} T.~R., eds., The Future of Cool-Star Astrophysics: 12th 
+  Cambridge Workshop on Cool Stars, Stellar Systems, and the Sun,
+  Univ. Colorado, Boulder,  2003, p. 683
+
+\bibitem[{{Mohanty} {et~al.}(2005){Mohanty}, {Jayawardhana}, \&
+  {Basri}}]{mohanty:2005}
+{Mohanty} S., {Jayawardhana} R., {Basri} G., 2005, \apj, 626, 498
+
+\bibitem[{{Muzerolle} {et~al.}(2003){Muzerolle}, {Hillenbrand}, {Calvet},
+  {Brice{\~n}o}, \& {Hartmann}}]{muzerolle:2003}
+{Muzerolle} J., {Hillenbrand} L., {Calvet} N., {Brice{\~n}o} C., {Hartmann} L.,
+  2003, \apj, 592, 266
+
+\bibitem[{{Padoan} \& {Nordlund}(2002)}]{padoan:2002}
+{Padoan} P., {Nordlund} {\AA}., 2002, \apj, 576, 870
+
+\bibitem[{{Palla} \& {Baraffe}(2005)}]{palla:2005}
+{Palla} F., {Baraffe} I., 2005, \aap, 432, L57
+
+\bibitem[{{Pinfield} {et~al.}(2003){Pinfield}, {Dobbie}, {Jameson}, {Steele},
+  {Jones}, \& {Katsiyannis}}]{pinfield:2003}
+{Pinfield} D.~J., {Dobbie} P.~D., {Jameson} R.~F., {Steele} I.~A., {Jones}
+  H.~R.~A., {Katsiyannis} A.~C., 2003, \mnras, 342, 1241
+
+\bibitem[{{Reipurth} \& {Clarke}(2001)}]{reipurth:2001}
+{Reipurth} B., {Clarke} C., 2001, \aj, 122, 432
+
+\bibitem[{{S{\'e}gransan} {et~al.}(2003){S{\'e}gransan}, {Kervella},
+  {Forveille}, \& {Queloz}}]{segransan:2003}
+{S{\'e}gransan} D., {Kervella} P., {Forveille} T., {Queloz} D., 2003, \aap,
+  397, L5
+
+\bibitem[{{Siegler} {et~al.}(2005){Siegler}, {Close}, {Cruz}, {Mart{\'{\i}}n},
+  \& {Reid}}]{siegler:2005}
+{Siegler} N., {Close} L.~M., {Cruz} K.~L., {Mart{\'{\i}}n} E.~L., {Reid} I.~N.,
+  2005, \apj, 621, 1023
+
+\bibitem[{{Stassun} {et~al.}(2006){Stassun}, {Mathieu}, \&
+  {Valenti}}]{stassun:2006}
+{Stassun} K.~G., {Mathieu} R.~D., {Valenti} J.~A., 2006, \nat, 440, 311
+
+\bibitem[{{Tinney} \& {Reid}(1998)}]{tinney:1998}
+{Tinney} C.~G., {Reid} I.~N., 1998, \mnras, 301, 1031
+
+\bibitem[{{Udry} {et~al.}(1999){Udry}, {Mayor}, \& {Queloz}}]{udry:1999}
+{Udry} S., {Mayor} M., {Queloz} D., 1999, in {Hearnshaw} J.~B., {Scarfe} C.~D.,
+  eds., ASP Conf. Ser. Vol.~185,  IAU Colloq.
+  170: Precise Stellar Radial Velocities, Astron. Soc. Pac., San
+  Francisco,  p. 367
+
+\bibitem[{{White} \& {Basri}(2003)}]{white:2003}
+{White} R.~J., {Basri} G., 2003, \apj, 582, 1109
+
+\bibitem[{{Whitworth} \& {Zinnecker}(2004)}]{whitworth:2004}
+{Whitworth} A.~P., {Zinnecker} H., 2004, \aap, 427, 299
+
+\bibitem[{{Wilking} {et~al.}(1999){Wilking}, {Greene}, \&
+  {Meyer}}]{wilking:1999}
+{Wilking} B.~A., {Greene} T.~P., {Meyer} M.~R., 1999, \aj, 117, 469
+
+\end{thebibliography}
 

### 2006-06-20 BD_radvel/kurosawa/kurosawa.tex
typos tidied up - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@747 25464f21-6099-402c-b30a-640f1d40d38b

@@
 association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
-cloud core. We obtained high-resolution echelle spectra at the VLT using
-Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
-epochs for each object, and measured the shifts in their RVs to
+cloud core. We obtained high-resolution echelle spectra at the
+Very Large Telescope using Ultraviolet and Visual Echelle
+Spectrograph (UVES) at two different epochs for each object,
+and measured the shifts in their RVs to
 identify candidates for binary/multiple systems in the sample. The
@@
 survey is sensitive to the binaries with separation $<0.1$~au.  We
-found 4 out of 17 objects (or $24^{+16}_{-13}$~per~cent by fraction)
+found that  4 out of 17 objects (or $24^{+16}_{-13}$~per~cent by fraction)
 show a significant RV change in 4--33~d time scale, and are 
@@
 is found to be very similar to that of the BD and VLM stars in
-Chamaeleon~I (Cha~). We also found the distribution of the mean
+Chamaeleon~I (Cha~I). We also found the distribution of the mean
 rotational velocities ($v\,\sin i$) of the 
@@
 Note that the median separation of binaries with solar-type primaries
-is 30~au \citep{duquennoy:1991}. Pioneering works on the RVs
+is 30~au \citep{duquennoy:1991}. Pioneering work on the RVs
 of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
@@
 unknown because the follow-up spectroscopic monitoring is lacking
-or still being undertaken. In addition to the follow-up observations,
+or is still being undertaken. In addition to the follow-up observations,
 the number of BDs and VLM star binary candidates needs to be increased
@@
 short-period/close binaries (once confirmed), and address whether
-there is a significant population of 'hidden' VLM companions. The
+there is a significant population of `hidden' VLM companions. The
 long term goal of this project to follow up the binary candidates
@@
 
-In Section~\ref{sec:observation-reduction}. we describe the
+In Section~\ref{sec:observation-reduction} we describe the
 observations and the data reduction. The results of radial velocity
@@
 
-We obtained high-resolution spectra with the Kueyen telescope of VLT
-(Cerro Parnal, Chile) using the UVES echelle spectrograph. The
+We obtained high-resolution spectra with the Kueyen telescope of the Very Large Telescope
+(VLT--Cerro Parnal, Chile) using the UVES echelle spectrograph. The
 observations were carried out between 2004 April 5 and 2004 May 17 in
 the service mode. For each object, spectra were obtained at two different
-epochs separated by 4--33~d. For each object at a
-given night, two separate spectra are obtained consecutively. This
+epochs separated by 4--33~d. For each object on a
+given night, two separate spectra were obtained consecutively. This
 allows us to derive more reliable uncertainty estimates in the RV
@@
 
-\caption{Summary of known properties of the targets from literatures: a.~\citet{luhman:1999}
+\caption{Summary of known properties of the targets from literature: a.~\citet{luhman:1999}
 (original list for $\rho$~Oph), b.~\citet*{ardila:2000} (original
@@
 uncertainties in RVs cased by the uncertainties in the flux levels.
-We have also used an alternative method of estimating
-$\sigma_{\mathrm{RRV}}$ values as described in
-(c.f.~\citealt{joergens:2006}). The standard deviations of the mean of
-the two independent RV measurements obtained from the two consecutive
-spectra taken in the same night were assigned as the uncertainties
-($\sigma_{\mathrm{RRV}}$). Although not shown here, we found that the
-results from the two methods agree each other quite well. 
-Note that for finding a shift in the radial velocities from two
-different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
-only requires the relative (with respect to a template) RV values.
-The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
-two epochs are also given in the same table.
+We also estimated the RV uncertainties using the standard deviations on the
+mean of the two independent RV measurements obtained from the two
+consecutive spectra taken on the same night (c.f.~\citealt{joergens:2006}).
+We found that these estimates agreed well with those obtained from
+the Monte Carlo method. The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
+two epochs are also given in Table~\ref{tab:summary_results}.
 
@@
 velocities (with respect to a template). 
-Alternatively, we also computed the cross-correlation functions of
-spectra of a same object (instead of using the spectra of the template
-LHS~49) from two different epochs in order to find
+We also  cross-correlated object spectra from the two epochs 
+(instead of using the spectra of the template LHS~49)  in order to find
 $\Delta\mathrm{RV}$. The resulting cross-correlation functions were
 found to be too noisy (due to the relatively low S/N in the object
-spectra), and the peak positions of the cross-correlation curves were
-not reliably located.
+spectra) for the  peak positions of the cross-correlation curves to be
+reliably located.
 
@@
 measurements of the higher mass counter parts (T~Tauri stars) in
-Upper Sco OB association. This is planned for a near future investigation
-as this is important for the study of the mass dependency of the kinematics
+Upper Sco OB association. This is planned for  future investigation
+since this is important for the study of the mass dependency of the kinematics
 in a young stellar cluster.
@@
 $\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
-reasonably matches the expected distribution.  This leas us to
+reasonably matches the expected distribution.  This leads us to
 conclude that the uncertainty estimates in RV values are 
@@
 given night, two separate spectra are obtained consecutively (with
-time separations of $\sim 0.5$~h.). Before co-adding the two spectra
-together, we have measured the RV from each spectrum to check if there
-is a large jump in the RV measurements in short
+time separations of $\sim 0.5$~h.). We have measured the RV from each spectrum to check if there
+is a large jump in the RV measurements on a  short
 time-scale. The size of the shifts in the RV values measured in the two
@@
 a candidate for a multiple system. This may indicate that it is  
-a triple system with one of objects located within 0.1~au from the
+a triple system with one of the objects located within 0.1~au of the
 primary.  In addition, we identify USco~112 and 128 as binary
 candidates, but they did not find them as multiples. Further they found USco~67, 75,
-130 and 132 as non-multiple, and so did we.
+130 and 132 as non-multiple, as did we.
 

### 2006-06-20 BD_radvel/kurosawa/kurosawa.tex
Minor change.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@748 25464f21-6099-402c-b30a-640f1d40d38b

@@
 from the follow-up radial velocity measurements, they were able to determined
-the precise oribital and physical parameters of the system.  The projected
+the precise orbital and physical parameters of the system.  The projected
 semimajor axis and the period of the binary are found as
@@
 
-In Section~\ref{sec:observation-reduction} we describe the
+In Section~\ref{sec:observation-reduction}, we describe the
 observations and the data reduction. The results of radial velocity
@@
 given night, two separate spectra are obtained consecutively (with
-time separations of $\sim 0.5$~h.). We have measured the RV from each spectrum to check if there
-is a large jump in the RV measurements on a  short
-time-scale. The size of the shifts in the RV values measured in the two
-consecutive spectra are found in between $0.02\pm0.10$ (USco~128)
-and  $2.04\pm1.67\,\kmps$ (USco~66), and the average size of the
-shifts $0.36\,\kmps$, which is much smaller than the
+time separations of $\sim 0.5$~h.). We have measured the RV from each
+spectrum to check if there is a large jump in the RV measurements on a
+short time-scale. The size of the shifts in the RV values measured in
+the two consecutive spectra are found in between $0.02\pm0.10$
+(USco~128) and  $2.04\pm1.67\,\kmps$ (USco~66), and the average size
+of the shifts $0.36\,\kmps$, which is much smaller than the 
 expected RV variation based on the models of \citet{palla:2005};

### 2006-08-17 BD_radvel/mn060888mj_rev/kurosawa.tex
started revising after ref's comment.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@781 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-06-20 BD_radvel/kurosawa/kurosawa.tex
@@
 \usepackage{graphicx}
+\usepackage{color}
 
@@
 the cross-correlation technique, but also the validity of the wavelength
-calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}18.18\pm0.62\,\kmps$
+calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}19.18\pm0.62\,\kmps$
 which is in good agreement with the Elodie radial velocity measurement
@@
 procedure: (1)~add random gaussian deviate noise to the object spectra using the
-corresponding variance spectra, (2)~compute the cross-correlation
+corresponding variance spectra\footnote{\textcolor{red}{Defined by the variance of the
+chi-square fit to the signal obtained during optimum extraction.}}, 
+(2)~compute the cross-correlation
 curve using the spectra with added noise and the template, (3)~measure
@@
 (3)~designate the object as a non-constant RV object or a binary
-candidate if $p<10^{-3}$ (1~per~cent).  When computing $\chi^{2}$, we
+candidate if $p<10^{-3}$ (\textcolor{red}{0.1~per~cent}).  When computing $\chi^{2}$, we
 use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$). 
@@
   which appear in the right-most bin in the histogram. There
-  are four objects which satisfy this condition. The
-  expected distribution (dashed) for RV constant objects based on the RV
-  uncertainties in the observations (Table~\ref{tab:summary_results})
-  and based on the $\chi^{2}$ probability function is also shown for a
-  comparison.  The match between the expected distribution and the
+  are four objects which satisfy this condition. 
+  \textcolor{red}{The expected distribution (dashed) for RV constant
+  objects is also shown for a comparison.} The distribution is
+  normalized with the total number of objects that have $p<10^{-3}$.
+  The match between the expected distribution and the
   histogram is reasonable, indicating that our uncertainty estimates

### 2006-08-18 BD_radvel/mn060888mj_rev/kurosawa.tex
Th revision still in progress.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@783 25464f21-6099-402c-b30a-640f1d40d38b

@@
 Before applying the cross-correlation technique to our main targets,
-we have applied the technique to the radial velocity standard HD~140538
+we have applied the technique to the radial velocity standard
+HD~140538 \textcolor{red}{(G2.5V)}
 for which an high-accuracy RV measurement via the fixed-configuration,
-cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
+cross-dispersed \'{e}celle spectrograph Elodie \citep{baranne:1996}
 is available. This was done so to ensure not only the validity of
 the cross-correlation technique, but also the validity of the wavelength
-calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}19.18\pm0.62\,\kmps$
+calibration. In this test, we found the heliocentric 
+\textcolor{red}{
+$\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
+}
 which is in good agreement with the Elodie radial velocity measurement
 of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
+\textcolor{red}{
+  Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
+  by combining the uncertainty ($0.4~\kmps$) in the heliocentric RV of
+  the template star HD~74497 (G3V)) and the uncertainty in the
+  relative RV of HD~140538 ($0.02~\kmps$), measured with respect to
+  the template star.  Clearly, the former dominates in the uncertainty
+  in the value of $\mathrm{RV_{HD\,140538}}$ shown above. The
+  uncertainty in the heliocentric RV of the template is rather large
+  since it was determined from a few photospheric lines.
+}
 
@@
 constant population on the left side reasonably matches the expected
-curve. This reassures that our uncertainties in RV values are
-reasonable, and an additional systematic error may not be necessary in
-this analysis. 
+curve. 
+\textcolor{red}{To quantify this point, we have computed the
+chi-square probability to test the goodness of the fit of the expected
+distribution to the histogram. We restrict the fit to the first 4 bins
+from the left $\left(0 < -\log_{10}\left(p\right) < 2 \right)$ the
+histogram since the objects in the second bin from the right
+$\left(2.5 < -\log_{10}\left(p\right) < 3 \right)$ are `potentially'
+RV-variable object, although we have flagged them as the RV-constant
+objects. In this analysis, we find the probability of 0.5 which
+indicates that the fit is reasonable. Further, if we re-normalized the
+expected distribution, accounting for that fact we neglected the
+objects in the second bin from the right, we find the chi-square
+probability of the fit increases to 0.9.  This, in turn, indicates}
+that our uncertainties in RV values are reasonable, and an additional
+systematic error may not be necessary in this analysis.
+
 The boundary ($p=10^{-3}$) between the RV variable and the RV

### 2006-08-19 torus/diffusion_mod.f90
still a problem with medianing - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@784 25464f21-6099-402c-b30a-640f1d40d38b

@@ -153,7 +153,6 @@ contains
 
   subroutine gaussSeidelSweep(grid,  tol, demax, converged)
     use input_variables, only : blockhandout
-    include 'mpif.h'
     type(octal), pointer   :: thisOctal, neighbourOctal, startOctal
     type(octal), pointer  :: child 
     type(GRIDTYPE) :: grid
@@ -176,14 +175,6 @@ contains
     integer :: iOctal
     integer :: iOctal_beg, iOctal_end
     real(double) :: phi, DeltaPhi, DeltaZ, deltaR
-     logical :: dcAllocated
-     integer, dimension(:), allocatable :: octalsBelongRank
-     logical :: rankComplete
-     integer :: iRank
-     integer :: tag = 0
-     integer :: tempInt
-     real(double), allocatable :: eArray(:), tArray(:)
-     integer :: nEdens, nVoxels
 
 
     np = 1
@@ -200,26 +191,6 @@ contains
        stop
     endif
 
-    ! FOR MPI IMPLEMENTATION=======================================================
-    !  Get my process rank # 
-    call MPI_COMM_RANK(MPI_COMM_WORLD, my_rank, ierr)
-  
-    ! Find the total # of precessor being used in this run
-    call MPI_COMM_SIZE(MPI_COMM_WORLD, np, ierr)
-    
-    ! we will use an array to store the rank of the process
-    !   which will calculate each octal's variables
-    allocate(octalsBelongRank(size(octalArray)))
-    
-    if (my_rank == 0) then
-  !     print *, ' '
-  !     print *, 'Gauss-Seidel sweep  computed by ', np-1, ' processors.'
-  !     print *, ' '
-       call mpiBlockHandout(np,octalsBelongRank,blockDivFactor=1,tag=tag,&
-                            setDebug=.false.)
-    
-    endif
-    ! ============================================================================
 
     
     ! default loop indices
@@ -227,10 +198,6 @@ contains
     ioctal_end = nOctal
 
 
- if (my_rank /= 0) then
-  blockLoop: do     
- call mpiGetBlock(my_rank,iOctal_beg,iOctal_end,rankComplete,tag,setDebug=.false.)
-   if (rankComplete) exit blockLoop 
 
 
 !$OMP PARALLEL DEFAULT(NONE) &
@@ -610,55 +577,9 @@ contains
 !$OMP BARRIER
 !$OMP END PARALLEL 
 
- if (.not.blockHandout) exit blockloop
[…]

### 2006-08-19 torus/disc_hydro_mod.f90

@@ -332,7 +332,6 @@ contains
 
     use input_variables, only : variableDustsublimation, rGap
 
- include 'mpif.h'
 
 
     type(GRIDTYPE) :: grid
@@ -356,14 +355,6 @@ contains
     integer :: nOctals, nVoxels
     character(len=80) :: ofile
     real :: rGapCM
-    ! For MPI implementations
-    integer       ::   my_rank        ! my processor rank
-    integer       ::   ierr           ! error flag
-
-
-    ! FOR MPI IMPLEMENTATION=======================================================
-    !  Get my process rank # 
-    call MPI_COMM_RANK(MPI_COMM_WORLD, my_rank, ierr)
 
 
 
@@ -374,28 +365,21 @@ contains
     call findTotalMass(grid%octreeRoot, totalMass)
 
 
-    if(my_rank == 0) &
     write(*,*) "Total disc mass: ",totalMass/msol," solar masses"
 
 
-    if(my_rank == 0) then
     write(plotfile,'(a,i3.3,a)') "rho",0,".gif/gif"
     call plot_AMR_values(grid, "rho", "x-z", 0.0, plotfile, .true., .false.,boxfac=0.01)
-    endif
 
     do while(.not.converged)
     
-    if(my_rank == 0) then
        write(*,*) "Starting iteration number",nIter
        write(*,*) "Calling the lucy algorithm to get temperature..."
-    endif
 
        totalMass = 0.
        call findTotalMass(grid%octreeRoot, totalMass)
 
 
-    print *,'Process ',my_rank,' waiting to do lucy.'
-    call MPI_BARRIER(MPI_COMM_WORLD, ierr) 
 
        if (nIter == 1) then
           maxIter = 2
@@ -409,28 +393,20 @@ contains
 
 
 
-    if(my_rank == 0) &
        write(*,*) "Zeroing new density values..."
        call zeroChiline(grid%octreeRoot)       
 
-    if(my_rank == 0) then
        if (geometry == "ppdisk") open(unit=137, file='surface_density.dat', status='replace', form='formatted')
-    endif
 
-    if(my_rank == 0) &
        write(*,*) "Solving the vertical hydrostatic equilibrium..."
        drho = 0.
        call throughoutMidpane(grid, mStar, sigma0, rDisk, drho)
 
-    if(my_rank == 0) then
        if (geometry == "ppdisk") close(137)
-    endif
 
-    if(my_rank == 0) &
[…]

### 2006-08-19 torus/formal_solutions.f90

@@ -239,9 +239,7 @@ contains
        nr_wind, nr_acc, nr_core, nphi, dir_obs, dist_obs, grid, sampleFreq, opaqueCore,  &
        flux, lambda, nlam, filename, thin_disc_on, ttau_disc_on, ttau_jet_on, ttau_discwind_on, npix, &
        do_alphadisc_check, alphadisc_par, thinLine, emissOff, pos_disp) 
-    use parallel_mod
     implicit none
-    include 'mpif.h'        
     real,         intent(in)  :: lambda0       ! [A] Wavelength of the line center
     real,         intent(in)  :: mass_ion      ! mass of atom in [g]
     real(double), intent(in)  :: R_star        ! [10^10 cm] radius of a star
@@ -322,16 +320,6 @@ contains
     real(double), parameter :: a2= -0.23d0      ! coefficiets in the linear limb dakening law 
     real(double), parameter :: a0= 1.0d0-a1-a2  ! coefficiets in the linear limb dakening law 
 
-    ! For MPI implementations
-    integer             ::   my_rank            ! my processor rank
-    integer             ::   ncpu               ! The number of processes
-    integer             ::   ierr               ! error flag
-    double precision    ::  flux_sum, flux_tmp
-    integer,allocatable ::   BelongRank(:)  
-    integer             ::   tag = 0
-    logical             ::   rankComplete
-    real(double), allocatable :: buffer1(:), buffer2(:)
-    real(double)        :: buffer3(3), buffer4(3)
 
     halfboxsize = grid%octreeRoot%subcellSize 
 
@@ -427,26 +415,10 @@ contains
     flux_map(:,:) = 0.0d0
     F_core=0.0d0; F_acc=0.0d0; F_wind=0.0d0  ! ONLY rank =z has correct flux!
 
-    ! FOR MPI IMPLEMENTATION=======================================================
-    !  Get my process rank # 
-    call MPI_COMM_RANK(MPI_COMM_WORLD, my_rank, ierr)
-  
-    ! Find the total # of precessor being used in this run
-    call MPI_COMM_SIZE(MPI_COMM_WORLD, ncpu, ierr)
-    
- 
-    print *, ' '
-    print *, 'Compute_obs_line_flux routine computed by ', ncpu-1, ' processors.'
-    print *, ' '
-    print *, '         ===> RAY LOOP parallelized <=== '
-    print *, ' '
-
[…]

### 2006-08-19 torus/lucy_mod.f90

@@ -307,7 +307,6 @@ contains
     use input_variables, only : rinner, router, variableDustSublimation, zoomFactor, blockhandout
     use input_variables, only : smoothFactor, doSmoothGrid, lambdasmooth, plot_maps
     implicit none
- include 'mpif.h'
     type(GRIDTYPE) :: grid
     integer :: nSource
     integer :: iSmoothLam
@@ -388,46 +387,6 @@ contains
     integer :: noctals, nvoxels, nCellsInDiffusion
     integer :: omp_get_num_threads, omp_get_thread_num
 
-    ! For MPI implementations
-  ! For MPI implementations =====================================================
-  integer ::   my_rank        ! my processor rank
-  integer ::   n_proc         ! The number of processes
-  integer ::   ierr           ! error flag
-  integer ::   n_rmdr, m      !
-  integer ::   mphotons       ! number of photons (actual) 
-  integer ::   tempInt        !
-  real, dimension(:), allocatable :: tempRealArray
-  real, dimension(:), allocatable :: tempRealArray2
-  integer, dimension(:), allocatable :: photonBelongsRank
-  integer, parameter :: tag = 0
-  logical :: rankComplete
-    ! data space to store values from all processors
-    real, save, allocatable  :: buffer_real(:)     
-    logical, save  :: first_time = .true.
-
-!    ! find the number of the processors for the first time.    
-!    if (first_time) then
-       call MPI_COMM_SIZE(MPI_COMM_WORLD, n_proc, ierr)
-!       allocate(buffer_real(n_proc))
-!       first_time = .false.
-!    end if
-
-       allocate(buffer_real(n_proc))
-
-    ! FOR MPI IMPLEMENTATION=======================================================
-    !  Get my process rank # 
-    call MPI_COMM_RANK(MPI_COMM_WORLD, my_rank, ierr)
-  
-    ! Find the total # of precessor being used in this run
-    call MPI_COMM_SIZE(MPI_COMM_WORLD, n_proc, ierr)
-    
-    if (my_rank .eq. 0) then
-       print *, ' '
-       print *, 'Lucy radiative equilibrium routine computed by ', n_proc, ' processors.'
-       print *, ' '
-    endif
[…]

### 2006-08-19 torus/parallel_mod.f90

@@ -2,254 +2,10 @@ module parallel_mod
 
 ! subprograms used for parallel computation
 
-  !use MPI__INCLUDE
-  !use MPI
   implicit none
 
-contains  
-
-  subroutine mpiBlockHandout(nProc,unitBelongsRank,&
-                             blockDivFactor,tag,&
-                             minBlockSize,maxBlockSize,setDebug)
-    ! this routine will divide a task into many small blocks, and
-    !   hand them out to processes that request work.
-  
-    use input_variables, only: blockhandout
-    implicit none
-    include 'mpif.h'  
-  
-    integer, intent(in) :: nProc    ! the number of processes
-    integer, intent(in) :: blockDivFactor ! used to set block size
-    integer, dimension(:), intent(inout) :: unitBelongsRank
-    integer, intent(in) :: tag ! MPI tag (probably zero)
-    integer,intent(in),optional :: minBlockSize
-    integer,intent(in),optional :: maxBlockSize
-    logical,intent(in),optional :: setDebug ! print debug messages
-  
-    integer :: blockSize
-    integer :: iErr     ! error flag
-    integer :: nUnits
-    integer :: startUnit, endUnit
-    integer :: iRank
-    logical, dimension(:), allocatable :: rankComplete
-    logical :: debugInfo
-    integer, dimension(MPI_STATUS_SIZE) :: mpiStatus    
-    character*(MPI_MAX_ERROR_STRING) :: errorString
-        !    ^ outdated, but required to work with MPI wrapper 
-    integer :: errorLength, count
 
 
-    if (present(setDebug)) then
-      debugInfo = setDebug
-    else
-      debugInfo = .false.
-    end if
-    
-    if (present(minBlockSize)) then
-      if (minBlockSize > nUnits) then
-        print *, 'Warning: in ''mpiBlockHandout'', minBlockSize > nUnits'
-      end if
-    end if
-    
-    unitBelongsRank = -999
-    nUnits = SIZE(unitBelongsRank)
-    startUnit = 1
-    
-    blockSize = nUnits / (nProc * blockDivFactor)
-
-    ! force blockSize to be within sensible limits
-    blockSize = MAX(1,blockSize)
-    if (present(minBlockSize)) blockSize = MAX(minBlockSize,blockSize) 
[…]

### 2006-08-19 torus/stateq_mod.f90

@@ -2870,9 +2870,7 @@ contains
 
     USE input_variables, ONLY: LyContThick, statEq1stOctant, blockHandout
   
-    use parallel_mod
     implicit none
-    include 'mpif.h'
     type(GRIDTYPE),intent(inout):: grid      
     character(len=*),intent(in) :: contfile      ! filename for continuum flux
     logical,intent(in)          :: lte           ! true if lte conditions
@@ -2927,10 +2925,6 @@ contains
     real(double) :: dummy
     integer       ::   ioctal_beg, ioctal_end  
     logical :: mapped_already
-    ! For MPI implementations
-    integer       ::   my_rank        ! my processor rank
-    integer       ::   np             ! The number of processes
-    integer       ::   ierr           ! error flag
 
     numLTEsubcells = 0
 
@@ -2969,11 +2963,6 @@ contains
 
 
     ! 2-D case for rotationally symmetric geometries
-        print *, "grid%statEq2d=", grid%statEq2d
-        print *, "grid%amr2dOnly=", grid%amr2dOnly
-        print *, "statEq1stOctant=", statEq1stOctant
-        print *, "lte=", lte
-        print *, "recalcPrevious=", recalcPrevious
     mapped_already =.false.
     if (grid%statEq2d .and. (.not. lte) ) then
        ! we first get a list of the octals that lie in a plane across the
@@ -3102,7 +3091,6 @@ contains
     ! takes an array of pointers to octals, and calculates the statistical 
     !   equilibrium. 
 
-    include 'mpif.h'
     type(octalWrapper), intent(inout), dimension(:) :: octalArray
     logical, intent(in) :: setupCoeffs  ! whether to store the departure 
                                         !   coefficients in the octal structure.
@@ -3123,12 +3111,6 @@ contains
 !    integer, parameter :: ntrial_max = 20
     integer, parameter :: ntrial_max = 50
     logical :: be_gentle
-     logical :: dcAllocated
-     integer, dimension(:), allocatable :: octalsBelongRank
-     logical :: rankComplete
-     integer :: iRank
-     integer :: tag = 0
-     integer :: tempInt
 
     if ( firstTime .and.  (  &
          grid%geometry(1:8) == 'windtest'  .or.   &
@@ -3204,26 +3186,6 @@ contains
 
 
       
[…]

### 2006-08-19 torus/torusMain.f90

@@ -70,11 +70,8 @@
   use photoion_mod
   use formal_solutions
 !$mpi   use parallel_mod
-   !use MPI__INCLUDE   
-   !use MPI
 
   implicit none
-   include 'mpif.h'  
 
   integer, parameter :: nOuterLoop = 10
   integer :: iOuterLoop
@@ -432,40 +429,10 @@
   integer :: iInner_beg, iInner_end ! beginning and end of the innerPhotonLoop index.
 !  integer ::   iphase_beg, iphase_end  ! the beginning and the end of the phase index.
 
-  ! For MPI implementations =====================================================
-  integer ::   my_rank        ! my processor rank
-  integer ::   n_proc         ! The number of processes
-  integer ::   ierr           ! error flag
-  integer ::   n_rmdr, m      !
-  integer ::   mphotons       ! number of photons (actual) 
-  integer ::   tempInt        !
-  real, dimension(:), allocatable :: tempRealArray
-  real, dimension(:), allocatable :: tempRealArray2
-  real(double), dimension(:), allocatable :: tempDoubleArray
-  real(double), dimension(:), allocatable :: tempDoubleArray2
-  integer, dimension(:), allocatable :: photonBelongsRank
-  integer, parameter :: tag = 0
-  logical :: rankComplete
-
-  ! FOR MPI IMPLEMENTATION=======================================================
-  !  initialize the system for running MPI
-  call MPI_INIT(ierr) 
-
-  !  Get my process rank # 
-  call MPI_COMM_RANK(MPI_COMM_WORLD, my_rank, ierr)
-  
-  ! Find the total # of precessor being used in this run
-  call MPI_COMM_SIZE(MPI_COMM_WORLD, n_proc, ierr)
-  
-  call unixGetHostname(tempChar, tempInt) 
-  print *, 'Process ', my_rank,' running on host ',TRIM(ADJUSTL(tempChar))
-  
-  !===============================================================================
 
 
   !
   ! For time statistics
-  if (my_rank==1) &
   call tune(6, "Torus Main") ! start a stopwatch  
 
 
@@ -477,10 +444,6 @@
   allocate(iSeed(1:iSize))
   call random_seed(get=iSeed)
 
-     call MPI_BARRIER(MPI_COMM_WORLD, ierr) 
-     call MPI_BCAST(iSeed, iSize, MPI_INTEGER, 0, MPI_COMM_WORLD, ierr)
-  call random_seed(put=iseed)
-! write(*,*) my_rank,"random seed",iseed(1:isize)
[…]

### 2006-08-19 BD_radvel/mn060888mj_rev/kurosawa.tex
Still doing the revision after the ref's comment.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@785 25464f21-6099-402c-b30a-640f1d40d38b

@@
 with respect to the template star LHS~049 and the average radial
-velocities ($\overline{\mathrm{RV}}$) are also given. }
+velocities ($\overline{\mathrm{RV}}$) are also given.  
+\textcolor{red}{
+N.B.~the uncertainties listed along with the heliocentric radial
+velocities in column~4 and 6 includes the uncertainty in the
+heliocentric RV of the template star, but $\sigma_{\mathrm{RRV}}$
+do not.
+}
+}
 
@@
   by combining the uncertainty ($0.4~\kmps$) in the heliocentric RV of
-  the template star HD~74497 (G3V)) and the uncertainty in the
+  the template star HD~74497 (G3V) and the uncertainty in the
   relative RV of HD~140538 ($0.02~\kmps$), measured with respect to
@@
 
-The result of the heliocentric RV measurements (from two epochs for
-each object) is summarised in Table~\ref{tab:summary_results} along
-with the uncertainties. The table also lists the uncertainties in
-the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
-is the uncertainty of RV with respect to the template star. 
+\textcolor{red}{
+  The result of the heliocentric RV measurements (from two
+  epochs for each object) is summarised in Table 2 along with their
+  uncertainties.  The uncertainties listed with the
+  absolute/heliocentric RV values in the 4-th and 6-th columns in the
+  table include the uncertainty of the absolute/heliocentric RV of
+  the template star. On the other hand, the uncertainties in the
+  `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) listed in the 5-th
+  column do not include the uncertainty of the template star. It is
+  $\sigma_{\mathrm{RRV}}$ that is relevant for the identification of RV variable
+  objects.  
+}
+
 To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
@@
 computing $\Delta\mathrm{RV}$ we do not require the knowledge of
-absolute radial velocities, but only the relative
+absolute\textcolor{red}{/heliocentric} radial velocities, but only the relative
 velocities (with respect to a template). 
@@
 \textcolor{red}{To quantify this point, we have computed the
-chi-square probability to test the goodness of the fit of the expected
+$\chi^{2}$ probability to test the goodness of the fit of the expected
 distribution to the histogram. We restrict the fit to the first 4 bins
@@
 expected distribution, accounting for that fact we neglected the
-objects in the second bin from the right, we find the chi-square
+objects in the second bin from the right, we find the $\chi^{2}$
 probability of the fit increases to 0.9.  This, in turn, indicates}
@@
   The match between the expected distribution and the
-  histogram is reasonable, indicating that our uncertainty estimates
+  histogram is reasonable \textcolor{red}{(c.f.~Section~\ref{sub:Radial-velocities})},
+  indicating that our uncertainty estimates 
   in RV values are also reasonable.  }

### 2006-08-19 BD_radvel/mn060888mj_rev/kurosawa.tex
RK's revision finished.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@786 25464f21-6099-402c-b30a-640f1d40d38b

@@
 of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
-the upper limit for the systematic error in the RV measurements \citep{bailer-jones:2004}.
-The accuracy of the wavelength calibration will be demonstrated in
-the RV measurements of a RV standard in the following section. A typical
+the upper limit for the systematic error in the RV measurements
+\citep{bailer-jones:2004}.
+\textcolor{red}{
+As we will find out in the following section
+(Section~\ref{sub:Radial-velocities}), the systematic error may be
+ignored based on result of the $\chi^{2}$ probability analysis we
+performed without the introduction of assumed systematic error.
+}
+A typical
 signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
@@
 spectra.
+
+\textcolor{red}{
+In addition to the main targets in Table~\ref{tab:literatures}, we
+also obtained the spectra of LHS~49 (on 2004-April-17) and HD~140538
+(on 2004-May-06), which are the RV template and the RV standard
+stars respectively.  These data were obtained using the same telescope
+and the same instrument set up as for our main targets.  The S/N of
+the both objects were about 60. 
+}
 
@@
 curve. 
-\textcolor{red}{To quantify this point, we have computed the
+\textcolor{red}{
+To quantify this point, we have computed the
 $\chi^{2}$ probability to test the goodness of the fit of the expected
 distribution to the histogram. We restrict the fit to the first 4 bins
-from the left $\left(0 < -\log_{10}\left(p\right) < 2 \right)$ the
+from the left $\left(0 < -\log_{10}p < 2 \right)$ the
 histogram since the objects in the second bin from the right
-$\left(2.5 < -\log_{10}\left(p\right) < 3 \right)$ are `potentially'
+$\left(2.5 < -\log_{10}p < 3 \right)$ are `potentially'
 RV-variable object, although we have flagged them as the RV-constant
@@
 objects in the second bin from the right, we find the $\chi^{2}$
-probability of the fit increases to 0.9.  This, in turn, indicates}
+probability of the fit increases to 0.9.  This, in turn, indicates
 that our uncertainties in RV values are reasonable, and an additional
 systematic error may not be necessary in this analysis. 
+}
+
+\textcolor{red}{
+There are two possible
+source of systematic errors: (1)~the RV shifts caused by surface/atmospheric
+activity, and (2)~the RV shifts due to the limit of the stability of
+autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
+negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
+The size of RV errors caused by (2) is expected to be $<1\,\kmps$
+\citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
+additional systematic error was not needed to be added to the RV
+uncertainties of \citet{joergens:2006} who used the same instruments
+as ours, and used the same method of estimating the
+uncertainties.
+}
 
@@
 objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
-a non-member). The gaussian fit (dashed) of the radial velociity
+a non-member). The gaussian fit (dashed) of the radial velocity
 distribution gives a standard deviation of $1.0\,\kmps$ and the peak
@@
 Using the $v\,\sin i$ data in \citet{joergens:2001}, the same histogram
-bin size used for UScoOB obects and a log-normal fit, we find the
+bin size used for UScoOB objects and a log-normal fit, we find the
 $v\,\sin i$ distribution of the BD and VLM stars (8 objects) in Cha~I
@@
 rotational velocity distribution gives a standard deviation
-$27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
+$27.8\,\kmps$ and the peak position $16.9\,\kmps$.}
 \label{fig:vrot_histrogram}
@@
 of the primary ($V_{1}$), (2)~evolve the orbit by the time separation
-of the RV measuremets used in the observations for this object, and
+of the RV measurements used in the observations for this object, and
 take another simulated measurement of RV ($V_{2}$), (3)~from $V_{1}$,
@@
 
-In Section~\ref{sub:Radial-velocities}
-(see Fig.~\ref{fig:chisq-test}), we found the histogram of the
-$\chi^{2}$ probability $p$, for the RV data fit assuming constant RV,
-reasonably matches the expected distribution.  This leads us to
-conclude that the uncertainty estimates in RV values are 
-reasonable.  There are two possible
-source of errors: (1)~the RV shifts caused by surface/atmospheric
-activity, and (2)~the RV shifts due to the limit of the stability of
-autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
-negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
-The size of RV errors caused by (2) is expected to be $<1\,\kmps$
-\citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
-additional systematic error was not needed to be added to the RV
-uncertainties of \citet{joergens:2006} who used the same instruments
-as ours, and used the same method of estimating the
-uncertainties. Hence, we expect the systematic error to be much
-smaller than $1\,\kmps$ if one is required.
-
 An alternative explanation for the RV variations found in the binary
@@
 \citet{palla:2005}. They studied the non-adiabatic, linear
-instability of very VLM stars and BD during the deturium burning phase
+instability of very VLM stars and BD during the deuterium burning phase
 in the core, and found unstable fundamental modes in the time-scale
@@
 i.e. without correcting for bias. 
+\textcolor{red}{
+Finally, we note that the binary fraction found in this paper may be
+over-estimated because of the nature of our survey (magnitude-limited
+and incomplete), hence because of a possible bias towards the brighter
+objects.
+}
 
@@
 
-We thank the staff of VLT of the ESO for carrying out the observations
+We would like to thank the anonymous referee for constructive
+comments and suggestions for improving the clarity of the manuscript.
+We also thank the staff of VLT of the ESO for carrying out the observations
 in service mode. RK is grateful for Rob Jeffries  and Tim Naylor for helpful
@@
 \bibitem[{{Basri} \& {Reiners}(2006)}]{basri:2006}
-{Basri} G., {Reiners} A., 2006, preprint (astro-ph/0604259)
+{Basri} G., {Reiners} A., 2006, \aj, 132, 663
 
@@
 % LocalWords:  LL ESO interorder autoguiding FWHM jones Oph wilking mohanty Sp
-% LocalWords:  GY USco LHS HJD gaussian Cen garcia sanchez HD RRV pc CCF exp
-% LocalWords:  obs
+% LocalWords:  GY USco LHS HJD gaussian Cen garcia sanchez HD RRV pc CCF exp AJ
+% LocalWords:  obs ApJ PASP MNRAS Chamaeleon semimajor siegler Praesepe stassun
+% LocalWords:  mccaughrean segransan tinney palla kenyon Jeffries Naylor Bromm
+% LocalWords:  natexlab Reiners Bonnell Moraux Brandner Baraffe ndez McElwain
+% LocalWords:  astro ph de Zeeuw de Zeeuw de Bruijne Hoogerwerf Lub Blaauw
+% LocalWords:  Battrick

### 2006-08-20 BD_radvel/mn060888mj_rev/kurosawa.tex
Finished my revision (RK).
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@787 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-\section{Observations}
-
-\label{sec:observation-reduction}
-
-Our sample consists of 18 young, very low-mass objects: 15 objects in
-the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$,
-\citealt{dezeeuw:1999}) from the list of \citet*{ardila:2000} and 3
-objects in the $\rho$~Ophiuchi cloud core ($\mathrm{d\approx150\,
-pc}$, \citealt{dezeeuw:1997}) from \citet{luhman:1999}. The spectral
-type of the objects range between M5 and M8.5, and the age
-$<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999}; \citealt{ardila:2000};
-\citealt{muzerolle:2003}; \citealt{kraus:2005}).  The sample is not
-complete, and the selection was solely based on brightness and the
-observability. The basic properties of the targets based on the
-literature is summarised in Table~\ref{tab:literatures}.
-
-We obtained high-resolution spectra with the Kueyen telescope of the Very Large Telescope
-(VLT--Cerro Parnal, Chile) using the UVES echelle spectrograph. The
-observations were carried out between 2004 April 5 and 2004 May 17 in
-the service mode. For each object, spectra were obtained at two different
-epochs separated by 4--33~d. For each object on a
-given night, two separate spectra were obtained consecutively. This
-allows us to derive more reliable uncertainty estimates in the RV
-values of our targets (c.f.~\citealt{joergens:2006}).  The data were
-obtained using the red arm of UVES spectrograph with two mosaic CCDs
-(EEV + MIT/LL with 2k$\times$4k pixels). The wavelength coverage of
-6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$ were
-used. The slit width and length of 1'' and 12'' were used respectively
-with a typical seeing of 0.8''.
-
-The data were reduced via the standard ESO pipeline procedures for
-UVES echelle spectra. In summary, the data were corrected for bias,
-interorder background, sky background, sky emission lines and cosmic
-ray hits. They were then flattened, optimally extracted, and finally
-the different orders were merged. No binning was performed to achieve
-high resolution required for the RV measurements. The wavelength was
-calibrated using the Thorium-Argon arc spectra with a typical value
-of the standard deviation of the dispersion solution of 5~m\AA\,
-which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
-However, the autoguiding of the telescope keeps the star at the centre
-of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
-the upper limit for the systematic error in the RV measurements
-\citep{bailer-jones:2004}.
-\textcolor{red}{
-As we will find out in the following section
-(Section~\ref{sub:Radial-velocities}), the systematic error may be
-ignored based on result of the $\chi^{2}$ probability analysis we
-performed without the introduction of assumed systematic error.
-}
-A typical
-signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
-15, and the heliocentric velocity correction was applied to the final
-spectra.
-
-\textcolor{red}{
-In addition to the main targets in Table~\ref{tab:literatures}, we
-also obtained the spectra of LHS~49 (on 2004-April-17) and HD~140538
-(on 2004-May-06), which are the RV template and the RV standard
-stars respectively.  These data were obtained using the same telescope
-and the same instrument set up as for our main targets.  The S/N of
-the both objects were about 60. 
-}
-
-%==========================================
-
+%==========================================
 \begin{table*}
@@
 
+\section{Observations}
+
+\label{sec:observation-reduction}
+
+Our sample consists of 18 young, very low-mass objects: 15 objects in
+the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$,
+\citealt{dezeeuw:1999}) from the list of \citet*{ardila:2000} and 3
+objects in the $\rho$~Ophiuchi cloud core ($\mathrm{d\approx150\,
+pc}$, \citealt{dezeeuw:1997}) from \citet{luhman:1999}. The spectral
+type of the objects range between M5 and M8.5, and the age
+$<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999}; \citealt{ardila:2000};
+\citealt{muzerolle:2003}; \citealt{kraus:2005}).  The sample is not
+complete, and the selection was solely based on brightness and the
+observability. The basic properties of the targets based on the
+literature is summarised in Table~\ref{tab:literatures}.
+
+We obtained high-resolution spectra with the Kueyen telescope of the Very Large Telescope
+(VLT--Cerro Parnal, Chile) using the UVES echelle spectrograph. The
+observations were carried out between 2004 April 5 and 2004 May 17 in
+the service mode. For each object, spectra were obtained at two different
+epochs separated by 4--33~d. For each object on a
+given night, two separate spectra were obtained consecutively. This
+allows us to derive more reliable uncertainty estimates in the RV
+values of our targets (c.f.~\citealt{joergens:2006}).  The data were
+obtained using the red arm of UVES spectrograph with two mosaic CCDs
+(EEV + MIT/LL with 2k$\times$4k pixels). The wavelength coverage of
+6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$ were
+used. The slit width and length of 1'' and 12'' were used respectively
+with a typical seeing of 0.8''.
+
+The data were reduced via the standard ESO pipeline procedures for
+UVES echelle spectra. In summary, the data were corrected for bias,
+interorder background, sky background, sky emission lines and cosmic
+ray hits. They were then flattened, optimally extracted, and finally
+the different orders were merged. No binning was performed to achieve
+high resolution required for the RV measurements. The wavelength was
+calibrated using the Thorium-Argon arc spectra with a typical value
+of the standard deviation of the dispersion solution of 5~m\AA\,
+which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
+However, the autoguiding of the telescope keeps the star at the centre
+of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
+the upper limit for the systematic error in the RV measurements
+\citep{bailer-jones:2004}.
+\textcolor{red}{
+As we will find out in the following section
+(Section~\ref{sub:Radial-velocities}), the systematic error may be
+ignored based on the result of the $\chi^{2}$ probability analysis we
+performed without the introduction of an assumed systematic error.
+}
+A typical
+signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
+15, and the heliocentric velocity correction was applied to the final
+spectra.
+
+\textcolor{red}{
+In addition to the main targets in Table~\ref{tab:literatures}, we
+also obtained the spectra of LHS~49 (on 2004-April-17) and HD~140538
+(on 2004-May-06), which are the RV template and the RV standard
+stars respectively.  These data were obtained using the same telescope
+and the same instrument set up as for our main targets.  The S/N of
+the both objects were about 60. 
+}
+
 \section{Results}
@@
 N.B.~the uncertainties listed along with the heliocentric radial
-velocities in column~4 and 6 includes the uncertainty in the
-heliocentric RV of the template star, but $\sigma_{\mathrm{RRV}}$
-do not.
+velocities in column~4 and 6 include the uncertainty in the
+heliocentric RV of the template star, but $\sigma_{\mathrm{RRV}}$ in
+column~5 do not.
 }
@@
   uncertainty in the heliocentric RV of the template is rather large
-  since it was determined from a few photospheric lines.
+  because it was determined from a few photospheric lines.
 }
@@
 \textcolor{red}{
-  The result of the heliocentric RV measurements (from two
-  epochs for each object) is summarised in Table 2 along with their
-  uncertainties.  The uncertainties listed with the
-  absolute/heliocentric RV values in the 4-th and 6-th columns in the
-  table include the uncertainty of the absolute/heliocentric RV of
-  the template star. On the other hand, the uncertainties in the
-  `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) listed in the 5-th
-  column do not include the uncertainty of the template star. It is
-  $\sigma_{\mathrm{RRV}}$ that is relevant for the identification of RV variable
-  objects.  
+  The result of the heliocentric RV measurements (from two epochs for
+  each object) is summarised in Table 2 along with their
+  uncertainties.  The uncertainties listed in columns~4 and 6 along
+  with the absolute/heliocentric RV values include the uncertainty of
+  the absolute/heliocentric RV of the template star. On the other
+  hand, the uncertainties in the `relative' radial velocities
+  ($\sigma_{\mathrm{RRV}}$) listed in column~5 of the table do not
+  include the uncertainty of the template star. It is
+  $\sigma_{\mathrm{RRV}}$ that is relevant for the identification of
+  RV variable objects.
 }
@@
 corresponding variance spectra\footnote{\textcolor{red}{Defined by the variance of the
-chi-square fit to the signal obtained during optimum extraction.}}, 
+$\chi^{2}$ fit to the signal obtained during optimum extraction \citep[c.f.][]{horne:1986}.}}, 
 (2)~compute the cross-correlation
@@
 \textcolor{red}{
-To quantify this point, we have computed the
+To quantify this point, we compute the
 $\chi^{2}$ probability to test the goodness of the fit of the expected
 distribution to the histogram. We restrict the fit to the first 4 bins
-from the left $\left(0 < -\log_{10}p < 2 \right)$ the
+from the left $\left(0 < -\log_{10}p < 2 \right)$ of the
 histogram since the objects in the second bin from the right
 $\left(2.5 < -\log_{10}p < 3 \right)$ are `potentially'
-RV-variable object, although we have flagged them as the RV-constant
+RV-variable, although we have flagged them as the RV-constant
 objects. In this analysis, we find the probability of 0.5 which
@@
 There are two possible
-source of systematic errors: (1)~the RV shifts caused by surface/atmospheric
+sources of systematic errors: (1)~the RV shifts caused by surface/atmospheric
 activity, and (2)~the RV shifts due to the limit of the stability of
@@
 over-estimated because of the nature of our survey (magnitude-limited
-and incomplete), hence because of a possible bias towards the brighter
+and incomplete), and because of a possible bias towards brighter
 objects.
@@
 {Guenther} E.~W., {Wuchterl} G., 2003, \aap, 401, 677
+
+\bibitem[{{Horne}(1986)}]{horne:1986}
+{Horne} K., 1986, \pasp, 98, 609
 

### 2006-08-21 BD_radvel/mn060888mj_rev/kurosawa.tex
Still working on the tim's revision.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@790 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \textcolor{red}{
-As we will find out in the following section
+As we will demonstrate in the following section
 (Section~\ref{sub:Radial-velocities}), the systematic error may be
@@
   Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
-  by combining the uncertainty ($0.4~\kmps$) in the heliocentric RV of
-  the template star HD~74497 (G3V) and the uncertainty in the
-  relative RV of HD~140538 ($0.02~\kmps$), measured with respect to
-  the template star.  Clearly, the former dominates in the uncertainty
-  in the value of $\mathrm{RV_{HD\,140538}}$ shown above. The
-  uncertainty in the heliocentric RV of the template is rather large
-  because it was determined from a few photospheric lines.
+  by combining (in quadrature) the uncertainty ($0.4~\kmps$) in the
+  heliocentric RV of the template star HD~74497 (G3V) and the
+  uncertainty in the relative RV of HD~140538 ($0.02~\kmps$), measured
+  by cross correlation with the template star.  Clearly, the former
+  dominates in the uncertainty in the value of
+  $\mathrm{RV_{HD\,140538}}$ shown above. The uncertainty in the
+  heliocentric RV of the template is rather large because it was
+  determined from a few photospheric lines.
 }
@@
 \textcolor{red}{
-  The result of the heliocentric RV measurements (from two epochs for
-  each object) is summarised in Table 2 along with their
-  uncertainties.  The uncertainties listed in columns~4 and 6 along
-  with the absolute/heliocentric RV values include the uncertainty of
-  the absolute/heliocentric RV of the template star. On the other
-  hand, the uncertainties in the `relative' radial velocities
-  ($\sigma_{\mathrm{RRV}}$) listed in column~5 of the table do not
-  include the uncertainty of the template star. It is
+  The results of the heliocentric RV measurements (from two epochs for
+  each object) are summarised in Table 2 along with their
+  uncertainties.  The uncertainties listed in columns~4 and 6 include
+  the uncertainty of the absolute RV of the template star, added in
+  quadrature with the uncertainty found from the cross correlation
+  analysis. On the other hand, the uncertainties in the relative
+  radial velocities ($\sigma_{\mathrm{RRV}}$) listed in column~5 of
+  the table \emph{do not} include the uncertainty of the template star. It is
   $\sigma_{\mathrm{RRV}}$ that is relevant for the identification of
@@
 that our uncertainties in RV values are reasonable, and an additional
-systematic error may not be necessary in this analysis. 
+systematic error is not necessary in this analysis. 
 }
-
 \textcolor{red}{
-There are two possible
-sources of systematic errors: (1)~the RV shifts caused by surface/atmospheric
-activity, and (2)~the RV shifts due to the limit of the stability of
-autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
-negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
-The size of RV errors caused by (2) is expected to be $<1\,\kmps$
-\citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
-additional systematic error was not needed to be added to the RV
-uncertainties of \citet{joergens:2006} who used the same instruments
-as ours, and used the same method of estimating the
-uncertainties.
+The assertion is supported by the re-analysis of BD RVs, obtained by
+\citet{joergens:2006} who used the same instruments setup
+as ours, by \citet{maxted:2005}. 
 }

### 2006-08-22 BD_radvel/mn060888mj_rev/kurosawa.tex
Version ok-ed by Stu. Waiting for Tim's OK sign.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@791 25464f21-6099-402c-b30a-640f1d40d38b

@@
   \textcolor{red}{The expected distribution (dashed) for RV constant
-  objects is also shown for a comparison.} The distribution is
-  normalized with the total number of objects that have $p<10^{-3}$.
+  objects is also shown for a comparison. The distribution is
+  normalized with the total number of objects that have $p<10^{-3}$}.
   The match between the expected distribution and the
@@
 \textcolor{red}{
-Finally, we note that the binary fraction found in this paper may be
-over-estimated because of the nature of our survey (magnitude-limited
-and incomplete), and because of a possible bias towards brighter
-objects.
+It is possible that out binary fraction is an overestimate since we
+are biased to brighter objects. However the lack of a double-lined
+system suggests that a primary-to-secondary luminosity ratio of $\gg 1$
+for the RV variables found in this paper. 
 }
@@
 % LocalWords:  natexlab Reiners Bonnell Moraux Brandner Baraffe ndez McElwain
-% LocalWords:  astro ph de Zeeuw de Zeeuw de Bruijne Hoogerwerf Lub Blaauw
-% LocalWords:  Battrick
+% LocalWords:  astro ph de Zeeuw de Zeeuw de Bruijne Hoogerwerf Lub Blaauw VLTI
+% LocalWords:  Battrick horne benedict Acknowledgements

### 2006-08-22 BD_radvel/mn060888mj_rev/kurosawa.tex
Some typos fixed. RK.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@792 25464f21-6099-402c-b30a-640f1d40d38b

@@
   by cross correlation with the template star.  Clearly, the former
-  dominates in the uncertainty in the value of
+  dominates in the uncertainty of
   $\mathrm{RV_{HD\,140538}}$ shown above. The uncertainty in the
@@
   \textcolor{red}{The expected distribution (dashed) for RV constant
-  objects is also shown for a comparison. The distribution is
-  normalized with the total number of objects that have $p<10^{-3}$}.
+  objects is also shown for a comparison, and is 
+  normalized to the total number of objects that have $p>10^{-3}$}.
   The match between the expected distribution and the
@@
 \textcolor{red}{
-It is possible that out binary fraction is an overestimate since we
-are biased to brighter objects. However the lack of a double-lined
+It is possible that our binary fraction is an overestimate since we
+are biased to brighter objects. However the lack of a double-line
 system suggests that a primary-to-secondary luminosity ratio of $\gg 1$

### 2006-08-26 BD_radvel/mn060888mj_rev/kurosawa.tex
A typo fixed. RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@793 25464f21-6099-402c-b30a-640f1d40d38b
This is the version re-submitted.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@797 25464f21-6099-402c-b30a-640f1d40d38b

@@
 of systems have a semimajor axis $<20\,\mathrm{au}$ (see also
-\citealt{siegler:2005} but \citealt{luhman:2004}). An
+\citealt{siegler:2005} but note too the results of \citealt{luhman:2004}). An
 \emph{HST} study of more than 80 field late M and L dwarfs \citep{gizis:2003}
@@
 observations were carried out between 2004 April 5 and 2004 May 17 in
-the service mode. For each object, spectra were obtained at two different
+ service mode. For each object, spectra were obtained at two different
 epochs separated by 4--33~d. For each object on a
@@
 \textcolor{red}{
-As we will demonstrate in the following section
-(Section~\ref{sub:Radial-velocities}), the systematic error may be
-ignored based on the result of the $\chi^{2}$ probability analysis we
-performed without the introduction of an assumed systematic error.
+In fact, we find that any systematic error is negligible compared to
+the random error associated with our radial velocity measurements (see
+Section~\ref{sub:Radial-velocities}).
 }
@@
 stars respectively.  These data were obtained using the same telescope
-and the same instrument set up as for our main targets.  The S/N of
+and the same instrument setup as for our main targets.  The S/N of
 the both objects were about 60. 
@@
 \textcolor{red}{
-The assertion is supported by the re-analysis of BD RVs, obtained by
-\citet{joergens:2006} who used the same instruments setup
+This assertion is supported by the re-analysis of BD RVs, obtained by
+\citet{joergens:2006} using the same instruments setup
 as ours, by \citet{maxted:2005}. 

### 2006-09-01 BD_radvel/astro-ph/kurosawa.tex
I forgot to add some files last time.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@813 25464f21-6099-402c-b30a-640f1d40d38b

--- 2006-08-26 BD_radvel/mn060888mj_rev/kurosawa.tex
@@
 \citep{bailer-jones:2004}.
-\textcolor{red}{
+\textcolor{black}{
 In fact, we find that any systematic error is negligible compared to
@@
 
-\textcolor{red}{
+\textcolor{black}{
 In addition to the main targets in Table~\ref{tab:literatures}, we
@@
 velocities ($\overline{\mathrm{RV}}$) are also given.  
-\textcolor{red}{
+\textcolor{black}{
 N.B.~the uncertainties listed along with the heliocentric radial
@@
 we have applied the technique to the radial velocity standard
-HD~140538 \textcolor{red}{(G2.5V)}
+HD~140538 \textcolor{black}{(G2.5V)}
 for which an high-accuracy RV measurement via the fixed-configuration,
@@
 calibration. In this test, we found the heliocentric 
-\textcolor{red}{
+\textcolor{black}{
 $\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
@@
 of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
-\textcolor{red}{
+\textcolor{black}{
   Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
@@
 
-\textcolor{red}{
+\textcolor{black}{
   The results of the heliocentric RV measurements (from two epochs for
@@
 procedure: (1)~add random gaussian deviate noise to the object spectra using the
-corresponding variance spectra\footnote{\textcolor{red}{Defined by the variance of the
+corresponding variance spectra\footnote{\textcolor{black}{Defined by the variance of the
 $\chi^{2}$ fit to the signal obtained during optimum extraction \citep[c.f.][]{horne:1986}.}}, 
@@
 computing $\Delta\mathrm{RV}$ we do not require the knowledge of
-absolute\textcolor{red}{/heliocentric} radial velocities, but only the relative
+absolute\textcolor{black}{/heliocentric} radial velocities, but only the relative
 velocities (with respect to a template). 
@@
 (3)~designate the object as a non-constant RV object or a binary
-candidate if $p<10^{-3}$ (\textcolor{red}{0.1~per~cent}).  When computing $\chi^{2}$, we
+candidate if $p<10^{-3}$ (\textcolor{black}{0.1~per~cent}).  When computing $\chi^{2}$, we
 use the uncertainties in the relative RV ($\sigma_{\mathrm{RRV}}$). 
@@
 curve. 
-\textcolor{red}{
+\textcolor{black}{
 To quantify this point, we compute the
@@
 }
-\textcolor{red}{
+\textcolor{black}{
 This assertion is supported by the re-analysis of BD RVs, obtained by
@@
   are four objects which satisfy this condition. 
-  \textcolor{red}{The expected distribution (dashed) for RV constant
+  \textcolor{black}{The expected distribution (dashed) for RV constant
   objects is also shown for a comparison, and is 
@@
   The match between the expected distribution and the
-  histogram is reasonable \textcolor{red}{(c.f.~Section~\ref{sub:Radial-velocities})},
+  histogram is reasonable \textcolor{black}{(c.f.~Section~\ref{sub:Radial-velocities})},
   indicating that our uncertainty estimates 
@@
 i.e. without correcting for bias. 
-\textcolor{red}{
+\textcolor{black}{
 It is possible that our binary fraction is an overestimate since we

### 2008-05-27 torus/docs/how_to_build_torus.tex
A document describing how to build torus.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1306 25464f21-6099-402c-b30a-640f1d40d38b

% This document is a brief guide to obtaining and building the 
% Torus code.
%
% Initial version by Dave Acreman, May 2008

\documentclass{article}

\usepackage{a4}

\begin{document}

\title{Building the Torus Radiative Transfer Code}
\author{David Acreman}

\maketitle

\section{Introduction}

This document describes how to build the Torus radiative transfer
code. It is assumed that you are using csh or tcsh as your UNIX
shell. The symbol \verb  \$ indicates your UNIX prompt.

\section{Getting started}

\subsection{Obtaining the code}

The torus code is managed using CVS (Concurrent Version System). To
download the code from the remote repository type: 
%
\begin{verbatim}
$ cvs -d pinky:/h/th/CVS -q co torus 
\end{verbatim}
%
You will need to have an account on pinky to be able to do this.

\subsection{Building Torus}

Torus is comes with a Makefile which can be used to 
build the code for a number of different systems. System specific
options (e.g. compiler flags) are specified in the Makefile so you
should not need to set these up, unless you are using a new system.

The environment variable \verb SYSTEM  is used to tell the Makefile
which configuration to use. For example to use the ``zen''
configuration type 
\begin{verbatim}
$ setenv SYSTEM zen 
\end{verbatim}
Alternatively you can set this environment variable in your .cshrc
file so it is always correctly set.

You can now go into the torus directory and build the code
%
\begin{verbatim}
$ cd torus
$ make
\end{verbatim}

\section{Building Torus with options}

\subsection{Make options}

Several options can be passed to the make process on the command
line, see table~\ref{table:make_options}
for a summary.

\begin{table}
  \begin{center}
    \begin{tabular}[|l|l|l|]{|l|l|l|}
\hline
    Option    & Description & Default \\
\hline
      pgplot  & link with pgplot libraries  & yes \\
      cfitsio & link with cfitsio libraries & yes \\
      debug   & switch on debugging flags   & no  \\
      profile & enable profiling            & no  \\
      static  & perform static linking      & no  \\
      trace   & use Intel trace collector   & no  \\
\hline
  \end{tabular}
\caption{Options which can be supplied to the make command when
  building torus.}
\label{table:make_options}
\end{center}
\end{table}

For example to build torus without linking to the pgplot libraries and
with debug flags enabled use
\begin{verbatim}
$ make pgplot=no debug=yes 
\end{verbatim}

You may wish to remove all files from a previous build and start from
scratch (for example if you have previously compiled with debug flags
and need to recompile without debug flags). The Makefile has an option
to clean up files from the previous build 
\begin{verbatim}
$ make clean
\end{verbatim}

\end{document}

### 2008-07-07 torus/benchmarks/sphbench/sphbench.f90
Disc benchmark set up using SPH particles.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1337 25464f21-6099-402c-b30a-640f1d40d38b

@@ -1,0 +1,131 @@
+! A test of SPH-Torus which uses particles to represent the benchmark disc 
+
+program sphbench
+
+use torus_mod, only: torus
+
+  implicit none
+
+! number of particle spaces
+  integer, parameter :: nx=100
+  integer, parameter :: ny=100
+  integer, parameter :: nz=100
+  integer, parameter :: npart=(nx+1)*(ny+1)*(nz+1)
+
+! loop and particle indices
+  integer :: i, j, k, ipart
+
+! Define double precision 
+  integer, parameter :: db = selected_real_kind(15,307)
+
+! Grid size and centre offsets in cm 
+  real(db), parameter :: xsize   = 8.0d16
+  real(db), parameter :: ysize   = 8.0d16
+  real(db), parameter :: zsize   = 8.0d16
+  real(db), parameter :: xoffset = 4.0d16
+  real(db), parameter :: yoffset = 4.0d16
+  real(db), parameter :: zoffset = 4.0d16
+
+! Cartesian x,y,z co-ordinates
+  real(db) :: x(npart), y(npart), z(npart), r
+
+! Torus arguments
+  integer, parameter :: b_idim  = npart + 1 ! Set maximum array sizes
+  integer, parameter :: b_npart = npart + 1 ! Gas particles + one point mass
+  integer, parameter :: b_nactive=-99       ! Not used
+  integer, parameter :: b_nptmass = 1       ! Number of point masses
+  integer, parameter :: b_num_gas = npart   ! Number of gas particles
+  real(kind=8) :: b_xyzmh(5,b_idim)
+  real(kind=4) :: b_rho(b_idim)
+  integer(kind=1) :: b_iphase(b_idim) 
+  real(kind=8), parameter :: b_udist=1.0 ! unit of distance
+  real(kind=8), parameter :: b_umass=1.0 ! units of mass
+  real(kind=8), parameter :: b_utime=1.0 ! Units of time
+  real(kind=8), parameter :: b_time=1.0e16_db  ! Current time, used as age of star
+  real(kind=8) :: b_temp(b_num_gas)
+  real(kind=8), parameter :: temp_min=3.0
+
+! Source parameters
+  real(db), parameter :: source_x = 0.0
+  real(db), parameter :: source_y = 0.0
+  real(db), parameter :: source_z = 0.0
+
[…]

### 2008-09-19 torus/docs/how_to_build_torus.tex
Added make depends step.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1339 25464f21-6099-402c-b30a-640f1d40d38b
fixes to disc_hydro_mod - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1441 25464f21-6099-402c-b30a-640f1d40d38b

@@
 $ cd torus
+$ make depends
 $ make
@@
 \hline
-      pgplot  & link with pgplot libraries  & yes \\
       cfitsio & link with cfitsio libraries & yes \\
@@
 
-For example to build torus without linking to the pgplot libraries and
+For example to build torus without linking to the cfitsio libraries and
 with debug flags enabled use
 \begin{verbatim}
-$ make pgplot=no debug=yes 
+$ make cfitsio=no debug=yes 
 \end{verbatim}

### 2008-09-19 torus/amr_mod.f90

@@ -136,8 +136,10 @@ CONTAINS
        if (associated(thisOctal%ionFrac)) then
           thisOctal%ionFrac(subcell,:) = parentOctal%ionFrac(parentsubcell,:)
        endif
-       thisOctal%nh(subcell) = parentOctal%nh(parentsubcell)
-       thisOctal%ne(subcell) = parentOctal%ne(parentsubcell)
+       if (associated(thisOctal%nh)) &
+            thisOctal%nh(subcell) = parentOctal%nh(parentsubcell)
+       if (associated(thisOctal%ne)) &
+            thisOctal%ne(subcell) = parentOctal%ne(parentsubcell)
 
        parentOctal%hasChild(parentsubcell) = .false.
        call interpFromParent(subcellCentre(thisOctal, subcell), thisOctal%subcellSize, grid, &
@@ -9838,7 +9840,15 @@ end function readparameterfrom2dmap
     call copyAttribute(dest%dustType, source%dustType)
     call copyAttribute(dest%oldFrac, source%oldFrac)
     call copyAttribute(dest%diffusionApprox, source%diffusionApprox)
-
+    call copyAttribute(dest%diffusionCoeff, source%diffusionCoeff)
+    call copyAttribute(dest%undersampled, source%undersampled)
+    call copyAttribute(dest%nDiffusion, source%nDiffusion)
+    call copyAttribute(dest%nDirectPhotons, source%nDirectPhotons)
+    call copyAttribute(dest%oldtemperature, source%oldtemperature)
+    call copyAttribute(dest%eDens, source%eDens)
+    call copyAttribute(dest%oldeDens, source%oldeDens)
+    call copyAttribute(dest%kappaRoss, source%kappaRoss)
+ 
     call copyAttribute(dest%nh2, source%nh2)
     call copyAttribute(dest%microturb, source%microturb)
     call copyAttribute(dest%molmicroturb, source%molmicroturb)
@@ -16258,6 +16268,7 @@ end function readparameterfrom2dmap
        thisOctal%dustTypeFraction(:,1) = 1.d0
        thisOctal%inflow = .true.
        call allocateAttribute(thisOctal%diffusionApprox, thisOctal%maxChildren)
+       call allocateAttribute(thisOctal%changed, thisOctal%maxChildren)
        call allocateAttribute(thisOctal%nDiffusion, thisOctal%maxChildren)
[…]

### 2008-09-19 torus/disc_hydro_mod.f90

@@ -261,15 +261,16 @@ contains
   subroutine throughoutMidpane(grid, mStar, sigma0, rDisk, drho)
 
     type(GRIDTYPE) :: grid
-    real(double) :: zAxis(10000)
-    real(double) :: rho(10000)
-    real :: temperature(10000)
-    real(double) :: subcellsize(10000)
+    integer, parameter :: maxvals = 100000
+    real(double) :: zAxis(maxVals)
+    real(double) :: rho(maxVals)
+    real :: temperature(maxVals)
+    real(double) :: subcellsize(maxvals)
     real :: mStar, sigma0, rDisk
     integer :: nz
     real :: xpos, ypos, radius, drho, smallestSubcell
     logical :: converged 
-    real(double) :: xAxis(1000000)
+    real(double) :: xAxis(maxVals*10)
     integer :: nx, i
 
     nx = 0
@@ -277,7 +278,6 @@ contains
     call stripSimilarValues(xAxis,nx,1.d-5*grid%halfSmallestSubcell)
     xAxis(1:nx) = xAxis(1:nx) + 1.d-5*grid%halfSmallestSubcell
 
-    write(*,*) "getxvalues after strip",nx
     xPos = grid%halfSmallestSubcell - grid%octreeRoot%subcellSize
     smallestSubcell = 2. * grid%halfSmallestSubcell
     
@@ -397,7 +397,7 @@ contains
        totalMass = 0.
        call findTotalMass(grid%octreeRoot, totalMass)
 
-       call torus_mpi_barrier('waiting to do lucy.')
+       call torus_mpi_barrier()
 
        if (nIter == 1) then
           maxIter = 2
@@ -440,7 +440,7 @@ contains
 
        totalMass = 0.
        call findTotalMass(grid%octreeRoot, totalMass)
-       write(*,*) "Total disc mass: ",totalMass/msol," solar masses"
+       if (myRankisZero) write(*,*) "Total disc mass: ",totalMass/msol," solar masses"
 
 
 
@@ -511,10 +511,8 @@ contains
           write(*,*) "Maximum number of iterations exceeded. Aborting."
           converged = .true.
        else
-          write(*,*) "calling set temperature..."
           temp = 20.
           call setTemperature(grid%octreeRoot, temp)
-          write(*,*) "done."
        endif
        
     enddo

### 2008-09-19 torus/lucy_mod.F90

@@ -2949,8 +2949,8 @@ subroutine setBiasOnTau(grid, iLambda)
 #endif
 
     deallocate(octalArray)
-    call writeVtkFile(grid, "bias.vtk", &
-            valueTypeString=(/"bias"/))
+!    call writeVtkFile(grid, "bias.vtk", &
+!            valueTypeString=(/"bias"/))
 
   end subroutine setBiasOnTau
 

### 2009-06-02 torus/docs/how_to_build_torus.tex
Replace image_f77.f files and spec_f77.f files with F90 versions which use the USENDF cpp key to control whether NDF support is enabled. It is no longer necessary to specify whether NDF support is enabled when defining the SYSTEM in the Makefile. The default behaviour is not to use NDF but this can be changed by using make ndf=yes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1932 25464f21-6099-402c-b30a-640f1d40d38b

@@
       cfitsio & link with cfitsio libraries & yes \\
+      ndf & build with NDF file support & no \\
       debug   & switch on debugging flags   & no  \\

### 2009-06-02 torus/image_ndf.F90

@@ -1,5 +1,6 @@
-      subroutine writeImagef77(thisImageI, thisImageQ, thisImageU,
-     &thisImageV, thisImageVel, scale, nPix, filename)
+#ifdef USENDF
+      subroutine writeImagef77(thisImageI, thisImageQ, thisImageU, &
+      thisImageV, thisImageVel, scale, nPix, filename)
       implicit none
       include '/star/include/DAT_PAR'
       include '/star/include/SAE_PAR'
@@ -45,10 +46,8 @@
       call ndf_acput('rstar',ndfo,'unit',1,status)
       call ndf_acput('yaxis',ndfo,'lab',2,status)
       call ndf_acput('rstar',ndfo,'unit',2,status)
-      call ndf_amap(ndfo,'centre',1,'_real','update',oaxisp1,
-     &ubnd(1),status)
-      call ndf_amap(ndfo,'centre',2,'_real','update',oaxisp2,
-     &ubnd(1),status)
+      call ndf_amap(ndfo,'centre',1,'_real','update',oaxisp1,ubnd(1),status)
+      call ndf_amap(ndfo,'centre',2,'_real','update',oaxisp2,ubnd(1),status)
       call ndf_map(ndfo,'data','_real','write',iptr,nelm,status)
 
       if (status .ne. sai__ok) then
@@ -57,8 +56,7 @@
       endif
 
 
-      call fillNdfImage(scale,%val(iptr),%val(oaxisp1), %val(oaxisp2), 
-     &npix, thisImageI)
+      call fillNdfImage(scale,%val(iptr),%val(oaxisp1), %val(oaxisp2),npix, thisImageI)
 
       CALL NDF_XNEW(NDFO,'POLARIMETRY','EXT',0,0,PLOC,STATUS)
       CALL NDF_PLACE(PLOC,'STOKES_Q',PLACE,STATUS)
@@ -89,11 +87,10 @@
       call hds_stop(status)
 
 
-      end 
+    end subroutine writeImagef77
        
 
-      subroutine fillNdfImage(scale, ndfimage, axis1, axis2, nPix, 
-     & thisImage)
+      subroutine fillNdfImage(scale, ndfimage, axis1, axis2, nPix, thisImage)
       implicit none
       integer  nPix
       real thisImage(nPix,nPix), scale
@@ -106,11 +103,10 @@
          axis1(i) = real(i) * scale
          do j = 1, npix
             axis2(j) = real(j) * scale
[…]

### 2009-06-02 torus/spec_ndf.F90

@@ -1,21 +1,21 @@
+#ifdef USENDF
 
-
-C
-C ********************************************************************
-C
-      SUBROUTINE WRTSP(NPTS,STOKES_I,STOKES_Q,STOKES_QV,STOKES_U,
-     &                 STOKES_UV,LAMBDA,FILENAME)
-C
-C This routine reads in a polarization spectrum from a TSP format file
-C and puts it into the 'current' arrays
-C
+!
+! ********************************************************************
+!
+      SUBROUTINE WRTSP(NPTS,STOKES_I,STOKES_Q,STOKES_QV,STOKES_U, &
+                      STOKES_UV,LAMBDA,FILENAME)
+!
+! This routine reads in a polarization spectrum from a TSP format file
+! and puts it into the 'current' arrays
+!
       IMPLICIT NONE
       INTEGER OUT_LU
       INCLUDE '/star/include/DAT_PAR'
       INCLUDE '/star/include/SAE_PAR'
-C
-C The current arrays
-C
+!
+! The current arrays
+!
       INTEGER NPTS
       REAL STOKES_I(*)
       REAL STOKES_Q(*)
@@ -23,12 +23,11 @@ C
       REAL STOKES_U(*)
       REAL STOKES_UV(*)
       REAL LAMBDA(*)
-C
-C Misc.
-C
+!
+! Misc.
+!
       INTEGER SP
       INTEGER NDF
-      ! CHARACTER*(*) CPARAM ! Unused? Commented out by nhs.
       CHARACTER*80 PATH,FILENAME
       CHARACTER*64 NAME
       CHARACTER*80 ERROR
@@ -40,18 +39,18 @@ C
       INTEGER PTRQ,PTRQV,PTRU,PTRUV,APTR
       CHARACTER*(DAT__SZLOC) PLOC,DLOC,QLOC,LOC      
       INTEGER STATUS
-C
+
       STATUS = SAI__OK
       LBND(1) = 1
       UBND(1) = NPTS
-C
-C Begin the ndf and hds systems
-C
+!
+! Begin the ndf and hds systems
+!
       CALL NDF_BEGIN
       CALL HDS_START(STATUS)
-C
-C Create a new tsp ndf and map it
-C
+!
[…]

### 2009-06-24 SPH-Torus-paper1/sphtorus_benchmark.tex
Initial import of the first SPH-Torus paper
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1970 25464f21-6099-402c-b30a-640f1d40d38b

\documentclass[usenatbib]{mn2e}

\usepackage{graphicx}
\usepackage{subfigure}

\begin{document}

\title{Modelling circumstellar discs with 3D radiation hydrodynamics}
\author[David M. Acreman, David A. Rundle, Tim J. Harries]{David M. Acreman, David
  A. Rundle, Tim J. Harries\\
School of Physics, University of Exeter, Stocker Road, Exeter EX4
4QL. E-mail acreman@astro.ex.ac.uk
}

\maketitle

\begin{abstract}

We present results from combining a grid-based radiative transfer code
with a Smoothed Particle Hydrodynamics code to produce a flexible
system for modelling radiation hydrodynamics. The system is tested
using a benchmark model of a circumstellar disc. We find that the SED
and temperature distribution within the disc are highly sensitive to
the representation of the disc inner edge, which depends critically on
both the grid and SPH resolution. The system is then used to model a
circumstellar disc around a T-Tauri star and is found to produce a
steady state disc in both hydrostatic and radiative equilibrium.

\end{abstract}

\begin{keywords}
hydrodynamics -- radiative transfer -- methods: numerical
\end{keywords}

\section{Introduction}

The interaction between matter and radiation is of great importance in
a range of astrophysical processes. A major challenge in star
formation simulations is to incorporate self-consistent radiative
feedback from protostars. Once this is achieved it is possible to
relax the simplifying assumptions relating to the equation of state
and to study the effects of radiative feedback, for example the impact
on disc fragmentation. A flux limited diffusion approximation can be
used to represent radiative transport in regions of high optical
depth, however this method is not suited to modelling regions of low
optical depth where an alternative method, such as a Monte-Carlo
method, must be used.

This paper presents a results from coupling the {\small{TORUS}} radiative
transfer code \citep{harries_2000} with the SPH (Smoothed Particle
Hydrodynamics) code of \cite{bate_2009}.  {\small{TORUS}} performs radiative
transfer calculations using the Monte-Carlo method of \cite{lucy_1999}
with a flux limited diffusion approximation in regions of high optical
depth. The radiative transfer calculations are performed on a grid
which uses adaptive mesh refinement (AMR) to allow variable
resolution.  The SPH method is well suited to dealing with the large
range in size scales encountered during star formation processes, hence
an SPH code coupled to a combined Monte-Carlo and flux limited
diffusion radiative transfer code is a very flexible method for
performing star formation calculations incorporating radiative
feedback.

There is not a unique approach to coupling an SPH code to a radiative
transfer code and a number of different approaches have been developed
(\cite{nayakshin_2009}, \cite{pawlik_2008} and references
therein). This paper focuses on radiative transfer calculations using
an adaptive grid in the context of modelling processes in star
formation.

Accurately coupling the SPH component to the radiative transfer
component requires an effective transformation from the Lagrangian
particle description of SPH to the Eulerian grid description of an AMR
grid. The procedure used for this transformation is tested using a
benchmark case (see Sections~\ref{section:description_of_benchmark}
and~\ref{section:grid_generation}). The spectral energy distribution
and temperature distribution of the benchmark disc are examined in
Section~\ref{section:seds} in order to understand how well the
radiative transfer calculation works with the gridded density field
and to understand the effects of grid and SPH spatial resolution. A
simulation of a circumstellar disc around a T Tauri star is presented
in Section~\ref{section:sph_disc} with the aim of calculating an
equilibrium state in three dimensional hydrostatic and radiative
balance.

\section{Circumstellar disc benchmark}
\label{section:description_of_benchmark}

When constructing validation tests of a numerical method it is often
valuable to use a simplified test case with well known results. We
base our SPH disc benchmark on the axisymmetric circumstellar disc of
\cite{pascucci_2004}.  Representing a structure with rotational
symmetry using a 3D geometry allows us to validate the operation of
our method against well tested results from other codes while fully
exercising the 3D capabilities of our own system.

The density of the disc benchmark described by \cite{pascucci_2004} is
given by
\begin{equation}
\rho\left(r,z\right) = \rho_0 \left( \frac{r}{r_d} \right)^{-1} \exp
\left( - \frac{\pi}{4} \left( \frac{z}{h\left(r \right)}  \right)^2 \right)
\label{eqn:pascucci_density}
\end{equation}
where $r$ is the distance from the central star in the mid-plane and
$z$ is the height from the mid-plane. The expression $h\left( r
\right)$ is given by
\begin{equation}
h\left( r \right) = z_d \left( \frac{r}{r_d}\right)^{1.125}  
\end{equation}
and $\rho_0$, $z_d$ and $r_d$ are constant parameters.  We base our
benchmark model on the most optically thick case presented by
\cite{pascucci_2004} which has a mid-plane optical depth of $\tau=100$
at $\lambda=550~\rm{nm}$ and a mass of 0.011~$\rm{M}_{\sun}$. This
requires $r_d=500~\rm{AU}$, $z_d=0.25 r_d$ and
$\rho_{0}=8.1614\times10^{-18}~\rm{g~cm^{-3}}$, with the disc truncated at
an outer radius of 1000~AU and an inner radius of 1~AU.

The benchmark disc is implemented using an ensemble of equal mass SPH
particles. If all the particles have the same mass then the number
density is proportional to the mass density, hence the SPH particles
sample a probability density distribution such that the probability of
finding a particle in a given volume is proportional to the mass in
that volume as a fraction of the total mass \citep{gingold_1977}. 
Hence the analytical density function can be converted into a
probability function which describes the probability of finding a
particle in a given volume.  An ensemble of particle positions can
then be calculated by randomly sampling the probability density
functions for $r$ and $z$ and assigning a uniformly random spherical
polar angle $\theta$. The particle's density is set to the value given
by Eqn~\ref{eqn:pascucci_density} based on the particle's position.

Each particle is assigned a smoothing length $h_{\rm{smooth}}$ given by 
\begin{equation}
h_{\rm{smooth}} = 1.2 \left( \frac{m_{\rm{part}}}{\rho_{\rm{part}}} \right) ^{1/3}
\end{equation}
where $m_{\rm{part}}$ is the particle mass and $\rho_{\rm{part}}$ is
the particle density, according to the method of
\cite{price_2008}. The smoothing length is used when reconstructing
properties represented by the ensemble of particles, for example the
density distribution on the radiative transfer grid is 
constructed using a kernel smoothing method (see
Section~\ref{section:grid_generation}).

\section{Generation of adaptive grid from SPH-particles}

\label{section:grid_generation}

An important step in setting up grid-based radiative transfer using
SPH particles is determining an effective transformation of the
required model fields (e.g. density) between the SPH particle
representation and the grid representation.  The representation on
grid should preserve important properties of the SPH model, e.g. total
mass and density gradients. This section determines a grid
construction method which allows a good degree of control over the
number of cells in the grid while maintaining an accurate
representation of the density distribution.

\subsection{Grid generation method}

{\small{TORUS}} uses an adaptive grid based on the octree method. In a 3D
geometry the initial grid comprises 8 cells (one octal) with 2 cells
in each dimension. An algorithm is applied to determine whether to
split each cell into a further 8 cells, similar to the method of
\cite{kurosawa_2001}. The properties of the adaptive grid are
determined by a combination of the algorithm used to decide when to
split a cell and the method used to assign density values to cells.

The density in a given grid cell is calculated using a kernel
smoothing method. The kernel smoothed density is normalised by the sum
of the kernel weights, if the sum of the weights is greater than 0.3,
to ensure a smooth density distribution within the interior of the
disc. If the sum of the weights is less than 0.3 then the density is
not normalised by the sum of the weights, in order to avoid numerical
effects at the free surface as described by \cite{price_2007}.  The
method used to construct an AMR grid from SPH particles is described
in more detail in \cite{rundle_2009}.

\subsection{Grid generation tests}

Two grid splitting conditions were tested. The first method splits a
grid cell if the mass within the cell exceeds a given limit. For this
condition the resolution is highest where the density is highest
(i.e. resolution increases towards the disc mid-plane and towards the
centre of the disc) which is analogous to the effective spatial
resolution of SPH.  The second condition decides whether to split the
cell based on the fractional density difference between the most dense
and least dense SPH particles contained within the cell. The quantity
\begin{equation}
f_{\rm{split}}=\frac{\rho_{\rm{max}} - \rho_{\rm{min}}}{\rho_{\rm{max}} + \rho_{\rm{min}}}
\end{equation}
is calculated, where $\rho_{\rm{max}}$ is the highest SPH particle
density and $\rho_{\rm{min}}$ is the lowest SPH particle density, and
the cell is split if a specified value of $f_{\rm{split}}$ is
exceeded.

To illustrate the effects of the different splitting methods two
example grids are shown in Fig.~\ref{fig:example_meshes}. A grid
constructed from $10^7$ particles, using a mass per cell limit of
$5\times10^{26}~\rm{g}$, is plotted in
Fig.~\ref{fig:mass_condition_mesh}. This plot is a slice along $y=0$
showing the grid in the $x$-$z$ plane and shows the increased
resolution towards the disc centre and mid-plane.  A grid with 
$f_{\rm{split}}=0.1$, also using $10^7$ particles, is plotted in
Fig.~\ref{fig:density_condition_mesh}. The resolution is highest at
the edge of the disc, where there are large density gradients, and the
resolution also increases towards the centre of the disc.
\begin{figure*}
  \subfigure[AMR grid with a mass per cell condition of
    $5\times10^{26}~\rm{g}$.]
    {\includegraphics[scale=0.22]{figures/set1_mesh}
  \label{fig:mass_condition_mesh}}
  \subfigure[Grid with a density condition of
    $f_{\rm{split}}=0.1$.]
    {\includegraphics[scale=0.22]{figures/set2_mesh}
      \label{fig:density_condition_mesh}}
  \caption{Example AMR grids for a mass per cell splitting condition (left)
    and a density contrast splitting condition (right). In both cases
    $10^7$ particles were used. The axis units are $10^{16}$~cm.}
  \label{fig:example_meshes}
\end{figure*}

For each splitting condition a number of AMR grids were generated
using different values of the mass per cell limit or
$f_{\rm{split}}$. This was repeated for discs represented by $10^5$,
$10^6$ and $10^7$ SPH particles. Figure~\ref{fig:grid_tests} plots the
number of octals generated as a function of mass per cell or
$f_{\rm{split}}$ (solid line), and the percentage error in the disc
mass (dashed line). The percentage error in disc mass is calculated by
comparing the total mass on the AMR grid with the known mass of
$0.011~\rm{M}_{\sun}$ based on the analytical form of the density
distribution, and a positive value indicates that mass on the grid is
too large. In all cases the total mass obtained by summing the masses
of all SPH particles is correct to within a factor of $10^{-8}$.
\begin{figure*}
  \subfigure[Mass per cell condition and $10^5$ particles]{\includegraphics[scale=0.3]{figures/1e5_set1}}
  \subfigure[Mass per cell condition and $10^6$ particles]{\includegraphics[scale=0.3]{figures/1e6_set1}}
  \subfigure[Mass per cell condition and $10^7$ particles]{\includegraphics[scale=0.3]{figures/1e7_set1}}
  \subfigure[Density contrast condition and $10^5$ particles]{\includegraphics[scale=0.3]{figures/1e5_set2}}
  \subfigure[Density contrast condition and $10^6$ particles]{\includegraphics[scale=0.3]{figures/1e6_set2}}
  \subfigure[Density contrast condition and $10^7$ particles]{\includegraphics[scale=0.3]{figures/1e7_set2}}
  \caption{Number of octals (solid line) and percentage mass error
    (dashed line) for AMR grids generated using different grid
    splitting methods and different numbers of particles. }
  \label{fig:grid_tests}
\end{figure*}

The mass per cell condition allows a wide range in the total number of
octals while maintaining a total mass which is correct to within a few
percent. The number of octals as a function of mass per cell limit is
consistent between runs with different numbers of SPH particles, apart
from the case with $10^5$ particles and a mass limit of
$10^{26}$~g. In this case the mass per cell limit is smaller than the
SPH particle mass and the grid is over sampling the SPH resolution. In
the other cases the mass per cell limit is greater than the SPH
particle mass. For mass per cell limits of $10^{28}$g and less the
total mass error varies only slowly as a function of mass per
cell. There is a positive bias in the total mass but using more SPH
particles results in a more accurate total mass.

If a density contrast condition is used then the total number of
octals depends on the number of particles, unlike in the mass per cell
case. The general form of the number of octals as a function of
density contrast is the same in all three cases but the normalisation
varies substantially. In order to ensure a total mass accurate to with
1~per~cent the density contrast condition would require at least $10^7$
particles and a density contrast threshold of no more than 0.3.

The density contrast condition is effective in adding extra resolution
in regions of high density contrast (see
Fig.~\ref{fig:density_condition_mesh}) but has a less robust total
mass representation than the mass per cell limit. By using a
combination of these two conditions it is possible to add extra
resolution in high contrast regions and still maintain an accurate
total mass.

\section{SED generation and temperature distribution}

\label{section:seds}

Ensuring a consistent representation of mass and density in the grid
representation and in the SPH representation is an important
requirement in ensuring accurate radiative transfer calculations. In
order to have confidence in the results of the calculations we must
also ensure that the temperature distribution is realistic. By
comparing the Spectral Energy Distribution (SED) from our disc with the
benchmark results we have a global measure of how well the density and
temperature distributions are represented. In order to get an accurate
SED both the density and temperature distributions must be well
represented.

The disc was initially modelled using $10^5$ SPH particles and a mass
per cell limit of $5\times10^{26}$g was used to construct the
AMR grid. The mass per cell limit was chosen in
preference to the density contrast limit to give the highest
resolution near the central region of the disc, which we expect to be
most important for determining the SED. SEDs were calculated using the
{\small{TORUS}} code for viewing angles of 12.5 and 77.5 degrees (where an
inclination angle of zero degrees indicates that the disc is viewed
face-on) and the results are plotted in Fig.~\ref{fig:seds} (dashed line). Also
plotted in Fig.~\ref{fig:seds} are the benchmark results of
\cite{pascucci_2004} (solid line).
\begin{figure*}
  \includegraphics[scale=0.3]{figures/sed_013}
  \includegraphics[scale=0.3]{figures/sed_077}
  \caption{SEDs from the benchmark disc with $10^5 $ particles. SEDs
    are shown for inclination angles of 12.5 degrees (left) and 77.5
    degrees (right). The benchmark SED is plotted as a solid line and
    the {\small{TORUS}} SED is plotted as a dashed line.}
  \label{fig:seds}
\end{figure*}
Both SEDs show significant departures from the benchmark results;
there is excess emission between 10-100 $\mu\rm{m}$ and at a viewing angle of
77.5 degrees there is also a significant reduction in the short
wavelength flux. The density distribution in the central region of
this disc is plotted in Fig.~\ref{fig:basic_dens} which shows that the
central 1AU gap is not represented. There are two effects in
operation; firstly the grid resolution in this region is larger than
1AU and secondly the smoothing lengths of the particles are 
larger than 1AU. In order to correctly represent the central gap there
needs to be higher grid resolution around the central source and 
more SPH particles are required so that the smoothing lengths are
smaller. 
\begin{figure}
\includegraphics[scale=0.2]{figures/basic_dens}
\caption{Density in central region of disc with $10^5$ particles. Axis
units are $10^{13}$cm.}
\label{fig:basic_dens}
\end{figure}

Decreasing the mass per cell limit to achieve the required resolution
around the central source would result in too many cells being
generated in other regions of the disc. In order to achieve a grid
resolution of less than 1AU around the source it was necessary to
specify additional criteria for refining the grid. Three cubes of
increased resolution were added to the AMR grid with sizes
$1.5\times10^{15}$~cm, $3\times10^{14}$~cm and
$6\times10^{13}$~cm. Within each cube it was required that the cell
size be no larger than 0.1 of the cube dimension.

In order to confirm that the grid modifications provide sufficient
resolution to generate an accurate SED three calculations were
performed with the central part of the disc forced to the correct
density values from the analytical density description.  A spherical region
with radius $1.0\times10^{15}$~cm, $5.0\times10^{14}$~cm or
$2.5\times10^{14}$~cm was over written with the benchmark disc density
after the initial grid generation was performed. The resulting SEDs
are plotted in Fig.~\ref{fig:sed_forced}. The solid line shows the
benchmark result and the other lines show SEDs for forcing regions of
radius $1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm
(short dashed line) and $2.5\times10^{14}$~cm (dotted line).
\begin{figure*}
  \includegraphics[scale=0.3]{figures/seds_forced_13.pdf}
  \includegraphics[scale=0.3]{figures/seds_forced_77.pdf}
  \caption{SEDs from SPH benchmark disc for inclination angles of 12.5
    degrees and 77.5 degrees. The benchmark SED is plotted as a solid
    line. The {\small{TORUS}} density distribution is forced to the correct
    value with a radius of $1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm
(short dashed line) and $2.5\times10^{14}$~cm (dotted line).} 
  \label{fig:sed_forced}
\end{figure*}
With the correct density forced out to a radius of
$1.0\times10^{15}$~cm the SED is close to the benchmark result for
both viewing angles, however if the forced region is reduced in size
there is a significant discrepancy relative to the benchmark SED. This
confirms that the grid now has enough resolution to generate an
accurate SED but also indicates that using $10^5$ particles does not
give a sufficiently accurate density distribution within the central
$1.0\times10^{15}$~cm of the disc.

Further calculations were performed using different numbers of SPH
particles and the enhanced grid resolution described above. SEDs are
plotted in Fig.~\ref{fig:n_part_sed_013} for a viewing angle of 12.5
degrees and Fig.~\ref{fig:n_part_sed_077} for a viewing angle of 77.5
degrees. The density distribution in the central region is plotted in
Fig.~\ref{fig:n_part_central_dens}.
%
\begin{figure*}
  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/sed_013_1e5}}
  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/sed_013_1e6}}
  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/sed_013_1e7}}
  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/sed_013_1e8}}
  \caption{SEDs at a 12.5 degree inclination angle for discs represented by different numbers of SPH
    particles. The benchmark result is plotted as a solid line and the
  modelled SED is plotted as a dashed line. } 
  \label{fig:n_part_sed_013}
\end{figure*}
%
\begin{figure*}
  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/sed_077_1e5}}
  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/sed_077_1e6}}
  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/sed_077_1e7}}
  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/sed_077_1e8}}
  \caption{SEDs at a 77.5 degree inclination angle for discs represented by different numbers of SPH
    particles. The benchmark result is plotted as a solid line and the
  modelled SED is plotted as a dashed line. } 
  \label{fig:n_part_sed_077}
\end{figure*}
%
\begin{figure*}
  \subfigure[$10^5$ particles]{\includegraphics[scale=0.22]{figures/dens_1e5}}
  \subfigure[$10^6$ particles]{\includegraphics[scale=0.22]{figures/dens_1e6}}
  \subfigure[$10^7$ particles]{\includegraphics[scale=0.22]{figures/dens_1e7}}
  \subfigure[$10^8$ particles]{\includegraphics[scale=0.22]{figures/dens_1e8}}
  \caption{Central density on AMR grid derived from different numbers
    of SPH particles. The axis units are $10^{13}$~cm.} 
  \label{fig:n_part_central_dens}
\end{figure*}
With $10^5$ and $10^6$ particles a central gap is present but is too
large. With $10^7$ particles there
is more material close in to the source but the gap itself is not
represented and the source is obscured. Only with $10^8$ particles is
a gap of approximately the correct size present.

Figure~\ref{fig:n_part_tem_diff} shows fractional errors in the
temperature distribution for different numbers of particles. {\small{TORUS}}
calculates the temperature distribution using a high resolution 2D
geometry, in order to determine the correct temperature as a function
of cylindrical polar $r$ and $z$ co-ordinates. This is then
compared to the temperature from the SPH disc for each SPH
particle. Positive values of the fractional error indicate that the
SPH disc is hotter than the expected value.
\begin{figure*}
  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run1}}
  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run2}}
  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run3}}
  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run4}}
  \caption{Fractional temperature error for discs represented by
    different numbers of SPH particles. Axis units are AU.} 
  \label{fig:n_part_tem_diff}
\end{figure*}
When using $10^5$ particles to represent the disc there is a
too much heating in the disc mid plane and insufficient heating
further out of the mid plane. The effect is reduced when $10^6$
particles are used but is only reduced to a low level with $10^8$
particles. The representation of the central region of the disc not
only has a significant impact on the SEDs but also on the temperature
distribution within the disc.

\section{Coupled SPH and Monte-Carlo radiative transfer simulation of
  a circumstellar disc}

\label{section:sph_disc}

\subsection{Description of model}

A model system was constructed similar to the classical T Tauri star
AA Tau. \cite{o'sullivan_2005} determine the properties of AA Tau
using Monte-Carlo modelling of the observed SED, and we use these
derived properties as a basis for constructing our model system. The
disc of $0.02~{M}_{\odot}$ is initialised with an outer radius of
150~AU, and an inner radius of 0.5~AU, surrounding a central star of
mass $1~M_{\odot}$. The central star is represented by a sink particle
which accretes gas particles within an accretion radius of 0.5~AU. The
disc itself is initially represented using $2\times10^5$ particles of
equal mass, although some of these particles are accreted by the
central sink particle as the simulation progresses. The central star
has a radius of $2~\rm{R}_{\odot}$, a temperature of 4000~K and a
luminosity of $0.9~\rm{L}_{\odot}$.

The disc is initially evolved using only the SPH part of the code in
order to bring the disc into dynamical equilibrium. During this
initial phase the internal energies of the SPH particles are
determined using an equation of state which is isothermal
perpendicular to the plane of the disc and has a $T\propto 1/r$ radial
dependence. The disc is evolved for approximately 3000
years of simulated time in order to allow transient effects from the
initialisation to dissipate. Approximately 10~per~cent of the gas particles are
accreted by the sink particle during this initial phase but the mass
does not change significantly after this time.

After the initial period the disc is evolved using the combined SPH
and radiative transfer code. In this configuration the internal
energies of the SPH particles are set using the temperatures
calculated by the radiative transfer code. The SPH part of the code
does not change the particle temperatures and they retain the
temperature assigned by the radiative transfer code until the next
radiation time step. The temperatures calculated by the radiative
transfer code are equilibrium temperatures, as it is assumed that the
time scale for radiative equilibrium is short compared to the
dynamical time scale of the disc.

The SPH code uses a non-dimensionalised unit system and the radiative
transfer step is called after an elapsed time of 1.0 code units (1.89
years). This time interval was chosen to allow the hydrodynamics to
respond to the radiative heating and achieve a suitable balance
between the hydrodynamics and the slower radiative transfer
calculation.

The AMR grid is constructed using a maximum mass per cell of
$5.0\times10^{26}~\rm{g}$, corresponding approximately to the mass of
two SPH particles. The density in a cylindrical region around the
source was reduced to a very low value to ensure that the disc did not
completely obscure the source. The radius of this region is
$R_{\rm{gap}}=0.5~\rm{AU}$ which corresponds to the accretion radius
of the SPH sink particle. Two extra levels of grid refinement were
added in a box around the central source to ensure that the grid had
enough resolution to allow the gap around the source to be
resolved. The first box of extra refinement had size $10R_{\rm{gap}}$
in the plane of the disc and size $40R_{\rm{gap}}$ perpendicular to
the disc with a maximum cell size of $R_{\rm{gap}}$; the second box of
extra refinement had size $2.5R_{\rm{gap}}$ in the plane of the disc
and size $20R_{\rm{gap}}$ perpendicular to the disc with a maximum
cell size of $0.5R_{\rm{gap}}$. A real circumstellar disc will be
truncated by the stellar magnetosphere so there is a physical
justification for enforcing a low density region around the star.

\subsection{Transient effects}

When the radiative transfer calculation is introduced there is an
adjustment of the disc towards a new hydrostatic balance which is
consistent with the new temperature structure. As the temperature
structure is dependent on the density structure is is necessary to
iterate the solution towards a state where both hydrostatic and
radiative balance are simultaneously achieved. This section examines
how the structure of the disc evolves towards such a state. The
ultimate aim of this simulation is to achieve a disc which is in
hydrostatic and radiative balance so the transients are of interest
from a numerical, rather than a physical, perspective.

Particle densities as a function of radius are plotted in
Fig.~\ref{fig:trans_rho} for four different times during the period
when the disc is adjusting towards equilibrium. The first plot shows
the distribution immediately before the radiative transfer is
introduced (i.e. this is the density distribution from the SPH code
alone, with a vertically isothermal equation of state). At any given
radius there is a spread of particle densities as the density varies
with height out of the disc mid-plane. The second frame is
approximately 30 years after radiative transfer has been
introduced. The peak density (at around $2\times10^{14}~\rm{cm}$) has
been increased but at this time there is no observable effect on the
outer regions of the disc. In the third frame density enhancements are
seen in the density profile at radii of approximately
$4\times10^{14}~\rm{cm}$ and $7\times10^{14}~\rm{cm}$. In the fourth
frame these enhancements have propagated outwards and a third
enhancement is also seen, although with a lower amplitude.

The particle positions, as a function of cylindrical polar $r$ and $z$
co-ordinates, are plotted in Fig.~\ref{fig:trans_rz} (note the
expanded vertical scale). From an initially relaxed state (first
frame) the central region of the disc is seen to collapse in the
second frame, which accounts for the increase in density seen in
Fig.~\ref{fig:trans_rho}. 
\begin{figure*}
  \includegraphics[scale=0.3]{figures/rho_vs_r_5147}
  \includegraphics[scale=0.3]{figures/rho_vs_r_5197}
  \includegraphics[scale=0.3]{figures/rho_vs_r_5397}
  \includegraphics[scale=0.3]{figures/rho_vs_r_5597}
  \caption{Particle density as a function of cylindrical polar radius
    for a disc modelled using the combined SPH-radiative transfer
    code. Four different times are shown to illustrate the transient
    effects present as the disc evolves towards an equilibrium state.}
\label{fig:trans_rho}
\end{figure*}
\begin{figure*}
  \includegraphics[scale=0.3]{figures/rz_5147}
  \includegraphics[scale=0.3]{figures/rz_5197}
  \includegraphics[scale=0.3]{figures/rz_5397}
  \includegraphics[scale=0.3]{figures/rz_5597}
  \caption{Particle positions as a function of cylindrical r and z
    co-ordinates for a disc modelled using the combined SPH-radiative
    transfer code. Four different times are shown to illustrate the
    transient effects present as the disc evolves towards an
    equilibrium state.}
\label{fig:trans_rz}
\end{figure*}
Several fluctuations in the disc scale height can be seen as the
simulation progresses. Such fluctuations have been observed previously
in codes which calculate both radiative transfer and vertical hydrostatic
equilibrium \citep{min_2009,watanabe_2008}. With our coupled radiative
transfer and 3 dimensional hydrodynamics code we find that the
oscillations propagate outwards through the disc and that successive
oscillations are of reduced amplitude, hence we find that it is
possible to evolve this disc to a steady state solution.

The transient effects of the disc adjusting toward a new equilibrium
state are not limited to scale height
fluctuations. Figure~\ref{fig:sigma_transients} shows surface density
plots for two different times during the adjustment phase, which
indicates that there are transient effects in the surface density as
well as in the scale height. These effects would not be present in a
code which calculates vertical hydrostatic equilibrium only.
\begin{figure}
  \includegraphics[scale=0.3]{figures/sigma}
  \caption{Surface density, as a function of cylindrical polar radius,
  after a simulated time of 3200~yr (solid line) and 3319~yr.}
  \label{fig:sigma_transients}
\end{figure}
% Dump number 5397 is at 3200 yrs
% Dump number 5597 is at 3319 yrs

\subsection{Equilibrium state of disc}

The surface density of the disc, after 4986~years of simulated time
(the latest simulated time), is shown in Fig.~\ref{fig:sigma_final}.
Away from the inner and outer edges of the disc the surface density is
well represented by a power law profile as a function of radius.
\begin{figure}
  \includegraphics[scale=0.3]{figures/sigma_final}
  \caption{Surface density as a function of radius after 4986~years of simulated time.}
  \label{fig:sigma_final}
\end{figure}

The scale height of the disc was determined by fitting Gaussians to
the vertical density profile in 100 radial bins. The fitted scale
height, as a function of radius, is plotted in
Fig.~\ref{fig:scale_height}.  Within the central 10~AU the density
profile appears flat so it was not possible to fit a meaningful scale
height.
\begin{figure}
  \includegraphics[scale=0.3]{figures/scale_height}
  \caption{Disc scale height as a function of radius  after 4986~years of simulated time.}
  \label{fig:scale_height}
\end{figure}

The average temperature within one scale height of the disc mid plane
is plotted as a solid line in Fig.~\ref{fig:mid_tem}. The dashed line
is a power law variation of temperature with radius with an index of
$-0.35$. Although this line is not a formal best fit it has been
plotted to indicate that this temperature profile is well represented
by a power law outside 15AU.
\begin{figure}
  \includegraphics[scale=0.3]{figures/mid_tem}
  \caption{Average temperature within one scale height of the mid plane, as a function of
    radius, after 4986~years of simulated time.}
  \label{fig:mid_tem}
\end{figure}

\section{Conclusions}

\label{section:conclusions}

We have presented results from a combined SPH and grid-based radiative
transfer code, which has been used to model a non-self gravitating
circumstellar disc. Validation tests of the method have revealed a
number of factors which must be taken into consideration when setting
up a model of this type.

Although we have found a method for constructing an AMR grid from SPH
particles which is robust, in terms of the total mass on the grid, we
found that it was necessary to add additional grid refinement in the
central region of the disc to allow the inner edge to be well
represented. The inner edge of the disc has a disproportionately large
effect on the temperature distribution in the disc and on the emergent
SED. Consequently the accuracy of the solution is dependent upon the
accurate representation of a region which constitutes a small fraction
of the disc by volume. As the method combines both SPH and grid
elements it is important that both these components have sufficient
resolution to represent the disc inner edge. This presents a
particular challenge for a SPH code which uses equal mass particles
but is achievable with a large number of particles.

The combined SPH-radiative transfer code was able to evolve a
circumstellar disc to a state of radiative and hydrostatic
equilibrium. Fluctuations in scale height were seen, which have also
been observed in codes which combine radiative transfer and vertical
hydrostatic equilibrium calculations. However there were also
transient effects seen in the surface density distribution which would
not be present if the hydrostatic equilibrium was calculated in the
vertical direction only.

By adding self-gravity to the SPH model this method could be used to
explore the effects of radiative transfer on disc
fragmentation. However the model would need to be constructed
carefully to ensure sufficient resolution at the disc inner edge so
that the temperature distribution in the disc is accurate. Such a
model is expected to be feasible although computationally demanding.

\section*{Acknowledgments}
Calculations presented here were performed using the University of
Exeter Supercomputer. DMA is funded by an EPSRC grant.

\bibliographystyle{mn2e}
\bibliography{torus}

\end{document}

### 2009-06-24 SPH-Torus-paper1/sphtorus_benchmark.tex
Add plots of fractional temperature in the disc mid-plane.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1972 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
+To allow a more quantitative comparison the fractional difference in
+mid-plane temperature, compared with the results of
+\cite{pascucci_2004}, is plotted in
+Fig.~\ref{fig:n_part_tem_diff_midpane}.
+\begin{figure*}
+  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/mp_comp1}}
+  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/mp_comp2}}
+  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/mp_comp3}}
+  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/mp_comp4}}
+  \caption{Fractional temperature error in the mid-plane for discs represented by
+    different numbers of SPH particles.} 
+  \label{fig:n_part_tem_diff_midpane}
+\end{figure*}
+In each case the particles are binned into 1~AU bins and the particle
+closest to the mid-plane in that bin is found. The mid-plane
+temperature from \cite{pascucci_2004} is linearly interpolated to the
+cyclindrical radius of the particle and the fractional temperature
+error is calculated.
+
 \section{Coupled SPH and Monte-Carlo radiative transfer simulation of

### 2009-06-29 SPH-Torus-paper1/sphtorus_benchmark.tex
move temperature plots before SEDs in benchmark comparison section.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1974 25464f21-6099-402c-b30a-640f1d40d38b

--- 2009-06-24 SPH-Torus-paper1/sphtorus_benchmark.tex
@@
 
-\section{SED generation and temperature distribution}
+\section{Temperature distribution and SED generation}
 
@@
 Further calculations were performed using different numbers of SPH
-particles and the enhanced grid resolution described above. SEDs are
-plotted in Fig.~\ref{fig:n_part_sed_013} for a viewing angle of 12.5
-degrees and Fig.~\ref{fig:n_part_sed_077} for a viewing angle of 77.5
-degrees. The density distribution in the central region is plotted in
-Fig.~\ref{fig:n_part_central_dens}.
+particles and the enhanced grid resolution described
+above. Figure~\ref{fig:n_part_tem_diff} shows fractional errors in the
+temperature distribution for different numbers of
+particles. {\small{TORUS}} calculates the temperature distribution
+using a high resolution 2D geometry, in order to determine the correct
+temperature as a function of cylindrical polar $r$ and $z$
+co-ordinates. This is then compared to the temperature from the SPH
+disc for each SPH particle. Positive values of the fractional error
+indicate that the SPH disc is hotter than the expected value.
+\begin{figure*}
+  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run1}}
+  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run2}}
+  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run3}}
+  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run4}}
+  \caption{Fractional temperature error for discs represented by
+    different numbers of SPH particles. Axis units are AU.} 
+  \label{fig:n_part_tem_diff}
+\end{figure*}
+When using $10^5$ particles to represent the disc there is a too much
+heating in the disc mid plane and insufficient heating further out of
+the mid plane. The effect is reduced when $10^6$ particles are used
+but is only reduced to a low level with $10^8$ particles.
+
+To allow a more quantitative comparison the mid-plane temperature and
+the benchmark mid-plane temperature are plotted in
+Fig.~\ref{fig:n_part_tem_diff_midpane} for all particles within 0.01
+scale heights of the mid-plane. The fractional temperature error for
+each particle is also plotted where a positive error indicates a
+temperature hotter than the benchmark value.
+\begin{figure*}
+  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/mp_comp1}}
+  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/mp_comp2}}
+  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/mp_comp3}}
+  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/mp_comp4}}
+  \caption{Fractional temperature error in the mid-plane for discs represented by
+    different numbers of SPH particles.} 
+  \label{fig:n_part_tem_diff_midpane}
+\end{figure*}
+SEDs are plotted in Fig.~\ref{fig:n_part_sed_013} for a viewing angle
+of 12.5 degrees and Fig.~\ref{fig:n_part_sed_077} for a viewing angle
+of 77.5 degrees.
+
+The density distribution in the central region is
+plotted in Fig.~\ref{fig:n_part_central_dens}.
 %
@@
 With $10^5$ and $10^6$ particles a central gap is present but is too
-large. With $10^7$ particles there
-is more material close in to the source but the gap itself is not
-represented and the source is obscured. Only with $10^8$ particles is
-a gap of approximately the correct size present.
-
-Figure~\ref{fig:n_part_tem_diff} shows fractional errors in the
-temperature distribution for different numbers of particles. {\small{TORUS}}
-calculates the temperature distribution using a high resolution 2D
-geometry, in order to determine the correct temperature as a function
-of cylindrical polar $r$ and $z$ co-ordinates. This is then
-compared to the temperature from the SPH disc for each SPH
-particle. Positive values of the fractional error indicate that the
-SPH disc is hotter than the expected value.
-\begin{figure*}
-  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run1}}
-  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run2}}
-  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run3}}
-  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run4}}
-  \caption{Fractional temperature error for discs represented by
-    different numbers of SPH particles. Axis units are AU.} 
-  \label{fig:n_part_tem_diff}
-\end{figure*}
-When using $10^5$ particles to represent the disc there is a
-too much heating in the disc mid plane and insufficient heating
-further out of the mid plane. The effect is reduced when $10^6$
-particles are used but is only reduced to a low level with $10^8$
-particles. The representation of the central region of the disc not
-only has a significant impact on the SEDs but also on the temperature
-distribution within the disc.
+large. With $10^7$ particles there is more material close in to the
+source but the gap itself is not represented and the source is
+obscured. Only with $10^8$ particles is a gap of approximately the
+correct size present.  The representation of the central region of the
+disc is significantly affected by the number of particles used to
+represent the disc. The representation of the central region has a
+significant impact on both the temperature distribution within the
+disc and the emergent SEDs.
 
@@
 transfer step is called after an elapsed time of 1.0 code units (1.89
-years). This time interval was chosen to allow the hydrodynamics to
-respond to the radiative heating and achieve a suitable balance
-between the hydrodynamics and the slower radiative transfer
-calculation.
+years) which corresponds to 3 hydrodynamics time steps. This time
+interval was chosen to allow the hydrodynamics to respond to the
+radiative heating and achieve a suitable balance between the
+hydrodynamics and the slower radiative transfer calculation.
 

### 2009-08-25 SPH-Torus-paper1/sphtorus_benchmark.tex
Major updates including new grid generation stuff and new disc run using cylindrical polar co-ordinates.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2021 25464f21-6099-402c-b30a-640f1d40d38b

--- 2009-06-24 SPH-Torus-paper1/sphtorus_benchmark.tex
@@
 \title{Modelling circumstellar discs with 3D radiation hydrodynamics}
-\author[David M. Acreman, David A. Rundle, Tim J. Harries]{David M. Acreman, David
-  A. Rundle, Tim J. Harries\\
+\author[David M. Acreman et al]{David M. Acreman et al\\
 School of Physics, University of Exeter, Stocker Road, Exeter EX4
@@
 properties represented by the ensemble of particles, for example the
-density distribution on the radiative transfer grid is 
-constructed using a kernel smoothing method (see
+density distribution on the radiative transfer grid (see
 Section~\ref{section:grid_generation}).
 
-\section{Generation of adaptive grid from SPH-particles}
+\section{Generation of an adaptive grid from SPH particles}
 
@@
 
-An important step in setting up grid-based radiative transfer using
-SPH particles is determining an effective transformation of the
-required model fields (e.g. density) between the SPH particle
-representation and the grid representation.  The representation on
-grid should preserve important properties of the SPH model, e.g. total
-mass and density gradients. This section determines a grid
-construction method which allows a good degree of control over the
-number of cells in the grid while maintaining an accurate
-representation of the density distribution.
+An important step in setting up grid-based radiative transfer using a
+density distribution derived from SPH particles is determining an
+effective transformation from the Lagrangian particle description to
+the Eulerian grid desciption.  The representation on grid should
+preserve important properties of the SPH model (e.g. total mass) but
+also needs to take account of the possibility that a radiative
+transfer calculation requires the highest resolution in different
+regions to a hydrodynamics calculation (e.g. to resolve opacity
+gradients). This section determines a grid construction method which
+allows a good degree of control over the number of cells in the grid,
+and the location of the highest resolution regions, while maintaining
+an accurate representation of the disc mass.
 
@@
 
-The density in a given grid cell is calculated using a kernel
-smoothing method. The kernel smoothed density is normalised by the sum
-of the kernel weights, if the sum of the weights is greater than 0.3,
-to ensure a smooth density distribution within the interior of the
-disc. If the sum of the weights is less than 0.3 then the density is
-not normalised by the sum of the weights, in order to avoid numerical
-effects at the free surface as described by \cite{price_2007}.  The
-method used to construct an AMR grid from SPH particles is described
-in more detail in \cite{rundle_2009}.
+The density in a given grid cell is calculated using an exponential
+kernel smooth. If the sum of the kernel weights is greater than 0.3
+the density is normalised by the sum of the kernel weights, to ensure a
+smooth density distribution within the interior of the disc. If the
+sum of the weights is less than 0.3 then the density is not normalised
+by the sum of the weights, in order to avoid numerical effects at the
+free surface, as described by \cite{price_2007}.
 
-\subsection{Grid generation tests}
+%The method used to
+%construct an AMR grid from SPH particles is described in more detail
+%in \cite{rundle_2009}.
+
+\subsection{Cartesian grid generation tests}
 
@@
 grid cell if the mass within the cell exceeds a given limit. For this
-condition the resolution is highest where the density is highest
-(i.e. resolution increases towards the disc mid-plane and towards the
-centre of the disc) which is analogous to the effective spatial
-resolution of SPH.  The second condition decides whether to split the
-cell based on the fractional density difference between the most dense
-and least dense SPH particles contained within the cell. The quantity
+condition the resolution is highest where the density is highest and
+the grid cell size is analogous to the SPH particle smoothing
+length. The second condition decides whether to split the cell based
+on the fractional density difference between the most dense and least
+dense SPH particles contained within the cell. The quantity
 \begin{equation}
@@
 the cell is split if a specified value of $f_{\rm{split}}$ is
-exceeded.
+exceeded. The first condition gives a resolution like that of the
+original SPH representation whereas the second condition should be
+better at representing gradients in density which are likely to be
+important for radiative transfer calculations.
 
@@
 $5\times10^{26}~\rm{g}$, is plotted in
-Fig.~\ref{fig:mass_condition_mesh}. This plot is a slice along $y=0$
-showing the grid in the $x$-$z$ plane and shows the increased
-resolution towards the disc centre and mid-plane.  A grid with 
+Fig.~\ref{fig:mass_condition_mesh}. This plot is a slice perpendicular
+to the disc mid-plane and shows increased resolution towards the disc
+centre and mid-plane where the density is higher.  A grid with
 $f_{\rm{split}}=0.1$, also using $10^7$ particles, is plotted in
-Fig.~\ref{fig:density_condition_mesh}. The resolution is highest at
-the edge of the disc, where there are large density gradients, and the
-resolution also increases towards the centre of the disc.
+Fig.~\ref{fig:density_condition_mesh}. The resolution increases
+towards the edge of the disc, where there are large density gradients,
+and also increases towards the centre of the disc. 
 \begin{figure*}
@@
 distribution, and a positive value indicates that mass on the grid is
-too large. In all cases the total mass obtained by summing the masses
-of all SPH particles is correct to within a factor of $10^{-8}$.
+too large.
 \begin{figure*}
@@
   \caption{Number of octals (solid line) and percentage mass error
-    (dashed line) for AMR grids generated using different grid
+    (dashed line) for cartesian AMR grids generated using different grid
     splitting methods and different numbers of particles. }
@@
 particle mass. For mass per cell limits of $10^{28}$g and less the
-total mass error varies only slowly as a function of mass per
-cell. There is a positive bias in the total mass but using more SPH
-particles results in a more accurate total mass.
+total mass error varies only slowly as a function of mass per cell and
+is accurate to within a few percent. There is a positive bias in the
+total mass but using more SPH particles results in a more accurate
+total mass.
 
@@
 The density contrast condition is effective in adding extra resolution
-in regions of high density contrast (see
-Fig.~\ref{fig:density_condition_mesh}) but has a less robust total
-mass representation than the mass per cell limit. By using a
-combination of these two conditions it is possible to add extra
-resolution in high contrast regions and still maintain an accurate
-total mass.
+in regions of high density contrast which are likely to be important
+in radiative transfer calculations. However the density split
+condition has a less robust total mass representation than the mass
+per cell limit. By using a combination of these two conditions it is
+possible to add extra resolution in high contrast regions and still
+maintain an accurate total mass.
 
-\section{SED generation and temperature distribution}
+\subsection{Cylindrical polar grid generation}
+
+For some geometries it may be appropriate to use a cylindrical polar
+co-ordinate system. A mass per cell splitting condition can still be
+used but it needs to be modified to take into account the increase in 
+cell volume as cylindrical polar radius increases, for fixed values of
+$dr$ and $dz$.  
+%
+Consider a cartesian grid with cubic volume elements and let
+\begin{equation}
+dl_{\rm{cart}} = dx = dy = dz 
+\end{equation}
+so that
+\begin{equation}
+dl_{\rm{cart}} = \left( \frac{dM_{\rm{cart}}}{\rho_{\rm{cell}}} \right)
+^{1/3}
+\label{eqn:cart_cell}
+\end{equation}
+where $dM_{\rm{cart}}$ is the mass of a cell in a cartesian grid and
+$\rho_{\rm{cell}}$ is the density of the cell. 
+%
+In a cylindrical polar grid the mass of a cell is given by
+\begin{equation}
+dM_{\rm{cyl}} = \rho_{\rm{cell}} \frac{2 \pi r dr dz}{n_{\rm{azi}}}
+\end{equation}
+if there are $n_{\rm{azi}}$ uniform azimuthal cells. If the 
+resolution in $r$ and $z$ is the same then we can define 
+\begin{equation}
+dl_{\rm{cyl}} = dr = dz 
+\end{equation}
+which is related to the cell mass and density by
+\begin{equation}
+dl_{\rm{cyl}} = \left( \frac{n_{\rm{azi}} dM_{\rm{cyl}}}{2 \pi r
+  \rho_{\rm{cell}}} \right)  ^{1/2}
+\label{eqn:cyl_cell}
+\end{equation}
+If we require the resolution in cylindrical polar $r$ and $z$
+to match the resolution in cartesian $x$, $y$ and $z$ then $dl_{\rm{cyl}} =
+dl_{\rm{cart}}$. From eqn~\ref{eqn:cart_cell} and \ref{eqn:cyl_cell} 
+\begin{equation}
+dM_{\rm{cyl}} = \frac{2 \pi r}{n_{\rm{azi}}} \rho^{1/3} dM_{\rm{cart}}^{2/3}
+\end{equation}
+which describes the required conversion from a mass per cell limit
+suitable for a cartesian grid ($dM_{\rm{cart}}$) to an equivalent mass
+per cell limit suitable for a cylindrical polar grid ($dM_{\rm{cyl}}$).
+
+The grid generation tests were run using a cylindrical polar geometry
+with the modified mass per cell limit described above and an
+unmodified density contrast condition. The results are plotted in
+Fig.~\ref{fig:cp_grid_tests}.
+\begin{figure*}
+  \subfigure[Mass per cell condition and $10^5$ particles]{\includegraphics[scale=0.3]{figures/1e5_cyl_set1}}
+  \subfigure[Mass per cell condition and $10^6$ particles]{\includegraphics[scale=0.3]{figures/1e6_cyl_set1}}
+  \subfigure[Mass per cell condition and $10^7$ particles]{\includegraphics[scale=0.3]{figures/1e7_cyl_set1}}
+  \subfigure[Density contrast condition and $10^5$ particles]{\includegraphics[scale=0.3]{figures/1e5_cyl_set2}}
+  \subfigure[Density contrast condition and $10^6$ particles]{\includegraphics[scale=0.3]{figures/1e6_cyl_set2}}
+  \subfigure[Density contrast condition and $10^7$ particles]{\includegraphics[scale=0.3]{figures/1e7_cyl_set2}}
+  \caption{Number of octals (solid line) and percentage mass error
+    (dashed line) for cylindrical polar AMR grids generated using different grid
+    splitting methods and different numbers of particles. }
+  \label{fig:cp_grid_tests}
+\end{figure*}
+Using a cylindrical polar geometry results in a significantly reduced
+number of octals in the AMR grid but with larger mass errors. Provided
+the mass per cell limit is no more than $10^{27}\rm{g}$ then the total
+mass is well represented with significantly fewer cells than in a
+cartesian grid. The density contrast condition alone does not
+represent the total mass to within 3\% accuracy even with
+$f_{\rm{split}}=0.1$. Although this condition successfully adds
+enhanced resolution in regions of density contrast needs to be
+combined with a mass per cell limit to ensure a robust total mass
+representation.
+
+\section{Comparison of temperature distribution and SEDs with
+  benchmark results}
 
@@
 
-Ensuring a consistent representation of mass and density in the grid
-representation and in the SPH representation is an important
-requirement in ensuring accurate radiative transfer calculations. In
-order to have confidence in the results of the calculations we must
-also ensure that the temperature distribution is realistic. By
-comparing the Spectral Energy Distribution (SED) from our disc with the
-benchmark results we have a global measure of how well the density and
-temperature distributions are represented. In order to get an accurate
-SED both the density and temperature distributions must be well
-represented.
+Having investigated the procdure for setting up the radiative transfer
+grid we now proceed to studying the accuracy of the results from the
+radiative transfer calculation. This was carried out by comparing
+temperature distributions and spectral energy distributions (SEDs)
+from the benchmark disc. Temperature distribution errors provide a
+clear picture of where errors in the radiative transfer calculation
+are located whereas SEDs provide a direct link to an observable
+quantity and are a stringent test of the accuracy of the radiative
+transfer calculation.
 
-The disc was initially modelled using $10^5$ SPH particles and a mass
-per cell limit of $5\times10^{26}$g was used to construct the
-AMR grid. The mass per cell limit was chosen in
-preference to the density contrast limit to give the highest
-resolution near the central region of the disc, which we expect to be
-most important for determining the SED. SEDs were calculated using the
-{\small{TORUS}} code for viewing angles of 12.5 and 77.5 degrees (where an
-inclination angle of zero degrees indicates that the disc is viewed
-face-on) and the results are plotted in Fig.~\ref{fig:seds} (dashed line). Also
-plotted in Fig.~\ref{fig:seds} are the benchmark results of
-\cite{pascucci_2004} (solid line).
+The disc was initially modelled using $10^5$ SPH particles with an AMR
+grid contructed from a mass per cell limit of $5\times10^{26}$g.  The
+mass per cell limit was chosen in preference to the density contrast
+limit to give the highest resolution near the central region of the
+disc, which we expect to be most important for determining the
+SED. SEDs were calculated using the {\small{TORUS}} code for viewing
+angles of 12.5 and 77.5 degrees (where an inclination angle of zero
+degrees indicates that the disc is viewed face-on) and the results are
+plotted in Fig.~\ref{fig:seds} (dashed line). Also plotted in
+Fig.~\ref{fig:seds} are the benchmark results of \cite{pascucci_2004}
+(solid line).
 \begin{figure*}
@@
 Both SEDs show significant departures from the benchmark results;
-there is excess emission between 10-100 $\mu\rm{m}$ and at a viewing angle of
-77.5 degrees there is also a significant reduction in the short
-wavelength flux. The density distribution in the central region of
+there is excess emission between 10-100 $\mu\rm{m}$ and at a viewing
+angle of 77.5 degrees there is also a significant reduction in flux
+below 1~$\mu\rm{m}$. The density distribution in the central region of
 this disc is plotted in Fig.~\ref{fig:basic_dens} which shows that the
@@
 operation; firstly the grid resolution in this region is larger than
-1AU and secondly the smoothing lengths of the particles are 
-larger than 1AU. In order to correctly represent the central gap there
-needs to be higher grid resolution around the central source and 
-more SPH particles are required so that the smoothing lengths are
-smaller. 
+1AU and secondly the smoothing lengths of the particles are larger
+than 1AU. In order to correctly represent the central gap there needs
+to be higher grid resolution around the central source and more SPH
+particles are required so that the smoothing lengths are smaller.
 \begin{figure}
@@
 
+\subsection{Grid resolution}
 Decreasing the mass per cell limit to achieve the required resolution
@@
 $6\times10^{13}$~cm. Within each cube it was required that the cell
-size be no larger than 0.1 of the cube dimension.
-
-In order to confirm that the grid modifications provide sufficient
-resolution to generate an accurate SED three calculations were
-performed with the central part of the disc forced to the correct
-density values from the analytical density description.  A spherical region
-with radius $1.0\times10^{15}$~cm, $5.0\times10^{14}$~cm or
-$2.5\times10^{14}$~cm was over written with the benchmark disc density
-after the initial grid generation was performed. The resulting SEDs
-are plotted in Fig.~\ref{fig:sed_forced}. The solid line shows the
-benchmark result and the other lines show SEDs for forcing regions of
-radius $1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm
-(short dashed line) and $2.5\times10^{14}$~cm (dotted line).
+size be no larger than 0.1 of the cube dimension. In order to confirm
+that the grid modifications provide sufficient resolution to generate
+an accurate SED three calculations were performed with the central
+part of the disc forced to the correct density values from the
+analytical density description.  A spherical region with radius
+$1.0\times10^{15}$~cm, $5.0\times10^{14}$~cm or $2.5\times10^{14}$~cm
+was over written with the benchmark disc density after the initial
+grid generation was performed. The resulting SEDs are plotted in
+Fig.~\ref{fig:sed_forced}. The solid line shows the benchmark result
+and the other lines show SEDs for forcing regions of radius
+$1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm (short
+dashed line) and $2.5\times10^{14}$~cm (dotted line).
 \begin{figure*}
@@
 
+\subsection{Number of particles}
 Further calculations were performed using different numbers of SPH
-particles and the enhanced grid resolution described above. SEDs are
-plotted in Fig.~\ref{fig:n_part_sed_013} for a viewing angle of 12.5
-degrees and Fig.~\ref{fig:n_part_sed_077} for a viewing angle of 77.5
-degrees. The density distribution in the central region is plotted in
-Fig.~\ref{fig:n_part_central_dens}.
-%
+particles and the enhanced grid resolution described above in order to
+determine the impact of the number of SPH particles on the accuracy of
+the radiative transfer calculation. The density distribution in the
+central region of the disc is plotted in
+Fig.~\ref{fig:n_part_central_dens} in order to show how the
+representation improves as the number of particles is increased.
+\begin{figure*}
+  \subfigure[$10^5$ particles]{\includegraphics[scale=0.22]{figures/dens_1e5}}
+  \subfigure[$10^6$ particles]{\includegraphics[scale=0.22]{figures/dens_1e6}}
+  \subfigure[$10^7$ particles]{\includegraphics[scale=0.22]{figures/dens_1e7}}
+  \subfigure[$10^8$ particles]{\includegraphics[scale=0.22]{figures/dens_1e8}}
+  \caption{Central density on AMR grid derived from different numbers
+    of SPH particles. The axis units are $10^{13}$~cm.} 
+  \label{fig:n_part_central_dens}
+\end{figure*}
+With $10^5$ and $10^6$ particles a central gap is present but is too
+large. With $10^7$ particles there is more material close in to the
+source but the gap itself is not represented and the source is
+obscured. Only with $10^8$ particles is a gap of approximately the
+correct size present.  The representation of the central 1~AU gap is
+significantly affected by the number of particles used to represent
+the disc, with a large number of particles required to achieve an
+accurate density distribution in this spatially small region.
+
+Figure~\ref{fig:n_part_tem_diff} shows fractional errors in the
+temperature distribution for different numbers of
+particles. {\small{TORUS}} calculates the temperature distribution
+using a high resolution 2D geometry, in order to determine the correct
+temperature as a function of cylindrical polar $r$ and $z$
+co-ordinates. This is then compared to the temperature from the SPH
+disc for each SPH particle. Positive values of the fractional error
+indicate that the SPH disc is hotter than the expected value.
+\begin{figure*}
+  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/tdiff_1e5}}
+  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/tdiff_1e6}}
+  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/tdiff_1e7}}
+  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/tdiff_1e8}}
+  \caption{Fractional temperature error for discs represented by
+    different numbers of SPH particles. Axis units are AU.} 
+  \label{fig:n_part_tem_diff}
+\end{figure*}
+When using $10^5$ particles to represent the disc there is a too much
+heating in the disc mid plane and insufficient heating further out of
+the mid plane. The effect is reduced when $10^6$ particles are used
+but is only reduced to a low level with $10^8$ particles.
+
+To allow a more quantitative comparison the mid-plane temperature and
+the benchmark mid-plane temperature are plotted in
+Fig.~\ref{fig:n_part_tem_diff_midpane} for all particles within 0.01
+scale heights of the mid-plane. The fractional temperature error for
+each particle is also plotted where a positive error indicates a
+temperature hotter than the benchmark value.
+\begin{figure*}
+  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/mp_temp_1}}
+  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/mp_temp_2}}
+  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/mp_temp_3}}
+  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/mp_temp_4}}
+  \caption{Fractional temperature error in the mid-plane for discs represented by
+    different numbers of SPH particles.} 
+  \label{fig:n_part_tem_diff_midpane}
+\end{figure*}
+
+SEDs are plotted in Fig.~\ref{fig:n_part_sed_013} for a viewing angle
+of 12.5 degrees and Fig.~\ref{fig:n_part_sed_077} for a viewing angle
+of 77.5 degrees. At the shortest wavelengths the 12.5 degrees
+inclination angle SED is dominated by emission from the central
+star. This region is well represented with $10^5$ and $10^8$ particles
+but is less well represented with $10^6$ or $10^7$ particles where the
+central star is obscured. At the longest wavelengths the disc is optically
+thin and the SEDs will be well modelled provided the total disc mass
+is accurately represented. In all four cases the total disc mass is
+well represented at the long wavelength SED matches the benchmark
+results. At intermediate wavelengths the SED is sensitive to the
+details of the disc representation. Accurately modelling the SED from
+this disc is challenging even with $10^8$ particles. 
 \begin{figure*}
@@
 \end{figure*}
-%
 \begin{figure*}
@@
 \end{figure*}
-%
-\begin{figure*}
-  \subfigure[$10^5$ particles]{\includegraphics[scale=0.22]{figures/dens_1e5}}
-  \subfigure[$10^6$ particles]{\includegraphics[scale=0.22]{figures/dens_1e6}}
-  \subfigure[$10^7$ particles]{\includegraphics[scale=0.22]{figures/dens_1e7}}
-  \subfigure[$10^8$ particles]{\includegraphics[scale=0.22]{figures/dens_1e8}}
-  \caption{Central density on AMR grid derived from different numbers
-    of SPH particles. The axis units are $10^{13}$~cm.} 
-  \label{fig:n_part_central_dens}
-\end{figure*}
-With $10^5$ and $10^6$ particles a central gap is present but is too
-large. With $10^7$ particles there
-is more material close in to the source but the gap itself is not
-represented and the source is obscured. Only with $10^8$ particles is
-a gap of approximately the correct size present.
-
-Figure~\ref{fig:n_part_tem_diff} shows fractional errors in the
-temperature distribution for different numbers of particles. {\small{TORUS}}
-calculates the temperature distribution using a high resolution 2D
-geometry, in order to determine the correct temperature as a function
-of cylindrical polar $r$ and $z$ co-ordinates. This is then
-compared to the temperature from the SPH disc for each SPH
-particle. Positive values of the fractional error indicate that the
-SPH disc is hotter than the expected value.
-\begin{figure*}
-  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run1}}
-  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run2}}
-  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run3}}
-  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/tdiff_run4}}
-  \caption{Fractional temperature error for discs represented by
-    different numbers of SPH particles. Axis units are AU.} 
-  \label{fig:n_part_tem_diff}
-\end{figure*}
-When using $10^5$ particles to represent the disc there is a
-too much heating in the disc mid plane and insufficient heating
-further out of the mid plane. The effect is reduced when $10^6$
-particles are used but is only reduced to a low level with $10^8$
-particles. The representation of the central region of the disc not
-only has a significant impact on the SEDs but also on the temperature
-distribution within the disc.
 
@@
 disc of $0.02~{M}_{\odot}$ is initialised with an outer radius of
-150~AU, and an inner radius of 0.5~AU, surrounding a central star of
+150~AU, and an inner radius of 1.0~AU, surrounding a central star of
 mass $1~M_{\odot}$. The central star is represented by a sink particle
-which accretes gas particles within an accretion radius of 0.5~AU. The
-disc itself is initially represented using $2\times10^5$ particles of
+which accretes gas particles within an accretion radius of 1.0~AU. The
+disc itself is initially represented using $10^6$ particles of
 equal mass, although some of these particles are accreted by the
@@
 perpendicular to the plane of the disc and has a $T\propto 1/r$ radial
-dependence. The disc is evolved for approximately 3000
-years of simulated time in order to allow transient effects from the
-initialisation to dissipate. Approximately 10~per~cent of the gas particles are
-accreted by the sink particle during this initial phase but the mass
-does not change significantly after this time.
+dependence. The disc is evolved for approximately 4000 years of
+simulated time in order to allow transient effects from the
+initialisation to dissipate. As the disc settles towards an
+equilibrium state there are vertical motions which cause fluctuations
+in the envelope of the disc, with the inner regions of the disc
+reaching equilibrium more rapidly than the outer regions.
 
-After the initial period the disc is evolved using the combined SPH
-and radiative transfer code. In this configuration the internal
-energies of the SPH particles are set using the temperatures
-calculated by the radiative transfer code. The SPH part of the code
-does not change the particle temperatures and they retain the
-temperature assigned by the radiative transfer code until the next
-radiation time step. The temperatures calculated by the radiative
-transfer code are equilibrium temperatures, as it is assumed that the
-time scale for radiative equilibrium is short compared to the
-dynamical time scale of the disc.
+The disc is then evolved using the combined SPH and radiative transfer
+code. In this configuration the internal energies of the SPH particles
+are set using the temperatures calculated by the radiative transfer
+code. The SPH part of the code does not change the particle
+temperatures and they retain the temperature assigned by the radiative
+transfer code until the next radiation time step. The temperatures
+calculated by the radiative transfer code are equilibrium
+temperatures, as it is assumed that the time scale for radiative
+equilibrium is short compared to the dynamical time scale of the disc.
+A radiative transfer calculation is performed after every four
+hydrodynamics time steps (equivalent to every 2.4 years). The freqency
+with which the radiative transfer is calculated is determined by the
+sound crossing time in the inner regions of the disc as this is the
+time scale over which the scale height in this region will vary and
+effect the transfer of radiation into the outer parts of the disc.
 
-The SPH code uses a non-dimensionalised unit system and the radiative
-transfer step is called after an elapsed time of 1.0 code units (1.89
-years). This time interval was chosen to allow the hydrodynamics to
-respond to the radiative heating and achieve a suitable balance
-between the hydrodynamics and the slower radiative transfer
-calculation.
-
-The AMR grid is constructed using a maximum mass per cell of
-$5.0\times10^{26}~\rm{g}$, corresponding approximately to the mass of
-two SPH particles. The density in a cylindrical region around the
+A cylindrical polar grid, with adaptive $r$ and $z$ cells and 16
+azimuthal cells, was used for the raditive transfer step. The AMR grid
+was constructed using a maximum mass per cell of
+$3.0\times10^{25}~\rm{g}$ and a density splitting condition of
+$f_{\rm{split}}=0.1$. The density in a cylindrical region around the
 source was reduced to a very low value to ensure that the disc did not
 completely obscure the source. The radius of this region is
-$R_{\rm{gap}}=0.5~\rm{AU}$ which corresponds to the accretion radius
+$R_{\rm{gap}}=1.0~\rm{AU}$ which corresponds to the accretion radius
 of the SPH sink particle. Two extra levels of grid refinement were
@@
 enough resolution to allow the gap around the source to be
-resolved. The first box of extra refinement had size $10R_{\rm{gap}}$
-in the plane of the disc and size $40R_{\rm{gap}}$ perpendicular to
-the disc with a maximum cell size of $R_{\rm{gap}}$; the second box of
-extra refinement had size $2.5R_{\rm{gap}}$ in the plane of the disc
-and size $20R_{\rm{gap}}$ perpendicular to the disc with a maximum
-cell size of $0.5R_{\rm{gap}}$. A real circumstellar disc will be
-truncated by the stellar magnetosphere so there is a physical
-justification for enforcing a low density region around the star.
+resolved. The first box of extra refinement has size $10^{14}~\rm{cm}$
+with cells no larger than $10^{13}~\rm{cm}$ and the second box has
+size $4\times10^{13}~\rm{cm}$ with cells no larger than
+$4\times10^{12}~\rm{cm}$.  A real circumstellar disc will be truncated
+by the stellar magnetosphere so there is a physical justification for
+enforcing a low density region around the star.
 
-\subsection{Transient effects}
+Plots of the disc internal energy are shown in Fig.~\ref{fig:log_u} at siz
+different times during the simulation. Figure~\ref{fig:frame1} shows
+the initial state before the radiative transfer is switched on. The
+disc is vertically isothermal. The second frame (Fig.~\ref{fig:frame2}
+is shortly after the raditive transfer has been swithced on. The inner
+disc has collapsed and there is heating seen in parts of the disc
+exposed to radiation from the central star. In Fig.~\ref{fig:frame3} a
+scale height enhancement is present in the disc at a radius of
+approximately $3\times10^{15}~\rm{cm}$ which shadows the region
+immediately behind causing it to cool. Figure~\ref{fig:frame4} shows
+several such scale height enhancements an in each case there is
+cooling behind the enhancement. The scale height fluctations are able
+to affect the mid-plane temperature due to vertical transport of
+radiation. In Fig.~\ref{fig:frame5} the inner region of the disc has
+settled and the scale height enhancements are seen only in the outer
+disc and by the last frame (Fig.~\ref{fig:frame6}) the disc has
+reached a steady state in hydrostatic and radiative equilibrium. 
+\begin{figure*}
+  \subfigure[]{\includegraphics[scale=0.3]{figures/u_DSC6675}\label{fig:frame1}}
+  \subfigure[]{\includegraphics[scale=0.3]{figures/u_DSC6691}\label{fig:frame2}}
+  \subfigure[]{\includegraphics[scale=0.3]{figures/u_DSC6763}\label{fig:frame3}}
+  \subfigure[]{\includegraphics[scale=0.3]{figures/u_DSC7363}\label{fig:frame4}}
+  \subfigure[]{\includegraphics[scale=0.3]{figures/u_DSC9363}\label{fig:frame5}}
+  \subfigure[]{\includegraphics[scale=0.3]{figures/u_run2_DSC1024}\label{fig:frame6}}
+  \caption{Particle plots showing internal energy in cyclindrical
+    polar co-ordinates. Axis units are cm.}
+  \label{fig:log_u}
+\end{figure*}
 
-When the radiative transfer calculation is introduced there is an
-adjustment of the disc towards a new hydrostatic balance which is
-consistent with the new temperature structure. As the temperature
-structure is dependent on the density structure is is necessary to
-iterate the solution towards a state where both hydrostatic and
-radiative balance are simultaneously achieved. This section examines
-how the structure of the disc evolves towards such a state. The
-ultimate aim of this simulation is to achieve a disc which is in
-hydrostatic and radiative balance so the transients are of interest
-from a numerical, rather than a physical, perspective.
-
-Particle densities as a function of radius are plotted in
-Fig.~\ref{fig:trans_rho} for four different times during the period
-when the disc is adjusting towards equilibrium. The first plot shows
-the distribution immediately before the radiative transfer is
-introduced (i.e. this is the density distribution from the SPH code
-alone, with a vertically isothermal equation of state). At any given
-radius there is a spread of particle densities as the density varies
-with height out of the disc mid-plane. The second frame is
-approximately 30 years after radiative transfer has been
-introduced. The peak density (at around $2\times10^{14}~\rm{cm}$) has
-been increased but at this time there is no observable effect on the
-outer regions of the disc. In the third frame density enhancements are
-seen in the density profile at radii of approximately
-$4\times10^{14}~\rm{cm}$ and $7\times10^{14}~\rm{cm}$. In the fourth
-frame these enhancements have propagated outwards and a third
-enhancement is also seen, although with a lower amplitude.
-
-The particle positions, as a function of cylindrical polar $r$ and $z$
-co-ordinates, are plotted in Fig.~\ref{fig:trans_rz} (note the
-expanded vertical scale). From an initially relaxed state (first
-frame) the central region of the disc is seen to collapse in the
-second frame, which accounts for the increase in density seen in
-Fig.~\ref{fig:trans_rho}. 
-\begin{figure*}
-  \includegraphics[scale=0.3]{figures/rho_vs_r_5147}
-  \includegraphics[scale=0.3]{figures/rho_vs_r_5197}
-  \includegraphics[scale=0.3]{figures/rho_vs_r_5397}
-  \includegraphics[scale=0.3]{figures/rho_vs_r_5597}
-  \caption{Particle density as a function of cylindrical polar radius
-    for a disc modelled using the combined SPH-radiative transfer
-    code. Four different times are shown to illustrate the transient
-    effects present as the disc evolves towards an equilibrium state.}
-\label{fig:trans_rho}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[scale=0.3]{figures/rz_5147}
-  \includegraphics[scale=0.3]{figures/rz_5197}
-  \includegraphics[scale=0.3]{figures/rz_5397}
-  \includegraphics[scale=0.3]{figures/rz_5597}
-  \caption{Particle positions as a function of cylindrical r and z
-    co-ordinates for a disc modelled using the combined SPH-radiative
-    transfer code. Four different times are shown to illustrate the
-    transient effects present as the disc evolves towards an
-    equilibrium state.}
-\label{fig:trans_rz}
-\end{figure*}
-Several fluctuations in the disc scale height can be seen as the
-simulation progresses. Such fluctuations have been observed previously
-in codes which calculate both radiative transfer and vertical hydrostatic
-equilibrium \citep{min_2009,watanabe_2008}. With our coupled radiative
-transfer and 3 dimensional hydrodynamics code we find that the
-oscillations propagate outwards through the disc and that successive
-oscillations are of reduced amplitude, hence we find that it is
-possible to evolve this disc to a steady state solution.
-
-The transient effects of the disc adjusting toward a new equilibrium
-state are not limited to scale height
-fluctuations. Figure~\ref{fig:sigma_transients} shows surface density
-plots for two different times during the adjustment phase, which
-indicates that there are transient effects in the surface density as
-well as in the scale height. These effects would not be present in a
-code which calculates vertical hydrostatic equilibrium only.
-\begin{figure}
-  \includegraphics[scale=0.3]{figures/sigma}
-  \caption{Surface density, as a function of cylindrical polar radius,
-  after a simulated time of 3200~yr (solid line) and 3319~yr.}
-  \label{fig:sigma_transients}
-\end{figure}
-% Dump number 5397 is at 3200 yrs
-% Dump number 5597 is at 3319 yrs
-
-\subsection{Equilibrium state of disc}
+%%% Up to here so far ... %%%
 

### 2009-08-25 SPH-Torus-paper1/figures/getfigs.sh
New figures.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2023 25464f21-6099-402c-b30a-640f1d40d38b

@@ -1,0 +1,192 @@
+#!/bin/ksh
+#set -ax
+
+#################################################
+#  Grid generation study
+#################################################
+
+############
+# Figure 1 #
+############
+
+# Get mesh plots
+scp zen:/scratch/acreman/sph_disc/grid_tests/working/runs/cyl_geom_F/npart_1e7/set1/run_5.e26/mesh0000.tif .
+/sw/bin/convert mesh0000.tif set1_mesh.pdf
+rm mesh0000.tif
+
+scp zen:/scratch/acreman/sph_disc/grid_tests/working/runs/cyl_geom_F/npart_1e7/set2/run_0.1/mesh0000.tif .
+/sw/bin/convert mesh0000.tif set2_mesh.pdf
+rm mesh0000.tif
+
+############
+# Figure 2 #
+############
+
+# Get plots from grid generation parameter study
+# Cartesian grids
+export BASE_DIR=zen:/scratch/acreman/sph_disc/grid_tests/working/runs/cyl_geom_F/
+for num_part in 1e5 1e6  1e7; do
+    work_dir=npart_${num_part}
+    for dir in set1 set2; do
+	for file in ${dir}.ps; do
+	    this_fig=${dir}.ps
+	    scp ${BASE_DIR}/${work_dir}/${dir}/${this_fig} ${num_part}_${this_fig}
+	    ps2pdf ${num_part}_${this_fig}
+	    rm ${num_part}_${this_fig}
+	done
+    done
+done
+
+############
+# Figure 3 #
+############
+
+export BASE_DIR=zen:/scratch/acreman/sph_disc/grid_tests/working/runs/cyl_geom_T/
+for num_part in 1e5 1e6  1e7; do
+    work_dir=npart_${num_part}
+    for dir in set1 set2; do
+	for file in ${dir}.ps; do
+	    this_fig=${dir}.ps
+	    scp ${BASE_DIR}/${work_dir}/${dir}/${this_fig} ${num_part}_cyl_${this_fig}
+	    ps2pdf ${num_part}_cyl_${this_fig}
+	    rm ${num_part}_cyl_${this_fig}
+	done
+    done
+done
+
+#################################################
+# sphbench
+#################################################
+
+############
[…]

### 2009-08-26 SPH-Torus-paper1/figures/getfigs.sh
Updated versions of disc property plots.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2024 25464f21-6099-402c-b30a-640f1d40d38b

@@ -174,19 +174,11 @@ scp zen:/scratch/acreman/SPH-Torus_runs/run0001/run2/dumps/u_run2_DSC1024.ps .
 ps2pdf u_run2_DSC1024.ps
 rm u_run2_DSC1024.ps
 
-cp ~/sph_disc_pp/profiles/sigma.ps .
-ps2pdf sigma.ps
-
-cp ~/sph_disc_pp/profiles/sigma_final.ps .
-ps2pdf sigma_final.ps
-
-cp ~/sph_disc_pp/scale_height/mid_tem.ps .
-ps2pdf mid_tem.ps
-
-cp ~/sph_disc_pp/scale_height/scale_height.ps .
-ps2pdf scale_height.ps
-
-rm *.ps
+for fig in sigma.ps mid_tem.ps scale_height.ps; do 
+    scp zen:/scratch/acreman/SPH-Torus_runs/run0001/post_processing/disc_props/${fig} . 
+    ps2pdf ${fig} 
+    rm ${fig}
+done
 
 exit
 

### 2009-08-26 SPH-Torus-paper1/sphtorus_benchmark.tex
Updated section of SPH-Torus disc.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2025 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
+\subsection{Results}
+
 Plots of the disc internal energy are shown in Fig.~\ref{fig:log_u} at siz
@@
 
-%%% Up to here so far ... %%%
-
-The surface density of the disc, after 4986~years of simulated time
-(the latest simulated time), is shown in Fig.~\ref{fig:sigma_final}.
-Away from the inner and outer edges of the disc the surface density is
-well represented by a power law profile as a function of radius.
+The surface density of the disc is shown in Fig.~\ref{fig:sigma} where
+the solid line is the isothermal disc and the dotted line is the disc
+at the final time step.  Away from the inner and outer edges of the
+disc the surface density is well represented by a power law profile as
+a function of radius.
 \begin{figure}
-  \includegraphics[scale=0.3]{figures/sigma_final}
-  \caption{Surface density as a function of radius after 4986~years of simulated time.}
-  \label{fig:sigma_final}
+  \includegraphics[scale=0.3]{figures/sigma}
+  \caption{Surface density as a function of radius.}
+  \label{fig:sigma}
 \end{figure}
-
 The scale height of the disc was determined by fitting Gaussians to
@@
 profile appears flat so it was not possible to fit a meaningful scale
-height.
+height. The solid line is the isothermal disc and the dotted line is
+the disc at the final time step.
 \begin{figure}
   \includegraphics[scale=0.3]{figures/scale_height}
-  \caption{Disc scale height as a function of radius  after 4986~years of simulated time.}
+  \caption{Disc scale height as a function of radius.}
   \label{fig:scale_height}
 \end{figure}
-
 The average temperature within one scale height of the disc mid plane
-is plotted as a solid line in Fig.~\ref{fig:mid_tem}. The dashed line
-is a power law variation of temperature with radius with an index of
-$-0.35$. Although this line is not a formal best fit it has been
-plotted to indicate that this temperature profile is well represented
-by a power law outside 15AU.
+is plotted in Fig.~\ref{fig:mid_tem}. The solid line is the isothermal
+disc and the dotted line is the disc at the final time step.
 \begin{figure}
   \includegraphics[scale=0.3]{figures/mid_tem}
-  \caption{Average temperature within one scale height of the mid plane, as a function of
-    radius, after 4986~years of simulated time.}
+  \caption{Average temperature within one scale height of the mid plane as a function of
+    radius.}
   \label{fig:mid_tem}

### 2009-08-27 SPH-Torus-paper1/sphtorus_benchmark.tex
Minor changes.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2026 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-We present results from combining a grid-based radiative transfer code
-with a Smoothed Particle Hydrodynamics code to produce a flexible
-system for modelling radiation hydrodynamics. The system is tested
-using a benchmark model of a circumstellar disc. We find that the SED
-and temperature distribution within the disc are highly sensitive to
-the representation of the disc inner edge, which depends critically on
-both the grid and SPH resolution. The system is then used to model a
-circumstellar disc around a T-Tauri star and is found to produce a
-steady state disc in both hydrostatic and radiative equilibrium.
+  We present results from combining a grid-based radiative transfer
+  code with a Smoothed Particle Hydrodynamics code to produce a
+  flexible system for modelling radiation hydrodynamics. We use a
+  benchmark model of a circumstellar disc to determine a robust method
+  for constructing a gridded density density distribution from SPH
+  particles. The benchmark disc is then used to determine the accuracy
+  of the radiative transfer results. We find that the SED and 
+  the temperature distribution within the disc are sensitive
+  to the representation of the disc inner edge, which depends
+  critically on both the grid and SPH resolution. The code is then
+  used to model a circumstellar disc around a T-Tauri star. As the
+  disc adjusts towards equilibrium vertical motions in the disc are
+  induced resulting in scale height enhancements which intecept
+  radiation from the central star. Vertical transport of radiation
+  enables these perturbations to influence the mid-plane temperature
+  of the disc. The vertical motions decay over time and the disc
+  ultimately reaches a state of simulatanous hydrostatic and radiative
+  equilibrium.
 
@@
 
-This paper presents a results from coupling the {\small{TORUS}} radiative
-transfer code \citep{harries_2000} with the SPH (Smoothed Particle
-Hydrodynamics) code of \cite{bate_2009}.  {\small{TORUS}} performs radiative
-transfer calculations using the Monte-Carlo method of \cite{lucy_1999}
-with a flux limited diffusion approximation in regions of high optical
-depth. The radiative transfer calculations are performed on a grid
-which uses adaptive mesh refinement (AMR) to allow variable
+This paper presents a results from coupling the {\small{TORUS}}
+radiative transfer code \citep{harries_2000} with the SPH (Smoothed
+Particle Hydrodynamics) code of \cite{bate_2009}.  {\small{TORUS}}
+performs radiative transfer calculations using the Monte-Carlo method
+of \cite{lucy_1999} with a diffusion approximation in regions of high
+optical depth. The radiative transfer calculations are performed on a
+grid which uses adaptive mesh refinement (AMR) to allow variable
 resolution.  The SPH method is well suited to dealing with the large
-range in size scales encountered during star formation processes, hence
-an SPH code coupled to a combined Monte-Carlo and flux limited
-diffusion radiative transfer code is a very flexible method for
-performing star formation calculations incorporating radiative
-feedback.
+range in size scales encountered during star formation processes,
+hence an SPH code coupled to a Monte-Carlo radiative transfer code is
+a very flexible method for performing star formation calculations
+incorporating radiative feedback.
 
@@
 grid. The procedure used for this transformation is tested using a
-benchmark case (see Sections~\ref{section:description_of_benchmark}
+cicumstellar disc benchmark (see
+Sections~\ref{section:description_of_benchmark}
 and~\ref{section:grid_generation}). The spectral energy distribution
@@
 simulation of a circumstellar disc around a T Tauri star is presented
-in Section~\ref{section:sph_disc} with the aim of calculating an
-equilibrium state in three dimensional hydrostatic and radiative
-balance.
+in Section~\ref{section:sph_disc}.
 
@@
 and the location of the highest resolution regions, while maintaining
-an accurate representation of the disc mass.
+an accurate representation of the total disc mass.
 
@@
 \end{equation}
-where $dM_{\rm{cart}}$ is the mass of a cell in a cartesian grid and
+where $dM_{\rm{cart}}$ is the mass of a cell in the cartesian grid and
 $\rho_{\rm{cell}}$ is the density of the cell. 
@@
 heating in the disc mid plane and insufficient heating further out of
-the mid plane. The effect is reduced when $10^6$ particles are used
-but is only reduced to a low level with $10^8$ particles.
+the mid plane. The effect is reduced as the number of particles is
+increased and reaches a very low level with $10^8$ particles.
 
@@
 inclination angle SED is dominated by emission from the central
-star. This region is well represented with $10^5$ and $10^8$ particles
-but is less well represented with $10^6$ or $10^7$ particles where the
-central star is obscured. At the longest wavelengths the disc is optically
-thin and the SEDs will be well modelled provided the total disc mass
-is accurately represented. In all four cases the total disc mass is
-well represented at the long wavelength SED matches the benchmark
-results. At intermediate wavelengths the SED is sensitive to the
-details of the disc representation. Accurately modelling the SED from
-this disc is challenging even with $10^8$ particles. 
+star. This region of the SED is well represented with $10^5$ and
+$10^8$ particles but is less well represented with $10^6$ or $10^7$
+particles where the central star is obscured. At the longest
+wavelengths the disc is optically thin and the SEDs will be well
+modelled provided the total disc mass is accurately represented. In
+all four cases the total disc mass is well represented and the long
+wavelength SED matches the benchmark results. At intermediate
+wavelengths the SED is sensitive to the details of the disc
+representation and it is clear that accurately modelling the SED from
+this disc is challenging, even with $10^8$ particles. 
 \begin{figure*}
@@
 
-Plots of the disc internal energy are shown in Fig.~\ref{fig:log_u} at siz
-different times during the simulation. Figure~\ref{fig:frame1} shows
-the initial state before the radiative transfer is switched on. The
-disc is vertically isothermal. The second frame (Fig.~\ref{fig:frame2}
-is shortly after the raditive transfer has been swithced on. The inner
-disc has collapsed and there is heating seen in parts of the disc
-exposed to radiation from the central star. In Fig.~\ref{fig:frame3} a
-scale height enhancement is present in the disc at a radius of
-approximately $3\times10^{15}~\rm{cm}$ which shadows the region
-immediately behind causing it to cool. Figure~\ref{fig:frame4} shows
-several such scale height enhancements an in each case there is
-cooling behind the enhancement. The scale height fluctations are able
-to affect the mid-plane temperature due to vertical transport of
-radiation. In Fig.~\ref{fig:frame5} the inner region of the disc has
-settled and the scale height enhancements are seen only in the outer
-disc and by the last frame (Fig.~\ref{fig:frame6}) the disc has
-reached a steady state in hydrostatic and radiative equilibrium. 
+Plots of the disc internal energy are shown in Fig.~\ref{fig:log_u} at
+siz different times during the simulation. Figure~\ref{fig:frame1}
+shows the initial state before the radiative transfer is switched on
+when there is a vertically isothermal equation of state. The second
+frame (Fig.~\ref{fig:frame2} is shortly after the raditive transfer
+has been switched on. The inner disc has collapsed and there is
+heating seen in parts of the disc exposed to radiation from the
+central star. In Fig.~\ref{fig:frame3} a scale height enhancement is
+present in the disc at a radius of approximately
+$3\times10^{15}~\rm{cm}$ which shadows the region immediately behind
+causing it to cool. Figure~\ref{fig:frame4} shows several such scale
+height enhancements an in each case there is cooling behind the
+enhancement. The scale height fluctations are able to affect the
+mid-plane temperature due to vertical transport of radiation. In
+Fig.~\ref{fig:frame5} the inner region of the disc has settled and the
+scale height enhancements are seen only in the outer disc and by the
+last frame (Fig.~\ref{fig:frame6}) the disc has reached a steady state
+in hydrostatic and radiative equilibrium.
 \begin{figure*}
@@
 The surface density of the disc is shown in Fig.~\ref{fig:sigma} where
-the solid line is the isothermal disc and the dotted line is the disc
-at the final time step.  Away from the inner and outer edges of the
-disc the surface density is well represented by a power law profile as
-a function of radius.
+the solid line is the vertically isothermal disc shown in
+Fig.~\ref{fig:frame1} and the dotted line is the disc at the final
+time step (Fig.~\ref{fig:frame6}).  Away from the inner and outer
+edges of the disc the surface density is well represented by a power
+law profile as a function of radius.
 \begin{figure}
@@
 central region of the disc to allow the inner edge to be well
-represented. The inner edge of the disc has a disproportionately large
+represented. The inner edge of the disc has a large
 effect on the temperature distribution in the disc and on the emergent
@@
 particular challenge for a SPH code which uses equal mass particles
-but is achievable with a large number of particles.
+but is achievable with a large number of particles. Accurately
+modelling the SED using this method seems to be considerably more
+demanding than accurately representing the temperature structure
+within the disc and temperature errors can be reduced to a managable
+level with a realistic number of SPH particles in the disc.
 
@@
 circumstellar disc to a state of radiative and hydrostatic
-equilibrium. Fluctuations in scale height were seen, which have also
-been observed in codes which combine radiative transfer and vertical
-hydrostatic equilibrium calculations. However there were also
-transient effects seen in the surface density distribution which would
-not be present if the hydrostatic equilibrium was calculated in the
-vertical direction only.
-
-By adding self-gravity to the SPH model this method could be used to
-explore the effects of radiative transfer on disc
-fragmentation. However the model would need to be constructed
-carefully to ensure sufficient resolution at the disc inner edge so
-that the temperature distribution in the disc is accurate. Such a
-model is expected to be feasible although computationally demanding.
+equilibrium. As the disc settles towards an equilibrium state, vertical
+motions are seen which give the appearance of an outward propagating
+scale height fluctuation. This is a vertical motion which decays more
+rapidly at smaller radii and is seen whether radiative transfer is
+included or not. One consequence of these fluctuations is that they
+can intecept radiation from the central star which can then be
+vertically transported into the mid-plane of the disc. Even thought
+the fluctuations are of a small amplitude they exert an influence on
+the mid-plane temperature.
 

### 2009-08-28 SPH-Torus-paper1/sphtorus_benchmark.tex
Minor updates.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2027 25464f21-6099-402c-b30a-640f1d40d38b

@@
 transfer code and a number of different approaches have been developed
-(\cite{nayakshin_2009}, \cite{pawlik_2008} and references
-therein). This paper focuses on radiative transfer calculations using
-an adaptive grid in the context of modelling processes in star
-formation.
+(\cite{pawlik_2008} and references therein). This paper focuses on
+radiative transfer calculations using an adaptive grid in the context
+of modelling a circumstellar disc.
 
-Accurately coupling the SPH component to the radiative transfer
+Accurately coupling the radiative transfer component to the SPH
 component requires an effective transformation from the Lagrangian
@@
 exceeded. The first condition gives a resolution like that of the
-original SPH representation whereas the second condition should be
-better at representing gradients in density which are likely to be
-important for radiative transfer calculations.
+original SPH representation whereas the second condition should better
+represent gradients in density which are important for radiative
+transfer calculations.
 
@@
 temperatures, as it is assumed that the time scale for radiative
-equilibrium is short compared to the dynamical time scale of the disc.
+equilibrium is short compared to the dynamical time scale of the disc
+(i.e. the ``prompt escape'' regime decribed by \cite{nayakshin_2009}).
 A radiative transfer calculation is performed after every four
@@
 
-The surface density of the disc is shown in Fig.~\ref{fig:sigma} where
-the solid line is the vertically isothermal disc shown in
-Fig.~\ref{fig:frame1} and the dotted line is the disc at the final
-time step (Fig.~\ref{fig:frame6}).  Away from the inner and outer
-edges of the disc the surface density is well represented by a power
-law profile as a function of radius.
+The surface density of the disc is shown in Fig.~\ref{fig:sigma}, the
+scale height is shown in Fig.~\ref{fig:scale_height} and the radial
+temperature profile is shown in Fig.~\ref{fig:mid_tem}.  The solid
+lines are from the vertically isothermal disc shown in
+Fig.~\ref{fig:frame1} and the dotted lines are the disc at the final
+time step shown in Fig.~\ref{fig:frame6}. The scale height of the disc
+was determined by allocating particles to 100 radial bins and fitting
+a Gaussian to the vertical density profile. The radial temperature
+profile is the average temperature within one scale height of the
+mid-plane for each radial bin.
 \begin{figure}
@@
 \end{figure}
-The scale height of the disc was determined by fitting Gaussians to
-the vertical density profile in 100 radial bins. The fitted scale
-height, as a function of radius, is plotted in
-Fig.~\ref{fig:scale_height}.  Within the central 10~AU the density
-profile appears flat so it was not possible to fit a meaningful scale
-height. The solid line is the isothermal disc and the dotted line is
-the disc at the final time step.
 \begin{figure}
@@
 \end{figure}
-The average temperature within one scale height of the disc mid plane
-is plotted in Fig.~\ref{fig:mid_tem}. The solid line is the isothermal
-disc and the dotted line is the disc at the final time step.
 \begin{figure}
@@
 \end{figure}     
+The majority of the surface density profile is well represented by a
+power law and does not change significantly as a result of including
+radiative transfer, except within the central
+region. Figures~\ref{fig:scale_height} and \ref{fig:mid_tem} show that
+the disc is hotter close to the mid-plane, except within a region
+between 10--20 AU of the centre, but has a smaller scale
+height. Figure~\ref{fig:log_u} shows that the vertical temperature
+gradient in the disc is such that temperature increases with height
+out of the mid-plane. Although the disc is hotter when radiative
+transfer is included the vertical temperature gradient tends to reduce
+the pressure gradient which is required for hydrostatic support
+resulting in a smaller scale height.
 
@@
 
-We have presented results from a combined SPH and grid-based radiative
-transfer code, which has been used to model a non-self gravitating
-circumstellar disc. Validation tests of the method have revealed a
-number of factors which must be taken into consideration when setting
-up a model of this type.
+We have presented results from a combined SPH and AMR grid-based
+radiative transfer code, which has been used to model a non-self
+gravitating circumstellar disc. Validation tests of the method have
+revealed a number of factors which must be taken into consideration
+when setting up a model of this type.
 
@@
 effect on the temperature distribution in the disc and on the emergent
-SED. Consequently the accuracy of the solution is dependent upon the
+SEDs. Consequently the accuracy of the solution is dependent upon the
 accurate representation of a region which constitutes a small fraction
@@
 circumstellar disc to a state of radiative and hydrostatic
-equilibrium. As the disc settles towards an equilibrium state, vertical
-motions are seen which give the appearance of an outward propagating
-scale height fluctuation. This is a vertical motion which decays more
-rapidly at smaller radii and is seen whether radiative transfer is
-included or not. One consequence of these fluctuations is that they
+equilibrium. As the disc settles towards an equilibrium state,
+vertical motions are seen which give the appearance of an outward
+propagating scale height fluctuation. This is a vertical motion which
+decays more rapidly at smaller radii and is seen whether radiative
+transfer is included or not. These are not the same as the
+instabilities seen in other radiation hydrodynamics disc models
+\citep{min_2009}. One consequence of these fluctuations is that they
 can intecept radiation from the central star which can then be
-vertically transported into the mid-plane of the disc. Even thought
-the fluctuations are of a small amplitude they exert an influence on
-the mid-plane temperature.
+vertically transported into the mid-plane of the disc hence even
+thought the fluctuations are of a small amplitude they exert an
+influence on the mid-plane temperature.
 

### 2009-09-28 SPH-Torus-paper1/sphtorus_benchmark.tex
Added paragraph explaining the benchmark case. Also corrected some typos.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2032 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \label{section:description_of_benchmark}
+
+The accuracy of the SPH method has previously been examined in detail
+(e.g. \cite{price_2008b} and references therein) so we do not attempt
+to benchmark the SPH component of the code here. Radiative transfer in
+a circumstellar disc has been studied in detail by
+\cite{pascucci_2004} and this benchmark is regularly used to test the
+accuracy of the {\small{TORUS}} code. Consequently we can be confident
+in the accuracy of the SPH and raditive transfer codes individually so
+we focus here on the accuracy of the mechansim by which they are
+coupled. Hence the benchmark case presented here is a ``static''
+benchmark in which we represent an analytical density distribution
+with SPH particles and test whether the radiative transfer code can
+calculate accurate results using this SPH density representation.
 
@@
 \begin{equation}
-dM_{\rm{cyl}} = \rho_{\rm{cell}} \frac{2 \pi r dr dz}{n_{\rm{azi}}}
+dM_{\rm{cyl}} = \rho_{\rm{cell}} \frac{2 \pi r dr dz}{n_{\rm{az}}}
 \end{equation}
-if there are $n_{\rm{azi}}$ uniform azimuthal cells. If the 
+if there are $n_{\rm{az}}$ uniform azimuthal cells. If the 
 resolution in $r$ and $z$ is the same then we can define 
@@
 \begin{equation}
-dl_{\rm{cyl}} = \left( \frac{n_{\rm{azi}} dM_{\rm{cyl}}}{2 \pi r
+dl_{\rm{cyl}} = \left( \frac{n_{\rm{az}} dM_{\rm{cyl}}}{2 \pi r
   \rho_{\rm{cell}}} \right)  ^{1/2}
@@
 \begin{equation}
-dM_{\rm{cyl}} = \frac{2 \pi r}{n_{\rm{azi}}} \rho^{1/3} dM_{\rm{cart}}^{2/3}
+dM_{\rm{cyl}} = \frac{2 \pi r}{n_{\rm{az}}} \rho^{1/3} dM_{\rm{cart}}^{2/3}
 \end{equation}
@@
 $f_{\rm{split}}=0.1$. Although this condition successfully adds
-enhanced resolution in regions of density contrast needs to be
-combined with a mass per cell limit to ensure a robust total mass
+enhanced resolution in regions of higher density contrast it needs to
+be combined with a mass per cell limit to ensure a robust total mass
 representation.
@@
 source was reduced to a very low value to ensure that the disc did not
-completely obscure the source. The radius of this region is
-$R_{\rm{gap}}=1.0~\rm{AU}$ which corresponds to the accretion radius
-of the SPH sink particle. Two extra levels of grid refinement were
-added in a box around the central source to ensure that the grid had
-enough resolution to allow the gap around the source to be
-resolved. The first box of extra refinement has size $10^{14}~\rm{cm}$
-with cells no larger than $10^{13}~\rm{cm}$ and the second box has
-size $4\times10^{13}~\rm{cm}$ with cells no larger than
-$4\times10^{12}~\rm{cm}$.  A real circumstellar disc will be truncated
-by the stellar magnetosphere so there is a physical justification for
-enforcing a low density region around the star.
+completely obscure the source. A real circumstellar disc will be
+truncated by the stellar magnetosphere so there is a physical
+justification for enforcing a low density region around the star. The
+radius of this region is $R_{\rm{gap}}=1.0~\rm{AU}$ which corresponds
+to the accretion radius of the SPH sink particle. Two extra levels of
+grid refinement were added in a box around the central source to
+ensure that the grid had enough resolution to allow the gap around the
+source to be resolved. The first box of extra refinement has size
+$10^{14}~\rm{cm}$ with cells no larger than $10^{13}~\rm{cm}$ and the
+second box has size $4\times10^{13}~\rm{cm}$ with cells no larger than
+$4\times10^{12}~\rm{cm}$.
 
@@
 Plots of the disc internal energy are shown in Fig.~\ref{fig:log_u} at
-siz different times during the simulation. Figure~\ref{fig:frame1}
+six different times during the simulation. Figure~\ref{fig:frame1}
 shows the initial state before the radiative transfer is switched on
@@
 causing it to cool. Figure~\ref{fig:frame4} shows several such scale
-height enhancements an in each case there is cooling behind the
-enhancement. The scale height fluctations are able to affect the
+height enhancements and in each case there is cooling behind the
+enhancement as the scale height fluctations are able to affect the
 mid-plane temperature due to vertical transport of radiation. In
@@
 power law and does not change significantly as a result of including
-radiative transfer, except within the central
-region. Figures~\ref{fig:scale_height} and \ref{fig:mid_tem} show that
-the disc is hotter close to the mid-plane, except within a region
-between 10--20 AU of the centre, but has a smaller scale
-height. Figure~\ref{fig:log_u} shows that the vertical temperature
-gradient in the disc is such that temperature increases with height
-out of the mid-plane. Although the disc is hotter when radiative
-transfer is included the vertical temperature gradient tends to reduce
-the pressure gradient which is required for hydrostatic support
-resulting in a smaller scale height.
+radiative transfer. Figures~\ref{fig:scale_height} and
+\ref{fig:mid_tem} show that the disc is hotter close to the mid-plane,
+except within a region between 10--20 AU of the centre, but has a
+smaller scale height. Figure~\ref{fig:log_u} shows that the vertical
+temperature gradient in the disc is such that temperature increases
+with height out of the mid-plane. Although the disc is hotter when
+radiative transfer is included the vertical temperature gradient tends
+to reduce the pressure gradient which is required for hydrostatic
+support resulting in a smaller scale height.
 

### 2009-09-28 SPH-Torus-paper1/sphtorus_benchmark.tex
Added a paragraph on timing and RT overhead.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2033 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
+Monte-Carlo radiative transfer calculations can be computationally
+demanding so the calculation was parallelised using MPI (Message
+Passing Interface) libraries. Parallelising code in this way allows
+for parallel computation in both the radiation and hydrodynamics steps
+and can be applied to a shared memory or a distributed memory computer
+architecture. Evolving the disc using both the radiation and
+hydrodynamics codes took a total wall time of 560 hours using 128 MPI
+processes, of which 440 hours was spent in radiation calculations. The
+radiation calculations take approximately 4~times as long as the
+hydrodynamics calculations so the combined code is significantly
+slower than the SPH code alone. However the calculation is still
+feasible and we expect the combined code to be used in applications
+where the increased accuracy of the Monte-Carlo radiation calculation,
+over faster alternatives, is of importance.
+
 \subsection{Results}

### 2009-09-29 torus/amr_mod.f90
fixed a weird bug in phaseloop - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2035 25464f21-6099-402c-b30a-640f1d40d38b

@@ -15932,8 +15932,8 @@ end function readparameterfrom2dmap
     tau = 0.d0
     currentPosition = rVec
     if (PRESENT(nTau)) then
-       xArray = 0.d0
-       tauArray = 0.d0
+       xArray(1) = 0.d0
+       tauArray(1) = 0.d0
        ntau = 1
     endif
 

### 2009-09-29 torus/phaseloop_mod.F90

@@ -698,41 +698,6 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
         weightDust = chanceDust / probDust
         weightPhoto = (1. - chanceDust) / (1. - probDust)
 
-!        if (writeoutput) write(*,*) "WeightDust",weightDust
-!        if (writeoutput) write(*,*) "WeightPhoto",weightPhoto
-!        if (writeoutput) write(*,*) "core + envelope luminosity",lCore+totEnvelopeEmission*1.d30
-        energyPerPhoton =  ((lCore + totEnvelopeEmission*1.d30) / dble(nPhotons))/1.d20
-!        if (writeoutput) write(*,*) "Energy per photon: ", energyPerPhoton
-
-     endif
-
-     
-
-
-
-     if (geometry == "hourglass") then
-        call computeProbDist(grid, totLineEmission, &
-             totWindContinuumEmission,lamline, .false.)
-        weightLinePhoton = 1.
-        weightContPhoton = 0.
-        probLinePhoton = 1.
-        probContPhoton = 0.
-     endif
-
-     if (doRaman) then
-        call computeProbDist(grid, totLineEmission, &
-             totWindContinuumEmission,lamline, .false.)
-        if (writeoutput) write(*,*) "Total Raman Line Emission: ",totLineEmission
-        weightLinePhoton = 1.
-        weightContPhoton = 0.
-        probLinePhoton = 1.
-        probContPhoton = 0.
-     endif
-
-
-
-     if (grid%lineEmission) then
-
         ! integrate the line and continuum emission and read the 
         ! intrinsic profile
 
@@ -769,71 +734,7 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
 
         if (grid%resonanceLine) totWindContinuumEmission = 0.
 
-              if (j < nTau) then
-                 t = 0.
-                 if ((tauExt(j+1) - tauExt(j)) /= 0.) then
-                    t = (thisTau - tauExt(j)) / (tauExt(j+1) - tauExt(j))
-                 endif
-                 dlambda = lambda(j) + (lambda(j+1)-lambda(j))*t
-              else
-                 dlambda = lambda(nTau)
-              endif
 
-
-
-                    
-              ! New photon position 
-              thisPhoton%position = thisPhoton%position + real(dlambda,kind=oct)*thisPhoton%direction
[…]

### 2009-09-29 SPH-Torus-paper1/sphtorus_benchmark.tex
Add section on transient oscillations.
Spell checked.


git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2037 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \usepackage{subfigure}
+
+\def\aap{{ A\&A}}
+\def\AaA{{ A\&A}}
+\def\aaps{{ A\&AS}}
+\def\AJ{{AJ}}
+\def\aj{{AJ}}
+\def\ApJ{{ApJ}}
+\def\apj{{ApJ}}
+\def\apjl{{ApJL}}
+\def\ApJL{{ApJL}}
+\def\ApJSupp{{ApJS}}
+\def\MN{{MNRAS}}
+\def\mnras{{MNRAS}}
+\def\pasj{{PASJ}}
+\def\nat{Nature}
+\def\ARAA{{ARA\&A}}
+\def\Obs{{ Observatory}}
+\def\PTRS{{Phil. Trans. Roy. Soc.}}
+\def\azh{{Astronomicheskii Zhurnal}}
+\def\apjs{{ApJS}}
+\def\araa{{ARA\&A}}
+\def\apss{{Ap\&SS}}
 
@@
   disc adjusts towards equilibrium vertical motions in the disc are
-  induced resulting in scale height enhancements which intecept
+  induced resulting in scale height enhancements which intercept
   radiation from the central star. Vertical transport of radiation
@@
   of the disc. The vertical motions decay over time and the disc
-  ultimately reaches a state of simulatanous hydrostatic and radiative
+  ultimately reaches a state of simultaneous hydrostatic and radiative
   equilibrium.
@@
 grid. The procedure used for this transformation is tested using a
-cicumstellar disc benchmark (see
+circumstellar disc benchmark (see
 Sections~\ref{section:description_of_benchmark}
@@
 (e.g. \cite{price_2008b} and references therein) so we do not attempt
-to benchmark the SPH component of the code here. Radiative transfer in
-a circumstellar disc has been studied in detail by
-\cite{pascucci_2004} and this benchmark is regularly used to test the
-accuracy of the {\small{TORUS}} code. Consequently we can be confident
-in the accuracy of the SPH and raditive transfer codes individually so
-we focus here on the accuracy of the mechansim by which they are
+to benchmark the SPH component of the code here. Likewise the  {\small{TORUS}}
+radiative transfer code has also been benchmarked elsewhere
+\citep{pinte_2009}. Consequently we can be confident
+in the accuracy of the SPH and radiative transfer codes individually so
+we focus here on the accuracy of the mechanism by which they are
 coupled. Hence the benchmark case presented here is a ``static''
@@
 effective transformation from the Lagrangian particle description to
-the Eulerian grid desciption.  The representation on grid should
+the Eulerian grid description.  The representation on grid should
 preserve important properties of the SPH model (e.g. total mass) but
@@
 by the sum of the weights, in order to avoid numerical effects at the
-free surface, as described by \cite{price_2007}.
-
-%The method used to
-%construct an AMR grid from SPH particles is described in more detail
-%in \cite{rundle_2009}.
+free surface, as described by \cite{price_2007}. For more details of
+the algorithm used to generate the AMR grid from SPH particles see
+\cite{rundle_2009}.
 
@@
   \caption{Number of octals (solid line) and percentage mass error
-    (dashed line) for cartesian AMR grids generated using different grid
+    (dashed line) for Cartesian AMR grids generated using different grid
     splitting methods and different numbers of particles. }
@@
 %
-Consider a cartesian grid with cubic volume elements and let
+Consider a Cartesian grid with cubic volume elements and let
 \begin{equation}
@@
 \end{equation}
-where $dM_{\rm{cart}}$ is the mass of a cell in the cartesian grid and
+where $dM_{\rm{cart}}$ is the mass of a cell in the Cartesian grid and
 $\rho_{\rm{cell}}$ is the density of the cell. 
@@
 If we require the resolution in cylindrical polar $r$ and $z$
-to match the resolution in cartesian $x$, $y$ and $z$ then $dl_{\rm{cyl}} =
+to match the resolution in Cartesian $x$, $y$ and $z$ then $dl_{\rm{cyl}} =
 dl_{\rm{cart}}$. From eqn~\ref{eqn:cart_cell} and \ref{eqn:cyl_cell} 
@@
 which describes the required conversion from a mass per cell limit
-suitable for a cartesian grid ($dM_{\rm{cart}}$) to an equivalent mass
+suitable for a Cartesian grid ($dM_{\rm{cart}}$) to an equivalent mass
 per cell limit suitable for a cylindrical polar grid ($dM_{\rm{cyl}}$).
@@
 mass is well represented with significantly fewer cells than in a
-cartesian grid. The density contrast condition alone does not
+Cartesian grid. The density contrast condition alone does not
 represent the total mass to within 3\% accuracy even with
@@
 
-Having investigated the procdure for setting up the radiative transfer
+Having investigated the procedure for setting up the radiative transfer
 grid we now proceed to studying the accuracy of the results from the
@@
 The disc was initially modelled using $10^5$ SPH particles with an AMR
-grid contructed from a mass per cell limit of $5\times10^{26}$g.  The
+grid constructed from a mass per cell limit of $5\times10^{26}$g.  The
 mass per cell limit was chosen in preference to the density contrast
@@
 equilibrium is short compared to the dynamical time scale of the disc
-(i.e. the ``prompt escape'' regime decribed by \cite{nayakshin_2009}).
+(i.e. the ``prompt escape'' regime described by \cite{nayakshin_2009}).
 A radiative transfer calculation is performed after every four
-hydrodynamics time steps (equivalent to every 2.4 years). The freqency
+hydrodynamics time steps (equivalent to every 2.4 years). The frequency
 with which the radiative transfer is calculated is determined by the
@@
 A cylindrical polar grid, with adaptive $r$ and $z$ cells and 16
-azimuthal cells, was used for the raditive transfer step. The AMR grid
+azimuthal cells, was used for the radiative transfer step. The AMR grid
 was constructed using a maximum mass per cell of
@@
 when there is a vertically isothermal equation of state. The second
-frame (Fig.~\ref{fig:frame2} is shortly after the raditive transfer
+frame (Fig.~\ref{fig:frame2} is shortly after the radiative transfer
 has been switched on. The inner disc has collapsed and there is
@@
 height enhancements and in each case there is cooling behind the
-enhancement as the scale height fluctations are able to affect the
+enhancement as the scale height fluctuations are able to affect the
 mid-plane temperature due to vertical transport of radiation. In
@@
   \subfigure[]{\includegraphics[scale=0.3]{figures/u_run2_DSC1024}\label{fig:frame6}}
-  \caption{Particle plots showing internal energy in cyclindrical
+  \caption{Particle plots showing internal energy in cylindrical
     polar co-ordinates. Axis units are cm.}
@@
 \end{figure*}
+
+Transient oscillations, as the disc adjusts towards equilibrium, are
+observed whether radiative transfer is included or not. They are
+vertical motions which decay more rapidly at smaller radii and hence
+give the appearance of propagating outwards, even though the motion is
+vertical. Other disc models using radiation hydrodynamics have found
+oscillatory solutions with inwards propagating waves
+(e.g. \cite{min_2009}) which are fundamentally different to the
+transient effects seen in this case. However it should be noted that
+\cite{min_2009} only found an oscillatory solution in their most
+optically thick disc, which is significantly more massive than our
+model disc, and may represent a different regime to that considered
+here.
 
@@
 demanding than accurately representing the temperature structure
-within the disc and temperature errors can be reduced to a managable
+within the disc and temperature errors can be reduced to a manageable
 level with a realistic number of SPH particles in the disc.
@@
 \citep{min_2009}. One consequence of these fluctuations is that they
-can intecept radiation from the central star which can then be
+can intercept radiation from the central star which can then be
 vertically transported into the mid-plane of the disc hence even

### 2009-09-29 torus/amr_mod.f90
fixed bug that fixed bug that broke overnight test - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2038 25464f21-6099-402c-b30a-640f1d40d38b

@@ -15910,9 +15910,8 @@ end function readparameterfrom2dmap
 
   subroutine tauAlongPathFast(ilambda, grid, rVec, direction, tau, tauMax, ross, startOctal, startSubcell, nTau, &
        xArray, tauArray, distanceToEdge)
-    use input_variables, only : rGap
     type(GRIDTYPE) :: grid
-    type(VECTOR) :: rVec, direction, currentPosition, beforeVec, afterVec
+    type(VECTOR) :: rVec, direction, currentPosition
     real, optional,intent(out) :: xArray(:), tauArray(:)
     integer, optional, intent(out) :: nTau
     integer :: iLambda
@@ -15927,7 +15926,6 @@ end function readparameterfrom2dmap
     real(double) :: kappaSca, kappaAbs, kappaExt
     integer :: subcell
     logical, optional :: ross
-    logical :: planetGap
     kappaAbs = 0.d0; kappaSca = 0.d0
     tau = 0.d0
     currentPosition = rVec

### 2009-10-01 torus/timedep_mod.F90
fixes to timedep prompted by overnight fail - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2041 25464f21-6099-402c-b30a-640f1d40d38b

@@ -361,20 +361,19 @@ contains
     real(double) :: fac
     real(double) :: totalLineEmission, totalContEmission, t1, t2, t3, t4, t5, t6, checkLum, t7
     real(double) :: checkLumSource
-    real(double) :: distanceToEdge, photonTagTime
+    real(double) :: photonTagTime
     real(double) :: firstObserverTime, timeToObserver, lastObserverTime
-    real(double) :: tempDouble
-    real(double), allocatable :: tempDoubleArray(:)
     real :: lambda0
     logical :: useFileForStack
     logical :: beenScattered
     logical :: radiativeEquPhoton, seedRun
     integer :: nEscaped
     integer :: nFromMatterThisThread
-    real(double) :: inc
 #ifdef MPI
     include 'mpif.h'
     integer :: ierr
+    real(double) :: tempDouble
+    real(double), allocatable :: tempDoubleArray(:)
 #endif
     firstObserverTime = sedTime(1)
     lastObserverTime = sedTime(nTime)
@@ -823,7 +822,7 @@ contains
     type(VECTOR) :: rVec
     type(octal), pointer   :: thisOctal
     type(octal), pointer  :: child 
-    real(double) :: deltaT, equilibriumTime, Teq, deltaUdens, newUDens
+    real(double) :: deltaT, equilibriumTime,deltaUdens, newUDens
     real(double) :: fac, oldUdens, t
     real :: kappaP
     integer :: subcell, i
@@ -1018,9 +1017,7 @@ contains
     type(VECTOR) :: rVec
     real(double),intent(inout) :: deltaT, temp, udens, adot, eta, rho, equilibriumTime, chiline
     integer :: subcell, i
-    real :: kappap
-    real(double) :: currentTemp, newTemp, newUdens, deltaUdens, t, fac, oldUdens
-    real(double) ::  teq
+    real(double) :: t
 
     do subcell = 1, thisOctal%maxChildren
        if (thisOctal%hasChild(subcell)) then

### 2009-10-01 SPH-Torus-paper1/sphtorus_benchmark.tex
introduction changed and new refs included - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2042 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-The interaction between matter and radiation is of great importance in
-a range of astrophysical processes. A major challenge in star
-formation simulations is to incorporate self-consistent radiative
-feedback from protostars. Once this is achieved it is possible to
-relax the simplifying assumptions relating to the equation of state
-and to study the effects of radiative feedback, for example the impact
-on disc fragmentation. A flux limited diffusion approximation can be
-used to represent radiative transport in regions of high optical
-depth, however this method is not suited to modelling regions of low
-optical depth where an alternative method, such as a Monte-Carlo
-method, must be used.
+Hydrodynamics calculations are used to investigate a variety of problems associated with star formation, such as the collapse of protostellar cores (e.g.
+\citealt{goodwin_2004}), the fragmentation of protostellar discs (e.g.
+\citealt{boss_1997}), and on the largest scale the gravo-turbulent collapse of a molecular cloud to form stars (e.g.
+\citealt{bate_2003, bate_2005}).
 
-This paper presents a results from coupling the {\small{TORUS}}
-radiative transfer code \citep{harries_2000} with the SPH (Smoothed
-Particle Hydrodynamics) code of \cite{bate_2009}.  {\small{TORUS}}
+Sophisticated as such calculations appear, the underlying physics regarding the thermal properties of the gas is much simplified.
+One of the usual approximations is the use of an equation of state (eos) in determining the pressure of the gas.
+An isothermal eos is often a good approximation in the most rarified regions, where the material is able to radiate, and thus cool, freely.
+The gas may be compressed adiabatically in the highest density regions, and a barytropic eos is sometimes adopted, with the polytropic exponent switching at a critical density in an attempt to reproduce the results of one-dimensional collapse calculations that incorporate radiative-transfer \citep{masunaga_1998}.
+The crucial point here is that the energy dumped into the cluster from accretion onto, and gravitation contraction of, the newly formed stars is neglected, and the radiation emitted by compressed gas (the `$P\,dV$' terms) is assumed to  escape without further interaction.
+
+The solution is to include radiation-transfer self-consistently  and perform a radiation-hydrodynamics (RHD) calculation.
+The simplest way to do this is to assume that the energy is transported by radiative diffusion of photons.
+The diffusion approximation is a good one at high optical depth, but breaks down in optically thin regions since the diffusion speed may exceed the speed of light as the mean-free-path tends to infinity; an essentially arbitrary flux limiter is adopted in this regime.
+Furthermore the approximation is often implemented as a grey method, typically using Rosseland mean  opacities tabulated as a function of temperature.
+Finally the diffusion approximation cannot treat the effects of shadowing, as radiation field may diffuse around optically thick obstacles.
+The crucial advantage of the diffusion approximation though is of course speed: the radiation transport step is straightforward to implement and is not hugely dominant in the RHD calculation.
+The first cluster collapse and disc fragmentation calculations using flux-limited diffusion have just started appearing in the literature \citep{boss_2008, bate_2009b, offner_2009, stamatellos_2009}.
+The fundamental result of including a more complete thermal treatment is broadly in line with prior expectations i.e.
+the heating of the gas inhibits the fragmentation process.
+
+Meanwhile dedicated radiation transfer (RT) codes  have progressed far beyond the diffusion approximation and now take into account a wide array of microphysical processes such as polychromatic radiation transfer incorporating polarization state, multiple scattering, Mie phase matrices etc.
+These sophisticated RT codes have been employed to model cores (e.g.
+\citealt{stamatellos_2005}), discs (reviewed by \citealt{dullemond_2007}) and even entire clusters \citep{kurosawa_2004}.
+The principle barrier to using these codes in RHD is that of  of computation time, but the increase in CPU power and the  adoption of parallelization mean that it is now feasible to conduct a full treatment of RT along with the hydrodynamics, thereby dropping the diffusion approximation.
+
+This paper presents a method of coupling the {\sc torus}
+radiative transfer code \citep{harries_2000} with the smoothed
+particle hydrodynamics (SPH) code of \cite{bate_2009}.  {\sc torus}
 performs radiative transfer calculations using the Monte-Carlo method
@@
 
-There is not a unique approach to coupling an SPH code to a radiative
-transfer code and a number of different approaches have been developed
-(\cite{pawlik_2008} and references therein). This paper focuses on
-radiative transfer calculations using an adaptive grid in the context
-of modelling a circumstellar disc.
-
 Accurately coupling the radiative transfer component to the SPH
@@
 Sections~\ref{section:description_of_benchmark}
-and~\ref{section:grid_generation}). The spectral energy distribution
-and temperature distribution of the benchmark disc are examined in
-Section~\ref{section:seds} in order to understand how well the
+and~\ref{section:grid_generation}). The temperature distribution and spectral energy distribution
+ of the benchmark disc are examined in
+Section~\ref{section:seds} in order to investigate how well the
 radiative transfer calculation works with the gridded density field
@@
 (e.g. \cite{price_2008b} and references therein) so we do not attempt
-to benchmark the SPH component of the code here. Likewise the  {\small{TORUS}}
+to benchmark the SPH component of the code here. Likewise the  {\sc torus}
 radiative transfer code has also been benchmarked elsewhere
@@
 we focus here on the accuracy of the mechanism by which they are
-coupled. Hence the benchmark case presented here is a ``static''
+coupled. Hence the benchmark case presented here is a `static'
 benchmark in which we represent an analytical density distribution
@@
 
-When constructing validation tests of a numerical method it is often
-valuable to use a simplified test case with well known results. We
-base our SPH disc benchmark on the axisymmetric circumstellar disc of
+We base our SPH disc benchmark on the axisymmetric circumstellar disc of
 \cite{pascucci_2004}.  Representing a structure with rotational
@@
 
-{\small{TORUS}} uses an adaptive grid based on the octree method. In a 3D
+{\sc torus} uses an adaptive grid based on the octree method. In a 3D
 geometry the initial grid comprises 8 cells (one octal) with 2 cells
@@
 from the case with $10^5$ particles and a mass limit of
-$10^{26}$~g. In this case the mass per cell limit is smaller than the
+$10^{26}$\,g. In this case the mass per cell limit is smaller than the
 SPH particle mass and the grid is over sampling the SPH resolution. In
 the other cases the mass per cell limit is greater than the SPH
-particle mass. For mass per cell limits of $10^{28}$g and less the
+particle mass. For mass per cell limits of $10^{28}$\,g and less the
 total mass error varies only slowly as a function of mass per cell and
@@
 disc, which we expect to be most important for determining the
-SED. SEDs were calculated using the {\small{TORUS}} code for viewing
+SED. SEDs were calculated using the {\sc torus} code for viewing
 angles of 12.5 and 77.5 degrees (where an inclination angle of zero
@@
     degrees (right). The benchmark SED is plotted as a solid line and
-    the {\small{TORUS}} SED is plotted as a dashed line.}
+    the {\sc torus} SED is plotted as a dashed line.}
   \label{fig:seds}
@@
     degrees and 77.5 degrees. The benchmark SED is plotted as a solid
-    line. The {\small{TORUS}} density distribution is forced to the correct
+    line. The {\sc torus} density distribution is forced to the correct
     value with a radius of $1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm
@@
 temperature distribution for different numbers of
-particles. {\small{TORUS}} calculates the temperature distribution
+particles. {\sc torus} calculates the temperature distribution
 using a high resolution 2D geometry, in order to determine the correct

### 2009-10-02 SPH-Torus-paper1/sphtorus_benchmark.tex
changes from meeting - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2043 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-Hydrodynamics calculations are used to investigate a variety of problems associated with star formation, such as the collapse of protostellar cores (e.g.
+Hydrodynamics calculations are used in investigations of  a variety of problems associated with star formation, such as the collapse of protostellar cores (e.g.
 \citealt{goodwin_2004}), the fragmentation of protostellar discs (e.g.
@@
 The gas may be compressed adiabatically in the highest density regions, and a barytropic eos is sometimes adopted, with the polytropic exponent switching at a critical density in an attempt to reproduce the results of one-dimensional collapse calculations that incorporate radiative-transfer \citep{masunaga_1998}.
-The crucial point here is that the energy dumped into the cluster from accretion onto, and gravitation contraction of, the newly formed stars is neglected, and the radiation emitted by compressed gas (the `$P\,dV$' terms) is assumed to  escape without further interaction.
+The crucial point here is that the energy dumped into the cluster from accretion onto, and gravitation contraction of, the newly formed stars is neglected, and the radiation emitted by compressed gas (the `$P\,dV$' term) is assumed to  escape without further interaction.
 
@@
 
-Meanwhile dedicated radiation transfer (RT) codes  have progressed far beyond the diffusion approximation and now take into account a wide array of microphysical processes such as polychromatic radiation transfer incorporating polarization state, multiple scattering, Mie phase matrices etc.
+Meanwhile dedicated radiation transfer (RT) codes  have progressed far beyond the diffusion approximation and now take into account a wide array of processes such as polychromatic radiation transfer incorporating the radiation's polarization state, multiple scattering, Mie phase matrices etc.
 These sophisticated RT codes have been employed to model cores (e.g.
@@
 radiative transfer calculation works with the gridded density field
-and to understand the effects of grid and SPH spatial resolution. A
-simulation of a circumstellar disc around a T Tauri star is presented
-in Section~\ref{section:sph_disc}.
+and to understand the effects of grid and SPH spatial resolution. Finally the hybrid code is 
+tested under realistic conditions via a simulation of a circumstellar disc around a 
+T Tauri star (Section~\ref{section:sph_disc}).
 
@@
 \citep{pinte_2009}. Consequently we can be confident
-in the accuracy of the SPH and radiative transfer codes individually so
-we focus here on the accuracy of the mechanism by which they are
-coupled. Hence the benchmark case presented here is a `static'
+in the accuracy of the SPH and radiative transfer codes individually and we instead
+ focus on the accuracy of the mechanism by which they are
+coupled. The benchmark case presented here is therefore a `static'
 benchmark in which we represent an analytical density distribution
@@
 exercising the 3D capabilities of our own system.
+The geometry is a stringent test of the gridding method, since it contains a large range in linear scales that need to be resolved, and sharp density gradients (in particular the disc inner edge).
 
@@
 quantity and are a stringent test of the accuracy of the radiative
-transfer calculation.
+transfer calculation. The key problem here is that the resolution necessary for adequately
+describing the fluid flow is not necessarily the same as required for accurately 
+modelling the radiation field.
 
 The disc was initially modelled using $10^5$ SPH particles with an AMR
-grid constructed from a mass per cell limit of $5\times10^{26}$g.  The
-mass per cell limit was chosen in preference to the density contrast
+grid constructed from a mass per cell limit of $5\times10^{26}$g.  
+This number of SPH particles would normally be considered as sufficient to adequately represent a disc of this mass in a purely hydrodynamical calculation.
+The mass per cell limit was chosen in preference to the density contrast
 limit to give the highest resolution near the central region of the
 disc, which we expect to be most important for determining the
-SED. SEDs were calculated using the {\sc torus} code for viewing
+temperature of the disc at the inner edge and the SED.
+
+In figure xxx we plot the temperature distribution at radiative equilibrium for the benchmark disc. 
+{\sc torus} calculates the temperature distribution
+using a high resolution 2D geometry, in order to determine the correct
+temperature as a function of cylindrical polar $r$ and $z$
+co-ordinates. This is then compared to the temperature from the SPH
+disc for each SPH particle. Positive values of the fractional error
+indicate that the SPH disc is hotter than the expected value.
+The temperatures show deviations of $\pm$ 50\% (XXXX CHECK) from the benchmark values, a deviation that is purely driven by the resolution of the density field derived from the SPH particles, since a `{\sc torus} only' calculation, where the AMR grid is refined on optical depth criteria and the cell densities are found from the analytical description of the density structure (equation xxxx), matches the benchmark temperatures to within 2\%.
+The systematic differences in the temperature distribution are due to an increased vertical transport of radiation from the surface layers of the disc to the mid-plane due to a lack of spatial resolution, leading to errors in the calculation of the specific intensities (particularly in the inner disc region).
+These systematic differences are more readily apparent in the emergent SEDs, which are a more sensitive probe of the accuracy of the RT calculation than  the temperature distribution.
+
+SEDs were calculated using the {\sc torus} code for viewing
 angles of 12.5 and 77.5 degrees (where an inclination angle of zero
@@
 angle of 77.5 degrees there is also a significant reduction in flux
-below 1~$\mu\rm{m}$. The density distribution in the central region of
+below 1~$\mu\rm{m}$. Both these discrepancies are attributable to a lack of resolution within a few au of the central object. The density distribution in the central region of
 this disc is plotted in Fig.~\ref{fig:basic_dens} which shows that the
-central 1AU gap is not represented. There are two effects in
+central 1\,au gap is not represented. There are two effects in
 operation; firstly the grid resolution in this region is larger than
-1AU and secondly the smoothing lengths of the particles are larger
-than 1AU. In order to correctly represent the central gap there needs
+1\,au  and secondly the smoothing lengths of the particles are larger
+than 1\,au. In order to correctly represent the central gap there needs
 to be higher grid resolution around the central source and more SPH
@@
 generated in other regions of the disc. In order to achieve a grid
-resolution of less than 1AU around the source it was necessary to
+resolution of less than 1\,au around the source it was necessary to
 specify additional criteria for refining the grid. Three cubes of
@@
 \end{figure*}
+The effective resolution of the AMR mesh is dependent on two factors; the probability of having sufficient particles to adequately sample the small volume of the disc inner-edge, and the particle smoothing length (which determines the effective spatial resolution of the SPH density representation).
 With $10^5$ and $10^6$ particles a central gap is present but is too
 large. With $10^7$ particles there is more material close in to the
-source but the gap itself is not represented and the source is
+source but the gap itself is not represented (because the smoothing length of the particles near the disc inner-edge is too large) and the source is
 obscured. Only with $10^8$ particles is a gap of approximately the
-correct size present.  The representation of the central 1~AU gap is
+correct size present.  The representation of the central 1\,au gap is
 significantly affected by the number of particles used to represent
@@
 temperature distribution for different numbers of
-particles. {\sc torus} calculates the temperature distribution
-using a high resolution 2D geometry, in order to determine the correct
-temperature as a function of cylindrical polar $r$ and $z$
-co-ordinates. This is then compared to the temperature from the SPH
-disc for each SPH particle. Positive values of the fractional error
-indicate that the SPH disc is hotter than the expected value.
+particles. 
 \begin{figure*}
@@
   \caption{Fractional temperature error for discs represented by
-    different numbers of SPH particles. Axis units are AU.} 
+    different numbers of SPH particles. Axis units are au.} 
   \label{fig:n_part_tem_diff}
@@
 the mid plane. The effect is reduced as the number of particles is
-increased and reaches a very low level with $10^8$ particles.
+increased and reaches a very low level with $10^8$ particles, at which stage the
+temperature distribution agrees with the benchmark to within $\sim$10\%.
 
@@
 of 77.5 degrees. At the shortest wavelengths the 12.5 degrees
-inclination angle SED is dominated by emission from the central
+inclination angle SED is dominated by the photosphere of the central
 star. This region of the SED is well represented with $10^5$ and
-$10^8$ particles but is less well represented with $10^6$ or $10^7$
+$10^8$ particles but is of course less well represented with $10^6$ or $10^7$
 particles where the central star is obscured. At the longest
@@
 modelled provided the total disc mass is accurately represented. In
-all four cases the total disc mass is well represented and the long
+all four cases the total disc mass is well represented (XXX cite section) and the long
 wavelength SED matches the benchmark results. At intermediate
@@
 representation and it is clear that accurately modelling the SED from
-this disc is challenging, even with $10^8$ particles. 
+this disc is challenging, even with $10^8$ particles. (XXXX need to discuss this in the conclusion).
 \begin{figure*}
@@
 \label{section:sph_disc}
+
+The above analysis indicates that the hybrid code is capable of successfully passing the density distribution from the hydrodynamics step to the radiative-transfer code, and that accurate temperatures assuming radiative equilibrium can be passed back to the SPH code in order to update the gas pressure and perform the next hydrodynamical step.
+In order to test the feasibility of performing a radiation-hydrodynamics calculation using the hybrid code we adopt a `realistic' test problem, that of a circumstellar disc around a classical T Tauri star.
+The mid-plane optical depths here are higher than that of the Pascucci benchmark, providing a more demanding challenge both in terms of computation time and required numerical accuracy.
 
@@
 (i.e. the ``prompt escape'' regime described by \cite{nayakshin_2009}).
-A radiative transfer calculation is performed after every four
-hydrodynamics time steps (equivalent to every 2.4 years). The frequency
-with which the radiative transfer is calculated is determined by the
+
+The frequency with which the radiative transfer is calculated is determined by the
 sound crossing time in the inner regions of the disc as this is the
 time scale over which the scale height in this region will vary and
-effect the transfer of radiation into the outer parts of the disc.
+effect the transfer of radiation into the outer parts of the disc. (XXX put numbers
+here to justify the 1 every 4). A radiative transfer calculation is performed after every four
+hydrodynamics time steps (equivalent to every 2.4 years).
 
-A cylindrical polar grid, with adaptive $r$ and $z$ cells and 16
-azimuthal cells, was used for the radiative transfer step. The AMR grid
+A cylindrical polar grid, with adaptive $r$ and $z$ cells was used for the radiative transfer step. 
+The cells were split in the azimuthal direction to give a cell spacing of 22.5 degrees.
+This azimuthal splitting allows for the existence of non-axisymmetric instabilities (such as radiatively driven warps) which may occur due to either physical or numerical effects, while ensuring the calculation remains tractable.
+The AMR grid
 was constructed using a maximum mass per cell of
@@
 slower than the SPH code alone. However the calculation is still
-feasible and we expect the combined code to be used in applications
+feasible and we expect the combined code only to be used in applications
 where the increased accuracy of the Monte-Carlo radiation calculation,
-over faster alternatives, is of importance.
+over faster alternatives such as flux-limited diffusion, is of importance.
 
@@
 model disc, and may represent a different regime to that considered
-here.
+here. We note that the disc retains its azimuthal symmetry throughout 
+(XXXX Check!) the simulation and we find no evidence for warping instabilities.
 
@@
 \ref{fig:mid_tem} show that the disc is hotter close to the mid-plane,
-except within a region between 10--20 AU of the centre, but has a
+except within a region between 10--20 au of the centre, but has a
 smaller scale height. Figure~\ref{fig:log_u} shows that the vertical
@@
 to reduce the pressure gradient which is required for hydrostatic
-support resulting in a smaller scale height.
+support resulting in a smaller scale height. Note the slight drop in scale height
+just outwards from the disc inner edge; indicative of a puffed-up inner edge
+\citep{dullemond_2001}.
 
@@
 
-We have presented results from a combined SPH and AMR grid-based
+We have presented results from a hybrid SPH and AMR grid-based
 radiative transfer code, which has been used to model a non-self

### 2009-10-02 torus/amr_mod.f90
fix for gfortran - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2044 25464f21-6099-402c-b30a-640f1d40d38b

@@ -16141,8 +16141,8 @@ end function readparameterfrom2dmap
   end subroutine getMagStreamValues3
 
   type(VECTOR)  function magStreamVelocity(point, grid) result(vel)
-    type(GRIDTYPE) :: grid
-    type(VECTOR) :: point
+    type(GRIDTYPE), intent(in) :: grid
+    type(VECTOR),intent(in) :: point
     real(double) :: minDist, dist, dist1, dist2, t
     integer :: i, j, isample, istream
     minDist = 1.d30
@@ -17706,7 +17706,7 @@ end function readparameterfrom2dmap
            
   real(double) function molebenchDensity(position,grid) result(rho)
 
-    type(VECTOR) :: position
+    type(VECTOR),intent(in) :: position
     TYPE(gridtype), INTENT(IN) :: grid
     logical, save :: firsttime = .true.
     integer, parameter :: nr = 50

### 2009-10-02 torus/photoion_mod.F90

@@ -4462,12 +4462,12 @@ end subroutine readHeIIrecombination
    end subroutine addToEmission
 
   subroutine identifyTransition(grid, lambda, iIon, iTransition, ok)
-    type(GRIDTYPE) :: grid
-    real(double) :: lambda
+    type(GRIDTYPE),intent(in) :: grid
+    real(double),intent(in) :: lambda
     integer, intent(out) :: iIon, iTransition
+    logical, intent(out) :: ok
     integer :: i, j
     character(len=80) :: message
-    logical, intent(out) :: ok
 
     ok = .false.
 

### 2009-10-09 SPH-Torus-paper1/sphtorus_benchmark.tex
Updates following meeting of DA and TH.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2047 25464f21-6099-402c-b30a-640f1d40d38b

@@
 grid constructed from a mass per cell limit of $5\times10^{26}$g.
-This number of SPH particles would normally be considered as sufficient to adequately represent a disc of this mass in a purely hydrodynamical calculation.
-The mass per cell limit was chosen in preference to the density contrast
-limit to give the highest resolution near the central region of the
-disc, which we expect to be most important for determining the
-temperature of the disc at the inner edge and the SED.
+This number of SPH particles would normally be considered as
+sufficient to adequately represent a disc of this mass in a purely
+hydrodynamical calculation. The mass per cell limit was chosen in
+preference to the density contrast limit to give the highest
+resolution near the central region of the disc, which we expect to be
+most important for determining the temperature of the disc at the
+inner edge and the SED.
 
-In figure xxx we plot the temperature distribution at radiative equilibrium for the benchmark disc. 
-{\sc torus} calculates the temperature distribution
-using a high resolution 2D geometry, in order to determine the correct
+In Fig.~\ref{fig:nomod_tem_diff} we plot the fractional error in the
+temperature distribution at radiative equilibrium for the benchmark
+disc.  {\sc torus} calculates the temperature distribution using a
+high resolution 2D geometry, in order to determine the correct
 temperature as a function of cylindrical polar $r$ and $z$
@@
 disc for each SPH particle. Positive values of the fractional error
-indicate that the SPH disc is hotter than the expected value.
-The temperatures show deviations of $\pm$ 50\% (XXXX CHECK) from the benchmark values, a deviation that is purely driven by the resolution of the density field derived from the SPH particles, since a `{\sc torus} only' calculation, where the AMR grid is refined on optical depth criteria and the cell densities are found from the analytical description of the density structure (equation xxxx), matches the benchmark temperatures to within 2\%.
-The systematic differences in the temperature distribution are due to an increased vertical transport of radiation from the surface layers of the disc to the mid-plane due to a lack of spatial resolution, leading to errors in the calculation of the specific intensities (particularly in the inner disc region).
-These systematic differences are more readily apparent in the emergent SEDs, which are a more sensitive probe of the accuracy of the RT calculation than  the temperature distribution.
+indicate that the SPH disc is hotter than the expected value. The
+temperatures show deviations of $-30$\% to $+50$\%  from the
+benchmark values, a deviation that is purely driven by the resolution
+of the density field derived from the SPH particles, since a `{\sc
+  torus} only' calculation, where the AMR grid is refined on optical
+depth criteria and the cell densities are found from the analytical
+description of the density structure (Eqn.~\ref{eqn:pascucci_density}), matches the
+benchmark temperatures to within 2\%. The systematic differences in
+the temperature distribution are due to an increased vertical
+transport of radiation from the surface layers of the disc to the
+mid-plane due to a lack of spatial resolution, leading to errors in
+the calculation of the specific intensities (particularly in the inner
+disc region).  These systematic differences are more readily apparent
+in the emergent SEDs, which are a more sensitive probe of the accuracy
+of the RT calculation than the temperature distribution.
+
+\begin{figure}
+  \includegraphics[scale=0.3]{figures/nomod_tem_diff}
+  \caption{Temperature difference between SPH benchmark disc and high
+    accuracy 2D result.}
+  \label{fig:nomod_tem_diff}
+\end{figure}
 
@@
 modelled provided the total disc mass is accurately represented. In
-all four cases the total disc mass is well represented (XXX cite section) and the long
+all four cases the total disc mass is well represented (see Section~\ref{section:grid_generation}) and the long
 wavelength SED matches the benchmark results. At intermediate
@@
 representation and it is clear that accurately modelling the SED from
-this disc is challenging, even with $10^8$ particles. (XXXX need to discuss this in the conclusion).
+this disc is challenging, even with $10^8$ particles.
 \begin{figure*}
@@
 
-The frequency with which the radiative transfer is calculated is determined by the
-sound crossing time in the inner regions of the disc as this is the
-time scale over which the scale height in this region will vary and
-effect the transfer of radiation into the outer parts of the disc. (XXX put numbers
-here to justify the 1 every 4). A radiative transfer calculation is performed after every four
-hydrodynamics time steps (equivalent to every 2.4 years).
+The frequency with which the radiative transfer is calculated is
+determined by the sound crossing time in the inner regions of the disc
+as this is the time scale over which the scale height in this region
+will vary and effect the transfer of radiation into the outer parts of
+the disc.  The vertical sound crossing time at a radius of
+10~au is typically 2 years, so a radiative transfer calculation is
+performed after every four hydrodynamics time steps (equivalent to
+every 2.4 years).
 
@@
 here. We note that the disc retains its azimuthal symmetry throughout 
-(XXXX Check!) the simulation and we find no evidence for warping instabilities.
+the simulation and we find no evidence for warping instabilities.
 
@@
 but is achievable with a large number of particles. Accurately
-modelling the SED using this method seems to be considerably more
+modelling the SED using this method is considerably more
 demanding than accurately representing the temperature structure
-within the disc and temperature errors can be reduced to a manageable
-level with a realistic number of SPH particles in the disc.
+within the disc. Temperature errors can be reduced to a manageable
+level using a realistic number of SPH particles, yielding a 
+temperature distribution suitable for use in a hydrodynamics
+calculation, however even with a disc composed of $10^8$ SPH particles
+the modelled SEDs show significant deviations from the benchmark results.
 

### 2009-10-09 SPH-Torus-paper1/sphtorus_benchmark.tex
Improved figure captions and formatting.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2048 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \title{Modelling circumstellar discs with 3D radiation hydrodynamics}
-\author[David M. Acreman et al]{David M. Acreman et al\\
+\author[David M. Acreman, Tim J. Harries and David A. Rundle]{David M. Acreman, Tim J. Harries and David A. Rundle\\
 School of Physics, University of Exeter, Stocker Road, Exeter EX4
@@
 \cite{pascucci_2004} which has a mid-plane optical depth of $\tau=100$
-at $\lambda=550~\rm{nm}$ and a mass of 0.011~$\rm{M}_{\sun}$. This
-requires $r_d=500~\rm{AU}$, $z_d=0.25 r_d$ and
-$\rho_{0}=8.1614\times10^{-18}~\rm{g~cm^{-3}}$, with the disc truncated at
-an outer radius of 1000~AU and an inner radius of 1~AU.
+at $\lambda=550\,\rm{nm}$ and a mass of 0.011\,$\rm{M}_{\sun}$. This
+requires $r_d=500\,\rm{au}$, $z_d=0.25 r_d$ and
+$\rho_{0}=8.1614\times10^{-18}\,\rm{g\,cm^{-3}}$, with the disc truncated at
+an outer radius of 1000\,au and an inner radius of 1\,au.
 
@@
 constructed from $10^7$ particles, using a mass per cell limit of
-$5\times10^{26}~\rm{g}$, is plotted in
+$5\times10^{26}\,\rm{g}$, is plotted in
 Fig.~\ref{fig:mass_condition_mesh}. This plot is a slice perpendicular
@@
   \subfigure[AMR grid with a mass per cell condition of
-    $5\times10^{26}~\rm{g}$.]
+    $5\times10^{26}\,\rm{g}$.]
     {\includegraphics[scale=0.22]{figures/set1_mesh}
@@
       \label{fig:density_condition_mesh}}
-  \caption{Example AMR grids for a mass per cell splitting condition (left)
-    and a density contrast splitting condition (right). In both cases
-    $10^7$ particles were used. The axis units are $10^{16}$~cm.}
+  \caption{Example AMR grids for a mass per cell splitting condition
+    of  $5\times10^{26}\,\rm{g}$ (left)
+    and a density contrast splitting condition of $f_{\rm{split}}=0.1$
+    (right) contructed
+    from $10^7$ SPH particles. The grids are
+    slices perpendicular to the disc mid-plane and the axis units are $10^{16}$\,cm.}
   \label{fig:example_meshes}
@@
 comparing the total mass on the AMR grid with the known mass of
-$0.011~\rm{M}_{\sun}$ based on the analytical form of the density
+$0.011\,\rm{M}_{\sun}$ based on the analytical form of the density
 distribution, and a positive value indicates that mass on the grid is
@@
   \subfigure[Density contrast condition and $10^7$ particles]{\includegraphics[scale=0.3]{figures/1e7_set2}}
-  \caption{Number of octals (solid line) and percentage mass error
-    (dashed line) for Cartesian AMR grids generated using different grid
-    splitting methods and different numbers of particles. }
+  \caption{Number of octals (solid line) and percentage error in total
+    disc mass (dashed line) for the benchmark disc represented on
+    Cartesian AMR grids generated using different grid splitting
+    methods (mass per cell limit or density contrast limit) and
+    different numbers of particles ($10^5$, $10^6$ or $10^7$). }
   \label{fig:grid_tests}
@@
 in regions of high density contrast which are likely to be important
-in radiative transfer calculations. However the density split
-condition has a less robust total mass representation than the mass
-per cell limit. By using a combination of these two conditions it is
-possible to add extra resolution in high contrast regions and still
-maintain an accurate total mass.
+in radiative transfer calculations. However this condition has a less
+robust total mass representation than the mass per cell limit. By
+using a combination of these two conditions it is possible to add
+extra resolution in high contrast regions and still maintain an
+accurate total mass.
 
@@
 co-ordinate system. A mass per cell splitting condition can still be
-used but it needs to be modified to take into account the increase in 
-cell volume as cylindrical polar radius increases, for fixed values of
-$dr$ and $dz$.  
+used but needs to be modified to take into account that for fixed
+values of $dr$ and $dz$ the cell volume increases as cylindrical polar
+radius increases.
 %
@@
   \subfigure[Density contrast condition and $10^7$ particles]{\includegraphics[scale=0.3]{figures/1e7_cyl_set2}}
-  \caption{Number of octals (solid line) and percentage mass error
-    (dashed line) for cylindrical polar AMR grids generated using different grid
-    splitting methods and different numbers of particles. }
+  \caption{Number of octals (solid line) and percentage error in total
+    disc mass (dashed line) for the benchmark disc represented on
+    cylindrical polar AMR grids generated using different grid splitting
+    methods (mass per cell limit or density contrast limit) and
+    different numbers of particles ($10^5$, $10^6$ or $10^7$).}
   \label{fig:cp_grid_tests}
@@
 The disc was initially modelled using $10^5$ SPH particles with an AMR
-grid constructed from a mass per cell limit of $5\times10^{26}$g.
+grid constructed from a mass per cell limit of $5\times10^{26}$\,g.
 This number of SPH particles would normally be considered as
@@
   \includegraphics[scale=0.3]{figures/nomod_tem_diff}
-  \caption{Temperature difference between SPH benchmark disc and high
-    accuracy 2D result.}
+  \caption{Fractional errors in the temperature distribution of a
+    $10^5$ particle disc. The radiative transfer grid is a Cartesian
+    grid generated using a mass per cell limit of
+    $5\times10^{26}$\,g. Axis units are au.}
   \label{fig:nomod_tem_diff}
@@
   \includegraphics[scale=0.3]{figures/sed_077}
-  \caption{SEDs from the benchmark disc with $10^5 $ particles. SEDs
-    are shown for inclination angles of 12.5 degrees (left) and 77.5
-    degrees (right). The benchmark SED is plotted as a solid line and
-    the {\sc torus} SED is plotted as a dashed line.}
+  \caption{SEDs from the benchmark disc represented by $10^5 $ particles and a
+    Cartesian radiative transfer grid generated using a mass per cell
+    limit of $5\times10^{26}$\,g. SEDs are shown for inclination
+    angles of 12.5 degrees (left) and 77.5 degrees (right). The
+    benchmark SED is plotted as a solid line and the {\sc torus} SED
+    is plotted as a dashed line. The corresponding fractional
+    temperature errors are plotted in Fig.\ref{fig:nomod_tem_diff}.}
   \label{fig:seds}
@@
 angle of 77.5 degrees there is also a significant reduction in flux
-below 1~$\mu\rm{m}$. Both these discrepancies are attributable to a lack of resolution within a few au of the central object. The density distribution in the central region of
+below 1\,$\mu\rm{m}$. Both these discrepancies are attributable to a lack of resolution within a few au of the central object. The density distribution in the central region of
 this disc is plotted in Fig.~\ref{fig:basic_dens} which shows that the
@@
 \includegraphics[scale=0.2]{figures/basic_dens}
-\caption{Density in central region of disc with $10^5$ particles. Axis
-units are $10^{13}$cm.}
+\caption{Density in the central region of the benchmark disc
+  represented by $10^5$ particles and a Cartesian radiative transfer
+  grid generated using a mass per cell limit of
+  $5\times10^{26}$\,g. Axis units are $10^{13}$cm. The central gap of
+  1\,au ($1.5\time10^{13}$\,cm) is not represented and the effects on
+  the temperature distribution and emergent SEDs are shown in
+  Fig.~\ref{fig:nomod_tem_diff} and Fig.~\ref{fig:seds}
+  respectively.}
 \label{fig:basic_dens}
@@
 \subsection{Grid resolution}
+\label{subsec:grid_res}
+
 Decreasing the mass per cell limit to achieve the required resolution
@@
 increased resolution were added to the AMR grid with sizes
-$1.5\times10^{15}$~cm, $3\times10^{14}$~cm and
-$6\times10^{13}$~cm. Within each cube it was required that the cell
+$1.5\times10^{15}$\,cm, $3\times10^{14}$\,cm and
+$6\times10^{13}$\,cm. Within each cube it was required that the cell
 size be no larger than 0.1 of the cube dimension. In order to confirm
@@
 analytical density description.  A spherical region with radius
-$1.0\times10^{15}$~cm, $5.0\times10^{14}$~cm or $2.5\times10^{14}$~cm
+$1.0\times10^{15}$\,cm, $5.0\times10^{14}$\,cm or $2.5\times10^{14}$\,cm
 was over written with the benchmark disc density after the initial
@@
 and the other lines show SEDs for forcing regions of radius
-$1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm (short
-dashed line) and $2.5\times10^{14}$~cm (dotted line).
+$1.0\times10^{15}$\,cm (long dashed line), $5.0\times10^{14}$\,cm (short
+dashed line) and $2.5\times10^{14}$\,cm (dotted line).
 \begin{figure*}
@@
   \includegraphics[scale=0.3]{figures/seds_forced_77.pdf}
-  \caption{SEDs from SPH benchmark disc for inclination angles of 12.5
-    degrees and 77.5 degrees. The benchmark SED is plotted as a solid
-    line. The {\sc torus} density distribution is forced to the correct
-    value with a radius of $1.0\times10^{15}$~cm (long dashed line), $5.0\times10^{14}$~cm
-(short dashed line) and $2.5\times10^{14}$~cm (dotted line).} 
+  \caption{ SEDs from the benchmark disc represented by $10^5 $ particles and
+    a Cartesian radiative transfer grid generated using a mass per
+    cell limit of $5\times10^{26}$\,g. Extra resolution has been added
+    around the central source and the {\sc torus} density distribution
+    is forced to the correct value within a radius of
+    $1.0\times10^{15}$\,cm (long dashed line), $5.0\times10^{14}$\,cm
+    (short dashed line) and $2.5\times10^{14}$\,cm (dotted line). SEDs
+    are shown for inclination angles of 12.5 degrees (left) and 77.5
+    degrees (right) with the benchmark result plotted as a solid
+    line.}
   \label{fig:sed_forced}
@@
 With the correct density forced out to a radius of
-$1.0\times10^{15}$~cm the SED is close to the benchmark result for
+$1.0\times10^{15}$\,cm the SED is close to the benchmark result for
 both viewing angles, however if the forced region is reduced in size
@@
 give a sufficiently accurate density distribution within the central
-$1.0\times10^{15}$~cm of the disc.
+$1.0\times10^{15}$\,cm of the disc.
 
@@
   \subfigure[$10^8$ particles]{\includegraphics[scale=0.22]{figures/dens_1e8}}
-  \caption{Central density on AMR grid derived from different numbers
-    of SPH particles. The axis units are $10^{13}$~cm.} 
+  \caption{Density in the central region of the disc as represented on AMR grids derived from different numbers
+    of SPH particles. The AMR grid is generated using a mass per cell
+    limit of $5\times10^{26}$\,g with extra resolution at the origin
+    as described in Section~\ref{subsec:grid_res}. The axis units are $10^{13}$\,cm.}
   \label{fig:n_part_central_dens}
@@
   \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/tdiff_1e8}}
-  \caption{Fractional temperature error for discs represented by
-    different numbers of SPH particles. Axis units are au.} 
+  \caption{Fractional errors in the temperature distribution of discs
+    represented by $10^5$, $10^6$, $10^7$ and $10^8$ particles. The
+    AMR grid is generated using a mass per cell limit of
+    $5\times10^{26}$\,g with extra resolution at the origin as
+    described in Section~\ref{subsec:grid_res}. The axis units are
+    $10^{13}$\,cm. The corresponding density distributions in the
+    central part of the disc are plotted in
+    Fig.~\ref{fig:n_part_central_dens}.}
   \label{fig:n_part_tem_diff}
@@
   \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/mp_temp_4}}
-  \caption{Fractional temperature error in the mid-plane for discs represented by
-    different numbers of SPH particles.} 
+  \caption{Fractional temperature error, as a function of radius, for particles within 0.01
+    scale heights of the mid-plane for discs represented by $10^5$,
+    $10^6$, $10^7$ and $10^8$ particles. }
   \label{fig:n_part_tem_diff_midpane}
@@
   \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/sed_013_1e8}}
-  \caption{SEDs at a 12.5 degree inclination angle for discs represented by different numbers of SPH
-    particles. The benchmark result is plotted as a solid line and the
-  modelled SED is plotted as a dashed line. } 
+  \caption{SEDs at a 12.5 degree inclination angle for discs
+    represented by $10^5$, $10^6$, $10^7$ and $10^8$ particles. The
+    benchmark result is plotted as a solid line and the {\sc torus}
+    SEDs are plotted as dashed lines. The corresponding density
+    distributions in the central part of the disc are plotted in
+    Fig.~\ref{fig:n_part_central_dens} and fractional temperature
+    errors are plotted in Fig.~\ref{fig:n_part_tem_diff}.}
   \label{fig:n_part_sed_013}
@@
   \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/sed_077_1e8}}
-  \caption{SEDs at a 77.5 degree inclination angle for discs represented by different numbers of SPH
-    particles. The benchmark result is plotted as a solid line and the
-  modelled SED is plotted as a dashed line. } 
+  \caption{SEDs at a 77.5 degree inclination angle for discs
+    represented by $10^5$, $10^6$, $10^7$ and $10^8$ particles. The
+    benchmark result is plotted as a solid line and the {\sc torus}
+    SEDs are plotted as dashed lines. The corresponding density
+    distributions in the central part of the disc are plotted in
+    Fig.~\ref{fig:n_part_central_dens} and fractional temperature
+    errors are plotted in Fig.~\ref{fig:n_part_tem_diff}.}
   \label{fig:n_part_sed_077}
@@
 
-The above analysis indicates that the hybrid code is capable of successfully passing the density distribution from the hydrodynamics step to the radiative-transfer code, and that accurate temperatures assuming radiative equilibrium can be passed back to the SPH code in order to update the gas pressure and perform the next hydrodynamical step.
-In order to test the feasibility of performing a radiation-hydrodynamics calculation using the hybrid code we adopt a `realistic' test problem, that of a circumstellar disc around a classical T Tauri star.
-The mid-plane optical depths here are higher than that of the Pascucci benchmark, providing a more demanding challenge both in terms of computation time and required numerical accuracy.
+The above analysis indicates that the hybrid code is capable of
+successfully passing the density distribution from the hydrodynamics
+step to the radiative-transfer code, and that accurate temperatures
+assuming radiative equilibrium can be passed back to the SPH code in
+order to update the gas pressure and perform the next hydrodynamical
+step. In order to test the feasibility of performing a
+radiation-hydrodynamics calculation using the hybrid code we adopt a
+`realistic' test problem, that of a circumstellar disc around a
+classical T Tauri star. The mid-plane optical depths here are higher
+than that of the Pascucci benchmark, providing a more demanding
+challenge both in terms of computation time and required numerical
+accuracy.
 
@@
 derived properties as a basis for constructing our model system. The
-disc of $0.02~{M}_{\odot}$ is initialised with an outer radius of
-150~AU, and an inner radius of 1.0~AU, surrounding a central star of
-mass $1~M_{\odot}$. The central star is represented by a sink particle
-which accretes gas particles within an accretion radius of 1.0~AU. The
+disc of $0.02\,{M}_{\odot}$ is initialised with an outer radius of
+150\,au, and an inner radius of 1.0\,au, surrounding a central star of
+mass $1\,M_{\odot}$. The central star is represented by a sink particle
+which accretes gas particles within an accretion radius of 1.0\,au. The
 disc itself is initially represented using $10^6$ particles of
@@
 central sink particle as the simulation progresses. The central star
-has a radius of $2~\rm{R}_{\odot}$, a temperature of 4000~K and a
-luminosity of $0.9~\rm{L}_{\odot}$.
+has a radius of $2\,\rm{R}_{\odot}$, a temperature of 4000\,K and a
+luminosity of $0.9\,\rm{L}_{\odot}$.
 
@@
 the disc.  The vertical sound crossing time at a radius of
-10~au is typically 2 years, so a radiative transfer calculation is
+10\,au is typically 2 years, so a radiative transfer calculation is
 performed after every four hydrodynamics time steps (equivalent to
@@
 was constructed using a maximum mass per cell of
-$3.0\times10^{25}~\rm{g}$ and a density splitting condition of
+$3.0\times10^{25}\,\rm{g}$ and a density splitting condition of
 $f_{\rm{split}}=0.1$. The density in a cylindrical region around the
@@
 justification for enforcing a low density region around the star. The
-radius of this region is $R_{\rm{gap}}=1.0~\rm{AU}$ which corresponds
+radius of this region is $R_{\rm{gap}}=1.0\,\rm{au}$ which corresponds
 to the accretion radius of the SPH sink particle. Two extra levels of
@@
 source to be resolved. The first box of extra refinement has size
-$10^{14}~\rm{cm}$ with cells no larger than $10^{13}~\rm{cm}$ and the
-second box has size $4\times10^{13}~\rm{cm}$ with cells no larger than
-$4\times10^{12}~\rm{cm}$.
+$1\times10^{14}\,\rm{cm}$ with cells no larger than $1\times10^{13}\,\rm{cm}$ and the
+second box has size $4\times10^{13}\,\rm{cm}$ with cells no larger than
+$4\times10^{12}\,\rm{cm}$.
 
@@
 processes, of which 440 hours was spent in radiation calculations. The
-radiation calculations take approximately 4~times as long as the
+radiation calculations take approximately four times as long as the
 hydrodynamics calculations so the combined code is significantly
@@
 present in the disc at a radius of approximately
-$3\times10^{15}~\rm{cm}$ which shadows the region immediately behind
+$3\times10^{15}\,\rm{cm}$ which shadows the region immediately behind
 causing it to cool. Figure~\ref{fig:frame4} shows several such scale
@@
   \subfigure[]{\includegraphics[scale=0.3]{figures/u_run2_DSC1024}\label{fig:frame6}}
-  \caption{Particle plots showing internal energy in cylindrical
-    polar co-ordinates. Axis units are cm.}
+  \caption{Internal energy distribution in the model disc at six
+    different times as the disc adjusts towards
+    equilibrium. Figure~\ref{fig:frame1} shows the initial vertically
+    isothermal state and Fig.~\ref{fig:frame6} shows the steady state in
+    hydrostatic and radiative equilibrium. Intermediate frames show
+    the effect of scale height fluctuations on the internal energy
+    within the disc. Internal energy is plotted for each particle in a
+    cylindrical polar co-ordinate system and the axis units are cm.}
   \label{fig:log_u}
@@
   \includegraphics[scale=0.3]{figures/sigma}
-  \caption{Surface density as a function of radius.}
+  \caption{Surface density as a function of radius for the model
+    disc. The solid line is the vertically isothermal disc prior to
+    the radiative transfer code being switched on. The dotted line in
+    shows the disc once is has reached a state of hydrostatic and
+    radiative equilibrium.}
   \label{fig:sigma}
@@
   \includegraphics[scale=0.3]{figures/scale_height}
-  \caption{Disc scale height as a function of radius.}
+  \caption{Scale height of the model disc as a function of radius. The
+    solid line is the vertically isothermal disc prior to the
+    radiative transfer code being switched on. The dotted line in
+    shows the disc once is has reached a state of hydrostatic and
+    radiative equilibrium.}
   \label{fig:scale_height}
@@
   \includegraphics[scale=0.3]{figures/mid_tem}
-  \caption{Average temperature within one scale height of the mid plane as a function of
-    radius.}
+  \caption{Average temperature within one scale height of the mid
+    plane as a function of radius for the model disc. The solid line
+    is the vertically isothermal disc prior to the radiative transfer
+    code being switched on. The dotted line in shows the disc once is
+    has reached a state of hydrostatic and radiative equilibrium.}
   \label{fig:mid_tem}
@@
 \ref{fig:mid_tem} show that the disc is hotter close to the mid-plane,
-except within a region between 10--20 au of the centre, but has a
+except within a region between 10--20\,au of the centre, but has a
 smaller scale height. Figure~\ref{fig:log_u} shows that the vertical

### 2009-10-12 SPH-Torus-paper1/sphtorus_benchmark.tex
After spell check
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2050 25464f21-6099-402c-b30a-640f1d40d38b

@@
     and a density contrast splitting condition of $f_{\rm{split}}=0.1$
-    (right) contructed
+    (right) constructed
     from $10^7$ SPH particles. The grids are

### 2009-10-12 SPH-Torus-paper1/sphtorus_benchmark.tex
Minor updates
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2051 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-The solution is to include radiation-transfer self-consistently  and perform a radiation-hydrodynamics (RHD) calculation.
-The simplest way to do this is to assume that the energy is transported by radiative diffusion of photons.
-The diffusion approximation is a good one at high optical depth, but breaks down in optically thin regions since the diffusion speed may exceed the speed of light as the mean-free-path tends to infinity; an essentially arbitrary flux limiter is adopted in this regime.
-Furthermore the approximation is often implemented as a grey method, typically using Rosseland mean  opacities tabulated as a function of temperature.
-Finally the diffusion approximation cannot treat the effects of shadowing, as radiation field may diffuse around optically thick obstacles.
+The solution is to include radiation-transfer self-consistently  and
+perform a radiation-hydrodynamics (RHD) calculation. The simplest way
+to do this is to assume that the energy is transported by radiative
+diffusion of photons. The diffusion approximation is a good one at
+high optical depth, but breaks down in optically thin regions since
+the diffusion speed may exceed the speed of light as the
+mean-free-path tends to infinity; an essentially arbitrary flux
+limiter is adopted in this regime. Furthermore the approximation is
+often implemented as a grey method, typically using Rosseland mean
+opacities tabulated as a function of temperature. Finally the
+diffusion approximation cannot treat the effects of shadowing, as the radiation field may diffuse around optically thick obstacles.
 The crucial advantage of the diffusion approximation though is of course speed: the radiation transport step is straightforward to implement and is not hugely dominant in the RHD calculation.
@@
   \label{fig:mass_condition_mesh}}
-  \subfigure[Grid with a density condition of
+  \subfigure[AMR grid with a density condition of
     $f_{\rm{split}}=0.1$.]
@@
   grid generated using a mass per cell limit of
-  $5\times10^{26}$\,g. Axis units are $10^{13}$cm. The central gap of
-  1\,au ($1.5\time10^{13}$\,cm) is not represented and the effects on
+  $5\times10^{26}$\,g. Axis units are $10^{13}$cm. The central 1\,au gap 
+   is not represented and the effects on
   the temperature distribution and emergent SEDs are shown in

### 2009-10-12 SPH-Torus-paper1/sphtorus_benchmark.tex
Minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2052 25464f21-6099-402c-b30a-640f1d40d38b

@@
 the disc.  The vertical sound crossing time at a radius of
-10\,au is typically 2 years, so a radiative transfer calculation is
+10\,au is typically approximately 2 years, so a radiative transfer calculation is
 performed after every four hydrodynamics time steps (equivalent to

### 2009-10-12 torus/timedep_mod.F90
updates to timepdep - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2053 25464f21-6099-402c-b30a-640f1d40d38b

@@ -22,14 +22,14 @@ module timedep_mod
   public :: runtimeDependentRT, timeDependentRTtest
 
   type STACKTYPE
-     real(double) :: freq(1000000)
+     real(double) :: freq(10000000)
      real(double) :: eps(1000000)
-     type(VECTOR) :: direction(1000000)
-     type(VECTOR) :: position(1000000)
-     logical :: photonFromSource(100000)
-     logical :: photonFromGas(1000000)
-     logical :: beenScattered(1000000)
-     logical :: radiativeEquPhoton(1000000)
+     type(VECTOR) :: direction(10000000)
+     type(VECTOR) :: position(10000000)
+     logical :: photonFromSource(1000000)
+     logical :: photonFromGas(10000000)
+     logical :: beenScattered(10000000)
+     logical :: radiativeEquPhoton(10000000)
   end type STACKTYPE
 
 contains
@@ -1205,10 +1205,12 @@ contains
 
   subroutine timeDependentRTtest()
     real(double) :: currentTime, endTime
-    integer, parameter :: nx = 100
+    integer, parameter :: nx = 20
     integer, parameter :: nProb = nx + 1
     real(double) :: etaCont(nx)
     real(double) :: aDot(nx)
+    real(double) :: oldaDot(nx)
+    real(double) :: oldetaCont(nx)
     real(double) :: rho(nx)
     real(double) :: kappa(nx)
     real(double) :: temperature(nx)
@@ -1217,6 +1219,7 @@ contains
     real(double) :: distanceGridPhotonFromSource(nx)
     logical :: photonFromSource, photonFromGas
     real(double) :: prob(nProb)
+    real(double) :: bias(nProb)
     real(double) :: photonProb(nProb)
     real(double) :: photonEnergy
     real(double) :: xCen(nx)
@@ -1255,7 +1258,7 @@ contains
 
     real(double) :: epsOverDeltaT, newDeltaT, tot, albedo, diffusionTime
 !    real(double) ::t
-    logical :: outOFtime, scattered
+    logical :: outOFtime, scattered, dumpnow
     type(VECTOR) :: rVec, uHat
     integer :: i, iMonte, nMonte, iPos,iter, nPhotons
     character(len=30) :: outfile
@@ -1263,7 +1266,7 @@ contains
[…]

### 2010-04-19 torus/stateq_mod.F90
Fix undefined variable detected by gfortran with -Wextra.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2224 25464f21-6099-402c-b30a-640f1d40d38b

@@ -4259,7 +4259,7 @@ contains
        sum_Nm_nLTE = 0.0d0
        do j = 1, maxLevels
           Nm_nLTE = thisOctal%N(thisSubcell, j)
-          sum_Nm_nLTE = sum_Nm_LTE + Nm_nLTE
+          sum_Nm_nLTE = sum_Nm_nLTE + Nm_nLTE
        end do
 
        sum_Nm_LTE = 0.0d0

### 2010-04-19 torus/amr_mod.f90
Add a new subroutine to make sure all pointers from child octals to the parent octal are correct. Compiling with nagfor showed up some dangling pointers from child octals to parent octals.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2225 25464f21-6099-402c-b30a-640f1d40d38b

@@ -1354,6 +1354,22 @@ CONTAINS
 
   END SUBROUTINE countVoxels
 
+  RECURSIVE SUBROUTINE fixParentPointers(thisOctal)
+      
+    TYPE(OCTAL), POINTER  :: thisOctal 
+    TYPE(OCTAL), POINTER  :: child
+    INTEGER :: i
+        
+    IF ( thisOctal%nChildren > 0 ) THEN
+       ! call this subroutine recursively on each of its children
+       DO i = 1, thisOctal%nChildren, 1
+          child => thisOctal%child(i)
+          thisOctal%child(i)%parent => thisOctal
+          CALL fixParentPointers(child)
+       END DO
+    END IF
+        
+  END SUBROUTINE fixParentPointers
 
   SUBROUTINE startReturnSamples (startPoint,direction,grid,          &
              sampleFreq,nSamples,maxSamples,thin_disc_on, opaqueCore,hitCore,      &

### 2010-04-19 torus/torusMain.F90

@@ -1716,6 +1716,7 @@ end subroutine pre_initAMRGrid
           call initFirstOctal(grid,amrGridCentre,amrGridSize, amr1d, amr2d, amr3d, young_cluster, nDustType, romData=romData) 
           call writeInfo("First octal initialized.", TRIVIAL)
           call splitGrid(grid%octreeRoot,limitScalar,limitScalar2,grid,romData=romData)
+          call fixParentPointers(grid%octreeRoot)
           call writeInfo("...initial adaptive grid configuration complete", TRIVIAL)
 
            ! This section is getting rather long. Maybe this should be done in 

### 2010-04-19 torus/gridio_mod.F90
Fixes to get daily test building.
Add -Wextra for gfortran build.


git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2227 25464f21-6099-402c-b30a-640f1d40d38b

@@ -2765,7 +2765,7 @@ contains
          logical :: fileFormatted
          type(OCTAL), pointer :: thisOctal, parent, child, depth3
 !         character(len=80) :: message
-	 integer :: i, iChild, ithread, j
+	 integer :: i, iChild, ithread
 
 
          allocate(depth3)

### 2010-04-19 torus/mpi_amr_mod.F90

@@ -1493,7 +1493,7 @@ contains
           endif
        endif
     endif
-666 continue
+
   end function octalOnThread
 
   subroutine periodBoundary(grid, justGrav)

### 2010-04-19 torus/photoionAMR_mod.F90

@@ -897,7 +897,7 @@ if (.false.) then
  write(vtkFilename,'(a,i2.2,a)') "photo",niter,".vtk"
  call writeVtkFile(grid, vtkFilename, &
       valueTypeString=(/"rho          ","HI           " , "temperature  ", &
-      "dust1"/))
+      "dust1        "/))
  call writeAMRgrid("tmp.grid",.false.,grid)
 enddo
 

### 2010-04-19 BD_disc/old.tex
New project
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2228 25464f21-6099-402c-b30a-640f1d40d38b

% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty'
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

\documentclass[useAMS,usenatbib]{mn2e}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.  
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{subfigure}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\newcommand\mnras{MNRAS}
\newcommand\pasp {PASP}
\newcommand\aj   {AJ}
\newcommand\apj  {ApJ}
\newcommand\apjl  {ApJL}
\newcommand\apjs  {ApJS}
\newcommand\aap  {A\&A}
\newcommand\aaps  {A\&AS}
\newcommand\apss  {AP\&SS}
\newcommand\gca  {Geochim. Cosmochim. Acta}
\newcommand\araa {ARA\&A}
\usepackage{multirow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[**]{**}  \author[N.J.  Mayne and Tim
Harries]{N.J. Mayne$^{1}$\thanks{E-mail: nathan@astro.ex.ac.uk
    (NJM)} and Tim Harries$^{1}$\\
  $^{1}$ School of Physics,
  University of Exeter, Stocker Road, Exeter, EX4 4QL.\\
}
 \begin{document}

\date{Accepted ?. Received ?; in
  original form ?}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2009}

\maketitle

\label{firstpage}

\begin{abstract}
SORT OUT REFERENCE TO THE FILTER RESPONSES IN THE SEDS FIGURES say
discussed later
more about stellar photosphere overlapping with disc

FINESSE FIGURE SIZES

CHANGE ALL WORDING FOR NEW FIGURES** CHANGED AGE TO 1 MYR FOR SUB
FIGURES AND NEED TO ACKNOWLEDGE THROUGHT

CHOSE 10 MYRS AS PRE-MS CONTRACTION AGES ARE PROBABLY A  FACTOR OF 2 WRONG

ADD FILTERS TO OTHER SEDS FIGURES

Note about fitting objects in the next paper.

   \end{abstract}

\begin{keywords}
  stars:evolution -- stars:formation -- stars: pre-main-sequence --
  techniques: photometric -- catalogues -- (stars) Hertzsprung-Russell
  H-R diagram
\end{keywords}

\section{Introduction}
\label{intro}

Theoretical study of Brown Dwarfs (BDs) and the subsequent development
of testable hypotheses for observational studies is a critical, and
somewhat uncertain, area within the field of star and planet
formation. Several of the key physical parameters and mechanisms
remain unclear within this mass regime
\citep{2007ApJ...664.1154S}. Uncertainty remains over fundamental
issues such as the initial formation mechanisms, the subsequent
evolution and dominance of a star-disc interaction through to the
possible dependence of planet formation mechanisms on stellar mass
\citep[for a review of BD formation mechanisms see
][]{2006astro.ph..2367W}.

Perhaps the two most fundamental challenges are formulating the
formation mechanism of BDs and deriving the resulting
initial-mass-function (IMF). Whether the BD IMF or formation
mechanisms are different to their higher mass, solar-type, equivalents
(T Tauri Stars, hereafter termed TTS) is an open question. Derivations
of reliable IMFs depend, obviously, on robust derivations of stellar
mass, and more subtly, on derivations of stellar ages (as IMFs are
usually defined for assumed coeval populations). The study of
classical T Tauri (CTTS) and disc systems of
\cite{1997AJ....114..288M} found that given an expected range of
parameters the scatter in infrared photometry matched the observed
CTTS locus well. However the work of \cite{1997AJ....114..288M},
discussed in more detail later, only included parameterised `flat'
discs. Once disc flaring is considerd it is clear from previous work
that misidentification of high mass stars with circumstellar discs is
likely. \cite{2004ApJ...617.1177W} show that high-mass (HM) stars with
circumstellar discs are likely to be mis-identified as younger Class I
sources. This problem also exists at lower masses where the presence
of circumstellar discs can dramatically shift the spectral energy
distributions (SEDs) and therefore colours and magnitudes of BDs
\citep{2004MNRAS.351..607W}. Therefore, deriving robust masses (and
ages), and subsequently IMFs for BDs requires an understanding of
these effects of disc presence.

The presence, or fraction (for populations) of associated discs is
itself also crucial in isolating the formation mechanisms of
BDs. Precise determination of disc parameters for BDs and comparison
with the TTS results may allow the differentiation of currently
competing theories of the BD formation mechanism. Essentially, a
mechanism similar to that seen in higher mass stars i.e. cloud
collapse and fragmentation will result in a similar fraction of discs
across the BD mass boundary, whereas a formation mechanism dominated
by dynamical interactions \citep[ejections, accretion disc stripping
from near collisions or tidal interactions etc.]{2003IAUS..211...27B}
will result in a markedly different disc parameters, such as fractions
of stars with discs or radial sizes of the discs themselves, across
the BD mass boundary. Fundamentally a different disc fraction for BD
stars to TTS would provide persuasive evidence of a different
formation mechanism across the two mass regimes, as would an increase
in the average radial size of discs, indicative of truncation for BD
objects. Therefore, to progress our understanding of the fundamental
issues of both the formation mechanism and emerging IMFs for BDs,
consideration of the effects of an associated circumstellar disc and
their subsequent ubiquity are essential.

Another fundamental, and important, unresolved issue is the mechanism
of planet formation. A critical, and currently ill defined constraint
for the planet formation models is the timescale available for planet
formation within the circumstellar disc. Current favoured formation
mechanisms such as core accretion or gravitational instability are
separated by these timescales. Disc fractions have again been used, in
conjunction with stellar ages, to derive the disc dissipation
timescale, which obviously constrains the planet formation
timescale. Studies of TTS have derived a disc dissipation timescale of
$\approx$ 5 Myrs \citep{2001ApJ...553L.153H}, with very few discs
shown to survive out to $\approx$ 20 Myrs
\citep{2004ApJ...612..496M}. However, the derivation of a disc
dissipation timescale from disc fractions suffers from several
intrinsic problems, for instance the inconsistent (and often
contradictory) methods of deriving ages \citep[see][for a full
discussion]{2008MNRAS.386..261M}. Notwithstanding this, disc fraction
surveys have also been published for lower mass and BD systems, such
as \cite{2004A&A...427..245S} and \cite{2004ApJ...609L..33M}, deriving
a similar order-of-magnitude disc dissipation timescale. The
probability of forming planets around BDs is clearly sensitive to any
changes in disc dissipation timescale across the TTS to BD mass
boundary.

Some studies of disc lifetimes find no significant difference between
BD stars and their higher mass counterparts
\citep{2003AJ....126.1515J}, however a possible correlation of disc
lifetime with stellar mass is proposed in \cite{2007ApJ...660.1517S}.
Additionally, \cite{2009arXiv0901.2603K} find that, for TTS older than
3 Myrs, the disc dispersal time is mass dependent for intermediate
mass (IM) to solar-type stars. This result only holds for the mass
transition stated (IM to solar-type) and is based on stars with
combined dust signatures, from infrared (IR) excesses and accretion
indicators (using a EW[H$\alpha$], criterion).
\cite{2009arXiv0901.4120D} also find, for TTS, a mass dependent
general SED shape for disc candidates, with higher mass stars showing
a featureless continuum at $\lambda>$8.0$\mu$m with lower mass stars
generally showing strong silicate and PAH features at 10 and 2$\mu$m,
indicative of mass dependent disc evolution. Whether in fact the disc
lifetimes and therefore rate or type of involved physical processes
are a function of stellar mass could provide another piece of evidence
separating the previously assumed continuous (in mass) evolutionary
principles of stars into a dichotomy separated by the hydrogen-burning
mass limit, and alter the probability of forming planets in the BD
regime.

To test the hypothesis that disc dissipation timescales are
independent of stellar mass one again requires accurate masses for BD
with associated discs (hereafter, BDD) systems, alongside reliable
disc fractions. The derivation of masses for BDD systems is
complicated by disc presence, but additionally, the detection of disc
presence at a given age is not simply a function of the disc
dissipation timescale.

Several mechanisms may act to completely dissipate a circumsteller
disc. These include accretion from the disc ($\delta M_{\rm
  disc}=\dot{M}$), photoevaporation or photoionisation due to flux
from the central and neighbouring stars, and the formation of giant
planets or interaction with binary partners. However, the entire disc
does not have to be dissipated to be missed by disc fraction surveys.
More subtly, disc fractions can be altered due to wavelength dependent
detection. This is due to the peak flux of the thermal blackbody
emission of the disc being proportional to the temperature,
$\lambda^{\rm thermal}_{\rm peak}\propto T_{\rm disc}$, and the
temperature in the disc being approximately a function of distance
from the star. Thus for a given system, as one increases the
wavelength of observation, the corresponding radial position of the
effective source will increase. Moreover, as the disc flux must be
separated from the photospheric flux the important quantity is the
separation in wavelength between the emission peaks for the stellar
and thermal disc components. Therefore the presence of an inner disc
hole can change derived disc fractions, as a function of
wavelength. Interestingly, \cite{2009arXiv0901.2603K} find that
results for disc dissipation timescales based only on their accretion
indicators or inferred disc presence do not agree, perhaps due to
inclusion of transitional objects, where the inner disc is being
cleared, and is therefore not detected at their target
wavelength. \cite{2009arXiv0901.2603K} suggest that this is caused by
photoevaporation of the inner disc, leading to a mass dependent disc
lifetime, at their wavelength, for their sample. However, as discussed
in \cite{2009arXiv0901.4120D}, the inner hole can be created via dust
grain growth and midplane settling, giant planet formation or
photoevaporation by ultraviolet (UV) and far-UV (FUV) flux
\citep{2007MNRAS.378..369N}.  \cite{2009arXiv0901.4120D} argue that if
binarity or giant planet formation or photoevaporation cause inner
disc clearing the resulting system would not show active accretion
from radii below the inner disc boundary. For the case of clearing by
dust grain growth and settling accretion from a hot gas disc within
the inner radius is still possible, and indeed evidence for such a hot
gas inner disc has been found through SED fitting
\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Additionally,
\cite{2009arXiv0901.4445E} argue that for M stars, with a pure
reprocessing disc where the inner disc radius ($R_{\rm inner}$) is
equal to the dust sublimation radius ($R_{\rm dust}$, discussed in
Section \ref{physics}), the stellar and thermal components are not
separable at wavelengths shorter than 6$\mu$m. In the case of
\cite{2009arXiv0901.4445E}, the inner disc hole was created by
photoionising radiation from the central star destroying the dust
component of the disc. Recent direct evidence for a photoevaporating
disc has been found for the circumstellar disc around a low mass TTS
in the Sigma Orionis cluster \citep{2009arXiv0902.0457R}. The
detection was characterised by a tenuous photoevaporation wind and
little or no accretion, and a disc detection at 24$\mu$m indicative of
a large inner hole. Additionally, for BDs, \cite{2009arXiv0902.0638M}
find that the disc mass and radius distributions in the Orion
Trapezium cluster are consistent with photoevaporation over 1 Myr (the
adopted age of the cluster), from UV and FUV flux generated by the
massive $\theta^1$ Ori C.

Whichever mechanism is responsible for clearing the inner disc hole it
is clear that its presence leads to confusion in the validity of disc
fractions at a given wavelength. The important quantity here is the
separation in wavelength between the emission peaks for the stellar
and thermal disc components, as it is these components which must be
separated. For BDD systems it is likely that difficulties detecting
the disc will be exacerbated by the lower temperatures of the
photosphere and therefore the smaller separation in wavelength from
the thermal disc emission component, compared to TTS
systems. Therefore, to derive disc fractions for BD populations we
require detailed comparison models with which to guide disc candidate
selection. These models must necessarily include a treatment of
accretion and dust destruction, given that these factors deplete the
inner (and total) disc thereby affecting disc detection.

Although the creation of the inner disc hole could have several
causes, at least part of the effect is undoubtedly due to
accretion. Accretion acts to directly deplete the inner disc (where
the material is accreted from). Accretion also depletes the inner disc
indirectly, as accretion generates hot continuum emission
\citep{1998ASPC..154.1709G}, increasing the photoionising UV and FUV
flux available \citep{1998ASPC..154.1709G}, and therefore affecting
the derived disc fraction \citep{2009arXiv0901.3684H}. This effect may
be amplified for BDD systems where the combined photospheric emission
is dominated by accretion flux. However, accretion columns modeled by
\cite{2004MNRAS.348..879A} were found to produce negligible levels of
photoionising flux due in part to the high optical depth of the column
itself to Lyman continuum photons. Additionally, due to the high
concentrations of hydrogen in the accretion column and hotspot the
emission is more likely to be characterised by a stellar atmosphere
than a black body. However, for our work as emission from a stellar
atmosphere or a black body of equal temperature are approximately
equal for wavelengths longer than the Lyman edge we have neglected
this effect. Whilst the accretion column and hotspot may not
contribute to the photoinising flux within the system they will of
course alter the disc evolution by an increase of the emitted
flux. This increase in flux will lead to an increase in temperature of
the disc inner and outer regions, and more particulary a change in the
dust sublimation effects at the inner edge.

The current proposed mechanism of accretion is a magnetically
channelled accretion `column', where material from a truncated (at the
co-rotation radius $R_{\rm co}$) inner disc boundary falls onto the
surface of the star along magnetic field lines
\citep{1990RvMA....3..234C,1991ApJ...370L..39K}. This mechanism is
widely accepted, with strong evidence found from the excessive widths
of H$\alpha$ ($>$10$\AA$) emission lines, over that caused by
chromospheric activity and stellar rotation
\citep{1998ASPC..154.1793W}, caused by the high velocities of
infalling matter, ~100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.

Accretion rates can be derived by modelling this magnetospheric
accretion with a characteristic `column' temperature and assuming
statistical equilibrium of the state populations. The resulting line
ratios can then be fitted to the observed spectra. Accretion rates can
also be calculated from model comparison of the Equivalent Width (EW)
of the H$\alpha$ line itself, or perhaps more reliably, as they are
less affected by extinction, that of the hydrogen recombination lines
of Pa$\beta$ and Br$\gamma$. Accretion rates have been derived using
these methods for many TTS and more recently for BDs
\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
with accretion rates in the range $\dot{M_{\rm
    acc}}=$10$^{-6}$-10$^{-12} M_{\odot}yr^{-1}$, and typical
accretion rates in the range log$(\frac{\dot{M}}{M_{\odot}}
yr^{-1})=$-10 to -8 with only FU Orionis type objects accreting at
rates higher than this. The mechanism producing accretion rates as
high as those observed episodically in FU Orionis type objects is
likely to be produced by some accretion mechanism instability, or
perhaps by encounters with other cluster members \citep[see][for
discussion]{2008arXiv0810.2854P}. Additionally, much lower accretion
rates of $\dot{M}\approx$ 10$^{-13}M_{\odot}yr^{-1}$ have been derived
for BDs using flux blueward of 4000$\AA$ where the photospheric flux
becomes negligible \citep{2009arXiv0901.3684H}.

Analysis of the derived accretion rate data has led several authors to
propose a strong correlation between accretion rate and stellar mass
\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
of an approximate form: $\dot{M_{\rm acc}}\propto M_{*}^{~2}$. This
correlation has no clear physical basis and it has been suggested that
it could be caused solely by selection biases and detection thresholds
\citep{2006MNRAS.370L..10C}. \cite{2006ApJ...648..484H} points out
that Bondi-Hoyle accretion naturally results in a clear
$\dot{M}\propto M^2_*$ relationship, but is not a desirable formalism
to adopt as it completely ignores angular momentum of the accreting
material. This proposed correlation could have important implications
with regards to disc lifetimes and planet formation probabilities as a
function of mass.

As discussed, discs associated with BD systems lead to difficulties in
accurate classification of the underlying BD
\citep{2004MNRAS.351..607W}. Furthermore, accretion, both direct and
indirect, can act to alter the disc signature, and clearly the
photospheric signature. For cooler BD systems, where the stellar flux
is generally redward of any accretion flux, increased accretion fluxes
could dominate the resulting SED. Given that the derivation of a
robust relationship of the form $\dot{M}\propto M^{\alpha}_*$ requires
accurate mass and accretion derivations, then clearly the effects of
circumstellar disc and increased accretion rates must be considered,
before any such relationship can be accepted. As there is currently no
clear theory linking accretion rate and mass (ignoring Bondi-Hoyle
accretion), this relationship is driven by observations.  However, the
observational constraints must be interpreted using a self-consistent
set of accreting BDD and BD systems to better understand their
implications. In other words, what do the observations really tell us?
Is there a real relationship between mass and accretion rate or would
simulated systems outside this relationship (and attributed scatter)
not be detected or included in the current observational surveys, due
to misclassification?

A further use of disc fractions, in conjunction with stellar ages, is
to aid the understanding of the angular momentum evolution of star and
disc systems. Recent evidence from TTS, from correlations of stars
with IR excesses and slower rotational rates
\citep{2007ApJ...671..605C} has seemed to strongly support a mechanism
of disc-locking, where the central star is rotationally braked through
magnetic locking to the accretion disc
\citep{1993AJ....106..372E,1990RvMA....3..234C,1991ApJ...370L..39K}. A
similar mechanism has been put forward, but has yet to be
unambiguously confirmed, for BD stars. However, current studies have
found a much weaker correlation between the slower rotators and those
where a disc presence is inferred for BDs. Some authors have therefore
proposed an `imperfect' disc-locking mechanism for stars in the lower
mass regime ($M_*<0.4M_{\odot}$, inclusive of the BD mass regime,
$M_*<0.08M_{\odot}$) \citep{2005A&A...430.1005L}. This weaker
correlation could also be due to `imperfect' disc-locking or
observational effects and mass dependence of the disc dissipation
timescale \citep{2004A&A...419..249S,2005A&A...429.1007S}.

If disc-locking is present for BDD systems, as for TTS stars, one
would expect accretion of material from a magnetic truncation radius,
$R_{\rm T}$ \citep{2007prpl.conf..479B}.  \cite{2007prpl.conf..479B}
show that the magnetic truncation radius, $R_{\rm T}$, must be less
than the co-rotation radius, $R_{\rm co}$ (where the Keplerian angular
rotation rate of the disc is the same as the angular rotation rate of
the star), as material outside this radius will have too much angular
momentum to fall onto the star. This is implicitly adopted in the
proposed accretion mechanism, where the disc is magnetically
truncated, and therefore locked to the star. This magnetic truncation
would lead to an inner wall (and inner hole) of the accretion
disc. Evidence for an inner disc wall has been found from near-IR
excesses from the inner rims of Herbig Ae stars, with emission peaking
at 2-3$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
position of this wall is affected by several factors, discussed
further in Sections \ref{dust_edge} and \ref{inner_edge}. The previous
work of \cite{1997AJ....114..288M} explored the effects of simple mass
accretion and the radius to the inner disc on the infrared colours of
CTTS, useing a prescribed range of inner disc
radii. \cite{1997AJ....114..288M} find that the scatter in infrared
colours for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
$\dot{M_{\rm acc}}=$10$^{-9}$to 10$^{-5} M_{\odot}yr^{-1}$, matches
the scatter of the CTTS locus found in the data. The models of
\cite{1997AJ....114..288M} used physically flat discs however meaning
their results will not stand for discs with significant flaring. More
importantly for our work \cite{1997AJ....114..288M} find a correlation
of the infrared locus of models with the accretion and inner disc
location. Essentially, changes in the stellar flux levels and position
of the inner wall lead to temperature changes of this inner edge and
therefore changes in the balance of flux across the infrared
wavelength regime. As this study does not include the effects of
vertical hydrostatic equilibirum or even the study of flared discs one
would expect, perhaps, a more complex relationship between the inner
edge position and infrared excess in `real' systems. This means that
studies aiming to provide evidence of disc locking by comparing disc
indicators with rotation rates may include unforseen biases. As the
rotation rate will effect the co-rotation radius and therefore
truncate the disc at different radii, thereby enhancing or suppressing
any relationship of infrared excess (or disc presence) with rotation
rate.

In summary, several key areas in the theoretical studies of BDs hinge
critically on observational constraints, where the derived values are
heavily affected by disc and/or accretion presence.  Formation
mechanisms, IMFs, disc dissipation timescales, accretion rate--stellar
mass relationships and studies of disc-locking mechanisms using
correlations of rotation rates with infrared excesses, all require
derivations of either masses, ages or disc fractions (or a
combination), supplemented by other parameters. The consequences of
the disc structure for BD accretion discs, particularly vertical
structure, given the assumption of vertical hydrostatic equilibrium,
have already been discussed for a limited range of BD parameters in
\cite{2004MNRAS.351..607W}. Indeed \cite{2004MNRAS.351..607W} have
shown that BDD systems seen at higher inclinations can be confused
with CTTS systems, having similar colours and
magnitudes. Additionally, a benchmark model grid of spectra for star
and disc systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$
has previously been published in \cite{2006ApJS..167..256R}.

In this work we explore the effects of accretion and disc presence on
the derivation of the stellar parameters and explore the intrinsic
biases, or relationships, which will effect or inhibit conclusions on
mass to accretion rate or rotation to infrared excess correlations. We
have extended the similar work of \cite{2004MNRAS.351..607W} by
inclusion of a simple treatment of accretion and a sophisticated
implementation of dust sublimation (amongst other improvements). The
complete model grid, with derived photometry and isochrones, is
available online through our browsing tool
\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
which is described in Appendix \ref{website}. The aim of this online
database is to complement that of \cite{2006ApJS..167..256R}. Finally,
subsequent papers will introduce expansion to the model grid and an
online fitting tool.

The structure of this paper is as follows. In Section \ref{model} we
outline the model used, including an explanation of our physical
assumptions (Section \ref{physics}), a brief description of the
radiative transfer code (Section \ref{torus}), and an explanation of
the derivation of emergent quantities such as photometric magnitudes
(Section \ref{derived}). The ranges of the input variables are then
explained and, where possible, justified using observational
constraints in Section \ref{par_space}, with the total parameter space
covered shown in Table \ref{par_space_table}. Section
\ref{disc_struct} then contains analysis and description of the
resulting temperature and dust density structures of the discs. The
consequences of these changes in disc structure on the SEDs of these
objects is then discussed in Section \ref{sed_analysis}. Section
\ref{photometry} then details problems caused for the derivation of
the primary parameters age, mass and disc fractions from photometry
and the resulting relations built on these parameters; accretion rate
to stellar mass and rotational period to disc presence. Finally,
conclusions are drawn, with a summary, in Section
\ref{conclusions}.**REWRITE AT END**A CASE STUDY IS THEN INCLUDED AS
SECTION \ref{object}.**

\section{Model}
\label{model}

In this Section we detail the physical model adopted and assumptions
made (Section \ref{physics}), then explain key elements of the
radiative transfer code (Section \ref{torus}). Then we discuss the
derived values, such as broadband photometric magnitudes and colours
(in Section \ref{derived}). Some internal consistency checks are
detail in Appendix \ref{consistency}.

\subsection{Physical model and assumptions}
\label{physics}

\subsubsection{Photospheric flux}
\label{phot_flux}

To model an accreting BDD system we must first model the underlying
photospheric flux. To provide a self-consistent set of model spectra
we have adopted a BD stellar interior and atmospheric model grid. We
have then constructed the total photospheric flux for any input value
of stellar age and mass by interpolating for surface gravity (log(g)),
effective temperature ($T_{\rm eff}$), radius ($R_*/R_{\odot}$) and
luminosity ($L_*/L_{\odot}$). These values were then used to
interpolate atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2}
\AA^{-1}$) from 1200 to 2$\times$ 10$^7$ $\AA$ (or 0.12 to 2000
$\mu$m). These spectra were then smoothed using 200 logarithmically
spaced points. Careful inspection ensured that no spectral features
were removed during smoothing. The stellar interior models used for
this study are the `DUSTY00' models of \cite{2000ApJ...542..464C}
combined with the `AMES-Dusty', atmospheric models of
\cite{2000ApJ...542..464C}, which are all available online
\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
approximate $T_{\rm eff}$ (effective temperature) range of $\approx
$3000K$<T_{\rm eff}<$1600K the AMES-Dusty atmospheres are most
applicable (2700K$>T_{\rm eff}>$1700K). We did try including dynamic
application of atmospheres based on the derived $T_{\rm eff}$,
i.e. using AMES-Cond for $T_{\rm eff}<$1700K, however this resulted in
large discontinuities between the model atmospheres and resulting
spectra. As this only affects stars at the very edge of our
temperature range, i.e. for the oldest and lowest mass objects (for
the AMES-Cond case), we have adopted the same model throughout.

\subsubsection{Accretion flux}
\label{acc_flux}

Secondly, we require a model of the accretion flux for the system. The
flux due to accretion was added onto the intrinsic photospheric flux
using the simple approximation of blackbody emission. The selected
accretion rate was used to derive an accretion luminosity ($L_{\rm acc}$),
where the material was modelled as falling from the disc inner edge
onto the surface of the star. $L_{\rm acc}$ is calculated according to
\ref{Lacc}, 
\begin{equation}
{L_{\rm acc}=\frac{GM_*\dot{M}}{R_*}\times (1-\frac{R_*}{R_{\rm inner}})},
\label{Lacc}
\end{equation}
where $M_*$ is the stellar mass, $\dot{M}$ the mass accretion rate,
$R_*$ the stellar radius and $R_{\rm inner}$ the radius of the disc inner
boundary.

The initial inner disc radius was set to be the co-rotation radius
(this is discussed in more detail in Section
\ref{disc_parameters}). During the radiative transfer simulations of
the disc the final inner dust disc radius may be extended past the
co-rotation radius. This is due to dust sublimation effects (see
Sections \ref{dust_edge} and \ref{inner_edge} for an
explanation). However, as the gas within the disc is not sublimated it
will always extend down to the co-rotation radius and we assume
accretion will still occur from this radius. A full discussion of the
differences between the initial and resulting final radii of the dust
disc can be found in Section \ref{inner_edge}. Once the accretion
luminosity was derived, an adopted areal coverage ($A$), over the
stellar surface, was used to calculate an effective temperature
($T_{\rm acc}$), for the accretion `hot' spot, where
\begin{equation}
{T_{\rm acc}=(\frac{L_{\rm acc}}{4\pi R^2_{*} \sigma \times A})^{\frac{1}{4}}}.
\label{Tacc}
\end{equation}

Finally, a blackbody flux distribution is generated at $T_{\rm acc}$
and added onto the intrinsic stellar photospheric flux. In general one
would expect this to be an overestimate of the accretion flux, as for
pre-MS BDs large convective zones are expected on the stellar surface,
and some of the accretion energy may act to further drive these
convective currents, meaning flux is lost. It is worth noting however
that observationally UV excesses are often used to recreate and then
subtract an assumed accretion flux using a blackbody flux curve,
essentially the reverse of this method.

\subsubsection{Disc parameters}
\label{disc_parameters}

In this study we assume that accretion from the central star occurs
along magnetically channelled columns from the inner disc boundary.
For TTS stars, \cite{2007prpl.conf..479B} show that the magnetic
truncation radius ($R_{\rm mag}$) is less than the co-rotation radius
($R_{\rm co}$), where the angular Keplerian velocity of the
disc is equal to the surface angular velocity of the central star.
Calculations of the magnetic truncation radius depend on derivations
of the surface magnetic field \citep{1991ApJ...370L..39K}. This is
currently unavailable for BD stars, due to increased molecular species
obscuring the Zeeman splitting signatures, that are normally used to
derive stellar surface magnetic fields. Therefore, for our model grid
we have adopted an initial inner disc radius as the co-rotation
radius,
\begin{equation}
{R_{\rm inner}=({GM_*\tau^2\over{4\pi ^2}})^{1\over{3}}},
\label{inner_eq}
\end{equation}
 where $\tau$ is the stellar rotation period and $R_{\rm inner}$ is
the inner radius. This is effectively adopting a disc-locking
mechanism (without associated angular momentum loss), as for
disc-locked stars, $R_{\rm mag}\approx R_{\rm co}$,
\citep{1991ApJ...370L..39K,1994ApJ...429..781S}. Therefore, for our
model simulations, this inner edge radius is dependent on, and derived
from, the adopted value of the rotational period for the central star,
as well as being weakly dependent on the stellar mass. As discussed in
Section \ref{intro}, the inner disc can be cleared through a number of
mechanisms, including binarity or Giant planet formation,
photoevaporation or photoionisation of the disc and dust grain growth
or settling. For BDD systems where a disc is modeled a treatment of
dust sublimation due to photoionising UV and FUV flux is included
(discussed in Section \ref{dust_edge}). However, the effects of
binarity or Giant planet formation are neglected. Further to the
stellar mass and period required prior to calculation of the inner
disc radius, we require a disc mass (in stellar masses).

For this work the disc outer edge was set at 300 AU, this was chosen
as a maximum size of the circumstellar
disc. \cite{2008A&A...486..877B} have shown that the disc outer radius
has little effect on the resulting SED. However, in our subsequent
paper we will include models for outer radii of 100 AU and plan to
extend this parameter range further to smaller values of the outer
radius in the future.

\subsubsection{naked and disc systems}
\label{naked_BDD}

The combined (accretion plus photosphere) SED is then used as a
boundary condition for the {\sc torus} radiative transfer code and
as a benchmark set of SEDs to model `naked' BD systems. The set of
`naked' photospheres (plus accretion) are diluted by the factor
$(R_*/Distance)^2$ to a distance of 10pc. The `negligibly' accreting,
`naked' stars can be used to produce absolute magnitude (and intrinsic
colour) isochrones for comparison. Whilst, the remainder are used to
model systems showing active accretion where no disc is detected. For
instance, \cite{2009arXiv0901.2603K} find 43 stars within their sample
are actively accreting whilst no disc is detected (out of a total
sample of 1253).

In summary the key required input variables to setup the model grid
are as follows. Stellar age and mass, which are used to derive the
stellar flux. Further supplemented by an accretion rate, areal
coverage and rotation period, used to generate the the accretion flux.
The inner disc radius is then derived using the rotation rate, but a
disc mass fraction must be adopted.

\subsection{Radiative transfer code: {\sc torus}}
\label{torus}

In this section we briefly explain the key elements of the radiative
transfer code used to model the BDD systems.

We have used the {\sc torus} radiative transfer code which is
described in \cite{2000MNRAS.315..722H}, including the subsequent
refinements i.e.  addition of Adaptive-Mesh-Refinement (AMR)
introduced in \cite{2004MNRAS.350..565H}. {\sc torus} uses the
criterion of \cite{1999A&A...344..282L} in a radiative equilibrium
algorithm. The simulation also calculates \textit{vertical hydrostatic
  equilibrium} and dust sublimation for the disc, similar to that
described in \cite{2007ApJ...661..374T}.

\subsubsection{Dust Size distribution}
\label{dust_size}

We have adopted a similar treatment to \cite{2002ApJ...564..887W}.
With the size distribution of dust particle given by,
\begin{equation}
\label{particle_dist}
n(a)da=C_ia^{-q}\times exp^{[-(a/a_c)^p]}da
\end{equation}.
Where $n(a)da$ is the number of particles of size $a$ (within the
increment $da$), $a_{\rm c}$ is the characteristic particle size, with $p$
and $q$ simply used to control the shape of the distribution. $C_i$
controls the relative abundance of each constituent species ($i$) in
the dust. \cite{2002ApJ...564..887W} found that simulated SEDs fit
observed SEDs better using this adjusted size distribution for the
dust particles, as opposed to a simple power law. The best fitting
values found in \cite{2002ApJ...564..887W} were $q=$3.0, $p=$0.6 with
$a_{\rm c}=$50 $\mu$m, also with an associated maximum and minimum grain size
of $a_{\rm min}=$5 nm and $a_{\rm max}=$1mm. Subsequent works have adopted a
slightly steeper power law dependence, with $q=$3.5
\citep{2008A&A...486..877B,2008ApJ...676L.143M,2008arXiv0810.2552P}.
Therefore we have adopted the values of \cite{2002ApJ...564..887W}
except for the parameter $q$ where we have used $q=$3.5.
\cite{2002ApJ...564..887W} calculated the $C_i$ values for amorphous
Carbon and silicon by requiring the dust to deplete a solar abundance
of either component completely \citep[using abundances
from][]{1989GeCoA..53..197A,1993ASPC...40..410N}. We have set $C_i=$1
and adjusted the species using a grain fractional abundance \cite[an
equivalent process to that of][]{2002ApJ...564..887W}, however we have
adjusted these grain fractions using the updated solar abundances of
\cite{2006CoAst.147...76A}. The resulting difference in opacity
between grain fractions matching the work of
\cite{2002ApJ...564..887W} and the new grain fractions is only a
slight enhancement of the silicate feature (due to the relative
abundance of Silicon increasing) which has little effect on the
resulting SEDs. Figure \ref{albedo} shows the
resulting albedo, and scattering and absorption opacities, for our
dust population, with a the vertical dashed line showing 10$\mu$m.

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/albedo.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figures of the albedo (\textit{top panel}), and scattering
   (dashed line) and absorption (solid line) opacties (\textit{bottom
     panel}) against log($\lambda$) (in $\mu$m) for our adopted dust
   population. For \textit{both panels} the vertical dashed line is
   plotted at 10$\mu$m to higlight the silicate features.
   \label{albedo}}
\end{figure}

\subsubsection{Dust sublimation and the Inner Disc Edge}
\label{dust_edge}

We have also applied dust sublimation during our simulations. This
treatment is similar to that detailed in \cite{2007ApJ...661..374T},
but improved and generalised with respect to the applicable
geometries.

The practical implementation is as follows: An initial coarse
approximate temperature structure is found for the grid without dust,
only a fixed gas distribution. Then, first three full \textit{Lucy}
algorithm iterations are run for a grid with a maximum cell opacity of
0.1 (with dust added to this level). Three more iterations are then
performed with dust opacity limited to $\tau=$1 per cell. A further
three \textit{Lucy} algorithm iterations are then performed with the
full dust opacity, where dust is added until the gas-to-dust ratio is
achieved($\epsilon =$100). For each iteration (from the first to the
ninth) dust in cells which reach the sublimation temperature and
density is removed from the disc by setting the opacity to zero for
the cell. Once these nine iterations are complete, the grid is refined
around the disc photosphere, and the radiative transfer alogrithm is
iterated through to convergence. After this first convergence, a
vertical hydrostatic equilibrium algorithm is run, after which the
disc grid is unrefined and then re-refined around the disc
photosphere. This process continues for five hydrostatic equilibrium
calculations. Finally, once the hydrostatic equilibrium iteratins are
complete we perform a final dust sublimation run to remove any cells
where the dust temperature has moved above the sublimation temperature
and further refine the photosphere and inner edge of the disc (whilst
also unrefining cells where the opacity has reduced significantly and
high resolution is no longer required). In this model the dust
sublimation is effectively digital i.e. when the density and
temperature for sublimation is reached for a given cell the dust is
destroyed. We did attempt a more realistic model where the dust
sublimation causes the dust to be destroyed at an evanescently
decaying rate into the particular region. This was expected to lead to
a more realistic situation where the dust destruction propogates into
the disc material, and does not instantly destroy an entire
cell. However, this implementation lead to incremental sections of
dust being removed after each iteration, resulting in little change in
the overall density structure of the disc. This is perhaps interesting
for real systems, in that the dust sublimation should not be expected
to act as a digital `switch'.

As our models are magnetically truncated at the co-rotation radius, we
have implicitly generated an inner hole. This also means that the disc
will have an inner wall at this radius. Evidence for inner walls in
circumstellar discs is apparent from the SEDs of disc systems, where a
peak in emission is found between 2 and 3$\mu$m. The temperatures
reached by such inner walls are expected to generate thermal flux
contributions within this wavelength range
\citep{2001ApJ...560..957D}. In fact the structure, radius and
generation mechanism of the inner wall will lead to markedly different
contributions to the SED. As discussed in Section \ref{intro} several
mechanisms can act to clear the inner disc.

Binarity and Giant planet formation would be expected to clear an
inner disc and shut down accretion from within the inner wall due to
gravitational perturbations. In addition, photoevaporation from UV and
UV flux is expected to halt accretion from radii within the inner disc
due to the removal of this material via a stellar/disc wind
\citep{2006MNRAS.369..229A}. These two clearing mechanisms could be
differentiate by the resulting masses of the discs
\citep{2007MNRAS.378..369N}.  However, for our model systems we have
neglected both of these effects.

For our models we have initially cleared the inner disc by invoking a
magnetic truncation radius, however, further disc clearing will be
caused by the dust destruction/sublimation mechanism we have included.
In some cases where the radius in the disc at which the dust
sublimation temperature and densities are reached, ($R_{\rm sub}$)
will be less than the co-rotation radius ($R_{\rm co}$). For these
cases, $R_{\rm sub}<R_{\rm co}$, the inner wall radius and shape will
be controlled by sublimation. Effectively meaning the final inner disc
radius, after the radiative transfer simulation, will not equal the
initial inner disc radius. The differences in the starting and
resulting inner wall radii and the shapes of the inner edges are
discussed in Section \ref{inner_edge}. If the inner disc is cleared
via dust sublimation one would expect a residual hot gas disc interior
to the inner wall. This is as the gas component will not be destroyed
and is free to extend to the co-rotation radius.  Evidence for a hot
gas inner disc component has been found through SED fitting by
\cite{2005ApJ...623..952E} and \cite{2008ApJ...689..513T}.  In
particular, \cite{2008ApJ...689..513T}, found that emission apparent
from within the inner wall radius could not be well fit by a modeled
spherical halo, or optically thin disc, dust component.

Furthermore, as the dust sublimation limit is temperature and density
dependent \citep{1994ApJ...421..615P}, dust sublimation can lead to
changes in shape of the inner wall. As the density of the
circumstellar disc will vary with scale height one would expect the
dust sublimation radius to vary concurrently with scale height. This
results in a curved inner wall \citep{2001A&A...371..186N}. As
explained by \cite{2007ApJ...661..374T}, the fact that near-IR
excesses of disc systems do not appear strongly dependent on
inclination indicates that the inner walls are not
vertical. \cite{2007ApJ...661..374T} also showed that grain growth and
midplane settling will lead to a curved inner wall (and a hot inner
gas disc). The curvature is caused by changes in the vertical dust
density distributions as a function of dust size, or midplane
settling. Essentially, larger grains will sink more efficiently
towards the midplane of the disc, and due to their larger surface
areas cool more efficiently. Therefore, as the scaleheight increases
the relative proportion of larger to smaller grains will reduce and
the cooling become less efficient. This will result in higher
temperatures being reached for larger scale heights at a fixed radius,
thereby curving the inner wall as the upper layers of the disc reach
the sublimation temperature at closer radii.
\cite{2007ApJ...661..374T}, modeled this effect by using two dust
distributions, a small and a large, with different vertical
distributions indicative of increased midplane settling for the larger
grains. For this study we have adopted a size distribution for one
population of dust grains, with one characteristic vertical
distribution. As such curvature of the inner wall in our simulations
will be dominated simply by the dust sublimation temperature, and
density. The resulting shapes and radial positions of the inner walls
after the radiative transfer simulations are complete are discussed in
detail in Section \ref{inner_edge}.

For our model grid we have adopted a gas-to-dust ratio, $\epsilon$, of
100, and the gas population is assumed essentially static with a zero
optical depth. Therefore, it does not contribute to the resulting SED,
and we have not included a hot inner gas disc as found by
\cite{2008ApJ...689..513T}.

\subsubsection{SEDs}
\label{seds}

Once the radiative transfer code was completed simulated SEDs were
generated. These SEDs can be generated for any distance and for any
system-observer inclination. For our models we have set the distance,
again, to 10pc to create absolute flux SEDs and selected ten
inclinations (0, 27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$). A
further useful feature of the {\sc torus} code is that the emitted
photons which make up the SED are tagged on their way to the
observer. These tags separate the photons into four groups. Firstly,
photons are separated by source into thermal (disc) or stellar groups.
These groups are then subdivided into photons which reach the observer
either directly or after scattering (for example see Figure
\ref{disc_eg_173}). The resulting SEDs are discussed in Section
\ref{seds}.

\subsection{Photometric systems and derived quantities}
\label{derived}

To allow us to investigate the effects of disc presence and accretion
luminosity on the derivation of parameters for BD stars we can first
study the produced SEDs. However, many observational studies use
non-spectroscopic data to derive the pertinent parameters. Therefore,
to examine the practical effects in the `observational plane' we have
used the SEDs to produce broadband photometric magnitudes, and
subsequently colours. Broadband magnitudes were also derived in a
large range of other filter sets not used explicitly in the analysis
within this paper. These magnitudes are available online
\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
and are briefly discussed in Appendix \ref{website}. In addition,
monochromatic fluxes have been derived for all filters, and again are
available online and discussed in Appendix \ref{website}. The
additional magnitudes and monochromatic fluxes are also discussed in
detail in the subsequent paper introducing the online fitting tool.

To derive broadband photometric magnitudes and colours the SEDs of
either the disc or naked systems were folded through the filter
responses of the required photometric system. As the fluxes in all
cases are absolute, derived for an observer to object distance of
10pc, no conversion is required to derive absolute magnitudes and
therefore intrinsic colours.

For the naked systems the flux is spherically symmetric however,
clearly, for the BDD systems different inclinations will result in
very different SEDs and therefore magnitudes and colours. Therefore,
for the BDD systems, photometric magnitudes and colours must be
derived for each inclination selected.

We have integrated using photon counting and calibrated using a Vega
spectrum for magnitudes in the optical and near-IR regimes. The filter
bandpasses selected are, the optical system of
\cite{1998A&A...333..231B} for \textit{UBVRI} and the \textit{CIT}
system of \cite{1982AJ.....87.1029E,2004PASP..116....9S} for
\textit{JHK}, with the required shift of -0.015$\mu$m as prescribed by
\cite{2004PASP..116....9S}.

We have also derived magnitudes in the mid-IR range using the IRAC and
MIPS systems of the \textit{Spitzer} space telescope. These magnitudes
were derived using a conversion of flux to Data Number (DN) and
calibrated using zero points derived from the zero magnitude fluxes
published in the IRAC handbook
\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}
and the MIPS instrument calibration website
\footnote{http://ssc.spitzer.caltech.edu/mips/calib/}.

These specific filter sets have been chosen due to their ubiquitous
use and suitability for the derivation of the key stellar parameters
of age, mass and, for populations, disc fractions. Therefore, by
studying the changes of magnitudes (and colours) in these photometric
systems we can test the predicted effects on these derived parameters
caused by changes in the input parameters of our model grid. The
optical magnitudes \textit{VI} are used to explore age related effects
of varying the parameter space. Flux in the \textit{VI} bands is only
minimally affected by accretion flux \citep{1998ASPC..154.1709G} and
disc thermal flux \citep{1998apsf.book.....H} and, additionally, in a
\textit{V, V-I} CMD, the reddening vector lies parallel to the pre-MS,
minimising any age effect of extinction uncertainty, \citep[for a full
discussion see][]{2008MNRAS.386..261M,2007MNRAS.375.1220M}. The
near-IR passbands of \textit{JHK} are most often used to derive
stellar masses as for pre-MS objects the reddening vector, in for
instance, a \textit{J, J-K} CMD, is almost perpendicular to the
isochrones, minimising the mass effect of extinction uncertainties
\citep[the \textit{CIT} systems was chosen to
match][]{2000ApJ...542..464C}. Finally, as is now well documented the
\textit{Spitzer} IRAC passbands provide the best data with which to
unambiguously separate naked and star-disc systems
\citep{2005ApJ...620L..51L}. In addition, at longer wavelengths, the
MIPS instrument provides sensitivity to disc systems at much larger
radii (or debris discs).

Once the model grid was completed several checks were performed to
verify the consistency of our results. For each individual model these
checks were passed to our satisfaction before publication. Some
problems remain, and these are explained in Appendix
\ref{consistency}.

\section{Parameter space}
\label{par_space}

This section details the range of each of the input parameters we have
varied and, where possible, gives justification for the selected
ranges from published observations. The simulations in this paper
cover variations in the stellar mass, stellar age, stellar rotation
rate, accretion rate, the areal coverage of the accretion stream, disc
mass fraction and the system inclination. In a subsequent paper we
introduce variation of the outer radius and using an analytical
vertical disc structure as oppose to vertical hydrostatic equilibrium.
.A summary of the values adopted for each input variable is shown in
Table \ref{par_space_table}.

\subsection{Mass} 
\label{par_mass}

Representative masses within the BD regime were chosen as follows:
0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 $M_{\odot}$.

\subsection{Age}
\label{par_age}

Typical disc lifetimes for solar type stars are of order $\approx$ 10
Myrs \citep{2001ApJ...553L.153H}. Therefore, we have adopted input
ages of 1 and 10 Myrs for our model grid, to span the approximate
range of ages over which discs influence will be important.

\subsection{Rotation rate}
\label{par_rotation}

Data for rotation rates, from periodic variability surveys, are widely
available for a range of different age clusters of TTS. However, fewer
studies exist on the rotation rates of BD mass objects. To select a
feasible range of periods for our model grid we have collated the
results from some recent studies of BD variability. Rotation period
data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
where periods are found over the range 5.78$-$74.4 hours ($\approx$
0.24$-$3.1 days) for BD mass objects. In some cases the periodic
variability is irregular and assumed to come from active accretion hot
spots on the BD surface \citep[see][for discussion of variability
causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
and evidence of accretion are also found to correlate with slower
rotating TTS, which the authors construe as evidence for a disc
locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
period$ relationship extending into the BD mass regime, this faster
rotation in younger mass objects is taken as evidence for a decreasing
effectiveness of the angular momentum removal of the disc locking
mechanism, i.e. imperfect disc locking. In addition,
\cite{2004A&A...419..249S} argue that when compared with data from
younger clusters disc lifetimes can be seen to decrease with central
object mass.

\cite{2005A&A...429.1007S} study rotation period data for stars in the
vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
some BD objects with irregular variability indicative of accretion hot
spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
the mass-period relationship of these data in comparison with data
from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
Ori sample has an age of around 2$-$3 Myrs or there is still
significant disc locking (concluded using the slope of the mass-period
relation). More specifically for the BD mass regime, they find
\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
lower period limit of 2$-$4 hours, therefore at any age a fraction of
BD stars rotate at short and constant period. Given that these objects
should spin up as they hydrostatically contract they invoke rotational
braking in the BD mass regime as a mechanism of removing significant
angular momentum.

\cite{2003ApJ...594..971J} study the rotational periods of BD (and
very low mass stars) in the Chameleon I region. This region is $\le$ 1
Myrs old, and the authors find rotation periods of 2.19, 3.376 and
3.21 days for their BD mass counterparts. Using supplementary data
from the literature \cite{2003ApJ...594..971J} propose that a shorter
lifetime of $\approx$5 Myrs for accretions discs around BDs is more
probable and is inferred from the derivation of a shorter locking
timescale. However, as discussed in the previous studies, an imperfect
disc locking mechanisms is also hypothesised as responsible for the
less significant loss in angular momentum out to ages of 10 Myrs. The
data mentioned above and other datasets are summarised and discussed
in \cite{2007prpl.conf..297H}, where a strong argument for the
mass-period relationship can be found, shown in their Fig 6, alongside
further support for either a shorter disc lifetime or imperfect disc
locking mechanism for BD stars.

Therefore, in summary, it is currently unclear if any disc locking
mechanisms efficiency or disc lifetimes are a function of mass, with
an associated phase change over the TTS to BD mass limit. Rotation
rate and disc presence data are being used to explore issue.
Therefore, to create a set of useful models to help contextualise the
observational constraints we must adopt a realistic, and bounding,
range of rotation rates. For our model grid, and associated age range
($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
placed at around the approximate median for the faster rotating
samples, providing a useful benchmark for exploring possible detection
limits of faster rotators with discs. The longer period is set at the
approximate edge of the slow rotating tail, providing a limiting case
for the slower rotating, disc-locked, candidates.

\subsection{Areal Coverage}
\label{par_cov}

As discussed in Section \ref{par_rotation} evidence for irregular
periodic variability has been found in BD stars with detections of
associated stellar discs. This is construed as evidence for accretion
hot spots formed as magnetically channeled material hits the stellar
surface \citep[see discussion
in][]{1995A&A...299...89B,2007prpl.conf..297H}. The irregularity is
thought to be caused by changes in the magnetospheric structure and
accretion rate \citep{1995A&A...299...89B}. For our model we have
assumed that disc material is disrupted at the co-rotation radius and
channeled onto the star in the form of accretion hot spots with a
characteristic temperature. Therefore, to calculate the characteristic
temperature and the resulting blackbody accretion flux we must adopt
an accretion rate and areal coverage of the accretion stream.

Little observational evidence can be found for approximate sizes of
accretion hot spots due to their more transient nature and often
smaller coverages, when compared to cooler or `plage' spots
\citep{2007prpl.conf..297H}. \cite{1995A&A...299...89B} modeled the
size of the cool spots on solar-type stars for a selection of
periodically variable candidates. They found projections of cooler
spots, onto the stellar disc, of a few to ~60\%.
\cite{1995A&A...299...89B} also found projected sizes, onto the
stellar disc, of typically a few \% to around 10\% for hot spots.
\cite{1996AJ....112.2159B} used observations of YY Orionis monitoring
flux amplitude variations as a function of wavelength to derive a
probable hot spot area of around 10\%. The spot temperature was also
modeled for YY Orionis in \cite{1996AJ....112.2159B}, resulting in a
best fitting areal coverage of 11\%. Therefore, to bound the probable
areal coverage range of the accretion hot spots we have adopted areal
coverages of 1 and 10\%.

\subsection{Accretion Rate}
\label{par_accn}

Accretion rates derived for pre-MS stars are of order -6 to -11
log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$ \citep{2006A&A...452..245N}.
With the largest accretion rates found in so-called FU Orionis type
objects (after the object where they were first observed). For the
more typical accretion rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9}
M_{\odot}yr^{-1}$, for TTS,][]{2009arXiv0901.4120D}, several studies
have now suggested that the accretion rate is strongly correlated with
the mass of the central star. This relationship was perhaps first
suggested by \cite{2003ApJ...592..266M} using various accretion
diagnostics. Later, \citep{2005ApJ...625..906M} derived a relationship
of approximately $\dot{M}\propto M_*^{~2}$. Further evidence was put
forward by \cite{2004A&A...424..603N}, where accretion rates as low as
5$\times$ 10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More
recently, even lower accretion rates of $\approx$10$^{-13}M_{\odot}
yr^{-1}$, have been derived for BDs by \cite{2009arXiv0901.3684H}.
Further support for a dependence of accretion rate on stellar mass was
apparent in the significantly more homogeneous dataset of
\cite{2006A&A...452..245N}. \cite{2006A&A...452..245N} analysed a set
of accretion rates and masses derived for pre-MS stars in $\rho$
Ophiuchi and compared these results to stars in Taurus. They found
that the accretion rate scales with central object mass, into the BD
regime. However, work by \cite{2006MNRAS.370L..10C} suggests that much
of this result is likely to be caused by biases and sensitivity
limits.

For any $\dot{M}\propto M_*$ relationship to be ratified, clearly, the
associated mass derivations must be shown to be accurate. For the BD
mass regime it has been demonstrated that classification, either
spectroscopic or photometric, and therefore accurate mass derivation
is exceedingly difficult for BDD systems
\citep{2004MNRAS.351..607W}. The inclusion of significant levels of
accretion flux will act to exacerbate this problem. Essentially, as BD
mass objects have relatively cool photospheres, compared to the
temperature of the accretion hotspots, meaning that for lower
accretion rates, than for their CTTS counterparsts, the accretion flux
dominates the small wavelength regime of the SED.

Therefore, to strengthen, or reject, any stellar mass to accretion
rate relationship, the limits of observational classification (and
mass derivation) of accreting BDD systems must be understood. To
provide a benchmark model grid of such systems, with which to aid
interpretation of the observational data, we must select a range of
accretion rates including and exceeding those detected for systems
previously classified as BDs.

As the relationship $\dot{M}\propto M_*^{~2}$ predicts lower accretion
rates for BD mass objects it is essential that we model systems at
higher accretion rates, which may have been missed in current
observational studies. Therefore, we have adopted accretion rates of
-6, -7, -8, -9, -10, -11 \& -12
log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$.

\subsection{Disc Mass}
\label{par_mdisc}

A further required input parameter is the mass of the circumstellar
disc. Previously studies modeling BD discs have adopted a range of
disc mass fractions, for instance \citep{2004MNRAS.351..607W} use 0.1,
0.01 and 0.001$M_*$. \cite{2002ApJ...564..887W} fit observed spectra
with modeled SEDs to derive a disc mass of 0.003$M_*$, for HH 30
IRS. Subsequent derivations of disc masses have converged to within an
order of magnitude, with the following specific results: 0.03$M_*$
\citep[$\rho$ Ophiuchi,][]{2002A&A...393..597N}, 0.055$M_*$ \citep[GM
Aurigae,][]{2003MNRAS.342...79R}, 0.03$M_*$ \citep[GY 5, GY 11, and GY
310,][]{2004ApJ...609L..33M} and 0.022$M_*$\citep[2MASS
J04442713+2512164,][]{2008A&A...486..877B}. As the derived disc masses
all have a similar order of magnitude we have adopted $M_{\rm
  disc}\approx $0.01$M_*$. As changes in disc masses are expected to
change the resulting SED less than perhaps, accretion rate for
example, we have not varied the disc mass for this study. The results
of simulations varying this parameter will be published in a future
paper.

\subsection{Inclination}
\label{par_inc}

Discs around BD stars exhibit increased flaring, due to the reduced
surface gravity in the disc \citep{2004MNRAS.351..607W}. This
increased flaring, and therefore larger scaleheight of the disc
results in a smaller opening angle, when compared to higher mass stars
and their circumstellar discs. As has been shown in
\cite{2004MNRAS.351..607W} effects caused by variations in the system
inclination angle are much more significant for BDD systems, again
compared to their higher mass analogues. Therefore, we have simulated
ten observer to system inclination angles spaced evenly in
$cos(inclination)$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
and 90$^{\circ}$.

A final list of all varied parameters and their values can be seen
in Table \ref{par_space_table}.

\begin{table*}
\begin{tabular}{|l|l|}
Input parameter&Values (\# values)\\
\hline
Mass ($M_{\odot}$)&0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 (8)\\
Age (Myr)&1 \& 10 (2)\\
Rotation period (days)&0.5 \& 5 (2)\\
Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&-6, -7, -8, -9, -10,
-11 \& -12 (7)\\
Disc mass ($M_*$)&0.01 (1)\\
Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
(10)\\
\end{tabular}
\caption{List of all varied input parameters. Resulting in a total
  number of models of 448 (plus 40 models without radiative transfer
  simulations for the naked BDs) and 4480 SEDs (plus 40 for naked
  BDs). \label{par_space_table}}
\end{table*}

GOT HERE NEEDS ALOT OF RE-READING FROM HERE ON IN**

\section{Result and Analysis}
\label{results}

Uncertainty remains over the formation mechanisms, resulting IMFs and
subsequent interaction mechanisms with associated circumstellar disc,
for BDs. Furthermore, no current theoretical explanation can be
demonstrated for the suspected stellar mass-accretion rate
relationship \citep[$\dot{M}\propto
M_*^2$,][]{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}
derived from observations. In addition doubt remains over the
existence of a disc-locking mechanism in BDD systems, with predictions
of a correlation of rotation rate with infrared excess possibly
providing an intrinsic bias \citep{1997AJ....114..288M}. Theoretical
models are built upon constraints, such as ages, masses and disc
fractions, and correlations, such as the accretion rate to stellar
mass relation and rotation rate to period relation (disc-locking),
derived from the data. Critically, these resulting constraints and
relationships involve both the application of existing models, such as
isochrones to derive ages, and the selection of bias-minimised
samples, for instance removal of foreground or background contaminant
stars. Clearly, if one is to adopt a new theoretical model or use an
observed correlation as a constraint one must explore the suspected
intrinsic biases and the reliability of the selection criteria.

For our model grid we have selected a range of input parameters
covering expected, from observations, ranges. We have input the
fundamental parameters of age and mass by adoption of a set of
theoretical isochrones. We have intrinsically included a correlation
of rotation rate with initial inner edge position by setting this at
the co-rotation radius, which is expected to result in a correlation
of rotation rate with IR excess \citep{1997AJ....114..288M} (the
reverese of that expected due to angular momentum loss through
disc-locking). We have not assumed a relationship between accretion
rate and stellar mass for our model grid. Therefore, analysis of our
model grid in an attempt to recover the fundamental parameters of age
and mass, and show accretion rate to stellar mass or rotation rate to
infrared excess relationships, will allow us to assess the reliability
of these current theoretical models or relationships.

In this Section we first discuss the physical structure, both density
and temperature, of the BDD disc systems (Section \ref{disc_struct}
across our parameter space. Then we discuss the resulting simulated
SEDs for these BDD systems (Section \ref{sed_analysis}). Finally, we
produce simulated photometric observations (Section
\ref{photometry}). These simulated observations allows us to show that
recovery of the input masses and ages for our accreting BDD systems is
unreliable. We show that despite and intrinsic relationship between
rotation rate and initial inner edge position we do not recover a
rotation rate correlation with IR excess. In addition, despite not
intrinsically including a dependence of accretion rate on stellar mass
in our grid. We show that current observational techniques and
theoretical models applied to the grid would result in a relationship
of this type being derived.

\subsection{Disc Structure}
\label{disc_struct}

The initial density structure in our BDD systems is setup as described
in \cite{2004MNRAS.351..607W} with the the disc surface density
conserved, $\Sigma ^{\beta - \alpha}$. The intial scaleheight,
$h\propto r^{\beta}$, where r is the radial distance from the star,
and the density, $\rho \propto r^{-\alpha}$. The initial values of
$\alpha$ and $\beta$ where 2.1 and 1.1 respectively \citep[see][for
full discussion of disc structure]{2004MNRAS.351..607W}. The values
for $\alpha$ and $\beta$ where chosen to optimise resolution of the
vertically evolving disc, but minor variations are largely
inconsequential as the systems evolves from this state. In our models
we have, however, placed in the inner disc edge at the co-rotation
radius, as opposed to the dust destruction radius used in
\cite{2004MNRAS.351..607W}. The initial disc scaleheight at 100 AU,
$h(100)$, was set to 25 AU. As the simulation used vertical
hydrostatic equilibrium and dust sublimation, both the disc
scaleheight and inner edge location then evolved in the systems
dependent on the input parameters. I this section we discuss the
structure of the discs in terms of these two generated
characteristics, i.e the disc scaleheight and inner edge location.

\subsubsection{Disc Flaring}
\label{disc_flaring}

As discussed in \cite{2004MNRAS.351..607W} the scaleheights of discs
around CTTS stars have scaleheights at 100 AU of between $h$(100)$=$7
to 20 AU, whereas for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and
0.01 $M_{\odot}$ respectively). Our models adopt the same formalism
for solving hydrostatic equilibirum and therefore, at negligible
accreion rates, our disc scaleheights are comparable (**). As the
accretion rate increases the flux levels of the central star increase
and lead to heating of the disc. This in turn leads to vertical
expansion in the disc. For our models we found that levels of vertical
flaring increased marginally with accretion rate. Significant
differences, more than $>$5 AU increase in $h(50)$, in the vertical
structure where not apparent until the high accretion rates of -7 and
-6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. Figures \ref{flare_-12_183}
and \ref{flare_-7_193} show the density structure ($log({\rho})$) in
the disc from radial distances of 0 to 50 AU for an example systems
($M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5 and areal coverage=10\%),
at accretion rates of -12 and -7
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively.

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/flare_-12_183.ps"
   hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
 \caption{Figure showing the density structure ($log({\rho}$) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
   coverage=10\% and accretion rate of -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
   \label{flare_-12_183}}
\end{figure}

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/flare_-7_193.ps"
  hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
\caption{Figure showing the density structure ($log({\rho}$) of the
  BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
  coverage=10\% and accretion rate of -7
  log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
   \label{flare_-7_193}}
\end{figure}

Figure \ref{flare_-12_183} shows that for a typical BDD system the
resulting disc is highly flared and therefore, the opening angle for
stellar radiation is much smaller. As discussed the flaring for BDD
systems was found to be larger than CTTS systems by
\cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
degree of disc flaring depends on the disc temperature structure and
the mass of the central star, with the disc scaleheight $h\propto
\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{1973A&A....24..337S}. Recently,
\cite{2009arXiv0901.4445E} suggest the inverse relation of flaring
with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
evidence from \cite{2006ApJ...644..364A}, where SEDs for 17 systems in
the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with
flared or flat disc models. In general, \cite{2006ApJ...644..364A}
find that lower mass objects achieve better fits with the flat disc
models and higher mass objects with the flared discs.

The results of \cite{2006ApJ...644..364A} show that above a mass of
50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
discs. Whilst at masses below 50$M_{\rm Jup}$ only one object is better
fit by the flared disc model, with the remaining objects (10/17)
better fit with flat models. Whether, this result is statistically
significant enough to assert a $h\propto M_*$ is doubtful as the
fitting process contains, presumably two fixed scaleheight
distributions. Therefore, for our study we continue to assume that our
flared BDD systems will have larger characteristic scaleheights than
typical CTTS systems.

A quick comparison of Figures \ref{flare_-12_183} and
\ref{flare_-7_193} show an increase in the scaleheight at 50 AU of
$>$5 AU, as the accretion rate moves from -12 to -7
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. However, despite this small
change with high levels of accretion our grid shows scaleheights
comparable to the work of \cite{2004MNRAS.351..607W} and as such
result in similar consequences for the SEDs and photometric
magnitudes. The effects of this flaring and the increase in flaring
for very high accretion levels on SEDs and photometric magnitudes are
discussed in Sections \ref{sed_analysis} and \ref{photometry},
respectively.

\subsubsection{Inner Edge}
\label{inner_edge}

Our models include a sophisticated treatment of dust sublimation
(described in Section \ref{dust_edge}. In contrast to the models of
\cite{2004MNRAS.351..607W}, who apply a dust destruction radius, we
set the intial inner radius of the disc at the co-rotation radius of
the system. However, as our models then sublimate dust during the
temperature convergence routine this inner edge location may
change. As the flux levels of the central star increase with
increasing accretion rates the flux incident on the inner edge
increases and leads to increasing erosion of the inner edge of the
dust disc.

As the inner edge moves its  temperature is expected  to change, this
has been predicted to lead to a correlation of inner edge position and
IR excess  \citep{1997AJ....114..288M}. This  may act to  bias surveys
correlating rotation  rates with IR  excess to search for  evidence of
disc-locking. However, the flux from  the inner edge will usually peak
between 2 and 3$\mu$m \citep{2001ApJ...560..957D}, given that the dust
sublimation   temperature  peaks   at  $\approx$1400K   for  canonical
densities. This means that for  models where dust is sublimated at the
inner edge  will have maximum temperatures of  $\approx$1400K and this
correlation of disc position and temperature will be lost.

Equation \ref{inner_eq} shows that as the rotation period, of the
star, increases the co-rotation radius decreases. This will result in,
initially, shorter period systems having closer and hotter inner edges
than their longer period counterparts. In addition, if the accretion
rate is increased in these systems the incident flux on the inner wall
will increase leading to a rise in the temperature of the inner
edge. At some point, in both cases the dust sublimation temperature
may be reached, leading to a change in radial position of the wall. In
addition, the temperature of the inner edge will then tend to a
maximum temperature, of the dust sublimation temperature. Figure
\ref{lum_sub} shows the total stellar luminosity (accretion luminosity
plus the intrinsic stellar luminosity), in log($L_*/L_{\odot}$)
against the change in inner disc location, $R_{\rm co}-R_{\rm inner}$
in AU (\textit{top panel}) and $R_*$ \textit{bottom panel}. Ths change
in inner edge location is from the initially set co-rotation radius to
the final radius after dust sublimation, if applicable.

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/lum_sub.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figure showing the combined stellar luminosity (accretion
   plust intrinsic stellar luminosity) in units of
   log($L_*/L_{\odot}$) against the change in inner edge location
   shown in units of AU (\textit{top panel}) and $R_*$ (\textit{bottom
     panel}).
   \label{lum_sub}}
\end{figure}

The \textit{top panel} of Figure \ref{lum_sub} shows that as the
luminosty increases the total change in the inner radius increases as
more of the disc is sublimated. The total change for lower
luminosities at lower than ~0.2 log($L_*/L_{\odot}$) is small (less
than ~0.02 AU). As the luminosities increases to larger, and extreme
values, due to increasing accretion, the dust sublimation
increases. In the \textit{bottom panel} the change in inner radius
tends towards around ~120 $R_*$. Increases in accretion rate, for
extreme accretors, dominates the increase in stellar luminosity. As
pre-MS stars age they contract. Therefore, for lower accretion rates,
younger, and therefore larger stars will have greater luminosities
than the equivalent older stars. Therefore, the major contributors to
the X-axis of Figure \ref{lum_sub} are controlled by the input
parameters of accretion rate and age. The initial inner wall radius
was set as the magnetic co-rotation radius (see Section
\ref{physics}). This distance is a strong function of rotational
period, with $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
\ref{inner_eq}) which is in turn a function of stellar radius. The
stellar radius itself is then a function of the stellar
age. Therefore, the initial inner wall edge position will change as a
function of the input variables of rotational period and age. The
initial position of the inner edge will control the amount of the
stellar flux intercepted by the inner edge wall. Therefore the amount
that the disc will be sublimated will also be a function of the
initial position of the inner edge.

Figure \ref{delta_radius} shows the initial inner edge position, or
the co-rotation radius ($R_*$) against the change in inner edge
location ( $R_{\rm inner}-R_{\rm co}$, $R_*$). The \textit{panels} of
Figure \ref{delta_radius} then shows these data for two accretion
levels and at the two ages and rotation periods. These input variables
for our model grid are the underlying variables controlling, as
discussed, the dust sublimation process. The \textit{top panels} are
for models with accretion rates of -9, -10, -11 and -12
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, classed as typical accretors
here and throughout the rest of this work. The typical accretors are
then separated further into three groups in the \textit{top left
  panel} specifically, -9, -10 and -11 \& -12
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (blue, red and black dots
respectively). The \textit{bottom panels} show the data for models with
accretion rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
(blue, red and black dots respectively), which we have classed as
extreme accretors. The \textit{right panels} show the data seperated
by age, with 1 and 10 Myrs (as crosses and triangles respectively),
and rotation period, with 0.5 and 5 days (as red and blue symbols
respectively).

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/delta_radius.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figure showing data for the co-rotation radius ($R_{\rm
     co}$) against the change in inner edge location ( $R_{\rm
     inner}-R_{\rm co}$) both in units of $R_*$. The typical accretors
   are shown in the \textit{top panels} and the extreme accretors in
   the \textit{bottom panels} (see text for explanation). The
   accretion rates are then further subdivided. The \textit{top left
     panel} shows accretion rates of -9, -10 and -11 \& -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, red and black dots
   respectively. In the \textit{bottom left panel} accretion rates of
   -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as
   blue, red, and black dots. In addition the \textit{left panels}
   seperates the systems by age and period. The systems with ages of 1
   and 10 Myrs are shown as crosses and triangles respectively. The
   systems with rotation rates of 0.5 and 5 days are then shown as red
   or blue symbols respectively. \label{delta_radius}}
\end{figure}

The classification of models into typical and extreme accretors is
based on observations (see discussion in \ref{par_accn}) and also
evidence from the simulations themselves. Figure \ref{delta_radius},
\textit{left panels}, shows that dust sublimation does not become
significant until accretion rates of around -9
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and increases dramatically with
increasing accretion rate thereafter.  This accretion rate, -9
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, is also, unsurprisingly the
accretion rate at which the underlying photospheric emission is
overwhelmed by the accretion flux, and the photospheric features are
lost (see Section \ref{sed_analysis}). The \textit{right panels} of
Figure \ref{delta_radius} show that dust sublimation occurs only for
rotation periods of 0.5 days for typical accretors. For the extreme
accretors the systems with both rotation periods undergo sublimation
but the effect is more significant in the systems with shorter
rotation periods.  The \textit{right panels} also show that for
extreme accretors the older systems undergo more dust sublimation,
whereas for the typical accretors the older systems undergo little or
no dust sublimation.

The density of material in the disc falls with increasing radius from
the star ($\rho\propto R_*^{\alpha}$). The dust sublimation
temperature is also density dependent
\citep{1994ApJ...421..615P}. Therefore, for systems where the inner
edge has been eroded significantly from the co-rotation radius the
temperature of the inner edge will fall as the final radius
increases. In this case a correlation of inner edge temperature and
inner edge radius is expected with a resulting slope determined, at
least in part, by the radial density distribution of the disc. In this
case the the final inner edge radius and therefore temperature is no
longer strongly correlated with the rotation rate. Figure
\ref{inner_temp} shows the final inner edge location ($R_{\rm inner}$,
($R_*$) against the Temperature of the inner wall ($T_{\rm inner}$,
(K)). The \textit{left panel} shows the systems designated as typical
accretors and the \textit{right panel} those with extreme accretion
rates. For \textit{both panels} the systems with rotation periods of
0.5 and 5 days are plotted in read and blue respectively. Those
systems where the change in inner radius was greater than 1$R_*$, and
therefore classes as significantly sublimated, are plotted as
crosses. These systems are only present for the extreme accretors, as
shown in Figure \ref{delta_radius}. Furthermore, for the typical
accretors Figure \ref{delta_radius} shows that only the shorter period
objects, in general, experience any disc erosion at the inner
edge.

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/inner_temp.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figure showing data for the inner edge location ($R_{\rm
     inner}$, $R_*$). The typical accretors are shown in the
   \textit{left panel} and the extreme accretors in the \textit{right
     panel} (see text for explanation). In \textit{both panels}
   seperate the systems by period, with those systems with rotation
   periods of 0.5 and 5 days shown as red and blue symbols
   respectively. In addition systems where the total change in the
   inner radius is greater than 1$R_*$ are marked as crosses (this is
   only achieved by some systems classed as extreme
   accretors).\label{inner_temp}}
\end{figure}

Figure \ref{inner_temp} shows that for those systems where signifcant
disc erosion ($\Delta R_{\rm inner} > 1.0 R_*$) has occured the
resulting temperature of the inner edge is weakly correlated with the
inner edge radius, but, critically, not correlated with rotation
rate. The inner edge temperatures of the remaining systems for the
extreme accretors are slightly anti-correlated with the radius to the
inner edge. For the systems with typical acccretion rates, and longer
periods, Figure \ref{inner_temp} shows there is a again a weak
correlation between the radius to, and the temperature of the inner
edge. For the shorter period models with typical accretion rates ther
is no clear correlation between the temperature at the inner edge and
radius to this edge. The \textit{left panel} of Figure
\ref{inner_temp} shows that, taken as a whole, our models with typical
accretion rates show a clear correlation between the temperature at
the inner edge and the radius to this boundary. This agrees with the
work of \cite{1997AJ....114..288M} where this correlation is found for
there $R_{\rm inner}=$1$-$12$R_*$ and $\dot{M_{\rm acc}}=$10$^{-9}$to
10$^{-5} M_{\odot}yr^{-1}$, for flat disc
models. \cite{1997AJ....114..288M} use correlation, and the derivation
of IR magnitudes, to predict a relationship between IR excess and
radius to the inner wall. Our data indicate that this correlation, for
typically accreting systems will translate into a correlation between
rotation rate and IR excess. This could have important implications
for studies of disc-locking where disc presence is examined as a
function of rotation rates, provide an intrinsic bias. In practice
however, this correlation is weak, if observable, in our data due to
inner disc wall shape, inclination and flaring effcts. This is
discussed in more detail in Section \ref{photometry} **.

For simulations without dust sublimation, and analytic density
distributions, the inner disc edge is characterised solely by the
intial disc density prescription. If one includes vertical hydrostatic
equilibrium the scaleheight of the disc inner edge can change but the
radial distribution of dust will not. Dust sublimation physics will
alter the vertical structure, but crucially will also alter the radial
distribution of dust. This means that dust sublimation effects will
control the shape of the inner disc wall and possibly change this from
a vertical wall.  Evidence that real inner disc boundaries (for CTTS)
are not vertical walls comes from a lack of dependence of the derived
IR excess on system inclination \citep{2007ApJ...661..374T}. As
discussed in Section \ref{dust_edge} the disc inner hole can be
created by several mechanisms, however, for this study we have only
included a treatment of magnetic truncation (initially) and subsequent
dust sublimation. The effects of dust sublimation have been shown to
produce curved inner walls due to the temperature and density
dependence of the dust sublimation temperature
\citep{2005A&A...438..899I}. The curved boundary in this case is
concave, as density increases towards the midplane of the disc, the
dust sublimation temperature increases, meaning the destruction radius
moves closer to the star. A curved inner boundary is also found to
result from dust sublimation in \cite{2007ApJ...661..374T}. In
\cite{2007ApJ...661..374T} two populations of dust grains where
included with different scaleheight distributions. This is essentially
a simple model of grain growth and subsequent midplane
settling. \cite{2007ApJ...661..374T}, found a convex inner disc
boundary, this is due to the larger grains cooling more
efficiently. These larger grains dominate the dust towards smaller
vertical distances from the midplane, and therefore the increased
cooling means that the dust sublimation temperature is reached at
closer radii. The implications of the inner edge shape for the
simulated SEDs and photometry are discussed in Section
\ref{sed_analysis} and \ref{photometry}.

For systems where dust sublimation does not occur, or is minimal the
inner edge of the system will remain as a vertical wall, as perscribed
by our initial density distribution. However, as one increases the
flux levels of a given system, by increasing the accretion rates (or
moving to younger ages) the inner edge will increase in
temperature. As the flux levels increase, in a given model, the dust
at the inner edge will sublimate. The dust in the regions of lowest
density or maximum flux interception will be preferentially
destroyed. This will lead to a reduction in the scaleheight and a
slight concave cavity at the inner wall. The inner edge will then move
towards a convex boundary as the inner edge is forced radially outward
towards regions of lower density with increasing flux levels. This
outward movement will result in the outer, vertical, regions of the
dust disc eroding. Increasing the flux still further will lead to
significant dust sublimation and an outward migration. This subsequent
migration will move the inner edge into regions of lower density and
greater scaleheight.

The transition in shape and position of the inner edge for a given
model as the accretion rate, and therefore flux levels, are increased
is shown in Figures \ref{no_sub_183} to \ref{sub_181}. The model
chosen for illustrative purposes has the following parameters,
$M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%. The model
shown in Figure \ref{no_sub_183} has $\tau$=5 days and accretion
rate=-12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (model shown in Figure
\ref{flare_-12_183}), with Figures \ref{sub_169} to \ref{sub_181}
showing models with $\tau$=0.5 days and accretion rates=-12, -9, -7
and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. The \textit{right
  panels} of Figures \ref{no_sub_183} to \ref{sub_181} show the
temperature structure of the final converged disc structure. The
\textit{left panels} of Figures \ref{no_sub_183} to \ref{sub_181} show
the final log($\rho$) distribution for regions where dust is present,
scaled to a different minimum density (log($\rho_{\rm min}=1^{-13}$)
compared to Figures \ref{flare_-12_183} and \ref{flare_-7_193}. The
lower (log) density threshold is used in this case to better trace the
inner edge and denser regions of the disc, whereas Figure
\ref{flare_-12_183} and \ref{flare_-7_193} show the outer diffuse
regions of the disc, or disc limits. Additionally, for Figures
\ref{sub_169} to \ref{sub_181} (the sublimated systems), the
\textit{right panels} also show the initial density, in the same units
as the final density, this is shown as a background grey scale (with
the same maximum and minimum as for the final density) to illustrate
the effects of sublimation.

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
  \caption{Figure showing final density (log($\rho$)) where dust is
    present (colour scale) as the \textit{left panel} and temperature,
    \textit{right panel}, for a system with no dust
    sublimation. System parameters are: $M_*$=0.04$M_{\odot}$, Age=1
    Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate=-12
    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
  \label{no_sub_183}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_169_density.ps}\label{sub_169_a}}
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_169_temp.ps}\label{sub_169_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate=-12
    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
  \label{sub_169}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_175_density.ps}\label{sub_175_a}}
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_175_temp.ps}\label{sub_175_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate=-9
    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
  \label{sub_175}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate=-7
    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
  \label{sub_179}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate=-6
    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
  \label{sub_181}
\end{figure*}

Figure \ref{no_sub_183} shows the inner disc edge as a vertical wall
with no dust sublimation, the inner wall has not changed location from
the initial disc description. The \textit{right panel} of Figure
\ref{no_sub_183} shows that the corresponding temperature structure is
smooth and interpolation at the inner edge yields a temperature of
~900K. For the shorter period model the inner edge has undergone some
dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
shows that the inner edge has lost dust slightly, peferentially, along
the midplane. Again for Figure \ref{sub_169} the change in inner edge
location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
sublimation (and inner wall) temperature is ~1450K, for a density of
~$2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
\ref{sub_169}).The \textit{left panel} of Figure \ref{sub_169} shows
that for even for a negligible accretion rate of -12
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, sublimation has begun to erode
the inner edge, for the younger and faster rotating systems. Here the
final density distribution has moved radially outward as can be seen
by comparing the grey and colour scales in the \textit{left panel} of
Figure \ref{sub_169}. Additionally, the inner edge has become slightly
concave. As the flux levels of the central star increase the
temperature of the inner edge surpasses the sublimation temperature at
an increasing radius, destroying more of the disc an pushing the inner
edge radially outwards. The \textit{left panel} of Figure
\ref{sub_175} shows that for an accretion rate of -9
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, increased sublimation has
pushed the inner wall slightly farther from the star (wehn compared to
Figure \ref{sub_169}), here, $\Delta R~0.52R_*$ ($~1.1\times
10^{-3}$AU), and $T_{\rm inner}~1450$. Again the final density
distribution has moved radially outward as can be seen by comparing
the grey and colour scales in the \textit{left panel} of Figure
\ref{sub_175}. The \textit{right panel} of Figure \ref{sub_175} shows
that the gas interior to the inner edge extending down to the
co-rotation radius, which is not sublimated, will reach temperatures
in excess, or equal to, the inner edge, which in this model is
~1400K. Such hot gas inner discs interior to the dust disc have been
postulated through SED fitting
\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Again, the shape of
the inner wall has changed in Figure \ref{sub_175}, the top and bottom
sections of the disc have eroded and the inner wall is convex. The
model in Figure \ref{sub_175} has an accretion rate of -9
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, which is the transition point
between our two groups of accretors, typical and extreme. Figure
\ref{sub_175} shows that for typical accretion rates, and faster
rotation periods (and younger ages) signicant dust sublimation is
expected to occur at the inner edge, resulting in a curved inner wall
at around ~1400K. Increasing the accretion rate, and therefore flux
levels, still further leads to significant erosion of the inner disc.
For the extreme accretors the dust sublimation at the inner edge now
changes the inner wall position by many multiples of the stellar
radius. Figures \ref{sub_179} and \ref{sub_181} are for systems with
accretion rates typical in outburst or episodic accretion systems, -7
and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ respectively. The inner
edges for these sytems are eroded radially by 7.1 and 36.1 ($R_*$)
respectively (0.016 and 0.080 AU, respectively), visible by comparing
the grey and colour scales of Figure \ref{sub_179} and
\ref{sub_181}. As this occurs the disc inner edge moves far enough
that the density drop (with radius) occuring in the disc causing the
sublimation temperature to fall. Consequently the disc inner edge
becomes cooler as it can not sustain temperatures above the
sublimation temperature. This is shown in the \textit{right panels} of
Figures \ref{sub_179} and \ref{sub_181}, with approximate temperatures
at the inner edge of 1370 and 1260K. In addition, the inner edge has
become concave and, again due to changes in the underlying disc
density distribution, much larger in scaleheight.

A similar sequence is apparent across the grid for set
masses. However, the balance of the rotation period, and therefore
inner edge location, and age and areal coverage, therefore flux
levels, leads to changes in the accretion rate at which the dust
sublimation starts. However, in almost all cases the dust sublimation
does not become significant until at least -9
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as discussed above).

\subsection{SEDs}
\label{sed_analysis}

The resulting converged disc structures, as discussed in Section
\ref{seds} are then used to create simulated SEDs. In this section we
explore features in these derived SEDs and link them back to the
physical structures within the disc discussed in Section
\ref{disc_struct}. For analysis purposes our SEDs will comprise
contributions from four main luminosity sources. Firstly, the
accretion luminosity ($L_{\rm acc}$) and the intrinsic stellar
luminosity ($L_{*}$), will effectively be combined and provide flux at
the shorter wavelength section of the SED. For our parameter space the
temperature of the photospheres has a range of ~3000K$<T_{\rm
  eff}$1600K, this will comprise flux contributions peaking in the
range, 0.97 to 1.8 $\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
    acc}}$). The accretion spot temperatures, for typical accretors,
will range from ~340$>T_{\rm acc}>$9400K, emitting in the range 0.3 to
8.5 $\mu$m. For the extreme accretors temperatures can reach as high
as 53,000K, provide flux to $~$0.05 $\mu$m. The second pair of
luminosity sources are from consituent parts of the circumstellar
disc. The inner edge, ($L_{\rm wall}$), at temperatures of ~370 to
~1500K, or flux contributions from ~1.85 to 7.7 $\mu$m
\citep[nominally 2 to 3 $\mu$m][]{2001ApJ...560..957D}, and the outer
disc ($L_{\rm disc}$), at temperatures of ~300K or less contributing
flux longward of ~10 $\mu$m. As discussed in Section \ref{seds} the
{\sc torus} radiative transfer code tags the photons before they
reach the simulated observe in one of four ways, stellar and thermal,
either direct or scattered. These components allow us to analyses the
contributions from the main flux contributors discussed, i.e. $L_{\rm
  acc}$ and $L_*$ equals stellar scattered or direct, with thermal
emission comprising $L_{\rm wall}$ and $L_{\rm disc}$. Figure
\ref{disc_eg_173} shows a typically accreting BDD system with the
component photon contributions highlighted, with $M_*=0.04M_{\odot}$
at 1 Myr with an areal coverage of 10\%, accretion rate of -10
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
days. The solid black line is the total simulated SED, with the
stellar photons shown as blue lines and the thermal as red. The
scattered and direct contributions are then shown as dashed and solid
lines respecitvely. The horizontal and vertical dotted lines then show
the approximate ranges of the flux contributions from the (from left
to right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red)
and $L_{\rm disc}$ (black).

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/disc_eg_173.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figure showing the SED (log($\lambda \mu$m against
   log(flux), flux in ergs$/s/cm^2/\AA$) for $M_*=0.04M_{\odot}$ at 1
   Myr with an areal coverage of 10\%, accretion rate of -10
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
   days. The solid black line is the total simulated SED. The stellar
   components of the flux are shown in blue and the thermal in read,
   with direct emission appearing as solid lines and scattered photons
   as dashed lines. The vertical dotted bars linked by horizontal bars
   show the approximate (log) wavelength ranges of the luminosity
   components. With the blue lines denoting the accretion luminosity
   ($L_{\rm acc}$) and the first (left to right) black lines showing
   the photospheric contribution ($L_*$). The final two sets of lines
   show the inner edge contribution ($L_{\rm wall}$) in red and the
   outer disc ($L_{\rm disc}$) in black. \label{disc_eg_173}}
\end{figure}

Figure \ref{disc_eg_173} shows that the photosphere and accretion
luminosities dominate the SED at wavelengths shortward of
~1$\mu$m. After this, for this model, the SED is dominated by
contributions from the disc, at shorter wavelengths, the inner edge
and then at larger wavelengths the outer disc. As shown in Figure
\ref{disc_eg_173} the intrinsic stellar photosphere and accretion
luminosities overlap, in terms of peak wavelength of emission. This
overlap essentially means that the combined stellar flux ($L_*+L_{\rm
  acc}$) will eventually become dominated by the accretion flux, as
one increases the accretion rate. With the features of the intrinsic
stellar photosphere or atmosphere eventually lost or swamped by the
accretion flux. This will lead to difficulties in using spectral
features to identify BDD systems for wavelengths shorter than ~1
$\mu$m, and, of course, for wavelengths longer than this the SED
becomes dominated by disc emission. Therefore, once the SED of a BDD
system, at shorter wavelengths, becomes dominated by accretion
luminosity spectral classification of these systems (or at least their
central stars) will become unreliable. As discussed in Section
\ref{inner_edge} observations of the inner edge location seperate the
BDD systems into two groups, the typical accretors ($\dot{M}\leq$-9
log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$) and extreme accretors
($\dot{M}>$-9 log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$). This division
between typical and extreme accretors is based on observational
results (see Section \ref{par_accn}) as well as consequence of
sublimation. The typical accretors show limited sublimation at the
disc inner edge leading to a weak correlation in inner edge
temperature with edge radius. Whereas, for the extreme accretors the
inner edge is significantly eroded and the dust sublimation
temperature reached, which can not be exceeded. This effectively means
that the inner edge temperature is weakly correlated with temperature
(with a different characteristic slope to the typical accretors), as
the dust sublimation temperature is density dependent, which is in
turn dependent on radial position (see Figures \ref{delta_radius} and
\ref{inner_temp}).

\subsubsection{Accretion Dominance}
\label{acc_dominance}

Figure \ref{acc_dom} shows the affect of the increasing accretion
blackbody flux (for increasing accretion rates) for a BD star,
$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photons originating from the
star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
{\sc torus} we can seperate these flux contributions simply by
observing the naked star system. The panels in Figure \ref{acc_dom}
show the flux from a naked system, with no treatment of the disc. This
enables us to view the effect of increasing accretion rate on the
photospheric flux in isolation. The accretion rates included in all
panels are -8, -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
(blue, black and red lines respectively). The \textit{bottom panels}
show the systems with a rotation period of 5 days and \textit{top
  panels} for those with a rotation period of 0.5 days. Given our
assumption that accretion occurs from the co-rotation radius,
decreasing the rotational period moves this accretion radius closer to
the star, $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
\ref{inner_eq}). As the accretion radius moves father from the star the
potential energy released by the accreted material is reduced. This
effect can be seen when comparing the \textit{top} and \textit{bottom
  panels}, although the effect is marginal for all but the highest
displayed accretion rates. The \textit{left panels} show accretion
streams with an areal coverage of 10\% and the \textit{left panels}
1\%. As the areal coverage reduces the effective temperature of the
accretion hot spot increases, resulting in an increase in accretion
flux, and resulting shift to bluer wavelengths of the peak flux. This
can be seen clearly by comparing the \textit{left} and \textit{right
  panels} of Figure \ref{acc_dom}. Perhaps the most important, albeit
qualitative, result shown is Figure \ref{acc_dom} is an insight into
the accretion rate at which the accretion blackbody flux dominates
over the photospheric flux. Figure \ref{acc_dom} shows that as the
accretion rate raises above -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
for systems with 1 or 10\% areal coverage, the accretion flux
dominates the emergent SED at both periods. Therefore for reasonable
coverages (1-10\%) and rotational periods (0.5-5 days) the
photospheric flux is effectively swamped by accretion flux for
accretion rates log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-9$. This
suggests that accreting BD systems with accretion rates as low as -9
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ could be difficult to identify
from SEDs as BD stars, and may well be classified as higher mass
stars.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/acc_dom.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the photospheric flux
   (log(ergs$/s/cm^2/\AA$)) against $\lambda$ (log($\mu$m)) of a Brown
   Dwarf with $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but
   blackbody fluxes from an accretion stream at the rates of -8, -9
   and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as blue,
   black and red lines respectively. The \textit{bottom panels} show
   accretion for a star rotating at 5 days, with the \textit{top
     panels} showing that of 0.5 days. The \textit{left panels} systems
   with an areal coverage of 10\% and the \textit{right panels} has
   1\%.
   \label{acc_dom}}
\end{figure*}

Therefore, the shorter wavelength component of the SED for extreme
accretors is dominated by the accretion luminosity. For the typical
accretors the intrinsic photospheric emission is important and the
flux levels of this component are dependent on the stellar parameters
of mass and age, through evolution of the stellar radius and
temperature, as is well understood. In general, the bluer (short
wavelength) components of the SEDs are therefore contrOlled by the
stellar input parameters (mass and age) and the accretion input
parameters (accretion rate and areal coverage, and to a lesser extent
rotation rate).

\subsubsection{Flaring and Obscuration}
\label{flare_obscure}

As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
discussed in Section \ref{disc_flaring} BDD systems under vertical
hydrostatic equilibirum have highly flared discs. As discussed in
\cite{2004MNRAS.351..607W} this increased flaring (when compared to
CTTS stars) leads to occulltation at the star at lower inclination
angles and, therefore, significant changes to the SED. Increases in
the inclination angle, for these systems, quickly lead a significant
proportion of the stellar flux being intercepted, and reprocessed, by
the highly flared disc. This reprossecing will lead to a change in the
flux levels at the shorter, bluer, wavelengths as more stellar flux is
reprocessed and intercepted by the disc. It will also lead to
significant changes in the flux reaching the observer from the inner
and outer regions of the disc.

Figure \ref{flare_sed_fast} shows the SEDs for a range of inclinations
for BDD systems with two accretion rates. The BDD system has a central
stellar mass of $0.04M_{\odot}$, an age of 1Myr, a rotation period of
0.5 days and an areal coverage of the accretion stream of 10\%. The
\textit{top panels} show the SEDs for a star with an accretion rate of
-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (the lowest in our typical
accretion range). The \textit{bottom panels} then show SEDs for
systems with an accretion rate of -8
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (classed as an extreme
accretor). From left to right the \textit{panels} then show the naked
stellar flux then the fluxes from BDD systems seen at inclination
angles of 0$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$, or face-on, the
approximate expectation value of inclination and edge-on. For each of
the \textit{second} to the \textit{fourth panels} the flux components
are then shown as in Figure \ref{disc_eg_173}, i.e. the total SED
shown as a black line, then stellar light shown in blue and thermal in
red, with direct shown as bold and scattered as dashed lines. The
inset graph in the \textit{bottom right} panel of Figure
\ref{flare_sed_fast} simply shows a lower flux scale, as the flux
levels have fallen to the lowest shown division in the main Figure.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/flare_sed_fast.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing SEDs of a system with a central stellar mass
   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
   and an areal coverage of the accretion stream of 10\%. The
   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
   to right) show the naked stellar flux (\textit{first panel}), then
   constituent fluxes for SEDs at inclination angles of 0$^{\circ}$,
   64$^{\circ}$ and 90$^{\circ}$. The \textit{second} to
   \textit{fourth panels} on each line then show the total flux as a
   black line, with the component fluxes presented as explained Figure
   \ref{disc_eg_173}. The \textit{top panels} are for systems with an
   accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
   the \textit{lower panels} are for an accretion rate of -8
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{bottom right
     panel} inset Figure shows an enlargement of the lower flux levels
   of this SED. \label{flare_sed_fast}}
\end{figure*}

Figure \ref{flare_sed_fast} shows, by comparing the \textit{top
  panels} that as a disc is added to the system and the inclination of
the BDD system is increased more stellar (and accretion flux) is
reprocessed by the disc, for a negligibly accreting system. As one
moves from inclinations of 0 to 64$^{\circ}$ the stellar flux has
reduced as has the thermal component. At edge-on inclinations the
system is only visible through scattered light, and some (slight)
thermal emission from the outer disc at wavelengths $\lambda>30\mu$m
(indicative of temperatures of ~100K. Increasing the accretion rate
from -12 to -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ leads to a
significant increase in the naked stellar flux (compare \textit{top
  left} and \textit{bottom left panels}). As we add a disc and
increase the viewing inclination for the extreme accreting system
(\textit{bottom panels}), we also lose stellar flux. In the extreme
accretor case however the fall in flux contribution to the total SED
from the photosphere (and accretion) is much more significant. Indeed,
at edge-on inclinations the system becomes only visible in the thermal
(~100K) disc regime, with the scattered light significantly reduced.

As shown in Section \ref{disc_struct}, and more specifically, Figures
\ref{flare_-12_183} and \ref{flare_-7_193} as one increases the
accretion rate for BDD systems, in general, the outer disc structure
increases in vertical height. Effectively, the greater flux levels
increase the temperature of the outer disc and the condition of
vertical hydrostatic equilibrium leads to a vertical expansion. This
vertical expansion leads to a significant change in the angle at which
photons emitted from the stellar photosphere are interecepted by the
outer disc. This is an extension of the effected found in
\cite{2004MNRAS.351..607W}, where it was found that this effect alone
can shift the SED, and therefore colours and magnitudes, of inclined
BDD systems to those indicative of higher mass CTTS. The actual
changes in flux are complicated by dust sublimation and shape changes
of the inner edge (discussed later). As the inclination of the BDD
system is increased we see the total flux drop significantly once we
exceed the opening angle of the BDD system. This opening angle will
decrease with vertical scaleheight of the outer disc. Figure
\ref{flare_inc} shows the total SEDs for the BDD system of Figures
\ref{flare_-12_183} and \ref{flare_-7_193}, with the coresponding
accretion rates as \textit{left} and \textit{right panels}
respectively. The solid lines of \textit{both panels} of Figure
\ref{flare_inc} show the total SED for each of our ten simulated
inclinations, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84 and
90$^{\circ}$ (with the flux decreasing with increasing
inclination). The dashed line then highlights the inclination at which
the flux observed drops significantly, at 71 and 56$^{\circ}$ for the
accretion rates of -12 and -7 (or \textit{left} and \textit{right
  panels}), respectively. Whilst this effect is probably artificially
enhanced for such extreme accretion rates it is illustrative of the
general trend, notwithstanding complications from inner edge shape
**MENTION ABOUT NOT BEING BOUND MATERIAL?**NOT ENTIRELY HAPPY WITH
FLARESEDFAST**.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/flare_inc.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure of total SED flux reaching the observer for viewing
   angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90$^{\circ}$. SEDs
   shown are for systems shown in Figures \ref{flare_-12_183} and
   \ref{flare_-7_193}, as the \textit{left} and \textit{right panels}
   respectively. In both panels the dashed line highlights the angle
   at which a significant fall in flux reaching the observer occurs.
   The values of inclination at which the fall in flux occurs are
   71$^{\circ}$ and 56$^{\circ}$ for the accretion rates of -12 and -7
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, \textit{left} and
   \textit{right panels} respectively. \label{flare_inc}}
\end{figure*}

\subsubsection{Inner Edge Shape}
\label{inner_shape}

As discussed in Section \ref{disc_struct} the addition of dust
sublimation leads to a change in the shape of the inner edge, where
the temperature is sufficient. Figures \ref{no_sub_183} to
\ref{sub_181} show a range in inner edge shapes, from flat walls
through concave to convex curves, caused by the radial density profile
of the disc and the dependence of the sublimation temperature on
density. This change in shape, as noted by \cite{2007ApJ...661..374T},
will lead to changes in the characteristics of the SED, or derived IR
excess, with inclination angle \citep{2007ApJ...661..374T}. For
concave and vertical walls the inner edge is visible over a smaller
range of viewing angles than for a convex inner edge.

Figures \ref{typ_curve} and \ref{ext_curve} show the thermal direct
radiation, originating from the disc, as a function of inclination for
the two groups of accretors, typical and extreme respectively. The
models included in Figure \ref{typ_curve} as the \textit{left} and
\textit{right panels} are those shown in Figures \ref{sub_169} and
\ref{sub_175} respectively. Whereas, the models included in Figure
\ref{ext_curve} as the \textit{left} and \textit{right panels} are
those shown in Figures \ref{sub_179} and \ref{sub_181}
respectively. For each \textit{panel} of Figures \ref{typ_curve} and
\ref{ext_curve} the thermal direct flux is plotted as a solid black
line at each modeled inclination, namely, 0, 27, 39, 48, 56, 64, 71,
77, 84 \& 90$^{\circ}$. The dashed line in each case shows where a
significant fall in the flux reaching the observer from direct thermal
emission from the disc is apparent.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/typ_curve.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing thermal direct flux reaching the observer at
   inclination angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \&
   90$^{\circ}$, for typical accretors. The \textit{left panel} shows
   the flux from the model shown in Section \ref{disc_struct}, Figure
   \ref{sub_169}. The \textit{right panel} shows the flux from the
   model shown as Figure \ref{sub_175} in Section
   \ref{disc_struct}. In both panels the dashed line highlights the
   angle at which a significant fall in flux from direct thermal
   emission is observed.  The values of inclination at which the fall
   in flux occurs are 77$^{\circ}$ for \textit{both panels} and
   therefore accretion rates. \label{typ_curve}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/ext_curve.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing thermal direct flux reaching the observer at
   inclination angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \&
   90$^{\circ}$, for extreme accretors. The \textit{left panel} shows
   the flux from the model shown in Section \ref{disc_struct}, Figure
   \ref{sub_179}. The \textit{right panel} shows the flux from
   the model shown as Figure \ref{sub_181} in Section
   \ref{disc_struct}. In both panels the dashed line highlights the
   angle at which a significant fall in flux from direct thermal
   emission is observed.  The values of inclination at which the fall
   in flux occurs are 71$^{\circ}$ and 64$^{\circ}$ for the
   \textit{left} and \textit{right panels}
   respectively.\label{ext_curve}}
\end{figure*}

For typically accreting systems, where little or no dust sublimation
has occured the inner edge remains either a vertical or slightly
concave wall, as shown in Figures \ref{sub_169} and
\ref{sub_175}. For these systems flux reaching an observer from
direct thermal emission, i.e. from, in the main, the disc inner edge,
falls rapidly with increasing viewing angle, after the maximum opening
angle is achieved. This is shown in Figure \ref{typ_curve} where at
the viewing angle of 77$^{\circ}$ the flux shown falls significantly,
for both accretion rates. This opening angle is larger than found for
the slower rotating, counter parts, as shown by Figure
\ref{flare_inc}, where a transition in occultation occurs at
71$^{circ}$. For the case in \ref{typ_curve} the system has the
shorter rotation period, leading to a larger opening angle, as the
flux from the central star does not reach the outer disc, and
subsequently flare it. Figure \ref{typ_curve} shows that after an
angle of 77$^{\circ}$ the flux from the inner edge falls to zero. The
systems displayed in Figure \ref{typ_curve} have inner edge
temperatures of ~1400K, meaning their flux emission peaks at a
wavelength of ~2$\mu$m. The flux observed at the expected peak
wavelength falls to zero at inclinations of 77$^{\circ}$, indicative
of a vertical wall being obscured by the outer disc, before the limit
of the opening angle is reached.

Figure \ref{inner_inc_sed} shows the full SEDs and the components (as
tagged by {\sc torus}), for the models displayed in Figures
\ref{sub_169} and \ref{sub_179} and the \textit{left panels} of
Figures \ref{typ_curve} and \ref{ext_curve}. The \textit{top panels}
show the SEDs for an accretion rate of -12
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (model from Figure
\ref{sub_169}) for inclinations of 64, 71 and 77$^{\circ}$, moving
from the \textit{leftmost} to \textit{far right panel}. The same
inclinations are shown in the \textit{bottom panels}, which show the
SEDs, and components, for the model with an accretion rate of -7
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, displayed in Figure
\ref{sub_179}. As discussed in Section \ref{disc_struct}, the model
with the higher accretion rate has a a much larger, in scaleheight,
and convex inner boundary. The lower accretion rate model has a
vertical inner wall, close to the star. The analysis of Figures
\ref{typ_curve} and \ref{ext_curve} show that the flux from the inner
wall should fall dramitically at different limiting inclinations for
either accretion rate.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/inner_inc_sed.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing SEDs of a system with a central stellar mass
   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
   and an areal coverage of the accretion stream of 10\%. The
   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
   to right) show the constituent fluxes for SEDs at inclination
   angles of 64$^{\circ}$, 71$^{\circ}$ and 77$^{\circ}$. The total
   flux is shown as a black line, with the component fluxes presented
   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
   for systems with an accretion rate of -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and the \textit{lower
     panels} are for an accretion rate of -7
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The SEDs from the
   \textit{top} and \textit{bottom panels} are derived from the models
   presented in Figures \ref{sub_169} and \ref{sub_179},
   respectively.\label{inner_inc_sed}}
\end{figure*}

Figure \ref{inner_inc_sed} shows that for negligible accretion rates
(\textit{top panels}), where the inner edge is a vertical wall, the
total flux falls rapidly after exceeding a viewing angle of
71$^{\circ}$. After an inclination of 71$^{\circ}$, the negiliby
accreting system is dominated by scattered light from the central
star. The system accreting at -7
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, however, maintains high flux
levels, and thermal contributions to the SED, for inclination angles
above 71$^{\circ}$, particularily between 1 and 3$\mu$m. Essentially,
as shown by comparing Figures \ref{sub_169} and \ref{sub_179}, with
increasing flux and subsequent dust sublimation the inner edge has
grown vertically and become convex. As shown perviously by
\cite{2007ApJ...661..374T}, a vertical (or concave) inner edge will
have strong dependence on inclination angel as the inner edge is
obscured at lower inclinations. For the larger convex wall, the SEDs
shown in \ref{inner_inc_sed} show that the resulting flux is less
dependent on inclination angle.

Once accretion rates reach extreme levels the inner edge is sublimated
far from the central star. For these systems the resulting inner edge
is both larger, in terms of scaleheight, and convex. Figure
\ref{ext_curve} shows that the flux falls dramatically at an
occultation angle of 71 and 64$^{\circ}$ for accretion rates of -7 and
-6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, respectively
(\textit{left} and \textit{right panels}, respectively). For the
accretion rate of -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ this is
indicative of a larger opening angle (71$^{\circ}$) for the the
shorter period object, when compared to the more slowly rotating
equivalent (56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
  panel}). Additionally, Figure \ref{inner_inc_sed} shows that the
total SED, has a strong thermal component and is only weakly dependent
on inclination angle, between 1 and 3 $\mu$m . This increase in
opening angle with increase in rotation rate is again due to more flux
being intercepted by a larger and closer inner wall. This interception
of flux by the inner edge leads to a cooler and less vertically
extended outer disc in the shorter period objects when compared to the
slower rotating systems. Figures \ref{ext_curve} and
\ref{inner_inc_sed} also shows that, contrary to the typical
accretors, the flux from the inner edge does not fall off as quickly
with inclination angle after occultation. The inner edge temperatures
are ~1300 and ~1200K for the accretion rates of -7 (\textit{left
  panel}) and -6 (\textit{right panel})
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ respectively. This leads to
peak emission at ~2.2 to 2.4 $\mu$m. Figures \ref{ext_curve} and
\ref{inner_inc_sed} shows that even for inclinations above the
occulation or opening angle of the disc flux from the inner edge
persists. This is indicative of a large and convex inner edge, as is
observed in Figures \ref{sub_179} and \ref{sub_181}. Once again these
extreme accretion rates probably over accentuate the result but help
illumate the consequences of changes in the disc structure.

Therefore, the longer (in wavelength) component of the final SED is
dominated by the disc inner edge ($L_{\rm wall}$), temperature and
shape and the outer disc scaleheight ($L_{\rm disc}$). The shape and
location of the inner disc walls are controlled, primarily, by the
stellar rotation rate (and stellar radius) and accretion rate (and
stellar flux). Given that the stellar flux and radius decrease as the
pre-MS star ages (or decreases in mass) the flux levels and the
position of the inner edge are also weakly affected by the age of the
central star.

As shown in Figure \ref{inner_temp} the location of the inner edge and
the corresponding temperature are correlated (differently) for typical
and extreme accretors. This correlation is dominated by the dust
sublimation temperature for the extreme accretors, and therefore the
radial density profile. However, for the typical accretors the
correlation between temperature and inner radius retains some
dependence on the co-rotation radius (temperature is correlated with
rotation period). This is as the sublimation temperature is not
reached for the longer period models. Therefore, one might expect the
resulting SEDs for typical accretors to show a correlation in shape,
between 2 to 3 $\mu$m, caused by the inner wall temperature changes,
in turn caused by changes in the rotation period. Figures
\ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} show the SEDs (and
constituent parts as explained in Figures \ref{disc_eg_173}) for a BDD
model at the two rotation periods. The model has a mass of
0.04$M_{\odot}$ and an age of 1 Myr, with accretion rates of -12 and
-9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in Figures \ref{rot_-12_1Myr}
and \ref{rot_-9_1Myr} respectively, both at an areal coverage of
10\%. The \textit{top panels} show the SEDs for a rotation period of
0.5 days, and the \textit{bottom panels} the SEDs for a rotation
period of 5 days. The \textit{first}, \textit{second}, \textit{third}
and \textit{fourth panels} then show inclination angles of 0, 56, 64
and 90$^{\circ}$ respectively.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/rot_-12_1Myr.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{NOW SYSTEM SHOWN IN FIGURE ABOVE?**Figure showing SEDs of a
   system with a central stellar mass of $0.04M_{\odot}$, an age of
   1Myr an accretion rate of -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
   of 10\%. The \textit{panels}, both \textit{top} and
   \textit{bottom}, (from left to right) show the SEDs and constituent
   fluxes at inclination angles of 0$^{\circ}$, 56$^{\circ}$,
   64$^{\circ}$ and 90$^{\circ}$. The component fluxes are presented
   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
   for systems with a rotation period of 0.5 days and the
   \textit{lower panels} are for a rotation period of 5
   days. \label{rot_-12_1Myr}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/rot_-9_1Myr.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing SEDs of a system with a central stellar mass
   of $0.04M_{\odot}$, an age of 1Myr an accretion rate of -9
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
   of 10\%. The \textit{panels}, both \textit{top} and
   \textit{bottom}, (from left to right) show the SEDs and constituent
   fluxes at inclination angles of 0$^{\circ}$, 56$^{\circ}$,
   64$^{\circ}$ and 90$^{\circ}$. The component fluxes are presented
   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
   for systems with a rotation period of 0.5 days and the
   \textit{lower panels} are for a rotation period of 5
   days. \label{rot_-9_1Myr}}
\end{figure*}

Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} show that for these
BDD systems with typical accretion rates, the changes in SED with
rotation period are small, apart from perhaps the face-on
configuration. The systems in the \textit{top} and \textit{bottom
  panels} of Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} have
inner edge temperatures of ~1470 \& ~900K, and ~1460 \& ~940K
respectively. This leads to different peak emissions for the slower
and faster rotating stars, of approximately 2 and 3 $\mu$m. However,
as is shown by Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} very
little resulting change is apparent in any of the SEDs apart from the
face-on configuration. Essentially, any change in the SED shape caused
by changing emission at the inner disc edge is smoothed out by the
resulting interactions with the rest of the disc structure. As pre-MS
stars age they contract and reduce in luminosity, this will lead to
changes in the co-rotation radius and inner edge temperature. The
models in Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} are for an
age of 1 Myr. Therefore, changes in the SED could also be more
apparent for older systems, with lower stellar luminosities. Figures
\ref{comp_rot_-12} and \ref{comp_rot_-9} show the same system as
Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr}, i.e. with accretion
rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
respectively, but for ages of 1 and 10 Myrs. In Figures
\ref{comp_rot_-12} and \ref{comp_rot_-9} only the total SED are shown
for the shorter period, a solid black line, and the longer period, as
a dashed blue line. The \textit{top panels} show the SEDs for 1 Myr
systems and the \textit{bottom panels} the 10 Myr systems. The
\textit{first}, \textit{second}, \textit{third} and \textit{fourth
  panels} again show the viewing angles of 0, 56, 64 and 90$^{\circ}$
respectively.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/comp_rot_-12.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing SEDs of a system with a central stellar mass
   of $0.04M_{\odot}$ and accretion rate of -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
   of 10\%. The SEDs are shown in \textit{each panel} for a rotation
   period of 0.5 (solid black line) and 5 (dashed blue line) days. The
   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
   to right) show the total SEDs inclination angles of 0$^{\circ}$,
   56$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$. The \textit{top
     panels} are for systems with an age of 1 Myr and the
   \textit{lower panels} are for an age of 10
   Myrs. \label{comp_rot_-12}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/comp_rot_-9.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing SEDs of a system with a central stellar mass
   of $0.04M_{\odot}$ and accretion rate of -9
   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
   of 10\%. The SEDs are shown in \textit{each panel} for a rotation
   period of 0.5 (solid black line) and 5 (dashed blue line) days. The
   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
   to right) show the total SEDs inclination angles of 0$^{\circ}$,
   56$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$. The \textit{top
     panels} are for systems with an age of 1 Myr and the
   \textit{lower panels} are for an age of 10
   Myrs. \label{comp_rot_-9}}
\end{figure*}

Figures \ref{comp_rot_-12} and \ref{comp_rot_-9} show that for typical
accretors the resulting SEDs do not, in general, change significantly
with changing rotation rate. For the face-on configuration
(\textit{far left panels}) the SED slope over 2 to 3$\mu$m is
marginally different only**. Essentially, flux redistribution from the
highly flared outer regions of the disc and inner edge shape changes
lead to a loss of correlations of SED shape (from 2 to 3$\mu$m)with
inner edge temperature. This leads to a loss of any correlation
between IR excess and inner edge location as predicted for the, flat,
discs of \cite{1997AJ....114..288M}.

\subsubsection{SED summary}
\label{sed_summary}

The shape of the combined SED, $L_*+L_{\rm acc}+L_{\rm wall}+L_{\rm
  disc}$, is controlled by the combined stellar flux (intrinsic
stellar temperature and luminosity, and accretion stream temperature
and luminosity), and the disc characteristics (inner edge location and
temperature, and outer disc flaring). The stellar flux and temperature
both increase with increasing accretion rates and reducing areal
coverages. The stellar flux (at constant temperature) also reduces as
a pre-MS star contracts with age (or reduces in mass). Furthermore,
the inner disc flux increases as the inner wall becomes hotter, larger
and more visible with increasing incident flux. The outer disc
component also increases as the outer disc flares. The flaring and
temperature of the disc are controlled by the stellar flux and the
rotation rate. Finally, and most importantly, the shape of the SED
will be dominated by the inclination of the system, especially for
extremely flared systems. This results in the observable SED being a
major function of the input variables, age (and mass), accretion rate
(and areal coverage), rotation period and system inclination.

As we have discussed in this Section and Section \ref{disc_struct} the
underlying disc structures are caused by complicated interplays
between the sublimation physics, vertical hydrostatic equilibrium and
emission of the disc components. However, several underlying trends
have been observed in the physical characteristics of the
systems. Most notably the correlation, to different strengths, of the
disc inner wall location and its resulting temperature, as found in
\cite{1997AJ....114..288M}. However, \cite{1997AJ....114..288M} go on
to predict a correlation in IR excess with inner edge location. Given
that the initial inner edge location is dependent (chiefly) on the
rotation period one might expect a corelation of rotation rate with IR
excess. This has been shown to be unlikely due to complications in the
inner edge location due to dust sublimation, and obscuration of the
inner disc edge at higher inclination angles. In addition, for large
groups of stars there is evidence for a correlation in stellar mass
with accretion rates. Although we have shown that the observable SEDs
of BDD systems at higher accretion rates are difficult to classify as
such, most surveys supporting this relationship use photometric data.

\subsection{Photometry}
\label{photometry}

Practically, most parameters for young pre-MS stars are derived from
surveys of populations, usually open clusters, using broadband
photometry and subsequently constructed colour-magnitude and
colour-colour diagrams (CMDs and CoCoDs respectively,
hereafter). Therefore, in this Section, we demonstrate the prohibitive
effects on the broadband photometry of varying our input
parameters. In this Section we, in particular, relate the discussed
features of disc structures (\ref{disc_struct}) and the resulting
simulated SEDs (\ref{sed_analysis}) in terms of the derived
photometry, in Section \ref{indv_phot}. Furthermore, we explore the
consequences of our model grid on the derivation of the primary
parameters of age, mass and disc fractions, from populations, in
Section \ref{populations}. This in turn leads to highlighting
selection effects with, for instance, the mass to accretion rate
relation, in Section \ref{sum_relations}.  For the derivation of ages
optical CMDs, in particular in \textit{V, V-I}, are most often used,
and indeed most suitable. Whereas, IR CMDs, such as a \textit{J, J-K}
CMD, are most suitable for mass derivation \cite[see references and
discussions in][ and Section
\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.

\subsection{Effects of Disc Presence and Accretion on Photometry}
\label{indv_phot}

For the derivation of ages optical CMDs, in particular in \textit{V,
  V-I}, are most often used, and indeed most suitable. Whereas, IR
CMDs, such as a \textit{J, J-K} CMD, are most suitable for mass
derivation \cite[see references and discussions in][ and Section
\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.

As discussed in Section \ref{sed_analysis} the presence of a
circumstellar disc and accretion result in significant changes to the
simulated SEDs for our models. Firstly, the photophere of the central
star is dominated by the accretion luminosities for accretion rates of
$\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$ as shown in Section
\ref{acc_dominance}. Secondly, for increasing accretion rates the
outer disc flaring increases, resulting in occultation of the star at
smaller inclination angles, as discussed in Section
\ref{flare_obscure}. Finally, the location of the inner edge and flux
intercepted by this edge lead to changes in its shape and subsequent
dependence of the observed SED with inclination, as discussed in
Section \ref{inner_shape}. In this Section we explore the effects of
these changes in SED shape on the derived photometry in CMDs used for
age and mass derivation for stars. The use of isochrones for the
derivation of single star parameters is completely unreliable
\citep[see discussion in][]{2008MNRAS.386..261M}. However, exploring
the changes in the CMDs of single objects will elucidate the causes of
scatters from the expected locii in CMDs of populations of BDs.

\subsubsection{Accretion Dominance-Photometry}
\label{acc_dom_phot}

Accretion flux was shown to dominate the underlying, intrinsic,
photospheric SED for accretion rates of
$\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$ (see Figure \ref{acc_dom} in
Section \ref{acc_dominance}). As one would expect this leads to
significant changes in the derived photometric magnitudes for bands
blueward of a few microns, where the accretion and photospheric flux
dominate. This is shown in Figure \ref{naked_acc}. Figure
\ref{naked_acc} shows CMDs in $M_V$, $(V-I)_0$ (\textit{left panels})
and $M_J$, $(J-K)_0$ (\textit{right panels}) of naked stars with
accretion rates of -2, -9 and -8
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, shown as black, red and blue
lines resepctively (in \textit{all panels}). The \textit{top panels},
then show the two rotational periods of 5 and 0.5 days, as dashed and
solid lines respectively, for a coverage of 10\%. The \textit{bottom panels},
then show the two areal spot coverages of 1 and 10\%, as dashed and
solid lines respectively, for a rotational period of 5 days.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/naked_acc.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the naked systems for accretion rates of -8,
   -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, shown in
   \textit{all panels} as blue, red and black lines respectively. The
   model shown for \textit{all panel} has a mass of 0.04$M_{\odot}$
   and an age of 1Myr. The \textit{top panels} are models with areal
   spot coverages of 10\%, and the \textit{lower panels} are for
   models with rotational periods of 5 days. The dashed and solid
   lines then delineate the rotation periods for the \textit{top
     panels} and coverages for the \textit{bottom panels}. The dashed
   lines show the rotational periods of 5 days (\textit{top panels})
   and coverages of 1\% (\textit{bottom panels}). The solid lines
   denotes periods of 0.5 days (\textit{top panels}) and coverages of
   10\% (\textit{bottom panels}). For accretion rates of -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (black line, \textit{all
     panels}), are representative of all models at this rate, as the
   models are coincident within the CMD.\label{naked_acc}}
\end{figure*}

As the rotation rate increases the co-rotation radius also increases,
as shown in Equation \ref{inner_eq}, $R_{\rm inner}\propto
\tau^{\frac{2}{3}}$. Therefore, as Equations \ref{Lacc} and
\ref{Tacc}, show, $L_{\rm acc}\propto 1- \frac{R_*}{R_{\rm inner}}$
and $T_{\rm acc}\propto \frac{L_{\rm
    acc}}{A^{\frac{1}{4}}}$. Therefore, the temperature of the
accretion hot spot increases as the coverage lowers and the rotational
period increases (the latter is due to the increase in potential
energy lost by the mass accreted). This can be seen in Figure
\ref{acc_dom} with lower areal coverages and longer rotational periods
leading to accretion fluxes at peaking at shorter wavelengths. The
\textit{left panels} of Figure \ref{naked_acc} show that as the
accretion rate increases the stars move blueward and to brighter
magnitudes in the $M_V$, $(V-I)_0$ CMD. Furthermore, as the accretion
spot temperature is maximised i.e. moving to longer periods of
rotation or smaller areal coverages (solid to dashed lines), the stars
also move blueward. For the \textit{right panels}, or $M_J$, $(J-K)_0$
CMDs the behaviour is less intuitive. Increases in accretion rate lead
to a slight brightening and an initial move redward, followed by a
move blueward. This is as the lower accretion rates have lower hot
spot temperatures, with peak wavelengths between 1 and 3 $\mu$m
(corresponding to temperatures of $~$2800K to $~$900K, the range of
the BD photosphere). This leads to increases in the red flux and
changes in the slope from $J$ to $K$. At the higher accretion rates
the accretion flux dominates and cause the blueward shift as the slope
becomes larger. For the highest accretion rate, in the \textit{bottom
  right panel}, a change to a hotter spot (reduction in coverage, from
solid to dashed lines) results in a move redward in the CMD. This can
be understood by observing the blue solid lines in the \textit{top
  panels} of Figure \ref{acc_dom}. Essentially, the reduction in spot
temperature moves the accretion flux to much shorter wavelengths,
$~$0.5 to $~$0.3 $\mu$m, meaning that the flux in the $J$ and $K$
bands becomes more like the photosphere, and less dominated by
accretion. The \textit{top right panel} of Figure \ref{naked_acc} then
shows that increases in the rotation period (from solid to dashed
lines) shows a move blueward in the CMD, resulting in changes of the
peak accretion flux emission from $~$0.58 to $~$0.5 $\mu$m, meaning
significant flux from the accretion hot spot will still fall in the
$J$ and $K$ bands, and the slope will be increased.

\subsubsection{Effect of Flaring and Obscuration on Photometry}
\label{flare_obscure_phot}

As described by \cite{2004MNRAS.351..607W} the increased flaring, in
BDD systems when compared to CTTS, leads to more significant changes
in the photometric characteristics of the BDD stars with inclination
changes. The increased flaring shown in Figures \ref{flare_-12_183}
and \ref{flare_-7_193} results in increased obscuration of the central
star (and inner edge) at earlier inclinations. This obscuration is
shown to occur at lower inclination angles for objects accreting at
higher levels, as shown in Figure \ref{flare_inc}. Figure
\ref{flare_inc} shows that significant obscuration occurs at
inclinations of 71 and 56$^{\circ}$ for accretion rates of -12 and -7
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively. The changes in
flux with inclination will clearly lead to a change in the observed
magnitude with inclination. Figure \ref{flare_mag} shows the $M_V$ and
$M_J$ magnitude, in the \textit{top} and \textit{bottom panels}
respectively, as a function of inclination with the individual points
marked as crosses. The \textit{top} and \textit{bottom panels} show
accretion rates of -12, -9 and -7 as black, red and blue lines. The
solid lines are for objects with rotational periods of 0.5 days and
the dashed lines are for periods of 5 days. The \textit{inset panel}
within the \textit{bottom panels} shows an enlargment of the section
of inclinations from 40 to 80$^{\circ}$. For \textit{all panels} the
vertical dotted lines show the inclinations for which significant
drops in flux are observed (see Figure \ref{flare_inc}) for -12 and -7
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in black and blue respectively.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/flare_mag.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing magnitude change with inclination for $M_V$
   (\textit{top panel}) and $M_J$ (\textit{bottom panel}) for the
   models shown in Section \ref{disc_struct}, Figures \ref{no_sub_183}
   to \ref{sub_181}. The accretion rates of -7, -9 and -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as blue, red and
   black lines respectively. The individual points are shown as
   crosses for all data. The dashed lines show the systems with
   rotational periods of 5 days and the solid lines 0.5 days, in
   \textit{all panels}. A section of the \textit{bottom panel} has
   been enlarged and is shown as the \textit{inset panel}. Note the
   models for -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are coincident
   in this Figure. \textit{All panels} show the inclinations are which
   obscuration occurs for -12 and -7
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as dashed black and blue
   lines respectively. \label{flare_mag}}
\end{figure*}

Figure \ref{flare_mag} shows that the occultation starts earlier for
the higher accretion rates, shown by the increase in both magnitudes
(\textit{top} and \textit{bottom panels}) with inclination angle at
around 56 and 71$^{\circ}$, as also shown in Figure
\ref{flare_inc}. The slower rotation rates, for the highest accretion
rates, show a generally fainter magnitude, than the faster rotating
systems, caused by a larger disc scaleheight. For $M_J$ the fall in
magnitude is again earlier and more significant for the larger
accretion rates. However, at higher inclinations the systems become
brighter again, show in the \textit{inset panel}. This brightening is
due to the curved inner wall, as shown in Figures \ref{inner_inc_sed}
(discussed in more detail in Section \ref{inner_edge_phot}.

The change in magnitude, will also lead to a change in colour. As
described $V$, $V-I$ and $J$, $J-K$ CMDs are ubiquitously used for
derivation of ages and masses. The use of isochrones to derive ages
and masses of individual stars is not reliable. However, it is
informative to explore the changes in the CMD position of our BDD
systems. Figure \ref{flare_VVI} shows $M_V$, $(V-I)_o$ CMDs for the
accretion rates of -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$,
as the \textit{left} and \textit{right panels} resepctively. The
systems are those shown in Figure \ref{flare_-12_183} and
\ref{flare_-7_193}, at all modeled inclinations. For \textit{both
  panels} the red dashed line, with the data points marked as crosses,
shows the changes in CMD position with inclination of the BDD system
at different inclinations for a 1 Myr system (with an areal coverage
of 10\% and a $\tau$ of 5 days). The solid blue line is the matching
isochrone for naked systems, with the naked $M_*=0.04M_{\odot}$ marked
as a triangle. Again, for \textit{both panels} the inclinations at
which significant drops in flux were found in Figure \ref{flare_inc}
in red text.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/flare_VVI.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the positions within a $M_V$, $(V-I)_0$ of
   the models in Figures \ref{flare_-12_183} and \ref{flare_-7_193}
   (Section \ref{disc_struct}) as the \textit{left} and \textit{right
     panels} respectively. The solid blue line are the 1Myr naked
   isochrones at the accretion rates of -12 and -7
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ for the \textit{left} and
   \textit{right panels} respectively (with an areal coverage of 10\%
   and a $\tau$ of 5 days). The dashed red line is the BDD system with
   $M_*=0.04M_{\odot}$ at all simulated inclinations. The triangles,
   in both panels are the 0.04$M_{\odot}$ stars on the naked
   isochrones and the crosses show this mass over the range of
   inclinations with an associated disc. Figure \ref{flare_inc}
   predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ models respectively,
   and these are denoted by the text within the
   figure.\label{flare_VVI}}
\end{figure*}

Figure \ref{flare_VVI} shows that as the system changes in inclination
it leads to a sigificant dimming in both cases. The inclinations from
\ref{flare_inc} where significant flux is lost are shown and it can be
seen that a significant drop in magnitude is apparent just before this
inclination (as also shown in Figure \ref{flare_mag}). The models in
\textit{both panels} get slightly redder as we increase to the
obscuration angle, caused by scattered light from the disc this can be
observed for the accretion rate of -12
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in Figures \ref{rot_-12_1Myr}
and \ref{comp_rot_-12}.

Figure \ref{flare_JJK} shows the same data as Figure \ref{flare_VVI}
with the same notation and symbol meanings.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/flare_JJK.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the positions within a $M_J$, $(J-K)_0$ of
   the models in Figures \ref{flare_-12_183} and \ref{flare_-7_193}
   (Section \ref{disc_struct}) as the \textit{left} and \textit{right
     panels} respectively. The solid blue line are the 1Myr naked
   isochrones at the accretion rates of -12 and -7
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ for the \textit{left} and
   \textit{right panels} respectively (with an areal coverage of 10\%
   and a $\tau$ of 5 days). The dashed red line is the BDD system with
   $M_*=0.04M_{\odot}$ at all simulated inclinations. The triangles,
   in both panels are the 0.04$M_{\odot}$ stars on the naked
   isochrones and the crosses show this mass over the range of
   inclinations with an associated disc. Figure \ref{flare_inc}
   predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ models respectively,
   and these are denoted by the text within the
   figure.\label{flare_JJK}}
\end{figure*}

Figure \ref{flare_JJK} again, as in Figure \ref{flare_VVI}, shows the
BDD systems dimming with increasing inclination, with some move
towards redder colours. There is an offset between the naked and BDD
systems at face on inclinations, caused by the inner disc wall. This
is particularily large for the higher accretion rate (\textit{right
  panel}). This increase in reddening for the higher accretion rates
is due to the much larger and curved inner disc edge as shown in
Figure \ref{sub_179}. This curved inner edge also leads to less
dependence of $(J-K)_0$ as a function of inclination angle, as
compared to the lower accretion rate.

\subsubsection{Inner Edge and Photometry}
\label{inner_edge_phot}

It is clear that the scatter within a CMD, in particular for the
$M_J$, $(J-K)_0$ CMD, is strongly affected by the emission from the
inner edge (as shown in Figure \ref{flare_JJK}).

Figure \ref{inner_VVI} shows the position in a CMD of the models from
Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179} and
\ref{sub_181}. The accretion rates shown are -12, -7, -9 and -6
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as the \textit{top left},
\textit{bottom left}, \textit{top right} and \textit{bottom right
  panels}. The solid blue line in \textit{all panels} of Figure
\ref{inner_VVI} show the naked isochrone at 1 Myr (with an areal
coverage of 10\% and $\tau$ of 0.5 days), at the shown accretion
rate. The dashed red line shows the BDD system matching the naked
isochrone, except with $M_0.04M_{\odot}$, at all inclination rates,
with the datapoints marked as crosses. The blue triangles are then the
naked stars at $M_0.04M_{\odot}$. The points at which the thermal
direct flux reaching the observer drops significantly are marked in
red text for each system, as shown in Figures \ref{typ_curve} and
\ref{ext_curve}.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/inner_VVI.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the positions within a $M_V$, $(V-I)_0$ of
   the models in Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179}
   and \ref{sub_181} as the \textit{top left}, \textit{bottom left},
   \textit{top right} and \textit{bottom right panels}
   respectively. As for Figure \ref{flare_VVI}, the solid blue line is
   the naked isochrone at 1 Myr for the corresponding accretion rate
   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The
   dashed red line is the BDD isochrone at the same age and accretion
   rate. The inclination of each model at which obscuration is
   expected to occur, from Figures \ref{typ_curve} and
   \ref{ext_curve}, is denoted in text.\label{inner_VVI}}
\end{figure*}

Figure \ref{inner_VVI} shows for the $M_V$, $(V-I)_0$, the inclination
increase again dims the star for these models and moves it intially
redward, until it exceeds the expected obscuration angle, found from
Figures \ref{typ_curve} and \ref{ext_curve}. However, as we move
through the accretion rates from -12
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (\textit{top left panel}) to -6
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (\textit{bottom right panel})
the transition from edge-on to face-on system tends to a sharper
feature, with the reddest point at the obscuration angle. As would be
expected from the SEDs shown in Figure \ref{inner_inc_sed}. This is
caused by maximising the amount of the inner edge which is visible,
whilst the stellar photosphere is still visible (which also
contributes in these passbands).

Figure \ref{inner_JJK} shows the same information as Figure
\ref{inner_VVI} but for a $M_J$, $(J-K)_0$ CMD. Here, the BDD
isochrones are initially much redder than their naked counterparts, as
expeted due to IR excesses caused by the disc inner edges. As the
inclination increase for the lower accretion rates (\textit{top left}
and \textit{bottom left panels}) the system moves first redward and
then sharply blueward as the SED becomes dominated by scattered light
only. As can be seen in Figure \ref{inner_inc_sed}. For the extreme
accretion rates the wall is no longer vertical and the change in
infrared colours is smoother up until the obscuration angle.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/inner_JJK.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the positions within a $M_J$, $(J-K)_0$ of
   the models in Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179}
   and \ref{sub_181} as the \textit{top left}, \textit{bottom left},
   \textit{top right} and \textit{bottom right panels}
   respectively. As for Figure \ref{flare_VVI}, the solid blue line is
   the naked isochrone at 1 Myr for the corresponding accretion rate
   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The
   dashed red line is the BDD isochrone at the same age and accretion
   rate. The inclination of each model at which obscuration is
   expected to occur, from Figures \ref{typ_curve} and
   \ref{ext_curve}, is denoted in text.\label{inner_JJK}}
\end{figure*}

\section{Populations}
\label{populations}

Practically, the derivation of parameters for pre-MS populations uses
CMDs and isochrones applied to clusters or populations of stars. In
this section we explore the scatters of our BDD systems across our
grid of input values within typical or commonly used CMDs and CoCoDs
for deriving ages, masses and disc fractions.

To delineate the effects of the accretion rate and circumstellar discs
we have subdivided the grid into two groups (as discussed in Sections
\ref{disc_struct} and \ref{sed_analysis}), those with accretion rates
typical for higher mass CTTS objects, defined as
$\dot{M}=$10$^{-12}M_{\odot}yr^{-1}$ (negligible) to
$\dot{M}=$10$^{-9}M_{\odot}yr^{-1}$ and those with elevated accretion
rates, where $\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$. For several of the
plots in this section the magnitude and colours for the
$M_*=0.01M_{\odot}$ at high inclinations become extremely faint and
red, respectively. In some cases these objects appear slightly without
the scale of the diagram the axes where limited in this way to be able
to show the changes in colour an magnitude for the majority of stars
better. The colours and magnitudes for these lowest mass stars are not
necessarily unreliable but simple hinder the aesthetics of the plots,
and as they are at the limits of our grid we have decided to omit them
from some Figures by trimming the axes. Additionally, stars at the
highest inclinations, i.e edge on disc systems, are often omitted from
the Figures due to their extremely faint magnitudes, meaning they
would not be practically observable.

\subsection{Age and Mass Derivations}
\label{age_mass_pop}

As discussed in Section \ref{indv_phot} for the derivation of the
primary parameters of age and mass the CMDs most suitable and commonly
used are $M_V$, $(V-I)_0$ and $M_J$, $(J-K)_0$. Furthermore, these
CMDs are indicative of the associated CMDs, for instance $M_R$,
$(R-I)_0$ or $M_J$, $(J-H)_0$ etc. Also as discussed in
\cite{2008MNRAS.386..261M} the use of isochrones for the derivation of
masses and ages for individual pre-MS stars is unreliable at
best. Practically, therefore, median ages are derived from
populations. Subsequently, derived masses are still unreliable but at
least based on a consistent age. This problem is being addressed by
Bell et al (in prep), where $K$ band photometry and known eclipsing
binaries are being used to refine pre-MS isochrones. In this section
we plot the data for our 1 Myr systems only and explore the resulting
scatters caused by the disc presence and accretion luminosity.

Figures \ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext} shows
four CMDs in $M_V$, $(V-I)_0$ for the typical and extreme accretors
respectively. For the typical accretors, Figure
\ref{spread_opt_VVI_typ}, shows the isochrones constructed for naked
systems at 1 Myr, for accretion rates of -12 and -9
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as the solid and dashed black
lines. Whereas in Figure \ref{spread_opt_VVI_ext} the naked isochrones
of -9 and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as dashed and
solid black lines respectively. The \textit{top left panel}, in both
Figures (\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}) shows
a pre-MS isochrone at 1 Myr from \cite{2000A&A...358..593S} adjusted
to a distance of 250pc and an extinction of $A_V=2$ mag, simulating a
background population of CTTS stars. The dots in \textit{each panel},
for both Figures (\ref{spread_opt_VVI_typ} and
\ref{spread_opt_VVI_ext}) are the 1 Myr BDD systems for all
inclinations, rotational periods, areal spot coverages and the
individual accretion rates within the accretion type classes. The
\textit{panels} of the Figures \ref{spread_opt_VVI_typ} and
\ref{spread_opt_VVI_ext} then seperate the systems by the input
variables. The \textit{top left panel} shows either the accretion
rates of -9, -10 and -11 \& -12 or -6, -7 and -8
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures
\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}
respectively. These three classes are then shown as blue, black and
red dots respectively. The \textit{bottom left panels} then show those
systems with areal coverages of 1 and 10\% as blue and red dots
resepectively. The \textit{top right panels} then shows systems with
rotational periods of 0.5 and 5 days as blue and red dots
respectively. Finally, the \textit{bottom right panels} show the
systems seperated by inclination. These groups are $\theta \leq
48^{\circ}$ as blue dots (classed as face-on systems), $\theta> 56$ \&
$64^{\circ}$ (classed as the expected systems, as the expectation
value of $cos(\theta)=60^{\circ}$) as black dots and $\theta \geq
71^{\circ}$ (classed as edge-on systems) as red dots. Figure
\ref{spread_opt_RRI_typ} also shows the same data as for Figure
\ref{spread_opt_VVI_typ}, but for $M_R$, $(R-I)_0$ CMDs.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/spread_opt_VVI_typ.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
   accretors ($\dot{M} \leq$ -9
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The black solid and dashed
   lines in \textit{all panels} are the naked star isochrones for
   accretion rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
   respectively. The \textit{top left} only shows the 1 Myr pre-MS
   isochrone of \citet{2000A&A...358..593S} adjusted to a distance
   modulus of 7 and an extinction of $A_V=2$, simulating a reddened
   background population. The dots are the data for typical accretors
   for models at 1 Myr. The data are then seperated by input
   variables, in the \textit{panels}. The \textit{top left panel}
   shows three accretion classes, -9, -10 and -11 \& -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as blue, black and red dots
   respectively (the lowest two accretion rates are grouped as they
   are coincident). The \textit{top right panel} shows the rotational
   periods of 0.5 and 5 days as blue and red dots respectively. The
   \textit{bottom left panel} shows the areal spot coverages of 1 and
   10\% as blue and red dots resepctively. The \textit{bottom right
     panel} shows three groups of inclinations, $\theta \leq$
   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
   71$^{\circ}$ , as blue, red and black dots
   respectively.\label{spread_opt_VVI_typ}}
\end{figure*}

As can be seen in Figure \ref{spread_opt_VVI_typ} current accretion in
a star and disc systems, for rates typical in the BD mass regime,
creates a scatter in our simulated photometry indicative of a much
larger isochronal age spread than 10 Myr. Indeed, for many BDD systems
even at nominal accretion rates of -11 or -12
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, for our simulations, the
colours of these stars move significantly blueward of the expected BD
locus in a $M_V$, $(V-I)_0$ CMD. As the dots in Figure
\ref{spread_opt_VVI_typ} are the simulated photometry of BDD systems
over a range of typical input parameters (see Section
\ref{par_space}), an observed coeval 1 Myr population could reasonably
be expected to show a similar scatter. The naked isochrones show that
this spread in simulated photometry, would lead to a spread in
isochronal age greater than the $\approx$10 Myr spread claimed for
higher mass stars in some star forming regions (for instance the
ONC). Furthermore, for the higher accretion rates of -9 or -10
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the movement of the star
within the CMD will effectively move the star into the contamination
region expected for background CTTS or MS stars at a $(V-I)_0$ of
$\leq$1.5 and $M_V$ 12-10, and as such the star would not be included
in a photometrically selected BD sample. The solid green line, in the
\textit{top left panel}, showing the 1 Myr isochrone of
\cite{2000A&A...358..593S} at a distance of 250 pc and extinction of
$A_V=2$ mags shows that the BDD systems with higher accretion rates
could easily be confused for a background CTTS or MS population (as MS
stars are simply less luminous at a roughly constant \textit{V-I} than
the CTTS counterparts). Indeed miss classification of a BDD system as
a CTTS system has already been revealed in \cite{}**CHECK WHITE AND
BASRI. Furthermore, scatter, although somewhat reduced, can be
observed in the simulated photometry of the negligibly accreting
systems, for example in the \textit{top left panel} some red dots,
accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (which
will be negligible compared to the photospheric flux, see Figure
\ref{acc_dom}), still scatter significantly. These objects may still
be included in a `wide' photometric selection. This scatter is a
strong function of inclination, as shown in the \textit{bottom right
  panel}, where, as the inclination is increased the objects are
pushed lower in the CMD. Indeed, for the edge on cases some objects
have magnitudes fainter than show in Figure \ref{spread_opt_VVI_typ}
($M_V\approx 20$). This is expected as the star becomes obscured by
the flared disc, interestingly for these systems the \textit{bottom
  right panel} shows that this occurs for inclinations above around
71$^{\circ}$ (as found in Figure \ref{flare_inc}) in most cases yet
even for the lower inclination angles some objects have very faint
magnitudes, this is due to the disc flaring leading to a smaller
opening angle and is discussed in Section \ref{disc_struct}. The
\textit{bottom left panel} shows that for naked systems accretion
rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ lead to the stars
being scattered into the region occupied by background CTTS and
contamination (the lower accretion rates are all coincident with the
-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for 1 Myr). Crucially, the
\textit{top left panel} shows that the scatter from the isochrone is,
generally, correlated with accretion rate. Effectively, as the
accertion rate increases the BDD system moves farter away from the
isochrone and is therefore less likely to be classified as a BDD
system and included in any taget samples of such objects. The
\textit{top right panel} shows that the scatter, in $M_V$, in our
simulated photometry from the isochrones is significant for both areal
coverages. The \textit{bottom left panel}, shows significant scatter
in the simulated photometry for both adopted rotation periods. This
panel also shows that scatter in this diagram is not obviously
correlated with the rotation period and therefore inner edge
position. Overall, as found in \cite{2004MNRAS.351..607W}, the
dominant scattering effect for BD disc systems in an optical CMD
appears to be caused by accretion rate and inclination, and therefore
obscuration effects of the disc on the star. This suggests that for a
given photometric survey of BDD systems accreting at typical accretion
rates and with an expected range of inclinations (centred on around
60$^{\circ}$) one would expect to exclude a significant fraction of
these objects from any isochrone based selection.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/spread_opt_VVI_ext.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As Figure \ref{spread_opt_VVI_typ} except for extreme
   accretors, $\dot{M}\geq$ -8
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. In this Figure the solid
   black line now shows naked systems with an accretion rate of -6
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as opposed to -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as in Figure
   \ref{spread_opt_VVI_typ}, the dashed black line is still for an
   accretion rate of -9
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. \label{spread_opt_VVI_ext}}
\end{figure*}

Figure \ref{spread_opt_VVI_ext} shows that for extreme accretion rates
the BDD objects move significantly blueward and brighter than the
naked isochrone (the naked isochrone at -9
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ is shown for
comparison). Comparison of the \textit{four panels} again show that,
in general, the scatter is chiefly correlated with accretion rate and
inclination. Essentially, Figure \ref{spread_opt_VVI_ext} shows that
for, admittedly extreme, accretion rates BDD systems will not be
included in a photometrically (or indeed spectroscopically, from
Section \ref{sed_analysis}) selected sample.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/spread_opt_RRI_typ.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As Figure \ref{spread_opt_RRI_typ}, but in $M_R$, $(R-I)_0$,
   with the pre-MS isochrone omitted.\label{spread_opt_RRI_typ}}
\end{figure*}

Similar scattering, as observed in Figure \ref{spread_opt_VVI_typ},
occurs when using CMDs constructed using \textit{R, R-I} \citep[using
the photometric system of][]{1998A&A...333..231B}. Figure
\ref{spread_opt_RRI_typ} shows the \textit{R, R-I} CMD.

Similar consequences are apparent in CMDs best suited, and most used,
for derivation of masses using isochrones. Figure
\ref{spread_ir_JJK_typ} shows the same data as Figure
\ref{spread_opt_VVI_typ} in the same format except in this case the
pre-MS isochrone of \cite{2000A&A...358..593S} has been smoothed,
purely for aesthetics and to remove the sharper features. Again Figure
\ref{spread_ir_JJK_ext} contains the same data in the same format as
Figure \ref{spread_opt_VVI_ext} except that the naked star isochrone
at an accretion rate of -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ is
not shown as it lies significantly blueward of the CMD.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/spread_ir_JJK_typ.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As Figure \ref{spread_opt_VVI_typ}, in $M_J$, $(J-K)_0$, in
   this Figure the pre-MS isochrone of \citet{2000A&A...358..593S},
   has been smoothed.\label{spread_ir_JJK_typ}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/spread_ir_JJK_ext.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As for Figure \ref{spread_opt_VVI_ext}, except that the -6
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ isochrone is not shown (lies
   significantly blueward of locus of data), and the pre-MS isochrone
   has been smoothed.\label{spread_ir_JJK_ext}}
\end{figure*}

Figure \ref{spread_ir_JJK_typ} shows that for typical accretion rates
and expected ranges of the other input variables the spread in CMD
positions is large. Indeed. the \textit{top left panel} again shows
that, as in the $M_V$ $(V-I)_0$ case, some of the BDD objects will
appear as redenned background CTTS objects. Scrutiny of the
\textit{individual panels} shows no clear correlation of CMD position
with input variable except for the inclination. As shown in the
\textit{bottom right panel} as the inclination increases the systems
move to fainter magnitudes and redder colours, in general. The
\textit{top right panel} of Figure \ref{spread_ir_JJK_typ} shows that
for typical accretion rates there does not appear to be a correlation
of $(J-K)_0$ colour with rotation rate as expected from the modeling
of flat disc by \cite{1997AJ....114..288M}. It is clear that assigning
masses to accreting BDD systems using isochrones, for our model grid,
would result in the incorrect masses. In addition, photometric sample
selection for BD systems will also exclude the majority of our higher
accretion rate objects. Figure \ref{spread_ir_JJK_ext} shows that for
extreme accretors the scatter is much larger, and again correlated
only with inclination, and perhaps accretion rate to a lesser degree
(\textit{bottom right} and \textit{top left panels} of Figure
\ref{spread_ir_JJK_ext}).

\subsubsection{Summary}

GOT HERE**combined the next two paragraphs

Now summarise on the effects of the CMD classification*** Then sort
out effect on the rotational period to JK excess and Mstar to Macc
relation.**

Therefore, if one adopts the range of input parameters we have used
(see Section \ref{par_space} for justification), our simulated
photometry shows, qualitatively, that a coeval 1 Myr population of
accreting BD stars and BDD systems, with typical accretion rates and
range of inclinations, will exhibit a scatter in apparent isochronal
age of $>$10 Myr. Furthermore, some objects will be scattered below
and blueward of a 10 Myr isochrone. This has been shown for CMDs in
\textit{V, V-I} and \textit{R, R-I}. It is important to note at this
point that these conclusions are qualitative, and obviously based on
our assumptions. However, the repercussion for isochronal age
derivation and sample selection in the BD regime could be
profound. Indeed this study has only included the effects of current
or ongoing accretion from a disc, it has totally neglected any effects
of accretion, both past and present, on the evolution of the central
star. This past accretion could also act to reduce the stars radius,
accelerating contraction
\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
additional scatter in a coeval population proportional to the range in
accretion rates \citep[See][for full
discussion]{2008MNRAS.386..261M}. Our findings support those of
\cite{2004MNRAS.351..607W}, showing that a significant scatter is
caused by obscuration of the central source by the central disc. In
addition we have shown that the scatter blueward, into the CTTS or
background MS locus, is caused by active accretion at levels found in
CTTS stars, but currently not regularly recorded in stars classified
or selected as BDs.

Therefore, as for derivations of age, given our assumptions, and the
adopted range of input parameters, a 1 Myr coeval population scatters
significantly in a \textit{J, J-K} CMD. The \textit{J, J-K} CMD is
representative of CMDs constructed from the \textit{JHK}
passbands. So, qualitatively at least, derivation of masses using
isochronal fitting of our simulated photometry would not produce
reliable or accurate results. Again, as discussed for optical CMDs,
these simulations do not include any of the effects of past or current
accretion on the evolution of the central object, which is expected to
significantly exacerbate the observed scatter. This is also true for
the naked systems with small increases in accretion rate leading to
significant scatters in the CMDs. Additionally, given the evidence
discussed in \cite{2004MNRAS.351..607W}, supported by the evidence
from our own simulated photometry shown in Figures
\ref{spread_opt_VVI_typ}, \ref{spread_opt_VVI_ext},
\ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext}, it is clear that
young, accreting, BDD systems are likely to be misidentified when
using photometric colours or magnitudes, even at generally canonical
accretion rates. This casts doubt on the veracity of the mass to
accretion rate relationship. For our model grid we have not assumed
any such relation, therefore, as our data would also show a similar
relation it suggests that the observed result may be caused by
intrinsic scattering. The relation, $\dot{M}\propto M_*^{2}$ suggests
that their is a dearth of lower mass stars accreting at higher
rates. We have shown that for accretion rates in the range -12 to -9
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with higher
accretion rates would be preferentially missed using photometric or
isochronal selection.

Therefore, again as for the optical case, given our assumptions and
parameter space, BDD systems accreting at higher rates would not be
identified with the correct mass in most cases using IR CMDs.

\subsection{Disc fractions}
\label{disc_fractions_phot}

Disc fractions have been derived using infrared excesses previously in
\textit{JHK}, however recent works pre-dominantly use \textit{Spitzer}
IRAC magnitudes. Furthermore, MIPS magnitudes are used to identify
so-called debris discs, where IR excesses are not apparent at shorter
wavelengths. Finally, disc fractions have also been derived using the
$\alpha$ criteria, where $\alpha=\frac{dlog\lambda
  F\lambda}{dlogF\lambda}$ between two limiting wavelengths,
originally used to distinguish amongst Class I, II or II sources, but
now used to detect disc presence
\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
used as a selection criterion for disc presence for TTS stars. We have
constructed the $\alpha$ values for our model grid by adopting the
limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
8.0$\mu$m.

Now switch to figures just showing inclination and accretion rate (not
rotation rate).

Whilst magnitudes are affected by accretion rates, ages, rotational
periods etc, practically, for colour, colour plots the inclination is key.

TYPICAL ACCRETORS
location in the cMD is proportonal to the accretion rate and
inclination and this sontinues into the IR colours

GOT HERE***
for typical accretors the accretion rate becomes unimportant and the
resulting thing is just inclination for extreme accretors the
accretion rate becomes key again

First a Jh jk colo col d to show this, all ages used both 1 and 10 Myr

NOT SURE IF I SHOULD LIMIT BY AGE ALL THE DISC FRACTIONS PLOTS? used 1
and 10 myr sample as age doesn't effect the position in the col-col
plot very much

WHERE TO PUT THIS** CLEARPAGE THING**
show that only inclination and accretion matter, age notmimportant for
discs, disc and non disc systems separation observed in panels where
there are no black disc systems. For extreme accretors mention fact
that the inner edge temperature is now function of accretion rate etc.
\clearpage

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_JHJK_typ.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing $(J-H)_0$, $(J-K)_0$ colour-colour diagram
   for typical accretors ($\dot{M}<leq$ -9
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The dots are then all
   models (at 1 and 10 Myrs) with discs and the black crosses are the
   naked systems, in \textit{all panels}. The data are then seperated
   by input variable in \textit{each panel}. The \textit{top left
     panel} shows accretion rates of -9, -10 and -11 \& -12
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, black and red dots
   respectively. The \textit{top right panel} shows the systems with
   rotational periods of 0.5 and 5 days as blue and red dots
   respectively. The \textit{bottom left panel} shows systems with
   areal spot coverages of 1 and 10\% as blue and red dots
   respectively. Finally, the \textit{bottom right panel} seperates
   the systems into three groups inclination, $\theta \leq$
   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
   71$^{\circ}$ , as blue, red and black dots
   respectively.\label{disc_frac_JHJK_typ}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_JHJK_ext.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As for Figure \ref{disc_frac_JHJK_typ} but for extreme
   accretors, $\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
   .\label{disc_frac_JHJK_ext}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_irac_typ.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing typically accreting systems ($\dot{M}\leq$-9
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$), in irac photometric
   bands. The \textit{left panels} show the $([3.6]-[4.5])_0$ against
   $([4.5]-[5.8])_0$ CoCoD, and the \textit{right panels} show the
   $([3.6]-[4.5])_0$ against $([5.8]-[8.0])_0$ CoCoD. In \textit{all
     panels} the dots are disc systems and crosses naked systems. The
   \textit{top panels} then seperate the systems by accretion rate
   with, -9, -10 and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
   as blue, black and red dots respectively. The \textit{bottom
     panels} seperate the systems by inclination with $\theta \leq$
   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
   71$^{\circ}$ , as blue, red and black dots
   respectively. \label{disc_frac_irac_typ}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_irac_ext.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As for Figure \ref{disc_frac_irac_typ} but for extreme
   accretors, $\dot{M} \geq$ -8
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.\label{disc_frac_irac_ext}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_irac_mips_typ.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing the $([3.6]-[4.5])$, $([8.0]-24)$ CMDs as the
   \textit{left panels} and $([3.6]-[5.8])$, $([8.0]-24)$ CMDs as the
   \textit{right panels}, combining irac and mips photometric
   channels. The sytems are again seperated by accretion rate and
   inclination angle in the \textit{top} and \textit{bottom} panels as
   in figure \ref{disc_frac_irac_typ}.\label{disc_frac_irac_mips_typ}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_irac_mips_ext.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{As for Figure \ref{disc_frac_irac_mips_typ} but for extreme
   accretors ($\dot{M} \geq$ -8
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$).\label{disc_frac_irac_mips_ext}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_mips.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing CMDs of mips photometry for the typical
   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) and
   extreme ($\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$)
   accretors, as the \textit{left panels} and \textit{right panels}
   respectively. The \textit{top panels} seperate the systems by
   accretion rate in the way described in Figures
   \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} in the
   \textit{left} and \textit{right panels} respectively. The
   \textit{bottom panels} then seperate the systems by inclination as
   described in Figure \ref{disc_frac_irac_typ}. The \textit{inset
     panels} in the \textit{top panels} then show a larger region with
   the BDD systems as red dots and the naked systems as blue
   crosses.\label{disc_frac_mips}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/disc_frac_alpha.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing $\alpha$ value \citep{2006AJ....131.1574L}
   (against an arbitrary model number) used
   \citet{2009arXiv0901.2603K}, $\alpha=\frac{dlog(\lambda
     F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
   $\mu$m). Crosses show the simulated objects without discs and dots
   are those with circumstellar disc, the horizontal line is the
   $\alpha>-$2 cut used to identify disc candidates for solar type
   stars in \citet{2009arXiv0901.2603K}. Note, that stars of
   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
   estimates, in the atmosphere models, for longer wavelengths
   ($\lambda>$4$\mu$m). The \textit{left panels} show typical
   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
   and the \textit{right panels} the extreme ($\dot{M} \geq$ -8
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors. The \textit{top
     panels} seperate the systems by accretion rate in the way
   described in Figures \ref{disc_frac_irac_typ} and
   \ref{disc_frac_irac_ext} in the \textit{left} and \textit{right
     panels} respectively. The \textit{bottom panels} then seperate
   the systems by inclination as described in Figure
   \ref{disc_frac_irac_typ}.\label{disc_frac_alpha}}
\end{figure*}

\subsubsection{Practical Observations}
PRACTICAL OBSERVATIONS:

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/irac_cut.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing all simulated photometry for the entire
   studied parameter range at ages 1Myr and 10Myr as dots (blue and
   red respectively), and the naked photometry as crosses. The dashed
   lines are a recent BD disc excess cuts used in
   \citet{2005ApJ...631L..69L} for IC348 at a nominal age of 3-4Myr
   \citet{2008MNRAS.386..261M}. It must be noted that the naked stars
   of $M=$0.01$M_{\odot}$ are not included in this figure as their
   SEDs do not extend far enough into the IRAC passbands to derive
   reliable colours. The \textit{left panel} shows the typical
   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
   and the \textit{right panel} the extreme ($\dot{M} \geq$ -8
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors.\label{irac_cut}}
\end{figure*}

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/irac_cut_2.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing an observational cut used in
   \citet{2008ApJ...688..362L} for data of the $\sigma$ Orionis
   cluster. It must be noted that the naked stars of
   $M=$0.01$M_{\odot}$ are not included in this figure as their SEDs
   do not extend far enough into the IRAC passbands to derive reliable
   colours. The systems are seperated by age as described in Figure
   \ref{irac_cut}. The \textit{left} and \textit{right panels} again
   show the typical ($\dot{M} \leq$ -9
   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) and extreme ($\dot{M} \geq$
   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors respectively as
   in Figure \ref{irac_cut}.\label{irac_cut_2}}
\end{figure*}

CASE STUDY:

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/rho_oph_102.ps"
   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing CMDs and CoCoDs of systems with matching
   parameters to $\rho$ Ophiucus 102 from
   \citet{2002A&A...393..597N}. The object $\rho$ Ophiusucs 102 is
   shown in \textit{all panels} as a black star, the BDD systems are
   the seperated by age, with the 1 and 10 Myr systems appearing as
   blue and red dots respectively. The \textit{top left panel} shows a
   $M_J$, $(J-H)_0$ CMD, the \textit{top right panel} a $M_J$,
   $(J-K)_0$ CMD, the \textit{bottom left panel} a $M_R$, $(R-I)_0$
   CMD and the \textit{bottom right panel} shows a $(J-H)_0$,
   $(J-K)_0$ CoCoD.\label{rho_oph_102}}
\end{figure*}

SHOW ROTATION RATE CORRELATION LOST AS  \cite{1997AJ....114..288M} HAD
FLAT DISCS FACE ON WE HAVE VIEWING ANGLES AND VERTICAL HYDRO

we find no correlation in general so is unlikely to effect the
population selection or attempts to show slow rotator to disc presence
correlations: i.e. nairn

Now we conclude on the rotaton rate to IR relation and the mass to
accretion rate relationship.
For individal model the J-K is dependent on lots of variables so the
correlation with rotation rate is non existent

NOTE ABOUT SUBSEQUENT PAPER WITH ANALTIC SOLUTIONS

\subsection{Summary}

summarise on the photometric sections

\section{Conclusions}
\label{conclusions}

COPY IN THE MAIN FROM PERVIOUS PAPER REWRITE WITH BETTER EMPHASIS.

\subsection{Derivation of Primary parameters}

\subsection{Consequences for Accretion Rate to Stellar Mass
  relationship}

\subsection{Summary}

rho outer and tau inner

RESULTS:

AGE, MASS AND DISC FRACTION PROBLEMS:
INCLINATION AND FLARING AS PER WALKER

THEREFORE:
CAN'T ASSERT M TO MACC RELATION

LOSS OF ROATIOANL PERIOD PROPORTIONALITY WITH IR EXCESS

DISC STRUCT=

FLARING INCREASES AS THE FLUX INCREASES, THEREFORE OPENING ANGLE
REDUCES

INNERR EDE ORIGINAL LOCATION PROPORTIONAL TO ROTATTION RATE
RINAL POSITION PROPORTINAL TO INNER EDGE LOCATION

INNER EDGE ALSO PUFFS UP AND THEN GETS BLASTED AWAY OVER RANGE OF
ACCRETION RATES AS THE FLUX IS INCREASED.

In this section we discuss the physical structures of our resulting
BDD systems and how these vary with our input parameters. Following
the work of \cite{2004MNRAS.351..607W} it is clear that for BDD
systems in vertical hydrostatic equilibrium the disc flaring leads to
increased obscuration of the central star and probable miss
classification. In addition, \cite{1997AJ....114..288M} predicted a
correlation between rotation rate and infrared excess due to the
change in position (radial) and therefore temperature of the inner
edge.

Vertical disc structure \cite{2004MNRAS.351..607W}

Rotation rate correlation with infrared excess \cite{1997AJ....114..288M}

The structure of this paper is as follows. In Section \ref{model} we
outline the model used, including an explanation of our physical
assumptions (Section \ref{physics}), a brief description of the
radiative transfer code (Section \ref{torus}), and an explanation of
the derivation of emergent quantities such as photometric magnitudes
(Section \ref{derived}). The ranges of the input variables are then
explained and, where possible, justified using observational
constraints in Section \ref{par_space}, with the total parameter space
covered shown in Table \ref{par_space_table}. Section
\ref{disc_struct} then contains analysis and description of the
resulting temperature and dust density structures of the discs. The
consequences of these changes in disc structure on the SEDs of these
objects is then discussed in Section \ref{sed_analysis}. Section
\ref{photometry} then details problems caused for the derivation of
the primary parameters age, mass and disc fractions from photometry
and the resulting relations built on these parameters; accretion rate
to stellar mass and rotational period to disc presence. Finally,
conclusions are drawn, with a summary, in Section
\ref{conclusions}.**REWRITE AT END**

\section[]{ACKNOWLEDGMENTS}

\bibliographystyle{mn2e}
\bibliography{references}
\appendix

\section{Consistency Checks and Problems}
\label{consistency}

Firstly, a check was made on the photospheric input flux and the
resulting stellar direct flux (tagged by {\sc torus}) after the radiative
transfer simulation. The resulting flux distributions should match
most closely for face-on configurations, and then match in shape only,
with the stellar direct flux level dropping towards higher
inclinations, as more photons are scattered and absorbed by the disc.

We also directly compared the magnitudes and colours of our naked BD
systems with the lowest accretion rate (-12
log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ to those published in
\cite{2000ApJ...542..464C}, in the same photometric system
(\textit{CIT}). We found significant colour differences ($\delta
(J-K)\le$ 0.1), between our derived values and those of
\cite{2000ApJ...542..464C}. As a further check we derived the
magnitudes in the \cite{1998A&A...333..231B} system (by both adopting
the published zero points, and by using a Vega reference spectrum),
and applied conversions of \cite{1992ApJS...82..351L}\footnote{We have
  also included the wavelength shift mention in
  \cite{2004PASP..116....9S}}, to the \textit{CIT} system. For each
method we failed to match the magnitudes and colours published in
\cite{2000ApJ...542..464C}. As a final test we passed the downloaded,
unaltered, atmospheric spectra directly through the filter response
program, without interpolation, for the closest matches in log(g) and
$T_{\rm eff}$ from the interior models published in
\cite{2000ApJ...542..464C}. These magnitudes and colours also failed
to match. Therefore, we must conclude that the most likely cause of
the mismatch is due to improvements in the model atmospheres available
online \footnote{http://perso.ens-lyon.fr/france.allard/} (this is
likely as the models available online, have a later time stamp,
$\approx$ 2005 compared to 2000). For the final published magnitudes,
for the naked systems, we have used a similar wavelength resolution as
in our BDD systems, i.e. 200 logarithmically spaced points. This means
that magnitudes derived from these spectra will differ slightly from
those derived from the full spectra, but this effect is negligible,
and increased resolutionfor only some of our model grid (i.e naked
stars) will hamper comparison between the models.

The final test of the derived colours and magnitudes was a comparison
of the naked systems with the results for the almost face-on BDD
systems. The results for the optical passbands should be similar and
an appraisal of the component SED, i.e. showing the stellar direct
flux, as can be seen in Figure \ref{disc_eg_173}.

We have adopted zeropoints derived using a Vega reference spectrum for
the optical and near-IR passbands. As a test we have compared our
derived zeropoints using the filter response of
\cite{1998A&A...333..231B} and the Vega reference spectrum against
those published in \cite{1998A&A...333..231B}. For our photometric
systems we integrate the summed number of photons counted by the
simulated telescope systems, however to test the zeropoints and match
the system of \cite{1998A&A...333..231B} we must integrate the summed
energy. The zeropoints we derived \citep[with the values of][in
parenthesis]{1998A&A...333..231B} were: $U=$20.977(20.94),
$B=$20.499(20.498), $V=$21.116(21.10), $R=$21.676(21.655),
$I=$22.376(22.371), $J=$23.735(23.755), $H=$24.989(24.860),
$K=$25.884(26.006) and $L=$27.809(27.875). Our derived zeropoints and
those of \cite{1998A&A...333..231B} match to within 0.05 mags (and
usually much closer) for all bands except the \textit{H,K} and
\textit{L} bands. This is probably due to the previously noted IR
excess (although detected at longer wavelengths) of the observed Vega
spectrum. \cite{1998A&A...333..231B} use a combined model spectrum of
Vega and Sirius as their reference spectrum. As a further test we also
used the synthetic A0V stellar spectrum of \cite{1993ASPC...41...55C}
to derive zeropoints but were still unable to improve the match to the
\cite{1998A&A...333..231B} photometric system for the \textit{JHK}
colours. However, for these colours we have adopted the \textit{CIT}
system, but were unable to find published zeropoints, and therefore
used the Vega reference spectrum. Essentially this may mean there is a
small offset in our \textit{JHK} photometry, however as most of our
results are based on differential photometry this will not affect our
conclusions.

A further complication with our adopted photometric systems is the
range of zeropoints available for the \textit{Spitzer} IRAC
photometry. For this study, as stated, we have adopted zeropoints
calculated using the zero magnitude flux from the IRAC handbook
\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}.
The resulting zeropoints were: Channel 1[3.6]=19.541, channel
2[4.5]=19.089, channel 3[5.8]=17.395 and channel 4[8.0]=17.966. The
corresponding zeropoints derived for the MIPS passbands where: channel
1[24]=2.139, channel 2[70]=-0.2726 and channel 3[160]=-1.990.

In summary, several careful consistency checks were performed to
confirm that the resulting SEDs and photometric magnitudes behaved as
expected and matched any available published results. A failure to
match the published zeropoints in the near-IR bands of the
\cite{1998A&A...333..231B} using a Vega reference spectrum was
probably due to an IR excess in our observed Vega spectrum. However as
in general most of the conclusions or implications of this study are
based on differential photometry, this should not affect them
adversely.  Furthermore, a failure to match the published magnitudes
(and colours) for the atmospheric models in
\cite{2000ApJ...542..464C}, even using published zeropoints for the
excellently defined system of \cite{1998A&A...333..231B}, and
subsequent conversions to the required \textit{CIT} system
\citep{1992ApJS...82..351L}, was prescribed to an update in the model
atmospheres available online.

\section{Website**}
\label{website}

\label{lastpage}
\end{document}

### 2010-04-19 BD_disc/old_paper.tex
New project
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2228 25464f21-6099-402c-b30a-640f1d40d38b

--- 2010-04-19 BD_disc/old.tex
@@
 \usepackage{graphicx}
-\usepackage{subfigure}
 
@@
 
-\title[**]{**}  \author[N.J.  Mayne and Tim
+\title[Accreting Brown Dwarfs]{Problems with the characterisation of
+  accreting Brown Dwarfs: A public grid of simulated SEDs and
+  photometry}  \author[N.J.  Mayne and Tim
 Harries]{N.J. Mayne$^{1}$\thanks{E-mail: nathan@astro.ex.ac.uk
@@
 \begin{abstract}
-SORT OUT REFERENCE TO THE FILTER RESPONSES IN THE SEDS FIGURES say
-discussed later
-more about stellar photosphere overlapping with disc
-
-FINESSE FIGURE SIZES
-
-CHANGE ALL WORDING FOR NEW FIGURES** CHANGED AGE TO 1 MYR FOR SUB
-FIGURES AND NEED TO ACKNOWLEDGE THROUGHT
-
-CHOSE 10 MYRS AS PRE-MS CONTRACTION AGES ARE PROBABLY A  FACTOR OF 2 WRONG
-
-ADD FILTERS TO OTHER SEDS FIGURES
-
-Note about fitting objects in the next paper.
+
+   1) All graphs of SEDS in log log units.
+
+  1a) Add in the new data and write in using more masses.
+
+  1b) Write in the extra inclinations-check from incs.lis.
+
+  1c) Write in that using same points for photosphere.dat
+
+  1) BOUY ET AL 2008, NEUGEBAUER 1984 AND SKRUTSKIE 2006 TRUNCATED AUTHOR LIST.
+
+  2) CHANGE SYMBOLS OF NAKED STARS IN IR EXCESS AND IR EXCESS 2 TO
+  MAKE CLEARER.
+
+  3) REWRITE CONCLUSIONS WITH MORE REFERENCE TO
+  \cite{2004MNRAS.351..607W}, \cite{2006A&A...452..245N} AND
+  \cite{2006MNRAS.370L..10C}.
+
+  4) REDO \& CHECK ALL FIGURES.
+
+  5) COMPARE FINAL INNER RADIUS, AFTER SUBLIMATION, TO COROTATION
+  RADIUS-HOT GAS STUFF.
+
+  6) ADD IN DISCUSSION FOR MIPS AND CHECK ZEROPOINTS
+
+  7) NEED A DISCUSSION OF THE DISC SCALEHEIGHT ETC (PROBABLY IN MODEL
+  OR PAR SPACE): $\rho \propto R^{-\alpha}$, $\alpha =
+  2.25$. $h\propto R^{\beta}$, $\beta = 1.25$. $\sigma = R^{(\beta
+    -\alpha)}$, AND IS CONSERVED. $R_{\rm outer}=300$ AU. DISC SCALEHEIGHT
+  AT 100 AU $H(100)=12.5$ AU
+
+  8) ADD IN DISCUSSION OF THE TIME TAKEN FOR EACH MODEL AND
+  SED-JUSTIFY SMALL NUMBER OF GRID. EACH MODEL (FOR ALL INCLINATIONS)
+  =** HOURS OF SUPERCOMPUTER TIME ON ** CORES
+
+  9) WHAT ABOUT EFFECT OF VERTICAL WALL FOR LONGER PERIOD OBJECTS (NO
+  DUST SUBLIMATION) VERSUS SHORTER PERIOD AND CURVED WALL
+
+  10) PUT IN INNER BOUNDARY PICTURES
+
+  11) SORT OUT PLACEMENT OF CLEARPAGE.
+
+  12) SORT RESULTS BIT ABOUT IRAC FLUX, THIS IS FROM REGIONS BEHIND
+  THE INNER EDGE SO WHY IS THE TREND REVERSED, IT IS NOT COMING FROM
+  THE OUTER FLARED REGIONS OF THE DISC BUT FROM JUST BEHIND THE PUFFED
+  UP INNER EGDE. THEREFORE, FOR LONGER PERIOD OBJECTS THE INNER EDGE
+  IS SMALLER AND THE DISC FLARED SO REGIONS JUST BEHIND CAN EMIT MORE
+  FLUX. FOR SHORTER PERIOD OBJECTS, THE INNER EDGE IS PUFFED UP AND
+  DOMINATES THE SED.
+
+  13) TO PROVE THE POINT ABOVE PRODUCE AN IMAGE BATCH  FILE TO PRODUCE
+  IMAGES FOR A TEST CASE I.E. CLOSE INNER EDGE DISTANT ONE ETC.
+
+  14) Add in reference to the Mike Meyer paper about changes due to
+  inner radius.
+
+15) Reference to bouy et al 2008 showing that the outer radius has a
+negligible effect
+
+16) IMAGES.
+
+17) Add in the Herschel filters.
+
+18) Disc mass fraction.
+
+19) IMF implications.
+
+20) ADD IN RHO OPH 102 STUFF- and add in comparison to stars without accretion
+
+21) Write in a bit about do we expect to see the correlation with
+rotation rate.
+
+22) Colours of 0.01Msol and 0.01Gyr models are very different.-REMOVE
+
+23) Notes abnout isong 200 pts for SEDS naked in consisitency checks
+used full resolution
+
+24) NOTE ABOUT THE FACT THAT 0.01Msol STARS ARE OFF THE BOTTOM OF SOME
+PLOTS AS THEY DIVE DOWN VERY ABRUPTLY.ASK ISABELLE ABOUT THIS
+
+25) Add in comments to mention that due to numerics some models have
+inner edges up to 100K above the 1700K mean dust sublimation temps.
+
+26) Note about colour colour plots cut in magnitude for J and removed
+the 0.01Msol stars from the naked
+
+27) For detections add in piece about the overlapping stars i.e what
+would be missed.
+
+28) missing 0.01 in alpha graph also.
+
+29) Adjust size of the smaller figures (i.e non-four) to fit.
+
+30) Change argument around to say rotation period correlation not
+present.
+
+31) Plots of inner temp against dust sublimation inner radius etc
+
+32) inclination against magnitude for different accretion rates.-one mass
+
+33) Sot out JJK isochrone
+
+34) Note about r=300 but outer radius doesnt matter largey see bouy
+and vitell 2008 or something.
 
@@
 \label{intro}
+
+\textbf{Motivation-why study discs around Brown dwarfs?}
 
@@
 ][]{2006astro.ph..2367W}.
+
+\textit{-Brown Dwarf formation mechanisms \& IMF.}
 
@@
 in the average radial size of discs, indicative of truncation for BD
-objects. Therefore, to progress our understanding of the fundamental
-issues of both the formation mechanism and emerging IMFs for BDs,
-consideration of the effects of an associated circumstellar disc and
-their subsequent ubiquity are essential.
+objects.
+
+Therefore, to progress our understanding of the fundamental issues of
+both the formation mechanism and emerging IMFs for BDs, consideration
+of the effects of an associated circumstellar disc and their
+subsequent ubiquity are essential.
+
+\textit{-Planet formation and disc dissipation timescales.}
 
@@
 
+\textit{Mass dependent disc lifetimes.}
+
 Some studies of disc lifetimes find no significant difference between
@@
 dissipation timescale.
+
+\textit{-Accretion from an inner disc and clearing mechanisms.}
 
@@
 
+\textit{-Accreting systems, relationship of stellar mass and accretion
+  rate.}
+
 Although the creation of the inner disc hole could have several
@@
 
+\textit{-Disc locking and star disc interaction: rotation.}
+
 A further use of disc fractions, in conjunction with stellar ages, is
@@
 position of this wall is affected by several factors, discussed
-further in Sections \ref{dust_edge} and \ref{inner_edge}. The previous
-work of \cite{1997AJ....114..288M} explored the effects of simple mass
+further in Section \ref{physics}. The previous work of
+\cite{1997AJ....114..288M} explored the effects of simple mass
 accretion and the radius to the inner disc on the infrared colours of
@@
 therefore changes in the balance of flux across the infrared
-wavelength regime. As this study does not include the effects of
+wavelength regime. As this study does not include the effectos of
 vertical hydrostatic equilibirum or even the study of flared discs one
@@
 
+\textbf{Aims.}
+
+\textit{Key areas: Require, Mass, age and disc fractions}
+
 In summary, several key areas in the theoretical studies of BDs hinge
@@
 derivations of either masses, ages or disc fractions (or a
-combination), supplemented by other parameters. The consequences of
-the disc structure for BD accretion discs, particularly vertical
-structure, given the assumption of vertical hydrostatic equilibrium,
-have already been discussed for a limited range of BD parameters in
-\cite{2004MNRAS.351..607W}. Indeed \cite{2004MNRAS.351..607W} have
-shown that BDD systems seen at higher inclinations can be confused
-with CTTS systems, having similar colours and
-magnitudes. Additionally, a benchmark model grid of spectra for star
-and disc systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$
-has previously been published in \cite{2006ApJS..167..256R}.
+combination), supplemented by other parameters.
+
+\textit{Previous complementary studies}
+
+The consequences of the disc structure for BD accretion discs,
+particularly vertical structure, given the assumption of vertical
+hydrostatic equilibrium, have already been discussed for a limited
+range of BD parameters in \cite{2004MNRAS.351..607W}. Indeed
+\cite{2004MNRAS.351..607W} have shown that BDD systems seen at higher
+inclinations can be confused with CTTS systems,
+having similar colours and magnitudes. Additionally, a benchmark model
+grid of spectra for star and disc systems in the mass range
+0.1$M_{\odot}<M_*<$50$M_{\odot}$ has previously been published in
+\cite{2006ApJS..167..256R}.
+
+\textit{What we are actually doing in the paper}
 
@@
 database is to complement that of \cite{2006ApJS..167..256R}. Finally,
-subsequent papers will introduce expansion to the model grid and an
-online fitting tool.
+a subsequent paper will introduce expansion to the model grid and an
+online fitting tool.**
+
+\textbf{Structure.}
+
+**REDO THIS AT THE VERY END**
 
@@
 explained and, where possible, justified using observational
-constraints in Section \ref{par_space}, with the total parameter space
-covered shown in Table \ref{par_space_table}. Section
-\ref{disc_struct} then contains analysis and description of the
-resulting temperature and dust density structures of the discs. The
-consequences of these changes in disc structure on the SEDs of these
-objects is then discussed in Section \ref{sed_analysis}. Section
-\ref{photometry} then details problems caused for the derivation of
-the primary parameters age, mass and disc fractions from photometry
-and the resulting relations built on these parameters; accretion rate
-to stellar mass and rotational period to disc presence. Finally,
-conclusions are drawn, with a summary, in Section
-\ref{conclusions}.**REWRITE AT END**A CASE STUDY IS THEN INCLUDED AS
-SECTION \ref{object}.**
+constraints in Section \ref{par_space}. Section \ref{results} contains
+the analysis and discussion of the main results of the model grid,
+first discussing the effects on the derivations of the primary
+parameters (Section \ref{derive_primary}), mass and age, and then the
+effects on disc fraction derivation (Section \ref{derive_frac}).
+Finally, conclusions are drawn, with a summary, in Section
+\ref{conclusions}.
 
@@
 derived values, such as broadband photometric magnitudes and colours
-(in Section \ref{derived}). Some internal consistency checks are
-detail in Appendix \ref{consistency}.
+(in Section \ref{derived}). Finally, we detail some internal
+consistency checks (Section \ref{checks}).
 
@@
 
+This section details some of the key physical assumptions made to
+generate our model grid.
+
 \subsubsection{Photospheric flux}
@@
 
-To model an accreting BDD system we must first model the underlying
-photospheric flux. To provide a self-consistent set of model spectra
-we have adopted a BD stellar interior and atmospheric model grid. We
-have then constructed the total photospheric flux for any input value
-of stellar age and mass by interpolating for surface gravity (log(g)),
-effective temperature ($T_{\rm eff}$), radius ($R_*/R_{\odot}$) and
-luminosity ($L_*/L_{\odot}$). These values were then used to
-interpolate atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2}
-\AA^{-1}$) from 1200 to 2$\times$ 10$^7$ $\AA$ (or 0.12 to 2000
-$\mu$m). These spectra were then smoothed using 200 logarithmically
-spaced points. Careful inspection ensured that no spectral features
-were removed during smoothing. The stellar interior models used for
-this study are the `DUSTY00' models of \cite{2000ApJ...542..464C}
-combined with the `AMES-Dusty', atmospheric models of
-\cite{2000ApJ...542..464C}, which are all available online
+\textit{-Model \& interpolation.}
+
+In order to model an accreting BDD system we must first model the
+underlying photospheric flux. To provide a self-consistent set of
+model spectra we have adopted a BD stellar interior and atmospheric
+model grid. We have then constructed the total photospheric flux for
+any input value of stellar age and mass by interpolating for surface
+gravity (log(g)), effective temperature ($T_{\rm eff}$), radius
+($R_*/R_{\odot}$) and luminosity ($L_*/L_{\odot}$). These values were
+then used to interpolate atmospheric spectra for flux (ergs
+s$^{-1}$cm$^{-2} \AA^{-1}$) from 1200 to 2$\times$ 10$^7$ $\AA$ (or
+0.12 to 2000 $\mu$m). These spectra were then smoothed using 200
+logarithmically spaced points. Careful inspection ensured that no
+spectral features were removed during smoothing. The stellar interior
+models used for this study are the `DUSTY00' models of
+\cite{2000ApJ...542..464C} combined with the `AMES-Dusty', atmospheric
+models of \cite{2000ApJ...542..464C}, which are all available online
 \footnote{http://perso.ens-lyon.fr/france.allard/}. For our
@@
 
+\textit{-Blackbody flux given, Equation: Rinner, Coverage \& Rate.}
+
 Secondly, we require a model of the accretion flux for the system. The
@@
 where the material was modelled as falling from the disc inner edge
-onto the surface of the star. $L_{\rm acc}$ is calculated according to
+onto the surface of the star. $L_{\rm acc}$ is calculated acoording to
 \ref{Lacc}, 
@@
 co-rotation radius. This is due to dust sublimation effects (see
-Sections \ref{dust_edge} and \ref{inner_edge} for an
+Sections \ref{disc_parameters} and \ref{dust_edge} for
 explanation). However, as the gas within the disc is not sublimated it
@@
 differences between the initial and resulting final radii of the dust
-disc can be found in Section \ref{inner_edge}. Once the accretion
-luminosity was derived, an adopted areal coverage ($A$), over the
-stellar surface, was used to calculate an effective temperature
-($T_{\rm acc}$), for the accretion `hot' spot, where
+disc can be found in Section \ref{inner_edge_position}. Once the
+accretion luminosity was derived, an adopted areal coverage ($A$),
+over the stellar surface, was used to calculate an effective
+temperature ($T_{\rm acc}$), for the accretion `hot' spot, where
 \begin{equation}
-{T_{\rm acc}=(\frac{L_{\rm acc}}{4\pi R^2_{*} \sigma \times A})^{\frac{1}{4}}}.
+{T_{\rm acc}=\frac{L_{\rm acc}}{(4\pi R^2_{*} \sigma \times A)^{\frac{1}{4}}}}.
 \label{Tacc}
@@
 that observationally UV excesses are often used to recreate and then
-subtract an assumed accretion flux using a blackbody flux curve,
-essentially the reverse of this method.
+subtract an assumed accretion flux using a blackbody flux curve.
 
@@
 \label{disc_parameters}
+
+\textit{-Inner disc boundary, Co-rotation, i.e. magnetically
+  truncated: rotational period.}
 
@@
 
+\textit{-Disc outer edge.}
+
 For this work the disc outer edge was set at 300 AU, this was chosen
@@
 has little effect on the resulting SED. However, in our subsequent
-paper we will include models for outer radii of 100 AU and plan to
+paper we have included models for outer radii of 100 AU and plan to
 extend this parameter range further to smaller values of the outer
@@
 
+\textit{Naked and TORUS versions.}
+
 The combined (accretion plus photosphere) SED is then used as a
-boundary condition for the {\sc torus} radiative transfer code and
-as a benchmark set of SEDs to model `naked' BD systems. The set of
-`naked' photospheres (plus accretion) are diluted by the factor
+boundary condition for the TORUS radiative transfer code and as a
+benchmark set of SEDs to model `naked' BD systems. The set of `naked'
+photospheres (plus accretion) are diluted by the factor
 $(R_*/Distance)^2$ to a distance of 10pc. The `negligibly' accreting,
@@
 
-\subsection{Radiative transfer code: {\sc torus}}
+\subsection{Radiative transfer code: TORUS}
 \label{torus}
@@
 
-We have used the {\sc torus} radiative transfer code which is
-described in \cite{2000MNRAS.315..722H}, including the subsequent
-refinements i.e.  addition of Adaptive-Mesh-Refinement (AMR)
-introduced in \cite{2004MNRAS.350..565H}. {\sc torus} uses the
-criterion of \cite{1999A&A...344..282L} in a radiative equilibrium
-algorithm. The simulation also calculates \textit{vertical hydrostatic
-  equilibrium} and dust sublimation for the disc, similar to that
-described in \cite{2007ApJ...661..374T}.
+\textbf{TORUS.}
+
+\textit{Radiative transfer code.}
+
+We have used the TORUS radiative transfer code which is described in
+\cite{2000MNRAS.315..722H}, including the subsequent refinements i.e.
+addition of Adaptive-Mesh-Refinement (AMR) introduced in
+\cite{2004MNRAS.350..565H}. TORUS uses the criterion of
+\cite{1999A&A...344..282L} in a radiative equilibrium algorithm. The
+simulation also calculates \textit{vertical hydrostatic equilibrium}
+and dust sublimation for the disc, similar to that described in
+\cite{2007ApJ...661..374T}.
 
@@
 \label{dust_size}
+
+\textit{-Size distribution.}
 
@@
 slight enhancement of the silicate feature (due to the relative
-abundance of Silicon increasing) which has little effect on the
+abundance of Silicon increasing) which as little effect on the
 resulting SEDs. Figure \ref{albedo} shows the
@@
 
-We have also applied dust sublimation during our simulations. This
-treatment is similar to that detailed in \cite{2007ApJ...661..374T},
-but improved and generalised with respect to the applicable
-geometries.
+\textit{-Dust sublimation}
+
+In addition, we have also applied dust sublimation during our
+simulations. This treatment is similar to that
+detailed in \cite{2007ApJ...661..374T}, but improved and generalised
+with respect to the applicable geometries.
 
@@
 photosphere. This process continues for five hydrostatic equilibrium
-calculations. Finally, once the hydrostatic equilibrium iteratins are
-complete we perform a final dust sublimation run to remove any cells
-where the dust temperature has moved above the sublimation temperature
-and further refine the photosphere and inner edge of the disc (whilst
-also unrefining cells where the opacity has reduced significantly and
-high resolution is no longer required). In this model the dust
-sublimation is effectively digital i.e. when the density and
-temperature for sublimation is reached for a given cell the dust is
-destroyed. We did attempt a more realistic model where the dust
-sublimation causes the dust to be destroyed at an evanescently
-decaying rate into the particular region. This was expected to lead to
-a more realistic situation where the dust destruction propogates into
-the disc material, and does not instantly destroy an entire
-cell. However, this implementation lead to incremental sections of
-dust being removed after each iteration, resulting in little change in
-the overall density structure of the disc. This is perhaps interesting
-for real systems, in that the dust sublimation should not be expected
-to act as a digital `switch'.
+calculations. In this model the dust sublimation is effectively
+digital i.e. when the density and temperature for sublimation is
+reached for a given cell the dust is destroyed. We did attempt a more
+realistic model where the dust sublimation causes the dust to be
+destroyed at an evanescently decaying rate into the particular
+region. This was expected to lead to a more realistic situation where
+the dust destruction propogates into the disc material, and does not
+instantly destroy an entire region. However, this implementation lead
+to incremental sections of dust being removed after each iteration,
+resulting in little change in the overall density structure of the
+disc. This is perhaps interesting for real systems, in that the dust
+sublimation should not be expected to act as a digital `switch'.
+
+\textit{Analytic disc structures}
+
+We have also modeled the same grid without using vertical hydrostatic
+equilibrium and, instead, adopting analytic solutions for the
+structure of the disc. These models are included in our subsequent
+paper describing the fitting routine and will be analysed in more
+detail in a later work.
+
+\textit{-Inner disc location}
 
@@
 initial inner disc radius. The differences in the starting and
-resulting inner wall radii and the shapes of the inner edges are
-discussed in Section \ref{inner_edge}. If the inner disc is cleared
-via dust sublimation one would expect a residual hot gas disc interior
-to the inner wall. This is as the gas component will not be destroyed
-and is free to extend to the co-rotation radius.  Evidence for a hot
-gas inner disc component has been found through SED fitting by
+resulting inner wall radii are discussed in Section
+\ref{inner_edge_position}. If the inner disc is cleared via dust
+sublimation one would expect a residual hot gas disc interior to the
+inner wall. This is as the gas component will not be destroyed and is
+free to extend to the co-rotation radius.  Evidence for a hot gas
+inner disc component has been found through SED fitting by
 \cite{2005ApJ...623..952E} and \cite{2008ApJ...689..513T}.  In
@@
 after the radiative transfer simulations are complete are discussed in
-detail in Section \ref{inner_edge}.
+detail in Section \ref{inner_edge_position}.
+
+\textit{-Gas treatment-opacity}
 
@@
 
+\textit{SEDs, at 10pc and inclinations-flagging}
+
 Once the radiative transfer code was completed simulated SEDs were
@@
 inclinations (0, 27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$). A
-further useful feature of the {\sc torus} code is that the emitted
-photons which make up the SED are tagged on their way to the
-observer. These tags separate the photons into four groups. Firstly,
-photons are separated by source into thermal (disc) or stellar groups.
-These groups are then subdivided into photons which reach the observer
+further useful feature of the TORUS code is that the emitted photons
+which make up the SED are tagged on their way to the observer. These
+tags separate the photons into four groups. Firstly, photons are
+separated by source into thermal (disc) or stellar groups.  These
+groups are then subdivided into photons which reach the observer
 either directly or after scattering (for example see Figure
-\ref{disc_eg_173}). The resulting SEDs are discussed in Section
-\ref{seds}.
+\ref{disc_eg}).
 
@@
 additional magnitudes and monochromatic fluxes are also discussed in
-detail in the subsequent paper introducing the online fitting tool.
+detail in the subsequent paper introducing the online fitting tool.**
+
+\textbf{Simulated Photometry.}
 
@@
 
+\textit{-Ten inclinations: 0, 27, 39, 48, 56, 64, 71, 77, 84 and 90 $^{\circ}$.}
+
 For the naked systems the flux is spherically symmetric however,
@@
 derived for each inclination selected.
+
+\textit{-Through filter passbands:near-infrared: CIT, Optical:
+ Bessels, Mid-IR: Spitzer.}
+
+\textit{-Vega calibrated, except Spitzer-Zeropoints (IRAC handbook).}
 
@@
 \footnote{http://ssc.spitzer.caltech.edu/mips/calib/}.
+
+\textit{-near-IR=old disc excess \& masses, Optical=Ages \& Mid-IR=New
+  disc fractions.}
 
@@
 
+\subsection{Consistency checks and problems}
+\label{checks}
+
+\textbf{Consistency checks and problems.}
+
 Once the model grid was completed several checks were performed to
@@
 checks were passed to our satisfaction before publication. Some
-problems remain, and these are explained in Appendix
-\ref{consistency}.
-
-\section{Parameter space}
-\label{par_space}
-
-This section details the range of each of the input parameters we have
-varied and, where possible, gives justification for the selected
-ranges from published observations. The simulations in this paper
-cover variations in the stellar mass, stellar age, stellar rotation
-rate, accretion rate, the areal coverage of the accretion stream, disc
-mass fraction and the system inclination. In a subsequent paper we
-introduce variation of the outer radius and using an analytical
-vertical disc structure as oppose to vertical hydrostatic equilibrium.
-.A summary of the values adopted for each input variable is shown in
-Table \ref{par_space_table}.
-
-\subsection{Mass} 
-\label{par_mass}
-
-Representative masses within the BD regime were chosen as follows:
-0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 $M_{\odot}$.
-
-\subsection{Age}
-\label{par_age}
-
-Typical disc lifetimes for solar type stars are of order $\approx$ 10
-Myrs \citep{2001ApJ...553L.153H}. Therefore, we have adopted input
-ages of 1 and 10 Myrs for our model grid, to span the approximate
-range of ages over which discs influence will be important.
-
-\subsection{Rotation rate}
-\label{par_rotation}
-
-Data for rotation rates, from periodic variability surveys, are widely
-available for a range of different age clusters of TTS. However, fewer
-studies exist on the rotation rates of BD mass objects. To select a
-feasible range of periods for our model grid we have collated the
-results from some recent studies of BD variability. Rotation period
-data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
-where periods are found over the range 5.78$-$74.4 hours ($\approx$
-0.24$-$3.1 days) for BD mass objects. In some cases the periodic
-variability is irregular and assumed to come from active accretion hot
-spots on the BD surface \citep[see][for discussion of variability
-causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
-and evidence of accretion are also found to correlate with slower
-rotating TTS, which the authors construe as evidence for a disc
-locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
-period$ relationship extending into the BD mass regime, this faster
-rotation in younger mass objects is taken as evidence for a decreasing
-effectiveness of the angular momentum removal of the disc locking
-mechanism, i.e. imperfect disc locking. In addition,
-\cite{2004A&A...419..249S} argue that when compared with data from
-younger clusters disc lifetimes can be seen to decrease with central
-object mass.
-
-\cite{2005A&A...429.1007S} study rotation period data for stars in the
-vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
-\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
-\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
-variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
-for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
-some BD objects with irregular variability indicative of accretion hot
-spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
-the mass-period relationship of these data in comparison with data
-from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
-\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
-Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
-Ori sample has an age of around 2$-$3 Myrs or there is still
-significant disc locking (concluded using the slope of the mass-period
-relation). More specifically for the BD mass regime, they find
-\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
-lower period limit of 2$-$4 hours, therefore at any age a fraction of
-BD stars rotate at short and constant period. Given that these objects
-should spin up as they hydrostatically contract they invoke rotational
-braking in the BD mass regime as a mechanism of removing significant
-angular momentum.
-
-\cite{2003ApJ...594..971J} study the rotational periods of BD (and
-very low mass stars) in the Chameleon I region. This region is $\le$ 1
-Myrs old, and the authors find rotation periods of 2.19, 3.376 and
-3.21 days for their BD mass counterparts. Using supplementary data
-from the literature \cite{2003ApJ...594..971J} propose that a shorter
-lifetime of $\approx$5 Myrs for accretions discs around BDs is more
-probable and is inferred from the derivation of a shorter locking
-timescale. However, as discussed in the previous studies, an imperfect
-disc locking mechanisms is also hypothesised as responsible for the
-less significant loss in angular momentum out to ages of 10 Myrs. The
-data mentioned above and other datasets are summarised and discussed
-in \cite{2007prpl.conf..297H}, where a strong argument for the
-mass-period relationship can be found, shown in their Fig 6, alongside
-further support for either a shorter disc lifetime or imperfect disc
-locking mechanism for BD stars.
-
-Therefore, in summary, it is currently unclear if any disc locking
-mechanisms efficiency or disc lifetimes are a function of mass, with
-an associated phase change over the TTS to BD mass limit. Rotation
-rate and disc presence data are being used to explore issue.
-Therefore, to create a set of useful models to help contextualise the
-observational constraints we must adopt a realistic, and bounding,
-range of rotation rates. For our model grid, and associated age range
-($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
-placed at around the approximate median for the faster rotating
-samples, providing a useful benchmark for exploring possible detection
-limits of faster rotators with discs. The longer period is set at the
-approximate edge of the slow rotating tail, providing a limiting case
-for the slower rotating, disc-locked, candidates.
-
-\subsection{Areal Coverage}
-\label{par_cov}
-
-As discussed in Section \ref{par_rotation} evidence for irregular
-periodic variability has been found in BD stars with detections of
-associated stellar discs. This is construed as evidence for accretion
-hot spots formed as magnetically channeled material hits the stellar
-surface \citep[see discussion
-in][]{1995A&A...299...89B,2007prpl.conf..297H}. The irregularity is
-thought to be caused by changes in the magnetospheric structure and
-accretion rate \citep{1995A&A...299...89B}. For our model we have
-assumed that disc material is disrupted at the co-rotation radius and
-channeled onto the star in the form of accretion hot spots with a
-characteristic temperature. Therefore, to calculate the characteristic
-temperature and the resulting blackbody accretion flux we must adopt
-an accretion rate and areal coverage of the accretion stream.
-
-Little observational evidence can be found for approximate sizes of
-accretion hot spots due to their more transient nature and often
-smaller coverages, when compared to cooler or `plage' spots
-\citep{2007prpl.conf..297H}. \cite{1995A&A...299...89B} modeled the
-size of the cool spots on solar-type stars for a selection of
-periodically variable candidates. They found projections of cooler
-spots, onto the stellar disc, of a few to ~60\%.
-\cite{1995A&A...299...89B} also found projected sizes, onto the
-stellar disc, of typically a few \% to around 10\% for hot spots.
-\cite{1996AJ....112.2159B} used observations of YY Orionis monitoring
-flux amplitude variations as a function of wavelength to derive a
-probable hot spot area of around 10\%. The spot temperature was also
-modeled for YY Orionis in \cite{1996AJ....112.2159B}, resulting in a
-best fitting areal coverage of 11\%. Therefore, to bound the probable
-areal coverage range of the accretion hot spots we have adopted areal
-coverages of 1 and 10\%.
-
-\subsection{Accretion Rate}
-\label{par_accn}
-
-Accretion rates derived for pre-MS stars are of order -6 to -11
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$ \citep{2006A&A...452..245N}.
-With the largest accretion rates found in so-called FU Orionis type
-objects (after the object where they were first observed). For the
-more typical accretion rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9}
-M_{\odot}yr^{-1}$, for TTS,][]{2009arXiv0901.4120D}, several studies
-have now suggested that the accretion rate is strongly correlated with
-the mass of the central star. This relationship was perhaps first
-suggested by \cite{2003ApJ...592..266M} using various accretion
-diagnostics. Later, \citep{2005ApJ...625..906M} derived a relationship
-of approximately $\dot{M}\propto M_*^{~2}$. Further evidence was put
-forward by \cite{2004A&A...424..603N}, where accretion rates as low as
-5$\times$ 10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More
-recently, even lower accretion rates of $\approx$10$^{-13}M_{\odot}
-yr^{-1}$, have been derived for BDs by \cite{2009arXiv0901.3684H}.
-Further support for a dependence of accretion rate on stellar mass was
-apparent in the significantly more homogeneous dataset of
-\cite{2006A&A...452..245N}. \cite{2006A&A...452..245N} analysed a set
-of accretion rates and masses derived for pre-MS stars in $\rho$
-Ophiuchi and compared these results to stars in Taurus. They found
-that the accretion rate scales with central object mass, into the BD
-regime. However, work by \cite{2006MNRAS.370L..10C} suggests that much
-of this result is likely to be caused by biases and sensitivity
-limits.
-
-For any $\dot{M}\propto M_*$ relationship to be ratified, clearly, the
-associated mass derivations must be shown to be accurate. For the BD
-mass regime it has been demonstrated that classification, either
-spectroscopic or photometric, and therefore accurate mass derivation
-is exceedingly difficult for BDD systems
-\citep{2004MNRAS.351..607W}. The inclusion of significant levels of
-accretion flux will act to exacerbate this problem. Essentially, as BD
-mass objects have relatively cool photospheres, compared to the
-temperature of the accretion hotspots, meaning that for lower
-accretion rates, than for their CTTS counterparsts, the accretion flux
-dominates the small wavelength regime of the SED.
-
-Therefore, to strengthen, or reject, any stellar mass to accretion
-rate relationship, the limits of observational classification (and
-mass derivation) of accreting BDD systems must be understood. To
-provide a benchmark model grid of such systems, with which to aid
-interpretation of the observational data, we must select a range of
-accretion rates including and exceeding those detected for systems
-previously classified as BDs.
-
-As the relationship $\dot{M}\propto M_*^{~2}$ predicts lower accretion
-rates for BD mass objects it is essential that we model systems at
-higher accretion rates, which may have been missed in current
-observational studies. Therefore, we have adopted accretion rates of
--6, -7, -8, -9, -10, -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$.
-
-\subsection{Disc Mass}
-\label{par_mdisc}
-
-A further required input parameter is the mass of the circumstellar
-disc. Previously studies modeling BD discs have adopted a range of
-disc mass fractions, for instance \citep{2004MNRAS.351..607W} use 0.1,
-0.01 and 0.001$M_*$. \cite{2002ApJ...564..887W} fit observed spectra
-with modeled SEDs to derive a disc mass of 0.003$M_*$, for HH 30
-IRS. Subsequent derivations of disc masses have converged to within an
-order of magnitude, with the following specific results: 0.03$M_*$
-\citep[$\rho$ Ophiuchi,][]{2002A&A...393..597N}, 0.055$M_*$ \citep[GM
-Aurigae,][]{2003MNRAS.342...79R}, 0.03$M_*$ \citep[GY 5, GY 11, and GY
-310,][]{2004ApJ...609L..33M} and 0.022$M_*$\citep[2MASS
-J04442713+2512164,][]{2008A&A...486..877B}. As the derived disc masses
-all have a similar order of magnitude we have adopted $M_{\rm
-  disc}\approx $0.01$M_*$. As changes in disc masses are expected to
-change the resulting SED less than perhaps, accretion rate for
-example, we have not varied the disc mass for this study. The results
-of simulations varying this parameter will be published in a future
-paper.
-
-\subsection{Inclination}
-\label{par_inc}
-
-Discs around BD stars exhibit increased flaring, due to the reduced
-surface gravity in the disc \citep{2004MNRAS.351..607W}. This
-increased flaring, and therefore larger scaleheight of the disc
-results in a smaller opening angle, when compared to higher mass stars
-and their circumstellar discs. As has been shown in
-\cite{2004MNRAS.351..607W} effects caused by variations in the system
-inclination angle are much more significant for BDD systems, again
-compared to their higher mass analogues. Therefore, we have simulated
-ten observer to system inclination angles spaced evenly in
-$cos(inclination)$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
-and 90$^{\circ}$.
-
-A final list of all varied parameters and their values can be seen
-in Table \ref{par_space_table}.
-
-\begin{table*}
-\begin{tabular}{|l|l|}
-Input parameter&Values (\# values)\\
-\hline
-Mass ($M_{\odot}$)&0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 (8)\\
-Age (Myr)&1 \& 10 (2)\\
-Rotation period (days)&0.5 \& 5 (2)\\
-Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
-Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&-6, -7, -8, -9, -10,
--11 \& -12 (7)\\
-Disc mass ($M_*$)&0.01 (1)\\
-Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
-(10)\\
-\end{tabular}
-\caption{List of all varied input parameters. Resulting in a total
-  number of models of 448 (plus 40 models without radiative transfer
-  simulations for the naked BDs) and 4480 SEDs (plus 40 for naked
-  BDs). \label{par_space_table}}
-\end{table*}
-
-GOT HERE NEEDS ALOT OF RE-READING FROM HERE ON IN**
-
-\section{Result and Analysis}
-\label{results}
-
-Uncertainty remains over the formation mechanisms, resulting IMFs and
-subsequent interaction mechanisms with associated circumstellar disc,
-for BDs. Furthermore, no current theoretical explanation can be
-demonstrated for the suspected stellar mass-accretion rate
-relationship \citep[$\dot{M}\propto
-M_*^2$,][]{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}
-derived from observations. In addition doubt remains over the
-existence of a disc-locking mechanism in BDD systems, with predictions
-of a correlation of rotation rate with infrared excess possibly
-providing an intrinsic bias \citep{1997AJ....114..288M}. Theoretical
-models are built upon constraints, such as ages, masses and disc
-fractions, and correlations, such as the accretion rate to stellar
-mass relation and rotation rate to period relation (disc-locking),
-derived from the data. Critically, these resulting constraints and
-relationships involve both the application of existing models, such as
-isochrones to derive ages, and the selection of bias-minimised
-samples, for instance removal of foreground or background contaminant
-stars. Clearly, if one is to adopt a new theoretical model or use an
-observed correlation as a constraint one must explore the suspected
-intrinsic biases and the reliability of the selection criteria.
-
-For our model grid we have selected a range of input parameters
-covering expected, from observations, ranges. We have input the
-fundamental parameters of age and mass by adoption of a set of
-theoretical isochrones. We have intrinsically included a correlation
-of rotation rate with initial inner edge position by setting this at
-the co-rotation radius, which is expected to result in a correlation
-of rotation rate with IR excess \citep{1997AJ....114..288M} (the
-reverese of that expected due to angular momentum loss through
-disc-locking). We have not assumed a relationship between accretion
-rate and stellar mass for our model grid. Therefore, analysis of our
-model grid in an attempt to recover the fundamental parameters of age
-and mass, and show accretion rate to stellar mass or rotation rate to
-infrared excess relationships, will allow us to assess the reliability
-of these current theoretical models or relationships.
-
-In this Section we first discuss the physical structure, both density
-and temperature, of the BDD disc systems (Section \ref{disc_struct}
-across our parameter space. Then we discuss the resulting simulated
-SEDs for these BDD systems (Section \ref{sed_analysis}). Finally, we
-produce simulated photometric observations (Section
-\ref{photometry}). These simulated observations allows us to show that
-recovery of the input masses and ages for our accreting BDD systems is
-unreliable. We show that despite and intrinsic relationship between
-rotation rate and initial inner edge position we do not recover a
-rotation rate correlation with IR excess. In addition, despite not
-intrinsically including a dependence of accretion rate on stellar mass
-in our grid. We show that current observational techniques and
-theoretical models applied to the grid would result in a relationship
-of this type being derived.
-
-\subsection{Disc Structure}
-\label{disc_struct}
-
-The initial density structure in our BDD systems is setup as described
-in \cite{2004MNRAS.351..607W} with the the disc surface density
-conserved, $\Sigma ^{\beta - \alpha}$. The intial scaleheight,
-$h\propto r^{\beta}$, where r is the radial distance from the star,
-and the density, $\rho \propto r^{-\alpha}$. The initial values of
-$\alpha$ and $\beta$ where 2.1 and 1.1 respectively \citep[see][for
-full discussion of disc structure]{2004MNRAS.351..607W}. The values
-for $\alpha$ and $\beta$ where chosen to optimise resolution of the
-vertically evolving disc, but minor variations are largely
-inconsequential as the systems evolves from this state. In our models
-we have, however, placed in the inner disc edge at the co-rotation
-radius, as opposed to the dust destruction radius used in
-\cite{2004MNRAS.351..607W}. The initial disc scaleheight at 100 AU,
-$h(100)$, was set to 25 AU. As the simulation used vertical
-hydrostatic equilibrium and dust sublimation, both the disc
-scaleheight and inner edge location then evolved in the systems
-dependent on the input parameters. I this section we discuss the
-structure of the discs in terms of these two generated
-characteristics, i.e the disc scaleheight and inner edge location.
-
-\subsubsection{Disc Flaring}
-\label{disc_flaring}
-
-As discussed in \cite{2004MNRAS.351..607W} the scaleheights of discs
-around CTTS stars have scaleheights at 100 AU of between $h$(100)$=$7
-to 20 AU, whereas for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and
-0.01 $M_{\odot}$ respectively). Our models adopt the same formalism
-for solving hydrostatic equilibirum and therefore, at negligible
-accreion rates, our disc scaleheights are comparable (**). As the
-accretion rate increases the flux levels of the central star increase
-and lead to heating of the disc. This in turn leads to vertical
-expansion in the disc. For our models we found that levels of vertical
-flaring increased marginally with accretion rate. Significant
-differences, more than $>$5 AU increase in $h(50)$, in the vertical
-structure where not apparent until the high accretion rates of -7 and
--6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. Figures \ref{flare_-12_183}
-and \ref{flare_-7_193} show the density structure ($log({\rho})$) in
-the disc from radial distances of 0 to 50 AU for an example systems
-($M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5 and areal coverage=10\%),
-at accretion rates of -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/flare_-12_183.ps"
-   hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
- \caption{Figure showing the density structure ($log({\rho}$) of the
-   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
-   coverage=10\% and accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-   \label{flare_-12_183}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/flare_-7_193.ps"
-  hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
-\caption{Figure showing the density structure ($log({\rho}$) of the
-  BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
-  coverage=10\% and accretion rate of -7
-  log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-   \label{flare_-7_193}}
-\end{figure}
-
-Figure \ref{flare_-12_183} shows that for a typical BDD system the
-resulting disc is highly flared and therefore, the opening angle for
-stellar radiation is much smaller. As discussed the flaring for BDD
-systems was found to be larger than CTTS systems by
-\cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
-degree of disc flaring depends on the disc temperature structure and
-the mass of the central star, with the disc scaleheight $h\propto
-\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{1973A&A....24..337S}. Recently,
-\cite{2009arXiv0901.4445E} suggest the inverse relation of flaring
-with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
-evidence from \cite{2006ApJ...644..364A}, where SEDs for 17 systems in
-the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with
-flared or flat disc models. In general, \cite{2006ApJ...644..364A}
-find that lower mass objects achieve better fits with the flat disc
-models and higher mass objects with the flared discs.
-
-The results of \cite{2006ApJ...644..364A} show that above a mass of
-50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
-discs. Whilst at masses below 50$M_{\rm Jup}$ only one object is better
-fit by the flared disc model, with the remaining objects (10/17)
-better fit with flat models. Whether, this result is statistically
-significant enough to assert a $h\propto M_*$ is doubtful as the
-fitting process contains, presumably two fixed scaleheight
-distributions. Therefore, for our study we continue to assume that our
-flared BDD systems will have larger characteristic scaleheights than
-typical CTTS systems.
-
-A quick comparison of Figures \ref{flare_-12_183} and
-\ref{flare_-7_193} show an increase in the scaleheight at 50 AU of
-$>$5 AU, as the accretion rate moves from -12 to -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. However, despite this small
-change with high levels of accretion our grid shows scaleheights
-comparable to the work of \cite{2004MNRAS.351..607W} and as such
-result in similar consequences for the SEDs and photometric
-magnitudes. The effects of this flaring and the increase in flaring
-for very high accretion levels on SEDs and photometric magnitudes are
-discussed in Sections \ref{sed_analysis} and \ref{photometry},
-respectively.
-
-\subsubsection{Inner Edge}
-\label{inner_edge}
-
-Our models include a sophisticated treatment of dust sublimation
-(described in Section \ref{dust_edge}. In contrast to the models of
-\cite{2004MNRAS.351..607W}, who apply a dust destruction radius, we
-set the intial inner radius of the disc at the co-rotation radius of
-the system. However, as our models then sublimate dust during the
-temperature convergence routine this inner edge location may
-change. As the flux levels of the central star increase with
-increasing accretion rates the flux incident on the inner edge
-increases and leads to increasing erosion of the inner edge of the
-dust disc.
-
-As the inner edge moves its  temperature is expected  to change, this
-has been predicted to lead to a correlation of inner edge position and
-IR excess  \citep{1997AJ....114..288M}. This  may act to  bias surveys
-correlating rotation  rates with IR  excess to search for  evidence of
-disc-locking. However, the flux from  the inner edge will usually peak
-between 2 and 3$\mu$m \citep{2001ApJ...560..957D}, given that the dust
-sublimation   temperature  peaks   at  $\approx$1400K   for  canonical
-densities. This means that for  models where dust is sublimated at the
-inner edge  will have maximum temperatures of  $\approx$1400K and this
-correlation of disc position and temperature will be lost.
-
-Equation \ref{inner_eq} shows that as the rotation period, of the
-star, increases the co-rotation radius decreases. This will result in,
-initially, shorter period systems having closer and hotter inner edges
-than their longer period counterparts. In addition, if the accretion
-rate is increased in these systems the incident flux on the inner wall
-will increase leading to a rise in the temperature of the inner
-edge. At some point, in both cases the dust sublimation temperature
-may be reached, leading to a change in radial position of the wall. In
-addition, the temperature of the inner edge will then tend to a
-maximum temperature, of the dust sublimation temperature. Figure
-\ref{lum_sub} shows the total stellar luminosity (accretion luminosity
-plus the intrinsic stellar luminosity), in log($L_*/L_{\odot}$)
-against the change in inner disc location, $R_{\rm co}-R_{\rm inner}$
-in AU (\textit{top panel}) and $R_*$ \textit{bottom panel}. Ths change
-in inner edge location is from the initially set co-rotation radius to
-the final radius after dust sublimation, if applicable.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/lum_sub.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing the combined stellar luminosity (accretion
-   plust intrinsic stellar luminosity) in units of
-   log($L_*/L_{\odot}$) against the change in inner edge location
-   shown in units of AU (\textit{top panel}) and $R_*$ (\textit{bottom
-     panel}).
-   \label{lum_sub}}
-\end{figure}
-
-The \textit{top panel} of Figure \ref{lum_sub} shows that as the
-luminosty increases the total change in the inner radius increases as
-more of the disc is sublimated. The total change for lower
-luminosities at lower than ~0.2 log($L_*/L_{\odot}$) is small (less
-than ~0.02 AU). As the luminosities increases to larger, and extreme
-values, due to increasing accretion, the dust sublimation
-increases. In the \textit{bottom panel} the change in inner radius
-tends towards around ~120 $R_*$. Increases in accretion rate, for
-extreme accretors, dominates the increase in stellar luminosity. As
-pre-MS stars age they contract. Therefore, for lower accretion rates,
-younger, and therefore larger stars will have greater luminosities
-than the equivalent older stars. Therefore, the major contributors to
-the X-axis of Figure \ref{lum_sub} are controlled by the input
-parameters of accretion rate and age. The initial inner wall radius
-was set as the magnetic co-rotation radius (see Section
-\ref{physics}). This distance is a strong function of rotational
-period, with $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
-\ref{inner_eq}) which is in turn a function of stellar radius. The
-stellar radius itself is then a function of the stellar
-age. Therefore, the initial inner wall edge position will change as a
-function of the input variables of rotational period and age. The
-initial position of the inner edge will control the amount of the
-stellar flux intercepted by the inner edge wall. Therefore the amount
-that the disc will be sublimated will also be a function of the
-initial position of the inner edge.
-
-Figure \ref{delta_radius} shows the initial inner edge position, or
-the co-rotation radius ($R_*$) against the change in inner edge
-location ( $R_{\rm inner}-R_{\rm co}$, $R_*$). The \textit{panels} of
-Figure \ref{delta_radius} then shows these data for two accretion
-levels and at the two ages and rotation periods. These input variables
-for our model grid are the underlying variables controlling, as
-discussed, the dust sublimation process. The \textit{top panels} are
-for models with accretion rates of -9, -10, -11 and -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, classed as typical accretors
-here and throughout the rest of this work. The typical accretors are
-then separated further into three groups in the \textit{top left
-  panel} specifically, -9, -10 and -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (blue, red and black dots
-respectively). The \textit{bottom panels} show the data for models with
-accretion rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-(blue, red and black dots respectively), which we have classed as
-extreme accretors. The \textit{right panels} show the data seperated
-by age, with 1 and 10 Myrs (as crosses and triangles respectively),
-and rotation period, with 0.5 and 5 days (as red and blue symbols
-respectively).
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/delta_radius.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing data for the co-rotation radius ($R_{\rm
-     co}$) against the change in inner edge location ( $R_{\rm
-     inner}-R_{\rm co}$) both in units of $R_*$. The typical accretors
-   are shown in the \textit{top panels} and the extreme accretors in
-   the \textit{bottom panels} (see text for explanation). The
-   accretion rates are then further subdivided. The \textit{top left
-     panel} shows accretion rates of -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, red and black dots
-   respectively. In the \textit{bottom left panel} accretion rates of
-   -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as
-   blue, red, and black dots. In addition the \textit{left panels}
-   seperates the systems by age and period. The systems with ages of 1
-   and 10 Myrs are shown as crosses and triangles respectively. The
-   systems with rotation rates of 0.5 and 5 days are then shown as red
-   or blue symbols respectively. \label{delta_radius}}
-\end{figure}
-
-The classification of models into typical and extreme accretors is
-based on observations (see discussion in \ref{par_accn}) and also
-evidence from the simulations themselves. Figure \ref{delta_radius},
-\textit{left panels}, shows that dust sublimation does not become
-significant until accretion rates of around -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and increases dramatically with
-increasing accretion rate thereafter.  This accretion rate, -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, is also, unsurprisingly the
-accretion rate at which the underlying photospheric emission is
-overwhelmed by the accretion flux, and the photospheric features are
-lost (see Section \ref{sed_analysis}). The \textit{right panels} of
-Figure \ref{delta_radius} show that dust sublimation occurs only for
-rotation periods of 0.5 days for typical accretors. For the extreme
-accretors the systems with both rotation periods undergo sublimation
-but the effect is more significant in the systems with shorter
-rotation periods.  The \textit{right panels} also show that for
-extreme accretors the older systems undergo more dust sublimation,
-whereas for the typical accretors the older systems undergo little or
-no dust sublimation.
-
-The density of material in the disc falls with increasing radius from
-the star ($\rho\propto R_*^{\alpha}$). The dust sublimation
-temperature is also density dependent
-\citep{1994ApJ...421..615P}. Therefore, for systems where the inner
-edge has been eroded significantly from the co-rotation radius the
-temperature of the inner edge will fall as the final radius
-increases. In this case a correlation of inner edge temperature and
-inner edge radius is expected with a resulting slope determined, at
-least in part, by the radial density distribution of the disc. In this
-case the the final inner edge radius and therefore temperature is no
-longer strongly correlated with the rotation rate. Figure
-\ref{inner_temp} shows the final inner edge location ($R_{\rm inner}$,
-($R_*$) against the Temperature of the inner wall ($T_{\rm inner}$,
-(K)). The \textit{left panel} shows the systems designated as typical
-accretors and the \textit{right panel} those with extreme accretion
-rates. For \textit{both panels} the systems with rotation periods of
-0.5 and 5 days are plotted in read and blue respectively. Those
-systems where the change in inner radius was greater than 1$R_*$, and
-therefore classes as significantly sublimated, are plotted as
-crosses. These systems are only present for the extreme accretors, as
-shown in Figure \ref{delta_radius}. Furthermore, for the typical
-accretors Figure \ref{delta_radius} shows that only the shorter period
-objects, in general, experience any disc erosion at the inner
-edge.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/inner_temp.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing data for the inner edge location ($R_{\rm
-     inner}$, $R_*$). The typical accretors are shown in the
-   \textit{left panel} and the extreme accretors in the \textit{right
-     panel} (see text for explanation). In \textit{both panels}
-   seperate the systems by period, with those systems with rotation
-   periods of 0.5 and 5 days shown as red and blue symbols
-   respectively. In addition systems where the total change in the
-   inner radius is greater than 1$R_*$ are marked as crosses (this is
-   only achieved by some systems classed as extreme
-   accretors).\label{inner_temp}}
-\end{figure}
-
-Figure \ref{inner_temp} shows that for those systems where signifcant
-disc erosion ($\Delta R_{\rm inner} > 1.0 R_*$) has occured the
-resulting temperature of the inner edge is weakly correlated with the
-inner edge radius, but, critically, not correlated with rotation
-rate. The inner edge temperatures of the remaining systems for the
-extreme accretors are slightly anti-correlated with the radius to the
-inner edge. For the systems with typical acccretion rates, and longer
-periods, Figure \ref{inner_temp} shows there is a again a weak
-correlation between the radius to, and the temperature of the inner
-edge. For the shorter period models with typical accretion rates ther
-is no clear correlation between the temperature at the inner edge and
-radius to this edge. The \textit{left panel} of Figure
-\ref{inner_temp} shows that, taken as a whole, our models with typical
-accretion rates show a clear correlation between the temperature at
-the inner edge and the radius to this boundary. This agrees with the
-work of \cite{1997AJ....114..288M} where this correlation is found for
-there $R_{\rm inner}=$1$-$12$R_*$ and $\dot{M_{\rm acc}}=$10$^{-9}$to
-10$^{-5} M_{\odot}yr^{-1}$, for flat disc
-models. \cite{1997AJ....114..288M} use correlation, and the derivation
-of IR magnitudes, to predict a relationship between IR excess and
-radius to the inner wall. Our data indicate that this correlation, for
-typically accreting systems will translate into a correlation between
-rotation rate and IR excess. This could have important implications
-for studies of disc-locking where disc presence is examined as a
-function of rotation rates, provide an intrinsic bias. In practice
-however, this correlation is weak, if observable, in our data due to
-inner disc wall shape, inclination and flaring effcts. This is
-discussed in more detail in Section \ref{photometry} **.
-
-For simulations without dust sublimation, and analytic density
-distributions, the inner disc edge is characterised solely by the
-intial disc density prescription. If one includes vertical hydrostatic
-equilibrium the scaleheight of the disc inner edge can change but the
-radial distribution of dust will not. Dust sublimation physics will
-alter the vertical structure, but crucially will also alter the radial
-distribution of dust. This means that dust sublimation effects will
-control the shape of the inner disc wall and possibly change this from
-a vertical wall.  Evidence that real inner disc boundaries (for CTTS)
-are not vertical walls comes from a lack of dependence of the derived
-IR excess on system inclination \citep{2007ApJ...661..374T}. As
-discussed in Section \ref{dust_edge} the disc inner hole can be
-created by several mechanisms, however, for this study we have only
-included a treatment of magnetic truncation (initially) and subsequent
-dust sublimation. The effects of dust sublimation have been shown to
-produce curved inner walls due to the temperature and density
-dependence of the dust sublimation temperature
-\citep{2005A&A...438..899I}. The curved boundary in this case is
-concave, as density increases towards the midplane of the disc, the
-dust sublimation temperature increases, meaning the destruction radius
-moves closer to the star. A curved inner boundary is also found to
-result from dust sublimation in \cite{2007ApJ...661..374T}. In
-\cite{2007ApJ...661..374T} two populations of dust grains where
-included with different scaleheight distributions. This is essentially
-a simple model of grain growth and subsequent midplane
-settling. \cite{2007ApJ...661..374T}, found a convex inner disc
-boundary, this is due to the larger grains cooling more
-efficiently. These larger grains dominate the dust towards smaller
-vertical distances from the midplane, and therefore the increased
-cooling means that the dust sublimation temperature is reached at
-closer radii. The implications of the inner edge shape for the
-simulated SEDs and photometry are discussed in Section
-\ref{sed_analysis} and \ref{photometry}.
-
-For systems where dust sublimation does not occur, or is minimal the
-inner edge of the system will remain as a vertical wall, as perscribed
-by our initial density distribution. However, as one increases the
-flux levels of a given system, by increasing the accretion rates (or
-moving to younger ages) the inner edge will increase in
-temperature. As the flux levels increase, in a given model, the dust
-at the inner edge will sublimate. The dust in the regions of lowest
-density or maximum flux interception will be preferentially
-destroyed. This will lead to a reduction in the scaleheight and a
-slight concave cavity at the inner wall. The inner edge will then move
-towards a convex boundary as the inner edge is forced radially outward
-towards regions of lower density with increasing flux levels. This
-outward movement will result in the outer, vertical, regions of the
-dust disc eroding. Increasing the flux still further will lead to
-significant dust sublimation and an outward migration. This subsequent
-migration will move the inner edge into regions of lower density and
-greater scaleheight.
-
-The transition in shape and position of the inner edge for a given
-model as the accretion rate, and therefore flux levels, are increased
-is shown in Figures \ref{no_sub_183} to \ref{sub_181}. The model
-chosen for illustrative purposes has the following parameters,
-$M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%. The model
-shown in Figure \ref{no_sub_183} has $\tau$=5 days and accretion
-rate=-12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (model shown in Figure
-\ref{flare_-12_183}), with Figures \ref{sub_169} to \ref{sub_181}
-showing models with $\tau$=0.5 days and accretion rates=-12, -9, -7
-and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. The \textit{right
-  panels} of Figures \ref{no_sub_183} to \ref{sub_181} show the
-temperature structure of the final converged disc structure. The
-\textit{left panels} of Figures \ref{no_sub_183} to \ref{sub_181} show
-the final log($\rho$) distribution for regions where dust is present,
-scaled to a different minimum density (log($\rho_{\rm min}=1^{-13}$)
-compared to Figures \ref{flare_-12_183} and \ref{flare_-7_193}. The
-lower (log) density threshold is used in this case to better trace the
-inner edge and denser regions of the disc, whereas Figure
-\ref{flare_-12_183} and \ref{flare_-7_193} show the outer diffuse
-regions of the disc, or disc limits. Additionally, for Figures
-\ref{sub_169} to \ref{sub_181} (the sublimated systems), the
-\textit{right panels} also show the initial density, in the same units
-as the final density, this is shown as a background grey scale (with
-the same maximum and minimum as for the final density) to illustrate
-the effects of sublimation.
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
-  \caption{Figure showing final density (log($\rho$)) where dust is
-    present (colour scale) as the \textit{left panel} and temperature,
-    \textit{right panel}, for a system with no dust
-    sublimation. System parameters are: $M_*$=0.04$M_{\odot}$, Age=1
-    Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate=-12
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
-  \label{no_sub_183}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_169_density.ps}\label{sub_169_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_169_temp.ps}\label{sub_169_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-12
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
-  \label{sub_169}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_175_density.ps}\label{sub_175_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_175_temp.ps}\label{sub_175_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-9
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
-  \label{sub_175}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-7
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
-  \label{sub_179}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-6
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
-  \label{sub_181}
-\end{figure*}
-
-Figure \ref{no_sub_183} shows the inner disc edge as a vertical wall
-with no dust sublimation, the inner wall has not changed location from
-the initial disc description. The \textit{right panel} of Figure
-\ref{no_sub_183} shows that the corresponding temperature structure is
-smooth and interpolation at the inner edge yields a temperature of
-~900K. For the shorter period model the inner edge has undergone some
-dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
-shows that the inner edge has lost dust slightly, peferentially, along
-the midplane. Again for Figure \ref{sub_169} the change in inner edge
-location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
-sublimation (and inner wall) temperature is ~1450K, for a density of
-~$2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
-\ref{sub_169}).The \textit{left panel} of Figure \ref{sub_169} shows
-that for even for a negligible accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, sublimation has begun to erode
-the inner edge, for the younger and faster rotating systems. Here the
-final density distribution has moved radially outward as can be seen
-by comparing the grey and colour scales in the \textit{left panel} of
-Figure \ref{sub_169}. Additionally, the inner edge has become slightly
-concave. As the flux levels of the central star increase the
-temperature of the inner edge surpasses the sublimation temperature at
-an increasing radius, destroying more of the disc an pushing the inner
-edge radially outwards. The \textit{left panel} of Figure
-\ref{sub_175} shows that for an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, increased sublimation has
-pushed the inner wall slightly farther from the star (wehn compared to
-Figure \ref{sub_169}), here, $\Delta R~0.52R_*$ ($~1.1\times
-10^{-3}$AU), and $T_{\rm inner}~1450$. Again the final density
-distribution has moved radially outward as can be seen by comparing
-the grey and colour scales in the \textit{left panel} of Figure
-\ref{sub_175}. The \textit{right panel} of Figure \ref{sub_175} shows
-that the gas interior to the inner edge extending down to the
-co-rotation radius, which is not sublimated, will reach temperatures
-in excess, or equal to, the inner edge, which in this model is
-~1400K. Such hot gas inner discs interior to the dust disc have been
-postulated through SED fitting
-\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Again, the shape of
-the inner wall has changed in Figure \ref{sub_175}, the top and bottom
-sections of the disc have eroded and the inner wall is convex. The
-model in Figure \ref{sub_175} has an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, which is the transition point
-between our two groups of accretors, typical and extreme. Figure
-\ref{sub_175} shows that for typical accretion rates, and faster
-rotation periods (and younger ages) signicant dust sublimation is
-expected to occur at the inner edge, resulting in a curved inner wall
-at around ~1400K. Increasing the accretion rate, and therefore flux
-levels, still further leads to significant erosion of the inner disc.
-For the extreme accretors the dust sublimation at the inner edge now
-changes the inner wall position by many multiples of the stellar
-radius. Figures \ref{sub_179} and \ref{sub_181} are for systems with
-accretion rates typical in outburst or episodic accretion systems, -7
-and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ respectively. The inner
-edges for these sytems are eroded radially by 7.1 and 36.1 ($R_*$)
-respectively (0.016 and 0.080 AU, respectively), visible by comparing
-the grey and colour scales of Figure \ref{sub_179} and
-\ref{sub_181}. As this occurs the disc inner edge moves far enough
-that the density drop (with radius) occuring in the disc causing the
-sublimation temperature to fall. Consequently the disc inner edge
-becomes cooler as it can not sustain temperatures above the
-sublimation temperature. This is shown in the \textit{right panels} of
-Figures \ref{sub_179} and \ref{sub_181}, with approximate temperatures
-at the inner edge of 1370 and 1260K. In addition, the inner edge has
-become concave and, again due to changes in the underlying disc
-density distribution, much larger in scaleheight.
-
-A similar sequence is apparent across the grid for set
-masses. However, the balance of the rotation period, and therefore
-inner edge location, and age and areal coverage, therefore flux
-levels, leads to changes in the accretion rate at which the dust
-sublimation starts. However, in almost all cases the dust sublimation
-does not become significant until at least -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as discussed above).
-
-\subsection{SEDs}
-\label{sed_analysis}
-
-The resulting converged disc structures, as discussed in Section
-\ref{seds} are then used to create simulated SEDs. In this section we
-explore features in these derived SEDs and link them back to the
-physical structures within the disc discussed in Section
-\ref{disc_struct}. For analysis purposes our SEDs will comprise
-contributions from four main luminosity sources. Firstly, the
-accretion luminosity ($L_{\rm acc}$) and the intrinsic stellar
-luminosity ($L_{*}$), will effectively be combined and provide flux at
-the shorter wavelength section of the SED. For our parameter space the
-temperature of the photospheres has a range of ~3000K$<T_{\rm
-  eff}$1600K, this will comprise flux contributions peaking in the
-range, 0.97 to 1.8 $\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
-    acc}}$). The accretion spot temperatures, for typical accretors,
-will range from ~340$>T_{\rm acc}>$9400K, emitting in the range 0.3 to
-8.5 $\mu$m. For the extreme accretors temperatures can reach as high
-as 53,000K, provide flux to $~$0.05 $\mu$m. The second pair of
-luminosity sources are from consituent parts of the circumstellar
-disc. The inner edge, ($L_{\rm wall}$), at temperatures of ~370 to
-~1500K, or flux contributions from ~1.85 to 7.7 $\mu$m
-\citep[nominally 2 to 3 $\mu$m][]{2001ApJ...560..957D}, and the outer
-disc ($L_{\rm disc}$), at temperatures of ~300K or less contributing
-flux longward of ~10 $\mu$m. As discussed in Section \ref{seds} the
-{\sc torus} radiative transfer code tags the photons before they
-reach the simulated observe in one of four ways, stellar and thermal,
-either direct or scattered. These components allow us to analyses the
-contributions from the main flux contributors discussed, i.e. $L_{\rm
-  acc}$ and $L_*$ equals stellar scattered or direct, with thermal
-emission comprising $L_{\rm wall}$ and $L_{\rm disc}$. Figure
-\ref{disc_eg_173} shows a typically accreting BDD system with the
-component photon contributions highlighted, with $M_*=0.04M_{\odot}$
-at 1 Myr with an areal coverage of 10\%, accretion rate of -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
-days. The solid black line is the total simulated SED, with the
-stellar photons shown as blue lines and the thermal as red. The
-scattered and direct contributions are then shown as dashed and solid
-lines respecitvely. The horizontal and vertical dotted lines then show
-the approximate ranges of the flux contributions from the (from left
-to right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red)
-and $L_{\rm disc}$ (black).
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/disc_eg_173.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing the SED (log($\lambda \mu$m against
-   log(flux), flux in ergs$/s/cm^2/\AA$) for $M_*=0.04M_{\odot}$ at 1
-   Myr with an areal coverage of 10\%, accretion rate of -10
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
-   days. The solid black line is the total simulated SED. The stellar
-   components of the flux are shown in blue and the thermal in read,
-   with direct emission appearing as solid lines and scattered photons
-   as dashed lines. The vertical dotted bars linked by horizontal bars
-   show the approximate (log) wavelength ranges of the luminosity
-   components. With the blue lines denoting the accretion luminosity
-   ($L_{\rm acc}$) and the first (left to right) black lines showing
-   the photospheric contribution ($L_*$). The final two sets of lines
-   show the inner edge contribution ($L_{\rm wall}$) in red and the
-   outer disc ($L_{\rm disc}$) in black. \label{disc_eg_173}}
-\end{figure}
-
-Figure \ref{disc_eg_173} shows that the photosphere and accretion
-luminosities dominate the SED at wavelengths shortward of
-~1$\mu$m. After this, for this model, the SED is dominated by
-contributions from the disc, at shorter wavelengths, the inner edge
-and then at larger wavelengths the outer disc. As shown in Figure
-\ref{disc_eg_173} the intrinsic stellar photosphere and accretion
-luminosities overlap, in terms of peak wavelength of emission. This
-overlap essentially means that the combined stellar flux ($L_*+L_{\rm
-  acc}$) will eventually become dominated by the accretion flux, as
-one increases the accretion rate. With the features of the intrinsic
-stellar photosphere or atmosphere eventually lost or swamped by the
-accretion flux. This will lead to difficulties in using spectral
-features to identify BDD systems for wavelengths shorter than ~1
-$\mu$m, and, of course, for wavelengths longer than this the SED
-becomes dominated by disc emission. Therefore, once the SED of a BDD
-system, at shorter wavelengths, becomes dominated by accretion
-luminosity spectral classification of these systems (or at least their
-central stars) will become unreliable. As discussed in Section
-\ref{inner_edge} observations of the inner edge location seperate the
-BDD systems into two groups, the typical accretors ($\dot{M}\leq$-9
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$) and extreme accretors
-($\dot{M}>$-9 log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$). This division
-between typical and extreme accretors is based on observational
-results (see Section \ref{par_accn}) as well as consequence of
-sublimation. The typical accretors show limited sublimation at the
-disc inner edge leading to a weak correlation in inner edge
-temperature with edge radius. Whereas, for the extreme accretors the
-inner edge is significantly eroded and the dust sublimation
-temperature reached, which can not be exceeded. This effectively means
-that the inner edge temperature is weakly correlated with temperature
-(with a different characteristic slope to the typical accretors), as
-the dust sublimation temperature is density dependent, which is in
-turn dependent on radial position (see Figures \ref{delta_radius} and
-\ref{inner_temp}).
-
-\subsubsection{Accretion Dominance}
-\label{acc_dominance}
-
-Figure \ref{acc_dom} shows the affect of the increasing accretion
-blackbody flux (for increasing accretion rates) for a BD star,
-$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photons originating from the
-star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
-{\sc torus} we can seperate these flux contributions simply by
-observing the naked star system. The panels in Figure \ref{acc_dom}
-show the flux from a naked system, with no treatment of the disc. This
-enables us to view the effect of increasing accretion rate on the
-photospheric flux in isolation. The accretion rates included in all
-panels are -8, -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-(blue, black and red lines respectively). The \textit{bottom panels}
-show the systems with a rotation period of 5 days and \textit{top
-  panels} for those with a rotation period of 0.5 days. Given our
-assumption that accretion occurs from the co-rotation radius,
-decreasing the rotational period moves this accretion radius closer to
-the star, $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
-\ref{inner_eq}). As the accretion radius moves father from the star the
-potential energy released by the accreted material is reduced. This
-effect can be seen when comparing the \textit{top} and \textit{bottom
-  panels}, although the effect is marginal for all but the highest
-displayed accretion rates. The \textit{left panels} show accretion
-streams with an areal coverage of 10\% and the \textit{left panels}
-1\%. As the areal coverage reduces the effective temperature of the
-accretion hot spot increases, resulting in an increase in accretion
-flux, and resulting shift to bluer wavelengths of the peak flux. This
-can be seen clearly by comparing the \textit{left} and \textit{right
-  panels} of Figure \ref{acc_dom}. Perhaps the most important, albeit
-qualitative, result shown is Figure \ref{acc_dom} is an insight into
-the accretion rate at which the accretion blackbody flux dominates
-over the photospheric flux. Figure \ref{acc_dom} shows that as the
-accretion rate raises above -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-for systems with 1 or 10\% areal coverage, the accretion flux
-dominates the emergent SED at both periods. Therefore for reasonable
-coverages (1-10\%) and rotational periods (0.5-5 days) the
-photospheric flux is effectively swamped by accretion flux for
-accretion rates log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-9$. This
-suggests that accreting BD systems with accretion rates as low as -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ could be difficult to identify
-from SEDs as BD stars, and may well be classified as higher mass
-stars.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the photospheric flux
-   (log(ergs$/s/cm^2/\AA$)) against $\lambda$ (log($\mu$m)) of a Brown
-   Dwarf with $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but
-   blackbody fluxes from an accretion stream at the rates of -8, -9
-   and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as blue,
-   black and red lines respectively. The \textit{bottom panels} show
-   accretion for a star rotating at 5 days, with the \textit{top
-     panels} showing that of 0.5 days. The \textit{left panels} systems
-   with an areal coverage of 10\% and the \textit{right panels} has
-   1\%.
-   \label{acc_dom}}
-\end{figure*}
-
-Therefore, the shorter wavelength component of the SED for extreme
-accretors is dominated by the accretion luminosity. For the typical
-accretors the intrinsic photospheric emission is important and the
-flux levels of this component are dependent on the stellar parameters
-of mass and age, through evolution of the stellar radius and
-temperature, as is well understood. In general, the bluer (short
-wavelength) components of the SEDs are therefore contrOlled by the
-stellar input parameters (mass and age) and the accretion input
-parameters (accretion rate and areal coverage, and to a lesser extent
-rotation rate).
-
-\subsubsection{Flaring and Obscuration}
-\label{flare_obscure}
-
-As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
-discussed in Section \ref{disc_flaring} BDD systems under vertical
-hydrostatic equilibirum have highly flared discs. As discussed in
-\cite{2004MNRAS.351..607W} this increased flaring (when compared to
-CTTS stars) leads to occulltation at the star at lower inclination
-angles and, therefore, significant changes to the SED. Increases in
-the inclination angle, for these systems, quickly lead a significant
-proportion of the stellar flux being intercepted, and reprocessed, by
-the highly flared disc. This reprossecing will lead to a change in the
-flux levels at the shorter, bluer, wavelengths as more stellar flux is
-reprocessed and intercepted by the disc. It will also lead to
-significant changes in the flux reaching the observer from the inner
-and outer regions of the disc.
-
-Figure \ref{flare_sed_fast} shows the SEDs for a range of inclinations
-for BDD systems with two accretion rates. The BDD system has a central
-stellar mass of $0.04M_{\odot}$, an age of 1Myr, a rotation period of
-0.5 days and an areal coverage of the accretion stream of 10\%. The
-\textit{top panels} show the SEDs for a star with an accretion rate of
--12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (the lowest in our typical
-accretion range). The \textit{bottom panels} then show SEDs for
-systems with an accretion rate of -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (classed as an extreme
-accretor). From left to right the \textit{panels} then show the naked
-stellar flux then the fluxes from BDD systems seen at inclination
-angles of 0$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$, or face-on, the
-approximate expectation value of inclination and edge-on. For each of
-the \textit{second} to the \textit{fourth panels} the flux components
-are then shown as in Figure \ref{disc_eg_173}, i.e. the total SED
-shown as a black line, then stellar light shown in blue and thermal in
-red, with direct shown as bold and scattered as dashed lines. The
-inset graph in the \textit{bottom right} panel of Figure
-\ref{flare_sed_fast} simply shows a lower flux scale, as the flux
-levels have fallen to the lowest shown division in the main Figure.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_sed_fast.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
-   and an areal coverage of the accretion stream of 10\%. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the naked stellar flux (\textit{first panel}), then
-   constituent fluxes for SEDs at inclination angles of 0$^{\circ}$,
-   64$^{\circ}$ and 90$^{\circ}$. The \textit{second} to
-   \textit{fourth panels} on each line then show the total flux as a
-   black line, with the component fluxes presented as explained Figure
-   \ref{disc_eg_173}. The \textit{top panels} are for systems with an
-   accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   the \textit{lower panels} are for an accretion rate of -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{bottom right
-     panel} inset Figure shows an enlargement of the lower flux levels
-   of this SED. \label{flare_sed_fast}}
-\end{figure*}
-
-Figure \ref{flare_sed_fast} shows, by comparing the \textit{top
-  panels} that as a disc is added to the system and the inclination of
-the BDD system is increased more stellar (and accretion flux) is
-reprocessed by the disc, for a negligibly accreting system. As one
-moves from inclinations of 0 to 64$^{\circ}$ the stellar flux has
-reduced as has the thermal component. At edge-on inclinations the
-system is only visible through scattered light, and some (slight)
-thermal emission from the outer disc at wavelengths $\lambda>30\mu$m
-(indicative of temperatures of ~100K. Increasing the accretion rate
-from -12 to -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ leads to a
-significant increase in the naked stellar flux (compare \textit{top
-  left} and \textit{bottom left panels}). As we add a disc and
-increase the viewing inclination for the extreme accreting system
-(\textit{bottom panels}), we also lose stellar flux. In the extreme
-accretor case however the fall in flux contribution to the total SED
-from the photosphere (and accretion) is much more significant. Indeed,
-at edge-on inclinations the system becomes only visible in the thermal
-(~100K) disc regime, with the scattered light significantly reduced.
-
-As shown in Section \ref{disc_struct}, and more specifically, Figures
-\ref{flare_-12_183} and \ref{flare_-7_193} as one increases the
-accretion rate for BDD systems, in general, the outer disc structure
-increases in vertical height. Effectively, the greater flux levels
-increase the temperature of the outer disc and the condition of
-vertical hydrostatic equilibrium leads to a vertical expansion. This
-vertical expansion leads to a significant change in the angle at which
-photons emitted from the stellar photosphere are interecepted by the
-outer disc. This is an extension of the effected found in
-\cite{2004MNRAS.351..607W}, where it was found that this effect alone
-can shift the SED, and therefore colours and magnitudes, of inclined
-BDD systems to those indicative of higher mass CTTS. The actual
-changes in flux are complicated by dust sublimation and shape changes
-of the inner edge (discussed later). As the inclination of the BDD
-system is increased we see the total flux drop significantly once we
-exceed the opening angle of the BDD system. This opening angle will
-decrease with vertical scaleheight of the outer disc. Figure
-\ref{flare_inc} shows the total SEDs for the BDD system of Figures
-\ref{flare_-12_183} and \ref{flare_-7_193}, with the coresponding
-accretion rates as \textit{left} and \textit{right panels}
-respectively. The solid lines of \textit{both panels} of Figure
-\ref{flare_inc} show the total SED for each of our ten simulated
-inclinations, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84 and
-90$^{\circ}$ (with the flux decreasing with increasing
-inclination). The dashed line then highlights the inclination at which
-the flux observed drops significantly, at 71 and 56$^{\circ}$ for the
-accretion rates of -12 and -7 (or \textit{left} and \textit{right
-  panels}), respectively. Whilst this effect is probably artificially
-enhanced for such extreme accretion rates it is illustrative of the
-general trend, notwithstanding complications from inner edge shape
-**MENTION ABOUT NOT BEING BOUND MATERIAL?**NOT ENTIRELY HAPPY WITH
-FLARESEDFAST**.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_inc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure of total SED flux reaching the observer for viewing
-   angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90$^{\circ}$. SEDs
-   shown are for systems shown in Figures \ref{flare_-12_183} and
-   \ref{flare_-7_193}, as the \textit{left} and \textit{right panels}
-   respectively. In both panels the dashed line highlights the angle
-   at which a significant fall in flux reaching the observer occurs.
-   The values of inclination at which the fall in flux occurs are
-   71$^{\circ}$ and 56$^{\circ}$ for the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, \textit{left} and
-   \textit{right panels} respectively. \label{flare_inc}}
-\end{figure*}
-
-\subsubsection{Inner Edge Shape}
-\label{inner_shape}
-
-As discussed in Section \ref{disc_struct} the addition of dust
-sublimation leads to a change in the shape of the inner edge, where
-the temperature is sufficient. Figures \ref{no_sub_183} to
-\ref{sub_181} show a range in inner edge shapes, from flat walls
-through concave to convex curves, caused by the radial density profile
-of the disc and the dependence of the sublimation temperature on
-density. This change in shape, as noted by \cite{2007ApJ...661..374T},
-will lead to changes in the characteristics of the SED, or derived IR
-excess, with inclination angle \citep{2007ApJ...661..374T}. For
-concave and vertical walls the inner edge is visible over a smaller
-range of viewing angles than for a convex inner edge.
-
-Figures \ref{typ_curve} and \ref{ext_curve} show the thermal direct
-radiation, originating from the disc, as a function of inclination for
-the two groups of accretors, typical and extreme respectively. The
-models included in Figure \ref{typ_curve} as the \textit{left} and
-\textit{right panels} are those shown in Figures \ref{sub_169} and
-\ref{sub_175} respectively. Whereas, the models included in Figure
-\ref{ext_curve} as the \textit{left} and \textit{right panels} are
-those shown in Figures \ref{sub_179} and \ref{sub_181}
-respectively. For each \textit{panel} of Figures \ref{typ_curve} and
-\ref{ext_curve} the thermal direct flux is plotted as a solid black
-line at each modeled inclination, namely, 0, 27, 39, 48, 56, 64, 71,
-77, 84 \& 90$^{\circ}$. The dashed line in each case shows where a
-significant fall in the flux reaching the observer from direct thermal
-emission from the disc is apparent.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/typ_curve.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing thermal direct flux reaching the observer at
-   inclination angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \&
-   90$^{\circ}$, for typical accretors. The \textit{left panel} shows
-   the flux from the model shown in Section \ref{disc_struct}, Figure
-   \ref{sub_169}. The \textit{right panel} shows the flux from the
-   model shown as Figure \ref{sub_175} in Section
-   \ref{disc_struct}. In both panels the dashed line highlights the
-   angle at which a significant fall in flux from direct thermal
-   emission is observed.  The values of inclination at which the fall
-   in flux occurs are 77$^{\circ}$ for \textit{both panels} and
-   therefore accretion rates. \label{typ_curve}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/ext_curve.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing thermal direct flux reaching the observer at
-   inclination angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \&
-   90$^{\circ}$, for extreme accretors. The \textit{left panel} shows
-   the flux from the model shown in Section \ref{disc_struct}, Figure
-   \ref{sub_179}. The \textit{right panel} shows the flux from
-   the model shown as Figure \ref{sub_181} in Section
-   \ref{disc_struct}. In both panels the dashed line highlights the
-   angle at which a significant fall in flux from direct thermal
-   emission is observed.  The values of inclination at which the fall
-   in flux occurs are 71$^{\circ}$ and 64$^{\circ}$ for the
-   \textit{left} and \textit{right panels}
-   respectively.\label{ext_curve}}
-\end{figure*}
-
-For typically accreting systems, where little or no dust sublimation
-has occured the inner edge remains either a vertical or slightly
-concave wall, as shown in Figures \ref{sub_169} and
-\ref{sub_175}. For these systems flux reaching an observer from
-direct thermal emission, i.e. from, in the main, the disc inner edge,
-falls rapidly with increasing viewing angle, after the maximum opening
-angle is achieved. This is shown in Figure \ref{typ_curve} where at
-the viewing angle of 77$^{\circ}$ the flux shown falls significantly,
-for both accretion rates. This opening angle is larger than found for
-the slower rotating, counter parts, as shown by Figure
-\ref{flare_inc}, where a transition in occultation occurs at
-71$^{circ}$. For the case in \ref{typ_curve} the system has the
-shorter rotation period, leading to a larger opening angle, as the
-flux from the central star does not reach the outer disc, and
-subsequently flare it. Figure \ref{typ_curve} shows that after an
-angle of 77$^{\circ}$ the flux from the inner edge falls to zero. The
-systems displayed in Figure \ref{typ_curve} have inner edge
-temperatures of ~1400K, meaning their flux emission peaks at a
-wavelength of ~2$\mu$m. The flux observed at the expected peak
-wavelength falls to zero at inclinations of 77$^{\circ}$, indicative
-of a vertical wall being obscured by the outer disc, before the limit
-of the opening angle is reached.
-
-Figure \ref{inner_inc_sed} shows the full SEDs and the components (as
-tagged by {\sc torus}), for the models displayed in Figures
-\ref{sub_169} and \ref{sub_179} and the \textit{left panels} of
-Figures \ref{typ_curve} and \ref{ext_curve}. The \textit{top panels}
-show the SEDs for an accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (model from Figure
-\ref{sub_169}) for inclinations of 64, 71 and 77$^{\circ}$, moving
-from the \textit{leftmost} to \textit{far right panel}. The same
-inclinations are shown in the \textit{bottom panels}, which show the
-SEDs, and components, for the model with an accretion rate of -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, displayed in Figure
-\ref{sub_179}. As discussed in Section \ref{disc_struct}, the model
-with the higher accretion rate has a a much larger, in scaleheight,
-and convex inner boundary. The lower accretion rate model has a
-vertical inner wall, close to the star. The analysis of Figures
-\ref{typ_curve} and \ref{ext_curve} show that the flux from the inner
-wall should fall dramitically at different limiting inclinations for
-either accretion rate.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_inc_sed.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
-   and an areal coverage of the accretion stream of 10\%. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the constituent fluxes for SEDs at inclination
-   angles of 64$^{\circ}$, 71$^{\circ}$ and 77$^{\circ}$. The total
-   flux is shown as a black line, with the component fluxes presented
-   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
-   for systems with an accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and the \textit{lower
-     panels} are for an accretion rate of -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The SEDs from the
-   \textit{top} and \textit{bottom panels} are derived from the models
-   presented in Figures \ref{sub_169} and \ref{sub_179},
-   respectively.\label{inner_inc_sed}}
-\end{figure*}
-
-Figure \ref{inner_inc_sed} shows that for negligible accretion rates
-(\textit{top panels}), where the inner edge is a vertical wall, the
-total flux falls rapidly after exceeding a viewing angle of
-71$^{\circ}$. After an inclination of 71$^{\circ}$, the negiliby
-accreting system is dominated by scattered light from the central
-star. The system accreting at -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, however, maintains high flux
-levels, and thermal contributions to the SED, for inclination angles
-above 71$^{\circ}$, particularily between 1 and 3$\mu$m. Essentially,
-as shown by comparing Figures \ref{sub_169} and \ref{sub_179}, with
-increasing flux and subsequent dust sublimation the inner edge has
-grown vertically and become convex. As shown perviously by
-\cite{2007ApJ...661..374T}, a vertical (or concave) inner edge will
-have strong dependence on inclination angel as the inner edge is
-obscured at lower inclinations. For the larger convex wall, the SEDs
-shown in \ref{inner_inc_sed} show that the resulting flux is less
-dependent on inclination angle.
-
-Once accretion rates reach extreme levels the inner edge is sublimated
-far from the central star. For these systems the resulting inner edge
-is both larger, in terms of scaleheight, and convex. Figure
-\ref{ext_curve} shows that the flux falls dramatically at an
-occultation angle of 71 and 64$^{\circ}$ for accretion rates of -7 and
--6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, respectively
-(\textit{left} and \textit{right panels}, respectively). For the
-accretion rate of -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ this is
-indicative of a larger opening angle (71$^{\circ}$) for the the
-shorter period object, when compared to the more slowly rotating
-equivalent (56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
-  panel}). Additionally, Figure \ref{inner_inc_sed} shows that the
-total SED, has a strong thermal component and is only weakly dependent
-on inclination angle, between 1 and 3 $\mu$m . This increase in
-opening angle with increase in rotation rate is again due to more flux
-being intercepted by a larger and closer inner wall. This interception
-of flux by the inner edge leads to a cooler and less vertically
-extended outer disc in the shorter period objects when compared to the
-slower rotating systems. Figures \ref{ext_curve} and
-\ref{inner_inc_sed} also shows that, contrary to the typical
-accretors, the flux from the inner edge does not fall off as quickly
-with inclination angle after occultation. The inner edge temperatures
-are ~1300 and ~1200K for the accretion rates of -7 (\textit{left
-  panel}) and -6 (\textit{right panel})
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ respectively. This leads to
-peak emission at ~2.2 to 2.4 $\mu$m. Figures \ref{ext_curve} and
-\ref{inner_inc_sed} shows that even for inclinations above the
-occulation or opening angle of the disc flux from the inner edge
-persists. This is indicative of a large and convex inner edge, as is
-observed in Figures \ref{sub_179} and \ref{sub_181}. Once again these
-extreme accretion rates probably over accentuate the result but help
-illumate the consequences of changes in the disc structure.
-
-Therefore, the longer (in wavelength) component of the final SED is
-dominated by the disc inner edge ($L_{\rm wall}$), temperature and
-shape and the outer disc scaleheight ($L_{\rm disc}$). The shape and
-location of the inner disc walls are controlled, primarily, by the
-stellar rotation rate (and stellar radius) and accretion rate (and
-stellar flux). Given that the stellar flux and radius decrease as the
-pre-MS star ages (or decreases in mass) the flux levels and the
-position of the inner edge are also weakly affected by the age of the
-central star.
-
-As shown in Figure \ref{inner_temp} the location of the inner edge and
-the corresponding temperature are correlated (differently) for typical
-and extreme accretors. This correlation is dominated by the dust
-sublimation temperature for the extreme accretors, and therefore the
-radial density profile. However, for the typical accretors the
-correlation between temperature and inner radius retains some
-dependence on the co-rotation radius (temperature is correlated with
-rotation period). This is as the sublimation temperature is not
-reached for the longer period models. Therefore, one might expect the
-resulting SEDs for typical accretors to show a correlation in shape,
-between 2 to 3 $\mu$m, caused by the inner wall temperature changes,
-in turn caused by changes in the rotation period. Figures
-\ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} show the SEDs (and
-constituent parts as explained in Figures \ref{disc_eg_173}) for a BDD
-model at the two rotation periods. The model has a mass of
-0.04$M_{\odot}$ and an age of 1 Myr, with accretion rates of -12 and
--9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in Figures \ref{rot_-12_1Myr}
-and \ref{rot_-9_1Myr} respectively, both at an areal coverage of
-10\%. The \textit{top panels} show the SEDs for a rotation period of
-0.5 days, and the \textit{bottom panels} the SEDs for a rotation
-period of 5 days. The \textit{first}, \textit{second}, \textit{third}
-and \textit{fourth panels} then show inclination angles of 0, 56, 64
-and 90$^{\circ}$ respectively.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_-12_1Myr.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{NOW SYSTEM SHOWN IN FIGURE ABOVE?**Figure showing SEDs of a
-   system with a central stellar mass of $0.04M_{\odot}$, an age of
-   1Myr an accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The \textit{panels}, both \textit{top} and
-   \textit{bottom}, (from left to right) show the SEDs and constituent
-   fluxes at inclination angles of 0$^{\circ}$, 56$^{\circ}$,
-   64$^{\circ}$ and 90$^{\circ}$. The component fluxes are presented
-   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
-   for systems with a rotation period of 0.5 days and the
-   \textit{lower panels} are for a rotation period of 5
-   days. \label{rot_-12_1Myr}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_-9_1Myr.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$, an age of 1Myr an accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The \textit{panels}, both \textit{top} and
-   \textit{bottom}, (from left to right) show the SEDs and constituent
-   fluxes at inclination angles of 0$^{\circ}$, 56$^{\circ}$,
-   64$^{\circ}$ and 90$^{\circ}$. The component fluxes are presented
-   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
-   for systems with a rotation period of 0.5 days and the
-   \textit{lower panels} are for a rotation period of 5
-   days. \label{rot_-9_1Myr}}
-\end{figure*}
-
-Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} show that for these
-BDD systems with typical accretion rates, the changes in SED with
-rotation period are small, apart from perhaps the face-on
-configuration. The systems in the \textit{top} and \textit{bottom
-  panels} of Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} have
-inner edge temperatures of ~1470 \& ~900K, and ~1460 \& ~940K
-respectively. This leads to different peak emissions for the slower
-and faster rotating stars, of approximately 2 and 3 $\mu$m. However,
-as is shown by Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} very
-little resulting change is apparent in any of the SEDs apart from the
-face-on configuration. Essentially, any change in the SED shape caused
-by changing emission at the inner disc edge is smoothed out by the
-resulting interactions with the rest of the disc structure. As pre-MS
-stars age they contract and reduce in luminosity, this will lead to
-changes in the co-rotation radius and inner edge temperature. The
-models in Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} are for an
-age of 1 Myr. Therefore, changes in the SED could also be more
-apparent for older systems, with lower stellar luminosities. Figures
-\ref{comp_rot_-12} and \ref{comp_rot_-9} show the same system as
-Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr}, i.e. with accretion
-rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-respectively, but for ages of 1 and 10 Myrs. In Figures
-\ref{comp_rot_-12} and \ref{comp_rot_-9} only the total SED are shown
-for the shorter period, a solid black line, and the longer period, as
-a dashed blue line. The \textit{top panels} show the SEDs for 1 Myr
-systems and the \textit{bottom panels} the 10 Myr systems. The
-\textit{first}, \textit{second}, \textit{third} and \textit{fourth
-  panels} again show the viewing angles of 0, 56, 64 and 90$^{\circ}$
-respectively.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/comp_rot_-12.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$ and accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The SEDs are shown in \textit{each panel} for a rotation
-   period of 0.5 (solid black line) and 5 (dashed blue line) days. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the total SEDs inclination angles of 0$^{\circ}$,
-   56$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$. The \textit{top
-     panels} are for systems with an age of 1 Myr and the
-   \textit{lower panels} are for an age of 10
-   Myrs. \label{comp_rot_-12}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/comp_rot_-9.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$ and accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The SEDs are shown in \textit{each panel} for a rotation
-   period of 0.5 (solid black line) and 5 (dashed blue line) days. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the total SEDs inclination angles of 0$^{\circ}$,
-   56$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$. The \textit{top
-     panels} are for systems with an age of 1 Myr and the
-   \textit{lower panels} are for an age of 10
-   Myrs. \label{comp_rot_-9}}
-\end{figure*}
-
-Figures \ref{comp_rot_-12} and \ref{comp_rot_-9} show that for typical
-accretors the resulting SEDs do not, in general, change significantly
-with changing rotation rate. For the face-on configuration
-(\textit{far left panels}) the SED slope over 2 to 3$\mu$m is
-marginally different only**. Essentially, flux redistribution from the
-highly flared outer regions of the disc and inner edge shape changes
-lead to a loss of correlations of SED shape (from 2 to 3$\mu$m)with
-inner edge temperature. This leads to a loss of any correlation
-between IR excess and inner edge location as predicted for the, flat,
-discs of \cite{1997AJ....114..288M}.
-
-\subsubsection{SED summary}
-\label{sed_summary}
-
-The shape of the combined SED, $L_*+L_{\rm acc}+L_{\rm wall}+L_{\rm
-  disc}$, is controlled by the combined stellar flux (intrinsic
-stellar temperature and luminosity, and accretion stream temperature
-and luminosity), and the disc characteristics (inner edge location and
-temperature, and outer disc flaring). The stellar flux and temperature
-both increase with increasing accretion rates and reducing areal
-coverages. The stellar flux (at constant temperature) also reduces as
-a pre-MS star contracts with age (or reduces in mass). Furthermore,
-the inner disc flux increases as the inner wall becomes hotter, larger
-and more visible with increasing incident flux. The outer disc
-component also increases as the outer disc flares. The flaring and
-temperature of the disc are controlled by the stellar flux and the
-rotation rate. Finally, and most importantly, the shape of the SED
-will be dominated by the inclination of the system, especially for
-extremely flared systems. This results in the observable SED being a
-major function of the input variables, age (and mass), accretion rate
-(and areal coverage), rotation period and system inclination.
-
-As we have discussed in this Section and Section \ref{disc_struct} the
-underlying disc structures are caused by complicated interplays
-between the sublimation physics, vertical hydrostatic equilibrium and
-emission of the disc components. However, several underlying trends
-have been observed in the physical characteristics of the
-systems. Most notably the correlation, to different strengths, of the
-disc inner wall location and its resulting temperature, as found in
-\cite{1997AJ....114..288M}. However, \cite{1997AJ....114..288M} go on
-to predict a correlation in IR excess with inner edge location. Given
-that the initial inner edge location is dependent (chiefly) on the
-rotation period one might expect a corelation of rotation rate with IR
-excess. This has been shown to be unlikely due to complications in the
-inner edge location due to dust sublimation, and obscuration of the
-inner disc edge at higher inclination angles. In addition, for large
-groups of stars there is evidence for a correlation in stellar mass
-with accretion rates. Although we have shown that the observable SEDs
-of BDD systems at higher accretion rates are difficult to classify as
-such, most surveys supporting this relationship use photometric data.
-
-\subsection{Photometry}
-\label{photometry}
-
-Practically, most parameters for young pre-MS stars are derived from
-surveys of populations, usually open clusters, using broadband
-photometry and subsequently constructed colour-magnitude and
-colour-colour diagrams (CMDs and CoCoDs respectively,
-hereafter). Therefore, in this Section, we demonstrate the prohibitive
-effects on the broadband photometry of varying our input
-parameters. In this Section we, in particular, relate the discussed
-features of disc structures (\ref{disc_struct}) and the resulting
-simulated SEDs (\ref{sed_analysis}) in terms of the derived
-photometry, in Section \ref{indv_phot}. Furthermore, we explore the
-consequences of our model grid on the derivation of the primary
-parameters of age, mass and disc fractions, from populations, in
-Section \ref{populations}. This in turn leads to highlighting
-selection effects with, for instance, the mass to accretion rate
-relation, in Section \ref{sum_relations}.  For the derivation of ages
-optical CMDs, in particular in \textit{V, V-I}, are most often used,
-and indeed most suitable. Whereas, IR CMDs, such as a \textit{J, J-K}
-CMD, are most suitable for mass derivation \cite[see references and
-discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
-
-\subsection{Effects of Disc Presence and Accretion on Photometry}
-\label{indv_phot}
-
-For the derivation of ages optical CMDs, in particular in \textit{V,
-  V-I}, are most often used, and indeed most suitable. Whereas, IR
-CMDs, such as a \textit{J, J-K} CMD, are most suitable for mass
-derivation \cite[see references and discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
-
-As discussed in Section \ref{sed_analysis} the presence of a
-circumstellar disc and accretion result in significant changes to the
-simulated SEDs for our models. Firstly, the photophere of the central
-star is dominated by the accretion luminosities for accretion rates of
-$\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$ as shown in Section
-\ref{acc_dominance}. Secondly, for increasing accretion rates the
-outer disc flaring increases, resulting in occultation of the star at
-smaller inclination angles, as discussed in Section
-\ref{flare_obscure}. Finally, the location of the inner edge and flux
-intercepted by this edge lead to changes in its shape and subsequent
-dependence of the observed SED with inclination, as discussed in
-Section \ref{inner_shape}. In this Section we explore the effects of
-these changes in SED shape on the derived photometry in CMDs used for
-age and mass derivation for stars. The use of isochrones for the
-derivation of single star parameters is completely unreliable
-\citep[see discussion in][]{2008MNRAS.386..261M}. However, exploring
-the changes in the CMDs of single objects will elucidate the causes of
-scatters from the expected locii in CMDs of populations of BDs.
-
-\subsubsection{Accretion Dominance-Photometry}
-\label{acc_dom_phot}
-
-Accretion flux was shown to dominate the underlying, intrinsic,
-photospheric SED for accretion rates of
-$\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$ (see Figure \ref{acc_dom} in
-Section \ref{acc_dominance}). As one would expect this leads to
-significant changes in the derived photometric magnitudes for bands
-blueward of a few microns, where the accretion and photospheric flux
-dominate. This is shown in Figure \ref{naked_acc}. Figure
-\ref{naked_acc} shows CMDs in $M_V$, $(V-I)_0$ (\textit{left panels})
-and $M_J$, $(J-K)_0$ (\textit{right panels}) of naked stars with
-accretion rates of -2, -9 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, shown as black, red and blue
-lines resepctively (in \textit{all panels}). The \textit{top panels},
-then show the two rotational periods of 5 and 0.5 days, as dashed and
-solid lines respectively, for a coverage of 10\%. The \textit{bottom panels},
-then show the two areal spot coverages of 1 and 10\%, as dashed and
-solid lines respectively, for a rotational period of 5 days.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/naked_acc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the naked systems for accretion rates of -8,
-   -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, shown in
-   \textit{all panels} as blue, red and black lines respectively. The
-   model shown for \textit{all panel} has a mass of 0.04$M_{\odot}$
-   and an age of 1Myr. The \textit{top panels} are models with areal
-   spot coverages of 10\%, and the \textit{lower panels} are for
-   models with rotational periods of 5 days. The dashed and solid
-   lines then delineate the rotation periods for the \textit{top
-     panels} and coverages for the \textit{bottom panels}. The dashed
-   lines show the rotational periods of 5 days (\textit{top panels})
-   and coverages of 1\% (\textit{bottom panels}). The solid lines
-   denotes periods of 0.5 days (\textit{top panels}) and coverages of
-   10\% (\textit{bottom panels}). For accretion rates of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (black line, \textit{all
-     panels}), are representative of all models at this rate, as the
-   models are coincident within the CMD.\label{naked_acc}}
-\end{figure*}
-
-As the rotation rate increases the co-rotation radius also increases,
-as shown in Equation \ref{inner_eq}, $R_{\rm inner}\propto
-\tau^{\frac{2}{3}}$. Therefore, as Equations \ref{Lacc} and
-\ref{Tacc}, show, $L_{\rm acc}\propto 1- \frac{R_*}{R_{\rm inner}}$
-and $T_{\rm acc}\propto \frac{L_{\rm
-    acc}}{A^{\frac{1}{4}}}$. Therefore, the temperature of the
-accretion hot spot increases as the coverage lowers and the rotational
-period increases (the latter is due to the increase in potential
-energy lost by the mass accreted). This can be seen in Figure
-\ref{acc_dom} with lower areal coverages and longer rotational periods
-leading to accretion fluxes at peaking at shorter wavelengths. The
-\textit{left panels} of Figure \ref{naked_acc} show that as the
-accretion rate increases the stars move blueward and to brighter
-magnitudes in the $M_V$, $(V-I)_0$ CMD. Furthermore, as the accretion
-spot temperature is maximised i.e. moving to longer periods of
-rotation or smaller areal coverages (solid to dashed lines), the stars
-also move blueward. For the \textit{right panels}, or $M_J$, $(J-K)_0$
-CMDs the behaviour is less intuitive. Increases in accretion rate lead
-to a slight brightening and an initial move redward, followed by a
-move blueward. This is as the lower accretion rates have lower hot
-spot temperatures, with peak wavelengths between 1 and 3 $\mu$m
-(corresponding to temperatures of $~$2800K to $~$900K, the range of
-the BD photosphere). This leads to increases in the red flux and
-changes in the slope from $J$ to $K$. At the higher accretion rates
-the accretion flux dominates and cause the blueward shift as the slope
-becomes larger. For the highest accretion rate, in the \textit{bottom
-  right panel}, a change to a hotter spot (reduction in coverage, from
-solid to dashed lines) results in a move redward in the CMD. This can
-be understood by observing the blue solid lines in the \textit{top
-  panels} of Figure \ref{acc_dom}. Essentially, the reduction in spot
-temperature moves the accretion flux to much shorter wavelengths,
-$~$0.5 to $~$0.3 $\mu$m, meaning that the flux in the $J$ and $K$
-bands becomes more like the photosphere, and less dominated by
-accretion. The \textit{top right panel} of Figure \ref{naked_acc} then
-shows that increases in the rotation period (from solid to dashed
-lines) shows a move blueward in the CMD, resulting in changes of the
-peak accretion flux emission from $~$0.58 to $~$0.5 $\mu$m, meaning
-significant flux from the accretion hot spot will still fall in the
-$J$ and $K$ bands, and the slope will be increased.
-
-\subsubsection{Effect of Flaring and Obscuration on Photometry}
-\label{flare_obscure_phot}
-
-As described by \cite{2004MNRAS.351..607W} the increased flaring, in
-BDD systems when compared to CTTS, leads to more significant changes
-in the photometric characteristics of the BDD stars with inclination
-changes. The increased flaring shown in Figures \ref{flare_-12_183}
-and \ref{flare_-7_193} results in increased obscuration of the central
-star (and inner edge) at earlier inclinations. This obscuration is
-shown to occur at lower inclination angles for objects accreting at
-higher levels, as shown in Figure \ref{flare_inc}. Figure
-\ref{flare_inc} shows that significant obscuration occurs at
-inclinations of 71 and 56$^{\circ}$ for accretion rates of -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively. The changes in
-flux with inclination will clearly lead to a change in the observed
-magnitude with inclination. Figure \ref{flare_mag} shows the $M_V$ and
-$M_J$ magnitude, in the \textit{top} and \textit{bottom panels}
-respectively, as a function of inclination with the individual points
-marked as crosses. The \textit{top} and \textit{bottom panels} show
-accretion rates of -12, -9 and -7 as black, red and blue lines. The
-solid lines are for objects with rotational periods of 0.5 days and
-the dashed lines are for periods of 5 days. The \textit{inset panel}
-within the \textit{bottom panels} shows an enlargment of the section
-of inclinations from 40 to 80$^{\circ}$. For \textit{all panels} the
-vertical dotted lines show the inclinations for which significant
-drops in flux are observed (see Figure \ref{flare_inc}) for -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in black and blue respectively.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_mag.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing magnitude change with inclination for $M_V$
-   (\textit{top panel}) and $M_J$ (\textit{bottom panel}) for the
-   models shown in Section \ref{disc_struct}, Figures \ref{no_sub_183}
-   to \ref{sub_181}. The accretion rates of -7, -9 and -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as blue, red and
-   black lines respectively. The individual points are shown as
-   crosses for all data. The dashed lines show the systems with
-   rotational periods of 5 days and the solid lines 0.5 days, in
-   \textit{all panels}. A section of the \textit{bottom panel} has
-   been enlarged and is shown as the \textit{inset panel}. Note the
-   models for -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are coincident
-   in this Figure. \textit{All panels} show the inclinations are which
-   obscuration occurs for -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as dashed black and blue
-   lines respectively. \label{flare_mag}}
-\end{figure*}
-
-Figure \ref{flare_mag} shows that the occultation starts earlier for
-the higher accretion rates, shown by the increase in both magnitudes
-(\textit{top} and \textit{bottom panels}) with inclination angle at
-around 56 and 71$^{\circ}$, as also shown in Figure
-\ref{flare_inc}. The slower rotation rates, for the highest accretion
-rates, show a generally fainter magnitude, than the faster rotating
-systems, caused by a larger disc scaleheight. For $M_J$ the fall in
-magnitude is again earlier and more significant for the larger
-accretion rates. However, at higher inclinations the systems become
-brighter again, show in the \textit{inset panel}. This brightening is
-due to the curved inner wall, as shown in Figures \ref{inner_inc_sed}
-(discussed in more detail in Section \ref{inner_edge_phot}.
-
-The change in magnitude, will also lead to a change in colour. As
-described $V$, $V-I$ and $J$, $J-K$ CMDs are ubiquitously used for
-derivation of ages and masses. The use of isochrones to derive ages
-and masses of individual stars is not reliable. However, it is
-informative to explore the changes in the CMD position of our BDD
-systems. Figure \ref{flare_VVI} shows $M_V$, $(V-I)_o$ CMDs for the
-accretion rates of -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$,
-as the \textit{left} and \textit{right panels} resepctively. The
-systems are those shown in Figure \ref{flare_-12_183} and
-\ref{flare_-7_193}, at all modeled inclinations. For \textit{both
-  panels} the red dashed line, with the data points marked as crosses,
-shows the changes in CMD position with inclination of the BDD system
-at different inclinations for a 1 Myr system (with an areal coverage
-of 10\% and a $\tau$ of 5 days). The solid blue line is the matching
-isochrone for naked systems, with the naked $M_*=0.04M_{\odot}$ marked
-as a triangle. Again, for \textit{both panels} the inclinations at
-which significant drops in flux were found in Figure \ref{flare_inc}
-in red text.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_VVI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_V$, $(V-I)_0$ of
-   the models in Figures \ref{flare_-12_183} and \ref{flare_-7_193}
-   (Section \ref{disc_struct}) as the \textit{left} and \textit{right
-     panels} respectively. The solid blue line are the 1Myr naked
-   isochrones at the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ for the \textit{left} and
-   \textit{right panels} respectively (with an areal coverage of 10\%
-   and a $\tau$ of 5 days). The dashed red line is the BDD system with
-   $M_*=0.04M_{\odot}$ at all simulated inclinations. The triangles,
-   in both panels are the 0.04$M_{\odot}$ stars on the naked
-   isochrones and the crosses show this mass over the range of
-   inclinations with an associated disc. Figure \ref{flare_inc}
-   predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
-   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ models respectively,
-   and these are denoted by the text within the
-   figure.\label{flare_VVI}}
-\end{figure*}
-
-Figure \ref{flare_VVI} shows that as the system changes in inclination
-it leads to a sigificant dimming in both cases. The inclinations from
-\ref{flare_inc} where significant flux is lost are shown and it can be
-seen that a significant drop in magnitude is apparent just before this
-inclination (as also shown in Figure \ref{flare_mag}). The models in
-\textit{both panels} get slightly redder as we increase to the
-obscuration angle, caused by scattered light from the disc this can be
-observed for the accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in Figures \ref{rot_-12_1Myr}
-and \ref{comp_rot_-12}.
-
-Figure \ref{flare_JJK} shows the same data as Figure \ref{flare_VVI}
-with the same notation and symbol meanings.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_JJK.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_J$, $(J-K)_0$ of
-   the models in Figures \ref{flare_-12_183} and \ref{flare_-7_193}
-   (Section \ref{disc_struct}) as the \textit{left} and \textit{right
-     panels} respectively. The solid blue line are the 1Myr naked
-   isochrones at the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ for the \textit{left} and
-   \textit{right panels} respectively (with an areal coverage of 10\%
-   and a $\tau$ of 5 days). The dashed red line is the BDD system with
-   $M_*=0.04M_{\odot}$ at all simulated inclinations. The triangles,
-   in both panels are the 0.04$M_{\odot}$ stars on the naked
-   isochrones and the crosses show this mass over the range of
-   inclinations with an associated disc. Figure \ref{flare_inc}
-   predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
-   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ models respectively,
-   and these are denoted by the text within the
-   figure.\label{flare_JJK}}
-\end{figure*}
-
-Figure \ref{flare_JJK} again, as in Figure \ref{flare_VVI}, shows the
-BDD systems dimming with increasing inclination, with some move
-towards redder colours. There is an offset between the naked and BDD
-systems at face on inclinations, caused by the inner disc wall. This
-is particularily large for the higher accretion rate (\textit{right
-  panel}). This increase in reddening for the higher accretion rates
-is due to the much larger and curved inner disc edge as shown in
-Figure \ref{sub_179}. This curved inner edge also leads to less
-dependence of $(J-K)_0$ as a function of inclination angle, as
-compared to the lower accretion rate.
-
-\subsubsection{Inner Edge and Photometry}
-\label{inner_edge_phot}
-
-It is clear that the scatter within a CMD, in particular for the
-$M_J$, $(J-K)_0$ CMD, is strongly affected by the emission from the
-inner edge (as shown in Figure \ref{flare_JJK}).
-
-Figure \ref{inner_VVI} shows the position in a CMD of the models from
-Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179} and
-\ref{sub_181}. The accretion rates shown are -12, -7, -9 and -6
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as the \textit{top left},
-\textit{bottom left}, \textit{top right} and \textit{bottom right
-  panels}. The solid blue line in \textit{all panels} of Figure
-\ref{inner_VVI} show the naked isochrone at 1 Myr (with an areal
-coverage of 10\% and $\tau$ of 0.5 days), at the shown accretion
-rate. The dashed red line shows the BDD system matching the naked
-isochrone, except with $M_0.04M_{\odot}$, at all inclination rates,
-with the datapoints marked as crosses. The blue triangles are then the
-naked stars at $M_0.04M_{\odot}$. The points at which the thermal
-direct flux reaching the observer drops significantly are marked in
-red text for each system, as shown in Figures \ref{typ_curve} and
-\ref{ext_curve}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_VVI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_V$, $(V-I)_0$ of
-   the models in Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179}
-   and \ref{sub_181} as the \textit{top left}, \textit{bottom left},
-   \textit{top right} and \textit{bottom right panels}
-   respectively. As for Figure \ref{flare_VVI}, the solid blue line is
-   the naked isochrone at 1 Myr for the corresponding accretion rate
-   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The
-   dashed red line is the BDD isochrone at the same age and accretion
-   rate. The inclination of each model at which obscuration is
-   expected to occur, from Figures \ref{typ_curve} and
-   \ref{ext_curve}, is denoted in text.\label{inner_VVI}}
-\end{figure*}
-
-Figure \ref{inner_VVI} shows for the $M_V$, $(V-I)_0$, the inclination
-increase again dims the star for these models and moves it intially
-redward, until it exceeds the expected obscuration angle, found from
-Figures \ref{typ_curve} and \ref{ext_curve}. However, as we move
-through the accretion rates from -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (\textit{top left panel}) to -6
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (\textit{bottom right panel})
-the transition from edge-on to face-on system tends to a sharper
-feature, with the reddest point at the obscuration angle. As would be
-expected from the SEDs shown in Figure \ref{inner_inc_sed}. This is
-caused by maximising the amount of the inner edge which is visible,
-whilst the stellar photosphere is still visible (which also
-contributes in these passbands).
-
-Figure \ref{inner_JJK} shows the same information as Figure
-\ref{inner_VVI} but for a $M_J$, $(J-K)_0$ CMD. Here, the BDD
-isochrones are initially much redder than their naked counterparts, as
-expeted due to IR excesses caused by the disc inner edges. As the
-inclination increase for the lower accretion rates (\textit{top left}
-and \textit{bottom left panels}) the system moves first redward and
-then sharply blueward as the SED becomes dominated by scattered light
-only. As can be seen in Figure \ref{inner_inc_sed}. For the extreme
-accretion rates the wall is no longer vertical and the change in
-infrared colours is smoother up until the obscuration angle.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_JJK.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_J$, $(J-K)_0$ of
-   the models in Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179}
-   and \ref{sub_181} as the \textit{top left}, \textit{bottom left},
-   \textit{top right} and \textit{bottom right panels}
-   respectively. As for Figure \ref{flare_VVI}, the solid blue line is
-   the naked isochrone at 1 Myr for the corresponding accretion rate
-   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The
-   dashed red line is the BDD isochrone at the same age and accretion
-   rate. The inclination of each model at which obscuration is
-   expected to occur, from Figures \ref{typ_curve} and
-   \ref{ext_curve}, is denoted in text.\label{inner_JJK}}
-\end{figure*}
-
-\section{Populations}
-\label{populations}
-
-Practically, the derivation of parameters for pre-MS populations uses
-CMDs and isochrones applied to clusters or populations of stars. In
-this section we explore the scatters of our BDD systems across our
-grid of input values within typical or commonly used CMDs and CoCoDs
-for deriving ages, masses and disc fractions.
-
-To delineate the effects of the accretion rate and circumstellar discs
-we have subdivided the grid into two groups (as discussed in Sections
-\ref{disc_struct} and \ref{sed_analysis}), those with accretion rates
-typical for higher mass CTTS objects, defined as
-$\dot{M}=$10$^{-12}M_{\odot}yr^{-1}$ (negligible) to
-$\dot{M}=$10$^{-9}M_{\odot}yr^{-1}$ and those with elevated accretion
-rates, where $\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$. For several of the
-plots in this section the magnitude and colours for the
-$M_*=0.01M_{\odot}$ at high inclinations become extremely faint and
-red, respectively. In some cases these objects appear slightly without
-the scale of the diagram the axes where limited in this way to be able
-to show the changes in colour an magnitude for the majority of stars
-better. The colours and magnitudes for these lowest mass stars are not
-necessarily unreliable but simple hinder the aesthetics of the plots,
-and as they are at the limits of our grid we have decided to omit them
-from some Figures by trimming the axes. Additionally, stars at the
-highest inclinations, i.e edge on disc systems, are often omitted from
-the Figures due to their extremely faint magnitudes, meaning they
-would not be practically observable.
-
-\subsection{Age and Mass Derivations}
-\label{age_mass_pop}
-
-As discussed in Section \ref{indv_phot} for the derivation of the
-primary parameters of age and mass the CMDs most suitable and commonly
-used are $M_V$, $(V-I)_0$ and $M_J$, $(J-K)_0$. Furthermore, these
-CMDs are indicative of the associated CMDs, for instance $M_R$,
-$(R-I)_0$ or $M_J$, $(J-H)_0$ etc. Also as discussed in
-\cite{2008MNRAS.386..261M} the use of isochrones for the derivation of
-masses and ages for individual pre-MS stars is unreliable at
-best. Practically, therefore, median ages are derived from
-populations. Subsequently, derived masses are still unreliable but at
-least based on a consistent age. This problem is being addressed by
-Bell et al (in prep), where $K$ band photometry and known eclipsing
-binaries are being used to refine pre-MS isochrones. In this section
-we plot the data for our 1 Myr systems only and explore the resulting
-scatters caused by the disc presence and accretion luminosity.
-
-Figures \ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext} shows
-four CMDs in $M_V$, $(V-I)_0$ for the typical and extreme accretors
-respectively. For the typical accretors, Figure
-\ref{spread_opt_VVI_typ}, shows the isochrones constructed for naked
-systems at 1 Myr, for accretion rates of -12 and -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as the solid and dashed black
-lines. Whereas in Figure \ref{spread_opt_VVI_ext} the naked isochrones
-of -9 and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as dashed and
-solid black lines respectively. The \textit{top left panel}, in both
-Figures (\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}) shows
-a pre-MS isochrone at 1 Myr from \cite{2000A&A...358..593S} adjusted
-to a distance of 250pc and an extinction of $A_V=2$ mag, simulating a
-background population of CTTS stars. The dots in \textit{each panel},
-for both Figures (\ref{spread_opt_VVI_typ} and
-\ref{spread_opt_VVI_ext}) are the 1 Myr BDD systems for all
-inclinations, rotational periods, areal spot coverages and the
-individual accretion rates within the accretion type classes. The
-\textit{panels} of the Figures \ref{spread_opt_VVI_typ} and
-\ref{spread_opt_VVI_ext} then seperate the systems by the input
-variables. The \textit{top left panel} shows either the accretion
-rates of -9, -10 and -11 \& -12 or -6, -7 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures
-\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}
-respectively. These three classes are then shown as blue, black and
-red dots respectively. The \textit{bottom left panels} then show those
-systems with areal coverages of 1 and 10\% as blue and red dots
-resepectively. The \textit{top right panels} then shows systems with
-rotational periods of 0.5 and 5 days as blue and red dots
-respectively. Finally, the \textit{bottom right panels} show the
-systems seperated by inclination. These groups are $\theta \leq
-48^{\circ}$ as blue dots (classed as face-on systems), $\theta> 56$ \&
-$64^{\circ}$ (classed as the expected systems, as the expectation
-value of $cos(\theta)=60^{\circ}$) as black dots and $\theta \geq
-71^{\circ}$ (classed as edge-on systems) as red dots. Figure
-\ref{spread_opt_RRI_typ} also shows the same data as for Figure
-\ref{spread_opt_VVI_typ}, but for $M_R$, $(R-I)_0$ CMDs.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_VVI_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
-   accretors ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The black solid and dashed
-   lines in \textit{all panels} are the naked star isochrones for
-   accretion rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-   respectively. The \textit{top left} only shows the 1 Myr pre-MS
-   isochrone of \citet{2000A&A...358..593S} adjusted to a distance
-   modulus of 7 and an extinction of $A_V=2$, simulating a reddened
-   background population. The dots are the data for typical accretors
-   for models at 1 Myr. The data are then seperated by input
-   variables, in the \textit{panels}. The \textit{top left panel}
-   shows three accretion classes, -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as blue, black and red dots
-   respectively (the lowest two accretion rates are grouped as they
-   are coincident). The \textit{top right panel} shows the rotational
-   periods of 0.5 and 5 days as blue and red dots respectively. The
-   \textit{bottom left panel} shows the areal spot coverages of 1 and
-   10\% as blue and red dots resepctively. The \textit{bottom right
-     panel} shows three groups of inclinations, $\theta \leq$
-   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
-   71$^{\circ}$ , as blue, red and black dots
-   respectively.\label{spread_opt_VVI_typ}}
-\end{figure*}
-
-As can be seen in Figure \ref{spread_opt_VVI_typ} current accretion in
-a star and disc systems, for rates typical in the BD mass regime,
-creates a scatter in our simulated photometry indicative of a much
-larger isochronal age spread than 10 Myr. Indeed, for many BDD systems
-even at nominal accretion rates of -11 or -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, for our simulations, the
-colours of these stars move significantly blueward of the expected BD
-locus in a $M_V$, $(V-I)_0$ CMD. As the dots in Figure
-\ref{spread_opt_VVI_typ} are the simulated photometry of BDD systems
-over a range of typical input parameters (see Section
-\ref{par_space}), an observed coeval 1 Myr population could reasonably
-be expected to show a similar scatter. The naked isochrones show that
-this spread in simulated photometry, would lead to a spread in
-isochronal age greater than the $\approx$10 Myr spread claimed for
-higher mass stars in some star forming regions (for instance the
-ONC). Furthermore, for the higher accretion rates of -9 or -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the movement of the star
-within the CMD will effectively move the star into the contamination
-region expected for background CTTS or MS stars at a $(V-I)_0$ of
-$\leq$1.5 and $M_V$ 12-10, and as such the star would not be included
-in a photometrically selected BD sample. The solid green line, in the
-\textit{top left panel}, showing the 1 Myr isochrone of
-\cite{2000A&A...358..593S} at a distance of 250 pc and extinction of
-$A_V=2$ mags shows that the BDD systems with higher accretion rates
-could easily be confused for a background CTTS or MS population (as MS
-stars are simply less luminous at a roughly constant \textit{V-I} than
-the CTTS counterparts). Indeed miss classification of a BDD system as
-a CTTS system has already been revealed in \cite{}**CHECK WHITE AND
-BASRI. Furthermore, scatter, although somewhat reduced, can be
-observed in the simulated photometry of the negligibly accreting
-systems, for example in the \textit{top left panel} some red dots,
-accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (which
-will be negligible compared to the photospheric flux, see Figure
-\ref{acc_dom}), still scatter significantly. These objects may still
-be included in a `wide' photometric selection. This scatter is a
-strong function of inclination, as shown in the \textit{bottom right
-  panel}, where, as the inclination is increased the objects are
-pushed lower in the CMD. Indeed, for the edge on cases some objects
-have magnitudes fainter than show in Figure \ref{spread_opt_VVI_typ}
-($M_V\approx 20$). This is expected as the star becomes obscured by
-the flared disc, interestingly for these systems the \textit{bottom
-  right panel} shows that this occurs for inclinations above around
-71$^{\circ}$ (as found in Figure \ref{flare_inc}) in most cases yet
-even for the lower inclination angles some objects have very faint
-magnitudes, this is due to the disc flaring leading to a smaller
-opening angle and is discussed in Section \ref{disc_struct}. The
-\textit{bottom left panel} shows that for naked systems accretion
-rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ lead to the stars
-being scattered into the region occupied by background CTTS and
-contamination (the lower accretion rates are all coincident with the
--12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for 1 Myr). Crucially, the
-\textit{top left panel} shows that the scatter from the isochrone is,
-generally, correlated with accretion rate. Effectively, as the
-accertion rate increases the BDD system moves farter away from the
-isochrone and is therefore less likely to be classified as a BDD
-system and included in any taget samples of such objects. The
-\textit{top right panel} shows that the scatter, in $M_V$, in our
-simulated photometry from the isochrones is significant for both areal
-coverages. The \textit{bottom left panel}, shows significant scatter
-in the simulated photometry for both adopted rotation periods. This
-panel also shows that scatter in this diagram is not obviously
-correlated with the rotation period and therefore inner edge
-position. Overall, as found in \cite{2004MNRAS.351..607W}, the
-dominant scattering effect for BD disc systems in an optical CMD
-appears to be caused by accretion rate and inclination, and therefore
-obscuration effects of the disc on the star. This suggests that for a
-given photometric survey of BDD systems accreting at typical accretion
-rates and with an expected range of inclinations (centred on around
-60$^{\circ}$) one would expect to exclude a significant fraction of
-these objects from any isochrone based selection.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_VVI_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_opt_VVI_typ} except for extreme
-   accretors, $\dot{M}\geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. In this Figure the solid
-   black line now shows naked systems with an accretion rate of -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as opposed to -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as in Figure
-   \ref{spread_opt_VVI_typ}, the dashed black line is still for an
-   accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. \label{spread_opt_VVI_ext}}
-\end{figure*}
-
-Figure \ref{spread_opt_VVI_ext} shows that for extreme accretion rates
-the BDD objects move significantly blueward and brighter than the
-naked isochrone (the naked isochrone at -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ is shown for
-comparison). Comparison of the \textit{four panels} again show that,
-in general, the scatter is chiefly correlated with accretion rate and
-inclination. Essentially, Figure \ref{spread_opt_VVI_ext} shows that
-for, admittedly extreme, accretion rates BDD systems will not be
-included in a photometrically (or indeed spectroscopically, from
-Section \ref{sed_analysis}) selected sample.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_RRI_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_opt_RRI_typ}, but in $M_R$, $(R-I)_0$,
-   with the pre-MS isochrone omitted.\label{spread_opt_RRI_typ}}
-\end{figure*}
-
-Similar scattering, as observed in Figure \ref{spread_opt_VVI_typ},
-occurs when using CMDs constructed using \textit{R, R-I} \citep[using
-the photometric system of][]{1998A&A...333..231B}. Figure
-\ref{spread_opt_RRI_typ} shows the \textit{R, R-I} CMD.
-
-Similar consequences are apparent in CMDs best suited, and most used,
-for derivation of masses using isochrones. Figure
-\ref{spread_ir_JJK_typ} shows the same data as Figure
-\ref{spread_opt_VVI_typ} in the same format except in this case the
-pre-MS isochrone of \cite{2000A&A...358..593S} has been smoothed,
-purely for aesthetics and to remove the sharper features. Again Figure
-\ref{spread_ir_JJK_ext} contains the same data in the same format as
-Figure \ref{spread_opt_VVI_ext} except that the naked star isochrone
-at an accretion rate of -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ is
-not shown as it lies significantly blueward of the CMD.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_ir_JJK_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_opt_VVI_typ}, in $M_J$, $(J-K)_0$, in
-   this Figure the pre-MS isochrone of \citet{2000A&A...358..593S},
-   has been smoothed.\label{spread_ir_JJK_typ}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_ir_JJK_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_opt_VVI_ext}, except that the -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ isochrone is not shown (lies
-   significantly blueward of locus of data), and the pre-MS isochrone
-   has been smoothed.\label{spread_ir_JJK_ext}}
-\end{figure*}
-
-Figure \ref{spread_ir_JJK_typ} shows that for typical accretion rates
-and expected ranges of the other input variables the spread in CMD
-positions is large. Indeed. the \textit{top left panel} again shows
-that, as in the $M_V$ $(V-I)_0$ case, some of the BDD objects will
-appear as redenned background CTTS objects. Scrutiny of the
-\textit{individual panels} shows no clear correlation of CMD position
-with input variable except for the inclination. As shown in the
-\textit{bottom right panel} as the inclination increases the systems
-move to fainter magnitudes and redder colours, in general. The
-\textit{top right panel} of Figure \ref{spread_ir_JJK_typ} shows that
-for typical accretion rates there does not appear to be a correlation
-of $(J-K)_0$ colour with rotation rate as expected from the modeling
-of flat disc by \cite{1997AJ....114..288M}. It is clear that assigning
-masses to accreting BDD systems using isochrones, for our model grid,
-would result in the incorrect masses. In addition, photometric sample
-selection for BD systems will also exclude the majority of our higher
-accretion rate objects. Figure \ref{spread_ir_JJK_ext} shows that for
-extreme accretors the scatter is much larger, and again correlated
-only with inclination, and perhaps accretion rate to a lesser degree
-(\textit{bottom right} and \textit{top left panels} of Figure
-\ref{spread_ir_JJK_ext}).
-
-\subsubsection{Summary}
-
-GOT HERE**combined the next two paragraphs
-
-Now summarise on the effects of the CMD classification*** Then sort
-out effect on the rotational period to JK excess and Mstar to Macc
-relation.**
-
-Therefore, if one adopts the range of input parameters we have used
-(see Section \ref{par_space} for justification), our simulated
-photometry shows, qualitatively, that a coeval 1 Myr population of
-accreting BD stars and BDD systems, with typical accretion rates and
-range of inclinations, will exhibit a scatter in apparent isochronal
-age of $>$10 Myr. Furthermore, some objects will be scattered below
-and blueward of a 10 Myr isochrone. This has been shown for CMDs in
-\textit{V, V-I} and \textit{R, R-I}. It is important to note at this
-point that these conclusions are qualitative, and obviously based on
-our assumptions. However, the repercussion for isochronal age
-derivation and sample selection in the BD regime could be
-profound. Indeed this study has only included the effects of current
-or ongoing accretion from a disc, it has totally neglected any effects
-of accretion, both past and present, on the evolution of the central
-star. This past accretion could also act to reduce the stars radius,
-accelerating contraction
-\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
-additional scatter in a coeval population proportional to the range in
-accretion rates \citep[See][for full
-discussion]{2008MNRAS.386..261M}. Our findings support those of
-\cite{2004MNRAS.351..607W}, showing that a significant scatter is
-caused by obscuration of the central source by the central disc. In
-addition we have shown that the scatter blueward, into the CTTS or
-background MS locus, is caused by active accretion at levels found in
-CTTS stars, but currently not regularly recorded in stars classified
-or selected as BDs.
-
-Therefore, as for derivations of age, given our assumptions, and the
-adopted range of input parameters, a 1 Myr coeval population scatters
-significantly in a \textit{J, J-K} CMD. The \textit{J, J-K} CMD is
-representative of CMDs constructed from the \textit{JHK}
-passbands. So, qualitatively at least, derivation of masses using
-isochronal fitting of our simulated photometry would not produce
-reliable or accurate results. Again, as discussed for optical CMDs,
-these simulations do not include any of the effects of past or current
-accretion on the evolution of the central object, which is expected to
-significantly exacerbate the observed scatter. This is also true for
-the naked systems with small increases in accretion rate leading to
-significant scatters in the CMDs. Additionally, given the evidence
-discussed in \cite{2004MNRAS.351..607W}, supported by the evidence
-from our own simulated photometry shown in Figures
-\ref{spread_opt_VVI_typ}, \ref{spread_opt_VVI_ext},
-\ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext}, it is clear that
-young, accreting, BDD systems are likely to be misidentified when
-using photometric colours or magnitudes, even at generally canonical
-accretion rates. This casts doubt on the veracity of the mass to
-accretion rate relationship. For our model grid we have not assumed
-any such relation, therefore, as our data would also show a similar
-relation it suggests that the observed result may be caused by
-intrinsic scattering. The relation, $\dot{M}\propto M_*^{2}$ suggests
-that their is a dearth of lower mass stars accreting at higher
-rates. We have shown that for accretion rates in the range -12 to -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with higher
-accretion rates would be preferentially missed using photometric or
-isochronal selection.
-
-Therefore, again as for the optical case, given our assumptions and
-parameter space, BDD systems accreting at higher rates would not be
-identified with the correct mass in most cases using IR CMDs.
-
-\subsection{Disc fractions}
-\label{disc_fractions_phot}
-
-Disc fractions have been derived using infrared excesses previously in
-\textit{JHK}, however recent works pre-dominantly use \textit{Spitzer}
-IRAC magnitudes. Furthermore, MIPS magnitudes are used to identify
-so-called debris discs, where IR excesses are not apparent at shorter
-wavelengths. Finally, disc fractions have also been derived using the
-$\alpha$ criteria, where $\alpha=\frac{dlog\lambda
-  F\lambda}{dlogF\lambda}$ between two limiting wavelengths,
-originally used to distinguish amongst Class I, II or II sources, but
-now used to detect disc presence
-\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
-used as a selection criterion for disc presence for TTS stars. We have
-constructed the $\alpha$ values for our model grid by adopting the
-limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
-8.0$\mu$m.
-
-Now switch to figures just showing inclination and accretion rate (not
-rotation rate).
-
-Whilst magnitudes are affected by accretion rates, ages, rotational
-periods etc, practically, for colour, colour plots the inclination is key.
-
-TYPICAL ACCRETORS
-location in the cMD is proportonal to the accretion rate and
-inclination and this sontinues into the IR colours
-
-GOT HERE***
-for typical accretors the accretion rate becomes unimportant and the
-resulting thing is just inclination for extreme accretors the
-accretion rate becomes key again
-
-First a Jh jk colo col d to show this, all ages used both 1 and 10 Myr
-
-NOT SURE IF I SHOULD LIMIT BY AGE ALL THE DISC FRACTIONS PLOTS? used 1
-and 10 myr sample as age doesn't effect the position in the col-col
-plot very much
-
-WHERE TO PUT THIS** CLEARPAGE THING**
-show that only inclination and accretion matter, age notmimportant for
-discs, disc and non disc systems separation observed in panels where
-there are no black disc systems. For extreme accretors mention fact
-that the inner edge temperature is now function of accretion rate etc.
-\clearpage
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_JHJK_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing $(J-H)_0$, $(J-K)_0$ colour-colour diagram
-   for typical accretors ($\dot{M}<leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The dots are then all
-   models (at 1 and 10 Myrs) with discs and the black crosses are the
-   naked systems, in \textit{all panels}. The data are then seperated
-   by input variable in \textit{each panel}. The \textit{top left
-     panel} shows accretion rates of -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, black and red dots
-   respectively. The \textit{top right panel} shows the systems with
-   rotational periods of 0.5 and 5 days as blue and red dots
-   respectively. The \textit{bottom left panel} shows systems with
-   areal spot coverages of 1 and 10\% as blue and red dots
-   respectively. Finally, the \textit{bottom right panel} seperates
-   the systems into three groups inclination, $\theta \leq$
-   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
-   71$^{\circ}$ , as blue, red and black dots
-   respectively.\label{disc_frac_JHJK_typ}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_JHJK_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{disc_frac_JHJK_typ} but for extreme
-   accretors, $\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-   .\label{disc_frac_JHJK_ext}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing typically accreting systems ($\dot{M}\leq$-9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$), in irac photometric
-   bands. The \textit{left panels} show the $([3.6]-[4.5])_0$ against
-   $([4.5]-[5.8])_0$ CoCoD, and the \textit{right panels} show the
-   $([3.6]-[4.5])_0$ against $([5.8]-[8.0])_0$ CoCoD. In \textit{all
-     panels} the dots are disc systems and crosses naked systems. The
-   \textit{top panels} then seperate the systems by accretion rate
-   with, -9, -10 and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-   as blue, black and red dots respectively. The \textit{bottom
-     panels} seperate the systems by inclination with $\theta \leq$
-   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
-   71$^{\circ}$ , as blue, red and black dots
-   respectively. \label{disc_frac_irac_typ}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{disc_frac_irac_typ} but for extreme
-   accretors, $\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.\label{disc_frac_irac_ext}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_mips_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the $([3.6]-[4.5])$, $([8.0]-24)$ CMDs as the
-   \textit{left panels} and $([3.6]-[5.8])$, $([8.0]-24)$ CMDs as the
-   \textit{right panels}, combining irac and mips photometric
-   channels. The sytems are again seperated by accretion rate and
-   inclination angle in the \textit{top} and \textit{bottom} panels as
-   in figure \ref{disc_frac_irac_typ}.\label{disc_frac_irac_mips_typ}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_mips_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{disc_frac_irac_mips_typ} but for extreme
-   accretors ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$).\label{disc_frac_irac_mips_ext}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_mips.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing CMDs of mips photometry for the typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) and
-   extreme ($\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$)
-   accretors, as the \textit{left panels} and \textit{right panels}
-   respectively. The \textit{top panels} seperate the systems by
-   accretion rate in the way described in Figures
-   \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} in the
-   \textit{left} and \textit{right panels} respectively. The
-   \textit{bottom panels} then seperate the systems by inclination as
-   described in Figure \ref{disc_frac_irac_typ}. The \textit{inset
-     panels} in the \textit{top panels} then show a larger region with
-   the BDD systems as red dots and the naked systems as blue
-   crosses.\label{disc_frac_mips}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_alpha.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing $\alpha$ value \citep{2006AJ....131.1574L}
-   (against an arbitrary model number) used
-   \citet{2009arXiv0901.2603K}, $\alpha=\frac{dlog(\lambda
-     F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
-   $\mu$m). Crosses show the simulated objects without discs and dots
-   are those with circumstellar disc, the horizontal line is the
-   $\alpha>-$2 cut used to identify disc candidates for solar type
-   stars in \citet{2009arXiv0901.2603K}. Note, that stars of
-   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
-   estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4$\mu$m). The \textit{left panels} show typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
-   and the \textit{right panels} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors. The \textit{top
-     panels} seperate the systems by accretion rate in the way
-   described in Figures \ref{disc_frac_irac_typ} and
-   \ref{disc_frac_irac_ext} in the \textit{left} and \textit{right
-     panels} respectively. The \textit{bottom panels} then seperate
-   the systems by inclination as described in Figure
-   \ref{disc_frac_irac_typ}.\label{disc_frac_alpha}}
-\end{figure*}
-
-\subsubsection{Practical Observations}
-PRACTICAL OBSERVATIONS:
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_cut.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing all simulated photometry for the entire
-   studied parameter range at ages 1Myr and 10Myr as dots (blue and
-   red respectively), and the naked photometry as crosses. The dashed
-   lines are a recent BD disc excess cuts used in
-   \citet{2005ApJ...631L..69L} for IC348 at a nominal age of 3-4Myr
-   \citet{2008MNRAS.386..261M}. It must be noted that the naked stars
-   of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours. The \textit{left panel} shows the typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
-   and the \textit{right panel} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors.\label{irac_cut}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_cut_2.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing an observational cut used in
-   \citet{2008ApJ...688..362L} for data of the $\sigma$ Orionis
-   cluster. It must be noted that the naked stars of
-   $M=$0.01$M_{\odot}$ are not included in this figure as their SEDs
-   do not extend far enough into the IRAC passbands to derive reliable
-   colours. The systems are seperated by age as described in Figure
-   \ref{irac_cut}. The \textit{left} and \textit{right panels} again
-   show the typical ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) and extreme ($\dot{M} \geq$
-   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors respectively as
-   in Figure \ref{irac_cut}.\label{irac_cut_2}}
-\end{figure*}
-
-CASE STUDY:
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rho_oph_102.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing CMDs and CoCoDs of systems with matching
-   parameters to $\rho$ Ophiucus 102 from
-   \citet{2002A&A...393..597N}. The object $\rho$ Ophiusucs 102 is
-   shown in \textit{all panels} as a black star, the BDD systems are
-   the seperated by age, with the 1 and 10 Myr systems appearing as
-   blue and red dots respectively. The \textit{top left panel} shows a
-   $M_J$, $(J-H)_0$ CMD, the \textit{top right panel} a $M_J$,
-   $(J-K)_0$ CMD, the \textit{bottom left panel} a $M_R$, $(R-I)_0$
-   CMD and the \textit{bottom right panel} shows a $(J-H)_0$,
-   $(J-K)_0$ CoCoD.\label{rho_oph_102}}
-\end{figure*}
-
-SHOW ROTATION RATE CORRELATION LOST AS  \cite{1997AJ....114..288M} HAD
-FLAT DISCS FACE ON WE HAVE VIEWING ANGLES AND VERTICAL HYDRO
-
-we find no correlation in general so is unlikely to effect the
-population selection or attempts to show slow rotator to disc presence
-correlations: i.e. nairn
-
-Now we conclude on the rotaton rate to IR relation and the mass to
-accretion rate relationship.
-For individal model the J-K is dependent on lots of variables so the
-correlation with rotation rate is non existent
-
-NOTE ABOUT SUBSEQUENT PAPER WITH ANALTIC SOLUTIONS
-
-\subsection{Summary}
-
-summarise on the photometric sections
-
-\section{Conclusions}
-\label{conclusions}
-
-COPY IN THE MAIN FROM PERVIOUS PAPER REWRITE WITH BETTER EMPHASIS.
-
-\subsection{Derivation of Primary parameters}
-
-\subsection{Consequences for Accretion Rate to Stellar Mass
-  relationship}
-
-\subsection{Summary}
-
-rho outer and tau inner
-
-RESULTS:
-
-AGE, MASS AND DISC FRACTION PROBLEMS:
-INCLINATION AND FLARING AS PER WALKER
-
-THEREFORE:
-CAN'T ASSERT M TO MACC RELATION
-
-LOSS OF ROATIOANL PERIOD PROPORTIONALITY WITH IR EXCESS
-
-DISC STRUCT=
-
-FLARING INCREASES AS THE FLUX INCREASES, THEREFORE OPENING ANGLE
-REDUCES
-
-INNERR EDE ORIGINAL LOCATION PROPORTIONAL TO ROTATTION RATE
-RINAL POSITION PROPORTINAL TO INNER EDGE LOCATION
-
-INNER EDGE ALSO PUFFS UP AND THEN GETS BLASTED AWAY OVER RANGE OF
-ACCRETION RATES AS THE FLUX IS INCREASED.
-
-In this section we discuss the physical structures of our resulting
-BDD systems and how these vary with our input parameters. Following
-the work of \cite{2004MNRAS.351..607W} it is clear that for BDD
-systems in vertical hydrostatic equilibrium the disc flaring leads to
-increased obscuration of the central star and probable miss
-classification. In addition, \cite{1997AJ....114..288M} predicted a
-correlation between rotation rate and infrared excess due to the
-change in position (radial) and therefore temperature of the inner
-edge.
-
-Vertical disc structure \cite{2004MNRAS.351..607W}
-
-Rotation rate correlation with infrared excess \cite{1997AJ....114..288M}
-
-The structure of this paper is as follows. In Section \ref{model} we
-outline the model used, including an explanation of our physical
-assumptions (Section \ref{physics}), a brief description of the
-radiative transfer code (Section \ref{torus}), and an explanation of
-the derivation of emergent quantities such as photometric magnitudes
-(Section \ref{derived}). The ranges of the input variables are then
-explained and, where possible, justified using observational
-constraints in Section \ref{par_space}, with the total parameter space
-covered shown in Table \ref{par_space_table}. Section
-\ref{disc_struct} then contains analysis and description of the
-resulting temperature and dust density structures of the discs. The
-consequences of these changes in disc structure on the SEDs of these
-objects is then discussed in Section \ref{sed_analysis}. Section
-\ref{photometry} then details problems caused for the derivation of
-the primary parameters age, mass and disc fractions from photometry
-and the resulting relations built on these parameters; accretion rate
-to stellar mass and rotational period to disc presence. Finally,
-conclusions are drawn, with a summary, in Section
-\ref{conclusions}.**REWRITE AT END**
-
-\section[]{ACKNOWLEDGMENTS}
-
-\bibliographystyle{mn2e}
-\bibliography{references}
-\appendix
-
-\section{Consistency Checks and Problems}
-\label{consistency}
+problems remain, and these are explained in this section.
+
+\textit{-Compare photospheric flux to stellar direct for face-on.}
 
 Firstly, a check was made on the photospheric input flux and the
-resulting stellar direct flux (tagged by {\sc torus}) after the radiative
+resulting stellar direct flux (tagged by TORUS) after the radiative
 transfer simulation. The resulting flux distributions should match
@@
 inclinations, as more photons are scattered and absorbed by the disc.
+
+\textit{-Naked BD colours, to DUSTY published, no match-UPDATED
+  spectra.}
 
@@
 
+\textit{-Naked colours, compare to face-on colours (similar).}
+
 The final test of the derived colours and magnitudes was a comparison
@@
 an appraisal of the component SED, i.e. showing the stellar direct
-flux, as can be seen in Figure \ref{disc_eg_173}.
+flux, as can be seen in Figure \ref{disc_eg}.
+
+\textit{-Optical K band ZP different to Bessels.}
 
@@
 
+\textit{-Several IRAC ZPs available.}
+
 A further complication with our adopted photometric systems is the
@@
 1[24]=2.139, channel 2[70]=-0.2726 and channel 3[160]=-1.990.
+
+\textit{-Conclusions on checks:OK as differential phot for most part.}
 
@@
 
-\section{Website**}
+\section{Parameter space}
+\label{par_space}
+
+This section details the range of each of the input parameters we have
+varied and, where possible, gives justification for the selected
+ranges from published observations. The simulations in this paper
+cover variations in the stellar mass, stellar age, stellar rotation
+rate, accretion rate, the areal coverage of the accretion stream, disc
+mass fraction and the system inclination. In a subsequent paper we
+introduce variation of the outer radius and using an analytical
+vertical disc structure as oppose to vertical hydrostatic equilibrium.
+.A summary of the values adopted for each input variable is shown in
+Table \ref{par_space_table}.
+
+\subsection{Mass} 
+\label{par_mass}
+
+Representative masses within the BD regime were chosen as follows:
+0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 $M_{\odot}$.
+
+\subsection{Age}
+\label{par_age}
+
+Typical disc lifetimes for solar type stars are of order $\approx$ 10
+Myrs \citep{2001ApJ...553L.153H}. Therefore, we have adopted input
+ages of 1 and 10 Myrs for our model grid, to span the approximate
+range of ages over which discs influence will be important.
+
+\subsection{Rotation rate}
+\label{par_rotation}
+
+Data for rotation rates, from periodic variability surveys, are widely
+available for a range of different age clusters of TTS. However, fewer
+studies exist on the rotation rates of BD mass objects. To select a
+feasible range of periods for our model grid we have collated the
+results from some recent studies of BD variability. Rotation period
+data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
+\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
+where periods are found over the range 5.78$-$74.4 hours ($\approx$
+0.24$-$3.1 days) for BD mass objects. In some cases the periodic
+variability is irregular and assumed to come from active accretion hot
+spots on the BD surface \citep[see][for discussion of variability
+causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
+and evidence of accretion are also found to correlate with slower
+rotating TTS, which the authors construe as evidence for a disc
+locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
+period$ relationship extending into the BD mass regime, this faster
+rotation in younger mass objects is taken as evidence for a decreasing
+effectiveness of the angular momentum removal of the disc locking
+mechanism, i.e. imperfect disc locking. In addition,
+\cite{2004A&A...419..249S} argue that when compared with data from
+younger clusters disc lifetimes can be seen to decrease with central
+object mass.
+
+\cite{2005A&A...429.1007S} study rotation period data for stars in the
+vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
+\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
+\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
+variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
+for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
+some BD objects with irregular variability indicative of accretion hot
+spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
+the mass-period relationship of these data in comparison with data
+from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
+\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
+Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
+Ori sample has an age of around 2$-$3 Myrs or there is still
+significant disc locking (concluded using the slope of the mass-period
+relation). More specifically for the BD mass regime, they find
+\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
+lower period limit of 2$-$4 hours, therefore at any age a fraction of
+BD stars rotate at short and constant period. Given that these objects
+should spin up as they hydrostatically contract they invoke rotational
+braking in the BD mass regime as a mechanism of removing significant
+angular momentum.
+
+\cite{2003ApJ...594..971J} study the rotational periods of BD (and
+very low mass stars) in the Chameleon I region. This region is $\le$ 1
+Myrs old, and the authors find rotation periods of 2.19, 3.376 and
+3.21 days for their BD mass counterparts. Using supplementary data
+from the literature \cite{2003ApJ...594..971J} propose that a shorter
+lifetime of $\approx$5 Myrs for accretions discs around BDs is more
+probable and is inferred from the derivation of a shorter locking
+timescale. However, as discussed in the previous studies, an imperfect
+disc locking mechanisms is also hypothesised as responsible for the
+less significant loss in angular momentum out to ages of 10 Myrs. The
+data mentioned above and other datasets are summarised and discussed
+in \cite{2007prpl.conf..297H}, where a strong argument for the
+mass-period relationship can be found, shown in their Fig 6, alongside
+further support for either a shorter disc lifetime or imperfect disc
+locking mechanism for BD stars.
+
+Therefore, in summary, it is currently unclear if any disc locking
+mechanisms efficiency or disc lifetimes are a function of mass, with
+an associated phase change over the TTS to BD mass limit. Rotation
+rate and disc presence data are being used to explore issue.
+Therefore, to create a set of useful models to help contextualise the
+observational constraints we must adopt a realistic, and bounding,
+range of rotation rates. For our model grid, and associated age range
+($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
+placed at around the approximate median for the faster rotating
+samples, providing a useful benchmark for exploring possible detection
+limits of faster rotators with discs. The longer period is set at the
+approximate edge of the slow rotating tail, providing a limiting case
+for the slower rotating, disc-locked, candidates.
+
+\subsection{Areal Coverage}
+\label{par_cov}
+
+As discussed in Section \ref{par_rotation} evidence for irregular
+periodic variability has been found in BD stars with detections of
+associated stellar discs. This is construed as evidence for accretion
+hot spots formed as magnetically channeled material hits the stellar
+surface \citep[see discussion
+in][]{1995A&A...299...89B,2007prpl.conf..297H}. The irregularity is
+thought to be caused by changes in the magnetospheric structure and
+accretion rate \citep{1995A&A...299...89B}. For our model we have
+assumed that disc material is disrupted at the co-rotation radius and
+channeled onto the star in the form of accretion hot spots with a
+characteristic temperature. Therefore, to calculate the characteristic
+temperature and the resulting blackbody accretion flux we must adopt
+an accretion rate and areal coverage of the accretion stream.
+
+Little observational evidence can be found for approximate sizes of
+accretion hot spots due to their more transient nature and often
+smaller coverages, when compared to cooler or `plage' spots
+\citep{2007prpl.conf..297H}. \cite{1995A&A...299...89B} modeled the
+size of the cool spots on solar-type stars for a selection of
+periodically variable candidates. They found projections of cooler
+spots, onto the stellar disc, of a few to ~60\%.
+\cite{1995A&A...299...89B} also found projected sizes, onto the
+stellar disc, of typically a few \% to around 10\% for hot spots.
+\cite{1996AJ....112.2159B} used observations of YY Orionis monitoring
+flux amplitude variations as a function of wavelength to derive a
+probable hot spot area of around 10\%. The spot temperature was also
+modeled for YY Orionis in \cite{1996AJ....112.2159B}, resulting in a
+best fitting areal coverage of 11\%. Therefore, to bound the probable
+areal coverage range of the accretion hot spots we have adopted areal
+coverages of 1 and 10\%.
+
+\subsection{Accretion Rate}
+\label{par_accn}
+
+Accretion rates derived for pre-MS stars are of order -6 to -11
+log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$ \citep{2006A&A...452..245N}.
+With the largest accretion rates found in so-called FU Orionis type
+objects (after the object where they were first observed). For the
+more typical accretion rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9}
+M_{\odot}yr^{-1}$, for TTS,][]{2009arXiv0901.4120D}, several studies
+have now suggested that the accretion rate is strongly correlated with
+the mass of the central star. This relationship was perhaps first
+suggested by \cite{2003ApJ...592..266M} using various accretion
+diagnostics. Later, \citep{2005ApJ...625..906M} derived a relationship
+of approximately $\dot{M}\propto M_*^{~2}$. Further evidence was put
+forward by \cite{2004A&A...424..603N}, where accretion rates as low as
+5$\times$ 10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More
+recently, even lower accretion rates of $\approx$10$^{-13}M_{\odot}
+yr^{-1}$, have been derived for BDs by \cite{2009arXiv0901.3684H}.
+Further support for a dependence of accretion rate on stellar mass was
+apparent in the significantly more homogeneous dataset of
+\cite{2006A&A...452..245N}. \cite{2006A&A...452..245N} analysed a set
+of accretion rates and masses derived for pre-MS stars in $\rho$
+Ophiuchi and compared these results to stars in Taurus. They found
+that the accretion rate scales with central object mass, into the BD
+regime. However, work by \cite{2006MNRAS.370L..10C} suggests that much
+of this result is likely to be caused by biases and sensitivity
+limits.
+
+For any $\dot{M}\propto M_*$ relationship to be ratified, clearly, the
+associated mass derivations must be shown to be accurate. For the BD
+mass regime it has been demonstrated that classification, either
+spectroscopic or photometric, and therefore accurate mass derivation
+is exceedingly difficult for BDD systems
+\citep{2004MNRAS.351..607W}. The inclusion of significant levels of
+accretion flux will act to exacerbate this problem. Essentially, as BD
+mass objects have relatively cool photospheres, compared to the
+temperature of the accretion hotspots, meaning that for lower
+accretion rates, than for their CTTS counterparsts, the accretion flux
+dominates the small wavelength regime of the SED.
+
+Therefore, to strengthen, or reject, any stellar mass to accretion
+rate relationship, the limits of observational classification (and
+mass derivation) of accreting BDD systems must be understood. To
+provide a benchmark model grid of such systems, with which to aid
+interpretation of the observational data, we must select a range of
+accretion rates including and exceeding those detected for systems
+previously classified as BDs.
+
+As the relationship $\dot{M}\propto M_*^{~2}$ predicts lower accretion
+rates for BD mass objects it is essential that we model systems at
+higher accretion rates, which may have been missed in current
+observational studies. Therefore, we have adopted accretion rates of
+-6, -7, -8, -9, -10, -11 \& -12
+log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$.
+
+\subsection{Disc Mass}
+\label{par_mdisc}
+
+A further required input parameter is the mass of the circumstellar
+disc. Previously studies modeling BD discs have adopted a range of
+disc mass fractions, for instance \citep{2004MNRAS.351..607W} use 0.1,
+0.01 and 0.001$M_*$. \cite{2002ApJ...564..887W} fit observed spectra
+with modeled SEDs to derive a disc mass of 0.003$M_*$, for HH 30
+IRS. Subsequent derivations of disc masses have converged to within an
+order of magnitude, with the following specific results: 0.03$M_*$
+\citep[$\rho$ Ophiuchi,][]{2002A&A...393..597N}, 0.055$M_*$ \citep[GM
+Aurigae,][]{2003MNRAS.342...79R}, 0.03$M_*$ \citep[GY 5, GY 11, and GY
+310,][]{2004ApJ...609L..33M} and 0.022$M_*$\citep[2MASS
+J04442713+2512164,][]{2008A&A...486..877B}. As the derived disc masses
+all have a similar order of magnitude we have adopted $M_{\rm
+  disc}\approx $0.01$M_*$. As changes in disc masses are expected to
+change the resulting SED less than perhaps, accretion rate for
+example, we have not varied the disc mass for this study. The results
+of simulations varying this parameter will be published in a future
+paper.
+
+\subsection{Inclination}
+\label{par_inc}
+
+Discs around BD stars exhibit increased flaring, due to the reduced
+surface gravity in the disc \citep{2004MNRAS.351..607W}. This
+increased flaring, and therefore larger scaleheight of the disc
+results in a smaller opening angle, when compared to higher mass stars
+and their circumstellar discs. As has been shown in
+\cite{2004MNRAS.351..607W} effects caused by variations in the system
+inclination angle are much more significant for BDD systems, again
+compared to their higher mass analogues. Therefore, we have simulated
+ten observer to system inclination angles spaced evenly in
+$cos(inclination)$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
+and 90$^{\circ}$.
+
+A final list of all varied parameters and their values can be seen
+in Table \ref{par_space_table}.
+
+\begin{table*}
+\begin{tabular}{|l|l|}
+Input parameter&Values (\# values)\\
+\hline
+Mass ($M_{\odot}$)&0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 (8)\\
+Age (Myr)&1 \& 10 (2)\\
+Rotation period (days)&0.5 \& 5 (2)\\
+Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
+Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&-6, -7, -8, -9, -10,
+-11 \& -12 (7)\\
+Disc mass ($M_*$)&0.01 (1)\\
+Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
+(10)\\
+\end{tabular}
+\caption{List of all varied input parameters. Resulting in a total
+  number of models of 448 (plus 40 models without radiative transfer
+  simulations for the naked BDs) and 4480 SEDs (plus 40 for naked
+  BDs). \label{par_space_table}}
+\end{table*}
+
+\section{Results: Analysis and Discussion}
+\label{results}
+
+\textbf{Intro-Questions to answer:IMF, Formation, Disc timescales and
+  $\dot{M}\propto M_*^{\approx 2}$=Ages, Masses and Disc fractions}
+
+Uncertainty remains over the formation mechanisms, resulting IMFs and
+subsequent interaction mechanisms with associated circumstellar disc,
+for BDs. Furthermore, no current theoretical explanation can be
+demonstrated for the suspected stellar mass-accretion rate
+relationship \citep[$\dot{M}\propto
+M_*^2$,][]{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}
+derived from observations and doubt remains over the existence of a
+disc-locking mechanism in BDD systems. Theoretical models and are
+built upon constraints, such as ages, masses and disc fractions, and
+correlations, such as the accretion rate to stellar mass relation,
+derived from the data. Critically, these resulting constraints and
+relationships involve both the application of existing models, such as
+isochrones to derive ages, and the selection of bias-minimised
+samples, for instance removal of foreground or background contaminant
+stars. Clearly, if one is to adopt a new theoretical model or use an
+observed correlation as a constraint one must explore the suspected
+intrinsic biases and the reliability of the selection criteria.
+
+In this Section we explore the effects of disc presence and accretion
+(across the described representative ranges, Section \ref{par_space})
+for our model grid. Essentially the premise is that if one accepts the
+assumptions and physical processes within our model grid would one be
+able to derive robust parameters using existing methods and
+furthermore, are the correlations found in the data intrinsic to the
+grid.
+
+Practically, most parameters for young pre-MS stars are derived from
+surveys of populations, usually open clusters, using broadband
+photometry and subsequently constructed colour-magnitude and
+colour-colour diagrams (CMDs and CoCoDs respectively,
+hereafter). Therefore, in this Section, firstly we demonstrate the
+prohibitive effects on the broadband photometry of varying our input
+parameters (Section \ref{photometry}). Secondly, we explore the
+underlying causes of the photometric scatters and intrinsic
+correlations using the SEDs and structure of individual BDD systems
+(Section \ref{sed_causes}).
+
+\subsection{Photometry}
+\label{photometry}
+
+\subsubsection{Ages and Masses}
+\label{age_mass}
+
+For the derivation of ages optical CMDs, in particular in \textit{V,
+  V-I}, are most often used, and indeed most suitable. Whereas, IR
+CMDs, such as a \textit{J, J-K} CMD, are most suitable for mass
+derivation \cite[see references and discussions in][ and Section
+\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
+
+To delineate the effects of the accretion rate and circumstellar discs
+we have subdivided the grid into two groups, those with accretion
+rates typical for higher mass CTTS objects, defined as
+$\dot{M}=$10$^{-12}M_{\odot}yr^{-1}$ (negligible) to
+$\dot{M}=$10$^{-9}M_{\odot}yr^{-1}$ and those with elevated accretion
+rates, where $\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$. For several of the
+plots in this section the magnitude and colours for the
+$M_*=0.01M_{\odot}$ at high inclinations become extremely faint and
+red, respectively. In some cases these objects appear slightly without
+the scale of the diagram the axes where limited in this way to be able
+to show the changes in colour an magnitude for the majority of stars
+better. The colours and magnitudes for these lowest mass stars are not
+necessarily unreliable but simple hinder the aesthetics of the plots,
+and as they are at the limits of our grid we have decided to omit them
+from some Figures by trimming the axes. Additionally, stars at the
+highest inclinations, i.e edge on disc systems, are often omitted from
+the Figures due to their extremely faint magnitudes, meaning they
+would not be practically observable.
+
+\textit{Derivation of Ages}
+
+Figure \ref{spread_opt_VVI} shows four CMDs in \textit{V, V-I} with
+isochrones constructed from our data (comprising all masses from Table
+\ref{par_space_table}, excluding $M_*=0.01M_{\odot}$ for 10 Myr) at
+ages of 1 Myr and 10 Myrs, solid and dashed lines respectively. These
+isochrones are produced using the naked BD photometry at an accretion
+rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and a areal spot
+coverage of 10\%. The solid green line in the \textit{bottom left
+  panel} only is the 1Myr isochrone for naked systems at an accretion
+rate of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and a areal spot
+coverage of 10\%. The solid green line in the \textit{top left panel}
+only is the 1 Myr from \cite{2000A&A...358..593S} adjusted to a
+distance of 250pc and an extinction of $A_V=2$ mag, simulating a
+background population of CTTS stars. The remaining dots are the
+simulated photometry for the BD disc systems with accretion rates
+classed as typical (-9 to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$)
+at 1 Myr (only) for all areal coverages, periods and inclinations (see
+Table \ref{par_space_table}). The four panels then highlight the
+scatter in CMD space caused by variation across our input parameter
+space. The \textit{top left panel} splits the accretion rates into
+three, -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) as blue
+dots, -10 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black dots and -9
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red dots. The
+\textit{bottom left panel} shows the scatter due to period changes,
+with systems with periods of 5 days shown as blue dots and 0.5 days as
+red dots. The \textit{top right panel} shows the scatter caused by
+changes in areal coverage, with blue dots showing photometry from 1\%
+coverage systems and red dots for 10\% coverage systems. Finally, the
+\textit{bottom right panel} shows the results separated by inclination
+angles. The inclinations have been separated into three groups for the
+purposes of CMD analysis. These groups are $\theta \leq 48^{\circ}$ as
+blue dots (classed as face-on systems), $\theta> 56$ \& $64^{\circ}$
+(classed as the expected systems, as the expectation value of
+$cos(\theta)=60^{\circ}$) as black dots and $\theta \geq 71^{\circ}$
+(classed as edge-on systems) as red dots.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_opt_VVI.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{CMDs in $M_V, (V-I)_0$ showing,as lines, the isochrones for
+   all masses included in Table \ref{par_space_table} for ages 1 Myr
+   (solid) and 10 Myr (dashed). The isochrones are for naked BDs
+   without a disc, for the accretion rate -12
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (shown as in black), with
+   an areal coverage of 10\%. The solid green line in the \textit{top
+     left panel} only is the 1 Myr from \citet{2000A&A...358..593S}
+   adjusted to a distance of 250pc and an extinction of $A_V=2$ mag,
+   simulating a background population of CTTS stars. The dots are the
+   simulated photometry, of the star and disc system, for all models
+   at an age of 1 Myr with the accretion rates classed as typical (-9
+   to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). \textit{Top left
+     panel} shows the accretion rates separated into three groups -12
+   \& -11, -10 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as blue,
+   black and red dots respectively. \textit{Bottom left panel} shows
+   BDD systems with a rotation period of 5 days as blue dots and 0.5
+   days as red dots. \textit{Top right panel} shows those simulations
+   with an areal coverage of 1\% as blue dots and 10\% as red
+   dots. Finally, the \textit{bottom right panel} shows the systems in
+   three groups of inclinations, $\theta \leq 48^{\circ}$, as blue
+   dots, $\theta \geq 71^{\circ}$ as red dots and $\theta = 56$ \&
+   $64^{\circ}$ as black dots. \label{spread_opt_VVI}}
+\end{figure*}
+
+As can be seen in Figure \ref{spread_opt_VVI} current accretion in a
+star and disc system, for rates typical in the BD mass regime, creates
+a scatter in our simulated photometry indicative of a much larger
+isochronal age spread than 10 Myr. Indeed, for many BDD systems even
+at nominal accretion rates of -11 or -12
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, for our simulations, the
+colours of these stars move significantly blueward of the expected BD
+locus in a\textit{V, V-I} CMD. As the dots in Figure
+\ref{spread_opt_VVI} are the simulated photometry of BDD systems over
+a range of typical input parameters (see Section \ref{par_space}), an
+observed coeval 1 Myr population could reasonably be expected to show
+a similar scatter. The naked isochrones show that this spread in
+simulated photometry, would lead to a spread in isochronal age greater
+than the $\approx$10 Myr spread claimed for higher mass stars in some
+star forming regions (for instance the ONC). Furthermore, for the
+higher accretion rates of -9 or -10
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the movement of the star
+within the CMD will effectively move the star into the contamination
+region expected for background CTTS or MS stars at a \textit{V-I} of
+$\leq$1.5 and $M_V 12-10$, and as such the star would not be included
+in a photometrically selected BD sample. The solid green line, in the
+\textit{top left panel}, showing the 1 Myr isochrone of
+\cite{2000A&A...358..593S} at a distance of 250 pc and extinction of
+$A_V=2$ mags shows that the BDD systems with higher accretion rates
+could easily be confused for a background CTTS or MS population (as MS
+stars are simply less luminous at a roughly constant \textit{V-I} than
+the CTTS counterparts). Furthermore, scatter, although somewhat
+reduced, can be observed in the simulated photometry in the negligibly
+accreting systems, for example in the \textit{top left panel} some red
+dots, accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
+(which will be negligible compared to the photospheric flux, see
+Figure \ref{acc_dom}), still scatter below the 10 Myr. These objects
+may still be included in a `wide' photometric selection. This scatter
+is a strong function of inclination, as shown in the \textit{bottom
+  right panel}, where, as the inclination is increased the objects are
+pushed lower in the CMD. Indeed, for the edge on cases some objects
+have magnitudes fainter than show in Figure \ref{spread_opt_VVI}
+($M_V\approx 30$). This is expected as the star becomes obscured by
+the flared disc, interestingly for these systems the \textit{bottom
+  right panel} shows that this occurs for inclinations above around
+71$^{\circ}$ in most cases yet even for the lower inclination angles
+some objects have very faint magnitudes, this is due to the disc
+flaring leading to a smaller opening angle and is discussed later in
+Section \ref{disc_struct}. The \textit{top right panel} shows that the
+scatter, in \textit{V}, in our simulated photometry from the
+isochrones is significant for both areal coverages. However,
+significant scatter blueward in colour is slightly more evident for
+the lower areal coverage and therefore hotter accretion spot
+temperature, as is expected given that the higher spot temperature
+contributes more flux blueward of the photosphere. Finally, the
+\textit{bottom left panel}, shows significant scatter in the simulated
+photometry for both adopted rotation periods. This panel also shows
+that scatter in this diagram is not obviously correlated with the
+rotation period and therefore inner edge position. Additionally, the
+\textit{bottom left panel} shows that for naked systems accretion
+rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ lead to the stars
+being scattered into the region occupied by background CTTS and
+contamination (the lower accretion rates are all coincident with the
+-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for 1 Myr). Overall, as
+found in \cite{2004MNRAS.351..607W}, the dominant scattering effect
+for BD disc systems in an optical CMD appears to be caused by
+inclination and therefore obscuration effects of the disc on the
+star. This suggests that for a given photometric survey of BDD systems
+accreting at typical accretion rates and with an expected range of
+inclinations (centred on around 60$^{\circ}$) one would expect to
+exclude a significant fraction of these objects from any isochrone
+based selection.
+
+Similar scattering occurs when using CMDs constructed using \textit{R,
+  R-I} \citep[using the photometric system
+of][]{1998A&A...333..231B}. Figure \ref{spread_opt_RRI} shows the
+\textit{R, R-I} CMD.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_opt_RRI.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for Figure \ref{spread_opt_VVI} but the 1 Myr isochrone
+   of \citet{2000A&A...358..593S} is omitted and the CMDs are for
+   $M_R, (R-I)_0$. \label{spread_opt_RRI}}
+\end{figure*}
+
+Therefore, if one adopts the range of input parameters we have used
+(see Section \ref{par_space} for justification), our simulated
+photometry shows, qualitatively, that a coeval 1 Myr population of
+accreting BD stars and BDD systems, with typical accretion rates and
+range of inclinations, will exhibit a scatter in apparent isochronal
+age of $>$10 Myr. Furthermore, some objects will be scattered below
+and blueward of a 10 Myr isochrone. This has been shown for CMDs in
+\textit{V, V-I} and \textit{R, R-I}. It is important to note at this
+point that these conclusions are qualitative, and obviously based on
+our assumptions. However, the repercussion for isochronal age
+derivation and sample selection in the BD regime could be
+profound. Indeed this study has only included the effects of current
+or ongoing accretion from a disc, it has totally neglected any effects
+of accretion, both past and present, on the evolution of the central
+star. This past accretion could also act to reduce the stars radius,
+accelerating contraction
+\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
+additional scatter in a coeval population proportional to the range in
+accretion rates \citep[See][for full
+discussion]{2008MNRAS.386..261M}. Our findings support those of
+\cite{2004MNRAS.351..607W}, showing that a significant scatter is
+caused by obscuration of the central source by the central disc. In
+addition we have shown that the scatter blueward, into the CTTS or
+background MS locus, is caused by active accretion at levels found in
+CTTS stars, but currently not regularly recorded in stars classified
+or selected as BDs.
+
+\textbf{Derivation of Masses}
+
+Similar consequences are apparent when attempting to derive masses
+from isochrones using CMDs. We have constructed CMDs using the
+simulated photometry of our model grid in the \textit{JK}
+magnitudes. Figure \ref{spread_ir_JJK} shows CMDs in \textit{J, J-K} for
+the same data as Figure \ref{spread_opt_VVI}. The symbols have the
+same meanings as in Figure \ref{spread_opt_VVI}.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_ir_JJK.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for Figure \ref{spread_opt_VVI} but the CMDs is for $M_J,
+   (J-K)_0$.\label{spread_ir_JJK}}
+\end{figure*}
+
+As is shown by Figure \ref{spread_ir_JJK} a similar scatter is
+observed in our simulated photometry in the IR CMD as is evident in
+its optical counterparts. Once again, as shown in the \textit{top left
+  panel}, scatter is seen in both the nominal and higher accretion
+rates (-9 to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), meaning
+derivation of masses for objects using IR isochronal fitting of these
+objects would be very difficult. However, in this CMD the scatter is
+generally redward of the isochrone, this is still however into the
+region where background CTTS stars would be expected. The \textit{top
+  right panel} shows no correlation with areal coverage of the hot
+spot. Interestingly the \textit{bottom left panel} shows no clear
+evidence for a correlation in CMD position, and therefore distance
+from the isochrone, with rotation period of the system as found in
+\cite{1997AJ....114..288M}, this is discussed in more detail in
+Section \ref{disc_struct}. Additionally, \textit{bottom left panel}
+agains shows significant scatter away from the isochrone for the 1 Myr
+naked stars at an accretion rate of -9
+$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, however in this case the scatter
+is in the opposite sense (blueward as opposed to redward) to that
+caused by accretion and disc presence in the BDD systems. Again,
+scatter is still caused by changes in inclinations, as shown in the
+\textit{bottom right panel}, with fainter magnitudes for more inclined
+systems, as expected however, this effect causes a smaller change in
+magnitude in the IR due to less of the disc appearing optically thick
+at these wavelengths.
+
+Therefore, as for derivations of age, given our assumptions, and the
+adopted range of input parameters, a 1 Myr coeval population scatters
+significantly in a \textit{J, J-K} CMD. The \textit{J, J-K} CMD is
+representative of CMDs constructed from the \textit{JHK}
+passbands. So, qualitatively at least, derivation of masses using
+isochronal fitting of our simulated photometry would not produce
+reliable or accurate results. Again, as discussed for optical CMDs,
+these simulations do not include any of the effects of past or current
+accretion on the evolution of the central object, which is expected to
+significantly exacerbate the observed scatter. This is also true for
+the naked systems with small increases in accretion rate leading to
+significant scatters in the CMDs. Additionally, given the evidence
+discussed in \cite{2004MNRAS.351..607W}, supported by the evidence
+from our own simulated photometry shown in Figures
+\ref{spread_opt_VVI}, \ref{spread_RI} and \ref{spread_ir_JJK}, it is
+clear that young, accreting, BDD systems are likely to be
+misidentified when using photometric colours or magnitudes, even at
+generally canonical accretion rates. This casts doubt on the veracity
+of the mass to accretion rate relationship. For our model grid we have
+not assumed any such relation, therefore, as our data would also show
+a similar relation it suggests that the observed result may be caused
+by intrinsic scattering. The relation, $\dot{M}\propto M_*^{2}$
+suggests that their is a dearth of lower mass stars accreting at
+higher rates. We have shown that for accretion rates in the range -12
+to -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with
+higher accretion rates would be preferentially missed using
+photometric or isochronal selection.
+
+\subsubsection{Extreme accretion rates}
+\label{elevated_accn}
+
+\textbf{CMDs}
+
+BDD and naked BD systems with elevated or extreme accretion rates are
+also likely to be miss-classified, or not observable in the same
+dynamic magnitude range as a BD survey.  Figure \ref{high_acc_opt}
+shows our isochrones for the naked BD systems with accretion rates of
+-6, -7 \& -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ at 1 Myr (solid
+lines in red) with areal coverages of 10\%, and the pre-MS isochrone,
+at 1 Myr, of \cite{2000A&A...358..593S} for higher mass stars, down to
+$M_*=$0.1$M_{\odot}$ (solid black line). The remaining dots are the
+simulated photometry from our model grid for stars with an age of 1
+Myr and accretion rates of -6, -7 \& -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, and the complete range of all
+other input parameters (see Table \ref{par_space_table}. As can be
+seen by comparing Figure \ref{spread_opt_VVI} with Figure
+\ref{high_acc_opt} the simulated photometry for the naked systems
+changes dramatically with increasing accretion rate, meaning that even
+without the effects of a disc individual highly accreting BDs
+dramatically change position in an optical CMD. The simulated
+photometry of the disc systems is then separated in each panel. The
+\textit{top left panel} shows systems with accretion rates of -6, -7
+and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red, black and blue
+dots respectively. The \textit{top right panel} distinguishes the
+areal coverages of 1 and 10\% as red and blue dots respectively. The
+\textit{bottom left panel} separates the two rotational periods of 5
+and 0.5 days into blue and red dots respectively. Finally, the
+\textit{bottom right panel} plots the three adopted inclinations
+groups $\theta \leq 48^{\circ}$, $\theta> 56$ \& $64^{\circ}$,
+$cos(\theta)=60^{\circ}$) and $\theta \geq 71^{\circ}$, as blue, black
+and red dots respectively.
+
+The \textit{top left panel} shows that these objects are generally
+scattered to an apparently higher (isochronal) mass and older
+(isochronal) age, with the scatter increasing with accretion
+rates. This means that as the accretion rate increases the star is
+pushed to bluer and brighter colours and magnitudes, effectively, to
+higher stellar masses. The \textit{top right panel} shows that this
+effect is apparent for both areal coverages, it is perhaps surprising
+that in general there does not appear to be a reduction in the
+magnitude of the scatter when one moves to the larger areal
+coverage. The \textit{bottom left panel} shows again that there is no
+correlation in CMD position with rotation rate, and therefore
+co-rotation radius (again this is discussed further in Section
+\ref{disc_struct}. Finally, the \textit{bottom right panel} again
+shows that the system inclination scatters the resulting position
+within the CMD, with greater inclination meaning greater obscuration
+of the central star, by the disc, and therefore fainter magnitudes and
+redder colours, and it is clear that photometrically a highly
+obscured, highly accreting BDD system could be photometrically
+classified as contamination or a higher mass CTTS system.
+
+Once again, given our assumptions, qualitatively, young, pre-MS BD
+disc systems accreting at higher rates would not be identifiable as
+such from optical CMDs and isochronal fitting. Meaning it is likely
+that our data would indicate a stellar mass to accretion rate
+relation, even though we have not adopted such a relationship.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/high_acc_opt.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{The optical CMD, $M_V, (V-I)_0$ showing the effects of
+   extreme accretion rates. The solid black line is the pre-MS
+   isochrones of \citet{2000A&A...358..593S} at 1 Myr for masses down
+   to 0.1 $M_{\odot}$, the solid red lines are our derived isochrones
+   for the naked photospheric models at accretion rates of -6, -7 \&
+   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, colours of red, black
+   and blue respectively, using an areal coverage of 10\% (the coolest
+   and therefore lowest accretion luminosity). The dots are the
+   simulated photometry for the BDD systems for the three highest
+   accretion rates (as for the isochrones). \textit{Top left panel}
+   shows the accretion rates separated into three groups -6, -7 and -6
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red, black and blue dots
+   respectively. The data in the remaining panels is separated into
+   the groups used in Figure \ref{spread_opt_VVI} using the same
+   symbols and colours.\label{high_acc_opt}}
+\end{figure*}
+
+A similar situation is apparent for the IR passbands, where isochrones
+are often used to derive stellar masses. Figure \ref{high_acc_ir} is
+the IR version of Figure \ref{high_acc_opt}, the only difference
+between the figures are the colours and magnitudes, the conventions,
+symbols and models are the same. Figure \ref{high_acc_ir} shows the
+CMDs using \textit{J, J-K}, also using the same conventions for each
+of the \textit{four panels}.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/high_acc_ir.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As above but for $M_J, (J-K)_0$ colours. Here the effects
+   of high accretion can shift the stars into higher or lower mass bins.
+   \label{high_acc_ir}}
+\end{figure*}
+
+As can be seen by comparing Figure \ref{spread_ir_JJK} and Figure
+\ref{high_acc_ir}, accreting BD systems without discs are shifted
+brighter and bluer resulting in a large error in isochronal mass
+derivation. The simulated photometry for BDD systems however, shows
+large magnitudes of scatter redward and towards slightly brighter
+magnitudes. Given that the reddening vector is approximately
+horizontal in a \textit{J, J-K} CMD many of these objects will appear
+as heavily obscured objects of higher mass. The \textit{top left
+  panel} shows that the scatter does increase for higher accretion
+rates, however, even at the lower of the accretion rates (-8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), significant scatter is
+evident. The \textit{top right panel} shows that the scatter is
+roughly the same for both areal coverages. The \textit{bottom left
+  panel} shows, again, no correlation between rotation rate and
+scatter within the CMD. This is unsurprising as at these elvated
+accretion rates the increase in flux will lead to significant levels
+of dust sublimation of the inner edge, as discussed in more detail in
+Section \ref{disc_struct}. Finally, the \textit{bottom right panel}
+shows systems with a larger inclination having, generally lower
+magnitudes, and therefore lower masses, as expected.
+
+Therefore, again as for the optical case, given our assumptions and
+parameter space, BDD systems accreting at higher rates would not be
+identified with the correct mass in most cases using IR CMDs.
+
+\subsubsection{Disc fractions}
+\label{derive_frac}
+
+To distinguish between the proposed formation mechanisms for BDs, and
+to derive disc lifetimes, accurate derivations of disc fractions are
+required (as well as stellar masses).
+
+\textbf{Derivation of disc fractions.}
+
+Disc fractions have been derived using infrared excesses previously in
+\textit{JHK}, however recent works pre-dominantly use \textit{Spitzer}
+IRAC magnitudes. Furthermore, MIPS magnitudes are used to identify
+so-called debris discs, where IR excesses are not apparent at shorter
+wavelengths. Finally, disc fractions have also been derived using the
+$\alpha$ criteria, where $\alpha=\frac{dlog\lambda
+  F\lambda}{dlogF\lambda}$ between two limiting wavelengths,
+originally used to distinguish amongst Class I, II or II sources, but
+now used to detect disc presence
+\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
+used as a selection criterion for disc presence for TTS stars. We have
+constructed the $\alpha$ values for our model grid by adopting the
+limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
+8.0$\mu$m.
+
+\subsubsection{Colour-colour plots}
+\label{col_col_plots}
+
+Figure \ref{ir_excess} shows CoCoDs in \textit{J-H, J-K} for our
+simulated photometry for all accretion rates, masses, inclinations,
+coverages and periods, at 1 Myr only. The black crosses are the
+simulated photometry of the naked BD systems, with the dots the
+simulated photometry of the BDD systems, for 1 Myr only.  The
+\textit{top left panel} then separates the accretion rates with -12,
+-11, and -10 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as red dots
+and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as green dots and
+-8, -7, and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue
+dots. The \textit{top right panel} distinguishes those models with
+areal accretion stream coverages of 1 and 10\% as blue and red dots
+respectively. The \textit{bottom left panel} separates the rotational
+periods with 0.5 days shown as red dots and 5 days as blue dots. The
+\textit{bottom right panel} shows each of the three inclination groups
+$\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as
+green dots and $\theta \geq 71^{\circ}$ as red dots.
+
+As can be seen for all the panels of Figure \ref{ir_excess} there is a
+slight overlap between the naked or disc less objects and the BDD
+systems. This overlap is small, only some of the smallest mass naked
+objects appear redward of the main population. Generally, a well
+placed cut should identify a large proportion of the disc candidates
+as is well known, if there is little complication from variable
+extinction and a well defined photometric system. However, the fact
+that an overlap exist at all will lead to some confusion as to the
+position of any disc excess cut. For real data a cut will be placed at
+a user identified paucity or gap in the CoCoD. Therefore, in practice,
+if any other region of the population appears equally, or more, sparse
+the cut is likely to be miss-placed. In practice these disc fractions
+are known to be lower limits of the true values, so ostensibly a miss
+placed cut, essentially missing some disc candidates is not
+problematic. On further inspection however it does introduce a crucial
+bias. In all panels of Figure \ref{ir_excess} potential gaps or drops
+in the number of stars can be seen at $J-K \approx$ 1.5 \& 2.5. The
+\textit{top left panel} shows that changes in accretion rate do not
+appear, qualitatively, to correlate with CoCoD position, indeed
+changes in the different areal coverages (\textit{top left panel}),
+inclinations (\textit{bottom right panel}) and rotation rate
+(\textit{bottom left panel}) also appear to produce random scatter.
+
+Critically a strong correlation can be
+observed between CoCoD position and rotation period of the system in
+the \textit{bottom left panel}. This panel shows that longer period
+objects, in general, lie closer to the naked BD locus and are
+therefore more likely to be classed as disc less stars. Conversely,
+almost all of the short period objects lie well separated from the
+naked BD locus, and one could also argue for a separation between the
+two populations of different rotation periods at $J-K \approx$2. It is
+therefore, likely, that early surveys of BD (or perhaps TTS) stars
+attempting to find a correlation between disc presence and slower
+rotation rates, to support disc locking, were heavily affected by this
+bias. Essentially, unless the data are free from variable extinction
+and photometric errors are small, manually placing a disc excess cut
+based on population densities is likely to preferentially miss slower
+rotators and include faster rotators. This leads to an
+anti-correlation between disc presence and slow rotation period.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/ir_excess.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure showing relative positions of accreting BDs with
+   (naked) and without discs in $(J-H)_0, (J-K)_0$ CoCoDs. \textit{Top
+     left panel}, this shows all studied accretion rates as green, red
+   blue and black dots for -6, -7, -8 and -9, -10, -11, -12 (together)
+   respectively log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
+   \textit{Lower left panel}, here blue dots are star disc systems
+   with a rotation period of 5 days and red for 0.5
+   days. \textit{Upper right panel}, blue dots are those simulations
+   with an areal coverage of 1\% and red dots have 10\%. Finally, the
+   \textit{lower right panel}, the systems at different inclinations
+   are shown with 0, 60 and 90$^{\circ}$ shown as black, blue and
+   red dots respectively.
+   \label{ir_excess}}
+\end{figure*}
+
+More recent studies, and indeed those studies where strong support for
+a disc locking mechanism is found, use data from the IRAC camera on
+the \textit{Spitzer} space telescope \citep[as for TTS,
+see][]{2007ApJ...671..605C}. Therefore, using our simulated photometry
+in these passbands we are able to investigate any possible expected
+biases in observations of this type. Figures \ref{irac_excess} and
+\ref{irac_excess_2} are similar to Figure \ref{ir_excess} showing the
+same models and using the sames conventions and symbol meanings, only
+showing constructed CoCoDs using IRAC channels. It is important to
+note that objects, either naked or with discs, of mass,
+$M_*=$0.01$M_{\odot}$ are not included in Figures \ref{irac_excess} and
+\ref{irac_excess_2}, as their flux becomes unreliable and noise
+dominated at these longer wavelengths. Figure \ref{irac_excess} shows
+[4.5]-[5.8] against [3.6]-[4.5] and Figure \ref{irac_excess_2}
+shows [5.8]-[8.0] against [3.6]-[4.5], two commonly used disc
+identification CoCoDs. In both these figures the naked (disc less) BD
+population is very well separated from the main population, meaning in
+a region free of variable extinction and with reliable photometry disc
+excess cuts can be placed with a high degree of confidence. As seen
+for Figure \ref{ir_excess} little correlation is found between CoCoD
+position and accretion rate, areal coverage or inclination, however, a
+clear correlation is again found with rotational period.
+
+The effect of rotational period on the position of the BDD systems in
+the IRAC CoCoDs is the reverse of that found for \textit{JHK}. Longer
+period objects will be observed as lying further from the naked BD
+locus, resulting in any uncertainty in the cut position preferentially
+including shorter period systems. This may introduce a slight bias in
+disc fraction surveys carried out using IRAC data, perhaps falsely
+increasing the apparent strength of a disc-locking type correlation
+between inferred disc presence and slower rotators. However, if a
+similar effect is apparent in TTS (as would be expected albeit
+slightly reduced due to less significant flaring of the outer disc),
+the much clearer separation between naked and disc systems means that
+this bias will be much easier to avoid.  Therefore, our results do not
+affect the recent evidence for a disc-locking mechanism in TTS.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/irac_excess.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for figure \ref{ir_excess} but in IRAC colours
+   [3.6]-[4.5] against [4.5]-[5.8]. 
+   \label{irac_excess}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/irac_excess_2.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for figure \ref{irac_excess} but in IRAC colours
+   [3.6]-[4.5] against [5.8]-[8.0]. 
+   \label{irac_excess_2}}
+\end{figure*}
+
+\textbf{IRAC and MIPS diagrams}
+
+**NOTE ABOUT $M_*=$0.01$M_{\odot}$ CURRENTLY NOT REMOVED**
+
+Figures \ref{irac_mips_excess} and \ref{irac_mips_excess_2} show
+CoCoDs for colours constructed using IRAC and MIPS data. These Figures
+include the same models as Figures \ref{irac_excess} and
+\ref{irac_excess_2}, presented using the same symbols and colour
+conventions. The longer wavelength MIPS data provides better
+sensitivity to the outer disc emission. As with the IRAC data
+alone the separation between the BDD and naked systems is large and
+the clearest correlation between input parameter and colour-colour
+space position is rotation period. A evident in the \textit{bottom
+  left panels} of Figures \ref{irac_mips_excess} and
+\ref{irac_mips_excess_2}, the longer period systems generally lie
+redward in both [3.6]-[4.5] and [8.0]-[24.0] than the shorter period
+systems. Some correlation of colour-colour position and inclination is
+evident from the \textit{bottom right panels} of Figures
+\ref{irac_mips_excess} and \ref{irac_mips_excess_2}. In this case as
+the inclination increases the systems generally move redward in
+[8.0]-[24.0].
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/irac_mips_excess.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{A CoCoD constructed using both IRAC and MIPS data showing
+   [3.6]-[4.5] against [8.0]-[24.0]. The symbols are as described in
+   As for figure \ref{ir_excess}.
+   \label{irac_mips_excess}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/irac_mips_excess_2.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for figure \ref{irac_mips_excess} but using colours
+   [3.6]-[5.8] against [8.0]-[24.0].
+   \label{irac_mips_excess_2}}
+\end{figure*}
+
+Figure \ref{mips_four} shows CoCoDs constructed using only MIPS data,
+plotting the colours 24$-$70$\mu$m against 70$-$160$\mu$m for the 1 Myr
+naked and BDD systems. Figure \ref{mips_four} shows that, again, the
+naked and BDD systems are well separated. Figure \ref{mips_four} also
+shows the correlations in scatter for each input variable. For
+\textit{all panels} of Figure \ref{mips_four} the crosses show the
+naked systems and the dots are the BDD systems. The \textit{upper left
+  panel} separates the two accretion rates with -8 and -12
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ plotted as blue and red dots
+respectively. In the \textit{upper right panel} the BDD systems with 1
+and 10\% areal coverages are plotted as blue and red dots
+respectively. The \textit{lower left panel} plots the periods of 5 and
+0.5 days as blue and red dots respectively. \textit{lower right panel}
+separates the BDD systems by inclination with 0, 60 and 90$^{\circ}$
+plotted as black, blue and red dots respectively. As can be see in
+Figure \ref{mips_four} the inclination correlates strongly with CoCoD
+position with the almost edge-on systems appearing much redder than
+the naked or face on BDD systems. Furthermore, using the \textit{lower
+  panels} it can be seen that for each inclination the CoCoD position
+is then separated by rotation period, with two separated populations
+for each inclination group.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/mips_four.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for figure \ref{irac_excess} but in MIPS colours
+   [24]-[70]($\mu$m) against [70]-[160]($\mu$m). 
+   \label{mips_four}}
+\end{figure*}
+
+\subsubsection{Observational cuts}
+\label{obs_cuts}
+
+Some recent studies of disc fractions for BD populations have used
+data from the \textit{Spitzer} IRAC camera. Figures
+\ref{irac_cut} and \ref{irac_cut_2} show the simulated photometry for
+our complete model grid. Naked BDs are shown as crosses and BDD
+systems as dots, with 1 and 10 Myrs data shown as blue and red dots
+respectively. The dashed lines are cuts used in two recent
+publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
+a study of IC348 and Figure \ref{irac_cut_2} from
+\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis. In both cases
+the effects of extinction are either negligible in the plotted
+colours, with values of $E([3.6]-[4.5])<0.04$ \& $E([4.5]-[5.8])<0.02$
+for IC348, or the cuts have been placed in intrinsic colour space as
+for $\sigma$ Orionis. As can be seen from Figures \ref{irac_cut} and
+\ref{irac_cut_2} most of the disc systems from our simulated
+photometry would be correctly identified using these cuts. It is
+important to note that as for Figures \ref{irac_excess} and
+\ref{irac_excess_2} stars of mass, $M_*=$0.01$M_{\odot}$, are not
+included due to unreliable flux levels at these
+wavelengths. Additionally, our conclusions so far have been drawn from
+differential photometric arguments, in this case we are using
+intrinsic colours and these values are extremely sensitive to changes
+in zero point and photometric calibration.
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/irac_cut.ps"
+   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+ \caption{This shows all simulated photometry for the entire studied
+   parameter range at ages 1Myr and 10Myr as dots (blue and red
+   respectively), and the naked photometry as crosses. The dashed
+   lines are a recent BD disc excess
+   cuts used in \citet{2005ApJ...631L..69L} for IC348 at a nominal age
+   of 3-4Myr \citet{2008MNRAS.386..261M}. It must be noted that the naked
+   stars of $M=$0.01$M_{\odot}$ are not included in this figure as their
+   SEDs do not extend far enough into the IRAC passbands to derive
+   reliable colours.
+   \label{irac_cut}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/irac_cut_2.ps"
+   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+ \caption{This figure shows an observational cut used in
+   \citet{2008ApJ...688..362L} for data of the $\sigma$ Orionis
+   cluster. It must be noted that the naked
+   stars of $M=$0.01$M_{\odot}$ are not included in this figure as their
+   SEDs do not extend far enough into the IRAC passbands to derive
+   reliable colours.
+   \label{irac_cut_2}}
+\end{figure}
+
+\textbf{alpha}
+
+Disc fractions are also derived using the $\alpha$ value
+\citep{2006AJ....131.1574L}, essentially a slope of the SED between
+two wavelengths (at wavelengths longer than the stellar flux
+peak). Figure \ref{alpha_zoom} shows the derived $\alpha$ values
+between 3.6 and 8.0$\mu$m for our entire model grid (against an
+arbitrary model number), with dots showing BDD systems and crosses
+showing naked systems. As shown for TTS $\alpha>-$2 distinguishes
+systems with discs \citep{2009arXiv0901.2603K}. As can be seen in
+Figure \ref{alpha_zoom} almost all (except $\frac{3}{1120}$) disc
+systems would be successfully identified using this
+criterion. Suggesting that the $\alpha$ value is a reliable disc
+indicator for BD systems. Figure \ref{alpha_four} show the same Figure
+(Figure \ref{alpha_zoom} in \textit{four panels} with each panel
+showing spread caused by a particular input variable. The
+\textit{upper left panel} shows the alpha values for two different
+accretion rates, with -12 and -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue and red dots
+respectively. The \textit{upper right panel} differentiates
+populations with different areal coverages of the accretion stream,
+where 1 and 10\% are shown as blue and red dots respectively. The
+\textit{lower left panel} shows scatter caused by rotational period
+changes, with periods of 5 and 0.5 days shown as blue and red dots
+respectively. Finally, the \textit{lower right panel}, the systems at
+different inclinations are shown with 0, 60 and 90$^{\circ}$ shown as
+black, blue and red dots respectively. It is important to note that
+the lowest mass objects ($M_*=$0.01$M_{\odot}$) do not appear in Figures
+\ref{alpha_zoom} or \ref{alpha_four} due to unreliable flux estimates
+for the stellar atmospheres at the longer wavelengths ($\lambda >$4$\mu$m).
+
+Figure \ref{alpha_four} shows, as one would expect a similar
+scattering pattern to the IRAC photometry. This is as the $\alpha$
+value has been derived over a similar wavelength range, namely, 3.6
+to 8.0$\mu$m. Essentially, the $\alpha$ values shows the scatter is
+uncorrelated with coverage and accretion rate, as expected for the
+shorter wavelength accretion flux contribution. As the inclination
+angle increases the $\alpha$ value generally reduces. Finally, the
+shorter period objects lie closer to the naked BD locus in $\alpha$
+space.
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/alpha_zoom.ps"
+   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+ \caption{This Figure shows the $\alpha$ value
+   \citep{2006AJ....131.1574L} (against an arbitrary
+   model number)  used
+   \citet{2009arXiv0901.2603K}, $\alpha=\frac{dlog(\lambda
+     F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
+   $\mu$m). Crosses show the simulated objects without discs and dots
+   are
+   those with circumstellar disc, the horizontal line is the
+   $\alpha>-$2 cut used to identify disc candidates for solar type
+   stars in \citet{2009arXiv0901.2603K}. Note, that stars of
+   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
+   estimates, in the atmosphere models, for longer wavelengths
+   ($\lambda>$4$\mu$m).
+   \label{alpha_zoom}}
+\end{figure}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/alpha_four.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As Figure \ref{alpha_zoom} except each of the \textit{four
+     panels} shows the underlying scatter separated by input
+   variable. The \textit{upper left panel} shows the alpha values for
+   two different accretion rates, with -12 and -8
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue and red dots
+   respectively. The \textit{upper right panel} differentiates
+   populations with different areal coverages of the accretion stream,
+   where 1 and 10\% are shown as blue and red dots respectively. The
+   \textit{lower left panel} shows scatter caused by rotational period
+   changes, with periods of 5 and 0.5 days shown as blue and red dots
+   respectively. Finally, the \textit{lower right panel}, the systems
+   at different inclinations are shown with 0, 60 and 90$^{\circ}$
+   shown as black, blue and red dots respectively. Note, that stars of
+   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
+   estimates, in the atmosphere models, for longer wavelengths
+   ($\lambda>$4$\mu$m).
+   \label{alpha_four}}
+\end{figure*}
+
+\subsection{Physical causes of scatters and correlations}
+\label{scatter_causes}
+
+**ADD IN TEMPERATURE RANGES FOR DISCUSSION HERE**
+
+The scatters observed in our photometry, caused by varying our input
+parameters, are obviously caused by changes in the simulated
+SEDs. These changes are in turn due to changes in the physical
+structure of the system. In this Section we examine the simulated SEDs
+and resulting temperature and density structure of the discs to
+explain the photometric scatters.
+
+As discussed, Figure \ref{spread_opt_VVI} shows that for the optical CMD
+(\textit{V, V-I}), the scatter in colour appears correlated with areal
+coverage and accretion rate of the accretion stream. Objects with
+higher accretion rates and smaller areal coverages and, therefore,
+higher fluxes or accretion luminosities scatter blueward of the
+isochrone. There is also perhaps evidence of a weak correlation with
+rotation period and colour scatter in Figure
+\ref{spread_opt_VVI}. Finally, the scatter in the magnitude (\textit{V}),
+and to some extent colour (\textit{V-I}), present in the data in
+Figure \ref{spread_opt_VVI} is clearly correlated with inclination. For
+the IR CMD (\textit{J, J-K}), once again, scatter in magnitude appears
+strongly correlated with inclination. There is also a clear
+correlation of scatter in colour with rotation period, but the
+remaining two variables appear to show random scatter only.
+
+To explore the causes of the shifts we must relate the changes in the
+resulting SEDs to the relevant physical parameters. Essentially, the
+summed flux is comprised of four main components, the stellar
+photosphere (luminosity $L_*$), the accretion stream (luminosity
+$L_{\rm acc}$), the disc inner boundary or wall (luminosity $L_{\rm
+  wall}$), and the outer regions of the, highly-flared, circumstellar
+disc (luminosity $L_{\rm disc}$). For a given mass and age, the radius
+and intrinsic stellar photospheric flux are fixed. For our model grid
+the fluxes are produced at effective temperatures of 3000K$<T_{\rm
+  eff}$1600K.
+
+The flux from the accretion stream is dominant at shorter wavelengths,
+within our range, peaking below a wavelength of 1$\mu$m (see Figure
+\ref{acc_dom}). This is as the accretion hotspot can reach much higher
+temperatures than the stellar photosphere, up to 16700K. The accretion
+luminosity is calculated using equation \ref{Lacc} (in Section
+\ref{physics}), and the resulting flux levels are computed using an
+effective temperature (Equation \ref{Tacc}, Section \ref{physics}) to
+generate a blackbody emission curve. As the accretion flux is
+calculated using a blackbody law, the peak wavelength is a function of
+the effective temperature of the accretion spot, $\lambda_{\rm
+  peak}\propto \frac{1}{T_{\rm acc}}$. Therefore, the effects of the
+accretion flux component on the resulting SED, in terms of total flux
+and peak wavelength, are a strong function of the input variables,
+accretion rate and areal coverage. Essentially, high accretion rates
+and low areal coverages lead to an increased influence of accretion
+stream on the final SED. The increased accretion flux creates a blue
+excess, easily dominating the cooler BD photospheres at shorter
+wavelengths. The converse of this is also true i.e. lower accretion
+rates with larger hot spots results in a reduction of the influence of
+the accretion flux on the SED.
+
+The flux from the inner boundary is a function of the temperature of
+the inner wall. This is dependent on its proximity to the central
+object. The initial inner wall radius was set as the magnetic
+co-rotation radius (see Section \ref{physics}). This distance is a
+strong function of rotational period, with $R_{\rm inner}\propto
+\tau^{2/3}$ (see Equation \ref{inner_eq}). During the radiative
+transfer simulations the inclusion of dust sublimation effects will
+result in a shift of the inner wall radius for the hotter wall
+temperatures. The differences in the initial and final inner wall
+radius are discussed in Section \ref{inner_edge_position}. However,
+they do not show significant differences between initial and final
+inner wall radii. Therefore, for our purposes the inner disc radius
+can still be considered proportional to the rotation period. This
+inner boundary will clearly be cooler than the stellar surface, or the
+accretion hot spot, and will therefore contribute flux at longer
+wavelengths. The resulting flux component, for the inner wall,
+dominates at longer wavelengths, peaking at between 2 and 3$\mu$m
+\citep{2001ApJ...560..957D}. This is due to its cooler temperature,
+which is neccesarily less than the dust sublimation ($\approx$1400K).
+
+**CHECK THIS EMISSION FROM IRAC ACTUALLY FROM JUST BEHIND THE INNER
+EDGE-THEREFORE ARGUMENT STILL STANDS BUT MUST ADD IN A PUFFING UP OF
+THE INNER EDGE EFFECT**
+
+Finally, the flux from the outer flared region of the disc is simply a
+function of the temperature of the outer disc. This, in turn, is a
+function of the stellar flux reaching these regions of the disc. This
+is a function of the rotational period. For closer inner boundaries
+more flux is intercepted by the inner boundary and therefore less
+reaches the outer regions, for longer periods the farther inner wall
+radii means more flux reaches the outer disc regions (see Section
+\ref{disc_period_relation}). These regions of the disc will be cooler
+than the inner boundary and, therefore only have a significant flux
+contribution at wavelengths longer than 3$\mu$m.
+
+Therefore, the shape of the resulting SED, for a star-disc system of
+at fixed stellar mass and age, will be dependent on the dominance of
+the hot short wavelength accretion component, the cooler
+mid-wavelength component of the inner boundary, and the even cooler,
+longer wavelength component from the outer regions of the disc.
+Practically, for our model grid, the shape is therefore a function of:
+Accretion rate and coverage ($L_{\rm acc}$) and the rotation period
+($L_{\rm wall}$ \& $L_{\rm disc}$).
+
+The final, and most important variable affecting the shape of the SED
+is inclination. This variable affects the balance of the photospheric
+flux escaping ($L_*$ \& $L_{\rm acc}$) and that observed from the disc
+($L_{\rm wall}$ \& $L_{\rm disc}$). Essentially, the flux for all wavelengths
+will reduce as the inclination increases. However, this reduction,
+with inclination, will reduce toward longer wavelengths. This is as
+the opacity of the disc will reduce with increasing wavelength.
+
+So, to relate these changes to the scatter we observe in the CMDs of
+Figures \ref{spread_opt_VVI} and \ref{spread_ir_JJK}, we have plotted the CMDs
+for a star of $M=$0.04$M_{\odot}$, at an age of 1 Myr, for a range of
+parameters in optical and IR colours in Figure \ref{spread_cmd}.
+Figure \ref{spread_cmd} shows the \textit{V, V-I} (\textit{left
+  panel}) and \textit{J, J-K} (\textit{right panel}) CMDs. For
+\textit{both panels} the naked BD systems, with negligible accretion
+flux (-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 10\% coverage)
+are shown as black crosses. For \textit{both panels} the red coloured
+symbols are those which have the inner boundary component maximised,
+i.e. with the shorter rotation period of 0.5 days, and the blue
+symbols denote systems with the longer period of 5 days, and therefore
+minimised inner boundary flux. The circles represent those systems
+with the accretion flux component maximised, i.e. an accretion rate of
+-8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 1\% areal coverage,
+and the triangles show systems with the accretion component minimised,
+i.e. an accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
+with 10\% areal coverage. Finally, the open symbols (circles or
+triangles in both red and blue) show systems at an inclination of
+face-on, 0$^{\circ}$, and the filled symbols at edge on, 90$^{\circ}$.
+
+**CHECK AND REWRITE**
+
+Figure \ref{spread_cmd} shows, that increasing the accretion flux
+component moves the star blueward significantly in the optical
+colours, \textit{left panel}, and much less in the IR, \textit{right
+  panel} (compare the circles to triangles of the same colour and
+type, open or filled.). In addition, maximising the inner boundary
+component moves the system redward significantly in both CMDs,
+although to a greater extent in the IR, \textit{left panel} (compare
+different colour symbols of the same type). Finally, the inclination
+as shown in \cite{2004MNRAS.351..607W}, both reduces the magnitude and
+shifts the object in colour (compare open and filled symbols of same
+colour and type). Comparing the \textit{two panels} shows that the
+disc component has a much more significant affect in both CMDs,
+optical and IR, than the accretion component. Interestingly, the
+effect of a disc is still significant for the optical \textit{V, V-I}
+CMD. The accretion component has a much more significant effect in the
+optical \textit{V, V-I} CMD than the IR \textit{J, J-K}, and indeed is
+probably negligible in the latter. The effect of the two variables is
+then essentially additive in CMD space, weighted by their dominance in
+either CMD regime. This means a blue-shifted, accretion dominated
+object in a \textit{V, V-I} CMD will be less blue-shifted if the inner
+disc boundary component is also maximised. Whereas, for the \textit{J,
+  J-K} CMD, the inner boundary has a more significant effect and
+maximising the accretion component will only lessen the red-shifting
+from the maximised disc. It is perhaps surprising that for BDD systems
+both accretion and disc presence, due to the inner boundary, can
+scatter the star in an optical CMD.
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/spread_cmd.ps"
+   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+ \caption{CMDs showing the colours and magnitudes of a BD with
+   $M_*=$0.04$M_{\odot}$. For \textit{both panels} a BD with negligible
+   accretion flux, -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
+   10\% coverage without a disc is plotted as a black
+   cross. Triangles, in \textit{both panels}, are BDD systems with
+   negligible accretion flux, i.e. -12
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 10\% coverage. Circles,
+   in \textit{both panels}, show BDD systems with maximised accretion
+   flux, i.e. -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 1\%
+   coverage. The red symbols then have a maximised inner boundary
+   component with a period of 0.5 days and blue symbols a minimised
+   inner boundary component with a period of 5 days. Finally, for
+   \textit{both panels} inclinations of 0 \& 90$^{\circ}$ are shown
+   as open and filled symbols respectively. The \textit{left panel}
+   shows the $M_V, (V-I)_0$ CMD and \textit{right panel} the $M_J,
+   (J-K)_0$ CMD.
+   \label{spread_cmd}}
+\end{figure}
+\clearpage
+
+The TORUS code identifies and tags photons as they pass through the
+simulation in one of four ways: Stellar direct, stellar scattered and
+thermal direct or thermal scattered, as described in Section
+\ref{seds}. This allows us to plot the component flux distributions of
+the objects, with discs, shown in Figure \ref{spread_cmd} and examine
+their flux components. The convenient components discussed above,
+namely: stellar photosphere ($L_*$), accretion component ($L_{\rm acc}$),
+disc inner wall component ($L_{\rm wall}$) and outer disc component
+($L_{\rm disc}$), will have contributions from differently tagged
+photons. The stellar flux will comprise the accretion and intrinsic
+stellar photospheric components, with the direct flux reaching the
+observer without interaction with the disc. Photons scattering through
+the disc will be dominated by photons from the inner boundary for
+systems with a small inner disc radius. The inner boundary component
+and outer flared disc components will also include the direct and
+scattered thermal photons.
+
+Figures \ref{spread_spec_lowacc} and \ref{spread_spec_highacc} show
+the total and component fluxes for the BDD systems shown in Figure
+\ref{spread_cmd}. For \textit{all panels}, in both Figures, total flux
+is shown as the solid black line, with the stellar and thermal fluxes
+shown as blue and red lines respectively. Also, in both Figures, the
+direct and scattered components of the stellar and thermal flux are
+plotted as solid and dashed lines respectively. In addition for both
+Figures, the \textit{left panels} shows the minimised inner boundary
+component, with a period of 5 days, and the \textit{left panels} the
+maximised inner disc boundary component with a period of 0.5 days. The
+vertical lines show the approximate response limits in wavelength of
+the \textit{VI} and \textit{JK} filters as dashed and solid lines
+respectively. The \textit{lower panels} show systems at an edge-on
+inclination, of 90$^{\circ}$, and the \textit{upper panels} show
+face-on systems with an inclination of 0$^{\circ}$.  Figures
+\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} show the
+minimised and maximised accretion flux component systems respectively,
+i.e. -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 10\% areal
+coverage for Figure \ref{spread_spec_lowacc} and -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 1\% areal coverage for
+Figure \ref{spread_spec_highacc}.
+
+Comparing the \textit{left \& right panels} of Figures
+\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} shows that as
+the period shortens the proportion of flux reprocessed by the disc,
+and inner wall, increases dramatically. This affects the flux and flux
+slopes in both the filter response regimes, however, it is much more
+significant in the IR regime. This effect causes the reddening seen in
+Figure \ref{spread_cmd}, and its increase in magnitude when comparing
+the \textit{left} to the \textit{right panel}, or optical to IR CMD.
+Comparing the \textit{upper \& lower panels} of Figures
+\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} shows the flux
+becoming dominated by the scattered components, which causes the
+reduction in magnitude and slight reddening of the systems as the
+inclination increases. Finally, comparing Figure
+\ref{spread_spec_lowacc} to Figure \ref{spread_spec_highacc} shows
+that as the accretion is maximised there is a significant increase in
+the flux and flux gradient, across the optical filter bandpasses, for
+the longer period. Whereas, there is a less significant change in the
+optical CMD. This is caused by a higher proportion of the stellar
+intrinsic and accretion flux being intercepted by the inner disc
+boundary.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_spec_lowacc.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{This Figure shows SEDs for the minimised accretion flux
+   component systems (-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
+   10\% coverage), from Figure \ref{spread_cmd}, which are shown as
+   triangles. The total flux is shown as a black line, with stellar
+   flux in blue and thermal flux in red, separated into direct (solid
+   lines) and scattered (dashed lines) components. The inner boundary
+   component is maximised on the \textit{left} and minimised on the
+   \textit{right panels}, with periods of 0.5 and 5 days
+   respectively. The vertical lines are the approximate filter
+   response limits for the \textit{VI}, dashed, and \textit{JK},
+   solid, bands. Two inclinations of 0 \& 90$^{\circ}$ are shown as
+   the \textit{upper} and \textit{lower panels}, respectively.
+   \ref{spread_cmd}.
+   \label{spread_spec_lowacc}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_spec_lowacc_log.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As Figure \ref{spread_spec_lowacc} but in log space.
+   \label{spread_spec_lowacc_log}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_spec_highacc.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for Figure \ref{spread_spec_lowacc} but for a maximised
+   accretion flux component (-8
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
+   1\% coverage), shown as circles in Figure \ref{spread_cmd}.
+   \label{spread_spec_highacc}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/spread_spec_highacc_log.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As for Figure \ref{spread_spec_highacc} but in log space.
+   \label{spread_spec_highacc_log}}
+\end{figure*}
+
+\subsubsection{Accretion Dominance: $L_{\rm acc}$}
+\label{accn_dominance}
+
+Figure \ref{acc_dom} shows the affect of the increasing accretion
+blackbody flux (for increasing accretion rates) for a BD star,
+$M=$0.04$M_{\odot}$, at 1 Myr. The panels in this figure also show the
+flux from a naked system, with no treatment of the disc. This enables
+us to view the effect of increasing accretion rate on the photospheric
+flux in isolation. The accretion rates included in all panels are -6,
+-7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black
+lines respectively). The \textit{lower panels} show the systems with a
+rotation period of 0.5 days and \textit{upper panels} for those with a
+rotation period of 5 days. Given our assumption that accretion occurs
+from the co-rotation radius, decreasing the rotational period moves
+this accretion radius closer to the star. As the accretion radius
+moves closer to the star the potential energy released by the accreted
+material is reduced. This effect can be seen when comparing the
+\textit{upper} and \textit{lower panels}, although the effect is
+marginal for all but the highest accretion rates. The \textit{left
+  panels} show accretion streams with an areal coverage of 1\% and the
+\textit{left panels} 10\%. As the areal coverage reduces the effective
+temperature of the accretion hot spot increases, resulting in an
+increase in accretion flux, and resulting shift to bluer wavelengths
+of the peak flux. This can be seen clearly by comparing the
+\textit{left} and \textit{right panels} of Figure
+\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
+shown is Figure \ref{acc_dom} is an insight into the accretion rate at
+which the accretion blackbody flux dominates over the photospheric
+flux. Figure \ref{acc_dom} shows that as the accretion rate raises
+above -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for systems with 1\%
+areal coverage, the accretion flux dominates the emergent SED at both
+periods. For the larger coverage the accretion flux begins to dominate
+between -7 to -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. Therefore
+for reasonable coverages (1-10\%) and rotational periods (0.5-5 days)
+the photospheric flux is effectively swamped by accretion flux for
+accretion rates log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-7$ , and for
+the most conservative case (1\% coverage with 5 day period) at
+accretion rates much lower than this
+(log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-$8). This suggests that
+accreting BD systems with accretion rates as low as -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ could be difficult to identify
+from SEDs as BD stars, and may well be classified as higher mass
+stars.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/acc_dom.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{This figure shows the photospheric flux against $\lambda$
+   ($\mu$m) of a Brown Dwarf with $M=$0.04$M_{\odot}$, at 1 Myr. No
+   disc is included, but blackbody fluxes from an accretion stream at
+   the rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
+   are shown as blue, red and black lines respectively. The
+   \textit{lower panels} show accretion for a star rotating at 0.5
+   days, with the \textit{upper panels} showing that of 5 days. The
+   \textit{left panels} systems with an areal coverage of 1\% and the
+   \textit{right panels} has 10\%. CONSTRUCTED USING GRAPHPS**
+   \label{acc_dom}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/acc_dom_log.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As Figure \ref{acc_dom} but in log space.
+   \label{acc_dom_log}}
+\end{figure*}
+
+Therefore, one can see that for higher accretion spot temperatures,
+flux shortward of the photospheric flux is markedly increased. This
+results, in general, in a brighter and bluer magnitude and colour for
+the combined system.
+
+\subsubsection{Disc effects: Flaring, $L_{\rm disc}$}
+\label{flaring}
+
+**SOME IMAGES TO PROVE POINT**
+**ADD MIPS DISCUSSION HERE AND SCALE HEIGHT STUFF**
+
+Scatter in optical CMDs is dominated by disc inclination (see Figures
+\ref{spread_opt_VVI}, \ref{spread_RI} and \ref{spread_VB}), and, even at
+longer wavelengths, scatter in IR CMDs is still correlated with
+inclination (see Figure \ref{spread_ir_JJK}). \cite{2004MNRAS.351..607W}
+have already shown that increased disc inclination lead to significant
+changes in the spectroscopic, and photometric properties of BDD
+systems. The scatter in optical and IR CMDs (in Section
+\ref{derive_primary}), for our model grid, appears strongly correlated
+with system inclination. This is a similar effect as found in
+\cite{2004MNRAS.351..607W}, where increases in the inclination angle
+quickly lead a significant proportion of the stellar flux being
+intercepted, and reprocessed, by the highly flared disc.
+
+Figure \ref{disc_eg} shows examples of our derived spectra for a BD of
+$M=$0.04$M_{\odot}$ (the middle of our mass range), at 1 Myr, with a
+rotation period of 0.5 days, and an accretion stream covering 1\% of
+the stellar surface accreting at a negligible rate of -12
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{upper left panel}
+shows the SED for the naked BD system with the remaining panels
+showing the SEDs from the three modeled inclinations, after a TORUS
+simulation of a disc with $M_{disc}=$0.01$M_*$. The \textit{lower left,
+  upper right and lower right panels} show inclinations of 0, 60
+and 90$^{\circ}$ respectively. This figure plots, for the disc
+systems, the TORUS tagged component fluxes from the star (solid lines)
+and the disc or thermal flux (dashed lines), for both direct flux
+(black) and scattered flux (red). As the inclination of the system
+increases, the stellar direct flux can be seen to decrease, and the
+thermal and scattered components increase. This is simply caused by
+occultation of the star by the disc. The condition of vertical
+hydrostatic equilibrium applied during the TORUS simulation results in
+the disc flaring (see Section \ref{derive_primary}). This flaring is
+more pronounced for BD when compared to higher mass stars meaning a
+higher fraction of the stellar flux is intercepted by the disc at
+earlier inclinations. \cite{2004MNRAS.351..607W} have previously
+modeled this effect for a range of disc masses and found that this
+alone can shift the SED, and therefore colours and magnitudes, of
+inclined BDD systems to those indicative of higher mass CTTS.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/disc_eg.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure of the SEDs of a BDD of $M=$0.04$M_{\odot}$, at 1 Myr,
+   with a disc mass of $M_{\rm disc}=$0.01$M_{\rm star}$. The BD is rotating
+   with a period of 0.5 days and is accreting through a stream, with
+   an areal coverage of 1\%, at a rate of -12
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{upper left
+     panel} shows the photospheric spectrum of the naked star (naked stars have
+   spherically symmetric flux distributions, therefore the SED is not
+   a function of inclination), the total flux is shown as a bold
+   line. The \textit{lower left, upper right and lower right panels}
+   show the SEDs of the BDD systems at inclinations of 0,
+   60 and 90$^{\circ}$. For the BDD SEDs, the solid lines
+   are stellar flux and dashed are the thermal disc flux, with the
+   black denoting direct flux and red for scattered flux, i.e. black
+   solid line is direct stellar flux.
+   \label{disc_eg}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/disc_eg_log.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As Figure \ref{disc_eg} but in log space.
+   \label{disc_eg_log}}
+\end{figure*}
+
+The resulting density structure of the highly flared disc, for the
+system used to construct Figure \ref{disc_eg}, is shown in Figure
+\ref{flare_eg}. Figure \ref{flare_eg} shows that for a typical BDD
+system the resulting disc is highly flared and therefore, the opening
+angle for stellar radiation is much smaller. As discussed the flaring
+for BDD systems was found to be larger than CTTS systems by
+\cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
+degree of disc flaring depends on the disc temperature structure and
+the mass of the central star, with the disc scaleheight $h\propto
+\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{1973A&A....24..337S}. Recently,
+\cite{2009arXiv0901.4445E} suggest the inverse relation of flaring
+with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
+evidence from \cite{2006ApJ...644..364A}, where SEDs for 17 systems in
+the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat
+disc models. In general, \cite{2006ApJ...644..364A} find that lower
+mass objects achieve better fits with the flat disc models and higher
+mass objects with the flared discs.
+
+The results of \cite{2006ApJ...644..364A} show that above a mass of
+50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
+discs. Whilst at masses below 50$M_{\rm Jup}$ only one object is better
+fit by the flared disc model, with the remaining objects (10/17)
+better fit with flat models. Whether, this result is statistically
+significant enough to assert a $h\propto M_*$ is doubtful as the
+fitting process contains, presumably two fixed scaleheight
+distributions. Therefore, for our study we continue to assume that our
+flared BDD systems will have larger characteristic scaleheights than
+typical CTTS systems.
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/28_rho.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{A Figure of the density for the most flared
+   disc. $M_*=$0.01$M_{\odot}$, $\tau=$5 days, $\dot{M}=$-6
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, areal coverage of 1\% at 1
+   Myr **RUN NUMBER028**.
+   \label{flare_eg}}
+   \end{figure}
+
+\subsubsection{Disc effects: Inner wall, $L_{\rm wall}$}
+\label{inner_wall}
+
+Therefore, as the scattering in optical CMDs is dominated by system
+inclination, due to disc flaring, what dominates scattering in the IR?
+Clearly, system inclination still has a significant correlation with
+the scatter CMD position. However, as shown in Section
+\ref{derive_primary} IR CMD scatter appears strongly correlated with
+rotational period. A similar correlation between scatter and rotation
+period is evident for IR and IRAC (and perhaps MIPS) CoCoDs (although
+the trend is reversed), as shown in Section \ref{derive_frac}. The
+cause of this scatter is the relative flux contribution of the inner
+disc boundary, as discussed in Section \ref{scatter_causes}. It is
+also clear in Section \ref{derive_primary} that the longer wavelength
+photometric colours are better disc discriminators. Furthermore,
+interestingly, the $\alpha$ value, in our case the slope of the SED
+between 3.6 and 8.0$\mu$m \citep[chosen to
+match][]{2009arXiv0901.4120D}, is a very effective disc disriminator.
+
+The position of a given BDD system, in an IR CoCoD or CMD, is
+dominated by rotation period, and it is clear that this is due to the
+radial position of the inner wall (See discussion in Section
+\ref{scatter_causes}. As the rotation period decreases the inner disc
+co-rotation radius decreases, meaning a closer, hotter, inner disc
+wall. However, we have also included a treatment of dust sublimation
+which, during the radiative transfer modeling, will change the radial
+position for the higher temperature inner walls \citep[where
+$T_{\rm wall}$ exceeds $\approx$1400K][]{1994ApJ...421..615P}.
+
+\subsubsection{Disc structure and the inner edge}
+\label{inner_edge_position}
+**SHOULD BE PRINTED FROM TORUS**pooooo
+\textbf{Initial inner wall radius}
+
+Given the strong dependence of IR flux on the inner wall temperature,
+and therefore radial position, it is important to examine the final
+structure of the inner wall after the radiative transfer simulation.
+
+Table \ref{inner_edge} list the initial inner edge radius (from the
+central star), set at the co-rotation radius, in stellar radii for each
+mass increment. It is clear that the inner edge position is a strong
+function of rotation period and a much weaker function of stellar
+mass. This is obvious from our calculation of the co-rotation radius
+for which we use equation \ref{inner_eq}. Equation \ref{inner_eq}
+clearly shows the weak dependence on stellar mass ($R_{\rm inner}\propto
+M_*$) and strong dependence on rotation period ($R_{\rm inner}\propto \tau
+^2$). Table \ref{inner_edge_au} shows the same data as Table
+\ref{inner_edge} but converted using the stellar radius into AU, which
+reveals a magnetic truncation radius of between 0.0026$-$0.026 AU for
+1 Myr BDD systems.
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|}
+Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
+\hline
+Period (days)&0.5&5&0.5&5\\
+\hline
+Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius ($R_*$)}\\
+0.01&2.18&10.16&3.52&16.36\\
+0.02&2.42&11.24&3.33&15.47\\
+0.04&1.90&8.86&3.26&15.15\\
+0.06&1.57&7.32&3.13&14.53\\
+0.08&1.37&6.39&2.96&13.74\\
+\end{tabular}
+\caption{Table showing the initial inner edge radius (in $R_*$) for all models.
+  \label{inner_edge}}
+\end{table}
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|}
+Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
+\hline
+Period (days)&0.5&5&0.5&5\\
+\hline
+Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius (AU)}\\
+0.01&0.00264&0.0123&0.00265&0.0123\\
+0.02&0.00333&0.0155&0.00375&0.0174\\
+0.04&0.00403&0.0188&0.00411&0.0191\\
+0.06&0.00479&0.0195&0.00395&0.0183\\
+0.08&0.00527&0.0246&0.00501&0.0233\\
+\end{tabular}
+\caption{Table showing the initial inner edge radius (in $R_*$) for all models.
+ \label{inner_edge_au}}
+\end{table}
+
+\textbf{Dust sublimation radius}
+
+During the simulations of radiative transfer, implementation of dust
+sublimation, may result in changes in inner radius. For systems where
+the temperature of dust at the inner disc boundary exceeds
+$\approx$1400K \citep{1994ApJ...421..615P}, the inner disc will be
+destroyed and the inner radius increased. Table \ref{inner_edge_dust}
+shows the resulting radii for our model grid in stellar radii with the
+corresponding values in AU presented in Table
+\ref{inner_edge_dust_au}.**THIS TABLE MUST BE CHANGED TO INCLUDE
+DIFFERENT FLUXES**
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|}
+Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
+\hline
+Period (days)&0.5&5&0.5&5\\
+\hline
+Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius ($R_*$)}\\
+0.01&&&&\\
+0.02&&&&\\
+0.04&&&&\\
+0.06&&&&\\
+0.08&&&&\\
+\end{tabular}
+\caption{Table showing the final inner edge radius (in $R_*$) for all models.
+ \label{inner_edge_dust}}
+\end{table}
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|}
+Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
+\hline
+Period (days)&0.5&5&0.5&5\\
+\hline
+Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius (AU)}\\
+0.01&&&&\\
+0.02&&&&\\
+0.04&&&&\\
+0.06&&&&\\
+0.08&&&&\\
+\end{tabular}
+\caption{Table showing the final inner edge radius (in $R_*$) for all models.
+ \label{inner_edge_dust_au}}
+\end{table}
+
+\textbf{Compare $R_{\rm co}$ to $R_{\rm dust}$}
+
+**NEEDS TO BE DONE AFTER NEW DATA**
+
+Comparing Table \ref{inner_edge_dust_au} to Table \ref{inner_edge_au}
+shows that the inner disc radius is changed little from the initial
+co-rotation radius (QUOTE MAX CHANGE**) due to dust sublimation
+effects. The resulting inner radii are still, broadly, proportional to
+the rotation period. Therefore, for subsequent analysis, we assume an
+inner radius to rotation period relationship.
+
+Our final inner radii range from ** to ** AU. **COMPARE TO
+OTHER RESULTS?**
+
+\textbf{Dust sublimation regions}
+
+**AGAIN NEEDS TO BE DONE AFTER NEW DATA**
+
+In some cases however the inner disc radius has been changed by the
+implementation of dust sublimation. For these systems the resulting
+shape of the inner disc boundary has also changed. Evidence that real
+inner disc boundaries (for CTTS) are not vertical walls comes from a
+lack of dependence of the derived IR excess on system inclination
+\citep{2007ApJ...661..374T}. As discussed in Section \ref{dust_edge}
+the disc inner hole can be created by several mechanisms, however, for
+this study we have only included a treatment of magnetic truncation
+(initially) and subsequent dust sublimation. The effects of dust
+sublimation have been shown to produce curved inner walls due to the
+temperature and density dependence of the dust sublimation temperature
+\citep{2005A&A...438..899I}. The curved boundary in this case is
+concave, as density increases towards the midplane of the disc, the
+dust sublimation temperature increases, meaning the destruction radius
+moves closer to the star. A curved inner boundary is also found to
+result from dust sublimation in \cite{2007ApJ...661..374T}. In
+\cite{2007ApJ...661..374T} two populations of dust grains where
+included with different scaleheight distributions. This is essentially
+a simple model of grain growth and subsequent midplane
+settling. \cite{2007ApJ...661..374T}, found a convex inner disc
+boundary, this is due to the larger grains cooling more
+efficiently. These larger grains dominate the dust towards smaller
+vertical distances from the midplane, and therefore the increased
+cooling means that the dust sublimation temperature is reached at
+closer radii.
+
+For our dust distribution and dust sublimation implementation we
+produce a curved inner boundary, as can be seen in
+Figure \ref{curve_inner}. This is due to the density dependent dust
+sublimation temperature (as discussed in Section \ref{dust_edge}).
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/238_tau.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{A Figure of the opacity (scaled $1<\tau <0$) for the most
+   extreme case of a dust sublimated inner
+   boundary. $M_*=$0.08$M_{\odot}$, $\tau=$0.5 days, $\dot{M}=$-6
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, areal coverage of 1\% at 1
+   Myr **RUN NUMBER238**.
+   \label{curve_inner}}
+\end{figure}
+
+**CONCLUDE**
+
+\subsubsection{Disc effects: Inner wall to Outer edge balance,
+  $L_{\rm wall}$ to $L_{\rm disc}$}
+\label{disc_period_relation}
+
+\textbf{Why do inner disc radius changes cause photometric scatter?}
+
+**ADD SOME IMAGES**
+**PERHAPS ADD A FIGURE HER J-K, AND IRAC COLOUR VERSUS FINAL RADIUS**
+
+Physically, as the inner disc radius changes the flux intercepted by
+the inner wall is changed. At first glance it may appear more
+instructive to plot the \textit{bottom left panel} as a function of
+inner disc radius, to strengthen the correlation and remove the
+scatter within the Figure. However, intrinsic scatter will also be
+included due to inclination and accretion rate, the latter perhaps
+being less intuitive. Even though accretion flux is generally blueward
+of these passbands, interception and subsequent reprocessing of this
+additional flux for higher accretion rates increase scatter in a
+CoCoDs of this sort. Therefore, plotting the simulated photometry as a
+function of inner disc radius does not reduce the
+scatter. Furthermore, separating the populations using the rotational
+period is perhaps more useful for observational studies as this is
+often the most ubiquitous and precise data available. It is important
+at this stage to re-iterate that magnetic truncation and dust
+sublimation as we have assumed occur, is not the only method of
+producing an inner hole, for instance planet formation or
+photoevaporation can create significant inner holes, which are not
+necessarily correlated, in size, with rotation period.
+
+\textbf{SED change caused by inner radius}
+
+Figures \ref{rot_effect}, \ref{rot_effect_log}, \ref{rot_comp} and
+\ref{rot_comp_-7} show the effects of the changes in inner boundary
+radius due to rotational period changes on a BD, $M_*=$0.04$M_{\odot}$,
+at 1 Myr. For all these figures the \textit{left panel} shows the SEDs
+for a period of 0.5 days and the \textit{right panel} shows the SED
+for a period of 5 days. We have chosen to plot the SEDs as a function
+of rotational period for two reason. Firstly, rotational period will
+be the most easily, and precisely, observed variable. Secondly, the
+inner disc radius varies most strongly as a function of the rotational
+period (see Equation \ref{inner_eq}).The final inner radii for the
+systems shown in the \textit{left} and \textit{right panels} are **
+and ** AU, respectively (see Table \ref{inner_edge_dust_au}).
+
+Figures \ref{rot_effect} and \ref{rot_effect_log} show the total flux
+(in normal and log space respectively) for both canonical accretion
+rates (-8 \& -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, bold and
+dashed lines respectively). The SEDs are for systems with the smallest
+areal coverage (1\%) and therefore highest accretion flux, for each of
+the three inclinations (0, 60 and 90$^{\circ}$, black, red and
+blue respectively).
+
+Figures \ref{rot_comp} and \ref{rot_comp_-7} show the component flux
+for two inclinations, $0$ and $60^{\circ}$, \textit{upper} and
+\textit{lower panels} respectively. The component flux is separated
+into total (black lines), stellar (blue lines) and thermal or disc
+(red lines) flux. The stellar and thermal flux is then separated into
+direct (bold lines) or scattered (dashed lines) flux. The vertical
+bold lines on these figures show the approximate filter ranges for the
+IRAC channels ([3.6], [4.5], [5.8] \& [8.0]), with the vertical dashed
+lines showing the limits of the JHK filters of the CIT system. Figure
+\ref{rot_comp} shows the SEDs for a system with an accretion rate of
+-8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and Figure
+\ref{rot_comp_-7} an accretion rate of -7
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
+
+Figures \ref{rot_effect} and \ref{rot_effect_log} show that for
+systems with a typical accretion rate and shorter rotational periods,
+as the inclination increases the flux and slope of the SED decreases
+dramatically, for wavelengths shorter than $\approx$2$\mu$m. In this
+case the inner boundary is close to the central star. Conversely, the
+flux, and slope of the SED, at wavelengths longer than
+$\approx$2$\mu$m decreases less swiftly with increasing inclination.
+Effectively shorter period systems show a large change in flux and
+flux ratios in the $<$2$\mu$m range and a more constant flux or flux
+ratio in the $>$2$\mu$m range. This trend is clearly reversed for
+longer period objects. The objects, where the disc inner edge is
+farther from the star, show a large change in flux and flux ratio, as
+a function of inclination, for wavelengths $>$2$\mu$m and a smaller
+change for wavelengths $<$2$\mu$m. In addition, the total SED is
+dominated by the photosphere at shorter wavelengths.
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/rot_effect.ps"
+   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+ \caption{Figure showing flux against wavelength for a
+   $M_*=$0.04$M_{\odot}$ BD at 1 Myr, for two accretion rates -7
+   (dashed line) and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (bold
+   line) for the three modeled inclinations, 0 (black), 60 (red) and
+   90$^{\circ}$ (blue). The \textit{left panel} shows the SEDs for the
+   shorter rotation period system, with a closer disc inner
+   boundary. The \textit{right panel} shows the longer period system
+   with farther disc inner boundary.**USE GRAPHPS**
+   \label{rot_effect}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/rot_effect_log.ps"
+   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+ \caption{A Figure \ref{rot_effect} but in log space.
+   \label{rot_effect_log}}
+\end{figure}
+
+The wavelength dependent variations in flux, and SED slope, with
+inclination are particularly important when considering photometric or
+broadband magnitudes and colours. Figures \ref{rot_comp} and
+\ref{rot_comp_-7} show that the variations evident in Figures
+\ref{rot_effect} and \ref{rot_effect_log} have serious implications
+over the filter responses of the CIT \textit{JHK} and IRAC
+systems. Essentially, Figures \ref{rot_comp} and \ref{rot_comp_-7}
+show that for increasing inclinations discs have a much more apparent
+effect on the SED over the IRAC range for longer period systems, and
+in the CIT \textit{JHK} range for shorter period systems. Thereby
+explaining the opposite correlations in disc scatter and rotation
+period, found for IR and IRAC colours in Section \ref{derive_frac}.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/rot_comp.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{This Figure shows flux against wavelength for a
+   $M_*=$0.04$M_{\odot}$ BD at 1 Myr, with a disc ($M_{\rm disc}=$0.01$M_*$)
+   and associated accretion rate of -8
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ over a hot spot coverage of
+   1\%. The \textit{left panels} show systems with a stellar rotation
+   period of 0.5 days and the \textit{right panel} those with a
+   stellar rotation period of 5 days. The \textit{upper panels} show
+   systems observed at an inclination of $0^{\circ}$ and the
+   \textit{lower panel} those observed at an inclination of
+   $60^{\circ}$. For \textit{all panels} the total SED is shown
+   (solid, black line), alongside the components flux from the star
+   (blue) and thermal or disc (red) flux. These components are also
+   separated into direct flux (solid lines) or scattered flux (dashed
+   lines) from the star or disc. The extents of the filter responses
+   for the IRAC (including channels [3.6], [4.5], [5.8] \&
+   [8.0]) (solid vertical line) and the CIT (\textit{JHK})
+   (dashed vertical lines) bands are shown. 
+   \label{rot_comp}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/rot_comp_log.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As Figure \ref{rot_comp} but in log space.
+   \label{rot_comp_log}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/rot_comp_-7.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As above but for higher canonical accretion rate -7
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
+   \label{rot_comp_-7}}
+\end{figure*}
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/rot_comp_-7_log.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{As Figure \ref{rot_comp_-7} but in log space.
+   \label{rot_comp_-7_log}}
+\end{figure*}
+
+**NEED TO GET VALUES ETC FOR THIS SECTION AFTER NEW DATA**
+
+As the temperature of the surface of the disc generally decrease
+towards larger radii the longer the wavelength of the flux the further
+from the central object its origin will be.  Effectively, more flux is
+being intercepted by the disc inner wall for the shorter period
+systems and consequently less flux is impinging on the outer flared
+surface of this disc, creating larger changes as a function of
+inclination for shorter wavelengths. In the case of the longer periods
+more flux is escaping to the outer flared edge of the disc and greater
+change is seen as a function of inclination angle at longer
+wavelengths. Figures \ref{far_rho}, \ref{far_rho_bw}, \ref{close_rho},
+and \ref{close_rho_bw}, show the density structure for the inner
+regions of the disc ($R<**AU$) as a function of radius and scaleheight
+(10$^{10}$ cms). The inner edge location can be seen to move further
+out when moving from short period systems to long period systems, in
+Figures \ref{far_rho}/\ref{far_rho_bw} and
+\ref{close_rho}/\ref{close_rho_bw}, from ** to **AU in fact. Dust
+sublimation effects have shifted the shorter period inner wall to a
+slightly larger radius (see Section \ref{inner_edge_position}), but
+this is ,however, still closer than longer period counterpart. The
+final temperature distribution in the disc inner regions ($R<**AU$)
+can be seen in Figures \ref{far_temp}, \ref{far_temp_bw},
+\ref{close_temp} and \ref{close_temp_bw}. As can be seen by comparing
+Figure \ref{far_temp}/\ref{far_temp_bw} to Figure
+\ref{close_temp}/\ref{close_temp_bw}, the inner wall reaches
+significantly higher temperatures for the shorter period systems. For
+the closer systems, the curved inner edge is due to some of the disc
+regions exceeding the dust sublimation temperature, the remaining wall
+reaches temperatures of **K. Whereas, for the longer period object the
+inner wall reaches a temperature of **K. This produces the correlation
+of IR excess caused by the inner wall with rotation period seen for IR
+CoCoDs in Section \ref{derive_frac}. In addition, comparing the
+temperature structure at a farther disc radius, indicative of fluxes
+within the IRAC passbands, one finds that the disc temperature is
+larger for the longer period systems, $**$ compared to $**$K at $**$
+AU. This causes the resulting correlation, where larger IRAC excesses
+are found for longer period BDD systems.
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/far_rho0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{CHANGE THESE AXES IN 10$^{10}$ cms*****
+   \label{far_rho}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/far_rho_bw0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{far_rho_bw}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/close_rho0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{close_rho}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/close_rho_bw0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{close_rho_bw}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/far_temp0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{far_temp}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/far_temp_bw0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{far_temp_bw}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/close_temp0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{close_temp}}
+\end{figure}
+
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/close_temp_bw0000.ps"
+   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
+ \caption{
+   \label{close_temp_bw}}
+\end{figure}
+
+\textbf{Short conclusion, alpha}
+
+As can be seen the effects of a circumstellar disc on the observed SED
+are most constant for longer wavelengths. Wavelengths generally longer
+than 3$\mu$m are little effected by inclination, accretion rate,
+stellar mass etc. This explains, result that BDD systems are well
+selected by IRAC photometry and the $\alpha$ value. Essentially, as
+the wavelength limits used to construct Figure \ref{alpha_zoom} are
+3.6 and 8.0$\mu$m, it follows that the separation between disc-less
+and BDD systems should be at least similar in clarity to the IRAC
+CoCoDs.
+
+\section{Conclusions}
+\label{conclusions}
+
+**THIS CLEARLY NEEDS REWRITING AFTER THE NEW DATA ARE ANALYSED**
+
+We have constructed a model grid of SEDs, and subsequently photometric
+magnitudes and colours, for actively accreting BDs with or without an
+associated accretion disc. We have modeled the photospheric flux from
+these BDs by adopting (and interpolating) the interior `DUSTY00'
+models of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
+atmospheric models of \cite{2000ApJ...542..464C}. We have then assumed
+that accretion occurs from an inner edge of a magnetically truncated
+accretion disc (truncated at the co-rotation radius). The accretion
+flux is calculated using a simple blackbody emission, given the
+derivation of a characteristic spot effective temperature. SEDs were
+then produced for both naked BDs and BDD systems. For the BDD systems
+we have modeled the disc using the TORUS radiative transfer code using
+the Lucy radiative transfer algorithm and incorporating dust
+sublimation and including including a treatment of vertical
+hydrostatic equilibrium (see Section \ref{model} for a discussion of
+the code). To produce a `grid' of simulated systems we have varied
+several input parameters namely: stellar mass, stellar age, stellar
+rotation rate, accretion rate, the areal coverage of the accretion
+stream and the system inclination (the disc mass was fixed). The
+ranges of these variables were selected to represent and bound typical
+pre-MS BD systems, justification is provided using evidence from
+observational studies in Section \ref{par_space} and a final list of
+the values of these variables can be found in Table
+\ref{par_space_table}.
+
+Accepting our assumptions, parameter ranges and radiative transfer
+code our resulting simulated dataset has allowed us to qualitatively
+explore the effects of \emph{active} (current not past accretion)
+accretion, and disc presence, on both the SEDs, and photometric
+colours and magnitudes of these systems. This analysis (described in
+Section \ref{results}) has important implications in two main areas.
+
+\textbf{Effect of accretion and disc on derived parameters:}
+
+Firstly, as disc presence and active accretion change the
+characteristics of BD stars, both in terms of its spectrum and
+photometric magnitudes, they also, subsequently, imply changes in any
+derived parameters from these primary quantities.
+
+\textit{Age.}
+
+As discussed in Section \ref{results}, the SEDs of BD systems with
+typical accretion rates and associated discs, are changed significantly
+from the assumed underlying photospheric model flux, and therefore
+become difficult to classify. We have shown that derivation of an
+\emph{isochronal} (or photometric) age from our simulated photometry
+of a coeval BD sample, with typical accretion rates and associated
+circumstellar discs, would be inaccurate and exceedingly difficult. As
+discussed in Section \ref{results} this does not include any effects
+due to past accretion on the evolution of the central star, which acts
+to accelerate the gravitational contraction and make the star appear
+older \citep{1999MNRAS.310..360T,1999A&A...342..480S}, further
+scattering the apparent age of a coeval population.
+
+\textit{Mass, therefore IMF.}
+
+Concordantly, \emph{isochronal} derivations of mass and therefore
+IMFs, for our simulated photometry, of a coeval population of
+accreting BDs with associated discs, would be inaccurate and
+problematic. Again caused by the changes in the SEDs as a result of
+the accretion flux and increased occultation by the larger degree of
+flaring seen in BD discs \citep[for the latter, as found
+by][]{2004MNRAS.351..607W}
+
+\textit{Disc fraction-Spitzer best.}
+
+We have also qualitatively explored the effects of accretion and disc
+presence in our simulated dataset on disc fraction estimates.As is
+currently well known, longer wavelength bandpasses are much more
+reliable and suitable for disc identification. As shown in Section
+\ref{results} the naked and BDD disc loci were much more clearly
+separated in the CoCoD constructed using \textit{Spitzer} IRAC
+magnitudes than the shorter wavelength CIT \textit{JHK} passbands. In
+addition, we that the slope of the SED from 3.6 to 8.0$\mu$m, or
+$\alpha$ value, is an effective disc indicator. We have also
+tentatively shown that current observational cuts, when applied to our
+simulated photometry (with its associated photometric system), results
+in the reliable detection of disc candidates, for IRAC colours and
+$\alpha$ values, and therefore a robust lower limit disc fraction.
+
+\textbf{Effect of accretion and disc presence on emergent theories or
+  secondary parameters.}
+
+Secondly, the results of our simulated dataset have implications for
+secondary derived correlations and physical theories, which utilise
+the primary parameters discussed. It is clear that changes in derived
+ages and masses of a BD sample, due to typical accretion and disc
+presence, has serious implications in a range areas. Inaccuracies in
+age derivations for pre-MS populations are well known, especially for
+the BD mass regime. However, the combined effects of accretion and
+disc presence on BD SEDs, and therefore age and mass derivation, have
+not been previously explored. Therefore, some of the uncovered biases
+and problems in this paper may bring new light to a few areas of BD
+evolution.
+
+\textbf{`Imperfect' disc locking perhaps due to biases.}
+
+\textit{Disc timescales: Rotation rates affect disc detection as function of
+  wavelength.}
+
+Firstly, we have found a wavelength dependant bias of naked to BD disc
+loci separation within CoCoDs. As we have shown in Section
+\ref{results}, for shorter wavelength data (\textit{JHK}), objects
+with a longer period lie closer to the naked BD locus, with shorter
+period objects further removed. This bias is reversed for IRAC data,
+where shorter period objects lie closer to the naked locus (although
+still well separated) and longer period objects farther away, in
+colour-colour space. Whilst, for the longer wavelength
+\textit{Spitzer} data the clearer separation between the naked and BDD
+disc loci means that this bias may well be minimised (especially in
+regions without significant variable extinction), for shorter
+wavelength data these populations (naked and BDD disc) overlap. As
+disc excess cuts are usually placed empirically based on perceived
+paucity's in stellar density, within colour-colour space, this overlap
+and associated bias for \textit{JHK} data could lead to a significant
+bias in any sample of BD stars with an inferred discs. This wavelength
+dependant bias is essentially due to the change in inner radius of the
+circumstellar disc, as the wavelength of emitted flux is dependant on
+temperature and therefore radial position within the disc plane. For
+shorter periods the disc is truncated closer to the central star and
+the disc inner boundary intercepts more flux at all inclinations
+leading to a hotter inner wall and less incident flux on the outer
+flared edges of the disc. This means that for \textit{JHK} bandpasses,
+which are sensitive to flux from the inner boundary, shorter period
+objects appear more different to naked objects than longer, and
+therefore cooler inner boundary systems.
+
+The effect of this bias has not previously been accounted for in disc
+fraction, and therefore disc timescale derivation studies. Our model
+does not include angular momentum loss only changes in the disc inner
+radius through a disc locking mechanism (and subsequent dust
+sublimation). If disc-locking to a central star is true and slower
+rotators are therefore more likely to have associated discs, any
+correlation between disc presence and rotation rates will be weakened
+for \textit{JHK} data and strengthened for \textit{Spitzer} IRAC data
+due to the biases we observe, for BDs. These biases may well aid
+understanding of early claims for a weaker or `imperfect' disc locking
+mechanism for lower mass stars. The use of \textit{JHK} magnitudes
+would lead to a less clear correlation between slow rotators and disc
+presence for a BD sample.
+
+These biases may also apply to higher mass objects, as would be
+expected albeit at a weaker level due to the less significant flaring
+seen in the circumstellar disc of TTS. This, in turn, may explain
+early difficulties in finding any correlation between rotation rate
+and disc presence \citep[amongst other issues such as non-coevality,
+see][for discussion]{2007prpl.conf..297H}. Once data at longer
+wavelengths was used this correlation was found
+\citep{2007ApJ...671..605C}, which may have been enhanced by the
+revealed bias. It is important to note however, that this bias is not
+strong enough (given the clear separation of our simulated naked and
+BDD disc systems in IRAC colour-colour space) to cast any
+doubt over this result.  Finally, as we have stated inner holes in
+circumstellar disc may well be created by other period-independent
+mechanisms such as clearing from gas accretion onto a planet or due to
+photoevaporation from UV flux, the latter of which would be increased
+at high accretion rates, which we have not included.
+
+\textbf{Accretion rate to mass relationship in doubt for BD regime.}
+
+\textit{Mass to accretion rate relationship-high accretors of low mass
+  missed-literature high mass low accretors missed.}
+
+The second area which this study impacts on, and perhaps most
+significantly, is the recent evidence for a stellar mass to accretion
+rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
+\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}.
+This relationship has been extended into the BD mass regime in
+\cite{2006A&A...452..245N}. However, arguments based on selection and
+detection thresholds have already cast this relation into doubt
+\citep{2006MNRAS.370L..10C}. As we have shown in Section \ref{results}
+a relationship of this kind is self-reinforcing as lower mass objects
+with higher accretion rates have little chance of being correctly
+identified as such due to both the accretion flux and flared
+associated disc. Essentially, at present it is unclear how many BD
+stars are not included in this relationship due to misidentification.
+As explained in \cite{2004MNRAS.351..607W}, BD systems with a disc,
+without including accretion effects, can have the characteristics of
+higher mass CTTS stars, due to increased disc flaring from a reduced
+surface gravity in the disc. The effects of accretion at typical or
+larger rates further exacerbate the situation both spectroscopically,
+as the photospheric flux essentially becomes swamped or completely
+veiled, and photometrically as the resulting colours and magnitudes
+are significantly shifted. Therefore, for our simulated dataset a
+relationship of this sort may well be derived, if typical methods are
+used to identify BD objects with discs and derive masses, ages and
+accretion rates, even though it is not present.
+
+\textbf{Link to deriving accretion rates-paper II}.
+
+This work has argued qualitatively, largely using positions within
+CMDs or CoCoDs, highlighting problems with the proposed stellar mass
+to accretion rate relationship. A further quantitative examination of
+methods used to derive accretion rates and their results when applied
+to our simulated dataset is certainly required, ***and this will be
+the subject of a future publication***, to confirm our conjectures.
+
+\textbf{SUMMARY}
+
+**WRITE AT THE VERY END**
+
+In summary, our simulated dataset shows that for typical parameter
+ranges for BD stars and BDD systems, disc presence and accretion flux
+lead to:
+
+Difficulty deriving the following stellar parameters for a coeval population:
+\begin{itemize}
+\item{Isochronal ages}
+\item{Isochronal masses}
+\item{IMFs}
+\end{itemize}
+
+And we have shown:
+\begin{itemize}
+\item{\textit{Spitzer} IRAC magnitudes are required for reliable disc
+    identification}
+\item{A correlation between naked to BDD disc system separation (in a
+    CoCoD, as a function of wavelength.}
+\item{Low mass, high accretion rate systems are likely to be
+    misidentified and therefore not included in any study relating
+    $M_*\propto\dot{M}$}
+\end{itemize}
+
+\section[]{ACKNOWLEDGMENTS}
+The computations reported here were performed using the
+University of Exeter Supercomputer.
+
+\bibliographystyle{mn2e}
+\bibliography{references}
+\appendix
+
+\section{Website}
 \label{website}
+
+**NEEDS LOTS OF WORK**
+
+As stated throughout this paper the data presented are available from
+a web page
+\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
+  disc}. In this Appendix we briefly discuss the data included, and
+the different ways of accessing or visualising these data on the
+website.
+
+\subsection{Available Data}
+\label{web_data}
+
+The magnitudes and colours presented in this paper are avaiable both
+as individual magnitudes and as isochrones or mass tracks. Photometric
+magnitudes have also been derived for several other systems and are
+available online.
+
+\textit{Full list of filters}
+
+These are Johnson, Cousins \textit{UBVRI(JHK)}
+\citep{1966ARA&A...4..193J,2005ARA&A..43..293B}, \textit{Tycho} $V_t$
+and $B_t$ \citep{2000PASP..112..961B}, Bessell \textit{UBVRIJHKL}
+\citep{1988PASP..100.1134B,1998A&A...333..231B}, SDSS \textit{UGRIZ}
+\citep{1996AJ....111.1748F}, 2MASS $JHK_s$
+\citep{2003AJ....126.1090C,2006AJ....131.1163S}, MKO \textit{JHK}
+\citep{2002PASP..114..169S,2002PASP..114..180T}, UKIRT \textit{ZYJHK}
+\citep{2001MNRAS.325..563H}, IRAS 12, 25, 60 and 100 $\mu$m
+\citep{1984ApJ...278L...1N} and SCUBA \textit{450WB} and
+\textit{850WB} \citep{1999MNRAS.303..659H}. For further information on
+these magnitudes, such as the filter responses used and the adopted
+zeropoints please refer to the website.
+
+\textit{Monochromatic fluxes}
+
+In addition to the magnitudes derived for each of these bands
+monochromatic fluxes have also been derived for all bands listed
+above. These have been derived following closely the methods of
+\cite{2006ApJS..167..256R}, extended to further passbands. For details
+of the assumed SED shape, central wavelengths and bandpasses adopted
+please refer to the website.
+
+**PERHAPS INCLUDE FORMULA FOR DERIVATION**
+
+\subsection{Navigation}
+\label{navigation}
+
+The main page contains links to download the entire dataset in several
+formats alonside files describing the format.
+
+\begin{enumerate}
+\item All SEDs ($\AA$ and ergs s$^{-1}$ cm$^{-2} \AA ^{-1}$) 
+\item All SEDs ($\mu$m and mJy)
+\item All Photometric Magnitudes for all BDD systems.
+\item All Photometric Magnitudes for all Naked systems.
+\item All Monochromatic Fluxes for all Naked systems ($\mu$m and ergs
+  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
+\item All Monochromatic Fluxes for all Naked systems ($\mu$m and mJy)
+\item All Monochromatic Fluxes for all BDD systems ($\mu$m and ergs
+  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
+\item All Monochromatic Fluxes for all BDD systems ($\mu$m and mJy)
+\end{enumerate}
+
+Also included is a link to the calibration information listing all the
+filtersponse sources, adopted zero points, central wavelengths,
+bandwidths and assumed SED shapes (for monochromatic flux
+derivation). A brief scientific overview is also available explaining,
+in general terms, the dataset and model.
+
+\subsection{Browsing Tools}
+\label{tools}
+
+For users who wish to investigate the dataset in a more specific or
+interactive fashion two browsing tools are included.
+
+The isochrones, mass tracks and individual stars magnitudes and
+colours generated and presented in the work can be queried using the
+``Isochrone and Mass Track Tool''. This allows the user to select the
+parameters of the model required and retrieve the specific data.
+
+Secondly, an iteractive tool is included allowing a user to select a
+given set of parameters and download the ``SEDs, monochromatic fluxes
+or magnitudes''. In addition this tool plots the SEDs for the Naked
+system or the three inclinations, in the case of BDD systems and
+allows users to select filters sets, whose monochromatic flux values
+will be overlaid on the displayed SEDs.
 

### 2010-04-19 BD_disc/temp.tex
New project
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2228 25464f21-6099-402c-b30a-640f1d40d38b

--- 2010-04-19 BD_disc/old_paper.tex
@@
 \end{keywords}
-
-\section{Introduction}
-\label{intro}
-
-\textbf{Motivation-why study discs around Brown dwarfs?}
-
-Theoretical study of Brown Dwarfs (BDs) and the subsequent development
-of testable hypotheses for observational studies is a critical, and
-somewhat uncertain, area within the field of star and planet
-formation. Several of the key physical parameters and mechanisms
-remain unclear within this mass regime
-\citep{2007ApJ...664.1154S}. Uncertainty remains over fundamental
-issues such as the initial formation mechanisms, the subsequent
-evolution and dominance of a star-disc interaction through to the
-possible dependence of planet formation mechanisms on stellar mass
-\citep[for a review of BD formation mechanisms see
-][]{2006astro.ph..2367W}.
-
-\textit{-Brown Dwarf formation mechanisms \& IMF.}
-
-Perhaps the two most fundamental challenges are formulating the
-formation mechanism of BDs and deriving the resulting
-initial-mass-function (IMF). Whether the BD IMF or formation
-mechanisms are different to their higher mass, solar-type, equivalents
-(T Tauri Stars, hereafter termed TTS) is an open question. Derivations
-of reliable IMFs depend, obviously, on robust derivations of stellar
-mass, and more subtly, on derivations of stellar ages (as IMFs are
-usually defined for assumed coeval populations). The study of
-classical T Tauri (CTTS) and disc systems of
-\cite{1997AJ....114..288M} found that given an expected range of
-parameters the scatter in infrared photometry matched the observed
-CTTS locus well. However the work of \cite{1997AJ....114..288M},
-discussed in more detail later, only included parameterised `flat'
-discs. Once disc flaring is considerd it is clear from previous work
-that misidentification of high mass stars with circumstellar discs is
-likely. \cite{2004ApJ...617.1177W} show that high-mass (HM) stars with
-circumstellar discs are likely to be mis-identified as younger Class I
-sources. This problem also exists at lower masses where the presence
-of circumstellar discs can dramatically shift the spectral energy
-distributions (SEDs) and therefore colours and magnitudes of BDs
-\citep{2004MNRAS.351..607W}. Therefore, deriving robust masses (and
-ages), and subsequently IMFs for BDs requires an understanding of
-these effects of disc presence.
-
-The presence, or fraction (for populations) of associated discs is
-itself also crucial in isolating the formation mechanisms of
-BDs. Precise determination of disc parameters for BDs and comparison
-with the TTS results may allow the differentiation of currently
-competing theories of the BD formation mechanism. Essentially, a
-mechanism similar to that seen in higher mass stars i.e. cloud
-collapse and fragmentation will result in a similar fraction of discs
-across the BD mass boundary, whereas a formation mechanism dominated
-by dynamical interactions \citep[ejections, accretion disc stripping
-from near collisions or tidal interactions etc.]{2003IAUS..211...27B}
-will result in a markedly different disc parameters, such as fractions
-of stars with discs or radial sizes of the discs themselves, across
-the BD mass boundary. Fundamentally a different disc fraction for BD
-stars to TTS would provide persuasive evidence of a different
-formation mechanism across the two mass regimes, as would an increase
-in the average radial size of discs, indicative of truncation for BD
-objects.
-
-Therefore, to progress our understanding of the fundamental issues of
-both the formation mechanism and emerging IMFs for BDs, consideration
-of the effects of an associated circumstellar disc and their
-subsequent ubiquity are essential.
-
-\textit{-Planet formation and disc dissipation timescales.}
-
-Another fundamental, and important, unresolved issue is the mechanism
-of planet formation. A critical, and currently ill defined constraint
-for the planet formation models is the timescale available for planet
-formation within the circumstellar disc. Current favoured formation
-mechanisms such as core accretion or gravitational instability are
-separated by these timescales. Disc fractions have again been used, in
-conjunction with stellar ages, to derive the disc dissipation
-timescale, which obviously constrains the planet formation
-timescale. Studies of TTS have derived a disc dissipation timescale of
-$\approx$ 5 Myrs \citep{2001ApJ...553L.153H}, with very few discs
-shown to survive out to $\approx$ 20 Myrs
-\citep{2004ApJ...612..496M}. However, the derivation of a disc
-dissipation timescale from disc fractions suffers from several
-intrinsic problems, for instance the inconsistent (and often
-contradictory) methods of deriving ages \citep[see][for a full
-discussion]{2008MNRAS.386..261M}. Notwithstanding this, disc fraction
-surveys have also been published for lower mass and BD systems, such
-as \cite{2004A&A...427..245S} and \cite{2004ApJ...609L..33M}, deriving
-a similar order-of-magnitude disc dissipation timescale. The
-probability of forming planets around BDs is clearly sensitive to any
-changes in disc dissipation timescale across the TTS to BD mass
-boundary.
-
-\textit{Mass dependent disc lifetimes.}
-
-Some studies of disc lifetimes find no significant difference between
-BD stars and their higher mass counterparts
-\citep{2003AJ....126.1515J}, however a possible correlation of disc
-lifetime with stellar mass is proposed in \cite{2007ApJ...660.1517S}.
-Additionally, \cite{2009arXiv0901.2603K} find that, for TTS older than
-3 Myrs, the disc dispersal time is mass dependent for intermediate
-mass (IM) to solar-type stars. This result only holds for the mass
-transition stated (IM to solar-type) and is based on stars with
-combined dust signatures, from infrared (IR) excesses and accretion
-indicators (using a EW[H$\alpha$], criterion).
-\cite{2009arXiv0901.4120D} also find, for TTS, a mass dependent
-general SED shape for disc candidates, with higher mass stars showing
-a featureless continuum at $\lambda>$8.0$\mu$m with lower mass stars
-generally showing strong silicate and PAH features at 10 and 2$\mu$m,
-indicative of mass dependent disc evolution. Whether in fact the disc
-lifetimes and therefore rate or type of involved physical processes
-are a function of stellar mass could provide another piece of evidence
-separating the previously assumed continuous (in mass) evolutionary
-principles of stars into a dichotomy separated by the hydrogen-burning
-mass limit, and alter the probability of forming planets in the BD
-regime.
-
-To test the hypothesis that disc dissipation timescales are
-independent of stellar mass one again requires accurate masses for BD
-with associated discs (hereafter, BDD) systems, alongside reliable
-disc fractions. The derivation of masses for BDD systems is
-complicated by disc presence, but additionally, the detection of disc
-presence at a given age is not simply a function of the disc
-dissipation timescale.
-
-\textit{-Accretion from an inner disc and clearing mechanisms.}
-
-Several mechanisms may act to completely dissipate a circumsteller
-disc. These include accretion from the disc ($\delta M_{\rm
-  disc}=\dot{M}$), photoevaporation or photoionisation due to flux
-from the central and neighbouring stars, and the formation of giant
-planets or interaction with binary partners. However, the entire disc
-does not have to be dissipated to be missed by disc fraction surveys.
-More subtly, disc fractions can be altered due to wavelength dependent
-detection. This is due to the peak flux of the thermal blackbody
-emission of the disc being proportional to the temperature,
-$\lambda^{\rm thermal}_{\rm peak}\propto T_{\rm disc}$, and the
-temperature in the disc being approximately a function of distance
-from the star. Thus for a given system, as one increases the
-wavelength of observation, the corresponding radial position of the
-effective source will increase. Moreover, as the disc flux must be
-separated from the photospheric flux the important quantity is the
-separation in wavelength between the emission peaks for the stellar
-and thermal disc components. Therefore the presence of an inner disc
-hole can change derived disc fractions, as a function of
-wavelength. Interestingly, \cite{2009arXiv0901.2603K} find that
-results for disc dissipation timescales based only on their accretion
-indicators or inferred disc presence do not agree, perhaps due to
-inclusion of transitional objects, where the inner disc is being
-cleared, and is therefore not detected at their target
-wavelength. \cite{2009arXiv0901.2603K} suggest that this is caused by
-photoevaporation of the inner disc, leading to a mass dependent disc
-lifetime, at their wavelength, for their sample. However, as discussed
-in \cite{2009arXiv0901.4120D}, the inner hole can be created via dust
-grain growth and midplane settling, giant planet formation or
-photoevaporation by ultraviolet (UV) and far-UV (FUV) flux
-\citep{2007MNRAS.378..369N}.  \cite{2009arXiv0901.4120D} argue that if
-binarity or giant planet formation or photoevaporation cause inner
-disc clearing the resulting system would not show active accretion
-from radii below the inner disc boundary. For the case of clearing by
-dust grain growth and settling accretion from a hot gas disc within
-the inner radius is still possible, and indeed evidence for such a hot
-gas inner disc has been found through SED fitting
-\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Additionally,
-\cite{2009arXiv0901.4445E} argue that for M stars, with a pure
-reprocessing disc where the inner disc radius ($R_{\rm inner}$) is
-equal to the dust sublimation radius ($R_{\rm dust}$, discussed in
-Section \ref{physics}), the stellar and thermal components are not
-separable at wavelengths shorter than 6$\mu$m. In the case of
-\cite{2009arXiv0901.4445E}, the inner disc hole was created by
-photoionising radiation from the central star destroying the dust
-component of the disc. Recent direct evidence for a photoevaporating
-disc has been found for the circumstellar disc around a low mass TTS
-in the Sigma Orionis cluster \citep{2009arXiv0902.0457R}. The
-detection was characterised by a tenuous photoevaporation wind and
-little or no accretion, and a disc detection at 24$\mu$m indicative of
-a large inner hole. Additionally, for BDs, \cite{2009arXiv0902.0638M}
-find that the disc mass and radius distributions in the Orion
-Trapezium cluster are consistent with photoevaporation over 1 Myr (the
-adopted age of the cluster), from UV and FUV flux generated by the
-massive $\theta^1$ Ori C.
-
-Whichever mechanism is responsible for clearing the inner disc hole it
-is clear that its presence leads to confusion in the validity of disc
-fractions at a given wavelength. The important quantity here is the
-separation in wavelength between the emission peaks for the stellar
-and thermal disc components, as it is these components which must be
-separated. For BDD systems it is likely that difficulties detecting
-the disc will be exacerbated by the lower temperatures of the
-photosphere and therefore the smaller separation in wavelength from
-the thermal disc emission component, compared to TTS
-systems. Therefore, to derive disc fractions for BD populations we
-require detailed comparison models with which to guide disc candidate
-selection. These models must necessarily include a treatment of
-accretion and dust destruction, given that these factors deplete the
-inner (and total) disc thereby affecting disc detection.
-
-\textit{-Accreting systems, relationship of stellar mass and accretion
-  rate.}
-
-Although the creation of the inner disc hole could have several
-causes, at least part of the effect is undoubtedly due to
-accretion. Accretion acts to directly deplete the inner disc (where
-the material is accreted from). Accretion also depletes the inner disc
-indirectly, as accretion generates hot continuum emission
-\citep{1998ASPC..154.1709G}, increasing the photoionising UV and FUV
-flux available \citep{1998ASPC..154.1709G}, and therefore affecting
-the derived disc fraction \citep{2009arXiv0901.3684H}. This effect may
-be amplified for BDD systems where the combined photospheric emission
-is dominated by accretion flux. However, accretion columns modeled by
-\cite{2004MNRAS.348..879A} were found to produce negligible levels of
-photoionising flux due in part to the high optical depth of the column
-itself to Lyman continuum photons. Additionally, due to the high
-concentrations of hydrogen in the accretion column and hotspot the
-emission is more likely to be characterised by a stellar atmosphere
-than a black body. However, for our work as emission from a stellar
-atmosphere or a black body of equal temperature are approximately
-equal for wavelengths longer than the Lyman edge we have neglected
-this effect. Whilst the accretion column and hotspot may not
-contribute to the photoinising flux within the system they will of
-course alter the disc evolution by an increase of the emitted
-flux. This increase in flux will lead to an increase in temperature of
-the disc inner and outer regions, and more particulary a change in the
-dust sublimation effects at the inner edge.
-
-The current proposed mechanism of accretion is a magnetically
-channelled accretion `column', where material from a truncated (at the
-co-rotation radius $R_{\rm co}$) inner disc boundary falls onto the
-surface of the star along magnetic field lines
-\citep{1990RvMA....3..234C,1991ApJ...370L..39K}. This mechanism is
-widely accepted, with strong evidence found from the excessive widths
-of H$\alpha$ ($>$10$\AA$) emission lines, over that caused by
-chromospheric activity and stellar rotation
-\citep{1998ASPC..154.1793W}, caused by the high velocities of
-infalling matter, ~100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.
-
-Accretion rates can be derived by modelling this magnetospheric
-accretion with a characteristic `column' temperature and assuming
-statistical equilibrium of the state populations. The resulting line
-ratios can then be fitted to the observed spectra. Accretion rates can
-also be calculated from model comparison of the Equivalent Width (EW)
-of the H$\alpha$ line itself, or perhaps more reliably, as they are
-less affected by extinction, that of the hydrogen recombination lines
-of Pa$\beta$ and Br$\gamma$. Accretion rates have been derived using
-these methods for many TTS and more recently for BDs
-\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
-with accretion rates in the range $\dot{M_{\rm
-    acc}}=$10$^{-6}$-10$^{-12} M_{\odot}yr^{-1}$, and typical
-accretion rates in the range log$(\frac{\dot{M}}{M_{\odot}}
-yr^{-1})=$-10 to -8 with only FU Orionis type objects accreting at
-rates higher than this. The mechanism producing accretion rates as
-high as those observed episodically in FU Orionis type objects is
-likely to be produced by some accretion mechanism instability, or
-perhaps by encounters with other cluster members \citep[see][for
-discussion]{2008arXiv0810.2854P}. Additionally, much lower accretion
-rates of $\dot{M}\approx$ 10$^{-13}M_{\odot}yr^{-1}$ have been derived
-for BDs using flux blueward of 4000$\AA$ where the photospheric flux
-becomes negligible \citep{2009arXiv0901.3684H}.
-
-Analysis of the derived accretion rate data has led several authors to
-propose a strong correlation between accretion rate and stellar mass
-\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
-of an approximate form: $\dot{M_{\rm acc}}\propto M_{*}^{~2}$. This
-correlation has no clear physical basis and it has been suggested that
-it could be caused solely by selection biases and detection thresholds
-\citep{2006MNRAS.370L..10C}. \cite{2006ApJ...648..484H} points out
-that Bondi-Hoyle accretion naturally results in a clear
-$\dot{M}\propto M^2_*$ relationship, but is not a desirable formalism
-to adopt as it completely ignores angular momentum of the accreting
-material. This proposed correlation could have important implications
-with regards to disc lifetimes and planet formation probabilities as a
-function of mass.
-
-As discussed, discs associated with BD systems lead to difficulties in
-accurate classification of the underlying BD
-\citep{2004MNRAS.351..607W}. Furthermore, accretion, both direct and
-indirect, can act to alter the disc signature, and clearly the
-photospheric signature. For cooler BD systems, where the stellar flux
-is generally redward of any accretion flux, increased accretion fluxes
-could dominate the resulting SED. Given that the derivation of a
-robust relationship of the form $\dot{M}\propto M^{\alpha}_*$ requires
-accurate mass and accretion derivations, then clearly the effects of
-circumstellar disc and increased accretion rates must be considered,
-before any such relationship can be accepted. As there is currently no
-clear theory linking accretion rate and mass (ignoring Bondi-Hoyle
-accretion), this relationship is driven by observations.  However, the
-observational constraints must be interpreted using a self-consistent
-set of accreting BDD and BD systems to better understand their
-implications. In other words, what do the observations really tell us?
-Is there a real relationship between mass and accretion rate or would
-simulated systems outside this relationship (and attributed scatter)
-not be detected or included in the current observational surveys, due
-to misclassification?
-
-\textit{-Disc locking and star disc interaction: rotation.}
-
-A further use of disc fractions, in conjunction with stellar ages, is
-to aid the understanding of the angular momentum evolution of star and
-disc systems. Recent evidence from TTS, from correlations of stars
-with IR excesses and slower rotational rates
-\citep{2007ApJ...671..605C} has seemed to strongly support a mechanism
-of disc-locking, where the central star is rotationally braked through
-magnetic locking to the accretion disc
-\citep{1993AJ....106..372E,1990RvMA....3..234C,1991ApJ...370L..39K}. A
-similar mechanism has been put forward, but has yet to be
-unambiguously confirmed, for BD stars. However, current studies have
-found a much weaker correlation between the slower rotators and those
-where a disc presence is inferred for BDs. Some authors have therefore
-proposed an `imperfect' disc-locking mechanism for stars in the lower
-mass regime ($M_*<0.4M_{\odot}$, inclusive of the BD mass regime,
-$M_*<0.08M_{\odot}$) \citep{2005A&A...430.1005L}. This weaker
-correlation could also be due to `imperfect' disc-locking or
-observational effects and mass dependence of the disc dissipation
-timescale \citep{2004A&A...419..249S,2005A&A...429.1007S}.
-
-If disc-locking is present for BDD systems, as for TTS stars, one
-would expect accretion of material from a magnetic truncation radius,
-$R_{\rm T}$ \citep{2007prpl.conf..479B}.  \cite{2007prpl.conf..479B}
-show that the magnetic truncation radius, $R_{\rm T}$, must be less
-than the co-rotation radius, $R_{\rm co}$ (where the Keplerian angular
-rotation rate of the disc is the same as the angular rotation rate of
-the star), as material outside this radius will have too much angular
-momentum to fall onto the star. This is implicitly adopted in the
-proposed accretion mechanism, where the disc is magnetically
-truncated, and therefore locked to the star. This magnetic truncation
-would lead to an inner wall (and inner hole) of the accretion
-disc. Evidence for an inner disc wall has been found from near-IR
-excesses from the inner rims of Herbig Ae stars, with emission peaking
-at 2-3$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
-position of this wall is affected by several factors, discussed
-further in Section \ref{physics}. The previous work of
-\cite{1997AJ....114..288M} explored the effects of simple mass
-accretion and the radius to the inner disc on the infrared colours of
-CTTS, useing a prescribed range of inner disc
-radii. \cite{1997AJ....114..288M} find that the scatter in infrared
-colours for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
-$\dot{M_{\rm acc}}=$10$^{-9}$to 10$^{-5} M_{\odot}yr^{-1}$, matches
-the scatter of the CTTS locus found in the data. The models of
-\cite{1997AJ....114..288M} used physically flat discs however meaning
-their results will not stand for discs with significant flaring. More
-importantly for our work \cite{1997AJ....114..288M} find a correlation
-of the infrared locus of models with the accretion and inner disc
-location. Essentially, changes in the stellar flux levels and position
-of the inner wall lead to temperature changes of this inner edge and
-therefore changes in the balance of flux across the infrared
-wavelength regime. As this study does not include the effectos of
-vertical hydrostatic equilibirum or even the study of flared discs one
-would expect, perhaps, a more complex relationship between the inner
-edge position and infrared excess in `real' systems. This means that
-studies aiming to provide evidence of disc locking by comparing disc
-indicators with rotation rates may include unforseen biases. As the
-rotation rate will effect the co-rotation radius and therefore
-truncate the disc at different radii, thereby enhancing or suppressing
-any relationship of infrared excess (or disc presence) with rotation
-rate.
-
-\textbf{Aims.}
-
-\textit{Key areas: Require, Mass, age and disc fractions}
-
-In summary, several key areas in the theoretical studies of BDs hinge
-critically on observational constraints, where the derived values are
-heavily affected by disc and/or accretion presence.  Formation
-mechanisms, IMFs, disc dissipation timescales, accretion rate--stellar
-mass relationships and studies of disc-locking mechanisms using
-correlations of rotation rates with infrared excesses, all require
-derivations of either masses, ages or disc fractions (or a
-combination), supplemented by other parameters.
-
-\textit{Previous complementary studies}
-
-The consequences of the disc structure for BD accretion discs,
-particularly vertical structure, given the assumption of vertical
-hydrostatic equilibrium, have already been discussed for a limited
-range of BD parameters in \cite{2004MNRAS.351..607W}. Indeed
-\cite{2004MNRAS.351..607W} have shown that BDD systems seen at higher
-inclinations can be confused with CTTS systems,
-having similar colours and magnitudes. Additionally, a benchmark model
-grid of spectra for star and disc systems in the mass range
-0.1$M_{\odot}<M_*<$50$M_{\odot}$ has previously been published in
-\cite{2006ApJS..167..256R}.
-
-\textit{What we are actually doing in the paper}
-
-In this work we explore the effects of accretion and disc presence on
-the derivation of the stellar parameters and explore the intrinsic
-biases, or relationships, which will effect or inhibit conclusions on
-mass to accretion rate or rotation to infrared excess correlations. We
-have extended the similar work of \cite{2004MNRAS.351..607W} by
-inclusion of a simple treatment of accretion and a sophisticated
-implementation of dust sublimation (amongst other improvements). The
-complete model grid, with derived photometry and isochrones, is
-available online through our browsing tool
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
-which is described in Appendix \ref{website}. The aim of this online
-database is to complement that of \cite{2006ApJS..167..256R}. Finally,
-a subsequent paper will introduce expansion to the model grid and an
-online fitting tool.**
-
-\textbf{Structure.}
-
-**REDO THIS AT THE VERY END**
-
-The structure of this paper is as follows. In Section \ref{model} we
-outline the model used, including an explanation of our physical
-assumptions (Section \ref{physics}), a brief description of the
-radiative transfer code (Section \ref{torus}), and an explanation of
-the derivation of emergent quantities such as photometric magnitudes
-(Section \ref{derived}). The ranges of the input variables are then
-explained and, where possible, justified using observational
-constraints in Section \ref{par_space}. Section \ref{results} contains
-the analysis and discussion of the main results of the model grid,
-first discussing the effects on the derivations of the primary
-parameters (Section \ref{derive_primary}), mass and age, and then the
-effects on disc fraction derivation (Section \ref{derive_frac}).
-Finally, conclusions are drawn, with a summary, in Section
-\ref{conclusions}.
-
-\section{Model}
-\label{model}
-
-In this Section we detail the physical model adopted and assumptions
-made (Section \ref{physics}), then explain key elements of the
-radiative transfer code (Section \ref{torus}). Then we discuss the
-derived values, such as broadband photometric magnitudes and colours
-(in Section \ref{derived}). Finally, we detail some internal
-consistency checks (Section \ref{checks}).
-
-\subsection{Physical model and assumptions}
-\label{physics}
-
-This section details some of the key physical assumptions made to
-generate our model grid.
-
-\subsubsection{Photospheric flux}
-\label{phot_flux}
-
-\textit{-Model \& interpolation.}
-
-In order to model an accreting BDD system we must first model the
-underlying photospheric flux. To provide a self-consistent set of
-model spectra we have adopted a BD stellar interior and atmospheric
-model grid. We have then constructed the total photospheric flux for
-any input value of stellar age and mass by interpolating for surface
-gravity (log(g)), effective temperature ($T_{\rm eff}$), radius
-($R_*/R_{\odot}$) and luminosity ($L_*/L_{\odot}$). These values were
-then used to interpolate atmospheric spectra for flux (ergs
-s$^{-1}$cm$^{-2} \AA^{-1}$) from 1200 to 2$\times$ 10$^7$ $\AA$ (or
-0.12 to 2000 $\mu$m). These spectra were then smoothed using 200
-logarithmically spaced points. Careful inspection ensured that no
-spectral features were removed during smoothing. The stellar interior
-models used for this study are the `DUSTY00' models of
-\cite{2000ApJ...542..464C} combined with the `AMES-Dusty', atmospheric
-models of \cite{2000ApJ...542..464C}, which are all available online
-\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
-approximate $T_{\rm eff}$ (effective temperature) range of $\approx
-$3000K$<T_{\rm eff}<$1600K the AMES-Dusty atmospheres are most
-applicable (2700K$>T_{\rm eff}>$1700K). We did try including dynamic
-application of atmospheres based on the derived $T_{\rm eff}$,
-i.e. using AMES-Cond for $T_{\rm eff}<$1700K, however this resulted in
-large discontinuities between the model atmospheres and resulting
-spectra. As this only affects stars at the very edge of our
-temperature range, i.e. for the oldest and lowest mass objects (for
-the AMES-Cond case), we have adopted the same model throughout.
-
-\subsubsection{Accretion flux}
-\label{acc_flux}
-
-\textit{-Blackbody flux given, Equation: Rinner, Coverage \& Rate.}
-
-Secondly, we require a model of the accretion flux for the system. The
-flux due to accretion was added onto the intrinsic photospheric flux
-using the simple approximation of blackbody emission. The selected
-accretion rate was used to derive an accretion luminosity ($L_{\rm acc}$),
-where the material was modelled as falling from the disc inner edge
-onto the surface of the star. $L_{\rm acc}$ is calculated acoording to
-\ref{Lacc}, 
-\begin{equation}
-{L_{\rm acc}=\frac{GM_*\dot{M}}{R_*}\times (1-\frac{R_*}{R_{\rm inner}})},
-\label{Lacc}
-\end{equation}
-where $M_*$ is the stellar mass, $\dot{M}$ the mass accretion rate,
-$R_*$ the stellar radius and $R_{\rm inner}$ the radius of the disc inner
-boundary.
-
-The initial inner disc radius was set to be the co-rotation radius
-(this is discussed in more detail in Section
-\ref{disc_parameters}). During the radiative transfer simulations of
-the disc the final inner dust disc radius may be extended past the
-co-rotation radius. This is due to dust sublimation effects (see
-Sections \ref{disc_parameters} and \ref{dust_edge} for
-explanation). However, as the gas within the disc is not sublimated it
-will always extend down to the co-rotation radius and we assume
-accretion will still occur from this radius. A full discussion of the
-differences between the initial and resulting final radii of the dust
-disc can be found in Section \ref{inner_edge_position}. Once the
-accretion luminosity was derived, an adopted areal coverage ($A$),
-over the stellar surface, was used to calculate an effective
-temperature ($T_{\rm acc}$), for the accretion `hot' spot, where
-\begin{equation}
-{T_{\rm acc}=\frac{L_{\rm acc}}{(4\pi R^2_{*} \sigma \times A)^{\frac{1}{4}}}}.
-\label{Tacc}
-\end{equation}
-
-Finally, a blackbody flux distribution is generated at $T_{\rm acc}$
-and added onto the intrinsic stellar photospheric flux. In general one
-would expect this to be an overestimate of the accretion flux, as for
-pre-MS BDs large convective zones are expected on the stellar surface,
-and some of the accretion energy may act to further drive these
-convective currents, meaning flux is lost. It is worth noting however
-that observationally UV excesses are often used to recreate and then
-subtract an assumed accretion flux using a blackbody flux curve.
-
-\subsubsection{Disc parameters}
-\label{disc_parameters}
-
-\textit{-Inner disc boundary, Co-rotation, i.e. magnetically
-  truncated: rotational period.}
-
-In this study we assume that accretion from the central star occurs
-along magnetically channelled columns from the inner disc boundary.
-For TTS stars, \cite{2007prpl.conf..479B} show that the magnetic
-truncation radius ($R_{\rm mag}$) is less than the co-rotation radius
-($R_{\rm co}$), where the angular Keplerian velocity of the
-disc is equal to the surface angular velocity of the central star.
-Calculations of the magnetic truncation radius depend on derivations
-of the surface magnetic field \citep{1991ApJ...370L..39K}. This is
-currently unavailable for BD stars, due to increased molecular species
-obscuring the Zeeman splitting signatures, that are normally used to
-derive stellar surface magnetic fields. Therefore, for our model grid
-we have adopted an initial inner disc radius as the co-rotation
-radius,
-\begin{equation}
-{R_{\rm inner}=({GM_*\tau^2\over{4\pi ^2}})^{1\over{3}}},
-\label{inner_eq}
-\end{equation}
- where $\tau$ is the stellar rotation period and $R_{\rm inner}$ is
-the inner radius. This is effectively adopting a disc-locking
-mechanism (without associated angular momentum loss), as for
-disc-locked stars, $R_{\rm mag}\approx R_{\rm co}$,
-\citep{1991ApJ...370L..39K,1994ApJ...429..781S}. Therefore, for our
-model simulations, this inner edge radius is dependent on, and derived
-from, the adopted value of the rotational period for the central star,
-as well as being weakly dependent on the stellar mass. As discussed in
-Section \ref{intro}, the inner disc can be cleared through a number of
-mechanisms, including binarity or Giant planet formation,
-photoevaporation or photoionisation of the disc and dust grain growth
-or settling. For BDD systems where a disc is modeled a treatment of
-dust sublimation due to photoionising UV and FUV flux is included
-(discussed in Section \ref{dust_edge}). However, the effects of
-binarity or Giant planet formation are neglected. Further to the
-stellar mass and period required prior to calculation of the inner
-disc radius, we require a disc mass (in stellar masses).
-
-\textit{-Disc outer edge.}
-
-For this work the disc outer edge was set at 300 AU, this was chosen
-as a maximum size of the circumstellar
-disc. \cite{2008A&A...486..877B} have shown that the disc outer radius
-has little effect on the resulting SED. However, in our subsequent
-paper we have included models for outer radii of 100 AU and plan to
-extend this parameter range further to smaller values of the outer
-radius in the future.
-
-\subsubsection{naked and disc systems}
-\label{naked_BDD}
-
-\textit{Naked and TORUS versions.}
-
-The combined (accretion plus photosphere) SED is then used as a
-boundary condition for the TORUS radiative transfer code and as a
-benchmark set of SEDs to model `naked' BD systems. The set of `naked'
-photospheres (plus accretion) are diluted by the factor
-$(R_*/Distance)^2$ to a distance of 10pc. The `negligibly' accreting,
-`naked' stars can be used to produce absolute magnitude (and intrinsic
-colour) isochrones for comparison. Whilst, the remainder are used to
-model systems showing active accretion where no disc is detected. For
-instance, \cite{2009arXiv0901.2603K} find 43 stars within their sample
-are actively accreting whilst no disc is detected (out of a total
-sample of 1253).
-
-In summary the key required input variables to setup the model grid
-are as follows. Stellar age and mass, which are used to derive the
-stellar flux. Further supplemented by an accretion rate, areal
-coverage and rotation period, used to generate the the accretion flux.
-The inner disc radius is then derived using the rotation rate, but a
-disc mass fraction must be adopted.
-
-\subsection{Radiative transfer code: TORUS}
-\label{torus}
-
-In this section we briefly explain the key elements of the radiative
-transfer code used to model the BDD systems.
-
-\textbf{TORUS.}
-
-\textit{Radiative transfer code.}
-
-We have used the TORUS radiative transfer code which is described in
-\cite{2000MNRAS.315..722H}, including the subsequent refinements i.e.
-addition of Adaptive-Mesh-Refinement (AMR) introduced in
-\cite{2004MNRAS.350..565H}. TORUS uses the criterion of
-\cite{1999A&A...344..282L} in a radiative equilibrium algorithm. The
-simulation also calculates \textit{vertical hydrostatic equilibrium}
-and dust sublimation for the disc, similar to that described in
-\cite{2007ApJ...661..374T}.
-
-\subsubsection{Dust Size distribution}
-\label{dust_size}
-
-\textit{-Size distribution.}
-
-We have adopted a similar treatment to \cite{2002ApJ...564..887W}.
-With the size distribution of dust particle given by,
-\begin{equation}
-\label{particle_dist}
-n(a)da=C_ia^{-q}\times exp^{[-(a/a_c)^p]}da
-\end{equation}.
-Where $n(a)da$ is the number of particles of size $a$ (within the
-increment $da$), $a_{\rm c}$ is the characteristic particle size, with $p$
-and $q$ simply used to control the shape of the distribution. $C_i$
-controls the relative abundance of each constituent species ($i$) in
-the dust. \cite{2002ApJ...564..887W} found that simulated SEDs fit
-observed SEDs better using this adjusted size distribution for the
-dust particles, as opposed to a simple power law. The best fitting
-values found in \cite{2002ApJ...564..887W} were $q=$3.0, $p=$0.6 with
-$a_{\rm c}=$50 $\mu$m, also with an associated maximum and minimum grain size
-of $a_{\rm min}=$5 nm and $a_{\rm max}=$1mm. Subsequent works have adopted a
-slightly steeper power law dependence, with $q=$3.5
-\citep{2008A&A...486..877B,2008ApJ...676L.143M,2008arXiv0810.2552P}.
-Therefore we have adopted the values of \cite{2002ApJ...564..887W}
-except for the parameter $q$ where we have used $q=$3.5.
-\cite{2002ApJ...564..887W} calculated the $C_i$ values for amorphous
-Carbon and silicon by requiring the dust to deplete a solar abundance
-of either component completely \citep[using abundances
-from][]{1989GeCoA..53..197A,1993ASPC...40..410N}. We have set $C_i=$1
-and adjusted the species using a grain fractional abundance \cite[an
-equivalent process to that of][]{2002ApJ...564..887W}, however we have
-adjusted these grain fractions using the updated solar abundances of
-\cite{2006CoAst.147...76A}. The resulting difference in opacity
-between grain fractions matching the work of
-\cite{2002ApJ...564..887W} and the new grain fractions is only a
-slight enhancement of the silicate feature (due to the relative
-abundance of Silicon increasing) which as little effect on the
-resulting SEDs. Figure \ref{albedo} shows the
-resulting albedo, and scattering and absorption opacities, for our
-dust population, with a the vertical dashed line showing 10$\mu$m.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/albedo.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figures of the albedo (\textit{top panel}), and scattering
-   (dashed line) and absorption (solid line) opacties (\textit{bottom
-     panel}) against log($\lambda$) (in $\mu$m) for our adopted dust
-   population. For \textit{both panels} the vertical dashed line is
-   plotted at 10$\mu$m to higlight the silicate features.
-   \label{albedo}}
-\end{figure}
-
-\subsubsection{Dust sublimation and the Inner Disc Edge}
-\label{dust_edge}
-
-\textit{-Dust sublimation}
-
-In addition, we have also applied dust sublimation during our
-simulations. This treatment is similar to that
-detailed in \cite{2007ApJ...661..374T}, but improved and generalised
-with respect to the applicable geometries.
-
-The practical implementation is as follows: An initial coarse
-approximate temperature structure is found for the grid without dust,
-only a fixed gas distribution. Then, first three full \textit{Lucy}
-algorithm iterations are run for a grid with a maximum cell opacity of
-0.1 (with dust added to this level). Three more iterations are then
-performed with dust opacity limited to $\tau=$1 per cell. A further
-three \textit{Lucy} algorithm iterations are then performed with the
-full dust opacity, where dust is added until the gas-to-dust ratio is
-achieved($\epsilon =$100). For each iteration (from the first to the
-ninth) dust in cells which reach the sublimation temperature and
-density is removed from the disc by setting the opacity to zero for
-the cell. Once these nine iterations are complete, the grid is refined
-around the disc photosphere, and the radiative transfer alogrithm is
-iterated through to convergence. After this first convergence, a
-vertical hydrostatic equilibrium algorithm is run, after which the
-disc grid is unrefined and then re-refined around the disc
-photosphere. This process continues for five hydrostatic equilibrium
-calculations. In this model the dust sublimation is effectively
-digital i.e. when the density and temperature for sublimation is
-reached for a given cell the dust is destroyed. We did attempt a more
-realistic model where the dust sublimation causes the dust to be
-destroyed at an evanescently decaying rate into the particular
-region. This was expected to lead to a more realistic situation where
-the dust destruction propogates into the disc material, and does not
-instantly destroy an entire region. However, this implementation lead
-to incremental sections of dust being removed after each iteration,
-resulting in little change in the overall density structure of the
-disc. This is perhaps interesting for real systems, in that the dust
-sublimation should not be expected to act as a digital `switch'.
-
-\textit{Analytic disc structures}
-
-We have also modeled the same grid without using vertical hydrostatic
-equilibrium and, instead, adopting analytic solutions for the
-structure of the disc. These models are included in our subsequent
-paper describing the fitting routine and will be analysed in more
-detail in a later work.
-
-\textit{-Inner disc location}
-
-As our models are magnetically truncated at the co-rotation radius, we
-have implicitly generated an inner hole. This also means that the disc
-will have an inner wall at this radius. Evidence for inner walls in
-circumstellar discs is apparent from the SEDs of disc systems, where a
-peak in emission is found between 2 and 3$\mu$m. The temperatures
-reached by such inner walls are expected to generate thermal flux
-contributions within this wavelength range
-\citep{2001ApJ...560..957D}. In fact the structure, radius and
-generation mechanism of the inner wall will lead to markedly different
-contributions to the SED. As discussed in Section \ref{intro} several
-mechanisms can act to clear the inner disc.
-
-Binarity and Giant planet formation would be expected to clear an
-inner disc and shut down accretion from within the inner wall due to
-gravitational perturbations. In addition, photoevaporation from UV and
-UV flux is expected to halt accretion from radii within the inner disc
-due to the removal of this material via a stellar/disc wind
-\citep{2006MNRAS.369..229A}. These two clearing mechanisms could be
-differentiate by the resulting masses of the discs
-\citep{2007MNRAS.378..369N}.  However, for our model systems we have
-neglected both of these effects.
-
-For our models we have initially cleared the inner disc by invoking a
-magnetic truncation radius, however, further disc clearing will be
-caused by the dust destruction/sublimation mechanism we have included.
-In some cases where the radius in the disc at which the dust
-sublimation temperature and densities are reached, ($R_{\rm sub}$)
-will be less than the co-rotation radius ($R_{\rm co}$). For these
-cases, $R_{\rm sub}<R_{\rm co}$, the inner wall radius and shape will
-be controlled by sublimation. Effectively meaning the final inner disc
-radius, after the radiative transfer simulation, will not equal the
-initial inner disc radius. The differences in the starting and
-resulting inner wall radii are discussed in Section
-\ref{inner_edge_position}. If the inner disc is cleared via dust
-sublimation one would expect a residual hot gas disc interior to the
-inner wall. This is as the gas component will not be destroyed and is
-free to extend to the co-rotation radius.  Evidence for a hot gas
-inner disc component has been found through SED fitting by
-\cite{2005ApJ...623..952E} and \cite{2008ApJ...689..513T}.  In
-particular, \cite{2008ApJ...689..513T}, found that emission apparent
-from within the inner wall radius could not be well fit by a modeled
-spherical halo, or optically thin disc, dust component.
-
-Furthermore, as the dust sublimation limit is temperature and density
-dependent \citep{1994ApJ...421..615P}, dust sublimation can lead to
-changes in shape of the inner wall. As the density of the
-circumstellar disc will vary with scale height one would expect the
-dust sublimation radius to vary concurrently with scale height. This
-results in a curved inner wall \citep{2001A&A...371..186N}. As
-explained by \cite{2007ApJ...661..374T}, the fact that near-IR
-excesses of disc systems do not appear strongly dependent on
-inclination indicates that the inner walls are not
-vertical. \cite{2007ApJ...661..374T} also showed that grain growth and
-midplane settling will lead to a curved inner wall (and a hot inner
-gas disc). The curvature is caused by changes in the vertical dust
-density distributions as a function of dust size, or midplane
-settling. Essentially, larger grains will sink more efficiently
-towards the midplane of the disc, and due to their larger surface
-areas cool more efficiently. Therefore, as the scaleheight increases
-the relative proportion of larger to smaller grains will reduce and
-the cooling become less efficient. This will result in higher
-temperatures being reached for larger scale heights at a fixed radius,
-thereby curving the inner wall as the upper layers of the disc reach
-the sublimation temperature at closer radii.
-\cite{2007ApJ...661..374T}, modeled this effect by using two dust
-distributions, a small and a large, with different vertical
-distributions indicative of increased midplane settling for the larger
-grains. For this study we have adopted a size distribution for one
-population of dust grains, with one characteristic vertical
-distribution. As such curvature of the inner wall in our simulations
-will be dominated simply by the dust sublimation temperature, and
-density. The resulting shapes and radial positions of the inner walls
-after the radiative transfer simulations are complete are discussed in
-detail in Section \ref{inner_edge_position}.
-
-\textit{-Gas treatment-opacity}
-
-For our model grid we have adopted a gas-to-dust ratio, $\epsilon$, of
-100, and the gas population is assumed essentially static with a zero
-optical depth. Therefore, it does not contribute to the resulting SED,
-and we have not included a hot inner gas disc as found by
-\cite{2008ApJ...689..513T}.
-
-\subsubsection{SEDs}
-\label{seds}
-
-\textit{SEDs, at 10pc and inclinations-flagging}
-
-Once the radiative transfer code was completed simulated SEDs were
-generated. These SEDs can be generated for any distance and for any
-system-observer inclination. For our models we have set the distance,
-again, to 10pc to create absolute flux SEDs and selected ten
-inclinations (0, 27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$). A
-further useful feature of the TORUS code is that the emitted photons
-which make up the SED are tagged on their way to the observer. These
-tags separate the photons into four groups. Firstly, photons are
-separated by source into thermal (disc) or stellar groups.  These
-groups are then subdivided into photons which reach the observer
-either directly or after scattering (for example see Figure
-\ref{disc_eg}).
-
-\subsection{Photometric systems and derived quantities}
-\label{derived}
-
-To allow us to investigate the effects of disc presence and accretion
-luminosity on the derivation of parameters for BD stars we can first
-study the produced SEDs. However, many observational studies use
-non-spectroscopic data to derive the pertinent parameters. Therefore,
-to examine the practical effects in the `observational plane' we have
-used the SEDs to produce broadband photometric magnitudes, and
-subsequently colours. Broadband magnitudes were also derived in a
-large range of other filter sets not used explicitly in the analysis
-within this paper. These magnitudes are available online
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
-and are briefly discussed in Appendix \ref{website}. In addition,
-monochromatic fluxes have been derived for all filters, and again are
-available online and discussed in Appendix \ref{website}. The
-additional magnitudes and monochromatic fluxes are also discussed in
-detail in the subsequent paper introducing the online fitting tool.**
-
-\textbf{Simulated Photometry.}
-
-To derive broadband photometric magnitudes and colours the SEDs of
-either the disc or naked systems were folded through the filter
-responses of the required photometric system. As the fluxes in all
-cases are absolute, derived for an observer to object distance of
-10pc, no conversion is required to derive absolute magnitudes and
-therefore intrinsic colours.
-
-\textit{-Ten inclinations: 0, 27, 39, 48, 56, 64, 71, 77, 84 and 90 $^{\circ}$.}
-
-For the naked systems the flux is spherically symmetric however,
-clearly, for the BDD systems different inclinations will result in
-very different SEDs and therefore magnitudes and colours. Therefore,
-for the BDD systems, photometric magnitudes and colours must be
-derived for each inclination selected.
-
-\textit{-Through filter passbands:near-infrared: CIT, Optical:
- Bessels, Mid-IR: Spitzer.}
-
-\textit{-Vega calibrated, except Spitzer-Zeropoints (IRAC handbook).}
-
-We have integrated using photon counting and calibrated using a Vega
-spectrum for magnitudes in the optical and near-IR regimes. The filter
-bandpasses selected are, the optical system of
-\cite{1998A&A...333..231B} for \textit{UBVRI} and the \textit{CIT}
-system of \cite{1982AJ.....87.1029E,2004PASP..116....9S} for
-\textit{JHK}, with the required shift of -0.015$\mu$m as prescribed by
-\cite{2004PASP..116....9S}.
-
-We have also derived magnitudes in the mid-IR range using the IRAC and
-MIPS systems of the \textit{Spitzer} space telescope. These magnitudes
-were derived using a conversion of flux to Data Number (DN) and
-calibrated using zero points derived from the zero magnitude fluxes
-published in the IRAC handbook
-\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}
-and the MIPS instrument calibration website
-\footnote{http://ssc.spitzer.caltech.edu/mips/calib/}.
-
-\textit{-near-IR=old disc excess \& masses, Optical=Ages \& Mid-IR=New
-  disc fractions.}
-
-These specific filter sets have been chosen due to their ubiquitous
-use and suitability for the derivation of the key stellar parameters
-of age, mass and, for populations, disc fractions. Therefore, by
-studying the changes of magnitudes (and colours) in these photometric
-systems we can test the predicted effects on these derived parameters
-caused by changes in the input parameters of our model grid. The
-optical magnitudes \textit{VI} are used to explore age related effects
-of varying the parameter space. Flux in the \textit{VI} bands is only
-minimally affected by accretion flux \citep{1998ASPC..154.1709G} and
-disc thermal flux \citep{1998apsf.book.....H} and, additionally, in a
-\textit{V, V-I} CMD, the reddening vector lies parallel to the pre-MS,
-minimising any age effect of extinction uncertainty, \citep[for a full
-discussion see][]{2008MNRAS.386..261M,2007MNRAS.375.1220M}. The
-near-IR passbands of \textit{JHK} are most often used to derive
-stellar masses as for pre-MS objects the reddening vector, in for
-instance, a \textit{J, J-K} CMD, is almost perpendicular to the
-isochrones, minimising the mass effect of extinction uncertainties
-\citep[the \textit{CIT} systems was chosen to
-match][]{2000ApJ...542..464C}. Finally, as is now well documented the
-\textit{Spitzer} IRAC passbands provide the best data with which to
-unambiguously separate naked and star-disc systems
-\citep{2005ApJ...620L..51L}. In addition, at longer wavelengths, the
-MIPS instrument provides sensitivity to disc systems at much larger
-radii (or debris discs).
-
-\subsection{Consistency checks and problems}
-\label{checks}
-
-\textbf{Consistency checks and problems.}
-
-Once the model grid was completed several checks were performed to
-verify the consistency of our results. For each individual model these
-checks were passed to our satisfaction before publication. Some
-problems remain, and these are explained in this section.
-
-\textit{-Compare photospheric flux to stellar direct for face-on.}
-
-Firstly, a check was made on the photospheric input flux and the
-resulting stellar direct flux (tagged by TORUS) after the radiative
-transfer simulation. The resulting flux distributions should match
-most closely for face-on configurations, and then match in shape only,
-with the stellar direct flux level dropping towards higher
-inclinations, as more photons are scattered and absorbed by the disc.
-
-\textit{-Naked BD colours, to DUSTY published, no match-UPDATED
-  spectra.}
-
-We also directly compared the magnitudes and colours of our naked BD
-systems with the lowest accretion rate (-12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ to those published in
-\cite{2000ApJ...542..464C}, in the same photometric system
-(\textit{CIT}). We found significant colour differences ($\delta
-(J-K)\le$ 0.1), between our derived values and those of
-\cite{2000ApJ...542..464C}. As a further check we derived the
-magnitudes in the \cite{1998A&A...333..231B} system (by both adopting
-the published zero points, and by using a Vega reference spectrum),
-and applied conversions of \cite{1992ApJS...82..351L}\footnote{We have
-  also included the wavelength shift mention in
-  \cite{2004PASP..116....9S}}, to the \textit{CIT} system. For each
-method we failed to match the magnitudes and colours published in
-\cite{2000ApJ...542..464C}. As a final test we passed the downloaded,
-unaltered, atmospheric spectra directly through the filter response
-program, without interpolation, for the closest matches in log(g) and
-$T_{\rm eff}$ from the interior models published in
-\cite{2000ApJ...542..464C}. These magnitudes and colours also failed
-to match. Therefore, we must conclude that the most likely cause of
-the mismatch is due to improvements in the model atmospheres available
-online \footnote{http://perso.ens-lyon.fr/france.allard/} (this is
-likely as the models available online, have a later time stamp,
-$\approx$ 2005 compared to 2000). For the final published magnitudes,
-for the naked systems, we have used a similar wavelength resolution as
-in our BDD systems, i.e. 200 logarithmically spaced points. This means
-that magnitudes derived from these spectra will differ slightly from
-those derived from the full spectra, but this effect is negligible,
-and increased resolutionfor only some of our model grid (i.e naked
-stars) will hamper comparison between the models.
-
-\textit{-Naked colours, compare to face-on colours (similar).}
-
-The final test of the derived colours and magnitudes was a comparison
-of the naked systems with the results for the almost face-on BDD
-systems. The results for the optical passbands should be similar and
-an appraisal of the component SED, i.e. showing the stellar direct
-flux, as can be seen in Figure \ref{disc_eg}.
-
-\textit{-Optical K band ZP different to Bessels.}
-
-We have adopted zeropoints derived using a Vega reference spectrum for
-the optical and near-IR passbands. As a test we have compared our
-derived zeropoints using the filter response of
-\cite{1998A&A...333..231B} and the Vega reference spectrum against
-those published in \cite{1998A&A...333..231B}. For our photometric
-systems we integrate the summed number of photons counted by the
-simulated telescope systems, however to test the zeropoints and match
-the system of \cite{1998A&A...333..231B} we must integrate the summed
-energy. The zeropoints we derived \citep[with the values of][in
-parenthesis]{1998A&A...333..231B} were: $U=$20.977(20.94),
-$B=$20.499(20.498), $V=$21.116(21.10), $R=$21.676(21.655),
-$I=$22.376(22.371), $J=$23.735(23.755), $H=$24.989(24.860),
-$K=$25.884(26.006) and $L=$27.809(27.875). Our derived zeropoints and
-those of \cite{1998A&A...333..231B} match to within 0.05 mags (and
-usually much closer) for all bands except the \textit{H,K} and
-\textit{L} bands. This is probably due to the previously noted IR
-excess (although detected at longer wavelengths) of the observed Vega
-spectrum. \cite{1998A&A...333..231B} use a combined model spectrum of
-Vega and Sirius as their reference spectrum. As a further test we also
-used the synthetic A0V stellar spectrum of \cite{1993ASPC...41...55C}
-to derive zeropoints but were still unable to improve the match to the
-\cite{1998A&A...333..231B} photometric system for the \textit{JHK}
-colours. However, for these colours we have adopted the \textit{CIT}
-system, but were unable to find published zeropoints, and therefore
-used the Vega reference spectrum. Essentially this may mean there is a
-small offset in our \textit{JHK} photometry, however as most of our
-results are based on differential photometry this will not affect our
-conclusions.
-
-\textit{-Several IRAC ZPs available.}
-
-A further complication with our adopted photometric systems is the
-range of zeropoints available for the \textit{Spitzer} IRAC
-photometry. For this study, as stated, we have adopted zeropoints
-calculated using the zero magnitude flux from the IRAC handbook
-\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}.
-The resulting zeropoints were: Channel 1[3.6]=19.541, channel
-2[4.5]=19.089, channel 3[5.8]=17.395 and channel 4[8.0]=17.966. The
-corresponding zeropoints derived for the MIPS passbands where: channel
-1[24]=2.139, channel 2[70]=-0.2726 and channel 3[160]=-1.990.
-
-\textit{-Conclusions on checks:OK as differential phot for most part.}
-
-In summary, several careful consistency checks were performed to
-confirm that the resulting SEDs and photometric magnitudes behaved as
-expected and matched any available published results. A failure to
-match the published zeropoints in the near-IR bands of the
-\cite{1998A&A...333..231B} using a Vega reference spectrum was
-probably due to an IR excess in our observed Vega spectrum. However as
-in general most of the conclusions or implications of this study are
-based on differential photometry, this should not affect them
-adversely.  Furthermore, a failure to match the published magnitudes
-(and colours) for the atmospheric models in
-\cite{2000ApJ...542..464C}, even using published zeropoints for the
-excellently defined system of \cite{1998A&A...333..231B}, and
-subsequent conversions to the required \textit{CIT} system
-\citep{1992ApJS...82..351L}, was prescribed to an update in the model
-atmospheres available online.
-
-\section{Parameter space}
-\label{par_space}
-
-This section details the range of each of the input parameters we have
-varied and, where possible, gives justification for the selected
-ranges from published observations. The simulations in this paper
-cover variations in the stellar mass, stellar age, stellar rotation
-rate, accretion rate, the areal coverage of the accretion stream, disc
-mass fraction and the system inclination. In a subsequent paper we
-introduce variation of the outer radius and using an analytical
-vertical disc structure as oppose to vertical hydrostatic equilibrium.
-.A summary of the values adopted for each input variable is shown in
-Table \ref{par_space_table}.
-
-\subsection{Mass} 
-\label{par_mass}
-
-Representative masses within the BD regime were chosen as follows:
-0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 $M_{\odot}$.
-
-\subsection{Age}
-\label{par_age}
-
-Typical disc lifetimes for solar type stars are of order $\approx$ 10
-Myrs \citep{2001ApJ...553L.153H}. Therefore, we have adopted input
-ages of 1 and 10 Myrs for our model grid, to span the approximate
-range of ages over which discs influence will be important.
-
-\subsection{Rotation rate}
-\label{par_rotation}
-
-Data for rotation rates, from periodic variability surveys, are widely
-available for a range of different age clusters of TTS. However, fewer
-studies exist on the rotation rates of BD mass objects. To select a
-feasible range of periods for our model grid we have collated the
-results from some recent studies of BD variability. Rotation period
-data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
-where periods are found over the range 5.78$-$74.4 hours ($\approx$
-0.24$-$3.1 days) for BD mass objects. In some cases the periodic
-variability is irregular and assumed to come from active accretion hot
-spots on the BD surface \citep[see][for discussion of variability
-causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
-and evidence of accretion are also found to correlate with slower
-rotating TTS, which the authors construe as evidence for a disc
-locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
-period$ relationship extending into the BD mass regime, this faster
-rotation in younger mass objects is taken as evidence for a decreasing
-effectiveness of the angular momentum removal of the disc locking
-mechanism, i.e. imperfect disc locking. In addition,
-\cite{2004A&A...419..249S} argue that when compared with data from
-younger clusters disc lifetimes can be seen to decrease with central
-object mass.
-
-\cite{2005A&A...429.1007S} study rotation period data for stars in the
-vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
-\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
-\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
-variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
-for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
-some BD objects with irregular variability indicative of accretion hot
-spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
-the mass-period relationship of these data in comparison with data
-from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
-\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
-Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
-Ori sample has an age of around 2$-$3 Myrs or there is still
-significant disc locking (concluded using the slope of the mass-period
-relation). More specifically for the BD mass regime, they find
-\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
-lower period limit of 2$-$4 hours, therefore at any age a fraction of
-BD stars rotate at short and constant period. Given that these objects
-should spin up as they hydrostatically contract they invoke rotational
-braking in the BD mass regime as a mechanism of removing significant
-angular momentum.
-
-\cite{2003ApJ...594..971J} study the rotational periods of BD (and
-very low mass stars) in the Chameleon I region. This region is $\le$ 1
-Myrs old, and the authors find rotation periods of 2.19, 3.376 and
-3.21 days for their BD mass counterparts. Using supplementary data
-from the literature \cite{2003ApJ...594..971J} propose that a shorter
-lifetime of $\approx$5 Myrs for accretions discs around BDs is more
-probable and is inferred from the derivation of a shorter locking
-timescale. However, as discussed in the previous studies, an imperfect
-disc locking mechanisms is also hypothesised as responsible for the
-less significant loss in angular momentum out to ages of 10 Myrs. The
-data mentioned above and other datasets are summarised and discussed
-in \cite{2007prpl.conf..297H}, where a strong argument for the
-mass-period relationship can be found, shown in their Fig 6, alongside
-further support for either a shorter disc lifetime or imperfect disc
-locking mechanism for BD stars.
-
-Therefore, in summary, it is currently unclear if any disc locking
-mechanisms efficiency or disc lifetimes are a function of mass, with
-an associated phase change over the TTS to BD mass limit. Rotation
-rate and disc presence data are being used to explore issue.
-Therefore, to create a set of useful models to help contextualise the
-observational constraints we must adopt a realistic, and bounding,
-range of rotation rates. For our model grid, and associated age range
-($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
-placed at around the approximate median for the faster rotating
-samples, providing a useful benchmark for exploring possible detection
-limits of faster rotators with discs. The longer period is set at the
-approximate edge of the slow rotating tail, providing a limiting case
-for the slower rotating, disc-locked, candidates.
-
-\subsection{Areal Coverage}
-\label{par_cov}
-
-As discussed in Section \ref{par_rotation} evidence for irregular
-periodic variability has been found in BD stars with detections of
-associated stellar discs. This is construed as evidence for accretion
-hot spots formed as magnetically channeled material hits the stellar
-surface \citep[see discussion
-in][]{1995A&A...299...89B,2007prpl.conf..297H}. The irregularity is
-thought to be caused by changes in the magnetospheric structure and
-accretion rate \citep{1995A&A...299...89B}. For our model we have
-assumed that disc material is disrupted at the co-rotation radius and
-channeled onto the star in the form of accretion hot spots with a
-characteristic temperature. Therefore, to calculate the characteristic
-temperature and the resulting blackbody accretion flux we must adopt
-an accretion rate and areal coverage of the accretion stream.
-
-Little observational evidence can be found for approximate sizes of
-accretion hot spots due to their more transient nature and often
-smaller coverages, when compared to cooler or `plage' spots
-\citep{2007prpl.conf..297H}. \cite{1995A&A...299...89B} modeled the
-size of the cool spots on solar-type stars for a selection of
-periodically variable candidates. They found projections of cooler
-spots, onto the stellar disc, of a few to ~60\%.
-\cite{1995A&A...299...89B} also found projected sizes, onto the
-stellar disc, of typically a few \% to around 10\% for hot spots.
-\cite{1996AJ....112.2159B} used observations of YY Orionis monitoring
-flux amplitude variations as a function of wavelength to derive a
-probable hot spot area of around 10\%. The spot temperature was also
-modeled for YY Orionis in \cite{1996AJ....112.2159B}, resulting in a
-best fitting areal coverage of 11\%. Therefore, to bound the probable
-areal coverage range of the accretion hot spots we have adopted areal
-coverages of 1 and 10\%.
-
-\subsection{Accretion Rate}
-\label{par_accn}
-
-Accretion rates derived for pre-MS stars are of order -6 to -11
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$ \citep{2006A&A...452..245N}.
-With the largest accretion rates found in so-called FU Orionis type
-objects (after the object where they were first observed). For the
-more typical accretion rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9}
-M_{\odot}yr^{-1}$, for TTS,][]{2009arXiv0901.4120D}, several studies
-have now suggested that the accretion rate is strongly correlated with
-the mass of the central star. This relationship was perhaps first
-suggested by \cite{2003ApJ...592..266M} using various accretion
-diagnostics. Later, \citep{2005ApJ...625..906M} derived a relationship
-of approximately $\dot{M}\propto M_*^{~2}$. Further evidence was put
-forward by \cite{2004A&A...424..603N}, where accretion rates as low as
-5$\times$ 10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More
-recently, even lower accretion rates of $\approx$10$^{-13}M_{\odot}
-yr^{-1}$, have been derived for BDs by \cite{2009arXiv0901.3684H}.
-Further support for a dependence of accretion rate on stellar mass was
-apparent in the significantly more homogeneous dataset of
-\cite{2006A&A...452..245N}. \cite{2006A&A...452..245N} analysed a set
-of accretion rates and masses derived for pre-MS stars in $\rho$
-Ophiuchi and compared these results to stars in Taurus. They found
-that the accretion rate scales with central object mass, into the BD
-regime. However, work by \cite{2006MNRAS.370L..10C} suggests that much
-of this result is likely to be caused by biases and sensitivity
-limits.
-
-For any $\dot{M}\propto M_*$ relationship to be ratified, clearly, the
-associated mass derivations must be shown to be accurate. For the BD
-mass regime it has been demonstrated that classification, either
-spectroscopic or photometric, and therefore accurate mass derivation
-is exceedingly difficult for BDD systems
-\citep{2004MNRAS.351..607W}. The inclusion of significant levels of
-accretion flux will act to exacerbate this problem. Essentially, as BD
-mass objects have relatively cool photospheres, compared to the
-temperature of the accretion hotspots, meaning that for lower
-accretion rates, than for their CTTS counterparsts, the accretion flux
-dominates the small wavelength regime of the SED.
-
-Therefore, to strengthen, or reject, any stellar mass to accretion
-rate relationship, the limits of observational classification (and
-mass derivation) of accreting BDD systems must be understood. To
-provide a benchmark model grid of such systems, with which to aid
-interpretation of the observational data, we must select a range of
-accretion rates including and exceeding those detected for systems
-previously classified as BDs.
-
-As the relationship $\dot{M}\propto M_*^{~2}$ predicts lower accretion
-rates for BD mass objects it is essential that we model systems at
-higher accretion rates, which may have been missed in current
-observational studies. Therefore, we have adopted accretion rates of
--6, -7, -8, -9, -10, -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$.
-
-\subsection{Disc Mass}
-\label{par_mdisc}
-
-A further required input parameter is the mass of the circumstellar
-disc. Previously studies modeling BD discs have adopted a range of
-disc mass fractions, for instance \citep{2004MNRAS.351..607W} use 0.1,
-0.01 and 0.001$M_*$. \cite{2002ApJ...564..887W} fit observed spectra
-with modeled SEDs to derive a disc mass of 0.003$M_*$, for HH 30
-IRS. Subsequent derivations of disc masses have converged to within an
-order of magnitude, with the following specific results: 0.03$M_*$
-\citep[$\rho$ Ophiuchi,][]{2002A&A...393..597N}, 0.055$M_*$ \citep[GM
-Aurigae,][]{2003MNRAS.342...79R}, 0.03$M_*$ \citep[GY 5, GY 11, and GY
-310,][]{2004ApJ...609L..33M} and 0.022$M_*$\citep[2MASS
-J04442713+2512164,][]{2008A&A...486..877B}. As the derived disc masses
-all have a similar order of magnitude we have adopted $M_{\rm
-  disc}\approx $0.01$M_*$. As changes in disc masses are expected to
-change the resulting SED less than perhaps, accretion rate for
-example, we have not varied the disc mass for this study. The results
-of simulations varying this parameter will be published in a future
-paper.
-
-\subsection{Inclination}
-\label{par_inc}
-
-Discs around BD stars exhibit increased flaring, due to the reduced
-surface gravity in the disc \citep{2004MNRAS.351..607W}. This
-increased flaring, and therefore larger scaleheight of the disc
-results in a smaller opening angle, when compared to higher mass stars
-and their circumstellar discs. As has been shown in
-\cite{2004MNRAS.351..607W} effects caused by variations in the system
-inclination angle are much more significant for BDD systems, again
-compared to their higher mass analogues. Therefore, we have simulated
-ten observer to system inclination angles spaced evenly in
-$cos(inclination)$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
-and 90$^{\circ}$.
-
-A final list of all varied parameters and their values can be seen
-in Table \ref{par_space_table}.
-
-\begin{table*}
-\begin{tabular}{|l|l|}
-Input parameter&Values (\# values)\\
-\hline
-Mass ($M_{\odot}$)&0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 (8)\\
-Age (Myr)&1 \& 10 (2)\\
-Rotation period (days)&0.5 \& 5 (2)\\
-Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
-Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&-6, -7, -8, -9, -10,
--11 \& -12 (7)\\
-Disc mass ($M_*$)&0.01 (1)\\
-Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
-(10)\\
-\end{tabular}
-\caption{List of all varied input parameters. Resulting in a total
-  number of models of 448 (plus 40 models without radiative transfer
-  simulations for the naked BDs) and 4480 SEDs (plus 40 for naked
-  BDs). \label{par_space_table}}
-\end{table*}
 
@@
 \label{scatter_causes}
-
+USE THIS BIT FOR THE SEDS SECTION
 **ADD IN TEMPERATURE RANGES FOR DISCUSSION HERE**

### 2010-04-19 BD_disc/todo.tex
New project
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2228 25464f21-6099-402c-b30a-640f1d40d38b

--- 2010-04-19 BD_disc/temp.tex
@@
-% mn2esample.tex
-%
-% v2.1 released 22nd May 2002 (G. Hutton)
-%
-% The mnsample.tex file has been amended to highlight
-% the proper use of LaTeX2e code with the class file
-% and using natbib cross-referencing. These changes
-% do not reflect the original paper by A. V. Raveendran.
-%
-% Previous versions of this sample document were
-% compatible with the LaTeX 2.09 style file mn.sty'
-% v1.2 released 5th September 1994 (M. Reed)
-% v1.1 released 18th July 1994
-% v1.0 released 28th January 1994
-
-\documentclass[useAMS,usenatbib]{mn2e}
-
-% If your system does not have the AMS fonts version 2.0 installed, then
-% remove the useAMS option.  
-% useAMS allows you to obtain upright Greek characters.
-% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
-% this guide for further information.
-%
-% If you are using AMS 2.0 fonts, bold math letters/symbols are available
-% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
-% preferably \bmath).
-%
-% The usenatbib command allows the use of Patrick Daly's natbib.sty for
-% cross-referencing.
-%
-% If you wish to typeset the paper in Times font (if you do not have the
-% PostScript Type 1 Computer Modern fonts you will need to do this to get
-% smoother fonts in a PDF file) then uncomment the next line
-% \usepackage{Times}
-\usepackage{lscape}
-\usepackage{graphicx}
-
-%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
-\newcommand\mnras{MNRAS}
-\newcommand\pasp {PASP}
-\newcommand\aj   {AJ}
-\newcommand\apj  {ApJ}
-\newcommand\apjl  {ApJL}
-\newcommand\apjs  {ApJS}
-\newcommand\aap  {A\&A}
-\newcommand\aaps  {A\&AS}
-\newcommand\apss  {AP\&SS}
-\newcommand\gca  {Geochim. Cosmochim. Acta}
-\newcommand\araa {ARA\&A}
-\usepackage{multirow}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title[Accreting Brown Dwarfs]{Problems with the characterisation of
-  accreting Brown Dwarfs: A public grid of simulated SEDs and
-  photometry}  \author[N.J.  Mayne and Tim
-Harries]{N.J. Mayne$^{1}$\thanks{E-mail: nathan@astro.ex.ac.uk
-    (NJM)} and Tim Harries$^{1}$\\
-  $^{1}$ School of Physics,
-  University of Exeter, Stocker Road, Exeter, EX4 4QL.\\
-}
- \begin{document}
-
-\date{Accepted ?. Received ?; in
-  original form ?}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2009}
-
-\maketitle
-
-\label{firstpage}
-
 \begin{abstract}
@@
 
-26) Note about colour colour plots cut in magnitude for J and removed
-the 0.01Msol stars from the naked
-
 27) For detections add in piece about the overlapping stars i.e what
 would be missed.
-
-28) missing 0.01 in alpha graph also.
-
-29) Adjust size of the smaller figures (i.e non-four) to fit.
-
-30) Change argument around to say rotation period correlation not
-present.
-
-31) Plots of inner temp against dust sublimation inner radius etc
-
-32) inclination against magnitude for different accretion rates.-one mass
-
-33) Sot out JJK isochrone
 
@@
    \end{abstract}
-
-\begin{keywords}
-  stars:evolution -- stars:formation -- stars: pre-main-sequence --
-  techniques: photometric -- catalogues -- (stars) Hertzsprung-Russell
-  H-R diagram
-\end{keywords}
-
-\section{Results: Analysis and Discussion}
-\label{results}
-
-\textbf{Intro-Questions to answer:IMF, Formation, Disc timescales and
-  $\dot{M}\propto M_*^{\approx 2}$=Ages, Masses and Disc fractions}
-
-Uncertainty remains over the formation mechanisms, resulting IMFs and
-subsequent interaction mechanisms with associated circumstellar disc,
-for BDs. Furthermore, no current theoretical explanation can be
-demonstrated for the suspected stellar mass-accretion rate
-relationship \citep[$\dot{M}\propto
-M_*^2$,][]{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}
-derived from observations and doubt remains over the existence of a
-disc-locking mechanism in BDD systems. Theoretical models and are
-built upon constraints, such as ages, masses and disc fractions, and
-correlations, such as the accretion rate to stellar mass relation,
-derived from the data. Critically, these resulting constraints and
-relationships involve both the application of existing models, such as
-isochrones to derive ages, and the selection of bias-minimised
-samples, for instance removal of foreground or background contaminant
-stars. Clearly, if one is to adopt a new theoretical model or use an
-observed correlation as a constraint one must explore the suspected
-intrinsic biases and the reliability of the selection criteria.
-
-In this Section we explore the effects of disc presence and accretion
-(across the described representative ranges, Section \ref{par_space})
-for our model grid. Essentially the premise is that if one accepts the
-assumptions and physical processes within our model grid would one be
-able to derive robust parameters using existing methods and
-furthermore, are the correlations found in the data intrinsic to the
-grid.
-
-Practically, most parameters for young pre-MS stars are derived from
-surveys of populations, usually open clusters, using broadband
-photometry and subsequently constructed colour-magnitude and
-colour-colour diagrams (CMDs and CoCoDs respectively,
-hereafter). Therefore, in this Section, firstly we demonstrate the
-prohibitive effects on the broadband photometry of varying our input
-parameters (Section \ref{photometry}). Secondly, we explore the
-underlying causes of the photometric scatters and intrinsic
-correlations using the SEDs and structure of individual BDD systems
-(Section \ref{sed_causes}).
-
-\subsection{Photometry}
-\label{photometry}
-
-\subsubsection{Ages and Masses}
-\label{age_mass}
-
-For the derivation of ages optical CMDs, in particular in \textit{V,
-  V-I}, are most often used, and indeed most suitable. Whereas, IR
-CMDs, such as a \textit{J, J-K} CMD, are most suitable for mass
-derivation \cite[see references and discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
-
-To delineate the effects of the accretion rate and circumstellar discs
-we have subdivided the grid into two groups, those with accretion
-rates typical for higher mass CTTS objects, defined as
-$\dot{M}=$10$^{-12}M_{\odot}yr^{-1}$ (negligible) to
-$\dot{M}=$10$^{-9}M_{\odot}yr^{-1}$ and those with elevated accretion
-rates, where $\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$. For several of the
-plots in this section the magnitude and colours for the
-$M_*=0.01M_{\odot}$ at high inclinations become extremely faint and
-red, respectively. In some cases these objects appear slightly without
-the scale of the diagram the axes where limited in this way to be able
-to show the changes in colour an magnitude for the majority of stars
-better. The colours and magnitudes for these lowest mass stars are not
-necessarily unreliable but simple hinder the aesthetics of the plots,
-and as they are at the limits of our grid we have decided to omit them
-from some Figures by trimming the axes. Additionally, stars at the
-highest inclinations, i.e edge on disc systems, are often omitted from
-the Figures due to their extremely faint magnitudes, meaning they
-would not be practically observable.
-
-\textit{Derivation of Ages}
-
-Figure \ref{spread_opt_VVI} shows four CMDs in \textit{V, V-I} with
-isochrones constructed from our data (comprising all masses from Table
-\ref{par_space_table}, excluding $M_*=0.01M_{\odot}$ for 10 Myr) at
-ages of 1 Myr and 10 Myrs, solid and dashed lines respectively. These
-isochrones are produced using the naked BD photometry at an accretion
-rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and a areal spot
-coverage of 10\%. The solid green line in the \textit{bottom left
-  panel} only is the 1Myr isochrone for naked systems at an accretion
-rate of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and a areal spot
-coverage of 10\%. The solid green line in the \textit{top left panel}
-only is the 1 Myr from \cite{2000A&A...358..593S} adjusted to a
-distance of 250pc and an extinction of $A_V=2$ mag, simulating a
-background population of CTTS stars. The remaining dots are the
-simulated photometry for the BD disc systems with accretion rates
-classed as typical (-9 to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$)
-at 1 Myr (only) for all areal coverages, periods and inclinations (see
-Table \ref{par_space_table}). The four panels then highlight the
-scatter in CMD space caused by variation across our input parameter
-space. The \textit{top left panel} splits the accretion rates into
-three, -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) as blue
-dots, -10 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black dots and -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red dots. The
-\textit{bottom left panel} shows the scatter due to period changes,
-with systems with periods of 5 days shown as blue dots and 0.5 days as
-red dots. The \textit{top right panel} shows the scatter caused by
-changes in areal coverage, with blue dots showing photometry from 1\%
-coverage systems and red dots for 10\% coverage systems. Finally, the
-\textit{bottom right panel} shows the results separated by inclination
-angles. The inclinations have been separated into three groups for the
-purposes of CMD analysis. These groups are $\theta \leq 48^{\circ}$ as
-blue dots (classed as face-on systems), $\theta> 56$ \& $64^{\circ}$
-(classed as the expected systems, as the expectation value of
-$cos(\theta)=60^{\circ}$) as black dots and $\theta \geq 71^{\circ}$
-(classed as edge-on systems) as red dots.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_VVI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{CMDs in $M_V, (V-I)_0$ showing,as lines, the isochrones for
-   all masses included in Table \ref{par_space_table} for ages 1 Myr
-   (solid) and 10 Myr (dashed). The isochrones are for naked BDs
-   without a disc, for the accretion rate -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (shown as in black), with
-   an areal coverage of 10\%. The solid green line in the \textit{top
-     left panel} only is the 1 Myr from \citet{2000A&A...358..593S}
-   adjusted to a distance of 250pc and an extinction of $A_V=2$ mag,
-   simulating a background population of CTTS stars. The dots are the
-   simulated photometry, of the star and disc system, for all models
-   at an age of 1 Myr with the accretion rates classed as typical (-9
-   to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). \textit{Top left
-     panel} shows the accretion rates separated into three groups -12
-   \& -11, -10 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as blue,
-   black and red dots respectively. \textit{Bottom left panel} shows
-   BDD systems with a rotation period of 5 days as blue dots and 0.5
-   days as red dots. \textit{Top right panel} shows those simulations
-   with an areal coverage of 1\% as blue dots and 10\% as red
-   dots. Finally, the \textit{bottom right panel} shows the systems in
-   three groups of inclinations, $\theta \leq 48^{\circ}$, as blue
-   dots, $\theta \geq 71^{\circ}$ as red dots and $\theta = 56$ \&
-   $64^{\circ}$ as black dots. \label{spread_opt_VVI}}
-\end{figure*}
-
-As can be seen in Figure \ref{spread_opt_VVI} current accretion in a
-star and disc system, for rates typical in the BD mass regime, creates
-a scatter in our simulated photometry indicative of a much larger
-isochronal age spread than 10 Myr. Indeed, for many BDD systems even
-at nominal accretion rates of -11 or -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, for our simulations, the
-colours of these stars move significantly blueward of the expected BD
-locus in a\textit{V, V-I} CMD. As the dots in Figure
-\ref{spread_opt_VVI} are the simulated photometry of BDD systems over
-a range of typical input parameters (see Section \ref{par_space}), an
-observed coeval 1 Myr population could reasonably be expected to show
-a similar scatter. The naked isochrones show that this spread in
-simulated photometry, would lead to a spread in isochronal age greater
-than the $\approx$10 Myr spread claimed for higher mass stars in some
-star forming regions (for instance the ONC). Furthermore, for the
-higher accretion rates of -9 or -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the movement of the star
-within the CMD will effectively move the star into the contamination
-region expected for background CTTS or MS stars at a \textit{V-I} of
-$\leq$1.5 and $M_V 12-10$, and as such the star would not be included
-in a photometrically selected BD sample. The solid green line, in the
-\textit{top left panel}, showing the 1 Myr isochrone of
-\cite{2000A&A...358..593S} at a distance of 250 pc and extinction of
-$A_V=2$ mags shows that the BDD systems with higher accretion rates
-could easily be confused for a background CTTS or MS population (as MS
-stars are simply less luminous at a roughly constant \textit{V-I} than
-the CTTS counterparts). Furthermore, scatter, although somewhat
-reduced, can be observed in the simulated photometry in the negligibly
-accreting systems, for example in the \textit{top left panel} some red
-dots, accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-(which will be negligible compared to the photospheric flux, see
-Figure \ref{acc_dom}), still scatter below the 10 Myr. These objects
-may still be included in a `wide' photometric selection. This scatter
-is a strong function of inclination, as shown in the \textit{bottom
-  right panel}, where, as the inclination is increased the objects are
-pushed lower in the CMD. Indeed, for the edge on cases some objects
-have magnitudes fainter than show in Figure \ref{spread_opt_VVI}
-($M_V\approx 30$). This is expected as the star becomes obscured by
-the flared disc, interestingly for these systems the \textit{bottom
-  right panel} shows that this occurs for inclinations above around
-71$^{\circ}$ in most cases yet even for the lower inclination angles
-some objects have very faint magnitudes, this is due to the disc
-flaring leading to a smaller opening angle and is discussed later in
-Section \ref{disc_struct}. The \textit{top right panel} shows that the
-scatter, in \textit{V}, in our simulated photometry from the
-isochrones is significant for both areal coverages. However,
-significant scatter blueward in colour is slightly more evident for
-the lower areal coverage and therefore hotter accretion spot
-temperature, as is expected given that the higher spot temperature
-contributes more flux blueward of the photosphere. Finally, the
-\textit{bottom left panel}, shows significant scatter in the simulated
-photometry for both adopted rotation periods. This panel also shows
-that scatter in this diagram is not obviously correlated with the
-rotation period and therefore inner edge position. Additionally, the
-\textit{bottom left panel} shows that for naked systems accretion
-rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ lead to the stars
-being scattered into the region occupied by background CTTS and
-contamination (the lower accretion rates are all coincident with the
--12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for 1 Myr). Overall, as
-found in \cite{2004MNRAS.351..607W}, the dominant scattering effect
-for BD disc systems in an optical CMD appears to be caused by
-inclination and therefore obscuration effects of the disc on the
-star. This suggests that for a given photometric survey of BDD systems
-accreting at typical accretion rates and with an expected range of
-inclinations (centred on around 60$^{\circ}$) one would expect to
-exclude a significant fraction of these objects from any isochrone
-based selection.
-
-Similar scattering occurs when using CMDs constructed using \textit{R,
-  R-I} \citep[using the photometric system
-of][]{1998A&A...333..231B}. Figure \ref{spread_opt_RRI} shows the
-\textit{R, R-I} CMD.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_RRI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_opt_VVI} but the 1 Myr isochrone
-   of \citet{2000A&A...358..593S} is omitted and the CMDs are for
-   $M_R, (R-I)_0$. \label{spread_opt_RRI}}
-\end{figure*}
-
-Therefore, if one adopts the range of input parameters we have used
-(see Section \ref{par_space} for justification), our simulated
-photometry shows, qualitatively, that a coeval 1 Myr population of
-accreting BD stars and BDD systems, with typical accretion rates and
-range of inclinations, will exhibit a scatter in apparent isochronal
-age of $>$10 Myr. Furthermore, some objects will be scattered below
-and blueward of a 10 Myr isochrone. This has been shown for CMDs in
-\textit{V, V-I} and \textit{R, R-I}. It is important to note at this
-point that these conclusions are qualitative, and obviously based on
-our assumptions. However, the repercussion for isochronal age
-derivation and sample selection in the BD regime could be
-profound. Indeed this study has only included the effects of current
-or ongoing accretion from a disc, it has totally neglected any effects
-of accretion, both past and present, on the evolution of the central
-star. This past accretion could also act to reduce the stars radius,
-accelerating contraction
-\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
-additional scatter in a coeval population proportional to the range in
-accretion rates \citep[See][for full
-discussion]{2008MNRAS.386..261M}. Our findings support those of
-\cite{2004MNRAS.351..607W}, showing that a significant scatter is
-caused by obscuration of the central source by the central disc. In
-addition we have shown that the scatter blueward, into the CTTS or
-background MS locus, is caused by active accretion at levels found in
-CTTS stars, but currently not regularly recorded in stars classified
-or selected as BDs.
-
-\textbf{Derivation of Masses}
-
-Similar consequences are apparent when attempting to derive masses
-from isochrones using CMDs. We have constructed CMDs using the
-simulated photometry of our model grid in the \textit{JK}
-magnitudes. Figure \ref{spread_ir_JJK} shows CMDs in \textit{J, J-K} for
-the same data as Figure \ref{spread_opt_VVI}. The symbols have the
-same meanings as in Figure \ref{spread_opt_VVI}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_ir_JJK.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_opt_VVI} but the CMDs is for $M_J,
-   (J-K)_0$.\label{spread_ir_JJK}}
-\end{figure*}
-
-As is shown by Figure \ref{spread_ir_JJK} a similar scatter is
-observed in our simulated photometry in the IR CMD as is evident in
-its optical counterparts. Once again, as shown in the \textit{top left
-  panel}, scatter is seen in both the nominal and higher accretion
-rates (-9 to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), meaning
-derivation of masses for objects using IR isochronal fitting of these
-objects would be very difficult. However, in this CMD the scatter is
-generally redward of the isochrone, this is still however into the
-region where background CTTS stars would be expected. The \textit{top
-  right panel} shows no correlation with areal coverage of the hot
-spot. Interestingly the \textit{bottom left panel} shows no clear
-evidence for a correlation in CMD position, and therefore distance
-from the isochrone, with rotation period of the system as found in
-\cite{1997AJ....114..288M}, this is discussed in more detail in
-Section \ref{disc_struct}. Additionally, \textit{bottom left panel}
-agains shows significant scatter away from the isochrone for the 1 Myr
-naked stars at an accretion rate of -9
-$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, however in this case the scatter
-is in the opposite sense (blueward as opposed to redward) to that
-caused by accretion and disc presence in the BDD systems. Again,
-scatter is still caused by changes in inclinations, as shown in the
-\textit{bottom right panel}, with fainter magnitudes for more inclined
-systems, as expected however, this effect causes a smaller change in
-magnitude in the IR due to less of the disc appearing optically thick
-at these wavelengths.
-
-Therefore, as for derivations of age, given our assumptions, and the
-adopted range of input parameters, a 1 Myr coeval population scatters
-significantly in a \textit{J, J-K} CMD. The \textit{J, J-K} CMD is
-representative of CMDs constructed from the \textit{JHK}
-passbands. So, qualitatively at least, derivation of masses using
-isochronal fitting of our simulated photometry would not produce
-reliable or accurate results. Again, as discussed for optical CMDs,
-these simulations do not include any of the effects of past or current
-accretion on the evolution of the central object, which is expected to
-significantly exacerbate the observed scatter. This is also true for
-the naked systems with small increases in accretion rate leading to
-significant scatters in the CMDs. Additionally, given the evidence
-discussed in \cite{2004MNRAS.351..607W}, supported by the evidence
-from our own simulated photometry shown in Figures
-\ref{spread_opt_VVI}, \ref{spread_RI} and \ref{spread_ir_JJK}, it is
-clear that young, accreting, BDD systems are likely to be
-misidentified when using photometric colours or magnitudes, even at
-generally canonical accretion rates. This casts doubt on the veracity
-of the mass to accretion rate relationship. For our model grid we have
-not assumed any such relation, therefore, as our data would also show
-a similar relation it suggests that the observed result may be caused
-by intrinsic scattering. The relation, $\dot{M}\propto M_*^{2}$
-suggests that their is a dearth of lower mass stars accreting at
-higher rates. We have shown that for accretion rates in the range -12
-to -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with
-higher accretion rates would be preferentially missed using
-photometric or isochronal selection.
-
-\subsubsection{Extreme accretion rates}
-\label{elevated_accn}
-
-\textbf{CMDs}
-
-BDD and naked BD systems with elevated or extreme accretion rates are
-also likely to be miss-classified, or not observable in the same
-dynamic magnitude range as a BD survey.  Figure \ref{high_acc_opt}
-shows our isochrones for the naked BD systems with accretion rates of
--6, -7 \& -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ at 1 Myr (solid
-lines in red) with areal coverages of 10\%, and the pre-MS isochrone,
-at 1 Myr, of \cite{2000A&A...358..593S} for higher mass stars, down to
-$M_*=$0.1$M_{\odot}$ (solid black line). The remaining dots are the
-simulated photometry from our model grid for stars with an age of 1
-Myr and accretion rates of -6, -7 \& -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, and the complete range of all
-other input parameters (see Table \ref{par_space_table}. As can be
-seen by comparing Figure \ref{spread_opt_VVI} with Figure
-\ref{high_acc_opt} the simulated photometry for the naked systems
-changes dramatically with increasing accretion rate, meaning that even
-without the effects of a disc individual highly accreting BDs
-dramatically change position in an optical CMD. The simulated
-photometry of the disc systems is then separated in each panel. The
-\textit{top left panel} shows systems with accretion rates of -6, -7
-and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red, black and blue
-dots respectively. The \textit{top right panel} distinguishes the
-areal coverages of 1 and 10\% as red and blue dots respectively. The
-\textit{bottom left panel} separates the two rotational periods of 5
-and 0.5 days into blue and red dots respectively. Finally, the
-\textit{bottom right panel} plots the three adopted inclinations
-groups $\theta \leq 48^{\circ}$, $\theta> 56$ \& $64^{\circ}$,
-$cos(\theta)=60^{\circ}$) and $\theta \geq 71^{\circ}$, as blue, black
-and red dots respectively.
-
-The \textit{top left panel} shows that these objects are generally
-scattered to an apparently higher (isochronal) mass and older
-(isochronal) age, with the scatter increasing with accretion
-rates. This means that as the accretion rate increases the star is
-pushed to bluer and brighter colours and magnitudes, effectively, to
-higher stellar masses. The \textit{top right panel} shows that this
-effect is apparent for both areal coverages, it is perhaps surprising
-that in general there does not appear to be a reduction in the
-magnitude of the scatter when one moves to the larger areal
-coverage. The \textit{bottom left panel} shows again that there is no
-correlation in CMD position with rotation rate, and therefore
-co-rotation radius (again this is discussed further in Section
-\ref{disc_struct}. Finally, the \textit{bottom right panel} again
-shows that the system inclination scatters the resulting position
-within the CMD, with greater inclination meaning greater obscuration
-of the central star, by the disc, and therefore fainter magnitudes and
-redder colours, and it is clear that photometrically a highly
-obscured, highly accreting BDD system could be photometrically
-classified as contamination or a higher mass CTTS system.
-
-Once again, given our assumptions, qualitatively, young, pre-MS BD
-disc systems accreting at higher rates would not be identifiable as
-such from optical CMDs and isochronal fitting. Meaning it is likely
-that our data would indicate a stellar mass to accretion rate
-relation, even though we have not adopted such a relationship.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/high_acc_opt.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{The optical CMD, $M_V, (V-I)_0$ showing the effects of
-   extreme accretion rates. The solid black line is the pre-MS
-   isochrones of \citet{2000A&A...358..593S} at 1 Myr for masses down
-   to 0.1 $M_{\odot}$, the solid red lines are our derived isochrones
-   for the naked photospheric models at accretion rates of -6, -7 \&
-   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, colours of red, black
-   and blue respectively, using an areal coverage of 10\% (the coolest
-   and therefore lowest accretion luminosity). The dots are the
-   simulated photometry for the BDD systems for the three highest
-   accretion rates (as for the isochrones). \textit{Top left panel}
-   shows the accretion rates separated into three groups -6, -7 and -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red, black and blue dots
-   respectively. The data in the remaining panels is separated into
-   the groups used in Figure \ref{spread_opt_VVI} using the same
-   symbols and colours.\label{high_acc_opt}}
-\end{figure*}
-
-A similar situation is apparent for the IR passbands, where isochrones
-are often used to derive stellar masses. Figure \ref{high_acc_ir} is
-the IR version of Figure \ref{high_acc_opt}, the only difference
-between the figures are the colours and magnitudes, the conventions,
-symbols and models are the same. Figure \ref{high_acc_ir} shows the
-CMDs using \textit{J, J-K}, also using the same conventions for each
-of the \textit{four panels}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/high_acc_ir.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As above but for $M_J, (J-K)_0$ colours. Here the effects
-   of high accretion can shift the stars into higher or lower mass bins.
-   \label{high_acc_ir}}
-\end{figure*}
-
-As can be seen by comparing Figure \ref{spread_ir_JJK} and Figure
-\ref{high_acc_ir}, accreting BD systems without discs are shifted
-brighter and bluer resulting in a large error in isochronal mass
-derivation. The simulated photometry for BDD systems however, shows
-large magnitudes of scatter redward and towards slightly brighter
-magnitudes. Given that the reddening vector is approximately
-horizontal in a \textit{J, J-K} CMD many of these objects will appear
-as heavily obscured objects of higher mass. The \textit{top left
-  panel} shows that the scatter does increase for higher accretion
-rates, however, even at the lower of the accretion rates (-8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), significant scatter is
-evident. The \textit{top right panel} shows that the scatter is
-roughly the same for both areal coverages. The \textit{bottom left
-  panel} shows, again, no correlation between rotation rate and
-scatter within the CMD. This is unsurprising as at these elvated
-accretion rates the increase in flux will lead to significant levels
-of dust sublimation of the inner edge, as discussed in more detail in
-Section \ref{disc_struct}. Finally, the \textit{bottom right panel}
-shows systems with a larger inclination having, generally lower
-magnitudes, and therefore lower masses, as expected.
-
-Therefore, again as for the optical case, given our assumptions and
-parameter space, BDD systems accreting at higher rates would not be
-identified with the correct mass in most cases using IR CMDs.
-
-\subsubsection{Disc fractions}
-\label{derive_frac}
-
-To distinguish between the proposed formation mechanisms for BDs, and
-to derive disc lifetimes, accurate derivations of disc fractions are
-required (as well as stellar masses).
-
-\textbf{Derivation of disc fractions.}
-
-Disc fractions have been derived using infrared excesses previously in
-\textit{JHK}, however recent works pre-dominantly use \textit{Spitzer}
-IRAC magnitudes. Furthermore, MIPS magnitudes are used to identify
-so-called debris discs, where IR excesses are not apparent at shorter
-wavelengths. Finally, disc fractions have also been derived using the
-$\alpha$ criteria, where $\alpha=\frac{dlog\lambda
-  F\lambda}{dlogF\lambda}$ between two limiting wavelengths,
-originally used to distinguish amongst Class I, II or II sources, but
-now used to detect disc presence
-\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
-used as a selection criterion for disc presence for TTS stars. We have
-constructed the $\alpha$ values for our model grid by adopting the
-limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
-8.0$\mu$m.
-
-\subsubsection{Colour-colour plots}
-\label{col_col_plots}
-
-Figure \ref{ir_excess} shows CoCoDs in \textit{J-H, J-K} for our
-simulated photometry for all accretion rates, masses, inclinations,
-coverages and periods, at 1 Myr only. The black crosses are the
-simulated photometry of the naked BD systems, with the dots the
-simulated photometry of the BDD systems, for 1 Myr only.  The
-\textit{top left panel} then separates the accretion rates with -12,
--11, and -10 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as red dots
-and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as green dots and
--8, -7, and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue
-dots. The \textit{top right panel} distinguishes those models with
-areal accretion stream coverages of 1 and 10\% as blue and red dots
-respectively. The \textit{bottom left panel} separates the rotational
-periods with 0.5 days shown as red dots and 5 days as blue dots. The
-\textit{bottom right panel} shows each of the three inclination groups
-$\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as
-green dots and $\theta \geq 71^{\circ}$ as red dots.
-
-As can be seen for all the panels of Figure \ref{ir_excess} there is a
-slight overlap between the naked or disc less objects and the BDD
-systems. This overlap is small, only some of the smallest mass naked
-objects appear redward of the main population. Generally, a well
-placed cut should identify a large proportion of the disc candidates
-as is well known, if there is little complication from variable
-extinction and a well defined photometric system. However, the fact
-that an overlap exist at all will lead to some confusion as to the
-position of any disc excess cut. For real data a cut will be placed at
-a user identified paucity or gap in the CoCoD. Therefore, in practice,
-if any other region of the population appears equally, or more, sparse
-the cut is likely to be miss-placed. In practice these disc fractions
-are known to be lower limits of the true values, so ostensibly a miss
-placed cut, essentially missing some disc candidates is not
-problematic. On further inspection however it does introduce a crucial
-bias. In all panels of Figure \ref{ir_excess} potential gaps or drops
-in the number of stars can be seen at $J-K \approx$ 1.5 \& 2.5. The
-\textit{top left panel} shows that changes in accretion rate do not
-appear, qualitatively, to correlate with CoCoD position, indeed
-changes in the different areal coverages (\textit{top left panel}),
-inclinations (\textit{bottom right panel}) and rotation rate
-(\textit{bottom left panel}) also appear to produce random scatter.
-
-Critically a strong correlation can be
-observed between CoCoD position and rotation period of the system in
-the \textit{bottom left panel}. This panel shows that longer period
-objects, in general, lie closer to the naked BD locus and are
-therefore more likely to be classed as disc less stars. Conversely,
-almost all of the short period objects lie well separated from the
-naked BD locus, and one could also argue for a separation between the
-two populations of different rotation periods at $J-K \approx$2. It is
-therefore, likely, that early surveys of BD (or perhaps TTS) stars
-attempting to find a correlation between disc presence and slower
-rotation rates, to support disc locking, were heavily affected by this
-bias. Essentially, unless the data are free from variable extinction
-and photometric errors are small, manually placing a disc excess cut
-based on population densities is likely to preferentially miss slower
-rotators and include faster rotators. This leads to an
-anti-correlation between disc presence and slow rotation period.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/ir_excess.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing relative positions of accreting BDs with
-   (naked) and without discs in $(J-H)_0, (J-K)_0$ CoCoDs. \textit{Top
-     left panel}, this shows all studied accretion rates as green, red
-   blue and black dots for -6, -7, -8 and -9, -10, -11, -12 (together)
-   respectively log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
-   \textit{Lower left panel}, here blue dots are star disc systems
-   with a rotation period of 5 days and red for 0.5
-   days. \textit{Upper right panel}, blue dots are those simulations
-   with an areal coverage of 1\% and red dots have 10\%. Finally, the
-   \textit{lower right panel}, the systems at different inclinations
-   are shown with 0, 60 and 90$^{\circ}$ shown as black, blue and
-   red dots respectively.
-   \label{ir_excess}}
-\end{figure*}
-
-More recent studies, and indeed those studies where strong support for
-a disc locking mechanism is found, use data from the IRAC camera on
-the \textit{Spitzer} space telescope \citep[as for TTS,
-see][]{2007ApJ...671..605C}. Therefore, using our simulated photometry
-in these passbands we are able to investigate any possible expected
-biases in observations of this type. Figures \ref{irac_excess} and
-\ref{irac_excess_2} are similar to Figure \ref{ir_excess} showing the
-same models and using the sames conventions and symbol meanings, only
-showing constructed CoCoDs using IRAC channels. It is important to
-note that objects, either naked or with discs, of mass,
-$M_*=$0.01$M_{\odot}$ are not included in Figures \ref{irac_excess} and
-\ref{irac_excess_2}, as their flux becomes unreliable and noise
-dominated at these longer wavelengths. Figure \ref{irac_excess} shows
-[4.5]-[5.8] against [3.6]-[4.5] and Figure \ref{irac_excess_2}
-shows [5.8]-[8.0] against [3.6]-[4.5], two commonly used disc
-identification CoCoDs. In both these figures the naked (disc less) BD
-population is very well separated from the main population, meaning in
-a region free of variable extinction and with reliable photometry disc
-excess cuts can be placed with a high degree of confidence. As seen
-for Figure \ref{ir_excess} little correlation is found between CoCoD
-position and accretion rate, areal coverage or inclination, however, a
-clear correlation is again found with rotational period.
-
-The effect of rotational period on the position of the BDD systems in
-the IRAC CoCoDs is the reverse of that found for \textit{JHK}. Longer
-period objects will be observed as lying further from the naked BD
-locus, resulting in any uncertainty in the cut position preferentially
-including shorter period systems. This may introduce a slight bias in
-disc fraction surveys carried out using IRAC data, perhaps falsely
-increasing the apparent strength of a disc-locking type correlation
-between inferred disc presence and slower rotators. However, if a
-similar effect is apparent in TTS (as would be expected albeit
-slightly reduced due to less significant flaring of the outer disc),
-the much clearer separation between naked and disc systems means that
-this bias will be much easier to avoid.  Therefore, our results do not
-affect the recent evidence for a disc-locking mechanism in TTS.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_excess.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{ir_excess} but in IRAC colours
-   [3.6]-[4.5] against [4.5]-[5.8]. 
-   \label{irac_excess}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_excess_2.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{irac_excess} but in IRAC colours
-   [3.6]-[4.5] against [5.8]-[8.0]. 
-   \label{irac_excess_2}}
-\end{figure*}
-
-\textbf{IRAC and MIPS diagrams}
-
-**NOTE ABOUT $M_*=$0.01$M_{\odot}$ CURRENTLY NOT REMOVED**
-
-Figures \ref{irac_mips_excess} and \ref{irac_mips_excess_2} show
-CoCoDs for colours constructed using IRAC and MIPS data. These Figures
-include the same models as Figures \ref{irac_excess} and
-\ref{irac_excess_2}, presented using the same symbols and colour
-conventions. The longer wavelength MIPS data provides better
-sensitivity to the outer disc emission. As with the IRAC data
-alone the separation between the BDD and naked systems is large and
-the clearest correlation between input parameter and colour-colour
-space position is rotation period. A evident in the \textit{bottom
-  left panels} of Figures \ref{irac_mips_excess} and
-\ref{irac_mips_excess_2}, the longer period systems generally lie
-redward in both [3.6]-[4.5] and [8.0]-[24.0] than the shorter period
-systems. Some correlation of colour-colour position and inclination is
-evident from the \textit{bottom right panels} of Figures
-\ref{irac_mips_excess} and \ref{irac_mips_excess_2}. In this case as
-the inclination increases the systems generally move redward in
-[8.0]-[24.0].
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_mips_excess.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{A CoCoD constructed using both IRAC and MIPS data showing
-   [3.6]-[4.5] against [8.0]-[24.0]. The symbols are as described in
-   As for figure \ref{ir_excess}.
-   \label{irac_mips_excess}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_mips_excess_2.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{irac_mips_excess} but using colours
-   [3.6]-[5.8] against [8.0]-[24.0].
-   \label{irac_mips_excess_2}}
-\end{figure*}
-
-Figure \ref{mips_four} shows CoCoDs constructed using only MIPS data,
-plotting the colours 24$-$70$\mu$m against 70$-$160$\mu$m for the 1 Myr
-naked and BDD systems. Figure \ref{mips_four} shows that, again, the
-naked and BDD systems are well separated. Figure \ref{mips_four} also
-shows the correlations in scatter for each input variable. For
-\textit{all panels} of Figure \ref{mips_four} the crosses show the
-naked systems and the dots are the BDD systems. The \textit{upper left
-  panel} separates the two accretion rates with -8 and -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ plotted as blue and red dots
-respectively. In the \textit{upper right panel} the BDD systems with 1
-and 10\% areal coverages are plotted as blue and red dots
-respectively. The \textit{lower left panel} plots the periods of 5 and
-0.5 days as blue and red dots respectively. \textit{lower right panel}
-separates the BDD systems by inclination with 0, 60 and 90$^{\circ}$
-plotted as black, blue and red dots respectively. As can be see in
-Figure \ref{mips_four} the inclination correlates strongly with CoCoD
-position with the almost edge-on systems appearing much redder than
-the naked or face on BDD systems. Furthermore, using the \textit{lower
-  panels} it can be seen that for each inclination the CoCoD position
-is then separated by rotation period, with two separated populations
-for each inclination group.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/mips_four.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{irac_excess} but in MIPS colours
-   [24]-[70]($\mu$m) against [70]-[160]($\mu$m). 
-   \label{mips_four}}
-\end{figure*}
-
-\subsubsection{Observational cuts}
-\label{obs_cuts}
-
-Some recent studies of disc fractions for BD populations have used
-data from the \textit{Spitzer} IRAC camera. Figures
-\ref{irac_cut} and \ref{irac_cut_2} show the simulated photometry for
-our complete model grid. Naked BDs are shown as crosses and BDD
-systems as dots, with 1 and 10 Myrs data shown as blue and red dots
-respectively. The dashed lines are cuts used in two recent
-publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
-a study of IC348 and Figure \ref{irac_cut_2} from
-\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis. In both cases
-the effects of extinction are either negligible in the plotted
-colours, with values of $E([3.6]-[4.5])<0.04$ \& $E([4.5]-[5.8])<0.02$
-for IC348, or the cuts have been placed in intrinsic colour space as
-for $\sigma$ Orionis. As can be seen from Figures \ref{irac_cut} and
-\ref{irac_cut_2} most of the disc systems from our simulated
-photometry would be correctly identified using these cuts. It is
-important to note that as for Figures \ref{irac_excess} and
-\ref{irac_excess_2} stars of mass, $M_*=$0.01$M_{\odot}$, are not
-included due to unreliable flux levels at these
-wavelengths. Additionally, our conclusions so far have been drawn from
-differential photometric arguments, in this case we are using
-intrinsic colours and these values are extremely sensitive to changes
-in zero point and photometric calibration.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/irac_cut.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{This shows all simulated photometry for the entire studied
-   parameter range at ages 1Myr and 10Myr as dots (blue and red
-   respectively), and the naked photometry as crosses. The dashed
-   lines are a recent BD disc excess
-   cuts used in \citet{2005ApJ...631L..69L} for IC348 at a nominal age
-   of 3-4Myr \citet{2008MNRAS.386..261M}. It must be noted that the naked
-   stars of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours.
-   \label{irac_cut}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/irac_cut_2.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{This figure shows an observational cut used in
-   \citet{2008ApJ...688..362L} for data of the $\sigma$ Orionis
-   cluster. It must be noted that the naked
-   stars of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours.
-   \label{irac_cut_2}}
-\end{figure}
-
-\textbf{alpha}
-
-Disc fractions are also derived using the $\alpha$ value
-\citep{2006AJ....131.1574L}, essentially a slope of the SED between
-two wavelengths (at wavelengths longer than the stellar flux
-peak). Figure \ref{alpha_zoom} shows the derived $\alpha$ values
-between 3.6 and 8.0$\mu$m for our entire model grid (against an
-arbitrary model number), with dots showing BDD systems and crosses
-showing naked systems. As shown for TTS $\alpha>-$2 distinguishes
-systems with discs \citep{2009arXiv0901.2603K}. As can be seen in
-Figure \ref{alpha_zoom} almost all (except $\frac{3}{1120}$) disc
-systems would be successfully identified using this
-criterion. Suggesting that the $\alpha$ value is a reliable disc
-indicator for BD systems. Figure \ref{alpha_four} show the same Figure
-(Figure \ref{alpha_zoom} in \textit{four panels} with each panel
-showing spread caused by a particular input variable. The
-\textit{upper left panel} shows the alpha values for two different
-accretion rates, with -12 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue and red dots
-respectively. The \textit{upper right panel} differentiates
-populations with different areal coverages of the accretion stream,
-where 1 and 10\% are shown as blue and red dots respectively. The
-\textit{lower left panel} shows scatter caused by rotational period
-changes, with periods of 5 and 0.5 days shown as blue and red dots
-respectively. Finally, the \textit{lower right panel}, the systems at
-different inclinations are shown with 0, 60 and 90$^{\circ}$ shown as
-black, blue and red dots respectively. It is important to note that
-the lowest mass objects ($M_*=$0.01$M_{\odot}$) do not appear in Figures
-\ref{alpha_zoom} or \ref{alpha_four} due to unreliable flux estimates
-for the stellar atmospheres at the longer wavelengths ($\lambda >$4$\mu$m).
-
-Figure \ref{alpha_four} shows, as one would expect a similar
-scattering pattern to the IRAC photometry. This is as the $\alpha$
-value has been derived over a similar wavelength range, namely, 3.6
-to 8.0$\mu$m. Essentially, the $\alpha$ values shows the scatter is
-uncorrelated with coverage and accretion rate, as expected for the
-shorter wavelength accretion flux contribution. As the inclination
-angle increases the $\alpha$ value generally reduces. Finally, the
-shorter period objects lie closer to the naked BD locus in $\alpha$
-space.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/alpha_zoom.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{This Figure shows the $\alpha$ value
-   \citep{2006AJ....131.1574L} (against an arbitrary
-   model number)  used
-   \citet{2009arXiv0901.2603K}, $\alpha=\frac{dlog(\lambda
-     F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
-   $\mu$m). Crosses show the simulated objects without discs and dots
-   are
-   those with circumstellar disc, the horizontal line is the
-   $\alpha>-$2 cut used to identify disc candidates for solar type
-   stars in \citet{2009arXiv0901.2603K}. Note, that stars of
-   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
-   estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4$\mu$m).
-   \label{alpha_zoom}}
-\end{figure}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/alpha_four.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{alpha_zoom} except each of the \textit{four
-     panels} shows the underlying scatter separated by input
-   variable. The \textit{upper left panel} shows the alpha values for
-   two different accretion rates, with -12 and -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue and red dots
-   respectively. The \textit{upper right panel} differentiates
-   populations with different areal coverages of the accretion stream,
-   where 1 and 10\% are shown as blue and red dots respectively. The
-   \textit{lower left panel} shows scatter caused by rotational period
-   changes, with periods of 5 and 0.5 days shown as blue and red dots
-   respectively. Finally, the \textit{lower right panel}, the systems
-   at different inclinations are shown with 0, 60 and 90$^{\circ}$
-   shown as black, blue and red dots respectively. Note, that stars of
-   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
-   estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4$\mu$m).
-   \label{alpha_four}}
-\end{figure*}
-
-\subsection{Physical causes of scatters and correlations}
-\label{scatter_causes}
-USE THIS BIT FOR THE SEDS SECTION
-**ADD IN TEMPERATURE RANGES FOR DISCUSSION HERE**
-
-The scatters observed in our photometry, caused by varying our input
-parameters, are obviously caused by changes in the simulated
-SEDs. These changes are in turn due to changes in the physical
-structure of the system. In this Section we examine the simulated SEDs
-and resulting temperature and density structure of the discs to
-explain the photometric scatters.
-
-As discussed, Figure \ref{spread_opt_VVI} shows that for the optical CMD
-(\textit{V, V-I}), the scatter in colour appears correlated with areal
-coverage and accretion rate of the accretion stream. Objects with
-higher accretion rates and smaller areal coverages and, therefore,
-higher fluxes or accretion luminosities scatter blueward of the
-isochrone. There is also perhaps evidence of a weak correlation with
-rotation period and colour scatter in Figure
-\ref{spread_opt_VVI}. Finally, the scatter in the magnitude (\textit{V}),
-and to some extent colour (\textit{V-I}), present in the data in
-Figure \ref{spread_opt_VVI} is clearly correlated with inclination. For
-the IR CMD (\textit{J, J-K}), once again, scatter in magnitude appears
-strongly correlated with inclination. There is also a clear
-correlation of scatter in colour with rotation period, but the
-remaining two variables appear to show random scatter only.
-
-To explore the causes of the shifts we must relate the changes in the
-resulting SEDs to the relevant physical parameters. Essentially, the
-summed flux is comprised of four main components, the stellar
-photosphere (luminosity $L_*$), the accretion stream (luminosity
-$L_{\rm acc}$), the disc inner boundary or wall (luminosity $L_{\rm
-  wall}$), and the outer regions of the, highly-flared, circumstellar
-disc (luminosity $L_{\rm disc}$). For a given mass and age, the radius
-and intrinsic stellar photospheric flux are fixed. For our model grid
-the fluxes are produced at effective temperatures of 3000K$<T_{\rm
-  eff}$1600K.
-
-The flux from the accretion stream is dominant at shorter wavelengths,
-within our range, peaking below a wavelength of 1$\mu$m (see Figure
-\ref{acc_dom}). This is as the accretion hotspot can reach much higher
-temperatures than the stellar photosphere, up to 16700K. The accretion
-luminosity is calculated using equation \ref{Lacc} (in Section
-\ref{physics}), and the resulting flux levels are computed using an
-effective temperature (Equation \ref{Tacc}, Section \ref{physics}) to
-generate a blackbody emission curve. As the accretion flux is
-calculated using a blackbody law, the peak wavelength is a function of
-the effective temperature of the accretion spot, $\lambda_{\rm
-  peak}\propto \frac{1}{T_{\rm acc}}$. Therefore, the effects of the
-accretion flux component on the resulting SED, in terms of total flux
-and peak wavelength, are a strong function of the input variables,
-accretion rate and areal coverage. Essentially, high accretion rates
-and low areal coverages lead to an increased influence of accretion
-stream on the final SED. The increased accretion flux creates a blue
-excess, easily dominating the cooler BD photospheres at shorter
-wavelengths. The converse of this is also true i.e. lower accretion
-rates with larger hot spots results in a reduction of the influence of
-the accretion flux on the SED.
-
-The flux from the inner boundary is a function of the temperature of
-the inner wall. This is dependent on its proximity to the central
-object. The initial inner wall radius was set as the magnetic
-co-rotation radius (see Section \ref{physics}). This distance is a
-strong function of rotational period, with $R_{\rm inner}\propto
-\tau^{2/3}$ (see Equation \ref{inner_eq}). During the radiative
-transfer simulations the inclusion of dust sublimation effects will
-result in a shift of the inner wall radius for the hotter wall
-temperatures. The differences in the initial and final inner wall
-radius are discussed in Section \ref{inner_edge_position}. However,
-they do not show significant differences between initial and final
-inner wall radii. Therefore, for our purposes the inner disc radius
-can still be considered proportional to the rotation period. This
-inner boundary will clearly be cooler than the stellar surface, or the
-accretion hot spot, and will therefore contribute flux at longer
-wavelengths. The resulting flux component, for the inner wall,
-dominates at longer wavelengths, peaking at between 2 and 3$\mu$m
-\citep{2001ApJ...560..957D}. This is due to its cooler temperature,
-which is neccesarily less than the dust sublimation ($\approx$1400K).
-
-**CHECK THIS EMISSION FROM IRAC ACTUALLY FROM JUST BEHIND THE INNER
-EDGE-THEREFORE ARGUMENT STILL STANDS BUT MUST ADD IN A PUFFING UP OF
-THE INNER EDGE EFFECT**
-
-Finally, the flux from the outer flared region of the disc is simply a
-function of the temperature of the outer disc. This, in turn, is a
-function of the stellar flux reaching these regions of the disc. This
-is a function of the rotational period. For closer inner boundaries
-more flux is intercepted by the inner boundary and therefore less
-reaches the outer regions, for longer periods the farther inner wall
-radii means more flux reaches the outer disc regions (see Section
-\ref{disc_period_relation}). These regions of the disc will be cooler
-than the inner boundary and, therefore only have a significant flux
-contribution at wavelengths longer than 3$\mu$m.
-
-Therefore, the shape of the resulting SED, for a star-disc system of
-at fixed stellar mass and age, will be dependent on the dominance of
-the hot short wavelength accretion component, the cooler
-mid-wavelength component of the inner boundary, and the even cooler,
-longer wavelength component from the outer regions of the disc.
-Practically, for our model grid, the shape is therefore a function of:
-Accretion rate and coverage ($L_{\rm acc}$) and the rotation period
-($L_{\rm wall}$ \& $L_{\rm disc}$).
-
-The final, and most important variable affecting the shape of the SED
-is inclination. This variable affects the balance of the photospheric
-flux escaping ($L_*$ \& $L_{\rm acc}$) and that observed from the disc
-($L_{\rm wall}$ \& $L_{\rm disc}$). Essentially, the flux for all wavelengths
-will reduce as the inclination increases. However, this reduction,
-with inclination, will reduce toward longer wavelengths. This is as
-the opacity of the disc will reduce with increasing wavelength.
-
-So, to relate these changes to the scatter we observe in the CMDs of
-Figures \ref{spread_opt_VVI} and \ref{spread_ir_JJK}, we have plotted the CMDs
-for a star of $M=$0.04$M_{\odot}$, at an age of 1 Myr, for a range of
-parameters in optical and IR colours in Figure \ref{spread_cmd}.
-Figure \ref{spread_cmd} shows the \textit{V, V-I} (\textit{left
-  panel}) and \textit{J, J-K} (\textit{right panel}) CMDs. For
-\textit{both panels} the naked BD systems, with negligible accretion
-flux (-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 10\% coverage)
-are shown as black crosses. For \textit{both panels} the red coloured
-symbols are those which have the inner boundary component maximised,
-i.e. with the shorter rotation period of 0.5 days, and the blue
-symbols denote systems with the longer period of 5 days, and therefore
-minimised inner boundary flux. The circles represent those systems
-with the accretion flux component maximised, i.e. an accretion rate of
--8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 1\% areal coverage,
-and the triangles show systems with the accretion component minimised,
-i.e. an accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-with 10\% areal coverage. Finally, the open symbols (circles or
-triangles in both red and blue) show systems at an inclination of
-face-on, 0$^{\circ}$, and the filled symbols at edge on, 90$^{\circ}$.
-
-**CHECK AND REWRITE**
-
-Figure \ref{spread_cmd} shows, that increasing the accretion flux
-component moves the star blueward significantly in the optical
-colours, \textit{left panel}, and much less in the IR, \textit{right
-  panel} (compare the circles to triangles of the same colour and
-type, open or filled.). In addition, maximising the inner boundary
-component moves the system redward significantly in both CMDs,
-although to a greater extent in the IR, \textit{left panel} (compare
-different colour symbols of the same type). Finally, the inclination
-as shown in \cite{2004MNRAS.351..607W}, both reduces the magnitude and
-shifts the object in colour (compare open and filled symbols of same
-colour and type). Comparing the \textit{two panels} shows that the
-disc component has a much more significant affect in both CMDs,
-optical and IR, than the accretion component. Interestingly, the
-effect of a disc is still significant for the optical \textit{V, V-I}
-CMD. The accretion component has a much more significant effect in the
-optical \textit{V, V-I} CMD than the IR \textit{J, J-K}, and indeed is
-probably negligible in the latter. The effect of the two variables is
-then essentially additive in CMD space, weighted by their dominance in
-either CMD regime. This means a blue-shifted, accretion dominated
-object in a \textit{V, V-I} CMD will be less blue-shifted if the inner
-disc boundary component is also maximised. Whereas, for the \textit{J,
-  J-K} CMD, the inner boundary has a more significant effect and
-maximising the accretion component will only lessen the red-shifting
-from the maximised disc. It is perhaps surprising that for BDD systems
-both accretion and disc presence, due to the inner boundary, can
-scatter the star in an optical CMD.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/spread_cmd.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{CMDs showing the colours and magnitudes of a BD with
-   $M_*=$0.04$M_{\odot}$. For \textit{both panels} a BD with negligible
-   accretion flux, -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   10\% coverage without a disc is plotted as a black
-   cross. Triangles, in \textit{both panels}, are BDD systems with
-   negligible accretion flux, i.e. -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 10\% coverage. Circles,
-   in \textit{both panels}, show BDD systems with maximised accretion
-   flux, i.e. -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 1\%
-   coverage. The red symbols then have a maximised inner boundary
-   component with a period of 0.5 days and blue symbols a minimised
-   inner boundary component with a period of 5 days. Finally, for
-   \textit{both panels} inclinations of 0 \& 90$^{\circ}$ are shown
-   as open and filled symbols respectively. The \textit{left panel}
-   shows the $M_V, (V-I)_0$ CMD and \textit{right panel} the $M_J,
-   (J-K)_0$ CMD.
-   \label{spread_cmd}}
-\end{figure}
-\clearpage
-
-The TORUS code identifies and tags photons as they pass through the
-simulation in one of four ways: Stellar direct, stellar scattered and
-thermal direct or thermal scattered, as described in Section
-\ref{seds}. This allows us to plot the component flux distributions of
-the objects, with discs, shown in Figure \ref{spread_cmd} and examine
-their flux components. The convenient components discussed above,
-namely: stellar photosphere ($L_*$), accretion component ($L_{\rm acc}$),
-disc inner wall component ($L_{\rm wall}$) and outer disc component
-($L_{\rm disc}$), will have contributions from differently tagged
-photons. The stellar flux will comprise the accretion and intrinsic
-stellar photospheric components, with the direct flux reaching the
-observer without interaction with the disc. Photons scattering through
-the disc will be dominated by photons from the inner boundary for
-systems with a small inner disc radius. The inner boundary component
-and outer flared disc components will also include the direct and
-scattered thermal photons.
-
-Figures \ref{spread_spec_lowacc} and \ref{spread_spec_highacc} show
-the total and component fluxes for the BDD systems shown in Figure
-\ref{spread_cmd}. For \textit{all panels}, in both Figures, total flux
-is shown as the solid black line, with the stellar and thermal fluxes
-shown as blue and red lines respectively. Also, in both Figures, the
-direct and scattered components of the stellar and thermal flux are
-plotted as solid and dashed lines respectively. In addition for both
-Figures, the \textit{left panels} shows the minimised inner boundary
-component, with a period of 5 days, and the \textit{left panels} the
-maximised inner disc boundary component with a period of 0.5 days. The
-vertical lines show the approximate response limits in wavelength of
-the \textit{VI} and \textit{JK} filters as dashed and solid lines
-respectively. The \textit{lower panels} show systems at an edge-on
-inclination, of 90$^{\circ}$, and the \textit{upper panels} show
-face-on systems with an inclination of 0$^{\circ}$.  Figures
-\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} show the
-minimised and maximised accretion flux component systems respectively,
-i.e. -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 10\% areal
-coverage for Figure \ref{spread_spec_lowacc} and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 1\% areal coverage for
-Figure \ref{spread_spec_highacc}.
-
-Comparing the \textit{left \& right panels} of Figures
-\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} shows that as
-the period shortens the proportion of flux reprocessed by the disc,
-and inner wall, increases dramatically. This affects the flux and flux
-slopes in both the filter response regimes, however, it is much more
-significant in the IR regime. This effect causes the reddening seen in
-Figure \ref{spread_cmd}, and its increase in magnitude when comparing
-the \textit{left} to the \textit{right panel}, or optical to IR CMD.
-Comparing the \textit{upper \& lower panels} of Figures
-\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} shows the flux
-becoming dominated by the scattered components, which causes the
-reduction in magnitude and slight reddening of the systems as the
-inclination increases. Finally, comparing Figure
-\ref{spread_spec_lowacc} to Figure \ref{spread_spec_highacc} shows
-that as the accretion is maximised there is a significant increase in
-the flux and flux gradient, across the optical filter bandpasses, for
-the longer period. Whereas, there is a less significant change in the
-optical CMD. This is caused by a higher proportion of the stellar
-intrinsic and accretion flux being intercepted by the inner disc
-boundary.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_lowacc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{This Figure shows SEDs for the minimised accretion flux
-   component systems (-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   10\% coverage), from Figure \ref{spread_cmd}, which are shown as
-   triangles. The total flux is shown as a black line, with stellar
-   flux in blue and thermal flux in red, separated into direct (solid
-   lines) and scattered (dashed lines) components. The inner boundary
-   component is maximised on the \textit{left} and minimised on the
-   \textit{right panels}, with periods of 0.5 and 5 days
-   respectively. The vertical lines are the approximate filter
-   response limits for the \textit{VI}, dashed, and \textit{JK},
-   solid, bands. Two inclinations of 0 \& 90$^{\circ}$ are shown as
-   the \textit{upper} and \textit{lower panels}, respectively.
-   \ref{spread_cmd}.
-   \label{spread_spec_lowacc}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_lowacc_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_spec_lowacc} but in log space.
-   \label{spread_spec_lowacc_log}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_highacc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_spec_lowacc} but for a maximised
-   accretion flux component (-8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   1\% coverage), shown as circles in Figure \ref{spread_cmd}.
-   \label{spread_spec_highacc}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_highacc_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_spec_highacc} but in log space.
-   \label{spread_spec_highacc_log}}
-\end{figure*}
-
-\subsubsection{Accretion Dominance: $L_{\rm acc}$}
-\label{accn_dominance}
-
-Figure \ref{acc_dom} shows the affect of the increasing accretion
-blackbody flux (for increasing accretion rates) for a BD star,
-$M=$0.04$M_{\odot}$, at 1 Myr. The panels in this figure also show the
-flux from a naked system, with no treatment of the disc. This enables
-us to view the effect of increasing accretion rate on the photospheric
-flux in isolation. The accretion rates included in all panels are -6,
--7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black
-lines respectively). The \textit{lower panels} show the systems with a
-rotation period of 0.5 days and \textit{upper panels} for those with a
-rotation period of 5 days. Given our assumption that accretion occurs
-from the co-rotation radius, decreasing the rotational period moves
-this accretion radius closer to the star. As the accretion radius
-moves closer to the star the potential energy released by the accreted
-material is reduced. This effect can be seen when comparing the
-\textit{upper} and \textit{lower panels}, although the effect is
-marginal for all but the highest accretion rates. The \textit{left
-  panels} show accretion streams with an areal coverage of 1\% and the
-\textit{left panels} 10\%. As the areal coverage reduces the effective
-temperature of the accretion hot spot increases, resulting in an
-increase in accretion flux, and resulting shift to bluer wavelengths
-of the peak flux. This can be seen clearly by comparing the
-\textit{left} and \textit{right panels} of Figure
-\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
-shown is Figure \ref{acc_dom} is an insight into the accretion rate at
-which the accretion blackbody flux dominates over the photospheric
-flux. Figure \ref{acc_dom} shows that as the accretion rate raises
-above -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for systems with 1\%
-areal coverage, the accretion flux dominates the emergent SED at both
-periods. For the larger coverage the accretion flux begins to dominate
-between -7 to -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. Therefore
-for reasonable coverages (1-10\%) and rotational periods (0.5-5 days)
-the photospheric flux is effectively swamped by accretion flux for
-accretion rates log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-7$ , and for
-the most conservative case (1\% coverage with 5 day period) at
-accretion rates much lower than this
-(log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-$8). This suggests that
-accreting BD systems with accretion rates as low as -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ could be difficult to identify
-from SEDs as BD stars, and may well be classified as higher mass
-stars.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{This figure shows the photospheric flux against $\lambda$
-   ($\mu$m) of a Brown Dwarf with $M=$0.04$M_{\odot}$, at 1 Myr. No
-   disc is included, but blackbody fluxes from an accretion stream at
-   the rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-   are shown as blue, red and black lines respectively. The
-   \textit{lower panels} show accretion for a star rotating at 0.5
-   days, with the \textit{upper panels} showing that of 5 days. The
-   \textit{left panels} systems with an areal coverage of 1\% and the
-   \textit{right panels} has 10\%. CONSTRUCTED USING GRAPHPS**
-   \label{acc_dom}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{acc_dom} but in log space.
-   \label{acc_dom_log}}
-\end{figure*}
-
-Therefore, one can see that for higher accretion spot temperatures,
-flux shortward of the photospheric flux is markedly increased. This
-results, in general, in a brighter and bluer magnitude and colour for
-the combined system.
-
-\subsubsection{Disc effects: Flaring, $L_{\rm disc}$}
-\label{flaring}
-
-**SOME IMAGES TO PROVE POINT**
-**ADD MIPS DISCUSSION HERE AND SCALE HEIGHT STUFF**
-
-Scatter in optical CMDs is dominated by disc inclination (see Figures
-\ref{spread_opt_VVI}, \ref{spread_RI} and \ref{spread_VB}), and, even at
-longer wavelengths, scatter in IR CMDs is still correlated with
-inclination (see Figure \ref{spread_ir_JJK}). \cite{2004MNRAS.351..607W}
-have already shown that increased disc inclination lead to significant
-changes in the spectroscopic, and photometric properties of BDD
-systems. The scatter in optical and IR CMDs (in Section
-\ref{derive_primary}), for our model grid, appears strongly correlated
-with system inclination. This is a similar effect as found in
-\cite{2004MNRAS.351..607W}, where increases in the inclination angle
-quickly lead a significant proportion of the stellar flux being
-intercepted, and reprocessed, by the highly flared disc.
-
-Figure \ref{disc_eg} shows examples of our derived spectra for a BD of
-$M=$0.04$M_{\odot}$ (the middle of our mass range), at 1 Myr, with a
-rotation period of 0.5 days, and an accretion stream covering 1\% of
-the stellar surface accreting at a negligible rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{upper left panel}
-shows the SED for the naked BD system with the remaining panels
-showing the SEDs from the three modeled inclinations, after a TORUS
-simulation of a disc with $M_{disc}=$0.01$M_*$. The \textit{lower left,
-  upper right and lower right panels} show inclinations of 0, 60
-and 90$^{\circ}$ respectively. This figure plots, for the disc
-systems, the TORUS tagged component fluxes from the star (solid lines)
-and the disc or thermal flux (dashed lines), for both direct flux
-(black) and scattered flux (red). As the inclination of the system
-increases, the stellar direct flux can be seen to decrease, and the
-thermal and scattered components increase. This is simply caused by
-occultation of the star by the disc. The condition of vertical
-hydrostatic equilibrium applied during the TORUS simulation results in
-the disc flaring (see Section \ref{derive_primary}). This flaring is
-more pronounced for BD when compared to higher mass stars meaning a
-higher fraction of the stellar flux is intercepted by the disc at
-earlier inclinations. \cite{2004MNRAS.351..607W} have previously
-modeled this effect for a range of disc masses and found that this
-alone can shift the SED, and therefore colours and magnitudes, of
-inclined BDD systems to those indicative of higher mass CTTS.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_eg.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure of the SEDs of a BDD of $M=$0.04$M_{\odot}$, at 1 Myr,
-   with a disc mass of $M_{\rm disc}=$0.01$M_{\rm star}$. The BD is rotating
-   with a period of 0.5 days and is accreting through a stream, with
-   an areal coverage of 1\%, at a rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{upper left
-     panel} shows the photospheric spectrum of the naked star (naked stars have
-   spherically symmetric flux distributions, therefore the SED is not
-   a function of inclination), the total flux is shown as a bold
-   line. The \textit{lower left, upper right and lower right panels}
-   show the SEDs of the BDD systems at inclinations of 0,
-   60 and 90$^{\circ}$. For the BDD SEDs, the solid lines
-   are stellar flux and dashed are the thermal disc flux, with the
-   black denoting direct flux and red for scattered flux, i.e. black
-   solid line is direct stellar flux.
-   \label{disc_eg}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_eg_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{disc_eg} but in log space.
-   \label{disc_eg_log}}
-\end{figure*}
-
-The resulting density structure of the highly flared disc, for the
-system used to construct Figure \ref{disc_eg}, is shown in Figure
-\ref{flare_eg}. Figure \ref{flare_eg} shows that for a typical BDD
-system the resulting disc is highly flared and therefore, the opening
-angle for stellar radiation is much smaller. As discussed the flaring
-for BDD systems was found to be larger than CTTS systems by
-\cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
-degree of disc flaring depends on the disc temperature structure and
-the mass of the central star, with the disc scaleheight $h\propto
-\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{1973A&A....24..337S}. Recently,
-\cite{2009arXiv0901.4445E} suggest the inverse relation of flaring
-with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
-evidence from \cite{2006ApJ...644..364A}, where SEDs for 17 systems in
-the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat
-disc models. In general, \cite{2006ApJ...644..364A} find that lower
-mass objects achieve better fits with the flat disc models and higher
-mass objects with the flared discs.
-
-The results of \cite{2006ApJ...644..364A} show that above a mass of
-50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
-discs. Whilst at masses below 50$M_{\rm Jup}$ only one object is better
-fit by the flared disc model, with the remaining objects (10/17)
-better fit with flat models. Whether, this result is statistically
-significant enough to assert a $h\propto M_*$ is doubtful as the
-fitting process contains, presumably two fixed scaleheight
-distributions. Therefore, for our study we continue to assume that our
-flared BDD systems will have larger characteristic scaleheights than
-typical CTTS systems.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/28_rho.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{A Figure of the density for the most flared
-   disc. $M_*=$0.01$M_{\odot}$, $\tau=$5 days, $\dot{M}=$-6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, areal coverage of 1\% at 1
-   Myr **RUN NUMBER028**.
-   \label{flare_eg}}
-   \end{figure}
-
-\subsubsection{Disc effects: Inner wall, $L_{\rm wall}$}
-\label{inner_wall}
-
-Therefore, as the scattering in optical CMDs is dominated by system
-inclination, due to disc flaring, what dominates scattering in the IR?
-Clearly, system inclination still has a significant correlation with
-the scatter CMD position. However, as shown in Section
-\ref{derive_primary} IR CMD scatter appears strongly correlated with
-rotational period. A similar correlation between scatter and rotation
-period is evident for IR and IRAC (and perhaps MIPS) CoCoDs (although
-the trend is reversed), as shown in Section \ref{derive_frac}. The
-cause of this scatter is the relative flux contribution of the inner
-disc boundary, as discussed in Section \ref{scatter_causes}. It is
-also clear in Section \ref{derive_primary} that the longer wavelength
-photometric colours are better disc discriminators. Furthermore,
-interestingly, the $\alpha$ value, in our case the slope of the SED
-between 3.6 and 8.0$\mu$m \citep[chosen to
-match][]{2009arXiv0901.4120D}, is a very effective disc disriminator.
-
-The position of a given BDD system, in an IR CoCoD or CMD, is
-dominated by rotation period, and it is clear that this is due to the
-radial position of the inner wall (See discussion in Section
-\ref{scatter_causes}. As the rotation period decreases the inner disc
-co-rotation radius decreases, meaning a closer, hotter, inner disc
-wall. However, we have also included a treatment of dust sublimation
-which, during the radiative transfer modeling, will change the radial
-position for the higher temperature inner walls \citep[where
-$T_{\rm wall}$ exceeds $\approx$1400K][]{1994ApJ...421..615P}.
-
-\subsubsection{Disc structure and the inner edge}
-\label{inner_edge_position}
-**SHOULD BE PRINTED FROM TORUS**pooooo
-\textbf{Initial inner wall radius}
-
-Given the strong dependence of IR flux on the inner wall temperature,
-and therefore radial position, it is important to examine the final
-structure of the inner wall after the radiative transfer simulation.
-
-Table \ref{inner_edge} list the initial inner edge radius (from the
-central star), set at the co-rotation radius, in stellar radii for each
-mass increment. It is clear that the inner edge position is a strong
-function of rotation period and a much weaker function of stellar
-mass. This is obvious from our calculation of the co-rotation radius
-for which we use equation \ref{inner_eq}. Equation \ref{inner_eq}
-clearly shows the weak dependence on stellar mass ($R_{\rm inner}\propto
-M_*$) and strong dependence on rotation period ($R_{\rm inner}\propto \tau
-^2$). Table \ref{inner_edge_au} shows the same data as Table
-\ref{inner_edge} but converted using the stellar radius into AU, which
-reveals a magnetic truncation radius of between 0.0026$-$0.026 AU for
-1 Myr BDD systems.
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius ($R_*$)}\\
-0.01&2.18&10.16&3.52&16.36\\
-0.02&2.42&11.24&3.33&15.47\\
-0.04&1.90&8.86&3.26&15.15\\
-0.06&1.57&7.32&3.13&14.53\\
-0.08&1.37&6.39&2.96&13.74\\
-\end{tabular}
-\caption{Table showing the initial inner edge radius (in $R_*$) for all models.
-  \label{inner_edge}}
-\end{table}
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius (AU)}\\
-0.01&0.00264&0.0123&0.00265&0.0123\\
-0.02&0.00333&0.0155&0.00375&0.0174\\
-0.04&0.00403&0.0188&0.00411&0.0191\\
-0.06&0.00479&0.0195&0.00395&0.0183\\
-0.08&0.00527&0.0246&0.00501&0.0233\\
-\end{tabular}
-\caption{Table showing the initial inner edge radius (in $R_*$) for all models.
- \label{inner_edge_au}}
-\end{table}
-
-\textbf{Dust sublimation radius}
-
-During the simulations of radiative transfer, implementation of dust
-sublimation, may result in changes in inner radius. For systems where
-the temperature of dust at the inner disc boundary exceeds
-$\approx$1400K \citep{1994ApJ...421..615P}, the inner disc will be
-destroyed and the inner radius increased. Table \ref{inner_edge_dust}
-shows the resulting radii for our model grid in stellar radii with the
-corresponding values in AU presented in Table
-\ref{inner_edge_dust_au}.**THIS TABLE MUST BE CHANGED TO INCLUDE
-DIFFERENT FLUXES**
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius ($R_*$)}\\
-0.01&&&&\\
-0.02&&&&\\
-0.04&&&&\\
-0.06&&&&\\
-0.08&&&&\\
-\end{tabular}
-\caption{Table showing the final inner edge radius (in $R_*$) for all models.
- \label{inner_edge_dust}}
-\end{table}
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius (AU)}\\
-0.01&&&&\\
-0.02&&&&\\
-0.04&&&&\\
-0.06&&&&\\
-0.08&&&&\\
-\end{tabular}
-\caption{Table showing the final inner edge radius (in $R_*$) for all models.
- \label{inner_edge_dust_au}}
-\end{table}
-
-\textbf{Compare $R_{\rm co}$ to $R_{\rm dust}$}
-
-**NEEDS TO BE DONE AFTER NEW DATA**
-
-Comparing Table \ref{inner_edge_dust_au} to Table \ref{inner_edge_au}
-shows that the inner disc radius is changed little from the initial
-co-rotation radius (QUOTE MAX CHANGE**) due to dust sublimation
-effects. The resulting inner radii are still, broadly, proportional to
-the rotation period. Therefore, for subsequent analysis, we assume an
-inner radius to rotation period relationship.
-
-Our final inner radii range from ** to ** AU. **COMPARE TO
-OTHER RESULTS?**
-
-\textbf{Dust sublimation regions}
-
-**AGAIN NEEDS TO BE DONE AFTER NEW DATA**
-
-In some cases however the inner disc radius has been changed by the
-implementation of dust sublimation. For these systems the resulting
-shape of the inner disc boundary has also changed. Evidence that real
-inner disc boundaries (for CTTS) are not vertical walls comes from a
-lack of dependence of the derived IR excess on system inclination
-\citep{2007ApJ...661..374T}. As discussed in Section \ref{dust_edge}
-the disc inner hole can be created by several mechanisms, however, for
-this study we have only included a treatment of magnetic truncation
-(initially) and subsequent dust sublimation. The effects of dust
-sublimation have been shown to produce curved inner walls due to the
-temperature and density dependence of the dust sublimation temperature
-\citep{2005A&A...438..899I}. The curved boundary in this case is
-concave, as density increases towards the midplane of the disc, the
-dust sublimation temperature increases, meaning the destruction radius
-moves closer to the star. A curved inner boundary is also found to
-result from dust sublimation in \cite{2007ApJ...661..374T}. In
-\cite{2007ApJ...661..374T} two populations of dust grains where
-included with different scaleheight distributions. This is essentially
-a simple model of grain growth and subsequent midplane
-settling. \cite{2007ApJ...661..374T}, found a convex inner disc
-boundary, this is due to the larger grains cooling more
-efficiently. These larger grains dominate the dust towards smaller
-vertical distances from the midplane, and therefore the increased
-cooling means that the dust sublimation temperature is reached at
-closer radii.
-
-For our dust distribution and dust sublimation implementation we
-produce a curved inner boundary, as can be seen in
-Figure \ref{curve_inner}. This is due to the density dependent dust
-sublimation temperature (as discussed in Section \ref{dust_edge}).
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/238_tau.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{A Figure of the opacity (scaled $1<\tau <0$) for the most
-   extreme case of a dust sublimated inner
-   boundary. $M_*=$0.08$M_{\odot}$, $\tau=$0.5 days, $\dot{M}=$-6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, areal coverage of 1\% at 1
-   Myr **RUN NUMBER238**.
-   \label{curve_inner}}
-\end{figure}
-
-**CONCLUDE**
-
-\subsubsection{Disc effects: Inner wall to Outer edge balance,
-  $L_{\rm wall}$ to $L_{\rm disc}$}
-\label{disc_period_relation}
-
-\textbf{Why do inner disc radius changes cause photometric scatter?}
-
-**ADD SOME IMAGES**
-**PERHAPS ADD A FIGURE HER J-K, AND IRAC COLOUR VERSUS FINAL RADIUS**
-
-Physically, as the inner disc radius changes the flux intercepted by
-the inner wall is changed. At first glance it may appear more
-instructive to plot the \textit{bottom left panel} as a function of
-inner disc radius, to strengthen the correlation and remove the
-scatter within the Figure. However, intrinsic scatter will also be
-included due to inclination and accretion rate, the latter perhaps
-being less intuitive. Even though accretion flux is generally blueward
-of these passbands, interception and subsequent reprocessing of this
-additional flux for higher accretion rates increase scatter in a
-CoCoDs of this sort. Therefore, plotting the simulated photometry as a
-function of inner disc radius does not reduce the
-scatter. Furthermore, separating the populations using the rotational
-period is perhaps more useful for observational studies as this is
-often the most ubiquitous and precise data available. It is important
-at this stage to re-iterate that magnetic truncation and dust
-sublimation as we have assumed occur, is not the only method of
-producing an inner hole, for instance planet formation or
-photoevaporation can create significant inner holes, which are not
-necessarily correlated, in size, with rotation period.
-
-\textbf{SED change caused by inner radius}
-
-Figures \ref{rot_effect}, \ref{rot_effect_log}, \ref{rot_comp} and
-\ref{rot_comp_-7} show the effects of the changes in inner boundary
-radius due to rotational period changes on a BD, $M_*=$0.04$M_{\odot}$,
-at 1 Myr. For all these figures the \textit{left panel} shows the SEDs
-for a period of 0.5 days and the \textit{right panel} shows the SED
-for a period of 5 days. We have chosen to plot the SEDs as a function
-of rotational period for two reason. Firstly, rotational period will
-be the most easily, and precisely, observed variable. Secondly, the
-inner disc radius varies most strongly as a function of the rotational
-period (see Equation \ref{inner_eq}).The final inner radii for the
-systems shown in the \textit{left} and \textit{right panels} are **
-and ** AU, respectively (see Table \ref{inner_edge_dust_au}).
-
-Figures \ref{rot_effect} and \ref{rot_effect_log} show the total flux
-(in normal and log space respectively) for both canonical accretion
-rates (-8 \& -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, bold and
-dashed lines respectively). The SEDs are for systems with the smallest
-areal coverage (1\%) and therefore highest accretion flux, for each of
-the three inclinations (0, 60 and 90$^{\circ}$, black, red and
-blue respectively).
-
-Figures \ref{rot_comp} and \ref{rot_comp_-7} show the component flux
-for two inclinations, $0$ and $60^{\circ}$, \textit{upper} and
-\textit{lower panels} respectively. The component flux is separated
-into total (black lines), stellar (blue lines) and thermal or disc
-(red lines) flux. The stellar and thermal flux is then separated into
-direct (bold lines) or scattered (dashed lines) flux. The vertical
-bold lines on these figures show the approximate filter ranges for the
-IRAC channels ([3.6], [4.5], [5.8] \& [8.0]), with the vertical dashed
-lines showing the limits of the JHK filters of the CIT system. Figure
-\ref{rot_comp} shows the SEDs for a system with an accretion rate of
--8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and Figure
-\ref{rot_comp_-7} an accretion rate of -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
-
-Figures \ref{rot_effect} and \ref{rot_effect_log} show that for
-systems with a typical accretion rate and shorter rotational periods,
-as the inclination increases the flux and slope of the SED decreases
-dramatically, for wavelengths shorter than $\approx$2$\mu$m. In this
-case the inner boundary is close to the central star. Conversely, the
-flux, and slope of the SED, at wavelengths longer than
-$\approx$2$\mu$m decreases less swiftly with increasing inclination.
-Effectively shorter period systems show a large change in flux and
-flux ratios in the $<$2$\mu$m range and a more constant flux or flux
-ratio in the $>$2$\mu$m range. This trend is clearly reversed for
-longer period objects. The objects, where the disc inner edge is
-farther from the star, show a large change in flux and flux ratio, as
-a function of inclination, for wavelengths $>$2$\mu$m and a smaller
-change for wavelengths $<$2$\mu$m. In addition, the total SED is
-dominated by the photosphere at shorter wavelengths.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/rot_effect.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing flux against wavelength for a
-   $M_*=$0.04$M_{\odot}$ BD at 1 Myr, for two accretion rates -7
-   (dashed line) and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (bold
-   line) for the three modeled inclinations, 0 (black), 60 (red) and
-   90$^{\circ}$ (blue). The \textit{left panel} shows the SEDs for the
-   shorter rotation period system, with a closer disc inner
-   boundary. The \textit{right panel} shows the longer period system
-   with farther disc inner boundary.**USE GRAPHPS**
-   \label{rot_effect}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/rot_effect_log.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{A Figure \ref{rot_effect} but in log space.
-   \label{rot_effect_log}}
-\end{figure}
-
-The wavelength dependent variations in flux, and SED slope, with
-inclination are particularly important when considering photometric or
-broadband magnitudes and colours. Figures \ref{rot_comp} and
-\ref{rot_comp_-7} show that the variations evident in Figures
-\ref{rot_effect} and \ref{rot_effect_log} have serious implications
-over the filter responses of the CIT \textit{JHK} and IRAC
-systems. Essentially, Figures \ref{rot_comp} and \ref{rot_comp_-7}
-show that for increasing inclinations discs have a much more apparent
-effect on the SED over the IRAC range for longer period systems, and
-in the CIT \textit{JHK} range for shorter period systems. Thereby
-explaining the opposite correlations in disc scatter and rotation
-period, found for IR and IRAC colours in Section \ref{derive_frac}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{This Figure shows flux against wavelength for a
-   $M_*=$0.04$M_{\odot}$ BD at 1 Myr, with a disc ($M_{\rm disc}=$0.01$M_*$)
-   and associated accretion rate of -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ over a hot spot coverage of
-   1\%. The \textit{left panels} show systems with a stellar rotation
-   period of 0.5 days and the \textit{right panel} those with a
-   stellar rotation period of 5 days. The \textit{upper panels} show
-   systems observed at an inclination of $0^{\circ}$ and the
-   \textit{lower panel} those observed at an inclination of
-   $60^{\circ}$. For \textit{all panels} the total SED is shown
-   (solid, black line), alongside the components flux from the star
-   (blue) and thermal or disc (red) flux. These components are also
-   separated into direct flux (solid lines) or scattered flux (dashed
-   lines) from the star or disc. The extents of the filter responses
-   for the IRAC (including channels [3.6], [4.5], [5.8] \&
-   [8.0]) (solid vertical line) and the CIT (\textit{JHK})
-   (dashed vertical lines) bands are shown. 
-   \label{rot_comp}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{rot_comp} but in log space.
-   \label{rot_comp_log}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp_-7.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As above but for higher canonical accretion rate -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
-   \label{rot_comp_-7}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp_-7_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{rot_comp_-7} but in log space.
-   \label{rot_comp_-7_log}}
-\end{figure*}
-
-**NEED TO GET VALUES ETC FOR THIS SECTION AFTER NEW DATA**
-
-As the temperature of the surface of the disc generally decrease
-towards larger radii the longer the wavelength of the flux the further
-from the central object its origin will be.  Effectively, more flux is
-being intercepted by the disc inner wall for the shorter period
-systems and consequently less flux is impinging on the outer flared
-surface of this disc, creating larger changes as a function of
-inclination for shorter wavelengths. In the case of the longer periods
-more flux is escaping to the outer flared edge of the disc and greater
-change is seen as a function of inclination angle at longer
-wavelengths. Figures \ref{far_rho}, \ref{far_rho_bw}, \ref{close_rho},
-and \ref{close_rho_bw}, show the density structure for the inner
-regions of the disc ($R<**AU$) as a function of radius and scaleheight
-(10$^{10}$ cms). The inner edge location can be seen to move further
-out when moving from short period systems to long period systems, in
-Figures \ref{far_rho}/\ref{far_rho_bw} and
-\ref{close_rho}/\ref{close_rho_bw}, from ** to **AU in fact. Dust
-sublimation effects have shifted the shorter period inner wall to a
-slightly larger radius (see Section \ref{inner_edge_position}), but
-this is ,however, still closer than longer period counterpart. The
-final temperature distribution in the disc inner regions ($R<**AU$)
-can be seen in Figures \ref{far_temp}, \ref{far_temp_bw},
-\ref{close_temp} and \ref{close_temp_bw}. As can be seen by comparing
-Figure \ref{far_temp}/\ref{far_temp_bw} to Figure
-\ref{close_temp}/\ref{close_temp_bw}, the inner wall reaches
-significantly higher temperatures for the shorter period systems. For
-the closer systems, the curved inner edge is due to some of the disc
-regions exceeding the dust sublimation temperature, the remaining wall
-reaches temperatures of **K. Whereas, for the longer period object the
-inner wall reaches a temperature of **K. This produces the correlation
-of IR excess caused by the inner wall with rotation period seen for IR
-CoCoDs in Section \ref{derive_frac}. In addition, comparing the
-temperature structure at a farther disc radius, indicative of fluxes
-within the IRAC passbands, one finds that the disc temperature is
-larger for the longer period systems, $**$ compared to $**$K at $**$
-AU. This causes the resulting correlation, where larger IRAC excesses
-are found for longer period BDD systems.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_rho0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{CHANGE THESE AXES IN 10$^{10}$ cms*****
-   \label{far_rho}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_rho_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{far_rho_bw}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_rho0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_rho}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_rho_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_rho_bw}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_temp0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{far_temp}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_temp_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{far_temp_bw}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_temp0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_temp}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_temp_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_temp_bw}}
-\end{figure}
-
-\textbf{Short conclusion, alpha}
-
-As can be seen the effects of a circumstellar disc on the observed SED
-are most constant for longer wavelengths. Wavelengths generally longer
-than 3$\mu$m are little effected by inclination, accretion rate,
-stellar mass etc. This explains, result that BDD systems are well
-selected by IRAC photometry and the $\alpha$ value. Essentially, as
-the wavelength limits used to construct Figure \ref{alpha_zoom} are
-3.6 and 8.0$\mu$m, it follows that the separation between disc-less
-and BDD systems should be at least similar in clarity to the IRAC
-CoCoDs.
 
@@
 \end{itemize}
-
-\section[]{ACKNOWLEDGMENTS}
-The computations reported here were performed using the
-University of Exeter Supercomputer.
-
-\bibliographystyle{mn2e}
-\bibliography{references}
-\appendix
-
-\section{Website}
-\label{website}
-
-**NEEDS LOTS OF WORK**
-
-As stated throughout this paper the data presented are available from
-a web page
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
-  disc}. In this Appendix we briefly discuss the data included, and
-the different ways of accessing or visualising these data on the
-website.
-
-\subsection{Available Data}
-\label{web_data}
-
-The magnitudes and colours presented in this paper are avaiable both
-as individual magnitudes and as isochrones or mass tracks. Photometric
-magnitudes have also been derived for several other systems and are
-available online.
-
-\textit{Full list of filters}
-
-These are Johnson, Cousins \textit{UBVRI(JHK)}
-\citep{1966ARA&A...4..193J,2005ARA&A..43..293B}, \textit{Tycho} $V_t$
-and $B_t$ \citep{2000PASP..112..961B}, Bessell \textit{UBVRIJHKL}
-\citep{1988PASP..100.1134B,1998A&A...333..231B}, SDSS \textit{UGRIZ}
-\citep{1996AJ....111.1748F}, 2MASS $JHK_s$
-\citep{2003AJ....126.1090C,2006AJ....131.1163S}, MKO \textit{JHK}
-\citep{2002PASP..114..169S,2002PASP..114..180T}, UKIRT \textit{ZYJHK}
-\citep{2001MNRAS.325..563H}, IRAS 12, 25, 60 and 100 $\mu$m
-\citep{1984ApJ...278L...1N} and SCUBA \textit{450WB} and
-\textit{850WB} \citep{1999MNRAS.303..659H}. For further information on
-these magnitudes, such as the filter responses used and the adopted
-zeropoints please refer to the website.
-
-\textit{Monochromatic fluxes}
-
-In addition to the magnitudes derived for each of these bands
-monochromatic fluxes have also been derived for all bands listed
-above. These have been derived following closely the methods of
-\cite{2006ApJS..167..256R}, extended to further passbands. For details
-of the assumed SED shape, central wavelengths and bandpasses adopted
-please refer to the website.
-
-**PERHAPS INCLUDE FORMULA FOR DERIVATION**
-
-\subsection{Navigation}
-\label{navigation}
-
-The main page contains links to download the entire dataset in several
-formats alonside files describing the format.
-
-\begin{enumerate}
-\item All SEDs ($\AA$ and ergs s$^{-1}$ cm$^{-2} \AA ^{-1}$) 
-\item All SEDs ($\mu$m and mJy)
-\item All Photometric Magnitudes for all BDD systems.
-\item All Photometric Magnitudes for all Naked systems.
-\item All Monochromatic Fluxes for all Naked systems ($\mu$m and ergs
-  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
-\item All Monochromatic Fluxes for all Naked systems ($\mu$m and mJy)
-\item All Monochromatic Fluxes for all BDD systems ($\mu$m and ergs
-  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
-\item All Monochromatic Fluxes for all BDD systems ($\mu$m and mJy)
-\end{enumerate}
-
-Also included is a link to the calibration information listing all the
-filtersponse sources, adopted zero points, central wavelengths,
-bandwidths and assumed SED shapes (for monochromatic flux
-derivation). A brief scientific overview is also available explaining,
-in general terms, the dataset and model.
-
-\subsection{Browsing Tools}
-\label{tools}
-
-For users who wish to investigate the dataset in a more specific or
-interactive fashion two browsing tools are included.
-
-The isochrones, mass tracks and individual stars magnitudes and
-colours generated and presented in the work can be queried using the
-``Isochrone and Mass Track Tool''. This allows the user to select the
-parameters of the model required and retrieve the specific data.
-
-Secondly, an iteractive tool is included allowing a user to select a
-given set of parameters and download the ``SEDs, monochromatic fluxes
-or magnitudes''. In addition this tool plots the SEDs for the Naked
-system or the three inclinations, in the case of BDD systems and
-allows users to select filters sets, whose monochromatic flux values
-will be overlaid on the displayed SEDs.
-
-\label{lastpage}
-\end{document}

### 2010-05-11 BD_disc/paper.tex
updates - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2265 25464f21-6099-402c-b30a-640f1d40d38b

--- 2010-04-19 BD_disc/old.tex
@@
 \newcommand\araa {ARA\&A}
+\newcommand\logmdot {$\log \dot{M}$}
 \usepackage{multirow}
@@
 \begin{abstract}
-SORT OUT REFERENCE TO THE FILTER RESPONSES IN THE SEDS FIGURES say
-discussed later
-more about stellar photosphere overlapping with disc
-
-FINESSE FIGURE SIZES
-
-CHANGE ALL WORDING FOR NEW FIGURES** CHANGED AGE TO 1 MYR FOR SUB
-FIGURES AND NEED TO ACKNOWLEDGE THROUGHT
-
-CHOSE 10 MYRS AS PRE-MS CONTRACTION AGES ARE PROBABLY A  FACTOR OF 2 WRONG
-
-ADD FILTERS TO OTHER SEDS FIGURES
-
-Note about fitting objects in the next paper.
-
+To Do
+\begin{enumerate}
+\item{Read new papers and put in any relevant stuff.}
+\item{Sort structure paragraph at end of intro.}
+\item{Sort out headings of sections.}
+\item{Sort clearpage problem, perhaps change to includegraphics.}
+\item{Sort out the webpage stuff.}
+\end{enumerate}
 \end{abstract}
@@
 formation. Several of the key physical parameters and mechanisms
-remain unclear within this mass regime
-\citep{2007ApJ...664.1154S}. Uncertainty remains over fundamental
-issues such as the initial formation mechanisms, the subsequent
-evolution and dominance of a star-disc interaction through to the
-possible dependence of planet formation mechanisms on stellar mass
-\citep[for a review of BD formation mechanisms see
-][]{2006astro.ph..2367W}.
+remain unclear within this mass regime \citep{2007ApJ...664.1154S}.
+Uncertainty remains over fundamental issues such as the initial
+formation mechanisms, the subsequent evolution and dominance of a
+star-disc interaction through to the possible dependence of planet
+formation mechanisms on stellar mass \citep[for a review of BD
+formation mechanisms see][]{2006astro.ph..2367W}.
 
@@
 CTTS locus well. However the work of \cite{1997AJ....114..288M},
-discussed in more detail later, only included parameterised `flat'
-discs. Once disc flaring is considerd it is clear from previous work
+discussed in more detail later, only included parametrised `flat'
+discs. Once disc flaring is considered it is clear from previous work
 that misidentification of high mass stars with circumstellar discs is
@@
 general SED shape for disc candidates, with higher mass stars showing
-a featureless continuum at $\lambda>$8.0$\mu$m with lower mass stars
-generally showing strong silicate and PAH features at 10 and 2$\mu$m,
-indicative of mass dependent disc evolution. Whether in fact the disc
-lifetimes and therefore rate or type of involved physical processes
-are a function of stellar mass could provide another piece of evidence
+a featureless continuum at $\lambda>8.0$\,$\mu$m and lower mass stars
+generally showing strong silicate and PAH features at 10 and 2\,$\mu$m,
+indicative of mass dependent disc evolution. If the disc lifetimes and
+therefore rate or type of involved physical processes are a function
+of stellar mass. This could provide another piece of evidence
 separating the previously assumed continuous (in mass) evolutionary
-principles of stars into a dichotomy separated by the hydrogen-burning
-mass limit, and alter the probability of forming planets in the BD
-regime.
+principles of stars. Resulting in a dichotomy separated by the
+hydrogen-burning mass limit. This would also lead to a change in the
+probability of forming planets in the BD regime, compared to CTTS.
 
@@
 in \cite{2009arXiv0901.4120D}, the inner hole can be created via dust
-grain growth and midplane settling, giant planet formation or
+grain growth and mid plane settling, giant planet formation or
 photoevaporation by ultraviolet (UV) and far-UV (FUV) flux
@@
 Section \ref{physics}), the stellar and thermal components are not
-separable at wavelengths shorter than 6$\mu$m. In the case of
+separable at wavelengths shorter than 6\,$\mu$m. In the case of
 \cite{2009arXiv0901.4445E}, the inner disc hole was created by
@@
 detection was characterised by a tenuous photoevaporation wind and
-little or no accretion, and a disc detection at 24$\mu$m indicative of
+little or no accretion, and a disc detection at 24\,$\mu$m indicative of
 a large inner hole. Additionally, for BDs, \cite{2009arXiv0902.0638M}
@@
 flux. This increase in flux will lead to an increase in temperature of
-the disc inner and outer regions, and more particulary a change in the
+the disc inner and outer regions, and more particularly a change in the
 dust sublimation effects at the inner edge.
@@
 widely accepted, with strong evidence found from the excessive widths
-of H$\alpha$ ($>$10$\AA$) emission lines, over that caused by
+of H$\alpha$ ($>$10\,\AA) emission lines, over that caused by
 chromospheric activity and stellar rotation
 \citep{1998ASPC..154.1793W}, caused by the high velocities of
-infalling matter, ~100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.
+infalling matter, $~$100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.
 
@@
 \citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
-with accretion rates in the range $\dot{M_{\rm
-    acc}}=$10$^{-6}$-10$^{-12} M_{\odot}yr^{-1}$, and typical
-accretion rates in the range log$(\frac{\dot{M}}{M_{\odot}}
-yr^{-1})=$-10 to -8 with only FU Orionis type objects accreting at
+with accretion rates in the range $\dot{M}_{\rm
+    acc}=$10$^{-6}$--10$^{-12} M_{\odot}yr^{-1}$, and typical
+accretion rates in the range \logmdot = log$(\frac{\dot{M}}{M_{\odot}}
+yr^{-1})=-10$ to $-8$ with only FU Orionis type objects accreting at
 rates higher than this. The mechanism producing accretion rates as
@@
 rates of $\dot{M}\approx$ 10$^{-13}M_{\odot}yr^{-1}$ have been derived
-for BDs using flux blueward of 4000$\AA$ where the photospheric flux
+for BDs using flux blueward of 4000\,\AA where the photospheric flux
 becomes negligible \citep{2009arXiv0901.3684H}.
@@
 truncated, and therefore locked to the star. This magnetic truncation
-would lead to an inner wall (and inner hole) of the accretion
-disc. Evidence for an inner disc wall has been found from near-IR
-excesses from the inner rims of Herbig Ae stars, with emission peaking
-at 2-3$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
+would lead to an inner wall (and inner hole) of the accretion disc.
+Evidence for an inner disc wall has been found from near-IR excesses
+from the inner rims of Herbig Ae stars, with emission peaking at
+2--3\,$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
 position of this wall is affected by several factors, discussed
@@
 accretion and the radius to the inner disc on the infrared colours of
-CTTS, useing a prescribed range of inner disc
-radii. \cite{1997AJ....114..288M} find that the scatter in infrared
-colours for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
+CTTS, using a prescribed range of inner disc radii.
+\cite{1997AJ....114..288M} find that the scatter in infrared colours
+for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
 $\dot{M_{\rm acc}}=$10$^{-9}$to 10$^{-5} M_{\odot}yr^{-1}$, matches
@@
 wavelength regime. As this study does not include the effects of
-vertical hydrostatic equilibirum or even the study of flared discs one
+vertical hydrostatic equilibrium or even the study of flared discs one
 would expect, perhaps, a more complex relationship between the inner
@@
 studies aiming to provide evidence of disc locking by comparing disc
-indicators with rotation rates may include unforseen biases. As the
+indicators with rotation rates may include unforeseen biases. As the
 rotation rate will effect the co-rotation radius and therefore
@@
 heavily affected by disc and/or accretion presence. Formation
-mechanisms, IMFs, disc dissipation timescales, accretion rate--stellar
-mass relationships and studies of disc-locking mechanisms using
-correlations of rotation rates with infrared excesses, all require
-derivations of either masses, ages or disc fractions (or a
-combination), supplemented by other parameters. The consequences of
-the disc structure for BD accretion discs, particularly vertical
-structure, given the assumption of vertical hydrostatic equilibrium,
-have already been discussed for a limited range of BD parameters in
-\cite{2004MNRAS.351..607W}. Indeed \cite{2004MNRAS.351..607W} have
-shown that BDD systems seen at higher inclinations can be confused
-with CTTS systems, having similar colours and
-magnitudes. Additionally, a benchmark model grid of spectra for star
-and disc systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$
-has previously been published in \cite{2006ApJS..167..256R}.
+mechanisms, planet formation, IMFs, disc dissipation timescales,
+accretion rate--stellar mass relationships and studies of disc-locking
+mechanisms using correlations of rotation rates with infrared
+excesses, all require derivations of either masses, ages or disc
+fractions (or a combination), supplemented by other parameters. The
+consequences of the disc structure for BD accretion discs,
+particularly vertical structure, given the assumption of vertical
+hydrostatic equilibrium, have already been discussed for a limited
+range of BD parameters in \cite{2004MNRAS.351..607W}. Indeed
+\cite{2004MNRAS.351..607W} have shown that BDD systems seen at higher
+inclinations can be confused with CTTS systems, having similar colours
+and magnitudes. A benchmark model grid of spectra for star and disc
+systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$ has
+previously been published in \cite{2006ApJS..167..256R}.
 
@@
 online fitting tool.
+
+**THIS PARAGRAPH IS CURRENTLY WRONG, WILL REQRITE AT THE END**
 
@@
 to stellar mass and rotational period to disc presence. Finally,
-conclusions are drawn, with a summary, in Section
-\ref{conclusions}.**REWRITE AT END**A CASE STUDY IS THEN INCLUDED AS
-SECTION \ref{object}.**
+conclusions are drawn, with a summary, in Section \ref{conclusions}..
 
@@
 interpolate atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2}
-\AA^{-1}$) from 1200 to 2$\times$ 10$^7$ $\AA$ (or 0.12 to 2000
+{\rm \AA}^{-1}$) from 1200 to 2$\times$ 10$^7$ \AA (or 0.12 to 2000\,
 $\mu$m). These spectra were then smoothed using 200 logarithmically
@@
 approximate $T_{\rm eff}$ (effective temperature) range of $\approx
-$3000K$<T_{\rm eff}<$1600K the AMES-Dusty atmospheres are most
-applicable (2700K$>T_{\rm eff}>$1700K). We did try including dynamic
+$3000\,K$<T_{\rm eff}<$1600\,K the AMES-Dusty atmospheres are most
+applicable (2700\,K$>T_{\rm eff}>$1700\,K). We did try including dynamic
 application of atmospheres based on the derived $T_{\rm eff}$,
-i.e. using AMES-Cond for $T_{\rm eff}<$1700K, however this resulted in
+i.e. using AMES-Cond for $T_{\rm eff}<$1700\,K, however this resulted in
 large discontinuities between the model atmospheres and resulting
@@
 \begin{equation}
-{L_{\rm acc}=\frac{GM_*\dot{M}}{R_*}\times (1-\frac{R_*}{R_{\rm inner}})},
+{L_{\rm acc}=\frac{GM_*\dot{M}}{R_*} \left( 1-\frac{R_*}{R_{\rm inner}}\right)},
 \label{Lacc}
@@
 \begin{equation}
-{T_{\rm acc}=(\frac{L_{\rm acc}}{4\pi R^2_{*} \sigma \times A})^{\frac{1}{4}}}.
+{T_{\rm acc}=\left(\frac{L_{\rm acc}}{4\pi R^2_{*} \sigma A}\right)^{\frac{1}{4}}}.
 \label{Tacc}
@@
 \begin{equation}
-{R_{\rm inner}=({GM_*\tau^2\over{4\pi ^2}})^{1\over{3}}},
+{R_{\rm inner}=\left({GM_*\tau^2\over{4\pi ^2}}\right)^{1\over{3}}},
 \label{inner_eq}
 \end{equation}
- where $\tau$ is the stellar rotation period and $R_{\rm inner}$ is
-the inner radius. This is effectively adopting a disc-locking
-mechanism (without associated angular momentum loss), as for
-disc-locked stars, $R_{\rm mag}\approx R_{\rm co}$,
+where $\tau$ is the stellar rotation period and $R_{\rm inner}$ is the
+inner radius. This is effectively adopting a disc-locking mechanism
+(without associated angular momentum loss), as for disc-locked stars,
+$R_{\rm mag}\approx R_{\rm co}$,
 \citep{1991ApJ...370L..39K,1994ApJ...429..781S}. Therefore, for our
@@
 or settling. For BDD systems where a disc is modeled a treatment of
-dust sublimation due to photoionising UV and FUV flux is included
-(discussed in Section \ref{dust_edge}). However, the effects of
-binarity or Giant planet formation are neglected. Further to the
-stellar mass and period required prior to calculation of the inner
-disc radius, we require a disc mass (in stellar masses).
+dust sublimation is included (discussed in Section \ref{dust_edge}).
+However, the effects of binarity or Giant planet formation are
+neglected. Further to the stellar mass and period required prior to
+calculation of the inner disc radius, we require a disc mass (in
+stellar masses).
 
@@
 `naked' photospheres (plus accretion) are diluted by the factor
-$(R_*/Distance)^2$ to a distance of 10pc. The `negligibly' accreting,
+$(R_*/{\rm distance})^2$ to a distance of 10pc. The `negligibly' accreting,
 `naked' stars can be used to produce absolute magnitude (and intrinsic
@@
 values found in \cite{2002ApJ...564..887W} were $q=$3.0, $p=$0.6 with
-$a_{\rm c}=$50 $\mu$m, also with an associated maximum and minimum grain size
+$a_{\rm c}=$50\,$\mu$m, also with an associated maximum and minimum grain size
 of $a_{\rm min}=$5 nm and $a_{\rm max}=$1mm. Subsequent works have adopted a
@@
 resulting albedo, and scattering and absorption opacities, for our
-dust population, with a the vertical dashed line showing 10$\mu$m.
+dust population, with a the vertical dashed line showing 10\,$\mu$m.
 
@@
  \caption{Figures of the albedo (\textit{top panel}), and scattering
-   (dashed line) and absorption (solid line) opacties (\textit{bottom
+   (dashed line) and absorption (solid line) opacities (\textit{bottom
      panel}) against log($\lambda$) (in $\mu$m) for our adopted dust
    population. For \textit{both panels} the vertical dashed line is
-   plotted at 10$\mu$m to higlight the silicate features.
+   plotted at 10\,$\mu$m to highlight the silicate features.
    \label{albedo}}
@@
 the cell. Once these nine iterations are complete, the grid is refined
-around the disc photosphere, and the radiative transfer alogrithm is
+around the disc photosphere, and the radiative transfer algorithm is
 iterated through to convergence. After this first convergence, a
@@
 photosphere. This process continues for five hydrostatic equilibrium
-calculations. Finally, once the hydrostatic equilibrium iteratins are
+calculations. Finally, once the hydrostatic equilibrium iterations are
 complete we perform a final dust sublimation run to remove any cells
@@
 decaying rate into the particular region. This was expected to lead to
-a more realistic situation where the dust destruction propogates into
+a more realistic situation where the dust destruction propagates into
 the disc material, and does not instantly destroy an entire
@@
 circumstellar discs is apparent from the SEDs of disc systems, where a
-peak in emission is found between 2 and 3$\mu$m. The temperatures
+peak in emission is found between 2 and 3\,$\mu$m. The temperatures
 reached by such inner walls are expected to generate thermal flux
@@
 gravitational perturbations. In addition, photoevaporation from UV and
-UV flux is expected to halt accretion from radii within the inner disc
-due to the removal of this material via a stellar/disc wind
+FUV flux is expected to halt accretion from radii within the inner
+disc due to the removal of this material via a stellar/disc wind
 \citep{2006MNRAS.369..229A}. These two clearing mechanisms could be
-differentiate by the resulting masses of the discs
+differentiated by the resulting masses of the discs
 \citep{2007MNRAS.378..369N}. However, for our model systems we have
@@
 system-observer inclination. For our models we have set the distance,
-again, to 10pc to create absolute flux SEDs and selected ten
-inclinations (0, 27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$). A
-further useful feature of the {\sc torus} code is that the emitted
-photons which make up the SED are tagged on their way to the
-observer. These tags separate the photons into four groups. Firstly,
-photons are separated by source into thermal (disc) or stellar groups.
-These groups are then subdivided into photons which reach the observer
-either directly or after scattering (for example see Figure
-\ref{disc_eg_173}). The resulting SEDs are discussed in Section
-\ref{seds}.
+to 10pc to create absolute flux SEDs and selected ten inclinations (0,
+27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$). A further useful
+feature of the {\sc torus} code is that the emitted photons which make
+up the SED are tagged on their way to the observer. These tags
+separate the photons into four groups. Firstly, photons are separated
+by source into thermal (disc) or stellar groups. These groups are then
+subdivided into photons which reach the observer either directly or
+after scattering (for example see Figure \ref{disc_eg_173}). The
+resulting SEDs are discussed in Section \ref{seds}.
 
@@
 system of \cite{1982AJ.....87.1029E,2004PASP..116....9S} for
-\textit{JHK}, with the required shift of -0.015$\mu$m as prescribed by
+\textit{JHK}, with the required shift of $-0.015$\,$\mu$m as prescribed by
 \cite{2004PASP..116....9S}.
@@
 vertical disc structure as oppose to vertical hydrostatic equilibrium.
-.A summary of the values adopted for each input variable is shown in
+A summary of the values adopted for each input variable is shown in
 Table \ref{par_space_table}.
@@
 
-Typical disc lifetimes for solar type stars are of order $\approx$ 10
-Myrs \citep{2001ApJ...553L.153H}. Therefore, we have adopted input
-ages of 1 and 10 Myrs for our model grid, to span the approximate
-range of ages over which discs influence will be important.
+Typical disc lifetimes for solar type stars are of order 10 Myrs
+\citep{2001ApJ...553L.153H}. Therefore, we have adopted input ages of
+1 and 10 Myrs for our model grid, to span the approximate range of
+ages over which the discs influence will be important.
 
@@
 periodically variable candidates. They found projections of cooler
-spots, onto the stellar disc, of a few to ~60\%.
+spots, onto the stellar disc, of a few to $~$60\%.
 \cite{1995A&A...299...89B} also found projected sizes, onto the
@@
 
-Accretion rates derived for pre-MS stars are of order -6 to -11
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$ \citep{2006A&A...452..245N}.
-With the largest accretion rates found in so-called FU Orionis type
-objects (after the object where they were first observed). For the
-more typical accretion rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9}
-M_{\odot}yr^{-1}$, for TTS,][]{2009arXiv0901.4120D}, several studies
-have now suggested that the accretion rate is strongly correlated with
-the mass of the central star. This relationship was perhaps first
-suggested by \cite{2003ApJ...592..266M} using various accretion
-diagnostics. Later, \citep{2005ApJ...625..906M} derived a relationship
-of approximately $\dot{M}\propto M_*^{~2}$. Further evidence was put
-forward by \cite{2004A&A...424..603N}, where accretion rates as low as
-5$\times$ 10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More
-recently, even lower accretion rates of $\approx$10$^{-13}M_{\odot}
-yr^{-1}$, have been derived for BDs by \cite{2009arXiv0901.3684H}.
-Further support for a dependence of accretion rate on stellar mass was
+Accretion rates derived for pre-MS stars are of order \logmdot = $-6$
+to $-11$ \citep{2006A&A...452..245N}.  With the largest accretion
+rates found in so-called FU Orionis type objects (after the object
+where they were first observed). For the more typical accretion rates
+\citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9} M_{\odot}yr^{-1}$, for
+  TTS,][]{2009arXiv0901.4120D}, several studies have now suggested
+that the accretion rate is strongly correlated with the mass of the
+central star. This relationship was perhaps first suggested by
+\cite{2003ApJ...592..266M} using various accretion diagnostics. Later,
+\citep{2005ApJ...625..906M} derived a relationship of approximately
+$\dot{M}\propto M_*^{~2}$. Further evidence was put forward by
+\cite{2004A&A...424..603N}, where accretion rates as low as 5$\times$
+10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More recently,
+even lower accretion rates of $\approx$10$^{-13}M_{\odot} yr^{-1}$,
+have been derived for BDs by \cite{2009arXiv0901.3684H}.  Further
+support for a dependence of accretion rate on stellar mass was
 apparent in the significantly more homogeneous dataset of
@@
 observational studies. Therefore, we have adopted accretion rates of
--6, -7, -8, -9, -10, -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$.
+\logmdot = $-6$, $-7$, $-8$, $-9$, $-10$, $-11$ \& $-12$.
 
@@
 Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
-Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&-6, -7, -8, -9, -10,
--11 \& -12 (7)\\
+Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&$-6$, $-7$, $-8$, $-9$, $-10$,
+$-11$ \& $-12$ (7)\\
 Disc mass ($M_*$)&0.01 (1)\\
@@
 \end{table*}
-
-GOT HERE NEEDS ALOT OF RE-READING FROM HERE ON IN**
 
@@
 of rotation rate with IR excess \citep{1997AJ....114..288M} (the
-reverese of that expected due to angular momentum loss through
+reverse of that expected due to angular momentum loss through
 disc-locking). We have not assumed a relationship between accretion
@@
 In this Section we first discuss the physical structure, both density
-and temperature, of the BDD disc systems (Section \ref{disc_struct}
+and temperature, of the BDD disc systems (Section \ref{disc_struct})
 across our parameter space. Then we discuss the resulting simulated
 SEDs for these BDD systems (Section \ref{sed_analysis}). Finally, we
-produce simulated photometric observations (Section
-\ref{photometry}). These simulated observations allows us to show that
-recovery of the input masses and ages for our accreting BDD systems is
-unreliable. We show that despite and intrinsic relationship between
-rotation rate and initial inner edge position we do not recover a
-rotation rate correlation with IR excess. In addition, despite not
-intrinsically including a dependence of accretion rate on stellar mass
-in our grid. We show that current observational techniques and
-theoretical models applied to the grid would result in a relationship
-of this type being derived.
+produce simulated photometric observations (Section \ref{photometry}).
+These simulated observations allows us to show that recovery of the
+input masses and ages for our accreting BDD systems is unreliable. We
+show that despite an intrinsic relationship between rotation rate and
+initial inner edge position we do not recover a rotation rate
+correlation with IR excess. In addition, despite not intrinsically
+including a dependence of accretion rate on stellar mass in our grid.
+We show that current observational techniques and theoretical models
+applied to the grid would result in a relationship of this type being
+derived.
 
@@
 in \cite{2004MNRAS.351..607W} with the the disc surface density
-conserved, $\Sigma ^{\beta - \alpha}$. The intial scaleheight,
+conserved, $\Sigma ^{\beta - \alpha}$. The initial scaleheight,
 $h\propto r^{\beta}$, where r is the radial distance from the star,
 and the density, $\rho \propto r^{-\alpha}$. The initial values of
-$\alpha$ and $\beta$ where 2.1 and 1.1 respectively \citep[see][for
+$\alpha$ and $\beta$ were 2.1 and 1.1 respectively \citep[see][for
 full discussion of disc structure]{2004MNRAS.351..607W}. The values
-for $\alpha$ and $\beta$ where chosen to optimise resolution of the
+for $\alpha$ and $\beta$ were chosen to optimise resolution of the
 vertically evolving disc, but minor variations are largely
 inconsequential as the systems evolves from this state. In our models
-we have, however, placed in the inner disc edge at the co-rotation
+we have, however, placed at the inner disc edge at the co-rotation
 radius, as opposed to the dust destruction radius used in
@@
 scaleheight and inner edge location then evolved in the systems
-dependent on the input parameters. I this section we discuss the
+dependent on the input parameters. In this section we discuss the
 structure of the discs in terms of these two generated
@@
 
-As discussed in \cite{2004MNRAS.351..607W} the scaleheights of discs
-around CTTS stars have scaleheights at 100 AU of between $h$(100)$=$7
-to 20 AU, whereas for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and
-0.01 $M_{\odot}$ respectively). Our models adopt the same formalism
-for solving hydrostatic equilibirum and therefore, at negligible
-accreion rates, our disc scaleheights are comparable (**). As the
-accretion rate increases the flux levels of the central star increase
-and lead to heating of the disc. This in turn leads to vertical
-expansion in the disc. For our models we found that levels of vertical
-flaring increased marginally with accretion rate. Significant
-differences, more than $>$5 AU increase in $h(50)$, in the vertical
-structure where not apparent until the high accretion rates of -7 and
--6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. Figures \ref{flare_-12_183}
-and \ref{flare_-7_193} show the density structure ($log({\rho})$) in
-the disc from radial distances of 0 to 50 AU for an example systems
-($M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5 and areal coverage=10\%),
-at accretion rates of -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively.
+As discussed in \cite{2004MNRAS.351..607W} discs around CTTS stars
+have scaleheights at 100 AU of between $h$(100)$=$7 to 20 AU, whereas
+for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and 0.01 $M_{\odot}$
+respectively). Our models adopt the same formalism for solving
+hydrostatic equilibrium and therefore, at negligible accretion rates,
+our disc scaleheights are comparable. As the accretion rate increases
+the flux levels of the central star increase and lead to heating of
+the disc. This in turn leads to vertical expansion in the disc. For
+our models we found that levels of vertical flaring increased
+marginally with accretion rate. Significant differences, more than
+$>$5 AU increase in $h(50)$, in the vertical structure were not
+apparent until the high accretion rates of \logmdot = $-7$ and
+$-6$. Figures \ref{flare_-12_183} and \ref{flare_-7_193} show the
+density structure ($log({\rho})$) in the disc from radial distances of
+0 to 50 AU for example systems ($M_*=0.04M_{\odot}$, Age=1 Myrs,
+$\tau$=5 and areal coverage=10\%), with accretion rates of \logmdot =
+$-12$ and $-7$, respectively.
 
@@
   \special{psfile="Fig/flare_-12_183.ps"
-   hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
- \caption{Figure showing the density structure ($log({\rho}$) of the
+   hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
+ \caption{Figure showing the density structure ($log({\rho}$)) of the
    BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
-   coverage=10\% and accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+   coverage=10\% and accretion rate of \logmdot=$-12$.
    \label{flare_-12_183}}
@@
   \special{psfile="Fig/flare_-7_193.ps"
-  hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
-\caption{Figure showing the density structure ($log({\rho}$) of the
+  hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
+\caption{Figure showing the density structure ($log({\rho}$)) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
-  coverage=10\% and accretion rate of -7
-  log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+  coverage=10\% and accretion rate of \logmdot=$-7$.
    \label{flare_-7_193}}
@@
 resulting disc is highly flared and therefore, the opening angle for
-stellar radiation is much smaller. As discussed the flaring for BDD
-systems was found to be larger than CTTS systems by
+stellar radiation is small. As discussed the flaring for BDD systems
+was found to be larger than CTTS systems by
 \cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
@@
 \ref{flare_-7_193} show an increase in the scaleheight at 50 AU of
-$>$5 AU, as the accretion rate moves from -12 to -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. However, despite this small
-change with high levels of accretion our grid shows scaleheights
-comparable to the work of \cite{2004MNRAS.351..607W} and as such
-result in similar consequences for the SEDs and photometric
-magnitudes. The effects of this flaring and the increase in flaring
-for very high accretion levels on SEDs and photometric magnitudes are
-discussed in Sections \ref{sed_analysis} and \ref{photometry},
-respectively.
+$>$5 AU, as the accretion rate moves from \logmdot =$-12$ to
+$-7$. However, despite this small change with high levels of accretion
+our grid shows scaleheights comparable to the work of
+\cite{2004MNRAS.351..607W} and as such result in similar consequences
+for the SEDs and photometric magnitudes. The effects of this flaring
+and the increase in flaring for very high accretion levels on SEDs and
+photometric magnitudes are discussed in Sections \ref{sed_analysis}
+and \ref{photometry}, respectively.
 
@@
 Our models include a sophisticated treatment of dust sublimation
-(described in Section \ref{dust_edge}. In contrast to the models of
+(described in Section \ref{dust_edge}). In contrast to the models of
 \cite{2004MNRAS.351..607W}, who apply a dust destruction radius, we
-set the intial inner radius of the disc at the co-rotation radius of
+set the initial inner radius of the disc at the co-rotation radius of
 the system. However, as our models then sublimate dust during the
-temperature convergence routine this inner edge location may
-change. As the flux levels of the central star increase with
-increasing accretion rates the flux incident on the inner edge
-increases and leads to increasing erosion of the inner edge of the
-dust disc.
+temperature convergence routine this inner edge location may change.
+As the flux levels of the central star increase with increasing
+accretion rates the flux incident on the inner edge increases and
+leads to increasing erosion of the inner edge of the dust disc.
 
@@
 disc-locking. However, the flux from the inner edge will usually peak
-between 2 and 3$\mu$m \citep{2001ApJ...560..957D}, given that the dust
-sublimation   temperature  peaks   at  $\approx$1400K   for  canonical
-densities. This means that for  models where dust is sublimated at the
-inner edge  will have maximum temperatures of  $\approx$1400K and this
+between 2 and 3\,$\mu$m \citep{2001ApJ...560..957D}, given that the dust
+sublimation temperature peaks at $\approx$1400\,K for canonical
+densities. This means that for models where dust is sublimated the
+inner edge will have maximum temperatures of $\approx$1400\,K and this
 correlation of disc position and temperature will be lost.
@@
 rate is increased in these systems the incident flux on the inner wall
-will increase leading to a rise in the temperature of the inner
-edge. At some point, in both cases the dust sublimation temperature
-may be reached, leading to a change in radial position of the wall. In
+will increase leading to a rise in the temperature of the inner edge.
+At some point, in both cases the dust sublimation temperature may be
+reached, leading to a change in radial position of the wall. In
 addition, the temperature of the inner edge will then tend to a
@@
 against the change in inner disc location, $R_{\rm co}-R_{\rm inner}$
-in AU (\textit{top panel}) and $R_*$ \textit{bottom panel}. Ths change
-in inner edge location is from the initially set co-rotation radius to
-the final radius after dust sublimation, if applicable.
+in units of AU (\textit{top panel}) and $R_*$ \textit{bottom panel}.
+This change in inner edge location is from the initially set
+co-rotation radius to the final radius after dust sublimation, if
+applicable.
 
@@
  \caption{Figure showing the combined stellar luminosity (accretion
-   plust intrinsic stellar luminosity) in units of
+   plus intrinsic stellar luminosity) in units of
    log($L_*/L_{\odot}$) against the change in inner edge location
@@
 The \textit{top panel} of Figure \ref{lum_sub} shows that as the
-luminosty increases the total change in the inner radius increases as
+luminosity increases the total change in the inner radius increases as
 more of the disc is sublimated. The total change for lower
-luminosities at lower than ~0.2 log($L_*/L_{\odot}$) is small (less
-than ~0.02 AU). As the luminosities increases to larger, and extreme
+luminosities at lower than $~$0.2 log($L_*/L_{\odot}$) is small (less
+than $~$0.02 AU). As the luminosities increases to larger, and extreme
 values, due to increasing accretion, the dust sublimation
 increases. In the \textit{bottom panel} the change in inner radius
-tends towards around ~120 $R_*$. Increases in accretion rate, for
+tends towards around $~$120 $R_*$. Increases in accretion rate, for
 extreme accretors, dominates the increase in stellar luminosity. As
@@
 for models with accretion rates of -9, -10, -11 and -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, classed as typical accretors
+log$(\frac{\dot{M}}{M_{\odot}}yr{-1})$, classed as typical accretors
 here and throughout the rest of this work. The typical accretors are
@@
   panel} specifically, -9, -10 and -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (blue, red and black dots
-respectively). The \textit{bottom panels} show the data for models with
-accretion rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
-(blue, red and black dots respectively), which we have classed as
-extreme accretors. The \textit{right panels} show the data seperated
-by age, with 1 and 10 Myrs (as crosses and triangles respectively),
-and rotation period, with 0.5 and 5 days (as red and blue symbols
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black dots
+respectively). The \textit{bottom panels} show the data for models
+with accretion rates of \logmdot = $-6$, $-7$ and $-8$ (blue, red and
+black dots respectively), which we have classed as extreme
+accretors. The \textit{right panels} show the data separated by age,
+with 1 and 10 Myrs (as crosses and triangles respectively), and
+rotation period, with 0.5 and 5 days (as red and blue symbols
 respectively).
@@
    accretion rates are then further subdivided. The \textit{top left
-     panel} shows accretion rates of -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, red and black dots
+     panel} shows accretion rates of \logmdot = $-9$, $-10$, $-11$
+   \& $-12$ as blue, red and black dots
    respectively. In the \textit{bottom left panel} accretion rates of
-   -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as
+   \logmdot = $-6$, $-7$ and $-8$ are shown as
    blue, red, and black dots. In addition the \textit{left panels}
-   seperates the systems by age and period. The systems with ages of 1
+   separates the systems by age and period. The systems with ages of 1
    and 10 Myrs are shown as crosses and triangles respectively. The
@@
 \textit{left panels}, shows that dust sublimation does not become
-significant until accretion rates of around -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and increases dramatically with
-increasing accretion rate thereafter.  This accretion rate, -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, is also, unsurprisingly the
-accretion rate at which the underlying photospheric emission is
-overwhelmed by the accretion flux, and the photospheric features are
-lost (see Section \ref{sed_analysis}). The \textit{right panels} of
-Figure \ref{delta_radius} show that dust sublimation occurs only for
-rotation periods of 0.5 days for typical accretors. For the extreme
-accretors the systems with both rotation periods undergo sublimation
-but the effect is more significant in the systems with shorter
-rotation periods.  The \textit{right panels} also show that for
-extreme accretors the older systems undergo more dust sublimation,
-whereas for the typical accretors the older systems undergo little or
-no dust sublimation.
+significant until accretion rates of around \logmdot=$-9$ and
+increases dramatically with increasing accretion rate thereafter.
+This accretion rate is also, unsurprisingly the accretion rate at
+which the underlying photospheric emission is overwhelmed by the
+accretion flux, and the photospheric features are lost (see Section
+\ref{sed_analysis}). The \textit{right panels} of Figure
+\ref{delta_radius} show that dust sublimation occurs only for rotation
+periods of 0.5 days for typical accretors. For the extreme accretors
+the systems with both rotation periods undergo sublimation but the
+effect is more significant in the systems with shorter rotation
+periods.  The \textit{right panels} also show that for extreme
+accretors the older systems undergo more dust sublimation, whereas for
+the typical accretors the older systems undergo little or no dust
+sublimation.
 
@@
 the star ($\rho\propto R_*^{\alpha}$). The dust sublimation
-temperature is also density dependent
-\citep{1994ApJ...421..615P}. Therefore, for systems where the inner
-edge has been eroded significantly from the co-rotation radius the
-temperature of the inner edge will fall as the final radius
-increases. In this case a correlation of inner edge temperature and
-inner edge radius is expected with a resulting slope determined, at
-least in part, by the radial density distribution of the disc. In this
-case the the final inner edge radius and therefore temperature is no
-longer strongly correlated with the rotation rate. Figure
-\ref{inner_temp} shows the final inner edge location ($R_{\rm inner}$,
-($R_*$) against the Temperature of the inner wall ($T_{\rm inner}$,
-(K)). The \textit{left panel} shows the systems designated as typical
-accretors and the \textit{right panel} those with extreme accretion
-rates. For \textit{both panels} the systems with rotation periods of
-0.5 and 5 days are plotted in read and blue respectively. Those
-systems where the change in inner radius was greater than 1$R_*$, and
-therefore classes as significantly sublimated, are plotted as
-crosses. These systems are only present for the extreme accretors, as
-shown in Figure \ref{delta_radius}. Furthermore, for the typical
-accretors Figure \ref{delta_radius} shows that only the shorter period
-objects, in general, experience any disc erosion at the inner
-edge.
+temperature is also density dependent \citep{1994ApJ...421..615P}.
+Therefore, for systems where the inner edge has been eroded
+significantly from the co-rotation radius the temperature of the inner
+edge will fall as the final radius increases. In this case a
+correlation of inner edge temperature and inner edge radius is
+expected with a resulting slope determined, at least in part, by the
+radial density distribution of the disc. In this case the the final
+inner edge radius and therefore temperature is no longer strongly
+correlated with the rotation rate. Figure \ref{inner_temp} shows the
+final inner edge location ($R_{\rm inner}$, $R_*$) against the
+temperature of the inner wall ($T_{\rm inner}$, K). The \textit{left
+  panel} shows the systems designated as typical accretors and the
+\textit{right panel} those with extreme accretion rates. For
+\textit{both panels} the systems with rotation periods of 0.5 and 5
+days are plotted in red and blue respectively. Those systems where the
+change in inner radius was greater than 1$R_*$, and therefore classes
+as significantly sublimated, are plotted as crosses. These systems are
+only present for the extreme accretors, as shown in Figure
+\ref{delta_radius}. Furthermore, for the typical accretors Figure
+\ref{delta_radius} shows that only the shorter period objects, in
+general, experience any disc erosion at the inner edge.
 
@@
      panel} (see text for explanation). In \textit{both panels}
-   seperate the systems by period, with those systems with rotation
+   separate the systems by period, with those systems with rotation
    periods of 0.5 and 5 days shown as red and blue symbols
@@
 
-Figure \ref{inner_temp} shows that for those systems where signifcant
-disc erosion ($\Delta R_{\rm inner} > 1.0 R_*$) has occured the
+Figure \ref{inner_temp} shows that for those systems where significant
+disc erosion ($\Delta R_{\rm inner} > 1.0 R_*$) has occurred the
 resulting temperature of the inner edge is weakly correlated with the
-inner edge radius, but, critically, not correlated with rotation
-rate. The inner edge temperatures of the remaining systems for the
-extreme accretors are slightly anti-correlated with the radius to the
-inner edge. For the systems with typical acccretion rates, and longer
-periods, Figure \ref{inner_temp} shows there is a again a weak
+inner edge radius, but, critically, not correlated with rotation rate.
+The inner edge temperatures of the remaining systems for the extreme
+accretors are slightly anti-correlated with the radius to the inner
+edge. For the systems with typical acccretion rates, and longer
+periods, Figure \ref{inner_temp} shows there is again a weak
 correlation between the radius to, and the temperature of the inner
-edge. For the shorter period models with typical accretion rates ther
+edge. For the shorter period models with typical accretion rates there
 is no clear correlation between the temperature at the inner edge and
@@
 there $R_{\rm inner}=$1$-$12$R_*$ and $\dot{M_{\rm acc}}=$10$^{-9}$to
-10$^{-5} M_{\odot}yr^{-1}$, for flat disc
-models. \cite{1997AJ....114..288M} use correlation, and the derivation
-of IR magnitudes, to predict a relationship between IR excess and
-radius to the inner wall. Our data indicate that this correlation, for
+10$^{-5} M_{\odot}yr^{-1}$, for flat disc models.
+\cite{1997AJ....114..288M} use this correlation, and the derivation of
+IR magnitudes, to predict a relationship between IR excess and radius
+to the inner wall. Our data indicate that this correlation, for
 typically accreting systems will translate into a correlation between
@@
 function of rotation rates, provide an intrinsic bias. In practice
-however, this correlation is weak, if observable, in our data due to
-inner disc wall shape, inclination and flaring effcts. This is
-discussed in more detail in Section \ref{photometry} **.
+however, this correlation is weak, an unobservable, in our data due to
+inner disc wall shape, inclination and flaring effects. This is
+discussed in more detail in Section \ref{photometry}.
 
@@
 distributions, the inner disc edge is characterised solely by the
-intial disc density prescription. If one includes vertical hydrostatic
-equilibrium the scaleheight of the disc inner edge can change but the
-radial distribution of dust will not. Dust sublimation physics will
-alter the vertical structure, but crucially will also alter the radial
-distribution of dust. This means that dust sublimation effects will
-control the shape of the inner disc wall and possibly change this from
-a vertical wall.  Evidence that real inner disc boundaries (for CTTS)
-are not vertical walls comes from a lack of dependence of the derived
-IR excess on system inclination \citep{2007ApJ...661..374T}. As
-discussed in Section \ref{dust_edge} the disc inner hole can be
-created by several mechanisms, however, for this study we have only
-included a treatment of magnetic truncation (initially) and subsequent
-dust sublimation. The effects of dust sublimation have been shown to
-produce curved inner walls due to the temperature and density
-dependence of the dust sublimation temperature
+initial disc density prescription. If one includes vertical
+hydrostatic equilibrium the scaleheight of the disc inner edge can
+change but the radial distribution of dust will not. Dust sublimation
+physics will alter the vertical structure, but crucially will also
+alter the radial distribution of dust. This means that dust
+sublimation effects will control the shape of the inner disc wall and
+possibly change this from a vertical wall. Evidence that real inner
+disc boundaries (for CTTS) are not vertical walls comes from a lack of
+dependence of the derived IR excess on system inclination
+\citep{2007ApJ...661..374T}. As discussed in Section \ref{dust_edge}
+the disc inner hole can be created by several mechanisms, however, for
+this study we have only included a treatment of magnetic truncation
+(initially) and subsequent dust sublimation. The effects of dust
+sublimation have been shown to produce curved inner walls due to the
+temperature and density dependence of the dust sublimation temperature
 \citep{2005A&A...438..899I}. The curved boundary in this case is
-concave, as density increases towards the midplane of the disc, the
+convex, as density increases towards the midplane of the disc, the
 dust sublimation temperature increases, meaning the destruction radius
@@
 included with different scaleheight distributions. This is essentially
-a simple model of grain growth and subsequent midplane
-settling. \cite{2007ApJ...661..374T}, found a convex inner disc
-boundary, this is due to the larger grains cooling more
-efficiently. These larger grains dominate the dust towards smaller
-vertical distances from the midplane, and therefore the increased
-cooling means that the dust sublimation temperature is reached at
-closer radii. The implications of the inner edge shape for the
-simulated SEDs and photometry are discussed in Section
-\ref{sed_analysis} and \ref{photometry}.
+a simple model of grain growth and subsequent midplane settling.
+\cite{2007ApJ...661..374T}, found a concave inner disc boundary, this
+is due to the larger grains cooling more efficiently. These larger
+grains dominate the dust towards smaller vertical distances from the
+midplane, and therefore the increased cooling means that the dust
+sublimation temperature is reached at closer radii. The implications
+of the inner edge shape for the simulated SEDs and photometry are
+discussed in Section \ref{sed_analysis} and \ref{photometry}.
 
 For systems where dust sublimation does not occur, or is minimal the
-inner edge of the system will remain as a vertical wall, as perscribed
+inner edge of the system will remain as a vertical wall, as prescribed
 by our initial density distribution. However, as one increases the
@@
 shown in Figure \ref{no_sub_183} has $\tau$=5 days and accretion
-rate=-12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (model shown in Figure
+rate \logmdot$=-12$ (model shown in Figure
 \ref{flare_-12_183}), with Figures \ref{sub_169} to \ref{sub_181}
-showing models with $\tau$=0.5 days and accretion rates=-12, -9, -7
-and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. The \textit{right
+showing models with $\tau$=0.5 days and accretion rates \logmdot=$-12$, $-9$, $-7$
+and $-6$. The \textit{right
   panels} of Figures \ref{no_sub_183} to \ref{sub_181} show the
@@
 the final log($\rho$) distribution for regions where dust is present,
-scaled to a different minimum density (log($\rho_{\rm min}=1^{-13}$)
-compared to Figures \ref{flare_-12_183} and \ref{flare_-7_193}. The
-lower (log) density threshold is used in this case to better trace the
-inner edge and denser regions of the disc, whereas Figure
-\ref{flare_-12_183} and \ref{flare_-7_193} show the outer diffuse
-regions of the disc, or disc limits. Additionally, for Figures
-\ref{sub_169} to \ref{sub_181} (the sublimated systems), the
-\textit{right panels} also show the initial density, in the same units
+scaled to a different minimum density (log($\rho_{\rm
+  min}$)$=1^{-13}$) compared to Figures \ref{flare_-12_183} and
+\ref{flare_-7_193}. The lower (log) density threshold is used in this
+case to better trace the inner edge and denser regions of the disc,
+whereas Figure \ref{flare_-12_183} and \ref{flare_-7_193} show the
+outer diffuse regions of the disc, or disc limits. Additionally, for
+Figures \ref{sub_169} to \ref{sub_181} (the sublimated systems), the
+\textit{left panels} also show the initial density, in the same units
 as the final density, this is shown as a background grey scale (with
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
   \caption{Figure showing final density (log($\rho$)) where dust is
@@
     sublimation. System parameters are: $M_*$=0.04$M_{\odot}$, Age=1
-    Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate=-12
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate \logmdot$=-12$.}
   \label{no_sub_183}
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_169_density.ps}\label{sub_169_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_169_temp.ps}\label{sub_169_b}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_169_density.ps}\label{sub_169_a}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_169_temp.ps}\label{sub_169_b}}
   \caption{Figure showing both the initial (grey scale) and final
@@
     $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-12
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    $\tau$=0.5 days and accretion rate \logmdot=$-12$.}
   \label{sub_169}
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_175_density.ps}\label{sub_175_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_175_temp.ps}\label{sub_175_b}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_175_density.ps}\label{sub_175_a}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_175_temp.ps}\label{sub_175_b}}
   \caption{Figure showing both the initial (grey scale) and final
@@
     $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-9
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    $\tau$=0.5 days and accretion rate \logmdot$=-9$.}
   \label{sub_175}
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
   \caption{Figure showing both the initial (grey scale) and final
@@
     $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-7
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    $\tau$=0.5 days and accretion rate \logmdot$=-7$.}
   \label{sub_179}
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
-  \subfigure[]{\includegraphics[scale=0.3,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
   \caption{Figure showing both the initial (grey scale) and final
@@
     $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate=-6
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    $\tau$=0.5 days and accretion rate \logmdot$=-6$.}
   \label{sub_181}
@@
 smooth and interpolation at the inner edge yields a temperature of
-~900K. For the shorter period model the inner edge has undergone some
-dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
-shows that the inner edge has lost dust slightly, peferentially, along
-the midplane. Again for Figure \ref{sub_169} the change in inner edge
-location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
-sublimation (and inner wall) temperature is ~1450K, for a density of
-~$2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
+$~$900\,K. For the shorter period model the inner edge has undergone
+some dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
+shows that the inner edge has lost dust slightly, preferentially,
+along the midplane. Again for Figure \ref{sub_169} the change in inner
+edge location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
+sublimation (and inner wall) temperature is $~$1450\,K, for a density
+of $~2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
 \ref{sub_169}).The \textit{left panel} of Figure \ref{sub_169} shows
-that for even for a negligible accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, sublimation has begun to erode
-the inner edge, for the younger and faster rotating systems. Here the
-final density distribution has moved radially outward as can be seen
-by comparing the grey and colour scales in the \textit{left panel} of
-Figure \ref{sub_169}. Additionally, the inner edge has become slightly
+that for even for a negligible accretion rate of \logmdot=$-12$,
+sublimation has begun to erode the inner edge, for the younger and
+faster rotating systems.  Here the final density distribution has
+moved radially outward as can be seen by comparing the grey and colour
+scales in the \textit{left panel} of Figure
+\ref{sub_169}. Additionally, the inner edge has become slightly
 concave. As the flux levels of the central star increase the
 temperature of the inner edge surpasses the sublimation temperature at
-an increasing radius, destroying more of the disc an pushing the inner
-edge radially outwards. The \textit{left panel} of Figure
-\ref{sub_175} shows that for an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, increased sublimation has
-pushed the inner wall slightly farther from the star (wehn compared to
-Figure \ref{sub_169}), here, $\Delta R~0.52R_*$ ($~1.1\times
-10^{-3}$AU), and $T_{\rm inner}~1450$. Again the final density
-distribution has moved radially outward as can be seen by comparing
-the grey and colour scales in the \textit{left panel} of Figure
-\ref{sub_175}. The \textit{right panel} of Figure \ref{sub_175} shows
-that the gas interior to the inner edge extending down to the
-co-rotation radius, which is not sublimated, will reach temperatures
-in excess, or equal to, the inner edge, which in this model is
-~1400K. Such hot gas inner discs interior to the dust disc have been
-postulated through SED fitting
+an increasing radius, destroying more of the disc and pushing the
+inner edge radially outwards. The \textit{left panel} of Figure
+\ref{sub_175} shows that for an accretion rate of \logmdot$=-9$,
+increased sublimation has pushed the inner wall slightly farther from
+the star (when compared to Figure \ref{sub_169}), here, $\Delta
+R~0.52R_*$ ($~1.1\times 10^{-3}$AU), and $T_{\rm inner}~1450$. Again
+the final density distribution has moved radially outward as can be
+seen by comparing the grey and colour scales in the \textit{left
+  panel} of Figure \ref{sub_175}. The \textit{right panel} of Figure
+\ref{sub_175} shows that the gas interior to the inner edge extending
+down to the co-rotation radius, which is not sublimated, will reach
+temperatures in excess, or equal to, the inner edge, which in this
+model is $~$1400\,K. Such hot gas inner discs interior to the dust
+disc have been postulated through SED fitting
 \citep{2005ApJ...623..952E,2008ApJ...689..513T}. Again, the shape of
@@
 sections of the disc have eroded and the inner wall is convex. The
-model in Figure \ref{sub_175} has an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, which is the transition point
-between our two groups of accretors, typical and extreme. Figure
-\ref{sub_175} shows that for typical accretion rates, and faster
-rotation periods (and younger ages) signicant dust sublimation is
-expected to occur at the inner edge, resulting in a curved inner wall
-at around ~1400K. Increasing the accretion rate, and therefore flux
-levels, still further leads to significant erosion of the inner disc.
-For the extreme accretors the dust sublimation at the inner edge now
-changes the inner wall position by many multiples of the stellar
-radius. Figures \ref{sub_179} and \ref{sub_181} are for systems with
-accretion rates typical in outburst or episodic accretion systems, -7
-and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ respectively. The inner
-edges for these sytems are eroded radially by 7.1 and 36.1 ($R_*$)
-respectively (0.016 and 0.080 AU, respectively), visible by comparing
-the grey and colour scales of Figure \ref{sub_179} and
-\ref{sub_181}. As this occurs the disc inner edge moves far enough
-that the density drop (with radius) occuring in the disc causing the
-sublimation temperature to fall. Consequently the disc inner edge
-becomes cooler as it can not sustain temperatures above the
-sublimation temperature. This is shown in the \textit{right panels} of
-Figures \ref{sub_179} and \ref{sub_181}, with approximate temperatures
-at the inner edge of 1370 and 1260K. In addition, the inner edge has
-become concave and, again due to changes in the underlying disc
-density distribution, much larger in scaleheight.
+model in Figure \ref{sub_175} has an accretion rate of \logmdot=$-9$,
+which is the transition point between our two groups of accretors,
+typical and extreme. Figure \ref{sub_175} shows that for typical
+accretion rates, and faster rotation periods (and younger ages)
+significant dust sublimation is expected to occur at the inner edge,
+resulting in a curved inner wall at around $~$1400\,K. Increasing the
+accretion rate, and therefore flux levels still further leads to
+significant erosion of the inner disc.  For the extreme accretors the
+dust sublimation at the inner edge now changes the inner wall position
+by many multiples of the stellar radius. Figures \ref{sub_179} and
+\ref{sub_181} are for systems with accretion rates typical in outburst
+or episodic accretion systems, \logmdot$=-7$ and $-6$
+respectively. The inner edges for these systems are eroded radially by
+7.1 and 36.1 ($R_*$) respectively (0.016 and 0.080 AU, respectively),
+visible by comparing the grey and colour scales of Figure
+\ref{sub_179} and \ref{sub_181}.  As this occurs the disc inner edge
+moves far enough that the density drop (with radius) occurring in the
+disc causing the sublimation temperature to fall. Consequently the
+disc inner edge becomes cooler as it can not sustain temperatures
+above the sublimation temperature.  This is shown in the \textit{right
+  panels} of Figures \ref{sub_179} and \ref{sub_181}, with approximate
+temperatures at the inner edge of 1370 and 1260\,K. In addition, the
+inner edge has become concave and, again due to changes in the
+underlying disc density distribution, much larger in scaleheight.
 
@@
 sublimation starts. However, in almost all cases the dust sublimation
-does not become significant until at least -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as discussed above).
+does not become significant until at least \logmdot=$-9$ (as discussed
+above).
 
@@
 the shorter wavelength section of the SED. For our parameter space the
-temperature of the photospheres has a range of ~3000K$<T_{\rm
-  eff}$1600K, this will comprise flux contributions peaking in the
-range, 0.97 to 1.8 $\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
+temperature of the photospheres has a range of $~$3000\,K$<T_{\rm
+  eff}<$1600\,K, this will comprise flux contributions peaking in the
+range, 0.97 to 1.8\,$\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
     acc}}$). The accretion spot temperatures, for typical accretors,
-will range from ~340$>T_{\rm acc}>$9400K, emitting in the range 0.3 to
-8.5 $\mu$m. For the extreme accretors temperatures can reach as high
-as 53,000K, provide flux to $~$0.05 $\mu$m. The second pair of
-luminosity sources are from consituent parts of the circumstellar
-disc. The inner edge, ($L_{\rm wall}$), at temperatures of ~370 to
-~1500K, or flux contributions from ~1.85 to 7.7 $\mu$m
-\citep[nominally 2 to 3 $\mu$m][]{2001ApJ...560..957D}, and the outer
-disc ($L_{\rm disc}$), at temperatures of ~300K or less contributing
-flux longward of ~10 $\mu$m. As discussed in Section \ref{seds} the
-{\sc torus} radiative transfer code tags the photons before they
-reach the simulated observe in one of four ways, stellar and thermal,
-either direct or scattered. These components allow us to analyses the
+will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range 0.3
+to 8.5\,$\mu$m. For the extreme accretors temperatures which can reach
+as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The second pair of
+luminosity sources are from constituent parts of the circumstellar
+disc. The inner edge, ($L_{\rm wall}$), at temperatures of $~$370 to
+$~$1500\,K, or flux contributions from $~$1.85 to 7.7\,$\mu$m
+\citep[nominally 2 to 3\,$\mu$m][]{2001ApJ...560..957D}, and the outer
+disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less contributing
+flux longward of $~$10\,$\mu$m. As discussed in Section \ref{seds} the
+{\sc torus} radiative transfer code tags the photons before they reach
+the simulated observer in one of four ways, stellar and thermal,
+either direct or scattered. These components allow us to analyse the
 contributions from the main flux contributors discussed, i.e. $L_{\rm
@@
 component photon contributions highlighted, with $M_*=0.04M_{\odot}$
-at 1 Myr with an areal coverage of 10\%, accretion rate of -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
+at 1 Myr with an areal coverage of 10\%, accretion rate of
+\logmdot=$-10$ and rotation period of 0.5
 days. The solid black line is the total simulated SED, with the
@@
 scattered and direct contributions are then shown as dashed and solid
-lines respecitvely. The horizontal and vertical dotted lines then show
+lines respectively. The horizontal and vertical dotted lines then show
 the approximate ranges of the flux contributions from the (from left
 to right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red)
-and $L_{\rm disc}$ (black).
+and $L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
+Figure \ref{disc_eg_173} show the approximate ranges of the $V$, $I$,
+$J$, and $K$ photometric bands we have adopted.
 
@@
   \special{psfile="Fig/disc_eg_173.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing the SED (log($\lambda \mu$m against
-   log(flux), flux in ergs$/s/cm^2/\AA$) for $M_*=0.04M_{\odot}$ at 1
-   Myr with an areal coverage of 10\%, accretion rate of -10
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
-   days. The solid black line is the total simulated SED. The stellar
-   components of the flux are shown in blue and the thermal in read,
-   with direct emission appearing as solid lines and scattered photons
-   as dashed lines. The vertical dotted bars linked by horizontal bars
-   show the approximate (log) wavelength ranges of the luminosity
-   components. With the blue lines denoting the accretion luminosity
-   ($L_{\rm acc}$) and the first (left to right) black lines showing
-   the photospheric contribution ($L_*$). The final two sets of lines
-   show the inner edge contribution ($L_{\rm wall}$) in red and the
-   outer disc ($L_{\rm disc}$) in black. \label{disc_eg_173}}
+   hoffset=250 voffset=-20 hscale=36 vscale=36 angle=90}
+ \caption{Figure showing the SED log($\lambda \mu$m) against
+   log(flux), flux in ergs$/s/cm^2/{\rm \AA}$) for $M_*=0.04M_{\odot}$
+   at 1 Myr with an areal coverage of 10\%, accretion rate of \logmdot
+   = $-10$ and rotation period of 0.5 days. The solid black line is
+   the total simulated SED. The stellar components of the flux are
+   shown in blue and the thermal in red, with direct emission
+   appearing as solid lines and scattered photons as dashed lines. The
+   vertical dotted bars linked by horizontal bars show the approximate
+   (log) wavelength ranges of the luminosity components. With the blue
+   lines denoting the accretion luminosity ($L_{\rm acc}$) and the
+   first (left to right) black lines showing the photospheric
+   contribution ($L_*$). The final two sets of lines show the inner
+   edge contribution ($L_{\rm wall}$) in red and the outer disc
+   ($L_{\rm disc}$) in black. The vertical and horizontal dashed lines
+   (in the \textit{lower panels}) denote the approximate sensitivity
+   ranges of our chosen $V$, $I$, $J$ and $K$
+   filters. \label{disc_eg_173}}
 \end{figure}
@@
 luminosities dominate the SED at wavelengths shortward of
-~1$\mu$m. After this, for this model, the SED is dominated by
+$~$1$\,\mu$m. After this, for this model, the SED is dominated by
 contributions from the disc, at shorter wavelengths, the inner edge
@@
 accretion flux. This will lead to difficulties in using spectral
-features to identify BDD systems for wavelengths shorter than ~1
+features to identify BDD systems for wavelengths shorter than $~$1
 $\mu$m, and, of course, for wavelengths longer than this the SED
@@
 central stars) will become unreliable. As discussed in Section
-\ref{inner_edge} observations of the inner edge location seperate the
+\ref{inner_edge} observations of the inner edge location separate the
 BDD systems into two groups, the typical accretors ($\dot{M}\leq$-9
 log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$) and extreme accretors
-($\dot{M}>$-9 log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$). This division
+($\dot{M}>-9$). This division
 between typical and extreme accretors is based on observational
@@
 
-Figure \ref{acc_dom} shows the affect of the increasing accretion
+Figure \ref{acc_dom} shows the affect of increasing the accretion
 blackbody flux (for increasing accretion rates) for a BD star,
@@
 star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
-{\sc torus} we can seperate these flux contributions simply by
+{\sc torus} we can separate these flux contributions simply by
 observing the naked star system. The panels in Figure \ref{acc_dom}
@@
 photospheric flux in isolation. The accretion rates included in all
-panels are -8, -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-(blue, black and red lines respectively). The \textit{bottom panels}
-show the systems with a rotation period of 5 days and \textit{top
-  panels} for those with a rotation period of 0.5 days. Given our
-assumption that accretion occurs from the co-rotation radius,
-decreasing the rotational period moves this accretion radius closer to
-the star, $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
-\ref{inner_eq}). As the accretion radius moves father from the star the
-potential energy released by the accreted material is reduced. This
-effect can be seen when comparing the \textit{top} and \textit{bottom
-  panels}, although the effect is marginal for all but the highest
-displayed accretion rates. The \textit{left panels} show accretion
-streams with an areal coverage of 10\% and the \textit{left panels}
-1\%. As the areal coverage reduces the effective temperature of the
-accretion hot spot increases, resulting in an increase in accretion
-flux, and resulting shift to bluer wavelengths of the peak flux. This
-can be seen clearly by comparing the \textit{left} and \textit{right
-  panels} of Figure \ref{acc_dom}. Perhaps the most important, albeit
-qualitative, result shown is Figure \ref{acc_dom} is an insight into
-the accretion rate at which the accretion blackbody flux dominates
-over the photospheric flux. Figure \ref{acc_dom} shows that as the
-accretion rate raises above -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-for systems with 1 or 10\% areal coverage, the accretion flux
-dominates the emergent SED at both periods. Therefore for reasonable
-coverages (1-10\%) and rotational periods (0.5-5 days) the
-photospheric flux is effectively swamped by accretion flux for
-accretion rates log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-9$. This
-suggests that accreting BD systems with accretion rates as low as -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ could be difficult to identify
-from SEDs as BD stars, and may well be classified as higher mass
-stars.
+panels are \logmdot = $-8$, $-9$ and $-12$ (blue, black and red lines
+respectively). The \textit{bottom panels} show the systems with a
+rotation period of 5 days and \textit{top panels} for those with a
+rotation period of 0.5 days. Given our assumption that accretion
+occurs from the co-rotation radius, decreasing the rotational period
+moves this accretion radius closer to the star, $R_{\rm inner}\propto
+\tau^{2/3}$ (see Equation \ref{inner_eq}). As the accretion radius
+moves father from the star the potential energy released by the
+accreted material is reduced. This effect can be seen when comparing
+the \textit{top} and \textit{bottom panels}, although the effect is
+marginal for all but the highest displayed accretion rates. The
+\textit{left panels} show accretion streams with an areal coverage of
+10\% and the \textit{left panels} 1\%. As the areal coverage reduces
+the effective temperature of the accretion hot spot increases,
+resulting in an increase in accretion flux, and resulting shift to
+bluer wavelengths of the peak flux. This can be seen clearly by
+comparing the \textit{left} and \textit{right panels} of Figure
+\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
+shown is Figure \ref{acc_dom} is an insight into the accretion rate at
+which the accretion blackbody flux dominates over the photospheric
+flux. Figure \ref{acc_dom} shows that as the accretion rate raises
+above \logmdot = $-9$ for systems with 1 or 10\% areal coverage, the
+accretion flux dominates the emergent SED at both periods. Therefore
+for reasonable coverages (1-10\%) and rotational periods (0.5-5 days)
+the photospheric flux is effectively swamped by accretion flux for
+accretion rates \logmdot$>-9$. This suggests that accreting BD systems
+with accretion rates as low as \logmdot$=-9$ could be difficult to
+identify from SEDs as BD stars, and may well be classified as higher
+mass stars.
 
@@
    hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the photospheric flux
-   (log(ergs$/s/cm^2/\AA$)) against $\lambda$ (log($\mu$m)) of a Brown
-   Dwarf with $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but
-   blackbody fluxes from an accretion stream at the rates of -8, -9
-   and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as blue,
-   black and red lines respectively. The \textit{bottom panels} show
-   accretion for a star rotating at 5 days, with the \textit{top
-     panels} showing that of 0.5 days. The \textit{left panels} systems
-   with an areal coverage of 10\% and the \textit{right panels} has
-   1\%.
-   \label{acc_dom}}
+ \caption{Figure showing the photospheric flux (log(ergs$/s/cm^2/{\rm
+     \AA}$)) against $\lambda$ (log($\mu$m)) of a Brown Dwarf with
+   $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
+   fluxes from an accretion stream at the rates of \logmdot $=-8$,
+   $-9$ and $-12$ are shown as blue, black and red lines
+   respectively. The \textit{bottom panels} show accretion for a star
+   rotating at 5 days, with the \textit{top panels} showing that of
+   0.5 days. The \textit{left panels} systems with an areal coverage
+   of 10\% and the \textit{right panels} has 1\%. The vertical and
+   horizontal dashed lines (in the \textit{lower panels}) denote the
+   approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
+   filters.\label{acc_dom}}
 \end{figure*}
 
-Therefore, the shorter wavelength component of the SED for extreme
-accretors is dominated by the accretion luminosity. For the typical
-accretors the intrinsic photospheric emission is important and the
-flux levels of this component are dependent on the stellar parameters
-of mass and age, through evolution of the stellar radius and
-temperature, as is well understood. In general, the bluer (short
-wavelength) components of the SEDs are therefore contrOlled by the
+As is well known the shorter wavelength component of the SED for
+extreme accretors is dominated by the accretion luminosity. For the
+typical accretors the intrinsic photospheric emission is important and
+the flux levels of this component are dependent on the stellar
+parameters of mass and age, through evolution of the stellar radius
+and temperature, as is well understood. In general, the bluer (short
+wavelength) components of the SEDs are therefore controlled by the
 stellar input parameters (mass and age) and the accretion input
@@
 discussed in Section \ref{disc_flaring} BDD systems under vertical
-hydrostatic equilibirum have highly flared discs. As discussed in
+hydrostatic equilibrium have highly flared discs. As discussed in
 \cite{2004MNRAS.351..607W} this increased flaring (when compared to
@@
 proportion of the stellar flux being intercepted, and reprocessed, by
-the highly flared disc. This reprossecing will lead to a change in the
+the highly flared disc. This reprocessing will lead to a change in the
 flux levels at the shorter, bluer, wavelengths as more stellar flux is
@@
 \textit{top panels} show the SEDs for a star with an accretion rate of
--12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (the lowest in our typical
+\logmdot$=-12$ (the lowest in our typical
 accretion range). The \textit{bottom panels} then show SEDs for
-systems with an accretion rate of -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (classed as an extreme
+systems with an accretion rate of \logmdot$=-8$ (classed as an extreme
 accretor). From left to right the \textit{panels} then show the naked
@@
      panel} inset Figure shows an enlargement of the lower flux levels
-   of this SED. \label{flare_sed_fast}}
+   of this SED. The vertical and horizontal dashed lines (in the
+   \textit{third panels} across) denote the approximate sensitivity
+   ranges of our chosen
+   $V$, $I$, $J$ and $K$ filters. \label{flare_sed_fast}}
 \end{figure*}
@@
 system is only visible through scattered light, and some (slight)
-thermal emission from the outer disc at wavelengths $\lambda>30\mu$m
-(indicative of temperatures of ~100K. Increasing the accretion rate
+thermal emission from the outer disc at wavelengths $\lambda>30\,\mu$m
+(indicative of temperatures of $~$100\,K. Increasing the accretion rate
 from -12 to -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ leads to a
@@
 at edge-on inclinations the system becomes only visible in the thermal
-(~100K) disc regime, with the scattered light significantly reduced.
+($~$100\,K) disc regime, with the scattered light significantly reduced.
 
@@
 vertical expansion leads to a significant change in the angle at which
-photons emitted from the stellar photosphere are interecepted by the
+photons emitted from the stellar photosphere are intercepted by the
 outer disc. This is an extension of the effected found in
@@
 \ref{flare_inc} shows the total SEDs for the BDD system of Figures
-\ref{flare_-12_183} and \ref{flare_-7_193}, with the coresponding
+\ref{flare_-12_183} and \ref{flare_-7_193}, with the corresponding
 accretion rates as \textit{left} and \textit{right panels}
@@
 enhanced for such extreme accretion rates it is illustrative of the
-general trend, notwithstanding complications from inner edge shape
-**MENTION ABOUT NOT BEING BOUND MATERIAL?**NOT ENTIRELY HAPPY WITH
-FLARESEDFAST**.
+general trend, notwithstanding complications from inner edge shape.
 
@@
    71$^{\circ}$ and 56$^{\circ}$ for the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, \textit{left} and
-   \textit{right panels} respectively. \label{flare_inc}}
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, \textit{left} and
+   \textit{right panels} respectively. The vertical and horizontal
+   dashed lines denote the approximate sensitivity ranges of our chosen
+   $V$, $I$, $J$ and $K$ filters. \label{flare_inc}}
 \end{figure*}
@@
    in flux occurs are 77$^{\circ}$ for \textit{both panels} and
-   therefore accretion rates. \label{typ_curve}}
+   therefore accretion rates. The vertical and horizontal dashed lines
+   denote the approximate sensitivity ranges of our chosen $V$, $I$,
+   $J$ and $K$ filters. \label{typ_curve}}
 \end{figure*}
@@
    \textit{left} and \textit{right panels}
-   respectively.\label{ext_curve}}
+   respectively.  The vertical and horizontal dashed lines (in the
+   \textit{lower panels}) denote the approximate sensitivity ranges of
+   our chosen $V$, $I$, $J$ and $K$ filters.\label{ext_curve}}
 \end{figure*}
@@
 For typically accreting systems, where little or no dust sublimation
-has occured the inner edge remains either a vertical or slightly
-concave wall, as shown in Figures \ref{sub_169} and
-\ref{sub_175}. For these systems flux reaching an observer from
-direct thermal emission, i.e. from, in the main, the disc inner edge,
-falls rapidly with increasing viewing angle, after the maximum opening
-angle is achieved. This is shown in Figure \ref{typ_curve} where at
-the viewing angle of 77$^{\circ}$ the flux shown falls significantly,
-for both accretion rates. This opening angle is larger than found for
-the slower rotating, counter parts, as shown by Figure
-\ref{flare_inc}, where a transition in occultation occurs at
-71$^{circ}$. For the case in \ref{typ_curve} the system has the
-shorter rotation period, leading to a larger opening angle, as the
-flux from the central star does not reach the outer disc, and
-subsequently flare it. Figure \ref{typ_curve} shows that after an
-angle of 77$^{\circ}$ the flux from the inner edge falls to zero. The
-systems displayed in Figure \ref{typ_curve} have inner edge
-temperatures of ~1400K, meaning their flux emission peaks at a
-wavelength of ~2$\mu$m. The flux observed at the expected peak
-wavelength falls to zero at inclinations of 77$^{\circ}$, indicative
-of a vertical wall being obscured by the outer disc, before the limit
-of the opening angle is reached.
+has occurred the inner edge remains either a vertical or slightly
+concave wall, as shown in Figures \ref{sub_169} and \ref{sub_175}. For
+these systems flux reaching an observer from direct thermal emission,
+i.e. from, in the main, the disc inner edge, falls rapidly with
+increasing viewing angle, after the maximum opening angle is achieved.
+This is shown in Figure \ref{typ_curve} where at the viewing angle of
+77$^{\circ}$ the flux shown falls significantly, for both accretion
+rates. This opening angle is larger than found for the slower
+rotating, counter parts, as shown by Figure \ref{flare_inc}, where a
+transition in occultation occurs at 71$^{\circ}$. For the case shown
+in Figure \ref{typ_curve} the system has the shorter rotation period,
+leading to a larger opening angle, as the flux from the central star
+does not reach the outer disc, and subsequently flare it. Figure
+\ref{typ_curve} shows that after an angle of 77$^{\circ}$ the flux
+from the inner edge falls to zero. The systems displayed in Figure
+\ref{typ_curve} have inner edge temperatures of $~$1400\,K, meaning
+their flux emission peaks at a wavelength of $~$2\,$\mu$m. The flux
+observed at the expected peak wavelength falls to zero at inclinations
+of 77$^{\circ}$, indicative of a vertical wall being obscured by the
+outer disc, before the limit of the opening angle is reached.
 
@@
 \ref{typ_curve} and \ref{ext_curve} show that the flux from the inner
-wall should fall dramitically at different limiting inclinations for
+wall should fall dramatically at different limiting inclinations for
 either accretion rate.
@@
    \textit{top} and \textit{bottom panels} are derived from the models
-   presented in Figures \ref{sub_169} and \ref{sub_179},
-   respectively.\label{inner_inc_sed}}
+   presented in Figures \ref{sub_169} and \ref{sub_179}, respectively.
+   The vertical and horizontal dashed lines (in the \textit{second
+     panels} across) denote the approximate sensitivity ranges of our
+   chosen $V$, $I$, $J$ and $K$ filters.\label{inner_inc_sed}}
 \end{figure*}
@@
 total flux falls rapidly after exceeding a viewing angle of
-71$^{\circ}$. After an inclination of 71$^{\circ}$, the negiliby
+71$^{\circ}$. After an inclination of 71$^{\circ}$, the negligibly
 accreting system is dominated by scattered light from the central
@@
 levels, and thermal contributions to the SED, for inclination angles
-above 71$^{\circ}$, particularily between 1 and 3$\mu$m. Essentially,
+above 71$^{\circ}$, particularly between 1 and 3\,$\mu$m. Essentially,
 as shown by comparing Figures \ref{sub_169} and \ref{sub_179}, with
 increasing flux and subsequent dust sublimation the inner edge has
-grown vertically and become convex. As shown perviously by
+grown vertically and become convex. As shown previously by
 \cite{2007ApJ...661..374T}, a vertical (or concave) inner edge will
@@
 accretion rate of -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ this is
-indicative of a larger opening angle (71$^{\circ}$) for the the
-shorter period object, when compared to the more slowly rotating
-equivalent (56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
+indicative of a larger opening angle (71$^{\circ}$) for the shorter
+period object, when compared to the more slowly rotating equivalent
+(56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
   panel}). Additionally, Figure \ref{inner_inc_sed} shows that the
 total SED, has a strong thermal component and is only weakly dependent
-on inclination angle, between 1 and 3 $\mu$m . This increase in
+on inclination angle, between 1 and 3\,$\mu$m . This increase in
 opening angle with increase in rotation rate is again due to more flux
@@
 slower rotating systems. Figures \ref{ext_curve} and
-\ref{inner_inc_sed} also shows that, contrary to the typical
-accretors, the flux from the inner edge does not fall off as quickly
-with inclination angle after occultation. The inner edge temperatures
-are ~1300 and ~1200K for the accretion rates of -7 (\textit{left
+\ref{inner_inc_sed} also show that, contrary to the typical accretors,
+the flux from the inner edge does not fall off as quickly with
+inclination angle after occultation. The inner edge temperatures are
+$~$1300 and $~$1200\,K for the accretion rates of -7 (\textit{left
   panel}) and -6 (\textit{right panel})
 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ respectively. This leads to
-peak emission at ~2.2 to 2.4 $\mu$m. Figures \ref{ext_curve} and
+peak emission at $~$2.2 to 2.4\,$\mu$m. Figures \ref{ext_curve} and
 \ref{inner_inc_sed} shows that even for inclinations above the
@@
 extreme accretion rates probably over accentuate the result but help
-illumate the consequences of changes in the disc structure.
+illuminate the consequences of changes in the disc structure.
 
@@
 resulting SEDs for typical accretors to show a correlation in shape,
-between 2 to 3 $\mu$m, caused by the inner wall temperature changes,
+between 2 and 3\,$\mu$m, caused by the inner wall temperature changes,
 in turn caused by changes in the rotation period. Figures
@@
 0.04$M_{\odot}$ and an age of 1 Myr, with accretion rates of -12 and
--9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in Figures \ref{rot_-12_1Myr}
+-9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures \ref{rot_-12_1Myr}
 and \ref{rot_-9_1Myr} respectively, both at an areal coverage of
@@
    hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{NOW SYSTEM SHOWN IN FIGURE ABOVE?**Figure showing SEDs of a
+ \caption{Figure showing SEDs of a
    system with a central stellar mass of $0.04M_{\odot}$, an age of
@@
    for systems with a rotation period of 0.5 days and the
-   \textit{lower panels} are for a rotation period of 5
-   days. \label{rot_-12_1Myr}}
+   \textit{lower panels} are for a rotation period of 5 days. The
+   vertical and horizontal dashed lines (in the \textit{third panels}
+     across) denote the approximate sensitivity ranges of our chosen
+   $V$, $I$, $J$ and $K$ filters. \label{rot_-12_1Myr}}
 \end{figure*}
@@
    \textit{lower panels} are for a rotation period of 5
-   days. \label{rot_-9_1Myr}}
+   days.  The vertical and horizontal dashed lines (in the
+   \textit{third panels across}) denote the approximate sensitivity
+   ranges of our chosen $V$, $I$, $J$ and $K$ filters.
+   \label{rot_-9_1Myr}}
 \end{figure*}
@@
   panels} of Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} have
-inner edge temperatures of ~1470 \& ~900K, and ~1460 \& ~940K
+inner edge temperatures of $~$1470 \& $~$900\,K, and $~$1460 \& $~$940\,K
 respectively. This leads to different peak emissions for the slower
-and faster rotating stars, of approximately 2 and 3 $\mu$m. However,
+and faster rotating stars, of approximately 2 and 3\,$\mu$m. However,
 as is shown by Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} very
@@
    \textit{lower panels} are for an age of 10
-   Myrs. \label{comp_rot_-12}}
+   Myrs. The vertical and horizontal dashed lines (in the
+   \textit{third panels across}) denote the approximate sensitivity
+   ranges of our chosen $V$, $I$, $J$ and $K$
+   filters\label{comp_rot_-12}}
  \end{figure*}
@@
    \textit{lower panels} are for an age of 10
-   Myrs. \label{comp_rot_-9}}
+   Myrs. The vertical and horizontal dashed lines (in the
+   \textit{third panels across}) denote the approximate sensitivity
+   ranges of our chosen $V$, $I$, $J$ and $K$ filters
+   \label{comp_rot_-9}}
 \end{figure*}
@@
 with changing rotation rate. For the face-on configuration
-(\textit{far left panels}) the SED slope over 2 to 3$\mu$m is
-marginally different only**. Essentially, flux redistribution from the
+(\textit{far left panels}) the SED slope over 2 to 3\,$\mu$m is
+marginally different only. Essentially, flux redistribution from the
 highly flared outer regions of the disc and inner edge shape changes
-lead to a loss of correlations of SED shape (from 2 to 3$\mu$m)with
+lead to a loss of correlations of SED shape (from 2 to 3\,$\mu$m)with
 inner edge temperature. This leads to a loss of any correlation
@@
 emission of the disc components. However, several underlying trends
-have been observed in the physical characteristics of the
-systems. Most notably the correlation, to different strengths, of the
-disc inner wall location and its resulting temperature, as found in
+have been observed in the physical characteristics of the systems.
+Most notably the correlation, to different strengths, of the disc
+inner wall location and its resulting temperature, as found in
 \cite{1997AJ....114..288M}. However, \cite{1997AJ....114..288M} go on
-to predict a correlation in IR excess with inner edge location. Given
+to predict a correlation of IR excess with inner edge location. Given
 that the initial inner edge location is dependent (chiefly) on the
-rotation period one might expect a corelation of rotation rate with IR
-excess. This has been shown to be unlikely due to complications in the
-inner edge location due to dust sublimation, and obscuration of the
-inner disc edge at higher inclination angles. In addition, for large
-groups of stars there is evidence for a correlation in stellar mass
-with accretion rates. Although we have shown that the observable SEDs
-of BDD systems at higher accretion rates are difficult to classify as
-such, most surveys supporting this relationship use photometric data.
+rotation period one might expect a correlation of rotation rate with
+IR excess. This has been shown to be unlikely due to complications in
+the inner edge location due to dust sublimation, and obscuration of
+the inner disc edge at higher inclination angles. In addition, for
+large groups of stars there is evidence for a correlation in stellar
+mass with accretion rates. Although we have shown that the observable
+SEDs of BDD systems at higher accretion rates are difficult to
+classify as such, most surveys supporting this relationship use
+photometric data. Therefore, we must examine whether these problems
+translate into the broadband photometric magnitudes.
 
@@
 photometry and subsequently constructed colour-magnitude and
-colour-colour diagrams (CMDs and CoCoDs respectively,
-hereafter). Therefore, in this Section, we demonstrate the prohibitive
-effects on the broadband photometry of varying our input
-parameters. In this Section we, in particular, relate the discussed
-features of disc structures (\ref{disc_struct}) and the resulting
-simulated SEDs (\ref{sed_analysis}) in terms of the derived
-photometry, in Section \ref{indv_phot}. Furthermore, we explore the
-consequences of our model grid on the derivation of the primary
-parameters of age, mass and disc fractions, from populations, in
-Section \ref{populations}. This in turn leads to highlighting
-selection effects with, for instance, the mass to accretion rate
-relation, in Section \ref{sum_relations}.  For the derivation of ages
-optical CMDs, in particular in \textit{V, V-I}, are most often used,
-and indeed most suitable. Whereas, IR CMDs, such as a \textit{J, J-K}
-CMD, are most suitable for mass derivation \cite[see references and
-discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
+colour-colour diagrams (CMDs and CoCoDs respectively, hereafter).
+Therefore, in this Section, we demonstrate the prohibitive effects on
+the broadband photometry of varying our input parameters. In this
+Section we, in particular, relate the discussed features of disc
+structures (\ref{disc_struct}) and the resulting simulated SEDs
+(\ref{sed_analysis}) in terms of the derived photometry, in Section
+\ref{indv_phot}. Furthermore, we explore the consequences of our model
+grid on the derivation of the primary parameters of age, mass and disc
+fractions, from populations, in Section \ref{populations}. This in
+turn leads to highlighting selection effects with, for instance, the
+mass to accretion rate relation.
 
@@
 and $M_J$, $(J-K)_0$ (\textit{right panels}) of naked stars with
-accretion rates of -2, -9 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, shown as black, red and blue
-lines resepctively (in \textit{all panels}). The \textit{top panels},
+accretion rates of -12, -9 and -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, shown as black, red and blue
+lines respectively (in \textit{all panels}). The \textit{top panels},
 then show the two rotational periods of 5 and 0.5 days, as dashed and
-solid lines respectively, for a coverage of 10\%. The \textit{bottom panels},
-then show the two areal spot coverages of 1 and 10\%, as dashed and
-solid lines respectively, for a rotational period of 5 days.
+solid lines respectively, for a coverage of 10\%. The \textit{bottom
+  panels}, then show the two areal spot coverages of 1 and 10\%, as
+dashed and solid lines respectively, for a rotational period of 5
+days.
 
@@
  \caption{Figure showing the naked systems for accretion rates of -8,
-   -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, shown in
+   -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, shown in
    \textit{all panels} as blue, red and black lines respectively. The
@@
    10\% (\textit{bottom panels}). For accretion rates of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (black line, \textit{all
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (black line, \textit{all
      panels}), are representative of all models at this rate, as the
@@
 \ref{Tacc}, show, $L_{\rm acc}\propto 1- \frac{R_*}{R_{\rm inner}}$
-and $T_{\rm acc}\propto \frac{L_{\rm
-    acc}}{A^{\frac{1}{4}}}$. Therefore, the temperature of the
+and $T_{\rm acc}\propto (\frac{L_{\rm
+    acc}}{A})^{\frac{1}{4}}$. Therefore, the temperature of the
 accretion hot spot increases as the coverage lowers and the rotational
@@
 move blueward. This is as the lower accretion rates have lower hot
-spot temperatures, with peak wavelengths between 1 and 3 $\mu$m
-(corresponding to temperatures of $~$2800K to $~$900K, the range of
+spot temperatures, with peak wavelengths between 1 and 3\,$\mu$m
+(corresponding to temperatures of $~$2800\,K to $~$900\,K, the range of
 the BD photosphere). This leads to increases in the red flux and
@@
 solid to dashed lines) results in a move redward in the CMD. This can
-be understood by observing the blue solid lines in the \textit{top
+be understood by observing the solid blue lines in the \textit{top
   panels} of Figure \ref{acc_dom}. Essentially, the reduction in spot
 temperature moves the accretion flux to much shorter wavelengths,
-$~$0.5 to $~$0.3 $\mu$m, meaning that the flux in the $J$ and $K$
+$~$0.5 to $~$0.3\,$\mu$m, meaning that the flux in the $J$ and $K$
 bands becomes more like the photosphere, and less dominated by
@@
 lines) shows a move blueward in the CMD, resulting in changes of the
-peak accretion flux emission from $~$0.58 to $~$0.5 $\mu$m, meaning
+peak accretion flux emission from $~$0.58 to $~$0.5\,$\mu$m, meaning
 significant flux from the accretion hot spot will still fall in the
@@
 inclinations of 71 and 56$^{\circ}$ for accretion rates of -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively. The changes in
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, respectively. The changes in
 flux with inclination will clearly lead to a change in the observed
@@
 marked as crosses. The \textit{top} and \textit{bottom panels} show
-accretion rates of -12, -9 and -7 as black, red and blue lines. The
-solid lines are for objects with rotational periods of 0.5 days and
-the dashed lines are for periods of 5 days. The \textit{inset panel}
-within the \textit{bottom panels} shows an enlargment of the section
-of inclinations from 40 to 80$^{\circ}$. For \textit{all panels} the
-vertical dotted lines show the inclinations for which significant
-drops in flux are observed (see Figure \ref{flare_inc}) for -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in black and blue respectively.
+accretion rates of -12, -9 and -7
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black, red and blue lines.
+The solid lines are for objects with rotational periods of 0.5 days
+and the dashed lines are for periods of 5 days. The \textit{inset
+  panel} within the \textit{bottom panels} shows an enlargement of the
+section of inclinations from 40 to 80$^{\circ}$. For \textit{all
+  panels} the vertical dotted lines show the inclinations for which
+significant drops in flux are observed (see Figure \ref{flare_inc})
+for -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in black and
+blue respectively.
 
@@
    to \ref{sub_181}. The accretion rates of -7, -9 and -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as blue, red and
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as blue, red and
    black lines respectively. The individual points are shown as
@@
    been enlarged and is shown as the \textit{inset panel}. Note the
-   models for -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are coincident
+   models for -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are coincident
    in this Figure. \textit{All panels} show the inclinations are which
    obscuration occurs for -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as dashed black and blue
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as dashed black and blue
    lines respectively. \label{flare_mag}}
@@
 systems. Figure \ref{flare_VVI} shows $M_V$, $(V-I)_o$ CMDs for the
-accretion rates of -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$,
-as the \textit{left} and \textit{right panels} resepctively. The
+accretion rates of -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$,
+as the \textit{left} and \textit{right panels} respectively. The
 systems are those shown in Figure \ref{flare_-12_183} and
@@
 which significant drops in flux were found in Figure \ref{flare_inc}
-in red text.
+are noted in red text.
 
@@
    isochrones at the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ for the \textit{left} and
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for the \textit{left} and
    \textit{right panels} respectively (with an areal coverage of 10\%
@@
    predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
-   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ models respectively,
+   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ models respectively,
    and these are denoted by the text within the
@@
 Figure \ref{flare_VVI} shows that as the system changes in inclination
-it leads to a sigificant dimming in both cases. The inclinations from
-\ref{flare_inc} where significant flux is lost are shown and it can be
-seen that a significant drop in magnitude is apparent just before this
-inclination (as also shown in Figure \ref{flare_mag}). The models in
-\textit{both panels} get slightly redder as we increase to the
-obscuration angle, caused by scattered light from the disc this can be
-observed for the accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ in Figures \ref{rot_-12_1Myr}
+it leads to a significant dimming in both cases. The inclinations from
+Figure \ref{flare_inc} where significant flux is lost are shown and it
+can be seen that a significant drop in magnitude is apparent just
+before this inclination (as also shown in Figure \ref{flare_mag}). The
+models in \textit{both panels} get slightly redder as we increase to
+the obscuration angle, caused by scattered light from the disc this
+can be observed for the accretion rate of -12
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures \ref{rot_-12_1Myr}
 and \ref{comp_rot_-12}.
@@
 systems at face on inclinations, caused by the inner disc wall. This
-is particularily large for the higher accretion rate (\textit{right
+is particularly large for the higher accretion rate (\textit{right
   panel}). This increase in reddening for the higher accretion rates
@@
 Figure \ref{sub_179}. This curved inner edge also leads to less
-dependence of $(J-K)_0$ as a function of inclination angle, as
-compared to the lower accretion rate.
+dependence of $(J-K)_0$ on inclination angle, as compared to the lower
+accretion rate.
 
@@
 \ref{sub_181}. The accretion rates shown are -12, -7, -9 and -6
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as the \textit{top left},
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as the \textit{top left},
 \textit{bottom left}, \textit{top right} and \textit{bottom right
@@
 \ref{inner_VVI} show the naked isochrone at 1 Myr (with an areal
-coverage of 10\% and $\tau$ of 0.5 days), at the shown accretion
-rate. The dashed red line shows the BDD system matching the naked
-isochrone, except with $M_0.04M_{\odot}$, at all inclination rates,
-with the datapoints marked as crosses. The blue triangles are then the
-naked stars at $M_0.04M_{\odot}$. The points at which the thermal
-direct flux reaching the observer drops significantly are marked in
-red text for each system, as shown in Figures \ref{typ_curve} and
+coverage of 10\% and $\tau$ of 0.5 days), at the shown accretion rate.
+The dashed red line shows the BDD system matching the naked isochrone,
+except with $M_*=0.04M_{\odot}$, at all inclination rates, with the
+datapoints marked as crosses. The blue triangles are then the naked
+stars at $M_*=0.04M_{\odot}$. The points at which the thermal direct
+flux reaching the observer drops significantly are marked in red text
+for each system, as shown in Figures \ref{typ_curve} and
 \ref{ext_curve}.
@@
    the naked isochrone at 1 Myr for the corresponding accretion rate
-   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The
+   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The
    dashed red line is the BDD isochrone at the same age and accretion
@@
 Figure \ref{inner_VVI} shows for the $M_V$, $(V-I)_0$, the inclination
-increase again dims the star for these models and moves it intially
+increase again dims the star for these models and moves it initially
 redward, until it exceeds the expected obscuration angle, found from
@@
 through the accretion rates from -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (\textit{top left panel}) to -6
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (\textit{bottom right panel})
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (\textit{top left panel}) to -6
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (\textit{bottom right panel})
 the transition from edge-on to face-on system tends to a sharper
@@
 isochrones are initially much redder than their naked counterparts, as
-expeted due to IR excesses caused by the disc inner edges. As the
+expected due to IR excesses caused by the disc inner edges. As the
 inclination increase for the lower accretion rates (\textit{top left}
@@
 
-\section{Populations}
+\subsection{Populations}
 \label{populations}
@@
 plots in this section the magnitude and colours for the
-$M_*=0.01M_{\odot}$ at high inclinations become extremely faint and
-red, respectively. In some cases these objects appear slightly without
-the scale of the diagram the axes where limited in this way to be able
-to show the changes in colour an magnitude for the majority of stars
+$M_*=0.01M_{\odot}$ systems at high inclinations become extremely
+faint and red. In some cases these objects appear slightly without the
+scale of the diagram the axes were limited in this way to be able to
+show the changes in colour and magnitude for the majority of stars
 better. The colours and magnitudes for these lowest mass stars are not
-necessarily unreliable but simple hinder the aesthetics of the plots,
+necessarily unreliable but simply hinder the aesthetics of the plots,
 and as they are at the limits of our grid we have decided to omit them
@@
 
-\subsection{Age and Mass Derivations}
+\subsubsection{Age and Mass Derivations}
 \label{age_mass_pop}
@@
 \textit{panels} of the Figures \ref{spread_opt_VVI_typ} and
-\ref{spread_opt_VVI_ext} then seperate the systems by the input
+\ref{spread_opt_VVI_ext} then separate the systems by the input
 variables. The \textit{top left panel} shows either the accretion
@@
 systems with areal coverages of 1 and 10\% as blue and red dots
-resepectively. The \textit{top right panels} then shows systems with
+respectively. The \textit{top right panels} then shows systems with
 rotational periods of 0.5 and 5 days as blue and red dots
 respectively. Finally, the \textit{bottom right panels} show the
-systems seperated by inclination. These groups are $\theta \leq
+systems separated by inclination. These groups are $\theta \leq
 48^{\circ}$ as blue dots (classed as face-on systems), $\theta> 56$ \&
@@
    accretors ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The black solid and dashed
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The black solid and dashed
    lines in \textit{all panels} are the naked star isochrones for
-   accretion rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+   accretion rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
    respectively. The \textit{top left} only shows the 1 Myr pre-MS
@@
    background population. The dots are the data for typical accretors
-   for models at 1 Myr. The data are then seperated by input
+   for models at 1 Myr. The data are then separated by input
    variables, in the \textit{panels}. The \textit{top left panel}
    shows three accretion classes, -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as blue, black and red dots
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as blue, black and red dots
    respectively (the lowest two accretion rates are grouped as they
@@
 the CTTS counterparts). Indeed miss classification of a BDD system as
-a CTTS system has already been revealed in \cite{}**CHECK WHITE AND
-BASRI. Furthermore, scatter, although somewhat reduced, can be
-observed in the simulated photometry of the negligibly accreting
-systems, for example in the \textit{top left panel} some red dots,
-accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (which
-will be negligible compared to the photospheric flux, see Figure
-\ref{acc_dom}), still scatter significantly. These objects may still
-be included in a `wide' photometric selection. This scatter is a
+a CTTS system has already been revealed in
+\cite{2003ApJ...582.1109W}. Furthermore, scatter, although somewhat
+reduced, can be observed in the simulated photometry of the negligibly
+accreting systems, for example in the \textit{top left panel} some red
+dots, accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
+(which will be negligible compared to the photospheric flux, see
+Figure \ref{acc_dom}), still scatter significantly. These objects may
+still be included in a `wide' photometric selection. This scatter is a
 strong function of inclination, as shown in the \textit{bottom right
@@
   right panel} shows that this occurs for inclinations above around
-71$^{\circ}$ (as found in Figure \ref{flare_inc}) in most cases yet
-even for the lower inclination angles some objects have very faint
-magnitudes, this is due to the disc flaring leading to a smaller
+71$^{\circ}$ (as found in Figure \ref{flare_inc}) in most cases.
+However, even for the lower inclination angles some objects have very
+faint magnitudes, this is due to the disc flaring leading to a smaller
 opening angle and is discussed in Section \ref{disc_struct}. The
@@
 generally, correlated with accretion rate. Effectively, as the
-accertion rate increases the BDD system moves farter away from the
+accretion rate increases the BDD system moves farther away from the
 isochrone and is therefore less likely to be classified as a BDD
-system and included in any taget samples of such objects. The
+system and included in any target samples of such objects. The
 \textit{top right panel} shows that the scatter, in $M_V$, in our
@@
 panel also shows that scatter in this diagram is not obviously
-correlated with the rotation period and therefore inner edge
-position. Overall, as found in \cite{2004MNRAS.351..607W}, the
-dominant scattering effect for BD disc systems in an optical CMD
-appears to be caused by accretion rate and inclination, and therefore
-obscuration effects of the disc on the star. This suggests that for a
-given photometric survey of BDD systems accreting at typical accretion
-rates and with an expected range of inclinations (centred on around
+correlated with the rotation period and therefore inner edge position.
+Overall, as found in \cite{2004MNRAS.351..607W}, the dominant
+scattering effect for BD disc systems in an optical CMD appears to be
+caused by accretion rate and inclination, and therefore obscuration
+effects of the disc on the star. This suggests that for a given
+photometric survey of BDD systems accreting at typical accretion rates
+and with an expected range of inclinations (centred on around
 60$^{\circ}$) one would expect to exclude a significant fraction of
@@
    accretors, $\dot{M}\geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. In this Figure the solid
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. In this Figure the solid
    black line now shows naked systems with an accretion rate of -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as opposed to -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, as in Figure
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (as opposed to -12
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as in Figure
    \ref{spread_opt_VVI_typ}, the dashed black line is still for an
    accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. \label{spread_opt_VVI_ext}}
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. \label{spread_opt_VVI_ext}}
 \end{figure*}
@@
 naked isochrone (the naked isochrone at -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ is shown for
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ is shown for
 comparison). Comparison of the \textit{four panels} again show that,
@@
 Similar scattering, as observed in Figure \ref{spread_opt_VVI_typ},
-occurs when using CMDs constructed using \textit{R, R-I} \citep[using
-the photometric system of][]{1998A&A...333..231B}. Figure
-\ref{spread_opt_RRI_typ} shows the \textit{R, R-I} CMD.
+occurs when using CMDs constructed using $M_R$, $(R-I)_0$ \citep[using
+the photometric system of][]{1998A&A...333..231B}, except that the 1
+Myr pre-MS isochrone has been omitted. Figure \ref{spread_opt_RRI_typ}
+shows the $M_R$, $(R-I)_0$ CMD.
 
@@
 Figure \ref{spread_opt_VVI_ext} except that the naked star isochrone
-at an accretion rate of -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ is
+at an accretion rate of -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ is
 not shown as it lies significantly blueward of the CMD.
@@
  \caption{As for Figure \ref{spread_opt_VVI_ext}, except that the -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ isochrone is not shown (lies
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ isochrone is not shown (lies
    significantly blueward of locus of data), and the pre-MS isochrone
@@
 
-GOT HERE**combined the next two paragraphs
-
-Now summarise on the effects of the CMD classification*** Then sort
-out effect on the rotational period to JK excess and Mstar to Macc
-relation.**
-
 Therefore, if one adopts the range of input parameters we have used
@@
 accreting BD stars and BDD systems, with typical accretion rates and
-range of inclinations, will exhibit a scatter in apparent isochronal
-age of $>$10 Myr. Furthermore, some objects will be scattered below
-and blueward of a 10 Myr isochrone. This has been shown for CMDs in
-\textit{V, V-I} and \textit{R, R-I}. It is important to note at this
-point that these conclusions are qualitative, and obviously based on
-our assumptions. However, the repercussion for isochronal age
-derivation and sample selection in the BD regime could be
-profound. Indeed this study has only included the effects of current
-or ongoing accretion from a disc, it has totally neglected any effects
-of accretion, both past and present, on the evolution of the central
-star. This past accretion could also act to reduce the stars radius,
-accelerating contraction
+range of inclinations, will exhibit a significant scatter in apparent
+isochronal age of ($>$10 Myr). Furthermore, objects with typical (and
+extreme) accretion rates are scattered sufficiently in CMD space to
+prohibit their identification as pre-MS BDs. Indeed, these objects
+would not be included in a photometrically selected sample of BDs, and
+as such are unlikely to be assigned the correct masses or ages. The
+scatter from the naked 1 Myr systems, generally, increases with
+increasing accretion rate. It is important to note at this point that
+these conclusions are qualitative, and obviously based on our
+assumptions. However, the repercussion for isochronal age derivation
+and sample selection in the BD regime could be profound. Indeed this
+study has only included the effects of current or ongoing accretion
+from a disc, it has neglected any effects of accretion, both past and
+present, on the evolution of the central star. This past accretion
+could also act to reduce the stars radius, accelerating contraction
 \citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
 additional scatter in a coeval population proportional to the range in
-accretion rates \citep[See][for full
-discussion]{2008MNRAS.386..261M}. Our findings support those of
-\cite{2004MNRAS.351..607W}, showing that a significant scatter is
-caused by obscuration of the central source by the central disc. In
-addition we have shown that the scatter blueward, into the CTTS or
-background MS locus, is caused by active accretion at levels found in
-CTTS stars, but currently not regularly recorded in stars classified
-or selected as BDs.
-
-Therefore, as for derivations of age, given our assumptions, and the
-adopted range of input parameters, a 1 Myr coeval population scatters
-significantly in a \textit{J, J-K} CMD. The \textit{J, J-K} CMD is
-representative of CMDs constructed from the \textit{JHK}
-passbands. So, qualitatively at least, derivation of masses using
-isochronal fitting of our simulated photometry would not produce
-reliable or accurate results. Again, as discussed for optical CMDs,
-these simulations do not include any of the effects of past or current
-accretion on the evolution of the central object, which is expected to
-significantly exacerbate the observed scatter. This is also true for
-the naked systems with small increases in accretion rate leading to
-significant scatters in the CMDs. Additionally, given the evidence
-discussed in \cite{2004MNRAS.351..607W}, supported by the evidence
-from our own simulated photometry shown in Figures
-\ref{spread_opt_VVI_typ}, \ref{spread_opt_VVI_ext},
-\ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext}, it is clear that
-young, accreting, BDD systems are likely to be misidentified when
-using photometric colours or magnitudes, even at generally canonical
-accretion rates. This casts doubt on the veracity of the mass to
-accretion rate relationship. For our model grid we have not assumed
-any such relation, therefore, as our data would also show a similar
-relation it suggests that the observed result may be caused by
-intrinsic scattering. The relation, $\dot{M}\propto M_*^{2}$ suggests
-that their is a dearth of lower mass stars accreting at higher
-rates. We have shown that for accretion rates in the range -12 to -9
+accretion rates \citep[see][for full discussion]{2008MNRAS.386..261M}.
+Our findings support those of \cite{2004MNRAS.351..607W}, showing that
+a significant scatter is caused by obscuration of the central source
+by the central disc. In addition we have shown that the typical
+accretion rates may scatter BDD systems into the region of a CMD
+occupied by the CTTS or background MS locus.
+
+The fact that scatter in the CMD increases with increasing accretion
+rate casts doubt on the veracity of the mass to accretion rate
+relationship. For our model grid we have not assumed any such
+relation, therefore, as our data would also show a similar relation it
+suggests that the observed result may be caused by intrinsic
+scattering. The relation, $\dot{M}\propto M_*^{2}$ suggests that their
+is a dearth of lower mass stars accreting at higher rates. We have
+shown that for accretion rates in the range -12 to -9
 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with higher
@@
 
-Therefore, again as for the optical case, given our assumptions and
-parameter space, BDD systems accreting at higher rates would not be
-identified with the correct mass in most cases using IR CMDs.
-
-\subsection{Disc fractions}
+Additionally, we have adopted the co-rotation radius as the initial
+location of our inner wall. This leads to an initial proportionality
+between the rotation rate and inner edge temperature. As discussed in
+Section \ref{disc_struct} this correlation will be modified due to
+dust sublimation effects, weakening the correlation. The derived
+photometry however, at varying inclinations, does not show a strong
+correlation in IR, $(J-K)_0$, colour with rotational rate, as proposed
+by \cite{1997AJ....114..288M}.
+
+\subsubsection{Disc fractions}
 \label{disc_fractions_phot}
@@
 limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
-8.0$\mu$m.
-
-Now switch to figures just showing inclination and accretion rate (not
-rotation rate).
-
-Whilst magnitudes are affected by accretion rates, ages, rotational
-periods etc, practically, for colour, colour plots the inclination is key.
-
-TYPICAL ACCRETORS
-location in the cMD is proportonal to the accretion rate and
-inclination and this sontinues into the IR colours
-
-GOT HERE***
-for typical accretors the accretion rate becomes unimportant and the
-resulting thing is just inclination for extreme accretors the
-accretion rate becomes key again
-
-First a Jh jk colo col d to show this, all ages used both 1 and 10 Myr
-
-NOT SURE IF I SHOULD LIMIT BY AGE ALL THE DISC FRACTIONS PLOTS? used 1
-and 10 myr sample as age doesn't effect the position in the col-col
-plot very much
-
-WHERE TO PUT THIS** CLEARPAGE THING**
-show that only inclination and accretion matter, age notmimportant for
-discs, disc and non disc systems separation observed in panels where
-there are no black disc systems. For extreme accretors mention fact
-that the inner edge temperature is now function of accretion rate etc.
+8.0\,$\mu$m.
+
+As shown in Figure \ref{inner_temp}, Section \ref{disc_struct}, the
+inner edge temperature for typical accretors retains some correlation
+with rotation rate. In general the more slowly rotating objects having
+cooler inner edges. For the more extreme rotators the inner edge
+location is still weakly correlated with the inner edge
+temperature. In the extreme accretors case the correlation is caused
+by the radial fall in density, and therefore dust sublimation
+temperature as the inner edge is ablated. Therefore, for the extreme
+accretors the correlation between rotational period and inner edge
+temperature is lost. The inner edge temperature is in fact correlated
+with the flux and therefore accretion rate of the system. As shown in
+Figures \ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext} (in
+Section \ref{age_mass_pop}), there is no clear correlation in CMD
+position, and $(J-K)_0$ colour with rotation rate for either typical
+or extreme accretors. In fact any scatter in these Figures
+(\ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext}) appears to be
+most strongly correlated with accretion rate and inclination.
+
+Figures \ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext} show the
+$(J-H)_0$, $(J-K)_0$ CoCoDs for typical and extreme accretors
+respectively. The dots are the simulate BDD systems for both ages (as
+position in these CoCoDs is not a strong function of age) and masses,
+and the black crosses the naked systems, again at both ages (and all
+masses), for the accretion rates matching the shown BDD data. The
+\textit{panels} of these Figures then separate the BDD systems by
+accretion rate (\textit{top left}), areal spot coverage
+(\textit{bottom left}), rotational period (\textit{top right}) and
+inclination (\textit{bottom right}). The accretion rates of -9, -10
+and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as
+blue, black and red dots respectively in the \textit{top left panel}
+of Figure \ref{disc_frac_JHJK_typ}. For Figure
+\ref{disc_frac_JHJK_ext}, the \textit{top left panel} shows accretion
+rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown
+as blue, black and red dots respectively. The \textit{bottom left
+  panels} of both Figures \ref{disc_frac_JHJK_typ} and
+\ref{disc_frac_JHJK_ext} show the systems with areal spot coverages of
+1 and 10\% as blue and red dots respectively. The \textit{top right
+  panels} of both Figures \ref{disc_frac_JHJK_typ} and
+\ref{disc_frac_JHJK_ext} show the systems with rotational periods of
+0.5 and 5 days as blue and red dots respectively. Finally, The
+\textit{bottom right panels} of both Figures \ref{disc_frac_JHJK_typ}
+and \ref{disc_frac_JHJK_ext} show the systems with inclinations of
+$\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as
+black dots and $\theta \geq 71^{\circ}$ as red dots.
+
 \clearpage
@@
    for typical accretors ($\dot{M}<leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$). The dots are then all
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The dots are then all
    models (at 1 and 10 Myrs) with discs and the black crosses are the
-   naked systems, in \textit{all panels}. The data are then seperated
+   naked systems, in \textit{all panels}. The data are then separated
    by input variable in \textit{each panel}. The \textit{top left
      panel} shows accretion rates of -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, black and red dots
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as blue, black and red dots
    respectively. The \textit{top right panel} shows the systems with
@@
    areal spot coverages of 1 and 10\% as blue and red dots
-   respectively. Finally, the \textit{bottom right panel} seperates
+   respectively. Finally, the \textit{bottom right panel} separates
    the systems into three groups inclination, $\theta \leq$
@@
  \caption{As for Figure \ref{disc_frac_JHJK_typ} but for extreme
-   accretors, $\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+   accretors, $\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
    .\label{disc_frac_JHJK_ext}}
 \end{figure*}
+
+Figures \ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext} show
+that for typical and extreme accretion rates there is no clear
+correlation of rotation rate, areal coverage or inclination with the
+position in the CoCoD. Significantly no clear correlation between IR
+colours and rotation rate can be observed for the typical accretors.
+This suggests that the weak correlation found between inner edge
+temperature and rotational period does not produce a matching
+correlation with IR colours. For the extreme accretors, however, a
+correlation between IR colours and accretion rate is clear. As the
+accretion rate increases the systems move to redder CoCoDs. This is
+caused, as discussed by the dust inner edge being sublimated and the
+resulting sublimation decreasing, with density, radially. Therefore,
+one can not extend the predictions of \cite{1997AJ....114..288M},
+after adoption of a co-rotation radius to suggest that IR excesses may
+be correlated with rotation rates, for typical or extreme accretors.
+As can be seen for all the panels of Figures \ref{disc_frac_JHJK_typ}
+and \ref{disc_frac_JHJK_ext} there is a slight overlap between the
+naked or disc less objects (crosses) and the BDD systems (dots). This
+overlap is small, only some of the lowest mass naked objects appear
+redward of the main population. Generally, a well placed cut should
+identify a large proportion of the disc candidates as is well known,
+if there is little complication from variable extinction and a well
+defined photometric system. However, the fact that an overlap exist at
+all will lead to some confusion as to the position of any disc excess
+cut. For real data a cut will be placed at a user identified paucity
+or gap in the CoCoD. Therefore, in practice, if any other region of
+the population appears equally, or more, sparse the cut is likely to
+be miss-placed. In practice these disc fractions are known to be lower
+limits of the true values, so ostensibly a miss placed cut, missing
+some disc candidates is not problematic.
+
+The analysis in Section \ref{age_mass_pop} and Figures
+\ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext}, shows that
+accretion rate and inclination are the dominant variables controlling
+the photometric scatter, of the BDD systems. Therefore, for our
+subsequent analysis we will separate the systems using only these
+input variables.
+
+Figures \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} show
+CoCoDs for colours constructed using simulated IRAC photometry, for
+the typical and extreme accreting systems respectively. These two
+Figures contain the same data as Figures \ref{disc_frac_JHJK_typ} and
+\ref{disc_frac_JHJK_ext}, respectively. The naked systems are again
+shown as crosses and the BDD systems as dots. The \textit{left panels}
+of these Figures show $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs and
+the \textit{right panels} $([3.6]-[4.5])_0$, $([5.8]-[8.0])_0$
+CoCoDs. The \textit{top panels} then show the accretion rates of -9,
+-10, -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), for Figure
+\ref{disc_frac_irac_typ}, and -6, -7 and -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), for Figure
+\ref{disc_frac_irac_ext}, as blue, black and red dots
+respectively. The \textit{bottom panels} of both Figures show the
+systems with inclinations of $\theta \leq 48^{\circ}$ as blue dots,
+$\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
+71^{\circ}$ as red dots.
 
@@
  \caption{Figure showing typically accreting systems ($\dot{M}\leq$-9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$), in irac photometric
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), in irac photometric
    bands. The \textit{left panels} show the $([3.6]-[4.5])_0$ against
@@
      panels} the dots are disc systems and crosses naked systems. The
-   \textit{top panels} then seperate the systems by accretion rate
-   with, -9, -10 and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+   \textit{top panels} then separate the systems by accretion rate
+   with, -9, -10 and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
    as blue, black and red dots respectively. The \textit{bottom
-     panels} seperate the systems by inclination with $\theta \leq$
+     panels} separate the systems by inclination with $\theta \leq$
    48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
@@
    accretors, $\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.\label{disc_frac_irac_ext}}
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.\label{disc_frac_irac_ext}}
 \end{figure*}
+
+Figure \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} show that
+the naked and BDD systems are well separated. Supporting the view that
+IRAC magnitudes are well suited for disc candidate identification. For
+the typical accretors there is a possible correlation between
+inclination and position in the $([3.6]-[4.5])_0$, $([5.8]-[8.0])_0$
+CoCoD, (\textit{bottom right panel} of Figure
+\ref{disc_frac_irac_typ}). The systems which are edge-on
+(i.e. $\theta\geq$77$^{\circ}$) appear closer in colour to the naked
+systems. In the case of extreme the accretors the separation between
+the naked and BDD systems is correlated with accretion rate for both
+CoCoDs (\textit{top panels} of Figure
+\ref{disc_frac_irac_ext}). Effectively, as the accretion rate
+increases, in general the system moves to redder colours.
+
+Figure \ref{disc_frac_irac_mips_typ} and
+\ref{disc_frac_irac_mips_ext}, show the same data as Figure
+\ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext}, in the same
+format and with the same notations. Figures
+\ref{disc_frac_irac_mips_typ} and \ref{disc_frac_irac_mips_ext} show
+CoCoDs of simulated photometry from IRAC and MIPS magnitudes. For both
+Figures the \textit{left panels} show $([3.6]-[4.5])_0$,
+$([8.0]-24)_0$ and the \textit{right panels} $([3.6]-[5.8])_0$,
+$([8.0]-24)_0$ CoCoD, where 24, is the 24\,$\mu$m MIPS channel.
 
@@
    \textit{left panels} and $([3.6]-[5.8])$, $([8.0]-24)$ CMDs as the
-   \textit{right panels}, combining irac and mips photometric
-   channels. The sytems are again seperated by accretion rate and
+   \textit{right panels}, combining IRAC and MIPS photometric
+   channels. The systems are again separated by accretion rate and
    inclination angle in the \textit{top} and \textit{bottom} panels as
@@
    accretors ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$).\label{disc_frac_irac_mips_ext}}
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$).\label{disc_frac_irac_mips_ext}}
 \end{figure*}
+
+Figures \ref{disc_frac_irac_mips_typ} and
+\ref{disc_frac_irac_mips_ext} show that the BDD and naked systems are
+very well separated in CoCoDs utilising IRAC and longer wavelength
+MIPS data. For the systems with typical accretion rates, Figure
+\ref{disc_frac_irac_mips_typ}, no correlation between CoCoD position
+and accretion rate is obvious (\textit{top panels}). The \textit{lower
+  panels} of this Figure show that, in general, the locus of BDD stars
+is spread similarly for all but edge-on systems, which sometimes
+appear a little redder in $([8.0]-24)_0$. For the extreme accretors,
+Figure \ref{disc_frac_irac_mips_ext}, however, correlations in CoCoD
+position with both inclination and accretion rate are clear. The
+\textit{top panels} of Figure \ref{disc_frac_irac_mips_ext} show that
+as the accretion rate increases, in general, the systems move to
+redders colours in $([3.6]-[4.5])_0$ or $([3.6]-[5.8])_0$
+(\textit{left} and \textit{right panels} respectively). This is to be
+expected from our previous analysis of IRAC CoCoDs using this
+photometry. The \textit{lower panels} of Figure
+\ref{disc_frac_irac_mips_ext} show a correlation of inclination angle
+with the colours in both axes. These two correlations essentially mean
+that we can roughly identify systems, with regard to inclination and
+accretion rate, by their position within this CoCoD. For instance,
+extreme accretors with lower accretion rates seen face-on will occupy
+the bottom left of the BDD locus, with edge-on systems with the
+maximum accretion rate appearing to the top right. Comparing the
+scales on Figures \ref{disc_frac_irac_mips_typ} and
+\ref{disc_frac_irac_mips_ext} shows that these systems slightly
+overlap, but in general the extreme accretors will lie redward of the
+typical accretor locus in both colours.
+
+Figure \ref{disc_frac_mips} shows CoCoDs constructed solely from the
+longer wavelength MIPs photometry. Figure \ref{disc_frac_mips} shows
+the BDD data shown in previous Figures (such as Figure
+\ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext}) in $(24-70)_0$,
+$(70-160)_0$ CoCoDs. The \textit{left} and \textit{right panels} show
+the typically and extreme accreting systems, respectively. The
+\textit{inset panels}, in \textit{both top panels}, show larger areas
+to include the naked systems, as they are well removed from the BDD
+locus.
 
@@
  \caption{Figure showing CMDs of mips photometry for the typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) and
-   extreme ($\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$)
+   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and
+   extreme ($\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$)
    accretors, as the \textit{left panels} and \textit{right panels}
-   respectively. The \textit{top panels} seperate the systems by
+   respectively. The \textit{top panels} separate the systems by
    accretion rate in the way described in Figures
@@
    \textit{left} and \textit{right panels} respectively. The
-   \textit{bottom panels} then seperate the systems by inclination as
+   \textit{bottom panels} then separate the systems by inclination as
    described in Figure \ref{disc_frac_irac_typ}. The \textit{inset
@@
 \end{figure*}
+
+Figure \ref{disc_frac_mips} shows, in the \textit{inset panels}, that
+BDD and naked systems are very well separated in CoCoDs constructed
+using MIPs photometry. For the typical accretors, \textit{left panel},
+the position within the CoCoD appears strongly correlated with
+inclination only, with the edge on systems moving away from the main
+BDD locus, as expected. For the extreme accretors, \textit{right
+  panel}, significantly more structure is apparent. In this case as
+the accretion rate increases the systems move redward in both colours.
+Additionally, as the inclination increases the systems move to redder
+$(24-70)_0$ colours. This suggests, as with Figure
+\ref{disc_frac_irac_mips_ext}, for objects with extreme accretion
+rates, CoCoDs of this sort may help distinguish the characteristic
+inclination and accretion rate of the system. In practice, due to
+saturation and reddening effects and small sample sizes this may prove
+difficult. For our study this is interesting in that the fluxes for
+wavelengths longward of 24\,$\mu$m come from regions at temperatures of
+$~$120 K and below. This suggests that the outer disc flaring, as
+discussed in Section \ref{disc_struct}, leads to significantly
+structural changes in the outer, cooler disc, as a function of
+accretion rate. In addition, observing the separation of the naked and
+BDD systems within the CoCoDs it is clear that for systems within our
+grid, the best disc indicators are at longer wavelengths, as is well
+known from observations.
+
+Disc fractions are also derived using the $\alpha$ value
+\citep{2006AJ....131.1574L}, essentially a slope of the SED between
+two wavelengths (at wavelengths longer than the stellar flux peak).
+Figure \ref{disc_frac_alpha} shows the derived $\alpha$ values between
+3.6 and 8.0\,$\mu$m for our entire model grid (against an arbitrary
+model number), with dots showing BDD systems and crosses showing naked
+systems. The \textit{left} and \textit{right panels} of Figure
+\ref{disc_frac_alpha} show the typical and extreme accreting systems
+respectively. For TTS $\alpha>-$2 distinguishes between systems with
+and without discs \citep{2009arXiv0901.2603K}. As can be seen in
+Figure \ref{disc_frac_alpha} almost all the typical, and all of the
+extreme accreting BDD systems would be successfully identified using
+this criterion. Suggesting that the $\alpha$ value is a reliable disc
+indicator for BD systems. The \textit{top panels} of Figure
+\ref{disc_frac_alpha} show the alpha values separated by accretion
+rates, with -9, -10 and -11 \& -12, or -6, -7 and -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue, black and red
+dots respectively. The \textit{bottom panels} differentiate systems
+seen at different inclinations with $\theta \leq 48^{\circ}$ as blue
+dots, $\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
+71^{\circ}$ as red dots.
 
@@
    estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4$\mu$m). The \textit{left panels} show typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
+   ($\lambda>$4\,$\mu$m). The \textit{left panels} show typical
+   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors
    and the \textit{right panels} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors. The \textit{top
-     panels} seperate the systems by accretion rate in the way
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors. The \textit{top
+     panels} separate the systems by accretion rate in the way
    described in Figures \ref{disc_frac_irac_typ} and
    \ref{disc_frac_irac_ext} in the \textit{left} and \textit{right
-     panels} respectively. The \textit{bottom panels} then seperate
+     panels} respectively. The \textit{bottom panels} then separate
    the systems by inclination as described in Figure
@@
 
+Figure \ref{disc_frac_alpha} shows that except for a few systems
+($~\frac{1}{50}$), all of which are typical accretors at edge-on
+inclinations, a cut of $\alpha>-$2 would identify all of our BDD
+systems. Furthermore, the \textit{top left} panel shows that for
+typically accreting systems there would be no significant bias in
+selection with accretion rate. The \textit{bottom left panel} shows
+that the lowest $\alpha$ values are only apparent for the edge-on
+systems. The \textit{right panels} of Figure \ref{disc_frac_alpha},
+show that for extreme accretors the systems are well above the disc
+discriminator line, and move to greater $\alpha$ values with
+increasing accretion rate.
+
+In summary, for our model grid, the best disc discriminators are MIPs
+CoCoDs and the $\alpha$ values. With, in general, correlations in
+position within the CoCoDs or the $\alpha$ values seen with accretion
+rate only for the extreme accretors.
+
 \subsubsection{Practical Observations}
-PRACTICAL OBSERVATIONS:
+\label{object}
+
+Some recent studies of disc fractions for BD populations have used
+data from the \textit{Spitzer} IRAC camera. Figures \ref{irac_cut},
+\ref{irac_cut_2} and \ref{irac_cut_3} show the simulated photometry
+for our complete model grid. Naked BDs are shown as crosses and BDD
+systems as dots, with 1 and 10 Myrs data shown as blue and red dots
+respectively. The dashed lines are cuts used in three recent
+publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
+a study of IC348, Figure \ref{irac_cut_2} from
+\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis and Figure
+\ref{irac_cut_3} a study of the Taurus region from
+\cite{2008ApJ...674..336G}. In these cases the effects of extinction
+are either negligible in the plotted colours, with values of
+$E([3.6]-[4.5])<0.04$ and $E([4.5]-[5.8])<0.02$ for IC348 and $A_V
+\leq$4 mag \citep[which will be negligible in the IRAC
+CoCoD,][]{2004ApJS..154..363A}, or the cuts have been placed in
+intrinsic colour space as for $\sigma$ Orionis.
 
@@
    reliable colours. The \textit{left panel} shows the typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
+   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors
    and the \textit{right panel} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors.\label{irac_cut}}
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors.\label{irac_cut}}
 \end{figure*}
@@
    do not extend far enough into the IRAC passbands to derive reliable
-   colours. The systems are seperated by age as described in Figure
+   colours. The systems are separated by age as described in Figure
    \ref{irac_cut}. The \textit{left} and \textit{right panels} again
    show the typical ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) and extreme ($\dot{M} \geq$
-   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors respectively as
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and extreme ($\dot{M} \geq$
+   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors respectively as
    in Figure \ref{irac_cut}.\label{irac_cut_2}}
@@
 
-CASE STUDY:
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/irac_cut_3.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure showing an observational cut used in
+   \citet{2010arXiv1004.2541M} for data of the Taurus cloud. The
+   criteria applied for BDD system selection are that of
+   \citet{2008ApJ...674..336G}. It must be noted that the naked stars
+   of $M=$0.01$M_{\odot}$ are not included in this figure as their
+   SEDs do not extend far enough into the IRAC passbands to derive
+   reliable colours. The systems are separated by age as described in
+   Figure \ref{irac_cut}. The \textit{left} and \textit{right panels}
+   again show the typical ($\dot{M} \leq$ -9
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and extreme ($\dot{M} \geq$
+   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors respectively as
+   in Figure \ref{irac_cut}.\label{irac_cut_3}}
+\end{figure*}
+
+As can be seen from Figures \ref{irac_cut}, \ref{irac_cut_2} and
+\ref{irac_cut_3} almost all of the disc systems from our simulated
+photometry would be correctly identified using these cuts. It is
+important to note that our conclusions so far have been drawn from
+differential photometric arguments, in this case we are using
+intrinsic colours and these values are extremely sensitive to changes
+in zero point and photometric calibration. Figure \ref{irac_cut} shows
+that other than a few typically accreting systems the observational
+cut of \cite{2005ApJ...631L..69L} would select all of the BDD systems
+in our grid. Figure \ref{irac_cut_2} shows that the cut of
+\cite{2008ApJ...688..362L} would miss some typical and a very small
+number of extreme accreting BDD systems. Figure \ref{irac_cut_3} shows
+only very few BDD systems will be missed. The number of BDD systems
+not identified for Figure \ref{irac_cut_2} and \ref{irac_cut_3} is
+larger than that of \ref{irac_cut}, but these Figures show that there
+is no preferential selection based on age. A comparison between Figure
+\ref{irac_cut_2} and the \textit{bottom right panel} of Figure
+\ref{disc_frac_irac_typ}, shows that all of the missed BDD systems are
+edge-on systems. Given, that extreme reddening may move naked stars
+into the BDD region selected, in general, dis fractions are usually
+quoted as lower limits. Therefore, a small number of miss-identified
+BDD system is a small effect. This allows us to conclude, that
+ubiquitously used BDD cuts used in IRAC CoCoDs are reliable when
+applied to our simulated dataset.
+
+In a future publication we will release a fitting tool to be used in
+conjunction with the online database of naked and BDD systems (for
+both photometry and SED fitting). Therefore, we will be performing
+fits to observed systems using our grid. In this work we simply pick
+an example star and highlight its position in CMD and CoCoD space,
+compared to models covering the expected range of parameters.
+\cite{2004A&A...424..603N} derive an accretion rate of -9
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for $\rho$ Ophiucus 102. For
+this object \cite{2002A&A...393..597N} find a spectral type of M6,
+$T_{\rm eff}$ of 2700\,K, an extinction of $A_V$=3.0, a mass of
+$M_*$0.04-0.08$M_{\odot}$ and a distance of 150pc. Photometry for
+$\rho$ Ophiucus 102 is also published in \cite{2006A&A...452..245N},
+in $J$, $H$ and $K$. Additionally, $R$ and $I$ photometry has been
+published for this object in \cite{2005AJ....130.1733W}. We have
+adjusted our model spectra in the range $M_*$=0.04-0.08$M_{\odot}$,
+with accretion rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
+(for all remaining input parameters) to the correct distance and
+reddening. Figure \ref{rho_oph_102} shows, as dots, our BDD systems
+with the parameters in the range quoted, with $\rho$ Ophiucus 102 is
+shown as a black star. The \textit{panels} of Figure \ref{rho_oph_102}
+then show example CMDs and CoCoDs. The \textit{top left panel} shows a
+$M_J$, $(J-H)_0$ CMD, the \textit{bottom left panel} a $M_R$,
+$(R-I)_0$ CMD, the \textit{top right panel} a $M_J$, $(J-K)_0$ CMD and
+finally, the \textit{bottom right panel} a $(J-K)_0$, $(J-H)_0$ CoCoD.
 
@@
    parameters to $\rho$ Ophiucus 102 from
-   \citet{2002A&A...393..597N}. The object $\rho$ Ophiusucs 102 is
+   \citet{2002A&A...393..597N}. The object $\rho$ Ophiucus 102 is
    shown in \textit{all panels} as a black star, the BDD systems are
-   the seperated by age, with the 1 and 10 Myr systems appearing as
+   the separated by age, with the 1 and 10 Myr systems appearing as
    blue and red dots respectively. The \textit{top left panel} shows a
@@
 
-SHOW ROTATION RATE CORRELATION LOST AS  \cite{1997AJ....114..288M} HAD
-FLAT DISCS FACE ON WE HAVE VIEWING ANGLES AND VERTICAL HYDRO
-
-we find no correlation in general so is unlikely to effect the
-population selection or attempts to show slow rotator to disc presence
-correlations: i.e. nairn
-
-Now we conclude on the rotaton rate to IR relation and the mass to
-accretion rate relationship.
-For individal model the J-K is dependent on lots of variables so the
-correlation with rotation rate is non existent
-
-NOTE ABOUT SUBSEQUENT PAPER WITH ANALTIC SOLUTIONS
-
-\subsection{Summary}
-
-summarise on the photometric sections
+We have not performed a formal fitting of the object $\rho$ Ophiucus
+102. However, qualitatively, Figure \ref{rho_oph_102} shows that for
+$\rho$ Ophiucus 102 the colours are well matched by our grid, yet the
+magnitude is somewhat brighter. This could be an indication of
+uncertainties in the distance to the object, reddening or magnitudes.
+A full investigation is beyond the scope of this paper, but, as stated
+in a future publication we will release an online fitting tool to be
+used in conjunction with our grid.
 
@@
 
-COPY IN THE MAIN FROM PERVIOUS PAPER REWRITE WITH BETTER EMPHASIS.
-
-\subsection{Derivation of Primary parameters}
-
-\subsection{Consequences for Accretion Rate to Stellar Mass
-  relationship}
+We have constructed a model grid of SEDs, and subsequently photometric
+magnitudes and colours, for actively accreting BDs with or without an
+associated accretion disc. We have modeled the photospheric flux from
+these BDs by adopting (and interpolating) the interior `DUSTY00'
+models of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
+atmospheric models of \cite{2000ApJ...542..464C}. We have then assumed
+that accretion occurs from an inner edge of a magnetically truncated
+accretion disc (truncated at the co-rotation radius). The accretion
+flux is calculated using a simple blackbody emission, given the
+derivation of a characteristic spot effective temperature. SEDs were
+then produced for both naked BDs and BDD systems. For the BDD systems
+we have modeled the disc using the TORUS radiative transfer code using
+the Lucy radiative transfer algorithm and incorporating dust
+sublimation and including a treatment of vertical hydrostatic
+equilibrium (see Section \ref{model} for a discussion of the code). To
+produce a `grid' of simulated systems we have varied several input
+parameters namely: stellar mass, stellar age, stellar rotation rate,
+accretion rate, the areal coverage of the accretion stream and the
+system inclination (the disc mass was fixed). The ranges of these
+variables were selected to represent and bound typical pre-MS BD
+systems, justification is provided using evidence from observational
+studies in Section \ref{par_space} and a final list of the values of
+these variables can be found in Table \ref{par_space_table}.
+
+Accepting our assumptions, parameter ranges and radiative transfer
+code our resulting simulated dataset has allowed us to qualitatively
+explore the effects of \emph{active} (current not past accretion)
+accretion on disc structure. Furthermore through the simulation of
+observations we have explored the effects of accretion, and disc
+presence, on both the SEDs, and photometric colours and magnitudes of
+these systems.
+
+As discussed in Section \ref{disc_struct} vertical hydrostatic
+equilibrium, when applied to BDs, leads to increased flaring, when
+compared to CTTS. This has previously been explored by
+\cite{2004MNRAS.351..607W}. However, in our study we have included a
+simple treatment of accretion. This leads to increased flaring as more
+flux reaches the outer disc, and subsequently lower opening angles for
+BDD systems with higher accretion rates. Furthermore, the addition of
+dust sublimation has shown that for BDD systems the inner disc
+location, temperature and vertical size \& shape also varies with
+accretion rate. The inner edge position is correlated with temperature
+for the lower accreting models as suggested by
+\cite{1997AJ....114..288M}. For the systems with higher accretion
+rates the inner edge temperature is weakly correlated with
+temperature, mainly due to the radial fall in density and therefore
+dust sublimation temperature. The inner disc edge, initially
+prescribed as a vertical wall, then becomes concave and finally convex
+as dust sublimation is increased (with increasing flux from higher
+rates of accretion).
+
+Subsequently, the SEDs of BD systems with typical accretion rates and
+associated discs, are changed significantly from the assumed
+underlying photospheric model flux, and therefore become difficult to
+classify. In Section \ref{sed_analysis} we have shown that the BD
+photosphere becomes `swamped' or overwhelmed by the accretion flux for
+rates of $\dot{M}>$-9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The outer
+disc flaring observed in the BDD systems was shown to cause
+occultation and a subsequent, sharp, fall in flux at an inclination
+which decreases for more systems with higher accretion rates. The
+thermal direct flux emanating from the disc inner edge was found to
+fall less dramatically with inclination for the systems with a curved
+inner boundary, as expected from the work of
+\cite{2007ApJ...661..374T}.
+
+Subsequent derivation of photomertric magnitudes has allowed us to
+demonstrate that, as expected, increased accretion without disc
+presence, moves our naked systems to bluer and brighter magnitudes.
+Once a disc is added the increase in accretion flux interacts with the
+disc and does not necessarily lead to a simple motion toward brighter
+magnitudes and bluer colours. The increased flaring and obscuration
+present in BDD systems, over CTTS, leads to rapid falls in magnitude
+with inclination as an accretion (or flaring) dependent inclination.
+Furthermore, the disc inner edge leads to a shift redwards with
+increasing accretion rate as more flux is intercepted by the inner
+edge and the inner edge becomes convex and `puffed up'. For more
+typically accreting BDD systems with vertical inner edges, the motion
+in a CMD, with inclination, is more disjointed.
+
+In practice, however, most parameters for BDD systems are derived for
+populations. We have shown, in Section \ref{photometry} that
+derivation of an \emph{isochronal} (or photometric) age from our
+simulated photometry of a coeval BD sample, with typical accretion
+rates and associated circumstellar discs, would be inaccurate and
+exceedingly difficult. Indeed, the resulting photometric colours and
+magnitudes could be indicative of a more distant redenned CTTS
+population. For more extreme accretion rates the scatter, in CMD
+space, is significantly far from the pre-MS locus and as such these
+stars have little chance of being selected as BDs. As discussed in
+Section \ref{results} this does not include any effects due to past
+accretion on the evolution of the central star, which acts to
+accelerate the gravitational contraction and make the star appear
+older \citep{1999MNRAS.310..360T,1999A&A...342..480S}, further
+scattering the apparent age of a coeval population.
+
+Concordantly, \emph{isochronal} derivations of mass and therefore
+IMFs, for our simulated photometry, of a coeval population of
+accreting BDs with associated discs, would be inaccurate and
+problematic. Again caused by the changes in the SEDs as a result of
+the accretion flux and increased occultation by the larger degree of
+flaring seen in BD discs \citep[for the latter, as found
+by][]{2004MNRAS.351..607W}
+
+We have also qualitatively explored the effects of accretion and disc
+presence in our simulated dataset on disc fraction estimates. As is
+currently well known, longer wavelength bandpasses are much more
+reliable and suitable for disc identification. As shown in Section
+\ref{results} the naked and BDD disc loci were much more clearly
+separated in the CoCoD constructed using \textit{Spitzer} IRAC
+magnitudes than the shorter wavelength CIT \textit{JHK} passbands. In
+addition, we that the slope of the SED from 3.6 to 8.0\,$\mu$m, or
+$\alpha$ value, is an effective disc indicator. We have also
+tentatively shown that current observational cuts, when applied to our
+simulated photometry (with its associated photometric system), results
+in the reliable detection of disc candidates, for IRAC and MIPS
+colours and $\alpha$ values, and therefore a robust lower limit disc
+fraction.
+
+A further, derivative area this study impacts on, and perhaps most
+significantly, is the recent evidence for a stellar mass to accretion
+rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
+\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}.
+This relationship has been extended into the BD mass regime in
+\cite{2006A&A...452..245N}. However, arguments based on selection and
+detection thresholds have already cast this relation into doubt
+\citep{2006MNRAS.370L..10C}. As we have shown in Section \ref{results}
+a relationship of this kind is self-reinforcing as lower mass objects
+with higher accretion rates have little chance of being correctly
+identified as such due to both the accretion flux and flared
+associated disc. Essentially, at present it is unclear how many BD
+stars are not included in this relationship due to misidentification.
+As explained in \cite{2004MNRAS.351..607W}, BD systems with a disc,
+without including accretion effects, can have the characteristics of
+higher mass CTTS stars, due to increased disc flaring from a reduced
+surface gravity in the disc. The effects of accretion at typical or
+larger rates further exacerbate the situation both spectroscopically,
+as the photospheric flux essentially becomes swamped or completely
+veiled, and photometrically as the resulting colours and magnitudes
+are significantly shifted. Therefore, for our simulated dataset a
+relationship of this sort may well be derived, if typical methods are
+used to identify BD objects with discs and derive masses, ages and
+accretion rates, even though it is not present.
+
+Finally, although inner edge locations are correlated with their
+temperature we do not find a resulting correlation with IR excess. As
+our initial inner edge locations are placed at the co-rotation radius
+one might expect a correlation between rotation rate and IR excess.
+This in turn might suggest that studies of disc presence correlation
+with slower rotation rates, exploring disc-locking, may have intrinsic
+biases. However, for our systems with dust sublimation, vertical
+flaring, accretion and view over a range of inclinations any
+correlation is not apparent. The study of \cite{1997AJ....114..288M}
+used analytical prescribed flat discs. Whether, any correlation is
+apparent for such systems using our models is studied in an upcoming
+paper where we introduce a fitting tool to be used with the model grid
+and release a further set of models with analytic disc structures, and
+an increased parameter space.
 
 \subsection{Summary}
-
-rho outer and tau inner
-
-RESULTS:
-
-AGE, MASS AND DISC FRACTION PROBLEMS:
-INCLINATION AND FLARING AS PER WALKER
-
-THEREFORE:
-CAN'T ASSERT M TO MACC RELATION
-
-LOSS OF ROATIOANL PERIOD PROPORTIONALITY WITH IR EXCESS
-
-DISC STRUCT=
-
-FLARING INCREASES AS THE FLUX INCREASES, THEREFORE OPENING ANGLE
-REDUCES
-
-INNERR EDE ORIGINAL LOCATION PROPORTIONAL TO ROTATTION RATE
-RINAL POSITION PROPORTINAL TO INNER EDGE LOCATION
-
-INNER EDGE ALSO PUFFS UP AND THEN GETS BLASTED AWAY OVER RANGE OF
-ACCRETION RATES AS THE FLUX IS INCREASED.
-
-In this section we discuss the physical structures of our resulting
-BDD systems and how these vary with our input parameters. Following
-the work of \cite{2004MNRAS.351..607W} it is clear that for BDD
-systems in vertical hydrostatic equilibrium the disc flaring leads to
-increased obscuration of the central star and probable miss
-classification. In addition, \cite{1997AJ....114..288M} predicted a
-correlation between rotation rate and infrared excess due to the
-change in position (radial) and therefore temperature of the inner
-edge.
-
-Vertical disc structure \cite{2004MNRAS.351..607W}
-
-Rotation rate correlation with infrared excess \cite{1997AJ....114..288M}
-
-The structure of this paper is as follows. In Section \ref{model} we
-outline the model used, including an explanation of our physical
-assumptions (Section \ref{physics}), a brief description of the
-radiative transfer code (Section \ref{torus}), and an explanation of
-the derivation of emergent quantities such as photometric magnitudes
-(Section \ref{derived}). The ranges of the input variables are then
-explained and, where possible, justified using observational
-constraints in Section \ref{par_space}, with the total parameter space
-covered shown in Table \ref{par_space_table}. Section
-\ref{disc_struct} then contains analysis and description of the
-resulting temperature and dust density structures of the discs. The
-consequences of these changes in disc structure on the SEDs of these
-objects is then discussed in Section \ref{sed_analysis}. Section
-\ref{photometry} then details problems caused for the derivation of
-the primary parameters age, mass and disc fractions from photometry
-and the resulting relations built on these parameters; accretion rate
-to stellar mass and rotational period to disc presence. Finally,
-conclusions are drawn, with a summary, in Section
-\ref{conclusions}.**REWRITE AT END**
+\label{conc_summary}
+
+In summary, our simulated dataset shows that for typical parameter
+ranges for BD stars and BDD systems, disc presence and accretion flux
+lead to:
+
+Difficulty deriving the following stellar parameters for a coeval
+population:
+
+\begin{itemize}
+\item{Isochronal ages}
+\item{Isochronal masses}
+\item{IMFs}
+\end{itemize}
+
+And we have shown:
+\begin{itemize}
+\item{\textit{Spitzer} IRAC magnitudes are required for reliable disc
+    identification}
+\item{An expected correlation in inner disc edge with IR excess does
+    not occur for systems with dust sublimation and vertical
+    hydrostatic equilibrium view over a range of inclinations.}
+\item{Low mass, high accretion rate systems are likely to be
+    misidentified and therefore not included in any study relating
+    $M_*\propto\dot{M}$}
+\end{itemize}
 
@@
 systems with the lowest accretion rate (-12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ to those published in
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ to those published in
 \cite{2000ApJ...542..464C}, in the same photometric system
@@
 those derived from the full spectra, but this effect is negligible,
-and increased resolutionfor only some of our model grid (i.e naked
+and increased resolution for only some of our model grid (i.e naked
 stars) will hamper comparison between the models.
@@
 
-\section{Website**}
+\section{Website}
 \label{website}
+
+**THIS SECTION NEEDS TO BE SORTED**
+
+As stated throughout this paper the data presented are available from
+a web page
+\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
+  disc}. In this Appendix we briefly discuss the data included, and
+the different ways of accessing or visualising these data on the
+website.
+
+\subsection{Available Data}
+\label{web_data}
+
+The magnitudes and colours presented in this paper are avaiable both
+as individual magnitudes and as isochrones or mass tracks. Photometric
+magnitudes have also been derived for several other systems and are
+available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
+\citep{1966ARA&A...4..193J,2005ARA&A..43..293B}, \textit{Tycho} $V_t$
+and $B_t$ \citep{2000PASP..112..961B}, Bessell \textit{UBVRIJHKL}
+\citep{1988PASP..100.1134B,1998A&A...333..231B}, SDSS \textit{UGRIZ}
+\citep{1996AJ....111.1748F}, 2MASS $JHK_s$
+\citep{2003AJ....126.1090C,2006AJ....131.1163S}, MKO \textit{JHK}
+\citep{2002PASP..114..169S,2002PASP..114..180T}, UKIRT \textit{ZYJHK}
+\citep{2001MNRAS.325..563H}, IRAS 12, 25, 60 and 100\,$\mu$m
+\citep{1984ApJ...278L...1N} and SCUBA \textit{450WB} and
+\textit{850WB} \citep{1999MNRAS.303..659H}. For further information on
+these magnitudes, such as the filter responses used and the adopted
+zeropoints please refer to the website.
+
+\textit{Monochromatic fluxes}
+
+In addition to the magnitudes derived for each of these bands
+monochromatic fluxes have also been derived for all bands listed
+above. These have been derived following closely the methods of
+\cite{2006ApJS..167..256R}, extended to further passbands. For details
+of the assumed SED shape, central wavelengths and bandpasses adopted
+please refer to the website. The derivations of these monochromatic
+fluxes will be detailed in a coming paper, which details a fitting
+tool associated with these data.
+
+\subsection{Navigation}
+\label{navigation}
+
+The main page contains links to download the entire dataset in several
+formats alongside files describing the format.
+
+\begin{enumerate}
+\item All SEDs (\AA and ergs s$^{-1}$ cm$^{-2} {\rm \AA} ^{-1}$) 
+\item All SEDs ($\mu$m and mJy)
+\item All Photometric Magnitudes for all BDD systems.
+\item All Photometric Magnitudes for all Naked systems.
+\item All Monochromatic Fluxes for all Naked systems ($\mu$m and ergs
+  s$^{-1}$ cm$^{-2} {\rm \AA} ^{-1}$)
+\item All Monochromatic Fluxes for all Naked systems ($\mu$m and mJy)
+\item All Monochromatic Fluxes for all BDD systems ($\mu$m and ergs
+  s$^{-1}$ cm$^{-2} {\rm \AA} ^{-1}$)
+\item All Monochromatic Fluxes for all BDD systems ($\mu$m and mJy)
+\end{enumerate}
+
+Also included is a link to the calibration information listing all the
+filter response sources, adopted zero points, central wavelengths,
+bandwidths and assumed SED shapes (for monochromatic flux derivation).
+A brief scientific overview is also available explaining, in general
+terms, the dataset and model.
+
+\subsection{Browsing Tools}
+\label{tools}
+
+For users who wish to investigate the dataset in a more specific or
+interactive fashion two browsing tools are included.
+
+The isochrones, mass tracks and individual stars magnitudes and
+colours generated and presented in the work can be queried using the
+``Isochrone and Mass Track Tool''. This allows the user to select the
+parameters of the model required and retrieve the specific data.
+
+Secondly, an interactive tool is included allowing a user to select a
+given set of parameters and download the ``SEDs, monochromatic fluxes
+or magnitudes''. In addition this tool plots the SEDs for the Naked
+system or the three inclinations, in the case of BDD systems and
+allows users to select filters sets, whose monochromatic flux values
+will be overlaid on the displayed SEDs.
 

### 2010-05-18 BD_disc/paper.tex
from laptop - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2268 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-\title[**]{**}  \author[N.J.  Mayne and Tim
-Harries]{N.J. Mayne$^{1}$\thanks{E-mail: nathan@astro.ex.ac.uk
-    (NJM)} and Tim Harries$^{1}$\\
-  $^{1}$ School of Physics,
+\title[Brown dwarf discs]{On the properties of  discs around accreting brown dwarfs}  \author[Nathan J.  Mayne and Tim J. Harries]{Nathan J. Mayne\thanks{E-mail: nathan@astro.ex.ac.uk
+    (NJM)} and Tim J. Harries\\
+  School of Physics,
   University of Exeter, Stocker Road, Exeter, EX4 4QL.\\

### 2010-05-18 BD_disc/paper.tex
changes to intro - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2269 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2009}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2010}
 
@@
 
-Theoretical study of Brown Dwarfs (BDs) and the subsequent development
-of testable hypotheses for observational studies is a critical, and
-somewhat uncertain, area within the field of star and planet
-formation. Several of the key physical parameters and mechanisms
-remain unclear within this mass regime \citep{2007ApJ...664.1154S}.
-Uncertainty remains over fundamental issues such as the initial
-formation mechanisms, the subsequent evolution and dominance of a
-star-disc interaction through to the possible dependence of planet
-formation mechanisms on stellar mass \citep[for a review of BD
-formation mechanisms see][]{2006astro.ph..2367W}.
-
-Perhaps the two most fundamental challenges are formulating the
-formation mechanism of BDs and deriving the resulting
-initial-mass-function (IMF). Whether the BD IMF or formation
-mechanisms are different to their higher mass, solar-type, equivalents
-(T Tauri Stars, hereafter termed TTS) is an open question. Derivations
-of reliable IMFs depend, obviously, on robust derivations of stellar
-mass, and more subtly, on derivations of stellar ages (as IMFs are
-usually defined for assumed coeval populations). The study of
-classical T Tauri (CTTS) and disc systems of
-\cite{1997AJ....114..288M} found that given an expected range of
-parameters the scatter in infrared photometry matched the observed
-CTTS locus well. However the work of \cite{1997AJ....114..288M},
-discussed in more detail later, only included parametrised `flat'
-discs. Once disc flaring is considered it is clear from previous work
-that misidentification of high mass stars with circumstellar discs is
-likely. \cite{2004ApJ...617.1177W} show that high-mass (HM) stars with
-circumstellar discs are likely to be mis-identified as younger Class I
-sources. This problem also exists at lower masses where the presence
-of circumstellar discs can dramatically shift the spectral energy
-distributions (SEDs) and therefore colours and magnitudes of BDs
-\citep{2004MNRAS.351..607W}. Therefore, deriving robust masses (and
-ages), and subsequently IMFs for BDs requires an understanding of
-these effects of disc presence.
-
-The presence, or fraction (for populations) of associated discs is
-itself also crucial in isolating the formation mechanisms of
-BDs. Precise determination of disc parameters for BDs and comparison
-with the TTS results may allow the differentiation of currently
-competing theories of the BD formation mechanism. Essentially, a
-mechanism similar to that seen in higher mass stars i.e. cloud
-collapse and fragmentation will result in a similar fraction of discs
-across the BD mass boundary, whereas a formation mechanism dominated
-by dynamical interactions \citep[ejections, accretion disc stripping
-from near collisions or tidal interactions etc.]{2003IAUS..211...27B}
-will result in a markedly different disc parameters, such as fractions
-of stars with discs or radial sizes of the discs themselves, across
-the BD mass boundary. Fundamentally a different disc fraction for BD
-stars to TTS would provide persuasive evidence of a different
-formation mechanism across the two mass regimes, as would an increase
-in the average radial size of discs, indicative of truncation for BD
-objects. Therefore, to progress our understanding of the fundamental
-issues of both the formation mechanism and emerging IMFs for BDs,
-consideration of the effects of an associated circumstellar disc and
-their subsequent ubiquity are essential.
-
-Another fundamental, and important, unresolved issue is the mechanism
-of planet formation. A critical, and currently ill defined constraint
-for the planet formation models is the timescale available for planet
-formation within the circumstellar disc. Current favoured formation
-mechanisms such as core accretion or gravitational instability are
-separated by these timescales. Disc fractions have again been used, in
-conjunction with stellar ages, to derive the disc dissipation
-timescale, which obviously constrains the planet formation
-timescale. Studies of TTS have derived a disc dissipation timescale of
-$\approx$ 5 Myrs \citep{2001ApJ...553L.153H}, with very few discs
-shown to survive out to $\approx$ 20 Myrs
-\citep{2004ApJ...612..496M}. However, the derivation of a disc
-dissipation timescale from disc fractions suffers from several
-intrinsic problems, for instance the inconsistent (and often
-contradictory) methods of deriving ages \citep[see][for a full
-discussion]{2008MNRAS.386..261M}. Notwithstanding this, disc fraction
-surveys have also been published for lower mass and BD systems, such
-as \cite{2004A&A...427..245S} and \cite{2004ApJ...609L..33M}, deriving
-a similar order-of-magnitude disc dissipation timescale. The
-probability of forming planets around BDs is clearly sensitive to any
-changes in disc dissipation timescale across the TTS to BD mass
-boundary.
-
-Some studies of disc lifetimes find no significant difference between
-BD stars and their higher mass counterparts
-\citep{2003AJ....126.1515J}, however a possible correlation of disc
-lifetime with stellar mass is proposed in \cite{2007ApJ...660.1517S}.
-Additionally, \cite{2009arXiv0901.2603K} find that, for TTS older than
-3 Myrs, the disc dispersal time is mass dependent for intermediate
-mass (IM) to solar-type stars. This result only holds for the mass
-transition stated (IM to solar-type) and is based on stars with
-combined dust signatures, from infrared (IR) excesses and accretion
-indicators (using a EW[H$\alpha$], criterion).
-\cite{2009arXiv0901.4120D} also find, for TTS, a mass dependent
-general SED shape for disc candidates, with higher mass stars showing
-a featureless continuum at $\lambda>8.0$\,$\mu$m and lower mass stars
-generally showing strong silicate and PAH features at 10 and 2\,$\mu$m,
-indicative of mass dependent disc evolution. If the disc lifetimes and
-therefore rate or type of involved physical processes are a function
-of stellar mass. This could provide another piece of evidence
-separating the previously assumed continuous (in mass) evolutionary
-principles of stars. Resulting in a dichotomy separated by the
-hydrogen-burning mass limit. This would also lead to a change in the
-probability of forming planets in the BD regime, compared to CTTS.
-
-To test the hypothesis that disc dissipation timescales are
-independent of stellar mass one again requires accurate masses for BD
-with associated discs (hereafter, BDD) systems, alongside reliable
-disc fractions. The derivation of masses for BDD systems is
-complicated by disc presence, but additionally, the detection of disc
-presence at a given age is not simply a function of the disc
-dissipation timescale.
-
-Several mechanisms may act to completely dissipate a circumsteller
-disc. These include accretion from the disc ($\delta M_{\rm
-  disc}=\dot{M}$), photoevaporation or photoionisation due to flux
-from the central and neighbouring stars, and the formation of giant
-planets or interaction with binary partners. However, the entire disc
-does not have to be dissipated to be missed by disc fraction surveys.
-More subtly, disc fractions can be altered due to wavelength dependent
-detection. This is due to the peak flux of the thermal blackbody
-emission of the disc being proportional to the temperature,
-$\lambda^{\rm thermal}_{\rm peak}\propto T_{\rm disc}$, and the
-temperature in the disc being approximately a function of distance
-from the star. Thus for a given system, as one increases the
-wavelength of observation, the corresponding radial position of the
-effective source will increase. Moreover, as the disc flux must be
-separated from the photospheric flux the important quantity is the
-separation in wavelength between the emission peaks for the stellar
-and thermal disc components. Therefore the presence of an inner disc
-hole can change derived disc fractions, as a function of
-wavelength. Interestingly, \cite{2009arXiv0901.2603K} find that
-results for disc dissipation timescales based only on their accretion
-indicators or inferred disc presence do not agree, perhaps due to
-inclusion of transitional objects, where the inner disc is being
-cleared, and is therefore not detected at their target
-wavelength. \cite{2009arXiv0901.2603K} suggest that this is caused by
-photoevaporation of the inner disc, leading to a mass dependent disc
-lifetime, at their wavelength, for their sample. However, as discussed
-in \cite{2009arXiv0901.4120D}, the inner hole can be created via dust
-grain growth and mid plane settling, giant planet formation or
-photoevaporation by ultraviolet (UV) and far-UV (FUV) flux
-\citep{2007MNRAS.378..369N}.  \cite{2009arXiv0901.4120D} argue that if
-binarity or giant planet formation or photoevaporation cause inner
-disc clearing the resulting system would not show active accretion
-from radii below the inner disc boundary. For the case of clearing by
-dust grain growth and settling accretion from a hot gas disc within
-the inner radius is still possible, and indeed evidence for such a hot
-gas inner disc has been found through SED fitting
-\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Additionally,
-\cite{2009arXiv0901.4445E} argue that for M stars, with a pure
-reprocessing disc where the inner disc radius ($R_{\rm inner}$) is
-equal to the dust sublimation radius ($R_{\rm dust}$, discussed in
-Section \ref{physics}), the stellar and thermal components are not
-separable at wavelengths shorter than 6\,$\mu$m. In the case of
-\cite{2009arXiv0901.4445E}, the inner disc hole was created by
-photoionising radiation from the central star destroying the dust
-component of the disc. Recent direct evidence for a photoevaporating
-disc has been found for the circumstellar disc around a low mass TTS
-in the Sigma Orionis cluster \citep{2009arXiv0902.0457R}. The
-detection was characterised by a tenuous photoevaporation wind and
-little or no accretion, and a disc detection at 24\,$\mu$m indicative of
-a large inner hole. Additionally, for BDs, \cite{2009arXiv0902.0638M}
-find that the disc mass and radius distributions in the Orion
-Trapezium cluster are consistent with photoevaporation over 1 Myr (the
-adopted age of the cluster), from UV and FUV flux generated by the
-massive $\theta^1$ Ori C.
-
-Whichever mechanism is responsible for clearing the inner disc hole it
-is clear that its presence leads to confusion in the validity of disc
-fractions at a given wavelength. The important quantity here is the
-separation in wavelength between the emission peaks for the stellar
-and thermal disc components, as it is these components which must be
-separated. For BDD systems it is likely that difficulties detecting
-the disc will be exacerbated by the lower temperatures of the
-photosphere and therefore the smaller separation in wavelength from
-the thermal disc emission component, compared to TTS
-systems. Therefore, to derive disc fractions for BD populations we
-require detailed comparison models with which to guide disc candidate
-selection. These models must necessarily include a treatment of
-accretion and dust destruction, given that these factors deplete the
-inner (and total) disc thereby affecting disc detection.
-
-Although the creation of the inner disc hole could have several
-causes, at least part of the effect is undoubtedly due to
-accretion. Accretion acts to directly deplete the inner disc (where
-the material is accreted from). Accretion also depletes the inner disc
-indirectly, as accretion generates hot continuum emission
-\citep{1998ASPC..154.1709G}, increasing the photoionising UV and FUV
-flux available \citep{1998ASPC..154.1709G}, and therefore affecting
-the derived disc fraction \citep{2009arXiv0901.3684H}. This effect may
-be amplified for BDD systems where the combined photospheric emission
-is dominated by accretion flux. However, accretion columns modeled by
-\cite{2004MNRAS.348..879A} were found to produce negligible levels of
-photoionising flux due in part to the high optical depth of the column
-itself to Lyman continuum photons. Additionally, due to the high
-concentrations of hydrogen in the accretion column and hotspot the
-emission is more likely to be characterised by a stellar atmosphere
-than a black body. However, for our work as emission from a stellar
-atmosphere or a black body of equal temperature are approximately
-equal for wavelengths longer than the Lyman edge we have neglected
-this effect. Whilst the accretion column and hotspot may not
-contribute to the photoinising flux within the system they will of
-course alter the disc evolution by an increase of the emitted
-flux. This increase in flux will lead to an increase in temperature of
-the disc inner and outer regions, and more particularly a change in the
-dust sublimation effects at the inner edge.
-
-The current proposed mechanism of accretion is a magnetically
-channelled accretion `column', where material from a truncated (at the
-co-rotation radius $R_{\rm co}$) inner disc boundary falls onto the
-surface of the star along magnetic field lines
-\citep{1990RvMA....3..234C,1991ApJ...370L..39K}. This mechanism is
-widely accepted, with strong evidence found from the excessive widths
-of H$\alpha$ ($>$10\,\AA) emission lines, over that caused by
-chromospheric activity and stellar rotation
-\citep{1998ASPC..154.1793W}, caused by the high velocities of
-infalling matter, $~$100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.
-
-Accretion rates can be derived by modelling this magnetospheric
-accretion with a characteristic `column' temperature and assuming
-statistical equilibrium of the state populations. The resulting line
-ratios can then be fitted to the observed spectra. Accretion rates can
-also be calculated from model comparison of the Equivalent Width (EW)
-of the H$\alpha$ line itself, or perhaps more reliably, as they are
-less affected by extinction, that of the hydrogen recombination lines
-of Pa$\beta$ and Br$\gamma$. Accretion rates have been derived using
-these methods for many TTS and more recently for BDs
+There is now strong evidence that as brown dwarfs (BDs) form they pass
+through a Classical T~Tauri star (CTTS) phase, during which they
+possess a flared, dusty circumstellar disc from which they are
+actively accreting material (xxx; xxx). The accretion is thought to
+proceed via a magnetically-controlled funnel flow mechanism in which
+material from a truncated inner disc boundary falls onto the surface
+of the star along magnetic field lines
+\citep{1990RvMA....3..234C,1991ApJ...370L..39K} xxx.
+
+The truncated inner-edge of the circumstellar disc receives direct
+photospheric radiation and is strongly heated. This leads to an
+increased scaleheight, or `puffing up' of the inner disc rim, and
+subsequent shadowing of the region immediately beyond it (Dullemond
+reference). The density-dependent nature of the dust sublimation
+temperature (pollack ref) may also play a role in shaping the inner
+rim (isella ref; tannirkulam ref).
+
+As an aside, although we recognise that the inner hole in protostellar
+discs may be the result of giant planet formation or photoevaporation
+(xxx; xxx), these two mechanisms should result in a negligible
+mass-accretion rate and therefore would represent a distinct
+evolutionary state of brown dwarf disc (BDD) sytems to that of the
+CTTS-like phase we are considering here.
+
+The interpretation of the spectral energy distributions (SEDs) of
+pre-main-sequence (PMS) stars involves trying to distinguish the
+various contributions to the continuum from the hot spots at the base
+of the accretion flow, the photospheric flux, and the near-IR flux
+from the dusty inner disc. The complexity of the interplay between
+these contributions is excerbated by other, geometrical, effects such
+as the inclination (which changes the projected area of the inner disc
+wall visible to the observer) and the outer disc structure (which may
+obsure the inner disc for high inclincations). (xxx; xxx)
+
+In surveys, particularly those attempting to discern the PMS disc
+fraction (Xxx), this disentangling usually takes place using broad-band
+photometric measures and cuts in colour-colour or colour-magnitude
+space (xxx; xxx).  The important quantity here is the separation in
+wavelength between the emission peaks for the stellar and thermal disc
+components, as it is these components which must be separated. For BDD
+systems it is likely that difficulties detecting the disc will be
+exacerbated by the lower temperatures of the photosphere and therefore
+the smaller separation in wavelength from the thermal disc emission
+component, compared to CTTS systems. Therefore, to derive disc
+fractions for BD populations we require detailed comparison models
+with which to guide disc candidate selection.
+
+Comparison of accretion rates across the pre-main-sequence (PMS) mass
+spectrum has indicated that the accretion rate is strongly correlated
+with PMS mass,
 \citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
-with accretion rates in the range $\dot{M}_{\rm
-    acc}=$10$^{-6}$--10$^{-12} M_{\odot}yr^{-1}$, and typical
-accretion rates in the range \logmdot = log$(\frac{\dot{M}}{M_{\odot}}
-yr^{-1})=-10$ to $-8$ with only FU Orionis type objects accreting at
-rates higher than this. The mechanism producing accretion rates as
-high as those observed episodically in FU Orionis type objects is
-likely to be produced by some accretion mechanism instability, or
-perhaps by encounters with other cluster members \citep[see][for
-discussion]{2008arXiv0810.2854P}. Additionally, much lower accretion
-rates of $\dot{M}\approx$ 10$^{-13}M_{\odot}yr^{-1}$ have been derived
-for BDs using flux blueward of 4000\,\AA where the photospheric flux
-becomes negligible \citep{2009arXiv0901.3684H}.
-
-Analysis of the derived accretion rate data has led several authors to
-propose a strong correlation between accretion rate and stellar mass
-\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
-of an approximate form: $\dot{M_{\rm acc}}\propto M_{*}^{~2}$. This
-correlation has no clear physical basis and it has been suggested that
-it could be caused solely by selection biases and detection thresholds
-\citep{2006MNRAS.370L..10C}. \cite{2006ApJ...648..484H} points out
-that Bondi-Hoyle accretion naturally results in a clear
-$\dot{M}\propto M^2_*$ relationship, but is not a desirable formalism
-to adopt as it completely ignores angular momentum of the accreting
-material. This proposed correlation could have important implications
-with regards to disc lifetimes and planet formation probabilities as a
-function of mass.
-
-As discussed, discs associated with BD systems lead to difficulties in
-accurate classification of the underlying BD
-\citep{2004MNRAS.351..607W}. Furthermore, accretion, both direct and
-indirect, can act to alter the disc signature, and clearly the
-photospheric signature. For cooler BD systems, where the stellar flux
-is generally redward of any accretion flux, increased accretion fluxes
-could dominate the resulting SED. Given that the derivation of a
-robust relationship of the form $\dot{M}\propto M^{\alpha}_*$ requires
-accurate mass and accretion derivations, then clearly the effects of
-circumstellar disc and increased accretion rates must be considered,
-before any such relationship can be accepted. As there is currently no
-clear theory linking accretion rate and mass (ignoring Bondi-Hoyle
-accretion), this relationship is driven by observations.  However, the
-observational constraints must be interpreted using a self-consistent
-set of accreting BDD and BD systems to better understand their
-implications. In other words, what do the observations really tell us?
-Is there a real relationship between mass and accretion rate or would
-simulated systems outside this relationship (and attributed scatter)
-not be detected or included in the current observational surveys, due
-to misclassification?
-
-A further use of disc fractions, in conjunction with stellar ages, is
-to aid the understanding of the angular momentum evolution of star and
-disc systems. Recent evidence from TTS, from correlations of stars
-with IR excesses and slower rotational rates
-\citep{2007ApJ...671..605C} has seemed to strongly support a mechanism
-of disc-locking, where the central star is rotationally braked through
-magnetic locking to the accretion disc
-\citep{1993AJ....106..372E,1990RvMA....3..234C,1991ApJ...370L..39K}. A
-similar mechanism has been put forward, but has yet to be
-unambiguously confirmed, for BD stars. However, current studies have
-found a much weaker correlation between the slower rotators and those
-where a disc presence is inferred for BDs. Some authors have therefore
-proposed an `imperfect' disc-locking mechanism for stars in the lower
-mass regime ($M_*<0.4M_{\odot}$, inclusive of the BD mass regime,
-$M_*<0.08M_{\odot}$) \citep{2005A&A...430.1005L}. This weaker
-correlation could also be due to `imperfect' disc-locking or
-observational effects and mass dependence of the disc dissipation
-timescale \citep{2004A&A...419..249S,2005A&A...429.1007S}.
-
-If disc-locking is present for BDD systems, as for TTS stars, one
-would expect accretion of material from a magnetic truncation radius,
-$R_{\rm T}$ \citep{2007prpl.conf..479B}. \cite{2007prpl.conf..479B}
-show that the magnetic truncation radius, $R_{\rm T}$, must be less
-than the co-rotation radius, $R_{\rm co}$ (where the Keplerian angular
-rotation rate of the disc is the same as the angular rotation rate of
-the star), as material outside this radius will have too much angular
-momentum to fall onto the star. This is implicitly adopted in the
-proposed accretion mechanism, where the disc is magnetically
-truncated, and therefore locked to the star. This magnetic truncation
-would lead to an inner wall (and inner hole) of the accretion disc.
-Evidence for an inner disc wall has been found from near-IR excesses
-from the inner rims of Herbig Ae stars, with emission peaking at
-2--3\,$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
-position of this wall is affected by several factors, discussed
-further in Sections \ref{dust_edge} and \ref{inner_edge}. The previous
-work of \cite{1997AJ....114..288M} explored the effects of simple mass
-accretion and the radius to the inner disc on the infrared colours of
-CTTS, using a prescribed range of inner disc radii.
-\cite{1997AJ....114..288M} find that the scatter in infrared colours
-for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
-$\dot{M_{\rm acc}}=$10$^{-9}$to 10$^{-5} M_{\odot}yr^{-1}$, matches
-the scatter of the CTTS locus found in the data. The models of
-\cite{1997AJ....114..288M} used physically flat discs however meaning
-their results will not stand for discs with significant flaring. More
-importantly for our work \cite{1997AJ....114..288M} find a correlation
-of the infrared locus of models with the accretion and inner disc
-location. Essentially, changes in the stellar flux levels and position
-of the inner wall lead to temperature changes of this inner edge and
-therefore changes in the balance of flux across the infrared
-wavelength regime. As this study does not include the effects of
-vertical hydrostatic equilibrium or even the study of flared discs one
-would expect, perhaps, a more complex relationship between the inner
-edge position and infrared excess in `real' systems. This means that
-studies aiming to provide evidence of disc locking by comparing disc
-indicators with rotation rates may include unforeseen biases. As the
-rotation rate will effect the co-rotation radius and therefore
-truncate the disc at different radii, thereby enhancing or suppressing
-any relationship of infrared excess (or disc presence) with rotation
-rate.
-
-In summary, several key areas in the theoretical studies of BDs hinge
-critically on observational constraints, where the derived values are
-heavily affected by disc and/or accretion presence. Formation
-mechanisms, planet formation, IMFs, disc dissipation timescales,
-accretion rate--stellar mass relationships and studies of disc-locking
-mechanisms using correlations of rotation rates with infrared
-excesses, all require derivations of either masses, ages or disc
-fractions (or a combination), supplemented by other parameters. The
-consequences of the disc structure for BD accretion discs,
-particularly vertical structure, given the assumption of vertical
-hydrostatic equilibrium, have already been discussed for a limited
-range of BD parameters in \cite{2004MNRAS.351..607W}. Indeed
-\cite{2004MNRAS.351..607W} have shown that BDD systems seen at higher
-inclinations can be confused with CTTS systems, having similar colours
-and magnitudes. A benchmark model grid of spectra for star and disc
-systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$ has
-previously been published in \cite{2006ApJS..167..256R}.
-
-In this work we explore the effects of accretion and disc presence on
-the derivation of the stellar parameters and explore the intrinsic
-biases, or relationships, which will effect or inhibit conclusions on
-mass to accretion rate or rotation to infrared excess correlations. We
-have extended the similar work of \cite{2004MNRAS.351..607W} by
-inclusion of a simple treatment of accretion and a sophisticated
-implementation of dust sublimation (amongst other improvements). The
-complete model grid, with derived photometry and isochrones, is
+with an approximate form $\dot{M_{\rm acc}}\propto M_{*}^{~2}$. Since
+in the canonical picture the accretion rate is driven by the disc
+viscosity, and should be indepedent of the mass of the central object,
+this correlation is somewhat surprising. There is some danger that the
+correlation is the result of, or at least strengthened by, the
+presence of observational biases (xxxx): At the high-mass (CTTS) end of the
+mass spectrum the lowest accretion-rates cannot be measured via
+continuum methods since the excess is too small in contrast with the
+photopsheric emission. The emission lines will also be weak, and
+indeed the H$\alpha$ equivalent width (EW) may be less than the
+10\AA\ that traditionally demarc?ates classical from weak-lined T Tauri
+stars. Such objects should show doppler-broadened profiles, but the
+line wings will be weak, and the presence of underlying H$\alpha$
+absorption may become dominant. Thus there may be a population of
+low-accretion-rate CTTS which are current missing from the surveys.
+
+There are also risks of observational biases at the low-mass end of
+the correlation. Radiative-transfer modelling of H$\alpha$ emission
+from accreting BDs requires high temperatures ($>$\, 10\,kK) in the
+accretion funnels in order to recover the level of emission that is
+observed. (Cooling rate arguments can be invoked to explain the
+presence of such high temperatures). Recently some continuum
+measurements of accreting BDs have been conducted, and these broadly
+support the H$\alpha$ rates (xxxx). Nonetheless it is worth considering the
+observed effect that mass accretion at typical CTTS rates onto a BD
+might have. Parity between the BD photospheric luminosity and the
+accretion luminosity occurs at relatively low accretion rates
+\citep{2006MNRAS.370L..10C}. Such objects may not be detected as BDs
+at all in photometric surveys. Even before such an extreme case is
+reached, the additional luminosity provided by the accretion should
+have measurable effect on the BD colours. Furthermore the additional
+flux will be reprocessed by the disc, altering its scaleheight and
+possibly the shape of its inner edge.
+
+Here we present a grid of models of BDD systems, including a
+self-consistent treatment of the photospheric and accretion luminosity
+sources and the interaction of that flux with the circumstellar disc.
+We investigate the impact of the luminosity of the central source on
+location and shape of the disc inner rim, as well as the large-scale
+structure and flaring of the outer disc. We construct synthetic
+colour-colour and colour-magnitude diagrams in order to examine the
+efficacy of the photometric selections used to isolate brown dwarfs
+and measure disc fractions (xxx;xxx).
+
+The complete model grid, with derived photometry and isochrones, is
 available online through our browsing tool
 \footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
-which is described in Appendix \ref{website}. The aim of this online
-database is to complement that of \cite{2006ApJS..167..256R}. Finally,
-subsequent papers will introduce expansion to the model grid and an
-online fitting tool.
-
-**THIS PARAGRAPH IS CURRENTLY WRONG, WILL REQRITE AT THE END**
-
-The structure of this paper is as follows. In Section \ref{model} we
-outline the model used, including an explanation of our physical
-assumptions (Section \ref{physics}), a brief description of the
-radiative transfer code (Section \ref{torus}), and an explanation of
-the derivation of emergent quantities such as photometric magnitudes
-(Section \ref{derived}). The ranges of the input variables are then
-explained and, where possible, justified using observational
-constraints in Section \ref{par_space}, with the total parameter space
-covered shown in Table \ref{par_space_table}. Section
-\ref{disc_struct} then contains analysis and description of the
-resulting temperature and dust density structures of the discs. The
-consequences of these changes in disc structure on the SEDs of these
-objects is then discussed in Section \ref{sed_analysis}. Section
-\ref{photometry} then details problems caused for the derivation of
-the primary parameters age, mass and disc fractions from photometry
-and the resulting relations built on these parameters; accretion rate
-to stellar mass and rotational period to disc presence. Finally,
-conclusions are drawn, with a summary, in Section \ref{conclusions}..
+which is described in Appendix \ref{website}.
 
@@
 (in Section \ref{derived}). Some internal consistency checks are
-detail in Appendix \ref{consistency}.
+given in Appendix \ref{consistency}.
 
@@
 
-To model an accreting BDD system we must first model the underlying
-photospheric flux. To provide a self-consistent set of model spectra
-we have adopted a BD stellar interior and atmospheric model grid. We
-have then constructed the total photospheric flux for any input value
-of stellar age and mass by interpolating for surface gravity (log(g)),
-effective temperature ($T_{\rm eff}$), radius ($R_*/R_{\odot}$) and
-luminosity ($L_*/L_{\odot}$). These values were then used to
-interpolate atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2}
-{\rm \AA}^{-1}$) from 1200 to 2$\times$ 10$^7$ \AA (or 0.12 to 2000\,
-$\mu$m). These spectra were then smoothed using 200 logarithmically
-spaced points. Careful inspection ensured that no spectral features
-were removed during smoothing. The stellar interior models used for
-this study are the `DUSTY00' models of \cite{2000ApJ...542..464C}
-combined with the `AMES-Dusty', atmospheric models of
-\cite{2000ApJ...542..464C}, which are all available online
-\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
-approximate $T_{\rm eff}$ (effective temperature) range of $\approx
-$3000\,K$<T_{\rm eff}<$1600\,K the AMES-Dusty atmospheres are most
-applicable (2700\,K$>T_{\rm eff}>$1700\,K). We did try including dynamic
-application of atmospheres based on the derived $T_{\rm eff}$,
-i.e. using AMES-Cond for $T_{\rm eff}<$1700\,K, however this resulted in
-large discontinuities between the model atmospheres and resulting
-spectra. As this only affects stars at the very edge of our
-temperature range, i.e. for the oldest and lowest mass objects (for
-the AMES-Cond case), we have adopted the same model throughout.
+In order to model an accreting BDD system we must first model the
+underlying photospheric flux. We have adopted a BD stellar interior
+and atmospheric model grid and have then constructed the total
+photospheric flux for any input value of stellar age and mass by
+interpolating for surface gravity ($\log g$), effective temperature
+($T_{\rm eff}$), radius ($R_*/R_{\odot}$) and luminosity
+($L_*/L_{\odot}$). These values were then used to interpolate
+atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2} {\rm \AA}^{-1}$)
+from 1200 to 2$\times$ 10$^7$ \AA. The spectra were subsequently
+resampled onto 200 logarithmically spaced points. Careful inspection
+ensured that no spectral features were removed during resampling. The
+stellar interior models used for this study are the `DUSTY00' models
+of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
+atmospheric models of \cite{2000ApJ...542..464C}, which are all
+available online
+\footnote{http://perso.ens-lyon.fr/france.allard/}. For our $T_{\rm
+  eff}$ range of $\approx $3000\,K$<T_{\rm eff}<$1600\,K the
+AMES-Dusty atmospheres are the most applicable (2700\,K$>T_{\rm
+  eff}>$1700\,K). We did try including dynamic application of
+atmospheres based on the derived $T_{\rm eff}$, i.e. using AMES-Cond
+for $T_{\rm eff}<$1700\,K, but this resulted in large discontinuities
+between the model atmospheres and resulting spectra. Since this only
+affects stars at the very edge of our temperature range, i.e. for the
+oldest and lowest mass objects (for the AMES-Cond case), we have
+adopted the AMES-Dusty models throughout.
 
@@
 
-Secondly, we require a model of the accretion flux for the system. The
-flux due to accretion was added onto the intrinsic photospheric flux
-using the simple approximation of blackbody emission. The selected
-accretion rate was used to derive an accretion luminosity ($L_{\rm acc}$),
-where the material was modelled as falling from the disc inner edge
-onto the surface of the star. $L_{\rm acc}$ is calculated according to
-\ref{Lacc}, 
+We assumed blackbody emission for the accretion flux.  The selected
+accretion rate was used to derive an accretion luminosity ($L_{\rm
+  acc}$), where the material was modelled as free-falling from the
+disc inner edge onto the surface of the star. $L_{\rm acc}$ is
+calculated according to \ref{Lacc},
 \begin{equation}
@@
 \ref{disc_parameters}). During the radiative transfer simulations of
-the disc the final inner dust disc radius may be extended past the
-co-rotation radius. This is due to dust sublimation effects (see
-Sections \ref{dust_edge} and \ref{inner_edge} for an
-explanation). However, as the gas within the disc is not sublimated it
-will always extend down to the co-rotation radius and we assume
-accretion will still occur from this radius. A full discussion of the
-differences between the initial and resulting final radii of the dust
-disc can be found in Section \ref{inner_edge}. Once the accretion
-luminosity was derived, an adopted areal coverage ($A$), over the
-stellar surface, was used to calculate an effective temperature
-($T_{\rm acc}$), for the accretion `hot' spot, where
+the disc the final inner dust-disc radius may be beyond the
+co-rotation radius due to dust sublimation effects (see Sections
+\ref{dust_edge} and \ref{inner_edge} for an explanation). Once the
+accretion luminosity was derived, an adopted areal coverage ($A$),
+over the stellar surface, was used to calculate an effective
+temperature ($T_{\rm acc}$), for the accretion `hot' spot, where
 \begin{equation}
@@
 that observationally UV excesses are often used to recreate and then
-subtract an assumed accretion flux using a blackbody flux curve,
-essentially the reverse of this method.
+subtract an assumed accretion flux using a blackbody flux curve, which
+is essentially the reverse of this method.
 
@@
 along magnetically channelled columns from the inner disc boundary.
-For TTS stars, \cite{2007prpl.conf..479B} show that the magnetic
+For CTTS stars, \cite{2007prpl.conf..479B} show that the magnetic
 truncation radius ($R_{\rm mag}$) is less than the co-rotation radius
@@
 
-For this work the disc outer edge was set at 300 AU, this was chosen
+Although we solve for the vertical disc structure, the radial
+structure of the disc is a free parameter. We assume that the surface
+density varies as $\Sigma(r) \propto r^{-1}$.
+
+For this work the disc outer edge was set at 300\,AU, this was chosen
 as a maximum size of the circumstellar
@@
 has little effect on the resulting SED. However, in our subsequent
-paper we will include models for outer radii of 100 AU and plan to
+paper we will include models for outer radii of 100\,AU and plan to
 extend this parameter range further to smaller values of the outer
@@
 
-\subsubsection{naked and disc systems}
+\subsubsection{Naked and disc systems}
 \label{naked_BDD}
@@
 `naked' photospheres (plus accretion) are diluted by the factor
-$(R_*/{\rm distance})^2$ to a distance of 10pc. The `negligibly' accreting,
+$(R_*/{\rm distance})^2$ to a distance of 10\,pc. The `negligibly' accreting,
 `naked' stars can be used to produce absolute magnitude (and intrinsic
-colour) isochrones for comparison. Whilst, the remainder are used to
+colour) isochrones for comparison. The remainder are used to
 model systems showing active accretion where no disc is detected. For
@@
 In summary the key required input variables to setup the model grid
-are as follows. Stellar age and mass, which are used to derive the
-stellar flux. Further supplemented by an accretion rate, areal
-coverage and rotation period, used to generate the the accretion flux.
-The inner disc radius is then derived using the rotation rate, but a
-disc mass fraction must be adopted.
+are as follows: Stellar age and mass (which are used to derive the
+stellar flux) and accretion rate, areal coverage and rotation period
+(which are used to determine the the accretion flux and temperature).
+The disc parameters are set by a disc mass (expressed as a fraction of
+the BD mass), and a power-law distribution for the disc surface
+density.
 
@@
 refinements i.e.  addition of Adaptive-Mesh-Refinement (AMR)
-introduced in \cite{2004MNRAS.350..565H}. {\sc torus} uses the
-criterion of \cite{1999A&A...344..282L} in a radiative equilibrium
-algorithm. The simulation also calculates \textit{vertical hydrostatic
-  equilibrium} and dust sublimation for the disc, similar to that
-described in \cite{2007ApJ...661..374T}.
+introduced in \cite{2004MNRAS.350..565H}. {\sc torus} uses the method
+of \cite{1999A&A...344..282L} solve radiative equilibrium. The
+simulation also self-consistently solves the equation of
+\textit{vertical hydrostatic equilibrium} and dust sublimation for the
+disc (described in \cite{2007ApJ...661..374T}).
 
@@
 
-We have adopted a similar treatment to \cite{2002ApJ...564..887W}.
-With the size distribution of dust particle given by,
+We have adopted a similar dust model to \cite{2002ApJ...564..887W} 
+with the size distribution of dust particle given by,
 \begin{equation}
@@
 Where $n(a)da$ is the number of particles of size $a$ (within the
-increment $da$), $a_{\rm c}$ is the characteristic particle size, with $p$
-and $q$ simply used to control the shape of the distribution. $C_i$
-controls the relative abundance of each constituent species ($i$) in
-the dust. \cite{2002ApJ...564..887W} found that simulated SEDs fit
-observed SEDs better using this adjusted size distribution for the
-dust particles, as opposed to a simple power law. The best fitting
-values found in \cite{2002ApJ...564..887W} were $q=$3.0, $p=$0.6 with
-$a_{\rm c}=$50\,$\mu$m, also with an associated maximum and minimum grain size
-of $a_{\rm min}=$5 nm and $a_{\rm max}=$1mm. Subsequent works have adopted a
-slightly steeper power law dependence, with $q=$3.5
+increment $da$), $a_{\rm c}$ is the characteristic particle size, with
+$p$ and $q$ simply used to control the shape of the
+distribution. $C_i$ controls the relative abundance of each
+constituent species ($i$) in the dust. \cite{2002ApJ...564..887W}
+found that simulated SEDs fit observed SEDs better using this adjusted
+size distribution for the dust particles, as opposed to a simple power
+law. The best fitting values found in \cite{2002ApJ...564..887W} were
+$q=$3.0, $p=$0.6 with $a_{\rm c}=$50\,$\mu$m, also with an associated
+maximum and minimum grain size of $a_{\rm min}=$5 nm and $a_{\rm
+  max}=$1mm. A slightly steeper power law dependence, with $q=$3.5
+(corresponding to the canonical MRN distribution) is more widely
+adopted
 \citep{2008A&A...486..877B,2008ApJ...676L.143M,2008arXiv0810.2552P}.
-Therefore we have adopted the values of \cite{2002ApJ...564..887W}
+Here we have adopted the values of \cite{2002ApJ...564..887W}
 except for the parameter $q$ where we have used $q=$3.5.
 \cite{2002ApJ...564..887W} calculated the $C_i$ values for amorphous
-Carbon and silicon by requiring the dust to deplete a solar abundance
+carbon and silicon by requiring the dust to deplete a solar abundance
 of either component completely \citep[using abundances
-from][]{1989GeCoA..53..197A,1993ASPC...40..410N}. We have set $C_i=$1
-and adjusted the species using a grain fractional abundance \cite[an
-equivalent process to that of][]{2002ApJ...564..887W}, however we have
-adjusted these grain fractions using the updated solar abundances of
-\cite{2006CoAst.147...76A}. The resulting difference in opacity
-between grain fractions matching the work of
+  from][]{1989GeCoA..53..197A,1993ASPC...40..410N}. We have set
+$C_i=$1 and adjusted the species using a grain fractional abundance
+\cite[an equivalent process to that of][]{2002ApJ...564..887W},
+however we have adjusted these grain fractions using the updated solar
+abundances of \cite{2006CoAst.147...76A}. The resulting difference in
+opacity between grain fractions matching the work of
 \cite{2002ApJ...564..887W} and the new grain fractions is only a
@@
 abundance of Silicon increasing) which has little effect on the
-resulting SEDs. Figure \ref{albedo} shows the
-resulting albedo, and scattering and absorption opacities, for our
-dust population, with a the vertical dashed line showing 10\,$\mu$m.
+resulting SEDs. Figure \ref{albedo} shows the resulting albedo, and
+scattering and absorption opacities, for our dust population, with a
+the vertical dashed line showing 10\,$\mu$m.
 
@@
 
-\subsubsection{Dust sublimation and the Inner Disc Edge}
+\subsubsection{Dust sublimation and the inner disc edge}
 \label{dust_edge}
@@
 treatment is similar to that detailed in \cite{2007ApJ...661..374T},
-but improved and generalised with respect to the applicable
-geometries.
-
-The practical implementation is as follows: An initial coarse
-approximate temperature structure is found for the grid without dust,
-only a fixed gas distribution. Then, first three full \textit{Lucy}
-algorithm iterations are run for a grid with a maximum cell opacity of
-0.1 (with dust added to this level). Three more iterations are then
-performed with dust opacity limited to $\tau=$1 per cell. A further
-three \textit{Lucy} algorithm iterations are then performed with the
-full dust opacity, where dust is added until the gas-to-dust ratio is
-achieved($\epsilon =$100). For each iteration (from the first to the
-ninth) dust in cells which reach the sublimation temperature and
-density is removed from the disc by setting the opacity to zero for
-the cell. Once these nine iterations are complete, the grid is refined
-around the disc photosphere, and the radiative transfer algorithm is
-iterated through to convergence. After this first convergence, a
-vertical hydrostatic equilibrium algorithm is run, after which the
-disc grid is unrefined and then re-refined around the disc
-photosphere. This process continues for five hydrostatic equilibrium
-calculations. Finally, once the hydrostatic equilibrium iterations are
-complete we perform a final dust sublimation run to remove any cells
-where the dust temperature has moved above the sublimation temperature
-and further refine the photosphere and inner edge of the disc (whilst
-also unrefining cells where the opacity has reduced significantly and
-high resolution is no longer required). In this model the dust
-sublimation is effectively digital i.e. when the density and
-temperature for sublimation is reached for a given cell the dust is
-destroyed. We did attempt a more realistic model where the dust
-sublimation causes the dust to be destroyed at an evanescently
-decaying rate into the particular region. This was expected to lead to
-a more realistic situation where the dust destruction propagates into
-the disc material, and does not instantly destroy an entire
-cell. However, this implementation lead to incremental sections of
-dust being removed after each iteration, resulting in little change in
-the overall density structure of the disc. This is perhaps interesting
-for real systems, in that the dust sublimation should not be expected
-to act as a digital `switch'.
+but with some enhancements to ensure convergence of the sublimated
+rim.
+
+The dust sublimation proceeds as follows: An initial temperature
+distribution is found for the optically-thin limit by setting the
+global dust-to-gas ratio to a tiny value. Subsequent radiative
+equilibrium iterations are performed using the adopted dust-to-gas
+ratio of 0.01, but limiting the maximum optical depth across a given
+cell to $\tau_{\rm max}$. Cells whose temperature exceeds the local
+dust sublimation temperature have their dust-to-gas ratio set to
+zero. Radiative equilibrium iterations and sublimation sweeps are
+performed at $\tau_{\max} = $0.1, 1, and 10, with a final iteration of
+$\tau_{\max} = \infty$. Adequately solving the radiative-equilibrium
+necessiates resolving the disc's effective photosphere, and adaptive
+mesh refinement is used to split the grid at the
+optically-thin/optically-thick boundary in order that the maximum cell
+size at this boundary is $<1$ at a wavelength of 5500\,\AA. Once a
+self-consistent sublimated rim has been determined the equation of
+hydrostatic equilibrium is solved throughout the disc, and the
+sublimation iterations are restarted (the change in the density
+structure from the hydrostatical equilibrium step naturally feeds back
+into the shape of the inner rim). Five hydrostatic equilibrium steps
+are performed to ensure convergence, although a stable disc structure
+is normally found after three such iterations.
 
@@
 system-observer inclination. For our models we have set the distance,
-to 10pc to create absolute flux SEDs and selected ten inclinations (0,
-27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$). A further useful
-feature of the {\sc torus} code is that the emitted photons which make
-up the SED are tagged on their way to the observer. These tags
-separate the photons into four groups. Firstly, photons are separated
-by source into thermal (disc) or stellar groups. These groups are then
-subdivided into photons which reach the observer either directly or
-after scattering (for example see Figure \ref{disc_eg_173}). The
-resulting SEDs are discussed in Section \ref{seds}.
+to 10\,pc to create absolute flux SEDs and selected ten inclinations
+equi-spaced in $\cos i$ (0, 27, 39, 48, 56, 64, 71, 77, 84 and
+90$^{\circ}$). A further useful feature of the {\sc torus} code is
+that the emitted photon packets which make up the SED are tagged on their way
+to the observer. These tags separate the packets into four
+groups. Firstly, packets are separated by source into thermal (disc)
+or stellar groups. These groups are then subdivided into those which
+reach the observer either directly or after scattering (for example
+see Figure \ref{disc_eg_173}). The resulting SEDs are discussed in
+Section \ref{seds}.
 
@@
 
-To allow us to investigate the effects of disc presence and accretion
-luminosity on the derivation of parameters for BD stars we can first
-study the produced SEDs. However, many observational studies use
-non-spectroscopic data to derive the pertinent parameters. Therefore,
-to examine the practical effects in the `observational plane' we have
-used the SEDs to produce broadband photometric magnitudes, and
-subsequently colours. Broadband magnitudes were also derived in a
-large range of other filter sets not used explicitly in the analysis
-within this paper. These magnitudes are available online
+Many observational studies use non-spectroscopic data to derive the
+pertinent parameters. Therefore in order to examine the practical
+effects in the `observational plane' we have used the SEDs to produce
+broadband photometric magnitudes, and subsequently colours. Broadband
+magnitudes were also derived in a large range of other filter sets not
+used explicitly in the analysis within this paper. These magnitudes
+are available online
 \footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
@@
 monochromatic fluxes have been derived for all filters, and again are
-available online and discussed in Appendix \ref{website}. The
-additional magnitudes and monochromatic fluxes are also discussed in
-detail in the subsequent paper introducing the online fitting tool.
-
-To derive broadband photometric magnitudes and colours the SEDs of
-either the disc or naked systems were folded through the filter
-responses of the required photometric system. As the fluxes in all
-cases are absolute, derived for an observer to object distance of
-10pc, no conversion is required to derive absolute magnitudes and
+available online and discussed in Appendix \ref{website}.
+
+In order to derive broadband photometric magnitudes and colours the
+SEDs of either the disc or naked systems were folded through the
+filter responses of the required photometric system. As the fluxes in
+all cases are absolute, derived for an observer to object distance of
+10\,pc, no conversion is required to derive absolute magnitudes and
 therefore intrinsic colours.
 
-For the naked systems the flux is spherically symmetric however,
-clearly, for the BDD systems different inclinations will result in
-very different SEDs and therefore magnitudes and colours. Therefore,
-for the BDD systems, photometric magnitudes and colours must be
-derived for each inclination selected.
-
-We have integrated using photon counting and calibrated using a Vega
+We have integrated using photon-counting and calibrated using a Vega
 spectrum for magnitudes in the optical and near-IR regimes. The filter
@@
 rate, accretion rate, the areal coverage of the accretion stream, disc
-mass fraction and the system inclination. In a subsequent paper we
-introduce variation of the outer radius and using an analytical
-vertical disc structure as oppose to vertical hydrostatic equilibrium.
-A summary of the values adopted for each input variable is shown in
-Table \ref{par_space_table}.
+mass fraction and the system inclination. A summary of the values
+adopted for each input variable is shown in Table
+\ref{par_space_table}.
 
@@
 Representative masses within the BD regime were chosen as follows:
-0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 $M_{\odot}$.
+0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08\,$M_{\odot}$.
 
@@
 
-Typical disc lifetimes for solar type stars are of order 10 Myrs
+Typical disc lifetimes for solar type stars are of order 10\,Myrs
 \citep{2001ApJ...553L.153H}. Therefore, we have adopted input ages of
-1 and 10 Myrs for our model grid, to span the approximate range of
+1 and 10\,Myrs for our model grid, to span the approximate range of
 ages over which the discs influence will be important.
@@
 \label{par_rotation}
+
+XXXX nathan - please reduce by factor 2 in length!
 
@@
 
+XXXX TJH check this now
+
 Accretion rates derived for pre-MS stars are of order \logmdot = $-6$
@@
 that the accretion rate scales with central object mass, into the BD
-regime. However, work by \cite{2006MNRAS.370L..10C} suggests that much
-of this result is likely to be caused by biases and sensitivity
-limits.
+regime.
 
@@
 
-A further required input parameter is the mass of the circumstellar
-disc. Previously studies modeling BD discs have adopted a range of
+Previously studies modeling BD discs have adopted a range of
 disc mass fractions, for instance \citep{2004MNRAS.351..607W} use 0.1,
@@
 ten observer to system inclination angles spaced evenly in
-$cos(inclination)$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
+$\cos i$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
 and 90$^{\circ}$.

### 2010-05-18 BD_disc/paper.tex
more updates th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2270 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-We have also applied dust sublimation during our simulations. This
-treatment is similar to that detailed in \cite{2007ApJ...661..374T},
-but with some enhancements to ensure convergence of the sublimated
-rim.
-
-The dust sublimation proceeds as follows: An initial temperature
-distribution is found for the optically-thin limit by setting the
-global dust-to-gas ratio to a tiny value. Subsequent radiative
-equilibrium iterations are performed using the adopted dust-to-gas
-ratio of 0.01, but limiting the maximum optical depth across a given
-cell to $\tau_{\rm max}$. Cells whose temperature exceeds the local
-dust sublimation temperature have their dust-to-gas ratio set to
-zero. Radiative equilibrium iterations and sublimation sweeps are
-performed at $\tau_{\max} = $0.1, 1, and 10, with a final iteration of
-$\tau_{\max} = \infty$. Adequately solving the radiative-equilibrium
-necessiates resolving the disc's effective photosphere, and adaptive
-mesh refinement is used to split the grid at the
-optically-thin/optically-thick boundary in order that the maximum cell
-size at this boundary is $<1$ at a wavelength of 5500\,\AA. Once a
-self-consistent sublimated rim has been determined the equation of
+As our models assume magnetic-truncation at the co-rotation radius, we
+have implicitly generated an inner hole. This also means that the disc
+will have an inner wall at this radius. Evidence for inner walls in
+circumstellar discs is apparent from the SEDs of disc systems, where a
+peak in emission is found between 2 and 3\,$\mu$m. The temperatures
+reached by such inner walls are expected to generate thermal flux
+contributions within this wavelength range
+\citep{2001ApJ...560..957D}.
+
+For low-luminosity systems the dust sublimation radius ($R_{\rm sub}$)
+will be coincident with the co-rotation radius. However should
+the combined photospheric and accretion luminosities be sufficient the
+inner disc will be heated sufficiently that the dust close to the
+co-rotation radius will be sublimated, and we must account for this
+in our models. Furthermore, since the dust sublimation temperature has
+a density dependence \citep{1994ApJ...421..615P}, it is both the location and {\em
+  shape} of the inner wall that can change (Isella ref; Tannirkulam ref).
+
+Our treatment of dust sublimation is similar to that detailed in
+\cite{2007ApJ...661..374T}, but with some enhancements to ensure a
+swift convergence of the sublimated rim. The dust sublimation proceeds
+as follows: An initial temperature distribution is found for the
+optically-thin limit by setting the global dust-to-gas ratio to a tiny
+value. Subsequent radiative equilibrium iterations are performed using
+the adopted dust-to-gas ratio of 0.01, but limiting the maximum
+optical depth across a given cell to $\tau_{\rm max}$. Cells whose
+temperature exceeds the local dust sublimation temperature have their
+dust-to-gas ratio set to zero. Radiative equilibrium iterations and
+sublimation sweeps are performed at $\tau_{\max} = $0.1, 1, and 10,
+with a final iteration of $\tau_{\max} = \infty$. Adequately solving
+the radiative-equilibrium necessiates resolving the disc's effective
+photosphere, and adaptive mesh refinement is used to split the grid at
+the optically-thin/optically-thick boundary in order that the maximum
+cell size at this boundary is $<1$ at a wavelength of 5500\,\AA. Once
+a self-consistent sublimated rim has been determined the equation of
 hydrostatic equilibrium is solved throughout the disc, and the
@@
 
-As our models are magnetically truncated at the co-rotation radius, we
-have implicitly generated an inner hole. This also means that the disc
-will have an inner wall at this radius. Evidence for inner walls in
-circumstellar discs is apparent from the SEDs of disc systems, where a
-peak in emission is found between 2 and 3\,$\mu$m. The temperatures
-reached by such inner walls are expected to generate thermal flux
-contributions within this wavelength range
-\citep{2001ApJ...560..957D}. In fact the structure, radius and
-generation mechanism of the inner wall will lead to markedly different
-contributions to the SED. As discussed in Section \ref{intro} several
-mechanisms can act to clear the inner disc.
-
-Binarity and Giant planet formation would be expected to clear an
-inner disc and shut down accretion from within the inner wall due to
-gravitational perturbations. In addition, photoevaporation from UV and
-FUV flux is expected to halt accretion from radii within the inner
-disc due to the removal of this material via a stellar/disc wind
-\citep{2006MNRAS.369..229A}. These two clearing mechanisms could be
-differentiated by the resulting masses of the discs
-\citep{2007MNRAS.378..369N}. However, for our model systems we have
-neglected both of these effects.
-
-For our models we have initially cleared the inner disc by invoking a
-magnetic truncation radius, however, further disc clearing will be
-caused by the dust destruction/sublimation mechanism we have included.
-In some cases where the radius in the disc at which the dust
-sublimation temperature and densities are reached, ($R_{\rm sub}$)
-will be less than the co-rotation radius ($R_{\rm co}$). For these
-cases, $R_{\rm sub}<R_{\rm co}$, the inner wall radius and shape will
-be controlled by sublimation. Effectively meaning the final inner disc
-radius, after the radiative transfer simulation, will not equal the
-initial inner disc radius. The differences in the starting and
-resulting inner wall radii and the shapes of the inner edges are
-discussed in Section \ref{inner_edge}. If the inner disc is cleared
-via dust sublimation one would expect a residual hot gas disc interior
-to the inner wall. This is as the gas component will not be destroyed
-and is free to extend to the co-rotation radius.  Evidence for a hot
-gas inner disc component has been found through SED fitting by
-\cite{2005ApJ...623..952E} and \cite{2008ApJ...689..513T}.  In
-particular, \cite{2008ApJ...689..513T}, found that emission apparent
-from within the inner wall radius could not be well fit by a modeled
-spherical halo, or optically thin disc, dust component.
-
-Furthermore, as the dust sublimation limit is temperature and density
-dependent \citep{1994ApJ...421..615P}, dust sublimation can lead to
-changes in shape of the inner wall. As the density of the
-circumstellar disc will vary with scale height one would expect the
-dust sublimation radius to vary concurrently with scale height. This
-results in a curved inner wall \citep{2001A&A...371..186N}. As
-explained by \cite{2007ApJ...661..374T}, the fact that near-IR
-excesses of disc systems do not appear strongly dependent on
-inclination indicates that the inner walls are not
-vertical. \cite{2007ApJ...661..374T} also showed that grain growth and
-midplane settling will lead to a curved inner wall (and a hot inner
-gas disc). The curvature is caused by changes in the vertical dust
-density distributions as a function of dust size, or midplane
-settling. Essentially, larger grains will sink more efficiently
-towards the midplane of the disc, and due to their larger surface
-areas cool more efficiently. Therefore, as the scaleheight increases
-the relative proportion of larger to smaller grains will reduce and
-the cooling become less efficient. This will result in higher
-temperatures being reached for larger scale heights at a fixed radius,
-thereby curving the inner wall as the upper layers of the disc reach
-the sublimation temperature at closer radii.
-\cite{2007ApJ...661..374T}, modeled this effect by using two dust
-distributions, a small and a large, with different vertical
-distributions indicative of increased midplane settling for the larger
-grains. For this study we have adopted a size distribution for one
-population of dust grains, with one characteristic vertical
-distribution. As such curvature of the inner wall in our simulations
-will be dominated simply by the dust sublimation temperature, and
-density. The resulting shapes and radial positions of the inner walls
-after the radiative transfer simulations are complete are discussed in
-detail in Section \ref{inner_edge}.
-
 For our model grid we have adopted a gas-to-dust ratio, $\epsilon$, of
 100, and the gas population is assumed essentially static with a zero
-optical depth. Therefore, it does not contribute to the resulting SED,
-and we have not included a hot inner gas disc as found by
-\cite{2008ApJ...689..513T}.
+optical depth.
 
@@
 
-Uncertainty remains over the formation mechanisms, resulting IMFs and
-subsequent interaction mechanisms with associated circumstellar disc,
-for BDs. Furthermore, no current theoretical explanation can be
-demonstrated for the suspected stellar mass-accretion rate
-relationship \citep[$\dot{M}\propto
-M_*^2$,][]{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}
-derived from observations. In addition doubt remains over the
-existence of a disc-locking mechanism in BDD systems, with predictions
-of a correlation of rotation rate with infrared excess possibly
-providing an intrinsic bias \citep{1997AJ....114..288M}. Theoretical
-models are built upon constraints, such as ages, masses and disc
-fractions, and correlations, such as the accretion rate to stellar
-mass relation and rotation rate to period relation (disc-locking),
-derived from the data. Critically, these resulting constraints and
-relationships involve both the application of existing models, such as
-isochrones to derive ages, and the selection of bias-minimised
-samples, for instance removal of foreground or background contaminant
-stars. Clearly, if one is to adopt a new theoretical model or use an
-observed correlation as a constraint one must explore the suspected
-intrinsic biases and the reliability of the selection criteria.
-
-For our model grid we have selected a range of input parameters
-covering expected, from observations, ranges. We have input the
-fundamental parameters of age and mass by adoption of a set of
-theoretical isochrones. We have intrinsically included a correlation
-of rotation rate with initial inner edge position by setting this at
-the co-rotation radius, which is expected to result in a correlation
-of rotation rate with IR excess \citep{1997AJ....114..288M} (the
-reverse of that expected due to angular momentum loss through
-disc-locking). We have not assumed a relationship between accretion
-rate and stellar mass for our model grid. Therefore, analysis of our
-model grid in an attempt to recover the fundamental parameters of age
-and mass, and show accretion rate to stellar mass or rotation rate to
-infrared excess relationships, will allow us to assess the reliability
-of these current theoretical models or relationships.
-
 In this Section we first discuss the physical structure, both density
@@
 
-The initial density structure in our BDD systems is setup as described
-in \cite{2004MNRAS.351..607W} with the the disc surface density
+The initial density structure has the the disc surface density
 conserved, $\Sigma ^{\beta - \alpha}$. The initial scaleheight,
@@
 radius, as opposed to the dust destruction radius used in
-\cite{2004MNRAS.351..607W}. The initial disc scaleheight at 100 AU,
-$h(100)$, was set to 25 AU. As the simulation used vertical
+\cite{2004MNRAS.351..607W}. The initial disc scaleheight at 100\,AU,
+$h(100)$, was set to 25\,AU. As the simulation used vertical
 hydrostatic equilibrium and dust sublimation, both the disc
@@
 the flux levels of the central star increase and lead to heating of
-the disc. This in turn leads to vertical expansion in the disc. For
+the disc which in turn leads to vertical expansion. For
 our models we found that levels of vertical flaring increased
@@
 
-\subsubsection{Inner Edge}
+\subsubsection{Inner edge}
 \label{inner_edge}
@@
 
-\subsubsection{Accretion Dominance}
+\subsubsection{Accretion dominance}
 \label{acc_dominance}
@@
 
-\subsubsection{Flaring and Obscuration}
+\subsubsection{Flaring and obscuration}
 \label{flare_obscure}

### 2010-05-18 BD_disc/paper.tex
Changed intro and \cite names, e.g lamm_2004
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2271 25464f21-6099-402c-b30a-640f1d40d38b

@@
 % v1.2 released 5th September 1994 (M. Reed)
-% v1.1 released 18th July 1994
+% v1.1 released 18th July 
 % v1.0 released 28th January 1994
@@
 possess a flared, dusty circumstellar disc from which they are
-actively accreting material (xxx; xxx). The accretion is thought to
-proceed via a magnetically-controlled funnel flow mechanism in which
-material from a truncated inner disc boundary falls onto the surface
-of the star along magnetic field lines
-\citep{1990RvMA....3..234C,1991ApJ...370L..39K} xxx.
+actively accreting material
+\citep{jayawardhana_2003,mohanty_2004}. The accretion is
+thought to proceed via a magnetically-controlled funnel flow mechanism
+in which material from a truncated inner disc boundary falls onto the
+surface of the star along magnetic field lines
+\citep{camenzind_1990,koenigl_1991,mohanty_2008}.
 
@@
 increased scaleheight, or `puffing up' of the inner disc rim, and
-subsequent shadowing of the region immediately beyond it (Dullemond
-reference). The density-dependent nature of the dust sublimation
-temperature (pollack ref) may also play a role in shaping the inner
-rim (isella ref; tannirkulam ref).
+subsequent shadowing of the region immediately beyond it
+\citep{dullemond_2001}. The density-dependent nature of the dust
+sublimation temperature \citep{pollack_1994} may also play a
+role in shaping the inner rim
+\citep{isella_2005,tannirkulam_2007}.
 
@@
 discs may be the result of giant planet formation or photoevaporation
-(xxx; xxx), these two mechanisms should result in a negligible
-mass-accretion rate and therefore would represent a distinct
+\citep{dahm_2009,najita_2007}, these two mechanisms
+should result in a negligible mass-accretion rate
+\citep{dahm_2009} and therefore would represent a distinct
 evolutionary state of brown dwarf disc (BDD) sytems to that of the
@@
 wall visible to the observer) and the outer disc structure (which may
-obsure the inner disc for high inclincations). (xxx; xxx)
+obsure the inner disc for high inclincations)
+\citep{walker_2004,tannirkulam_2007}.
 
 In surveys, particularly those attempting to discern the PMS disc
-fraction (Xxx), this disentangling usually takes place using broad-band
+fraction , this disentangling usually takes place using broad-band
 photometric measures and cuts in colour-colour or colour-magnitude
-space (xxx; xxx).  The important quantity here is the separation in
-wavelength between the emission peaks for the stellar and thermal disc
-components, as it is these components which must be separated. For BDD
-systems it is likely that difficulties detecting the disc will be
-exacerbated by the lower temperatures of the photosphere and therefore
-the smaller separation in wavelength from the thermal disc emission
-component, compared to CTTS systems. Therefore, to derive disc
-fractions for BD populations we require detailed comparison models
-with which to guide disc candidate selection.
+space
+\citep{luhman_2005,Luhman_2008,gutermuth_2008}.
+The important quantity here is the separation in wavelength between
+the emission peaks for the stellar and thermal disc components, as it
+is these components which must be separated. For BDD systems it is
+likely that difficulties detecting the disc will be exacerbated by the
+lower temperatures of the photosphere and therefore the smaller
+separation in wavelength from the thermal disc emission component,
+compared to CTTS systems. Therefore, to derive disc fractions for BD
+populations we require detailed comparison models with which to guide
+disc candidate selection.
 
@@
 with PMS mass,
-\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
+\citep{muzerolle_2003,natta_2004,natta_2006},
 with an approximate form $\dot{M_{\rm acc}}\propto M_{*}^{~2}$. Since
@@
 correlation is the result of, or at least strengthened by, the
-presence of observational biases (xxxx): At the high-mass (CTTS) end of the
-mass spectrum the lowest accretion-rates cannot be measured via
-continuum methods since the excess is too small in contrast with the
-photopsheric emission. The emission lines will also be weak, and
-indeed the H$\alpha$ equivalent width (EW) may be less than the
-10\AA\ that traditionally demarc?ates classical from weak-lined T Tauri
-stars. Such objects should show doppler-broadened profiles, but the
-line wings will be weak, and the presence of underlying H$\alpha$
-absorption may become dominant. Thus there may be a population of
-low-accretion-rate CTTS which are current missing from the surveys.
+presence of observational biases \citep{clarke_2006}: At the
+high-mass (CTTS) end of the mass spectrum the lowest accretion-rates
+cannot be measured via continuum methods since the excess is too small
+in contrast with the photopsheric emission. The emission lines will
+also be weak, and indeed the H$\alpha$ equivalent width (EW) may be
+less than the 10\AA\ that traditionally demarcates classical from
+weak-lined T Tauri stars. Such objects should show doppler-broadened
+profiles, but the line wings will be weak, and the presence of
+underlying H$\alpha$ absorption may become dominant. Thus there may be
+a population of low-accretion-rate CTTS which are current missing from
+the surveys.
 
@@
 measurements of accreting BDs have been conducted, and these broadly
-support the H$\alpha$ rates (xxxx). Nonetheless it is worth considering the
-observed effect that mass accretion at typical CTTS rates onto a BD
-might have. Parity between the BD photospheric luminosity and the
-accretion luminosity occurs at relatively low accretion rates
-\citep{2006MNRAS.370L..10C}. Such objects may not be detected as BDs
-at all in photometric surveys. Even before such an extreme case is
-reached, the additional luminosity provided by the accretion should
-have measurable effect on the BD colours. Furthermore the additional
-flux will be reprocessed by the disc, altering its scaleheight and
-possibly the shape of its inner edge.
+support the H$\alpha$ rates
+\citep{muzerolle_2003,natta_2004,natta_2006}. Nonetheless
+it is worth considering the observed effect that mass accretion at
+typical CTTS rates onto a BD might have. Parity between the BD
+photospheric luminosity and the accretion luminosity occurs at
+relatively low accretion rates \citep{clarke_2006}. Such
+objects may not be detected as BDs at all in photometric surveys. Even
+before such an extreme case is reached, the additional luminosity
+provided by the accretion should have measurable effect on the BD
+colours. Furthermore the additional flux will be reprocessed by the
+disc, altering its scaleheight and possibly the shape of its inner
+edge.
 
@@
 efficacy of the photometric selections used to isolate brown dwarfs
-and measure disc fractions (xxx;xxx).
+and measure disc fractions
+\citep{luhman_2005,Luhman_2008,gutermuth_2008}.
 
@@
 stellar interior models used for this study are the `DUSTY00' models
-of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
-atmospheric models of \cite{2000ApJ...542..464C}, which are all
+of \cite{chabrier_2000} combined with the `AMES-Dusty',
+atmospheric models of \cite{chabrier_2000}, which are all
 available online
@@
 along magnetically channelled columns from the inner disc boundary.
-For CTTS stars, \cite{2007prpl.conf..479B} show that the magnetic
+For CTTS stars, \cite{bouvier_2007} show that the magnetic
 truncation radius ($R_{\rm mag}$) is less than the co-rotation radius
@@
 Calculations of the magnetic truncation radius depend on derivations
-of the surface magnetic field \citep{1991ApJ...370L..39K}. This is
+of the surface magnetic field \citep{koenigl_1991}. This is
 currently unavailable for BD stars, due to increased molecular species
@@
 $R_{\rm mag}\approx R_{\rm co}$,
-\citep{1991ApJ...370L..39K,1994ApJ...429..781S}. Therefore, for our
+\citep{koenigl_1991,shu_1994}. Therefore, for our
 model simulations, this inner edge radius is dependent on, and derived
@@
 as a maximum size of the circumstellar
-disc. \cite{2008A&A...486..877B} have shown that the disc outer radius
+disc. \cite{bouy_2008} have shown that the disc outer radius
 has little effect on the resulting SED. However, in our subsequent
@@
 model systems showing active accretion where no disc is detected. For
-instance, \cite{2009arXiv0901.2603K} find 43 stars within their sample
+instance, \cite{kennedy_2009} find 43 stars within their sample
 are actively accreting whilst no disc is detected (out of a total
@@
 We have used the {\sc torus} radiative transfer code which is
-described in \cite{2000MNRAS.315..722H}, including the subsequent
+described in \cite{harries_2000}, including the subsequent
 refinements i.e.  addition of Adaptive-Mesh-Refinement (AMR)
-introduced in \cite{2004MNRAS.350..565H}. {\sc torus} uses the method
-of \cite{1999A&A...344..282L} solve radiative equilibrium. The
+introduced in \cite{harries_2004}. {\sc torus} uses the method
+of \cite{lucy_1999} solve radiative equilibrium. The
 simulation also self-consistently solves the equation of
 \textit{vertical hydrostatic equilibrium} and dust sublimation for the
-disc (described in \cite{2007ApJ...661..374T}).
+disc (described in \cite{tannirkulam_2007}).
 
@@
 
-We have adopted a similar dust model to \cite{2002ApJ...564..887W} 
+We have adopted a similar dust model to \cite{wood_2002} 
 with the size distribution of dust particle given by,
@@
 distribution. $C_i$ controls the relative abundance of each
-constituent species ($i$) in the dust. \cite{2002ApJ...564..887W}
+constituent species ($i$) in the dust. \cite{wood_2002}
 found that simulated SEDs fit observed SEDs better using this adjusted
 size distribution for the dust particles, as opposed to a simple power
-law. The best fitting values found in \cite{2002ApJ...564..887W} were
+law. The best fitting values found in \cite{wood_2002} were
 $q=$3.0, $p=$0.6 with $a_{\rm c}=$50\,$\mu$m, also with an associated
@@
 adopted
-\citep{2008A&A...486..877B,2008ApJ...676L.143M,2008arXiv0810.2552P}.
-Here we have adopted the values of \cite{2002ApJ...564..887W}
+\citep{bouy_2008,morrow_2008,pascucci_2008}.
+Here we have adopted the values of \cite{wood_2002}
 except for the parameter $q$ where we have used $q=$3.5.
-\cite{2002ApJ...564..887W} calculated the $C_i$ values for amorphous
+\cite{wood_2002} calculated the $C_i$ values for amorphous
 carbon and silicon by requiring the dust to deplete a solar abundance
 of either component completely \citep[using abundances
-  from][]{1989GeCoA..53..197A,1993ASPC...40..410N}. We have set
+  from][]{anders_1989,noels_1993}. We have set
 $C_i=$1 and adjusted the species using a grain fractional abundance
-\cite[an equivalent process to that of][]{2002ApJ...564..887W},
+\cite[an equivalent process to that of][]{wood_2002},
 however we have adjusted these grain fractions using the updated solar
-abundances of \cite{2006CoAst.147...76A}. The resulting difference in
+abundances of \cite{asplund_2006}. The resulting difference in
 opacity between grain fractions matching the work of
-\cite{2002ApJ...564..887W} and the new grain fractions is only a
+\cite{wood_2002} and the new grain fractions is only a
 slight enhancement of the silicate feature (due to the relative
@@
 contributions within this wavelength range
-\citep{2001ApJ...560..957D}.
+\citep{dullemond_2001}.
 
@@
 in our models. Furthermore, since the dust sublimation temperature has
-a density dependence \citep{1994ApJ...421..615P}, it is both the location and {\em
+a density dependence \citep{pollack_1994}, it is both the location and {\em
   shape} of the inner wall that can change (Isella ref; Tannirkulam ref).
@@
 Our treatment of dust sublimation is similar to that detailed in
-\cite{2007ApJ...661..374T}, but with some enhancements to ensure a
+\cite{tannirkulam_2007}, but with some enhancements to ensure a
 swift convergence of the sublimated rim. The dust sublimation proceeds
@@
 bandpasses selected are, the optical system of
-\cite{1998A&A...333..231B} for \textit{UBVRI} and the \textit{CIT}
-system of \cite{1982AJ.....87.1029E,2004PASP..116....9S} for
+\cite{bessell_1998} for \textit{UBVRI} and the \textit{CIT}
+system of \cite{elias_1982,stephens_2004} for
 \textit{JHK}, with the required shift of $-0.015$\,$\mu$m as prescribed by
-\cite{2004PASP..116....9S}.
+\cite{stephens_2004}.
 
@@
 of varying the parameter space. Flux in the \textit{VI} bands is only
-minimally affected by accretion flux \citep{1998ASPC..154.1709G} and
-disc thermal flux \citep{1998apsf.book.....H} and, additionally, in a
+minimally affected by accretion flux \citep{gullbring_1998} and
+disc thermal flux \citep{hartmann_1998} and, additionally, in a
 \textit{V, V-I} CMD, the reddening vector lies parallel to the pre-MS,
 minimising any age effect of extinction uncertainty, \citep[for a full
-discussion see][]{2008MNRAS.386..261M,2007MNRAS.375.1220M}. The
+discussion see][]{mayne_2008,mayne_2007}. The
 near-IR passbands of \textit{JHK} are most often used to derive
@@
 \citep[the \textit{CIT} systems was chosen to
-match][]{2000ApJ...542..464C}. Finally, as is now well documented the
+match][]{chabrier_2000}. Finally, as is now well documented the
 \textit{Spitzer} IRAC passbands provide the best data with which to
 unambiguously separate naked and star-disc systems
-\citep{2005ApJ...620L..51L}. In addition, at longer wavelengths, the
+\citep{luhman_2005}. In addition, at longer wavelengths, the
 MIPS instrument provides sensitivity to disc systems at much larger
@@
 Typical disc lifetimes for solar type stars are of order 10\,Myrs
-\citep{2001ApJ...553L.153H}. Therefore, we have adopted input ages of
+\citep{haisch_2001}. Therefore, we have adopted input ages of
 1 and 10\,Myrs for our model grid, to span the approximate range of
@@
 data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
+\citep{mayne_2008}, is studied in \cite{scholz_2004},
 where periods are found over the range 5.78$-$74.4 hours ($\approx$
@@
 spots on the BD surface \citep[see][for discussion of variability
-causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
+causes]{bouvier_1995,herbst_2007}. Infrared excesses
 and evidence of accretion are also found to correlate with slower
 rotating TTS, which the authors construe as evidence for a disc
-locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
+locking scenario. \cite{scholz_2004} also find a $mass\propto
 period$ relationship extending into the BD mass regime, this faster
@@
 mechanism, i.e. imperfect disc locking. In addition,
-\cite{2004A&A...419..249S} argue that when compared with data from
+\cite{scholz_2004} argue that when compared with data from
 younger clusters disc lifetimes can be seen to decrease with central
@@
 
-\cite{2005A&A...429.1007S} study rotation period data for stars in the
+\cite{scholz_2005} study rotation period data for stars in the
 vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
-\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
-\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
+\citep{osorio_2002} and the ONC at an age of $\approx$2 Myrs
+\citep{mayne_2008}. Rotation periods, from photometric
 variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
-for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
+for BD mass stars are found. Again, \cite{scholz_2005} find
 some BD objects with irregular variability indicative of accretion hot
-spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
+spots on the stellar surface. \cite{scholz_2005} then analyse
 the mass-period relationship of these data in comparison with data
-from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
-\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
-Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
+from $\sigma$ Ori \citep[3 Myr,][]{scholz_2004}, NGC2264
+\citep[2 Myr,][]{lamm_2004} and then ONC \citep[1
+Myr][]{herbst_2002}. They conclude that either the $\epsilon$
 Ori sample has an age of around 2$-$3 Myrs or there is still
@@
 relation). More specifically for the BD mass regime, they find
-\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
+\citep[in agreement with][]{scholz_2004} an age independent BD
 lower period limit of 2$-$4 hours, therefore at any age a fraction of
@@
 
-\cite{2003ApJ...594..971J} study the rotational periods of BD (and
+\cite{joergens_2003} study the rotational periods of BD (and
 very low mass stars) in the Chameleon I region. This region is $\le$ 1
@@
 3.21 days for their BD mass counterparts. Using supplementary data
-from the literature \cite{2003ApJ...594..971J} propose that a shorter
+from the literature \cite{joergens_2003} propose that a shorter
 lifetime of $\approx$5 Myrs for accretions discs around BDs is more
@@
 surface \citep[see discussion
-in][]{1995A&A...299...89B,2007prpl.conf..297H}. The irregularity is
+in][]{bouvier_1995,2007prpl.conf..297H}. The irregularity is
 thought to be caused by changes in the magnetospheric structure and
-accretion rate \citep{1995A&A...299...89B}. For our model we have
+accretion rate \citep{bouvier_1995}. For our model we have
 assumed that disc material is disrupted at the co-rotation radius and
@@
 smaller coverages, when compared to cooler or `plage' spots
-\citep{2007prpl.conf..297H}. \cite{1995A&A...299...89B} modeled the
+\citep{2007prpl.conf..297H}. \cite{bouvier_1995} modeled the
 size of the cool spots on solar-type stars for a selection of
@@
 spots, onto the stellar disc, of a few to $~$60\%.
-\cite{1995A&A...299...89B} also found projected sizes, onto the
+\cite{bouvier_1995} also found projected sizes, onto the
 stellar disc, of typically a few \% to around 10\% for hot spots.
-\cite{1996AJ....112.2159B} used observations of YY Orionis monitoring
+\cite{bertout_1996} used observations of YY Orionis monitoring
 flux amplitude variations as a function of wavelength to derive a
 probable hot spot area of around 10\%. The spot temperature was also
-modeled for YY Orionis in \cite{1996AJ....112.2159B}, resulting in a
+modeled for YY Orionis in \cite{bertout_1996}, resulting in a
 best fitting areal coverage of 11\%. Therefore, to bound the probable
@@
 Accretion rates derived for pre-MS stars are of order \logmdot = $-6$
-to $-11$ \citep{2006A&A...452..245N}.  With the largest accretion
+to $-11$ \citep{natta_2006}.  With the largest accretion
 rates found in so-called FU Orionis type objects (after the object
@@
 \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9} M_{\odot}yr^{-1}$, for
-  TTS,][]{2009arXiv0901.4120D}, several studies have now suggested
+  TTS,][]{dahm_2009}, several studies have now suggested
 that the accretion rate is strongly correlated with the mass of the
 central star. This relationship was perhaps first suggested by
-\cite{2003ApJ...592..266M} using various accretion diagnostics. Later,
-\citep{2005ApJ...625..906M} derived a relationship of approximately
+\cite{muzerolle_2003} using various accretion diagnostics. Later,
+\citep{muzerolle_2005} derived a relationship of approximately
 $\dot{M}\propto M_*^{~2}$. Further evidence was put forward by
-\cite{2004A&A...424..603N}, where accretion rates as low as 5$\times$
+\cite{natta_2004}, where accretion rates as low as 5$\times$
 10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More recently,
 even lower accretion rates of $\approx$10$^{-13}M_{\odot} yr^{-1}$,
-have been derived for BDs by \cite{2009arXiv0901.3684H}.  Further
+have been derived for BDs by \cite{herczeg_2009}.  Further
 support for a dependence of accretion rate on stellar mass was
 apparent in the significantly more homogeneous dataset of
-\cite{2006A&A...452..245N}. \cite{2006A&A...452..245N} analysed a set
+\cite{natta_2006}. \cite{natta_2006} analysed a set
 of accretion rates and masses derived for pre-MS stars in $\rho$
@@
 is exceedingly difficult for BDD systems
-\citep{2004MNRAS.351..607W}. The inclusion of significant levels of
+\citep{walker_2004}. The inclusion of significant levels of
 accretion flux will act to exacerbate this problem. Essentially, as BD
@@
 Previously studies modeling BD discs have adopted a range of
-disc mass fractions, for instance \citep{2004MNRAS.351..607W} use 0.1,
-0.01 and 0.001$M_*$. \cite{2002ApJ...564..887W} fit observed spectra
+disc mass fractions, for instance \citep{walker_2004} use 0.1,
+0.01 and 0.001$M_*$. \cite{wood_2002} fit observed spectra
 with modeled SEDs to derive a disc mass of 0.003$M_*$, for HH 30
@@
 order of magnitude, with the following specific results: 0.03$M_*$
-\citep[$\rho$ Ophiuchi,][]{2002A&A...393..597N}, 0.055$M_*$ \citep[GM
-Aurigae,][]{2003MNRAS.342...79R}, 0.03$M_*$ \citep[GY 5, GY 11, and GY
-310,][]{2004ApJ...609L..33M} and 0.022$M_*$\citep[2MASS
-J04442713+2512164,][]{2008A&A...486..877B}. As the derived disc masses
+\citep[$\rho$ Ophiuchi,][]{natta_2002}, 0.055$M_*$ \citep[GM
+Aurigae,][]{rice_2003}, 0.03$M_*$ \citep[GY 5, GY 11, and GY
+310,][]{mohanty_2004} and 0.022$M_*$\citep[2MASS
+J04442713+2512164,][]{bouy_2008}. As the derived disc masses
 all have a similar order of magnitude we have adopted $M_{\rm
@@
 Discs around BD stars exhibit increased flaring, due to the reduced
-surface gravity in the disc \citep{2004MNRAS.351..607W}. This
+surface gravity in the disc \citep{walker_2004}. This
 increased flaring, and therefore larger scaleheight of the disc
@@
 and their circumstellar discs. As has been shown in
-\cite{2004MNRAS.351..607W} effects caused by variations in the system
+\cite{walker_2004} effects caused by variations in the system
 inclination angle are much more significant for BDD systems, again
@@
 $\alpha$ and $\beta$ were 2.1 and 1.1 respectively \citep[see][for
-  full discussion of disc structure]{2004MNRAS.351..607W}. The values
+  full discussion of disc structure]{walker_2004}. The values
 for $\alpha$ and $\beta$ were chosen to optimise resolution of the
@@
 radius, as opposed to the dust destruction radius used in
-\cite{2004MNRAS.351..607W}. The initial disc scaleheight at 100\,AU,
+\cite{walker_2004}. The initial disc scaleheight at 100\,AU,
 $h(100)$, was set to 25\,AU. As the simulation used vertical
@@
 
-As discussed in \cite{2004MNRAS.351..607W} discs around CTTS stars
+As discussed in \cite{walker_2004} discs around CTTS stars
 have scaleheights at 100 AU of between $h$(100)$=$7 to 20 AU, whereas
@@
 was found to be larger than CTTS systems by
-\cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
+\cite{walker_2004}. \cite{walker_2004}, state that the
 degree of disc flaring depends on the disc temperature structure and
 the mass of the central star, with the disc scaleheight $h\propto
-\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{1973A&A....24..337S}. Recently,
-\cite{2009arXiv0901.4445E} suggest the inverse relation of flaring
+\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{shakura_1973}. Recently,
+\cite{ercolano_2009} suggest the inverse relation of flaring
 with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
-evidence from \cite{2006ApJ...644..364A}, where SEDs for 17 systems in
+evidence from \cite{allers_2006}, where SEDs for 17 systems in
 the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with
-flared or flat disc models. In general, \cite{2006ApJ...644..364A}
+flared or flat disc models. In general, \cite{allers_2006}
 find that lower mass objects achieve better fits with the flat disc
@@
 
-The results of \cite{2006ApJ...644..364A} show that above a mass of
+The results of \cite{allers_2006} show that above a mass of
 50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
@@
 our grid shows scaleheights comparable to the work of
-\cite{2004MNRAS.351..607W} and as such result in similar consequences
+\cite{walker_2004} and as such result in similar consequences
 for the SEDs and photometric magnitudes. The effects of this flaring
@@
 (described in Section \ref{dust_edge}). In contrast to the models of
-\cite{2004MNRAS.351..607W}, who apply a dust destruction radius, we
+\cite{walker_2004}, who apply a dust destruction radius, we
 set the initial inner radius of the disc at the co-rotation radius of
@@
 has been predicted to lead to a correlation of inner edge position and
-IR excess \citep{1997AJ....114..288M}. This may act to bias surveys
+IR excess \citep{meyer_1997}. This may act to bias surveys
 correlating rotation rates with IR excess to search for evidence of
 disc-locking. However, the flux from the inner edge will usually peak
-between 2 and 3\,$\mu$m \citep{2001ApJ...560..957D}, given that the dust
+between 2 and 3\,$\mu$m \citep{dullemond_2001}, given that the dust
 sublimation temperature peaks at $\approx$1400\,K for canonical
@@
 the star ($\rho\propto R_*^{\alpha}$). The dust sublimation
-temperature is also density dependent \citep{1994ApJ...421..615P}.
+temperature is also density dependent \citep{pollack_1994}.
 Therefore, for systems where the inner edge has been eroded
@@
 the inner edge and the radius to this boundary. This agrees with the
-work of \cite{1997AJ....114..288M} where this correlation is found for
+work of \cite{meyer_1997} where this correlation is found for
 there $R_{\rm inner}=$1$-$12$R_*$ and $\dot{M_{\rm acc}}=$10$^{-9}$to
 10$^{-5} M_{\odot}yr^{-1}$, for flat disc models.
-\cite{1997AJ....114..288M} use this correlation, and the derivation of
+\cite{meyer_1997} use this correlation, and the derivation of
 IR magnitudes, to predict a relationship between IR excess and radius
@@
 dependence of the derived IR excess on system inclination
-\citep{2007ApJ...661..374T}. As discussed in Section \ref{dust_edge}
+\citep{tannirkulam_2007}. As discussed in Section \ref{dust_edge}
 the disc inner hole can be created by several mechanisms, however, for
@@
 temperature and density dependence of the dust sublimation temperature
-\citep{2005A&A...438..899I}. The curved boundary in this case is
+\citep{isella_2005}. The curved boundary in this case is
 convex, as density increases towards the midplane of the disc, the
@@
 moves closer to the star. A curved inner boundary is also found to
-result from dust sublimation in \cite{2007ApJ...661..374T}. In
-\cite{2007ApJ...661..374T} two populations of dust grains where
+result from dust sublimation in \cite{tannirkulam_2007}. In
+\cite{tannirkulam_2007} two populations of dust grains where
 included with different scaleheight distributions. This is essentially
 a simple model of grain growth and subsequent midplane settling.
-\cite{2007ApJ...661..374T}, found a concave inner disc boundary, this
+\cite{tannirkulam_2007}, found a concave inner disc boundary, this
 is due to the larger grains cooling more efficiently. These larger
@@
 disc have been postulated through SED fitting
-\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Again, the shape of
+\citep{eisner_2005,tannirkulam_2008}. Again, the shape of
 the inner wall has changed in Figure \ref{sub_175}, the top and bottom
@@
 $~$1500\,K, or flux contributions from $~$1.85 to 7.7\,$\mu$m
-\citep[nominally 2 to 3\,$\mu$m][]{2001ApJ...560..957D}, and the outer
+\citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and the outer
 disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less contributing
@@
 hydrostatic equilibrium have highly flared discs. As discussed in
-\cite{2004MNRAS.351..607W} this increased flaring (when compared to
+\cite{walker_2004} this increased flaring (when compared to
 CTTS stars) leads to occulltation at the star at lower inclination
@@
 outer disc. This is an extension of the effected found in
-\cite{2004MNRAS.351..607W}, where it was found that this effect alone
+\cite{walker_2004}, where it was found that this effect alone
 can shift the SED, and therefore colours and magnitudes, of inclined
@@
 of the disc and the dependence of the sublimation temperature on
-density. This change in shape, as noted by \cite{2007ApJ...661..374T},
+density. This change in shape, as noted by \cite{tannirkulam_2007},
 will lead to changes in the characteristics of the SED, or derived IR
-excess, with inclination angle \citep{2007ApJ...661..374T}. For
+excess, with inclination angle \citep{tannirkulam_2007}. For
 concave and vertical walls the inner edge is visible over a smaller
@@
 grown vertically and become convex. As shown previously by
-\cite{2007ApJ...661..374T}, a vertical (or concave) inner edge will
+\cite{tannirkulam_2007}, a vertical (or concave) inner edge will
 have strong dependence on inclination angel as the inner edge is
@@
 between IR excess and inner edge location as predicted for the, flat,
-discs of \cite{1997AJ....114..288M}.
+discs of \cite{meyer_1997}.
 
@@
 inner wall location and its resulting temperature, as found in
-\cite{1997AJ....114..288M}. However, \cite{1997AJ....114..288M} go on
+\cite{meyer_1997}. However, \cite{meyer_1997} go on
 to predict a correlation of IR excess with inner edge location. Given
@@
 derivation \cite[see references and discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
+\ref{derived}]{mayne_2007,mayne_2008}.
 
@@
 derivation of single star parameters is completely unreliable
-\citep[see discussion in][]{2008MNRAS.386..261M}. However, exploring
+\citep[see discussion in][]{mayne_2008}. However, exploring
 the changes in the CMDs of single objects will elucidate the causes of
@@
 
-As described by \cite{2004MNRAS.351..607W} the increased flaring, in
+As described by \cite{walker_2004} the increased flaring, in
 BDD systems when compared to CTTS, leads to more significant changes
@@
 $(R-I)_0$ or $M_J$, $(J-H)_0$ etc. Also as discussed in
-\cite{2008MNRAS.386..261M} the use of isochrones for the derivation of
+\cite{mayne_2008} the use of isochrones for the derivation of
 masses and ages for individual pre-MS stars is unreliable at
@@
 Figures (\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}) shows
-a pre-MS isochrone at 1 Myr from \cite{2000A&A...358..593S} adjusted
+a pre-MS isochrone at 1 Myr from \cite{siess_2000} adjusted
 to a distance of 250pc and an extinction of $A_V=2$ mag, simulating a
@@
    respectively. The \textit{top left} only shows the 1 Myr pre-MS
-   isochrone of \citet{2000A&A...358..593S} adjusted to a distance
+   isochrone of \citet{siess_2000} adjusted to a distance
    modulus of 7 and an extinction of $A_V=2$, simulating a reddened
@@
 \textit{top left panel}, showing the 1 Myr isochrone of
-\cite{2000A&A...358..593S} at a distance of 250 pc and extinction of
+\cite{siess_2000} at a distance of 250 pc and extinction of
 $A_V=2$ mags shows that the BDD systems with higher accretion rates
@@
 a CTTS system has already been revealed in
-\cite{2003ApJ...582.1109W}. Furthermore, scatter, although somewhat
+\cite{white_2003}. Furthermore, scatter, although somewhat
 reduced, can be observed in the simulated photometry of the negligibly
@@
 correlated with the rotation period and therefore inner edge position.
-Overall, as found in \cite{2004MNRAS.351..607W}, the dominant
+Overall, as found in \cite{walker_2004}, the dominant
 scattering effect for BD disc systems in an optical CMD appears to be
@@
 occurs when using CMDs constructed using $M_R$, $(R-I)_0$ \citep[using
-the photometric system of][]{1998A&A...333..231B}, except that the 1
+the photometric system of][]{bessell_1998}, except that the 1
 Myr pre-MS isochrone has been omitted. Figure \ref{spread_opt_RRI_typ}
@@
 \ref{spread_opt_VVI_typ} in the same format except in this case the
-pre-MS isochrone of \cite{2000A&A...358..593S} has been smoothed,
+pre-MS isochrone of \cite{siess_2000} has been smoothed,
 purely for aesthetics and to remove the sharper features. Again Figure
@@
  \caption{As Figure \ref{spread_opt_VVI_typ}, in $M_J$, $(J-K)_0$, in
-   this Figure the pre-MS isochrone of \citet{2000A&A...358..593S},
+   this Figure the pre-MS isochrone of \citet{siess_2000},
    has been smoothed.\label{spread_ir_JJK_typ}}
@@
 of $(J-K)_0$ colour with rotation rate as expected from the modeling
-of flat disc by \cite{1997AJ....114..288M}. It is clear that assigning
+of flat disc by \cite{meyer_1997}. It is clear that assigning
 masses to accreting BDD systems using isochrones, for our model grid,
@@
 could also act to reduce the stars radius, accelerating contraction
-\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
+\citep{tout_1999,siess_1999} and introducing
 additional scatter in a coeval population proportional to the range in
-accretion rates \citep[see][for full discussion]{2008MNRAS.386..261M}.
-Our findings support those of \cite{2004MNRAS.351..607W}, showing that
+accretion rates \citep[see][for full discussion]{mayne_2008}.
+Our findings support those of \cite{walker_2004}, showing that
 a significant scatter is caused by obscuration of the central source
@@
 correlation in IR, $(J-K)_0$, colour with rotational rate, as proposed
-by \cite{1997AJ....114..288M}.
+by \cite{meyer_1997}.
 
@@
 now used to detect disc presence
-\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
+\citep{lada_2006,kennedy_2009}. An $\alpha>$-2 is
 used as a selection criterion for disc presence for TTS stars. We have
 constructed the $\alpha$ values for our model grid by adopting the
-limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
+limiting wavelengths of \cite{kennedy_2009}, namely 3.6 to
 8.0\,$\mu$m.
@@
 resulting sublimation decreasing, with density, radially. Therefore,
-one can not extend the predictions of \cite{1997AJ....114..288M},
+one can not extend the predictions of \cite{meyer_1997},
 after adoption of a co-rotation radius to suggest that IR excesses may
@@
 Disc fractions are also derived using the $\alpha$ value
-\citep{2006AJ....131.1574L}, essentially a slope of the SED between
+\citep{lada_2006}, essentially a slope of the SED between
 two wavelengths (at wavelengths longer than the stellar flux peak).
@@
 respectively. For TTS $\alpha>-$2 distinguishes between systems with
-and without discs \citep{2009arXiv0901.2603K}. As can be seen in
+and without discs \citep{kennedy_2009}. As can be seen in
 Figure \ref{disc_frac_alpha} almost all the typical, and all of the
@@
    hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing $\alpha$ value \citep{2006AJ....131.1574L}
+ \caption{Figure showing $\alpha$ value \citep{lada_2006}
    (against an arbitrary model number) used
-   \citet{2009arXiv0901.2603K}, $\alpha=\frac{dlog(\lambda
+   \citet{kennedy_2009}, $\alpha=\frac{dlog(\lambda
      F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
@@
    $\alpha>-$2 cut used to identify disc candidates for solar type
-   stars in \citet{2009arXiv0901.2603K}. Note, that stars of
+   stars in \citet{kennedy_2009}. Note, that stars of
    $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
@@
 respectively. The dashed lines are cuts used in three recent
-publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
+publications, Figure \ref{irac_cut} is from \cite{luhman_2005}
 a study of IC348, Figure \ref{irac_cut_2} from
-\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis and Figure
+\cite{Luhman_2008} a study of $\sigma$ Orionis and Figure
 \ref{irac_cut_3} a study of the Taurus region from
-\cite{2008ApJ...674..336G}. In these cases the effects of extinction
+\cite{gutermuth_2008}. In these cases the effects of extinction
 are either negligible in the plotted colours, with values of
@@
 \leq$4 mag \citep[which will be negligible in the IRAC
-CoCoD,][]{2004ApJS..154..363A}, or the cuts have been placed in
+CoCoD,][]{allen_2004}, or the cuts have been placed in
 intrinsic colour space as for $\sigma$ Orionis.
@@
    lines are a recent BD disc excess cuts used in
-   \citet{2005ApJ...631L..69L} for IC348 at a nominal age of 3-4Myr
-   \citet{2008MNRAS.386..261M}. It must be noted that the naked stars
+   \citet{luhman_2005} for IC348 at a nominal age of 3-4Myr
+   \citet{mayne_2008}. It must be noted that the naked stars
    of $M=$0.01$M_{\odot}$ are not included in this figure as their
@@
  \caption{Figure showing an observational cut used in
-   \citet{2008ApJ...688..362L} for data of the $\sigma$ Orionis
+   \citet{Luhman_2008} for data of the $\sigma$ Orionis
    cluster. It must be noted that the naked stars of
@@
  \caption{Figure showing an observational cut used in
-   \citet{2010arXiv1004.2541M} for data of the Taurus cloud. The
+   \citet{monin_2010} for data of the Taurus cloud. The
    criteria applied for BDD system selection are that of
-   \citet{2008ApJ...674..336G}. It must be noted that the naked stars
+   \citet{gutermuth_2008}. It must be noted that the naked stars
    of $M=$0.01$M_{\odot}$ are not included in this figure as their
@@
 that other than a few typically accreting systems the observational
-cut of \cite{2005ApJ...631L..69L} would select all of the BDD systems
+cut of \cite{luhman_2005} would select all of the BDD systems
 in our grid. Figure \ref{irac_cut_2} shows that the cut of
-\cite{2008ApJ...688..362L} would miss some typical and a very small
+\cite{Luhman_2008} would miss some typical and a very small
 number of extreme accreting BDD systems. Figure \ref{irac_cut_3} shows
@@
 compared to models covering the expected range of parameters.
-\cite{2004A&A...424..603N} derive an accretion rate of -9
+\cite{natta_2004} derive an accretion rate of -9
 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for $\rho$ Ophiucus 102. For
-this object \cite{2002A&A...393..597N} find a spectral type of M6,
+this object \cite{natta_2002} find a spectral type of M6,
 $T_{\rm eff}$ of 2700\,K, an extinction of $A_V$=3.0, a mass of
 $M_*$0.04-0.08$M_{\odot}$ and a distance of 150pc. Photometry for
-$\rho$ Ophiucus 102 is also published in \cite{2006A&A...452..245N},
+$\rho$ Ophiucus 102 is also published in \cite{natta_2006},
 in $J$, $H$ and $K$. Additionally, $R$ and $I$ photometry has been
-published for this object in \cite{2005AJ....130.1733W}. We have
+published for this object in \cite{wilking_2005}. We have
 adjusted our model spectra in the range $M_*$=0.04-0.08$M_{\odot}$,
@@
    parameters to $\rho$ Ophiucus 102 from
-   \citet{2002A&A...393..597N}. The object $\rho$ Ophiucus 102 is
+   \citet{natta_2002}. The object $\rho$ Ophiucus 102 is
    shown in \textit{all panels} as a black star, the BDD systems are
@@
 these BDs by adopting (and interpolating) the interior `DUSTY00'
-models of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
-atmospheric models of \cite{2000ApJ...542..464C}. We have then assumed
+models of \cite{chabrier_2000} combined with the `AMES-Dusty',
+atmospheric models of \cite{chabrier_2000}. We have then assumed
 that accretion occurs from an inner edge of a magnetically truncated
@@
 compared to CTTS. This has previously been explored by
-\cite{2004MNRAS.351..607W}. However, in our study we have included a
+\cite{walker_2004}. However, in our study we have included a
 simple treatment of accretion. This leads to increased flaring as more
@@
 for the lower accreting models as suggested by
-\cite{1997AJ....114..288M}. For the systems with higher accretion
+\cite{meyer_1997}. For the systems with higher accretion
 rates the inner edge temperature is weakly correlated with
@@
 inner boundary, as expected from the work of
-\cite{2007ApJ...661..374T}.
+\cite{tannirkulam_2007}.
 
@@
 accelerate the gravitational contraction and make the star appear
-older \citep{1999MNRAS.310..360T,1999A&A...342..480S}, further
+older \citep{tout_1999,siess_1999}, further
 scattering the apparent age of a coeval population.
@@
 flaring seen in BD discs \citep[for the latter, as found
-by][]{2004MNRAS.351..607W}
+by][]{walker_2004}
 
@@
 rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
-\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}.
+\citep{muzerolle_2003,natta_2004,natta_2006}.
 This relationship has been extended into the BD mass regime in
-\cite{2006A&A...452..245N}. However, arguments based on selection and
+\cite{natta_2006}. However, arguments based on selection and
 detection thresholds have already cast this relation into doubt
-\citep{2006MNRAS.370L..10C}. As we have shown in Section \ref{results}
+\citep{clarke_2006}. As we have shown in Section \ref{results}
 a relationship of this kind is self-reinforcing as lower mass objects
@@
 stars are not included in this relationship due to misidentification.
-As explained in \cite{2004MNRAS.351..607W}, BD systems with a disc,
+As explained in \cite{walker_2004}, BD systems with a disc,
 without including accretion effects, can have the characteristics of
@@
 flaring, accretion and view over a range of inclinations any
-correlation is not apparent. The study of \cite{1997AJ....114..288M}
+correlation is not apparent. The study of \cite{meyer_1997}
 used analytical prescribed flat discs. Whether, any correlation is
@@
 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ to those published in
-\cite{2000ApJ...542..464C}, in the same photometric system
+\cite{chabrier_2000}, in the same photometric system
 (\textit{CIT}). We found significant colour differences ($\delta
 (J-K)\le$ 0.1), between our derived values and those of
-\cite{2000ApJ...542..464C}. As a further check we derived the
-magnitudes in the \cite{1998A&A...333..231B} system (by both adopting
+\cite{chabrier_2000}. As a further check we derived the
+magnitudes in the \cite{bessell_1998} system (by both adopting
 the published zero points, and by using a Vega reference spectrum),
-and applied conversions of \cite{1992ApJS...82..351L}\footnote{We have
+and applied conversions of \cite{leggett_1992}\footnote{We have
   also included the wavelength shift mention in
-  \cite{2004PASP..116....9S}}, to the \textit{CIT} system. For each
+  \cite{stephens_2004}}, to the \textit{CIT} system. For each
 method we failed to match the magnitudes and colours published in
-\cite{2000ApJ...542..464C}. As a final test we passed the downloaded,
+\cite{chabrier_2000}. As a final test we passed the downloaded,
 unaltered, atmospheric spectra directly through the filter response
@@
 $T_{\rm eff}$ from the interior models published in
-\cite{2000ApJ...542..464C}. These magnitudes and colours also failed
+\cite{chabrier_2000}. These magnitudes and colours also failed
 to match. Therefore, we must conclude that the most likely cause of
@@
 derived zeropoints using the filter response of
-\cite{1998A&A...333..231B} and the Vega reference spectrum against
-those published in \cite{1998A&A...333..231B}. For our photometric
+\cite{bessell_1998} and the Vega reference spectrum against
+those published in \cite{bessell_1998}. For our photometric
 systems we integrate the summed number of photons counted by the
 simulated telescope systems, however to test the zeropoints and match
-the system of \cite{1998A&A...333..231B} we must integrate the summed
+the system of \cite{bessell_1998} we must integrate the summed
 energy. The zeropoints we derived \citep[with the values of][in
-parenthesis]{1998A&A...333..231B} were: $U=$20.977(20.94),
+parenthesis]{bessell_1998} were: $U=$20.977(20.94),
 $B=$20.499(20.498), $V=$21.116(21.10), $R=$21.676(21.655),
@@
 $K=$25.884(26.006) and $L=$27.809(27.875). Our derived zeropoints and
-those of \cite{1998A&A...333..231B} match to within 0.05 mags (and
+those of \cite{bessell_1998} match to within 0.05 mags (and
 usually much closer) for all bands except the \textit{H,K} and
@@
 excess (although detected at longer wavelengths) of the observed Vega
-spectrum. \cite{1998A&A...333..231B} use a combined model spectrum of
+spectrum. \cite{bessell_1998} use a combined model spectrum of
 Vega and Sirius as their reference spectrum. As a further test we also
-used the synthetic A0V stellar spectrum of \cite{1993ASPC...41...55C}
+used the synthetic A0V stellar spectrum of \cite{cohen_1993}
 to derive zeropoints but were still unable to improve the match to the
-\cite{1998A&A...333..231B} photometric system for the \textit{JHK}
+\cite{bessell_1998} photometric system for the \textit{JHK}
 colours. However, for these colours we have adopted the \textit{CIT}
@@
 match the published zeropoints in the near-IR bands of the
-\cite{1998A&A...333..231B} using a Vega reference spectrum was
+\cite{bessell_1998} using a Vega reference spectrum was
 probably due to an IR excess in our observed Vega spectrum. However as
@@
 (and colours) for the atmospheric models in
-\cite{2000ApJ...542..464C}, even using published zeropoints for the
-excellently defined system of \cite{1998A&A...333..231B}, and
+\cite{chabrier_2000}, even using published zeropoints for the
+excellently defined system of \cite{bessell_1998}, and
 subsequent conversions to the required \textit{CIT} system
-\citep{1992ApJS...82..351L}, was prescribed to an update in the model
+\citep{leggett_1992}, was prescribed to an update in the model
 atmospheres available online.
@@
 available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
-\citep{1966ARA&A...4..193J,2005ARA&A..43..293B}, \textit{Tycho} $V_t$
-and $B_t$ \citep{2000PASP..112..961B}, Bessell \textit{UBVRIJHKL}
-\citep{1988PASP..100.1134B,1998A&A...333..231B}, SDSS \textit{UGRIZ}
-\citep{1996AJ....111.1748F}, 2MASS $JHK_s$
-\citep{2003AJ....126.1090C,2006AJ....131.1163S}, MKO \textit{JHK}
-\citep{2002PASP..114..169S,2002PASP..114..180T}, UKIRT \textit{ZYJHK}
-\citep{2001MNRAS.325..563H}, IRAS 12, 25, 60 and 100\,$\mu$m
-\citep{1984ApJ...278L...1N} and SCUBA \textit{450WB} and
-\textit{850WB} \citep{1999MNRAS.303..659H}. For further information on
+\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$
+and $B_t$ \citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
+\citep{bessell_1988,bessell_1998}, SDSS \textit{UGRIZ}
+\citep{fukugita_1996}, 2MASS $JHK_s$
+\citep{cohen_2003,skrutskie_2006}, MKO \textit{JHK}
+\citep{simons_2002,tokunaga_2002}, UKIRT \textit{ZYJHK}
+\citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
+\citep{neugebauer_1984} and SCUBA \textit{450WB} and
+\textit{850WB} \citep{holland_1999}. For further information on
 these magnitudes, such as the filter responses used and the adopted
@@
 above. These have been derived following closely the methods of
-\cite{2006ApJS..167..256R}, extended to further passbands. For details
+\cite{robitaille_2006}, extended to further passbands. For details
 of the assumed SED shape, central wavelengths and bandpasses adopted

### 2010-05-19 BD_disc/paper.tex
Shortened Rotation rate section (parameters) and changed inner_temp.ps
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2272 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-XXXX nathan - please reduce by factor 2 in length!
-
 Data for rotation rates, from periodic variability surveys, are widely
 available for a range of different age clusters of TTS. However, fewer
-studies exist on the rotation rates of BD mass objects. To select a
-feasible range of periods for our model grid we have collated the
-results from some recent studies of BD variability. Rotation period
-data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{mayne_2008}, is studied in \cite{scholz_2004},
-where periods are found over the range 5.78$-$74.4 hours ($\approx$
-0.24$-$3.1 days) for BD mass objects. In some cases the periodic
-variability is irregular and assumed to come from active accretion hot
-spots on the BD surface \citep[see][for discussion of variability
-causes]{bouvier_1995,herbst_2007}. Infrared excesses
-and evidence of accretion are also found to correlate with slower
-rotating TTS, which the authors construe as evidence for a disc
-locking scenario. \cite{scholz_2004} also find a $mass\propto
-period$ relationship extending into the BD mass regime, this faster
-rotation in younger mass objects is taken as evidence for a decreasing
-effectiveness of the angular momentum removal of the disc locking
-mechanism, i.e. imperfect disc locking. In addition,
-\cite{scholz_2004} argue that when compared with data from
-younger clusters disc lifetimes can be seen to decrease with central
-object mass.
-
-\cite{scholz_2005} study rotation period data for stars in the
-vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
-\citep{osorio_2002} and the ONC at an age of $\approx$2 Myrs
-\citep{mayne_2008}. Rotation periods, from photometric
+studies exist on the rotation rates of BD mass objects. Rotation
+period data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
+\citep{mayne_2008}, is studied in \cite{scholz_2004}, where periods
+are found over the range 5.78$-$74.4 hours ($\approx$ 0.24$-$3.1 days)
+for BD mass objects. \cite{scholz_2005} study rotation period data for
+stars in the vicinity of $\epsilon$ Ori, with an assumed age of
+$\approx$3 Myrs \citep{osorio_2002} and the ONC at an age of
+$\approx$2 Myrs \citep{mayne_2008}. Rotation periods, from photometric
 variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
-for BD mass stars are found. Again, \cite{scholz_2005} find
-some BD objects with irregular variability indicative of accretion hot
-spots on the stellar surface. \cite{scholz_2005} then analyse
-the mass-period relationship of these data in comparison with data
-from $\sigma$ Ori \citep[3 Myr,][]{scholz_2004}, NGC2264
-\citep[2 Myr,][]{lamm_2004} and then ONC \citep[1
-Myr][]{herbst_2002}. They conclude that either the $\epsilon$
-Ori sample has an age of around 2$-$3 Myrs or there is still
-significant disc locking (concluded using the slope of the mass-period
-relation). More specifically for the BD mass regime, they find
-\citep[in agreement with][]{scholz_2004} an age independent BD
-lower period limit of 2$-$4 hours, therefore at any age a fraction of
-BD stars rotate at short and constant period. Given that these objects
-should spin up as they hydrostatically contract they invoke rotational
-braking in the BD mass regime as a mechanism of removing significant
-angular momentum.
-
-\cite{joergens_2003} study the rotational periods of BD (and
-very low mass stars) in the Chameleon I region. This region is $\le$ 1
-Myrs old, and the authors find rotation periods of 2.19, 3.376 and
-3.21 days for their BD mass counterparts. Using supplementary data
-from the literature \cite{joergens_2003} propose that a shorter
-lifetime of $\approx$5 Myrs for accretions discs around BDs is more
-probable and is inferred from the derivation of a shorter locking
+for BD mass stars are found. \cite{joergens_2003} study the rotational
+periods of BD (and very low mass stars) in the Chameleon I
+region. This region is $\le$ 1 Myrs old, and the authors find rotation
+periods of 2.19, 3.376 and 3.21 days for their BD mass counterparts.
+
+In some cases the periodic variability is irregular and assumed to
+come from active accretion hot spots on the BD surface \citep[see][for
+discussion of variability causes]{bouvier_1995,herbst_2007},
+indicative of active accretion. All the studies mentioned infer a disc
+locking mechanism. Furthermore, \cite{scholz_2004} and
+\cite{scholz_2005} find evidence for a $mass\propto period$
+relationship extending into the BD regime. Additionally,
+\cite{joergens_2003} propose a shorter lifetime of $\approx$5 Myrs for
+BD discs, inferred from a shorter derived disc locking
 timescale. However, as discussed in the previous studies, an imperfect
 disc locking mechanisms is also hypothesised as responsible for the
-less significant loss in angular momentum out to ages of 10 Myrs. The
-data mentioned above and other datasets are summarised and discussed
-in \cite{2007prpl.conf..297H}, where a strong argument for the
-mass-period relationship can be found, shown in their Fig 6, alongside
-further support for either a shorter disc lifetime or imperfect disc
-locking mechanism for BD stars.
-
-Therefore, in summary, it is currently unclear if any disc locking
-mechanisms efficiency or disc lifetimes are a function of mass, with
-an associated phase change over the TTS to BD mass limit. Rotation
-rate and disc presence data are being used to explore issue.
+less significant loss in angular momentum out to ages of 10 Myrs, for
+BD discs. The data on BD rotation rates, disc presence and disc
+locking are summarised and discussed in \cite{herbst_2007}.
+
 Therefore, to create a set of useful models to help contextualise the
-observational constraints we must adopt a realistic, and bounding,
-range of rotation rates. For our model grid, and associated age range
-($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
-placed at around the approximate median for the faster rotating
-samples, providing a useful benchmark for exploring possible detection
-limits of faster rotators with discs. The longer period is set at the
-approximate edge of the slow rotating tail, providing a limiting case
-for the slower rotating, disc-locked, candidates.
+observational constraints, for study of disc locking mechanisms, we
+must adopt a realistic, and bounding range of rotation rates. For our
+model grid, and associated age range ($<$10 Myrs), we have selected
+0.5 and 5 days. With the limits set at at the approximate
+median of faster rotators and the edge of the slower rotators.
 
@@
 surface \citep[see discussion
-in][]{bouvier_1995,2007prpl.conf..297H}. The irregularity is
+in][]{bouvier_1995,herbst_2007}. The irregularity is
 thought to be caused by changes in the magnetospheric structure and
@@
 smaller coverages, when compared to cooler or `plage' spots
-\citep{2007prpl.conf..297H}. \cite{bouvier_1995} modeled the
+\citep{herbst_2007}. \cite{bouvier_1995} modeled the
 size of the cool spots on solar-type stars for a selection of
@@
 and the density, $\rho \propto r^{-\alpha}$. The initial values of
-$\alpha$ and $\beta$ were 2.1 and 1.1 respectively \citep[see][for
-  full discussion of disc structure]{walker_2004}. The values
+$\alpha$ and $\beta$ were 2.1 and 1.1 respectively. The values
 for $\alpha$ and $\beta$ were chosen to optimise resolution of the
@@
 
-\begin{figure}
-  \vspace*{174pt}
+\begin{figure*}
+  \vspace*{348pt}
   \special{psfile="Fig/inner_temp.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+     hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
  \caption{Figure showing data for the inner edge location ($R_{\rm
@@
    accretors).\label{inner_temp}}
-\end{figure}
+\end{figure*}
 
@@
 then show example CMDs and CoCoDs. The \textit{top left panel} shows a
-$M_J$, $(J-H)_0$ CMD, the \textit{bottom left panel} a $M_R$,
-$(R-I)_0$ CMD, the \textit{top right panel} a $M_J$, $(J-K)_0$ CMD and
-finally, the \textit{bottom right panel} a $(J-K)_0$, $(J-H)_0$ CoCoD.
+$J$, $J-H$ CMD, the \textit{bottom left panel} a $R$,
+$R-I$ CMD, the \textit{top right panel} a $J$, $J-K$ CMD and
+finally, the \textit{bottom right panel} a $J-K$, $J-H$ CoCoD.
 
@@
    blue and red dots respectively. The \textit{top left panel} shows a
-   $M_J$, $(J-H)_0$ CMD, the \textit{top right panel} a $M_J$,
-   $(J-K)_0$ CMD, the \textit{bottom left panel} a $M_R$, $(R-I)_0$
-   CMD and the \textit{bottom right panel} shows a $(J-H)_0$,
-   $(J-K)_0$ CoCoD.\label{rho_oph_102}}
+   $J$, $J-H$ CMD, the \textit{top right panel} a $J$,
+   $J-K$ CMD, the \textit{bottom left panel} a $R$, $R-I$
+   CMD and the \textit{bottom right panel} shows a $J-H$,
+   $J-K$ CoCoD.\label{rho_oph_102}}
 \end{figure*}

### 2010-05-19 BD_disc/temp.tex
Shortened Rotation rate section (parameters) and changed inner_temp.ps
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2272 25464f21-6099-402c-b30a-640f1d40d38b

@@
-% mn2esample.tex
-%
-% v2.1 released 22nd May 2002 (G. Hutton)
-%
-% The mnsample.tex file has been amended to highlight
-% the proper use of LaTeX2e code with the class file
-% and using natbib cross-referencing. These changes
-% do not reflect the original paper by A. V. Raveendran.
-%
-% Previous versions of this sample document were
-% compatible with the LaTeX 2.09 style file mn.sty'
-% v1.2 released 5th September 1994 (M. Reed)
-% v1.1 released 18th July 1994
-% v1.0 released 28th January 1994
+Data for rotation rates, from periodic variability surveys, are widely
+available for a range of different age clusters of TTS. However, fewer
+studies exist on the rotation rates of BD mass objects. To select a
+feasible range of periods for our model grid we have collated the
+results from some recent studies of BD variability. Rotation period
+data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
+\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
+where periods are found over the range 5.78$-$74.4 hours ($\approx$
+0.24$-$3.1 days) for BD mass objects. In some cases the periodic
+variability is irregular and assumed to come from active accretion hot
+spots on the BD surface \citep[see][for discussion of variability
+causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
+and evidence of accretion are also found to correlate with slower
+rotating TTS, which the authors construe as evidence for a disc
+locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
+period$ relationship extending into the BD mass regime, this faster
+rotation in younger mass objects is taken as evidence for a decreasing
+effectiveness of the angular momentum removal of the disc locking
+mechanism, i.e. imperfect disc locking. In addition,
+\cite{2004A&A...419..249S} argue that when compared with data from
+younger clusters disc lifetimes can be seen to decrease with central
+object mass.
 
-\documentclass[useAMS,usenatbib]{mn2e}
+\cite{2005A&A...429.1007S} study rotation period data for stars in the
+vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
+\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
+\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
+variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
+for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
+some BD objects with irregular variability indicative of accretion hot
+spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
+the mass-period relationship of these data in comparison with data
+from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
+\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
+Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
+Ori sample has an age of around 2$-$3 Myrs or there is still
+significant disc locking (concluded using the slope of the mass-period
+relation). More specifically for the BD mass regime, they find
+\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
+lower period limit of 2$-$4 hours, therefore at any age a fraction of
+BD stars rotate at short and constant period. Given that these objects
+should spin up as they hydrostatically contract they invoke rotational
+braking in the BD mass regime as a mechanism of removing significant
+angular momentum.
 
-% If your system does not have the AMS fonts version 2.0 installed, then
-% remove the useAMS option.  
-% useAMS allows you to obtain upright Greek characters.
-% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
-% this guide for further information.
-%
-% If you are using AMS 2.0 fonts, bold math letters/symbols are available
-% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
-% preferably \bmath).
-%
-% The usenatbib command allows the use of Patrick Daly's natbib.sty for
-% cross-referencing.
-%
-% If you wish to typeset the paper in Times font (if you do not have the
-% PostScript Type 1 Computer Modern fonts you will need to do this to get
-% smoother fonts in a PDF file) then uncomment the next line
-% \usepackage{Times}
-\usepackage{lscape}
-\usepackage{graphicx}
+\cite{2003ApJ...594..971J} study the rotational periods of BD (and
+very low mass stars) in the Chameleon I region. This region is $\le$ 1
+Myrs old, and the authors find rotation periods of 2.19, 3.376 and
+3.21 days for their BD mass counterparts. Using supplementary data
+from the literature \cite{2003ApJ...594..971J} propose that a shorter
+lifetime of $\approx$5 Myrs for accretions discs around BDs is more
+probable and is inferred from the derivation of a shorter locking
+timescale. However, as discussed in the previous studies, an imperfect
+disc locking mechanisms is also hypothesised as responsible for the
+less significant loss in angular momentum out to ages of 10 Myrs. The
+data mentioned above and other datasets are summarised and discussed
+in \cite{2007prpl.conf..297H}, where a strong argument for the
+mass-period relationship can be found, shown in their Fig 6, alongside
+further support for either a shorter disc lifetime or imperfect disc
+locking mechanism for BD stars.
 
-%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
-\newcommand\mnras{MNRAS}
-\newcommand\pasp {PASP}
-\newcommand\aj   {AJ}
-\newcommand\apj  {ApJ}
-\newcommand\apjl  {ApJL}
-\newcommand\apjs  {ApJS}
-\newcommand\aap  {A\&A}
-\newcommand\aaps  {A\&AS}
-\newcommand\apss  {AP\&SS}
-\newcommand\gca  {Geochim. Cosmochim. Acta}
-\newcommand\araa {ARA\&A}
-\usepackage{multirow}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title[Accreting Brown Dwarfs]{Problems with the characterisation of
-  accreting Brown Dwarfs: A public grid of simulated SEDs and
-  photometry}  \author[N.J.  Mayne and Tim
-Harries]{N.J. Mayne$^{1}$\thanks{E-mail: nathan@astro.ex.ac.uk
-    (NJM)} and Tim Harries$^{1}$\\
-  $^{1}$ School of Physics,
-  University of Exeter, Stocker Road, Exeter, EX4 4QL.\\
-}
- \begin{document}
-
-\date{Accepted ?. Received ?; in
-  original form ?}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2009}
-
-\maketitle
-
-\label{firstpage}
-
-\begin{abstract}
-
-   1) All graphs of SEDS in log log units.
-
-  1a) Add in the new data and write in using more masses.
-
-  1b) Write in the extra inclinations-check from incs.lis.
-
-  1c) Write in that using same points for photosphere.dat
-
-  1) BOUY ET AL 2008, NEUGEBAUER 1984 AND SKRUTSKIE 2006 TRUNCATED AUTHOR LIST.
-
-  2) CHANGE SYMBOLS OF NAKED STARS IN IR EXCESS AND IR EXCESS 2 TO
-  MAKE CLEARER.
-
-  3) REWRITE CONCLUSIONS WITH MORE REFERENCE TO
-  \cite{2004MNRAS.351..607W}, \cite{2006A&A...452..245N} AND
-  \cite{2006MNRAS.370L..10C}.
-
-  4) REDO \& CHECK ALL FIGURES.
-
-  5) COMPARE FINAL INNER RADIUS, AFTER SUBLIMATION, TO COROTATION
-  RADIUS-HOT GAS STUFF.
-
-  6) ADD IN DISCUSSION FOR MIPS AND CHECK ZEROPOINTS
-
-  7) NEED A DISCUSSION OF THE DISC SCALEHEIGHT ETC (PROBABLY IN MODEL
-  OR PAR SPACE): $\rho \propto R^{-\alpha}$, $\alpha =
-  2.25$. $h\propto R^{\beta}$, $\beta = 1.25$. $\sigma = R^{(\beta
-    -\alpha)}$, AND IS CONSERVED. $R_{\rm outer}=300$ AU. DISC SCALEHEIGHT
-  AT 100 AU $H(100)=12.5$ AU
-
-  8) ADD IN DISCUSSION OF THE TIME TAKEN FOR EACH MODEL AND
-  SED-JUSTIFY SMALL NUMBER OF GRID. EACH MODEL (FOR ALL INCLINATIONS)
-  =** HOURS OF SUPERCOMPUTER TIME ON ** CORES
-
-  9) WHAT ABOUT EFFECT OF VERTICAL WALL FOR LONGER PERIOD OBJECTS (NO
-  DUST SUBLIMATION) VERSUS SHORTER PERIOD AND CURVED WALL
-
-  10) PUT IN INNER BOUNDARY PICTURES
-
-  11) SORT OUT PLACEMENT OF CLEARPAGE.
-
-  12) SORT RESULTS BIT ABOUT IRAC FLUX, THIS IS FROM REGIONS BEHIND
-  THE INNER EDGE SO WHY IS THE TREND REVERSED, IT IS NOT COMING FROM
-  THE OUTER FLARED REGIONS OF THE DISC BUT FROM JUST BEHIND THE PUFFED
-  UP INNER EGDE. THEREFORE, FOR LONGER PERIOD OBJECTS THE INNER EDGE
-  IS SMALLER AND THE DISC FLARED SO REGIONS JUST BEHIND CAN EMIT MORE
-  FLUX. FOR SHORTER PERIOD OBJECTS, THE INNER EDGE IS PUFFED UP AND
-  DOMINATES THE SED.
-
-  13) TO PROVE THE POINT ABOVE PRODUCE AN IMAGE BATCH  FILE TO PRODUCE
-  IMAGES FOR A TEST CASE I.E. CLOSE INNER EDGE DISTANT ONE ETC.
-
-  14) Add in reference to the Mike Meyer paper about changes due to
-  inner radius.
-
-15) Reference to bouy et al 2008 showing that the outer radius has a
-negligible effect
-
-16) IMAGES.
-
-17) Add in the Herschel filters.
-
-18) Disc mass fraction.
-
-19) IMF implications.
-
-20) ADD IN RHO OPH 102 STUFF- and add in comparison to stars without accretion
-
-21) Write in a bit about do we expect to see the correlation with
-rotation rate.
-
-22) Colours of 0.01Msol and 0.01Gyr models are very different.-REMOVE
-
-23) Notes abnout isong 200 pts for SEDS naked in consisitency checks
-used full resolution
-
-24) NOTE ABOUT THE FACT THAT 0.01Msol STARS ARE OFF THE BOTTOM OF SOME
-PLOTS AS THEY DIVE DOWN VERY ABRUPTLY.ASK ISABELLE ABOUT THIS
-
-25) Add in comments to mention that due to numerics some models have
-inner edges up to 100K above the 1700K mean dust sublimation temps.
-
-26) Note about colour colour plots cut in magnitude for J and removed
-the 0.01Msol stars from the naked
-
-27) For detections add in piece about the overlapping stars i.e what
-would be missed.
-
-28) missing 0.01 in alpha graph also.
-
-29) Adjust size of the smaller figures (i.e non-four) to fit.
-
-30) Change argument around to say rotation period correlation not
-present.
-
-31) Plots of inner temp against dust sublimation inner radius etc
-
-32) inclination against magnitude for different accretion rates.-one mass
-
-33) Sot out JJK isochrone
-
-34) Note about r=300 but outer radius doesnt matter largey see bouy
-and vitell 2008 or something.
-
-   \end{abstract}
-
-\begin{keywords}
-  stars:evolution -- stars:formation -- stars: pre-main-sequence --
-  techniques: photometric -- catalogues -- (stars) Hertzsprung-Russell
-  H-R diagram
-\end{keywords}
-
-\section{Results: Analysis and Discussion}
-\label{results}
-
-\textbf{Intro-Questions to answer:IMF, Formation, Disc timescales and
-  $\dot{M}\propto M_*^{\approx 2}$=Ages, Masses and Disc fractions}
-
-Uncertainty remains over the formation mechanisms, resulting IMFs and
-subsequent interaction mechanisms with associated circumstellar disc,
-for BDs. Furthermore, no current theoretical explanation can be
-demonstrated for the suspected stellar mass-accretion rate
-relationship \citep[$\dot{M}\propto
-M_*^2$,][]{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}
-derived from observations and doubt remains over the existence of a
-disc-locking mechanism in BDD systems. Theoretical models and are
-built upon constraints, such as ages, masses and disc fractions, and
-correlations, such as the accretion rate to stellar mass relation,
-derived from the data. Critically, these resulting constraints and
-relationships involve both the application of existing models, such as
-isochrones to derive ages, and the selection of bias-minimised
-samples, for instance removal of foreground or background contaminant
-stars. Clearly, if one is to adopt a new theoretical model or use an
-observed correlation as a constraint one must explore the suspected
-intrinsic biases and the reliability of the selection criteria.
-
-In this Section we explore the effects of disc presence and accretion
-(across the described representative ranges, Section \ref{par_space})
-for our model grid. Essentially the premise is that if one accepts the
-assumptions and physical processes within our model grid would one be
-able to derive robust parameters using existing methods and
-furthermore, are the correlations found in the data intrinsic to the
-grid.
-
-Practically, most parameters for young pre-MS stars are derived from
-surveys of populations, usually open clusters, using broadband
-photometry and subsequently constructed colour-magnitude and
-colour-colour diagrams (CMDs and CoCoDs respectively,
-hereafter). Therefore, in this Section, firstly we demonstrate the
-prohibitive effects on the broadband photometry of varying our input
-parameters (Section \ref{photometry}). Secondly, we explore the
-underlying causes of the photometric scatters and intrinsic
-correlations using the SEDs and structure of individual BDD systems
-(Section \ref{sed_causes}).
-
-\subsection{Photometry}
-\label{photometry}
-
-\subsubsection{Ages and Masses}
-\label{age_mass}
-
-For the derivation of ages optical CMDs, in particular in \textit{V,
-  V-I}, are most often used, and indeed most suitable. Whereas, IR
-CMDs, such as a \textit{J, J-K} CMD, are most suitable for mass
-derivation \cite[see references and discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
-
-To delineate the effects of the accretion rate and circumstellar discs
-we have subdivided the grid into two groups, those with accretion
-rates typical for higher mass CTTS objects, defined as
-$\dot{M}=$10$^{-12}M_{\odot}yr^{-1}$ (negligible) to
-$\dot{M}=$10$^{-9}M_{\odot}yr^{-1}$ and those with elevated accretion
-rates, where $\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$. For several of the
-plots in this section the magnitude and colours for the
-$M_*=0.01M_{\odot}$ at high inclinations become extremely faint and
-red, respectively. In some cases these objects appear slightly without
-the scale of the diagram the axes where limited in this way to be able
-to show the changes in colour an magnitude for the majority of stars
-better. The colours and magnitudes for these lowest mass stars are not
-necessarily unreliable but simple hinder the aesthetics of the plots,
-and as they are at the limits of our grid we have decided to omit them
-from some Figures by trimming the axes. Additionally, stars at the
-highest inclinations, i.e edge on disc systems, are often omitted from
-the Figures due to their extremely faint magnitudes, meaning they
-would not be practically observable.
-
-\textit{Derivation of Ages}
-
-Figure \ref{spread_opt_VVI} shows four CMDs in \textit{V, V-I} with
-isochrones constructed from our data (comprising all masses from Table
-\ref{par_space_table}, excluding $M_*=0.01M_{\odot}$ for 10 Myr) at
-ages of 1 Myr and 10 Myrs, solid and dashed lines respectively. These
-isochrones are produced using the naked BD photometry at an accretion
-rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and a areal spot
-coverage of 10\%. The solid green line in the \textit{bottom left
-  panel} only is the 1Myr isochrone for naked systems at an accretion
-rate of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and a areal spot
-coverage of 10\%. The solid green line in the \textit{top left panel}
-only is the 1 Myr from \cite{2000A&A...358..593S} adjusted to a
-distance of 250pc and an extinction of $A_V=2$ mag, simulating a
-background population of CTTS stars. The remaining dots are the
-simulated photometry for the BD disc systems with accretion rates
-classed as typical (-9 to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$)
-at 1 Myr (only) for all areal coverages, periods and inclinations (see
-Table \ref{par_space_table}). The four panels then highlight the
-scatter in CMD space caused by variation across our input parameter
-space. The \textit{top left panel} splits the accretion rates into
-three, -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) as blue
-dots, -10 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black dots and -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red dots. The
-\textit{bottom left panel} shows the scatter due to period changes,
-with systems with periods of 5 days shown as blue dots and 0.5 days as
-red dots. The \textit{top right panel} shows the scatter caused by
-changes in areal coverage, with blue dots showing photometry from 1\%
-coverage systems and red dots for 10\% coverage systems. Finally, the
-\textit{bottom right panel} shows the results separated by inclination
-angles. The inclinations have been separated into three groups for the
-purposes of CMD analysis. These groups are $\theta \leq 48^{\circ}$ as
-blue dots (classed as face-on systems), $\theta> 56$ \& $64^{\circ}$
-(classed as the expected systems, as the expectation value of
-$cos(\theta)=60^{\circ}$) as black dots and $\theta \geq 71^{\circ}$
-(classed as edge-on systems) as red dots.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_VVI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{CMDs in $M_V, (V-I)_0$ showing,as lines, the isochrones for
-   all masses included in Table \ref{par_space_table} for ages 1 Myr
-   (solid) and 10 Myr (dashed). The isochrones are for naked BDs
-   without a disc, for the accretion rate -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (shown as in black), with
-   an areal coverage of 10\%. The solid green line in the \textit{top
-     left panel} only is the 1 Myr from \citet{2000A&A...358..593S}
-   adjusted to a distance of 250pc and an extinction of $A_V=2$ mag,
-   simulating a background population of CTTS stars. The dots are the
-   simulated photometry, of the star and disc system, for all models
-   at an age of 1 Myr with the accretion rates classed as typical (-9
-   to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). \textit{Top left
-     panel} shows the accretion rates separated into three groups -12
-   \& -11, -10 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as blue,
-   black and red dots respectively. \textit{Bottom left panel} shows
-   BDD systems with a rotation period of 5 days as blue dots and 0.5
-   days as red dots. \textit{Top right panel} shows those simulations
-   with an areal coverage of 1\% as blue dots and 10\% as red
-   dots. Finally, the \textit{bottom right panel} shows the systems in
-   three groups of inclinations, $\theta \leq 48^{\circ}$, as blue
-   dots, $\theta \geq 71^{\circ}$ as red dots and $\theta = 56$ \&
-   $64^{\circ}$ as black dots. \label{spread_opt_VVI}}
-\end{figure*}
-
-As can be seen in Figure \ref{spread_opt_VVI} current accretion in a
-star and disc system, for rates typical in the BD mass regime, creates
-a scatter in our simulated photometry indicative of a much larger
-isochronal age spread than 10 Myr. Indeed, for many BDD systems even
-at nominal accretion rates of -11 or -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, for our simulations, the
-colours of these stars move significantly blueward of the expected BD
-locus in a\textit{V, V-I} CMD. As the dots in Figure
-\ref{spread_opt_VVI} are the simulated photometry of BDD systems over
-a range of typical input parameters (see Section \ref{par_space}), an
-observed coeval 1 Myr population could reasonably be expected to show
-a similar scatter. The naked isochrones show that this spread in
-simulated photometry, would lead to a spread in isochronal age greater
-than the $\approx$10 Myr spread claimed for higher mass stars in some
-star forming regions (for instance the ONC). Furthermore, for the
-higher accretion rates of -9 or -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the movement of the star
-within the CMD will effectively move the star into the contamination
-region expected for background CTTS or MS stars at a \textit{V-I} of
-$\leq$1.5 and $M_V 12-10$, and as such the star would not be included
-in a photometrically selected BD sample. The solid green line, in the
-\textit{top left panel}, showing the 1 Myr isochrone of
-\cite{2000A&A...358..593S} at a distance of 250 pc and extinction of
-$A_V=2$ mags shows that the BDD systems with higher accretion rates
-could easily be confused for a background CTTS or MS population (as MS
-stars are simply less luminous at a roughly constant \textit{V-I} than
-the CTTS counterparts). Furthermore, scatter, although somewhat
-reduced, can be observed in the simulated photometry in the negligibly
-accreting systems, for example in the \textit{top left panel} some red
-dots, accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-(which will be negligible compared to the photospheric flux, see
-Figure \ref{acc_dom}), still scatter below the 10 Myr. These objects
-may still be included in a `wide' photometric selection. This scatter
-is a strong function of inclination, as shown in the \textit{bottom
-  right panel}, where, as the inclination is increased the objects are
-pushed lower in the CMD. Indeed, for the edge on cases some objects
-have magnitudes fainter than show in Figure \ref{spread_opt_VVI}
-($M_V\approx 30$). This is expected as the star becomes obscured by
-the flared disc, interestingly for these systems the \textit{bottom
-  right panel} shows that this occurs for inclinations above around
-71$^{\circ}$ in most cases yet even for the lower inclination angles
-some objects have very faint magnitudes, this is due to the disc
-flaring leading to a smaller opening angle and is discussed later in
-Section \ref{disc_struct}. The \textit{top right panel} shows that the
-scatter, in \textit{V}, in our simulated photometry from the
-isochrones is significant for both areal coverages. However,
-significant scatter blueward in colour is slightly more evident for
-the lower areal coverage and therefore hotter accretion spot
-temperature, as is expected given that the higher spot temperature
-contributes more flux blueward of the photosphere. Finally, the
-\textit{bottom left panel}, shows significant scatter in the simulated
-photometry for both adopted rotation periods. This panel also shows
-that scatter in this diagram is not obviously correlated with the
-rotation period and therefore inner edge position. Additionally, the
-\textit{bottom left panel} shows that for naked systems accretion
-rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ lead to the stars
-being scattered into the region occupied by background CTTS and
-contamination (the lower accretion rates are all coincident with the
--12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for 1 Myr). Overall, as
-found in \cite{2004MNRAS.351..607W}, the dominant scattering effect
-for BD disc systems in an optical CMD appears to be caused by
-inclination and therefore obscuration effects of the disc on the
-star. This suggests that for a given photometric survey of BDD systems
-accreting at typical accretion rates and with an expected range of
-inclinations (centred on around 60$^{\circ}$) one would expect to
-exclude a significant fraction of these objects from any isochrone
-based selection.
-
-Similar scattering occurs when using CMDs constructed using \textit{R,
-  R-I} \citep[using the photometric system
-of][]{1998A&A...333..231B}. Figure \ref{spread_opt_RRI} shows the
-\textit{R, R-I} CMD.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_RRI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_opt_VVI} but the 1 Myr isochrone
-   of \citet{2000A&A...358..593S} is omitted and the CMDs are for
-   $M_R, (R-I)_0$. \label{spread_opt_RRI}}
-\end{figure*}
-
-Therefore, if one adopts the range of input parameters we have used
-(see Section \ref{par_space} for justification), our simulated
-photometry shows, qualitatively, that a coeval 1 Myr population of
-accreting BD stars and BDD systems, with typical accretion rates and
-range of inclinations, will exhibit a scatter in apparent isochronal
-age of $>$10 Myr. Furthermore, some objects will be scattered below
-and blueward of a 10 Myr isochrone. This has been shown for CMDs in
-\textit{V, V-I} and \textit{R, R-I}. It is important to note at this
-point that these conclusions are qualitative, and obviously based on
-our assumptions. However, the repercussion for isochronal age
-derivation and sample selection in the BD regime could be
-profound. Indeed this study has only included the effects of current
-or ongoing accretion from a disc, it has totally neglected any effects
-of accretion, both past and present, on the evolution of the central
-star. This past accretion could also act to reduce the stars radius,
-accelerating contraction
-\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
-additional scatter in a coeval population proportional to the range in
-accretion rates \citep[See][for full
-discussion]{2008MNRAS.386..261M}. Our findings support those of
-\cite{2004MNRAS.351..607W}, showing that a significant scatter is
-caused by obscuration of the central source by the central disc. In
-addition we have shown that the scatter blueward, into the CTTS or
-background MS locus, is caused by active accretion at levels found in
-CTTS stars, but currently not regularly recorded in stars classified
-or selected as BDs.
-
-\textbf{Derivation of Masses}
-
-Similar consequences are apparent when attempting to derive masses
-from isochrones using CMDs. We have constructed CMDs using the
-simulated photometry of our model grid in the \textit{JK}
-magnitudes. Figure \ref{spread_ir_JJK} shows CMDs in \textit{J, J-K} for
-the same data as Figure \ref{spread_opt_VVI}. The symbols have the
-same meanings as in Figure \ref{spread_opt_VVI}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_ir_JJK.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_opt_VVI} but the CMDs is for $M_J,
-   (J-K)_0$.\label{spread_ir_JJK}}
-\end{figure*}
-
-As is shown by Figure \ref{spread_ir_JJK} a similar scatter is
-observed in our simulated photometry in the IR CMD as is evident in
-its optical counterparts. Once again, as shown in the \textit{top left
-  panel}, scatter is seen in both the nominal and higher accretion
-rates (-9 to -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), meaning
-derivation of masses for objects using IR isochronal fitting of these
-objects would be very difficult. However, in this CMD the scatter is
-generally redward of the isochrone, this is still however into the
-region where background CTTS stars would be expected. The \textit{top
-  right panel} shows no correlation with areal coverage of the hot
-spot. Interestingly the \textit{bottom left panel} shows no clear
-evidence for a correlation in CMD position, and therefore distance
-from the isochrone, with rotation period of the system as found in
-\cite{1997AJ....114..288M}, this is discussed in more detail in
-Section \ref{disc_struct}. Additionally, \textit{bottom left panel}
-agains shows significant scatter away from the isochrone for the 1 Myr
-naked stars at an accretion rate of -9
-$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, however in this case the scatter
-is in the opposite sense (blueward as opposed to redward) to that
-caused by accretion and disc presence in the BDD systems. Again,
-scatter is still caused by changes in inclinations, as shown in the
-\textit{bottom right panel}, with fainter magnitudes for more inclined
-systems, as expected however, this effect causes a smaller change in
-magnitude in the IR due to less of the disc appearing optically thick
-at these wavelengths.
-
-Therefore, as for derivations of age, given our assumptions, and the
-adopted range of input parameters, a 1 Myr coeval population scatters
-significantly in a \textit{J, J-K} CMD. The \textit{J, J-K} CMD is
-representative of CMDs constructed from the \textit{JHK}
-passbands. So, qualitatively at least, derivation of masses using
-isochronal fitting of our simulated photometry would not produce
-reliable or accurate results. Again, as discussed for optical CMDs,
-these simulations do not include any of the effects of past or current
-accretion on the evolution of the central object, which is expected to
-significantly exacerbate the observed scatter. This is also true for
-the naked systems with small increases in accretion rate leading to
-significant scatters in the CMDs. Additionally, given the evidence
-discussed in \cite{2004MNRAS.351..607W}, supported by the evidence
-from our own simulated photometry shown in Figures
-\ref{spread_opt_VVI}, \ref{spread_RI} and \ref{spread_ir_JJK}, it is
-clear that young, accreting, BDD systems are likely to be
-misidentified when using photometric colours or magnitudes, even at
-generally canonical accretion rates. This casts doubt on the veracity
-of the mass to accretion rate relationship. For our model grid we have
-not assumed any such relation, therefore, as our data would also show
-a similar relation it suggests that the observed result may be caused
-by intrinsic scattering. The relation, $\dot{M}\propto M_*^{2}$
-suggests that their is a dearth of lower mass stars accreting at
-higher rates. We have shown that for accretion rates in the range -12
-to -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with
-higher accretion rates would be preferentially missed using
-photometric or isochronal selection.
-
-\subsubsection{Extreme accretion rates}
-\label{elevated_accn}
-
-\textbf{CMDs}
-
-BDD and naked BD systems with elevated or extreme accretion rates are
-also likely to be miss-classified, or not observable in the same
-dynamic magnitude range as a BD survey.  Figure \ref{high_acc_opt}
-shows our isochrones for the naked BD systems with accretion rates of
--6, -7 \& -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ at 1 Myr (solid
-lines in red) with areal coverages of 10\%, and the pre-MS isochrone,
-at 1 Myr, of \cite{2000A&A...358..593S} for higher mass stars, down to
-$M_*=$0.1$M_{\odot}$ (solid black line). The remaining dots are the
-simulated photometry from our model grid for stars with an age of 1
-Myr and accretion rates of -6, -7 \& -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, and the complete range of all
-other input parameters (see Table \ref{par_space_table}. As can be
-seen by comparing Figure \ref{spread_opt_VVI} with Figure
-\ref{high_acc_opt} the simulated photometry for the naked systems
-changes dramatically with increasing accretion rate, meaning that even
-without the effects of a disc individual highly accreting BDs
-dramatically change position in an optical CMD. The simulated
-photometry of the disc systems is then separated in each panel. The
-\textit{top left panel} shows systems with accretion rates of -6, -7
-and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red, black and blue
-dots respectively. The \textit{top right panel} distinguishes the
-areal coverages of 1 and 10\% as red and blue dots respectively. The
-\textit{bottom left panel} separates the two rotational periods of 5
-and 0.5 days into blue and red dots respectively. Finally, the
-\textit{bottom right panel} plots the three adopted inclinations
-groups $\theta \leq 48^{\circ}$, $\theta> 56$ \& $64^{\circ}$,
-$cos(\theta)=60^{\circ}$) and $\theta \geq 71^{\circ}$, as blue, black
-and red dots respectively.
-
-The \textit{top left panel} shows that these objects are generally
-scattered to an apparently higher (isochronal) mass and older
-(isochronal) age, with the scatter increasing with accretion
-rates. This means that as the accretion rate increases the star is
-pushed to bluer and brighter colours and magnitudes, effectively, to
-higher stellar masses. The \textit{top right panel} shows that this
-effect is apparent for both areal coverages, it is perhaps surprising
-that in general there does not appear to be a reduction in the
-magnitude of the scatter when one moves to the larger areal
-coverage. The \textit{bottom left panel} shows again that there is no
-correlation in CMD position with rotation rate, and therefore
-co-rotation radius (again this is discussed further in Section
-\ref{disc_struct}. Finally, the \textit{bottom right panel} again
-shows that the system inclination scatters the resulting position
-within the CMD, with greater inclination meaning greater obscuration
-of the central star, by the disc, and therefore fainter magnitudes and
-redder colours, and it is clear that photometrically a highly
-obscured, highly accreting BDD system could be photometrically
-classified as contamination or a higher mass CTTS system.
-
-Once again, given our assumptions, qualitatively, young, pre-MS BD
-disc systems accreting at higher rates would not be identifiable as
-such from optical CMDs and isochronal fitting. Meaning it is likely
-that our data would indicate a stellar mass to accretion rate
-relation, even though we have not adopted such a relationship.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/high_acc_opt.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{The optical CMD, $M_V, (V-I)_0$ showing the effects of
-   extreme accretion rates. The solid black line is the pre-MS
-   isochrones of \citet{2000A&A...358..593S} at 1 Myr for masses down
-   to 0.1 $M_{\odot}$, the solid red lines are our derived isochrones
-   for the naked photospheric models at accretion rates of -6, -7 \&
-   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, colours of red, black
-   and blue respectively, using an areal coverage of 10\% (the coolest
-   and therefore lowest accretion luminosity). The dots are the
-   simulated photometry for the BDD systems for the three highest
-   accretion rates (as for the isochrones). \textit{Top left panel}
-   shows the accretion rates separated into three groups -6, -7 and -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as red, black and blue dots
-   respectively. The data in the remaining panels is separated into
-   the groups used in Figure \ref{spread_opt_VVI} using the same
-   symbols and colours.\label{high_acc_opt}}
-\end{figure*}
-
-A similar situation is apparent for the IR passbands, where isochrones
-are often used to derive stellar masses. Figure \ref{high_acc_ir} is
-the IR version of Figure \ref{high_acc_opt}, the only difference
-between the figures are the colours and magnitudes, the conventions,
-symbols and models are the same. Figure \ref{high_acc_ir} shows the
-CMDs using \textit{J, J-K}, also using the same conventions for each
-of the \textit{four panels}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/high_acc_ir.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As above but for $M_J, (J-K)_0$ colours. Here the effects
-   of high accretion can shift the stars into higher or lower mass bins.
-   \label{high_acc_ir}}
-\end{figure*}
-
-As can be seen by comparing Figure \ref{spread_ir_JJK} and Figure
-\ref{high_acc_ir}, accreting BD systems without discs are shifted
-brighter and bluer resulting in a large error in isochronal mass
-derivation. The simulated photometry for BDD systems however, shows
-large magnitudes of scatter redward and towards slightly brighter
-magnitudes. Given that the reddening vector is approximately
-horizontal in a \textit{J, J-K} CMD many of these objects will appear
-as heavily obscured objects of higher mass. The \textit{top left
-  panel} shows that the scatter does increase for higher accretion
-rates, however, even at the lower of the accretion rates (-8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), significant scatter is
-evident. The \textit{top right panel} shows that the scatter is
-roughly the same for both areal coverages. The \textit{bottom left
-  panel} shows, again, no correlation between rotation rate and
-scatter within the CMD. This is unsurprising as at these elvated
-accretion rates the increase in flux will lead to significant levels
-of dust sublimation of the inner edge, as discussed in more detail in
-Section \ref{disc_struct}. Finally, the \textit{bottom right panel}
-shows systems with a larger inclination having, generally lower
-magnitudes, and therefore lower masses, as expected.
-
-Therefore, again as for the optical case, given our assumptions and
-parameter space, BDD systems accreting at higher rates would not be
-identified with the correct mass in most cases using IR CMDs.
-
-\subsubsection{Disc fractions}
-\label{derive_frac}
-
-To distinguish between the proposed formation mechanisms for BDs, and
-to derive disc lifetimes, accurate derivations of disc fractions are
-required (as well as stellar masses).
-
-\textbf{Derivation of disc fractions.}
-
-Disc fractions have been derived using infrared excesses previously in
-\textit{JHK}, however recent works pre-dominantly use \textit{Spitzer}
-IRAC magnitudes. Furthermore, MIPS magnitudes are used to identify
-so-called debris discs, where IR excesses are not apparent at shorter
-wavelengths. Finally, disc fractions have also been derived using the
-$\alpha$ criteria, where $\alpha=\frac{dlog\lambda
-  F\lambda}{dlogF\lambda}$ between two limiting wavelengths,
-originally used to distinguish amongst Class I, II or II sources, but
-now used to detect disc presence
-\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
-used as a selection criterion for disc presence for TTS stars. We have
-constructed the $\alpha$ values for our model grid by adopting the
-limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
-8.0$\mu$m.
-
-\subsubsection{Colour-colour plots}
-\label{col_col_plots}
-
-Figure \ref{ir_excess} shows CoCoDs in \textit{J-H, J-K} for our
-simulated photometry for all accretion rates, masses, inclinations,
-coverages and periods, at 1 Myr only. The black crosses are the
-simulated photometry of the naked BD systems, with the dots the
-simulated photometry of the BDD systems, for 1 Myr only.  The
-\textit{top left panel} then separates the accretion rates with -12,
--11, and -10 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as red dots
-and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as green dots and
--8, -7, and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue
-dots. The \textit{top right panel} distinguishes those models with
-areal accretion stream coverages of 1 and 10\% as blue and red dots
-respectively. The \textit{bottom left panel} separates the rotational
-periods with 0.5 days shown as red dots and 5 days as blue dots. The
-\textit{bottom right panel} shows each of the three inclination groups
-$\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as
-green dots and $\theta \geq 71^{\circ}$ as red dots.
-
-As can be seen for all the panels of Figure \ref{ir_excess} there is a
-slight overlap between the naked or disc less objects and the BDD
-systems. This overlap is small, only some of the smallest mass naked
-objects appear redward of the main population. Generally, a well
-placed cut should identify a large proportion of the disc candidates
-as is well known, if there is little complication from variable
-extinction and a well defined photometric system. However, the fact
-that an overlap exist at all will lead to some confusion as to the
-position of any disc excess cut. For real data a cut will be placed at
-a user identified paucity or gap in the CoCoD. Therefore, in practice,
-if any other region of the population appears equally, or more, sparse
-the cut is likely to be miss-placed. In practice these disc fractions
-are known to be lower limits of the true values, so ostensibly a miss
-placed cut, essentially missing some disc candidates is not
-problematic. On further inspection however it does introduce a crucial
-bias. In all panels of Figure \ref{ir_excess} potential gaps or drops
-in the number of stars can be seen at $J-K \approx$ 1.5 \& 2.5. The
-\textit{top left panel} shows that changes in accretion rate do not
-appear, qualitatively, to correlate with CoCoD position, indeed
-changes in the different areal coverages (\textit{top left panel}),
-inclinations (\textit{bottom right panel}) and rotation rate
-(\textit{bottom left panel}) also appear to produce random scatter.
-
-Critically a strong correlation can be
-observed between CoCoD position and rotation period of the system in
-the \textit{bottom left panel}. This panel shows that longer period
-objects, in general, lie closer to the naked BD locus and are
-therefore more likely to be classed as disc less stars. Conversely,
-almost all of the short period objects lie well separated from the
-naked BD locus, and one could also argue for a separation between the
-two populations of different rotation periods at $J-K \approx$2. It is
-therefore, likely, that early surveys of BD (or perhaps TTS) stars
-attempting to find a correlation between disc presence and slower
-rotation rates, to support disc locking, were heavily affected by this
-bias. Essentially, unless the data are free from variable extinction
-and photometric errors are small, manually placing a disc excess cut
-based on population densities is likely to preferentially miss slower
-rotators and include faster rotators. This leads to an
-anti-correlation between disc presence and slow rotation period.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/ir_excess.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing relative positions of accreting BDs with
-   (naked) and without discs in $(J-H)_0, (J-K)_0$ CoCoDs. \textit{Top
-     left panel}, this shows all studied accretion rates as green, red
-   blue and black dots for -6, -7, -8 and -9, -10, -11, -12 (together)
-   respectively log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
-   \textit{Lower left panel}, here blue dots are star disc systems
-   with a rotation period of 5 days and red for 0.5
-   days. \textit{Upper right panel}, blue dots are those simulations
-   with an areal coverage of 1\% and red dots have 10\%. Finally, the
-   \textit{lower right panel}, the systems at different inclinations
-   are shown with 0, 60 and 90$^{\circ}$ shown as black, blue and
-   red dots respectively.
-   \label{ir_excess}}
-\end{figure*}
-
-More recent studies, and indeed those studies where strong support for
-a disc locking mechanism is found, use data from the IRAC camera on
-the \textit{Spitzer} space telescope \citep[as for TTS,
-see][]{2007ApJ...671..605C}. Therefore, using our simulated photometry
-in these passbands we are able to investigate any possible expected
-biases in observations of this type. Figures \ref{irac_excess} and
-\ref{irac_excess_2} are similar to Figure \ref{ir_excess} showing the
-same models and using the sames conventions and symbol meanings, only
-showing constructed CoCoDs using IRAC channels. It is important to
-note that objects, either naked or with discs, of mass,
-$M_*=$0.01$M_{\odot}$ are not included in Figures \ref{irac_excess} and
-\ref{irac_excess_2}, as their flux becomes unreliable and noise
-dominated at these longer wavelengths. Figure \ref{irac_excess} shows
-[4.5]-[5.8] against [3.6]-[4.5] and Figure \ref{irac_excess_2}
-shows [5.8]-[8.0] against [3.6]-[4.5], two commonly used disc
-identification CoCoDs. In both these figures the naked (disc less) BD
-population is very well separated from the main population, meaning in
-a region free of variable extinction and with reliable photometry disc
-excess cuts can be placed with a high degree of confidence. As seen
-for Figure \ref{ir_excess} little correlation is found between CoCoD
-position and accretion rate, areal coverage or inclination, however, a
-clear correlation is again found with rotational period.
-
-The effect of rotational period on the position of the BDD systems in
-the IRAC CoCoDs is the reverse of that found for \textit{JHK}. Longer
-period objects will be observed as lying further from the naked BD
-locus, resulting in any uncertainty in the cut position preferentially
-including shorter period systems. This may introduce a slight bias in
-disc fraction surveys carried out using IRAC data, perhaps falsely
-increasing the apparent strength of a disc-locking type correlation
-between inferred disc presence and slower rotators. However, if a
-similar effect is apparent in TTS (as would be expected albeit
-slightly reduced due to less significant flaring of the outer disc),
-the much clearer separation between naked and disc systems means that
-this bias will be much easier to avoid.  Therefore, our results do not
-affect the recent evidence for a disc-locking mechanism in TTS.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_excess.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{ir_excess} but in IRAC colours
-   [3.6]-[4.5] against [4.5]-[5.8]. 
-   \label{irac_excess}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_excess_2.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{irac_excess} but in IRAC colours
-   [3.6]-[4.5] against [5.8]-[8.0]. 
-   \label{irac_excess_2}}
-\end{figure*}
-
-\textbf{IRAC and MIPS diagrams}
-
-**NOTE ABOUT $M_*=$0.01$M_{\odot}$ CURRENTLY NOT REMOVED**
-
-Figures \ref{irac_mips_excess} and \ref{irac_mips_excess_2} show
-CoCoDs for colours constructed using IRAC and MIPS data. These Figures
-include the same models as Figures \ref{irac_excess} and
-\ref{irac_excess_2}, presented using the same symbols and colour
-conventions. The longer wavelength MIPS data provides better
-sensitivity to the outer disc emission. As with the IRAC data
-alone the separation between the BDD and naked systems is large and
-the clearest correlation between input parameter and colour-colour
-space position is rotation period. A evident in the \textit{bottom
-  left panels} of Figures \ref{irac_mips_excess} and
-\ref{irac_mips_excess_2}, the longer period systems generally lie
-redward in both [3.6]-[4.5] and [8.0]-[24.0] than the shorter period
-systems. Some correlation of colour-colour position and inclination is
-evident from the \textit{bottom right panels} of Figures
-\ref{irac_mips_excess} and \ref{irac_mips_excess_2}. In this case as
-the inclination increases the systems generally move redward in
-[8.0]-[24.0].
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_mips_excess.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{A CoCoD constructed using both IRAC and MIPS data showing
-   [3.6]-[4.5] against [8.0]-[24.0]. The symbols are as described in
-   As for figure \ref{ir_excess}.
-   \label{irac_mips_excess}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_mips_excess_2.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{irac_mips_excess} but using colours
-   [3.6]-[5.8] against [8.0]-[24.0].
-   \label{irac_mips_excess_2}}
-\end{figure*}
-
-Figure \ref{mips_four} shows CoCoDs constructed using only MIPS data,
-plotting the colours 24$-$70$\mu$m against 70$-$160$\mu$m for the 1 Myr
-naked and BDD systems. Figure \ref{mips_four} shows that, again, the
-naked and BDD systems are well separated. Figure \ref{mips_four} also
-shows the correlations in scatter for each input variable. For
-\textit{all panels} of Figure \ref{mips_four} the crosses show the
-naked systems and the dots are the BDD systems. The \textit{upper left
-  panel} separates the two accretion rates with -8 and -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ plotted as blue and red dots
-respectively. In the \textit{upper right panel} the BDD systems with 1
-and 10\% areal coverages are plotted as blue and red dots
-respectively. The \textit{lower left panel} plots the periods of 5 and
-0.5 days as blue and red dots respectively. \textit{lower right panel}
-separates the BDD systems by inclination with 0, 60 and 90$^{\circ}$
-plotted as black, blue and red dots respectively. As can be see in
-Figure \ref{mips_four} the inclination correlates strongly with CoCoD
-position with the almost edge-on systems appearing much redder than
-the naked or face on BDD systems. Furthermore, using the \textit{lower
-  panels} it can be seen that for each inclination the CoCoD position
-is then separated by rotation period, with two separated populations
-for each inclination group.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/mips_four.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for figure \ref{irac_excess} but in MIPS colours
-   [24]-[70]($\mu$m) against [70]-[160]($\mu$m). 
-   \label{mips_four}}
-\end{figure*}
-
-\subsubsection{Observational cuts}
-\label{obs_cuts}
-
-Some recent studies of disc fractions for BD populations have used
-data from the \textit{Spitzer} IRAC camera. Figures
-\ref{irac_cut} and \ref{irac_cut_2} show the simulated photometry for
-our complete model grid. Naked BDs are shown as crosses and BDD
-systems as dots, with 1 and 10 Myrs data shown as blue and red dots
-respectively. The dashed lines are cuts used in two recent
-publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
-a study of IC348 and Figure \ref{irac_cut_2} from
-\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis. In both cases
-the effects of extinction are either negligible in the plotted
-colours, with values of $E([3.6]-[4.5])<0.04$ \& $E([4.5]-[5.8])<0.02$
-for IC348, or the cuts have been placed in intrinsic colour space as
-for $\sigma$ Orionis. As can be seen from Figures \ref{irac_cut} and
-\ref{irac_cut_2} most of the disc systems from our simulated
-photometry would be correctly identified using these cuts. It is
-important to note that as for Figures \ref{irac_excess} and
-\ref{irac_excess_2} stars of mass, $M_*=$0.01$M_{\odot}$, are not
-included due to unreliable flux levels at these
-wavelengths. Additionally, our conclusions so far have been drawn from
-differential photometric arguments, in this case we are using
-intrinsic colours and these values are extremely sensitive to changes
-in zero point and photometric calibration.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/irac_cut.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{This shows all simulated photometry for the entire studied
-   parameter range at ages 1Myr and 10Myr as dots (blue and red
-   respectively), and the naked photometry as crosses. The dashed
-   lines are a recent BD disc excess
-   cuts used in \citet{2005ApJ...631L..69L} for IC348 at a nominal age
-   of 3-4Myr \citet{2008MNRAS.386..261M}. It must be noted that the naked
-   stars of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours.
-   \label{irac_cut}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/irac_cut_2.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{This figure shows an observational cut used in
-   \citet{2008ApJ...688..362L} for data of the $\sigma$ Orionis
-   cluster. It must be noted that the naked
-   stars of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours.
-   \label{irac_cut_2}}
-\end{figure}
-
-\textbf{alpha}
-
-Disc fractions are also derived using the $\alpha$ value
-\citep{2006AJ....131.1574L}, essentially a slope of the SED between
-two wavelengths (at wavelengths longer than the stellar flux
-peak). Figure \ref{alpha_zoom} shows the derived $\alpha$ values
-between 3.6 and 8.0$\mu$m for our entire model grid (against an
-arbitrary model number), with dots showing BDD systems and crosses
-showing naked systems. As shown for TTS $\alpha>-$2 distinguishes
-systems with discs \citep{2009arXiv0901.2603K}. As can be seen in
-Figure \ref{alpha_zoom} almost all (except $\frac{3}{1120}$) disc
-systems would be successfully identified using this
-criterion. Suggesting that the $\alpha$ value is a reliable disc
-indicator for BD systems. Figure \ref{alpha_four} show the same Figure
-(Figure \ref{alpha_zoom} in \textit{four panels} with each panel
-showing spread caused by a particular input variable. The
-\textit{upper left panel} shows the alpha values for two different
-accretion rates, with -12 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue and red dots
-respectively. The \textit{upper right panel} differentiates
-populations with different areal coverages of the accretion stream,
-where 1 and 10\% are shown as blue and red dots respectively. The
-\textit{lower left panel} shows scatter caused by rotational period
-changes, with periods of 5 and 0.5 days shown as blue and red dots
-respectively. Finally, the \textit{lower right panel}, the systems at
-different inclinations are shown with 0, 60 and 90$^{\circ}$ shown as
-black, blue and red dots respectively. It is important to note that
-the lowest mass objects ($M_*=$0.01$M_{\odot}$) do not appear in Figures
-\ref{alpha_zoom} or \ref{alpha_four} due to unreliable flux estimates
-for the stellar atmospheres at the longer wavelengths ($\lambda >$4$\mu$m).
-
-Figure \ref{alpha_four} shows, as one would expect a similar
-scattering pattern to the IRAC photometry. This is as the $\alpha$
-value has been derived over a similar wavelength range, namely, 3.6
-to 8.0$\mu$m. Essentially, the $\alpha$ values shows the scatter is
-uncorrelated with coverage and accretion rate, as expected for the
-shorter wavelength accretion flux contribution. As the inclination
-angle increases the $\alpha$ value generally reduces. Finally, the
-shorter period objects lie closer to the naked BD locus in $\alpha$
-space.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/alpha_zoom.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{This Figure shows the $\alpha$ value
-   \citep{2006AJ....131.1574L} (against an arbitrary
-   model number)  used
-   \citet{2009arXiv0901.2603K}, $\alpha=\frac{dlog(\lambda
-     F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
-   $\mu$m). Crosses show the simulated objects without discs and dots
-   are
-   those with circumstellar disc, the horizontal line is the
-   $\alpha>-$2 cut used to identify disc candidates for solar type
-   stars in \citet{2009arXiv0901.2603K}. Note, that stars of
-   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
-   estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4$\mu$m).
-   \label{alpha_zoom}}
-\end{figure}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/alpha_four.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{alpha_zoom} except each of the \textit{four
-     panels} shows the underlying scatter separated by input
-   variable. The \textit{upper left panel} shows the alpha values for
-   two different accretion rates, with -12 and -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue and red dots
-   respectively. The \textit{upper right panel} differentiates
-   populations with different areal coverages of the accretion stream,
-   where 1 and 10\% are shown as blue and red dots respectively. The
-   \textit{lower left panel} shows scatter caused by rotational period
-   changes, with periods of 5 and 0.5 days shown as blue and red dots
-   respectively. Finally, the \textit{lower right panel}, the systems
-   at different inclinations are shown with 0, 60 and 90$^{\circ}$
-   shown as black, blue and red dots respectively. Note, that stars of
-   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
-   estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4$\mu$m).
-   \label{alpha_four}}
-\end{figure*}
-
-\subsection{Physical causes of scatters and correlations}
-\label{scatter_causes}
-USE THIS BIT FOR THE SEDS SECTION
-**ADD IN TEMPERATURE RANGES FOR DISCUSSION HERE**
-
-The scatters observed in our photometry, caused by varying our input
-parameters, are obviously caused by changes in the simulated
-SEDs. These changes are in turn due to changes in the physical
-structure of the system. In this Section we examine the simulated SEDs
-and resulting temperature and density structure of the discs to
-explain the photometric scatters.
-
-As discussed, Figure \ref{spread_opt_VVI} shows that for the optical CMD
-(\textit{V, V-I}), the scatter in colour appears correlated with areal
-coverage and accretion rate of the accretion stream. Objects with
-higher accretion rates and smaller areal coverages and, therefore,
-higher fluxes or accretion luminosities scatter blueward of the
-isochrone. There is also perhaps evidence of a weak correlation with
-rotation period and colour scatter in Figure
-\ref{spread_opt_VVI}. Finally, the scatter in the magnitude (\textit{V}),
-and to some extent colour (\textit{V-I}), present in the data in
-Figure \ref{spread_opt_VVI} is clearly correlated with inclination. For
-the IR CMD (\textit{J, J-K}), once again, scatter in magnitude appears
-strongly correlated with inclination. There is also a clear
-correlation of scatter in colour with rotation period, but the
-remaining two variables appear to show random scatter only.
-
-To explore the causes of the shifts we must relate the changes in the
-resulting SEDs to the relevant physical parameters. Essentially, the
-summed flux is comprised of four main components, the stellar
-photosphere (luminosity $L_*$), the accretion stream (luminosity
-$L_{\rm acc}$), the disc inner boundary or wall (luminosity $L_{\rm
-  wall}$), and the outer regions of the, highly-flared, circumstellar
-disc (luminosity $L_{\rm disc}$). For a given mass and age, the radius
-and intrinsic stellar photospheric flux are fixed. For our model grid
-the fluxes are produced at effective temperatures of 3000K$<T_{\rm
-  eff}$1600K.
-
-The flux from the accretion stream is dominant at shorter wavelengths,
-within our range, peaking below a wavelength of 1$\mu$m (see Figure
-\ref{acc_dom}). This is as the accretion hotspot can reach much higher
-temperatures than the stellar photosphere, up to 16700K. The accretion
-luminosity is calculated using equation \ref{Lacc} (in Section
-\ref{physics}), and the resulting flux levels are computed using an
-effective temperature (Equation \ref{Tacc}, Section \ref{physics}) to
-generate a blackbody emission curve. As the accretion flux is
-calculated using a blackbody law, the peak wavelength is a function of
-the effective temperature of the accretion spot, $\lambda_{\rm
-  peak}\propto \frac{1}{T_{\rm acc}}$. Therefore, the effects of the
-accretion flux component on the resulting SED, in terms of total flux
-and peak wavelength, are a strong function of the input variables,
-accretion rate and areal coverage. Essentially, high accretion rates
-and low areal coverages lead to an increased influence of accretion
-stream on the final SED. The increased accretion flux creates a blue
-excess, easily dominating the cooler BD photospheres at shorter
-wavelengths. The converse of this is also true i.e. lower accretion
-rates with larger hot spots results in a reduction of the influence of
-the accretion flux on the SED.
-
-The flux from the inner boundary is a function of the temperature of
-the inner wall. This is dependent on its proximity to the central
-object. The initial inner wall radius was set as the magnetic
-co-rotation radius (see Section \ref{physics}). This distance is a
-strong function of rotational period, with $R_{\rm inner}\propto
-\tau^{2/3}$ (see Equation \ref{inner_eq}). During the radiative
-transfer simulations the inclusion of dust sublimation effects will
-result in a shift of the inner wall radius for the hotter wall
-temperatures. The differences in the initial and final inner wall
-radius are discussed in Section \ref{inner_edge_position}. However,
-they do not show significant differences between initial and final
-inner wall radii. Therefore, for our purposes the inner disc radius
-can still be considered proportional to the rotation period. This
-inner boundary will clearly be cooler than the stellar surface, or the
-accretion hot spot, and will therefore contribute flux at longer
-wavelengths. The resulting flux component, for the inner wall,
-dominates at longer wavelengths, peaking at between 2 and 3$\mu$m
-\citep{2001ApJ...560..957D}. This is due to its cooler temperature,
-which is neccesarily less than the dust sublimation ($\approx$1400K).
-
-**CHECK THIS EMISSION FROM IRAC ACTUALLY FROM JUST BEHIND THE INNER
-EDGE-THEREFORE ARGUMENT STILL STANDS BUT MUST ADD IN A PUFFING UP OF
-THE INNER EDGE EFFECT**
-
-Finally, the flux from the outer flared region of the disc is simply a
-function of the temperature of the outer disc. This, in turn, is a
-function of the stellar flux reaching these regions of the disc. This
-is a function of the rotational period. For closer inner boundaries
-more flux is intercepted by the inner boundary and therefore less
-reaches the outer regions, for longer periods the farther inner wall
-radii means more flux reaches the outer disc regions (see Section
-\ref{disc_period_relation}). These regions of the disc will be cooler
-than the inner boundary and, therefore only have a significant flux
-contribution at wavelengths longer than 3$\mu$m.
-
-Therefore, the shape of the resulting SED, for a star-disc system of
-at fixed stellar mass and age, will be dependent on the dominance of
-the hot short wavelength accretion component, the cooler
-mid-wavelength component of the inner boundary, and the even cooler,
-longer wavelength component from the outer regions of the disc.
-Practically, for our model grid, the shape is therefore a function of:
-Accretion rate and coverage ($L_{\rm acc}$) and the rotation period
-($L_{\rm wall}$ \& $L_{\rm disc}$).
-
-The final, and most important variable affecting the shape of the SED
-is inclination. This variable affects the balance of the photospheric
-flux escaping ($L_*$ \& $L_{\rm acc}$) and that observed from the disc
-($L_{\rm wall}$ \& $L_{\rm disc}$). Essentially, the flux for all wavelengths
-will reduce as the inclination increases. However, this reduction,
-with inclination, will reduce toward longer wavelengths. This is as
-the opacity of the disc will reduce with increasing wavelength.
-
-So, to relate these changes to the scatter we observe in the CMDs of
-Figures \ref{spread_opt_VVI} and \ref{spread_ir_JJK}, we have plotted the CMDs
-for a star of $M=$0.04$M_{\odot}$, at an age of 1 Myr, for a range of
-parameters in optical and IR colours in Figure \ref{spread_cmd}.
-Figure \ref{spread_cmd} shows the \textit{V, V-I} (\textit{left
-  panel}) and \textit{J, J-K} (\textit{right panel}) CMDs. For
-\textit{both panels} the naked BD systems, with negligible accretion
-flux (-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 10\% coverage)
-are shown as black crosses. For \textit{both panels} the red coloured
-symbols are those which have the inner boundary component maximised,
-i.e. with the shorter rotation period of 0.5 days, and the blue
-symbols denote systems with the longer period of 5 days, and therefore
-minimised inner boundary flux. The circles represent those systems
-with the accretion flux component maximised, i.e. an accretion rate of
--8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 1\% areal coverage,
-and the triangles show systems with the accretion component minimised,
-i.e. an accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-with 10\% areal coverage. Finally, the open symbols (circles or
-triangles in both red and blue) show systems at an inclination of
-face-on, 0$^{\circ}$, and the filled symbols at edge on, 90$^{\circ}$.
-
-**CHECK AND REWRITE**
-
-Figure \ref{spread_cmd} shows, that increasing the accretion flux
-component moves the star blueward significantly in the optical
-colours, \textit{left panel}, and much less in the IR, \textit{right
-  panel} (compare the circles to triangles of the same colour and
-type, open or filled.). In addition, maximising the inner boundary
-component moves the system redward significantly in both CMDs,
-although to a greater extent in the IR, \textit{left panel} (compare
-different colour symbols of the same type). Finally, the inclination
-as shown in \cite{2004MNRAS.351..607W}, both reduces the magnitude and
-shifts the object in colour (compare open and filled symbols of same
-colour and type). Comparing the \textit{two panels} shows that the
-disc component has a much more significant affect in both CMDs,
-optical and IR, than the accretion component. Interestingly, the
-effect of a disc is still significant for the optical \textit{V, V-I}
-CMD. The accretion component has a much more significant effect in the
-optical \textit{V, V-I} CMD than the IR \textit{J, J-K}, and indeed is
-probably negligible in the latter. The effect of the two variables is
-then essentially additive in CMD space, weighted by their dominance in
-either CMD regime. This means a blue-shifted, accretion dominated
-object in a \textit{V, V-I} CMD will be less blue-shifted if the inner
-disc boundary component is also maximised. Whereas, for the \textit{J,
-  J-K} CMD, the inner boundary has a more significant effect and
-maximising the accretion component will only lessen the red-shifting
-from the maximised disc. It is perhaps surprising that for BDD systems
-both accretion and disc presence, due to the inner boundary, can
-scatter the star in an optical CMD.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/spread_cmd.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{CMDs showing the colours and magnitudes of a BD with
-   $M_*=$0.04$M_{\odot}$. For \textit{both panels} a BD with negligible
-   accretion flux, -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   10\% coverage without a disc is plotted as a black
-   cross. Triangles, in \textit{both panels}, are BDD systems with
-   negligible accretion flux, i.e. -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 10\% coverage. Circles,
-   in \textit{both panels}, show BDD systems with maximised accretion
-   flux, i.e. -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and 1\%
-   coverage. The red symbols then have a maximised inner boundary
-   component with a period of 0.5 days and blue symbols a minimised
-   inner boundary component with a period of 5 days. Finally, for
-   \textit{both panels} inclinations of 0 \& 90$^{\circ}$ are shown
-   as open and filled symbols respectively. The \textit{left panel}
-   shows the $M_V, (V-I)_0$ CMD and \textit{right panel} the $M_J,
-   (J-K)_0$ CMD.
-   \label{spread_cmd}}
-\end{figure}
-\clearpage
-
-The TORUS code identifies and tags photons as they pass through the
-simulation in one of four ways: Stellar direct, stellar scattered and
-thermal direct or thermal scattered, as described in Section
-\ref{seds}. This allows us to plot the component flux distributions of
-the objects, with discs, shown in Figure \ref{spread_cmd} and examine
-their flux components. The convenient components discussed above,
-namely: stellar photosphere ($L_*$), accretion component ($L_{\rm acc}$),
-disc inner wall component ($L_{\rm wall}$) and outer disc component
-($L_{\rm disc}$), will have contributions from differently tagged
-photons. The stellar flux will comprise the accretion and intrinsic
-stellar photospheric components, with the direct flux reaching the
-observer without interaction with the disc. Photons scattering through
-the disc will be dominated by photons from the inner boundary for
-systems with a small inner disc radius. The inner boundary component
-and outer flared disc components will also include the direct and
-scattered thermal photons.
-
-Figures \ref{spread_spec_lowacc} and \ref{spread_spec_highacc} show
-the total and component fluxes for the BDD systems shown in Figure
-\ref{spread_cmd}. For \textit{all panels}, in both Figures, total flux
-is shown as the solid black line, with the stellar and thermal fluxes
-shown as blue and red lines respectively. Also, in both Figures, the
-direct and scattered components of the stellar and thermal flux are
-plotted as solid and dashed lines respectively. In addition for both
-Figures, the \textit{left panels} shows the minimised inner boundary
-component, with a period of 5 days, and the \textit{left panels} the
-maximised inner disc boundary component with a period of 0.5 days. The
-vertical lines show the approximate response limits in wavelength of
-the \textit{VI} and \textit{JK} filters as dashed and solid lines
-respectively. The \textit{lower panels} show systems at an edge-on
-inclination, of 90$^{\circ}$, and the \textit{upper panels} show
-face-on systems with an inclination of 0$^{\circ}$.  Figures
-\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} show the
-minimised and maximised accretion flux component systems respectively,
-i.e. -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 10\% areal
-coverage for Figure \ref{spread_spec_lowacc} and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with 1\% areal coverage for
-Figure \ref{spread_spec_highacc}.
-
-Comparing the \textit{left \& right panels} of Figures
-\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} shows that as
-the period shortens the proportion of flux reprocessed by the disc,
-and inner wall, increases dramatically. This affects the flux and flux
-slopes in both the filter response regimes, however, it is much more
-significant in the IR regime. This effect causes the reddening seen in
-Figure \ref{spread_cmd}, and its increase in magnitude when comparing
-the \textit{left} to the \textit{right panel}, or optical to IR CMD.
-Comparing the \textit{upper \& lower panels} of Figures
-\ref{spread_spec_lowacc} and \ref{spread_spec_highacc} shows the flux
-becoming dominated by the scattered components, which causes the
-reduction in magnitude and slight reddening of the systems as the
-inclination increases. Finally, comparing Figure
-\ref{spread_spec_lowacc} to Figure \ref{spread_spec_highacc} shows
-that as the accretion is maximised there is a significant increase in
-the flux and flux gradient, across the optical filter bandpasses, for
-the longer period. Whereas, there is a less significant change in the
-optical CMD. This is caused by a higher proportion of the stellar
-intrinsic and accretion flux being intercepted by the inner disc
-boundary.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_lowacc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{This Figure shows SEDs for the minimised accretion flux
-   component systems (-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   10\% coverage), from Figure \ref{spread_cmd}, which are shown as
-   triangles. The total flux is shown as a black line, with stellar
-   flux in blue and thermal flux in red, separated into direct (solid
-   lines) and scattered (dashed lines) components. The inner boundary
-   component is maximised on the \textit{left} and minimised on the
-   \textit{right panels}, with periods of 0.5 and 5 days
-   respectively. The vertical lines are the approximate filter
-   response limits for the \textit{VI}, dashed, and \textit{JK},
-   solid, bands. Two inclinations of 0 \& 90$^{\circ}$ are shown as
-   the \textit{upper} and \textit{lower panels}, respectively.
-   \ref{spread_cmd}.
-   \label{spread_spec_lowacc}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_lowacc_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_spec_lowacc} but in log space.
-   \label{spread_spec_lowacc_log}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_highacc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_spec_lowacc} but for a maximised
-   accretion flux component (-8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   1\% coverage), shown as circles in Figure \ref{spread_cmd}.
-   \label{spread_spec_highacc}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_spec_highacc_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_spec_highacc} but in log space.
-   \label{spread_spec_highacc_log}}
-\end{figure*}
-
-\subsubsection{Accretion Dominance: $L_{\rm acc}$}
-\label{accn_dominance}
-
-Figure \ref{acc_dom} shows the affect of the increasing accretion
-blackbody flux (for increasing accretion rates) for a BD star,
-$M=$0.04$M_{\odot}$, at 1 Myr. The panels in this figure also show the
-flux from a naked system, with no treatment of the disc. This enables
-us to view the effect of increasing accretion rate on the photospheric
-flux in isolation. The accretion rates included in all panels are -6,
--7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black
-lines respectively). The \textit{lower panels} show the systems with a
-rotation period of 0.5 days and \textit{upper panels} for those with a
-rotation period of 5 days. Given our assumption that accretion occurs
-from the co-rotation radius, decreasing the rotational period moves
-this accretion radius closer to the star. As the accretion radius
-moves closer to the star the potential energy released by the accreted
-material is reduced. This effect can be seen when comparing the
-\textit{upper} and \textit{lower panels}, although the effect is
-marginal for all but the highest accretion rates. The \textit{left
-  panels} show accretion streams with an areal coverage of 1\% and the
-\textit{left panels} 10\%. As the areal coverage reduces the effective
-temperature of the accretion hot spot increases, resulting in an
-increase in accretion flux, and resulting shift to bluer wavelengths
-of the peak flux. This can be seen clearly by comparing the
-\textit{left} and \textit{right panels} of Figure
-\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
-shown is Figure \ref{acc_dom} is an insight into the accretion rate at
-which the accretion blackbody flux dominates over the photospheric
-flux. Figure \ref{acc_dom} shows that as the accretion rate raises
-above -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for systems with 1\%
-areal coverage, the accretion flux dominates the emergent SED at both
-periods. For the larger coverage the accretion flux begins to dominate
-between -7 to -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. Therefore
-for reasonable coverages (1-10\%) and rotational periods (0.5-5 days)
-the photospheric flux is effectively swamped by accretion flux for
-accretion rates log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-7$ , and for
-the most conservative case (1\% coverage with 5 day period) at
-accretion rates much lower than this
-(log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})>-$8). This suggests that
-accreting BD systems with accretion rates as low as -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ could be difficult to identify
-from SEDs as BD stars, and may well be classified as higher mass
-stars.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{This figure shows the photospheric flux against $\lambda$
-   ($\mu$m) of a Brown Dwarf with $M=$0.04$M_{\odot}$, at 1 Myr. No
-   disc is included, but blackbody fluxes from an accretion stream at
-   the rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-   are shown as blue, red and black lines respectively. The
-   \textit{lower panels} show accretion for a star rotating at 0.5
-   days, with the \textit{upper panels} showing that of 5 days. The
-   \textit{left panels} systems with an areal coverage of 1\% and the
-   \textit{right panels} has 10\%. CONSTRUCTED USING GRAPHPS**
-   \label{acc_dom}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{acc_dom} but in log space.
-   \label{acc_dom_log}}
-\end{figure*}
-
-Therefore, one can see that for higher accretion spot temperatures,
-flux shortward of the photospheric flux is markedly increased. This
-results, in general, in a brighter and bluer magnitude and colour for
-the combined system.
-
-\subsubsection{Disc effects: Flaring, $L_{\rm disc}$}
-\label{flaring}
-
-**SOME IMAGES TO PROVE POINT**
-**ADD MIPS DISCUSSION HERE AND SCALE HEIGHT STUFF**
-
-Scatter in optical CMDs is dominated by disc inclination (see Figures
-\ref{spread_opt_VVI}, \ref{spread_RI} and \ref{spread_VB}), and, even at
-longer wavelengths, scatter in IR CMDs is still correlated with
-inclination (see Figure \ref{spread_ir_JJK}). \cite{2004MNRAS.351..607W}
-have already shown that increased disc inclination lead to significant
-changes in the spectroscopic, and photometric properties of BDD
-systems. The scatter in optical and IR CMDs (in Section
-\ref{derive_primary}), for our model grid, appears strongly correlated
-with system inclination. This is a similar effect as found in
-\cite{2004MNRAS.351..607W}, where increases in the inclination angle
-quickly lead a significant proportion of the stellar flux being
-intercepted, and reprocessed, by the highly flared disc.
-
-Figure \ref{disc_eg} shows examples of our derived spectra for a BD of
-$M=$0.04$M_{\odot}$ (the middle of our mass range), at 1 Myr, with a
-rotation period of 0.5 days, and an accretion stream covering 1\% of
-the stellar surface accreting at a negligible rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{upper left panel}
-shows the SED for the naked BD system with the remaining panels
-showing the SEDs from the three modeled inclinations, after a TORUS
-simulation of a disc with $M_{disc}=$0.01$M_*$. The \textit{lower left,
-  upper right and lower right panels} show inclinations of 0, 60
-and 90$^{\circ}$ respectively. This figure plots, for the disc
-systems, the TORUS tagged component fluxes from the star (solid lines)
-and the disc or thermal flux (dashed lines), for both direct flux
-(black) and scattered flux (red). As the inclination of the system
-increases, the stellar direct flux can be seen to decrease, and the
-thermal and scattered components increase. This is simply caused by
-occultation of the star by the disc. The condition of vertical
-hydrostatic equilibrium applied during the TORUS simulation results in
-the disc flaring (see Section \ref{derive_primary}). This flaring is
-more pronounced for BD when compared to higher mass stars meaning a
-higher fraction of the stellar flux is intercepted by the disc at
-earlier inclinations. \cite{2004MNRAS.351..607W} have previously
-modeled this effect for a range of disc masses and found that this
-alone can shift the SED, and therefore colours and magnitudes, of
-inclined BDD systems to those indicative of higher mass CTTS.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_eg.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure of the SEDs of a BDD of $M=$0.04$M_{\odot}$, at 1 Myr,
-   with a disc mass of $M_{\rm disc}=$0.01$M_{\rm star}$. The BD is rotating
-   with a period of 0.5 days and is accreting through a stream, with
-   an areal coverage of 1\%, at a rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{upper left
-     panel} shows the photospheric spectrum of the naked star (naked stars have
-   spherically symmetric flux distributions, therefore the SED is not
-   a function of inclination), the total flux is shown as a bold
-   line. The \textit{lower left, upper right and lower right panels}
-   show the SEDs of the BDD systems at inclinations of 0,
-   60 and 90$^{\circ}$. For the BDD SEDs, the solid lines
-   are stellar flux and dashed are the thermal disc flux, with the
-   black denoting direct flux and red for scattered flux, i.e. black
-   solid line is direct stellar flux.
-   \label{disc_eg}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_eg_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{disc_eg} but in log space.
-   \label{disc_eg_log}}
-\end{figure*}
-
-The resulting density structure of the highly flared disc, for the
-system used to construct Figure \ref{disc_eg}, is shown in Figure
-\ref{flare_eg}. Figure \ref{flare_eg} shows that for a typical BDD
-system the resulting disc is highly flared and therefore, the opening
-angle for stellar radiation is much smaller. As discussed the flaring
-for BDD systems was found to be larger than CTTS systems by
-\cite{2004MNRAS.351..607W}. \cite{2004MNRAS.351..607W}, state that the
-degree of disc flaring depends on the disc temperature structure and
-the mass of the central star, with the disc scaleheight $h\propto
-\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{1973A&A....24..337S}. Recently,
-\cite{2009arXiv0901.4445E} suggest the inverse relation of flaring
-with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
-evidence from \cite{2006ApJ...644..364A}, where SEDs for 17 systems in
-the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat
-disc models. In general, \cite{2006ApJ...644..364A} find that lower
-mass objects achieve better fits with the flat disc models and higher
-mass objects with the flared discs.
-
-The results of \cite{2006ApJ...644..364A} show that above a mass of
-50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
-discs. Whilst at masses below 50$M_{\rm Jup}$ only one object is better
-fit by the flared disc model, with the remaining objects (10/17)
-better fit with flat models. Whether, this result is statistically
-significant enough to assert a $h\propto M_*$ is doubtful as the
-fitting process contains, presumably two fixed scaleheight
-distributions. Therefore, for our study we continue to assume that our
-flared BDD systems will have larger characteristic scaleheights than
-typical CTTS systems.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/28_rho.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{A Figure of the density for the most flared
-   disc. $M_*=$0.01$M_{\odot}$, $\tau=$5 days, $\dot{M}=$-6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, areal coverage of 1\% at 1
-   Myr **RUN NUMBER028**.
-   \label{flare_eg}}
-   \end{figure}
-
-\subsubsection{Disc effects: Inner wall, $L_{\rm wall}$}
-\label{inner_wall}
-
-Therefore, as the scattering in optical CMDs is dominated by system
-inclination, due to disc flaring, what dominates scattering in the IR?
-Clearly, system inclination still has a significant correlation with
-the scatter CMD position. However, as shown in Section
-\ref{derive_primary} IR CMD scatter appears strongly correlated with
-rotational period. A similar correlation between scatter and rotation
-period is evident for IR and IRAC (and perhaps MIPS) CoCoDs (although
-the trend is reversed), as shown in Section \ref{derive_frac}. The
-cause of this scatter is the relative flux contribution of the inner
-disc boundary, as discussed in Section \ref{scatter_causes}. It is
-also clear in Section \ref{derive_primary} that the longer wavelength
-photometric colours are better disc discriminators. Furthermore,
-interestingly, the $\alpha$ value, in our case the slope of the SED
-between 3.6 and 8.0$\mu$m \citep[chosen to
-match][]{2009arXiv0901.4120D}, is a very effective disc disriminator.
-
-The position of a given BDD system, in an IR CoCoD or CMD, is
-dominated by rotation period, and it is clear that this is due to the
-radial position of the inner wall (See discussion in Section
-\ref{scatter_causes}. As the rotation period decreases the inner disc
-co-rotation radius decreases, meaning a closer, hotter, inner disc
-wall. However, we have also included a treatment of dust sublimation
-which, during the radiative transfer modeling, will change the radial
-position for the higher temperature inner walls \citep[where
-$T_{\rm wall}$ exceeds $\approx$1400K][]{1994ApJ...421..615P}.
-
-\subsubsection{Disc structure and the inner edge}
-\label{inner_edge_position}
-**SHOULD BE PRINTED FROM TORUS**pooooo
-\textbf{Initial inner wall radius}
-
-Given the strong dependence of IR flux on the inner wall temperature,
-and therefore radial position, it is important to examine the final
-structure of the inner wall after the radiative transfer simulation.
-
-Table \ref{inner_edge} list the initial inner edge radius (from the
-central star), set at the co-rotation radius, in stellar radii for each
-mass increment. It is clear that the inner edge position is a strong
-function of rotation period and a much weaker function of stellar
-mass. This is obvious from our calculation of the co-rotation radius
-for which we use equation \ref{inner_eq}. Equation \ref{inner_eq}
-clearly shows the weak dependence on stellar mass ($R_{\rm inner}\propto
-M_*$) and strong dependence on rotation period ($R_{\rm inner}\propto \tau
-^2$). Table \ref{inner_edge_au} shows the same data as Table
-\ref{inner_edge} but converted using the stellar radius into AU, which
-reveals a magnetic truncation radius of between 0.0026$-$0.026 AU for
-1 Myr BDD systems.
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius ($R_*$)}\\
-0.01&2.18&10.16&3.52&16.36\\
-0.02&2.42&11.24&3.33&15.47\\
-0.04&1.90&8.86&3.26&15.15\\
-0.06&1.57&7.32&3.13&14.53\\
-0.08&1.37&6.39&2.96&13.74\\
-\end{tabular}
-\caption{Table showing the initial inner edge radius (in $R_*$) for all models.
-  \label{inner_edge}}
-\end{table}
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius (AU)}\\
-0.01&0.00264&0.0123&0.00265&0.0123\\
-0.02&0.00333&0.0155&0.00375&0.0174\\
-0.04&0.00403&0.0188&0.00411&0.0191\\
-0.06&0.00479&0.0195&0.00395&0.0183\\
-0.08&0.00527&0.0246&0.00501&0.0233\\
-\end{tabular}
-\caption{Table showing the initial inner edge radius (in $R_*$) for all models.
- \label{inner_edge_au}}
-\end{table}
-
-\textbf{Dust sublimation radius}
-
-During the simulations of radiative transfer, implementation of dust
-sublimation, may result in changes in inner radius. For systems where
-the temperature of dust at the inner disc boundary exceeds
-$\approx$1400K \citep{1994ApJ...421..615P}, the inner disc will be
-destroyed and the inner radius increased. Table \ref{inner_edge_dust}
-shows the resulting radii for our model grid in stellar radii with the
-corresponding values in AU presented in Table
-\ref{inner_edge_dust_au}.**THIS TABLE MUST BE CHANGED TO INCLUDE
-DIFFERENT FLUXES**
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius ($R_*$)}\\
-0.01&&&&\\
-0.02&&&&\\
-0.04&&&&\\
-0.06&&&&\\
-0.08&&&&\\
-\end{tabular}
-\caption{Table showing the final inner edge radius (in $R_*$) for all models.
- \label{inner_edge_dust}}
-\end{table}
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|l|}
-Age (Myr)&\multicolumn{2}{|c|}{1}&\multicolumn{2}{|c|}{10}\\
-\hline
-Period (days)&0.5&5&0.5&5\\
-\hline
-Mass ($M_{\odot}$)&\multicolumn{4}{|c|}{Inner boundary radius (AU)}\\
-0.01&&&&\\
-0.02&&&&\\
-0.04&&&&\\
-0.06&&&&\\
-0.08&&&&\\
-\end{tabular}
-\caption{Table showing the final inner edge radius (in $R_*$) for all models.
- \label{inner_edge_dust_au}}
-\end{table}
-
-\textbf{Compare $R_{\rm co}$ to $R_{\rm dust}$}
-
-**NEEDS TO BE DONE AFTER NEW DATA**
-
-Comparing Table \ref{inner_edge_dust_au} to Table \ref{inner_edge_au}
-shows that the inner disc radius is changed little from the initial
-co-rotation radius (QUOTE MAX CHANGE**) due to dust sublimation
-effects. The resulting inner radii are still, broadly, proportional to
-the rotation period. Therefore, for subsequent analysis, we assume an
-inner radius to rotation period relationship.
-
-Our final inner radii range from ** to ** AU. **COMPARE TO
-OTHER RESULTS?**
-
-\textbf{Dust sublimation regions}
-
-**AGAIN NEEDS TO BE DONE AFTER NEW DATA**
-
-In some cases however the inner disc radius has been changed by the
-implementation of dust sublimation. For these systems the resulting
-shape of the inner disc boundary has also changed. Evidence that real
-inner disc boundaries (for CTTS) are not vertical walls comes from a
-lack of dependence of the derived IR excess on system inclination
-\citep{2007ApJ...661..374T}. As discussed in Section \ref{dust_edge}
-the disc inner hole can be created by several mechanisms, however, for
-this study we have only included a treatment of magnetic truncation
-(initially) and subsequent dust sublimation. The effects of dust
-sublimation have been shown to produce curved inner walls due to the
-temperature and density dependence of the dust sublimation temperature
-\citep{2005A&A...438..899I}. The curved boundary in this case is
-concave, as density increases towards the midplane of the disc, the
-dust sublimation temperature increases, meaning the destruction radius
-moves closer to the star. A curved inner boundary is also found to
-result from dust sublimation in \cite{2007ApJ...661..374T}. In
-\cite{2007ApJ...661..374T} two populations of dust grains where
-included with different scaleheight distributions. This is essentially
-a simple model of grain growth and subsequent midplane
-settling. \cite{2007ApJ...661..374T}, found a convex inner disc
-boundary, this is due to the larger grains cooling more
-efficiently. These larger grains dominate the dust towards smaller
-vertical distances from the midplane, and therefore the increased
-cooling means that the dust sublimation temperature is reached at
-closer radii.
-
-For our dust distribution and dust sublimation implementation we
-produce a curved inner boundary, as can be seen in
-Figure \ref{curve_inner}. This is due to the density dependent dust
-sublimation temperature (as discussed in Section \ref{dust_edge}).
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/238_tau.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{A Figure of the opacity (scaled $1<\tau <0$) for the most
-   extreme case of a dust sublimated inner
-   boundary. $M_*=$0.08$M_{\odot}$, $\tau=$0.5 days, $\dot{M}=$-6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, areal coverage of 1\% at 1
-   Myr **RUN NUMBER238**.
-   \label{curve_inner}}
-\end{figure}
-
-**CONCLUDE**
-
-\subsubsection{Disc effects: Inner wall to Outer edge balance,
-  $L_{\rm wall}$ to $L_{\rm disc}$}
-\label{disc_period_relation}
-
-\textbf{Why do inner disc radius changes cause photometric scatter?}
-
-**ADD SOME IMAGES**
-**PERHAPS ADD A FIGURE HER J-K, AND IRAC COLOUR VERSUS FINAL RADIUS**
-
-Physically, as the inner disc radius changes the flux intercepted by
-the inner wall is changed. At first glance it may appear more
-instructive to plot the \textit{bottom left panel} as a function of
-inner disc radius, to strengthen the correlation and remove the
-scatter within the Figure. However, intrinsic scatter will also be
-included due to inclination and accretion rate, the latter perhaps
-being less intuitive. Even though accretion flux is generally blueward
-of these passbands, interception and subsequent reprocessing of this
-additional flux for higher accretion rates increase scatter in a
-CoCoDs of this sort. Therefore, plotting the simulated photometry as a
-function of inner disc radius does not reduce the
-scatter. Furthermore, separating the populations using the rotational
-period is perhaps more useful for observational studies as this is
-often the most ubiquitous and precise data available. It is important
-at this stage to re-iterate that magnetic truncation and dust
-sublimation as we have assumed occur, is not the only method of
-producing an inner hole, for instance planet formation or
-photoevaporation can create significant inner holes, which are not
-necessarily correlated, in size, with rotation period.
-
-\textbf{SED change caused by inner radius}
-
-Figures \ref{rot_effect}, \ref{rot_effect_log}, \ref{rot_comp} and
-\ref{rot_comp_-7} show the effects of the changes in inner boundary
-radius due to rotational period changes on a BD, $M_*=$0.04$M_{\odot}$,
-at 1 Myr. For all these figures the \textit{left panel} shows the SEDs
-for a period of 0.5 days and the \textit{right panel} shows the SED
-for a period of 5 days. We have chosen to plot the SEDs as a function
-of rotational period for two reason. Firstly, rotational period will
-be the most easily, and precisely, observed variable. Secondly, the
-inner disc radius varies most strongly as a function of the rotational
-period (see Equation \ref{inner_eq}).The final inner radii for the
-systems shown in the \textit{left} and \textit{right panels} are **
-and ** AU, respectively (see Table \ref{inner_edge_dust_au}).
-
-Figures \ref{rot_effect} and \ref{rot_effect_log} show the total flux
-(in normal and log space respectively) for both canonical accretion
-rates (-8 \& -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, bold and
-dashed lines respectively). The SEDs are for systems with the smallest
-areal coverage (1\%) and therefore highest accretion flux, for each of
-the three inclinations (0, 60 and 90$^{\circ}$, black, red and
-blue respectively).
-
-Figures \ref{rot_comp} and \ref{rot_comp_-7} show the component flux
-for two inclinations, $0$ and $60^{\circ}$, \textit{upper} and
-\textit{lower panels} respectively. The component flux is separated
-into total (black lines), stellar (blue lines) and thermal or disc
-(red lines) flux. The stellar and thermal flux is then separated into
-direct (bold lines) or scattered (dashed lines) flux. The vertical
-bold lines on these figures show the approximate filter ranges for the
-IRAC channels ([3.6], [4.5], [5.8] \& [8.0]), with the vertical dashed
-lines showing the limits of the JHK filters of the CIT system. Figure
-\ref{rot_comp} shows the SEDs for a system with an accretion rate of
--8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and Figure
-\ref{rot_comp_-7} an accretion rate of -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
-
-Figures \ref{rot_effect} and \ref{rot_effect_log} show that for
-systems with a typical accretion rate and shorter rotational periods,
-as the inclination increases the flux and slope of the SED decreases
-dramatically, for wavelengths shorter than $\approx$2$\mu$m. In this
-case the inner boundary is close to the central star. Conversely, the
-flux, and slope of the SED, at wavelengths longer than
-$\approx$2$\mu$m decreases less swiftly with increasing inclination.
-Effectively shorter period systems show a large change in flux and
-flux ratios in the $<$2$\mu$m range and a more constant flux or flux
-ratio in the $>$2$\mu$m range. This trend is clearly reversed for
-longer period objects. The objects, where the disc inner edge is
-farther from the star, show a large change in flux and flux ratio, as
-a function of inclination, for wavelengths $>$2$\mu$m and a smaller
-change for wavelengths $<$2$\mu$m. In addition, the total SED is
-dominated by the photosphere at shorter wavelengths.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/rot_effect.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing flux against wavelength for a
-   $M_*=$0.04$M_{\odot}$ BD at 1 Myr, for two accretion rates -7
-   (dashed line) and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (bold
-   line) for the three modeled inclinations, 0 (black), 60 (red) and
-   90$^{\circ}$ (blue). The \textit{left panel} shows the SEDs for the
-   shorter rotation period system, with a closer disc inner
-   boundary. The \textit{right panel} shows the longer period system
-   with farther disc inner boundary.**USE GRAPHPS**
-   \label{rot_effect}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/rot_effect_log.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{A Figure \ref{rot_effect} but in log space.
-   \label{rot_effect_log}}
-\end{figure}
-
-The wavelength dependent variations in flux, and SED slope, with
-inclination are particularly important when considering photometric or
-broadband magnitudes and colours. Figures \ref{rot_comp} and
-\ref{rot_comp_-7} show that the variations evident in Figures
-\ref{rot_effect} and \ref{rot_effect_log} have serious implications
-over the filter responses of the CIT \textit{JHK} and IRAC
-systems. Essentially, Figures \ref{rot_comp} and \ref{rot_comp_-7}
-show that for increasing inclinations discs have a much more apparent
-effect on the SED over the IRAC range for longer period systems, and
-in the CIT \textit{JHK} range for shorter period systems. Thereby
-explaining the opposite correlations in disc scatter and rotation
-period, found for IR and IRAC colours in Section \ref{derive_frac}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{This Figure shows flux against wavelength for a
-   $M_*=$0.04$M_{\odot}$ BD at 1 Myr, with a disc ($M_{\rm disc}=$0.01$M_*$)
-   and associated accretion rate of -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ over a hot spot coverage of
-   1\%. The \textit{left panels} show systems with a stellar rotation
-   period of 0.5 days and the \textit{right panel} those with a
-   stellar rotation period of 5 days. The \textit{upper panels} show
-   systems observed at an inclination of $0^{\circ}$ and the
-   \textit{lower panel} those observed at an inclination of
-   $60^{\circ}$. For \textit{all panels} the total SED is shown
-   (solid, black line), alongside the components flux from the star
-   (blue) and thermal or disc (red) flux. These components are also
-   separated into direct flux (solid lines) or scattered flux (dashed
-   lines) from the star or disc. The extents of the filter responses
-   for the IRAC (including channels [3.6], [4.5], [5.8] \&
-   [8.0]) (solid vertical line) and the CIT (\textit{JHK})
-   (dashed vertical lines) bands are shown. 
-   \label{rot_comp}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{rot_comp} but in log space.
-   \label{rot_comp_log}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp_-7.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As above but for higher canonical accretion rate -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.
-   \label{rot_comp_-7}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_comp_-7_log.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{rot_comp_-7} but in log space.
-   \label{rot_comp_-7_log}}
-\end{figure*}
-
-**NEED TO GET VALUES ETC FOR THIS SECTION AFTER NEW DATA**
-
-As the temperature of the surface of the disc generally decrease
-towards larger radii the longer the wavelength of the flux the further
-from the central object its origin will be.  Effectively, more flux is
-being intercepted by the disc inner wall for the shorter period
-systems and consequently less flux is impinging on the outer flared
-surface of this disc, creating larger changes as a function of
-inclination for shorter wavelengths. In the case of the longer periods
-more flux is escaping to the outer flared edge of the disc and greater
-change is seen as a function of inclination angle at longer
-wavelengths. Figures \ref{far_rho}, \ref{far_rho_bw}, \ref{close_rho},
-and \ref{close_rho_bw}, show the density structure for the inner
-regions of the disc ($R<**AU$) as a function of radius and scaleheight
-(10$^{10}$ cms). The inner edge location can be seen to move further
-out when moving from short period systems to long period systems, in
-Figures \ref{far_rho}/\ref{far_rho_bw} and
-\ref{close_rho}/\ref{close_rho_bw}, from ** to **AU in fact. Dust
-sublimation effects have shifted the shorter period inner wall to a
-slightly larger radius (see Section \ref{inner_edge_position}), but
-this is ,however, still closer than longer period counterpart. The
-final temperature distribution in the disc inner regions ($R<**AU$)
-can be seen in Figures \ref{far_temp}, \ref{far_temp_bw},
-\ref{close_temp} and \ref{close_temp_bw}. As can be seen by comparing
-Figure \ref{far_temp}/\ref{far_temp_bw} to Figure
-\ref{close_temp}/\ref{close_temp_bw}, the inner wall reaches
-significantly higher temperatures for the shorter period systems. For
-the closer systems, the curved inner edge is due to some of the disc
-regions exceeding the dust sublimation temperature, the remaining wall
-reaches temperatures of **K. Whereas, for the longer period object the
-inner wall reaches a temperature of **K. This produces the correlation
-of IR excess caused by the inner wall with rotation period seen for IR
-CoCoDs in Section \ref{derive_frac}. In addition, comparing the
-temperature structure at a farther disc radius, indicative of fluxes
-within the IRAC passbands, one finds that the disc temperature is
-larger for the longer period systems, $**$ compared to $**$K at $**$
-AU. This causes the resulting correlation, where larger IRAC excesses
-are found for longer period BDD systems.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_rho0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{CHANGE THESE AXES IN 10$^{10}$ cms*****
-   \label{far_rho}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_rho_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{far_rho_bw}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_rho0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_rho}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_rho_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_rho_bw}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_temp0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{far_temp}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/far_temp_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{far_temp_bw}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_temp0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_temp}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/close_temp_bw0000.ps"
-   hoffset=30 voffset=0 hscale=30 vscale=25 angle=0}
- \caption{
-   \label{close_temp_bw}}
-\end{figure}
-
-\textbf{Short conclusion, alpha}
-
-As can be seen the effects of a circumstellar disc on the observed SED
-are most constant for longer wavelengths. Wavelengths generally longer
-than 3$\mu$m are little effected by inclination, accretion rate,
-stellar mass etc. This explains, result that BDD systems are well
-selected by IRAC photometry and the $\alpha$ value. Essentially, as
-the wavelength limits used to construct Figure \ref{alpha_zoom} are
-3.6 and 8.0$\mu$m, it follows that the separation between disc-less
-and BDD systems should be at least similar in clarity to the IRAC
-CoCoDs.
-
-\section{Conclusions}
-\label{conclusions}
-
-**THIS CLEARLY NEEDS REWRITING AFTER THE NEW DATA ARE ANALYSED**
-
-We have constructed a model grid of SEDs, and subsequently photometric
-magnitudes and colours, for actively accreting BDs with or without an
-associated accretion disc. We have modeled the photospheric flux from
-these BDs by adopting (and interpolating) the interior `DUSTY00'
-models of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
-atmospheric models of \cite{2000ApJ...542..464C}. We have then assumed
-that accretion occurs from an inner edge of a magnetically truncated
-accretion disc (truncated at the co-rotation radius). The accretion
-flux is calculated using a simple blackbody emission, given the
-derivation of a characteristic spot effective temperature. SEDs were
-then produced for both naked BDs and BDD systems. For the BDD systems
-we have modeled the disc using the TORUS radiative transfer code using
-the Lucy radiative transfer algorithm and incorporating dust
-sublimation and including including a treatment of vertical
-hydrostatic equilibrium (see Section \ref{model} for a discussion of
-the code). To produce a `grid' of simulated systems we have varied
-several input parameters namely: stellar mass, stellar age, stellar
-rotation rate, accretion rate, the areal coverage of the accretion
-stream and the system inclination (the disc mass was fixed). The
-ranges of these variables were selected to represent and bound typical
-pre-MS BD systems, justification is provided using evidence from
-observational studies in Section \ref{par_space} and a final list of
-the values of these variables can be found in Table
-\ref{par_space_table}.
-
-Accepting our assumptions, parameter ranges and radiative transfer
-code our resulting simulated dataset has allowed us to qualitatively
-explore the effects of \emph{active} (current not past accretion)
-accretion, and disc presence, on both the SEDs, and photometric
-colours and magnitudes of these systems. This analysis (described in
-Section \ref{results}) has important implications in two main areas.
-
-\textbf{Effect of accretion and disc on derived parameters:}
-
-Firstly, as disc presence and active accretion change the
-characteristics of BD stars, both in terms of its spectrum and
-photometric magnitudes, they also, subsequently, imply changes in any
-derived parameters from these primary quantities.
-
-\textit{Age.}
-
-As discussed in Section \ref{results}, the SEDs of BD systems with
-typical accretion rates and associated discs, are changed significantly
-from the assumed underlying photospheric model flux, and therefore
-become difficult to classify. We have shown that derivation of an
-\emph{isochronal} (or photometric) age from our simulated photometry
-of a coeval BD sample, with typical accretion rates and associated
-circumstellar discs, would be inaccurate and exceedingly difficult. As
-discussed in Section \ref{results} this does not include any effects
-due to past accretion on the evolution of the central star, which acts
-to accelerate the gravitational contraction and make the star appear
-older \citep{1999MNRAS.310..360T,1999A&A...342..480S}, further
-scattering the apparent age of a coeval population.
-
-\textit{Mass, therefore IMF.}
-
-Concordantly, \emph{isochronal} derivations of mass and therefore
-IMFs, for our simulated photometry, of a coeval population of
-accreting BDs with associated discs, would be inaccurate and
-problematic. Again caused by the changes in the SEDs as a result of
-the accretion flux and increased occultation by the larger degree of
-flaring seen in BD discs \citep[for the latter, as found
-by][]{2004MNRAS.351..607W}
-
-\textit{Disc fraction-Spitzer best.}
-
-We have also qualitatively explored the effects of accretion and disc
-presence in our simulated dataset on disc fraction estimates.As is
-currently well known, longer wavelength bandpasses are much more
-reliable and suitable for disc identification. As shown in Section
-\ref{results} the naked and BDD disc loci were much more clearly
-separated in the CoCoD constructed using \textit{Spitzer} IRAC
-magnitudes than the shorter wavelength CIT \textit{JHK} passbands. In
-addition, we that the slope of the SED from 3.6 to 8.0$\mu$m, or
-$\alpha$ value, is an effective disc indicator. We have also
-tentatively shown that current observational cuts, when applied to our
-simulated photometry (with its associated photometric system), results
-in the reliable detection of disc candidates, for IRAC colours and
-$\alpha$ values, and therefore a robust lower limit disc fraction.
-
-\textbf{Effect of accretion and disc presence on emergent theories or
-  secondary parameters.}
-
-Secondly, the results of our simulated dataset have implications for
-secondary derived correlations and physical theories, which utilise
-the primary parameters discussed. It is clear that changes in derived
-ages and masses of a BD sample, due to typical accretion and disc
-presence, has serious implications in a range areas. Inaccuracies in
-age derivations for pre-MS populations are well known, especially for
-the BD mass regime. However, the combined effects of accretion and
-disc presence on BD SEDs, and therefore age and mass derivation, have
-not been previously explored. Therefore, some of the uncovered biases
-and problems in this paper may bring new light to a few areas of BD
-evolution.
-
-\textbf{`Imperfect' disc locking perhaps due to biases.}
-
-\textit{Disc timescales: Rotation rates affect disc detection as function of
-  wavelength.}
-
-Firstly, we have found a wavelength dependant bias of naked to BD disc
-loci separation within CoCoDs. As we have shown in Section
-\ref{results}, for shorter wavelength data (\textit{JHK}), objects
-with a longer period lie closer to the naked BD locus, with shorter
-period objects further removed. This bias is reversed for IRAC data,
-where shorter period objects lie closer to the naked locus (although
-still well separated) and longer period objects farther away, in
-colour-colour space. Whilst, for the longer wavelength
-\textit{Spitzer} data the clearer separation between the naked and BDD
-disc loci means that this bias may well be minimised (especially in
-regions without significant variable extinction), for shorter
-wavelength data these populations (naked and BDD disc) overlap. As
-disc excess cuts are usually placed empirically based on perceived
-paucity's in stellar density, within colour-colour space, this overlap
-and associated bias for \textit{JHK} data could lead to a significant
-bias in any sample of BD stars with an inferred discs. This wavelength
-dependant bias is essentially due to the change in inner radius of the
-circumstellar disc, as the wavelength of emitted flux is dependant on
-temperature and therefore radial position within the disc plane. For
-shorter periods the disc is truncated closer to the central star and
-the disc inner boundary intercepts more flux at all inclinations
-leading to a hotter inner wall and less incident flux on the outer
-flared edges of the disc. This means that for \textit{JHK} bandpasses,
-which are sensitive to flux from the inner boundary, shorter period
-objects appear more different to naked objects than longer, and
-therefore cooler inner boundary systems.
-
-The effect of this bias has not previously been accounted for in disc
-fraction, and therefore disc timescale derivation studies. Our model
-does not include angular momentum loss only changes in the disc inner
-radius through a disc locking mechanism (and subsequent dust
-sublimation). If disc-locking to a central star is true and slower
-rotators are therefore more likely to have associated discs, any
-correlation between disc presence and rotation rates will be weakened
-for \textit{JHK} data and strengthened for \textit{Spitzer} IRAC data
-due to the biases we observe, for BDs. These biases may well aid
-understanding of early claims for a weaker or `imperfect' disc locking
-mechanism for lower mass stars. The use of \textit{JHK} magnitudes
-would lead to a less clear correlation between slow rotators and disc
-presence for a BD sample.
-
-These biases may also apply to higher mass objects, as would be
-expected albeit at a weaker level due to the less significant flaring
-seen in the circumstellar disc of TTS. This, in turn, may explain
-early difficulties in finding any correlation between rotation rate
-and disc presence \citep[amongst other issues such as non-coevality,
-see][for discussion]{2007prpl.conf..297H}. Once data at longer
-wavelengths was used this correlation was found
-\citep{2007ApJ...671..605C}, which may have been enhanced by the
-revealed bias. It is important to note however, that this bias is not
-strong enough (given the clear separation of our simulated naked and
-BDD disc systems in IRAC colour-colour space) to cast any
-doubt over this result.  Finally, as we have stated inner holes in
-circumstellar disc may well be created by other period-independent
-mechanisms such as clearing from gas accretion onto a planet or due to
-photoevaporation from UV flux, the latter of which would be increased
-at high accretion rates, which we have not included.
-
-\textbf{Accretion rate to mass relationship in doubt for BD regime.}
-
-\textit{Mass to accretion rate relationship-high accretors of low mass
-  missed-literature high mass low accretors missed.}
-
-The second area which this study impacts on, and perhaps most
-significantly, is the recent evidence for a stellar mass to accretion
-rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
-\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}.
-This relationship has been extended into the BD mass regime in
-\cite{2006A&A...452..245N}. However, arguments based on selection and
-detection thresholds have already cast this relation into doubt
-\citep{2006MNRAS.370L..10C}. As we have shown in Section \ref{results}
-a relationship of this kind is self-reinforcing as lower mass objects
-with higher accretion rates have little chance of being correctly
-identified as such due to both the accretion flux and flared
-associated disc. Essentially, at present it is unclear how many BD
-stars are not included in this relationship due to misidentification.
-As explained in \cite{2004MNRAS.351..607W}, BD systems with a disc,
-without including accretion effects, can have the characteristics of
-higher mass CTTS stars, due to increased disc flaring from a reduced
-surface gravity in the disc. The effects of accretion at typical or
-larger rates further exacerbate the situation both spectroscopically,
-as the photospheric flux essentially becomes swamped or completely
-veiled, and photometrically as the resulting colours and magnitudes
-are significantly shifted. Therefore, for our simulated dataset a
-relationship of this sort may well be derived, if typical methods are
-used to identify BD objects with discs and derive masses, ages and
-accretion rates, even though it is not present.
-
-\textbf{Link to deriving accretion rates-paper II}.
-
-This work has argued qualitatively, largely using positions within
-CMDs or CoCoDs, highlighting problems with the proposed stellar mass
-to accretion rate relationship. A further quantitative examination of
-methods used to derive accretion rates and their results when applied
-to our simulated dataset is certainly required, ***and this will be
-the subject of a future publication***, to confirm our conjectures.
-
-\textbf{SUMMARY}
-
-**WRITE AT THE VERY END**
-
-In summary, our simulated dataset shows that for typical parameter
-ranges for BD stars and BDD systems, disc presence and accretion flux
-lead to:
-
-Difficulty deriving the following stellar parameters for a coeval population:
-\begin{itemize}
-\item{Isochronal ages}
-\item{Isochronal masses}
-\item{IMFs}
-\end{itemize}
-
-And we have shown:
-\begin{itemize}
-\item{\textit{Spitzer} IRAC magnitudes are required for reliable disc
-    identification}
-\item{A correlation between naked to BDD disc system separation (in a
-    CoCoD, as a function of wavelength.}
-\item{Low mass, high accretion rate systems are likely to be
-    misidentified and therefore not included in any study relating
-    $M_*\propto\dot{M}$}
-\end{itemize}
-
-\section[]{ACKNOWLEDGMENTS}
-The computations reported here were performed using the
-University of Exeter Supercomputer.
-
-\bibliographystyle{mn2e}
-\bibliography{references}
-\appendix
-
-\section{Website}
-\label{website}
-
-**NEEDS LOTS OF WORK**
-
-As stated throughout this paper the data presented are available from
-a web page
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
-  disc}. In this Appendix we briefly discuss the data included, and
-the different ways of accessing or visualising these data on the
-website.
-
-\subsection{Available Data}
-\label{web_data}
-
-The magnitudes and colours presented in this paper are avaiable both
-as individual magnitudes and as isochrones or mass tracks. Photometric
-magnitudes have also been derived for several other systems and are
-available online.
-
-\textit{Full list of filters}
-
-These are Johnson, Cousins \textit{UBVRI(JHK)}
-\citep{1966ARA&A...4..193J,2005ARA&A..43..293B}, \textit{Tycho} $V_t$
-and $B_t$ \citep{2000PASP..112..961B}, Bessell \textit{UBVRIJHKL}
-\citep{1988PASP..100.1134B,1998A&A...333..231B}, SDSS \textit{UGRIZ}
-\citep{1996AJ....111.1748F}, 2MASS $JHK_s$
-\citep{2003AJ....126.1090C,2006AJ....131.1163S}, MKO \textit{JHK}
-\citep{2002PASP..114..169S,2002PASP..114..180T}, UKIRT \textit{ZYJHK}
-\citep{2001MNRAS.325..563H}, IRAS 12, 25, 60 and 100 $\mu$m
-\citep{1984ApJ...278L...1N} and SCUBA \textit{450WB} and
-\textit{850WB} \citep{1999MNRAS.303..659H}. For further information on
-these magnitudes, such as the filter responses used and the adopted
-zeropoints please refer to the website.
-
-\textit{Monochromatic fluxes}
-
-In addition to the magnitudes derived for each of these bands
-monochromatic fluxes have also been derived for all bands listed
-above. These have been derived following closely the methods of
-\cite{2006ApJS..167..256R}, extended to further passbands. For details
-of the assumed SED shape, central wavelengths and bandpasses adopted
-please refer to the website.
-
-**PERHAPS INCLUDE FORMULA FOR DERIVATION**
-
-\subsection{Navigation}
-\label{navigation}
-
-The main page contains links to download the entire dataset in several
-formats alonside files describing the format.
-
-\begin{enumerate}
-\item All SEDs ($\AA$ and ergs s$^{-1}$ cm$^{-2} \AA ^{-1}$) 
-\item All SEDs ($\mu$m and mJy)
-\item All Photometric Magnitudes for all BDD systems.
-\item All Photometric Magnitudes for all Naked systems.
-\item All Monochromatic Fluxes for all Naked systems ($\mu$m and ergs
-  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
-\item All Monochromatic Fluxes for all Naked systems ($\mu$m and mJy)
-\item All Monochromatic Fluxes for all BDD systems ($\mu$m and ergs
-  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
-\item All Monochromatic Fluxes for all BDD systems ($\mu$m and mJy)
-\end{enumerate}
-
-Also included is a link to the calibration information listing all the
-filtersponse sources, adopted zero points, central wavelengths,
-bandwidths and assumed SED shapes (for monochromatic flux
-derivation). A brief scientific overview is also available explaining,
-in general terms, the dataset and model.
-
-\subsection{Browsing Tools}
-\label{tools}
-
-For users who wish to investigate the dataset in a more specific or
-interactive fashion two browsing tools are included.
-
-The isochrones, mass tracks and individual stars magnitudes and
-colours generated and presented in the work can be queried using the
-``Isochrone and Mass Track Tool''. This allows the user to select the
-parameters of the model required and retrieve the specific data.
-
-Secondly, an iteractive tool is included allowing a user to select a
-given set of parameters and download the ``SEDs, monochromatic fluxes
-or magnitudes''. In addition this tool plots the SEDs for the Naked
-system or the three inclinations, in the case of BDD systems and
-allows users to select filters sets, whose monochromatic flux values
-will be overlaid on the displayed SEDs.
-
-\label{lastpage}
-\end{document}
+Therefore, in summary, it is currently unclear if any disc locking
+mechanisms efficiency or disc lifetimes are a function of mass, with
+an associated phase change over the TTS to BD mass limit. Rotation
+rate and disc presence data are being used to explore issue.
+Therefore, to create a set of useful models to help contextualise the
+observational constraints we must adopt a realistic, and bounding,
+range of rotation rates. For our model grid, and associated age range
+($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
+placed at around the approximate median for the faster rotating
+samples, providing a useful benchmark for exploring possible detection
+limits of faster rotators with discs. The longer period is set at the
+approximate edge of the slow rotating tail, providing a limiting case
+for the slower rotating, disc-locked, candidates.

### 2010-05-19 BD_disc/paper.tex
removed some files that shouldn't be in cvs - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2273 25464f21-6099-402c-b30a-640f1d40d38b

@@
 accretion funnels in order to recover the level of emission that is
-observed. (Cooling rate arguments can be invoked to explain the
-presence of such high temperatures). Recently some continuum
-measurements of accreting BDs have been conducted, and these broadly
-support the H$\alpha$ rates
-\citep{muzerolle_2003,natta_2004,natta_2006}. Nonetheless
-it is worth considering the observed effect that mass accretion at
-typical CTTS rates onto a BD might have. Parity between the BD
-photospheric luminosity and the accretion luminosity occurs at
-relatively low accretion rates \citep{clarke_2006}. Such
-objects may not be detected as BDs at all in photometric surveys. Even
-before such an extreme case is reached, the additional luminosity
-provided by the accretion should have measurable effect on the BD
-colours. Furthermore the additional flux will be reprocessed by the
-disc, altering its scaleheight and possibly the shape of its inner
-edge.
+observed \citep{muzerolle_2003,natta_2004,natta_2006}. (Cooling rate
+arguments can be invoked to explain the presence of such high
+temperatures). Recently some continuum measurements of accreting BDs
+have been conducted \cite{herczeg_2009}, and these broadly support the H$\alpha$
+rates.
+
+Nonetheless it is worth considering the observed effect that mass
+accretion at typical CTTS rates onto a BD might have. Parity between
+the BD photospheric luminosity and the accretion luminosity occurs at
+relatively low accretion rates \citep{clarke_2006}: Such objects may
+not be detected as BDs at all in photometric surveys. Even before such
+an extreme case is reached, the additional luminosity provided by the
+accretion should have measurable effect on the BD colours. Furthermore
+the additional flux will be reprocessed by the disc, altering its
+scaleheight and possibly the shape of its inner edge.
 
@@
 
-XXXX TJH check this now
-
 Accretion rates derived for pre-MS stars are of order \logmdot = $-6$
-to $-11$ \citep{natta_2006}.  With the largest accretion
-rates found in so-called FU Orionis type objects (after the object
-where they were first observed). For the more typical accretion rates
-\citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9} M_{\odot}yr^{-1}$, for
-  TTS,][]{dahm_2009}, several studies have now suggested
-that the accretion rate is strongly correlated with the mass of the
-central star. This relationship was perhaps first suggested by
+to $-11$ \citep{natta_2006}, with the largest accretion rates found in
+so-called FU Orionis type objects. For the more typical accretion
+rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9} M_{\odot}yr^{-1}$, for
+  TTS,][]{dahm_2009}, several studies have now suggested that the
+accretion rate is strongly correlated with the mass of the central
+star. This relationship was perhaps first suggested by
 \cite{muzerolle_2003} using various accretion diagnostics. Later,
@@
 even lower accretion rates of $\approx$10$^{-13}M_{\odot} yr^{-1}$,
-have been derived for BDs by \cite{herczeg_2009}.  Further
-support for a dependence of accretion rate on stellar mass was
-apparent in the significantly more homogeneous dataset of
-\cite{natta_2006}. \cite{natta_2006} analysed a set
-of accretion rates and masses derived for pre-MS stars in $\rho$
-Ophiuchi and compared these results to stars in Taurus. They found
-that the accretion rate scales with central object mass, into the BD
-regime.
-
-For any $\dot{M}\propto M_*$ relationship to be ratified, clearly, the
-associated mass derivations must be shown to be accurate. For the BD
-mass regime it has been demonstrated that classification, either
-spectroscopic or photometric, and therefore accurate mass derivation
-is exceedingly difficult for BDD systems
-\citep{walker_2004}. The inclusion of significant levels of
-accretion flux will act to exacerbate this problem. Essentially, as BD
-mass objects have relatively cool photospheres, compared to the
-temperature of the accretion hotspots, meaning that for lower
-accretion rates, than for their CTTS counterparsts, the accretion flux
-dominates the small wavelength regime of the SED.
-
-Therefore, to strengthen, or reject, any stellar mass to accretion
-rate relationship, the limits of observational classification (and
-mass derivation) of accreting BDD systems must be understood. To
-provide a benchmark model grid of such systems, with which to aid
-interpretation of the observational data, we must select a range of
-accretion rates including and exceeding those detected for systems
-previously classified as BDs.
+have been derived for BDs by \cite{herczeg_2009}.  Further support for
+a dependence of accretion rate on stellar mass was apparent in the
+significantly more homogeneous dataset of
+\cite{natta_2006}. \cite{natta_2006} analysed a set of accretion rates
+and masses derived for pre-MS stars in $\rho$ Ophiuchi and compared
+these results to stars in Taurus. They found that the accretion rate
+scales with central object mass into the BD regime, although with
+significant scatter.
 
@@
 Disc mass ($M_*$)&0.01 (1)\\
+Surface density profile & $r^{-1}$ (1) \\
 Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
@@
 \label{disc_struct}
+
+XXXX Nathan - add disc structure equation here and remove walker references.
 
@@
 
-As discussed in \cite{walker_2004} discs around CTTS stars
-have scaleheights at 100 AU of between $h$(100)$=$7 to 20 AU, whereas
-for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and 0.01 $M_{\odot}$
-respectively). Our models adopt the same formalism for solving
-hydrostatic equilibrium and therefore, at negligible accretion rates,
-our disc scaleheights are comparable. As the accretion rate increases
-the flux levels of the central star increase and lead to heating of
-the disc which in turn leads to vertical expansion. For
-our models we found that levels of vertical flaring increased
-marginally with accretion rate. Significant differences, more than
-$>$5 AU increase in $h(50)$, in the vertical structure were not
-apparent until the high accretion rates of \logmdot = $-7$ and
-$-6$. Figures \ref{flare_-12_183} and \ref{flare_-7_193} show the
-density structure ($log({\rho})$) in the disc from radial distances of
-0 to 50 AU for example systems ($M_*=0.04M_{\odot}$, Age=1 Myrs,
-$\tau$=5 and areal coverage=10\%), with accretion rates of \logmdot =
-$-12$ and $-7$, respectively.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/flare_-12_183.ps"
-   hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
- \caption{Figure showing the density structure ($log({\rho}$)) of the
+We have previously tested the {\sc torus} code against that used by
+Walker and co-workers, using a CTTS disc model and simultaneously
+solving for radiative and hydrostatic equilibrium (but not employing
+dust sublimation). These tests showed excellent agreement in density
+and temperature structure (as well as in the resultant SEDs). The
+results of these tests were presented by \cite{walker_2006}. It is
+therefore unsurprising that at negligible mass-accretion rates our
+disc structures are very similar to those present in
+\cite{walker_2004}. Typical discs around CTTS stars have scaleheights
+at 100\,AU of between $h$(100)$=$10 to 20\,AU, whereas for BDD
+systems, $h$(100)=20 to 60\,AU (for 0.08 and 0.01 $M_{\odot}$
+respectively). As the accretion rate increases the flux levels of the
+central star increase and lead to heating of the disc which in turn
+leads to vertical expansion. We found that levels of vertical flaring
+increased only marginally with accretion rate. Significant
+differences, more than $>$5\,AU increase in $h(50)$, in the vertical
+structure were not apparent until the high accretion rates of \logmdot
+= $-7$ and $-6$. Figures \ref{flare_-12_183} and \ref{flare_-7_193}
+show the density structure ($\log \rho$) in the disc from radial
+distances of 0 to 50\,AU for example systems ($M_*=0.04M_{\odot}$,
+Age=1\,Myrs, $\tau$=5\,d and areal coverage=10\%), with accretion
+rates of \logmdot = $-12$ and $-7$, respectively.
+
+\begin{figure*}
+\begin{center}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-12_183.ps}\label{flare_-12_183}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-7_193.ps}\label{flare_-7_193}}
+\end{center}
+ \caption{Figure showing the density structure ($\log \rho$) of the
    BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
-   coverage=10\% and accretion rate of \logmdot=$-12$.
-   \label{flare_-12_183}}
-\end{figure}
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/flare_-7_193.ps"
-  hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
-\caption{Figure showing the density structure ($log({\rho}$)) of the
-  BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
-  coverage=10\% and accretion rate of \logmdot=$-7$.
-   \label{flare_-7_193}}
-\end{figure}
-
-Figure \ref{flare_-12_183} shows that for a typical BDD system the
-resulting disc is highly flared and therefore, the opening angle for
-stellar radiation is small. As discussed the flaring for BDD systems
-was found to be larger than CTTS systems by
-\cite{walker_2004}. \cite{walker_2004}, state that the
-degree of disc flaring depends on the disc temperature structure and
-the mass of the central star, with the disc scaleheight $h\propto
-\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{shakura_1973}. Recently,
-\cite{ercolano_2009} suggest the inverse relation of flaring
-with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
-evidence from \cite{allers_2006}, where SEDs for 17 systems in
-the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with
-flared or flat disc models. In general, \cite{allers_2006}
-find that lower mass objects achieve better fits with the flat disc
-models and higher mass objects with the flared discs.
+   coverage=10\% and accretion rate of (a) \logmdot=$-12$ and (b) \logmdot = $-7$.}
+\end{figure*}
+
+\cite{walker_2004} state that the degree of disc flaring depends on
+the disc temperature structure and the mass of the central star, with
+the disc scaleheight $h\propto \frac{T_{\rm disc}}{M_*}^{1/2}$
+\citep{shakura_1973}. Recently however \cite{ercolano_2009} proposed
+the inverse relation of flaring with stellar mass, i.e. $h\propto
+M_*$. This suggestion was based on evidence from \cite{allers_2006},
+where SEDs for 17 systems in the mass range 6$M_{\rm
+  Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat disc
+models. In general, \cite{allers_2006} find that lower mass objects
+achieve better fits with the flat disc models and higher mass objects
+with the flared discs.
 
@@
 
-A quick comparison of Figures \ref{flare_-12_183} and
-\ref{flare_-7_193} show an increase in the scaleheight at 50 AU of
+A  comparison of Figures \ref{flare_-12_183} and
+\ref{flare_-7_193} shows an increase in the scaleheight at 50\,AU of
 $>$5 AU, as the accretion rate moves from \logmdot =$-12$ to
@@
 our grid shows scaleheights comparable to the work of
-\cite{walker_2004} and as such result in similar consequences
-for the SEDs and photometric magnitudes. The effects of this flaring
-and the increase in flaring for very high accretion levels on SEDs and
+\cite{walker_2004} and as such result in similar consequences for the
+SEDs and photometric magnitudes. The effects of this flaring and the
+increase in flaring for very high accretion levels on SEDs and
 photometric magnitudes are discussed in Sections \ref{sed_analysis}
@@
 
-\subsubsection{Inner edge}
+\subsubsection{Inner edge of the dust disc}
 \label{inner_edge}
 
+The inner edge of the gas disc is fixed at the co-rotation radius, at
+which point the gas threads onto the magnetic field and follows the
+field lines in a funnel flow towards the protostellar surface. We make
+the assumption that the dust (should it exist at the co-rotation
+radius) is destroyed in the funnel flows. This is a reasonable
+assumption from both theoretical and observational perspectives:
+Radiative-transfer models indicate the temperature in the funnel flows
+may be very much greater than the dust sublimation temperature
+($>10$\,kK, \citep{muzerolle_2003}), while dusty funnel flows are
+likely to be optically thick in the visible, which would lead to
+substantial photometric variability as the funnels transit the
+photosphere--an effect that is unobserved.
+
 Our models include a sophisticated treatment of dust sublimation
-(described in Section \ref{dust_edge}). In contrast to the models of
-\cite{walker_2004}, who apply a dust destruction radius, we
-set the initial inner radius of the disc at the co-rotation radius of
-the system. However, as our models then sublimate dust during the
-temperature convergence routine this inner edge location may change.
-As the flux levels of the central star increase with increasing
-accretion rates the flux incident on the inner edge increases and
-leads to increasing erosion of the inner edge of the dust disc.
+(described in Section \ref{dust_edge}).  As the flux levels of the
+central protostar increase with increasing accretion rates the flux
+incident on the inner edge increases and leads to increasing erosion
+of the inner edge of the dust disc.
 
@@
 has been predicted to lead to a correlation of inner edge position and
-IR excess \citep{meyer_1997}. This may act to bias surveys
-correlating rotation rates with IR excess to search for evidence of
+IR excess \citep{meyer_1997}. This may act to bias surveys correlating
+rotation rates with IR excess to search for evidence of
 disc-locking. However, the flux from the inner edge will usually peak
@@
 sublimation temperature peaks at $\approx$1400\,K for canonical
-densities. This means that for models where dust is sublimated the
-inner edge will have maximum temperatures of $\approx$1400\,K and this
-correlation of disc position and temperature will be lost.
+densities. This means that for models where dust is significantly
+sublimated the inner edge will {\em always} have a temperature of
+$\approx$1400\,K and this correlation of disc position and temperature
+will be lost.
 
@@
 applicable.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/lum_sub.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing the combined stellar luminosity (accretion
-   plus intrinsic stellar luminosity) in units of
-   log($L_*/L_{\odot}$) against the change in inner edge location
-   shown in units of AU (\textit{top panel}) and $R_*$ (\textit{bottom
-     panel}).
-   \label{lum_sub}}
-\end{figure}
-
-The \textit{top panel} of Figure \ref{lum_sub} shows that as the
-luminosity increases the total change in the inner radius increases as
-more of the disc is sublimated. The total change for lower
-luminosities at lower than $~$0.2 log($L_*/L_{\odot}$) is small (less
-than $~$0.02 AU). As the luminosities increases to larger, and extreme
-values, due to increasing accretion, the dust sublimation
-increases. In the \textit{bottom panel} the change in inner radius
-tends towards around $~$120 $R_*$. Increases in accretion rate, for
-extreme accretors, dominates the increase in stellar luminosity. As
-pre-MS stars age they contract. Therefore, for lower accretion rates,
-younger, and therefore larger stars will have greater luminosities
-than the equivalent older stars. Therefore, the major contributors to
-the X-axis of Figure \ref{lum_sub} are controlled by the input
-parameters of accretion rate and age. The initial inner wall radius
-was set as the magnetic co-rotation radius (see Section
-\ref{physics}). This distance is a strong function of rotational
-period, with $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
-\ref{inner_eq}) which is in turn a function of stellar radius. The
-stellar radius itself is then a function of the stellar
-age. Therefore, the initial inner wall edge position will change as a
-function of the input variables of rotational period and age. The
-initial position of the inner edge will control the amount of the
-stellar flux intercepted by the inner edge wall. Therefore the amount
-that the disc will be sublimated will also be a function of the
-initial position of the inner edge.
-
-Figure \ref{delta_radius} shows the initial inner edge position, or
-the co-rotation radius ($R_*$) against the change in inner edge
-location ( $R_{\rm inner}-R_{\rm co}$, $R_*$). The \textit{panels} of
-Figure \ref{delta_radius} then shows these data for two accretion
-levels and at the two ages and rotation periods. These input variables
-for our model grid are the underlying variables controlling, as
-discussed, the dust sublimation process. The \textit{top panels} are
-for models with accretion rates of -9, -10, -11 and -12
-log$(\frac{\dot{M}}{M_{\odot}}yr{-1})$, classed as typical accretors
-here and throughout the rest of this work. The typical accretors are
-then separated further into three groups in the \textit{top left
-  panel} specifically, -9, -10 and -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black dots
-respectively). The \textit{bottom panels} show the data for models
-with accretion rates of \logmdot = $-6$, $-7$ and $-8$ (blue, red and
-black dots respectively), which we have classed as extreme
-accretors. The \textit{right panels} show the data separated by age,
-with 1 and 10 Myrs (as crosses and triangles respectively), and
-rotation period, with 0.5 and 5 days (as red and blue symbols
-respectively).
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/delta_radius.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing data for the co-rotation radius ($R_{\rm
-     co}$) against the change in inner edge location ( $R_{\rm
-     inner}-R_{\rm co}$) both in units of $R_*$. The typical accretors
-   are shown in the \textit{top panels} and the extreme accretors in
-   the \textit{bottom panels} (see text for explanation). The
-   accretion rates are then further subdivided. The \textit{top left
-     panel} shows accretion rates of \logmdot = $-9$, $-10$, $-11$
-   \& $-12$ as blue, red and black dots
-   respectively. In the \textit{bottom left panel} accretion rates of
-   \logmdot = $-6$, $-7$ and $-8$ are shown as
-   blue, red, and black dots. In addition the \textit{left panels}
-   separates the systems by age and period. The systems with ages of 1
-   and 10 Myrs are shown as crosses and triangles respectively. The
-   systems with rotation rates of 0.5 and 5 days are then shown as red
-   or blue symbols respectively. \label{delta_radius}}
-\end{figure}
 
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
-  \caption{Figure showing final density (log($\rho$)) where dust is
-    present (colour scale) as the \textit{left panel} and temperature,
-    \textit{right panel}, for a system with no dust
-    sublimation. System parameters are: $M_*$=0.04$M_{\odot}$, Age=1
-    Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate \logmdot$=-12$.}
-  \label{no_sub_183}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_169_density.ps}\label{sub_169_a}}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_169_temp.ps}\label{sub_169_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate \logmdot=$-12$.}
-  \label{sub_169}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_175_density.ps}\label{sub_175_a}}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_175_temp.ps}\label{sub_175_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate \logmdot$=-9$.}
-  \label{sub_175}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate \logmdot$=-7$.}
-  \label{sub_179}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
-  \caption{Figure showing both the initial (grey scale) and final
-    density (log($\rho$)) where dust is present (colour scale) as the
-    \textit{left panel} and temperature, \textit{right panel}, for a
-    system with no dust sublimation. System parameters are:
-    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
-    $\tau$=0.5 days and accretion rate \logmdot$=-6$.}
-  \label{sub_181}
+  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
+  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
+  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
+  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
+  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
+  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
+
+  \caption{Figure showing both the initial (grey scale) final density
+    ($\log \rho$) where dust is present (colour scale, left-hand
+    panels) and temperature (right-hand panels). System parameters
+    are: $M_*$=0.04$\,M_{\odot}$, Age=1\,Myrs and areal coverage=10\%,
+    $\tau$=5\,days and accretion rate \logmdot$=-12$ (a, b);
+    $M_*$=0.04$M_{\odot}$, Age=1\,Myrs and areal coverage=10\%,
+    $\tau$=0.5\,days and accretion rate \logmdot$=-7$ (c, d);
+    $M_*$=0.04$M_{\odot}$, Age=1\,Myrs and areal coverage=10\%,
+    $\tau$=0.5\,days and accretion rate \logmdot$=-6$ (e, f).}
 \end{figure*}

### 2010-05-19 BD_disc/paper.tex
test
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2275 25464f21-6099-402c-b30a-640f1d40d38b

@@
     acc}}$). The accretion spot temperatures, for typical accretors,
-will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range 0.3
-to 8.5\,$\mu$m. For the extreme accretors temperatures which can reach
-as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The second pair of
-luminosity sources are from constituent parts of the circumstellar
-disc. The inner edge, ($L_{\rm wall}$), at temperatures of $~$370 to
-$~$1500\,K, or flux contributions from $~$1.85 to 7.7\,$\mu$m
-\citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and the outer
-disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less contributing
-flux longward of $~$10\,$\mu$m. As discussed in Section \ref{seds} the
-{\sc torus} radiative transfer code tags the photons before they reach
-the simulated observer in one of four ways, stellar and thermal,
-either direct or scattered. These components allow us to analyse the
-contributions from the main flux contributors discussed, i.e. $L_{\rm
-  acc}$ and $L_*$ equals stellar scattered or direct, with thermal
-emission comprising $L_{\rm wall}$ and $L_{\rm disc}$. Figure
-\ref{disc_eg_173} shows a typically accreting BDD system with the
-component photon contributions highlighted, with $M_*=0.04M_{\odot}$
-at 1 Myr with an areal coverage of 10\%, accretion rate of
-\logmdot=$-10$ and rotation period of 0.5
+will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range
+0.3 to 8.5\,$\mu$m. For the extreme accretors temperatures which can
+reach as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The
+second pair of luminosity sources are from constituent parts of the
+circumstellar disc. The inner edge, ($L_{\rm wall}$), at temperatures
+of $~$370 to $~$1500\,K, or flux contributions from $~$1.85 to
+7.7\,$\mu$m \citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and
+the outer disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less
+contributing flux longward of $~$10\,$\mu$m. Disentangling the
+accretion and stellar photospheroc flux becomes difficult as $T_{\rm
+  acc} \to T_{\rm eff}$, which for an acretion rate of -9 \logmdot,
+occurs at a fractional coverages of 20 and 10\%, for rotation periods
+of 5 and 0.5 days (with $M_*=0.04M_{\odot}$ and an age of 1 Myr). As
+discussed in Section \ref{seds} the {\sc torus} radiative transfer
+code tags the photons before they reach the simulated observer in one
+of four ways, stellar and thermal, either direct or scattered. These
+components allow us to analyse the contributions from the main flux
+contributors discussed, i.e. $L_{\rm acc}$ and $L_*$ equals stellar
+scattered or direct, with thermal emission comprising $L_{\rm wall}$
+and $L_{\rm disc}$. Figure \ref{disc_eg_173} shows a typically
+accreting BDD system with the component photon contributions
+highlighted, with $M_*=0.04M_{\odot}$ at 1 Myr with an areal coverage
+of 10\%, accretion rate of \logmdot=$-10$ and rotation period of 0.5
 days. The solid black line is the total simulated SED, with the

### 2010-05-19 BD_disc/paper.tex
New figure
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2276 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \textit{both panels} the systems with rotation periods of 0.5 and 5
-days are plotted in red and blue respectively. Those systems where the
-change in inner radius was greater than 1$R_*$, and therefore classes
-as significantly sublimated, are plotted as crosses. These systems are
-only present for the extreme accretors, as shown in Figure
-\ref{delta_radius}. Furthermore, for the typical accretors Figure
-\ref{delta_radius} shows that only the shorter period objects, in
-general, experience any disc erosion at the inner edge.
+days are plotted in red and blue respectively. Systems where $\Delta
+R_{\rm inner} < 1R_*$ are plotted ia crosses and $\Delta R_{\rm inner}
+> 1R_*$ as filled circles, with the latter denoting systems with
+significant sublimation. Significant sublimation is only found for the
+extreme accretors, as shown in Figure \ref{delta_radius}.
+Furthermore, for the typical accretors Figure \ref{delta_radius} shows
+that only the shorter period objects, in general, experience any disc
+erosion at the inner edge.
 
@@
        inner}$, $R_*$). The typical accretors are shown in the
-   \textit{left panel} and the extreme accretors in the \textit{right
-     panel} (see text for explanation). In \textit{both panels}
-   separate the systems by period, with those systems with rotation
-   periods of 0.5 and 5 days shown as red and blue symbols
-   respectively. In addition systems where the total change in the
-   inner radius is greater than 1$R_*$ are marked as crosses (this is
-   only achieved by some systems classed as extreme
-   accretors).\label{inner_temp}}
+     \textit{left panel} and the extreme accretors in the
+     \textit{right panel} (see text for explanation). In \textit{both
+       panels} separate the systems by period, with those systems with
+     rotation periods of 0.5 and 5 days shown as red and blue symbols
+     respectively. In addition, systems where $\Delta R_{\rm inner} <
+     1R_*$ are plotted ia crosses and $\Delta R_{\rm inner} > 1R_*$ as
+     filled circles (this is only achieved by some systems classed as
+     extreme accretors).\label{inner_temp}}
 \end{figure*}

### 2010-05-20 BD_disc/paper.tex
from th -th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2277 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \begin{tabular}{|l|l|}
+\hline
 Input parameter&Values (\# values)\\
@@
 (10)\\
+\hline
 \end{tabular}
@@
 
-\subsubsection{Inner edge of the dust disc}
+\subsubsection{Inner edge of the dust disc: location}
 \label{inner_edge}
@@
 densities. This means that for models where dust is significantly
-sublimated the inner edge will {\em always} have a temperature of
+sublimated the inner edge will {\em usually} have a temperature of
 $\approx$1400\,K and this correlation of disc position and temperature
-will be lost.
-
-Equation \ref{inner_eq} shows that as the rotation period, of the
-star, increases the co-rotation radius decreases. This will result in,
-initially, shorter period systems having closer and hotter inner edges
-than their longer period counterparts. In addition, if the accretion
-rate is increased in these systems the incident flux on the inner wall
-will increase leading to a rise in the temperature of the inner edge.
-At some point, in both cases the dust sublimation temperature may be
+will be lost (although see below).
+
+Equation \ref{inner_eq} shows that as the rotation period of the
+protostar increases the co-rotation radius decreases. This will result
+in, initially, shorter period systems having closer and hotter inner
+edges than their longer period counterparts. In addition, if the
+accretion rate is increased in these systems the incident flux on the
+inner wall will increase leading to a rise in the temperature of the
+inner edge.  At some point the dust sublimation temperature may be
 reached, leading to a change in radial position of the wall. In
-addition, the temperature of the inner edge will then tend to a
-maximum temperature, of the dust sublimation temperature. Figure
-\ref{lum_sub} shows the total stellar luminosity (accretion luminosity
-plus the intrinsic stellar luminosity), in log($L_*/L_{\odot}$)
-against the change in inner disc location, $R_{\rm co}-R_{\rm inner}$
-in units of AU (\textit{top panel}) and $R_*$ \textit{bottom panel}.
-This change in inner edge location is from the initially set
-co-rotation radius to the final radius after dust sublimation, if
-applicable.
-
-The classification of models into typical and extreme accretors is
-based on observations (see discussion in \ref{par_accn}) and also
-evidence from the simulations themselves. Figure \ref{delta_radius},
-\textit{left panels}, shows that dust sublimation does not become
-significant until accretion rates of around \logmdot=$-9$ and
-increases dramatically with increasing accretion rate thereafter.
-This accretion rate is also, unsurprisingly the accretion rate at
-which the underlying photospheric emission is overwhelmed by the
-accretion flux, and the photospheric features are lost (see Section
-\ref{sed_analysis}). The \textit{right panels} of Figure
-\ref{delta_radius} show that dust sublimation occurs only for rotation
-periods of 0.5 days for typical accretors. For the extreme accretors
-the systems with both rotation periods undergo sublimation but the
-effect is more significant in the systems with shorter rotation
-periods.  The \textit{right panels} also show that for extreme
-accretors the older systems undergo more dust sublimation, whereas for
-the typical accretors the older systems undergo little or no dust
-sublimation.
-
-The density of material in the disc falls with increasing radius from
-the star ($\rho\propto R_*^{\alpha}$).  The dust sublimation
-temperature is also density dependent \citep{pollack_1994}.
-Therefore, for systems where the inner edge has been eroded
-significantly from the co-rotation radius the temperature of the inner
-edge will fall as the final radius increases.  In this case a
-correlation of inner edge temperature and inner edge radius is
-expected with a resulting slope determined, at least in part, by the
+addition, the temperature of the inner edge will then tend to the dust
+sublimation temperature.
+
+A further complexity arises when one considers that the density of
+material in the disc falls with increasing radius from the star
+($\rho(r) \propto r^{\alpha}$), and that the dust sublimation
+temperature is density dependent \citep{pollack_1994}.  Therefore, for
+systems where the inner edge has been eroded significantly from the
+co-rotation radius the temperature of the inner edge will fall
+systematically as the inner dust disc radius increases.
+
+In order to examine the effect of dust sublimation on our models we
+have measured the radius of the inner edge of the dust disc by
+integrating from the centre along the midplane until an optical depth
+of 2/3 (at 5500\AA) is reached. Figure \ref{inner_temp} shows the
 radial density distribution of the disc.  In this case the the final
@@
 \textit{both panels} the systems with rotation periods of 0.5 and 5
-days are plotted in red and blue respectively. Systems where $\Delta
-R_{\rm inner} < 1R_*$ are plotted ia crosses and $\Delta R_{\rm inner}
-> 1R_*$ as filled circles, with the latter denoting systems with
-significant sublimation. Significant sublimation is only found for the
-extreme accretors, as shown in Figure \ref{delta_radius}.
-Furthermore, for the typical accretors Figure \ref{delta_radius} shows
-that only the shorter period objects, in general, experience any disc
-erosion at the inner edge.
+days are plotted in red and blue respectively. Those systems where the
+change in inner radius was greater than 1$R_*$, and therefore classes
+as significantly sublimated, are plotted as crosses.
 
@@
 
+The \textit{left panel} of Figure \ref{inner_temp} shows that, taken
+as a whole, our models with typical accretion rates show a clear
+correlation between the temperature at the inner edge and the radius
+to this boundary. This agrees with the work of \cite{meyer_1997} where
+this correlation is found for there $R_{\rm inner}=$1$-$12$R_*$ and
+\logmdot = $-9$ to $-5$, for flat disc models.  \cite{meyer_1997} use
+this correlation, and the derivation of IR magnitudes, to predict a
+relationship between IR excess and radius to the inner wall. Our data
+indicate that this correlation, for typically accreting systems will
+translate into a correlation between rotation rate and IR excess. This
+could have important implications for studies of disc-locking where
+disc presence is examined as a function of rotation rates, provide an
+intrinsic bias. In practice however, this correlation is weak (in fact
+unobservable) in our data due to the combined effects of the inner
+disc wall shape, inclination and flaring effects. This is discussed in
+more detail in Section \ref{photometry}.
+
 Figure \ref{inner_temp} shows that for those systems where significant
@@
 is no clear correlation between the temperature at the inner edge and
-radius to this edge. The \textit{left panel} of Figure
-\ref{inner_temp} shows that, taken as a whole, our models with typical
-accretion rates show a clear correlation between the temperature at
-the inner edge and the radius to this boundary. This agrees with the
-work of \cite{meyer_1997} where this correlation is found for
-there $R_{\rm inner}=$1$-$12$R_*$ and $\dot{M_{\rm acc}}=$10$^{-9}$to
-10$^{-5} M_{\odot}yr^{-1}$, for flat disc models.
-\cite{meyer_1997} use this correlation, and the derivation of
-IR magnitudes, to predict a relationship between IR excess and radius
-to the inner wall. Our data indicate that this correlation, for
-typically accreting systems will translate into a correlation between
-rotation rate and IR excess. This could have important implications
-for studies of disc-locking where disc presence is examined as a
-function of rotation rates, provide an intrinsic bias. In practice
-however, this correlation is weak, an unobservable, in our data due to
-inner disc wall shape, inclination and flaring effects. This is
-discussed in more detail in Section \ref{photometry}.
-
-For simulations without dust sublimation, and analytic density
-distributions, the inner disc edge is characterised solely by the
-initial disc density prescription. If one includes vertical
-hydrostatic equilibrium the scaleheight of the disc inner edge can
-change but the radial distribution of dust will not. Dust sublimation
-physics will alter the vertical structure, but crucially will also
-alter the radial distribution of dust. This means that dust
-sublimation effects will control the shape of the inner disc wall and
-possibly change this from a vertical wall. Evidence that real inner
-disc boundaries (for CTTS) are not vertical walls comes from a lack of
-dependence of the derived IR excess on system inclination
-\citep{tannirkulam_2007}. As discussed in Section \ref{dust_edge}
-the disc inner hole can be created by several mechanisms, however, for
-this study we have only included a treatment of magnetic truncation
-(initially) and subsequent dust sublimation. The effects of dust
-sublimation have been shown to produce curved inner walls due to the
-temperature and density dependence of the dust sublimation temperature
-\citep{isella_2005}. The curved boundary in this case is
-convex, as density increases towards the midplane of the disc, the
-dust sublimation temperature increases, meaning the destruction radius
-moves closer to the star. A curved inner boundary is also found to
-result from dust sublimation in \cite{tannirkulam_2007}. In
-\cite{tannirkulam_2007} two populations of dust grains where
-included with different scaleheight distributions. This is essentially
-a simple model of grain growth and subsequent midplane settling.
-\cite{tannirkulam_2007}, found a concave inner disc boundary, this
-is due to the larger grains cooling more efficiently. These larger
-grains dominate the dust towards smaller vertical distances from the
-midplane, and therefore the increased cooling means that the dust
-sublimation temperature is reached at closer radii. The implications
-of the inner edge shape for the simulated SEDs and photometry are
-discussed in Section \ref{sed_analysis} and \ref{photometry}.
-
-For systems where dust sublimation does not occur, or is minimal the
-inner edge of the system will remain as a vertical wall, as prescribed
-by our initial density distribution. However, as one increases the
-flux levels of a given system, by increasing the accretion rates (or
-moving to younger ages) the inner edge will increase in
-temperature. As the flux levels increase, in a given model, the dust
-at the inner edge will sublimate. The dust in the regions of lowest
-density or maximum flux interception will be preferentially
-destroyed. This will lead to a reduction in the scaleheight and a
-slight concave cavity at the inner wall. The inner edge will then move
-towards a convex boundary as the inner edge is forced radially outward
-towards regions of lower density with increasing flux levels. This
-outward movement will result in the outer, vertical, regions of the
-dust disc eroding. Increasing the flux still further will lead to
-significant dust sublimation and an outward migration. This subsequent
-migration will move the inner edge into regions of lower density and
-greater scaleheight.
-
-The transition in shape and position of the inner edge for a given
-model as the accretion rate, and therefore flux levels, are increased
-is shown in Figures \ref{no_sub_183} to \ref{sub_181}. The model
-chosen for illustrative purposes has the following parameters,
-$M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%. The model
-shown in Figure \ref{no_sub_183} has $\tau$=5 days and accretion
-rate \logmdot$=-12$ (model shown in Figure
-\ref{flare_-12_183}), with Figures \ref{sub_169} to \ref{sub_181}
-showing models with $\tau$=0.5 days and accretion rates \logmdot=$-12$, $-9$, $-7$
-and $-6$. The \textit{right
-  panels} of Figures \ref{no_sub_183} to \ref{sub_181} show the
-temperature structure of the final converged disc structure. The
-\textit{left panels} of Figures \ref{no_sub_183} to \ref{sub_181} show
-the final log($\rho$) distribution for regions where dust is present,
-scaled to a different minimum density (log($\rho_{\rm
-  min}$)$=1^{-13}$) compared to Figures \ref{flare_-12_183} and
-\ref{flare_-7_193}. The lower (log) density threshold is used in this
-case to better trace the inner edge and denser regions of the disc,
-whereas Figure \ref{flare_-12_183} and \ref{flare_-7_193} show the
-outer diffuse regions of the disc, or disc limits. Additionally, for
-Figures \ref{sub_169} to \ref{sub_181} (the sublimated systems), the
-\textit{left panels} also show the initial density, in the same units
-as the final density, this is shown as a background grey scale (with
-the same maximum and minimum as for the final density) to illustrate
-the effects of sublimation.
+radius to this edge.
+
+\subsubsection{Inner edge of the dust disc: shape}
+\label{inner_edge_shape}
+
+The initial shape of the inner edge of the dust disc is a vertical
+wall coincident with the co-rotation radius. In the previous section
+we have shown that models with a negligible accretion rate do not
+significantly sublimate the dust, and hence the edge remains
+vertical. This inner edge is heated by direct radiation from the
+protostar, and its scaleheight increases. Disc material behind the
+inner rim is shielded from direct radiation and has a smaller
+scaleheight, leading to the `puffed up' inner rim predicted by
+\cite{dullenmond_2001}. This effect is illustrated in
+Figure~\ref{no_sub_183}, a model in which there is negligible dust
+sublimation.
 
@@
 
-Figure \ref{no_sub_183} shows the inner disc edge as a vertical wall
-with no dust sublimation, the inner wall has not changed location from
-the initial disc description. The \textit{right panel} of Figure
-\ref{no_sub_183} shows that the corresponding temperature structure is
-smooth and interpolation at the inner edge yields a temperature of
-$~$900\,K. For the shorter period model the inner edge has undergone
-some dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
-shows that the inner edge has lost dust slightly, preferentially,
-along the midplane. Again for Figure \ref{sub_169} the change in inner
-edge location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
-sublimation (and inner wall) temperature is $~$1450\,K, for a density
-of $~2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
-\ref{sub_169}).The \textit{left panel} of Figure \ref{sub_169} shows
-that for even for a negligible accretion rate of \logmdot=$-12$,
-sublimation has begun to erode the inner edge, for the younger and
-faster rotating systems.  Here the final density distribution has
-moved radially outward as can be seen by comparing the grey and colour
-scales in the \textit{left panel} of Figure
-\ref{sub_169}. Additionally, the inner edge has become slightly
-concave. As the flux levels of the central star increase the
-temperature of the inner edge surpasses the sublimation temperature at
-an increasing radius, destroying more of the disc and pushing the
-inner edge radially outwards. The \textit{left panel} of Figure
-\ref{sub_175} shows that for an accretion rate of \logmdot$=-9$,
-increased sublimation has pushed the inner wall slightly farther from
-the star (when compared to Figure \ref{sub_169}), here, $\Delta
-R~0.52R_*$ ($~1.1\times 10^{-3}$AU), and $T_{\rm inner}~1450$. Again
-the final density distribution has moved radially outward as can be
-seen by comparing the grey and colour scales in the \textit{left
-  panel} of Figure \ref{sub_175}. The \textit{right panel} of Figure
-\ref{sub_175} shows that the gas interior to the inner edge extending
-down to the co-rotation radius, which is not sublimated, will reach
-temperatures in excess, or equal to, the inner edge, which in this
-model is $~$1400\,K. Such hot gas inner discs interior to the dust
-disc have been postulated through SED fitting
-\citep{eisner_2005,tannirkulam_2008}. Again, the shape of
-the inner wall has changed in Figure \ref{sub_175}, the top and bottom
-sections of the disc have eroded and the inner wall is convex. The
-model in Figure \ref{sub_175} has an accretion rate of \logmdot=$-9$,
-which is the transition point between our two groups of accretors,
-typical and extreme. Figure \ref{sub_175} shows that for typical
-accretion rates, and faster rotation periods (and younger ages)
-significant dust sublimation is expected to occur at the inner edge,
-resulting in a curved inner wall at around $~$1400\,K. Increasing the
-accretion rate, and therefore flux levels still further leads to
-significant erosion of the inner disc.  For the extreme accretors the
-dust sublimation at the inner edge now changes the inner wall position
-by many multiples of the stellar radius. Figures \ref{sub_179} and
-\ref{sub_181} are for systems with accretion rates typical in outburst
-or episodic accretion systems, \logmdot$=-7$ and $-6$
-respectively. The inner edges for these systems are eroded radially by
-7.1 and 36.1 ($R_*$) respectively (0.016 and 0.080 AU, respectively),
-visible by comparing the grey and colour scales of Figure
-\ref{sub_179} and \ref{sub_181}.  As this occurs the disc inner edge
-moves far enough that the density drop (with radius) occurring in the
-disc causing the sublimation temperature to fall. Consequently the
-disc inner edge becomes cooler as it can not sustain temperatures
-above the sublimation temperature.  This is shown in the \textit{right
-  panels} of Figures \ref{sub_179} and \ref{sub_181}, with approximate
-temperatures at the inner edge of 1370 and 1260\,K. In addition, the
-inner edge has become concave and, again due to changes in the
-underlying disc density distribution, much larger in scaleheight.
-
-A similar sequence is apparent across the grid for set
+As the flux of the central object increases significant dust
+sublimation occurs, leading to a change in the radial position of the
+dusty inner edge, but also shaping it: The density drops rapidly away
+from the midplane, and since the dust sublimation temperature also
+falls the edges of the inner dust disc become curved--this the
+mechanism described analytically by \cite{isella_2005}. We illustrate
+this effect in Figure~\ref{sub_179_a}, which also shows a scaleheight
+decrease behind the curved inner rim, over a significantly larger
+radial scale than the previous model.
+
+Finally the most extreme accretor (Figure~\ref{sub_181_a}) shows dust
+being destroyed to very large radii ($\sim 0.1$\, AU). A curved rim is
+present, without any obvious decrease in scaleheight behind the inner
+rim. The distance from the central object is such that the vertical
+component of gravity is much diminished, and the disc has a
+substantial scaleheight at the inner edge, meaning that it reprocesses
+significant protostellar radiation leading to a high near-IR excess.
+
+We note that a similar sequence is apparent across the grid for set
 masses. However, the balance of the rotation period, and therefore
@@
 discussed in Section \ref{seds} the {\sc torus} radiative transfer
-code tags the photons before they reach the simulated observer in one
-of four ways, stellar and thermal, either direct or scattered. These
-components allow us to analyse the contributions from the main flux
-contributors discussed, i.e. $L_{\rm acc}$ and $L_*$ equals stellar
-scattered or direct, with thermal emission comprising $L_{\rm wall}$
-and $L_{\rm disc}$. Figure \ref{disc_eg_173} shows a typically
-accreting BDD system with the component photon contributions
-highlighted, with $M_*=0.04M_{\odot}$ at 1 Myr with an areal coverage
-of 10\%, accretion rate of \logmdot=$-10$ and rotation period of 0.5
-days. The solid black line is the total simulated SED, with the
-stellar photons shown as blue lines and the thermal as red. The
-scattered and direct contributions are then shown as dashed and solid
-lines respectively. The horizontal and vertical dotted lines then show
-the approximate ranges of the flux contributions from the (from left
-to right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red)
-and $L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
+code tags the photon packets before they reach the simulated observer
+in one of four ways, stellar and thermal, either direct or
+scattered. These components allow us to analyse the contributions from
+the main flux contributors discussed, i.e. $L_{\rm acc}$ and $L_*$
+equals stellar scattered or direct, with thermal emission comprising
+$L_{\rm wall}$ and $L_{\rm disc}$.
+
+Figure \ref{disc_eg_173} shows a typically accreting BDD system with
+the component photon contributions highlighted, with
+$M_*=0.04M_{\odot}$ at 1 Myr with an areal coverage of 10\%, accretion
+rate of \logmdot=$-10$ and rotation period of 0.5 days. The solid
+black line is the total simulated SED, with the stellar photons shown
+as blue lines and the thermal as red. The scattered and direct
+contributions are then shown as dashed and solid lines
+respectively. The horizontal and vertical dotted lines then show the
+approximate ranges of the flux contributions from the (from left to
+right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red) and
+$L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
 Figure \ref{disc_eg_173} show the approximate ranges of the $V$, $I$,
@@
 one increases the accretion rate. With the features of the intrinsic
-stellar photosphere or atmosphere eventually lost or swamped by the
+stellar photosphere or atmosphere eventually become veiled by the
 accretion flux. This will lead to difficulties in using spectral
@@
 luminosity spectral classification of these systems (or at least their
-central stars) will become unreliable. As discussed in Section
-\ref{inner_edge} observations of the inner edge location separate the
-BDD systems into two groups, the typical accretors ($\dot{M}\leq$-9
-log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$) and extreme accretors
-($\dot{M}>-9$). This division
-between typical and extreme accretors is based on observational
-results (see Section \ref{par_accn}) as well as consequence of
-sublimation. The typical accretors show limited sublimation at the
-disc inner edge leading to a weak correlation in inner edge
-temperature with edge radius. Whereas, for the extreme accretors the
-inner edge is significantly eroded and the dust sublimation
-temperature reached, which can not be exceeded. This effectively means
-that the inner edge temperature is weakly correlated with temperature
-(with a different characteristic slope to the typical accretors), as
-the dust sublimation temperature is density dependent, which is in
-turn dependent on radial position (see Figures \ref{delta_radius} and
-\ref{inner_temp}).
+central stars) will become unreliable.
 
@@
 moves father from the star the potential energy released by the
-accreted material is reduced. This effect can be seen when comparing
-the \textit{top} and \textit{bottom panels}, although the effect is
-marginal for all but the highest displayed accretion rates. The
-\textit{left panels} show accretion streams with an areal coverage of
-10\% and the \textit{left panels} 1\%. As the areal coverage reduces
-the effective temperature of the accretion hot spot increases,
-resulting in an increase in accretion flux, and resulting shift to
-bluer wavelengths of the peak flux. This can be seen clearly by
-comparing the \textit{left} and \textit{right panels} of Figure
-\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
-shown is Figure \ref{acc_dom} is an insight into the accretion rate at
-which the accretion blackbody flux dominates over the photospheric
-flux. Figure \ref{acc_dom} shows that as the accretion rate raises
-above \logmdot = $-9$ for systems with 1 or 10\% areal coverage, the
-accretion flux dominates the emergent SED at both periods. Therefore
-for reasonable coverages (1-10\%) and rotational periods (0.5-5 days)
-the photospheric flux is effectively swamped by accretion flux for
-accretion rates \logmdot$>-9$. This suggests that accreting BD systems
-with accretion rates as low as \logmdot$=-9$ could be difficult to
-identify from SEDs as BD stars, and may well be classified as higher
-mass stars.
-
+accreted material is reduced (XXXX WHAT?). This effect can be seen
+when comparing the \textit{top} and \textit{bottom panels}, although
+the effect is marginal for all but the highest displayed accretion
+rates.
 \begin{figure*}
@@
 
+The \textit{left panels} show accretion streams with an areal coverage
+of 10\% and the \textit{left panels} 1\%. As the areal coverage
+reduces the effective temperature of the accretion hot spot increases,
+resulting in an increase in accretion flux, and resulting shift to
+bluer wavelengths of the peak flux. This can be seen clearly by
+comparing the \textit{left} and \textit{right panels} of Figure
+\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
+shown is Figure \ref{acc_dom} is an insight into the accretion rate at
+which the accretion blackbody flux dominates over the photospheric
+flux. Figure \ref{acc_dom} shows that as the accretion rate raises
+above \logmdot = $-9$ for systems with 1 or 10\% areal coverage, the
+accretion flux dominates the emergent SED at both periods. Therefore
+for reasonable coverages (1--10\%) and rotational periods (0.5--5 days)
+the photospheric flux is effectively swamped by accretion flux for
+accretion rates \logmdot$>-9$.
+
 As is well known the shorter wavelength component of the SED for
@@
 \cite{walker_2004} this increased flaring (when compared to
-CTTS stars) leads to occulltation at the star at lower inclination
+CTTS stars) leads to occultation at the star at lower inclination
 angles and, therefore, significant changes to the SED. Increases in
@@
 
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_inc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure of total SED flux reaching the observer for viewing
-   angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90$^{\circ}$. SEDs
-   shown are for systems shown in Figures \ref{flare_-12_183} and
-   \ref{flare_-7_193}, as the \textit{left} and \textit{right panels}
-   respectively. In both panels the dashed line highlights the angle
-   at which a significant fall in flux reaching the observer occurs.
-   The values of inclination at which the fall in flux occurs are
-   71$^{\circ}$ and 56$^{\circ}$ for the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, \textit{left} and
-   \textit{right panels} respectively. The vertical and horizontal
-   dashed lines denote the approximate sensitivity ranges of our chosen
-   $V$, $I$, $J$ and $K$ filters. \label{flare_inc}}
-\end{figure*}
-
-\subsubsection{Inner Edge Shape}
-\label{inner_shape}
-
-As discussed in Section \ref{disc_struct} the addition of dust
-sublimation leads to a change in the shape of the inner edge, where
-the temperature is sufficient. Figures \ref{no_sub_183} to
-\ref{sub_181} show a range in inner edge shapes, from flat walls
-through concave to convex curves, caused by the radial density profile
-of the disc and the dependence of the sublimation temperature on
-density. This change in shape, as noted by \cite{tannirkulam_2007},
-will lead to changes in the characteristics of the SED, or derived IR
-excess, with inclination angle \citep{tannirkulam_2007}. For
-concave and vertical walls the inner edge is visible over a smaller
-range of viewing angles than for a convex inner edge.
-
-Figures \ref{typ_curve} and \ref{ext_curve} show the thermal direct
-radiation, originating from the disc, as a function of inclination for
-the two groups of accretors, typical and extreme respectively. The
-models included in Figure \ref{typ_curve} as the \textit{left} and
-\textit{right panels} are those shown in Figures \ref{sub_169} and
-\ref{sub_175} respectively. Whereas, the models included in Figure
-\ref{ext_curve} as the \textit{left} and \textit{right panels} are
-those shown in Figures \ref{sub_179} and \ref{sub_181}
-respectively. For each \textit{panel} of Figures \ref{typ_curve} and
-\ref{ext_curve} the thermal direct flux is plotted as a solid black
-line at each modeled inclination, namely, 0, 27, 39, 48, 56, 64, 71,
-77, 84 \& 90$^{\circ}$. The dashed line in each case shows where a
-significant fall in the flux reaching the observer from direct thermal
-emission from the disc is apparent.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/typ_curve.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing thermal direct flux reaching the observer at
-   inclination angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \&
-   90$^{\circ}$, for typical accretors. The \textit{left panel} shows
-   the flux from the model shown in Section \ref{disc_struct}, Figure
-   \ref{sub_169}. The \textit{right panel} shows the flux from the
-   model shown as Figure \ref{sub_175} in Section
-   \ref{disc_struct}. In both panels the dashed line highlights the
-   angle at which a significant fall in flux from direct thermal
-   emission is observed.  The values of inclination at which the fall
-   in flux occurs are 77$^{\circ}$ for \textit{both panels} and
-   therefore accretion rates. The vertical and horizontal dashed lines
-   denote the approximate sensitivity ranges of our chosen $V$, $I$,
-   $J$ and $K$ filters. \label{typ_curve}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/ext_curve.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing thermal direct flux reaching the observer at
-   inclination angles of 0, 27, 39, 48, 56, 64, 71, 77, 84 \&
-   90$^{\circ}$, for extreme accretors. The \textit{left panel} shows
-   the flux from the model shown in Section \ref{disc_struct}, Figure
-   \ref{sub_179}. The \textit{right panel} shows the flux from
-   the model shown as Figure \ref{sub_181} in Section
-   \ref{disc_struct}. In both panels the dashed line highlights the
-   angle at which a significant fall in flux from direct thermal
-   emission is observed.  The values of inclination at which the fall
-   in flux occurs are 71$^{\circ}$ and 64$^{\circ}$ for the
-   \textit{left} and \textit{right panels}
-   respectively.  The vertical and horizontal dashed lines (in the
-   \textit{lower panels}) denote the approximate sensitivity ranges of
-   our chosen $V$, $I$, $J$ and $K$ filters.\label{ext_curve}}
-\end{figure*}
-
-For typically accreting systems, where little or no dust sublimation
-has occurred the inner edge remains either a vertical or slightly
-concave wall, as shown in Figures \ref{sub_169} and \ref{sub_175}. For
-these systems flux reaching an observer from direct thermal emission,
-i.e. from, in the main, the disc inner edge, falls rapidly with
-increasing viewing angle, after the maximum opening angle is achieved.
-This is shown in Figure \ref{typ_curve} where at the viewing angle of
-77$^{\circ}$ the flux shown falls significantly, for both accretion
-rates. This opening angle is larger than found for the slower
-rotating, counter parts, as shown by Figure \ref{flare_inc}, where a
-transition in occultation occurs at 71$^{\circ}$. For the case shown
-in Figure \ref{typ_curve} the system has the shorter rotation period,
-leading to a larger opening angle, as the flux from the central star
-does not reach the outer disc, and subsequently flare it. Figure
-\ref{typ_curve} shows that after an angle of 77$^{\circ}$ the flux
-from the inner edge falls to zero. The systems displayed in Figure
-\ref{typ_curve} have inner edge temperatures of $~$1400\,K, meaning
-their flux emission peaks at a wavelength of $~$2\,$\mu$m. The flux
-observed at the expected peak wavelength falls to zero at inclinations
-of 77$^{\circ}$, indicative of a vertical wall being obscured by the
-outer disc, before the limit of the opening angle is reached.
-
-Figure \ref{inner_inc_sed} shows the full SEDs and the components (as
-tagged by {\sc torus}), for the models displayed in Figures
-\ref{sub_169} and \ref{sub_179} and the \textit{left panels} of
-Figures \ref{typ_curve} and \ref{ext_curve}. The \textit{top panels}
-show the SEDs for an accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (model from Figure
-\ref{sub_169}) for inclinations of 64, 71 and 77$^{\circ}$, moving
-from the \textit{leftmost} to \textit{far right panel}. The same
-inclinations are shown in the \textit{bottom panels}, which show the
-SEDs, and components, for the model with an accretion rate of -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, displayed in Figure
-\ref{sub_179}. As discussed in Section \ref{disc_struct}, the model
-with the higher accretion rate has a a much larger, in scaleheight,
-and convex inner boundary. The lower accretion rate model has a
-vertical inner wall, close to the star. The analysis of Figures
-\ref{typ_curve} and \ref{ext_curve} show that the flux from the inner
-wall should fall dramatically at different limiting inclinations for
-either accretion rate.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_inc_sed.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
-   and an areal coverage of the accretion stream of 10\%. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the constituent fluxes for SEDs at inclination
-   angles of 64$^{\circ}$, 71$^{\circ}$ and 77$^{\circ}$. The total
-   flux is shown as a black line, with the component fluxes presented
-   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
-   for systems with an accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and the \textit{lower
-     panels} are for an accretion rate of -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The SEDs from the
-   \textit{top} and \textit{bottom panels} are derived from the models
-   presented in Figures \ref{sub_169} and \ref{sub_179}, respectively.
-   The vertical and horizontal dashed lines (in the \textit{second
-     panels} across) denote the approximate sensitivity ranges of our
-   chosen $V$, $I$, $J$ and $K$ filters.\label{inner_inc_sed}}
-\end{figure*}
-
-Figure \ref{inner_inc_sed} shows that for negligible accretion rates
-(\textit{top panels}), where the inner edge is a vertical wall, the
-total flux falls rapidly after exceeding a viewing angle of
-71$^{\circ}$. After an inclination of 71$^{\circ}$, the negligibly
-accreting system is dominated by scattered light from the central
-star. The system accreting at -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, however, maintains high flux
-levels, and thermal contributions to the SED, for inclination angles
-above 71$^{\circ}$, particularly between 1 and 3\,$\mu$m. Essentially,
-as shown by comparing Figures \ref{sub_169} and \ref{sub_179}, with
-increasing flux and subsequent dust sublimation the inner edge has
-grown vertically and become convex. As shown previously by
-\cite{tannirkulam_2007}, a vertical (or concave) inner edge will
-have strong dependence on inclination angel as the inner edge is
-obscured at lower inclinations. For the larger convex wall, the SEDs
-shown in \ref{inner_inc_sed} show that the resulting flux is less
-dependent on inclination angle.
-
-Once accretion rates reach extreme levels the inner edge is sublimated
-far from the central star. For these systems the resulting inner edge
-is both larger, in terms of scaleheight, and convex. Figure
-\ref{ext_curve} shows that the flux falls dramatically at an
-occultation angle of 71 and 64$^{\circ}$ for accretion rates of -7 and
--6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, respectively
-(\textit{left} and \textit{right panels}, respectively). For the
-accretion rate of -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ this is
-indicative of a larger opening angle (71$^{\circ}$) for the shorter
-period object, when compared to the more slowly rotating equivalent
-(56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
-  panel}). Additionally, Figure \ref{inner_inc_sed} shows that the
-total SED, has a strong thermal component and is only weakly dependent
-on inclination angle, between 1 and 3\,$\mu$m . This increase in
-opening angle with increase in rotation rate is again due to more flux
-being intercepted by a larger and closer inner wall. This interception
-of flux by the inner edge leads to a cooler and less vertically
-extended outer disc in the shorter period objects when compared to the
-slower rotating systems. Figures \ref{ext_curve} and
-\ref{inner_inc_sed} also show that, contrary to the typical accretors,
-the flux from the inner edge does not fall off as quickly with
-inclination angle after occultation. The inner edge temperatures are
-$~$1300 and $~$1200\,K for the accretion rates of -7 (\textit{left
-  panel}) and -6 (\textit{right panel})
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ respectively. This leads to
-peak emission at $~$2.2 to 2.4\,$\mu$m. Figures \ref{ext_curve} and
-\ref{inner_inc_sed} shows that even for inclinations above the
-occulation or opening angle of the disc flux from the inner edge
-persists. This is indicative of a large and convex inner edge, as is
-observed in Figures \ref{sub_179} and \ref{sub_181}. Once again these
-extreme accretion rates probably over accentuate the result but help
-illuminate the consequences of changes in the disc structure.
-
-Therefore, the longer (in wavelength) component of the final SED is
-dominated by the disc inner edge ($L_{\rm wall}$), temperature and
-shape and the outer disc scaleheight ($L_{\rm disc}$). The shape and
-location of the inner disc walls are controlled, primarily, by the
-stellar rotation rate (and stellar radius) and accretion rate (and
-stellar flux). Given that the stellar flux and radius decrease as the
-pre-MS star ages (or decreases in mass) the flux levels and the
-position of the inner edge are also weakly affected by the age of the
-central star.
-
-As shown in Figure \ref{inner_temp} the location of the inner edge and
-the corresponding temperature are correlated (differently) for typical
-and extreme accretors. This correlation is dominated by the dust
-sublimation temperature for the extreme accretors, and therefore the
-radial density profile. However, for the typical accretors the
-correlation between temperature and inner radius retains some
-dependence on the co-rotation radius (temperature is correlated with
-rotation period). This is as the sublimation temperature is not
-reached for the longer period models. Therefore, one might expect the
-resulting SEDs for typical accretors to show a correlation in shape,
-between 2 and 3\,$\mu$m, caused by the inner wall temperature changes,
-in turn caused by changes in the rotation period. Figures
-\ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} show the SEDs (and
-constituent parts as explained in Figures \ref{disc_eg_173}) for a BDD
-model at the two rotation periods. The model has a mass of
-0.04$M_{\odot}$ and an age of 1 Myr, with accretion rates of -12 and
--9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures \ref{rot_-12_1Myr}
-and \ref{rot_-9_1Myr} respectively, both at an areal coverage of
-10\%. The \textit{top panels} show the SEDs for a rotation period of
-0.5 days, and the \textit{bottom panels} the SEDs for a rotation
-period of 5 days. The \textit{first}, \textit{second}, \textit{third}
-and \textit{fourth panels} then show inclination angles of 0, 56, 64
-and 90$^{\circ}$ respectively.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_-12_1Myr.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a
-   system with a central stellar mass of $0.04M_{\odot}$, an age of
-   1Myr an accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The \textit{panels}, both \textit{top} and
-   \textit{bottom}, (from left to right) show the SEDs and constituent
-   fluxes at inclination angles of 0$^{\circ}$, 56$^{\circ}$,
-   64$^{\circ}$ and 90$^{\circ}$. The component fluxes are presented
-   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
-   for systems with a rotation period of 0.5 days and the
-   \textit{lower panels} are for a rotation period of 5 days. The
-   vertical and horizontal dashed lines (in the \textit{third panels}
-     across) denote the approximate sensitivity ranges of our chosen
-   $V$, $I$, $J$ and $K$ filters. \label{rot_-12_1Myr}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rot_-9_1Myr.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$, an age of 1Myr an accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The \textit{panels}, both \textit{top} and
-   \textit{bottom}, (from left to right) show the SEDs and constituent
-   fluxes at inclination angles of 0$^{\circ}$, 56$^{\circ}$,
-   64$^{\circ}$ and 90$^{\circ}$. The component fluxes are presented
-   as explained Figure \ref{disc_eg_173}. The \textit{top panels} are
-   for systems with a rotation period of 0.5 days and the
-   \textit{lower panels} are for a rotation period of 5
-   days.  The vertical and horizontal dashed lines (in the
-   \textit{third panels across}) denote the approximate sensitivity
-   ranges of our chosen $V$, $I$, $J$ and $K$ filters.
-   \label{rot_-9_1Myr}}
-\end{figure*}
-
-Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} show that for these
-BDD systems with typical accretion rates, the changes in SED with
-rotation period are small, apart from perhaps the face-on
-configuration. The systems in the \textit{top} and \textit{bottom
-  panels} of Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} have
-inner edge temperatures of $~$1470 \& $~$900\,K, and $~$1460 \& $~$940\,K
-respectively. This leads to different peak emissions for the slower
-and faster rotating stars, of approximately 2 and 3\,$\mu$m. However,
-as is shown by Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} very
-little resulting change is apparent in any of the SEDs apart from the
-face-on configuration. Essentially, any change in the SED shape caused
-by changing emission at the inner disc edge is smoothed out by the
-resulting interactions with the rest of the disc structure. As pre-MS
-stars age they contract and reduce in luminosity, this will lead to
-changes in the co-rotation radius and inner edge temperature. The
-models in Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} are for an
-age of 1 Myr. Therefore, changes in the SED could also be more
-apparent for older systems, with lower stellar luminosities. Figures
-\ref{comp_rot_-12} and \ref{comp_rot_-9} show the same system as
-Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr}, i.e. with accretion
-rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-respectively, but for ages of 1 and 10 Myrs. In Figures
-\ref{comp_rot_-12} and \ref{comp_rot_-9} only the total SED are shown
-for the shorter period, a solid black line, and the longer period, as
-a dashed blue line. The \textit{top panels} show the SEDs for 1 Myr
-systems and the \textit{bottom panels} the 10 Myr systems. The
-\textit{first}, \textit{second}, \textit{third} and \textit{fourth
-  panels} again show the viewing angles of 0, 56, 64 and 90$^{\circ}$
-respectively.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/comp_rot_-12.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$ and accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The SEDs are shown in \textit{each panel} for a rotation
-   period of 0.5 (solid black line) and 5 (dashed blue line) days. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the total SEDs inclination angles of 0$^{\circ}$,
-   56$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$. The \textit{top
-     panels} are for systems with an age of 1 Myr and the
-   \textit{lower panels} are for an age of 10
-   Myrs. The vertical and horizontal dashed lines (in the
-   \textit{third panels across}) denote the approximate sensitivity
-   ranges of our chosen $V$, $I$, $J$ and $K$
-   filters\label{comp_rot_-12}}
- \end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/comp_rot_-9.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$ and accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ with an an areal coverage
-   of 10\%. The SEDs are shown in \textit{each panel} for a rotation
-   period of 0.5 (solid black line) and 5 (dashed blue line) days. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the total SEDs inclination angles of 0$^{\circ}$,
-   56$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$. The \textit{top
-     panels} are for systems with an age of 1 Myr and the
-   \textit{lower panels} are for an age of 10
-   Myrs. The vertical and horizontal dashed lines (in the
-   \textit{third panels across}) denote the approximate sensitivity
-   ranges of our chosen $V$, $I$, $J$ and $K$ filters
-   \label{comp_rot_-9}}
-\end{figure*}
-
-Figures \ref{comp_rot_-12} and \ref{comp_rot_-9} show that for typical
-accretors the resulting SEDs do not, in general, change significantly
-with changing rotation rate. For the face-on configuration
-(\textit{far left panels}) the SED slope over 2 to 3\,$\mu$m is
-marginally different only. Essentially, flux redistribution from the
-highly flared outer regions of the disc and inner edge shape changes
-lead to a loss of correlations of SED shape (from 2 to 3\,$\mu$m)with
-inner edge temperature. This leads to a loss of any correlation
-between IR excess and inner edge location as predicted for the, flat,
-discs of \cite{meyer_1997}.
-
 \subsubsection{SED summary}
@@
 scatters from the expected locii in CMDs of populations of BDs.
-
-\subsubsection{Accretion Dominance-Photometry}
-\label{acc_dom_phot}
-
-Accretion flux was shown to dominate the underlying, intrinsic,
-photospheric SED for accretion rates of
-$\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$ (see Figure \ref{acc_dom} in
-Section \ref{acc_dominance}). As one would expect this leads to
-significant changes in the derived photometric magnitudes for bands
-blueward of a few microns, where the accretion and photospheric flux
-dominate. This is shown in Figure \ref{naked_acc}. Figure
-\ref{naked_acc} shows CMDs in $M_V$, $(V-I)_0$ (\textit{left panels})
-and $M_J$, $(J-K)_0$ (\textit{right panels}) of naked stars with
-accretion rates of -12, -9 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, shown as black, red and blue
-lines respectively (in \textit{all panels}). The \textit{top panels},
-then show the two rotational periods of 5 and 0.5 days, as dashed and
-solid lines respectively, for a coverage of 10\%. The \textit{bottom
-  panels}, then show the two areal spot coverages of 1 and 10\%, as
-dashed and solid lines respectively, for a rotational period of 5
-days.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/naked_acc.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the naked systems for accretion rates of -8,
-   -9 and -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, shown in
-   \textit{all panels} as blue, red and black lines respectively. The
-   model shown for \textit{all panel} has a mass of 0.04$M_{\odot}$
-   and an age of 1Myr. The \textit{top panels} are models with areal
-   spot coverages of 10\%, and the \textit{lower panels} are for
-   models with rotational periods of 5 days. The dashed and solid
-   lines then delineate the rotation periods for the \textit{top
-     panels} and coverages for the \textit{bottom panels}. The dashed
-   lines show the rotational periods of 5 days (\textit{top panels})
-   and coverages of 1\% (\textit{bottom panels}). The solid lines
-   denotes periods of 0.5 days (\textit{top panels}) and coverages of
-   10\% (\textit{bottom panels}). For accretion rates of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (black line, \textit{all
-     panels}), are representative of all models at this rate, as the
-   models are coincident within the CMD.\label{naked_acc}}
-\end{figure*}
-
-As the rotation rate increases the co-rotation radius also increases,
-as shown in Equation \ref{inner_eq}, $R_{\rm inner}\propto
-\tau^{\frac{2}{3}}$. Therefore, as Equations \ref{Lacc} and
-\ref{Tacc}, show, $L_{\rm acc}\propto 1- \frac{R_*}{R_{\rm inner}}$
-and $T_{\rm acc}\propto (\frac{L_{\rm
-    acc}}{A})^{\frac{1}{4}}$. Therefore, the temperature of the
-accretion hot spot increases as the coverage lowers and the rotational
-period increases (the latter is due to the increase in potential
-energy lost by the mass accreted). This can be seen in Figure
-\ref{acc_dom} with lower areal coverages and longer rotational periods
-leading to accretion fluxes at peaking at shorter wavelengths. The
-\textit{left panels} of Figure \ref{naked_acc} show that as the
-accretion rate increases the stars move blueward and to brighter
-magnitudes in the $M_V$, $(V-I)_0$ CMD. Furthermore, as the accretion
-spot temperature is maximised i.e. moving to longer periods of
-rotation or smaller areal coverages (solid to dashed lines), the stars
-also move blueward. For the \textit{right panels}, or $M_J$, $(J-K)_0$
-CMDs the behaviour is less intuitive. Increases in accretion rate lead
-to a slight brightening and an initial move redward, followed by a
-move blueward. This is as the lower accretion rates have lower hot
-spot temperatures, with peak wavelengths between 1 and 3\,$\mu$m
-(corresponding to temperatures of $~$2800\,K to $~$900\,K, the range of
-the BD photosphere). This leads to increases in the red flux and
-changes in the slope from $J$ to $K$. At the higher accretion rates
-the accretion flux dominates and cause the blueward shift as the slope
-becomes larger. For the highest accretion rate, in the \textit{bottom
-  right panel}, a change to a hotter spot (reduction in coverage, from
-solid to dashed lines) results in a move redward in the CMD. This can
-be understood by observing the solid blue lines in the \textit{top
-  panels} of Figure \ref{acc_dom}. Essentially, the reduction in spot
-temperature moves the accretion flux to much shorter wavelengths,
-$~$0.5 to $~$0.3\,$\mu$m, meaning that the flux in the $J$ and $K$
-bands becomes more like the photosphere, and less dominated by
-accretion. The \textit{top right panel} of Figure \ref{naked_acc} then
-shows that increases in the rotation period (from solid to dashed
-lines) shows a move blueward in the CMD, resulting in changes of the
-peak accretion flux emission from $~$0.58 to $~$0.5\,$\mu$m, meaning
-significant flux from the accretion hot spot will still fall in the
-$J$ and $K$ bands, and the slope will be increased.
-
-\subsubsection{Effect of Flaring and Obscuration on Photometry}
-\label{flare_obscure_phot}
-
-As described by \cite{walker_2004} the increased flaring, in
-BDD systems when compared to CTTS, leads to more significant changes
-in the photometric characteristics of the BDD stars with inclination
-changes. The increased flaring shown in Figures \ref{flare_-12_183}
-and \ref{flare_-7_193} results in increased obscuration of the central
-star (and inner edge) at earlier inclinations. This obscuration is
-shown to occur at lower inclination angles for objects accreting at
-higher levels, as shown in Figure \ref{flare_inc}. Figure
-\ref{flare_inc} shows that significant obscuration occurs at
-inclinations of 71 and 56$^{\circ}$ for accretion rates of -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, respectively. The changes in
-flux with inclination will clearly lead to a change in the observed
-magnitude with inclination. Figure \ref{flare_mag} shows the $M_V$ and
-$M_J$ magnitude, in the \textit{top} and \textit{bottom panels}
-respectively, as a function of inclination with the individual points
-marked as crosses. The \textit{top} and \textit{bottom panels} show
-accretion rates of -12, -9 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black, red and blue lines.
-The solid lines are for objects with rotational periods of 0.5 days
-and the dashed lines are for periods of 5 days. The \textit{inset
-  panel} within the \textit{bottom panels} shows an enlargement of the
-section of inclinations from 40 to 80$^{\circ}$. For \textit{all
-  panels} the vertical dotted lines show the inclinations for which
-significant drops in flux are observed (see Figure \ref{flare_inc})
-for -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in black and
-blue respectively.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_mag.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing magnitude change with inclination for $M_V$
-   (\textit{top panel}) and $M_J$ (\textit{bottom panel}) for the
-   models shown in Section \ref{disc_struct}, Figures \ref{no_sub_183}
-   to \ref{sub_181}. The accretion rates of -7, -9 and -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as blue, red and
-   black lines respectively. The individual points are shown as
-   crosses for all data. The dashed lines show the systems with
-   rotational periods of 5 days and the solid lines 0.5 days, in
-   \textit{all panels}. A section of the \textit{bottom panel} has
-   been enlarged and is shown as the \textit{inset panel}. Note the
-   models for -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are coincident
-   in this Figure. \textit{All panels} show the inclinations are which
-   obscuration occurs for -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as dashed black and blue
-   lines respectively. \label{flare_mag}}
-\end{figure*}
-
-Figure \ref{flare_mag} shows that the occultation starts earlier for
-the higher accretion rates, shown by the increase in both magnitudes
-(\textit{top} and \textit{bottom panels}) with inclination angle at
-around 56 and 71$^{\circ}$, as also shown in Figure
-\ref{flare_inc}. The slower rotation rates, for the highest accretion
-rates, show a generally fainter magnitude, than the faster rotating
-systems, caused by a larger disc scaleheight. For $M_J$ the fall in
-magnitude is again earlier and more significant for the larger
-accretion rates. However, at higher inclinations the systems become
-brighter again, show in the \textit{inset panel}. This brightening is
-due to the curved inner wall, as shown in Figures \ref{inner_inc_sed}
-(discussed in more detail in Section \ref{inner_edge_phot}.
-
-The change in magnitude, will also lead to a change in colour. As
-described $V$, $V-I$ and $J$, $J-K$ CMDs are ubiquitously used for
-derivation of ages and masses. The use of isochrones to derive ages
-and masses of individual stars is not reliable. However, it is
-informative to explore the changes in the CMD position of our BDD
-systems. Figure \ref{flare_VVI} shows $M_V$, $(V-I)_o$ CMDs for the
-accretion rates of -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$,
-as the \textit{left} and \textit{right panels} respectively. The
-systems are those shown in Figure \ref{flare_-12_183} and
-\ref{flare_-7_193}, at all modeled inclinations. For \textit{both
-  panels} the red dashed line, with the data points marked as crosses,
-shows the changes in CMD position with inclination of the BDD system
-at different inclinations for a 1 Myr system (with an areal coverage
-of 10\% and a $\tau$ of 5 days). The solid blue line is the matching
-isochrone for naked systems, with the naked $M_*=0.04M_{\odot}$ marked
-as a triangle. Again, for \textit{both panels} the inclinations at
-which significant drops in flux were found in Figure \ref{flare_inc}
-are noted in red text.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_VVI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_V$, $(V-I)_0$ of
-   the models in Figures \ref{flare_-12_183} and \ref{flare_-7_193}
-   (Section \ref{disc_struct}) as the \textit{left} and \textit{right
-     panels} respectively. The solid blue line are the 1Myr naked
-   isochrones at the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for the \textit{left} and
-   \textit{right panels} respectively (with an areal coverage of 10\%
-   and a $\tau$ of 5 days). The dashed red line is the BDD system with
-   $M_*=0.04M_{\odot}$ at all simulated inclinations. The triangles,
-   in both panels are the 0.04$M_{\odot}$ stars on the naked
-   isochrones and the crosses show this mass over the range of
-   inclinations with an associated disc. Figure \ref{flare_inc}
-   predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
-   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ models respectively,
-   and these are denoted by the text within the
-   figure.\label{flare_VVI}}
-\end{figure*}
-
-Figure \ref{flare_VVI} shows that as the system changes in inclination
-it leads to a significant dimming in both cases. The inclinations from
-Figure \ref{flare_inc} where significant flux is lost are shown and it
-can be seen that a significant drop in magnitude is apparent just
-before this inclination (as also shown in Figure \ref{flare_mag}). The
-models in \textit{both panels} get slightly redder as we increase to
-the obscuration angle, caused by scattered light from the disc this
-can be observed for the accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures \ref{rot_-12_1Myr}
-and \ref{comp_rot_-12}.
-
-Figure \ref{flare_JJK} shows the same data as Figure \ref{flare_VVI}
-with the same notation and symbol meanings.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_JJK.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_J$, $(J-K)_0$ of
-   the models in Figures \ref{flare_-12_183} and \ref{flare_-7_193}
-   (Section \ref{disc_struct}) as the \textit{left} and \textit{right
-     panels} respectively. The solid blue line are the 1Myr naked
-   isochrones at the accretion rates of -12 and -7
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for the \textit{left} and
-   \textit{right panels} respectively (with an areal coverage of 10\%
-   and a $\tau$ of 5 days). The dashed red line is the BDD system with
-   $M_*=0.04M_{\odot}$ at all simulated inclinations. The triangles,
-   in both panels are the 0.04$M_{\odot}$ stars on the naked
-   isochrones and the crosses show this mass over the range of
-   inclinations with an associated disc. Figure \ref{flare_inc}
-   predicts an occultation angle of 71 and 56$^{\circ}$ for the -12
-   and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ models respectively,
-   and these are denoted by the text within the
-   figure.\label{flare_JJK}}
-\end{figure*}
-
-Figure \ref{flare_JJK} again, as in Figure \ref{flare_VVI}, shows the
-BDD systems dimming with increasing inclination, with some move
-towards redder colours. There is an offset between the naked and BDD
-systems at face on inclinations, caused by the inner disc wall. This
-is particularly large for the higher accretion rate (\textit{right
-  panel}). This increase in reddening for the higher accretion rates
-is due to the much larger and curved inner disc edge as shown in
-Figure \ref{sub_179}. This curved inner edge also leads to less
-dependence of $(J-K)_0$ on inclination angle, as compared to the lower
-accretion rate.
-
-\subsubsection{Inner Edge and Photometry}
-\label{inner_edge_phot}
-
-It is clear that the scatter within a CMD, in particular for the
-$M_J$, $(J-K)_0$ CMD, is strongly affected by the emission from the
-inner edge (as shown in Figure \ref{flare_JJK}).
-
-Figure \ref{inner_VVI} shows the position in a CMD of the models from
-Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179} and
-\ref{sub_181}. The accretion rates shown are -12, -7, -9 and -6
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as the \textit{top left},
-\textit{bottom left}, \textit{top right} and \textit{bottom right
-  panels}. The solid blue line in \textit{all panels} of Figure
-\ref{inner_VVI} show the naked isochrone at 1 Myr (with an areal
-coverage of 10\% and $\tau$ of 0.5 days), at the shown accretion rate.
-The dashed red line shows the BDD system matching the naked isochrone,
-except with $M_*=0.04M_{\odot}$, at all inclination rates, with the
-datapoints marked as crosses. The blue triangles are then the naked
-stars at $M_*=0.04M_{\odot}$. The points at which the thermal direct
-flux reaching the observer drops significantly are marked in red text
-for each system, as shown in Figures \ref{typ_curve} and
-\ref{ext_curve}.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_VVI.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_V$, $(V-I)_0$ of
-   the models in Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179}
-   and \ref{sub_181} as the \textit{top left}, \textit{bottom left},
-   \textit{top right} and \textit{bottom right panels}
-   respectively. As for Figure \ref{flare_VVI}, the solid blue line is
-   the naked isochrone at 1 Myr for the corresponding accretion rate
-   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The
-   dashed red line is the BDD isochrone at the same age and accretion
-   rate. The inclination of each model at which obscuration is
-   expected to occur, from Figures \ref{typ_curve} and
-   \ref{ext_curve}, is denoted in text.\label{inner_VVI}}
-\end{figure*}
-
-Figure \ref{inner_VVI} shows for the $M_V$, $(V-I)_0$, the inclination
-increase again dims the star for these models and moves it initially
-redward, until it exceeds the expected obscuration angle, found from
-Figures \ref{typ_curve} and \ref{ext_curve}. However, as we move
-through the accretion rates from -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (\textit{top left panel}) to -6
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (\textit{bottom right panel})
-the transition from edge-on to face-on system tends to a sharper
-feature, with the reddest point at the obscuration angle. As would be
-expected from the SEDs shown in Figure \ref{inner_inc_sed}. This is
-caused by maximising the amount of the inner edge which is visible,
-whilst the stellar photosphere is still visible (which also
-contributes in these passbands).
-
-Figure \ref{inner_JJK} shows the same information as Figure
-\ref{inner_VVI} but for a $M_J$, $(J-K)_0$ CMD. Here, the BDD
-isochrones are initially much redder than their naked counterparts, as
-expected due to IR excesses caused by the disc inner edges. As the
-inclination increase for the lower accretion rates (\textit{top left}
-and \textit{bottom left panels}) the system moves first redward and
-then sharply blueward as the SED becomes dominated by scattered light
-only. As can be seen in Figure \ref{inner_inc_sed}. For the extreme
-accretion rates the wall is no longer vertical and the change in
-infrared colours is smoother up until the obscuration angle.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_JJK.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the positions within a $M_J$, $(J-K)_0$ of
-   the models in Figures \ref{sub_169}, \ref{sub_175}, \ref{sub_179}
-   and \ref{sub_181} as the \textit{top left}, \textit{bottom left},
-   \textit{top right} and \textit{bottom right panels}
-   respectively. As for Figure \ref{flare_VVI}, the solid blue line is
-   the naked isochrone at 1 Myr for the corresponding accretion rate
-   (-12, -9, -7 or -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The
-   dashed red line is the BDD isochrone at the same age and accretion
-   rate. The inclination of each model at which obscuration is
-   expected to occur, from Figures \ref{typ_curve} and
-   \ref{ext_curve}, is denoted in text.\label{inner_JJK}}
-\end{figure*}
-
-\subsection{Populations}
-\label{populations}
-
-Practically, the derivation of parameters for pre-MS populations uses
-CMDs and isochrones applied to clusters or populations of stars. In
-this section we explore the scatters of our BDD systems across our
-grid of input values within typical or commonly used CMDs and CoCoDs
-for deriving ages, masses and disc fractions.
-
-To delineate the effects of the accretion rate and circumstellar discs
-we have subdivided the grid into two groups (as discussed in Sections
-\ref{disc_struct} and \ref{sed_analysis}), those with accretion rates
-typical for higher mass CTTS objects, defined as
-$\dot{M}=$10$^{-12}M_{\odot}yr^{-1}$ (negligible) to
-$\dot{M}=$10$^{-9}M_{\odot}yr^{-1}$ and those with elevated accretion
-rates, where $\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$. For several of the
-plots in this section the magnitude and colours for the
-$M_*=0.01M_{\odot}$ systems at high inclinations become extremely
-faint and red. In some cases these objects appear slightly without the
-scale of the diagram the axes were limited in this way to be able to
-show the changes in colour and magnitude for the majority of stars
-better. The colours and magnitudes for these lowest mass stars are not
-necessarily unreliable but simply hinder the aesthetics of the plots,
-and as they are at the limits of our grid we have decided to omit them
-from some Figures by trimming the axes. Additionally, stars at the
-highest inclinations, i.e edge on disc systems, are often omitted from
-the Figures due to their extremely faint magnitudes, meaning they
-would not be practically observable.
 
@@
 
-\clearpage
-
 \begin{figure*}

### 2010-05-20 BD_disc/old.tex
minor typo change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2278 25464f21-6099-402c-b30a-640f1d40d38b

@@
 general SED shape for disc candidates, with higher mass stars showing
-a featureless continuum at $\lambda>$8.0$\mu$m with lower mass stars
+a featureless continuum at $\lambda>$8.0$\mu$m and lower mass stars
 generally showing strong silicate and PAH features at 10 and 2$\mu$m,
-indicative of mass dependent disc evolution. Whether in fact the disc
-lifetimes and therefore rate or type of involved physical processes
-are a function of stellar mass could provide another piece of evidence
+indicative of mass dependent disc evolution. If the disc lifetimes and
+therefore rate or type of involved physical processes are a function
+of stellar mass. This could provide another piece of evidence
 separating the previously assumed continuous (in mass) evolutionary
-principles of stars into a dichotomy separated by the hydrogen-burning
-mass limit, and alter the probability of forming planets in the BD
-regime.
+principles of stars. Resulting in a dichotomy separated by the
+hydrogen-burning mass limit. This would also lead to a change in the
+probability of forming planets in the BD regime, compared to CTTS.
 
@@
 \citep{1998ASPC..154.1793W}, caused by the high velocities of
-infalling matter, ~100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.
+infalling matter, $~$100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.
 
@@
 truncated, and therefore locked to the star. This magnetic truncation
-would lead to an inner wall (and inner hole) of the accretion
-disc. Evidence for an inner disc wall has been found from near-IR
-excesses from the inner rims of Herbig Ae stars, with emission peaking
-at 2-3$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
+would lead to an inner wall (and inner hole) of the accretion disc.
+Evidence for an inner disc wall has been found from near-IR excesses
+from the inner rims of Herbig Ae stars, with emission peaking at
+2-3$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
 position of this wall is affected by several factors, discussed
@@
 \end{equation}
- where $\tau$ is the stellar rotation period and $R_{\rm inner}$ is
-the inner radius. This is effectively adopting a disc-locking
-mechanism (without associated angular momentum loss), as for
-disc-locked stars, $R_{\rm mag}\approx R_{\rm co}$,
+where $\tau$ is the stellar rotation period and $R_{\rm inner}$ is the
+inner radius. This is effectively adopting a disc-locking mechanism
+(without associated angular momentum loss), as for disc-locked stars,
+$R_{\rm mag}\approx R_{\rm co}$,
 \citep{1991ApJ...370L..39K,1994ApJ...429..781S}. Therefore, for our
@@
  \caption{Figures of the albedo (\textit{top panel}), and scattering
-   (dashed line) and absorption (solid line) opacties (\textit{bottom
+   (dashed line) and absorption (solid line) opacities (\textit{bottom
      panel}) against log($\lambda$) (in $\mu$m) for our adopted dust
    population. For \textit{both panels} the vertical dashed line is
-   plotted at 10$\mu$m to higlight the silicate features.
+   plotted at 10$\mu$m to highlight the silicate features.
    \label{albedo}}
@@
 
-GOT HERE NEEDS ALOT OF RE-READING FROM HERE ON IN**
-
 \section{Result and Analysis}
@@
 
-As discussed in \cite{2004MNRAS.351..607W} the scaleheights of discs
-around CTTS stars have scaleheights at 100 AU of between $h$(100)$=$7
-to 20 AU, whereas for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and
-0.01 $M_{\odot}$ respectively). Our models adopt the same formalism
-for solving hydrostatic equilibirum and therefore, at negligible
-accreion rates, our disc scaleheights are comparable (**). As the
-accretion rate increases the flux levels of the central star increase
-and lead to heating of the disc. This in turn leads to vertical
-expansion in the disc. For our models we found that levels of vertical
-flaring increased marginally with accretion rate. Significant
-differences, more than $>$5 AU increase in $h(50)$, in the vertical
-structure where not apparent until the high accretion rates of -7 and
--6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. Figures \ref{flare_-12_183}
+As discussed in \cite{2004MNRAS.351..607W} discs around CTTS stars
+have scaleheights at 100 AU of between $h$(100)$=$7 to 20 AU, whereas
+for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and 0.01 $M_{\odot}$
+respectively). Our models adopt the same formalism for solving
+hydrostatic equilibrium and therefore, at negligible accretion rates,
+our disc scaleheights are comparable. As the accretion rate increases
+the flux levels of the central star increase and lead to heating of
+the disc. This in turn leads to vertical expansion in the disc. For
+our models we found that levels of vertical flaring increased
+marginally with accretion rate. Significant differences, more than
+$>$5 AU increase in $h(50)$, in the vertical structure were not
+apparent until the high accretion rates of -7 and -6
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. Figures \ref{flare_-12_183}
 and \ref{flare_-7_193} show the density structure ($log({\rho})$) in
-the disc from radial distances of 0 to 50 AU for an example systems
+the disc from radial distances of 0 to 50 AU for example systems
 ($M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5 and areal coverage=10\%),
-at accretion rates of -12 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, respectively.
+with accretion rates of -12 and -7
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, respectively.
 
@@
   \special{psfile="Fig/flare_-12_183.ps"
-   hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
- \caption{Figure showing the density structure ($log({\rho}$) of the
+   hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
+ \caption{Figure showing the density structure ($log({\rho}$)) of the
    BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
    coverage=10\% and accretion rate of -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
    \label{flare_-12_183}}
@@
   \special{psfile="Fig/flare_-7_193.ps"
-  hoffset=0 voffset=-50 hscale=33 vscale=33 angle=0}
-\caption{Figure showing the density structure ($log({\rho}$) of the
+  hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
+\caption{Figure showing the density structure ($log({\rho}$)) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
   coverage=10\% and accretion rate of -7
-  log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+  log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
    \label{flare_-7_193}}
@@
 $>$5 AU, as the accretion rate moves from -12 to -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. However, despite this small
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. However, despite this small
 change with high levels of accretion our grid shows scaleheights
@@
 sublimation temperature peaks at $\approx$1400K for canonical
-densities. This means that for  models where dust is sublimated at the
+densities. This means that for models where dust is sublimated the
 inner edge will have maximum temperatures of $\approx$1400K and this
@@
   panel} specifically, -9, -10 and -11 \& -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (blue, red and black dots
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black dots
 respectively). The \textit{bottom panels} show the data for models with
-accretion rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$
+accretion rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
 (blue, red and black dots respectively), which we have classed as
-extreme accretors. The \textit{right panels} show the data seperated
+extreme accretors. The \textit{right panels} show the data separated
 by age, with 1 and 10 Myrs (as crosses and triangles respectively),
@@
      panel} shows accretion rates of -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ as blue, red and black dots
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as blue, red and black dots
    respectively. In the \textit{bottom left panel} accretion rates of
-   -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ are shown as
+   -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as
    blue, red, and black dots. In addition the \textit{left panels}
-   seperates the systems by age and period. The systems with ages of 1
+   separates the systems by age and period. The systems with ages of 1
    and 10 Myrs are shown as crosses and triangles respectively. The
@@
 significant until accretion rates of around -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and increases dramatically with
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and increases dramatically with
 increasing accretion rate thereafter.  This accretion rate, -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, is also, unsurprisingly the
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, is also, unsurprisingly the
 accretion rate at which the underlying photospheric emission is
@@
 shown in Figure \ref{no_sub_183} has $\tau$=5 days and accretion
-rate=-12 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (model shown in Figure
+rate=-12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (model shown in Figure
 \ref{flare_-12_183}), with Figures \ref{sub_169} to \ref{sub_181}
 showing models with $\tau$=0.5 days and accretion rates=-12, -9, -7
-and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$. The \textit{right
+and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{right
   panels} of Figures \ref{no_sub_183} to \ref{sub_181} show the
@@
     Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate=-12
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.}
   \label{no_sub_183}
@@
     $\tau$=0.5 days and accretion rate=-12
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.}
   \label{sub_169}
@@
     $\tau$=0.5 days and accretion rate=-9
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.}
   \label{sub_175}
@@
     $\tau$=0.5 days and accretion rate=-7
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.}
   \label{sub_179}
@@
     $\tau$=0.5 days and accretion rate=-6
-    log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.}
+    log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.}
   \label{sub_181}
@@
 smooth and interpolation at the inner edge yields a temperature of
-~900K. For the shorter period model the inner edge has undergone some
-dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
-shows that the inner edge has lost dust slightly, peferentially, along
-the midplane. Again for Figure \ref{sub_169} the change in inner edge
-location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
-sublimation (and inner wall) temperature is ~1450K, for a density of
-~$2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
+$~$900K. For the shorter period model the inner edge has undergone
+some dust sublimation. The \textit{left panel} of Figure \ref{sub_169}
+shows that the inner edge has lost dust slightly, preferentially,
+along the midplane. Again for Figure \ref{sub_169} the change in inner
+edge location is small, $~0.45R_*$ ($~1.0\times 10^{-3}$AU), at the
+sublimation (and inner wall) temperature is $~$1450K, for a density of
+$~2.5\times 10^{-8}$ ($g/cm^3$) (\textit{right panel} of Figure
 \ref{sub_169}).The \textit{left panel} of Figure \ref{sub_169} shows
 that for even for a negligible accretion rate of -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, sublimation has begun to erode
-the inner edge, for the younger and faster rotating systems. Here the
-final density distribution has moved radially outward as can be seen
-by comparing the grey and colour scales in the \textit{left panel} of
-Figure \ref{sub_169}. Additionally, the inner edge has become slightly
-concave. As the flux levels of the central star increase the
-temperature of the inner edge surpasses the sublimation temperature at
-an increasing radius, destroying more of the disc an pushing the inner
-edge radially outwards. The \textit{left panel} of Figure
-\ref{sub_175} shows that for an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, increased sublimation has
-pushed the inner wall slightly farther from the star (wehn compared to
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, sublimation has begun to
+erode the inner edge, for the younger and faster rotating systems.
+Here the final density distribution has moved radially outward as can
+be seen by comparing the grey and colour scales in the \textit{left
+  panel} of Figure \ref{sub_169}. Additionally, the inner edge has
+become slightly concave. As the flux levels of the central star
+increase the temperature of the inner edge surpasses the sublimation
+temperature at an increasing radius, destroying more of the disc and
+pushing the inner edge radially outwards. The \textit{left panel} of
+Figure \ref{sub_175} shows that for an accretion rate of -9
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, increased sublimation has
+pushed the inner wall slightly farther from the star (when compared to
 Figure \ref{sub_169}), here, $\Delta R~0.52R_*$ ($~1.1\times
@@
 in excess, or equal to, the inner edge, which in this model is
-~1400K. Such hot gas inner discs interior to the dust disc have been
+$~$1400K. Such hot gas inner discs interior to the dust disc have been
 postulated through SED fitting
@@
 model in Figure \ref{sub_175} has an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$, which is the transition point
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, which is the transition point
 between our two groups of accretors, typical and extreme. Figure
 \ref{sub_175} shows that for typical accretion rates, and faster
-rotation periods (and younger ages) signicant dust sublimation is
+rotation periods (and younger ages) significant dust sublimation is
 expected to occur at the inner edge, resulting in a curved inner wall
-at around ~1400K. Increasing the accretion rate, and therefore flux
-levels, still further leads to significant erosion of the inner disc.
+at around $~$1400K. Increasing the accretion rate, and therefore flux
+levels still further leads to significant erosion of the inner disc.
 For the extreme accretors the dust sublimation at the inner edge now
@@
 accretion rates typical in outburst or episodic accretion systems, -7
-and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ respectively. The inner
-edges for these sytems are eroded radially by 7.1 and 36.1 ($R_*$)
+and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ respectively. The inner
+edges for these systems are eroded radially by 7.1 and 36.1 ($R_*$)
 respectively (0.016 and 0.080 AU, respectively), visible by comparing
-the grey and colour scales of Figure \ref{sub_179} and
-\ref{sub_181}. As this occurs the disc inner edge moves far enough
-that the density drop (with radius) occuring in the disc causing the
-sublimation temperature to fall. Consequently the disc inner edge
-becomes cooler as it can not sustain temperatures above the
-sublimation temperature. This is shown in the \textit{right panels} of
-Figures \ref{sub_179} and \ref{sub_181}, with approximate temperatures
-at the inner edge of 1370 and 1260K. In addition, the inner edge has
-become concave and, again due to changes in the underlying disc
-density distribution, much larger in scaleheight.
+the grey and colour scales of Figure \ref{sub_179} and \ref{sub_181}.
+As this occurs the disc inner edge moves far enough that the density
+drop (with radius) occurring in the disc causing the sublimation
+temperature to fall. Consequently the disc inner edge becomes cooler
+as it can not sustain temperatures above the sublimation temperature.
+This is shown in the \textit{right panels} of Figures \ref{sub_179}
+and \ref{sub_181}, with approximate temperatures at the inner edge of
+1370 and 1260K. In addition, the inner edge has become concave and,
+again due to changes in the underlying disc density distribution, much
+larger in scaleheight.
 
@@
 does not become significant until at least -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ (as discussed above).
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (as discussed above).
 
@@
 the shorter wavelength section of the SED. For our parameter space the
-temperature of the photospheres has a range of ~3000K$<T_{\rm
-  eff}$1600K, this will comprise flux contributions peaking in the
+temperature of the photospheres has a range of $~$3000K$<T_{\rm
+  eff}<$1600K, this will comprise flux contributions peaking in the
 range, 0.97 to 1.8 $\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
     acc}}$). The accretion spot temperatures, for typical accretors,
-will range from ~340$>T_{\rm acc}>$9400K, emitting in the range 0.3 to
-8.5 $\mu$m. For the extreme accretors temperatures can reach as high
-as 53,000K, provide flux to $~$0.05 $\mu$m. The second pair of
-luminosity sources are from consituent parts of the circumstellar
-disc. The inner edge, ($L_{\rm wall}$), at temperatures of ~370 to
-~1500K, or flux contributions from ~1.85 to 7.7 $\mu$m
+will range from $~$340$>T_{\rm acc}>$9400K, emitting in the range 0.3
+to 8.5 $\mu$m. For the extreme accretors temperatures which can reach
+as high as 53,000K, provide flux to $~$0.05 $\mu$m. The second pair of
+luminosity sources are from constituent parts of the circumstellar
+disc. The inner edge, ($L_{\rm wall}$), at temperatures of $~$370 to
+$~$1500K, or flux contributions from $~$1.85 to 7.7 $\mu$m
 \citep[nominally 2 to 3 $\mu$m][]{2001ApJ...560..957D}, and the outer
-disc ($L_{\rm disc}$), at temperatures of ~300K or less contributing
-flux longward of ~10 $\mu$m. As discussed in Section \ref{seds} the
-{\sc torus} radiative transfer code tags the photons before they
-reach the simulated observe in one of four ways, stellar and thermal,
-either direct or scattered. These components allow us to analyses the
+disc ($L_{\rm disc}$), at temperatures of $~$300K or less contributing
+flux longward of $~$10 $\mu$m. As discussed in Section \ref{seds} the
+{\sc torus} radiative transfer code tags the photons before they reach
+the simulated observer in one of four ways, stellar and thermal,
+either direct or scattered. These components allow us to analyse the
 contributions from the main flux contributors discussed, i.e. $L_{\rm
@@
 at 1 Myr with an areal coverage of 10\%, accretion rate of -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and rotation period of 0.5
 days. The solid black line is the total simulated SED, with the
@@
   \special{psfile="Fig/disc_eg_173.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figure showing the SED (log($\lambda \mu$m against
+   hoffset=250 voffset=-20 hscale=36 vscale=36 angle=90}
+ \caption{Figure showing the SED log($\lambda \mu$m) against
    log(flux), flux in ergs$/s/cm^2/\AA$) for $M_*=0.04M_{\odot}$ at 1
    Myr with an areal coverage of 10\%, accretion rate of -10
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$ and rotation period of 0.5
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and rotation period of 0.5
    days. The solid black line is the total simulated SED. The stellar
-   components of the flux are shown in blue and the thermal in read,
+   components of the flux are shown in blue and the thermal in red,
    with direct emission appearing as solid lines and scattered photons
@@
    show the inner edge contribution ($L_{\rm wall}$) in red and the
-   outer disc ($L_{\rm disc}$) in black. \label{disc_eg_173}}
+   outer disc ($L_{\rm disc}$) in black. The vertical and horizontal
+   dashed lines (in the \textit{lower
+     panels}) denote the approximate sensitivity ranges of our chosen
+   $V$, $I$, $J$ and $K$ filters. \label{disc_eg_173}}
 \end{figure}
@@
 luminosities dominate the SED at wavelengths shortward of
-~1$\mu$m. After this, for this model, the SED is dominated by
+$~$1$\mu$m. After this, for this model, the SED is dominated by
 contributions from the disc, at shorter wavelengths, the inner edge
@@
 central stars) will become unreliable. As discussed in Section
-\ref{inner_edge} observations of the inner edge location seperate the
+\ref{inner_edge} observations of the inner edge location separate the
 BDD systems into two groups, the typical accretors ($\dot{M}\leq$-9
@@
    with an areal coverage of 10\% and the \textit{right panels} has
-   1\%.
-   \label{acc_dom}}
+   1\%. The vertical and horizontal dashed lines (in the \textit{lower
+     panels}) denote the approximate sensitivity ranges of our chosen
+   $V$, $I$, $J$ and $K$ filters.\label{acc_dom}}
 \end{figure*}
 
-Therefore, the shorter wavelength component of the SED for extreme
-accretors is dominated by the accretion luminosity. For the typical
-accretors the intrinsic photospheric emission is important and the
-flux levels of this component are dependent on the stellar parameters
-of mass and age, through evolution of the stellar radius and
-temperature, as is well understood. In general, the bluer (short
-wavelength) components of the SEDs are therefore contrOlled by the
+As is well known the shorter wavelength component of the SED for
+extreme accretors is dominated by the accretion luminosity. For the
+typical accretors the intrinsic photospheric emission is important and
+the flux levels of this component are dependent on the stellar
+parameters of mass and age, through evolution of the stellar radius
+and temperature, as is well understood. In general, the bluer (short
+wavelength) components of the SEDs are therefore controlled by the
 stellar input parameters (mass and age) and the accretion input
@@
 thermal emission from the outer disc at wavelengths $\lambda>30\mu$m
-(indicative of temperatures of ~100K. Increasing the accretion rate
+(indicative of temperatures of $~$100K. Increasing the accretion rate
 from -12 to -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ leads to a
@@
 at edge-on inclinations the system becomes only visible in the thermal
-(~100K) disc regime, with the scattered light significantly reduced.
+($~$100K) disc regime, with the scattered light significantly reduced.
 
@@
 For typically accreting systems, where little or no dust sublimation
-has occured the inner edge remains either a vertical or slightly
-concave wall, as shown in Figures \ref{sub_169} and
-\ref{sub_175}. For these systems flux reaching an observer from
-direct thermal emission, i.e. from, in the main, the disc inner edge,
-falls rapidly with increasing viewing angle, after the maximum opening
-angle is achieved. This is shown in Figure \ref{typ_curve} where at
-the viewing angle of 77$^{\circ}$ the flux shown falls significantly,
-for both accretion rates. This opening angle is larger than found for
-the slower rotating, counter parts, as shown by Figure
-\ref{flare_inc}, where a transition in occultation occurs at
-71$^{circ}$. For the case in \ref{typ_curve} the system has the
-shorter rotation period, leading to a larger opening angle, as the
-flux from the central star does not reach the outer disc, and
-subsequently flare it. Figure \ref{typ_curve} shows that after an
-angle of 77$^{\circ}$ the flux from the inner edge falls to zero. The
-systems displayed in Figure \ref{typ_curve} have inner edge
-temperatures of ~1400K, meaning their flux emission peaks at a
-wavelength of ~2$\mu$m. The flux observed at the expected peak
-wavelength falls to zero at inclinations of 77$^{\circ}$, indicative
-of a vertical wall being obscured by the outer disc, before the limit
-of the opening angle is reached.
+has occurred the inner edge remains either a vertical or slightly
+concave wall, as shown in Figures \ref{sub_169} and \ref{sub_175}. For
+these systems flux reaching an observer from direct thermal emission,
+i.e. from, in the main, the disc inner edge, falls rapidly with
+increasing viewing angle, after the maximum opening angle is achieved.
+This is shown in Figure \ref{typ_curve} where at the viewing angle of
+77$^{\circ}$ the flux shown falls significantly, for both accretion
+rates. This opening angle is larger than found for the slower
+rotating, counter parts, as shown by Figure \ref{flare_inc}, where a
+transition in occultation occurs at 71$^{\circ}$. For the case shown
+in Figure \ref{typ_curve} the system has the shorter rotation period,
+leading to a larger opening angle, as the flux from the central star
+does not reach the outer disc, and subsequently flare it. Figure
+\ref{typ_curve} shows that after an angle of 77$^{\circ}$ the flux
+from the inner edge falls to zero. The systems displayed in Figure
+\ref{typ_curve} have inner edge temperatures of $~$1400K, meaning
+their flux emission peaks at a wavelength of $~$2$\mu$m. The flux
+observed at the expected peak wavelength falls to zero at inclinations
+of 77$^{\circ}$, indicative of a vertical wall being obscured by the
+outer disc, before the limit of the opening angle is reached.
 
@@
 levels, and thermal contributions to the SED, for inclination angles
-above 71$^{\circ}$, particularily between 1 and 3$\mu$m. Essentially,
+above 71$^{\circ}$, particularly between 1 and 3$\mu$m. Essentially,
 as shown by comparing Figures \ref{sub_169} and \ref{sub_179}, with
 increasing flux and subsequent dust sublimation the inner edge has
-grown vertically and become convex. As shown perviously by
+grown vertically and become convex. As shown previously by
 \cite{2007ApJ...661..374T}, a vertical (or concave) inner edge will
@@
 accretion rate of -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ this is
-indicative of a larger opening angle (71$^{\circ}$) for the the
-shorter period object, when compared to the more slowly rotating
-equivalent (56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
+indicative of a larger opening angle (71$^{\circ}$) for the shorter
+period object, when compared to the more slowly rotating equivalent
+(56$^{\circ}$, from Figure \ref{flare_inc}, \textit{right
   panel}). Additionally, Figure \ref{inner_inc_sed} shows that the
@@
 slower rotating systems. Figures \ref{ext_curve} and
-\ref{inner_inc_sed} also shows that, contrary to the typical
-accretors, the flux from the inner edge does not fall off as quickly
-with inclination angle after occultation. The inner edge temperatures
-are ~1300 and ~1200K for the accretion rates of -7 (\textit{left
+\ref{inner_inc_sed} also show that, contrary to the typical accretors,
+the flux from the inner edge does not fall off as quickly with
+inclination angle after occultation. The inner edge temperatures are
+$~$1300 and $~$1200K for the accretion rates of -7 (\textit{left
   panel}) and -6 (\textit{right panel})
 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ respectively. This leads to
-peak emission at ~2.2 to 2.4 $\mu$m. Figures \ref{ext_curve} and
+peak emission at $~$2.2 to 2.4 $\mu$m. Figures \ref{ext_curve} and
 \ref{inner_inc_sed} shows that even for inclinations above the
@@
 resulting SEDs for typical accretors to show a correlation in shape,
-between 2 to 3 $\mu$m, caused by the inner wall temperature changes,
+between 2 and 3 $\mu$m, caused by the inner wall temperature changes,
 in turn caused by changes in the rotation period. Figures
@@
   panels} of Figures \ref{rot_-12_1Myr} and \ref{rot_-9_1Myr} have
-inner edge temperatures of ~1470 \& ~900K, and ~1460 \& ~940K
+inner edge temperatures of $~$1470 \& $~$900K, and $~$1460 \& $~$940K
 respectively. This leads to different peak emissions for the slower
@@
 (\textit{far left panels}) the SED slope over 2 to 3$\mu$m is
-marginally different only**. Essentially, flux redistribution from the
+marginally different only. Essentially, flux redistribution from the
 highly flared outer regions of the disc and inner edge shape changes
@@
 solid to dashed lines) results in a move redward in the CMD. This can
-be understood by observing the blue solid lines in the \textit{top
+be understood by observing the solid blue lines in the \textit{top
   panels} of Figure \ref{acc_dom}. Essentially, the reduction in spot
@@
 
-Now switch to figures just showing inclination and accretion rate (not
-rotation rate).
-
-Whilst magnitudes are affected by accretion rates, ages, rotational
-periods etc, practically, for colour, colour plots the inclination is key.
-
-TYPICAL ACCRETORS
-location in the cMD is proportonal to the accretion rate and
-inclination and this sontinues into the IR colours
-
-GOT HERE***
-for typical accretors the accretion rate becomes unimportant and the
-resulting thing is just inclination for extreme accretors the
-accretion rate becomes key again
-
-First a Jh jk colo col d to show this, all ages used both 1 and 10 Myr
-
-NOT SURE IF I SHOULD LIMIT BY AGE ALL THE DISC FRACTIONS PLOTS? used 1
-and 10 myr sample as age doesn't effect the position in the col-col
-plot very much
-
-WHERE TO PUT THIS** CLEARPAGE THING**
-show that only inclination and accretion matter, age notmimportant for
-discs, disc and non disc systems separation observed in panels where
-there are no black disc systems. For extreme accretors mention fact
-that the inner edge temperature is now function of accretion rate etc.
+As shown in Figure \ref{inner_temp}, Section \ref{disc_struct}, the
+inner edge temperature for typical accretors retains some correlation
+with rotation rate. In general the more slowly rotating objects having
+cooler inner edges. For the more extreme rotators the inner edge
+location is still weakly correlated with the inner edge
+temperature. In the extreme accretors case the correlation is caused
+by the radial fall in density, and therefore dust sublimation
+temperature as the inner edge is ablated. Therefore, for the extreme
+accretors the correlation between rotational period and inner edge
+temperature is lost. The inner edge temperature is in fact correlated
+with the flux and therefore accretion rate of the system. As shown in
+Figures \ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext} (in
+Section \ref{age_mass_pop}), there is no clear correlation in CMD
+position, and $(J-K)_0$ colour with rotation rate for either typical
+or extreme accretors. In fact any scatter in these Figures
+(\ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext}) appears to be
+most strongly correlated with accretion rate and inclination.
+
+Figures \ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext} show the
+$(J-H)_0$, $(J-K)_0$ CoCoDs for typical and extreme accretors
+respectively. The dots are the simulate BDD systems for both ages (as
+position in these CoCoDs is not a strong function of age) and masses,
+and the black crosses the naked systems, again at both ages (and all
+masses), for the accretion rates matching the shown BDD data. The
+\textit{panels} of these Figures then separate the BDD systems by
+accretion rate (\textit{top left}), areal spot coverage
+(\textit{bottom left}), rotational period (\textit{top right}) and
+inclination (\textit{bottom right}). The accretion rates of -9, -10
+and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as
+blue, black and red dots respectively in the \textit{top left panel}
+of Figure \ref{disc_frac_JHJK_typ}. For Figure
+\ref{disc_frac_JHJK_ext}, the \textit{top left panel} shows accretion
+rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown
+as blue, black and red dots respectively. The \textit{bottom left
+  panels} of both Figures \ref{disc_frac_JHJK_typ} and
+\ref{disc_frac_JHJK_ext} show the systems with areal spot coverages of
+1 and 10\% as blue and red dots respectively. The \textit{top right
+  panels} of both Figures \ref{disc_frac_JHJK_typ} and
+\ref{disc_frac_JHJK_ext} show the systems with rotational periods of
+0.5 and 5 days as blue and red dots respectively. Finally, The
+\textit{bottom right panels} of both Figures \ref{disc_frac_JHJK_typ}
+and \ref{disc_frac_JHJK_ext} show the systems with inclinations of
+$\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as
+black dots and $\theta \geq 71^{\circ}$ as red dots.
+
 \clearpage
@@
    accretors, $\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$.\label{disc_frac_irac_ext}}
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.\label{disc_frac_irac_ext}}
 \end{figure*}
+
+Figure \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} show that
+the naked and BDD systems are well separated. Supporting the view that
+IRAC magnitudes are well suited for disc candidate identification. For
+the typical accretors there is a possible correlation between
+inclination and position in the $([3.6]-[4.5])_0$, $([5.8]-[8.0])_0$
+CoCoD, (\textit{bottom right panel} of Figure
+\ref{disc_frac_irac_typ}). The systems which are edge-on
+(i.e. $\theta\geq$77$^{\circ}$) appear closer in colour to the naked
+systems. In the case of extreme the accretors the separation between
+the naked and BDD systems is correlated with accretion rate for both
+CoCoDs (\textit{top panels} of Figure
+\ref{disc_frac_irac_ext}). Effectively, as the accretion rate
+increases, in general the system moves to redder colours.
+
+Figure \ref{disc_frac_irac_mips_typ} and
+\ref{disc_frac_irac_mips_ext}, show the same data as Figure
+\ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext}, in the same
+format and with the same notations. Figures
+\ref{disc_frac_irac_mips_typ} and \ref{disc_frac_irac_mips_ext} show
+CoCoDs of simulated photometry from IRAC and MIPS magnitudes. For both
+Figures the \textit{left panels} show $([3.6]-[4.5])_0$,
+$([8.0]-24)_0$ and the \textit{right panels} $([3.6]-[5.8])_0$,
+$([8.0]-24)_0$ CoCoD, where 24, is the 24$\mu$m MIPS channel.
 
@@
 \end{figure*}
+
+Figure \ref{disc_frac_mips} shows, in the \textit{inset panels}, that
+BDD and naked systems are very well separated in CoCoDs constructed
+using MIPs photometry. For the typical accretors, \textit{left panel},
+the position within the CoCoD appears strongly correlated with
+inclination only, with the edge on systems moving away from the main
+BDD locus, as expected. For the extreme accretors, \textit{right
+  panel}, significantly more structure is apparent. In this case as
+the accretion rate increases the systems move redward in both colours.
+Additionally, as the inclination increases the systems move to redder
+$(24-70)_0$ colours. This suggests, as with Figure
+\ref{disc_frac_irac_mips_ext}, for objects with extreme accretion
+rates, CoCoDs of this sort may help distinguish the characteristic
+inclination and accretion rate of the system. In practice, due to
+saturation and reddening effects and small sample sizes this may prove
+difficult. For our study this is interesting in that the fluxes for
+wavelengths longward of 24$\mu$m come from regions at temperatures of
+$~$120 K and below. This suggests that the outer disc flaring, as
+discussed in Section \ref{disc_struct}, leads to significantly
+structural changes in the outer, cooler disc, as a function of
+accretion rate. In addition, observing the separation of the naked and
+BDD systems within the CoCoDs it is clear that for systems within our
+grid, the best disc indicators are at longer wavelengths, as is well
+known from observations.
+
+Disc fractions are also derived using the $\alpha$ value
+\citep{2006AJ....131.1574L}, essentially a slope of the SED between
+two wavelengths (at wavelengths longer than the stellar flux peak).
+Figure \ref{disc_frac_alpha} shows the derived $\alpha$ values between
+3.6 and 8.0$\mu$m for our entire model grid (against an arbitrary
+model number), with dots showing BDD systems and crosses showing naked
+systems. The \textit{left} and \textit{right panels} of Figure
+\ref{disc_frac_alpha} show the typical and extreme accreting systems
+respectively. For TTS $\alpha>-$2 distinguishes between systems with
+and without discs \citep{2009arXiv0901.2603K}. As can be seen in
+Figure \ref{disc_frac_alpha} almost all the typical, and all of the
+extreme accreting BDD systems would be successfully identified using
+this criterion. Suggesting that the $\alpha$ value is a reliable disc
+indicator for BD systems. The \textit{top panels} of Figure
+\ref{disc_frac_alpha} show the alpha values separated by accretion
+rates, with -9, -10 and -11 \& -12, or -6, -7 and -8
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue, black and red
+dots respectively. The \textit{bottom panels} differentiate systems
+seen at different inclinations with $\theta \leq 48^{\circ}$ as blue
+dots, $\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
+71^{\circ}$ as red dots.
 
@@
    ($\lambda>$4$\mu$m). The \textit{left panels} show typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors
+   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors
    and the \textit{right panels} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^-1)$) accretors. The \textit{top
-     panels} seperate the systems by accretion rate in the way
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors. The \textit{top
+     panels} separate the systems by accretion rate in the way
    described in Figures \ref{disc_frac_irac_typ} and
    \ref{disc_frac_irac_ext} in the \textit{left} and \textit{right
-     panels} respectively. The \textit{bottom panels} then seperate
+     panels} respectively. The \textit{bottom panels} then separate
    the systems by inclination as described in Figure
@@
 
-CASE STUDY:
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/irac_cut_3.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure showing an observational cut used in
+   \citet{2010arXiv1004.2541M} for data of the Taurus cloud. The
+   criteria applied for BDD system selection are that of
+   \citet{2008ApJ...674..336G}. It must be noted that the naked stars
+   of $M=$0.01$M_{\odot}$ are not included in this figure as their
+   SEDs do not extend far enough into the IRAC passbands to derive
+   reliable colours. The systems are separated by age as described in
+   Figure \ref{irac_cut}. The \textit{left} and \textit{right panels}
+   again show the typical ($\dot{M} \leq$ -9
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and extreme ($\dot{M} \geq$
+   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors respectively as
+   in Figure \ref{irac_cut}.\label{irac_cut_3}}
+\end{figure*}
+
+As can be seen from Figures \ref{irac_cut}, \ref{irac_cut_2} and
+\ref{irac_cut_3} almost all of the disc systems from our simulated
+photometry would be correctly identified using these cuts. It is
+important to note that our conclusions so far have been drawn from
+differential photometric arguments, in this case we are using
+intrinsic colours and these values are extremely sensitive to changes
+in zero point and photometric calibration. Figure \ref{irac_cut} shows
+that other than a few typically accreting systems the observational
+cut of \cite{2005ApJ...631L..69L} would select all of the BDD systems
+in our grid. Figure \ref{irac_cut_2} shows that the cut of
+\cite{2008ApJ...688..362L} would miss some typical and a very small
+number of extreme accreting BDD systems. Figure \ref{irac_cut_3} shows
+only very few BDD systems will be missed. The number of BDD systems
+not identified for Figure \ref{irac_cut_2} and \ref{irac_cut_3} is
+larger than that of \ref{irac_cut}, but these Figures show that there
+is no preferential selection based on age. A comparison between Figure
+\ref{irac_cut_2} and the \textit{bottom right panel} of Figure
+\ref{disc_frac_irac_typ}, shows that all of the missed BDD systems are
+edge-on systems. Given, that extreme reddening may move naked stars
+into the BDD region selected, in general, dis fractions are usually
+quoted as lower limits. Therefore, a small number of miss-identified
+BDD system is a small effect. This allows us to conclude, that
+ubiquitously used BDD cuts used in IRAC CoCoDs are reliable when
+applied to our simulated dataset.
+
+In a future publication we will release a fitting tool to be used in
+conjunction with the online database of naked and BDD systems (for
+both photometry and SED fitting). Therefore, we will be performing
+fits to observed systems using our grid. In this work we simply pick
+an example star and highlight its position in CMD and CoCoD space,
+compared to models covering the expected range of parameters.
+\cite{2004A&A...424..603N} derive an accretion rate of -9
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for $\rho$ Ophiucus 102. For
+this object \cite{2002A&A...393..597N} find a spectral type of M6,
+$T_{\rm eff}$ of 2700K, an extinction of $A_V$=3.0, a mass of
+$M_*$0.04-0.08$M_{\odot}$ and a distance of 150pc. Photometry for
+$\rho$ Ophiucus 102 is also published in \cite{2006A&A...452..245N},
+in $J$, $H$ and $K$. Additionally, $R$ and $I$ photometry has been
+published for this object in \cite{2005AJ....130.1733W}. We have
+adjusted our model spectra in the range $M_*$=0.04-0.08$M_{\odot}$,
+with accretion rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
+(for all remaining input parameters) to the correct distance and
+reddening. Figure \ref{rho_oph_102} shows, as dots, our BDD systems
+with the parameters in the range quoted, with $\rho$ Ophiucus 102 is
+shown as a black star. The \textit{panels} of Figure \ref{rho_oph_102}
+then show example CMDs and CoCoDs. The \textit{top left panel} shows a
+$M_J$, $(J-H)_0$ CMD, the \textit{bottom left panel} a $M_R$,
+$(R-I)_0$ CMD, the \textit{top right panel} a $M_J$, $(J-K)_0$ CMD and
+finally, the \textit{bottom right panel} a $(J-K)_0$, $(J-H)_0$ CoCoD.
 
@@
 
-COPY IN THE MAIN FROM PERVIOUS PAPER REWRITE WITH BETTER EMPHASIS.
-
-\subsection{Derivation of Primary parameters}
-
-\subsection{Consequences for Accretion Rate to Stellar Mass
-  relationship}
+We have constructed a model grid of SEDs, and subsequently photometric
+magnitudes and colours, for actively accreting BDs with or without an
+associated accretion disc. We have modeled the photospheric flux from
+these BDs by adopting (and interpolating) the interior `DUSTY00'
+models of \cite{2000ApJ...542..464C} combined with the `AMES-Dusty',
+atmospheric models of \cite{2000ApJ...542..464C}. We have then assumed
+that accretion occurs from an inner edge of a magnetically truncated
+accretion disc (truncated at the co-rotation radius). The accretion
+flux is calculated using a simple blackbody emission, given the
+derivation of a characteristic spot effective temperature. SEDs were
+then produced for both naked BDs and BDD systems. For the BDD systems
+we have modeled the disc using the TORUS radiative transfer code using
+the Lucy radiative transfer algorithm and incorporating dust
+sublimation and including a treatment of vertical hydrostatic
+equilibrium (see Section \ref{model} for a discussion of the code). To
+produce a `grid' of simulated systems we have varied several input
+parameters namely: stellar mass, stellar age, stellar rotation rate,
+accretion rate, the areal coverage of the accretion stream and the
+system inclination (the disc mass was fixed). The ranges of these
+variables were selected to represent and bound typical pre-MS BD
+systems, justification is provided using evidence from observational
+studies in Section \ref{par_space} and a final list of the values of
+these variables can be found in Table \ref{par_space_table}.
+
+Accepting our assumptions, parameter ranges and radiative transfer
+code our resulting simulated dataset has allowed us to qualitatively
+explore the effects of \emph{active} (current not past accretion)
+accretion on disc structure. Furthermore through the simulation of
+observations we have explored the effects of accretion, and disc
+presence, on both the SEDs, and photometric colours and magnitudes of
+these systems.
+
+As discussed in Section \ref{disc_struct} vertical hydrostatic
+equilibrium, when applied to BDs, leads to increased flaring, when
+compared to CTTS. This has previously been explored by
+\cite{2004MNRAS.351..607W}. However, in our study we have included a
+simple treatment of accretion. This leads to increased flaring as more
+flux reaches the outer disc, and subsequently lower opening angles for
+BDD systems with higher accretion rates. Furthermore, the addition of
+dust sublimation has shown that for BDD systems the inner disc
+location, temperature and vertical size \& shape also varies with
+accretion rate. The inner edge position is correlated with temperature
+for the lower accreting models as suggested by
+\cite{1997AJ....114..288M}. For the systems with higher accretion
+rates the inner edge temperature is weakly correlated with
+temperature, mainly due to the radial fall in density and therefore
+dust sublimation temperature. The inner disc edge, initially
+prescribed as a vertical wall, then becomes concave and finally convex
+as dust sublimation is increased (with increasing flux from higher
+rates of accretion).
+
+Subsequently, the SEDs of BD systems with typical accretion rates and
+associated discs, are changed significantly from the assumed
+underlying photospheric model flux, and therefore become difficult to
+classify. In Section \ref{sed_analysis} we have shown that the BD
+photosphere becomes `swamped' or overwhelmed by the accretion flux for
+rates of $\dot{M}>$-9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The outer
+disc flaring observed in the BDD systems was shown to cause
+occultation and a subsequent, sharp, fall in flux at an inclination
+which decreases for more systems with higher accretion rates. The
+thermal direct flux emanating from the disc inner edge was found to
+fall less dramatically with inclination for the systems with a curved
+inner boundary, as expected from the work of
+\cite{2007ApJ...661..374T}.
+
+Subsequent derivation of photomertric magnitudes has allowed us to
+demonstrate that, as expected, increased accretion without disc
+presence, moves our naked systems to bluer and brighter magnitudes.
+Once a disc is added the increase in accretion flux interacts with the
+disc and does not necessarily lead to a simple motion toward brighter
+magnitudes and bluer colours. The increased flaring and obscuration
+present in BDD systems, over CTTS, leads to rapid falls in magnitude
+with inclination as an accretion (or flaring) dependent inclination.
+Furthermore, the disc inner edge leads to a shift redwards with
+increasing accretion rate as more flux is intercepted by the inner
+edge and the inner edge becomes convex and `puffed up'. For more
+typically accreting BDD systems with vertical inner edges, the motion
+in a CMD, with inclination, is more disjointed.
+
+In practice, however, most parameters for BDD systems are derived for
+populations. We have shown, in Section \ref{photometry} that
+derivation of an \emph{isochronal} (or photometric) age from our
+simulated photometry of a coeval BD sample, with typical accretion
+rates and associated circumstellar discs, would be inaccurate and
+exceedingly difficult. Indeed, the resulting photometric colours and
+magnitudes could be indicative of a more distant redenned CTTS
+population. For more extreme accretion rates the scatter, in CMD
+space, is significantly far from the pre-MS locus and as such these
+stars have little chance of being selected as BDs. As discussed in
+Section \ref{results} this does not include any effects due to past
+accretion on the evolution of the central star, which acts to
+accelerate the gravitational contraction and make the star appear
+older \citep{1999MNRAS.310..360T,1999A&A...342..480S}, further
+scattering the apparent age of a coeval population.
+
+Concordantly, \emph{isochronal} derivations of mass and therefore
+IMFs, for our simulated photometry, of a coeval population of
+accreting BDs with associated discs, would be inaccurate and
+problematic. Again caused by the changes in the SEDs as a result of
+the accretion flux and increased occultation by the larger degree of
+flaring seen in BD discs \citep[for the latter, as found
+by][]{2004MNRAS.351..607W}
+
+We have also qualitatively explored the effects of accretion and disc
+presence in our simulated dataset on disc fraction estimates. As is
+currently well known, longer wavelength bandpasses are much more
+reliable and suitable for disc identification. As shown in Section
+\ref{results} the naked and BDD disc loci were much more clearly
+separated in the CoCoD constructed using \textit{Spitzer} IRAC
+magnitudes than the shorter wavelength CIT \textit{JHK} passbands. In
+addition, we that the slope of the SED from 3.6 to 8.0$\mu$m, or
+$\alpha$ value, is an effective disc indicator. We have also
+tentatively shown that current observational cuts, when applied to our
+simulated photometry (with its associated photometric system), results
+in the reliable detection of disc candidates, for IRAC and MIPS
+colours and $\alpha$ values, and therefore a robust lower limit disc
+fraction.
+
+A further, derivative area this study impacts on, and perhaps most
+significantly, is the recent evidence for a stellar mass to accretion
+rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
+\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N}.
+This relationship has been extended into the BD mass regime in
+\cite{2006A&A...452..245N}. However, arguments based on selection and
+detection thresholds have already cast this relation into doubt
+\citep{2006MNRAS.370L..10C}. As we have shown in Section \ref{results}
+a relationship of this kind is self-reinforcing as lower mass objects
+with higher accretion rates have little chance of being correctly
+identified as such due to both the accretion flux and flared
+associated disc. Essentially, at present it is unclear how many BD
+stars are not included in this relationship due to misidentification.
+As explained in \cite{2004MNRAS.351..607W}, BD systems with a disc,
+without including accretion effects, can have the characteristics of
+higher mass CTTS stars, due to increased disc flaring from a reduced
+surface gravity in the disc. The effects of accretion at typical or
+larger rates further exacerbate the situation both spectroscopically,
+as the photospheric flux essentially becomes swamped or completely
+veiled, and photometrically as the resulting colours and magnitudes
+are significantly shifted. Therefore, for our simulated dataset a
+relationship of this sort may well be derived, if typical methods are
+used to identify BD objects with discs and derive masses, ages and
+accretion rates, even though it is not present.
+
+Finally, although inner edge locations are correlated with their
+temperature we do not find a resulting correlation with IR excess. As
+our initial inner edge locations are placed at the co-rotation radius
+one might expect a correlation between rotation rate and IR excess.
+This in turn might suggest that studies of disc presence correlation
+with slower rotation rates, exploring disc-locking, may have intrinsic
+biases. However, for our systems with dust sublimation, vertical
+flaring, accretion and view over a range of inclinations any
+correlation is not apparent. The study of \cite{1997AJ....114..288M}
+used analytical prescribed flat discs. Whether, any correlation is
+apparent for such systems using our models is studied in an upcoming
+paper where we introduce a fitting tool to be used with the model grid
+and release a further set of models with analytic disc structures, and
+an increased parameter space.
 
 \subsection{Summary}
-
-rho outer and tau inner
-
-RESULTS:
-
-AGE, MASS AND DISC FRACTION PROBLEMS:
-INCLINATION AND FLARING AS PER WALKER
-
-THEREFORE:
-CAN'T ASSERT M TO MACC RELATION
-
-LOSS OF ROATIOANL PERIOD PROPORTIONALITY WITH IR EXCESS
-
-DISC STRUCT=
-
-FLARING INCREASES AS THE FLUX INCREASES, THEREFORE OPENING ANGLE
-REDUCES
-
-INNERR EDE ORIGINAL LOCATION PROPORTIONAL TO ROTATTION RATE
-RINAL POSITION PROPORTINAL TO INNER EDGE LOCATION
-
-INNER EDGE ALSO PUFFS UP AND THEN GETS BLASTED AWAY OVER RANGE OF
-ACCRETION RATES AS THE FLUX IS INCREASED.
-
-In this section we discuss the physical structures of our resulting
-BDD systems and how these vary with our input parameters. Following
-the work of \cite{2004MNRAS.351..607W} it is clear that for BDD
-systems in vertical hydrostatic equilibrium the disc flaring leads to
-increased obscuration of the central star and probable miss
-classification. In addition, \cite{1997AJ....114..288M} predicted a
-correlation between rotation rate and infrared excess due to the
-change in position (radial) and therefore temperature of the inner
-edge.
-
-Vertical disc structure \cite{2004MNRAS.351..607W}
-
-Rotation rate correlation with infrared excess \cite{1997AJ....114..288M}
-
-The structure of this paper is as follows. In Section \ref{model} we
-outline the model used, including an explanation of our physical
-assumptions (Section \ref{physics}), a brief description of the
-radiative transfer code (Section \ref{torus}), and an explanation of
-the derivation of emergent quantities such as photometric magnitudes
-(Section \ref{derived}). The ranges of the input variables are then
-explained and, where possible, justified using observational
-constraints in Section \ref{par_space}, with the total parameter space
-covered shown in Table \ref{par_space_table}. Section
-\ref{disc_struct} then contains analysis and description of the
-resulting temperature and dust density structures of the discs. The
-consequences of these changes in disc structure on the SEDs of these
-objects is then discussed in Section \ref{sed_analysis}. Section
-\ref{photometry} then details problems caused for the derivation of
-the primary parameters age, mass and disc fractions from photometry
-and the resulting relations built on these parameters; accretion rate
-to stellar mass and rotational period to disc presence. Finally,
-conclusions are drawn, with a summary, in Section
-\ref{conclusions}.**REWRITE AT END**
+\label{conc_summary}
+
+In summary, our simulated dataset shows that for typical parameter
+ranges for BD stars and BDD systems, disc presence and accretion flux
+lead to:
+
+Difficulty deriving the following stellar parameters for a coeval
+population:
+
+\begin{itemize}
+\item{Isochronal ages}
+\item{Isochronal masses}
+\item{IMFs}
+\end{itemize}
+
+And we have shown:
+\begin{itemize}
+\item{\textit{Spitzer} IRAC magnitudes are required for reliable disc
+    identification}
+\item{An expected correlation in inner disc edge with IR excess does
+    not occur for systems with dust sublimation and vertical
+    hydrostatic equilibrium view over a range of inclinations.}
+\item{Low mass, high accretion rate systems are likely to be
+    misidentified and therefore not included in any study relating
+    $M_*\propto\dot{M}$}
+\end{itemize}
 
@@
 
-\section{Website**}
+\section{Website}
 \label{website}
+
+**THIS SECTION NEEDS TO BE SORTED**
+
+As stated throughout this paper the data presented are available from
+a web page
+\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
+  disc}. In this Appendix we briefly discuss the data included, and
+the different ways of accessing or visualising these data on the
+website.
+
+\subsection{Available Data}
+\label{web_data}
+
+The magnitudes and colours presented in this paper are avaiable both
+as individual magnitudes and as isochrones or mass tracks. Photometric
+magnitudes have also been derived for several other systems and are
+available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
+\citep{1966ARA&A...4..193J,2005ARA&A..43..293B}, \textit{Tycho} $V_t$
+and $B_t$ \citep{2000PASP..112..961B}, Bessell \textit{UBVRIJHKL}
+\citep{1988PASP..100.1134B,1998A&A...333..231B}, SDSS \textit{UGRIZ}
+\citep{1996AJ....111.1748F}, 2MASS $JHK_s$
+\citep{2003AJ....126.1090C,2006AJ....131.1163S}, MKO \textit{JHK}
+\citep{2002PASP..114..169S,2002PASP..114..180T}, UKIRT \textit{ZYJHK}
+\citep{2001MNRAS.325..563H}, IRAS 12, 25, 60 and 100 $\mu$m
+\citep{1984ApJ...278L...1N} and SCUBA \textit{450WB} and
+\textit{850WB} \citep{1999MNRAS.303..659H}. For further information on
+these magnitudes, such as the filter responses used and the adopted
+zeropoints please refer to the website.
+
+\textit{Monochromatic fluxes}
+
+In addition to the magnitudes derived for each of these bands
+monochromatic fluxes have also been derived for all bands listed
+above. These have been derived following closely the methods of
+\cite{2006ApJS..167..256R}, extended to further passbands. For details
+of the assumed SED shape, central wavelengths and bandpasses adopted
+please refer to the website. The derivations of these monochromatic
+fluxes will be detailed in a coming paper, which details a fitting
+tool associated with these data.
+
+\subsection{Navigation}
+\label{navigation}
+
+The main page contains links to download the entire dataset in several
+formats alongside files describing the format.
+
+\begin{enumerate}
+\item All SEDs ($\AA$ and ergs s$^{-1}$ cm$^{-2} \AA ^{-1}$) 
+\item All SEDs ($\mu$m and mJy)
+\item All Photometric Magnitudes for all BDD systems.
+\item All Photometric Magnitudes for all Naked systems.
+\item All Monochromatic Fluxes for all Naked systems ($\mu$m and ergs
+  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
+\item All Monochromatic Fluxes for all Naked systems ($\mu$m and mJy)
+\item All Monochromatic Fluxes for all BDD systems ($\mu$m and ergs
+  s$^{-1}$ cm$^{-2} \AA ^{-1}$)
+\item All Monochromatic Fluxes for all BDD systems ($\mu$m and mJy)
+\end{enumerate}
+
+Also included is a link to the calibration information listing all the
+filter response sources, adopted zero points, central wavelengths,
+bandwidths and assumed SED shapes (for monochromatic flux derivation).
+A brief scientific overview is also available explaining, in general
+terms, the dataset and model.
+
+\subsection{Browsing Tools}
+\label{tools}
+
+For users who wish to investigate the dataset in a more specific or
+interactive fashion two browsing tools are included.
+
+The isochrones, mass tracks and individual stars magnitudes and
+colours generated and presented in the work can be queried using the
+``Isochrone and Mass Track Tool''. This allows the user to select the
+parameters of the model required and retrieve the specific data.
+
+Secondly, an interactive tool is included allowing a user to select a
+given set of parameters and download the ``SEDs, monochromatic fluxes
+or magnitudes''. In addition this tool plots the SEDs for the Naked
+system or the three inclinations, in the case of BDD systems and
+allows users to select filters sets, whose monochromatic flux values
+will be overlaid on the displayed SEDs.
 

### 2010-05-20 BD_disc/paper.tex
minor typo change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2278 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-The resulting converged disc structures, as discussed in Section
-\ref{seds} are then used to create simulated SEDs. In this section we
-explore features in these derived SEDs and link them back to the
-physical structures within the disc discussed in Section
-\ref{disc_struct}. For analysis purposes our SEDs will comprise
-contributions from four main luminosity sources. Firstly, the
-accretion luminosity ($L_{\rm acc}$) and the intrinsic stellar
-luminosity ($L_{*}$), will effectively be combined and provide flux at
-the shorter wavelength section of the SED. For our parameter space the
-temperature of the photospheres has a range of $~$3000\,K$<T_{\rm
-  eff}<$1600\,K, this will comprise flux contributions peaking in the
-range, 0.97 to 1.8\,$\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
-    acc}}$). The accretion spot temperatures, for typical accretors,
-will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range
-0.3 to 8.5\,$\mu$m. For the extreme accretors temperatures which can
-reach as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The
-second pair of luminosity sources are from constituent parts of the
-circumstellar disc. The inner edge, ($L_{\rm wall}$), at temperatures
-of $~$370 to $~$1500\,K, or flux contributions from $~$1.85 to
-7.7\,$\mu$m \citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and
-the outer disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less
-contributing flux longward of $~$10\,$\mu$m. Disentangling the
-accretion and stellar photospheroc flux becomes difficult as $T_{\rm
-  acc} \to T_{\rm eff}$, which for an acretion rate of -9 \logmdot,
-occurs at a fractional coverages of 20 and 10\%, for rotation periods
-of 5 and 0.5 days (with $M_*=0.04M_{\odot}$ and an age of 1 Myr). As
-discussed in Section \ref{seds} the {\sc torus} radiative transfer
-code tags the photon packets before they reach the simulated observer
-in one of four ways, stellar and thermal, either direct or
-scattered. These components allow us to analyse the contributions from
-the main flux contributors discussed, i.e. $L_{\rm acc}$ and $L_*$
-equals stellar scattered or direct, with thermal emission comprising
-$L_{\rm wall}$ and $L_{\rm disc}$.
-
-Figure \ref{disc_eg_173} shows a typically accreting BDD system with
-the component photon contributions highlighted, with
-$M_*=0.04M_{\odot}$ at 1 Myr with an areal coverage of 10\%, accretion
-rate of \logmdot=$-10$ and rotation period of 0.5 days. The solid
-black line is the total simulated SED, with the stellar photons shown
-as blue lines and the thermal as red. The scattered and direct
-contributions are then shown as dashed and solid lines
-respectively. The horizontal and vertical dotted lines then show the
-approximate ranges of the flux contributions from the (from left to
-right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red) and
-$L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
-Figure \ref{disc_eg_173} show the approximate ranges of the $V$, $I$,
-$J$, and $K$ photometric bands we have adopted.
-
-\begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/disc_eg_173.ps"
-   hoffset=250 voffset=-20 hscale=36 vscale=36 angle=90}
- \caption{Figure showing the SED log($\lambda \mu$m) against
-   log(flux), flux in ergs$/s/cm^2/{\rm \AA}$) for $M_*=0.04M_{\odot}$
-   at 1 Myr with an areal coverage of 10\%, accretion rate of \logmdot
-   = $-10$ and rotation period of 0.5 days. The solid black line is
-   the total simulated SED. The stellar components of the flux are
-   shown in blue and the thermal in red, with direct emission
-   appearing as solid lines and scattered photons as dashed lines. The
-   vertical dotted bars linked by horizontal bars show the approximate
-   (log) wavelength ranges of the luminosity components. With the blue
-   lines denoting the accretion luminosity ($L_{\rm acc}$) and the
-   first (left to right) black lines showing the photospheric
-   contribution ($L_*$). The final two sets of lines show the inner
-   edge contribution ($L_{\rm wall}$) in red and the outer disc
-   ($L_{\rm disc}$) in black. The vertical and horizontal dashed lines
-   (in the \textit{lower panels}) denote the approximate sensitivity
-   ranges of our chosen $V$, $I$, $J$ and $K$
-   filters. \label{disc_eg_173}}
-\end{figure}
-
-Figure \ref{disc_eg_173} shows that the photosphere and accretion
-luminosities dominate the SED at wavelengths shortward of
-$~$1$\,\mu$m. After this, for this model, the SED is dominated by
-contributions from the disc, at shorter wavelengths, the inner edge
-and then at larger wavelengths the outer disc. As shown in Figure
-\ref{disc_eg_173} the intrinsic stellar photosphere and accretion
-luminosities overlap, in terms of peak wavelength of emission. This
-overlap essentially means that the combined stellar flux ($L_*+L_{\rm
-  acc}$) will eventually become dominated by the accretion flux, as
-one increases the accretion rate. With the features of the intrinsic
-stellar photosphere or atmosphere eventually become veiled by the
-accretion flux. This will lead to difficulties in using spectral
-features to identify BDD systems for wavelengths shorter than $~$1
-$\mu$m, and, of course, for wavelengths longer than this the SED
-becomes dominated by disc emission. Therefore, once the SED of a BDD
-system, at shorter wavelengths, becomes dominated by accretion
-luminosity spectral classification of these systems (or at least their
-central stars) will become unreliable.
-
-\subsubsection{Accretion dominance}
-\label{acc_dominance}
-
-Figure \ref{acc_dom} shows the affect of increasing the accretion
-blackbody flux (for increasing accretion rates) for a BD star,
-$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photons originating from the
-star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
-{\sc torus} we can separate these flux contributions simply by
-observing the naked star system. The panels in Figure \ref{acc_dom}
-show the flux from a naked system, with no treatment of the disc. This
-enables us to view the effect of increasing accretion rate on the
-photospheric flux in isolation. The accretion rates included in all
-panels are \logmdot = $-8$, $-9$ and $-12$ (blue, black and red lines
-respectively). The \textit{bottom panels} show the systems with a
-rotation period of 5 days and \textit{top panels} for those with a
-rotation period of 0.5 days. Given our assumption that accretion
-occurs from the co-rotation radius, decreasing the rotational period
-moves this accretion radius closer to the star, $R_{\rm inner}\propto
-\tau^{2/3}$ (see Equation \ref{inner_eq}). As the accretion radius
-moves father from the star the potential energy released by the
-accreted material is reduced (XXXX WHAT?). This effect can be seen
-when comparing the \textit{top} and \textit{bottom panels}, although
-the effect is marginal for all but the highest displayed accretion
-rates.
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the photospheric flux (log(ergs$/s/cm^2/{\rm
-     \AA}$)) against $\lambda$ (log($\mu$m)) of a Brown Dwarf with
-   $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
-   fluxes from an accretion stream at the rates of \logmdot $=-8$,
-   $-9$ and $-12$ are shown as blue, black and red lines
-   respectively. The \textit{bottom panels} show accretion for a star
-   rotating at 5 days, with the \textit{top panels} showing that of
-   0.5 days. The \textit{left panels} systems with an areal coverage
-   of 10\% and the \textit{right panels} has 1\%. The vertical and
-   horizontal dashed lines (in the \textit{lower panels}) denote the
-   approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
-   filters.\label{acc_dom}}
-\end{figure*}
-
-The \textit{left panels} show accretion streams with an areal coverage
-of 10\% and the \textit{left panels} 1\%. As the areal coverage
-reduces the effective temperature of the accretion hot spot increases,
-resulting in an increase in accretion flux, and resulting shift to
-bluer wavelengths of the peak flux. This can be seen clearly by
-comparing the \textit{left} and \textit{right panels} of Figure
-\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
-shown is Figure \ref{acc_dom} is an insight into the accretion rate at
-which the accretion blackbody flux dominates over the photospheric
-flux. Figure \ref{acc_dom} shows that as the accretion rate raises
-above \logmdot = $-9$ for systems with 1 or 10\% areal coverage, the
-accretion flux dominates the emergent SED at both periods. Therefore
-for reasonable coverages (1--10\%) and rotational periods (0.5--5 days)
-the photospheric flux is effectively swamped by accretion flux for
-accretion rates \logmdot$>-9$.
-
-As is well known the shorter wavelength component of the SED for
-extreme accretors is dominated by the accretion luminosity. For the
-typical accretors the intrinsic photospheric emission is important and
-the flux levels of this component are dependent on the stellar
-parameters of mass and age, through evolution of the stellar radius
-and temperature, as is well understood. In general, the bluer (short
-wavelength) components of the SEDs are therefore controlled by the
-stellar input parameters (mass and age) and the accretion input
-parameters (accretion rate and areal coverage, and to a lesser extent
-rotation rate).
-
-\subsubsection{Flaring and obscuration}
-\label{flare_obscure}
-
-As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
-discussed in Section \ref{disc_flaring} BDD systems under vertical
-hydrostatic equilibrium have highly flared discs. As discussed in
-\cite{walker_2004} this increased flaring (when compared to
-CTTS stars) leads to occultation at the star at lower inclination
-angles and, therefore, significant changes to the SED. Increases in
-the inclination angle, for these systems, quickly lead a significant
-proportion of the stellar flux being intercepted, and reprocessed, by
-the highly flared disc. This reprocessing will lead to a change in the
-flux levels at the shorter, bluer, wavelengths as more stellar flux is
-reprocessed and intercepted by the disc. It will also lead to
-significant changes in the flux reaching the observer from the inner
-and outer regions of the disc.
-
-Figure \ref{flare_sed_fast} shows the SEDs for a range of inclinations
-for BDD systems with two accretion rates. The BDD system has a central
-stellar mass of $0.04M_{\odot}$, an age of 1Myr, a rotation period of
-0.5 days and an areal coverage of the accretion stream of 10\%. The
-\textit{top panels} show the SEDs for a star with an accretion rate of
-\logmdot$=-12$ (the lowest in our typical
-accretion range). The \textit{bottom panels} then show SEDs for
-systems with an accretion rate of \logmdot$=-8$ (classed as an extreme
-accretor). From left to right the \textit{panels} then show the naked
-stellar flux then the fluxes from BDD systems seen at inclination
-angles of 0$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$, or face-on, the
-approximate expectation value of inclination and edge-on. For each of
-the \textit{second} to the \textit{fourth panels} the flux components
-are then shown as in Figure \ref{disc_eg_173}, i.e. the total SED
-shown as a black line, then stellar light shown in blue and thermal in
-red, with direct shown as bold and scattered as dashed lines. The
-inset graph in the \textit{bottom right} panel of Figure
-\ref{flare_sed_fast} simply shows a lower flux scale, as the flux
-levels have fallen to the lowest shown division in the main Figure.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/flare_sed_fast.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing SEDs of a system with a central stellar mass
-   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
-   and an areal coverage of the accretion stream of 10\%. The
-   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
-   to right) show the naked stellar flux (\textit{first panel}), then
-   constituent fluxes for SEDs at inclination angles of 0$^{\circ}$,
-   64$^{\circ}$ and 90$^{\circ}$. The \textit{second} to
-   \textit{fourth panels} on each line then show the total flux as a
-   black line, with the component fluxes presented as explained Figure
-   \ref{disc_eg_173}. The \textit{top panels} are for systems with an
-   accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
-   the \textit{lower panels} are for an accretion rate of -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{bottom right
-     panel} inset Figure shows an enlargement of the lower flux levels
-   of this SED. The vertical and horizontal dashed lines (in the
-   \textit{third panels} across) denote the approximate sensitivity
-   ranges of our chosen
-   $V$, $I$, $J$ and $K$ filters. \label{flare_sed_fast}}
-\end{figure*}
-
-Figure \ref{flare_sed_fast} shows, by comparing the \textit{top
-  panels} that as a disc is added to the system and the inclination of
-the BDD system is increased more stellar (and accretion flux) is
-reprocessed by the disc, for a negligibly accreting system. As one
-moves from inclinations of 0 to 64$^{\circ}$ the stellar flux has
-reduced as has the thermal component. At edge-on inclinations the
-system is only visible through scattered light, and some (slight)
-thermal emission from the outer disc at wavelengths $\lambda>30\,\mu$m
-(indicative of temperatures of $~$100\,K. Increasing the accretion rate
-from -12 to -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ leads to a
-significant increase in the naked stellar flux (compare \textit{top
-  left} and \textit{bottom left panels}). As we add a disc and
-increase the viewing inclination for the extreme accreting system
-(\textit{bottom panels}), we also lose stellar flux. In the extreme
-accretor case however the fall in flux contribution to the total SED
-from the photosphere (and accretion) is much more significant. Indeed,
-at edge-on inclinations the system becomes only visible in the thermal
-($~$100\,K) disc regime, with the scattered light significantly reduced.
-
-As shown in Section \ref{disc_struct}, and more specifically, Figures
-\ref{flare_-12_183} and \ref{flare_-7_193} as one increases the
-accretion rate for BDD systems, in general, the outer disc structure
-increases in vertical height. Effectively, the greater flux levels
-increase the temperature of the outer disc and the condition of
-vertical hydrostatic equilibrium leads to a vertical expansion. This
-vertical expansion leads to a significant change in the angle at which
-photons emitted from the stellar photosphere are intercepted by the
-outer disc. This is an extension of the effected found in
-\cite{walker_2004}, where it was found that this effect alone
-can shift the SED, and therefore colours and magnitudes, of inclined
-BDD systems to those indicative of higher mass CTTS. The actual
-changes in flux are complicated by dust sublimation and shape changes
-of the inner edge (discussed later). As the inclination of the BDD
-system is increased we see the total flux drop significantly once we
-exceed the opening angle of the BDD system. This opening angle will
-decrease with vertical scaleheight of the outer disc. Figure
-\ref{flare_inc} shows the total SEDs for the BDD system of Figures
-\ref{flare_-12_183} and \ref{flare_-7_193}, with the corresponding
-accretion rates as \textit{left} and \textit{right panels}
-respectively. The solid lines of \textit{both panels} of Figure
-\ref{flare_inc} show the total SED for each of our ten simulated
-inclinations, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84 and
-90$^{\circ}$ (with the flux decreasing with increasing
-inclination). The dashed line then highlights the inclination at which
-the flux observed drops significantly, at 71 and 56$^{\circ}$ for the
-accretion rates of -12 and -7 (or \textit{left} and \textit{right
-  panels}), respectively. Whilst this effect is probably artificially
-enhanced for such extreme accretion rates it is illustrative of the
-general trend, notwithstanding complications from inner edge shape.
-
-\subsubsection{SED summary}
-\label{sed_summary}
-
-The shape of the combined SED, $L_*+L_{\rm acc}+L_{\rm wall}+L_{\rm
-  disc}$, is controlled by the combined stellar flux (intrinsic
-stellar temperature and luminosity, and accretion stream temperature
-and luminosity), and the disc characteristics (inner edge location and
-temperature, and outer disc flaring). The stellar flux and temperature
-both increase with increasing accretion rates and reducing areal
-coverages. The stellar flux (at constant temperature) also reduces as
-a pre-MS star contracts with age (or reduces in mass). Furthermore,
-the inner disc flux increases as the inner wall becomes hotter, larger
-and more visible with increasing incident flux. The outer disc
-component also increases as the outer disc flares. The flaring and
-temperature of the disc are controlled by the stellar flux and the
-rotation rate. Finally, and most importantly, the shape of the SED
-will be dominated by the inclination of the system, especially for
-extremely flared systems. This results in the observable SED being a
-major function of the input variables, age (and mass), accretion rate
-(and areal coverage), rotation period and system inclination.
-
-As we have discussed in this Section and Section \ref{disc_struct} the
-underlying disc structures are caused by complicated interplays
-between the sublimation physics, vertical hydrostatic equilibrium and
-emission of the disc components. However, several underlying trends
-have been observed in the physical characteristics of the systems.
-Most notably the correlation, to different strengths, of the disc
-inner wall location and its resulting temperature, as found in
-\cite{meyer_1997}. However, \cite{meyer_1997} go on
-to predict a correlation of IR excess with inner edge location. Given
-that the initial inner edge location is dependent (chiefly) on the
-rotation period one might expect a correlation of rotation rate with
-IR excess. This has been shown to be unlikely due to complications in
-the inner edge location due to dust sublimation, and obscuration of
-the inner disc edge at higher inclination angles. In addition, for
-large groups of stars there is evidence for a correlation in stellar
-mass with accretion rates. Although we have shown that the observable
-SEDs of BDD systems at higher accretion rates are difficult to
-classify as such, most surveys supporting this relationship use
-photometric data. Therefore, we must examine whether these problems
-translate into the broadband photometric magnitudes.
+XXX
 

### 2010-05-20 BD_disc/temp.tex
minor typo change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2278 25464f21-6099-402c-b30a-640f1d40d38b

@@
-Data for rotation rates, from periodic variability surveys, are widely
-available for a range of different age clusters of TTS. However, fewer
-studies exist on the rotation rates of BD mass objects. To select a
-feasible range of periods for our model grid we have collated the
-results from some recent studies of BD variability. Rotation period
-data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{2008MNRAS.386..261M}, is studied in \cite{2004A&A...419..249S},
-where periods are found over the range 5.78$-$74.4 hours ($\approx$
-0.24$-$3.1 days) for BD mass objects. In some cases the periodic
-variability is irregular and assumed to come from active accretion hot
-spots on the BD surface \citep[see][for discussion of variability
-causes]{1995A&A...299...89B,2007prpl.conf..297H}. Infrared excesses
-and evidence of accretion are also found to correlate with slower
-rotating TTS, which the authors construe as evidence for a disc
-locking scenario. \cite{2004A&A...419..249S} also find a $mass\propto
-period$ relationship extending into the BD mass regime, this faster
-rotation in younger mass objects is taken as evidence for a decreasing
-effectiveness of the angular momentum removal of the disc locking
-mechanism, i.e. imperfect disc locking. In addition,
-\cite{2004A&A...419..249S} argue that when compared with data from
-younger clusters disc lifetimes can be seen to decrease with central
-object mass.
+The resulting converged disc structures, as discussed in Section
+\ref{seds} are then used to create simulated SEDs. In this section we
+explore features in these derived SEDs and link them back to the
+physical structures within the disc discussed in Section
+\ref{disc_struct}. For analysis purposes our SEDs will comprise
+contributions from four main luminosity sources. Firstly, the
+accretion luminosity ($L_{\rm acc}$) and the intrinsic stellar
+luminosity ($L_{*}$), will effectively be combined and provide flux at
+the shorter wavelength section of the SED. For our parameter space the
+temperature of the photospheres has a range of $~$3000\,K$<T_{\rm
+  eff}<$1600\,K, this will comprise flux contributions peaking in the
+range, 0.97 to 1.8\,$\mu$m ($\lambda_{\rm peak}\propto \frac{1}{T_{\rm
+    acc}}$). The accretion spot temperatures, for typical accretors,
+will range from $~$340$>T_{\rm acc}>$9400\,K, emitting in the range
+0.3 to 8.5\,$\mu$m. For the extreme accretors temperatures which can
+reach as high as 53\,000\,K, provide flux to $~$0.05\,$\mu$m. The
+second pair of luminosity sources are from constituent parts of the
+circumstellar disc. The inner edge, ($L_{\rm wall}$), at temperatures
+of $~$370 to $~$1500\,K, or flux contributions from $~$1.9 to
+7.8\,$\mu$m \citep[nominally 2 to 3\,$\mu$m][]{dullemond_2001}, and
+the outer disc ($L_{\rm disc}$), at temperatures of $~$300\,K or less
+contributing flux longward of $~$10\,$\mu$m. Disentangling the
+accretion and stellar photospheroc flux becomes difficult as $T_{\rm
+  acc} \to T_{\rm eff}$, which for an acretion rate of -9 \logmdot,
+occurs at a fractional coverages of 20 and 10\%, for rotation periods
+of 5 and 0.5 days (with $M_*=0.04M_{\odot}$ and an age of 1 Myr). As
+discussed in Section \ref{seds} the {\sc torus} radiative transfer
+code tags the photon packets before they reach the simulated observer
+in one of four ways, stellar and thermal, either direct or
+scattered. These components allow us to analyse the contributions from
+the main flux contributors discussed, i.e. $L_{\rm acc}$ and $L_*$
+equals stellar scattered or direct, with thermal emission comprising
+$L_{\rm wall}$ and $L_{\rm disc}$.
 
-\cite{2005A&A...429.1007S} study rotation period data for stars in the
-vicinity of $\epsilon$ Ori, with an assumed age of $\approx$3 Myrs
-\citep{2002A&A...384..937Z} and the ONC at an age of $\approx$2 Myrs
-\citep{2008MNRAS.386..261M}. Rotation periods, from photometric
-variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
-for BD mass stars are found. Again, \cite{2005A&A...429.1007S} find
-some BD objects with irregular variability indicative of accretion hot
-spots on the stellar surface. \cite{2005A&A...429.1007S} then analyse
-the mass-period relationship of these data in comparison with data
-from $\sigma$ Ori \citep[3 Myr,][]{2004A&A...419..249S}, NGC2264
-\citep[2 Myr,][]{2004A&A...417..557L} and then ONC \citep[1
-Myr][]{2002A&A...396..513H}. They conclude that either the $\epsilon$
-Ori sample has an age of around 2$-$3 Myrs or there is still
-significant disc locking (concluded using the slope of the mass-period
-relation). More specifically for the BD mass regime, they find
-\citep[in agreement with][]{2004A&A...419..249S} an age independent BD
-lower period limit of 2$-$4 hours, therefore at any age a fraction of
-BD stars rotate at short and constant period. Given that these objects
-should spin up as they hydrostatically contract they invoke rotational
-braking in the BD mass regime as a mechanism of removing significant
-angular momentum.
+Figure \ref{disc_eg_173} shows a typically accreting BDD system with
+the component photon contributions highlighted, with
+$M_*=0.04M_{\odot}$ at 1 Myr with an areal coverage of 10\%, accretion
+rate of \logmdot=$-10$ and rotation period of 0.5 days. The solid
+black line is the total simulated SED, with the stellar photons shown
+as blue lines and the thermal as red. The scattered and direct
+contributions are then shown as dashed and solid lines
+respectively. The horizontal and vertical dotted lines then show the
+approximate ranges of the flux contributions from the (from left to
+right), $L_{\rm acc}$ (blue), $L_*$ (black), $L_{\rm wall}$ (red) and
+$L_{\rm disc}$ (black). The vertical dashed lines at the bottom of
+Figure \ref{disc_eg_173} show the approximate ranges of the $V$, $I$,
+$J$, and $K$ photometric bands we have adopted.
 
-\cite{2003ApJ...594..971J} study the rotational periods of BD (and
-very low mass stars) in the Chameleon I region. This region is $\le$ 1
-Myrs old, and the authors find rotation periods of 2.19, 3.376 and
-3.21 days for their BD mass counterparts. Using supplementary data
-from the literature \cite{2003ApJ...594..971J} propose that a shorter
-lifetime of $\approx$5 Myrs for accretions discs around BDs is more
-probable and is inferred from the derivation of a shorter locking
-timescale. However, as discussed in the previous studies, an imperfect
-disc locking mechanisms is also hypothesised as responsible for the
-less significant loss in angular momentum out to ages of 10 Myrs. The
-data mentioned above and other datasets are summarised and discussed
-in \cite{2007prpl.conf..297H}, where a strong argument for the
-mass-period relationship can be found, shown in their Fig 6, alongside
-further support for either a shorter disc lifetime or imperfect disc
-locking mechanism for BD stars.
+\begin{figure}
+  \vspace*{174pt}
+  \special{psfile="Fig/disc_eg_173.ps"
+   hoffset=250 voffset=-20 hscale=36 vscale=36 angle=90}
+ \caption{Figure showing the SED log($\lambda \mu$m) against
+   log(flux), flux in ergs$/s/cm^2/{\rm \AA}$) for $M_*=0.04M_{\odot}$
+   at 1 Myr with an areal coverage of 10\%, accretion rate of \logmdot
+   = $-10$ and rotation period of 0.5 days. The solid black line is
+   the total simulated SED. The stellar components of the flux are
+   shown in blue and the thermal in red, with direct emission
+   appearing as solid lines and scattered photons as dashed lines. The
+   vertical dotted bars linked by horizontal bars show the approximate
+   (log) wavelength ranges of the luminosity components. With the blue
+   lines denoting the accretion luminosity ($L_{\rm acc}$) and the
+   first (left to right) black lines showing the photospheric
+   contribution ($L_*$). The final two sets of lines show the inner
+   edge contribution ($L_{\rm wall}$) in red and the outer disc
+   ($L_{\rm disc}$) in black. The vertical and horizontal dashed lines
+   (in the \textit{lower panels}) denote the approximate sensitivity
+   ranges of our chosen $V$, $I$, $J$ and $K$
+   filters. \label{disc_eg_173}}
+\end{figure}
 
-Therefore, in summary, it is currently unclear if any disc locking
-mechanisms efficiency or disc lifetimes are a function of mass, with
-an associated phase change over the TTS to BD mass limit. Rotation
-rate and disc presence data are being used to explore issue.
-Therefore, to create a set of useful models to help contextualise the
-observational constraints we must adopt a realistic, and bounding,
-range of rotation rates. For our model grid, and associated age range
-($<$10 Myrs), we have selected 0.5 and 5 days.  The lower limit is
-placed at around the approximate median for the faster rotating
-samples, providing a useful benchmark for exploring possible detection
-limits of faster rotators with discs. The longer period is set at the
-approximate edge of the slow rotating tail, providing a limiting case
-for the slower rotating, disc-locked, candidates.
+Figure \ref{disc_eg_173} shows that the photosphere and accretion
+luminosities dominate the SED at wavelengths shortward of
+$~$1$\,\mu$m. After this, for this model, the SED is dominated by
+contributions from the disc, at shorter wavelengths, the inner edge
+and then at larger wavelengths the outer disc. As shown in Figure
+\ref{disc_eg_173} the intrinsic stellar photosphere and accretion
+luminosities overlap, in terms of peak wavelength of emission. This
+overlap essentially means that the combined stellar flux ($L_*+L_{\rm
+  acc}$) will eventually become dominated by the accretion flux, as
+one increases the accretion rate. With the features of the intrinsic
+stellar photosphere or atmosphere eventually become veiled by the
+accretion flux. This will lead to difficulties in using spectral
+features to identify BDD systems for wavelengths shorter than $~$1
+$\mu$m, and, of course, for wavelengths longer than this the SED
+becomes dominated by disc emission. Therefore, once the SED of a BDD
+system, at shorter wavelengths, becomes dominated by accretion
+luminosity spectral classification of these systems (or at least their
+central stars) will become unreliable.
+
+\subsubsection{Accretion dominance}
+\label{acc_dominance}
+
+Figure \ref{acc_dom} shows the affect of increasing the accretion
+blackbody flux (for increasing accretion rates) for a BD star,
+$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photons originating from the
+star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
+{\sc torus} we can separate these flux contributions simply by
+observing the naked star system. The panels in Figure \ref{acc_dom}
+show the flux from a naked system, with no treatment of the disc. This
+enables us to view the effect of increasing accretion rate on the
+photospheric flux in isolation. The accretion rates included in all
+panels are \logmdot = $-8$, $-9$ and $-12$ (blue, black and red lines
+respectively). The \textit{bottom panels} show the systems with a
+rotation period of 5 days and \textit{top panels} for those with a
+rotation period of 0.5 days. Given our assumption that accretion
+occurs from the co-rotation radius, decreasing the rotational period
+moves this accretion radius closer to the star, $R_{\rm inner}\propto
+\tau^{2/3}$ (see Equation \ref{inner_eq}). As the accretion radius
+moves father from the star the potential energy released by the
+accreted material is reduced (XXXX WHAT?). This effect can be seen
+when comparing the \textit{top} and \textit{bottom panels}, although
+the effect is marginal for all but the highest displayed accretion
+rates.
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/acc_dom.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure showing the photospheric flux (log(ergs$/s/cm^2/{\rm
+     \AA}$)) against $\lambda$ (log($\mu$m)) of a Brown Dwarf with
+   $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
+   fluxes from an accretion stream at the rates of \logmdot $=-8$,
+   $-9$ and $-12$ are shown as blue, black and red lines
+   respectively. The \textit{bottom panels} show accretion for a star
+   rotating at 5 days, with the \textit{top panels} showing that of
+   0.5 days. The \textit{left panels} systems with an areal coverage
+   of 10\% and the \textit{right panels} has 1\%. The vertical and
+   horizontal dashed lines (in the \textit{lower panels}) denote the
+   approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
+   filters.\label{acc_dom}}
+\end{figure*}
+
+The \textit{left panels} show accretion streams with an areal coverage
+of 10\% and the \textit{left panels} 1\%. As the areal coverage
+reduces the effective temperature of the accretion hot spot increases,
+resulting in an increase in accretion flux, and resulting shift to
+bluer wavelengths of the peak flux. This can be seen clearly by
+comparing the \textit{left} and \textit{right panels} of Figure
+\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
+shown is Figure \ref{acc_dom} is an insight into the accretion rate at
+which the accretion blackbody flux dominates over the photospheric
+flux. Figure \ref{acc_dom} shows that as the accretion rate raises
+above \logmdot = $-9$ for systems with 1 or 10\% areal coverage, the
+accretion flux dominates the emergent SED at both periods. Therefore
+for reasonable coverages (1--10\%) and rotational periods (0.5--5 days)
+the photospheric flux is effectively swamped by accretion flux for
+accretion rates \logmdot$>-9$.
+
+As is well known the shorter wavelength component of the SED for
+extreme accretors is dominated by the accretion luminosity. For the
+typical accretors the intrinsic photospheric emission is important and
+the flux levels of this component are dependent on the stellar
+parameters of mass and age, through evolution of the stellar radius
+and temperature, as is well understood. In general, the bluer (short
+wavelength) components of the SEDs are therefore controlled by the
+stellar input parameters (mass and age) and the accretion input
+parameters (accretion rate and areal coverage, and to a lesser extent
+rotation rate).
+
+\subsubsection{Flaring and obscuration}
+\label{flare_obscure}
+
+As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
+discussed in Section \ref{disc_flaring} BDD systems under vertical
+hydrostatic equilibrium have highly flared discs. As discussed in
+\cite{walker_2004} this increased flaring (when compared to
+CTTS stars) leads to occultation at the star at lower inclination
+angles and, therefore, significant changes to the SED. Increases in
+the inclination angle, for these systems, quickly lead a significant
+proportion of the stellar flux being intercepted, and reprocessed, by
+the highly flared disc. This reprocessing will lead to a change in the
+flux levels at the shorter, bluer, wavelengths as more stellar flux is
+reprocessed and intercepted by the disc. It will also lead to
+significant changes in the flux reaching the observer from the inner
+and outer regions of the disc.
+
+Figure \ref{flare_sed_fast} shows the SEDs for a range of inclinations
+for BDD systems with two accretion rates. The BDD system has a central
+stellar mass of $0.04M_{\odot}$, an age of 1Myr, a rotation period of
+0.5 days and an areal coverage of the accretion stream of 10\%. The
+\textit{top panels} show the SEDs for a star with an accretion rate of
+\logmdot$=-12$ (the lowest in our typical
+accretion range). The \textit{bottom panels} then show SEDs for
+systems with an accretion rate of \logmdot$=-8$ (classed as an extreme
+accretor). From left to right the \textit{panels} then show the naked
+stellar flux then the fluxes from BDD systems seen at inclination
+angles of 0$^{\circ}$, 64$^{\circ}$ and 90$^{\circ}$, or face-on, the
+approximate expectation value of inclination and edge-on. For each of
+the \textit{second} to the \textit{fourth panels} the flux components
+are then shown as in Figure \ref{disc_eg_173}, i.e. the total SED
+shown as a black line, then stellar light shown in blue and thermal in
+red, with direct shown as bold and scattered as dashed lines. The
+inset graph in the \textit{bottom right} panel of Figure
+\ref{flare_sed_fast} simply shows a lower flux scale, as the flux
+levels have fallen to the lowest shown division in the main Figure.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/flare_sed_fast.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure showing SEDs of a system with a central stellar mass
+   of $0.04M_{\odot}$, an age of 1Myr, a rotation period of 0.5 days
+   and an areal coverage of the accretion stream of 10\%. The
+   \textit{panels}, both \textit{top} and \textit{bottom}, (from left
+   to right) show the naked stellar flux (\textit{first panel}), then
+   constituent fluxes for SEDs at inclination angles of 0$^{\circ}$,
+   64$^{\circ}$ and 90$^{\circ}$. The \textit{second} to
+   \textit{fourth panels} on each line then show the total flux as a
+   black line, with the component fluxes presented as explained Figure
+   \ref{disc_eg_173}. The \textit{top panels} are for systems with an
+   accretion rate of -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ and
+   the \textit{lower panels} are for an accretion rate of -8
+   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The \textit{bottom right
+     panel} inset Figure shows an enlargement of the lower flux levels
+   of this SED. The vertical and horizontal dashed lines (in the
+   \textit{third panels} across) denote the approximate sensitivity
+   ranges of our chosen
+   $V$, $I$, $J$ and $K$ filters. \label{flare_sed_fast}}
+\end{figure*}
+
+Figure \ref{flare_sed_fast} shows, by comparing the \textit{top
+  panels} that as a disc is added to the system and the inclination of
+the BDD system is increased more stellar (and accretion flux) is
+reprocessed by the disc, for a negligibly accreting system. As one
+moves from inclinations of 0 to 64$^{\circ}$ the stellar flux has
+reduced as has the thermal component. At edge-on inclinations the
+system is only visible through scattered light, and some (slight)
+thermal emission from the outer disc at wavelengths $\lambda>30\,\mu$m
+(indicative of temperatures of $~$100\,K. Increasing the accretion rate
+from -12 to -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ leads to a
+significant increase in the naked stellar flux (compare \textit{top
+  left} and \textit{bottom left panels}). As we add a disc and
+increase the viewing inclination for the extreme accreting system
+(\textit{bottom panels}), we also lose stellar flux. In the extreme
+accretor case however the fall in flux contribution to the total SED
+from the photosphere (and accretion) is much more significant. Indeed,
+at edge-on inclinations the system becomes only visible in the thermal
+($~$100\,K) disc regime, with the scattered light significantly reduced.
+
+As shown in Section \ref{disc_struct}, and more specifically, Figures
+\ref{flare_-12_183} and \ref{flare_-7_193} as one increases the
+accretion rate for BDD systems, in general, the outer disc structure
+increases in vertical height. Effectively, the greater flux levels
+increase the temperature of the outer disc and the condition of
+vertical hydrostatic equilibrium leads to a vertical expansion. This
+vertical expansion leads to a significant change in the angle at which
+photons emitted from the stellar photosphere are intercepted by the
+outer disc. This is an extension of the effected found in
+\cite{walker_2004}, where it was found that this effect alone
+can shift the SED, and therefore colours and magnitudes, of inclined
+BDD systems to those indicative of higher mass CTTS. The actual
+changes in flux are complicated by dust sublimation and shape changes
+of the inner edge (discussed later). As the inclination of the BDD
+system is increased we see the total flux drop significantly once we
+exceed the opening angle of the BDD system. This opening angle will
+decrease with vertical scaleheight of the outer disc. Figure
+\ref{flare_inc} shows the total SEDs for the BDD system of Figures
+\ref{flare_-12_183} and \ref{flare_-7_193}, with the corresponding
+accretion rates as \textit{left} and \textit{right panels}
+respectively. The solid lines of \textit{both panels} of Figure
+\ref{flare_inc} show the total SED for each of our ten simulated
+inclinations, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84 and
+90$^{\circ}$ (with the flux decreasing with increasing
+inclination). The dashed line then highlights the inclination at which
+the flux observed drops significantly, at 71 and 56$^{\circ}$ for the
+accretion rates of -12 and -7 (or \textit{left} and \textit{right
+  panels}), respectively. Whilst this effect is probably artificially
+enhanced for such extreme accretion rates it is illustrative of the
+general trend, notwithstanding complications from inner edge shape.
+
+\subsubsection{SED summary}
+\label{sed_summary}
+
+The shape of the combined SED, $L_*+L_{\rm acc}+L_{\rm wall}+L_{\rm
+  disc}$, is controlled by the combined stellar flux (intrinsic
+stellar temperature and luminosity, and accretion stream temperature
+and luminosity), and the disc characteristics (inner edge location and
+temperature, and outer disc flaring). The stellar flux and temperature
+both increase with increasing accretion rates and reducing areal
+coverages. The stellar flux (at constant temperature) also reduces as
+a pre-MS star contracts with age (or reduces in mass). Furthermore,
+the inner disc flux increases as the inner wall becomes hotter, larger
+and more visible with increasing incident flux. The outer disc
+component also increases as the outer disc flares. The flaring and
+temperature of the disc are controlled by the stellar flux and the
+rotation rate. Finally, and most importantly, the shape of the SED
+will be dominated by the inclination of the system, especially for
+extremely flared systems. This results in the observable SED being a
+major function of the input variables, age (and mass), accretion rate
+(and areal coverage), rotation period and system inclination.
+
+As we have discussed in this Section and Section \ref{disc_struct} the
+underlying disc structures are caused by complicated interplays
+between the sublimation physics, vertical hydrostatic equilibrium and
+emission of the disc components. However, several underlying trends
+have been observed in the physical characteristics of the systems.
+Most notably the correlation, to different strengths, of the disc
+inner wall location and its resulting temperature, as found in
+\cite{meyer_1997}. However, \cite{meyer_1997} go on
+to predict a correlation of IR excess with inner edge location. Given
+that the initial inner edge location is dependent (chiefly) on the
+rotation period one might expect a correlation of rotation rate with
+IR excess. This has been shown to be unlikely due to complications in
+the inner edge location due to dust sublimation, and obscuration of
+the inner disc edge at higher inclination angles. In addition, for
+large groups of stars there is evidence for a correlation in stellar
+mass with accretion rates. Although we have shown that the observable
+SEDs of BDD systems at higher accretion rates are difficult to
+classify as such, most surveys supporting this relationship use
+photometric data. Therefore, we must examine whether these problems
+translate into the broadband photometric magnitudes.

### 2010-05-21 BD_disc/paper.tex
working copy currently doing results
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2279 25464f21-6099-402c-b30a-640f1d40d38b

@@
    hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
- \caption{Figures of the albedo (\textit{top panel}), and scattering
-   (dashed line) and absorption (solid line) opacities (\textit{bottom
-     panel}) against log($\lambda$) (in $\mu$m) for our adopted dust
-   population. For \textit{both panels} the vertical dashed line is
+ \caption{Figures of the albedo (top panel), and scattering
+   (dashed line) and absorption (solid line) opacities (bottom
+     panel) against log($\lambda$) (in $\mu$m) for our adopted dust
+   population. For both panels the vertical dashed line is
    plotted at 10\,$\mu$m to highlight the silicate features.
@@
 
+XXX NJM REWORD THIS
+
 In this Section we first discuss the physical structure, both density
@@
 across our parameter space. Then we discuss the resulting simulated
-SEDs for these BDD systems (Section \ref{sed_analysis}). Finally, we
+SEDs for these BDD systems (Section \ref{observables}). Finally, we
 produce simulated photometric observations (Section \ref{photometry}).
@@
 increase in flaring for very high accretion levels on SEDs and
-photometric magnitudes are discussed in Sections \ref{sed_analysis}
-and \ref{photometry}, respectively.
+photometric magnitudes are discussed in Sections \ref{observables}
+and \ref{isochrones}, respectively.
 
@@
 final inner edge location ($R_{\rm inner}$, $R_*$) against the
-temperature of the inner wall ($T_{\rm inner}$, K). The \textit{left
-  panel} shows the systems designated as typical accretors and the
-\textit{right panel} those with extreme accretion rates.  For
-\textit{both panels} the systems with rotation periods of 0.5 and 5
+temperature of the inner wall ($T_{\rm inner}$, K). The left
+  panel shows the systems designated as typical accretors and the
+right panel those with extreme accretion rates.  For
+both panels the systems with rotation periods of 0.5 and 5
 days are plotted in red and blue respectively. Those systems where the
@@
        inner}$, $R_*$). The typical accretors are shown in the
-     \textit{left panel} and the extreme accretors in the
-     \textit{right panel} (see text for explanation). In \textit{both
-       panels} separate the systems by period, with those systems with
+     left panel and the extreme accretors in the
+     right panel (see text for explanation). In both
+       panels separate the systems by period, with those systems with
      rotation periods of 0.5 and 5 days shown as red and blue symbols
@@
 
-The \textit{left panel} of Figure \ref{inner_temp} shows that, taken
+The left panel of Figure \ref{inner_temp} shows that, taken
 as a whole, our models with typical accretion rates show a clear
@@
 disc wall shape, inclination and flaring effects. This is discussed in
-more detail in Section \ref{photometry}.
+more detail in Section \ref{isochrones}.
 
@@
 scaleheight, leading to the `puffed up' inner rim predicted by
-\cite{dullenmond_2001}. This effect is illustrated in
+\cite{dullemond_2001}. This effect is illustrated in
 Figure~\ref{no_sub_183}, a model in which there is negligible dust
@@
 
-\subsection{SEDs}
-\label{sed_analysis}
-
-XXX
-
-\subsection{Photometry}
-\label{photometry}
+\subsection{Observable Consequences of Disc Structure and Accretion}
+\label{observables}
+
+The resulting converged disc structures, as discussed in Section
+\ref{seds} are then used to create simulated SEDs and dervie broadband
+photometric magnitudes. In this section we discuss the effects of
+accretion and disc presence on the simulated observations.
+
+\subsubsection{Accretion dominance}
+\label{acc_dominance}
+
+Disentangling the accretion and stellar photospheric flux, in order to
+derive accretion rates, becomes difficult as $T_{\rm acc} \to T_{\rm
+  eff}$, which for an acretion rate of -9 \logmdot, occurs at a
+fractional coverages of 20 and 10\%, for rotation periods of 5 and 0.5
+days (with $M_*=0.04M_{\odot}$ and an age of 1 Myr). Additionally,
+higher accretion rates can produce enough flux to `veil' the
+underlying photospheric features, and significantly change the peak
+flux levels. Heavy veiling of atomic bands is well observed in CTTS
+systems \citep{kenyon_1995}.
+
+Figure \ref{acc_dom} shows the affect of increasing the accretion
+blackbody flux (for increasing accretion rates) for a BD star,
+$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photons originating from the
+star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
+{\sc torus} we can separate these flux contributions simply by
+observing the naked star system. The panels in Figure \ref{acc_dom}
+show the flux from a naked system, with no treatment of the disc. This
+enables us to view the effect of increasing accretion rate on the
+photospheric flux in isolation. The accretion rates included in all
+panels are \logmdot = $-8$, $-9$ and $-12$ (blue, black and red lines
+respectively). The bottom panels show the systems with a
+rotation period of 5 days and top panels for those with a
+rotation period of 0.5 days. Given our assumption that accretion
+occurs from the co-rotation radius, decreasing the rotational period
+moves this accretion radius closer to the star, $R_{\rm inner}\propto
+\tau^{2/3}$ (see Equation \ref{inner_eq}). As the accretion radius
+moves father from the star the potential energy released by the
+accreted material is increased. This effect can be seen
+when comparing the top and bottom panels, although
+the effect is marginal for all but the highest displayed accretion
+rates.
+
+\begin{figure*}
+  \vspace*{348pt}
+  \special{psfile="Fig/acc_dom.ps"
+   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+ \caption{Figure showing the photospheric flux (log(ergs$/s/cm^2/{\rm
+     \AA}$)) against $\lambda$ (log($\mu$m)) of a Brown Dwarf with
+   $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
+   fluxes from an accretion stream at the rates of \logmdot $=-8$,
+   $-9$ and $-12$ are shown as blue, black and red lines
+   respectively. The bottom panels show accretion for a star
+   rotating at 5 days, with the top panels showing that of
+   0.5 days. The left panels systems with an areal coverage
+   of 10\% and the right panels has 1\%. The vertical and
+   horizontal dashed lines (in the lower panels) denote the
+   approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
+   filters.\label{acc_dom}}
+\end{figure*}
+
+The left panels show accretion streams with an areal coverage of 10\%
+and the left panels 1\%. As the areal coverage reduces the effective
+temperature of the accretion hot spot increases, resulting in an
+increase in accretion flux, and resulting shift to bluer wavelengths
+of the peak flux. This can be seen clearly by comparing the left and
+right panels of Figure \ref{acc_dom}. Perhaps the most important,
+albeit qualitative, result shown is Figure \ref{acc_dom} is an insight
+into the accretion rate at which the accretion blackbody flux
+dominates over the photospheric flux. Figure \ref{acc_dom} shows that
+as the accretion rate raises above \logmdot = $-9$ for systems with 1
+or 10\% areal coverage, the accretion flux dominates the emergent SED
+at both periods. Effectively, the spectroscopic features of the
+photosphere are veiled by the additional continuum accretion
+flux. Therefore for reasonable coverages (1--10\%) and rotational
+periods (0.5--5 days) the photospheric flux is effectively veiled by
+accretion flux for accretion rates \logmdot$>-9$. It is also clear
+from Figure \ref{acc_dom} that the magnitude becomes brighter and the
+colour bluer (in terms of optical photometry) with increasing
+accretion rates as expected \citep{gullbring_1998}.
+
+\subsubsection{Flaring and the Inner Edge}
+\label{flare_inner_sec}
+
+As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
+discussed in Section \ref{disc_flaring} BDD systems under vertical
+hydrostatic equilibrium have highly flared discs. As discussed in
+\cite{walker_2004} this increased flaring (when compared to CTTS
+stars) leads to occultation at the star at lower inclination angles
+and, therefore, significant changes to the SED. Increases in the
+inclination angle, for these systems, quickly lead a significant
+proportion of the stellar flux being intercepted, and reprocessed, by
+the highly flared disc. This reprocessing will lead to a change in the
+flux levels at the shorter, bluer, wavelengths as more stellar flux is
+intercepted by the disc. It will also lead to significant changes in
+the flux reaching the observer from the inner and outer regions of the
+disc as the system approaches edge on. Also, as discussed in
+Section \ref{disc_struct} the addition of dust sublimation leads to a
+change in the shape of the inner edge, where the temperature is
+sufficient. Figures \ref{no_sub_183} to \ref{sub_179} \ref{sub_181}
+show a range in inner edge shapes, from flat walls through concave to
+convex curves, caused by the radial density profile of the disc and
+the dependence of the sublimation temperature on density. This change
+in shape, as noted for Herbig Ae stars by \cite{tannirkulam_2007}
+XX CHECK FOR A CTTS REFERENCESXXX, will lead to changes in the
+characteristics of the SED, or derived IR excess, with inclination
+angle \citep{tannirkulam_2007}, for close to face on viewing
+angles.
+
+\ref{flare_inner} shows the total SEDs for the BDD system of Figures
+\ref{flare_-12_183} and \ref{flare_-7_193} as the top and bottom
+panels respectively. The left panels show the flux over all the ten
+inclinations (see Table \ref{par_space_table}), with the dashed line
+showing the inclination at which a sharp fall in flux is seen. This
+inclination will be the angle at which the star and inner disc becomes
+obscured by the flared outer disc. These inclinations are 71$^{\circ}$
+and 56$^{\circ}$ for \logmdot=-12 and -7 respectively. This
+effectively means that for higher accretion rates a more significant
+fraction of the stars, in a given population, may have flux below a
+threshold detection limit. The right panel of Figure \ref{flare_inner}
+shows the angles of 0, 27, 39, and 48 $^{\circ}$, close to face
+on. Comparing the top and bottom panel show that flux levels for the
+higher accretion rate, with the larger and curved inner edge, vary
+more distinctly with inclination angle than the systems with a
+vertical wall. These trends although demonstrated for one subset are
+apparent throughout the grid, i.e.e for each mass and age. Whilst this
+effect is probably artificially enhanced for such extreme accretion
+rates it is illustrative of the general trend, notwithstanding
+complications from inner edge shape.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inner.ps}
+  \caption{Figure showing both total SEDs of the systems shown in
+    Figure \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
+    bottom panels respectively. The left panel shows all inclinations
+    (see Table \ref{par_space_table}), with the obscuration angle
+    shown as a dashed line, 71$^{\circ}$ and 56$^{\circ}$ for
+    \logmdot=-12 and -7 respectively. The right panels show only the
+    inclinations close to face on, i.e. 0, 27, 39, and 48 $^{\circ}$,
+    with a clear dependence on inclination of the flux levels for the
+    curved inner wall (lower right panel).\label{flare_inner}}
+\end{figure*}
+
+HERER****
+ write caption
+GOT HERE*** TUNE WHAT NEED FROM THIS FIGURE***
+
+SELECT THE CORRECT MODELS
+
+POINTS TO MAKE, MJ (and MV) brighter for high accretion, tail off
+starts earlier for high accretion
+
+J-K delta larger over short inclinations than low accretors 0.05 0.1
+factor two larger in magnitude!!! factor ten in flux?
+
+The changes in flux with inclination will clearly lead to changes in
+the observed magnitudes with inclination. Figure \ref{flare_inner_mag}
+shows the $M_V$ and $M_J$ magnitude, in the \textit{top} and
+\textit{bottom panels} respectively, as a function of inclination with
+the individual points marked as crosses. The \textit{top} and
+\textit{bottom panels} show accretion rates of -12, -9 and -7
+log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black, red and blue lines.
+The solid lines are for objects with rotational periods of 0.5 days
+and the dashed lines are for periods of 5 days. The \textit{inset
+  panel} within the \textit{bottom panels} shows an enlargement of the
+section of inclinations from 40 to 80$^{\circ}$. For \textit{all
+  panels} the vertical dotted lines show the inclinations for which
+significant drops in flux are observed (see Figure \ref{flare_inc})
+for -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in black and
+blue respectively.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inner_mag.ps}
+  \caption{Figure showing both XXX.\label{flare_inner_mag}}
+\end{figure*}
+
+XXXSUMMARISE THISXXX
+
+\subsection{Parameter derivation}
+\label{isochrones}
+
+XXXADD LINE ABOUT OBJECT
 
@@
 the broadband photometry of varying our input parameters. In this
-Section we, in particular, relate the discussed features of disc
-structures (\ref{disc_struct}) and the resulting simulated SEDs
-(\ref{sed_analysis}) in terms of the derived photometry, in Section
-\ref{indv_phot}. Furthermore, we explore the consequences of our model
-grid on the derivation of the primary parameters of age, mass and disc
-fractions, from populations, in Section \ref{populations}. This in
-turn leads to highlighting selection effects with, for instance, the
-mass to accretion rate relation.
-
-\subsection{Effects of Disc Presence and Accretion on Photometry}
-\label{indv_phot}
+Section we explore the consequences of our model grid on the
+derivation of the primary parameters of age, mass and disc fractions,
+from populations. This in turn leads to highlighting selection effects
+with, for instance, the mass to accretion rate relation.
+
+\subsubsection{Mass and Age Derivation}
+\label{mass_age}
 
@@
 derivation \cite[see references and discussions in][ and Section
-\ref{derived}]{mayne_2007,mayne_2008}.
+\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
 
@@
 derivation of single star parameters is completely unreliable
-\citep[see discussion in][]{mayne_2008}. However, exploring
-the changes in the CMDs of single objects will elucidate the causes of
-scatters from the expected locii in CMDs of populations of BDs.
-
-\subsubsection{Age and Mass Derivations}
-\label{age_mass_pop}
-
-As discussed in Section \ref{indv_phot} for the derivation of the
-primary parameters of age and mass the CMDs most suitable and commonly
-used are $M_V$, $(V-I)_0$ and $M_J$, $(J-K)_0$. Furthermore, these
-CMDs are indicative of the associated CMDs, for instance $M_R$,
-$(R-I)_0$ or $M_J$, $(J-H)_0$ etc. Also as discussed in
-\cite{mayne_2008} the use of isochrones for the derivation of
-masses and ages for individual pre-MS stars is unreliable at
-best. Practically, therefore, median ages are derived from
-populations. Subsequently, derived masses are still unreliable but at
-least based on a consistent age. This problem is being addressed by
-Bell et al (in prep), where $K$ band photometry and known eclipsing
-binaries are being used to refine pre-MS isochrones. In this section
-we plot the data for our 1 Myr systems only and explore the resulting
-scatters caused by the disc presence and accretion luminosity.
-
-Figures \ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext} shows
-four CMDs in $M_V$, $(V-I)_0$ for the typical and extreme accretors
-respectively. For the typical accretors, Figure
-\ref{spread_opt_VVI_typ}, shows the isochrones constructed for naked
-systems at 1 Myr, for accretion rates of -12 and -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as the solid and dashed black
-lines. Whereas in Figure \ref{spread_opt_VVI_ext} the naked isochrones
-of -9 and -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as dashed and
-solid black lines respectively. The \textit{top left panel}, in both
-Figures (\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}) shows
-a pre-MS isochrone at 1 Myr from \cite{siess_2000} adjusted
-to a distance of 250pc and an extinction of $A_V=2$ mag, simulating a
-background population of CTTS stars. The dots in \textit{each panel},
-for both Figures (\ref{spread_opt_VVI_typ} and
-\ref{spread_opt_VVI_ext}) are the 1 Myr BDD systems for all
-inclinations, rotational periods, areal spot coverages and the
-individual accretion rates within the accretion type classes. The
-\textit{panels} of the Figures \ref{spread_opt_VVI_typ} and
-\ref{spread_opt_VVI_ext} then separate the systems by the input
-variables. The \textit{top left panel} shows either the accretion
-rates of -9, -10 and -11 \& -12 or -6, -7 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in Figures
-\ref{spread_opt_VVI_typ} and \ref{spread_opt_VVI_ext}
-respectively. These three classes are then shown as blue, black and
-red dots respectively. The \textit{bottom left panels} then show those
-systems with areal coverages of 1 and 10\% as blue and red dots
-respectively. The \textit{top right panels} then shows systems with
-rotational periods of 0.5 and 5 days as blue and red dots
-respectively. Finally, the \textit{bottom right panels} show the
-systems separated by inclination. These groups are $\theta \leq
-48^{\circ}$ as blue dots (classed as face-on systems), $\theta> 56$ \&
-$64^{\circ}$ (classed as the expected systems, as the expectation
-value of $cos(\theta)=60^{\circ}$) as black dots and $\theta \geq
-71^{\circ}$ (classed as edge-on systems) as red dots. Figure
-\ref{spread_opt_RRI_typ} also shows the same data as for Figure
-\ref{spread_opt_VVI_typ}, but for $M_R$, $(R-I)_0$ CMDs.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_VVI_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
-   accretors ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The black solid and dashed
-   lines in \textit{all panels} are the naked star isochrones for
-   accretion rates of -12 and -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-   respectively. The \textit{top left} only shows the 1 Myr pre-MS
-   isochrone of \citet{siess_2000} adjusted to a distance
-   modulus of 7 and an extinction of $A_V=2$, simulating a reddened
-   background population. The dots are the data for typical accretors
-   for models at 1 Myr. The data are then separated by input
-   variables, in the \textit{panels}. The \textit{top left panel}
-   shows three accretion classes, -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as blue, black and red dots
-   respectively (the lowest two accretion rates are grouped as they
-   are coincident). The \textit{top right panel} shows the rotational
-   periods of 0.5 and 5 days as blue and red dots respectively. The
-   \textit{bottom left panel} shows the areal spot coverages of 1 and
-   10\% as blue and red dots resepctively. The \textit{bottom right
-     panel} shows three groups of inclinations, $\theta \leq$
-   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
-   71$^{\circ}$ , as blue, red and black dots
-   respectively.\label{spread_opt_VVI_typ}}
-\end{figure*}
-
-As can be seen in Figure \ref{spread_opt_VVI_typ} current accretion in
-a star and disc systems, for rates typical in the BD mass regime,
-creates a scatter in our simulated photometry indicative of a much
-larger isochronal age spread than 10 Myr. Indeed, for many BDD systems
-even at nominal accretion rates of -11 or -12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, for our simulations, the
-colours of these stars move significantly blueward of the expected BD
-locus in a $M_V$, $(V-I)_0$ CMD. As the dots in Figure
-\ref{spread_opt_VVI_typ} are the simulated photometry of BDD systems
-over a range of typical input parameters (see Section
+\citep[see discussion in][]{2008MNRAS.386..261M}. Practically,
+therefore, median ages are derived from populations. Subsequently,
+derived masses are still unreliable but at least based on a consistent
+age. This problem is being addressed by Bell et al (in prep), where
+$K$ band photometry and known eclipsing binaries are being used to
+refine pre-MS isochrones. In this section we plot the data for our 1
+Myr systems only and explore the resulting scatters caused by the disc
+presence and accretion luminosity.
+
+As can be seen in Figures \ref{age_mass_VVI} and \ref{age_mass_JHK}
+current accretion in a star and disc systems, for rates typical in the
+BD mass regime, creates a scatter in our simulated photometry
+indicative of a much larger isochronal age spread than 10 Myr. Indeed,
+for many BDD systems even at nominal accretion rates of -11 or -12
+\logmdot, for our simulations, the colours of these stars move
+significantly blueward of the expected BD locus in a $M_V$, $(V-I)_0$
+CMD. As the dots in these Figures are the simulated photometry of BDD
+systems over a range of typical input parameters (see Section
 \ref{par_space}), an observed coeval 1 Myr population could reasonably
@@
 ONC). Furthermore, for the higher accretion rates of -9 or -10
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the movement of the star
-within the CMD will effectively move the star into the contamination
-region expected for background CTTS or MS stars at a $(V-I)_0$ of
-$\leq$1.5 and $M_V$ 12-10, and as such the star would not be included
-in a photometrically selected BD sample. The solid green line, in the
-\textit{top left panel}, showing the 1 Myr isochrone of
-\cite{siess_2000} at a distance of 250 pc and extinction of
-$A_V=2$ mags shows that the BDD systems with higher accretion rates
-could easily be confused for a background CTTS or MS population (as MS
-stars are simply less luminous at a roughly constant \textit{V-I} than
-the CTTS counterparts). Indeed miss classification of a BDD system as
-a CTTS system has already been revealed in
-\cite{white_2003}. Furthermore, scatter, although somewhat
-reduced, can be observed in the simulated photometry of the negligibly
-accreting systems, for example in the \textit{top left panel} some red
-dots, accreting at -12 or -11 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-(which will be negligible compared to the photospheric flux, see
-Figure \ref{acc_dom}), still scatter significantly. These objects may
-still be included in a `wide' photometric selection. This scatter is a
+\logmdot the movement of the star within the CMD will effectively move
+the star into the contamination region expected for background CTTS or
+MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$ 12-10, and as such the
+star would not be included in a photometrically selected BD
+sample. The solid green line, in the \textit{top left panel}, showing
+the 1 Myr isochrone of \cite{2000A&A...358..593S} at a distance of 250
+pc and extinction of $A_V=2$ mags shows that the BDD systems with
+higher accretion rates could easily be confused for a background CTTS
+or MS population (as MS stars are simply less luminous at a roughly
+constant \textit{V-I} than the CTTS counterparts). Indeed miss
+classification of a BDD system as a CTTS system has already been
+revealed in \cite{2003ApJ...582.1109W}. Furthermore, scatter, although
+somewhat reduced, can be observed in the simulated photometry of the
+negligibly accreting systems, for example in the \textit{top left
+  panel} some red dots, accreting at -12 or -11 \logmdot (which will
+be negligible compared to the photospheric flux, see Figure
+\ref{acc_dom}), still scatter significantly. These objects may still
+be included in a `wide' photometric selection. This scatter is a
 strong function of inclination, as shown in the \textit{bottom right
@@
 \textit{bottom left panel} shows that for naked systems accretion
-rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ lead to the stars
-being scattered into the region occupied by background CTTS and
-contamination (the lower accretion rates are all coincident with the
--12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for 1 Myr). Crucially, the
-\textit{top left panel} shows that the scatter from the isochrone is,
-generally, correlated with accretion rate. Effectively, as the
+rates of -9 \logmdot lead to the stars being scattered into the region
+occupied by background CTTS and contamination (the lower accretion
+rates are all coincident with the -12 \logmdot for 1 Myr). Crucially,
+the \textit{top left panel} shows that the scatter from the isochrone
+is, generally, correlated with accretion rate. Effectively, as the
 accretion rate increases the BDD system moves farther away from the
@@
 correlated with the rotation period and therefore inner edge position.
-Overall, as found in \cite{walker_2004}, the dominant
+Overall, as found in \cite{2004MNRAS.351..607W}, the dominant
 scattering effect for BD disc systems in an optical CMD appears to be
@@
 60$^{\circ}$) one would expect to exclude a significant fraction of
-these objects from any isochrone based selection.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_VVI_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_opt_VVI_typ} except for extreme
-   accretors, $\dot{M}\geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. In this Figure the solid
-   black line now shows naked systems with an accretion rate of -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (as opposed to -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$, as in Figure
-   \ref{spread_opt_VVI_typ}, the dashed black line is still for an
-   accretion rate of -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. \label{spread_opt_VVI_ext}}
-\end{figure*}
+these objects from any isochrone based selection.  XXX EXPLAIN
+FIGURESXXX
 
@@
 naked isochrone (the naked isochrone at -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ is shown for
+\logmdot is shown for
 comparison). Comparison of the \textit{four panels} again show that,
@@
 
+XX MENTION THERE IS NO CORRELATION WITH ROTATTION RATE AS IS
+OBFUSCATED BY EFFECTS OF THE OTHER VARIABLES AND SAY INDICATIVE OF THE GRIDXXX
+
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_opt_RRI_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_opt_RRI_typ}, but in $M_R$, $(R-I)_0$,
-   with the pre-MS isochrone omitted.\label{spread_opt_RRI_typ}}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.ps}
+  \caption{Figure showing both XXX.\label{age_mass_VVI}}
 \end{figure*}
 
-Similar scattering, as observed in Figure \ref{spread_opt_VVI_typ},
-occurs when using CMDs constructed using $M_R$, $(R-I)_0$ \citep[using
-the photometric system of][]{bessell_1998}, except that the 1
-Myr pre-MS isochrone has been omitted. Figure \ref{spread_opt_RRI_typ}
-shows the $M_R$, $(R-I)_0$ CMD.
-
-Similar consequences are apparent in CMDs best suited, and most used,
-for derivation of masses using isochrones. Figure
-\ref{spread_ir_JJK_typ} shows the same data as Figure
-\ref{spread_opt_VVI_typ} in the same format except in this case the
-pre-MS isochrone of \cite{siess_2000} has been smoothed,
-purely for aesthetics and to remove the sharper features. Again Figure
-\ref{spread_ir_JJK_ext} contains the same data in the same format as
-Figure \ref{spread_opt_VVI_ext} except that the naked star isochrone
-at an accretion rate of -6 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ is
-not shown as it lies significantly blueward of the CMD.
-
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_ir_JJK_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As Figure \ref{spread_opt_VVI_typ}, in $M_J$, $(J-K)_0$, in
-   this Figure the pre-MS isochrone of \citet{siess_2000},
-   has been smoothed.\label{spread_ir_JJK_typ}}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.ps}
+  \caption{Figure showing both XXX.\label{age_mass_JJK}}
 \end{figure*}
 
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/spread_ir_JJK_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{spread_opt_VVI_ext}, except that the -6
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ isochrone is not shown (lies
-   significantly blueward of locus of data), and the pre-MS isochrone
-   has been smoothed.\label{spread_ir_JJK_ext}}
-\end{figure*}
+Figures \ref{age_mass_VVI} and \ref{age_mass_JJK} shows that as the
+system changes in inclination it leads to a significant dimming in
+both cases.
 
@@
 of $(J-K)_0$ colour with rotation rate as expected from the modeling
-of flat disc by \cite{meyer_1997}. It is clear that assigning
+of flat disc by \cite{1997AJ....114..288M}. It is clear that assigning
 masses to accreting BDD systems using isochrones, for our model grid,
@@
 \ref{spread_ir_JJK_ext}).
-
-\subsubsection{Summary}
 
@@
 could also act to reduce the stars radius, accelerating contraction
-\citep{tout_1999,siess_1999} and introducing
+\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
 additional scatter in a coeval population proportional to the range in
-accretion rates \citep[see][for full discussion]{mayne_2008}.
-Our findings support those of \cite{walker_2004}, showing that
+accretion rates \citep[see][for full discussion]{2008MNRAS.386..261M}.
+Our findings support those of \cite{2004MNRAS.351..607W}, showing that
 a significant scatter is caused by obscuration of the central source
@@
 correlation in IR, $(J-K)_0$, colour with rotational rate, as proposed
-by \cite{meyer_1997}.
-
-\subsubsection{Disc fractions}
-\label{disc_fractions_phot}
+by \cite{1997AJ....114..288M}.
+
+\subsubsection{Disc Fractions}
 
@@
 now used to detect disc presence
-\citep{lada_2006,kennedy_2009}. An $\alpha>$-2 is
+\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
 used as a selection criterion for disc presence for TTS stars. We have
 constructed the $\alpha$ values for our model grid by adopting the
-limiting wavelengths of \cite{kennedy_2009}, namely 3.6 to
-8.0\,$\mu$m.
-
-As shown in Figure \ref{inner_temp}, Section \ref{disc_struct}, the
-inner edge temperature for typical accretors retains some correlation
-with rotation rate. In general the more slowly rotating objects having
+limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
+8.0$\mu$m.
+
+XXX SAY OTHER FACTORS REMOVE THESE AS SUGGESTED FOR CTTS**** As shown
+in Figure \ref{inner_temp}, Section \ref{disc_struct}, the inner edge
+temperature for typical accretors retains some correlation with
+rotation rate. In general the more slowly rotating objects having
 cooler inner edges. For the more extreme rotators the inner edge
@@
 with the flux and therefore accretion rate of the system. As shown in
-Figures \ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext} (in
-Section \ref{age_mass_pop}), there is no clear correlation in CMD
-position, and $(J-K)_0$ colour with rotation rate for either typical
-or extreme accretors. In fact any scatter in these Figures
-(\ref{spread_ir_JJK_typ} and \ref{spread_ir_JJK_ext}) appears to be
-most strongly correlated with accretion rate and inclination.
-
-Figures \ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext} show the
-$(J-H)_0$, $(J-K)_0$ CoCoDs for typical and extreme accretors
-respectively. The dots are the simulate BDD systems for both ages (as
-position in these CoCoDs is not a strong function of age) and masses,
-and the black crosses the naked systems, again at both ages (and all
-masses), for the accretion rates matching the shown BDD data. The
-\textit{panels} of these Figures then separate the BDD systems by
-accretion rate (\textit{top left}), areal spot coverage
-(\textit{bottom left}), rotational period (\textit{top right}) and
-inclination (\textit{bottom right}). The accretion rates of -9, -10
-and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown as
-blue, black and red dots respectively in the \textit{top left panel}
-of Figure \ref{disc_frac_JHJK_typ}. For Figure
-\ref{disc_frac_JHJK_ext}, the \textit{top left panel} shows accretion
-rates of -6, -7 and -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ are shown
-as blue, black and red dots respectively. The \textit{bottom left
-  panels} of both Figures \ref{disc_frac_JHJK_typ} and
-\ref{disc_frac_JHJK_ext} show the systems with areal spot coverages of
-1 and 10\% as blue and red dots respectively. The \textit{top right
-  panels} of both Figures \ref{disc_frac_JHJK_typ} and
-\ref{disc_frac_JHJK_ext} show the systems with rotational periods of
-0.5 and 5 days as blue and red dots respectively. Finally, The
-\textit{bottom right panels} of both Figures \ref{disc_frac_JHJK_typ}
-and \ref{disc_frac_JHJK_ext} show the systems with inclinations of
-$\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as
-black dots and $\theta \geq 71^{\circ}$ as red dots.
+Figure \ref{spread_ir_JJK_typ} (in Section \ref{age_mass_pop}), there
+is no clear correlation in CMD position, and $(J-K)_0$ colour with
+rotation rate for either typical or extreme accretors. In fact any
+scatter in these Figures (\ref{spread_ir_JJK_typ} and
+\ref{spread_ir_JJK_ext}) appears to be most strongly correlated with
+accretion rate and inclination.
+
+XXX INTRODUCE FIGURE
 
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_JHJK_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing $(J-H)_0$, $(J-K)_0$ colour-colour diagram
-   for typical accretors ($\dot{M}<leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$). The dots are then all
-   models (at 1 and 10 Myrs) with discs and the black crosses are the
-   naked systems, in \textit{all panels}. The data are then separated
-   by input variable in \textit{each panel}. The \textit{top left
-     panel} shows accretion rates of -9, -10 and -11 \& -12
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as blue, black and red dots
-   respectively. The \textit{top right panel} shows the systems with
-   rotational periods of 0.5 and 5 days as blue and red dots
-   respectively. The \textit{bottom left panel} shows systems with
-   areal spot coverages of 1 and 10\% as blue and red dots
-   respectively. Finally, the \textit{bottom right panel} separates
-   the systems into three groups inclination, $\theta \leq$
-   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
-   71$^{\circ}$ , as blue, red and black dots
-   respectively.\label{disc_frac_JHJK_typ}}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_JHJK.ps}
+  \caption{Figure showing both XXX.\label{disc_frac_JHJK}}
 \end{figure*}
 
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_JHJK_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{disc_frac_JHJK_typ} but for extreme
-   accretors, $\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-   .\label{disc_frac_JHJK_ext}}
-\end{figure*}
-
-Figures \ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext} show
-that for typical and extreme accretion rates there is no clear
-correlation of rotation rate, areal coverage or inclination with the
-position in the CoCoD. Significantly no clear correlation between IR
-colours and rotation rate can be observed for the typical accretors.
-This suggests that the weak correlation found between inner edge
-temperature and rotational period does not produce a matching
-correlation with IR colours. For the extreme accretors, however, a
-correlation between IR colours and accretion rate is clear. As the
-accretion rate increases the systems move to redder CoCoDs. This is
-caused, as discussed by the dust inner edge being sublimated and the
-resulting sublimation decreasing, with density, radially. Therefore,
-one can not extend the predictions of \cite{meyer_1997},
-after adoption of a co-rotation radius to suggest that IR excesses may
-be correlated with rotation rates, for typical or extreme accretors.
-As can be seen for all the panels of Figures \ref{disc_frac_JHJK_typ}
-and \ref{disc_frac_JHJK_ext} there is a slight overlap between the
+XXXSAY AGAIN NO ROTATION RATE CORRELATIONXXXX
+
+Figure \ref{disc_frac_JHJK} shows that for typical and extreme
+accretion rates a correlation between IR colours and accretion
+rate. As the accretion rate increases the systems move to redder
+CoCoDs. This is caused, as discussed by the dust inner edge being
+sublimated and the resulting sublimation decreasing, with density,
+radially. Therefore, one can not extend the predictions of
+\cite{1997AJ....114..288M}, after adoption of a co-rotation radius to
+suggest that IR excesses may be correlated with rotation rates, for
+typical or extreme accretors.  As can be seen for all the panels of
+Figure \ref{disc_frac_JHJK} there is a slight overlap between the
 naked or disc less objects (crosses) and the BDD systems (dots). This
@@
 
-The analysis in Section \ref{age_mass_pop} and Figures
-\ref{disc_frac_JHJK_typ} and \ref{disc_frac_JHJK_ext}, shows that
-accretion rate and inclination are the dominant variables controlling
-the photometric scatter, of the BDD systems. Therefore, for our
-subsequent analysis we will separate the systems using only these
-input variables.
-
-Figures \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} show
-CoCoDs for colours constructed using simulated IRAC photometry, for
-the typical and extreme accreting systems respectively. These two
-Figures contain the same data as Figures \ref{disc_frac_JHJK_typ} and
-\ref{disc_frac_JHJK_ext}, respectively. The naked systems are again
-shown as crosses and the BDD systems as dots. The \textit{left panels}
-of these Figures show $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs and
-the \textit{right panels} $([3.6]-[4.5])_0$, $([5.8]-[8.0])_0$
-CoCoDs. The \textit{top panels} then show the accretion rates of -9,
--10, -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), for Figure
-\ref{disc_frac_irac_typ}, and -6, -7 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), for Figure
-\ref{disc_frac_irac_ext}, as blue, black and red dots
-respectively. The \textit{bottom panels} of both Figures show the
-systems with inclinations of $\theta \leq 48^{\circ}$ as blue dots,
-$\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
-71^{\circ}$ as red dots.
-
+IRACXXXX
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing typically accreting systems ($\dot{M}\leq$-9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$), in irac photometric
-   bands. The \textit{left panels} show the $([3.6]-[4.5])_0$ against
-   $([4.5]-[5.8])_0$ CoCoD, and the \textit{right panels} show the
-   $([3.6]-[4.5])_0$ against $([5.8]-[8.0])_0$ CoCoD. In \textit{all
-     panels} the dots are disc systems and crosses naked systems. The
-   \textit{top panels} then separate the systems by accretion rate
-   with, -9, -10 and -11 \& -12 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-   as blue, black and red dots respectively. The \textit{bottom
-     panels} separate the systems by inclination with $\theta \leq$
-   48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56, 64 \&
-   71$^{\circ}$ , as blue, red and black dots
-   respectively. \label{disc_frac_irac_typ}}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_irac.ps}
+  \caption{Figure showing both XXX.\label{disc_frac_irac}}
 \end{figure*}
@@
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{disc_frac_irac_typ} but for extreme
-   accretors, $\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$.\label{disc_frac_irac_ext}}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_mips.ps}
+  \caption{Figure showing both XXX.\label{disc_frac_mips}}
 \end{figure*}
+
+XXXSAY INDICATIVE OF LONGER WAVELENTHGS
 
@@
 $([8.0]-24)_0$ and the \textit{right panels} $([3.6]-[5.8])_0$,
-$([8.0]-24)_0$ CoCoD, where 24, is the 24\,$\mu$m MIPS channel.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_mips_typ.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing the $([3.6]-[4.5])$, $([8.0]-24)$ CMDs as the
-   \textit{left panels} and $([3.6]-[5.8])$, $([8.0]-24)$ CMDs as the
-   \textit{right panels}, combining IRAC and MIPS photometric
-   channels. The systems are again separated by accretion rate and
-   inclination angle in the \textit{top} and \textit{bottom} panels as
-   in figure \ref{disc_frac_irac_typ}.\label{disc_frac_irac_mips_typ}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_irac_mips_ext.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{As for Figure \ref{disc_frac_irac_mips_typ} but for extreme
-   accretors ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$).\label{disc_frac_irac_mips_ext}}
-\end{figure*}
-
-Figures \ref{disc_frac_irac_mips_typ} and
-\ref{disc_frac_irac_mips_ext} show that the BDD and naked systems are
-very well separated in CoCoDs utilising IRAC and longer wavelength
-MIPS data. For the systems with typical accretion rates, Figure
-\ref{disc_frac_irac_mips_typ}, no correlation between CoCoD position
-and accretion rate is obvious (\textit{top panels}). The \textit{lower
-  panels} of this Figure show that, in general, the locus of BDD stars
-is spread similarly for all but edge-on systems, which sometimes
-appear a little redder in $([8.0]-24)_0$. For the extreme accretors,
-Figure \ref{disc_frac_irac_mips_ext}, however, correlations in CoCoD
-position with both inclination and accretion rate are clear. The
-\textit{top panels} of Figure \ref{disc_frac_irac_mips_ext} show that
-as the accretion rate increases, in general, the systems move to
-redders colours in $([3.6]-[4.5])_0$ or $([3.6]-[5.8])_0$
-(\textit{left} and \textit{right panels} respectively). This is to be
-expected from our previous analysis of IRAC CoCoDs using this
-photometry. The \textit{lower panels} of Figure
-\ref{disc_frac_irac_mips_ext} show a correlation of inclination angle
-with the colours in both axes. These two correlations essentially mean
-that we can roughly identify systems, with regard to inclination and
-accretion rate, by their position within this CoCoD. For instance,
-extreme accretors with lower accretion rates seen face-on will occupy
-the bottom left of the BDD locus, with edge-on systems with the
-maximum accretion rate appearing to the top right. Comparing the
-scales on Figures \ref{disc_frac_irac_mips_typ} and
-\ref{disc_frac_irac_mips_ext} shows that these systems slightly
-overlap, but in general the extreme accretors will lie redward of the
-typical accretor locus in both colours.
-
-Figure \ref{disc_frac_mips} shows CoCoDs constructed solely from the
-longer wavelength MIPs photometry. Figure \ref{disc_frac_mips} shows
-the BDD data shown in previous Figures (such as Figure
-\ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext}) in $(24-70)_0$,
-$(70-160)_0$ CoCoDs. The \textit{left} and \textit{right panels} show
-the typically and extreme accreting systems, respectively. The
-\textit{inset panels}, in \textit{both top panels}, show larger areas
-to include the naked systems, as they are well removed from the BDD
-locus.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_mips.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing CMDs of mips photometry for the typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and
-   extreme ($\dot{M} \geq$ -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$)
-   accretors, as the \textit{left panels} and \textit{right panels}
-   respectively. The \textit{top panels} separate the systems by
-   accretion rate in the way described in Figures
-   \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} in the
-   \textit{left} and \textit{right panels} respectively. The
-   \textit{bottom panels} then separate the systems by inclination as
-   described in Figure \ref{disc_frac_irac_typ}. The \textit{inset
-     panels} in the \textit{top panels} then show a larger region with
-   the BDD systems as red dots and the naked systems as blue
-   crosses.\label{disc_frac_mips}}
-\end{figure*}
-
-Figure \ref{disc_frac_mips} shows, in the \textit{inset panels}, that
-BDD and naked systems are very well separated in CoCoDs constructed
-using MIPs photometry. For the typical accretors, \textit{left panel},
-the position within the CoCoD appears strongly correlated with
-inclination only, with the edge on systems moving away from the main
-BDD locus, as expected. For the extreme accretors, \textit{right
-  panel}, significantly more structure is apparent. In this case as
-the accretion rate increases the systems move redward in both colours.
-Additionally, as the inclination increases the systems move to redder
-$(24-70)_0$ colours. This suggests, as with Figure
-\ref{disc_frac_irac_mips_ext}, for objects with extreme accretion
-rates, CoCoDs of this sort may help distinguish the characteristic
-inclination and accretion rate of the system. In practice, due to
-saturation and reddening effects and small sample sizes this may prove
-difficult. For our study this is interesting in that the fluxes for
-wavelengths longward of 24\,$\mu$m come from regions at temperatures of
-$~$120 K and below. This suggests that the outer disc flaring, as
-discussed in Section \ref{disc_struct}, leads to significantly
-structural changes in the outer, cooler disc, as a function of
-accretion rate. In addition, observing the separation of the naked and
-BDD systems within the CoCoDs it is clear that for systems within our
-grid, the best disc indicators are at longer wavelengths, as is well
-known from observations.
+$([8.0]-24)_0$ CoCoD, where 24, is the 24$\mu$m MIPS channel.
+
+\subsubsection{Observational cuts}
+\label{cuts}
+
+XXXNOW ONE FIGURE WITH ALPHA
 
 Disc fractions are also derived using the $\alpha$ value
-\citep{lada_2006}, essentially a slope of the SED between
+\citep{2006AJ....131.1574L}, essentially a slope of the SED between
 two wavelengths (at wavelengths longer than the stellar flux peak).
 Figure \ref{disc_frac_alpha} shows the derived $\alpha$ values between
-3.6 and 8.0\,$\mu$m for our entire model grid (against an arbitrary
+3.6 and 8.0$\mu$m for our entire model grid (against an arbitrary
 model number), with dots showing BDD systems and crosses showing naked
@@
 respectively. For TTS $\alpha>-$2 distinguishes between systems with
-and without discs \citep{kennedy_2009}. As can be seen in
+and without discs \citep{2009arXiv0901.2603K}. As can be seen in
 Figure \ref{disc_frac_alpha} almost all the typical, and all of the
@@
 
+Some recent studies of disc fractions for BD populations have used
+data from the \textit{Spitzer} IRAC camera. Figures \ref{irac_cut},
+\ref{irac_cut_2} and \ref{irac_cut_3} show the simulated photometry
+for our complete model grid. Naked BDs are shown as crosses and BDD
+systems as dots, with 1 and 10 Myrs data shown as blue and red dots
+respectively. The dashed lines are cuts used in three recent
+publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
+a study of IC348, Figure \ref{irac_cut_2} from
+\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis and Figure
+\ref{irac_cut_3} a study of the Taurus region from
+\cite{2008ApJ...674..336G}. In these cases the effects of extinction
+are either negligible in the plotted colours, with values of
+$E([3.6]-[4.5])<0.04$ and $E([4.5]-[5.8])<0.02$ for IC348 and $A_V
+\leq$4 mag \citep[which will be negligible in the IRAC
+CoCoD,][]{2004ApJS..154..363A}, or the cuts have been placed in
+intrinsic colour space as for $\sigma$ Orionis.
+
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/disc_frac_alpha.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing $\alpha$ value \citep{lada_2006}
-   (against an arbitrary model number) used
-   \citet{kennedy_2009}, $\alpha=\frac{dlog(\lambda
-     F_{\lambda})}{dlog(\lambda)}|^{3.6}_{8.0}$ ($\lambda$ in
-   $\mu$m). Crosses show the simulated objects without discs and dots
-   are those with circumstellar disc, the horizontal line is the
-   $\alpha>-$2 cut used to identify disc candidates for solar type
-   stars in \citet{kennedy_2009}. Note, that stars of
-   $M_*<$0.01$M_{\odot}$ are not included due to unreliable flux
-   estimates, in the atmosphere models, for longer wavelengths
-   ($\lambda>$4\,$\mu$m). The \textit{left panels} show typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors
-   and the \textit{right panels} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors. The \textit{top
-     panels} separate the systems by accretion rate in the way
-   described in Figures \ref{disc_frac_irac_typ} and
-   \ref{disc_frac_irac_ext} in the \textit{left} and \textit{right
-     panels} respectively. The \textit{bottom panels} then separate
-   the systems by inclination as described in Figure
-   \ref{disc_frac_irac_typ}.\label{disc_frac_alpha}}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_cuts.ps}
+  \caption{Figure showing both XXX.\label{disc_frac_cuts}}
 \end{figure*}
@@
 
-In summary, for our model grid, the best disc discriminators are MIPs
-CoCoDs and the $\alpha$ values. With, in general, correlations in
-position within the CoCoDs or the $\alpha$ values seen with accretion
-rate only for the extreme accretors.
-
-\subsubsection{Practical Observations}
-\label{object}
-
-Some recent studies of disc fractions for BD populations have used
-data from the \textit{Spitzer} IRAC camera. Figures \ref{irac_cut},
-\ref{irac_cut_2} and \ref{irac_cut_3} show the simulated photometry
-for our complete model grid. Naked BDs are shown as crosses and BDD
-systems as dots, with 1 and 10 Myrs data shown as blue and red dots
-respectively. The dashed lines are cuts used in three recent
-publications, Figure \ref{irac_cut} is from \cite{luhman_2005}
-a study of IC348, Figure \ref{irac_cut_2} from
-\cite{Luhman_2008} a study of $\sigma$ Orionis and Figure
-\ref{irac_cut_3} a study of the Taurus region from
-\cite{gutermuth_2008}. In these cases the effects of extinction
-are either negligible in the plotted colours, with values of
-$E([3.6]-[4.5])<0.04$ and $E([4.5]-[5.8])<0.02$ for IC348 and $A_V
-\leq$4 mag \citep[which will be negligible in the IRAC
-CoCoD,][]{allen_2004}, or the cuts have been placed in
-intrinsic colour space as for $\sigma$ Orionis.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_cut.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing all simulated photometry for the entire
-   studied parameter range at ages 1Myr and 10Myr as dots (blue and
-   red respectively), and the naked photometry as crosses. The dashed
-   lines are a recent BD disc excess cuts used in
-   \citet{luhman_2005} for IC348 at a nominal age of 3-4Myr
-   \citet{mayne_2008}. It must be noted that the naked stars
-   of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours. The \textit{left panel} shows the typical
-   ($\dot{M} \leq$ -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors
-   and the \textit{right panel} the extreme ($\dot{M} \geq$ -8
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors.\label{irac_cut}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_cut_2.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing an observational cut used in
-   \citet{Luhman_2008} for data of the $\sigma$ Orionis
-   cluster. It must be noted that the naked stars of
-   $M=$0.01$M_{\odot}$ are not included in this figure as their SEDs
-   do not extend far enough into the IRAC passbands to derive reliable
-   colours. The systems are separated by age as described in Figure
-   \ref{irac_cut}. The \textit{left} and \textit{right panels} again
-   show the typical ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and extreme ($\dot{M} \geq$
-   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors respectively as
-   in Figure \ref{irac_cut}.\label{irac_cut_2}}
-\end{figure*}
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/irac_cut_3.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing an observational cut used in
-   \citet{monin_2010} for data of the Taurus cloud. The
-   criteria applied for BDD system selection are that of
-   \citet{gutermuth_2008}. It must be noted that the naked stars
-   of $M=$0.01$M_{\odot}$ are not included in this figure as their
-   SEDs do not extend far enough into the IRAC passbands to derive
-   reliable colours. The systems are separated by age as described in
-   Figure \ref{irac_cut}. The \textit{left} and \textit{right panels}
-   again show the typical ($\dot{M} \leq$ -9
-   log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) and extreme ($\dot{M} \geq$
-   -8 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$) accretors respectively as
-   in Figure \ref{irac_cut}.\label{irac_cut_3}}
-\end{figure*}
-
 As can be seen from Figures \ref{irac_cut}, \ref{irac_cut_2} and
@@
 that other than a few typically accreting systems the observational
-cut of \cite{luhman_2005} would select all of the BDD systems
+cut of \cite{2005ApJ...631L..69L} would select all of the BDD systems
 in our grid. Figure \ref{irac_cut_2} shows that the cut of
-\cite{Luhman_2008} would miss some typical and a very small
+\cite{2008ApJ...688..362L} would miss some typical and a very small
 number of extreme accreting BDD systems. Figure \ref{irac_cut_3} shows
@@
 
-In a future publication we will release a fitting tool to be used in
-conjunction with the online database of naked and BDD systems (for
-both photometry and SED fitting). Therefore, we will be performing
-fits to observed systems using our grid. In this work we simply pick
-an example star and highlight its position in CMD and CoCoD space,
-compared to models covering the expected range of parameters.
-\cite{natta_2004} derive an accretion rate of -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ for $\rho$ Ophiucus 102. For
-this object \cite{natta_2002} find a spectral type of M6,
-$T_{\rm eff}$ of 2700\,K, an extinction of $A_V$=3.0, a mass of
-$M_*$0.04-0.08$M_{\odot}$ and a distance of 150pc. Photometry for
-$\rho$ Ophiucus 102 is also published in \cite{natta_2006},
-in $J$, $H$ and $K$. Additionally, $R$ and $I$ photometry has been
-published for this object in \cite{wilking_2005}. We have
-adjusted our model spectra in the range $M_*$=0.04-0.08$M_{\odot}$,
-with accretion rates of -9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$
-(for all remaining input parameters) to the correct distance and
-reddening. Figure \ref{rho_oph_102} shows, as dots, our BDD systems
-with the parameters in the range quoted, with $\rho$ Ophiucus 102 is
-shown as a black star. The \textit{panels} of Figure \ref{rho_oph_102}
-then show example CMDs and CoCoDs. The \textit{top left panel} shows a
-$J$, $J-H$ CMD, the \textit{bottom left panel} a $R$,
-$R-I$ CMD, the \textit{top right panel} a $J$, $J-K$ CMD and
-finally, the \textit{bottom right panel} a $J-K$, $J-H$ CoCoD.
-
-\begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/rho_oph_102.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
- \caption{Figure showing CMDs and CoCoDs of systems with matching
-   parameters to $\rho$ Ophiucus 102 from
-   \citet{natta_2002}. The object $\rho$ Ophiucus 102 is
-   shown in \textit{all panels} as a black star, the BDD systems are
-   the separated by age, with the 1 and 10 Myr systems appearing as
-   blue and red dots respectively. The \textit{top left panel} shows a
-   $J$, $J-H$ CMD, the \textit{top right panel} a $J$,
-   $J-K$ CMD, the \textit{bottom left panel} a $R$, $R-I$
-   CMD and the \textit{bottom right panel} shows a $J-H$,
-   $J-K$ CoCoD.\label{rho_oph_102}}
-\end{figure*}
-
-We have not performed a formal fitting of the object $\rho$ Ophiucus
-102. However, qualitatively, Figure \ref{rho_oph_102} shows that for
-$\rho$ Ophiucus 102 the colours are well matched by our grid, yet the
-magnitude is somewhat brighter. This could be an indication of
-uncertainties in the distance to the object, reddening or magnitudes.
-A full investigation is beyond the scope of this paper, but, as stated
-in a future publication we will release an online fitting tool to be
-used in conjunction with our grid.
+XXXINTRO TABLE MINISED NAKED CONTAMIANTIO LOWER LIMITS
+
+\begin{table*}
+\begin{tabular}{|l|l|l|}
+\hline
+Colour index&Disc selection&Number missed (\# \& \%)\\
+\hline
+a(3.6-8.0)&$> -2.20$&26/4480=0.6\%\\
+irac\_3.6-irac\_4.5&$> +0.21$&201/4480=4.5\%\\
+irac\_3.6-irac\_5.8&$> +0.50$&12/4480=0.3\%\\
+irac\_4.5-irac\_5.8&$> +0.32$&9/4480=0.2\%\\
+irac\_4.5-irac\_8.0&$> +0.45$&7/4480=0.2\%\\
+irac\_5.8-irac\_8.0&$> +0.13$&13/4480=0.3\%\\
+irac\_8.0-mips\_24&$> -16.2$&0/4480=0.0\%\\
+mips\_24-mips\_70&$> +9.90$&2/4480=0.04\%\\
+mips\_70-mips\_160&$> -6.20$&0/4480=0.0\%\\
+\hline
+\end{tabular}
+\caption{List of all the cuts which when applied to our simulated
+  dataset provide the best disc candidate selection with minimised
+  contamination. \label{par_space_table}}
+\end{table*}
 
@@
 underlying photospheric model flux, and therefore become difficult to
-classify. In Section \ref{sed_analysis} we have shown that the BD
+classify. In Section \ref{observables} we have shown that the BD
 photosphere becomes `swamped' or overwhelmed by the accretion flux for
@@
 
-\section{Consistency Checks and Problems}
+\section{Consistency Checks}
 \label{consistency}
@@
 \footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
-  disc}. In this Appendix we briefly discuss the data included, and
-the different ways of accessing or visualising these data on the
-website.
+  disc}.
 
@@
 
-\subsection{Navigation}
-\label{navigation}
-
-The main page contains links to download the entire dataset in several
-formats alongside files describing the format.
-
-\begin{enumerate}
-\item All SEDs (\AA and ergs s$^{-1}$ cm$^{-2} {\rm \AA} ^{-1}$) 
-\item All SEDs ($\mu$m and mJy)
-\item All Photometric Magnitudes for all BDD systems.
-\item All Photometric Magnitudes for all Naked systems.
-\item All Monochromatic Fluxes for all Naked systems ($\mu$m and ergs
-  s$^{-1}$ cm$^{-2} {\rm \AA} ^{-1}$)
-\item All Monochromatic Fluxes for all Naked systems ($\mu$m and mJy)
-\item All Monochromatic Fluxes for all BDD systems ($\mu$m and ergs
-  s$^{-1}$ cm$^{-2} {\rm \AA} ^{-1}$)
-\item All Monochromatic Fluxes for all BDD systems ($\mu$m and mJy)
-\end{enumerate}
-
-Also included is a link to the calibration information listing all the
-filter response sources, adopted zero points, central wavelengths,
-bandwidths and assumed SED shapes (for monochromatic flux derivation).
-A brief scientific overview is also available explaining, in general
-terms, the dataset and model.
-
-\subsection{Browsing Tools}
-\label{tools}
-
-For users who wish to investigate the dataset in a more specific or
-interactive fashion two browsing tools are included.
-
-The isochrones, mass tracks and individual stars magnitudes and
-colours generated and presented in the work can be queried using the
-``Isochrone and Mass Track Tool''. This allows the user to select the
-parameters of the model required and retrieve the specific data.
-
-Secondly, an interactive tool is included allowing a user to select a
-given set of parameters and download the ``SEDs, monochromatic fluxes
-or magnitudes''. In addition this tool plots the SEDs for the Naked
-system or the three inclinations, in the case of BDD systems and
-allows users to select filters sets, whose monochromatic flux values
-will be overlaid on the displayed SEDs.
-
 \label{lastpage}

### 2010-05-24 BD_disc/paper.tex
Completely changed results section and conclusions-these sections need finessing
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2281 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \item{Sort structure paragraph at end of intro.}
-\item{Sort out headings of sections.}
-\item{Sort clearpage problem, perhaps change to includegraphics.}
-\item{Sort out the webpage stuff.}
 \end{enumerate}
@@
 space
-\citep{luhman_2005,Luhman_2008,gutermuth_2008}.
+\citep{luhman_2005b,luhman_2008,gutermuth_2008}.
 The important quantity here is the separation in wavelength between
@@
 and measure disc fractions
-\citep{luhman_2005,Luhman_2008,gutermuth_2008}.
+\citep{luhman_2005b,luhman_2008,gutermuth_2008}.
 
@@
 90$^{\circ}$). A further useful feature of the {\sc torus} code is
-that the emitted photon packets which make up the SED are tagged on their way
-to the observer. These tags separate the packets into four
+that the emitted photon packets which make up the SED are tagged on
+their way to the observer. These tags separate the packets into four
 groups. Firstly, packets are separated by source into thermal (disc)
 or stellar groups. These groups are then subdivided into those which
-reach the observer either directly or after scattering (for example
-see Figure \ref{disc_eg_173}). The resulting SEDs are discussed in
-Section \ref{seds}.
+reach the observer either directly or after scattering. The resulting
+SEDs are discussed in Section \ref{seds}.
 
@@
 unambiguously separate naked and star-disc systems
-\citep{luhman_2005}. In addition, at longer wavelengths, the
+\citep{luhman_2005a}. In addition, at longer wavelengths, the
 MIPS instrument provides sensitivity to disc systems at much larger
@@
 across our parameter space. Then we discuss the resulting simulated
-SEDs for these BDD systems (Section \ref{observables}). Finally, we
-produce simulated photometric observations (Section \ref{photometry}).
-These simulated observations allows us to show that recovery of the
-input masses and ages for our accreting BDD systems is unreliable. We
-show that despite an intrinsic relationship between rotation rate and
-initial inner edge position we do not recover a rotation rate
-correlation with IR excess. In addition, despite not intrinsically
-including a dependence of accretion rate on stellar mass in our grid.
-We show that current observational techniques and theoretical models
-applied to the grid would result in a relationship of this type being
-derived.
+observations in Section\ref{observables}. We present analysis in terms
+of the impacts of the disc structure on the SEDs and colours and
+magnitudes. Then in Section \ref{isochrones} we examine the
+reliability of age, mass and disc fraction derivation when applied to
+our model grid. In particular we discuss selection effects causing
+higher accreting systems to be unlikely to be classified as BDD
+systems. Essentially, despite not intrinsically including a dependence
+of accretion rate on stellar mass in our grid.  We show that current
+observational techniques and theoretical models applied to the grid
+would result in a relationship of this type being derived.
 
@@
 \cite{dullemond_2001}. This effect is illustrated in
-Figure~\ref{no_sub_183}, a model in which there is negligible dust
+Figure~\ref{no_sub_183_a}, a model in which there is negligible dust
 sublimation.
@@
 \label{observables}
+
+XXXNJM HAS RE-WRITTEN FROM HEREXXX
 
@@
 of the peak flux. This can be seen clearly by comparing the left and
-right panels of Figure \ref{acc_dom}. Perhaps the most important,
-albeit qualitative, result shown is Figure \ref{acc_dom} is an insight
-into the accretion rate at which the accretion blackbody flux
-dominates over the photospheric flux. Figure \ref{acc_dom} shows that
-as the accretion rate raises above \logmdot = $-9$ for systems with 1
-or 10\% areal coverage, the accretion flux dominates the emergent SED
-at both periods. Effectively, the spectroscopic features of the
-photosphere are veiled by the additional continuum accretion
-flux. Therefore for reasonable coverages (1--10\%) and rotational
-periods (0.5--5 days) the photospheric flux is effectively veiled by
-accretion flux for accretion rates \logmdot$>-9$. It is also clear
-from Figure \ref{acc_dom} that the magnitude becomes brighter and the
-colour bluer (in terms of optical photometry) with increasing
-accretion rates as expected \citep{gullbring_1998}.
+right panels of Figure \ref{acc_dom} As the rotation rate increases
+the co-rotation radius also increases, as shown in Equation
+\ref{inner_eq}, $R_{\rm inner}\propto \tau^{\frac{2}{3}}$. Therefore,
+as Equations \ref{Lacc} and \ref{Tacc}, show, $L_{\rm acc}\propto 1-
+\frac{R_*}{R_{\rm inner}}$ and $T_{\rm acc}\propto (\frac{L_{\rm
+    acc}}{A})^{\frac{1}{4}}$. Therefore, the temperature of the
+accretion hot spot increases as the rotational period increases, due
+to the increase in potential energy lost by the mass accreted. This
+can be seen in Figure by comparing the left and right panels of Figure
+\ref{acc_dom}. Perhaps the most important, albeit qualitative, result
+shown is Figure \ref{acc_dom} is an insight into the accretion rate at
+which the accretion blackbody flux dominates over the photospheric
+flux. Figure \ref{acc_dom} shows that as the accretion rate raises
+above \logmdot = $-9$ for systems with 1 or 10\% areal coverage, the
+accretion flux dominates the emergent SED at both
+periods. Effectively, the spectroscopic features of the photosphere
+are veiled by the additional continuum accretion flux. Therefore for
+reasonable coverages (1--10\%) and rotational periods (0.5--5 days)
+the photospheric flux is effectively veiled by accretion flux for
+accretion rates \logmdot$>-9$. It is also clear from Figure
+\ref{acc_dom} that the magnitude becomes brighter and the colour bluer
+(in terms of optical photometry) with increasing accretion rates as
+expected \citep{gullbring_1998}.
 
@@
 the flux reaching the observer from the inner and outer regions of the
-disc as the system approaches edge on. Also, as discussed in
-Section \ref{disc_struct} the addition of dust sublimation leads to a
-change in the shape of the inner edge, where the temperature is
-sufficient. Figures \ref{no_sub_183} to \ref{sub_179} \ref{sub_181}
-show a range in inner edge shapes, from flat walls through concave to
-convex curves, caused by the radial density profile of the disc and
-the dependence of the sublimation temperature on density. This change
-in shape, as noted for Herbig Ae stars by \cite{tannirkulam_2007}
-XX CHECK FOR A CTTS REFERENCESXXX, will lead to changes in the
-characteristics of the SED, or derived IR excess, with inclination
-angle \citep{tannirkulam_2007}, for close to face on viewing
-angles.
+disc as the system approaches edge on. Also, as discussed in Section
+\ref{disc_struct} the addition of dust sublimation leads to a change
+in the shape of the inner edge, where the temperature is
+sufficient. Figures \ref{no_sub_183_a} to \ref{sub_179_a}
+\ref{sub_181_a} show a range in inner edge shapes, from flat walls
+through concave to convex curves, caused by the radial density profile
+of the disc and the dependence of the sublimation temperature on
+density. This change in shape, as noted for Herbig Ae stars by
+\cite{tannirkulam_2007} XX CHECK FOR A CTTS REFERENCESXXX, will lead
+to changes in the characteristics of the SED, or derived IR excess,
+with inclination angle \citep{tannirkulam_2007}, for close to face on
+viewing angles.
 
@@
 
-HERER****
- write caption
-GOT HERE*** TUNE WHAT NEED FROM THIS FIGURE***
-
-SELECT THE CORRECT MODELS
-
-POINTS TO MAKE, MJ (and MV) brighter for high accretion, tail off
-starts earlier for high accretion
-
-J-K delta larger over short inclinations than low accretors 0.05 0.1
-factor two larger in magnitude!!! factor ten in flux?
-
 The changes in flux with inclination will clearly lead to changes in
-the observed magnitudes with inclination. Figure \ref{flare_inner_mag}
-shows the $M_V$ and $M_J$ magnitude, in the \textit{top} and
-\textit{bottom panels} respectively, as a function of inclination with
-the individual points marked as crosses. The \textit{top} and
-\textit{bottom panels} show accretion rates of -12, -9 and -7
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ as black, red and blue lines.
-The solid lines are for objects with rotational periods of 0.5 days
-and the dashed lines are for periods of 5 days. The \textit{inset
-  panel} within the \textit{bottom panels} shows an enlargement of the
-section of inclinations from 40 to 80$^{\circ}$. For \textit{all
-  panels} the vertical dotted lines show the inclinations for which
-significant drops in flux are observed (see Figure \ref{flare_inc})
-for -12 and -7 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ in black and
-blue respectively.
+the observed magnitudes and colours with inclination. Figure
+\ref{flare_inner_mag} shows the $M_V$ and $M_J$ magnitudes and the
+$(J-K)_0$ colour index, in the top, middle and bottom panels
+respectively. The colours and magnitudes are then marked as crosses as
+a function of inclination.  The systems shown in all panels have an
+age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5 and an
+areal coverage of 10\%. The systems with accretion rates of \logmdot
+-12, -9 and -7 are shown in black, red and blue, respectively, with
+the lowest panel omitting \logmdot =-9, and restricting the
+inclination to viewing angles close to face-on.  The top and middle
+panels also show the system with the highest accretion rate but with a
+rotation rate of 5 days as a dashed line. The vertical dotted lines in
+the lowest panel simply illustrate the total change in magnitude, over
+the shown inclination range.
 
@@
   \includegraphics[scale=0.6,angle=90]{./Fig/flare_inner_mag.ps}
-  \caption{Figure showing both XXX.\label{flare_inner_mag}}
+  \caption{Figure showing $M_V$, $M_J$ magnitudes and $(J-K)_0$ colour
+    index as a function of inclination, shown as top, middle and lower
+    panels respectively. The magnitude and colours of systems with
+    $M_*=0.04M_{\odot}$, an age of 1 Myr, areal coverage of 10\% and
+    rotation rate of 0.5 days are shown as crosses. The systems with
+    accretion rates of \logmdot = -12, -9 and -7, are shown in black,
+    red and blue respectively. The lowest panel omits the \logmdot -9
+    systems. The top and middle panels also the systems with the
+    highest accretion rate but for a rotation rate of 5 days. The
+    lowest panel also shows, as horizontal dotted lines, the total
+    change of colour with the illustrated
+    inclinations. \label{flare_inner_mag}}
 \end{figure*}
 
-XXXSUMMARISE THISXXX
+Accretion flux was shown to dominate the underlying, intrinsic,
+photospheric SED for accretion rates of \logmdot=-9 (see Figure
+\ref{acc_dom}). As one would expect this leads to significant changes
+in the derived photometric magnitudes for bands blueward of a few
+microns, where the accretion and photospheric flux dominate. This is
+shown in the top panel of Figure \ref{flare_inner_mag}. As the
+accretion rate increases the system moves to brighter magnitudes in
+$M_V$. The move to brighter magnitudes becomes significant once the
+accretion rate exceeds \logmdot=-9. Again moving from the fast to slow
+rotation period increases the potential energy released and in this
+case results in a brighter $M_V$ magnitude. As one moves to longer
+wavelength photometric bands, as shown in the middle panel. The
+increase in accretion rate affects these magnitudes, i.e. $M_J$ are
+les significantly affected. This is due to the significance of the
+inner edge at these longer wavelengths. The lowest panel shows that as
+the accretion rate is increase the IR colours generally get
+redder. Again, this is caused by interaction with the disc, as more
+flux is reprocessed by the inner edge.
+
+The top and middle panels of Figure \ref{flare_inner_mag} shows the
+change in magnitude caused by obscuration from the flared outer
+disc. The occultation starts earlier for the higher accretion rates,
+with the magnitudes in $M_V$ and $M_J$ moving fainter at earlier
+inclinations for the higher accretion rates.
+
+XXXNOT SURE ABOUT THIS NEXT BIT, PERHAPS A LITTLE WEAKXXX
+
+The lowest panel of Figure \ref{flare_inner_mag} shows the difference
+in the inclination dependence of the IR colour for large curved
+(\logmdot=-7) and smaller vertical (\logmdot=-12) inner walls. The
+$(J-K_0$ colour of the higher accretion rate system changes more as a
+function of inclination when compared to the lower accretion rate
+system. A total change in $(J-K)_0$ of $\approx$ 0.05 and 0.1 are
+found for \logmdot=-12 and -7 respectively. This doubling in the
+change in IR colour as a function of inclination for viewing angles
+close to face-on, is caused by the larger (vertically) and convex
+inner wall in the extreme accreting case. For the convex inner wall
+the effective emitting area one observes changes as a function of
+inclination, leading to this greater dependence of IR colour on
+inclination.
+
+Therefore, for individual systems changes in the accretion rate and
+disc structure lead to significant changes in magnitudes and
+colours. The data presented in this section are for an isolated mass
+and age. However, the trends presented are present throughout our
+model grid for any given subset, and as such are representative. The
+scatter or changes in magnitude in the individual systems will change
+as a function of the remaining variables, but the dominant input
+variables affecting simulated photometry are accretion rate and
+inclination. For populations of stars these changes in magnitude and
+colour act to scatter or spread a pre-MS BD locus in photometric
+space.
 
@@
 \label{isochrones}
-
-XXXADD LINE ABOUT OBJECT
 
@@
 
+To delineate the effects of the accretion rate and circumstellar discs
+we have subdivided the grid into two groups (as discussed in Sections
+\ref{disc_struct}), those with accretion rates typical for higher mass
+CTTS objects, defined as \logmdot=-12 (negligible) to \logmdot=-9 and
+those with elevated accretion rates, where \logmdot>-9. For several of
+the plots in this section the magnitude and colours for the
+$M_*=0.01M_{\odot}$ systems at high inclinations become extremely
+faint and red. In some cases these objects appear slightly without the
+scale of the diagram the axes were limited in this way to be able to
+show the changes in colour and magnitude for the majority of stars
+better. The colours and magnitudes for these lowest mass stars are not
+necessarily unreliable but simply hinder the aesthetics of the plots,
+and as they are at the limits of our grid we have decided to omit them
+from some Figures by trimming the axes. Additionally, stars at the
+highest inclinations, i.e edge on disc systems, are often omitted from
+the Figures due to their extremely faint magnitudes, meaning they
+would not be practically observable.
+
+As discussed in Section \ref{disc_struct} the inner edge location is
+correlated with inner edge temperature (albeit differently for the
+typical and extreme accretors). As noted by \cite{meyer_1997} this
+could lead to a correlation of IR excess with inner edge position. As
+expected however, scattered caused by variations in inclination and
+disc structure act to remove this correlation for populations.  The
+correlation for an individual set of a systems, i.e. all variables
+fixed except rotation rate, between IR colour and rotation rate is
+preserved. However, as shown in Section \ref{disc_struct} the changes
+caused by accretion rate and inclination angle are the most
+significant, and act to remove any correlation between rotation rate
+and IR colours for populations. In fact, for our grid the simulated
+photometry shows no significant correlation between rotation rate and
+IR colours. The work of \cite{meyer_1997} studied flat accreting disc,
+therefore, as we have increased variation in disc structure by
+applying vertical hydrostatic equilibrium it would be interesting to
+see if any correlation appears for analytically defined disc
+structures. We have run a set of parrallel models using analytical
+disc structures and will publish the results in a subsequent
+publication. Overall, as found in \cite{walker_2004}, the
+dominant scattering effect for BD disc systems in an optical CMD
+appears to be caused by accretion rate and inclination. Therefore for
+derivation of parameters we explore the scatter in pre-MS BD locii as
+a function of accretion rate and inclination.
+
 \subsubsection{Mass and Age Derivation}
@@
 derivation \cite[see references and discussions in][ and Section
-\ref{derived}]{2007MNRAS.375.1220M,2008MNRAS.386..261M}.
-
-As discussed in Section \ref{sed_analysis} the presence of a
-circumstellar disc and accretion result in significant changes to the
-simulated SEDs for our models. Firstly, the photophere of the central
-star is dominated by the accretion luminosities for accretion rates of
-$\dot{M}>$10$^{-9}M_{\odot}yr^{-1}$ as shown in Section
-\ref{acc_dominance}. Secondly, for increasing accretion rates the
-outer disc flaring increases, resulting in occultation of the star at
-smaller inclination angles, as discussed in Section
-\ref{flare_obscure}. Finally, the location of the inner edge and flux
-intercepted by this edge lead to changes in its shape and subsequent
-dependence of the observed SED with inclination, as discussed in
-Section \ref{inner_shape}. In this Section we explore the effects of
-these changes in SED shape on the derived photometry in CMDs used for
-age and mass derivation for stars. The use of isochrones for the
-derivation of single star parameters is completely unreliable
-\citep[see discussion in][]{2008MNRAS.386..261M}. Practically,
-therefore, median ages are derived from populations. Subsequently,
-derived masses are still unreliable but at least based on a consistent
-age. This problem is being addressed by Bell et al (in prep), where
-$K$ band photometry and known eclipsing binaries are being used to
-refine pre-MS isochrones. In this section we plot the data for our 1
-Myr systems only and explore the resulting scatters caused by the disc
-presence and accretion luminosity.
-
-As can be seen in Figures \ref{age_mass_VVI} and \ref{age_mass_JHK}
-current accretion in a star and disc systems, for rates typical in the
-BD mass regime, creates a scatter in our simulated photometry
-indicative of a much larger isochronal age spread than 10 Myr. Indeed,
-for many BDD systems even at nominal accretion rates of -11 or -12
-\logmdot, for our simulations, the colours of these stars move
-significantly blueward of the expected BD locus in a $M_V$, $(V-I)_0$
-CMD. As the dots in these Figures are the simulated photometry of BDD
-systems over a range of typical input parameters (see Section
-\ref{par_space}), an observed coeval 1 Myr population could reasonably
-be expected to show a similar scatter. The naked isochrones show that
-this spread in simulated photometry, would lead to a spread in
-isochronal age greater than the $\approx$10 Myr spread claimed for
-higher mass stars in some star forming regions (for instance the
-ONC). Furthermore, for the higher accretion rates of -9 or -10
+\ref{derived}]{mayne_2007,mayne_2008}.
+
+The use of pre-MS isochrones for the derivation of single star
+parameters is at the present time not proven to be reliable \citep[see
+discussion in][]{mayne_2008}. Practically, therefore, median
+ages are derived from populations. Subsequently, derived masses are
+still unreliable but at least based on a consistent age. This problem
+is being addressed by Bell et al (in prep), where $K$ band photometry
+and known eclipsing binaries are being used to refine pre-MS
+isochrones. In this section we plot the data for our 1 Myr systems
+only and explore the resulting scatters caused by the disc presence
+and accretion luminosity.
+
+Figures \ref{age_mass_VVI} and \ref{age_mass_JJK} shows CMDs in $M_V$
+\& $(V-I)_0$ and $M_J$ \& $(J-K)_0$ resepctively. The left panels of
+both figures shows stars classed as typical accretors with accretion
+rates of \logmdot=-9, -10 and -11 \& -12, shown as blue, black and red
+dots respectively in the top panels. The right panels of Figures
+\ref{age_mass_VVI} and \ref{age_mass_JJK} show systems with extreme
+accretion rates, with \logmdot=-6, 7 and -8 shown as blue, black and
+red dots respectively, in the top right panel. The bottom panels then
+show the systems seperated into groups by inclination. These groups
+are $\theta \leq 48^{\circ}$ as blue dots (classed as face-on
+systems), $\theta> 56$ \& $64^{\circ}$ (classed as the expected
+systems, as the expectation value of $cos(\theta)=60^{\circ}$) as
+black dots and $\theta \geq 71^{\circ}$ (classed as edge-on systems)
+as red dots (for typical, bottom left, and extreme, bottom right
+accretion rates). The left panels then show naked stars isochrones
+(created from our grid of simulated photometry) for 1 Myrs at
+accretion rates of \logmdot=-12 and -9, as solid and dashed lines
+respectively (with coverage of 10\% and rotation rates of 5
+days). Whereas the left hand panels show naked stars isochrones of
+\logmdot=-6 and -9 as solid and dashed black lines respectively (with
+coverage of 10\% and rotation rates of 5 days. The solid green line,
+in the top panels, shows the 1 Myr isochrone of
+\cite{siess_2000} adjusted to a distance of 250pc and an
+extinction of $A_V=2$ mag, simulating a background population of CTTS
+stars.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.ps}
+  \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
+    accretors (\logmdot $\leq$ -9) in the left panels, and extreme
+    accretors (\logmdot $>-9$) in the right panels. The black dashed
+    and solid lines correspond to naked BD isochrones (from our grid)
+    with \logmdot -9 and -12 for the left panels (typical accretors)
+    and -9 and -6 in the right panels (extreme accretors). The
+    rotation rates and areal coverages are set at 5 days and 10\%
+    respectively (changing these has little effect). The top panels
+    also include as a solid green line the 1 Myr pre-MS isochrone of
+    \citet{siess_2000} adjusted to a distance modulus of 7 and an
+    extinction of $A_V=2$, simulating a reddened background
+    population. The top panels then seperate the systems by accretion
+    rate with \logmdot=-9, -10 and -11 \& -12 in the top left panel,
+    and \logmdot=-6, -7 and -8 in the top right panel, shown blue,
+    black and red dots respectively for both cases. The lower panels
+    then split the systems into groups by inclination, with $\theta
+    \leq$ 48$^{\circ}$, $\theta \geq$ 77$^{\circ}$ and $\theta=$ 56,
+    64 \& 71$^{\circ}$, plotted as blue, red and black dots
+    respectively.\label{age_mass_VVI}}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.ps}
+  \caption{Figure showing the same data in the same format and with
+    the same symbol meanings as Figure \ref{age_mass_VVI}, but for
+    $M_J$ and $(J-K)_0$ CMDs. However, for this Figure the \logmdot=-6
+    isochrone is not shown (lies significantly blueward of locus of
+    data), and the pre-MS isochrone of \citet{siess_2000}, has been
+    smoothed.\label{age_mass_JJK}}
+\end{figure*}
+
+As can be seen in Figures \ref{age_mass_VVI} and \ref{age_mass_JJK}
+current accretion and disc presence in a star and disc systems creates
+a scatter in our simulated photometry indicative of a much larger
+isochronal age or mass spread. Indeed, for many BDD systems even at
+nominal accretion rates of \logmdot= -11 or -12, for our simulations,
+the colours of these stars move significantly blueward of the expected
+BD locus in a $M_V$, $(V-I)_0$ CMD and redward in a $M_J$, $(J-K)_0$
+CMD. As, in the case of typical accretors, the input variables are in
+the range expected for a BD population, one could reasonably expect
+observed true BD locii to show a similar scatter. It is clear that
+even a wide photometric selection would not include all of, even the
+negligibly accreting systems at expected inclinations. Whilst the
+derivation of masses and ages for these objects will be
+difficult. Furthermore, for the higher accretion rates of -9 or -10
 \logmdot the movement of the star within the CMD will effectively move
@@
 star would not be included in a photometrically selected BD
-sample. The solid green line, in the \textit{top left panel}, showing
-the 1 Myr isochrone of \cite{2000A&A...358..593S} at a distance of 250
-pc and extinction of $A_V=2$ mags shows that the BDD systems with
-higher accretion rates could easily be confused for a background CTTS
-or MS population (as MS stars are simply less luminous at a roughly
-constant \textit{V-I} than the CTTS counterparts). Indeed miss
+sample. The solid green line, in the top panels of Figures
+\ref{age_mass_VVI} and \ref{age_mass_JJK}, showing the 1 Myr isochrone
+of \cite{siess_2000} at a distance of 250 pc and extinction of $A_V=2$
+mags shows that the BDD systems with higher accretion rates could
+easily be confused for a background CTTS or MS population. Indeed miss
 classification of a BDD system as a CTTS system has already been
-revealed in \cite{2003ApJ...582.1109W}. Furthermore, scatter, although
-somewhat reduced, can be observed in the simulated photometry of the
-negligibly accreting systems, for example in the \textit{top left
-  panel} some red dots, accreting at -12 or -11 \logmdot (which will
-be negligible compared to the photospheric flux, see Figure
-\ref{acc_dom}), still scatter significantly. These objects may still
-be included in a `wide' photometric selection. This scatter is a
-strong function of inclination, as shown in the \textit{bottom right
-  panel}, where, as the inclination is increased the objects are
-pushed lower in the CMD. Indeed, for the edge on cases some objects
-have magnitudes fainter than show in Figure \ref{spread_opt_VVI_typ}
-($M_V\approx 20$). This is expected as the star becomes obscured by
-the flared disc, interestingly for these systems the \textit{bottom
-  right panel} shows that this occurs for inclinations above around
-71$^{\circ}$ (as found in Figure \ref{flare_inc}) in most cases.
-However, even for the lower inclination angles some objects have very
-faint magnitudes, this is due to the disc flaring leading to a smaller
-opening angle and is discussed in Section \ref{disc_struct}. The
-\textit{bottom left panel} shows that for naked systems accretion
-rates of -9 \logmdot lead to the stars being scattered into the region
-occupied by background CTTS and contamination (the lower accretion
-rates are all coincident with the -12 \logmdot for 1 Myr). Crucially,
-the \textit{top left panel} shows that the scatter from the isochrone
-is, generally, correlated with accretion rate. Effectively, as the
-accretion rate increases the BDD system moves farther away from the
-isochrone and is therefore less likely to be classified as a BDD
-system and included in any target samples of such objects. The
-\textit{top right panel} shows that the scatter, in $M_V$, in our
-simulated photometry from the isochrones is significant for both areal
-coverages. The \textit{bottom left panel}, shows significant scatter
-in the simulated photometry for both adopted rotation periods. This
-panel also shows that scatter in this diagram is not obviously
-correlated with the rotation period and therefore inner edge position.
-Overall, as found in \cite{2004MNRAS.351..607W}, the dominant
-scattering effect for BD disc systems in an optical CMD appears to be
-caused by accretion rate and inclination, and therefore obscuration
-effects of the disc on the star. This suggests that for a given
-photometric survey of BDD systems accreting at typical accretion rates
-and with an expected range of inclinations (centred on around
-60$^{\circ}$) one would expect to exclude a significant fraction of
-these objects from any isochrone based selection.  XXX EXPLAIN
-FIGURESXXX
-
-Figure \ref{spread_opt_VVI_ext} shows that for extreme accretion rates
-the BDD objects move significantly blueward and brighter than the
-naked isochrone (the naked isochrone at -9
-\logmdot is shown for
-comparison). Comparison of the \textit{four panels} again show that,
-in general, the scatter is chiefly correlated with accretion rate and
-inclination. Essentially, Figure \ref{spread_opt_VVI_ext} shows that
-for, admittedly extreme, accretion rates BDD systems will not be
-included in a photometrically (or indeed spectroscopically, from
-Section \ref{sed_analysis}) selected sample.
-
-XX MENTION THERE IS NO CORRELATION WITH ROTATTION RATE AS IS
-OBFUSCATED BY EFFECTS OF THE OTHER VARIABLES AND SAY INDICATIVE OF THE GRIDXXX
-
-\begin{figure*}
-  \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.ps}
-  \caption{Figure showing both XXX.\label{age_mass_VVI}}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.ps}
-  \caption{Figure showing both XXX.\label{age_mass_JJK}}
-\end{figure*}
-
-Figures \ref{age_mass_VVI} and \ref{age_mass_JJK} shows that as the
-system changes in inclination it leads to a significant dimming in
-both cases.
-
-Figure \ref{spread_ir_JJK_typ} shows that for typical accretion rates
-and expected ranges of the other input variables the spread in CMD
-positions is large. Indeed. the \textit{top left panel} again shows
-that, as in the $M_V$ $(V-I)_0$ case, some of the BDD objects will
-appear as redenned background CTTS objects. Scrutiny of the
-\textit{individual panels} shows no clear correlation of CMD position
-with input variable except for the inclination. As shown in the
-\textit{bottom right panel} as the inclination increases the systems
-move to fainter magnitudes and redder colours, in general. The
-\textit{top right panel} of Figure \ref{spread_ir_JJK_typ} shows that
-for typical accretion rates there does not appear to be a correlation
-of $(J-K)_0$ colour with rotation rate as expected from the modeling
-of flat disc by \cite{1997AJ....114..288M}. It is clear that assigning
-masses to accreting BDD systems using isochrones, for our model grid,
-would result in the incorrect masses. In addition, photometric sample
-selection for BD systems will also exclude the majority of our higher
-accretion rate objects. Figure \ref{spread_ir_JJK_ext} shows that for
-extreme accretors the scatter is much larger, and again correlated
-only with inclination, and perhaps accretion rate to a lesser degree
-(\textit{bottom right} and \textit{top left panels} of Figure
-\ref{spread_ir_JJK_ext}).
+revealed in \cite{white_2003}. For the extreme accretors, as shown in
+the right panels of Figures \ref{age_mass_VVI} and \ref{age_mass_JJK},
+there is little chance of these objects being classed,
+photometrically, as BD candidates or being assigned the correct
+mass. Therefore, if one attempted to locate a population of BDD
+systems with elevated or extreme accretion rates, target selection
+would have to be placed at much brighter magnitudes, and bluer for
+optical or redder for IR, colours.
+
+This scatter for both typical and extreme accretors is a strong
+function of inclination, where, as the inclination is increased the
+objects are pushed lower in the CMD. Indeed, for the edge on cases
+some objects have magnitudes fainter than those shown (for instance
+$M_V\approx 20$). This is expected as the star becomes obscured by the
+flared disc, interestingly for typical systems the bottom right panels
+show that this occurs for inclinations above around 71$^{\circ}$ (as
+found in Figure \ref{flare_inner}) in most cases.  However, even for
+the lower inclination angles some objects have very faint magnitudes,
+this is due to the disc flaring leading to a smaller opening angle and
+is discussed in Section \ref{disc_struct}. Crucially, the top panels
+show that the scatter from the isochrone is, generally, correlated
+with accretion rate. Effectively, as the accretion rate increases the
+BDD system moves farther away from the isochrone and is therefore less
+likely to be classified as a BDD system and included in any target
+samples of such objects. Overall, the dominant scattering effect for
+BDD systems in an optical CMD appears to be caused by accretion rate
+and inclination, and therefore obscuration effects of the disc on the
+star. This suggests that for a given photometric survey of BDD systems
+accreting at typical accretion rates and with an expected range of
+inclinations (centred on around 60$^{\circ}$) one would expect to
+exclude a significant fraction of these objects from any isochrone
+based selection.
+
+We have presented CMDs constructed using $M_V$, $(V-I)_0$ and $M_J$,
+$(J-K)_0$. The scatter and correlations of scatter with accretion rate
+and inclination found within these CMDs are however, representative of
+CMDs constructed using optical or near-IR colours and magnitudes.
 
@@
 range of inclinations, will exhibit a significant scatter in apparent
-isochronal age of ($>$10 Myr). Furthermore, objects with typical (and
-extreme) accretion rates are scattered sufficiently in CMD space to
-prohibit their identification as pre-MS BDs. Indeed, these objects
-would not be included in a photometrically selected sample of BDs, and
-as such are unlikely to be assigned the correct masses or ages. The
-scatter from the naked 1 Myr systems, generally, increases with
-increasing accretion rate. It is important to note at this point that
-these conclusions are qualitative, and obviously based on our
+isochronal age. Furthermore, objects with typical (and extreme)
+accretion rates are scattered sufficiently in CMD space to prohibit
+their identification as pre-MS BDs. Indeed, these objects would not be
+included in a photometrically selected sample of BDs, and as such are
+unlikely to be assigned the correct masses or ages. The scatter from
+the naked 1 Myr systems, generally, increases with increasing
+accretion rate. It is important to note at this point that these
+conclusions are qualitative, and obviously based on our
 assumptions. However, the repercussion for isochronal age derivation
@@
 could also act to reduce the stars radius, accelerating contraction
-\citep{1999MNRAS.310..360T,1999A&A...342..480S} and introducing
-additional scatter in a coeval population proportional to the range in
-accretion rates \citep[see][for full discussion]{2008MNRAS.386..261M}.
-Our findings support those of \cite{2004MNRAS.351..607W}, showing that
-a significant scatter is caused by obscuration of the central source
-by the central disc. In addition we have shown that the typical
-accretion rates may scatter BDD systems into the region of a CMD
-occupied by the CTTS or background MS locus.
+\citep{tout_1999,siess_1999} and introducing additional scatter in a
+coeval population proportional to the range in accretion rates
+\citep[see][for full discussion]{mayne_2008}.  Our findings support
+and extend those of \cite{walker_2004}, showing that a significant
+scatter is caused by obscuration of the central source by the central
+disc, which (in our case) is in turn a function of accretion rate. In
+addition we have shown that the typical accretion rates may scatter
+BDD systems into the region of a CMD occupied by the CTTS or
+background MS locus.
 
@@
 is a dearth of lower mass stars accreting at higher rates. We have
-shown that for accretion rates in the range -12 to -9
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ the BDD systems with higher
-accretion rates would be preferentially missed using photometric or
-isochronal selection.
-
-Additionally, we have adopted the co-rotation radius as the initial
-location of our inner wall. This leads to an initial proportionality
-between the rotation rate and inner edge temperature. As discussed in
-Section \ref{disc_struct} this correlation will be modified due to
-dust sublimation effects, weakening the correlation. The derived
-photometry however, at varying inclinations, does not show a strong
-correlation in IR, $(J-K)_0$, colour with rotational rate, as proposed
-by \cite{1997AJ....114..288M}.
+shown that for accretion rates in the range \logmdot=-12 to -9 the BDD
+systems with higher accretion rates would be preferentially missed
+using photometric or isochronal selection. Furthermore, for the
+extreme accretors the BDD systems are scattered far from the
+non-accreting naked BD locus. This effectively means that applying
+standard photometric selection and considering possible dynamic
+magnitude ranges (to define saturation and magnitude limits), the
+systems with extreme accretion rates would not be classified as BDD
+sytems.
 
@@
 originally used to distinguish amongst Class I, II or II sources, but
-now used to detect disc presence
-\citep{2006AJ....131.1574L,2009arXiv0901.2603K}. An $\alpha>$-2 is
-used as a selection criterion for disc presence for TTS stars. We have
-constructed the $\alpha$ values for our model grid by adopting the
-limiting wavelengths of \cite{2009arXiv0901.2603K}, namely 3.6 to
-8.0$\mu$m.
-
-XXX SAY OTHER FACTORS REMOVE THESE AS SUGGESTED FOR CTTS**** As shown
-in Figure \ref{inner_temp}, Section \ref{disc_struct}, the inner edge
-temperature for typical accretors retains some correlation with
-rotation rate. In general the more slowly rotating objects having
-cooler inner edges. For the more extreme rotators the inner edge
-location is still weakly correlated with the inner edge
-temperature. In the extreme accretors case the correlation is caused
-by the radial fall in density, and therefore dust sublimation
-temperature as the inner edge is ablated. Therefore, for the extreme
-accretors the correlation between rotational period and inner edge
-temperature is lost. The inner edge temperature is in fact correlated
-with the flux and therefore accretion rate of the system. As shown in
-Figure \ref{spread_ir_JJK_typ} (in Section \ref{age_mass_pop}), there
-is no clear correlation in CMD position, and $(J-K)_0$ colour with
-rotation rate for either typical or extreme accretors. In fact any
-scatter in these Figures (\ref{spread_ir_JJK_typ} and
-\ref{spread_ir_JJK_ext}) appears to be most strongly correlated with
-accretion rate and inclination.
-
-XXX INTRODUCE FIGURE
+now used to detect disc presence \citep{lada_2006,kennedy_2009}. An
+$\alpha>$-2 is used as a selection criterion for disc presence for TTS
+stars. We have constructed the $\alpha$ values for our model grid by
+adopting the limiting wavelengths of \cite{kennedy_2009}, namely 3.6
+to 8.0$\mu$m.
+
+Figure \ref{disc_frac_JHJK} shows the photometry for all models in our
+grid in a $(J-K)_0$, $(J-H)_0$ CoCoDs. In all panels all of the naked
+systems are shown as black crosses. The left panels show those
+systems with typical accretion rates and the right panels the extreme
+accretors. The top panels of Figure \ref{disc_frac_JHJK} then seperate
+the systems by accretion rate with \logmdot -9, -10 and -11 \& -12,
+and -6, -7 and -8, shown as blue, black and red dots respectively for
+the typical (top left panel) and extreme (top right panel) accretors.
+The bottom panels then shows the defined groups of inclination angles,
+with $\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \&
+$64^{\circ}$ as black dots and $\theta \geq 71^{\circ}$ as red dots.
 
@@
   \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_JHJK.ps}
-  \caption{Figure showing both XXX.\label{disc_frac_JHJK}}
+  \caption{Figure showing $(J-K)_0$, $(J-H)_0$ CoCoDs for typical
+    (left panel) and extreme accreting (right panels) systems. The top
+    panels then seperate the accretion rates with \logmdot=-9, -10 and
+    -11 \& -12, and \logmdot=-6, -7 \& -8 shown as blue, black and red
+    dots respectively for the typical (top left panel) and extreme
+    (top right panel) accretors. The bottom panels then show the
+    systems with the inclinations $\theta \leq 48^{\circ}$ as blue
+    dots, $\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
+    71^{\circ}$ as red dots.\label{disc_frac_JHJK}}
 \end{figure*}
 
-XXXSAY AGAIN NO ROTATION RATE CORRELATIONXXXX
-
-Figure \ref{disc_frac_JHJK} shows that for typical and extreme
-accretion rates a correlation between IR colours and accretion
-rate. As the accretion rate increases the systems move to redder
-CoCoDs. This is caused, as discussed by the dust inner edge being
-sublimated and the resulting sublimation decreasing, with density,
-radially. Therefore, one can not extend the predictions of
-\cite{1997AJ....114..288M}, after adoption of a co-rotation radius to
-suggest that IR excesses may be correlated with rotation rates, for
-typical or extreme accretors.  As can be seen for all the panels of
-Figure \ref{disc_frac_JHJK} there is a slight overlap between the
-naked or disc less objects (crosses) and the BDD systems (dots). This
-overlap is small, only some of the lowest mass naked objects appear
-redward of the main population. Generally, a well placed cut should
-identify a large proportion of the disc candidates as is well known,
-if there is little complication from variable extinction and a well
-defined photometric system. However, the fact that an overlap exist at
-all will lead to some confusion as to the position of any disc excess
-cut. For real data a cut will be placed at a user identified paucity
-or gap in the CoCoD. Therefore, in practice, if any other region of
-the population appears equally, or more, sparse the cut is likely to
-be miss-placed. In practice these disc fractions are known to be lower
-limits of the true values, so ostensibly a miss placed cut, missing
-some disc candidates is not problematic.
-
-IRACXXXX
+Figure \ref{disc_frac_JHJK} shows that there is, for both typical and
+extreme accretors, an overlap between the naked and BDD systems. This
+suggests that an empirically placed cut in a CoCoD of this type (in
+the absence of complications from variable reddening) could
+mis-identify some candidates. However, as disc fractions defined by
+placing a colour-colour cut are viewed as lower limits this effect may
+be small. There is some evidence of a correlation of accretion rate
+and inclination with scatter from the naked star locus. However, if
+present this is weak. Our grid show no corelation in a CoCoD of this
+type with rotation rate. In the case of the extreme accretors (right
+panels) there is a strong correlation of accretion rate and scatter
+from the naked stars. Additionally, the extreme acretors lie
+significantly removed from the naked stars locus. There is a
+possiblity that some of these objects may be lost due to saturation
+and limiting magnitude effects. Again, as with mass and age
+derivation, the present figures are representative of similar figures
+using alternative, similar magnitudes.
+
+CoCoDs constructed using longer the longer wavelength bands of the
+IRAC and MIPS cameras are most commonly used for disc fraction
+calculation. Selection based on these types of data are well accepted
+as indicators of disc presence. Figures \ref{disc_frac_irac} and
+\ref{disc_frac_mips} show example CoCoDs for IRAC and MIPs magnitudes
+respectively.
+
+Figures \ref{disc_frac_irac} and \ref{disc_frac_mips} show the same
+data in the same format with the same symbol meanings as Figure
+\ref{disc_frac_JHJK}, except the colour indices. Figure
+\ref{disc_frac_irac} shows $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs
+and Figure \ref{disc_frac_mips} shows a $(24-70)_0$, $(70-160)_0$
+CoCoDs. Figure \ref{disc_frac_mips} also shows, as insets within the
+top panels, a larger scale figure to include the naked systems.
+
 \begin{figure*}
@@
   \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_irac.ps}
-  \caption{Figure showing both XXX.\label{disc_frac_irac}}
+  \caption{Figure showing $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs
+    of both typical (left panels) and extreme (right panels)
+    accretors. The panels seperate the different accretion rates and
+    inclinations as in Figure
+    \ref{disc_frac_JHJK}.\label{disc_frac_irac}}
 \end{figure*}
@@
   \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_mips.ps}
-  \caption{Figure showing both XXX.\label{disc_frac_mips}}
+  \caption{Figure showing $(24-70)_0$, $(70-160)_0$ CoCoDs in the same
+    format as Figure \ref{disc_frac_JHJK}. The smaller inset panels in
+    the top panels show the seperation between the naked (blue
+    crosses) and BDD systems (red dots).\label{disc_frac_mips}}
 \end{figure*}
 
-XXXSAY INDICATIVE OF LONGER WAVELENTHGS
-
-Figure \ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext} show that
-the naked and BDD systems are well separated. Supporting the view that
-IRAC magnitudes are well suited for disc candidate identification. For
-the typical accretors there is a possible correlation between
-inclination and position in the $([3.6]-[4.5])_0$, $([5.8]-[8.0])_0$
-CoCoD, (\textit{bottom right panel} of Figure
-\ref{disc_frac_irac_typ}). The systems which are edge-on
-(i.e. $\theta\geq$77$^{\circ}$) appear closer in colour to the naked
-systems. In the case of extreme the accretors the separation between
-the naked and BDD systems is correlated with accretion rate for both
-CoCoDs (\textit{top panels} of Figure
-\ref{disc_frac_irac_ext}). Effectively, as the accretion rate
-increases, in general the system moves to redder colours.
-
-Figure \ref{disc_frac_irac_mips_typ} and
-\ref{disc_frac_irac_mips_ext}, show the same data as Figure
-\ref{disc_frac_irac_typ} and \ref{disc_frac_irac_ext}, in the same
-format and with the same notations. Figures
-\ref{disc_frac_irac_mips_typ} and \ref{disc_frac_irac_mips_ext} show
-CoCoDs of simulated photometry from IRAC and MIPS magnitudes. For both
-Figures the \textit{left panels} show $([3.6]-[4.5])_0$,
-$([8.0]-24)_0$ and the \textit{right panels} $([3.6]-[5.8])_0$,
-$([8.0]-24)_0$ CoCoD, where 24, is the 24$\mu$m MIPS channel.
+Figure \ref{disc_frac_irac} shows that, as expected, the IRAC CoCoDs
+clearly seperate the naked and BDD systems. Once again, as found in
+Figure \ref{disc_frac_JHJK}, for the extreme accretors the seperation
+of the BDD systems from the naked stars is a weak function of
+accretion rate. There is also a weak correlation with inclination,
+with the face-on and expected systems closer to the naked
+stars. Figure \ref{disc_frac_irac} is representative of CoCoDs
+constructed using other IRAC photometric channels. As we include
+longer wavelength bands in the IRAC CoCoDs the seperation between the
+disc and naked locii increases. As the wavelength gets longer the flux
+originates from regions of the disc at lower temperature and therefore
+greater radial distance from the star. As photometric emission is
+minimal past around three $\mu$m, systems with discs will have
+significantly different SEDs from naked systems.
+
+Figure \ref{disc_frac_mips} shows that as we increase the wavelength
+even further, into the range of the MIPS photometric bands, the
+seperation between naked and BDD systems increases still further. The
+inset panels show that the seperation between the naked and BDD
+systems is larger than in Figure \ref{disc_frac_irac}. Additionally,
+there are clear correlations of MIPS positions with accretion rate and
+inclination. For the extreme accretors the systems are clearly
+delineated by accretion rate and inclination. This is as the emission
+is coming from greater radial positions within the disc where the
+structure of the disc is a finer function of the input
+variables. XXXNJM TO CHECK THIS MORE NEEDEDXXX
+
+Therefore, for models within our grid, disc fractions can be easily
+derived using IRAC and MIPS data. Whereas, $JHK$ data used to derive a
+disc fraction will lead to a probable underestimate of the disc
+fraction. There also appears a correlation, especially for the extreme
+accretors, with position in the CoCoDs and accretion rate (and perhaps
+inclination).
 
@@
 
-XXXNOW ONE FIGURE WITH ALPHA
-
-Disc fractions are also derived using the $\alpha$ value
-\citep{2006AJ....131.1574L}, essentially a slope of the SED between
-two wavelengths (at wavelengths longer than the stellar flux peak).
-Figure \ref{disc_frac_alpha} shows the derived $\alpha$ values between
-3.6 and 8.0$\mu$m for our entire model grid (against an arbitrary
-model number), with dots showing BDD systems and crosses showing naked
-systems. The \textit{left} and \textit{right panels} of Figure
-\ref{disc_frac_alpha} show the typical and extreme accreting systems
-respectively. For TTS $\alpha>-$2 distinguishes between systems with
-and without discs \citep{2009arXiv0901.2603K}. As can be seen in
-Figure \ref{disc_frac_alpha} almost all the typical, and all of the
-extreme accreting BDD systems would be successfully identified using
-this criterion. Suggesting that the $\alpha$ value is a reliable disc
-indicator for BD systems. The \textit{top panels} of Figure
-\ref{disc_frac_alpha} show the alpha values separated by accretion
-rates, with -9, -10 and -11 \& -12, or -6, -7 and -8
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ shown as blue, black and red
-dots respectively. The \textit{bottom panels} differentiate systems
-seen at different inclinations with $\theta \leq 48^{\circ}$ as blue
-dots, $\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
-71^{\circ}$ as red dots.
-
-Some recent studies of disc fractions for BD populations have used
-data from the \textit{Spitzer} IRAC camera. Figures \ref{irac_cut},
-\ref{irac_cut_2} and \ref{irac_cut_3} show the simulated photometry
-for our complete model grid. Naked BDs are shown as crosses and BDD
-systems as dots, with 1 and 10 Myrs data shown as blue and red dots
-respectively. The dashed lines are cuts used in three recent
-publications, Figure \ref{irac_cut} is from \cite{2005ApJ...631L..69L}
-a study of IC348, Figure \ref{irac_cut_2} from
-\cite{2008ApJ...688..362L} a study of $\sigma$ Orionis and Figure
-\ref{irac_cut_3} a study of the Taurus region from
-\cite{2008ApJ...674..336G}. In these cases the effects of extinction
-are either negligible in the plotted colours, with values of
-$E([3.6]-[4.5])<0.04$ and $E([4.5]-[5.8])<0.02$ for IC348 and $A_V
-\leq$4 mag \citep[which will be negligible in the IRAC
-CoCoD,][]{2004ApJS..154..363A}, or the cuts have been placed in
-intrinsic colour space as for $\sigma$ Orionis.
+Recent derivations of disc fraction usually use colour-colour
+selection in the IRAC photometric bands. As we have shown within our
+model grid the seperation between the BDD and naked systems is
+clear. Therefore, we can examine the success of some recent
+observationally placed when applied to our model grid. Additionally,
+disc fractions have been derived using the $\alpha$ value
+\citep{lada_2006}, essentially a slope of the SED between two
+wavelengths (at wavelengths longer than the stellar flux peak). As
+these $\alpha$ values are usually derived at wavelengths across the
+IRAC bands one would expect the resulting disc fractions to be
+reliable.
+
+Figure \ref{disc_cuts} presents all the data for our model grid
+seperated by age, with 1 and 10 Myr BDD systems shown as blue and red
+dots respectively. The naked systems are shown as black crosses. The
+CoCoDs featured are from several recent publications where disc
+fractions have been derived. The selection criteria from theses
+studies are marked as dashed vertical and horizontal lines. The left
+panels show the typical accretors and the right panels the extreme
+accretors.
+
+The observational cuts applied, shown as dashed lines, are from
+\cite{luhman_2005b} a study of IC348, \cite{luhman_2008} a study of
+$\sigma$ Orionis and \cite{gutermuth_2008} a study if the Taurus
+region. In these cases the effects of extinction are either negligible
+in the plotted colours, with values of $E([3.6]-[4.5])<0.04$ and
+$E([4.5]-[5.8])<0.02$ for IC348 and $A_V \leq$4 mag \citep[which will
+be negligible in the IRAC CoCoD,][]{allen_2004}, or the cuts
+have been placed in intrinsic colour space as for $\sigma$
+Orionis. The cuts from \cite{luhman_2005b}, \cite{luhman_2008} and
+\cite{gutermuth_2008} appear as the top, top-middle and bottom-middle
+panels. The lower panel shows a recent BDD candidate selection using
+the $\alpha$ value from \citep{kennedy_2009}.
 
@@
   \includegraphics[scale=0.6,angle=90]{./Fig/disc_cuts.ps}
-  \caption{Figure showing both XXX.\label{disc_frac_cuts}}
+  \caption{Figure showing both from top to bottom, the disc candidate
+    selection of \citet{luhman_2005b}, \citet{luhman_2008},
+    \citet{gutermuth_2008} and \citet{kennedy_2009}. The photometry or
+    $\alpha$ values for all models are shown, with naked stars as
+    black crosses, 1 Myr BDD systems as blue dots and 10 Myr BDD
+    systems as red dots. The dashed horizontal and vertical lines are
+    disc selections from the studies in question. The left panels are
+    the typical accretors and the right panels the extreme
+    accretors. The top three panels are IRAC CoCoDs and the bottom
+    panel plots the $\alpha$ value against run number (an arbitary
+    number).\label{disc_cuts}}
 \end{figure*}
 
-Figure \ref{disc_frac_alpha} shows that except for a few systems
-($~\frac{1}{50}$), all of which are typical accretors at edge-on
-inclinations, a cut of $\alpha>-$2 would identify all of our BDD
-systems. Furthermore, the \textit{top left} panel shows that for
-typically accreting systems there would be no significant bias in
-selection with accretion rate. The \textit{bottom left panel} shows
-that the lowest $\alpha$ values are only apparent for the edge-on
-systems. The \textit{right panels} of Figure \ref{disc_frac_alpha},
-show that for extreme accretors the systems are well above the disc
-discriminator line, and move to greater $\alpha$ values with
-increasing accretion rate.
-
-As can be seen from Figures \ref{irac_cut}, \ref{irac_cut_2} and
-\ref{irac_cut_3} almost all of the disc systems from our simulated
-photometry would be correctly identified using these cuts. It is
-important to note that our conclusions so far have been drawn from
-differential photometric arguments, in this case we are using
-intrinsic colours and these values are extremely sensitive to changes
-in zero point and photometric calibration. Figure \ref{irac_cut} shows
-that other than a few typically accreting systems the observational
-cut of \cite{2005ApJ...631L..69L} would select all of the BDD systems
-in our grid. Figure \ref{irac_cut_2} shows that the cut of
-\cite{2008ApJ...688..362L} would miss some typical and a very small
-number of extreme accreting BDD systems. Figure \ref{irac_cut_3} shows
-only very few BDD systems will be missed. The number of BDD systems
-not identified for Figure \ref{irac_cut_2} and \ref{irac_cut_3} is
-larger than that of \ref{irac_cut}, but these Figures show that there
-is no preferential selection based on age. A comparison between Figure
-\ref{irac_cut_2} and the \textit{bottom right panel} of Figure
-\ref{disc_frac_irac_typ}, shows that all of the missed BDD systems are
-edge-on systems. Given, that extreme reddening may move naked stars
-into the BDD region selected, in general, dis fractions are usually
-quoted as lower limits. Therefore, a small number of miss-identified
-BDD system is a small effect. This allows us to conclude, that
-ubiquitously used BDD cuts used in IRAC CoCoDs are reliable when
-applied to our simulated dataset.
-
-XXXINTRO TABLE MINISED NAKED CONTAMIANTIO LOWER LIMITS
+Figure \ref{disc_cuts} shows that the recent observational cuts used
+to identify disc candidates would be, in the main, reliable for our
+model grid. imulated photometry would be correctly identified using
+these cuts. It is important to note that our conclusions so far have
+been drawn from differential photometric arguments, in this case we
+are using intrinsic colours and these values are extremely sensitive
+to changes in zero point and photometric calibration. The top panel of
+Figure \ref{disc_cuts} shows that other than a few typically accreting
+systems the observational cut of \cite{luhman_2005b} would select all
+of the BDD systems in our grid. The second panel down shows that the
+cut of \cite{luhman_2008} would miss some typical and a very small
+number of extreme accreting BDD systems (almost all are edge-on
+systems). The third panel down shows only very few BDD systems will be
+missed by the selection of \cite{gutermuth_2008}. Finally, the
+selection for CTTS candidates of $\alpha>-$2 \citep{kennedy_2009}
+appears reasonably applicable to our BDD systems. As can be seen in
+the bottom panel of Figure \ref{disc_cuts} almost all the typical, and
+all of the extreme accreting BDD systems would be successfully
+identified using this criterion. Again the missed typically accreting
+systems are edge-on systems. Given, that extreme reddening may move
+naked stars into the BDD region selected, in general, disc fractions
+are usually quoted as lower limits. Therefore, a small number of
+miss-identified BDD system is a small effect. This allows us to
+conclude, that ubiquitously used BDD selections within IRAC CoCoDs are
+reliable when applied to our model grid. Additionally, the $\alpha$
+value would be a reliable disc indicator for our model grid.
+
+Using our model grid we can define the optimal cuts for selecting BDD
+systems. These are shown in Table \ref{cuts_table}, with the colour
+index, suggested cut chosen to minimise contanimation from naked
+stars, and the fraction of missed BDD systems.
 
@@
 \hline
-a(3.6-8.0)&$> -2.20$&26/4480=0.6\%\\
-irac\_3.6-irac\_4.5&$> +0.21$&201/4480=4.5\%\\
-irac\_3.6-irac\_5.8&$> +0.50$&12/4480=0.3\%\\
-irac\_4.5-irac\_5.8&$> +0.32$&9/4480=0.2\%\\
-irac\_4.5-irac\_8.0&$> +0.45$&7/4480=0.2\%\\
-irac\_5.8-irac\_8.0&$> +0.13$&13/4480=0.3\%\\
-irac\_8.0-mips\_24&$> -16.2$&0/4480=0.0\%\\
-mips\_24-mips\_70&$> +9.90$&2/4480=0.04\%\\
-mips\_70-mips\_160&$> -6.20$&0/4480=0.0\%\\
+$\alpha(3.6-8.0)_0$&$> -2.20$&26/4480=0.6\%\\
+$([3.5]-[4.5])_0$&$> +0.21$&201/4480=4.5\%\\
+$([3.5]-[5.8])_0$&$> +0.50$&12/4480=0.3\%\\
+$([4.5]-[5.8])_0$&$> +0.32$&9/4480=0.2\%\\
+$([4.5]-[8.0])_0$&$> +0.45$&7/4480=0.2\%\\
+$([5.8]-[8.0])_0$&$> +0.13$&13/4480=0.3\%\\
+$([8.0]-24)_0$&$> -16.2$&0/4480=0.0\%\\
+$(24-70)_0$&$> +9.90$&2/4480=0.04\%\\m
+$(70-160)_0$&$> -6.20$&0/4480=0.0\%\\
 \hline
@@
   dataset provide the best disc candidate selection with minimised
-  contamination. \label{par_space_table}}
+  contamination. \label{cuts_table}}
 \end{table*}
@@
 compared to CTTS. This has previously been explored by
-\cite{walker_2004}. However, in our study we have included a
-simple treatment of accretion. This leads to increased flaring as more
-flux reaches the outer disc, and subsequently lower opening angles for
-BDD systems with higher accretion rates. Furthermore, the addition of
-dust sublimation has shown that for BDD systems the inner disc
-location, temperature and vertical size \& shape also varies with
-accretion rate. The inner edge position is correlated with temperature
-for the lower accreting models as suggested by
-\cite{meyer_1997}. For the systems with higher accretion
-rates the inner edge temperature is weakly correlated with
-temperature, mainly due to the radial fall in density and therefore
-dust sublimation temperature. The inner disc edge, initially
-prescribed as a vertical wall, then becomes concave and finally convex
-as dust sublimation is increased (with increasing flux from higher
-rates of accretion).
-
-Subsequently, the SEDs of BD systems with typical accretion rates and
+\cite{walker_2004}. However, in our study we have included a simple
+treatment of accretion. This leads to increased flaring as more flux
+reaches the outer disc, and subsequently lower opening angles for BDD
+systems with higher accretion rates. Furthermore, the addition of dust
+sublimation has shown that for BDD systems the inner disc location,
+temperature and vertical size \& shape also varies with accretion
+rate. The inner edge position is correlated with temperature for the
+lower accreting models as suggested by \cite{meyer_1997}. For the
+systems with higher accretion rates the inner edge temperature is
+weakly correlated with temperature, mainly due to the radial fall in
+density and therefore dust sublimation temperature. The inner disc
+edge, initially prescribed as a vertical wall, then becomes concave
+and finally convex as dust sublimation is increased (with increasing
+flux from higher rates of accretion).
+
+Subsequently, the SEDs of BDD systems with typical accretion rates and
 associated discs, are changed significantly from the assumed
@@
 classify. In Section \ref{observables} we have shown that the BD
-photosphere becomes `swamped' or overwhelmed by the accretion flux for
-rates of $\dot{M}>$-9 log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$. The outer
-disc flaring observed in the BDD systems was shown to cause
-occultation and a subsequent, sharp, fall in flux at an inclination
-which decreases for more systems with higher accretion rates. The
-thermal direct flux emanating from the disc inner edge was found to
-fall less dramatically with inclination for the systems with a curved
-inner boundary, as expected from the work of
-\cite{tannirkulam_2007}.
+photosphere becomes veiled by the accretion flux for rates of
+\logmdot$>$-9. The outer disc flaring observed in the BDD systems was
+shown to cause occultation and a subsequent, sharp, fall in flux at an
+inclination which decreases for more systems with higher accretion
+rates. We have also shown that for extreme accretion rates the inner
+wall increases in size and becomes convex in shape. We have also shown
+that this leads to a greater dependence on inclination (at
+inclinations close to face-on) of the IR colours.
 
@@
 increasing accretion rate as more flux is intercepted by the inner
-edge and the inner edge becomes convex and `puffed up'. For more
-typically accreting BDD systems with vertical inner edges, the motion
-in a CMD, with inclination, is more disjointed.
+edge and the inner edge becomes convex and `puffed up'.
 
 In practice, however, most parameters for BDD systems are derived for
-populations. We have shown, in Section \ref{photometry} that
+populations. We have shown, in Section \ref{isochrones} that
 derivation of an \emph{isochronal} (or photometric) age from our
@@
 accelerate the gravitational contraction and make the star appear
-older \citep{tout_1999,siess_1999}, further
-scattering the apparent age of a coeval population.
-
-Concordantly, \emph{isochronal} derivations of mass and therefore
-IMFs, for our simulated photometry, of a coeval population of
-accreting BDs with associated discs, would be inaccurate and
-problematic. Again caused by the changes in the SEDs as a result of
-the accretion flux and increased occultation by the larger degree of
-flaring seen in BD discs \citep[for the latter, as found
-by][]{walker_2004}
+older \citep{tout_1999,siess_1999}, further scattering the apparent
+age of a coeval population.  Concordantly, \emph{isochronal}
+derivations of mass and therefore IMFs, for our simulated photometry,
+of a coeval population of accreting BDs with associated discs, would
+be inaccurate and problematic. Again caused by the changes in the SEDs
+as a result of the accretion flux and increased occultation by the
+larger degree of flaring seen in BD discs \citep[for the latter, as
+found by][]{walker_2004}
 
@@
 magnitudes than the shorter wavelength CIT \textit{JHK} passbands. In
-addition, we that the slope of the SED from 3.6 to 8.0\,$\mu$m, or
+addition, we that the slope of the SED from 3.6 to 8.0$\mu$m, or
 $\alpha$ value, is an effective disc indicator. We have also
@@
 colours and $\alpha$ values, and therefore a robust lower limit disc
-fraction.
+fraction. Cuts derived from our model grid which could be used as a
+guide for observational disc candidate selection are presented in
+Table \ref{cuts_table}.
 
@@
 rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
-\citep{muzerolle_2003,natta_2004,natta_2006}.
-This relationship has been extended into the BD mass regime in
-\cite{natta_2006}. However, arguments based on selection and
-detection thresholds have already cast this relation into doubt
-\citep{clarke_2006}. As we have shown in Section \ref{results}
-a relationship of this kind is self-reinforcing as lower mass objects
-with higher accretion rates have little chance of being correctly
-identified as such due to both the accretion flux and flared
-associated disc. Essentially, at present it is unclear how many BD
-stars are not included in this relationship due to misidentification.
-As explained in \cite{walker_2004}, BD systems with a disc,
-without including accretion effects, can have the characteristics of
-higher mass CTTS stars, due to increased disc flaring from a reduced
-surface gravity in the disc. The effects of accretion at typical or
-larger rates further exacerbate the situation both spectroscopically,
-as the photospheric flux essentially becomes swamped or completely
-veiled, and photometrically as the resulting colours and magnitudes
-are significantly shifted. Therefore, for our simulated dataset a
-relationship of this sort may well be derived, if typical methods are
-used to identify BD objects with discs and derive masses, ages and
-accretion rates, even though it is not present.
+\citep{muzerolle_2003,natta_2004,natta_2006}. This relationship has
+been extended into the BD mass regime in \cite{natta_2006}. However,
+arguments based on selection and detection thresholds have already
+cast this relation into doubt \citep{clarke_2006}. As we have shown in
+Section \ref{results} a relationship of this kind is self-reinforcing
+as lower mass objects with higher accretion rates have little chance
+of being correctly identified as such due to both the accretion flux
+and flared associated disc. Essentially, at present it is unclear how
+many BD stars are not included in this relationship due to
+misidentification. As explained in \cite{walker_2004}, BD
+systems with a disc, without including accretion effects, can have the
+characteristics of higher mass CTTS stars, due to increased disc
+flaring from a reduced surface gravity in the disc. The effects of
+accretion at typical or larger rates further exacerbate the situation
+both spectroscopically, as the photospheric flux essentially becomes
+swamped or completely veiled, and photometrically as the resulting
+colours and magnitudes are significantly shifted. Therefore, for our
+simulated dataset a relationship of this sort may well be derived, if
+typical methods are used to identify BD objects with discs and derive
+masses, ages and accretion rates, even though it is not present.
 
@@
 flaring, accretion and view over a range of inclinations any
-correlation is not apparent. The study of \cite{meyer_1997}
-used analytical prescribed flat discs. Whether, any correlation is
-apparent for such systems using our models is studied in an upcoming
-paper where we introduce a fitting tool to be used with the model grid
-and release a further set of models with analytic disc structures, and
-an increased parameter space.
+correlation is not apparent. The study of \cite{meyer_1997} used
+analytical prescribed flat discs.
+
+We have also modeled the same parameter space using various analytical
+disc structures as opposed to vertical hydrostatic
+equilibrium. Additionally, we are extending the parameter range of our
+grid. Finally, we have created an online fitting tool. All of which
+will be featured in upcoming publications.
 
@@
     not occur for systems with dust sublimation and vertical
-    hydrostatic equilibrium view over a range of inclinations.}
+    hydrostatic equilibrium viewed over a range of inclinations.}
 \item{Low mass, high accretion rate systems are likely to be
@@
 an appraisal of the component SED, i.e. showing the stellar direct
-flux, as can be seen in Figure \ref{disc_eg_173}.
+flux.
 

### 2010-05-25 BD_disc/paper.tex
Copy for Revision by TJH
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2282 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-XXXX Nathan - add disc structure equation here and remove walker references.
+XXX Nathan - add disc structure equation here and remove walker references.
 
@@
 density. This change in shape, as noted for Herbig Ae stars by
-\cite{tannirkulam_2007} XX CHECK FOR A CTTS REFERENCESXXX, will lead
+\cite{tannirkulam_2007} XXXCHECK FOR A CTTS REFERENCESXXX, will lead
 to changes in the characteristics of the SED, or derived IR excess,
@@
 
-**THIS SECTION NEEDS TO BE SORTED**
-
 As stated throughout this paper the data presented are available from
 a web page
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
-  disc}.
+\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.
 

### 2010-05-25 BD_disc/paper.tex
Small typo corrected
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2283 25464f21-6099-402c-b30a-640f1d40d38b
Small change to a table
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2284 25464f21-6099-402c-b30a-640f1d40d38b
To work on at home
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2285 25464f21-6099-402c-b30a-640f1d40d38b

@@
 actively accreting material
-\citep{jayawardhana_2003,mohanty_2004}. The accretion is
-thought to proceed via a magnetically-controlled funnel flow mechanism
-in which material from a truncated inner disc boundary falls onto the
-surface of the star along magnetic field lines
-\citep{camenzind_1990,koenigl_1991,mohanty_2008}.
+\citep{jayawardhana_2003,mohanty_2004}. The accretion is thought to
+proceed via a magnetically-controlled funnel flow mechanism in which
+material from a truncated inner disc boundary falls onto the surface
+of the star along magnetic field lines
+\citep{camenzind_1990,koenigl_1991,muzerolle_2003,mohanty_2008}.
 
@@
 \citep{dullemond_2001}. The density-dependent nature of the dust
-sublimation temperature \citep{pollack_1994} may also play a
-role in shaping the inner rim
-\citep{isella_2005,tannirkulam_2007}.
-
-As an aside, although we recognise that the inner hole in protostellar
-discs may be the result of giant planet formation or photoevaporation
-\citep{dahm_2009,najita_2007}, these two mechanisms
-should result in a negligible mass-accretion rate
-\citep{dahm_2009} and therefore would represent a distinct
+sublimation temperature \citep{pollack_1994} may also play a role in
+shaping the inner rim
+\citep{isella_2005,tannirkulam_2007}\footnote{Although we recognise
+  that the inner hole in protostellar discs may be the result of giant
+  planet formation or photoevaporation \citep{dahm_2009,najita_2007},
+  these two mechanisms should result in a negligible mass-accretion
+  rate \citep{dahm_2009} and therefore would represent a distinct
   evolutionary state of brown dwarf disc (BDD) sytems to that of the
-CTTS-like phase we are considering here.
+  CTTS-like phase we are considering here.}.
 
@@
 In surveys, particularly those attempting to discern the PMS disc
-fraction , this disentangling usually takes place using broad-band
+fraction this disentangling usually takes place using broad-band
 photometric measures and cuts in colour-colour or colour-magnitude
-space
-\citep{luhman_2005b,luhman_2008,gutermuth_2008}.
-The important quantity here is the separation in wavelength between
-the emission peaks for the stellar and thermal disc components, as it
-is these components which must be separated. For BDD systems it is
-likely that difficulties detecting the disc will be exacerbated by the
-lower temperatures of the photosphere and therefore the smaller
-separation in wavelength from the thermal disc emission component,
-compared to CTTS systems. Therefore, to derive disc fractions for BD
-populations we require detailed comparison models with which to guide
-disc candidate selection.
+space \citep{luhman_2005b,luhman_2008,gutermuth_2008}.  The important
+quantity here is the separation in wavelength between the emission
+peaks for the stellar and thermal disc components, as it is these
+components which must be isolated. For BDD systems it is likely that
+difficulties detecting the disc will be exacerbated by the lower
+temperatures of the photosphere and therefore the smaller separation
+in wavelength from the thermal disc emission component, compared to
+CTTS systems. Therefore, to derive disc fractions for BD populations
+we require detailed comparison models with which to guide disc
+candidate selection.
 
@@
 The complete model grid, with derived photometry and isochrones, is
-available online through our browsing tool
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
-which is described in Appendix \ref{website}.
+available online through our browsing
+tool\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
+  disc} which is described in Appendix \ref{website}.
 
@@
 atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2} {\rm \AA}^{-1}$)
-from 1200 to 2$\times$ 10$^7$ \AA. The spectra were subsequently
+from 1200 to 2$\times$10$^7$ \AA. The spectra were subsequently
 resampled onto 200 logarithmically spaced points. Careful inspection
@@
 stellar interior models used for this study are the `DUSTY00' models
-of \cite{chabrier_2000} combined with the `AMES-Dusty',
-atmospheric models of \cite{chabrier_2000}, which are all
-available online
-\footnote{http://perso.ens-lyon.fr/france.allard/}. For our $T_{\rm
-  eff}$ range of $\approx $3000\,K$<T_{\rm eff}<$1600\,K the
+of \cite{chabrier_2000} combined with the `AMES-Dusty', atmospheric
+models of \cite{chabrier_2000}, which are all available
+online\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
+$T_{\rm eff}$ range of $\approx $3000\,K$<T_{\rm eff}<$1600\,K the
 AMES-Dusty atmospheres are the most applicable (2700\,K$>T_{\rm
@@
 disc inner edge onto the surface of the star. $L_{\rm acc}$ is
-calculated according to \ref{Lacc},
+calculated according to,
 \begin{equation}
@@
 along magnetically channelled columns from the inner disc boundary.
-For CTTS stars, \cite{bouvier_2007} show that the magnetic
-truncation radius ($R_{\rm mag}$) is less than the co-rotation radius
-($R_{\rm co}$), where the angular Keplerian velocity of the
-disc is equal to the surface angular velocity of the central star.
-Calculations of the magnetic truncation radius depend on derivations
-of the surface magnetic field \citep{koenigl_1991}. This is
-currently unavailable for BD stars, due to increased molecular species
-obscuring the Zeeman splitting signatures, that are normally used to
-derive stellar surface magnetic fields. Therefore, for our model grid
-we have adopted an initial inner disc radius as the co-rotation
-radius,
+For CTTS stars, \cite{bouvier_2007} show that the magnetic truncation
+radius ($R_{\rm mag}$) is less than the co-rotation radius ($R_{\rm
+  co}$), where the angular Keplerian velocity of the disc is equal to
+the surface angular velocity of the central star.  Calculations of the
+magnetic truncation radius depend on derivations of the surface
+magnetic field \citep{koenigl_1991}. This is currently unavailable for
+BD stars, due to increased molecular species obscuring the Zeeman
+splitting signatures that are normally used to derive stellar surface
+magnetic fields. Therefore, for our model grid we have adopted an
+initial inner disc radius as the co-rotation radius,
 \begin{equation}
@@
 Section \ref{intro}, the inner disc can be cleared through a number of
-mechanisms, including binarity or Giant planet formation,
+mechanisms, including binarity or giant planet formation,
 photoevaporation or photoionisation of the disc and dust grain growth
@@
 dust sublimation is included (discussed in Section \ref{dust_edge}).
-However, the effects of binarity or Giant planet formation are
+However, the effects of binarity or giant planet formation are
 neglected. Further to the stellar mass and period required prior to
@@
 We have used the {\sc torus} radiative transfer code which is
-described in \cite{harries_2000}, including the subsequent
-refinements i.e.  addition of Adaptive-Mesh-Refinement (AMR)
-introduced in \cite{harries_2004}. {\sc torus} uses the method
-of \cite{lucy_1999} solve radiative equilibrium. The
-simulation also self-consistently solves the equation of
-\textit{vertical hydrostatic equilibrium} and dust sublimation for the
-disc (described in \cite{tannirkulam_2007}).
+described in \cite{harries_2000}, including the subsequent refinements
+i.e.  addition of Adaptive-Mesh-Refinement (AMR) introduced in
+\cite{harries_2004}. {\sc torus} uses the method of \cite{lucy_1999}
+solve radiative equilibrium. The simulation also self-consistently
+solves the equation of vertical hydrostatic equilibrium and dust
+sublimation for the disc \citep[described in][]{tannirkulam_2007}.
 
@@
 n(a)da=C_ia^{-q}\times exp^{[-(a/a_c)^p]}da
-\end{equation}.
-Where $n(a)da$ is the number of particles of size $a$ (within the
+\end{equation},
+where $n(a)da$ is the number of particles of size $a$ (within the
 increment $da$), $a_{\rm c}$ is the characteristic particle size, with
@@
 slight enhancement of the silicate feature (due to the relative
-abundance of Silicon increasing) which has little effect on the
+abundance of silicon increasing) which has little effect on the
 resulting SEDs. Figure \ref{albedo} shows the resulting albedo, and
@@
 \begin{figure}
-  \vspace*{174pt}
-  \special{psfile="Fig/albedo.ps"
-   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
+  \includegraphics[scale=0.3,angle=90]{./Fig/albedo.ps}
  \caption{Figures of the albedo (top panel), and scattering
@@
 For low-luminosity systems the dust sublimation radius ($R_{\rm sub}$)
-will be coincident with the co-rotation radius. However should
-the combined photospheric and accretion luminosities be sufficient the
+will be coincident with the co-rotation radius. However should the
+combined photospheric and accretion luminosities be sufficient the
 inner disc will be heated sufficiently that the dust close to the
-co-rotation radius will be sublimated, and we must account for this
-in our models. Furthermore, since the dust sublimation temperature has
-a density dependence \citep{pollack_1994}, it is both the location and {\em
-  shape} of the inner wall that can change (Isella ref; Tannirkulam ref).
+co-rotation radius will be sublimated, and we must account for this in
+our models. Furthermore, since the dust sublimation temperature has a
+density dependence \citep{pollack_1994}, it is both the location and
+{\em shape} of the inner wall that can change
+\citep{isella_2005,tannirkulam_2007}.
 
@@
 For our model grid we have adopted a gas-to-dust ratio, $\epsilon$, of
-100, and the gas population is assumed essentially static with a zero
-optical depth.
+100, and the gas population is assumed to be essentially static with a
+zero optical depth.
 
@@
 calibrated using zero points derived from the zero magnitude fluxes
-published in the IRAC handbook
-\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}
-and the MIPS instrument calibration website
-\footnote{http://ssc.spitzer.caltech.edu/mips/calib/}.
+published in the IRAC
+handbook\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}
+and the MIPS instrument calibration
+website\footnote{http://ssc.spitzer.caltech.edu/mips/calib/}.
 
@@
 disc thermal flux \citep{hartmann_1998} and, additionally, in a
-\textit{V, V-I} CMD, the reddening vector lies parallel to the pre-MS,
+\textit{V, V$-$I} CMD, the reddening vector lies parallel to the pre-MS,
 minimising any age effect of extinction uncertainty, \citep[for a full
@@
 stellar masses as for pre-MS objects the reddening vector, in for
-instance, a \textit{J, J-K} CMD, is almost perpendicular to the
+instance, a \textit{J, J$-$K} CMD, is almost perpendicular to the
 isochrones, minimising the mass effect of extinction uncertainties
@@
 period data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{mayne_2008}, is studied in \cite{scholz_2004}, where periods
+\citep{mayne_2008}, was studied in \cite{scholz_2004}, where periods
 are found over the range 5.78$-$74.4 hours ($\approx$ 0.24$-$3.1 days)
@@
 come from active accretion hot spots on the BD surface \citep[see][for
-discussion of variability causes]{bouvier_1995,herbst_2007},
+a discussion of variability causes]{bouvier_1995,herbst_2007},
 indicative of active accretion. All the studies mentioned infer a disc
 locking mechanism. Furthermore, \cite{scholz_2004} and
-\cite{scholz_2005} find evidence for a $mass\propto period$
+\cite{scholz_2005} find evidence for a mass$\propto$period
 relationship extending into the BD regime. Additionally,
@@
 Therefore, to create a set of useful models to help contextualise the
-observational constraints, for study of disc locking mechanisms, we
-must adopt a realistic, and bounding range of rotation rates. For our
+observational constraints for study of disc locking mechanisms, we
+must adopt a realistic and bounding range of rotation rates. For our
 model grid, and associated age range ($<$10 Myrs), we have selected
-0.5 and 5 days. With the limits set at at the approximate
-median of faster rotators and the edge of the slower rotators.
+0.5 and 5 days. With the limits set at at the approximate median of
+faster rotators and the edge of the slower rotators.
 
@@
 
-Previously studies modeling BD discs have adopted a range of
-disc mass fractions, for instance \citep{walker_2004} use 0.1,
-0.01 and 0.001$M_*$. \cite{wood_2002} fit observed spectra
-with modeled SEDs to derive a disc mass of 0.003$M_*$, for HH 30
-IRS. Subsequent derivations of disc masses have converged to within an
-order of magnitude, with the following specific results: 0.03$M_*$
+Previously studies modeling BD discs have adopted a range of disc mass
+fractions, for instance \citep{walker_2004} use 0.1, 0.01 and
+0.001$M_*$. \cite{wood_2002} fitted observed spectra with modeled SEDs
+to derive a disc mass of 0.003$M_*$, for HH 30 IRS. Subsequent
+derivations of disc masses have converged to within an order of
+magnitude, with the following specific results: 0.03$M_*$
 \citep[$\rho$ Ophiuchi,][]{natta_2002}, 0.055$M_*$ \citep[GM
@@
 310,][]{mohanty_2004} and 0.022$M_*$\citep[2MASS
-J04442713+2512164,][]{bouy_2008}. As the derived disc masses
-all have a similar order of magnitude we have adopted $M_{\rm
-  disc}\approx $0.01$M_*$. As changes in disc masses are expected to
-change the resulting SED less than perhaps, accretion rate for
-example, we have not varied the disc mass for this study. The results
-of simulations varying this parameter will be published in a future
-paper.
+J04442713+2512164,][]{bouy_2008}. As the derived disc masses all have
+a similar order of magnitude we have adopted $M_{\rm disc}\approx
+$0.01$M_*$. As changes in disc masses are expected to change the
+resulting SED less than perhaps, accretion rate for example, we have
+not varied the disc mass for this study. The results of simulations
+varying this parameter will be published in a future paper.
 
@@
 Discs around BD stars exhibit increased flaring, due to the reduced
-surface gravity in the disc \citep{walker_2004}. This
-increased flaring, and therefore larger scaleheight of the disc
-results in a smaller opening angle, when compared to higher mass stars
-and their circumstellar discs. As has been shown in
+surface gravity in the disc \citep{walker_2004}. This increased
+flaring, and therefore larger scaleheight of the disc results in
+obscuration on the star at lower inclinations, when compared to higher
+mass stars and their circumstellar discs. As has been shown in
 \cite{walker_2004} effects caused by variations in the system
@@
 compared to their higher mass analogues. Therefore, we have simulated
-ten observer to system inclination angles spaced evenly in
-$\cos i$ space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84
-and 90$^{\circ}$.
+ten observer to system inclination angles spaced evenly in $\cos i$
+space, namely, 0, 27, 39, 48, 56, 64, 71, 77, 84 and 90$^{\circ}$.
 
@@
 
-XXX NJM REWORD THIS
-
 In this Section we first discuss the physical structure, both density
@@
 
-XXX Nathan - add disc structure equation here and remove walker references.
-
 The initial density structure has the the disc surface density
 conserved, $\Sigma ^{\beta - \alpha}$. The initial scaleheight,
-$h\propto r^{\beta}$, where r is the radial distance from the star,
-and the density, $\rho \propto r^{-\alpha}$. The initial values of
-$\alpha$ and $\beta$ were 2.1 and 1.1 respectively. The values
-for $\alpha$ and $\beta$ were chosen to optimise resolution of the
+$h\propto r^{\beta}$ ($h=h_0(r/R_*)^{\beta}$ where h=scaleheight and
+r=radial coordinate), where r is the radial distance from the star,
+and the density, $\rho \propto r^{-\alpha}$ ($\rho
+=\rho_0\frac{R_*}{r}exp(-\frac{1}{2}[z/h(r)]^2)$ where h=scaleheight,
+r=radial coordinate and z=vertical coordinate). The initial values of
+$\alpha$ and $\beta$ were 2.1 and 1.1 respectively. The values for
+$\alpha$ and $\beta$ were chosen to optimise resolution of the
 vertically evolving disc, but minor variations are largely
@@
 radius, as opposed to the dust destruction radius used in
-\cite{walker_2004}. The initial disc scaleheight at 100\,AU,
-$h(100)$, was set to 25\,AU. As the simulation used vertical
-hydrostatic equilibrium and dust sublimation, both the disc
-scaleheight and inner edge location then evolved in the systems
-dependent on the input parameters. In this section we discuss the
-structure of the discs in terms of these two generated
-characteristics, i.e the disc scaleheight and inner edge location.
+\cite{walker_2004}. The initial disc scaleheight at 100\,AU, $h(100)$,
+was set to 25\,AU. As the simulation used vertical hydrostatic
+equilibrium and dust sublimation, both the disc scaleheight and inner
+edge location then evolved in the systems dependent on the input
+parameters. In this section we discuss the structure of the discs in
+terms of these two generated characteristics, i.e the disc scaleheight
+and inner edge location.
 
@@
 dust sublimation). These tests showed excellent agreement in density
-and temperature structure (as well as in the resultant SEDs). The
+and temperature structure, as well as in the resultant SEDs. The
 results of these tests were presented by \cite{walker_2006}. It is
@@
 \end{center}
- \caption{Figure showing the density structure ($\log \rho$) of the
+ \caption{XXXNJM REMOVE WHITESPACEXXXFigure showing the density structure ($\log \rho$) of the
    BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
@@
 the disc temperature structure and the mass of the central star, with
-the disc scaleheight $h\propto \frac{T_{\rm disc}}{M_*}^{1/2}$
+the disc scaleheight $h\propto (\frac{T_{\rm disc}}{M_*})^{1/2}$
 \citep{shakura_1973}. Recently however \cite{ercolano_2009} proposed
@@
 
-The results of \cite{allers_2006} show that above a mass of
-50$M_{\rm Jup}$ all objects (6/17) are better fit with flared
-discs. Whilst at masses below 50$M_{\rm Jup}$ only one object is better
-fit by the flared disc model, with the remaining objects (10/17)
-better fit with flat models. Whether, this result is statistically
-significant enough to assert a $h\propto M_*$ is doubtful as the
-fitting process contains, presumably two fixed scaleheight
-distributions. Therefore, for our study we continue to assume that our
-flared BDD systems will have larger characteristic scaleheights than
-typical CTTS systems.
+The results of \cite{allers_2006} show that above a mass of 50$M_{\rm
+  Jup}$ all objects (6/17) are better fit with flared discs. Whilst at
+masses below 50$M_{\rm Jup}$ only one object is better fit by the
+flared disc model, with the remaining objects (10/17) better fit with
+flat models. Whether, this result is statistically significant enough
+to assert a $h\propto M_*$ is doubtful as the fitting process contains
+(presumably) two fixed scaleheight distributions. Therefore, for our
+study we continue to assume that our flared BDD systems will have
+larger characteristic scaleheights than typical CTTS systems.
 
@@
 may be very much greater than the dust sublimation temperature
-($>10$\,kK, \citep{muzerolle_2003}), while dusty funnel flows are
+\citep[$>10$\,kK,][]{muzerolle_2003}, while dusty funnel flows are
 likely to be optically thick in the visible, which would lead to
@@
 
-In order to examine the effect of dust sublimation on our models we
-have measured the radius of the inner edge of the dust disc by
-integrating from the centre along the midplane until an optical depth
-of 2/3 (at 5500\AA) is reached. Figure \ref{inner_temp} shows the
-radial density distribution of the disc.  In this case the the final
-inner edge radius and therefore temperature is no longer strongly
-correlated with the rotation rate. Figure \ref{inner_temp} shows the
-final inner edge location ($R_{\rm inner}$, $R_*$) against the
-temperature of the inner wall ($T_{\rm inner}$, K). The left
-  panel shows the systems designated as typical accretors and the
-right panel those with extreme accretion rates.  For
-both panels the systems with rotation periods of 0.5 and 5
-days are plotted in red and blue respectively. Those systems where the
-change in inner radius was greater than 1$R_*$, and therefore classes
-as significantly sublimated, are plotted as crosses.
+For further analysis, and throughout the rest of this paper, we will
+seperate the systems into two groups. These groups are those systems
+with \logmdot$\leq-9$ and \logmdot$\geq-9$, classed as typical and
+extreme accretors. This distinction is based on the point at which the
+systems undergo significant sublimation ($\Delta R_{\rm
+  inner}>1R_*$). In order to examine the effect of dust sublimation on
+our models we have measured the radius of the inner edge of the dust
+disc by integrating from the centre along the midplane until an
+optical depth of 2/3 (at 5500\AA) is reached. Figure \ref{inner_temp}
+shows the radial density distribution of the disc.  In this case the
+the final inner edge radius and therefore temperature is no longer
+strongly correlated with the rotation rate. Figure \ref{inner_temp}
+shows the final inner edge location ($R_{\rm inner}$, $R_*$) against
+the temperature of the inner wall ($T_{\rm inner}$, K). The left panel
+shows the systems designated as typical accretors and the right panel
+those with extreme accretion rates.  For both panels the systems with
+rotation periods of 0.5 and 5 days are plotted in red and blue
+respectively. Those systems where the change in inner radius was
+greater than 1$R_*$, and therefore classes as significantly
+sublimated, are plotted as crosses.
 
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/inner_temp.ps"
-     hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+\includegraphics[scale=0.5,angle=90]{./Fig/inner_temp.ps}
    \caption{Figure showing data for the inner edge location ($R_{\rm
@@
 sublimation starts. However, in almost all cases the dust sublimation
-does not become significant until at least \logmdot=$-9$ (as discussed
-above).
+does not become significant until at least \logmdot = $-9$ (as
+discussed previously).
 
@@
 \label{observables}
-
-XXXNJM HAS RE-WRITTEN FROM HEREXXX
 
@@
 Disentangling the accretion and stellar photospheric flux, in order to
-derive accretion rates, becomes difficult as $T_{\rm acc} \to T_{\rm
-  eff}$, which for an acretion rate of -9 \logmdot, occurs at a
+derive accretion rates becomes difficult as $T_{\rm acc} \to T_{\rm
+  eff}$, which for an accretion rate of \logmdot = $-9$, occurs at a
 fractional coverages of 20 and 10\%, for rotation periods of 5 and 0.5
@@
 underlying photospheric features, and significantly change the peak
-flux levels. Heavy veiling of atomic bands is well observed in CTTS
+flux levels. Heavy veiling of atomic bands has been observed in CTTS
 systems \citep{kenyon_1995}.
@@
 \begin{figure*}
-  \vspace*{348pt}
-  \special{psfile="Fig/acc_dom.ps"
-   hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
+\includegraphics[scale=0.6,angle=90]{./Fig/acc_dom.ps}
 \caption{Figure showing the photospheric flux (log(ergs$/s/cm^2/{\rm
@@
   $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
-   fluxes from an accretion stream at the rates of \logmdot $=-8$,
-   $-9$ and $-12$ are shown as blue, black and red lines
-   respectively. The bottom panels show accretion for a star
-   rotating at 5 days, with the top panels showing that of
-   0.5 days. The left panels systems with an areal coverage
-   of 10\% and the right panels has 1\%. The vertical and
-   horizontal dashed lines (in the lower panels) denote the
+  fluxes from an accretion stream at the rates of \logmdot $=-8$, $-9$
+  and $-12$ are shown as blue, black and red lines respectively. The
+  bottom panels show accretion for a star rotating at 5 days, with the
+  top panels showing that of 0.5 days. The left panels systems with an
+  areal coverage of 10\% and the right panels has 1\%. The vertical
+  and horizontal dashed lines (in the lower panels) denote the
   approximate sensitivity ranges of our chosen $V$, $I$, $J$ and $K$
@@
 (in terms of optical photometry) with increasing accretion rates as
-expected \citep{gullbring_1998}.
+expected \citep{gullbring_1998}. The impact on the photometry of BDD
+systems is discussed in the next Section for individual stars and in
+Section \ref{isochrones} for populations.
 
@@
 \label{flare_inner_sec}
+
+**GOT HERE NEED NEW FIGURE FOR INNER EDGE, ALSO REVERSE ARGUMENTS**
 
@@
 and, therefore, significant changes to the SED. Increases in the
-inclination angle, for these systems, quickly lead a significant
-proportion of the stellar flux being intercepted, and reprocessed, by
+inclination angle for these systems quickly lead to a significant
+proportion of the stellar flux being intercepted and reprocessed by
 the highly flared disc. This reprocessing will lead to a change in the
@@
 
-\ref{flare_inner} shows the total SEDs for the BDD system of Figures
-\ref{flare_-12_183} and \ref{flare_-7_193} as the top and bottom
-panels respectively. The left panels show the flux over all the ten
-inclinations (see Table \ref{par_space_table}), with the dashed line
-showing the inclination at which a sharp fall in flux is seen. This
-inclination will be the angle at which the star and inner disc becomes
-obscured by the flared outer disc. These inclinations are 71$^{\circ}$
-and 56$^{\circ}$ for \logmdot=-12 and -7 respectively. This
-effectively means that for higher accretion rates a more significant
-fraction of the stars, in a given population, may have flux below a
-threshold detection limit. The right panel of Figure \ref{flare_inner}
-shows the angles of 0, 27, 39, and 48 $^{\circ}$, close to face
-on. Comparing the top and bottom panel show that flux levels for the
-higher accretion rate, with the larger and curved inner edge, vary
-more distinctly with inclination angle than the systems with a
-vertical wall. These trends although demonstrated for one subset are
-apparent throughout the grid, i.e.e for each mass and age. Whilst this
-effect is probably artificially enhanced for such extreme accretion
-rates it is illustrative of the general trend, notwithstanding
-complications from inner edge shape.
+Figure \ref{flare_inner} shows the total SEDs for the BDD system of
+Figures \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
+bottom panels respectively. The left panels show the flux over all the
+ten inclinations (see Table \ref{par_space_table}), with the dashed
+line showing the inclination at which a sharp fall in flux is
+seen. This inclination will be the angle at which the star and inner
+disc becomes obscured by the flared outer disc. These inclinations are
+71$^{\circ}$ and 56$^{\circ}$ for \logmdot = $-$12 and $-$7
+respectively. This effectively means that for higher accretion rates a
+more significant fraction of the stars, in a given population, may
+have flux below a threshold detection limit. The right panel of Figure
+\ref{flare_inner} shows the angles of 0, 27, 39, and 48 $^{\circ}$,
+close to face on. Comparing the top and bottom panel show that flux
+levels for the higher accretion rate, with the larger and curved inner
+edge, vary more distinctly with inclination angle than the systems
+with a vertical wall. These trends although demonstrated for one
+subset are apparent throughout the grid, i.e.e for each mass and
+age. Whilst this effect is probably artificially enhanced for such
+extreme accretion rates it is illustrative of the general trend,
+notwithstanding complications from inner edge shape.
 
@@
     shown as a dashed line, 71$^{\circ}$ and 56$^{\circ}$ for
-    \logmdot=-12 and -7 respectively. The right panels show only the
+    \logmdot = $-$12 and $-$7 respectively. The right panels show only the
     inclinations close to face on, i.e. 0, 27, 39, and 48 $^{\circ}$,
@@
 age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5 and an
-areal coverage of 10\%. The systems with accretion rates of \logmdot
--12, -9 and -7 are shown in black, red and blue, respectively, with
-the lowest panel omitting \logmdot =-9, and restricting the
+areal coverage of 10\%. The systems with accretion rates of \logmdot =
+$-$12, $-$9 and $-$7 are shown in black, red and blue, respectively,
+with the lowest panel omitting \logmdot = $-$9, and restricting the
 inclination to viewing angles close to face-on.  The top and middle
@@
     rotation rate of 0.5 days are shown as crosses. The systems with
-    accretion rates of \logmdot = -12, -9 and -7, are shown in black,
-    red and blue respectively. The lowest panel omits the \logmdot -9
+    accretion rates of \logmdot = $-$12, $-$9 and $-$7, are shown in black,
+    red and blue respectively. The lowest panel omits the \logmdot $-$9
     systems. The top and middle panels also the systems with the
@@
 Accretion flux was shown to dominate the underlying, intrinsic,
-photospheric SED for accretion rates of \logmdot=-9 (see Figure
+photospheric SED for accretion rates of \logmdot = $-$9 (see Figure
 \ref{acc_dom}). As one would expect this leads to significant changes
@@
 $M_V$. The move to brighter magnitudes becomes significant once the
-accretion rate exceeds \logmdot=-9. Again moving from the fast to slow
+accretion rate exceeds \logmdot = $-$9. Again moving from the fast to slow
 rotation period increases the potential energy released and in this
@@
 in the inclination dependence of the IR colour for large curved
-(\logmdot=-7) and smaller vertical (\logmdot=-12) inner walls. The
-$(J-K_0$ colour of the higher accretion rate system changes more as a
+(\logmdot = $-$7) and smaller vertical (\logmdot = $-$12) inner walls. The
+$(J-K)_0$ colour of the higher accretion rate system changes more as a
 function of inclination when compared to the lower accretion rate
 system. A total change in $(J-K)_0$ of $\approx$ 0.05 and 0.1 are
-found for \logmdot=-12 and -7 respectively. This doubling in the
+found for \logmdot = $-$12 and $-$7 respectively. This doubling in the
 change in IR colour as a function of inclination for viewing angles
@@
 \ref{disc_struct}), those with accretion rates typical for higher mass
-CTTS objects, defined as \logmdot=-12 (negligible) to \logmdot=-9 and
-those with elevated accretion rates, where \logmdot>-9. For several of
+CTTS objects, defined as \logmdot = $-$12 (negligible) to \logmdot = $-$9 and
+those with elevated accretion rates, where \logmdot $>-$9. For several of
 the plots in this section the magnitude and colours for the
@@
 For the derivation of ages optical CMDs, in particular in \textit{V,
-  V-I}, are most often used, and indeed most suitable. Whereas, IR
-CMDs, such as a \textit{J, J-K} CMD, are most suitable for mass
+  V$-$I}, are most often used, and indeed most suitable. Whereas, IR
+CMDs, such as a \textit{J, J$-$K} CMD, are most suitable for mass
 derivation \cite[see references and discussions in][ and Section
@@
 both figures shows stars classed as typical accretors with accretion
-rates of \logmdot=-9, -10 and -11 \& -12, shown as blue, black and red
-dots respectively in the top panels. The right panels of Figures
-\ref{age_mass_VVI} and \ref{age_mass_JJK} show systems with extreme
-accretion rates, with \logmdot=-6, 7 and -8 shown as blue, black and
-red dots respectively, in the top right panel. The bottom panels then
-show the systems seperated into groups by inclination. These groups
-are $\theta \leq 48^{\circ}$ as blue dots (classed as face-on
-systems), $\theta> 56$ \& $64^{\circ}$ (classed as the expected
-systems, as the expectation value of $cos(\theta)=60^{\circ}$) as
-black dots and $\theta \geq 71^{\circ}$ (classed as edge-on systems)
-as red dots (for typical, bottom left, and extreme, bottom right
-accretion rates). The left panels then show naked stars isochrones
-(created from our grid of simulated photometry) for 1 Myrs at
-accretion rates of \logmdot=-12 and -9, as solid and dashed lines
-respectively (with coverage of 10\% and rotation rates of 5
-days). Whereas the left hand panels show naked stars isochrones of
-\logmdot=-6 and -9 as solid and dashed black lines respectively (with
+rates of \logmdot = $-$9, $-$10 and $-$11 \& $-$12, shown as blue,
+black and red dots respectively in the top panels. The right panels of
+Figures \ref{age_mass_VVI} and \ref{age_mass_JJK} show systems with
+extreme accretion rates, with \logmdot = $-$6, $-$7 and $-$8 shown as
+blue, black and red dots respectively, in the top right panel. The
+bottom panels then show the systems seperated into groups by
+inclination. These groups are $\theta \leq 48^{\circ}$ as blue dots
+(classed as face-on systems), $\theta> 56$ \& $64^{\circ}$ (classed as
+the expected systems, as the expectation value of
+$cos(\theta)=60^{\circ}$) as black dots and $\theta \geq 71^{\circ}$
+(classed as edge-on systems) as red dots (for typical, bottom left,
+and extreme, bottom right accretion rates). The left panels then show
+naked stars isochrones (created from our grid of simulated photometry)
+for 1 Myrs at accretion rates of \logmdot = $-$12 and $-$9, as solid and
+dashed lines respectively (with coverage of 10\% and rotation rates of
+5 days). Whereas the left hand panels show naked stars isochrones of
+\logmdot = $-$6 and $-$9 as solid and dashed black lines respectively (with
 coverage of 10\% and rotation rates of 5 days. The solid green line,
-in the top panels, shows the 1 Myr isochrone of
-\cite{siess_2000} adjusted to a distance of 250pc and an
-extinction of $A_V=2$ mag, simulating a background population of CTTS
-stars.
+in the top panels, shows the 1 Myr isochrone of \cite{siess_2000}
+adjusted to a distance of 250pc and an extinction of $A_V=2$ mag,
+simulating a background population of CTTS stars.
 
@@
   \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
-    accretors (\logmdot $\leq$ -9) in the left panels, and extreme
+    accretors (\logmdot $\leq$ $-$9) in the left panels, and extreme
     accretors (\logmdot $>-9$) in the right panels. The black dashed
     and solid lines correspond to naked BD isochrones (from our grid)
-    with \logmdot -9 and -12 for the left panels (typical accretors)
-    and -9 and -6 in the right panels (extreme accretors). The
-    rotation rates and areal coverages are set at 5 days and 10\%
-    respectively (changing these has little effect). The top panels
-    also include as a solid green line the 1 Myr pre-MS isochrone of
-    \citet{siess_2000} adjusted to a distance modulus of 7 and an
-    extinction of $A_V=2$, simulating a reddened background
+    with \logmdot $-$9 and $-$12 for the left panels (typical
+    accretors) and -9 and -6 in the right panels (extreme
+    accretors). The rotation rates and areal coverages are set at 5
+    days and 10\% respectively (changing these has little effect). The
+    top panels also include as a solid green line the 1 Myr pre-MS
+    isochrone of \citet{siess_2000} adjusted to a distance modulus of
+    7 and an extinction of $A_V=2$, simulating a reddened background
     population. The top panels then seperate the systems by accretion
-    rate with \logmdot=-9, -10 and -11 \& -12 in the top left panel,
-    and \logmdot=-6, -7 and -8 in the top right panel, shown blue,
+    rate with \logmdot = $-$9, $-$10 and $-$11 \& $-$12 in the top left panel,
+    and \logmdot = $-$6, $-$7 and $-$8 in the top right panel, shown blue,
     black and red dots respectively for both cases. The lower panels
@@
     the same symbol meanings as Figure \ref{age_mass_VVI}, but for
-    $M_J$ and $(J-K)_0$ CMDs. However, for this Figure the \logmdot=-6
-    isochrone is not shown (lies significantly blueward of locus of
-    data), and the pre-MS isochrone of \citet{siess_2000}, has been
+    $M_J$ and $(J-K)_0$ CMDs. However, for this Figure the \logmdot =
+    $-$6 isochrone is not shown (lies significantly blueward of locus
+    of data), and the pre-MS isochrone of \citet{siess_2000}, has been
     smoothed.\label{age_mass_JJK}}
@@
 isochronal age or mass spread. Indeed, for many BDD systems even at
-nominal accretion rates of \logmdot= -11 or -12, for our simulations,
-the colours of these stars move significantly blueward of the expected
-BD locus in a $M_V$, $(V-I)_0$ CMD and redward in a $M_J$, $(J-K)_0$
-CMD. As, in the case of typical accretors, the input variables are in
-the range expected for a BD population, one could reasonably expect
-observed true BD locii to show a similar scatter. It is clear that
-even a wide photometric selection would not include all of, even the
-negligibly accreting systems at expected inclinations. Whilst the
-derivation of masses and ages for these objects will be
-difficult. Furthermore, for the higher accretion rates of -9 or -10
-\logmdot the movement of the star within the CMD will effectively move
-the star into the contamination region expected for background CTTS or
-MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$ 12-10, and as such the
-star would not be included in a photometrically selected BD
-sample. The solid green line, in the top panels of Figures
+nominal accretion rates of \logmdot = $-$11 or $-$12, for our
+simulations, the colours of these stars move significantly blueward of
+the expected BD locus in a $M_V$, $(V-I)_0$ CMD and redward in a
+$M_J$, $(J-K)_0$ CMD. As, in the case of typical accretors, the input
+variables are in the range expected for a BD population, one could
+reasonably expect observed true BD locii to show a similar scatter. It
+is clear that even a wide photometric selection would not include all
+of, even the negligibly accreting systems at expected
+inclinations. Whilst the derivation of masses and ages for these
+objects will be difficult. Furthermore, for the higher accretion rates
+of \logmdot = $-$9 or $-$10 the movement of the star within the CMD
+will effectively move the star into the contamination region expected
+for background CTTS or MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$
+12-10, and as such the star would not be included in a photometrically
+selected BD sample. The solid green line, in the top panels of Figures
 \ref{age_mass_VVI} and \ref{age_mass_JJK}, showing the 1 Myr isochrone
@@
 is a dearth of lower mass stars accreting at higher rates. We have
-shown that for accretion rates in the range \logmdot=-12 to -9 the BDD
-systems with higher accretion rates would be preferentially missed
-using photometric or isochronal selection. Furthermore, for the
+shown that for accretion rates in the range \logmdot = $-$12 to $-$9
+the BDD systems with higher accretion rates would be preferentially
+missed using photometric or isochronal selection. Furthermore, for the
 extreme accretors the BDD systems are scattered far from the
@@
 grid in a $(J-K)_0$, $(J-H)_0$ CoCoDs. In all panels all of the naked
-systems are shown as black crosses. The left panels show those
-systems with typical accretion rates and the right panels the extreme
+systems are shown as black crosses. The left panels show those systems
+with typical accretion rates and the right panels the extreme
 accretors. The top panels of Figure \ref{disc_frac_JHJK} then seperate
-the systems by accretion rate with \logmdot -9, -10 and -11 \& -12,
-and -6, -7 and -8, shown as blue, black and red dots respectively for
-the typical (top left panel) and extreme (top right panel) accretors.
-The bottom panels then shows the defined groups of inclination angles,
-with $\theta \leq 48^{\circ}$ as blue dots, $\theta> 56$ \&
-$64^{\circ}$ as black dots and $\theta \geq 71^{\circ}$ as red dots.
+the systems by accretion rate with \logmdot = $-$9, $-$10 and $-$11 \&
+$-$12, and -6, -7 and -8, shown as blue, black and red dots
+respectively for the typical (top left panel) and extreme (top right
+panel) accretors.  The bottom panels then shows the defined groups of
+inclination angles, with $\theta \leq 48^{\circ}$ as blue dots,
+$\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
+71^{\circ}$ as red dots.
 
@@
     (left panel) and extreme accreting (right panels) systems. The top
-    panels then seperate the accretion rates with \logmdot=-9, -10 and
-    -11 \& -12, and \logmdot=-6, -7 \& -8 shown as blue, black and red
-    dots respectively for the typical (top left panel) and extreme
-    (top right panel) accretors. The bottom panels then show the
-    systems with the inclinations $\theta \leq 48^{\circ}$ as blue
-    dots, $\theta> 56$ \& $64^{\circ}$ as black dots and $\theta \geq
-    71^{\circ}$ as red dots.\label{disc_frac_JHJK}}
+    panels then seperate the accretion rates with \logmdot = $-$9,
+    $-$10 and $-$11 \& $-$12, and \logmdot = $-$6, $-$7 \& $-$8 shown
+    as blue, black and red dots respectively for the typical (top left
+    panel) and extreme (top right panel) accretors. The bottom panels
+    then show the systems with the inclinations $\theta \leq
+    48^{\circ}$ as blue dots, $\theta> 56$ \& $64^{\circ}$ as black
+    dots and $\theta \geq 71^{\circ}$ as red
+    dots.\label{disc_frac_JHJK}}
 \end{figure*}
@@
 panels) there is a strong correlation of accretion rate and scatter
-from the naked stars. Additionally, the extreme acretors lie
+from the naked stars. Additionally, the extreme accretors lie
 significantly removed from the naked stars locus. There is a
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/disc_cuts.ps}
+  \includegraphics[scale=0.65,angle=90]{./Fig/disc_cuts.ps}
   \caption{Figure showing both from top to bottom, the disc candidate
@@
 
-\begin{table*}
+\begin{table}
 \begin{tabular}{|l|l|l|}
@@
 $([8.0]-24)_0$&$> -16.2$&0/4480=0.0\%\\
-$(24-70)_0$&$> +9.90$&2/4480=0.04\%\\m
+$(24-70)_0$&$> +9.90$&2/4480=0.04\%\\
 $(70-160)_0$&$> -6.20$&0/4480=0.0\%\\
@@
   contamination. \label{cuts_table}}
-\end{table*}
+\end{table}
 
@@
 photosphere becomes veiled by the accretion flux for rates of
-\logmdot$>$-9. The outer disc flaring observed in the BDD systems was
+\logmdot$>-$9. The outer disc flaring observed in the BDD systems was
 shown to cause occultation and a subsequent, sharp, fall in flux at an

### 2010-05-26 BD_disc/paper.tex
Still struggling with the inner edge stuff
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2286 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-**GOT HERE NEED NEW FIGURE FOR INNER EDGE, ALSO REVERSE ARGUMENTS**
+**GOT HERE NEED NEW FIGURE FOR INNER EDGE AND NUMBERS WRONG***
+CHANGE flareinner.ps and flareinnermag.ps
 
@@
 levels for the higher accretion rate, with the larger and curved inner
-edge, vary more distinctly with inclination angle than the systems
+edge, vary less distinctly with inclination angle than the systems
 with a vertical wall. These trends although demonstrated for one
-subset are apparent throughout the grid, i.e.e for each mass and
-age. Whilst this effect is probably artificially enhanced for such
-extreme accretion rates it is illustrative of the general trend,
-notwithstanding complications from inner edge shape.
+subset are apparent throughout the grid, i.e. for each mass and age.
 
@@
 XXXNOT SURE ABOUT THIS NEXT BIT, PERHAPS A LITTLE WEAKXXX
+**SENSE OF ARGUMENT RIGHT BUT NUMBERS WRONG***
 
@@
 in the inclination dependence of the IR colour for large curved
-(\logmdot = $-$7) and smaller vertical (\logmdot = $-$12) inner walls. The
-$(J-K)_0$ colour of the higher accretion rate system changes more as a
-function of inclination when compared to the lower accretion rate
-system. A total change in $(J-K)_0$ of $\approx$ 0.05 and 0.1 are
-found for \logmdot = $-$12 and $-$7 respectively. This doubling in the
-change in IR colour as a function of inclination for viewing angles
-close to face-on, is caused by the larger (vertically) and convex
-inner wall in the extreme accreting case. For the convex inner wall
-the effective emitting area one observes changes as a function of
-inclination, leading to this greater dependence of IR colour on
-inclination.
+(\logmdot = $-$7) and smaller vertical (\logmdot = $-$12) inner
+walls. The $(J-K)_0$ colour of the higher accretion rate system
+changes less as a function of inclination when compared to the lower
+accretion rate system. A total change in $(J-K)_0$ of $\approx$ 0.05
+and 0.1 are found for \logmdot = $-$12 and $-$7 respectively. This
+halving in the change in IR colour as a function of inclination for
+viewing angles close to face-on, is caused by the larger (vertically)
+and convex inner wall in the extreme accreting case. For the convex
+inner wall the effective emitting area one observes does not change as
+much as a vertical wall as a function of inclination, leading to this
+reduced dependence of IR colour on inclination.
 
@@
 wall increases in size and becomes convex in shape. We have also shown
-that this leads to a greater dependence on inclination (at
-inclinations close to face-on) of the IR colours.
-
-Subsequent derivation of photomertric magnitudes has allowed us to
+that this leads to a reducedq dependence on inclination (at
+inclinations close to face-on) of the IR colours, compared to a
+vertical wall.
+
+Subsequent derivation of photometric magnitudes has allowed us to
 demonstrate that, as expected, increased accretion without disc

### 2010-05-26 BD_disc/paper.tex
inner edge stuff ringfenced
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2287 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-**GOT HERE NEED NEW FIGURE FOR INNER EDGE AND NUMBERS WRONG***
-CHANGE flareinner.ps and flareinnermag.ps
-
 As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
@@
 
-Figure \ref{flare_inner} shows the total SEDs for the BDD system of
+Figure \ref{flare_inc} shows the total SEDs for the BDD system of
 Figures \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
-bottom panels respectively. The left panels show the flux over all the
-ten inclinations (see Table \ref{par_space_table}), with the dashed
-line showing the inclination at which a sharp fall in flux is
-seen. This inclination will be the angle at which the star and inner
-disc becomes obscured by the flared outer disc. These inclinations are
-71$^{\circ}$ and 56$^{\circ}$ for \logmdot = $-$12 and $-$7
-respectively. This effectively means that for higher accretion rates a
-more significant fraction of the stars, in a given population, may
-have flux below a threshold detection limit. The right panel of Figure
-\ref{flare_inner} shows the angles of 0, 27, 39, and 48 $^{\circ}$,
-close to face on. Comparing the top and bottom panel show that flux
-levels for the higher accretion rate, with the larger and curved inner
-edge, vary less distinctly with inclination angle than the systems
-with a vertical wall. These trends although demonstrated for one
-subset are apparent throughout the grid, i.e. for each mass and age.
+bottom panels respectively. The lines show the flux over all the ten
+inclinations (see Table \ref{par_space_table}), with the dashed line
+showing the inclination at which a sharp fall in flux is seen. This
+inclination will be the angle at which the star and inner disc becomes
+obscured by the flared outer disc. These inclinations are 71$^{\circ}$
+and 56$^{\circ}$ for \logmdot = $-$12 and $-$7 respectively. This
+effectively means that for higher accretion rates a more significant
+fraction of the stars, in a given population, may have flux below a
+threshold detection limit.
 
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inner.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc.ps}
   \caption{Figure showing both total SEDs of the systems shown in
     Figure \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
-    bottom panels respectively. The left panel shows all inclinations
-    (see Table \ref{par_space_table}), with the obscuration angle
-    shown as a dashed line, 71$^{\circ}$ and 56$^{\circ}$ for
-    \logmdot = $-$12 and $-$7 respectively. The right panels show only the
-    inclinations close to face on, i.e. 0, 27, 39, and 48 $^{\circ}$,
-    with a clear dependence on inclination of the flux levels for the
-    curved inner wall (lower right panel).\label{flare_inner}}
+    bottom panels respectively. The lines show the SEDs of all
+    inclinations (see Table \ref{par_space_table}), with the
+    obscuration angle shown as a dashed line, 71$^{\circ}$ and
+    56$^{\circ}$ for \logmdot = $-$12 and $-$7
+    respectively.\label{flare_inc}}
 \end{figure*}
@@
 the observed magnitudes and colours with inclination. Figure
-\ref{flare_inner_mag} shows the $M_V$ and $M_J$ magnitudes and the
-$(J-K)_0$ colour index, in the top, middle and bottom panels
-respectively. The colours and magnitudes are then marked as crosses as
-a function of inclination.  The systems shown in all panels have an
-age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5 and an
-areal coverage of 10\%. The systems with accretion rates of \logmdot =
-$-$12, $-$9 and $-$7 are shown in black, red and blue, respectively,
-with the lowest panel omitting \logmdot = $-$9, and restricting the
-inclination to viewing angles close to face-on.  The top and middle
-panels also show the system with the highest accretion rate but with a
-rotation rate of 5 days as a dashed line. The vertical dotted lines in
-the lowest panel simply illustrate the total change in magnitude, over
-the shown inclination range.
+\ref{flare_inc_mag} shows the $M_V$ and $M_J$ magnitudes in the top
+and bottom panels respectively. The magnitudes are then marked as
+crosses as a function of inclination. The systems shown in both panels
+have an age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5
+and an areal coverage of 10\%. The systems with accretion rates of
+\logmdot = $-$12, $-$9 and $-$7 are shown in black, red and blue,
+respectively. The panels also show the system with the highest
+accretion rate but with a rotation rate of 5 days as a dashed
+line. The vertical dotted lines in the lowest panel simply illustrate
+the total change in magnitude, over the shown inclination range.
 
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inner_mag.ps}
-  \caption{Figure showing $M_V$, $M_J$ magnitudes and $(J-K)_0$ colour
-    index as a function of inclination, shown as top, middle and lower
-    panels respectively. The magnitude and colours of systems with
-    $M_*=0.04M_{\odot}$, an age of 1 Myr, areal coverage of 10\% and
-    rotation rate of 0.5 days are shown as crosses. The systems with
-    accretion rates of \logmdot = $-$12, $-$9 and $-$7, are shown in black,
-    red and blue respectively. The lowest panel omits the \logmdot $-$9
-    systems. The top and middle panels also the systems with the
-    highest accretion rate but for a rotation rate of 5 days. The
-    lowest panel also shows, as horizontal dotted lines, the total
-    change of colour with the illustrated
-    inclinations. \label{flare_inner_mag}}
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc_mag.ps}
+  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
+    inclination, shown as top, middle and lower panels
+    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
+    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
+    days are shown as crosses. The systems with accretion rates of
+    \logmdot = $-$12, $-$9 and $-$7, are shown in black, red and blue
+    respectively. The panels also the systems with the highest
+    accretion rate but for a rotation rate of 5 days. The lowest panel
+    also shows, as horizontal dotted lines, the total change of colour
+    with the illustrated inclinations. \label{flare_inc_mag}}
 \end{figure*}
@@
 microns, where the accretion and photospheric flux dominate. This is
-shown in the top panel of Figure \ref{flare_inner_mag}. As the
-accretion rate increases the system moves to brighter magnitudes in
-$M_V$. The move to brighter magnitudes becomes significant once the
-accretion rate exceeds \logmdot = $-$9. Again moving from the fast to slow
+shown in the top panel of Figure \ref{flare_inc_mag}. As the accretion
+rate increases the system moves to brighter magnitudes in $M_V$. The
+move to brighter magnitudes becomes significant once the accretion
+rate exceeds \logmdot = $-$9. Again moving from the fast to slow
 rotation period increases the potential energy released and in this
@@
 increase in accretion rate affects these magnitudes, i.e. $M_J$ are
-les significantly affected. This is due to the significance of the
-inner edge at these longer wavelengths. The lowest panel shows that as
-the accretion rate is increase the IR colours generally get
-redder. Again, this is caused by interaction with the disc, as more
-flux is reprocessed by the inner edge.
-
-The top and middle panels of Figure \ref{flare_inner_mag} shows the
+less significantly affected. Figure \ref{flare_inc_mag} also shows the
 change in magnitude caused by obscuration from the flared outer
@@
 
-XXXNOT SURE ABOUT THIS NEXT BIT, PERHAPS A LITTLE WEAKXXX
-**SENSE OF ARGUMENT RIGHT BUT NUMBERS WRONG***
-
-The lowest panel of Figure \ref{flare_inner_mag} shows the difference
-in the inclination dependence of the IR colour for large curved
-(\logmdot = $-$7) and smaller vertical (\logmdot = $-$12) inner
-walls. The $(J-K)_0$ colour of the higher accretion rate system
-changes less as a function of inclination when compared to the lower
-accretion rate system. A total change in $(J-K)_0$ of $\approx$ 0.05
-and 0.1 are found for \logmdot = $-$12 and $-$7 respectively. This
-halving in the change in IR colour as a function of inclination for
-viewing angles close to face-on, is caused by the larger (vertically)
-and convex inner wall in the extreme accreting case. For the convex
-inner wall the effective emitting area one observes does not change as
-much as a vertical wall as a function of inclination, leading to this
-reduced dependence of IR colour on inclination.
+XXXTHIS SECTION IS ON THE INNER EDGE AND NEEDS SORTINGXXX
+179 
+221
+
+Figure \ref{inner_inc} shows the SEDs for the viewing angles of 0, 27,
+39, and 48 $^{\circ}$, close to face on. The top and bottom panels of
+Figure \ref{inner_inc} show SEDs for models with a curved, as
+exemplified by Figure \ref{flare_-7_193}, and flat inner wall, as
+shown in Figure \ref{flare_-12_183} respectively. The specific models
+chosen have been selected to minimise flux differences between the two
+SEDs but have distinct inner edges. XXXMODELSXXX Comparing the top and
+bottom panel show that flux levels for the higher accretion rate, with
+the larger and curved inner edge, vary less distinctly with
+inclination angle than the systems with a vertical wall.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/inner_inc.ps}
+  \caption{Figure showing SEDs of systems with a curved and flat inner
+    wall as the top and bottom panels respectively. The lines show the
+    SEDs at viewing angles of 0, 27, 39, and 48 $^{\circ}$, close to
+    face-on.\label{inner_inc}}
+\end{figure*}
+
+Figure \ref{inner_inc} shows only that for inclinations close to
+face-on, the curved inner edge has SEDs with a stronger dependence on
+the viewing angle compared to the model with a vertical inner
+wall. This leads to a greater dependence of IR colour with
+inclination.  Figure \ref{inner_mag} shows the difference in the
+inclination dependence of the IR colour for large curved and smaller
+vertical inner walls, for the systems shown in Figure
+\ref{inner_inc}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[scale=0.6,angle=90]{./Fig/inner_mag.ps}
+  \caption{Figure showing the $(J-K)_0$ colour against the
+    inclinations of 0, 27, 39, and 48 $^{\circ}$, for the models shown
+    in Figure \ref{inner_inc}. The models with the flat, vertical
+    inner wall and curved inner edge are shown as the solid and dashed
+    lines respectively. The horizontal dotted lines show the change in
+    the colour index.\label{inner_mag}}
+\end{figure*}
+
+The $(J-K)_0$ colour of the higher accretion rate system changes less
+as a function of inclination when compared to the lower accretion rate
+system. A total change in $(J-K)_0$ of $\approx$ XXXVALUESXXX are
+found for the model with the flat and curved inner edge
+respectively. This reduction in the change in IR colour as a function
+of inclination for viewing angles close to face-on, is caused by the
+larger (vertically) and convex inner wall in the extreme accreting
+case. For the convex inner wall the effective emitting area one
+observes does not change as much as a vertical wall as a function of
+inclination, leading to this reduced dependence of IR colour on
+inclination.
+
+XXXEVERYTHING IS FINE FROM HEREXXX
 
@@
 show that this occurs for inclinations above around 71$^{\circ}$ (as
-found in Figure \ref{flare_inner}) in most cases.  However, even for
+found in Figure \ref{flare_inc}) in most cases.  However, even for
 the lower inclination angles some objects have very faint magnitudes,
@@
 wall increases in size and becomes convex in shape. We have also shown
-that this leads to a reducedq dependence on inclination (at
+that this leads to a reduced dependence on inclination (at
 inclinations close to face-on) of the IR colours, compared to a

### 2010-05-27 BD_disc/paper.tex
Best copy up to date for TJH to check and submit
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2288 25464f21-6099-402c-b30a-640f1d40d38b

@@
 density. This change in shape, as noted for Herbig Ae stars by
-\cite{tannirkulam_2007} XXXCHECK FOR A CTTS REFERENCESXXX, will lead
-to changes in the characteristics of the SED, or derived IR excess,
-with inclination angle \citep{tannirkulam_2007}, for close to face on
-viewing angles.
+\cite{tannirkulam_2007}, will lead to changes in the characteristics
+of the SED, or derived IR excess, with inclination angle
+\citep{tannirkulam_2007}, for close to face on viewing angles.
 
@@
 the observed magnitudes and colours with inclination. Figure
-\ref{flare_inc_mag} shows the $M_V$ and $M_J$ magnitudes in the top
+\ref{flare_mag} shows the $M_V$ and $M_J$ magnitudes in the top
 and bottom panels respectively. The magnitudes are then marked as
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc_mag.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
   \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
@@
     also shows, as horizontal dotted lines, the total change of colour
-    with the illustrated inclinations. \label{flare_inc_mag}}
+    with the illustrated inclinations. \label{flare_mag}}
 \end{figure*}
@@
 microns, where the accretion and photospheric flux dominate. This is
-shown in the top panel of Figure \ref{flare_inc_mag}. As the accretion
+shown in the top panel of Figure \ref{flare_mag}. As the accretion
 rate increases the system moves to brighter magnitudes in $M_V$. The
@@
 increase in accretion rate affects these magnitudes, i.e. $M_J$ are
-less significantly affected. Figure \ref{flare_inc_mag} also shows the
+less significantly affected. Figure \ref{flare_mag} also shows the
 change in magnitude caused by obscuration from the flared outer
@@
 XXXTHIS SECTION IS ON THE INNER EDGE AND NEEDS SORTINGXXX
-179 
-221
 
@@
 Figure \ref{inner_inc} show SEDs for models with a curved, as
-exemplified by Figure \ref{flare_-7_193}, and flat inner wall, as
+exemplified by Figure \ref{flare_-7_193}, and a flat inner wall, as
 shown in Figure \ref{flare_-12_183} respectively. The specific models
 chosen have been selected to minimise flux differences between the two
-SEDs but have distinct inner edges. XXXMODELSXXX Comparing the top and
-bottom panel show that flux levels for the higher accretion rate, with
-the larger and curved inner edge, vary less distinctly with
-inclination angle than the systems with a vertical wall.
+SEDs but have distinct inner edges. The top panel has a mass of
+0.04$M_{\odot}$, \logmdot = -8, areal coverage of 1\%, a rotational
+period of 5 days and an age of 10 Myrs. The bottom panel has a the
+same model but with rotation period of 0.5 days and an age of 1
+Myrs. Comparing the top and bottom panel show that flux levels for the
+higher accretion rate, with the larger and curved inner edge, vary
+less distinctly with inclination angle than the systems with a
+vertical wall. Although this effect is marginal. The weakness of the
+effect is probably due to mismatches in the disc structure and flux
+levels. Ideally, we would take the curved inner edge model and replace
+the inner edge with a vertical wall.
 
@@
 inclination dependence of the IR colour for large curved and smaller
-vertical inner walls, for the systems shown in Figure
-\ref{inner_inc}.
+vertical inner walls, for the systems shown in Figure \ref{inner_inc}.
 
@@
 as a function of inclination when compared to the lower accretion rate
-system. A total change in $(J-K)_0$ of $\approx$ XXXVALUESXXX are
+system. A total change in $(J-K)_0$ of $\approx$ 0.6 and 0.05 are
 found for the model with the flat and curved inner edge
@@
 structure of the disc is a finer function of the input
-variables. XXXNJM TO CHECK THIS MORE NEEDEDXXX
+variables.
 

### 2010-05-27 BD_disc/paper.tex
Latest Version
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2289 25464f21-6099-402c-b30a-640f1d40d38b

@@
 inclination dependence of the IR colour for large curved and smaller
-vertical inner walls, for the systems shown in Figure \ref{inner_inc}.
+vertical inner walls (shown as blue and black lines respectively), for
+the systems shown in Figure \ref{inner_inc}. The dotted lines are
+illustrative of the total change in $(J-K)_0$.
 
@@
     in Figure \ref{inner_inc}. The models with the flat, vertical
-    inner wall and curved inner edge are shown as the solid and dashed
+    inner wall and curved inner edge are shown as the black and blue
     lines respectively. The horizontal dotted lines show the change in

### 2010-06-10 BD_disc/paper.tex
Newest Inner edge Figures
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2290 25464f21-6099-402c-b30a-640f1d40d38b
removed abstract stuff
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2291 25464f21-6099-402c-b30a-640f1d40d38b
Almost version
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2294 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \begin{abstract}
-To Do
-\begin{enumerate}
-\item{Read new papers and put in any relevant stuff.}
-\item{Sort structure paragraph at end of intro.}
-\end{enumerate}
+
+  We present a grid of simulated accreting brown dwarf systems with
+  (and without) circumstellar discs. These simulations include solving
+  for vertical hydrostatic and radiative equilibirum
+  self-consistently, and a sophisticated implementation of dust
+  sublimation. We have simulated observations of the spectral energy
+  distributions and using several broadband photometric systems. The
+  resulting magnitudes and spectra are publicly available.
+
+  Analysis of the disc structures and simulated observations reveal a
+  natural dichotomy in accretion rates, with \logmdot $>-$9 and $\leq
+  -$9 classed as extreme and typical accretors respectively. The
+  photospheric emissions of the extreme accretors are shown to be
+  heavily veiled, and significant sublimation of the dust disc is
+  apparent in these systems.
+
+  Derivation of ages and masses from our simulated photometry, using
+  isochrones, is demostrated to be unreliable even for typical
+  accretors. Current brown dwarf disc candidate selection criteria
+  have been shown to be largely reliable when applied to our model
+  grid, for both accretion regimes. However, we suggest improved
+  selection criteria in several colour indices, derived from our grid.
+
+  We also show that as accretion rates increase, due to photometric
+  scatter, brown dwarf disc systems are less likely to be correctly
+  identified. This suggests that, within our grid, systems with higher
+  accretion rates would be preferentially lost during brown dwarf
+  target selection. Therefore, we suggest that observations used to
+  assert a $\dot{M}\propto M_*^{\sim 2}$ relationship may contain an
+  intrinsic selection bias.
+
 \end{abstract}
@@
 spectrum has indicated that the accretion rate is strongly correlated
-with PMS mass,
-\citep{muzerolle_2003,natta_2004,natta_2006},
-with an approximate form $\dot{M_{\rm acc}}\propto M_{*}^{~2}$. Since
-in the canonical picture the accretion rate is driven by the disc
+with PMS mass, \citep{muzerolle_2003,natta_2004,natta_2006}, with an
+approximate form $\dot{M}_{\rm acc}\propto M^{\sim 2}_{*}$. Since in
+the canonical picture the accretion rate is driven by the disc
 viscosity, and should be indepedent of the mass of the central object,
@@
 correlation is the result of, or at least strengthened by, the
-presence of observational biases \citep{clarke_2006}: At the
-high-mass (CTTS) end of the mass spectrum the lowest accretion-rates
-cannot be measured via continuum methods since the excess is too small
-in contrast with the photopsheric emission. The emission lines will
-also be weak, and indeed the H$\alpha$ equivalent width (EW) may be
-less than the 10\AA\ that traditionally demarcates classical from
+presence of observational biases \citep{clarke_2006}: At the high-mass
+(CTTS) end of the mass spectrum the lowest accretion-rates cannot be
+measured via continuum methods since the excess is too small in
+contrast with the photopsheric emission. The emission lines will also
+be weak, and indeed the H$\alpha$ equivalent width (EW) may be less
+than the 10\AA\ that traditionally demarcates classical from
 weak-lined T Tauri stars. Such objects should show doppler-broadened
@@
 temperatures). Recently some continuum measurements of accreting BDs
-have been conducted \cite{herczeg_2009}, and these broadly support the H$\alpha$
-rates.
+have been conducted \cite{herczeg_2009}, and these broadly support the
+H$\alpha$ rates.
 
@@
 the BD photospheric luminosity and the accretion luminosity occurs at
-relatively low accretion rates \citep{clarke_2006}: Such objects may
-not be detected as BDs at all in photometric surveys. Even before such
-an extreme case is reached, the additional luminosity provided by the
-accretion should have measurable effect on the BD colours. Furthermore
-the additional flux will be reprocessed by the disc, altering its
-scaleheight and possibly the shape of its inner edge.
+relatively low accretion rates \citep{clarke_2006} and such objects
+may not be detected as BDs at all in photometric surveys. Even before
+such an extreme case is reached, the additional luminosity provided by
+the accretion should have measurable effect on the BD
+colours. Furthermore the additional flux will be reprocessed by the
+disc, altering its scaleheight and possibly the shape of its inner
+edge.
 
@@
 periodically variable candidates. They found projections of cooler
-spots, onto the stellar disc, of a few to $~$60\%.
+spots, onto the stellar disc, of a few to $\sim$60\%.
 \cite{bouvier_1995} also found projected sizes, onto the
@@
 \citep{muzerolle_2005} derived a relationship of approximately
-$\dot{M}\propto M_*^{~2}$. Further evidence was put forward by
+$\dot{M}\propto M_*^{\sim 2}$. Further evidence was put forward by
 \cite{natta_2004}, where accretion rates as low as 5$\times$
@@
 
-As the relationship $\dot{M}\propto M_*^{~2}$ predicts lower accretion
+As the relationship $\dot{M}\propto M_*^{\sim 2}$ predicts lower accretion
 rates for BD mass objects it is essential that we model systems at
@@
 
-The initial density structure has the the disc surface density
-conserved, $\Sigma ^{\beta - \alpha}$. The initial scaleheight,
-$h\propto r^{\beta}$ ($h=h_0(r/R_*)^{\beta}$ where h=scaleheight and
-r=radial coordinate), where r is the radial distance from the star,
-and the density, $\rho \propto r^{-\alpha}$ ($\rho
-=\rho_0\frac{R_*}{r}exp(-\frac{1}{2}[z/h(r)]^2)$ where h=scaleheight,
-r=radial coordinate and z=vertical coordinate). The initial values of
-$\alpha$ and $\beta$ were 2.1 and 1.1 respectively. The values for
-$\alpha$ and $\beta$ were chosen to optimise resolution of the
-vertically evolving disc, but minor variations are largely
+The disc surface density is conserved in the initial density
+structure, $\Sigma ^{\beta - \alpha}$. The initial scaleheight ($h$)
+and density ($\rho$) follow $h\propto r^{\beta}$
+($h=h_0(r/R_*)^{\beta}$) and $\rho \propto r^{-\alpha}$ ($\rho
+=\rho_0\frac{R_*}{r}exp(-\frac{1}{2}[z/h(r)]^2)$) respectively., where
+$r$ and $z$ are the radial and vertical coordinates. The initial
+values of $\alpha$ and $\beta$ were 2.1 and 1.1 respectively. The
+values for $\alpha$ and $\beta$ were chosen to optimise resolution of
+the vertically evolving disc, but minor variations are largely
 inconsequential as the systems evolves from this state. In our models
@@
 \end{center}
- \caption{XXXNJM REMOVE WHITESPACEXXXFigure showing the density structure ($\log \rho$) of the
+ \caption{Figure showing the density structure ($\log \rho$) of the
    BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
@@
 the disc temperature structure and the mass of the central star, with
-the disc scaleheight $h\propto (\frac{T_{\rm disc}}{M_*})^{1/2}$
+the disc scaleheight $h\propto (T_{\rm disc}/M_*)^{1/2}$
 \citep{shakura_1973}. Recently however \cite{ercolano_2009} proposed
@@
 flared disc model, with the remaining objects (10/17) better fit with
-flat models. Whether, this result is statistically significant enough
+flat models. Whether this result is statistically significant enough
 to assert a $h\propto M_*$ is doubtful as the fitting process contains
@@
 
-A  comparison of Figures \ref{flare_-12_183} and
-\ref{flare_-7_193} shows an increase in the scaleheight at 50\,AU of
-$>$5 AU, as the accretion rate moves from \logmdot =$-12$ to
-$-7$. However, despite this small change with high levels of accretion
-our grid shows scaleheights comparable to the work of
-\cite{walker_2004} and as such result in similar consequences for the
-SEDs and photometric magnitudes. The effects of this flaring and the
-increase in flaring for very high accretion levels on SEDs and
-photometric magnitudes are discussed in Sections \ref{observables}
-and \ref{isochrones}, respectively.
+A comparison of Figures \ref{flare_-12_183} and \ref{flare_-7_193}
+shows an increase in the scaleheight at 50\,AU of $>$5 AU, as the
+accretion rate moves from \logmdot =$-12$ to $-7$. However, despite
+this small change with high levels of accretion our grid shows
+scaleheights comparable to the work of \cite{walker_2004} and as such
+result in similar consequences for the SEDs and photometric
+magnitudes. The effects of this flaring and the increase in flaring
+for very high accretion levels on SEDs and photometric magnitudes are
+discussed in Sections \ref{observables} and \ref{isochrones}
+respectively.
 
@@
 underlying photospheric features, and significantly change the peak
-flux levels. Heavy veiling of atomic bands has been observed in CTTS
-systems \citep{kenyon_1995}.
+flux levels. Heavy veiling of atomic bands has been extensively
+observed in CTTS systems \citep[e.g][]{kenyon_1995}.
 
@@
 blackbody flux (for increasing accretion rates) for a BD star,
-$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photons originating from the
-star (both from $L_*$ and $L_{\rm acc}$) will be tagged as stellar by
-{\sc torus} we can separate these flux contributions simply by
-observing the naked star system. The panels in Figure \ref{acc_dom}
+$M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photon packets originating
+from the star (both from $L_*$ and $L_{\rm acc}$) will be tagged as
+stellar by {\sc torus} we can separate these flux contributions simply
+by observing the naked star system. The panels in Figure \ref{acc_dom}
 show the flux from a naked system, with no treatment of the disc. This
@@
 panels are \logmdot = $-8$, $-9$ and $-12$ (blue, black and red lines
-respectively). The bottom panels show the systems with a
-rotation period of 5 days and top panels for those with a
-rotation period of 0.5 days. Given our assumption that accretion
-occurs from the co-rotation radius, decreasing the rotational period
-moves this accretion radius closer to the star, $R_{\rm inner}\propto
-\tau^{2/3}$ (see Equation \ref{inner_eq}). As the accretion radius
-moves father from the star the potential energy released by the
-accreted material is increased. This effect can be seen
-when comparing the top and bottom panels, although
-the effect is marginal for all but the highest displayed accretion
-rates.
+respectively). The bottom panels show the systems with a rotation
+period of 5 days and top panels for those with a rotation period of
+0.5 days. Given our assumption that accretion occurs from the
+co-rotation radius, decreasing the rotational period moves this
+accretion radius closer to the star, $R_{\rm inner}\propto \tau^{2/3}$
+(see Equation \ref{inner_eq}). As the accretion radius moves father
+from the star the potential energy released by the accreted material
+is increased. This effect can be seen when comparing the top and
+bottom panels, although the effect is marginal for all but the highest
+displayed accretion rates.
 
@@
 
-XXXTHIS SECTION IS ON THE INNER EDGE AND NEEDS SORTINGXXX
-
 Figure \ref{inner_inc} shows the SEDs for the viewing angles of 0, 27,
@@
 less distinctly with inclination angle than the systems with a
-vertical wall. Although this effect is marginal. The weakness of the
-effect is probably due to mismatches in the disc structure and flux
-levels. Ideally, we would take the curved inner edge model and replace
-the inner edge with a vertical wall.
+vertical wall. The difference in inclination dependence of the fluxes
+between the curved and vertical inner walls is marginal. This is due
+to differences in the stellar flux levels and disc
+structures. Essentially we are not comparing like for like systems,
+ideally we would replace the curved inner edge with a vertical wall in
+an eample system and recalculate the temperature structure and SED.
 
@@
 
-XXXEVERYTHING IS FINE FROM HEREXXX
-
 Therefore, for individual systems changes in the accretion rate and
@@
 \ref{disc_struct}), those with accretion rates typical for higher mass
-CTTS objects, defined as \logmdot = $-$12 (negligible) to \logmdot = $-$9 and
-those with elevated accretion rates, where \logmdot $>-$9. For several of
-the plots in this section the magnitude and colours for the
-$M_*=0.01M_{\odot}$ systems at high inclinations become extremely
-faint and red. In some cases these objects appear slightly without the
-scale of the diagram the axes were limited in this way to be able to
-show the changes in colour and magnitude for the majority of stars
-better. The colours and magnitudes for these lowest mass stars are not
-necessarily unreliable but simply hinder the aesthetics of the plots,
-and as they are at the limits of our grid we have decided to omit them
-from some Figures by trimming the axes. Additionally, stars at the
-highest inclinations, i.e edge on disc systems, are often omitted from
-the Figures due to their extremely faint magnitudes, meaning they
-would not be practically observable.
+CTTS objects, defined as \logmdot = $-$12 (negligible) to \logmdot =
+$-$9 and those with elevated accretion rates, where \logmdot
+$>-$9. For several of the plots in this section the magnitude and
+colours for the $M_*=0.01M_{\odot}$ systems at high inclinations
+become extremely faint and red. As we are interested in the morphology
+of the population as a whole these systems are sometimes without the
+scale of the CMDs and CoCoDs. Additionally, stars at the highest
+inclinations, i.e edge on disc systems, are often omitted from the
+Figures due to their extremely faint magnitudes, meaning they would
+not be practically observable.
 
@@
 The use of pre-MS isochrones for the derivation of single star
-parameters is at the present time not proven to be reliable \citep[see
-discussion in][]{mayne_2008}. Practically, therefore, median
-ages are derived from populations. Subsequently, derived masses are
-still unreliable but at least based on a consistent age. This problem
-is being addressed by Bell et al (in prep), where $K$ band photometry
-and known eclipsing binaries are being used to refine pre-MS
+parameters is at present not proven to be reliable \citep[see
+discussion in][]{mayne_2008}. Practically, therefore, median ages are
+derived from populations. Subsequently, derived masses are still
+unreliable but at least based on a consistent age. This problem is
+being addressed by Bell et al (in prep), where $K$ band photometry and
+known eclipsing binaries are being used to refine pre-MS
 isochrones. In this section we plot the data for our 1 Myr systems
@@
 reasonably expect observed true BD locii to show a similar scatter. It
-is clear that even a wide photometric selection would not include all
-of, even the negligibly accreting systems at expected
+is clear that even a wide photometric selection would not even include
+all of the negligibly accreting systems at expected
 inclinations. Whilst the derivation of masses and ages for these
@@
 for background CTTS or MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$
-12-10, and as such the star would not be included in a photometrically
-selected BD sample. The solid green line, in the top panels of Figures
-\ref{age_mass_VVI} and \ref{age_mass_JJK}, showing the 1 Myr isochrone
-of \cite{siess_2000} at a distance of 250 pc and extinction of $A_V=2$
-mags shows that the BDD systems with higher accretion rates could
-easily be confused for a background CTTS or MS population. Indeed miss
-classification of a BDD system as a CTTS system has already been
-revealed in \cite{white_2003}. For the extreme accretors, as shown in
-the right panels of Figures \ref{age_mass_VVI} and \ref{age_mass_JJK},
-there is little chance of these objects being classed,
-photometrically, as BD candidates or being assigned the correct
-mass. Therefore, if one attempted to locate a population of BDD
-systems with elevated or extreme accretion rates, target selection
+12--10, and as such the star would not be included in a
+photometrically selected BD sample. The solid green line, in the top
+panels of Figures \ref{age_mass_VVI} and \ref{age_mass_JJK}, showing
+the 1 Myr isochrone of \cite{siess_2000} at a distance of 250 pc and
+extinction of $A_V=2$ mags shows that the BDD systems with higher
+accretion rates could easily be confused for a background CTTS or MS
+population. Indeed misclassification of a BDD system as a CTTS system
+has already been revealed in \cite{white_2003}. For the extreme
+accretors, as shown in the right panels of Figures \ref{age_mass_VVI}
+and \ref{age_mass_JJK}, there is little chance of these objects being
+classed, photometrically, as BD candidates or being assigned the
+correct mass. Therefore, if one attempted to locate a population of
+BDD systems with elevated or extreme accretion rates, target selection
 would have to be placed at much brighter magnitudes, and bluer for
@@
 show that this occurs for inclinations above around 71$^{\circ}$ (as
-found in Figure \ref{flare_inc}) in most cases.  However, even for
-the lower inclination angles some objects have very faint magnitudes,
-this is due to the disc flaring leading to a smaller opening angle and
-is discussed in Section \ref{disc_struct}. Crucially, the top panels
+found in Figure \ref{flare_inc}) in most cases.  However, even for the
+lower inclination angles some objects have very faint magnitudes, this
+is due to the disc flaring leading to earlier obscuration of the star
+as discussed in Section \ref{disc_struct}. Crucially, the top panels
 show that the scatter from the isochrone is, generally, correlated
@@
 and inclination, and therefore obscuration effects of the disc on the
-star. This suggests that for a given photometric survey of BDD systems
-accreting at typical accretion rates and with an expected range of
-inclinations (centred on around 60$^{\circ}$) one would expect to
-exclude a significant fraction of these objects from any isochrone
-based selection.
+star.
 
@@
 coeval population proportional to the range in accretion rates
-\citep[see][for full discussion]{mayne_2008}.  Our findings support
-and extend those of \cite{walker_2004}, showing that a significant
-scatter is caused by obscuration of the central source by the central
-disc, which (in our case) is in turn a function of accretion rate. In
-addition we have shown that the typical accretion rates may scatter
-BDD systems into the region of a CMD occupied by the CTTS or
-background MS locus.
+\citep[see][for full discussion]{mayne_2008}. In addition we have
+shown that the typical accretion rates may scatter BDD systems into
+the region of a CMD occupied by the CTTS or background MS locus.
 
@@
 Disc fractions have been derived using infrared excesses previously in
-\textit{JHK}, however recent works pre-dominantly use \textit{Spitzer}
-IRAC magnitudes. Furthermore, MIPS magnitudes are used to identify
-so-called debris discs, where IR excesses are not apparent at shorter
-wavelengths. Finally, disc fractions have also been derived using the
-$\alpha$ criteria, where $\alpha=\frac{dlog\lambda
-  F\lambda}{dlogF\lambda}$ between two limiting wavelengths,
-originally used to distinguish amongst Class I, II or II sources, but
-now used to detect disc presence \citep{lada_2006,kennedy_2009}. An
-$\alpha>$-2 is used as a selection criterion for disc presence for TTS
-stars. We have constructed the $\alpha$ values for our model grid by
-adopting the limiting wavelengths of \cite{kennedy_2009}, namely 3.6
-to 8.0$\mu$m.
+\textit{JHK} \citep[e.g][]{lada_1995,carpenter_1997}, however recent
+works pre-dominantly use \textit{Spitzer} IRAC magnitudes
+\citep[e.g][]{luhman_2005b,luhman_2008,gutermuth_2008}. Furthermore,
+MIPS magnitudes are used to identify so-called debris discs, where IR
+excesses are not apparent at shorter wavelengths
+\citep[e.g][]{currie_2008,bryden_2009}. Finally, disc fractions have
+also been derived using the $\alpha$ criteria, where
+$\alpha=\frac{dlog\lambda F\lambda}{dlogF\lambda}$ between two
+limiting wavelengths, originally used to distinguish amongst Class I,
+II or II sources, but now used to detect disc presence
+\citep{lada_2006,kennedy_2009}. An $\alpha>-2$ is used as a selection
+criterion for disc presence for TTS stars. We have constructed the
+$\alpha$ values for our model grid by adopting the limiting
+wavelengths of \cite{kennedy_2009}, namely 3.6 to 8.0$\mu$m.
 
@@
 the systems by accretion rate with \logmdot = $-$9, $-$10 and $-$11 \&
-$-$12, and -6, -7 and -8, shown as blue, black and red dots
+$-$12, and $-$6, $-$7 and $-$8, shown as blue, black and red dots
 respectively for the typical (top left panel) and extreme (top right
@@
 placing a colour-colour cut are viewed as lower limits this effect may
-be small. There is some evidence of a correlation of accretion rate
-and inclination with scatter from the naked star locus. However, if
-present this is weak. Our grid show no corelation in a CoCoD of this
-type with rotation rate. In the case of the extreme accretors (right
-panels) there is a strong correlation of accretion rate and scatter
-from the naked stars. Additionally, the extreme accretors lie
-significantly removed from the naked stars locus. There is a
-possiblity that some of these objects may be lost due to saturation
-and limiting magnitude effects. Again, as with mass and age
-derivation, the present figures are representative of similar figures
-using alternative, similar magnitudes.
+be small. Our grid show no corelation in a CoCoD of this type with
+rotation rate. In the case of the extreme accretors (right panels)
+there is a strong correlation of accretion rate and scatter from the
+naked stars. Additionally, the extreme accretors lie significantly
+removed from the naked stars locus. There is a possiblity that some of
+these objects may be lost due to saturation and limiting magnitude
+effects. Again, as with mass and age derivation, the present figures
+are representative of similar figures using alternative, similar
+magnitudes.
 
@@
 to identify disc candidates would be, in the main, reliable for our
-model grid. imulated photometry would be correctly identified using
+model grid. Simulated photometry would be correctly identified using
 these cuts. It is important to note that our conclusions so far have
@@
 are usually quoted as lower limits. Therefore, a small number of
-miss-identified BDD system is a small effect. This allows us to
+miss-identified BDD system is a negligible effect. This allows us to
 conclude, that ubiquitously used BDD selections within IRAC CoCoDs are
@@
 Using our model grid we can define the optimal cuts for selecting BDD
-systems. These are shown in Table \ref{cuts_table}, with the colour
-index, suggested cut chosen to minimise contanimation from naked
-stars, and the fraction of missed BDD systems.
+systems. These are shown in Table \ref{cuts_table}, where the defined
+cuts are chosen to minimise contanimation from naked stars.
 
@@
 models of \cite{chabrier_2000} combined with the `AMES-Dusty',
-atmospheric models of \cite{chabrier_2000}. We have then assumed
-that accretion occurs from an inner edge of a magnetically truncated
+atmospheric models of \cite{chabrier_2000}. We have then assumed that
+accretion occurs from an inner edge of a magnetically truncated
 accretion disc (truncated at the co-rotation radius). The accretion
@@
 we have modeled the disc using the TORUS radiative transfer code using
-the Lucy radiative transfer algorithm and incorporating dust
-sublimation and including a treatment of vertical hydrostatic
+the \cite{lucy_1999} radiative equilibrium algorithm and incorporating
+dust sublimation and including a treatment of vertical hydrostatic
 equilibrium (see Section \ref{model} for a discussion of the code). To
@@
 code our resulting simulated dataset has allowed us to qualitatively
-explore the effects of \emph{active} (current not past accretion)
-accretion on disc structure. Furthermore through the simulation of
-observations we have explored the effects of accretion, and disc
-presence, on both the SEDs, and photometric colours and magnitudes of
-these systems.
+explore the effects of \emph{active} (current not past) accretion on
+disc structure. Furthermore through the simulation of observations we
+have explored the effects of accretion, and disc presence, on both the
+SEDs, and photometric colours and magnitudes of these systems.
 
@@
 treatment of accretion. This leads to increased flaring as more flux
-reaches the outer disc, and subsequently lower opening angles for BDD
-systems with higher accretion rates. Furthermore, the addition of dust
-sublimation has shown that for BDD systems the inner disc location,
-temperature and vertical size \& shape also varies with accretion
-rate. The inner edge position is correlated with temperature for the
-lower accreting models as suggested by \cite{meyer_1997}. For the
-systems with higher accretion rates the inner edge temperature is
-weakly correlated with temperature, mainly due to the radial fall in
-density and therefore dust sublimation temperature. The inner disc
-edge, initially prescribed as a vertical wall, then becomes concave
-and finally convex as dust sublimation is increased (with increasing
-flux from higher rates of accretion).
+reaches the outer disc, and subsequently lower inclinations angles at
+which the central star is obscured for BDD systems with higher
+accretion rates. Furthermore, the addition of dust sublimation has
+shown that for BDD systems the inner disc location, temperature and
+vertical size \& shape also varies with accretion rate. The inner edge
+position is correlated with temperature for the lower accreting models
+as suggested by \cite{meyer_1997}. For the systems with higher
+accretion rates the inner edge temperature is weakly correlated with
+temperature, mainly due to the radial fall in density and therefore
+dust sublimation temperature. The inner disc edge, initially
+prescribed as a vertical wall, then becomes concave and finally convex
+as dust sublimation is increased (with increasing flux from higher
+rates of accretion).
 
@@
 exceedingly difficult. Indeed, the resulting photometric colours and
-magnitudes could be indicative of a more distant redenned CTTS
-population. For more extreme accretion rates the scatter, in CMD
-space, is significantly far from the pre-MS locus and as such these
-stars have little chance of being selected as BDs. As discussed in
-Section \ref{results} this does not include any effects due to past
-accretion on the evolution of the central star, which acts to
-accelerate the gravitational contraction and make the star appear
-older \citep{tout_1999,siess_1999}, further scattering the apparent
-age of a coeval population.  Concordantly, \emph{isochronal}
+magnitudes could be indicative of a more distant, and with higher
+extinction levels, CTTS population. For more extreme accretion rates
+the scatter, in CMD space, is significantly far from the pre-MS locus
+and as such these stars have little chance of being selected as
+BDs. As discussed in Section \ref{results} this does not include any
+effects due to past accretion on the evolution of the central star,
+which acts to accelerate the gravitational contraction and make the
+star appear older \citep{tout_1999,siess_1999}, further scattering the
+apparent age of a coeval population.  Concordantly, \emph{isochronal}
 derivations of mass and therefore IMFs, for our simulated photometry,
@@
 significantly, is the recent evidence for a stellar mass to accretion
-rate correlation, of the form: $\dot{M_{acc}}\propto M_{*}^{~2}$
+rate correlation, of the form: $\dot{M}_{acc}\propto M^{\sim 2}_{*}$
 \citep{muzerolle_2003,natta_2004,natta_2006}. This relationship has
@@
 many BD stars are not included in this relationship due to
-misidentification. As explained in \cite{walker_2004}, BD
-systems with a disc, without including accretion effects, can have the
+misidentification. As explained in \cite{walker_2004}, BD systems with
+a disc, without including accretion effects, can have the
 characteristics of higher mass CTTS stars, due to increased disc
@@
 grid. Finally, we have created an online fitting tool. All of which
-will be featured in upcoming publications.
-
-\subsection{Summary}
-\label{conc_summary}
-
-In summary, our simulated dataset shows that for typical parameter
-ranges for BD stars and BDD systems, disc presence and accretion flux
-lead to:
-
-Difficulty deriving the following stellar parameters for a coeval
-population:
-
-\begin{itemize}
-\item{Isochronal ages}
-\item{Isochronal masses}
-\item{IMFs}
-\end{itemize}
-
-And we have shown:
-\begin{itemize}
-\item{\textit{Spitzer} IRAC magnitudes are required for reliable disc
-    identification}
-\item{An expected correlation in inner disc edge with IR excess does
-    not occur for systems with dust sublimation and vertical
-    hydrostatic equilibrium viewed over a range of inclinations.}
-\item{Low mass, high accretion rate systems are likely to be
-    misidentified and therefore not included in any study relating
-    $M_*\propto\dot{M}$}
-\end{itemize}
-
-\section[]{ACKNOWLEDGMENTS}
+will be featured in upcoming publications. Finally, we intend to
+explore the efficacy of accretion rate diagnostics by simlating line
+profiles of accreting systems for a range of accretion rates.
+
+\section*{ACKNOWLEDGMENTS}
+The simulations in this work were peformed using the University of
+Exeter supercomputer, an SGI Altix ICE 8200. NJM and TJH were
+supported by STFC grant ST/F003277/1. We would also like to thank Dave
+Acreman for help with the practicality of running the model grid.
 

### 2010-06-11 BD_disc/paper.tex
mods by tim - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2296 25464f21-6099-402c-b30a-640f1d40d38b

@@
 
-  We present a grid of simulated accreting brown dwarf systems with
-  (and without) circumstellar discs. These simulations include solving
-  for vertical hydrostatic and radiative equilibirum
-  self-consistently, and a sophisticated implementation of dust
-  sublimation. We have simulated observations of the spectral energy
-  distributions and using several broadband photometric systems. The
-  resulting magnitudes and spectra are publicly available.
-
-  Analysis of the disc structures and simulated observations reveal a
-  natural dichotomy in accretion rates, with \logmdot $>-$9 and $\leq
-  -$9 classed as extreme and typical accretors respectively. The
-  photospheric emissions of the extreme accretors are shown to be
-  heavily veiled, and significant sublimation of the dust disc is
-  apparent in these systems.
-
-  Derivation of ages and masses from our simulated photometry, using
-  isochrones, is demostrated to be unreliable even for typical
-  accretors. Current brown dwarf disc candidate selection criteria
-  have been shown to be largely reliable when applied to our model
-  grid, for both accretion regimes. However, we suggest improved
-  selection criteria in several colour indices, derived from our grid.
-
-  We also show that as accretion rates increase, due to photometric
-  scatter, brown dwarf disc systems are less likely to be correctly
-  identified. This suggests that, within our grid, systems with higher
-  accretion rates would be preferentially lost during brown dwarf
-  target selection. Therefore, we suggest that observations used to
-  assert a $\dot{M}\propto M_*^{\sim 2}$ relationship may contain an
-  intrinsic selection bias.
+  We present a grid of models of accreting brown dwarf systems with
+  circumstellar discs. The calculations involve a self-consistent
+  solution of both vertical hydrostatic and radiative equilibirum
+  along with a sophisticated treatment of dust sublimation. We have
+  simulated observations of the spectral energy distributions and
+  several broadband photometric systems. Analysis of the disc
+  structures and simulated observations reveal a natural dichotomy in
+  accretion rates, with \logmdot $>-$9 and $\leq -$9 classed as
+  extreme and typical accretors respectively.  Derivation of ages and
+  masses from our simulated photometry using isochrones is demostrated
+  to be unreliable even for typical accretors. Although current brown
+  dwarf disc candidate selection criteria have been shown to be
+  largely reliable when applied to our model grid we suggest improved
+  selection criteria in several colour indices. We show that as
+  accretion rates increase brown dwarf disc systems are less likely to
+  be correctly identified. This suggests that, within our grid,
+  systems with higher accretion rates would be preferentially lost
+  during brown dwarf target selection. We suggest that observations
+  used to assert a $\dot{M}\propto M_*^2$ relationship may
+  contain an intrinsic selection bias.
 
@@
 \citep{camenzind_1990,koenigl_1991,muzerolle_2003,mohanty_2008}.
-
-The truncated inner-edge of the circumstellar disc receives direct
-photospheric radiation and is strongly heated. This leads to an
-increased scaleheight, or `puffing up' of the inner disc rim, and
-subsequent shadowing of the region immediately beyond it
-\citep{dullemond_2001}. The density-dependent nature of the dust
-sublimation temperature \citep{pollack_1994} may also play a role in
-shaping the inner rim
-\citep{isella_2005,tannirkulam_2007}\footnote{Although we recognise
-  that the inner hole in protostellar discs may be the result of giant
-  planet formation or photoevaporation \citep{dahm_2009,najita_2007},
-  these two mechanisms should result in a negligible mass-accretion
-  rate \citep{dahm_2009} and therefore would represent a distinct
-  evolutionary state of brown dwarf disc (BDD) sytems to that of the
-  CTTS-like phase we are considering here.}.
 
@@
 with PMS mass, \citep{muzerolle_2003,natta_2004,natta_2006}, with an
-approximate form $\dot{M}_{\rm acc}\propto M^{\sim 2}_{*}$. Since in
-the canonical picture the accretion rate is driven by the disc
-viscosity, and should be indepedent of the mass of the central object,
-this correlation is somewhat surprising. There is some danger that the
+approximate form $\dot{M}_{\rm acc}\propto M^2_*$. Since in the
+canonical picture the accretion rate is driven by the disc viscosity,
+and should be indepedent of the mass of the central object, this
+correlation is somewhat surprising. There is some danger that the
 correlation is the result of, or at least strengthened by, the
@@
 profiles, but the line wings will be weak, and the presence of
-underlying H$\alpha$ absorption may become dominant. Thus there may be
-a population of low-accretion-rate CTTS which are current missing from
-the surveys.
+underlying H$\alpha$ absorption may become dominant. Thus there may
+well be a population of low-accretion-rate CTTS which are current
+missing from the surveys.
 
@@
 accretion funnels in order to recover the level of emission that is
-observed \citep{muzerolle_2003,natta_2004,natta_2006}. (Cooling rate
-arguments can be invoked to explain the presence of such high
-temperatures). Recently some continuum measurements of accreting BDs
-have been conducted \cite{herczeg_2009}, and these broadly support the
-H$\alpha$ rates.
+observed \citep{muzerolle_2003,natta_2004,natta_2006}. Although
+cooling rate arguments can be invoked to explain the presence of such
+high temperatures, the line ratios of Pa$\beta$ and Br$\gamma$
+indicate that the hydrodgen emission may not arise in the funnel flows
+\citep{gatti_2006}. However, recently some continuum measurements of
+accreting BDs have been conducted \citep{herczeg_2009}, and these
+broadly support the H$\alpha$ rates.
 
@@
 
-In this section we briefly explain the key elements of the radiative
-transfer code used to model the BDD systems.
-
-We have used the {\sc torus} radiative transfer code which is
-described in \cite{harries_2000}, including the subsequent refinements
-i.e.  addition of Adaptive-Mesh-Refinement (AMR) introduced in
-\cite{harries_2004}. {\sc torus} uses the method of \cite{lucy_1999}
-solve radiative equilibrium. The simulation also self-consistently
-solves the equation of vertical hydrostatic equilibrium and dust
-sublimation for the disc \citep[described in][]{tannirkulam_2007}.
+We have used the {\sc torus} radiative transfer code which was
+originally described by \cite{harries_2000} and was subsequently
+updated by \cite{harries_2004} and \cite{kurosawa_2004}. {\sc torus}
+  uses the method of \cite{lucy_1999} solve radiative equilibrium on
+  an AMR mesh. The code also self-consistently solves the
+  equation of vertical hydrostatic equilibrium and dust sublimation
+  for the disc \citep[described in][]{tannirkulam_2007}. The {\sc
+    torus} code has been extensively benchmarked \citep{pinte_2009}.
 
@@
 We have adopted a similar dust model to \cite{wood_2002} 
-with the size distribution of dust particle given by,
+with the size distribution of dust particle given by
 \begin{equation}
@@
 n(a)da=C_ia^{-q}\times exp^{[-(a/a_c)^p]}da
-\end{equation},
+\end{equation}
 where $n(a)da$ is the number of particles of size $a$ (within the
@@
 reached by such inner walls are expected to generate thermal flux
-contributions within this wavelength range
-\citep{dullemond_2001}.
+contributions within this wavelength range \citep{dullemond_2001}. The
+circumstellar disc receives direct photospheric radiation and is
+strongly heated. This leads to an increased scaleheight, or `puffing
+up' of the inner disc rim, and subsequent shadowing of the region
+immediately beyond it \citep{dullemond_2001}. The density-dependent
+nature of the dust sublimation temperature \citep{pollack_1994} may
+also play a role in shaping the inner rim
+\citep{isella_2005,tannirkulam_2007}\footnote{Although we recognise
+  that the inner hole in protostellar discs may be the result of giant
+  planet formation or photoevaporation \citep{dahm_2009,najita_2007},
+  these two mechanisms should result in a negligible mass-accretion
+  rate \citep{dahm_2009} and therefore would represent a distinct
+  evolutionary state of brown dwarf disc (BDD) sytems to that of the
+  CTTS-like phase we are considering here.}.
 
@@
 used explicitly in the analysis within this paper. These magnitudes
-are available online
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
+are available online\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
 and are briefly discussed in Appendix \ref{website}. In addition,
@@
 locking mechanism. Furthermore, \cite{scholz_2004} and
-\cite{scholz_2005} find evidence for a mass$\propto$period
+\cite{scholz_2005} find evidence for a mass $\propto$ period
 relationship extending into the BD regime. Additionally,
 \cite{joergens_2003} propose a shorter lifetime of $\approx$5 Myrs for
-BD discs, inferred from a shorter derived disc locking
+BD discs, inferred from a shorter derived disc-locking
 timescale. However, as discussed in the previous studies, an imperfect
@@
 \citep{muzerolle_2005} derived a relationship of approximately
-$\dot{M}\propto M_*^{\sim 2}$. Further evidence was put forward by
+$\dot{M}\propto M_*^2$. Further evidence was put forward by
 \cite{natta_2004}, where accretion rates as low as 5$\times$
-10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More recently,
-even lower accretion rates of $\approx$10$^{-13}M_{\odot} yr^{-1}$,
+10$^{-12} {\rm M}_{\odot} {\rm yr}^{-1}$ were found for BD stars. More recently,
+even lower accretion rates of $\approx$10$^{-13} {\rm M}_{\odot} {\rm yr}^{-1}$,
 have been derived for BDs by \cite{herczeg_2009}.  Further support for
@@
 
-As the relationship $\dot{M}\propto M_*^{\sim 2}$ predicts lower accretion
+As the relationship $\dot{M}\propto M_*^2$ predicts lower accretion
 rates for BD mass objects it is essential that we model systems at
@@
 0.001$M_*$. \cite{wood_2002} fitted observed spectra with modeled SEDs
-to derive a disc mass of 0.003$M_*$, for HH 30 IRS. Subsequent
+to derive a disc mass of 0.003$M_*$  for HH~30 IRS. Subsequent
 derivations of disc masses have converged to within an order of
@@
 material in the disc falls with increasing radius from the star
-($\rho(r) \propto r^{\alpha}$), and that the dust sublimation
+($\rho(r) \propto r^{-\alpha}$), and that the dust sublimation
 temperature is density dependent \citep{pollack_1994}.  Therefore, for
@@
 extreme accretors. This distinction is based on the point at which the
-systems undergo significant sublimation ($\Delta R_{\rm
-  inner}>1R_*$). In order to examine the effect of dust sublimation on
-our models we have measured the radius of the inner edge of the dust
-disc by integrating from the centre along the midplane until an
-optical depth of 2/3 (at 5500\AA) is reached. Figure \ref{inner_temp}
-shows the radial density distribution of the disc.  In this case the
-the final inner edge radius and therefore temperature is no longer
-strongly correlated with the rotation rate. Figure \ref{inner_temp}
-shows the final inner edge location ($R_{\rm inner}$, $R_*$) against
-the temperature of the inner wall ($T_{\rm inner}$, K). The left panel
-shows the systems designated as typical accretors and the right panel
-those with extreme accretion rates.  For both panels the systems with
-rotation periods of 0.5 and 5 days are plotted in red and blue
-respectively. Those systems where the change in inner radius was
-greater than 1$R_*$, and therefore classes as significantly
-sublimated, are plotted as crosses.
+systems undergo both significant sublimation ($\Delta R_{\rm
+  inner}>1R_*$) and have an accretion luminosity that is comparible to
+the photospheric luminosity (see Section~\ref{acc_dominance}). In
+order to examine the effect of dust sublimation on our models we have
+measured the radius of the inner edge of the dust disc by integrating
+from the centre along the midplane until an optical depth of 2/3 (at
+5500\AA) is reached. Figure \ref{inner_temp} shows the radial density
+distribution of the disc.  In this case the the final inner edge
+radius and therefore temperature is no longer strongly correlated with
+the rotation rate. Figure \ref{inner_temp} shows the final inner edge
+location ($R_{\rm inner}$, $R_*$) against the temperature of the inner
+wall ($T_{\rm inner}$, K). The left panel shows the systems designated
+as typical accretors and the right panel those with extreme accretion
+rates.  For both panels the systems with rotation periods of 0.5 and 5
+days are plotted in red and blue respectively. Those systems where the
+change in inner radius was greater than 1$R_*$, and therefore classes
+as significantly sublimated, are plotted as crosses.
 
@@
 underlying photospheric features, and significantly change the peak
-flux levels. Heavy veiling of atomic bands has been extensively
+flux levels. Heavy veiling of atomic lines has been extensively
 observed in CTTS systems \citep[e.g][]{kenyon_1995}.
@@
 as Equations \ref{Lacc} and \ref{Tacc}, show, $L_{\rm acc}\propto 1-
-\frac{R_*}{R_{\rm inner}}$ and $T_{\rm acc}\propto (\frac{L_{\rm
-    acc}}{A})^{\frac{1}{4}}$. Therefore, the temperature of the
+\frac{R_*}{R_{\rm inner}}$ and $T_{\rm acc}\propto (L_{\rm
+    acc}/A)^{\frac{1}{4}}$. Therefore, the temperature of the
 accretion hot spot increases as the rotational period increases, due
@@
 in the shape of the inner edge, where the temperature is
-sufficient. Figures \ref{no_sub_183_a} to \ref{sub_179_a}
+sufficient. Figures \ref{no_sub_183_a}, \ref{sub_179_a} and
 \ref{sub_181_a} show a range in inner edge shapes, from flat walls
@@
 Figure \ref{inner_inc} shows the SEDs for the viewing angles of 0, 27,
-39, and 48 $^{\circ}$, close to face on. The top and bottom panels of
-Figure \ref{inner_inc} show SEDs for models with a curved, as
-exemplified by Figure \ref{flare_-7_193}, and a flat inner wall, as
-shown in Figure \ref{flare_-12_183} respectively. The specific models
-chosen have been selected to minimise flux differences between the two
-SEDs but have distinct inner edges. The top panel has a mass of
-0.04$M_{\odot}$, \logmdot = -8, areal coverage of 1\%, a rotational
-period of 5 days and an age of 10 Myrs. The bottom panel has a the
-same model but with rotation period of 0.5 days and an age of 1
-Myrs. Comparing the top and bottom panel show that flux levels for the
-higher accretion rate, with the larger and curved inner edge, vary
-less distinctly with inclination angle than the systems with a
-vertical wall. The difference in inclination dependence of the fluxes
-between the curved and vertical inner walls is marginal. This is due
-to differences in the stellar flux levels and disc
-structures. Essentially we are not comparing like for like systems,
-ideally we would replace the curved inner edge with a vertical wall in
-an eample system and recalculate the temperature structure and SED.
+39, and 48$^{\circ}$. The top and bottom panels of Figure
+\ref{inner_inc} show SEDs for models with a curved, as exemplified by
+Figure \ref{flare_-7_193}, and a flat inner wall, as shown in Figure
+\ref{flare_-12_183} respectively. The specific models chosen have been
+selected to minimise flux differences between the two SEDs but have
+distinct inner edges. The top panel has a mass of 0.04$M_{\odot}$,
+\logmdot = -8, areal coverage of 1\%, a rotational period of 5 days
+and an age of 10 Myrs. The bottom panel has a the same model but with
+rotation period of 0.5 days and an age of 1 Myrs. Comparing the top
+and bottom panel show that flux levels for the higher accretion rate,
+with the larger and curved inner edge, vary less distinctly with
+inclination angle than the systems with a vertical wall. The
+difference in inclination dependence of the fluxes between the curved
+and vertical inner walls is marginal. This is due to differences in
+the stellar flux levels and disc structures.
 
@@
     wall as the top and bottom panels respectively. The lines show the
-    SEDs at viewing angles of 0, 27, 39, and 48 $^{\circ}$, close to
-    face-on.\label{inner_inc}}
+    SEDs at viewing angles of 0, 27, 39, and 48$^{\circ}$.
+\label{inner_inc}}
 \end{figure*}
@@
   \caption{Figure showing the $(J-K)_0$ colour against the
-    inclinations of 0, 27, 39, and 48 $^{\circ}$, for the models shown
+    inclinations of 0, 27, 39, and 48$^{\circ}$, for the models shown
     in Figure \ref{inner_inc}. The models with the flat, vertical
@@
 photometry and subsequently constructed colour-magnitude and
-colour-colour diagrams (CMDs and CoCoDs respectively, hereafter).
-Therefore, in this Section, we demonstrate the prohibitive effects on
-the broadband photometry of varying our input parameters. In this
-Section we explore the consequences of our model grid on the
+colour-colour diagrams (CMDs and CoCoDs respectively, hereafter).  In
+this Section we explore the consequences of our model grid on the
 derivation of the primary parameters of age, mass and disc fractions,
@@
 colours for the $M_*=0.01M_{\odot}$ systems at high inclinations
-become extremely faint and red. As we are interested in the morphology
-of the population as a whole these systems are sometimes without the
-scale of the CMDs and CoCoDs. Additionally, stars at the highest
-inclinations, i.e edge on disc systems, are often omitted from the
-Figures due to their extremely faint magnitudes, meaning they would
-not be practically observable.
+become extremely faint and red, and we omit them from the Figures in
+order to conserve an appropriate scaling for the majority of the
+models. Additionally, stars at the highest inclinations, i.e edge on
+disc systems, are often omitted from the Figures due to their
+extremely faint magnitudes, meaning they would not be practically
+observable.
 
@@
     and solid lines correspond to naked BD isochrones (from our grid)
-    with \logmdot $-$9 and $-$12 for the left panels (typical
+    with \logmdot\ $-$9 and $-$12 for the left panels (typical
     accretors) and -9 and -6 in the right panels (extreme
@@
 as discussed in Section \ref{disc_struct}. Crucially, the top panels
-show that the scatter from the isochrone is, generally, correlated
+show that the scatter from the isochrone is generally correlated
 with accretion rate. Effectively, as the accretion rate increases the
@@
 
-Therefore, if one adopts the range of input parameters we have used
-(see Section \ref{par_space} for justification), our simulated
-photometry shows, qualitatively, that a coeval 1 Myr population of
-accreting BD stars and BDD systems, with typical accretion rates and
-range of inclinations, will exhibit a significant scatter in apparent
+If one adopts the range of input parameters we have used (see Section
+\ref{par_space} for justification), our simulated photometry shows,
+qualitatively, that a coeval 1 Myr population of accreting BD stars
+and BDD systems, with typical accretion rates and range of
+inclinations, will exhibit a significant scatter in apparent
 isochronal age. Furthermore, objects with typical (and extreme)
@@
 suggests that the observed result may be caused by intrinsic
-scattering. The relation, $\dot{M}\propto M_*^{2}$ suggests that their
+scattering. The relation $\dot{M}\propto M_*^{2}$ suggests that their
 is a dearth of lower mass stars accreting at higher rates. We have
@@
 greater radial distance from the star. As photometric emission is
-minimal past around three $\mu$m, systems with discs will have
+minimal past around 3\,$\mu$m, systems with discs will have
 significantly different SEDs from naked systems.
@@
 then produced for both naked BDs and BDD systems. For the BDD systems
-we have modeled the disc using the TORUS radiative transfer code using
-the \cite{lucy_1999} radiative equilibrium algorithm and incorporating
-dust sublimation and including a treatment of vertical hydrostatic
-equilibrium (see Section \ref{model} for a discussion of the code). To
-produce a `grid' of simulated systems we have varied several input
-parameters namely: stellar mass, stellar age, stellar rotation rate,
-accretion rate, the areal coverage of the accretion stream and the
-system inclination (the disc mass was fixed). The ranges of these
-variables were selected to represent and bound typical pre-MS BD
-systems, justification is provided using evidence from observational
-studies in Section \ref{par_space} and a final list of the values of
-these variables can be found in Table \ref{par_space_table}.
+we have modeled the disc using the {\sc torus} radiative transfer code
+using the \cite{lucy_1999} radiative equilibrium algorithm and
+incorporating dust sublimation and including a treatment of vertical
+hydrostatic equilibrium (see Section \ref{model} for a discussion of
+the code). In order to produce a grid of simulated systems we have
+varied several input parameters namely: stellar mass, stellar age,
+stellar rotation rate, accretion rate, the areal coverage of the
+accretion stream and the system inclination (the disc mass was
+fixed). The ranges of these variables were selected to represent and
+bound typical pre-MS BD systems, justification is provided using
+evidence from observational studies in Section \ref{par_space} and a
+final list of the values of these variables can be found in Table
+\ref{par_space_table}.
 
@@
 shown that for BDD systems the inner disc location, temperature and
-vertical size \& shape also varies with accretion rate. The inner edge
+vertical size and shape also varies with accretion rate. The inner edge
 position is correlated with temperature for the lower accreting models
@@
 
-Subsequently, the SEDs of BDD systems with typical accretion rates and
-associated discs, are changed significantly from the assumed
+Subsequently the SEDs of BDD systems with typical accretion rates and
+associated discs change significantly from the assumed
 underlying photospheric model flux, and therefore become difficult to
@@
 
-In practice, however, most parameters for BDD systems are derived for
+In practice most parameters for BDD systems are derived for
 populations. We have shown, in Section \ref{isochrones} that
@@
 extinction levels, CTTS population. For more extreme accretion rates
-the scatter, in CMD space, is significantly far from the pre-MS locus
+the scatter (in CMD space) is significantly far from the pre-MS locus
 and as such these stars have little chance of being selected as
@@
 of a coeval population of accreting BDs with associated discs, would
-be inaccurate and problematic. Again caused by the changes in the SEDs
-as a result of the accretion flux and increased occultation by the
-larger degree of flaring seen in BD discs \citep[for the latter, as
-found by][]{walker_2004}
+be inaccurate and problematic. Again this caused by the changes in the
+SEDs as a result of the accretion flux and increased occultation by
+the larger degree of flaring seen in BD discs \citep[for the latter,
+  as found by][]{walker_2004}
 
@@
 simulated photometry (with its associated photometric system), results
-in the reliable detection of disc candidates, for IRAC and MIPS
+in the reliable detection of disc candidates for IRAC and MIPS
 colours and $\alpha$ values, and therefore a robust lower limit disc
@@
 
-A further, derivative area this study impacts on, and perhaps most
-significantly, is the recent evidence for a stellar mass to accretion
-rate correlation, of the form: $\dot{M}_{acc}\propto M^{\sim 2}_{*}$
+A further area this study impacts on (perhaps most
+significantly) is the recent evidence for a stellar mass to accretion
+rate correlation, of the approximate form: $\dot{M}_{acc}\propto M_*^2$
 \citep{muzerolle_2003,natta_2004,natta_2006}. This relationship has
@@
 flaring, accretion and view over a range of inclinations any
-correlation is not apparent. The study of \cite{meyer_1997} used
-analytical prescribed flat discs.
-
-We have also modeled the same parameter space using various analytical
-disc structures as opposed to vertical hydrostatic
-equilibrium. Additionally, we are extending the parameter range of our
-grid. Finally, we have created an online fitting tool. All of which
-will be featured in upcoming publications. Finally, we intend to
-explore the efficacy of accretion rate diagnostics by simlating line
-profiles of accreting systems for a range of accretion rates.
+correlation is not apparent.
+
+We intend to extend the range of BBD models, employing both an
+increased parameter space and also a set of models adopting analytical
+prescriptions of the disc structure (as opposed to hydrostatic
+equilibrium). We are also extending our emission line modelling
+efforts \citep{kurosawa_2006} to lower central star masses in order to
+identify both the location of the line emission in the light of the
+work by \cite{gatti_2006} and to examine the efficacy of line fluxes
+as an accretion rate probe. We are also extending our grid of CTTS
+magnetospheric accretion models to lower accretion rates in order to
+identify the limit at which low accretion rate CTTS are no longer
+identified as accreting from H$\alpha$ line flux and morphology.
 
@@
 the mismatch is due to improvements in the model atmospheres available
-online \footnote{http://perso.ens-lyon.fr/france.allard/} (this is
+online\footnote{http://perso.ens-lyon.fr/france.allard/} (this is
 likely as the models available online, have a later time stamp,
@@
 photometry. For this study, as stated, we have adopted zeropoints
-calculated using the zero magnitude flux from the IRAC handbook
-\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}.
+calculated using the zero magnitude flux from the IRAC
+handbook\footnote{http://ssc.spitzer.caltech.edu/documents/som/som8.0.irac.pdf}.
 The resulting zeropoints were: Channel 1[3.6]=19.541, channel
@@
 As stated throughout this paper the data presented are available from
-a web page
-\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.
+a web page\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.
 

### 2010-06-11 BD_disc/paper.tex
Final version to be submitted
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2297 25464f21-6099-402c-b30a-640f1d40d38b

@@
 peaks for the stellar and thermal disc components, as it is these
-components which must be isolated. For BDD systems it is likely that
-difficulties detecting the disc will be exacerbated by the lower
-temperatures of the photosphere and therefore the smaller separation
-in wavelength from the thermal disc emission component, compared to
-CTTS systems. Therefore, to derive disc fractions for BD populations
-we require detailed comparison models with which to guide disc
-candidate selection.
+components which must be isolated. For BD disc (BDD hereafter) systems
+it is likely that difficulties detecting the disc will be exacerbated
+by the lower temperatures of the photosphere and therefore the smaller
+separation in wavelength from the thermal disc emission component,
+compared to CTTS systems. Therefore, to derive disc fractions for BD
+populations we require detailed comparison models with which to guide
+disc candidate selection.
 
@@
 correlation is the result of, or at least strengthened by, the
-presence of observational biases \citep{clarke_2006}: At the high-mass
+presence of observational biases \citep{clarke_2006}. At the high-mass
 (CTTS) end of the mass spectrum the lowest accretion-rates cannot be
@@
 In summary the key required input variables to setup the model grid
-are as follows: Stellar age and mass (which are used to derive the
+are as follows: stellar age and mass (which are used to derive the
 stellar flux) and accretion rate, areal coverage and rotation period
@@
 Our treatment of dust sublimation is similar to that detailed in
-\cite{tannirkulam_2007}, but with some enhancements to ensure a
-swift convergence of the sublimated rim. The dust sublimation proceeds
-as follows: An initial temperature distribution is found for the
+\cite{tannirkulam_2007}, but with some enhancements to ensure a swift
+convergence of the sublimated rim. The dust sublimation proceeds as
+follows: An initial temperature distribution is found for the
 optically-thin limit by setting the global dust-to-gas ratio to a tiny
@@
 are performed to ensure convergence, although a stable disc structure
-is normally found after three such iterations.
+is normally found after three such iterations. For a more
+sophisticated, and chemically more complex, study of dust sublimation,
+albeit for higher mass objects see \cite{kama_2009}.
 
@@
 inconsequential as the systems evolves from this state. In our models
-we have, however, placed at the inner disc edge at the co-rotation
+we have, however, placed the inner disc edge at the co-rotation
 radius, as opposed to the dust destruction radius used in
@@
 The resulting converged disc structures, as discussed in Section
-\ref{seds} are then used to create simulated SEDs and dervie broadband
+\ref{seds} are then used to create simulated SEDs and derive broadband
 photometric magnitudes. In this section we discuss the effects of
@@
 of the peak flux. This can be seen clearly by comparing the left and
-right panels of Figure \ref{acc_dom} As the rotation rate increases
+right panels of Figure \ref{acc_dom}. As the rotation rate increases
 the co-rotation radius also increases, as shown in Equation
 \ref{inner_eq}, $R_{\rm inner}\propto \tau^{\frac{2}{3}}$. Therefore,
-as Equations \ref{Lacc} and \ref{Tacc}, show, $L_{\rm acc}\propto 1-
+as Equations \ref{Lacc} and \ref{Tacc} show $L_{\rm acc}\propto 1-
 \frac{R_*}{R_{\rm inner}}$ and $T_{\rm acc}\propto (L_{\rm
-    acc}/A)^{\frac{1}{4}}$. Therefore, the temperature of the
-accretion hot spot increases as the rotational period increases, due
-to the increase in potential energy lost by the mass accreted. This
-can be seen in Figure by comparing the left and right panels of Figure
+  acc}/A)^{\frac{1}{4}}$, the temperature of the accretion hot spot
+increases as the rotational period increases. This is due to the
+increase in potential energy lost by the mass accreted. This can be
+seen in Figure by comparing the left and right panels of Figure
 \ref{acc_dom}. Perhaps the most important, albeit qualitative, result
@@
 
-Figure \ref{inner_inc} shows the SEDs for the viewing angles of 0, 27,
-39, and 48$^{\circ}$. The top and bottom panels of Figure
-\ref{inner_inc} show SEDs for models with a curved, as exemplified by
-Figure \ref{flare_-7_193}, and a flat inner wall, as shown in Figure
-\ref{flare_-12_183} respectively. The specific models chosen have been
-selected to minimise flux differences between the two SEDs but have
-distinct inner edges. The top panel has a mass of 0.04$M_{\odot}$,
-\logmdot = -8, areal coverage of 1\%, a rotational period of 5 days
-and an age of 10 Myrs. The bottom panel has a the same model but with
-rotation period of 0.5 days and an age of 1 Myrs. Comparing the top
-and bottom panel show that flux levels for the higher accretion rate,
-with the larger and curved inner edge, vary less distinctly with
-inclination angle than the systems with a vertical wall. The
-difference in inclination dependence of the fluxes between the curved
-and vertical inner walls is marginal. This is due to differences in
-the stellar flux levels and disc structures.
-
-\begin{figure*}
-  \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/inner_inc.ps}
-  \caption{Figure showing SEDs of systems with a curved and flat inner
-    wall as the top and bottom panels respectively. The lines show the
-    SEDs at viewing angles of 0, 27, 39, and 48$^{\circ}$.
-\label{inner_inc}}
-\end{figure*}
-
-Figure \ref{inner_inc} shows only that for inclinations close to
-face-on, the curved inner edge has SEDs with a stronger dependence on
-the viewing angle compared to the model with a vertical inner
-wall. This leads to a greater dependence of IR colour with
-inclination.  Figure \ref{inner_mag} shows the difference in the
-inclination dependence of the IR colour for large curved and smaller
-vertical inner walls (shown as blue and black lines respectively), for
-the systems shown in Figure \ref{inner_inc}. The dotted lines are
-illustrative of the total change in $(J-K)_0$.
-
-\begin{figure*}
-  \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/inner_mag.ps}
-  \caption{Figure showing the $(J-K)_0$ colour against the
-    inclinations of 0, 27, 39, and 48$^{\circ}$, for the models shown
-    in Figure \ref{inner_inc}. The models with the flat, vertical
-    inner wall and curved inner edge are shown as the black and blue
-    lines respectively. The horizontal dotted lines show the change in
-    the colour index.\label{inner_mag}}
-\end{figure*}
-
-The $(J-K)_0$ colour of the higher accretion rate system changes less
-as a function of inclination when compared to the lower accretion rate
-system. A total change in $(J-K)_0$ of $\approx$ 0.6 and 0.05 are
-found for the model with the flat and curved inner edge
-respectively. This reduction in the change in IR colour as a function
-of inclination for viewing angles close to face-on, is caused by the
-larger (vertically) and convex inner wall in the extreme accreting
-case. For the convex inner wall the effective emitting area one
-observes does not change as much as a vertical wall as a function of
-inclination, leading to this reduced dependence of IR colour on
-inclination.
+For our model grid the inner edge shape clearly changes with
+increasing flux levels and therefore accretion rate. This, for
+individual systems will lead to the reduced dependence of the IR
+colours on inclination as the edge moves from a vertical to a convex
+boundary as found by \cite{isella_2005}. Practically, for populations
+of stars however disentangling this effect from the influences of
+various other parameters (such as changing disc scaleheights and
+accretion rates) on the IR colours is difficult. Essentially, matching
+flux levels between two systems whilst maintinaing a difference in
+inner wall shape is impossible.
 
@@
 colours. The data presented in this section are for an isolated mass
-and age. However, the trends presented are present throughout our
+and age. However, the trends described are evident throughout our
 model grid for any given subset, and as such are representative. The
@@
 could lead to a correlation of IR excess with inner edge position. As
-expected however, scattered caused by variations in inclination and
-disc structure act to remove this correlation for populations.  The
+expected however, scatter caused by variations in inclination and disc
+structure act to remove this correlation for populations.  The
 correlation for an individual set of a systems, i.e. all variables
@@
 disc structures and will publish the results in a subsequent
-publication. Overall, as found in \cite{walker_2004}, the
-dominant scattering effect for BD disc systems in an optical CMD
-appears to be caused by accretion rate and inclination. Therefore for
-derivation of parameters we explore the scatter in pre-MS BD locii as
-a function of accretion rate and inclination.
+publication. Overall, as found in \cite{walker_2004}, the dominant
+scattering effect for BD disc systems in an optical CMD appears to be
+caused by accretion rate and inclination. Therefore for derivation of
+parameters we explore the scatter in pre-MS BD locii as a function of
+accretion rate and inclination.
 
@@
 Figures \ref{age_mass_VVI} and \ref{age_mass_JJK} shows CMDs in $M_V$
-\& $(V-I)_0$ and $M_J$ \& $(J-K)_0$ resepctively. The left panels of
+\& $(V-I)_0$ and $M_J$ \& $(J-K)_0$ respectively. The left panels of
 both figures shows stars classed as typical accretors with accretion
@@
 naked stars isochrones (created from our grid of simulated photometry)
-for 1 Myrs at accretion rates of \logmdot = $-$12 and $-$9, as solid and
-dashed lines respectively (with coverage of 10\% and rotation rates of
-5 days). Whereas the left hand panels show naked stars isochrones of
-\logmdot = $-$6 and $-$9 as solid and dashed black lines respectively (with
-coverage of 10\% and rotation rates of 5 days. The solid green line,
-in the top panels, shows the 1 Myr isochrone of \cite{siess_2000}
-adjusted to a distance of 250pc and an extinction of $A_V=2$ mag,
-simulating a background population of CTTS stars.
+for 1 Myrs at accretion rates of \logmdot = $-$12 and $-$9, as solid
+and dashed lines respectively (with coverage of 10\% and rotation
+rates of 5 days). Whereas the left hand panels show naked stars
+isochrones of \logmdot = $-$6 and $-$9 as solid and dashed black lines
+respectively (with coverage of 10\% and rotation rates of 5 days. The
+solid green line, in the top panels, shows the 1 Myr isochrone of
+\cite{siess_2000} adjusted to a distance of 250pc and an extinction of
+$A_V=2$ mag, simulating a background population of CTTS stars.
 
@@
 of \logmdot = $-$9 or $-$10 the movement of the star within the CMD
-will effectively move the star into the contamination region expected
+will effectively shift the star into the contamination region expected
 for background CTTS or MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$
@@
 conclusions are qualitative, and obviously based on our
-assumptions. However, the repercussion for isochronal age derivation
+assumptions. However, the repercussions for isochronal age derivation
 and sample selection in the BD regime could be profound. Indeed this
@@
 \cite{luhman_2005b} a study of IC348, \cite{luhman_2008} a study of
-$\sigma$ Orionis and \cite{gutermuth_2008} a study if the Taurus
+$\sigma$ Orionis and \cite{gutermuth_2008} a study of the Taurus
 region. In these cases the effects of extinction are either negligible
@@
 Subsequently the SEDs of BDD systems with typical accretion rates and
-associated discs change significantly from the assumed
-underlying photospheric model flux, and therefore become difficult to
+associated discs change significantly from the assumed underlying
+photospheric model flux, and therefore become difficult to
 classify. In Section \ref{observables} we have shown that the BD
@@
 rates. We have also shown that for extreme accretion rates the inner
-wall increases in size and becomes convex in shape. We have also shown
-that this leads to a reduced dependence on inclination (at
-inclinations close to face-on) of the IR colours, compared to a
-vertical wall.
+wall increases in size and becomes convex in shape.
 

### 2010-06-25 BDD_submit/paper.tex
Equilibrium misspelt in abstract
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2320 25464f21-6099-402c-b30a-640f1d40d38b

--- 2010-06-11 BD_disc/paper.tex
@@
   circumstellar discs. The calculations involve a self-consistent
-  solution of both vertical hydrostatic and radiative equilibirum
+  solution of both vertical hydrostatic and radiative equilibrium
   along with a sophisticated treatment of dust sublimation. We have
@@
   during brown dwarf target selection. We suggest that observations
-  used to assert a $\dot{M}\propto M_*^2$ relationship may
-  contain an intrinsic selection bias.
+  used to assert a $\dot{M}\propto M_*^2$ relationship may contain an
+  intrinsic selection bias.
 

### 2010-06-30 BDD_submit/paper.tex
demonstrate misspelt in abstract
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2321 25464f21-6099-402c-b30a-640f1d40d38b
Problems with Figure 7 caption rectified
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2332 25464f21-6099-402c-b30a-640f1d40d38b

@@
   extreme and typical accretors respectively.  Derivation of ages and
-  masses from our simulated photometry using isochrones is demostrated
-  to be unreliable even for typical accretors. Although current brown
-  dwarf disc candidate selection criteria have been shown to be
-  largely reliable when applied to our model grid we suggest improved
-  selection criteria in several colour indices. We show that as
-  accretion rates increase brown dwarf disc systems are less likely to
-  be correctly identified. This suggests that, within our grid,
-  systems with higher accretion rates would be preferentially lost
-  during brown dwarf target selection. We suggest that observations
-  used to assert a $\dot{M}\propto M_*^2$ relationship may contain an
-  intrinsic selection bias.
+  masses from our simulated photometry using isochrones is
+  demonstrated to be unreliable even for typical accretors. Although
+  current brown dwarf disc candidate selection criteria have been
+  shown to be largely reliable when applied to our model grid we
+  suggest improved selection criteria in several colour indices. We
+  show that as accretion rates increase brown dwarf disc systems are
+  less likely to be correctly identified. This suggests that, within
+  our grid, systems with higher accretion rates would be
+  preferentially lost during brown dwarf target selection. We suggest
+  that observations used to assert a $\dot{M}\propto M_*^2$
+  relationship may contain an intrinsic selection bias.
 
@@
     an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
-    days are shown as crosses. The systems with accretion rates of
+    days are shown as solid lines. The systems with accretion rates of
     \logmdot = $-$12, $-$9 and $-$7, are shown in black, red and blue
-    respectively. The panels also the systems with the highest
-    accretion rate but for a rotation rate of 5 days. The lowest panel
-    also shows, as horizontal dotted lines, the total change of colour
-    with the illustrated inclinations. \label{flare_mag}}
+    respectively. The panels also show the systems with the highest
+    accretion rate but for a rotation rate of 5 days, as a dashed
+    line. The vertical dotted lines show the inclinations of
+    71$^{\circ}$ and 56$^{\circ}$. Finally, the inset panel simply
+    shows a magnification of the region of interested for the $M_J$
+    magnitude. \label{flare_mag}}
 \end{figure*}

### 2010-06-30 BDD_submit/paper.tex
More adjustment to figure caption number 7
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2333 25464f21-6099-402c-b30a-640f1d40d38b

@@
     an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
-    days are shown as solid lines. The systems with accretion rates of
-    \logmdot = $-$12, $-$9 and $-$7, are shown in black, red and blue
-    respectively. The panels also show the systems with the highest
-    accretion rate but for a rotation rate of 5 days, as a dashed
-    line. The vertical dotted lines show the inclinations of
-    71$^{\circ}$ and 56$^{\circ}$. Finally, the inset panel simply
-    shows a magnification of the region of interested for the $M_J$
-    magnitude. \label{flare_mag}}
+    days are shown as solid lines (and crosses). The systems with
+    accretion rates of \logmdot = $-$12, $-$9 and $-$7, are shown in
+    black, red and blue respectively. The panels also show the systems
+    with the highest accretion rate but for a rotation rate of 5 days,
+    as dashed lines (and crosses). The vertical dotted lines show the
+    inclinations of 71$^{\circ}$ and 56$^{\circ}$. Finally, the inset
+    panel simply shows a magnification of the region of interested for
+    the $M_J$ magnitude. \label{flare_mag}}
 \end{figure*}

### 2010-06-30 BDD_submit/paper.tex
More adjustment this time to text pertaining to Figure 7
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2334 25464f21-6099-402c-b30a-640f1d40d38b

@@
 the observed magnitudes and colours with inclination. Figure
-\ref{flare_mag} shows the $M_V$ and $M_J$ magnitudes in the top
-and bottom panels respectively. The magnitudes are then marked as
-crosses as a function of inclination. The systems shown in both panels
-have an age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5
-and an areal coverage of 10\%. The systems with accretion rates of
-\logmdot = $-$12, $-$9 and $-$7 are shown in black, red and blue,
+\ref{flare_mag} shows the $M_V$ and $M_J$ magnitudes in the top and
+bottom panels respectively. The magnitudes are then marked as crosses
+as a function of inclination. The systems shown in both panels have an
+age of 1 Myr, mass of $0.04M_{\odot}$, rotation rates of 0.5 and an
+areal coverage of 10\%. The systems with accretion rates of \logmdot =
+$-$12, $-$9 and $-$7 are shown in black, red and blue,
 respectively. The panels also show the system with the highest
@@
 line. The vertical dotted lines in the lowest panel simply illustrate
-the total change in magnitude, over the shown inclination range.
+the inclinations of 71$^{\circ}$ and 56$^{\circ}$.
 

### 2010-07-01 BDD_submit/paper.tex
Small typo in footnote 7
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2339 25464f21-6099-402c-b30a-640f1d40d38b

@@
 and applied conversions of \cite{leggett_1992}\footnote{We have
-  also included the wavelength shift mention in
+  also included the wavelength shift mentioned in
   \cite{stephens_2004}}, to the \textit{CIT} system. For each

### 2010-07-01 BDD_submit/paper.tex
Changed cuts, Taurus cut was applied by monin_2010 but was from gutermuth_2008
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2340 25464f21-6099-402c-b30a-640f1d40d38b

@@
 photometric measures and cuts in colour-colour or colour-magnitude
-space \citep{luhman_2005b,luhman_2008,gutermuth_2008}.  The important
-quantity here is the separation in wavelength between the emission
-peaks for the stellar and thermal disc components, as it is these
-components which must be isolated. For BD disc (BDD hereafter) systems
-it is likely that difficulties detecting the disc will be exacerbated
-by the lower temperatures of the photosphere and therefore the smaller
-separation in wavelength from the thermal disc emission component,
-compared to CTTS systems. Therefore, to derive disc fractions for BD
-populations we require detailed comparison models with which to guide
-disc candidate selection.
+space \citep{luhman_2005b,luhman_2008,gutermuth_2008,monin_2010}.  The
+important quantity here is the separation in wavelength between the
+emission peaks for the stellar and thermal disc components, as it is
+these components which must be isolated. For BD disc (BDD hereafter)
+systems it is likely that difficulties detecting the disc will be
+exacerbated by the lower temperatures of the photosphere and therefore
+the smaller separation in wavelength from the thermal disc emission
+component, compared to CTTS systems. Therefore, to derive disc
+fractions for BD populations we require detailed comparison models
+with which to guide disc candidate selection.
 
@@
 and measure disc fractions
-\citep{luhman_2005b,luhman_2008,gutermuth_2008}.
+\citep{luhman_2005b,luhman_2008,gutermuth_2008,monin_2010}.
 
@@
 works pre-dominantly use \textit{Spitzer} IRAC magnitudes
-\citep[e.g][]{luhman_2005b,luhman_2008,gutermuth_2008}. Furthermore,
+\citep[e.g][]{luhman_2005b,luhman_2008,gutermuth_2008,monin_2010}. Furthermore,
 MIPS magnitudes are used to identify so-called debris discs, where IR
@@
 \cite{luhman_2005b} a study of IC348, \cite{luhman_2008} a study of
-$\sigma$ Orionis and \cite{gutermuth_2008} a study of the Taurus
-region. In these cases the effects of extinction are either negligible
-in the plotted colours, with values of $E([3.6]-[4.5])<0.04$ and
-$E([4.5]-[5.8])<0.02$ for IC348 and $A_V \leq$4 mag \citep[which will
-be negligible in the IRAC CoCoD,][]{allen_2004}, or the cuts
-have been placed in intrinsic colour space as for $\sigma$
-Orionis. The cuts from \cite{luhman_2005b}, \cite{luhman_2008} and
-\cite{gutermuth_2008} appear as the top, top-middle and bottom-middle
-panels. The lower panel shows a recent BDD candidate selection using
-the $\alpha$ value from \citep{kennedy_2009}.
+$\sigma$ Orionis and \cite{monin_2010} \citep[using the criteria
+of][]{gutermuth_2008} a study of the Taurus region. In these cases the
+effects of extinction are either negligible in the plotted colours,
+with values of $E([3.6]-[4.5])<0.04$ and $E([4.5]-[5.8])<0.02$ for
+IC348 and $A_V \leq$4 mag \citep[which will be negligible in the IRAC
+CoCoD,][]{allen_2004}, or the cuts have been placed in intrinsic
+colour space as for $\sigma$ Orionis. The cuts from
+\cite{luhman_2005b}, \cite{luhman_2008} and \cite{monin_2010} appear
+as the top, top-middle and bottom-middle panels. The lower panel shows
+a recent BDD candidate selection using the $\alpha$ value from
+\citep{kennedy_2009}.
 
@@
     selection of \citet{luhman_2005b}, \citet{luhman_2008},
-    \citet{gutermuth_2008} and \citet{kennedy_2009}. The photometry or
-    $\alpha$ values for all models are shown, with naked stars as
-    black crosses, 1 Myr BDD systems as blue dots and 10 Myr BDD
-    systems as red dots. The dashed horizontal and vertical lines are
-    disc selections from the studies in question. The left panels are
-    the typical accretors and the right panels the extreme
-    accretors. The top three panels are IRAC CoCoDs and the bottom
-    panel plots the $\alpha$ value against run number (an arbitary
-    number).\label{disc_cuts}}
+    \citet{monin_2010} \citep[using the criteria of][]{gutermuth_2008}
+    and \citet{kennedy_2009}. The photometry or $\alpha$ values for
+    all models are shown, with naked stars as black crosses, 1 Myr BDD
+    systems as blue dots and 10 Myr BDD systems as red dots. The
+    dashed horizontal and vertical lines are disc selections from the
+    studies in question. The left panels are the typical accretors and
+    the right panels the extreme accretors. The top three panels are
+    IRAC CoCoDs and the bottom panel plots the $\alpha$ value against
+    run number (an arbitary number).\label{disc_cuts}}
 \end{figure*}
@@
 systems). The third panel down shows only very few BDD systems will be
-missed by the selection of \cite{gutermuth_2008}. Finally, the
-selection for CTTS candidates of $\alpha>-$2 \citep{kennedy_2009}
-appears reasonably applicable to our BDD systems. As can be seen in
-the bottom panel of Figure \ref{disc_cuts} almost all the typical, and
-all of the extreme accreting BDD systems would be successfully
-identified using this criterion. Again the missed typically accreting
-systems are edge-on systems. Given, that extreme reddening may move
-naked stars into the BDD region selected, in general, disc fractions
-are usually quoted as lower limits. Therefore, a small number of
-miss-identified BDD system is a negligible effect. This allows us to
-conclude, that ubiquitously used BDD selections within IRAC CoCoDs are
-reliable when applied to our model grid. Additionally, the $\alpha$
-value would be a reliable disc indicator for our model grid.
+missed by the selection of \cite{gutermuth_2008} which was applied to
+Taurus by\cite{monin_2010}. Finally, the selection for CTTS candidates
+of $\alpha>-$2 \citep{kennedy_2009} appears reasonably applicable to
+our BDD systems. As can be seen in the bottom panel of Figure
+\ref{disc_cuts} almost all the typical, and all of the extreme
+accreting BDD systems would be successfully identified using this
+criterion. Again the missed typically accreting systems are edge-on
+systems. Given, that extreme reddening may move naked stars into the
+BDD region selected, in general, disc fractions are usually quoted as
+lower limits. Therefore, a small number of miss-identified BDD system
+is a negligible effect. This allows us to conclude, that ubiquitously
+used BDD selections within IRAC CoCoDs are reliable when applied to
+our model grid. Additionally, the $\alpha$ value would be a reliable
+disc indicator for our model grid.
 

### 2010-07-12 BDD_submit/paper.tex
First response to referee very minor changes
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2364 25464f21-6099-402c-b30a-640f1d40d38b

@@
 from the dusty inner disc. The complexity of the interplay between
-these contributions is excerbated by other, geometrical, effects such
+these contributions is exacerbated by other, geometrical, effects such
 as the inclination (which changes the projected area of the inner disc
 wall visible to the observer) and the outer disc structure (which may
-obsure the inner disc for high inclincations)
+obscure the inner disc for high inclinations)
 \citep{walker_2004,tannirkulam_2007}.
@@
 canonical picture the accretion rate is driven by the disc viscosity,
-and should be indepedent of the mass of the central object, this
+and should be independent of the mass of the central object, this
 correlation is somewhat surprising. There is some danger that the
@@
 measured via continuum methods since the excess is too small in
-contrast with the photopsheric emission. The emission lines will also
+contrast with the photospheric emission. The emission lines will also
 be weak, and indeed the H$\alpha$ equivalent width (EW) may be less
 than the 10\AA\ that traditionally demarcates classical from
-weak-lined T Tauri stars. Such objects should show doppler-broadened
-profiles, but the line wings will be weak, and the presence of
-underlying H$\alpha$ absorption may become dominant. Thus there may
-well be a population of low-accretion-rate CTTS which are current
-missing from the surveys.
+weak-lined T Tauri stars \citep[although this boundary may well be
+spectral type dependent][]{navascues_2003}. Such objects should show
+doppler-broadened profiles, but the line wings will be weak, and the
+presence of underlying H$\alpha$ absorption may become dominant. Thus
+there may well be a population of low-accretion-rate CTTS which are
+current missing from the surveys.
 
@@
 high temperatures, the line ratios of Pa$\beta$ and Br$\gamma$
-indicate that the hydrodgen emission may not arise in the funnel flows
+indicate that the hydrogen emission may not arise in the funnel flows
 \citep{gatti_2006}. However, recently some continuum measurements of
@@
 for $T_{\rm eff}<$1700\,K, but this resulted in large discontinuities
-between the model atmospheres and resulting spectra. Since this only
-affects stars at the very edge of our temperature range, i.e. for the
-oldest and lowest mass objects (for the AMES-Cond case), we have
-adopted the AMES-Dusty models throughout.
+between the model atmospheres and resulting spectra. Additionally, for
+the higher temperatures in our range \cite{martin_2000} have found the
+NextGen models to be more applicable for $\sim T_{\rm
+  eff}>2300$K. However, as with the lower boundary this only applies
+to the edge of our temperature range and we feel it is better to use a
+consistent set of atmosphere and interior models across our
+grid. Since this only affects stars at the very edge of our
+temperature range, i.e. for the oldest and lowest mass objects (for
+the AMES-Cond case), we have adopted the AMES-Dusty models throughout.
 
@@
 would expect this to be an overestimate of the accretion flux, as for
-pre-MS BDs large convective zones are expected on the stellar surface,
-and some of the accretion energy may act to further drive these
-convective currents, meaning flux is lost. It is worth noting however
-that observationally UV excesses are often used to recreate and then
+BDs large convective zones are expected on the stellar surface, and
+some of the accretion energy may act to further drive these convective
+currents, meaning flux is lost. It is worth noting however that
+observationally UV excesses are often used to recreate and then
 subtract an assumed accretion flux using a blackbody flux curve, which
@@
   rate \citep{dahm_2009} and therefore would represent a distinct
-  evolutionary state of brown dwarf disc (BDD) sytems to that of the
+  evolutionary state of brown dwarf disc (BDD) systems to that of the
   CTTS-like phase we are considering here.}.
@@
 with a final iteration of $\tau_{\max} = \infty$. Adequately solving
-the radiative-equilibrium necessiates resolving the disc's effective
+the radiative-equilibrium necessitates resolving the disc's effective
 photosphere, and adaptive mesh refinement is used to split the grid at
@@
 $\dot{M}\propto M_*^2$. Further evidence was put forward by
-\cite{natta_2004}, where accretion rates as low as 5$\times$
-10$^{-12} {\rm M}_{\odot} {\rm yr}^{-1}$ were found for BD stars. More recently,
-even lower accretion rates of $\approx$10$^{-13} {\rm M}_{\odot} {\rm yr}^{-1}$,
-have been derived for BDs by \cite{herczeg_2009}.  Further support for
-a dependence of accretion rate on stellar mass was apparent in the
-significantly more homogeneous dataset of
+\cite{natta_2004}, where accretion rates as low as 5$\times$ 10$^{-12}
+{\rm M}_{\odot} {\rm yr}^{-1}$ were found for BD stars. More recently,
+even lower accretion rates of $\approx$10$^{-13} {\rm M}_{\odot} {\rm
+  yr}^{-1}$, have been derived for BDs by \cite{herczeg_2009}.
+Further support for a dependence of accretion rate on stellar mass was
+apparent in the significantly more homogeneous dataset of
 \cite{natta_2006}. \cite{natta_2006} analysed a set of accretion rates
-and masses derived for pre-MS stars in $\rho$ Ophiuchi and compared
-these results to stars in Taurus. They found that the accretion rate
-scales with central object mass into the BD regime, although with
-significant scatter.
+and masses derived for BD stars in $\rho$ Ophiuchi and compared these
+results to stars in Taurus. They found that the accretion rate scales
+with central object mass into the BD regime, although with significant
+scatter.
 
@@
 For further analysis, and throughout the rest of this paper, we will
-seperate the systems into two groups. These groups are those systems
+separate the systems into two groups. These groups are those systems
 with \logmdot$\leq-9$ and \logmdot$\geq-9$, classed as typical and
@@
 systems undergo both significant sublimation ($\Delta R_{\rm
-  inner}>1R_*$) and have an accretion luminosity that is comparible to
+  inner}>1R_*$) and have an accretion luminosity that is comparable to
 the photospheric luminosity (see Section~\ref{acc_dominance}). In
@@
      respectively. In addition, systems where $\Delta R_{\rm inner} <
-     1R_*$ are plotted ia crosses and $\Delta R_{\rm inner} > 1R_*$ as
+     1R_*$ are plotted as crosses and $\Delta R_{\rm inner} > 1R_*$ as
      filled circles (this is only achieved by some systems classed as
@@
 accretion rates) on the IR colours is difficult. Essentially, matching
-flux levels between two systems whilst maintinaing a difference in
+flux levels between two systems whilst maintaining a difference in
 inner wall shape is impossible.
@@
 inclination. For populations of stars these changes in magnitude and
-colour act to scatter or spread a pre-MS BD locus in photometric
-space.
+colour act to scatter or spread a BD locus in photometric space.
 
@@
 
-Practically, most parameters for young pre-MS stars are derived from
-surveys of populations, usually open clusters, using broadband
+Practically, most parameters for young pre-MS and BD stars are derived
+from surveys of populations, usually open clusters, using broadband
 photometry and subsequently constructed colour-magnitude and
@@
 see if any correlation appears for analytically defined disc
-structures. We have run a set of parrallel models using analytical
+structures. We have run a set of parallel models using analytical
 disc structures and will publish the results in a subsequent
@@
 caused by accretion rate and inclination. Therefore for derivation of
-parameters we explore the scatter in pre-MS BD locii as a function of
+parameters we explore the scatter in BD locii as a function of
 accretion rate and inclination.
@@
 
-The use of pre-MS isochrones for the derivation of single star
+The use of pre-MS and BD isochrones for the derivation of single star
 parameters is at present not proven to be reliable \citep[see
@@
 blue, black and red dots respectively, in the top right panel. The
-bottom panels then show the systems seperated into groups by
+bottom panels then show the systems separated into groups by
 inclination. These groups are $\theta \leq 48^{\circ}$ as blue dots
@@
 solid green line, in the top panels, shows the 1 Myr isochrone of
-\cite{siess_2000} adjusted to a distance of 250pc and an extinction of
+\cite{siess_2000} adjusted to a distance of 250 pc and an extinction of
 $A_V=2$ mag, simulating a background population of CTTS stars.
@@
     7 and an extinction of $A_V=2$, simulating a reddened background
-    population. The top panels then seperate the systems by accretion
+    population. The top panels then separate the systems by accretion
     rate with \logmdot = $-$9, $-$10 and $-$11 \& $-$12 in the top left panel,
@@
 accretion rates are scattered sufficiently in CMD space to prohibit
-their identification as pre-MS BDs. Indeed, these objects would not be
+their identification as BDs. Indeed, these objects would not be
 included in a photometrically selected sample of BDs, and as such are
@@
 systems with extreme accretion rates would not be classified as BDD
-sytems.
+systems.
 
@@
 with typical accretion rates and the right panels the extreme
-accretors. The top panels of Figure \ref{disc_frac_JHJK} then seperate
+accretors. The top panels of Figure \ref{disc_frac_JHJK} then separate
 the systems by accretion rate with \logmdot = $-$9, $-$10 and $-$11 \&
@@
     (left panel) and extreme accreting (right panels) systems. The top
-    panels then seperate the accretion rates with \logmdot = $-$9,
+    panels then separate the accretion rates with \logmdot = $-$9,
     $-$10 and $-$11 \& $-$12, and \logmdot = $-$6, $-$7 \& $-$8 shown
@@
 placing a colour-colour cut are viewed as lower limits this effect may
-be small. Our grid show no corelation in a CoCoD of this type with
+be small. Our grid show no correlation in a CoCoD of this type with
 rotation rate. In the case of the extreme accretors (right panels)
@@
 naked stars. Additionally, the extreme accretors lie significantly
-removed from the naked stars locus. There is a possiblity that some of
+removed from the naked stars locus. There is a possibility that some of
 these objects may be lost due to saturation and limiting magnitude
@@
     of both typical (left panels) and extreme (right panels)
-    accretors. The panels seperate the different accretion rates and
+    accretors. The panels separate the different accretion rates and
     inclinations as in Figure
@@
     format as Figure \ref{disc_frac_JHJK}. The smaller inset panels in
-    the top panels show the seperation between the naked (blue
+    the top panels show the separation between the naked (blue
     crosses) and BDD systems (red dots).\label{disc_frac_mips}}
@@
 Figure \ref{disc_frac_irac} shows that, as expected, the IRAC CoCoDs
-clearly seperate the naked and BDD systems. Once again, as found in
-Figure \ref{disc_frac_JHJK}, for the extreme accretors the seperation
+clearly separate the naked and BDD systems. Once again, as found in
+Figure \ref{disc_frac_JHJK}, for the extreme accretors the separation
 of the BDD systems from the naked stars is a weak function of
@@
 constructed using other IRAC photometric channels. As we include
-longer wavelength bands in the IRAC CoCoDs the seperation between the
+longer wavelength bands in the IRAC CoCoDs the separation between the
 disc and naked locii increases. As the wavelength gets longer the flux
@@
 even further, into the range of the MIPS photometric bands, the
-seperation between naked and BDD systems increases still further. The
-inset panels show that the seperation between the naked and BDD
+separation between naked and BDD systems increases still further. The
+inset panels show that the separation between the naked and BDD
 systems is larger than in Figure \ref{disc_frac_irac}. Additionally,
@@
 selection in the IRAC photometric bands. As we have shown within our
-model grid the seperation between the BDD and naked systems is
+model grid the separation between the BDD and naked systems is
 clear. Therefore, we can examine the success of some recent
@@
 Figure \ref{disc_cuts} presents all the data for our model grid
-seperated by age, with 1 and 10 Myr BDD systems shown as blue and red
+separated by age, with 1 and 10 Myr BDD systems shown as blue and red
 dots respectively. The naked systems are shown as black crosses. The
@@
     IRAC CoCoDs and the bottom panel plots the $\alpha$ value against
-    run number (an arbitary number).\label{disc_cuts}}
+    run number (an arbitrary number).\label{disc_cuts}}
 \end{figure*}
@@
 systems. These are shown in Table \ref{cuts_table}, where the defined
-cuts are chosen to minimise contanimation from naked stars.
+cuts are chosen to minimise contamination from naked stars.
 
@@
 fixed). The ranges of these variables were selected to represent and
-bound typical pre-MS BD systems, justification is provided using
-evidence from observational studies in Section \ref{par_space} and a
-final list of the values of these variables can be found in Table
+bound typical BD systems, justification is provided using evidence
+from observational studies in Section \ref{par_space} and a final list
+of the values of these variables can be found in Table
 \ref{par_space_table}.
@@
 extinction levels, CTTS population. For more extreme accretion rates
-the scatter (in CMD space) is significantly far from the pre-MS locus
-and as such these stars have little chance of being selected as
+the scatter (in CMD space) is significantly far from the naked BD
+locus and as such these stars have little chance of being selected as
 BDs. As discussed in Section \ref{results} this does not include any
@@
 \section*{ACKNOWLEDGMENTS}
-The simulations in this work were peformed using the University of
+The simulations in this work were performed using the University of
 Exeter supercomputer, an SGI Altix ICE 8200. NJM and TJH were
@@
 
-The magnitudes and colours presented in this paper are avaiable both
+The magnitudes and colours presented in this paper are available both
 as individual magnitudes and as isochrones or mass tracks. Photometric
@@
 available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
-\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$
-and $B_t$ \citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
+\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$ and $B_t$
+\citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
 \citep{bessell_1988,bessell_1998}, SDSS \textit{UGRIZ}
@@
 \citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
-\citep{neugebauer_1984} and SCUBA \textit{450WB} and
-\textit{850WB} \citep{holland_1999}. For further information on
-these magnitudes, such as the filter responses used and the adopted
-zeropoints please refer to the website.
+\citep{neugebauer_1984} and SCUBA \textit{450WB} and \textit{850WB}
+\citep{holland_1999}. For further information on these magnitudes,
+such as the filter responses used and the adopted zeropoints please
+refer to the website.
 

### 2010-07-12 torus/memory_mod.F90
Add ifdefs to allow nagfor build to work OK.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2365 25464f21-6099-402c-b30a-640f1d40d38b

@@ -6,6 +6,7 @@ module memory_mod
 
   implicit none
 
+#ifdef MEMCHECK
   interface mySizeOf
      module procedure mySizeOfDouble
      module procedure mySizeOfDouble2D
@@ -15,7 +16,8 @@ module memory_mod
      module procedure mySizeOfLogical
      module procedure mySizeOfVector
   end interface
-  
+#endif  
+
   public
   integer(kind=bigInt) :: globalMemoryFootprint
   
@@ -224,7 +226,7 @@ module memory_mod
 
     end function humanReadableMemory
 
-
+#ifdef MEMCHECK
     function mySizeOfInteger(p) result (i)
       integer, pointer :: p(:)
       integer :: i
@@ -273,5 +275,6 @@ module memory_mod
       i = 0
       if (associated(p)) i = sizeof(p)
     end function mySizeOfVector
+#endif
 
   end module memory_mod

### 2010-07-13 BDD_submit/paper.tex
Some spelling mistakes fixed. Thanks Dave Rundle
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2368 25464f21-6099-402c-b30a-640f1d40d38b

@@
 There is now strong evidence that as brown dwarfs (BDs) form they pass
-through a Classical T~Tauri star (CTTS) phase, during which they
+through a classical T~Tauri star (CTTS) phase, during which they
 possess a flared, dusty circumstellar disc from which they are
@@
 The interpretation of the spectral energy distributions (SEDs) of
-pre-main-sequence (PMS) stars involves trying to distinguish the
+pre-main-sequence (pre-MS) stars involves trying to distinguish the
 various contributions to the continuum from the hot spots at the base
@@
 from the dusty inner disc. The complexity of the interplay between
-these contributions is exacerbated by other, geometrical, effects such
+these contributions is exacerbated by other geometrical effects such
 as the inclination (which changes the projected area of the inner disc
-wall visible to the observer) and the outer disc structure (which may
-obscure the inner disc for high inclinations)
-\citep{walker_2004,tannirkulam_2007}.
-
-In surveys, particularly those attempting to discern the PMS disc
-fraction this disentangling usually takes place using broad-band
-photometric measures and cuts in colour-colour or colour-magnitude
-space \citep{luhman_2005b,luhman_2008,gutermuth_2008,monin_2010}.  The
+wall visible to the observer) and the outer disc structure
+\citep[which may obscure the inner disc for high
+inclinations][]{walker_2004,tannirkulam_2007}.
+
+In surveys, particularly those attempting to discern the pre-MS disc
+fraction disentangling of the SED components usually takes place using
+broad-band photometric measures and cuts in colour-colour or
+colour-magnitude space
+\citep{luhman_2005b,luhman_2008,gutermuth_2008,monin_2010}.  The
 important quantity here is the separation in wavelength between the
@@
 
-Comparison of accretion rates across the pre-main-sequence (PMS) mass
-spectrum has indicated that the accretion rate is strongly correlated
-with PMS mass, \citep{muzerolle_2003,natta_2004,natta_2006}, with an
+Comparison of accretion rates across the pre-MS mass spectrum has
+indicated that the accretion rate is strongly correlated with pre-MS
+mass, \citep{muzerolle_2003,natta_2004,natta_2006}, with an
 approximate form $\dot{M}_{\rm acc}\propto M^2_*$. Since in the
@@
 weak-lined T Tauri stars \citep[although this boundary may well be
-spectral type dependent][]{navascues_2003}. Such objects should show
+spectral type dependent,][]{navascues_2003}. Such objects should show
 doppler-broadened profiles, but the line wings will be weak, and the
@@
 
-In this Section we detail the physical model adopted and assumptions
+In this section we detail the physical model adopted and assumptions
 made (Section \ref{physics}), then explain key elements of the
@@
 
-In order to model an accreting BDD system we must first model the
+In order to model an accreting BDD system one must first model the
 underlying photospheric flux. We have adopted a BD stellar interior
@@
 online\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
-$T_{\rm eff}$ range of $\approx $3000\,K$<T_{\rm eff}<$1600\,K the
+$T_{\rm eff}$ range of $\approx$\,3000\,K\,$<T_{\rm eff}<$1600\,K the
 AMES-Dusty atmospheres are the most applicable (2700\,K$>T_{\rm
@@
 between the model atmospheres and resulting spectra. Additionally, for
-the higher temperatures in our range \cite{martin_2000} have found the
-NextGen models to be more applicable for $\sim T_{\rm
+the higher temperatures in our range, \cite{martin_2000} have found
+the NextGen models to be more applicable for $\sim T_{\rm
   eff}>2300$K. However, as with the lower boundary this only applies
@@
 Finally, a blackbody flux distribution is generated at $T_{\rm acc}$
-and added onto the intrinsic stellar photospheric flux. In general one
-would expect this to be an overestimate of the accretion flux, as for
-BDs large convective zones are expected on the stellar surface, and
-some of the accretion energy may act to further drive these convective
-currents, meaning flux is lost. It is worth noting however that
-observationally UV excesses are often used to recreate and then
+and added onto the intrinsic stellar photospheric flux. In general,
+one would expect this to be an overestimate of the accretion flux, as
+for BDs large convective zones are expected on the stellar surface,
+and some of the accretion energy may act to further drive these
+convective currents, meaning flux is lost. It is worth noting however
+that observationally UV excesses are often used to recreate and then
 subtract an assumed accretion flux using a blackbody flux curve, which
@@
 magnetic field \citep{koenigl_1991}. This is currently unavailable for
-BD stars, due to increased molecular species obscuring the Zeeman
-splitting signatures that are normally used to derive stellar surface
-magnetic fields. Therefore, for our model grid we have adopted an
-initial inner disc radius as the co-rotation radius,
+BDs, due to an increased number of molecular species obscuring
+the Zeeman splitting signatures that are normally used to derive
+stellar surface magnetic fields. Therefore, for our model grid we have
+adopted an initial inner disc radius as the co-rotation radius,
 \begin{equation}
@@
 updated by \cite{harries_2004} and \cite{kurosawa_2004}. {\sc torus}
-  uses the method of \cite{lucy_1999} solve radiative equilibrium on
-  an AMR mesh. The code also self-consistently solves the
-  equation of vertical hydrostatic equilibrium and dust sublimation
-  for the disc \citep[described in][]{tannirkulam_2007}. The {\sc
-    torus} code has been extensively benchmarked \citep{pinte_2009}.
+uses the method of \cite{lucy_1999} to solve radiative equilibrium on
+an AMR mesh. The code also self-consistently solves the equation of
+vertical hydrostatic equilibrium and dust sublimation for the disc
+\citep[described in][]{tannirkulam_2007}. The {\sc torus} code has
+been extensively benchmarked \citep[for radiative transfer in discs
+against][]{pinte_2009}.
 
@@
 
-As our models assume magnetic-truncation at the co-rotation radius, we
-have implicitly generated an inner hole. This also means that the disc
-will have an inner wall at this radius. Evidence for inner walls in
+As our models assume magnetic truncation at the co-rotation radius, we
+have generated an inner hole. This also means that the disc will have
+an inner wall at this radius. Evidence for inner walls in
 circumstellar discs is apparent from the SEDs of disc systems, where a
@@
 the optically-thin/optically-thick boundary in order that the maximum
-cell size at this boundary is $<1$ at a wavelength of 5500\,\AA. Once
-a self-consistent sublimated rim has been determined the equation of
-hydrostatic equilibrium is solved throughout the disc, and the
-sublimation iterations are restarted (the change in the density
-structure from the hydrostatical equilibrium step naturally feeds back
-into the shape of the inner rim). Five hydrostatic equilibrium steps
-are performed to ensure convergence, although a stable disc structure
-is normally found after three such iterations. For a more
-sophisticated, and chemically more complex, study of dust sublimation,
-albeit for higher mass objects see \cite{kama_2009}.
-
-For our model grid we have adopted a gas-to-dust ratio, $\epsilon$, of
-100, and the gas population is assumed to be essentially static with a
-zero optical depth.
+cell size at this boundary is $<$\,1 at a wavelength of
+5500\,\AA. Once a self-consistent sublimated rim has been determined,
+the equation of hydrostatic equilibrium is solved throughout the disc,
+and the sublimation iterations are restarted (the change in the
+density structure from the hydrostatical equilibrium step naturally
+feeds back into the shape of the inner rim). Five hydrostatic
+equilibrium steps are performed to ensure convergence, although a
+stable disc structure is normally found after three such
+iterations. For a more sophisticated, and chemically more complex,
+study of dust sublimation albeit for higher mass objects see
+\cite{kama_2009}.
+
+For our model grid the gas population is assumed to be essentially
+static with a zero optical depth.
 
@@
 generated. These SEDs can be generated for any distance and for any
-system-observer inclination. For our models we have set the distance,
-to 10\,pc to create absolute flux SEDs and selected ten inclinations
-equi-spaced in $\cos i$ (0, 27, 39, 48, 56, 64, 71, 77, 84 and
+system inclination. For our models we have set the distance, to 10\,pc
+to create absolute flux SEDs and selected ten inclinations equi-spaced
+in $\cos i$ (where $i$=0, 27, 39, 48, 56, 64, 71, 77, 84 and
 90$^{\circ}$). A further useful feature of the {\sc torus} code is
-that the emitted photon packets which make up the SED are tagged on
-their way to the observer. These tags separate the packets into four
-groups. Firstly, packets are separated by source into thermal (disc)
-or stellar groups. These groups are then subdivided into those which
-reach the observer either directly or after scattering. The resulting
-SEDs are discussed in Section \ref{seds}.
+that the emitted photon packets which contribute to the SED are tagged
+on their way to the observer. These tags separate the packets into
+four groups. Firstly, packets are separated by source into thermal
+(disc) or stellar groups. These groups are then subdivided into those
+which reach the observer either directly or after scattering. The
+resulting SEDs are discussed in Section \ref{seds}.
 
@@
 effects in the `observational plane' we have used the SEDs to produce
-broadband photometric magnitudes, and subsequently colours. Broadband
+broadband photometric magnitudes and subsequently colours. Broadband
 magnitudes were also derived in a large range of other filter sets not
 used explicitly in the analysis within this paper. These magnitudes
-are available online\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}
-and are briefly discussed in Appendix \ref{website}. In addition,
-monochromatic fluxes have been derived for all filters, and again are
-available online and discussed in Appendix \ref{website}.
+are available
+online\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
+  disc} and are briefly discussed in Appendix \ref{website}. In
+addition, monochromatic fluxes have been derived for all filters, and
+again are available online and discussed in Appendix \ref{website}.
 
@@
 
-We have integrated using photon-counting and calibrated using a Vega
-spectrum for magnitudes in the optical and near-IR regimes. The filter
-bandpasses selected are, the optical system of
-\cite{bessell_1998} for \textit{UBVRI} and the \textit{CIT}
-system of \cite{elias_1982,stephens_2004} for
-\textit{JHK}, with the required shift of $-0.015$\,$\mu$m as prescribed by
-\cite{stephens_2004}.
+We have integrated, the fluxes, using photon-counting and calibrated
+using a Vega spectrum for magnitudes in the optical and near-IR
+regimes. The filter bandpasses selected are, the optical system of
+\cite{bessell_1998} for \textit{UBVRI} and the \textit{CIT} system of
+\cite{elias_1982,stephens_2004} for \textit{JHK}, with the required
+shift of $-0.015$\,$\mu$m as prescribed by \cite{stephens_2004}.
 
@@
 
-These specific filter sets have been chosen due to their ubiquitous
-use and suitability for the derivation of the key stellar parameters
-of age, mass and, for populations, disc fractions. Therefore, by
-studying the changes of magnitudes (and colours) in these photometric
-systems we can test the predicted effects on these derived parameters
-caused by changes in the input parameters of our model grid. The
-optical magnitudes \textit{VI} are used to explore age related effects
-of varying the parameter space. Flux in the \textit{VI} bands is only
-minimally affected by accretion flux \citep{gullbring_1998} and
-disc thermal flux \citep{hartmann_1998} and, additionally, in a
-\textit{V, V$-$I} CMD, the reddening vector lies parallel to the pre-MS,
+We have chosen these specific filter due to their ubiquitous use and
+suitability for the derivation of the key stellar parameters of age,
+mass and, for populations, disc fractions. Therefore, by studying the
+changes of magnitudes (and colours) in these photometric systems we
+can test the predicted effects on these derived parameters caused by
+changes in the input parameters of our model grid. The optical
+magnitudes \textit{VI} are used to explore age-related effects of
+varying the parameter space. Flux in the \textit{VI} bands is only
+minimally affected by accretion flux \citep{gullbring_1998} and disc
+thermal flux \citep{hartmann_1998} and, additionally, in a \textit{V,
+  V$-$I} CMD, the reddening vector lies parallel to the pre-MS,
 minimising any age effect of extinction uncertainty, \citep[for a full
-discussion see][]{mayne_2008,mayne_2007}. The
-near-IR passbands of \textit{JHK} are most often used to derive
-stellar masses as for pre-MS objects the reddening vector, in for
-instance, a \textit{J, J$-$K} CMD, is almost perpendicular to the
-isochrones, minimising the mass effect of extinction uncertainties
-\citep[the \textit{CIT} systems was chosen to
+discussion see][]{mayne_2007,mayne_2008}. The near-IR passbands of
+\textit{JHK} are most often used to derive stellar masses. This is as
+for pre-MS objects the reddening vector, in for instance, a \textit{J,
+  J$-$K} CMD, is almost perpendicular to the isochrones. The direction
+of this vector acts to minimise the mass effect of extinction
+uncertainties \citep[the \textit{CIT} systems was chosen to
 match][]{chabrier_2000}. Finally, as is now well documented the
@@
 unambiguously separate naked and star-disc systems
-\citep{luhman_2005a}. In addition, at longer wavelengths, the
-MIPS instrument provides sensitivity to disc systems at much larger
-radii (or debris discs).
+\citep{luhman_2005a}. In addition, at longer wavelengths, the MIPS
+instrument provides sensitivity to disc systems at much larger radii
+(or debris discs).
 
@@
 studies exist on the rotation rates of BD mass objects. Rotation
-period data for $\sigma$ Ori, at an age of $\approx$ 3 Myrs
-\citep{mayne_2008}, was studied in \cite{scholz_2004}, where periods
-are found over the range 5.78$-$74.4 hours ($\approx$ 0.24$-$3.1 days)
-for BD mass objects. \cite{scholz_2005} study rotation period data for
-stars in the vicinity of $\epsilon$ Ori, with an assumed age of
-$\approx$3 Myrs \citep{osorio_2002} and the ONC at an age of
-$\approx$2 Myrs \citep{mayne_2008}. Rotation periods, from photometric
-variability, in the range 4.7$-$87.6 hours ($\approx$ 0.2$-$3.65 days)
-for BD mass stars are found. \cite{joergens_2003} study the rotational
-periods of BD (and very low mass stars) in the Chameleon I
-region. This region is $\le$ 1 Myrs old, and the authors find rotation
-periods of 2.19, 3.376 and 3.21 days for their BD mass counterparts.
+period data for $\sigma$ Ori, at an age of $\approx$\,3 Myrs
+\citep{mayne_2008}, was studied by \cite{scholz_2004}, where periods
+are found over the range 5.78$-$74.4 hours ($\approx$\,0.24$-$3.1
+days) for BD mass objects. \cite{scholz_2005} study rotation period
+data for stars in the vicinity of $\epsilon$ Ori, with an assumed age
+of $\approx$\,3 Myrs \citep{osorio_2002} and the ONC at an age of
+$\approx$\,2 Myrs \citep{mayne_2008}. Rotation periods, from
+photometric variability, in the range 4.7$-$87.6 hours
+($\approx$\,0.2$-$3.65 days) for BD mass stars are
+found. \cite{joergens_2003} study the rotational periods of BD (and
+very low mass stars) in the Chameleon I region. This region is
+$\le$\,1 Myrs old, and the authors find rotation periods of 2.19,
+3.376 and 3.21 days for their BD targets.
 
@@
 relationship extending into the BD regime. Additionally,
-\cite{joergens_2003} propose a shorter lifetime of $\approx$5 Myrs for
+\cite{joergens_2003} propose a shorter lifetime of $\approx$\,5 Myrs for
 BD discs, inferred from a shorter derived disc-locking
@@
 As discussed in Section \ref{par_rotation} evidence for irregular
-periodic variability has been found in BD stars with detections of
+periodic variability has been found in BDs with detections of
 associated stellar discs. This is construed as evidence for accretion
 hot spots formed as magnetically channeled material hits the stellar
-surface \citep[see discussion
-in][]{bouvier_1995,herbst_2007}. The irregularity is
-thought to be caused by changes in the magnetospheric structure and
-accretion rate \citep{bouvier_1995}. For our model we have
-assumed that disc material is disrupted at the co-rotation radius and
-channeled onto the star in the form of accretion hot spots with a
+surface \citep[see discussion in][]{bouvier_1995,herbst_2007}. The
+irregularity is thought to be caused by changes in the magnetospheric
+structure and accretion rate \citep{bouvier_1995}. For our model we
+have assumed that disc material is disrupted at the co-rotation radius
+and channeled onto the star in the form of accretion hot spots with a
 characteristic temperature. Therefore, to calculate the characteristic
@@
 accretion rate is strongly correlated with the mass of the central
-star. This relationship was perhaps first suggested by
-\cite{muzerolle_2003} using various accretion diagnostics. Later,
-\citep{muzerolle_2005} derived a relationship of approximately
-$\dot{M}\propto M_*^2$. Further evidence was put forward by
-\cite{natta_2004}, where accretion rates as low as 5$\times$ 10$^{-12}
-{\rm M}_{\odot} {\rm yr}^{-1}$ were found for BD stars. More recently,
-even lower accretion rates of $\approx$10$^{-13} {\rm M}_{\odot} {\rm
+star. This relationship was first suggested by \cite{muzerolle_2003}
+using various accretion diagnostics. Later, \cite{muzerolle_2005}
+derived a relationship of approximately $\dot{M}\propto
+M_*^2$. Further evidence was put forward by \cite{natta_2004}, where
+accretion rates as low as 5$\times$ 10$^{-12} {\rm M}_{\odot} {\rm
+  yr}^{-1}$ were found for BDs. More recently, even lower
+accretion rates of $\approx$\,10$^{-13} {\rm M}_{\odot} {\rm
   yr}^{-1}$, have been derived for BDs by \cite{herczeg_2009}.
@@
 \cite{natta_2006}. \cite{natta_2006} analysed a set of accretion rates
-and masses derived for BD stars in $\rho$ Ophiuchi and compared these
+and masses derived for BDs in $\rho$ Ophiuchi and compared these
 results to stars in Taurus. They found that the accretion rate scales
@@
 a similar order of magnitude we have adopted $M_{\rm disc}\approx
-$0.01$M_*$. As changes in disc masses are expected to change the
+$\,0.01$M_*$. As changes in disc masses are expected to change the
 resulting SED less than perhaps, accretion rate for example, we have
@@
 
-Discs around BD stars exhibit increased flaring, due to the reduced
+Discs around BDs exhibit increased flaring, due to the reduced
 surface gravity in the disc \citep{walker_2004}. This increased
@@
 \hline
-Input parameter&Values (\# values)\\
+Input parameter&Values (\# of values)\\
 \hline
@@
 
-In this Section we first discuss the physical structure, both density
+In this section we first discuss the physical structure, both density
 and temperature, of the BDD disc systems (Section \ref{disc_struct})
 across our parameter space. Then we discuss the resulting simulated
-observations in Section\ref{observables}. We present analysis in terms
-of the impacts of the disc structure on the SEDs and colours and
+observations in Section \ref{observables}. We present analysis in
+terms of the impacts of the disc structure on the SEDs and colours and
 magnitudes. Then in Section \ref{isochrones} we examine the
@@
 systems. Essentially, despite not intrinsically including a dependence
-of accretion rate on stellar mass in our grid.  We show that current
-observational techniques and theoretical models applied to the grid
-would result in a relationship of this type being derived.
+of accretion rate on stellar mass in our grid, we show that current
+observational techniques and theoretical models, applied to the grid
+,would result in a relationship of this type being derived.
 
@@
 structure, $\Sigma ^{\beta - \alpha}$. The initial scaleheight ($h$)
-and density ($\rho$) follow $h\propto r^{\beta}$
-($h=h_0(r/R_*)^{\beta}$) and $\rho \propto r^{-\alpha}$ ($\rho
-=\rho_0\frac{R_*}{r}exp(-\frac{1}{2}[z/h(r)]^2)$) respectively., where
+and density ($\rho$) follow $h=h_0(r/R_*)^{\beta}$$\rho
+=\rho_0\frac{R_*}{r}exp(-\frac{1}{2}[z/h(r)]^2)$ respectively., where
 $r$ and $z$ are the radial and vertical coordinates. The initial
@@
 
-We have previously tested the {\sc torus} code against that used by
-Walker and co-workers, using a CTTS disc model and simultaneously
-solving for radiative and hydrostatic equilibrium (but not employing
-dust sublimation). These tests showed excellent agreement in density
-and temperature structure, as well as in the resultant SEDs. The
-results of these tests were presented by \cite{walker_2006}. It is
-therefore unsurprising that at negligible mass-accretion rates our
-disc structures are very similar to those present in
-\cite{walker_2004}. Typical discs around CTTS stars have scaleheights
-at 100\,AU of between $h$(100)$=$10 to 20\,AU, whereas for BDD
-systems, $h$(100)=20 to 60\,AU (for 0.08 and 0.01 $M_{\odot}$
+We have previously tested the results of the {\sc torus} code against
+that used by Walker and co-workers, using a CTTS disc model and
+simultaneously solving for radiative and hydrostatic equilibrium (but
+not employing dust sublimation). These tests showed excellent
+agreement in density and temperature structure, as well as in the
+resultant SEDs. The results of these tests were presented by
+\cite{walker_2006}. It is therefore unsurprising that at negligible
+mass-accretion rates our disc structures are very similar to those
+present in \cite{walker_2004}. Typical discs around CTTS stars have
+scaleheights at 100\,AU of between $h$(100)$=$10 to 20\,AU, whereas
+for BDD systems, $h$(100)=20 to 60\,AU (for 0.08 and 0.01 $M_{\odot}$
 respectively). As the accretion rate increases the flux levels of the
@@
 \citep{shakura_1973}. Recently however \cite{ercolano_2009} proposed
-the inverse relation of flaring with stellar mass, i.e. $h\propto
-M_*$. This suggestion was based on evidence from \cite{allers_2006},
-where SEDs for 17 systems in the mass range 6$M_{\rm
-  Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat disc
+that the flaring varied in the opposite sense with stellar mass,
+i.e. $h\propto M_*$. This suggestion was based on evidence from
+\cite{allers_2006}, where SEDs for 17 systems in the mass range
+6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat disc
 models. In general, \cite{allers_2006} find that lower mass objects
@@
 \citep[$>10$\,kK,][]{muzerolle_2003}, while dusty funnel flows are
-likely to be optically thick in the visible, which would lead to
-substantial photometric variability as the funnels transit the
+likely to be optically thick in the visible regime, which would lead
+to substantial photometric variability as the funnels transit the
 photosphere--an effect that is unobserved.
@@
 
-As the inner edge moves its temperature is expected to change, this
+As the inner edge moves, its temperature is expected to change. This
 has been predicted to lead to a correlation of inner edge position and
@@
 between 2 and 3\,$\mu$m \citep{dullemond_2001}, given that the dust
-sublimation temperature peaks at $\approx$1400\,K for canonical
+sublimation temperature peaks at $\approx$\,1400\,K for canonical
 densities. This means that for models where dust is significantly
-sublimated the inner edge will {\em usually} have a temperature of
-$\approx$1400\,K and this correlation of disc position and temperature
-will be lost (although see below).
+sublimated, the inner edge will {\em usually} have a temperature of
+$\approx$\,1400\,K and this correlation of disc position and
+temperature will be lost (although see below).
 
@@
 systems where the inner edge has been eroded significantly from the
-co-rotation radius the temperature of the inner edge will fall
+co-rotation radius, the temperature of the inner edge will fall
 systematically as the inner dust disc radius increases.
@@
 For further analysis, and throughout the rest of this paper, we will
-separate the systems into two groups. These groups are those systems
-with \logmdot$\leq-9$ and \logmdot$\geq-9$, classed as typical and
-extreme accretors. This distinction is based on the point at which the
-systems undergo both significant sublimation ($\Delta R_{\rm
-  inner}>1R_*$) and have an accretion luminosity that is comparable to
-the photospheric luminosity (see Section~\ref{acc_dominance}). In
-order to examine the effect of dust sublimation on our models we have
-measured the radius of the inner edge of the dust disc by integrating
-from the centre along the midplane until an optical depth of 2/3 (at
-5500\AA) is reached. Figure \ref{inner_temp} shows the radial density
-distribution of the disc.  In this case the the final inner edge
-radius and therefore temperature is no longer strongly correlated with
-the rotation rate. Figure \ref{inner_temp} shows the final inner edge
-location ($R_{\rm inner}$, $R_*$) against the temperature of the inner
-wall ($T_{\rm inner}$, K). The left panel shows the systems designated
-as typical accretors and the right panel those with extreme accretion
-rates.  For both panels the systems with rotation periods of 0.5 and 5
-days are plotted in red and blue respectively. Those systems where the
-change in inner radius was greater than 1$R_*$, and therefore classes
-as significantly sublimated, are plotted as crosses.
+separate the systems into two groups; those systems with
+\logmdot$\leq-$9 and \logmdot$>-$9, classed as typical and extreme
+accretors. This distinction is based on the point at which the systems
+undergo both significant sublimation ($\Delta R_{\rm inner}>1R_*$) and
+have an accretion luminosity that is comparable to the photospheric
+luminosity (see Section~\ref{acc_dominance}). In order to examine the
+effect of dust sublimation on our models we have measured the radius
+of the inner edge of the dust disc by integrating from the centre
+along the midplane until an optical depth of 2/3 (at 5500\AA) is
+reached. Figure \ref{inner_temp} shows the radial density distribution
+of the disc.  In this case, the final inner edge radius, and therefore
+temperature, is no longer strongly correlated with the rotation
+rate. Figure \ref{inner_temp} shows the final inner edge location
+($R_{\rm inner}$) against the temperature of the inner wall ($T_{\rm
+  inner}$). The left panel shows the systems designated as typical
+accretors and the right panel those with extreme accretion rates.  For
+both panels the systems with rotation periods of 0.5 and 5 days are
+plotted in red and blue respectively. Those systems where the change
+in inner radius was greater than 1$R_*$, classed as significantly
+sublimated, are plotted as crosses.
 
@@
 \caption{Figure showing data for the inner edge location ($R_{\rm
-       inner}$, $R_*$). The typical accretors are shown in the
-     left panel and the extreme accretors in the
-     right panel (see text for explanation). In both
-       panels separate the systems by period, with those systems with
-     rotation periods of 0.5 and 5 days shown as red and blue symbols
-     respectively. In addition, systems where $\Delta R_{\rm inner} <
-     1R_*$ are plotted as crosses and $\Delta R_{\rm inner} > 1R_*$ as
-     filled circles (this is only achieved by some systems classed as
-     extreme accretors).\label{inner_temp}}
+    inner}$, $R_*$). The typical accretors are shown in the left panel
+  and the extreme accretors in the right panel (see text for
+  explanation). Both panels separate the systems by period, with those
+  systems with rotation periods of 0.5 and 5 days shown as red and
+  blue symbols respectively. In addition, systems where $\Delta R_{\rm
+    inner} < 1R_*$ are plotted as crosses and $\Delta R_{\rm inner} >
+  1R_*$ as filled circles (this is only achieved by some systems
+  classed as extreme accretors).\label{inner_temp}}
 \end{figure*}
@@
 Figure \ref{inner_temp} shows that for those systems where significant
-disc erosion ($\Delta R_{\rm inner} > 1.0 R_*$) has occurred the
+disc erosion ($\Delta R_{\rm inner} > 1 R_*$) has occurred the
 resulting temperature of the inner edge is weakly correlated with the
@@
 Finally the most extreme accretor (Figure~\ref{sub_181_a}) shows dust
-being destroyed to very large radii ($\sim 0.1$\, AU). A curved rim is
-present, without any obvious decrease in scaleheight behind the inner
-rim. The distance from the central object is such that the vertical
-component of gravity is much diminished, and the disc has a
+being destroyed out to very large radii ($\sim 0.1$\, AU). A curved
+rim is present, without any obvious decrease in scaleheight behind the
+inner rim. The distance from the central object is such that the
+vertical component of gravity is much diminished, and the disc has a
 substantial scaleheight at the inner edge, meaning that it reprocesses
@@
 
-Disentangling the accretion and stellar photospheric flux, in order to
-derive accretion rates becomes difficult as $T_{\rm acc} \to T_{\rm
-  eff}$, which for an accretion rate of \logmdot = $-9$, occurs at a
-fractional coverages of 20 and 10\%, for rotation periods of 5 and 0.5
-days (with $M_*=0.04M_{\odot}$ and an age of 1 Myr). Additionally,
-higher accretion rates can produce enough flux to `veil' the
-underlying photospheric features, and significantly change the peak
-flux levels. Heavy veiling of atomic lines has been extensively
-observed in CTTS systems \citep[e.g][]{kenyon_1995}.
-
-Figure \ref{acc_dom} shows the affect of increasing the accretion
-blackbody flux (for increasing accretion rates) for a BD star,
+As $T_{\rm acc} \to T_{\rm eff}$, disentangling the accretion and
+stellar photospheric flux, in order to derive accretion rates becomes
+difficult. This equivalence in accretion hot spot and stellar
+photospheric temperature, for an accretion rate of \logmdot = $-9$,
+occurs at a fractional coverages of 20 and 10\%, for rotation periods
+of 5 and 0.5 days (with $M_*=0.04M_{\odot}$ and an age of 1
+Myr). Additionally, higher accretion rates can produce enough flux to
+`veil' the underlying photospheric features, and significantly change
+the peak flux levels. Heavy veiling of atomic lines has been
+extensively observed in CTTS systems \citep[e.g][]{kenyon_1995}.
+
+Figure \ref{acc_dom} shows the effect of increasing the accretion
+blackbody flux (for increasing accretion rates) for a BD,
 $M=$0.04$M_{\odot}$, at 1 Myr. Whilst the photon packets originating
 from the star (both from $L_*$ and $L_{\rm acc}$) will be tagged as
-stellar by {\sc torus} we can separate these flux contributions simply
-by observing the naked star system. The panels in Figure \ref{acc_dom}
-show the flux from a naked system, with no treatment of the disc. This
-enables us to view the effect of increasing accretion rate on the
-photospheric flux in isolation. The accretion rates included in all
-panels are \logmdot = $-8$, $-9$ and $-12$ (blue, black and red lines
-respectively). The bottom panels show the systems with a rotation
-period of 5 days and top panels for those with a rotation period of
-0.5 days. Given our assumption that accretion occurs from the
-co-rotation radius, decreasing the rotational period moves this
-accretion radius closer to the star, $R_{\rm inner}\propto \tau^{2/3}$
-(see Equation \ref{inner_eq}). As the accretion radius moves father
-from the star the potential energy released by the accreted material
-is increased. This effect can be seen when comparing the top and
-bottom panels, although the effect is marginal for all but the highest
-displayed accretion rates.
+stellar by {\sc torus}, we can separate these flux contributions
+simply by observing the naked star system. The panels in Figure
+\ref{acc_dom} show the flux from a naked system, with no treatment of
+the disc. This enables us to view the effect of increasing accretion
+rate on the photospheric flux in isolation. The accretion rates
+included in all panels are \logmdot = $-8$, $-9$ and $-12$ (blue,
+black and red lines respectively). The bottom panels show the systems
+with a rotation period of 5 days and top panels for those with a
+rotation period of 0.5 days. Given our assumption that accretion
+occurs from the co-rotation radius, decreasing the rotational period
+moves this accretion radius closer to the star, $R_{\rm inner}\propto
+\tau^{2/3}$ (see Equation \ref{inner_eq}). As the accretion radius
+moves further from the star the potential energy released by the
+accreted material is increased. This effect can be seen when comparing
+the top and bottom panels, although the effect is marginal for all but
+the highest displayed accretion rates.
 
@@
 \includegraphics[scale=0.6,angle=90]{./Fig/acc_dom.ps}
-\caption{Figure showing the photospheric flux (log(ergs$/s/cm^2/{\rm
-    \AA}$)) against $\lambda$ (log($\mu$m)) of a Brown Dwarf with
+\caption{Figure showing the photospheric flux (log(ergs$\rm{/s/cm}^2/{\rm
+    \AA}$)) against $\lambda$ (log($\mu$m)) of a BD with
   $M=$0.04$M_{\odot}$, at 1 Myr. No disc is included, but blackbody
@@
 The left panels show accretion streams with an areal coverage of 10\%
-and the left panels 1\%. As the areal coverage reduces the effective
+and the left panels 1\%. As the areal coverage reduces, the effective
 temperature of the accretion hot spot increases, resulting in an
-increase in accretion flux, and resulting shift to bluer wavelengths
-of the peak flux. This can be seen clearly by comparing the left and
-right panels of Figure \ref{acc_dom}. As the rotation rate increases
-the co-rotation radius also increases, as shown in Equation
+increase in accretion flux, and a shift to bluer wavelengths of the
+peak flux. This can be seen clearly by comparing the left and right
+panels of Figure \ref{acc_dom}. As the rotation rate increases the
+co-rotation radius also increases, as shown in Equation
 \ref{inner_eq}, $R_{\rm inner}\propto \tau^{\frac{2}{3}}$. Therefore,
@@
 increase in potential energy lost by the mass accreted. This can be
-seen in Figure by comparing the left and right panels of Figure
+seen by comparing the left and right panels of Figure
 \ref{acc_dom}. Perhaps the most important, albeit qualitative, result
@@
 expected \citep{gullbring_1998}. The impact on the photometry of BDD
-systems is discussed in the next Section for individual stars and in
+systems is discussed in the next section for individual stars and in
 Section \ref{isochrones} for populations.
@@
 As shown in Figures \ref{flare_-12_183} and \ref{flare_-7_193} and
-discussed in Section \ref{disc_flaring} BDD systems under vertical
+discussed in Section \ref{disc_flaring}, BDD systems in vertical
 hydrostatic equilibrium have highly flared discs. As discussed in
 \cite{walker_2004} this increased flaring (when compared to CTTS
-stars) leads to occultation at the star at lower inclination angles
+stars) leads to occultation of the star at lower inclination angles
 and, therefore, significant changes to the SED. Increases in the
@@
 
-Figure \ref{flare_inc} shows the total SEDs for the BDD system of
-Figures \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
-bottom panels respectively. The lines show the flux over all the ten
+Figure \ref{flare_inc} shows the SEDs for the BDD system of Figures
+\ref{flare_-12_183} and \ref{flare_-7_193} as the top and bottom
+panels respectively. The lines show the flux over all the ten
 inclinations (see Table \ref{par_space_table}), with the dashed line
@@
 shown in the top panel of Figure \ref{flare_mag}. As the accretion
-rate increases the system moves to brighter magnitudes in $M_V$. The
+rate increases, the system moves to brighter magnitudes in $M_V$. The
 move to brighter magnitudes becomes significant once the accretion
@@
 
-Therefore, for individual systems changes in the accretion rate and
-disc structure lead to significant changes in magnitudes and
-colours. The data presented in this section are for an isolated mass
-and age. However, the trends described are evident throughout our
-model grid for any given subset, and as such are representative. The
-scatter or changes in magnitude in the individual systems will change
-as a function of the remaining variables, but the dominant input
-variables affecting simulated photometry are accretion rate and
-inclination. For populations of stars these changes in magnitude and
-colour act to scatter or spread a BD locus in photometric space.
+Thus, for individual systems changes in the accretion rate and disc
+structure lead to significant changes in magnitudes and colours. The
+data presented in this section are for an isolated mass and
+age. However, the trends described are evident throughout our model
+grid for any given subset, and as such are representative. The scatter
+or changes in magnitude in the individual systems will change as a
+function of the remaining variables, but the dominant input variables
+affecting simulated photometry are accretion rate and inclination. For
+populations of stars these changes in magnitude and colour act to
+scatter or spread a BD locus in photometric space.
 
@@
 
-Practically, most parameters for young pre-MS and BD stars are derived
+Practically, most parameters for young pre-MS and BDs are derived
 from surveys of populations, usually open clusters, using broadband
@@
 colour-colour diagrams (CMDs and CoCoDs respectively, hereafter).  In
-this Section we explore the consequences of our model grid on the
+this section we explore the consequences of our model grid on the
 derivation of the primary parameters of age, mass and disc fractions,
@@
 colours for the $M_*=0.01M_{\odot}$ systems at high inclinations
-become extremely faint and red, and we omit them from the Figures in
+become extremely faint and red, and we omit them from the figures in
 order to conserve an appropriate scaling for the majority of the
 models. Additionally, stars at the highest inclinations, i.e edge on
-disc systems, are often omitted from the Figures due to their
+disc systems, are often omitted from the figures due to their
 extremely faint magnitudes, meaning they would not be practically
@@
 caused by accretion rate and inclination. Therefore for derivation of
-parameters we explore the scatter in BD locii as a function of
+parameters we explore the scatter in BD loci as a function of
 accretion rate and inclination.
@@
 variables are in the range expected for a BD population, one could
-reasonably expect observed true BD locii to show a similar scatter. It
+reasonably expect observed true BD loci to show a similar scatter. It
 is clear that even a wide photometric selection would not even include
@@
 some objects have magnitudes fainter than those shown (for instance
-$M_V\approx 20$). This is expected as the star becomes obscured by the
+$M_V\approx$\,20). This is expected as the star becomes obscured by the
 flared disc, interestingly for typical systems the bottom right panels
@@
 \ref{par_space} for justification), our simulated photometry shows,
-qualitatively, that a coeval 1 Myr population of accreting BD stars
+qualitatively, that a coeval 1 Myr population of accreting BDs
 and BDD systems, with typical accretion rates and range of
@@
 longer wavelength bands in the IRAC CoCoDs the separation between the
-disc and naked locii increases. As the wavelength gets longer the flux
+disc and naked loci increases. As the wavelength gets longer the flux
 originates from regions of the disc at lower temperature and therefore
@@
 and flared associated disc. Essentially, at present it is unclear how
-many BD stars are not included in this relationship due to
+many BDs are not included in this relationship due to
 misidentification. As explained in \cite{walker_2004}, BD systems with
@@
 \appendix
+
+\section{Website}
+\label{website}
+
+As stated throughout this paper the data presented are available from
+a web page\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.
+
+\subsection{Available Data}
+\label{web_data}
+
+The magnitudes and colours presented in this paper are available both
+as individual magnitudes and as isochrones or mass tracks. Photometric
+magnitudes have also been derived for several other systems and are
+available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
+\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$ and $B_t$
+\citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
+\citep{bessell_1988,bessell_1998}, SDSS \textit{UGRIZ}
+\citep{fukugita_1996}, 2MASS $JHK_s$
+\citep{cohen_2003,skrutskie_2006}, MKO \textit{JHK}
+\citep{simons_2002,tokunaga_2002}, UKIRT \textit{ZYJHK}
+\citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
+\citep{neugebauer_1984} and SCUBA \textit{450WB} and \textit{850WB}
+\citep{holland_1999}. For further information on these magnitudes,
+such as the filter responses used and the adopted zeropoints please
+refer to the website.
+
+\textit{Monochromatic fluxes}
+
+In addition to the magnitudes derived for each of these bands
+monochromatic fluxes have also been derived for all bands listed
+above. These have been derived following closely the methods of
+\cite{robitaille_2006}, extended to further passbands. For details
+of the assumed SED shape, central wavelengths and bandpasses adopted
+please refer to the website. The derivations of these monochromatic
+fluxes will be detailed in a coming paper, which details a fitting
+tool associated with these data.
 
@@
 likely as the models available online, have a later time stamp,
-$\approx$ 2005 compared to 2000). For the final published magnitudes,
+$\approx$\,2005 compared to 2000). For the final published magnitudes,
 for the naked systems, we have used a similar wavelength resolution as
@@
 
-\section{Website}
-\label{website}
-
-As stated throughout this paper the data presented are available from
-a web page\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.
-
-\subsection{Available Data}
-\label{web_data}
-
-The magnitudes and colours presented in this paper are available both
-as individual magnitudes and as isochrones or mass tracks. Photometric
-magnitudes have also been derived for several other systems and are
-available online. These are Johnson, Cousins \textit{UBVRI(JHK)}
-\citep{johnson_1966,bessell_2005}, \textit{Tycho} $V_t$ and $B_t$
-\citep{bessell_2000}, Bessell \textit{UBVRIJHKL}
-\citep{bessell_1988,bessell_1998}, SDSS \textit{UGRIZ}
-\citep{fukugita_1996}, 2MASS $JHK_s$
-\citep{cohen_2003,skrutskie_2006}, MKO \textit{JHK}
-\citep{simons_2002,tokunaga_2002}, UKIRT \textit{ZYJHK}
-\citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
-\citep{neugebauer_1984} and SCUBA \textit{450WB} and \textit{850WB}
-\citep{holland_1999}. For further information on these magnitudes,
-such as the filter responses used and the adopted zeropoints please
-refer to the website.
-
-\textit{Monochromatic fluxes}
-
-In addition to the magnitudes derived for each of these bands
-monochromatic fluxes have also been derived for all bands listed
-above. These have been derived following closely the methods of
-\cite{robitaille_2006}, extended to further passbands. For details
-of the assumed SED shape, central wavelengths and bandpasses adopted
-please refer to the website. The derivations of these monochromatic
-fluxes will be detailed in a coming paper, which details a fitting
-tool associated with these data.
-
 \label{lastpage}

### 2010-07-15 torus/lucy_mod.F90
Eliminate unused variable warnings.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2378 25464f21-6099-402c-b30a-640f1d40d38b

@@ -34,7 +34,6 @@ contains
     use amr_mod, only: myScaleSmooth, myTauSmooth, findtotalmass, scaledensityamr
     use dust_mod, only: filldustuniform, stripdustaway, sublimatedust, sublimatedustwr104
 #ifdef MPI
-    use input_variables, only : blockhandout
     use mpi_global_mod, only: myRankGlobal, nThreadsGlobal
     use parallel_mod, only: mpiBlockHandout, mpiGetBlock
 #endif
@@ -139,9 +138,7 @@ contains
     ! For MPI implementations =====================================================
     integer ::   ierr           ! error flag
     !  integer ::   n_rmdr, m      !
-    integer, dimension(:), allocatable :: photonBelongsRank
     integer, parameter :: tag = 0
-    logical :: rankComplete
     integer(bigInt) ::  np, n_rmdr, m  
     real :: buffer_real(nThreadsGlobal)     
 

### 2010-07-15 torus/setupamr_mod.F90

@@ -60,7 +60,7 @@ contains
     character(len=80) :: message
     integer :: nVoxels, nOctals
 !    integer(bigInt) :: i
-    integer :: nUnrefine
+!    integer :: nUnrefine
     constantAbundance = .true.
 
 #ifdef MPI

### 2010-07-15 BDD_submit/paper.tex
Changed figures to .pdf and website url
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2379 25464f21-6099-402c-b30a-640f1d40d38b

@@
 available online through our browsing
-tool\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
-  disc} which is described in Appendix \ref{website}.
+tool\footnote{http://bd-server.astro.ex.ac.uk/} which is described in Appendix \ref{website}.
 
@@
 \begin{figure}
-  \includegraphics[scale=0.3,angle=90]{./Fig/albedo.ps}
+  \includegraphics[scale=0.3,angle=90]{./Fig/albedo.pdf}
  \caption{Figures of the albedo (top panel), and scattering
@@
 used explicitly in the analysis within this paper. These magnitudes
-are available
-online\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore
-  disc} and are briefly discussed in Appendix \ref{website}. In
-addition, monochromatic fluxes have been derived for all filters, and
-again are available online and discussed in Appendix \ref{website}.
+are available online\footnote{http://bd-server.astro.ex.ac.uk/} and
+are briefly discussed in Appendix \ref{website}. In addition,
+monochromatic fluxes have been derived for all filters, and again are
+available online and discussed in Appendix \ref{website}.
 
@@
 \begin{center}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-12_183.ps}\label{flare_-12_183}}
-  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-7_193.ps}\label{flare_-7_193}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-12_183.pdf}\label{flare_-12_183}}
+  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-7_193.pdf}\label{flare_-7_193}}
 \end{center}
@@
 \begin{figure*}
-\includegraphics[scale=0.5,angle=90]{./Fig/inner_temp.ps}
+\includegraphics[scale=0.5,angle=90]{./Fig/inner_temp.pdf}
 \caption{Figure showing data for the inner edge location ($R_{\rm
@@
   \centering
-  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
-  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
-  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
-  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
-  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
-  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
+  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/no_sub_183_density.pdf}\label{no_sub_183_a}}
+  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/no_sub_183_temp.pdf}\label{no_sub_183_b}}
+  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_179_density.pdf}\label{sub_179_a}}
+  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_179_temp.pdf}\label{sub_179_b}}
+  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_181_density.pdf}\label{sub_181_a}}
+  \subfigure[]{\includegraphics[scale=0.27,angle=0]{./Fig/sub_181_temp.pdf}\label{sub_181_b}}
 
@@
 \begin{figure*}
-\includegraphics[scale=0.6,angle=90]{./Fig/acc_dom.ps}
+\includegraphics[scale=0.6,angle=90]{./Fig/acc_dom.pdf}
 \caption{Figure showing the photospheric flux (log(ergs$\rm{/s/cm}^2/{\rm
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_inc.pdf}
   \caption{Figure showing both total SEDs of the systems shown in
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.pdf}
   \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_VVI.pdf}
   \caption{Figure showing CMDs in $M_V$, $(V-I)_0$ for typical
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/age_mass_JJK.pdf}
   \caption{Figure showing the same data in the same format and with
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_JHJK.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_JHJK.pdf}
   \caption{Figure showing $(J-K)_0$, $(J-H)_0$ CoCoDs for typical
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_irac.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_irac.pdf}
   \caption{Figure showing $([3.6]-[4.5])_0$, $([4.5]-[5.8])_0$ CoCoDs
@@
   \centering
-  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_mips.ps}
+  \includegraphics[scale=0.6,angle=90]{./Fig/disc_frac_mips.pdf}
   \caption{Figure showing $(24-70)_0$, $(70-160)_0$ CoCoDs in the same
@@
   \centering
-  \includegraphics[scale=0.65,angle=90]{./Fig/disc_cuts.ps}
+  \includegraphics[scale=0.65,angle=90]{./Fig/disc_cuts.pdf}
   \caption{Figure showing both from top to bottom, the disc candidate
@@
 As stated throughout this paper the data presented are available from
-a web page\footnote{http://www.astro.ex.ac.uk/research/bd\textunderscore disc}.
+a web page\footnote{http://bd-server.astro.ex.ac.uk/}.
 

### 2010-07-16 torus/amr_mod.f90
openmp updates - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2381 25464f21-6099-402c-b30a-640f1d40d38b

@@ -2511,7 +2511,7 @@ CONTAINS
 
     IMPLICIT NONE
 
-    TYPE(octal), POINTER              :: octalTree
+    TYPE(octal), POINTER, intent(in)              :: octalTree
     TYPE(vector), INTENT(IN)     :: point
     TYPE(vector)                 :: point2 ! may be projected point
     TYPE(octal), OPTIONAL, POINTER    :: startOctal
@@ -2616,8 +2616,13 @@ CONTAINS
 
        ! unrotated poistion should be passed here!
 
-       IF (PRESENT(velocity))  velocity = amrGridVelocity(octalTree,point,startOctal=resultOctal,&
-            actualSubcell=subcell) 
+       IF (PRESENT(velocity)) then
+          velocity = VECTOR(0.d0, 0.d0, 0.d0) 
+          if (associated(resultOctal%cornerVelocity)) then
+             velocity = amrGridVelocity(octalTree,point,startOctal=resultOctal,&
+                  actualSubcell=subcell) 
+          endif
+       ENDIF
 
 
 
@@ -2782,6 +2787,8 @@ CONTAINS
     logical, optional :: linearinterp
     logical :: linear
 
+    amrGridVelocity = VECTOR(0.d0, 0.d0, 0.d0)
+
     weights = 0.d0
     if(present(linearinterp)) then
        linear = linearinterp
@@ -2820,6 +2827,8 @@ CONTAINS
       IF (PRESENT(foundSubcell)) foundSubcell =  subcell
 
    END IF
+
+   if (.not.associated(resultOctal%cornerVelocity)) goto 666
 
       inc = 0.5 * resultOctal%subcellSize
       centre = subcellCentre(resultOctal,subcell)
@@ -11538,6 +11547,7 @@ end function readparameterfrom2dmap
     integer(double),save :: nlambda
     real(double) :: tgas
     
+!$OMP THREADPRIVATE (firstTime, nLambda, tgasArray, oneKappaAbsT, oneKappaScaT)
 
     if ( present(reset_kappa) ) then 
        if ( reset_kappa ) then 
@@ -11717,7 +11727,7 @@ end function readparameterfrom2dmap
           if (ndusttype .eq. 1) then
              if (grid%nLambda == 1) then
                 kappaAbs = thisOctal%dustTypeFraction(subcell, 1) *  &
-                     grid%oneKappaAbs(i,1) * thisOctal%rho(subcell)
[…]

### 2010-07-16 torus/amr_utils_mod.f90

@@ -583,13 +583,14 @@ module amr_utils_mod
     ! true if the point lies within the boundaries of the current octal
   
     use input_variables, only : hydrodynamics
+    use vector_mod, only : projectToXZ
     IMPLICIT NONE
     LOGICAL                       :: inOctal
     TYPE(octal), INTENT(IN)       :: thisOctal
     TYPE(vector), INTENT(IN) :: point
     TYPE(vector)             :: octVec2D
     real(double)                  :: r, phi, dphi, eps
-    logical, optional :: alreadyRotated
+    logical, intent(in), optional :: alreadyRotated
     logical :: doRotate
 
     doRotate = .true.

### 2010-07-16 torus/diffusion_mod.F90

@@ -254,11 +254,11 @@ contains
 !$OMP PARALLEL DEFAULT(NONE) &
 !$OMP PRIVATE(iOctal, eDens, dCoeff,subcell, thisOctal, octVec, startOctal, r) &
 !$OMP PRIVATE(neighbourOctal, neighbourSubcell, enplus1, firsttime, deltax, deltat) &
-!$OMP PRIVATE(deltaE, octalarray, grade, dcoeffhalf, lambda, bigr) &
+!$OMP PRIVATE(deltaE, grade, dcoeffhalf, lambda, bigr) &
 !$OMP PRIVATE(phi, DeltaPhi, rVec, DeltaR, DeltaZ) &
-!$OMP SHARED(overCorrect) & 
+!$OMP SHARED(overCorrect, octalArray) & 
 !$OMP SHARED(grid, tol, demax, ioctal_beg, ioctal_end) 
-!$OMP DO SCHEDULE(runtime)
+!$OMP DO SCHEDULE(static)
     do iOctal =  iOctal_beg, iOctal_end
 
        thisOctal => octalArray(iOctal)%content
@@ -624,10 +624,10 @@ contains
                       enPlus1 = arad*(10.d0**4)
                    endif
                 endif
-                          thisOctal%eDens(subcell) = enPlus1
-!                thisOctal%chiline(subcell) = enPlus1
-                          thisOctal%temperature(subcell) = sqrt(sqrt(enPlus1 * OneOveraRad))
-
+                !$OMP CRITICAL
+                thisOctal%eDens(subcell) = enPlus1
+                thisOctal%temperature(subcell) = sqrt(sqrt(enPlus1 * OneOveraRad))
+                !$OMP END CRITICAL
                 deltaE = abs(enPlus1-thisOctal%oldeDens(subcell)) &
                      / thisOctal%oldEdens(subcell)
                 deMax = max(deMax, deltaE)

### 2010-07-16 torus/lucy_mod.F90

@@ -106,7 +106,7 @@ contains
     real:: percent_undersampled
     integer(double) :: nAbs_sub, nScat_sub, nInf_sub  ! For OpenMP
     integer :: nKilled
-    integer       :: imonte_beg, imonte_end   ! the index boundary for the photon loops.
+    integer(bigInt)       :: imonte_beg, imonte_end   ! the index boundary for the photon loops.
     real(double)  :: kAbsArray(nlambda),kAbsArray2(nlambda)
     logical :: ok                             ! Did call to randomWalk complete OK?
     logical :: photonInDiffusionZone
@@ -352,10 +352,6 @@ contains
 
           call resetDirectGrid(grid%octreeRoot)
 
-          nInf_sub = 0
-          nScat_sub = 0
-          nAbs_sub = 0
-          nDiffusion_sub = 0
           nInf = 0
           nScat = 0
           nAbs = 0
@@ -410,6 +406,9 @@ contains
 
 #endif    
 
+#ifdef _OPENMP
+                 call testRandomOMP()
+#endif
                 !$OMP PARALLEL DEFAULT(NONE) &
                 !$OMP PRIVATE(iMonte, iSource, thisSource, rVec, uHat, rHat) &
                 !$OMP PRIVATE(escaped, wavelength, thisFreq, thisLam, iLam, octVec) &
@@ -431,14 +430,19 @@ contains
                 !$OMP SHARED(nAbs, nScat, nInf, nDiffusion, nKilled) 
 
 
-                !$OMP DO SCHEDULE(runtime)
+                 nInf_sub = 0
+                 nScat_sub = 0
+                 nAbs_sub = 0
+                 nDiffusion_sub = 0
 
-
+                !$OMP DO SCHEDULE(static)
                 photonloop: do iMonte = imonte_beg, imonte_end
 !                    if (mod(iMonte,imonte_end/10) == 0) write(*,*) "imonte ",imonte
 #ifdef MPI
                    !  if (MOD(i,nThreadsGlobal) /= myRankGlobal) cycle photonLoop
 #endif
+                   
+
                    thisPhotonAbs = 0
                    call randomSource(source, nSource, iSource)
                    thisSource = source(iSource)
@@ -538,7 +542,6 @@ contains
 
                             call amrGridValues(grid%octreeRoot, octVec, startOctal=thisOctal, &
[…]

### 2010-07-16 torus/parallel_mod.F90

@@ -342,6 +342,7 @@ contains
      deallocate(itest)
    end subroutine test_random_across_threads
 
+
 ! End of MPI routines ----------------------------------------------------------
 
 #else

### 2010-07-16 torus/phaseloop_mod.F90

@@ -326,7 +326,7 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
      o6yarray(i) = 1.e-10
   enddo
 
-  if (mie) nOuterLoop = nLambda
+  if (mie.or.dustPhysics) nOuterLoop = nLambda
 
   allocate(errorArray(nOuterLoop,1:nLambda))
   allocate(varianceArray(1:nLambda))
@@ -1346,7 +1346,7 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
            if (nSource > 0) then              
               if (.not.starOff) then
                  lCore = sumSourceLuminosityMonochromatic(source, nsource, dble(grid%lamArray(iLambdaPhoton)), grid)
-                 if (writeoutput) write(*,*) "Core luminosity is: ",lcore, " erg/s/A ", lcore/(fourpi * objectDistance**2)
+!                 if (writeoutput) write(*,*) "Core luminosity is: ",lcore, " erg/s/A ", lcore/(fourpi * objectDistance**2)
               else
                  lcore = tiny(lcore)
               endif
@@ -1470,9 +1470,9 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
 
 
         nFromEnv = 0
-!$OMP DO SCHEDULE(DYNAMIC)
+!$OMP DO SCHEDULE(static)
         innerPhotonLoop: do i = iInner_beg, iInner_end
-
+!           write(*,*) omp_get_thread_num(), i
 #ifdef MPI
  !  if (MOD(i,nThreadsGlobal) /= myRankGlobal) cycle innerPhotonLoop
 #endif

### 2010-07-16 torus/phasematrix_mod.f90

@@ -71,6 +71,8 @@ module phasematrix_mod
   real, allocatable, private, save :: prob(:,:), probtemp(:), cosArray(:)
   logical, save, private :: setupMieDir = .true.
 
+!$OMP THREADPRIVATE (prob, probtemp, cosArray, setupMieDir)
+
 contains
 
   ! this function applies a phase matrix to a stokes vector
@@ -399,6 +401,8 @@ contains
     type(PHASEMATRIX) :: miePhase(nDustType, nLambda, nMuMie)
     integer :: i, j
     logical, save :: firstTime = .true.
+
+!$OMP THREADPRIVATE(firstTime)
 
     do i = 1, nDustType
        do j = 1, nLambda

### 2010-07-16 torus/setupamr_mod.F90

@@ -820,7 +820,6 @@ contains
           child => thisOctal%child(i)
           call myFreeGrid(child)
        enddo
-       write(*,*) "deallocating at depth ",thisOctal%nDepth
        deallocate(thisOctal%child)
     endif
 

### 2010-07-16 torus/surface_mod.f90

@@ -212,7 +212,6 @@ contains
     nullify(surface%nuarray) 
     nullify(surface%hnuarray) 
     
-    print *, 'Deallocated memory used for surface'
 
     
   end subroutine emptySurface

### 2010-07-16 torus/timing.f90

@@ -108,11 +108,13 @@ contains
     
     if (dum_i.eq.1) then ! the first call in pair 
        !cpu_start(id_num) = ETIME(time_array)
-       call CPU_TIME(cpu_start(id_num))
+!       call CPU_TIME(cpu_start(id_num))
+       call wallTime(cpu_start(id_num))
        
     elseif (dum_i.eq.0) then ! the second call in pair
        !cpu_time = ETIME(time_array) - cpu_start(id_num)
-       call CPU_TIME(cputime)
+!       call CPU_TIME(cputime)
+       call wallTime(cpuTime)
        cputime = cputime - cpu_start(id_num)
 !       minutes = NINT(cputime)/60 ! this is wrong! (RK)
        minutes = INT(cputime/60.)
@@ -131,6 +133,13 @@ contains
     return
   end subroutine tune
 
+
+  subroutine wallTime(rSec)
+    integer ::  count,countRate
+    real :: rSec
+    call system_clock(count=count,count_rate=countRate)
+    rSec = real(count)/real(countRate)
+  end subroutine wallTime
 
 end module timing
 

### 2010-07-16 torus/vector_mod.f90

@@ -149,7 +149,7 @@ contains
     type(VECTOR) :: ZeroVec = VECTOR(0.d0,0.d0,0.d0)
     real(double) :: m, oneOverM
     logical, save :: firstTime = .true.
-
+    !$OMP THREADPRIVATE(firstTime)
     if (a .eq. ZeroVec) then
        if (firstTime) then
           write(*,'(a)') "! Attempt to normalize the zero vector"
@@ -527,7 +527,7 @@ contains
     type(VECTOR) :: OUT
     type(VECTOR), save :: outprev, rvecprev
     type(VECTOR),intent(in) :: rVec
-
+    !$OMP THREADPRIVATE(outprev, rvecprev)
     if(rvec .eq. rvecprev) then
        out = outprev
     else

### 2010-07-16 torus/lucy_mod.F90
g95 bug fixes - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2382 25464f21-6099-402c-b30a-640f1d40d38b

@@ -2106,7 +2106,6 @@ subroutine toNextEventAMR(grid, rVec, uHat,  escaped,  thisFreq, nLambda, lamArr
       photonInDiffusionZone, diffusionZoneTemp,  directPhoton, scatteredPhoton, &
        startOctal, foundOctal, foundSubcell, ilamIn, kappaAbsOut, kappaScaOut)
 
-   use input_variables, only : storeScattered, scatteredLightWavelength
    use diffusion_mod, only: randomwalk
 
    type(GRIDTYPE) :: grid

### 2010-07-16 BDD_submit/paper.tex
Various typos
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2383 25464f21-6099-402c-b30a-640f1d40d38b

@@
 mass, \citep{muzerolle_2003,natta_2004,natta_2006}, with an
-approximate form $\dot{M}_{\rm acc}\propto M^2_*$. Since in the
+approximate form $\dot{M}\propto M^2_*$. Since in the
 canonical picture the accretion rate is driven by the disc viscosity,
@@
 $R_{\rm mag}\approx R_{\rm co}$,
-\citep{koenigl_1991,shu_1994}. Therefore, for our
-model simulations, this inner edge radius is dependent on, and derived
-from, the adopted value of the rotational period for the central star,
-as well as being weakly dependent on the stellar mass. As discussed in
-Section \ref{intro}, the inner disc can be cleared through a number of
+\citep{koenigl_1991,shu_1994}. Therefore, for our model simulations,
+this inner edge radius is dependent on, and derived from, the adopted
+value of the rotational period for the central star, as well as being
+weakly dependent on the stellar mass. As discussed in Section
+\ref{intro}, the inner disc can be cleared through a number of
 mechanisms, including binarity or giant planet formation,
 photoevaporation or photoionisation of the disc and dust grain growth
-or settling. For BDD systems where a disc is modeled a treatment of
+or settling. For BDD systems where a disc is modelled a treatment of
 dust sublimation is included (discussed in Section \ref{dust_edge}).
@@
 smaller coverages, when compared to cooler or `plage' spots
-\citep{herbst_2007}. \cite{bouvier_1995} modeled the
+\citep{herbst_2007}. \cite{bouvier_1995} modelled the
 size of the cool spots on solar-type stars for a selection of
@@
 probable hot spot area of around 10\%. The spot temperature was also
-modeled for YY Orionis in \cite{bertout_1996}, resulting in a
+modelled for YY Orionis in \cite{bertout_1996}, resulting in a
 best fitting areal coverage of 11\%. Therefore, to bound the probable
@@
 fractions, for instance \citep{walker_2004} use 0.1, 0.01 and
-0.001$M_*$. \cite{wood_2002} fitted observed spectra with modeled SEDs
+0.001$M_*$. \cite{wood_2002} fitted observed spectra with modelled SEDs
 to derive a disc mass of 0.003$M_*$  for HH~30 IRS. Subsequent
@@
 (classed as edge-on systems) as red dots (for typical, bottom left,
-and extreme, bottom right accretion rates). The left panels then show
+and extreme, bottom right, accretion rates). The left panels then show
 naked stars isochrones (created from our grid of simulated photometry)
 for 1 Myrs at accretion rates of \logmdot = $-$12 and $-$9, as solid
-and dashed lines respectively (with coverage of 10\% and rotation
-rates of 5 days). Whereas the left hand panels show naked stars
-isochrones of \logmdot = $-$6 and $-$9 as solid and dashed black lines
-respectively (with coverage of 10\% and rotation rates of 5 days. The
-solid green line, in the top panels, shows the 1 Myr isochrone of
-\cite{siess_2000} adjusted to a distance of 250 pc and an extinction of
-$A_V=2$ mag, simulating a background population of CTTS stars.
+and dashed lines respectively (with an areal coverage of 10\% and
+rotation rates of 5 days). Whereas the left hand panels show naked
+star isochrones of \logmdot = $-$6 and $-$9 as solid and dashed black
+lines respectively (with an areal coverage of 10\% and rotation rates
+of 5 days). The solid green line, in the top panels, shows the 1 Myr
+isochrone of \cite{siess_2000} adjusted to a distance of 250 pc and an
+extinction of $A_V=2$ mag, simulating a background population of CTTS
+stars.
 
@@
 current accretion and disc presence in a star and disc systems creates
-a scatter in our simulated photometry indicative of a much larger
-isochronal age or mass spread. Indeed, for many BDD systems even at
-nominal accretion rates of \logmdot = $-$11 or $-$12, for our
-simulations, the colours of these stars move significantly blueward of
-the expected BD locus in a $M_V$, $(V-I)_0$ CMD and redward in a
-$M_J$, $(J-K)_0$ CMD. As, in the case of typical accretors, the input
-variables are in the range expected for a BD population, one could
-reasonably expect observed true BD loci to show a similar scatter. It
-is clear that even a wide photometric selection would not even include
-all of the negligibly accreting systems at expected
-inclinations. Whilst the derivation of masses and ages for these
-objects will be difficult. Furthermore, for the higher accretion rates
-of \logmdot = $-$9 or $-$10 the movement of the star within the CMD
-will effectively shift the star into the contamination region expected
-for background CTTS or MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$
-12--10, and as such the star would not be included in a
-photometrically selected BD sample. The solid green line, in the top
-panels of Figures \ref{age_mass_VVI} and \ref{age_mass_JJK}, showing
-the 1 Myr isochrone of \cite{siess_2000} at a distance of 250 pc and
-extinction of $A_V=2$ mags shows that the BDD systems with higher
-accretion rates could easily be confused for a background CTTS or MS
-population. Indeed misclassification of a BDD system as a CTTS system
-has already been revealed in \cite{white_2003}. For the extreme
-accretors, as shown in the right panels of Figures \ref{age_mass_VVI}
-and \ref{age_mass_JJK}, there is little chance of these objects being
-classed, photometrically, as BD candidates or being assigned the
-correct mass. Therefore, if one attempted to locate a population of
-BDD systems with elevated or extreme accretion rates, target selection
+a scatter in our simulated photometry indicative of a large isochronal
+age or mass spread. Indeed, for many BDD systems even at nominal
+accretion rates of \logmdot = $-$11 or $-$12, for our simulations, the
+colours of these stars move significantly blueward of the expected BD
+locus in a $M_V$, $(V-I)_0$ CMD (and redward in a $M_J$, $(J-K)_0$
+CMD). As, in the case of typical accretors, the input variables are in
+the range expected for a BD population, one could reasonably expect
+observed true BD loci to show a similar scatter. It is clear that even
+a wide photometric selection would not even include all of the
+negligibly accreting systems at expected inclinations. Furthermore,
+the derivation of masses and ages for these objects will be
+difficult. Additionally, for the higher accretion rates of \logmdot =
+$-$9 or $-$10 the movement of the star within the CMD will effectively
+shift the star into the contamination region expected for background
+CTTS or MS stars at a $(V-I)_0$ of $\leq$1.5 and $M_V$ 12--10, and as
+such the star would not be included in a photometrically selected BD
+sample. The solid green line, in the top panels of Figures
+\ref{age_mass_VVI} and \ref{age_mass_JJK}, showing the 1 Myr isochrone
+of \cite{siess_2000} at a distance of 250 pc and extinction of $A_V=2$
+mags, shows that the BDD systems with higher accretion rates could
+easily be confused for a background CTTS or MS population. Indeed
+misclassification of a BDD system as a CTTS system has already been
+revealed in \cite{white_2003}. For the extreme accretors, as shown in
+the right panels of Figures \ref{age_mass_VVI} and \ref{age_mass_JJK},
+there is little chance of these objects being classed,
+photometrically, as BD candidates or being assigned the correct
+mass. Therefore, if one attempted to locate a population of BDD
+systems with elevated or extreme accretion rates, target selection
 would have to be placed at much brighter magnitudes, and bluer for
@@
 limiting wavelengths, originally used to distinguish amongst Class I,
-II or II sources, but now used to detect disc presence
+II or III sources, but now used to detect disc presence
 \citep{lada_2006,kennedy_2009}. An $\alpha>-2$ is used as a selection
@@
 Figure \ref{disc_frac_JHJK} shows the photometry for all models in our
-grid in a $(J-K)_0$, $(J-H)_0$ CoCoDs. In all panels all of the naked
+grid in a $(J-K)_0$, $(J-H)_0$ CoCoDs. In all panels, all of the naked
 systems are shown as black crosses. The left panels show those systems
@@
 placing a colour-colour cut are viewed as lower limits this effect may
-be small. Our grid show no correlation in a CoCoD of this type with
-rotation rate. In the case of the extreme accretors (right panels)
-there is a strong correlation of accretion rate and scatter from the
-naked stars. Additionally, the extreme accretors lie significantly
-removed from the naked stars locus. There is a possibility that some of
-these objects may be lost due to saturation and limiting magnitude
-effects. Again, as with mass and age derivation, the present figures
-are representative of similar figures using alternative, similar
-magnitudes.
-
-CoCoDs constructed using longer the longer wavelength bands of the
-IRAC and MIPS cameras are most commonly used for disc fraction
+be small. The photometry from our grid shows no correlation in a CoCoD
+of this type with rotation rate. In the case of the extreme accretors
+(right panels) there is a strong correlation of accretion rate and
+scatter from the naked stars. Additionally, the extreme accretors lie
+significantly removed from the naked stars locus. There is a
+possibility that some of these objects may be lost due to saturation
+and limiting magnitude effects. Again, as with mass and age
+derivation, the present figures are representative of similar figures
+using alternative, passbands within the instrument filter sets.
+
+CoCoDs constructed using the longer wavelength bands of the IRAC and
+MIPS cameras are most commonly used for disc fraction
 calculation. Selection based on these types of data are well accepted
@@
 minimal past around 3\,$\mu$m, systems with discs will have
-significantly different SEDs from naked systems.
+significantly different SEDs from naked systems at these wavelengths.
 
@@
 
-Recent derivations of disc fraction usually use colour-colour
+Recent derivations of disc fractions usually use colour-colour
 selection in the IRAC photometric bands. As we have shown within our
@@
 clear. Therefore, we can examine the success of some recent
-observationally placed when applied to our model grid. Additionally,
-disc fractions have been derived using the $\alpha$ value
-\citep{lada_2006}, essentially a slope of the SED between two
-wavelengths (at wavelengths longer than the stellar flux peak). As
-these $\alpha$ values are usually derived at wavelengths across the
-IRAC bands one would expect the resulting disc fractions to be
-reliable.
+observationally placed cuts when applied to our model
+grid. Additionally, disc fractions have been derived using the
+$\alpha$ value \citep{lada_2006}, essentially a slope of the SED
+between two wavelengths (at wavelengths longer than the stellar flux
+peak). As these $\alpha$ values are usually derived at wavelengths
+across the IRAC bands one would expect the resulting disc fractions to
+be reliable.
 
@@
 dots respectively. The naked systems are shown as black crosses. The
-CoCoDs featured are from several recent publications where disc
-fractions have been derived. The selection criteria from theses
-studies are marked as dashed vertical and horizontal lines. The left
-panels show the typical accretors and the right panels the extreme
-accretors.
+colour combinations used to construct the CoCoDs featured are from
+several recent publications where disc fractions have been
+derived. The selection criteria from theses studies are marked as
+dashed lines. The left panels show the typical accretors and the right
+panels the extreme accretors.
 
@@
 \cite{luhman_2005b} a study of IC348, \cite{luhman_2008} a study of
-$\sigma$ Orionis and \cite{monin_2010} \citep[using the criteria
-of][]{gutermuth_2008} a study of the Taurus region. In these cases the
+$\sigma$ Orionis and \cite{monin_2010} a study of the Taurus region
+\citep[using the criteria of][]{gutermuth_2008}. In these cases the
 effects of extinction are either negligible in the plotted colours,
@@
 missed by the selection of \cite{gutermuth_2008} which was applied to
-Taurus by\cite{monin_2010}. Finally, the selection for CTTS candidates
+Taurus by \cite{monin_2010}. Finally, the selection for CTTS candidates
 of $\alpha>-$2 \citep{kennedy_2009} appears reasonably applicable to
@@
 magnitudes and colours, for actively accreting BDs with or without an
-associated accretion disc. We have modeled the photospheric flux from
+associated accretion disc. We have modelled the photospheric flux from
 these BDs by adopting (and interpolating) the interior `DUSTY00'
@@
 then produced for both naked BDs and BDD systems. For the BDD systems
-we have modeled the disc using the {\sc torus} radiative transfer code
-using the \cite{lucy_1999} radiative equilibrium algorithm and
-incorporating dust sublimation and including a treatment of vertical
-hydrostatic equilibrium (see Section \ref{model} for a discussion of
-the code). In order to produce a grid of simulated systems we have
-varied several input parameters namely: stellar mass, stellar age,
-stellar rotation rate, accretion rate, the areal coverage of the
-accretion stream and the system inclination (the disc mass was
+we have modelled the disc using the {\sc torus} radiative transfer
+code. The {\sc torus} code implements the \cite{lucy_1999} radiative
+equilibrium algorithm, incorporates dust sublimation and includes a
+treatment of vertical hydrostatic equilibrium (see Section \ref{model}
+for a discussion of the code). In order to produce a grid of simulated
+systems we have varied several input parameters namely: stellar mass,
+stellar age, stellar rotation rate, accretion rate, the areal coverage
+of the accretion stream and the system inclination (the disc mass was
 fixed). The ranges of these variables were selected to represent and
@@
 shown to cause occultation and a subsequent, sharp, fall in flux at an
-inclination which decreases for more systems with higher accretion
+inclination which decreases for systems with higher accretion
 rates. We have also shown that for extreme accretion rates the inner
@@
 extinction levels, CTTS population. For more extreme accretion rates
-the scatter (in CMD space) is significantly far from the naked BD
-locus and as such these stars have little chance of being selected as
+the scatter (in CMD space) is significantly removed from the naked BD
+locus such that these stars have little chance of being selected as
 BDs. As discussed in Section \ref{results} this does not include any
@@
 of a coeval population of accreting BDs with associated discs, would
-be inaccurate and problematic. Again this caused by the changes in the
-SEDs as a result of the accretion flux and increased occultation by
-the larger degree of flaring seen in BD discs \citep[for the latter,
-as found by][]{walker_2004}
+be inaccurate and problematic. Again this is caused by the changes in
+the SEDs as a result of the accretion flux and increased occultation
+by the larger degree of flaring seen in BD discs \citep[for the
+latter, as found by][]{walker_2004}
 
@@
 magnitudes than the shorter wavelength CIT \textit{JHK} passbands. In
-addition, we that the slope of the SED from 3.6 to 8.0$\mu$m, or
-$\alpha$ value, is an effective disc indicator. We have also
+addition, we have shown that the slope of the SED, or $\alpha$ value,
+from 3.6 to 8.0$\mu$m is an effective disc indicator. We have also
 tentatively shown that current observational cuts, when applied to our
 simulated photometry (with its associated photometric system), results
-in the reliable detection of disc candidates for IRAC and MIPS
-colours and $\alpha$ values, and therefore a robust lower limit disc
+in the reliable detection of disc candidates for IRAC and MIPS colours
+and $\alpha$ values, and therefore a robust lower limit disc
 fraction. Cuts derived from our model grid which could be used as a
@@
 significantly) is the recent evidence for a stellar mass to accretion
-rate correlation, of the approximate form: $\dot{M}_{acc}\propto M_*^2$
+rate correlation, of the approximate form: $\dot{M}\propto M_*^2$
 \citep{muzerolle_2003,natta_2004,natta_2006}. This relationship has

### 2010-07-16 torus/molecular_mod.F90
openmp stuff in mole mod - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2384 25464f21-6099-402c-b30a-640f1d40d38b

@@ -378,6 +378,8 @@ module molecular_mod
      real(double) :: nupper(200), nlower(200)
      real(double) :: levelpops(200), alphanubase(200), nmol
 
+     !$OMP THREADPRIVATE( firstTime1, firstTime2, firstAbundanceWarning )
+
      inlte = isinlte
 
 !Code to handle a restart. Read in grid from file 
@@ -1147,26 +1149,34 @@ module molecular_mod
 
 ! we will use an array to store the rank of the process
 ! which will calculate each octal's variables
+
+            ! Set the range of index for octal loop used later.     
+            np = nThreadsGlobal
+            n_rmdr = MOD(nMonte,np)
+            m = nMonte/np
             
-            allocate(octalsBelongRank(size(octalArray)))
+            if (myRankGlobal .lt. n_rmdr ) then
+               ioctal_beg = (m+1)*myRankGlobal + 1
+               ioctal_end = ioctal_beg + m
+            else
+               ioctal_beg = m*myRankGlobal + 1 + n_rmdr
+               ioctal_end = ioctal_beg + m - 1
+            end if
+            
 
-            if (my_rank == 0) then
-               print *, ' '
-               print *, 'molecular  computed by ', np-1, ' processors.'
-               print *, ' '
-               call mpiBlockHandout(np,octalsBelongRank,blockDivFactor=1,tag=tag,&
-                    maxBlockSize=10,setDebug=.false.)
 
-            endif
-     ! ============================================================================
-
-            if (my_rank /= 0) then
-               blockLoop: do     
-                  call mpiGetBlock(my_rank,iOctal_beg,iOctal_end,rankComplete,tag,setDebug=.false.)
-                  if (rankComplete) exit blockLoop 
 #endif
 
 ! iterate over all octals, all rays, solving the system self-consistently
+
+                !$OMP PARALLEL DEFAULT(NONE) &
+                !$OMP PRIVATE(iOctal, thisOctal) &
+		!$OMP PRIVATE(nh, ne, nhe, nprotons, collMatrix) &
[…]

### 2010-07-16 BDD_submit/paper.tex
Some minor typos and added Herschel filters
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2385 25464f21-6099-402c-b30a-640f1d40d38b

@@
 \citep{hawarden_2001}, IRAS 12, 25, 60 and 100\,$\mu$m
-\citep{neugebauer_1984} and SCUBA \textit{450WB} and \textit{850WB}
-\citep{holland_1999}. For further information on these magnitudes,
-such as the filter responses used and the adopted zeropoints please
-refer to the website.
-
-\textit{Monochromatic fluxes}
+\citep{neugebauer_1984}, SCUBA 450WB and 850WB
+\citep{holland_1999} \footnote{The SCUBA 2 filter responses are similar
+  to SCUBA}, Herschel PACS blue, green and red \citep{poglitsch_2008,
+  poglitsch_2010} and Herschel SPIRE, 250, 350 and 500
+\citep{griffin_2008,griffin_2010}. For further information on these
+magnitudes, such as the filter responses used and the adopted
+zeropoints please refer to the website.
 
@@
 We also directly compared the magnitudes and colours of our naked BD
-systems with the lowest accretion rate (-12
-log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ to those published in
-\cite{chabrier_2000}, in the same photometric system
+systems with the lowest accretion rate (\logmdot -12) to those
+published in \cite{chabrier_2000}, in the same photometric system
 (\textit{CIT}). We found significant colour differences ($\delta
 (J-K)\le$ 0.1), between our derived values and those of
-\cite{chabrier_2000}. As a further check we derived the
-magnitudes in the \cite{bessell_1998} system (by both adopting
-the published zero points, and by using a Vega reference spectrum),
-and applied conversions of \cite{leggett_1992}\footnote{We have
-  also included the wavelength shift mentioned in
-  \cite{stephens_2004}}, to the \textit{CIT} system. For each
-method we failed to match the magnitudes and colours published in
-\cite{chabrier_2000}. As a final test we passed the downloaded,
-unaltered, atmospheric spectra directly through the filter response
-program, without interpolation, for the closest matches in log(g) and
-$T_{\rm eff}$ from the interior models published in
-\cite{chabrier_2000}. These magnitudes and colours also failed
-to match. Therefore, we must conclude that the most likely cause of
-the mismatch is due to improvements in the model atmospheres available
+\cite{chabrier_2000}. As a further check we derived the magnitudes in
+the \cite{bessell_1998} system (by both adopting the published zero
+points, and by using a Vega reference spectrum), and applied
+conversions of \cite{leggett_1992}\footnote{We have also included the
+  wavelength shift mentioned in \cite{stephens_2004}}, to the
+\textit{CIT} system. For each method we failed to match the magnitudes
+and colours published in \cite{chabrier_2000}. As a final test we
+passed the downloaded, unaltered, atmospheric spectra directly through
+the filter response program, without interpolation, for the closest
+matches in log(g) and $T_{\rm eff}$ from the interior models published
+in \cite{chabrier_2000}. These magnitudes and colours also failed to
+match. Therefore, we must conclude that the most likely cause of the
+mismatch is due to improvements in the model atmospheres available
 online\footnote{http://perso.ens-lyon.fr/france.allard/} (this is

### 2010-08-17 torus/inputs_mod.f90
fix to molebench - mainly to do with negative opacities due to too small initnray - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2422 25464f21-6099-402c-b30a-640f1d40d38b

@@ -1223,7 +1223,7 @@ contains
             "Grid distance (pc): ","(a,f6.1,1x,a)", 1., ok, .true.)
        gridDistance = gridDistance * pcTocm   ! cm
        call getInteger("initnray", initnray, cLine, nLines, &
-               "Number of fixed rays for stage 1: ","(a,i4,a)", 100, ok, .false.)
+               "Number of fixed rays for stage 1: ","(a,i4,a)", 1024, ok, .false.)
        call getLogical("dongstep", dongstep, cLine, nLines, &
                "Use Ng Acceleration: ","(a,1l,a)", .false., ok, .false.)
        call getLogical("quasi", quasi, cLine, nLines, &

### 2010-08-17 torus/inputs_modV2.f90

@@ -132,6 +132,15 @@ contains
     call getLogical("photoionphysics", photoionPhysics, cLine, fLine, nLines, &
          "Include photoionization physics in calculation: ","(a,1l,1x,a)", .false., ok, .false.)
 
+
+    if (molecularPhysics.and.atomicPhysics) then
+       call writeFatal("Cannot conduct any calculation that simultaneously includes atoms and molecules")
+    endif
+
+    if (molecularPhysics.and.photoionPhysics) then
+       call writeFatal("Cannot conduct any calculation that simultaneously includes photoionization and molecules")
+    endif
+
 !    if (.not.(dustPhysics.or.atomicPhysics.or.molecularPhysics.or.photoionPhysics)) then
 !       call writeFatal("Must include one of: dustPhysics, atomicPhysics, molecularPhysics, photoionPhysics")
 !    endif
@@ -828,7 +837,7 @@ contains
        call getReal("distance", gridDistance, real(pctocm), cLine, fLine, nLines, &
             "Grid distance (pc): ","(a,f6.1,1x,a)", 1., ok, .true.)
        call getInteger("initnray", initnray, cLine, fLine, nLines, &
-               "Number of fixed rays for stage 1: ","(a,i4,a)", 100, ok, .false.)
+               "Number of fixed rays for stage 1: ","(a,i4,a)", 1024, ok, .false.)
        call getLogical("dongstep", dongstep, cLine, fLine, nLines, &
                "Use Ng Acceleration: ","(a,1l,a)", .false., ok, .false.)
        call getLogical("quasi", quasi, cLine, fLine, nLines, &

### 2010-08-17 torus/molecular_mod.F90

@@ -860,7 +860,6 @@ module molecular_mod
      integer       ::   n_rmdr
      integer       ::   ierr           ! error flag
      integer       ::   j
-     integer       ::   tag = 0 
      real(double), allocatable :: tArrayd(:,:),tempArrayd(:,:) 
 #endif
 
@@ -1028,7 +1027,7 @@ module molecular_mod
       endif
 
       call randomNumberGenerator(getIseed = fixedRaySeed)
-      write(*,*) "myrank ",myrankglobal,fixedRayseed
+
 ! This is the loop that controls everything
 ! 1) istage = 1, fixed rays to reduce variance between cells or 
 ! 2) istage = 2, random rays to ensure sufficient spatial/frequency sampling
@@ -1117,6 +1116,15 @@ module molecular_mod
                call randomNumberGenerator(randomSeed=.true.)
             endif
 
+!            call torus_mpi_barrier
+!            do i = 0, nThreadsGlobal-1
+!            call torus_mpi_barrier
+!               if (i==myrankGlobal) then
+!                  call randomNumberGenerator(getDouble=r)
+!                  write(*,*) myrankGlobal,r
+!               endif
+!            call torus_mpi_barrier
+!            enddo
 
 
 ! default loop indicies for single processor otherwise do MPI stuff
@@ -1693,6 +1701,11 @@ end subroutine molecularLoop
            dTau = alpha * dds * 1.d10
            attenuation = exp(-tau)
 ! Intensity along ray owing to line segment
+           do iTrans = 1, maxtrans
+              if (dtau(itrans) < -1.d0) then
+                 write(*,*) "dtau ERROR: ",dtau(itrans),alpha(itrans),dds,phiprofval
+              endif
+           enddo
            localradiationfield = exp(-dtau) 
 	   localradiationfield = OneArray - localradiationfield
            di0 = localradiationfield * snu
@@ -2212,9 +2225,9 @@ endif
[…]

### 2010-08-17 torus/random_mod.F90

@@ -273,9 +273,10 @@ contains
       IF(MJ.LT.MZ)MJ=MJ+MBIG
       MA(INEXT)=MJ
       RAN3=MJ*FAC
-!      if (ran3 > 1.d0) then
-!         write(*,*) "ran3 bug (real)",ran3
-!      endif
+      if ((ran3 < tiny(ran3)).or.(ran3 > 0.99999999999999d0)) then
+         write(*,*) "ran3 bug ",ran3
+         ran3 = min(0.99999999999999d0,max(ran3, tiny(ran3)))
+      endif
     END FUNCTION RAN3_double
 
   SUBROUTINE localsort(N,RA)

### 2010-08-17 torus/amr_utils_mod.f90
nagfor bug fixes and removal of image_ndf and spec_ndf - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2423 25464f21-6099-402c-b30a-640f1d40d38b

@@ -172,7 +172,6 @@ module amr_utils_mod
       LOGICAL, INTENT(INOUT) :: haveDescended
       LOGICAL, INTENT(INOUT) :: boundaryProblem
 !      type(vector) :: rVec
-      real(double),pointer :: fac
       INTEGER :: i
       
       IF ( inOctal(thisOctal,point,alreadyRotated=.true.) ) THEN
@@ -226,10 +225,6 @@ module amr_utils_mod
           write(*,*) thisOctal%subcellSize
 !          write(*,*) thisOctal%phi*radtodeg,thisOctal%dphi*radtodeg
           write(*,*) sqrt(thisOctal%centre%x**2+thisOctal%centre%y**2)
-          fac = -2.d0
-          fac = sqrt(fac)
-          allocate(fac)
-          allocate(fac)
        endif
           if(.not. suppresswarnings) then
                 STOP
@@ -267,8 +262,6 @@ module amr_utils_mod
            write(*,*) "inoctal ",inoctal(thisOctal,point), thisOctal%phimin*radtodeg, &
                 thisOctal%phimax*radtodeg,phi < phimin, phi > phimax, &
                 phi < thisOctal%phimax, phi > thisOctal%phimin
-            fac = -2.d0
-            write(*,*) sqrt(fac)
 !           rVec = subcellCentre(thisOctal,subcell)
 !           write(*,*) rVec%x+thisOctal%subcellSize/2.
 !           write(*,*) rVec%x-thisOctal%subcellSize/2.

### 2010-08-17 torus/angularImage_mod.F90

@@ -23,7 +23,7 @@ module angularImage
 ! Approximate latitude range of galactic plane
   real(double), parameter :: plane_lat=1.0_db 
   integer, parameter :: vr_file_lun=81
-  character(len=*), parameter :: vr_format="unformatted"
+  character(len=11),save :: vr_format="unformatted"
   integer :: vel_chan_num
   logical, save :: nColOnly 
 
@@ -31,11 +31,16 @@ module angularImage
 
     subroutine make_angular_image(grid)
 
-      use datacube_mod, only: DATACUBE, initCube, addVelocityAxis, writeDataCube, freeDataCube
+      use datacube_mod, only: DATACUBE, initCube, addVelocityAxis, freeDataCube
       use amr_mod, only: amrGridVelocity
       use h21cm_mod, only: h21cm_lambda
       use input_variables, only: intPosX, intPosY, intPosZ, npixels, nv, minVel, maxVel, intDeltaVx, intDeltaVy, intDeltaVz, &
-           galaxyPositionAngle, galaxyInclination, wanttau, splitCubes, dataCubeFileName, obsVelFromGrid
+           galaxyPositionAngle, galaxyInclination, splitCubes, obsVelFromGrid
+#ifdef USECFITSIO
+      use datacube_mod, only : writeDataCube
+      use input_variables, only : dataCubeFilename, wanttau
+#endif
+
 
       implicit none
 
@@ -102,6 +107,7 @@ module angularImage
 
       call process_cube_for_kvis(cube)
 
+#ifdef USECFITSIO
       call writeinfo("Writing data cubes", TRIVIAL)
       if(writeoutput) then
 
@@ -140,7 +146,7 @@ module angularImage
               write_ipos=.false., write_ineg=.false., write_Tau=.false., write_nCol=.true., write_axes=.false.)
 
       end if
-
+#endif
       call freeDataCube(cube)
      
     end subroutine make_angular_image

### 2010-08-17 torus/bhmie_mod.f90

@@ -141,13 +141,13 @@ contains
 !      REAL REALPART_SP
 !      COMPLEX SPCX
 !      REALPART_SP(SPCX)=(REAL(SPCX))
-      COMPLEX(kind=double) DPCX
-      DOUBLE PRECISION REALPART
-      DOUBLE PRECISION IMAGPART
+!      COMPLEX(kind=double) DPCX
+!      DOUBLE PRECISION REALPART
+!      DOUBLE PRECISION IMAGPART
 
-      REALPART(DPCX)=(DBLE(DPCX))
+!      REALPART(DPCX)=(DBLE(DPCX))
 
-      IMAGPART(DPCX)=(DIMAG(DPCX))
+!      IMAGPART(DPCX)=(DIMAG(DPCX))
 !***********************************************************************
 !*** Safety checks
 
@@ -258,14 +258,20 @@ main_loop:  DO N=1,NSTOP
 ! tjh changed above to this to get round fpe errors
 
           JUNK = REAL(((2.*EN+1.)/(EN*(EN+1.))))
+!          JUNK = JUNK *  &
+!             (REALPART(AN)*REALPART(BN)+IMAGPART(AN)*IMAGPART(BN))
           JUNK = JUNK *  &
-             (REALPART(AN)*REALPART(BN)+IMAGPART(AN)*IMAGPART(BN))
+             (REAL(AN)*REAL(BN)+AIMAG(AN)*AIMAG(BN))
           GSCA=GSCA+JUNK
 
           IF(N.GT.1)THEN
+!              GSCA=GSCA+REAL(((EN-1.)*(EN+1.)/EN)*                        &
+!              (REALPART(AN1)*REALPART(AN)+IMAGPART(AN1)*IMAGPART(AN)+     &
+!               REALPART(BN1)*REALPART(BN)+IMAGPART(BN1)*IMAGPART(BN)))
+
               GSCA=GSCA+REAL(((EN-1.)*(EN+1.)/EN)*                        &
-              (REALPART(AN1)*REALPART(AN)+IMAGPART(AN1)*IMAGPART(AN)+     &
-               REALPART(BN1)*REALPART(BN)+IMAGPART(BN1)*IMAGPART(BN)))
+              (REAL(AN1)*REAL(AN)+AIMAG(AN1)*AIMAG(AN)+     &
[…]

### 2010-08-17 torus/cmf_mod.F90

@@ -20,7 +20,6 @@ module cmf_mod
   use parallel_mod, only: torus_mpi_barrier
   use vtk_mod, only: writeVtkfile
   use octal_mod, only : allocateAttribute
-  use memory_mod, only : resetGlobalMemory
   implicit none
 
   private
@@ -2377,9 +2376,13 @@ contains
   
   subroutine calculateAtomSpectrum(grid, thisAtom, nAtom, iAtom, iTrans, viewVec, distance, source, nsource, nfile, &
        totalFlux, forceLambda, occultingDisc)
-    use input_variables, only : vturb, lineoff, nv, calcDataCube, dataCubeFilename
+    use input_variables, only : vturb, lineoff, nv, calcDataCube
     use messages_mod, only : myRankIsZero
-    use datacube_mod, only: DATACUBE, writeDataCube, freedatacube
+    use datacube_mod, only: DATACUBE, freedatacube
+#ifdef USECFITSIO
+    use input_variables, only : dataCubeFilename
+    use datacube_mod, only : writedataCube
+#endif
 #ifdef MPI
     include 'mpif.h'
 #endif
@@ -2465,7 +2468,10 @@ contains
        write(*,*) "Process ",my_rank, " create data cube done"
 #endif
        if (myrankiszero) then
+
+#ifdef USECFITSIO
           call writeDataCube(cube,datacubefilename)
+#endif
 !          write(plotfile,'(a,i3.3,a)') "flatimage",nfile,".fits.gz"
 !          call writeCollapsedDataCube(cube,plotfile)
        endif

### 2010-08-17 torus/datacube_mod.F90

@@ -47,6 +47,7 @@ module datacube_mod
 
 contains
 
+#ifdef USECFITSIO
   subroutine writeDataCube(thisCube, filename, write_Intensity, write_ipos, write_ineg, write_Tau, write_nCol, write_axes)
 
     use image_mod, only : deleteFitsFile
@@ -63,7 +64,6 @@ contains
     logical, optional, intent(in) :: write_nCol
     logical, optional, intent(in) :: write_axes
 
-#ifdef USECFITSIO
     integer :: status,unit,blocksize,bitpix,naxis
     integer, dimension(5) :: naxes
     integer :: group,fpixel,nelements
@@ -388,18 +388,20 @@ contains
 
       end subroutine addWCSinfo
 
-#endif
     
     
   end subroutine writeDataCube
 
+#endif
+
   !**********************************************************************
+
+#ifdef USECFITSIO
 
   subroutine readDataCube(thisCube)
 
     implicit none
     
-#ifdef USECFITSIO
     type(DATACUBE), intent(out) :: thisCube
     integer :: status, readwrite, unit, blocksize,nfound,group,firstpix,nbuffer,npixels, hdutype, hdu, junk
     character(len=512) :: filename
@@ -536,22 +538,20 @@ contains
     ! read_image
     call ftgpvj(unit,group,firstpix,nbuffer,nullval,thisCube%nsubpixels,anynull,status)   
 
-#else
-    type(DATACUBE) :: thisCube
 
-#endif
     return
 
   end subroutine readDataCube
+#endif
 
   !**********************************************************************
 
 
+#ifdef USECFITSIO
   subroutine print_error(status)
     ! PRINT_ERROR prints out the FITSIO error messages to the user.
     
     integer status
-#ifdef USECFITSIO
     character ( len = 30 ) errtext
     character ( len = 80 ) errmessage
 
@@ -570,10 +570,10 @@ contains
        print *,errmessage
        call ftgmsg(errmessage)
     end do
-#endif    
 
     return
   end subroutine print_error
+#endif    
 
   !***********************************************************
 
@@ -885,12 +885,12 @@ subroutine freeDataCube(thiscube)
 
   end subroutine freeDataCube
   
+#ifdef USECFITSIO
   subroutine writeCollapsedDataCube(thisCube, filename)
     use image_mod, only : deleteFitsFile, printfitsError
     type(DATACUBE) :: thisCube
     character(len=*) :: filename
[…]

### 2010-08-17 torus/image_mod.F90

@@ -634,17 +634,16 @@ module image_mod
 !! WRITE_IMAGE creates a FITS primary array containing a 2-D image.
 !
 
+#ifdef USECFITSIO
      subroutine writeFitsImage(image, filename, objectDistance, type)
 
 ! Arguments
-#ifdef USECFITSIO
+       
        use input_variables, only: lamStart, ImageinArcSec
-#endif
-       type(IMAGETYPE), intent(in)   :: image
+       type(IMAGETYPE),intent(in) :: image
        character (len=*), intent(in) :: filename, type
        real(double) :: objectDistance
 
-#ifdef USECFITSIO
 ! Local variables
        integer :: status,unit,blocksize,bitpix,naxis,naxes(2)
        integer :: group,fpixel,nelements
@@ -763,17 +762,17 @@ module image_mod
        if (status > 0) then
           call printFitserror(status)
        end if
-#endif
 
      end subroutine writeFitsImage
+#endif
 
+#ifdef USECFITSIO
      subroutine deleteFitsFile(filename,status)
        
 ! Arguments
        character ( len = * ) filename
        integer :: status
 
-#ifdef USECFITSIO
 ! Local variables
        integer unit,blocksize
 
@@ -817,10 +816,11 @@ module image_mod
        !  Free the unit number for later reuse.
        !
        call ftfiou(unit, status)
-#endif
 
      end subroutine deleteFitsFile
+#endif
 
+#ifdef USECFITSIO
      subroutine printFitsError(status)
 
        !
@@ -830,7 +830,6 @@ module image_mod
        !
        ! Arguments
        integer :: status
-#ifdef USECFITSIO
 
        ! Local variables
        character ( len = 30 ) errtext
@@ -854,8 +853,8 @@ module image_mod
           print *,errmessage
           call ftgmsg(errmessage)
        end do
-#endif
      end subroutine printFitsError
+#endif
 
      subroutine pixelLocate(image, xDist, yDist, ix, iy)
        type(IMAGETYPE) :: image
@@ -876,7 +875,11 @@ module image_mod
      end subroutine pixelLocate
             
   subroutine createLucyImage(grid, viewVec, lambda, xArray, nLambda, source, nSource)
-    use input_variables, only : npix, setimageSize, vmin, vmax, griddistance
+    use input_variables, only : npix, setimageSize, vmin, vmax
+
+#ifdef USECFITSIO
+    use input_variables, only : griddistance
+#endif
[…]

### 2010-08-17 torus/image_ndf.F90

@@ -1,257 +1,0 @@
-#ifdef USENDF
-      subroutine writeImagef77(thisImageI, thisImageQ, thisImageU, &
-      thisImageV, thisImageVel, scale, nPix, filename)
-      implicit none
-      include '/star/include/DAT_PAR'
-      include '/star/include/SAE_PAR'
-      integer npix
-      real thisImageI(nPix, nPix)
-      real thisImageQ(nPix, nPix)
-      real thisImageU(nPix, nPix)
-      real thisImageV(nPix, nPix)
-      real thisImageVel(nPix, nPix)
-      character*(*)  filename
-      character*(DAT__SZLOC) loc, ploc
-      integer place, ndfq, ndfu, ndfv, ndfvel
-      integer qptr, uptr, vptr, velptr
-      real scale
-      integer  iptr, oaxisp1, oaxisp2, ndfo
-      integer status
-      integer i,j
-      integer  lbnd(2), ubnd(2), nelm
-
-       status = 0
-
-       lbnd(1) = 1
-       ubnd(1) = nPix
-       lbnd(2) = 1
-       ubnd(2) = nPix
-       nelm = npix*npix
-
-       write(*,'(a,i4,a,i4)') "Writing image: ",npix," by ",npix
-
-!
-! Begin the ndf and hds systems
-!
-      call ndf_begin
-      call hds_start(status)
-!
-! create a new tsp ndf and map it
-!
-      call hds_new(filename,'output','ndf',0,0,loc,status)
-      call dat_new(loc,'data_array','_real',2,ubnd,status)
-      call ndf_find(loc, " ", ndfo, status)
-      call ndf_acre(ndfo,status)
-      call ndf_acput('xaxis',ndfo,'lab',1,status)
-      call ndf_acput('rstar',ndfo,'unit',1,status)
-      call ndf_acput('yaxis',ndfo,'lab',2,status)
-      call ndf_acput('rstar',ndfo,'unit',2,status)
-      call ndf_amap(ndfo,'centre',1,'_real','update',oaxisp1,ubnd(1),status)
-      call ndf_amap(ndfo,'centre',2,'_real','update',oaxisp2,ubnd(1),status)
-      call ndf_map(ndfo,'data','_real','write',iptr,nelm,status)
-
-      if (status .ne. sai__ok) then
-         write(*,'(a)') "! Error opening output ndf image"
-         stop
-      endif
-
-
[…]

### 2010-08-17 torus/molecular_mod.F90

@@ -2284,10 +2284,15 @@ subroutine calculateMoleculeSpectrum(grid, thisMolecule, dataCubeFilename, input
 
    use input_variables, only : itrans, nSubpixels, observerpos, rgbCube, &
         gridDistance, imageside, npixels
+#ifdef USECFITSIO
    use image_mod, only: deleteFitsFile
-
+#endif
 #ifdef MPI
        include 'mpif.h'
+#endif
+
+#ifdef USECFITSIO
+   integer :: status
 #endif
 
    type(GRIDTYPE) :: grid
@@ -2297,7 +2302,6 @@ subroutine calculateMoleculeSpectrum(grid, thisMolecule, dataCubeFilename, input
    type(VECTOR), optional :: inputViewVec
    character(len=*), optional :: dataCubeFilename
    character (len=80) :: filename, message
-   integer :: status
    real(double) :: pixelWidth
 
    type(OCTAL), pointer :: thisoctal
@@ -2433,6 +2437,7 @@ subroutine calculateMoleculeSpectrum(grid, thisMolecule, dataCubeFilename, input
    endif
 #endif
    
+#ifdef USECFITSIO
    if (writeoutput) then
       status = 0
       call writeinfo('Deleting previous Fits file', TRIVIAL)
@@ -2440,6 +2445,7 @@ subroutine calculateMoleculeSpectrum(grid, thisMolecule, dataCubeFilename, input
       call writeinfo('Writing Cube to Fits file: '//trim(filename), TRIVIAL)
       call writedatacube(cube, filename)
    endif
+#endif
 !     call createFluxSpectra(cube, thismolecule, itrans)
 
 !#ifdef MPI
@@ -2680,9 +2686,11 @@ subroutine calculateMoleculeSpectrum(grid, thisMolecule, dataCubeFilename, input
    subroutine createimage(cube, grid, viewvec, observerVec, thisMolecule, iTrans, nSubpixels, imagebasis, revVel)
 
      use input_variables, only : gridDistance, beamsize, npixels, nv, imageside, &
-          maxVel, usedust, lineimage, lamline, plotlevels, debug, wanttau, writetempfits, dotune, h21cm
+          maxVel, usedust, lineimage, lamline, plotlevels, debug, wanttau, dotune, h21cm
+#ifdef USECFITSIO
+    use input_variables, only : writetempfits
     use image_mod, only : deleteFitsFile
-
+#endif
 #ifdef MPI
      use mpi_global_mod, only: nThreadsGlobal
      include 'mpif.h'
[…]

### 2010-08-17 torus/outputs_mod.F90

@@ -18,8 +18,7 @@ contains
     use input_variables, only : photoionPhysics, splitoverMpi, dustPhysics, nImage, thisinclination
     use input_variables, only : SEDlamMin, SEDlamMax, SEDwavLin, SEDnumLam
     use input_variables, only : h21cm, internalView
-    use photoionAMR_mod, only : createImageSplitGrid
-    use input_variables, only : lambdaImage, outputimagetype, npixelsArray, dataCubeFilename, mie, gridDistance, nLambda
+    use input_variables, only : lambdaImage, npixelsArray, dataCubeFilename, mie, gridDistance, nLambda
     use input_variables, only : outfile, npix, ninclination, nImage, inclinations, inclinationArray
     use input_variables, only : lamStart, lamEnd
 !    use input_variables, only : rotateViewAboutX, rotateViewAboutY, rotateViewAboutZ
@@ -31,6 +30,11 @@ contains
     use disc_class, only : alpha_disc
     use blob_mod, only : blobtype
     use angularImage, only: make_angular_image, map_dI_to_particles
+#ifdef MPI
+    use input_variables, only : outputImageType
+    use photoionAMR_mod, only : createImageSplitGrid
+#endif
+
     type(BLOBTYPE) :: tblob(1)
     real(double) :: totalFlux
     type(SURFACETYPE) :: tsurface
@@ -73,12 +77,15 @@ contains
     endif
 
     if (photoionPhysics.and.splitoverMPI.and.calcImage) then
-       
        observerDirection = VECTOR(0.d0, -1.d0, 0.d0)
+#ifdef MPI
        do i = 1, nImage
           call createImageSplitGrid(grid, globalnSource, globalsourcearray, observerDirection, imageFilename(i), lambdaImage(i), &
                outputImageType(i), nPixelsArray(i))
        enddo
+#else
+    call writeFatal("Cannot calculate an image from a domain decomposed grid without MPI")
+#endif
     endif
 
     if (molecularPhysics.and.calcDataCube) then

### 2010-08-17 torus/phaseloop_mod.F90

@@ -18,7 +18,10 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
   use phasematrix_mod
   use disc_class
   use image_mod, only: IMAGETYPE, PVIMAGETYPE, initImage, initPVImage, addPhotonToImage, addphotontopvimage, &
-       createlucyimage, freeimage, freepvimage, smoothpvimage, writefalsecolourppm, writefitsimage, writeimage, writepvimage
+       createlucyimage, freeimage, freepvimage, smoothpvimage, writefalsecolourppm,  writeimage, writepvimage
+#ifdef USECFITSIO
+  use image_mod, only : writeFitsImage
+#endif
   use source_mod, only: SOURCETYPE
   use photon_mod, only: PHOTON, initPhoton, scatterPhoton, initplanetphoton
   use math_mod, only: thermalElectronVelocity, interpGridScalar2
@@ -2886,7 +2889,11 @@ enddo
            write(specFile,'(a,a,a,i3.3,a)') trim(outfile),"_"//trim(name_filter),"_image",iPhase,".fits"
            if (torusVersion(2:2) == "2") specfile = originaloutfile
 
+
+#ifdef USECFITSIO
            call writeFitsImage(obsImageSet(i), trim(specfile), objectDistance, "intensity")
+#endif
+
 !           write(specFile,'(a,a,a,i3.3,a)') trim(outfile),"_"//trim(name_filter),"_pol",iPhase,".fits"
 !           call writeFitsImage(obsImageSet(i), trim(specfile), objectDistance, "pol")
 !           write(specFile,'(a,a,a,i3.3,a)') trim(outfile),"_"//trim(name_filter),"_q",iPhase,".fits"

### 2010-08-17 torus/photoionAMR_mod.F90

@@ -5047,45 +5047,45 @@ contains
     i = grid%octreeRoot%nChildren
   END SUBROUTINE resizePhotoionCoeff
 
-  subroutine photoIonizationloopAMR(grid, source, nSource, nLambda, lamArray, readlucy, writelucy, &
-       lucyfileout, lucyfilein, maxIter, tLimit, sublimate)
-
-    use grid_mod
-    use source_mod
-
-    implicit none
-
-    type(GRIDTYPE) :: grid
-    logical, optional :: sublimate
-    character(len=*) :: lucyfileout, lucyfilein    
-    integer :: nSource
-    type(SOURCETYPE) :: source(:)
-    integer :: nlambda
-    real :: lamArray(:)
-    logical :: readLucy, writeLucy
-    integer :: maxIter
-    real(double) :: tlimit
-
-  end subroutine photoIonizationloopAMR
-
-  subroutine ionizeGrid(thisOctal)
-    use octal_mod
-    type(octal) :: thisOctal
-  end subroutine ionizeGrid
-
-
-  subroutine createImageSplitGrid(grid, nSource, source, observerDirection, imageFilename, lambdaImage, outputtype, npix)
-    use gridtype_mod
-    use vector_mod
-    use source_mod
-    type(GRIDTYPE) :: grid
-    integer :: nSource
-    type(SOURCETYPE) :: source(:)
-    type(VECTOR) :: observerDirection
-    real :: lambdaImage
-    character(len=*) :: imageFilename, outputType
-    integer :: npix
-  end subroutine createImageSplitGrid
+!  subroutine photoIonizationloopAMR(grid, source, nSource, nLambda, lamArray, readlucy, writelucy, &
+!       lucyfileout, lucyfilein, maxIter, tLimit, sublimate)
+!
+!    use grid_mod
+!    use source_mod
+!
+!    implicit none
+!
+!    type(GRIDTYPE) :: grid
+!    logical, optional :: sublimate
+!    character(len=*) :: lucyfileout, lucyfilein    
+!    integer :: nSource
+!    type(SOURCETYPE) :: source(:)
+!    integer :: nlambda
+!    real :: lamArray(:)
+!    logical :: readLucy, writeLucy
+!    integer :: maxIter
+!    real(double) :: tlimit
+!
+!  end subroutine photoIonizationloopAMR
+!
+!  subroutine ionizeGrid(thisOctal)
+!    use octal_mod
+!    type(octal) :: thisOctal
[…]

### 2010-08-17 torus/photoion_mod.F90

@@ -4143,7 +4143,10 @@ end subroutine readHeIIrecombination
 
   subroutine createImage(grid, nSource, source, observerDirection, totalflux, lambdaLine)
     use input_variables, only : nPhotons, npix, setimagesize
-    use image_mod, only: initImage, writeFitsImage, freeImage, IMAGETYPE
+    use image_mod, only: initImage, freeImage, IMAGETYPE
+#ifdef USECFITSIO
+    use image_mod, only: writeFitsImage
+#endif
     use math_mod, only: computeprobdist
     use source_mod, only: randomSource, getphotonpositiondirection
     use random_mod
@@ -4153,7 +4156,9 @@ end subroutine readHeIIrecombination
     include 'mpif.h'
 #endif
     type(GRIDTYPE) :: grid
+#ifdef USECFITSIO
     character(len=80) :: imageFilename
+#endif
     integer :: nSource
     real(double) :: lambdaLine
     type(SOURCETYPE) :: source(:), thisSource
@@ -4293,10 +4298,12 @@ end subroutine readHeIIrecombination
      totalFlux = tempTotalFlux
 #endif
 
+#ifdef USECFITSIO
     if (writeoutput) then
        write(imageFilename, '(a,i6.6,a)') "test_",nint(lambdaLine),".fits"
        call writeFitsImage(thisimage, imageFilename, 1.d0, "intensity")
     endif
+#endif
     call freeImage(thisImage)
   end subroutine createImage
 

### 2010-08-17 torus/physics_mod.F90

@@ -126,8 +126,8 @@ contains
     use input_variables, only : mCore, solveVerticalHydro, sigma0
     use cmf_mod, only : atomloop
     use photoion_mod, only : photoionizationLoop
-    use photoionAMR_mod, only: photoionizationLoopAMR
 #ifdef MPI
+    use photoionAMR_mod, only: photoionizationLoopAMR
     use hydrodynamics_mod, only : doHydrodynamics
 #endif
     use source_mod, only : globalNsource, globalSourceArray
@@ -198,9 +198,12 @@ contains
            call photoIonizationloop(grid, globalsourceArray, globalnSource, nLambda, xArray, readlucy, writelucy, &
              lucyfileNameout, lucyfileNamein)
         else
-
+#ifdef MPI
            call photoIonizationloopAMR(grid, globalsourceArray, globalnSource, nLambda, xArray, .false., .false., &
              " ", " ", 5, 1.d30, sublimate=.false.)
+#else
+           call writeFatal("Domain decomposed grid requires MPI")
+#endif
         endif
 
      end if

### 2010-08-17 torus/spec_ndf.F90

@@ -1,144 +1,0 @@
-#ifdef USENDF
-
-!
-! ********************************************************************
-!
-      SUBROUTINE WRTSP(NPTS,STOKES_I,STOKES_Q,STOKES_QV,STOKES_U, &
-                      STOKES_UV,LAMBDA,FILENAME)
-!
-! This routine reads in a polarization spectrum from a TSP format file
-! and puts it into the 'current' arrays
-!
-      IMPLICIT NONE
-      INTEGER OUT_LU
-      INCLUDE '/star/include/DAT_PAR'
-      INCLUDE '/star/include/SAE_PAR'
-!
-! The current arrays
-!
-      INTEGER NPTS
-      REAL STOKES_I(*)
-      REAL STOKES_Q(*)
-      REAL STOKES_QV(*)
-      REAL STOKES_U(*)
-      REAL STOKES_UV(*)
-      REAL LAMBDA(*)
-!
-! Misc.
-!
-      INTEGER SP
-      INTEGER NDF
-      CHARACTER*80 PATH,FILENAME
-      CHARACTER*64 NAME
-      CHARACTER*80 ERROR
-      INTEGER UBND(1),LBND(1),NDFO,OAXISP,NDFQ,NDFU,QPTR
-      INTEGER DIMS(10)
-      INTEGER NDIMS
-      INTEGER UPTR,QVPTR,UVPTR,PLACE
-      INTEGER NELM,PTR1,NDF1,NDF2,NDF3,IPTR
-      INTEGER PTRQ,PTRQV,PTRU,PTRUV,APTR
-      CHARACTER*(DAT__SZLOC) PLOC,DLOC,QLOC,LOC      
-      INTEGER STATUS
-
-      STATUS = SAI__OK
-      LBND(1) = 1
-      UBND(1) = NPTS
-!
-! Begin the ndf and hds systems
-!
-      CALL NDF_BEGIN
-      CALL HDS_START(STATUS)
-!
-! Create a new tsp ndf and map it
-!
-      CALL HDS_NEW(FILENAME,'OUTPUT','NDF',0,0,LOC,STATUS)
-      CALL DAT_NEW(LOC,'DATA_ARRAY','_REAL',1,UBND,STATUS)
-      CALL NDF_IMPRT(LOC,NDFO,STATUS)
[…]

### 2010-08-17 torus/amr_mod.f90
changes to kind_mod and phfit2 - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2424 25464f21-6099-402c-b30a-640f1d40d38b

@@ -19,6 +19,7 @@ module amr_mod
   use mpi_global_mod, only: myRankGlobal
   use gas_opacity_mod
   use amr_utils_mod
+  use phfit_mod, only : phfit2
 
   IMPLICIT NONE
 

### 2010-08-17 torus/fillGridMie.f90

@@ -1,69 +1,0 @@
-
-subroutine fillGridMie2(grid, scale, aMin, aMax, a0, qDist, pDist, grainType)
-
-  use gridtype_mod
-  use constants_mod
-  implicit none
-  type(GRIDTYPE) :: grid
-  real :: aMin, aMax, a0, qDist, pDist
-  real, allocatable :: sigmaAbs(:), sigmaSca(:)
-  real :: scale
-  character(len=*) :: grainType
-  integer :: i, j, k
-
-  scale = 1.
-
-  allocate(sigmaAbs(1:grid%nLambda))
-  allocate(sigmaSca(1:grid%nLambda))
-
-  write(*,'(a)') "Filling grid with mie cross-sections..."
-  call draineCrossSection(grid%lamArray, grid%nLambda, &
-       aMin, aMax, a0, qDist, pDist, &
-       sigmaAbs, sigmaSca, grainType)
-
-  !write(*,*) amin,amax,qdist
-  !do i = 1, grid%nLambda
-  !   write(*,*) grid%lamArray(i),sigmaAbs(i),sigmaSca(i)
-  !enddo
-
-  if (grid%cartesian) then
-
-     do i = 1, grid%nx
-        do j = 1, grid%ny
-           do k = 1, grid%nz
-
-
-              if (grid%inUse(i,j,k)) then
-                 grid%kappaAbs(i,j,k,1:grid%nLambda) = sigmaAbs  * grid%rho(i,j,k)
-                 grid%kappaSca(i,j,k,1:grid%nLambda) = sigmaSca  * grid%rho(i,j,k)
-              endif
-
-              !      write(*,*) grid%kappaAbs(i,j,k,1:grid%nLambda),grid%kappaSca(i,j,k,1:grid%nLambda), grid%rho(i,j,k),scale
-           enddo
-        enddo
-     enddo
-  else
-
-     do i = 1, grid%nr
-        do j = 1, grid%nmu
-           do k = 1, grid%nPhi
-
-              grid%kappaAbs(i,j,k,1:grid%nLambda) = sigmaAbs * grid%rho(i,j,k)
-              grid%kappaSca(i,j,k,1:grid%nLambda) = sigmaSca * grid%rho(i,j,k)
-
-           enddo
-        enddo
-     enddo
-
-  endif
-
-  where(grid%kappaAbs < 1.e-25) grid%kappaAbs = 1.e-25
[…]

### 2010-08-17 torus/formal_solutions.F90

@@ -1471,7 +1471,10 @@ contains
   ! Creates NDF image of flux map
   subroutine create_obs_flux_map(flux_ray, ray, dr, dphi, &
         nray, R_star, R_max, filename, npix)
-    use image_mod, only: IMAGETYPE, simply_writeimage, freeImage, initImage
+    use image_mod, only: IMAGETYPE, freeImage, initImage
+#ifdef USECFITSIO
+    use image_mod, only : writeFitsImage
+#endif
     implicit none
     integer, intent(in) :: nray  ! total number of rays
     real(double), intent(in) :: flux_ray(nray) ! Flux map  array dimension= nlam x #of integration points  
@@ -1488,6 +1491,8 @@ contains
     type(imagetype) ::  F_map  ! flux map   []
     integer :: i, j, ix, iy , k, nsize
     real :: x, y, flux, del, flux_min, offset
+    character(len=80) :: message
+    message = filename
 
     offset = 1.0e-4*R_star
     ! initializes the map
@@ -1526,7 +1531,10 @@ contains
     end do
 
     ! now save the image to a flie
-    call simply_writeImage(F_map, filename)
+
+#if USECFITSIO
+    call writeFitsImage(F_map, filename, 1.d0, "intensity")
+#endif
 
     ! clean up
     call freeImage(F_map)

### 2010-08-17 torus/image_mod.F90

@@ -272,143 +272,7 @@ module image_mod
      end subroutine freePVImage
 
 
-     subroutine writeImage(thisImage, filename, objectDistance, inArcsec, lambda_center, bandwidth)
-       
-       type(IMAGETYPE),intent(in) :: thisImage
-       character(len=*), intent(in) :: filename
-       real(double), intent(in) :: objectDistance ! in [cm]
-       logical, intent(in)      :: inArcsec       ! if T, the dimension of images are in arcsec
-       real(double), intent(in) :: lambda_center ! of the filter in [A]
-       real(double), intent(in) :: bandwidth     ! of the filter in [A]
-       !
-       real, allocatable :: piximageI(:,:)
-       real, allocatable :: piximageQ(:,:)
-       real, allocatable :: piximageU(:,:)
-       real, allocatable :: piximageV(:,:)
-       real, allocatable :: piximageVel(:,:)
-       real(double) :: area
-       real :: imScale
-       real :: physicalPixelSize
-       real :: angularPixelSize
-!       real :: pixelArea
-       real(double) :: scale, convert, c_in_m_per_sec
-
-       integer :: nPix, i, j !, nSize
-
-!       nSize = thisImage%nSize
-!       nPix = 2*thisImage%nSize + 1
-
-       npix = thisImage%nx ! assumes square image!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-       physicalPixelSize = 1.e10 * (thisImage%dx * thisImage%dy)
-       angularPixelSize = physicalPixelSize / objectDistance
-!       pixelArea = (angularPixelSize * radtoDeg * 3600.)**2 ! square arcsec
-
-       area = objectDistance**2
-
-       allocate(pixImageI(1:nPix,1:nPix))
-       allocate(pixImageQ(1:nPix,1:nPix))
-       allocate(pixImageU(1:nPix,1:nPix))
-       allocate(pixImageV(1:nPix,1:nPix))
-       allocate(pixImageVel(1:nPix,1:nPix))
-       pixImageVel = 0.
-
-
-       ! Note: stokes parameters are in erg/s/pix^2/sr, and we now converting 
-       ! them to Stokes Flux using a right conversion factor.
-
-       physicalPixelSize = thisImage%dx * 1.e10
-       angularPixelSize = physicalPixelSize / objectDistance
[…]

### 2010-08-17 torus/ion_mod.f90

@@ -10,6 +10,7 @@ module ion_mod
   use constants_mod
   use utils_mod
   use messages_mod
+  use phfit_mod, only : phfit2
 
   implicit none
 

### 2010-08-17 torus/kind_mod.f90

@@ -1,0 +1,20 @@
+module kind_mod
+  ! KIND parameters, specific to the individual system
+  ! double, octal and logic entries added by nhs
+
+  implicit none
+
+  integer, parameter :: single = kind(0.)
+  integer, parameter :: bigInt = kind(1000000000)
+  integer, parameter :: si = single
+  integer, parameter :: double = kind(0.d0)
+  integer, parameter :: db = double
+  integer, parameter :: quad = kind(0.d0)
+  integer, parameter :: qd = quad
+  integer, parameter :: oct = kind(0.d0)
+  integer, parameter :: oc = oct
+
+  integer, parameter :: logic = kind(.true.)
+  integer, parameter :: lg = logic
+
+end module kind_mod

### 2010-08-17 torus/modelatom_mod.f90

@@ -10,6 +10,7 @@ module modelatom_mod
   use stateq_mod, only:  expint
   use utils_mod, only: locate, sort
   use source_mod, only: SOURCETYPE
+  use phfit_mod, only : phfit2
 
   implicit none
 

### 2010-08-17 torus/phaseloop_mod.F90

@@ -18,7 +18,7 @@ subroutine do_phaseloop(grid, alreadyDoneInfall, meanDustParticleMass, rstar, ve
   use phasematrix_mod
   use disc_class
   use image_mod, only: IMAGETYPE, PVIMAGETYPE, initImage, initPVImage, addPhotonToImage, addphotontopvimage, &
-       createlucyimage, freeimage, freepvimage, smoothpvimage, writefalsecolourppm,  writeimage, writepvimage
+       createlucyimage, freeimage, freepvimage, smoothpvimage, writefalsecolourppm
 #ifdef USECFITSIO
   use image_mod, only : writeFitsImage
 #endif
@@ -2907,7 +2907,7 @@ enddo
            ! Check the the effectieve wavelength and the 
            ! bandwith of O6 image here later and replace 5000 and 1.0d0 below!
            !+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-           call writeImage(o6Image(1), specfile, objectDistance, imageInArcsec, 5000d0, 1.0d0)
+!           call writeImage(o6Image(1), specfile, objectDistance, imageInArcsec, 5000d0, 1.0d0)
         endif
         if (get_filter_set_name(filters) == "pn") then
            write(specFile,'(a,a,i3.3,a)') trim(outfile),"_image",iPhase,".ppm"
@@ -2922,7 +2922,6 @@ enddo
 
            call smoothPVimage(pvImage(iSlit), vfwhm/2.35, pfwhm/2.35)
 
-           call writePVimage(pvImage(iSlit), specfile, vSys)
         enddo
      endif
   end if ! (myRankIsZero)

### 2010-08-17 torus/phasematrix_mod.f90

@@ -577,9 +577,6 @@ contains
     if (useNdf) then
        write(message,*) "Writing spectrum to ",trim(outfile),".sdf"
        call writeInfo(message, TRIVIAL)
-       call wrtsp(nLambda,real(stokes_i),real(stokes_q),real(stokes_qv), &
-            real(stokes_u), &
-            real(stokes_uv),tmpXarray,outFile)
     else
        write(message,*) "Writing spectrum to ",trim(outfile),".dat"
        call writeInfo(message, TRIVIAL)

### 2010-08-17 torus/photoionAMR_mod.F90

@@ -21,6 +21,7 @@ use mpi_global_mod
 use unix_mod, only: unixGetenv
 use photon_mod
 use phasematrix_mod
+use phfit_mod, only : phfit2
 
 implicit none
 

### 2010-08-17 torus/photoion_mod.F90

@@ -14,6 +14,7 @@ use octal_mod, only: OCTAL, OCTALWRAPPER, subcellCentre, cellVolume
 use amr_mod, only: distanceToCellBoundary, randomPositionInCell, findsubcelllocal
 use source_mod, only: SOURCETYPE, sumSourceLuminosityMonochromatic
 use ion_mod, only: IONTYPE
+use phfit_mod, only : phfit2
 #ifdef MPI
 use mpi_global_mod, only : myrankGlobal
 #endif
